### 2021-12-01 JDR_3_Crosswalk.Rmd
Add files via upload

---
title             : "Job Demands-Resources model components through the lens of O*NET classifications"
shorttitle        : "O*NET JD-R"

author: 
  - name          : "Alicia Stachowski"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Menomenie, WI"
    email         : "stachowskia@uwstout.edu"
  - name          : "Renata Garcia Prieto Palacios Roji"
    affiliation   : "2"
  - name          : "John Kulas"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "University of Wisconsin - Stout"
  - id            : "2"
    institution   : "Montclair State University"

abstract: |
  O\*NET work characteristics were rated in terms of relevance, perception of demand, and perception as resource. All the results of this current study match the stress-appraisal stuff. Next steps: 1) discuss results within stress-appraisal framework (Lazarus & Bookman), 2) different literature on challenge and hindrance demands. Job Demands Resources theory that says resources and demands are relatively universal is NOT consistent with these findings. JDR neglects the other 2 literatures. Analytically pull O*Net descriptors that reflect universal demands/resources (e.g., autonomy) and see how much variability there is on those. Maybe forget about cross-walk thing. May actually want to start with this: https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit#gid=1041061499.

  We want to also group items by O\*NET categories so there's not so many (that makes ANOVAs more viable)

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "jdr.bib", "jobdemands_resources_bibtex.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

csl               : apa7.csl
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, echo=FALSE, warning=FALSE, message=FALSE)
```

In an attempt to integrate the O\*NET taxonomy within the orientation of the Job Demands-Resources  [@demerouti2001job; @bakker2003dual; @bakker2017job], a series of evaluations were made that used: 1) O\*NET terminology (both descriptor and response option), 2) JD-R influenced ratings of demand, challenge, or hindrance. The outcome of this integration is a cross-walk between the Department of Labor classifications and the I-O literature steeped JD-R. While O\*Net provides thorough documentation of information associated with job analyses, one of the remaining limitations is its lack of connection to theory. Given the popularity of the Job Demands-Resources Theory [JD-R; @demerouti2001job] in exploring questions related to everything from motivation to job design, we aim to explore the intersection between perceptions of job demands and resources, and the broad set of job characteristics provided on O\*Net. In an attempt to integrate the O\*Net taxonomy within the orientation of the JD-R framework [@demerouti2001job; @bakker2003dual; @bakker2017job], a series of evaluations were made that used: 1) direct O\*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance. Prior to a description of results, a brief overview of both the JD-R theory and O\*Net is provided.

## The Job demands-Resources Theory

The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model [@demerouti2001job]. One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands. *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; @demerouti2001job). 
Cognitively, the perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation [resulting from resources; @bakker2014job]. Pertinent to the current study, demanding job characteristics are frequently often associated with negative outcomes [e.g., @bakker2003dual], whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job].

## O\*Net Resource

Originally, the Advisory Panel for the Dictionary of Occupational Titles recommended a system that would “…promote the effective education, training, counseling, and employment of the American workforce. It should accomplish its purpose by providing a database system that identified, defines, classifies, and describes occupations in the economy in an accessible and flexible manner” (@advisory1993new, p. 6). The result was the now commonly used O\*NET. The Occupational Information Network (O\*NET; onetonline.org) contains a comprehensive description of occupations [@peterson2001understanding]. This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated. In fact, there was a call to work with experienced I/O psychologists over the summer to update the content for the [Industrial and Organizational Psychologist listing on O\*Net](https://www.onetonline.org/link/summary/19-3032.00). These data, and the tools provided for free on the website (e.g., Career Exploration Tools, “My Next Move for Veterans”, “My Next Move”, Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice, and also employers with information with which to craft job descriptions and help employees determine what skills are needed for promotion.

## Current Study

Interestingly, we have not yet integrated this practical and accessible resource within the JD-R framework. This paper aims to provide such a crosswalk or integration of the theory and practical occupations-focused data on O\*Net. Several broad research questions are examined across jobs:

>*Research Question 1*: Which O\*Net job characteristics are consistently rated as job resources?

>*Research Question 2*: Which O\*Net job characteristics are consistently rated as challenge demands?

>*Research Question 3*: Which O\*Net job characteristics are consistently rated as hinderance demands?

The other distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework. In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., [@bakker2013weekly]; [cavanaugh2000empirical]; [@gerich2017relevance]; [@podsakoff2007differential]; [@webster2011extending]).

Thus, a fourth question of interest explores just that possibility:

>*Research Question 4*: Which O\*Net job characteristics show wide variability in assigned JD-R classification of resource, challenge, or hinderance.

## ALTERNATIVELY, Alicia's JDR vs stress model predictions

Objective vs. Subjective Nature of Demands and Resources: The Role of Appraisal

  @searle2015merits note that the majority of the research on workplace demands is based on apriori classifications of demands. However, the stress experience, or process, described early on by @lazarus1984stress is grounded in the assumption that individual appraisals of stressors/demands vary. Their transactional theory or stress and coping states that people continuously appraise stimuli in their environments. An appraisal is the cognitive process whereby meaning is assigned to a stimulus. If a stimulus is appraised as a stressor (threat, challenge, potentially harmful), emotional distress leads to coping of some kind. This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes is not appraised as favorable [@lazarus1984stress]. The stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.

  We next consider the (limited) empirical evidence on this topic. First, some relatively recent research suggests that job demands and resources may not be universally appraised or assigned as such. Starting with job demands, @webster2011extending, for example, studied workload, role ambiguity, and role conflict demands, and found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hinderance to different degrees. While their study did include resources, it nonetheless points to individual difference on how people perceive stressors at work. Although part of a much larger study on retirement, @sonnega_comparison_2018 compared self-reported (subjective) ratings of degree of physical demand, stress, and need for intense concentration from the Health and Retirement Study with objective ratings from O*Net. Correlations physical demand (r = .52), stress (r = .10), and need for intense concentration (r = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than assumed. Next considering resources, @schmitz_interpreting_2019 captured subjective and objective resources in their study of retirement also. Correlations of composite variables for the resources of autonomy (r = .12), recognition of work (r = .07), decision freedom (r = .08), and advancement (r = -.01), while significant, certainly do not reflect high levels of overlap.

  We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees. @downes2021incorporating meta-analysis addresses this reality in depth, although it is beyond the scope of this project.

```{r study1}

temp <- read.csv("initial_data_screen.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script

x <- paste("item", sep="",1:404)
y <- t(temp[2,])
                                        ## decluttering Qualtrics excess
data <- temp[-c(1:3),]                                           ## Getting rid of all 3 weird Qualtrics rows
colnames(data) <- x

incomplete <- read.csv("inprogress.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script

data2 <- incomplete[-c(1:2),-c(10,12,16,113,199,285,371,379,400, 406:411)]

data3 <- as.data.frame(cbind(data2$V8,data2$V9,data2$V1,data2$V1,data2$V1,data2$V1,data2$V1,data2$V1,data2))

colnames(data3) <- x

rm(x, y, temp)

use <- rbind(data,data3)

## STILL NEED FILE WITH BAD RESPONDENTS IDENTIFIED (E.G., Item_18=2, na > 200, longstring > 20, CARELESS CHECKS > 1)

library(careless)
use$careless_long <- longstring(use[18:399])
use$missing <- rowSums(is.na(use[18:404]))

different <- use[ which(use$item18 == 2 | use$careless_long > 20 | use$missing > 200), ]

attention <- use[which(use$item61 == 5 & use$item145 == 5 & use$item248 == 2 & use$item308 == 3), ]

data <- data.frame(lapply(attention, function(x) as.numeric(as.character(x))))
data <- data[,c(1:404)]

numtot <- nrow(use)
numkicked <- nrow(different)
numvalid <- nrow(data)

```

```{r demos}

a <- descr::freq(use$item401, plot=FALSE)

use$item402[use$item402 == "Female " | use$item402 == "female" | use$item402 == "FEMALE" | use$item402 == "Woman" | use$item402 == "Mujer" | use$item402 == "feminine" | use$item402 == "fEMALE" | use$item402 == "F" | use$item402 == "Femenale" | use$item402 == "feminino" | use$item402 == "female " | use$item402 == "Fem" | use$item402 == "Feminine" | use$item402 == "feminine" | use$item402 == "WOMAN" | use$item402 == "Femal" | use$item402 == "femenine" | use$item402 == "Femenine" | use$item402 == "femenino" | use$item402 == "woman"]  <- "Female"

use$item402[use$item402 == "gerente" | use$item402 == "M" | use$item402 == "Make" | use$item402 == "Mal" | use$item402 == "male" | use$item402 == "MALE" | use$item402 == "male" | use$item402 == "Male" | use$item402 == "mals" | use$item402 == "man" | use$item402 == "masculine" | use$item402 == "Masculine" | use$item402 == "Man" | use$item402 == "mals " | use$item402 == "male " | use$item402 == "Male "]  <- "Male"

b <- descr::freq(use$item402, plot=FALSE)

##Job title
library(labourR)

#ESCO/ISCO classification using the labourR package
#ISCO = International Standard Classification of Occupations

attention$id <- 1:nrow(attention) #adds unique identifier to satisfy inane requirement of classify_occupation()

ISCO <- classify_occupation(attention, text_col = 'item400', isco_level = 1)

m3 <-merge(attention, ISCO, by.x = "id", by.y = "id", all.x = TRUE)

c <- descr::freq(m3$preferredLabel, plot=FALSE)

knowledge <- data[ which(m3$iscoGroup == "1" | m3$iscoGroup == "2"), ]
service <- data[ which(m3$iscoGroup == "3" | m3$iscoGroup == "4" | m3$iscoGroup == "5" | m3$iscoGroup == "6" | m3$iscoGroup == "7" | m3$iscoGroup == "8" | m3$iscoGroup == "9"), ]

data$item403[data$item403 == 2000]  <- 20

```

## Participants

Of the `r nrow(use)` Prolific panel individuals who initially accessed the survey link, `r nrow(different)` indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses [@R-careless]. Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of `r nrow(data)` respondents who constitute the current SIOP sample. `r round(a[1,3],2)`% had been in their referent job less than 6 months, `r round(a[2,3],1)`% between 6 months and a year, `r round(a[3,3],2)`% between one and five years, `r round(a[4,3],2)`% between 5 and 10 years, and `r round(a[5,3],2)`% more than 10 years.

Ages ranged from 18 to 65 with an average of `r round(mean(data[,403], na.rm=TRUE),2)` years old (SD = `r round(sd(data[,403], na.rm=TRUE),2)`). The survey offered a free-field gender identity category, although the sample predominantly self-identified as female (`r round(b[2,3],2)`%) or male (`r round(b[5,3],2)`%).

```{r generalrecodes}
## Qualtrics data all messed up

data$item82[data$item82 == 8]  <- 1
data$item82[data$item82 == 9]  <- 2
data$item82[data$item82 == 10] <- 3
data$item82[data$item82 == 11] <- 4
data$item82[data$item82 == 12] <- 5

data$item118[data$item118 == 9]  <- 1
data$item118[data$item118 == 10] <- 2
data$item118[data$item118 == 11] <- 3
data$item118[data$item118 == 12] <- 4
data$item118[data$item118 == 13] <- 5

data$item119[data$item119 == 11] <- 1
data$item119[data$item119 == 12] <- 2
data$item119[data$item119 == 13] <- 3
data$item119[data$item119 == 14] <- 4
data$item119[data$item119 == 15] <- 5

data$item120[data$item120 == 6]  <- 1
data$item120[data$item120 == 7]  <- 2
data$item120[data$item120 == 8]  <- 3
data$item120[data$item120 == 9]  <- 4
data$item120[data$item120 == 10] <- 5

data$item121[data$item121 == 6]  <- 1
data$item121[data$item121 == 7]  <- 2
data$item121[data$item121 == 8]  <- 3
data$item121[data$item121 == 9]  <- 4
data$item121[data$item121 == 10] <- 5

data$item122[data$item122 == 6]  <- 1
data$item122[data$item122 == 7]  <- 2
data$item122[data$item122 == 8]  <- 3
data$item122[data$item122 == 9]  <- 4
data$item122[data$item122 == 10] <- 5

data$item123[data$item123 == 6]  <- 1
data$item123[data$item123 == 7]  <- 2
data$item123[data$item123 == 8]  <- 3
data$item123[data$item123 == 9]  <- 4
data$item123[data$item123 == 10] <- 5

data$item124[data$item124 == 6]  <- 1
data$item124[data$item124 == 7]  <- 2
data$item124[data$item124 == 8]  <- 3
data$item124[data$item124 == 9]  <- 4
data$item124[data$item124 == 10] <- 5

data$item125[data$item125 == 6]  <- 1
data$item125[data$item125 == 7]  <- 2
data$item125[data$item125 == 8]  <- 3
data$item125[data$item125 == 9]  <- 4
data$item125[data$item125 == 10] <- 5

data$item126[data$item126 == 11]  <- 1
data$item126[data$item126 == 12]  <- 2
data$item126[data$item126 == 13]  <- 3
data$item126[data$item126 == 14]  <- 4
data$item126[data$item126 == 15]  <- 5

data$item127[data$item127 == 4]  <- 1
data$item127[data$item127 == 5]  <- 2
data$item127[data$item127 == 6]  <- 3
data$item127[data$item127 == 7]  <- 4
data$item127[data$item127 == 8]  <- 5

data$item128[data$item128 == 11]  <- 1
data$item128[data$item128 == 12]  <- 2
data$item128[data$item128 == 13]  <- 3
data$item128[data$item128 == 14]  <- 4
data$item128[data$item128 == 15]  <- 5

data$item129[data$item129 == 11]  <- 1
data$item129[data$item129 == 12]  <- 2
data$item129[data$item129 == 13]  <- 3
data$item129[data$item129 == 14]  <- 4
data$item129[data$item129 == 15]  <- 5

data$item130[data$item130 == 11]  <- 1
data$item130[data$item130 == 12]  <- 2
data$item130[data$item130 == 13]  <- 3
data$item130[data$item130 == 14]  <- 4
data$item130[data$item130 == 15]  <- 5

data$item131[data$item131 == 11]  <- 1
data$item131[data$item131 == 12]  <- 2
data$item131[data$item131 == 13]  <- 3
data$item131[data$item131 == 14]  <- 4
data$item131[data$item131 == 15]  <- 5

data$item132[data$item132 == 11]  <- 1
data$item132[data$item132 == 12]  <- 2
data$item132[data$item132 == 13]  <- 3
data$item132[data$item132 == 14]  <- 4
data$item132[data$item132 == 15]  <- 5

data$item133[data$item133 == 11]  <- 1
data$item133[data$item133 == 12]  <- 2
data$item133[data$item133 == 13]  <- 3
data$item133[data$item133 == 14]  <- 4
data$item133[data$item133 == 15]  <- 5

data$item134[data$item134 == 11]  <- 1
data$item134[data$item134 == 12]  <- 2
data$item134[data$item134 == 13]  <- 3
data$item134[data$item134 == 14]  <- 4
data$item134[data$item134 == 15]  <- 5

data$item135[data$item135 == 6]  <- 1
data$item135[data$item135 == 7]  <- 2
data$item135[data$item135 == 8]  <- 3
data$item135[data$item135 == 9]  <- 4
data$item135[data$item135 == 10] <- 5

data$item136[data$item136 == 6]  <- 1
data$item136[data$item136 == 7]  <- 2
data$item136[data$item136 == 8]  <- 3
data$item136[data$item136 == 9]  <- 4
data$item136[data$item136 == 10] <- 5

data$item137[data$item137 == 6]  <- 1
data$item137[data$item137 == 7]  <- 2
data$item137[data$item137 == 8]  <- 3
data$item137[data$item137 == 9]  <- 4
data$item137[data$item137 == 10] <- 5

data$item138[data$item138 == 16]  <- 1
data$item138[data$item138 == 17]  <- 2
data$item138[data$item138 == 18]  <- 3
data$item138[data$item138 == 19]  <- 4
data$item138[data$item138 == 20]  <- 5

data$item139[data$item139 == 6]  <- 1
data$item139[data$item139 == 7]  <- 2
data$item139[data$item139 == 8]  <- 3
data$item139[data$item139 == 9]  <- 4
data$item139[data$item139 == 10] <- 5

data$item140[data$item140 == 6]  <- 1
data$item140[data$item140 == 7]  <- 2
data$item140[data$item140 == 8]  <- 3
data$item140[data$item140 == 9]  <- 4
data$item140[data$item140 == 10] <- 5

data$item141[data$item141 == 6]  <- 1
data$item141[data$item141 == 7]  <- 2
data$item141[data$item141 == 8]  <- 3
data$item141[data$item141 == 9]  <- 4
data$item141[data$item141 == 10] <- 5

data$item142[data$item142 == 6]  <- 1
data$item142[data$item142 == 7]  <- 2
data$item142[data$item142 == 8]  <- 3
data$item142[data$item142 == 9]  <- 4
data$item142[data$item142 == 10] <- 5

data$item143[data$item143 == 6]  <- 1
data$item143[data$item143 == 7]  <- 2
data$item143[data$item143 == 8]  <- 3
data$item143[data$item143 == 9]  <- 4
data$item143[data$item143 == 10] <- 5

data$item144[data$item144 == 6]  <- 1
data$item144[data$item144 == 7]  <- 2
data$item144[data$item144 == 8]  <- 3
data$item144[data$item144 == 9]  <- 4
data$item144[data$item144 == 10] <- 5

## Attention check = 145

data$item146[data$item146 == 16]  <- 1
data$item146[data$item146 == 17]  <- 2
data$item146[data$item146 == 18]  <- 3
data$item146[data$item146 == 19]  <- 4
data$item146[data$item146 == 20]  <- 5

data$item147[data$item147 == 6]  <- 1
data$item147[data$item147 == 7]  <- 2
data$item147[data$item147 == 8]  <- 3
data$item147[data$item147 == 9]  <- 4
data$item147[data$item147 == 10] <- 5

data$item148[data$item148 == 6]  <- 1
data$item148[data$item148 == 7]  <- 2
data$item148[data$item148 == 8]  <- 3
data$item148[data$item148 == 9]  <- 4
data$item148[data$item148 == 10] <- 5

data$item149[data$item149 == 6]  <- 1
data$item149[data$item149 == 7]  <- 2
data$item149[data$item149 == 8]  <- 3
data$item149[data$item149 == 9]  <- 4
data$item149[data$item149 == 10] <- 5

data$item150[data$item150 == 11]  <- 1
data$item150[data$item150 == 12]  <- 2
data$item150[data$item150 == 13]  <- 3
data$item150[data$item150 == 14]  <- 4
data$item150[data$item150 == 15]  <- 5

data$item151[data$item151 == 11]  <- 1
data$item151[data$item151 == 12]  <- 2
data$item151[data$item151 == 13]  <- 3
data$item151[data$item151 == 14]  <- 4
data$item151[data$item151 == 15]  <- 5

data$item152[data$item152 == 11]  <- 1
data$item152[data$item152 == 12]  <- 2
data$item152[data$item152 == 13]  <- 3
data$item152[data$item152 == 14]  <- 4
data$item152[data$item152 == 15]  <- 5

data$item153[data$item153 == 11]  <- 1
data$item153[data$item153 == 12]  <- 2
data$item153[data$item153 == 13]  <- 3
data$item153[data$item153 == 14]  <- 4
data$item153[data$item153 == 15]  <- 5

data$item154[data$item154 == 11]  <- 1
data$item154[data$item154 == 12]  <- 2
data$item154[data$item154 == 13]  <- 3
data$item154[data$item154 == 14]  <- 4
data$item154[data$item154 == 15]  <- 5

data$item155[data$item155 == 11]  <- 1
data$item155[data$item155 == 12]  <- 2
data$item155[data$item155 == 13]  <- 3
data$item155[data$item155 == 14]  <- 4
data$item155[data$item155 == 15]  <- 5

data$item156[data$item156 == 11]  <- 1
data$item156[data$item156 == 12]  <- 2
data$item156[data$item156 == 13]  <- 3
data$item156[data$item156 == 14]  <- 4
data$item156[data$item156 == 15]  <- 5

data$item157[data$item157 == 11]  <- 1
data$item157[data$item157 == 12]  <- 2
data$item157[data$item157 == 13]  <- 3
data$item157[data$item157 == 14]  <- 4
data$item157[data$item157 == 15]  <- 5

data$item158[data$item158 == 6]  <- 1
data$item158[data$item158 == 7]  <- 2
data$item158[data$item158 == 8]  <- 3
data$item158[data$item158 == 9]  <- 4
data$item158[data$item158 == 10] <- 5

data$item159[data$item159 == 11]  <- 1
data$item159[data$item159 == 12]  <- 2
data$item159[data$item159 == 13]  <- 3
data$item159[data$item159 == 14]  <- 4
data$item159[data$item159 == 15]  <- 5

data$item160[data$item160 == 11]  <- 1
data$item160[data$item160 == 12]  <- 2
data$item160[data$item160 == 13]  <- 3
data$item160[data$item160 == 14]  <- 4
data$item160[data$item160 == 15]  <- 5

data$item161[data$item161 == 6]  <- 1
data$item161[data$item161 == 7]  <- 2
data$item161[data$item161 == 8]  <- 3
data$item161[data$item161 == 9]  <- 4
data$item161[data$item161 == 10] <- 5

data$item162[data$item162 == 11]  <- 1
data$item162[data$item162 == 12]  <- 2
data$item162[data$item162 == 13]  <- 3
data$item162[data$item162 == 14]  <- 4
data$item162[data$item162 == 15]  <- 5

data$item163[data$item163 == 11]  <- 1
data$item163[data$item163 == 12]  <- 2
data$item163[data$item163 == 13]  <- 3
data$item163[data$item163 == 14]  <- 4
data$item163[data$item163 == 15]  <- 5

data$item164[data$item164 == 11]  <- 1
data$item164[data$item164 == 12]  <- 2
data$item164[data$item164 == 13]  <- 3
data$item164[data$item164 == 14]  <- 4
data$item164[data$item164 == 15]  <- 5

data$item165[data$item165 == 11]  <- 1
data$item165[data$item165 == 12]  <- 2
data$item165[data$item165 == 13]  <- 3
data$item165[data$item165 == 14]  <- 4
data$item165[data$item165 == 15]  <- 5

data$item166[data$item166 == 11]  <- 1
data$item166[data$item166 == 12]  <- 2
data$item166[data$item166 == 13]  <- 3
data$item166[data$item166 == 14]  <- 4
data$item166[data$item166 == 15]  <- 5

data$item167[data$item167 == 18]  <- 1
data$item167[data$item167 == 19]  <- 2
data$item167[data$item167 == 20]  <- 3
data$item167[data$item167 == 21]  <- 4
data$item167[data$item167 == 22]  <- 5

data$item168[data$item168 == 11]  <- 1
data$item168[data$item168 == 12]  <- 2
data$item168[data$item168 == 13]  <- 3
data$item168[data$item168 == 14]  <- 4
data$item168[data$item168 == 15]  <- 5

data$item169[data$item169 == 11]  <- 1
data$item169[data$item169 == 12]  <- 2
data$item169[data$item169 == 13]  <- 3
data$item169[data$item169 == 14]  <- 4
data$item169[data$item169 == 15]  <- 5

data$item170[data$item170 == 11]  <- 1
data$item170[data$item170 == 12]  <- 2
data$item170[data$item170 == 13]  <- 3
data$item170[data$item170 == 14]  <- 4
data$item170[data$item170 == 15]  <- 5

data$item171[data$item171 == 11]  <- 1
data$item171[data$item171 == 12]  <- 2
data$item171[data$item171 == 13]  <- 3
data$item171[data$item171 == 14]  <- 4
data$item171[data$item171 == 15]  <- 5

data$item172[data$item172 == 11]  <- 1
data$item172[data$item172 == 12]  <- 2
data$item172[data$item172 == 13]  <- 3
data$item172[data$item172 == 14]  <- 4
data$item172[data$item172 == 15]  <- 5

data$item173[data$item173 == 11]  <- 1
data$item173[data$item173 == 12]  <- 2
data$item173[data$item173 == 13]  <- 3
data$item173[data$item173 == 14]  <- 4
data$item173[data$item173 == 15]  <- 5

data$item174[data$item174 == 11]  <- 1
data$item174[data$item174 == 12]  <- 2
data$item174[data$item174 == 13]  <- 3
data$item174[data$item174 == 14]  <- 4
data$item174[data$item174 == 15]  <- 5

data$item175[data$item175 == 11]  <- 1
data$item175[data$item175 == 12]  <- 2
data$item175[data$item175 == 13]  <- 3
data$item175[data$item175 == 14]  <- 4
data$item175[data$item175 == 15]  <- 5

data$item176[data$item176 == 11]  <- 1
data$item176[data$item176 == 12]  <- 2
data$item176[data$item176 == 13]  <- 3
data$item176[data$item176 == 14]  <- 4
data$item176[data$item176 == 15]  <- 5

data$item177[data$item177 == 11]  <- 1
data$item177[data$item177 == 12]  <- 2
data$item177[data$item177 == 13]  <- 3
data$item177[data$item177 == 14]  <- 4
data$item177[data$item177 == 15]  <- 5

data$item178[data$item178 == 11]  <- 1
data$item178[data$item178 == 12]  <- 2
data$item178[data$item178 == 13]  <- 3
data$item178[data$item178 == 14]  <- 4
data$item178[data$item178 == 15]  <- 5

data$item179[data$item179 == 11]  <- 1
data$item179[data$item179 == 12]  <- 2
data$item179[data$item179 == 13]  <- 3
data$item179[data$item179 == 14]  <- 4
data$item179[data$item179 == 15]  <- 5

data$item180[data$item180 == 11]  <- 1
data$item180[data$item180 == 12]  <- 2
data$item180[data$item180 == 13]  <- 3
data$item180[data$item180 == 14]  <- 4
data$item180[data$item180 == 15]  <- 5

data$item181[data$item181 == 11]  <- 1
data$item181[data$item181 == 12]  <- 2
data$item181[data$item181 == 13]  <- 3
data$item181[data$item181 == 14]  <- 4
data$item181[data$item181 == 15]  <- 5

data$item182[data$item182 == 11]  <- 1
data$item182[data$item182 == 12]  <- 2
data$item182[data$item182 == 13]  <- 3
data$item182[data$item182 == 14]  <- 4
data$item182[data$item182 == 15]  <- 5

data$item183[data$item183 == 11]  <- 1
data$item183[data$item183 == 12]  <- 2
data$item183[data$item183 == 13]  <- 3
data$item183[data$item183 == 14]  <- 4
data$item183[data$item183 == 15]  <- 5

data$item184[data$item184 == 21]  <- 1
data$item184[data$item184 == 22]  <- 2
data$item184[data$item184 == 23]  <- 3
data$item184[data$item184 == 24]  <- 4
data$item184[data$item184 == 25]  <- 5

data$item185[data$item185 == 11]  <- 1
data$item185[data$item185 == 12]  <- 2
data$item185[data$item185 == 13]  <- 3
data$item185[data$item185 == 14]  <- 4
data$item185[data$item185 == 15]  <- 5

data$item186[data$item186 == 11]  <- 1
data$item186[data$item186 == 12]  <- 2
data$item186[data$item186 == 13]  <- 3
data$item186[data$item186 == 14]  <- 4
data$item186[data$item186 == 15]  <- 5

data$item187[data$item187 == 11]  <- 1
data$item187[data$item187 == 12]  <- 2
data$item187[data$item187 == 13]  <- 3
data$item187[data$item187 == 14]  <- 4
data$item187[data$item187 == 15]  <- 5

data$item188[data$item188 == 11]  <- 1
data$item188[data$item188 == 12]  <- 2
data$item188[data$item188 == 13]  <- 3
data$item188[data$item188 == 14]  <- 4
data$item188[data$item188 == 15]  <- 5

data$item189[data$item189 == 11]  <- 1
data$item189[data$item189 == 12]  <- 2
data$item189[data$item189 == 13]  <- 3
data$item189[data$item189 == 14]  <- 4
data$item189[data$item189 == 15]  <- 5

data$item190[data$item190 == 11]  <- 1
data$item190[data$item190 == 12]  <- 2
data$item190[data$item190 == 13]  <- 3
data$item190[data$item190 == 14]  <- 4
data$item190[data$item190 == 15]  <- 5

data$item191[data$item191 == 11]  <- 1
data$item191[data$item191 == 12]  <- 2
data$item191[data$item191 == 13]  <- 3
data$item191[data$item191 == 14]  <- 4
data$item191[data$item191 == 15]  <- 5

data$item192[data$item192 == 11]  <- 1
data$item192[data$item192 == 12]  <- 2
data$item192[data$item192 == 13]  <- 3
data$item192[data$item192 == 14]  <- 4
data$item192[data$item192 == 15]  <- 5

data$item193[data$item193 == 11]  <- 1
data$item193[data$item193 == 12]  <- 2
data$item193[data$item193 == 13]  <- 3
data$item193[data$item193 == 14]  <- 4
data$item193[data$item193 == 15]  <- 5

data$item194[data$item194 == 11]  <- 1
data$item194[data$item194 == 12]  <- 2
data$item194[data$item194 == 13]  <- 3
data$item194[data$item194 == 14]  <- 4
data$item194[data$item194 == 15]  <- 5

data$item195[data$item195 == 11]  <- 1
data$item195[data$item195 == 12]  <- 2
data$item195[data$item195 == 13]  <- 3
data$item195[data$item195 == 14]  <- 4
data$item195[data$item195 == 15]  <- 5

data$item196[data$item196 == 11]  <- 1
data$item196[data$item196 == 12]  <- 2
data$item196[data$item196 == 13]  <- 3
data$item196[data$item196 == 14]  <- 4
data$item196[data$item196 == 15]  <- 5

data$item197[data$item197 == 11]  <- 1
data$item197[data$item197 == 12]  <- 2
data$item197[data$item197 == 13]  <- 3
data$item197[data$item197 == 14]  <- 4
data$item197[data$item197 == 15]  <- 5

data$item198[data$item198 == 11]  <- 1
data$item198[data$item198 == 12]  <- 2
data$item198[data$item198 == 13]  <- 3
data$item198[data$item198 == 14]  <- 4
data$item198[data$item198 == 15]  <- 5

data$item199[data$item199 == 11]  <- 1
data$item199[data$item199 == 12]  <- 2
data$item199[data$item199 == 13]  <- 3
data$item199[data$item199 == 14]  <- 4
data$item199[data$item199 == 15]  <- 5

data$item200[data$item200 == 11]  <- 1
data$item200[data$item200 == 12]  <- 2
data$item200[data$item200 == 13]  <- 3
data$item200[data$item200 == 14]  <- 4
data$item200[data$item200 == 15]  <- 5

data$item201[data$item201 == 11]  <- 1
data$item201[data$item201 == 12]  <- 2
data$item201[data$item201 == 13]  <- 3
data$item201[data$item201 == 14]  <- 4
data$item201[data$item201 == 15]  <- 5

data$item202[data$item202 == 11]  <- 1
data$item202[data$item202 == 12]  <- 2
data$item202[data$item202 == 13]  <- 3
data$item202[data$item202 == 14]  <- 4
data$item202[data$item202 == 15]  <- 5

data$item203[data$item203 == 9]   <- 1
data$item203[data$item203 == 10]  <- 2
data$item203[data$item203 == 11]  <- 3
data$item203[data$item203 == 12]  <- 4
data$item203[data$item203 == 13]  <- 5

data$item204[data$item204 == 11]  <- 1
data$item204[data$item204 == 12]  <- 2
data$item204[data$item204 == 13]  <- 3
data$item204[data$item204 == 14]  <- 4
data$item204[data$item204 == 15]  <- 5

data$item205[data$item205 == 6]  <- 1
data$item205[data$item205 == 7]  <- 2
data$item205[data$item205 == 8]  <- 3
data$item205[data$item205 == 9]  <- 4
data$item205[data$item205 == 10] <- 5

data$item206[data$item206 == 6]  <- 1
data$item206[data$item206 == 7]  <- 2
data$item206[data$item206 == 8]  <- 3
data$item206[data$item206 == 9]  <- 4
data$item206[data$item206 == 10] <- 5

data$item207[data$item207 == 6]  <- 1
data$item207[data$item207 == 7]  <- 2
data$item207[data$item207 == 8]  <- 3
data$item207[data$item207 == 9]  <- 4
data$item207[data$item207 == 10] <- 5

data$item208[data$item208 == 6]  <- 1
data$item208[data$item208 == 7]  <- 2
data$item208[data$item208 == 8]  <- 3
data$item208[data$item208 == 9]  <- 4
data$item208[data$item208 == 10] <- 5

data$item209[data$item209 == 6]  <- 1
data$item209[data$item209 == 7]  <- 2
data$item209[data$item209 == 8]  <- 3
data$item209[data$item209 == 9]  <- 4
data$item209[data$item209 == 10] <- 5

data$item210[data$item210 == 6]  <- 1
data$item210[data$item210 == 7]  <- 2
data$item210[data$item210 == 8]  <- 3
data$item210[data$item210 == 9]  <- 4
data$item210[data$item210 == 10] <- 5

data$item211[data$item211 == 11]  <- 1
data$item211[data$item211 == 12]  <- 2
data$item211[data$item211 == 13]  <- 3
data$item211[data$item211 == 14]  <- 4
data$item211[data$item211 == 15]  <- 5

data$item212[data$item212 == 4]  <- 1
data$item212[data$item212 == 5]  <- 2
data$item212[data$item212 == 6]  <- 3
data$item212[data$item212 == 7]  <- 4
data$item212[data$item212 == 8]  <- 5

data$item213[data$item213 == 11]  <- 1
data$item213[data$item213 == 12]  <- 2
data$item213[data$item213 == 13]  <- 3
data$item213[data$item213 == 14]  <- 4
data$item213[data$item213 == 15]  <- 5

data$item214[data$item214 == 11]  <- 1
data$item214[data$item214 == 12]  <- 2
data$item214[data$item214 == 13]  <- 3
data$item214[data$item214 == 14]  <- 4
data$item214[data$item214 == 15]  <- 5

data$item215[data$item215 == 11]  <- 1
data$item215[data$item215 == 12]  <- 2
data$item215[data$item215 == 13]  <- 3
data$item215[data$item215 == 14]  <- 4
data$item215[data$item215 == 15]  <- 5

data$item216[data$item216 == 11]  <- 1
data$item216[data$item216 == 12]  <- 2
data$item216[data$item216 == 13]  <- 3
data$item216[data$item216 == 14]  <- 4
data$item216[data$item216 == 15]  <- 5

data$item217[data$item217 == 11]  <- 1
data$item217[data$item217 == 12]  <- 2
data$item217[data$item217 == 13]  <- 3
data$item217[data$item217 == 14]  <- 4
data$item217[data$item217 == 15]  <- 5

data$item218[data$item218 == 11]  <- 1
data$item218[data$item218 == 12]  <- 2
data$item218[data$item218 == 13]  <- 3
data$item218[data$item218 == 14]  <- 4
data$item218[data$item218 == 15]  <- 5

data$item219[data$item219 == 11]  <- 1
data$item219[data$item219 == 12]  <- 2
data$item219[data$item219 == 13]  <- 3
data$item219[data$item219 == 14]  <- 4
data$item219[data$item219 == 15]  <- 5

data$item220[data$item220 == 6]  <- 1
data$item220[data$item220 == 7]  <- 2
data$item220[data$item220 == 8]  <- 3
data$item220[data$item220 == 9]  <- 4
data$item220[data$item220 == 10] <- 5

data$item221[data$item221 == 6]  <- 1
data$item221[data$item221 == 7]  <- 2
data$item221[data$item221 == 8]  <- 3
data$item221[data$item221 == 9]  <- 4
data$item221[data$item221 == 10] <- 5

data$item222[data$item222 == 6]  <- 1
data$item222[data$item222 == 7]  <- 2
data$item222[data$item222 == 8]  <- 3
data$item222[data$item222 == 9]  <- 4
data$item222[data$item222 == 10] <- 5

data$item223[data$item223 == 16] <- 1
data$item223[data$item223 == 17] <- 2
data$item223[data$item223 == 18] <- 3
data$item223[data$item223 == 19] <- 4
data$item223[data$item223 == 20] <- 5

data$item224[data$item224 == 6]  <- 1
data$item224[data$item224 == 7]  <- 2
data$item224[data$item224 == 8]  <- 3
data$item224[data$item224 == 9]  <- 4
data$item224[data$item224 == 10] <- 5

data$item225[data$item225 == 6]  <- 1
data$item225[data$item225 == 7]  <- 2
data$item225[data$item225 == 8]  <- 3
data$item225[data$item225 == 9]  <- 4
data$item225[data$item225 == 10] <- 5

data$item226[data$item226 == 6]  <- 1
data$item226[data$item226 == 7]  <- 2
data$item226[data$item226 == 8]  <- 3
data$item226[data$item226 == 9]  <- 4
data$item226[data$item226 == 10] <- 5

data$item227[data$item227 == 6]  <- 1
data$item227[data$item227 == 7]  <- 2
data$item227[data$item227 == 8]  <- 3
data$item227[data$item227 == 9]  <- 4
data$item227[data$item227 == 10] <- 5

data$item228[data$item228 == 6]  <- 1
data$item228[data$item228 == 7]  <- 2
data$item228[data$item228 == 8]  <- 3
data$item228[data$item228 == 9]  <- 4
data$item228[data$item228 == 10] <- 5

data$item229[data$item229 == 6]  <- 1
data$item229[data$item229 == 7]  <- 2
data$item229[data$item229 == 8]  <- 3
data$item229[data$item229 == 9]  <- 4
data$item229[data$item229 == 10] <- 5

data$item230[data$item230 == 16] <- 1
data$item230[data$item230 == 17] <- 2
data$item230[data$item230 == 18] <- 3
data$item230[data$item230 == 19] <- 4
data$item230[data$item230 == 20] <- 5

data$item231[data$item231 == 6]  <- 1
data$item231[data$item231 == 7]  <- 2
data$item231[data$item231 == 8]  <- 3
data$item231[data$item231 == 9]  <- 4
data$item231[data$item231 == 10] <- 5

data$item232[data$item232 == 6]  <- 1
data$item232[data$item232 == 7]  <- 2
data$item232[data$item232 == 8]  <- 3
data$item232[data$item232 == 9]  <- 4
data$item232[data$item232 == 10] <- 5

data$item233[data$item233 == 6]  <- 1
data$item233[data$item233 == 7]  <- 2
data$item233[data$item233 == 8]  <- 3
data$item233[data$item233 == 9]  <- 4
data$item233[data$item233 == 10] <- 5

data$item234[data$item234 == 11]  <- 1
data$item234[data$item234 == 12]  <- 2
data$item234[data$item234 == 13]  <- 3
data$item234[data$item234 == 14]  <- 4
data$item234[data$item234 == 15]  <- 5

data$item235[data$item235 == 11]  <- 1
data$item235[data$item235 == 12]  <- 2
data$item235[data$item235 == 13]  <- 3
data$item235[data$item235 == 14]  <- 4
data$item235[data$item235 == 15]  <- 5

data$item236[data$item236 == 11]  <- 1
data$item236[data$item236 == 12]  <- 2
data$item236[data$item236 == 13]  <- 3
data$item236[data$item236 == 14]  <- 4
data$item236[data$item236 == 15]  <- 5

data$item237[data$item237 == 11]  <- 1
data$item237[data$item237 == 12]  <- 2
data$item237[data$item237 == 13]  <- 3
data$item237[data$item237 == 14]  <- 4
data$item237[data$item237 == 15]  <- 5

data$item238[data$item238 == 11]  <- 1
data$item238[data$item238 == 12]  <- 2
data$item238[data$item238 == 13]  <- 3
data$item238[data$item238 == 14]  <- 4
data$item238[data$item238 == 15]  <- 5

data$item239[data$item239 == 11]  <- 1
data$item239[data$item239 == 12]  <- 2
data$item239[data$item239 == 13]  <- 3
data$item239[data$item239 == 14]  <- 4
data$item239[data$item239 == 15]  <- 5

data$item240[data$item240 == 11]  <- 1
data$item240[data$item240 == 12]  <- 2
data$item240[data$item240 == 13]  <- 3
data$item240[data$item240 == 14]  <- 4
data$item240[data$item240 == 15]  <- 5

data$item241[data$item241 == 11]  <- 1
data$item241[data$item241 == 12]  <- 2
data$item241[data$item241 == 13]  <- 3
data$item241[data$item241 == 14]  <- 4
data$item241[data$item241 == 15]  <- 5

data$item242[data$item242 == 6]  <- 1
data$item242[data$item242 == 7]  <- 2
data$item242[data$item242 == 8]  <- 3
data$item242[data$item242 == 9]  <- 4
data$item242[data$item242 == 10] <- 5

data$item243[data$item243 == 11]  <- 1
data$item243[data$item243 == 12]  <- 2
data$item243[data$item243 == 13]  <- 3
data$item243[data$item243 == 14]  <- 4
data$item243[data$item243 == 15]  <- 5

data$item244[data$item244 == 11]  <- 1
data$item244[data$item244 == 12]  <- 2
data$item244[data$item244 == 13]  <- 3
data$item244[data$item244 == 14]  <- 4
data$item244[data$item244 == 15]  <- 5

data$item245[data$item245 == 6]  <- 1
data$item245[data$item245 == 7]  <- 2
data$item245[data$item245 == 8]  <- 3
data$item245[data$item245 == 9]  <- 4
data$item245[data$item245 == 10] <- 5

data$item246[data$item246 == 11]  <- 1
data$item246[data$item246 == 12]  <- 2
data$item246[data$item246 == 13]  <- 3
data$item246[data$item246 == 14]  <- 4
data$item246[data$item246 == 15]  <- 5

data$item247[data$item247 == 11]  <- 1
data$item247[data$item247 == 12]  <- 2
data$item247[data$item247 == 13]  <- 3
data$item247[data$item247 == 14]  <- 4
data$item247[data$item247 == 15]  <- 5

## Attention check

data$item249[data$item249 == 11]  <- 1
data$item249[data$item249 == 12]  <- 2
data$item249[data$item249 == 13]  <- 3
data$item249[data$item249 == 14]  <- 4
data$item249[data$item249 == 15]  <- 5

data$item250[data$item250 == 11]  <- 1
data$item250[data$item250 == 12]  <- 2
data$item250[data$item250 == 13]  <- 3
data$item250[data$item250 == 14]  <- 4
data$item250[data$item250 == 15]  <- 5

data$item251[data$item251 == 11]  <- 1
data$item251[data$item251 == 12]  <- 2
data$item251[data$item251 == 13]  <- 3
data$item251[data$item251 == 14]  <- 4
data$item251[data$item251 == 15]  <- 5

data$item252[data$item252 == 18]  <- 1
data$item252[data$item252 == 19]  <- 2
data$item252[data$item252 == 20]  <- 3
data$item252[data$item252 == 21]  <- 4
data$item252[data$item252 == 22]  <- 5

data$item253[data$item253 == 11]  <- 1
data$item253[data$item253 == 12]  <- 2
data$item253[data$item253 == 13]  <- 3
data$item253[data$item253 == 14]  <- 4
data$item253[data$item253 == 15]  <- 5

data$item254[data$item254 == 11]  <- 1
data$item254[data$item254 == 12]  <- 2
data$item254[data$item254 == 13]  <- 3
data$item254[data$item254 == 14]  <- 4
data$item254[data$item254 == 15]  <- 5

data$item255[data$item255 == 11]  <- 1
data$item255[data$item255 == 12]  <- 2
data$item255[data$item255 == 13]  <- 3
data$item255[data$item255 == 14]  <- 4
data$item255[data$item255 == 15]  <- 5

data$item256[data$item256 == 11]  <- 1
data$item256[data$item256 == 12]  <- 2
data$item256[data$item256 == 13]  <- 3
data$item256[data$item256 == 14]  <- 4
data$item256[data$item256 == 15]  <- 5

data$item257[data$item257 == 11]  <- 1
data$item257[data$item257 == 12]  <- 2
data$item257[data$item257 == 13]  <- 3
data$item257[data$item257 == 14]  <- 4
data$item257[data$item257 == 15]  <- 5

data$item258[data$item258 == 11]  <- 1
data$item258[data$item258 == 12]  <- 2
data$item258[data$item258 == 13]  <- 3
data$item258[data$item258 == 14]  <- 4
data$item258[data$item258 == 15]  <- 5

data$item259[data$item259 == 11]  <- 1
data$item259[data$item259 == 12]  <- 2
data$item259[data$item259 == 13]  <- 3
data$item259[data$item259 == 14]  <- 4
data$item259[data$item259 == 15]  <- 5

data$item260[data$item260 == 11]  <- 1
data$item260[data$item260 == 12]  <- 2
data$item260[data$item260 == 13]  <- 3
data$item260[data$item260 == 14]  <- 4
data$item260[data$item260 == 15]  <- 5

data$item261[data$item261 == 11]  <- 1
data$item261[data$item261 == 12]  <- 2
data$item261[data$item261 == 13]  <- 3
data$item261[data$item261 == 14]  <- 4
data$item261[data$item261 == 15]  <- 5

data$item262[data$item262 == 11]  <- 1
data$item262[data$item262 == 12]  <- 2
data$item262[data$item262 == 13]  <- 3
data$item262[data$item262 == 14]  <- 4
data$item262[data$item262 == 15]  <- 5

data$item263[data$item263 == 11]  <- 1
data$item263[data$item263 == 12]  <- 2
data$item263[data$item263 == 13]  <- 3
data$item263[data$item263 == 14]  <- 4
data$item263[data$item263 == 15]  <- 5

data$item264[data$item264 == 11]  <- 1
data$item264[data$item264 == 12]  <- 2
data$item264[data$item264 == 13]  <- 3
data$item264[data$item264 == 14]  <- 4
data$item264[data$item264 == 15]  <- 5

data$item265[data$item265 == 11]  <- 1
data$item265[data$item265 == 12]  <- 2
data$item265[data$item265 == 13]  <- 3
data$item265[data$item265 == 14]  <- 4
data$item265[data$item265 == 15]  <- 5

data$item266[data$item266 == 11]  <- 1
data$item266[data$item266 == 12]  <- 2
data$item266[data$item266 == 13]  <- 3
data$item266[data$item266 == 14]  <- 4
data$item266[data$item266 == 15]  <- 5

data$item267[data$item267 == 11]  <- 1
data$item267[data$item267 == 12]  <- 2
data$item267[data$item267 == 13]  <- 3
data$item267[data$item267 == 14]  <- 4
data$item267[data$item267 == 15]  <- 5

data$item268[data$item268 == 11]  <- 1
data$item268[data$item268 == 12]  <- 2
data$item268[data$item268 == 13]  <- 3
data$item268[data$item268 == 14]  <- 4
data$item268[data$item268 == 15]  <- 5

data$item269[data$item269 == 21]  <- 1
data$item269[data$item269 == 22]  <- 2
data$item269[data$item269 == 23]  <- 3
data$item269[data$item269 == 24]  <- 4
data$item269[data$item269 == 25]  <- 5

data$item270[data$item270 == 11]  <- 1
data$item270[data$item270 == 12]  <- 2
data$item270[data$item270 == 13]  <- 3
data$item270[data$item270 == 14]  <- 4
data$item270[data$item270 == 15]  <- 5

data$item271[data$item271 == 11]  <- 1
data$item271[data$item271 == 12]  <- 2
data$item271[data$item271 == 13]  <- 3
data$item271[data$item271 == 14]  <- 4
data$item271[data$item271 == 15]  <- 5

data$item272[data$item272 == 11]  <- 1
data$item272[data$item272 == 12]  <- 2
data$item272[data$item272 == 13]  <- 3
data$item272[data$item272 == 14]  <- 4
data$item272[data$item272 == 15]  <- 5

data$item273[data$item273 == 11]  <- 1
data$item273[data$item273 == 12]  <- 2
data$item273[data$item273 == 13]  <- 3
data$item273[data$item273 == 14]  <- 4
data$item273[data$item273 == 15]  <- 5

data$item274[data$item274 == 11]  <- 1
data$item274[data$item274 == 12]  <- 2
data$item274[data$item274 == 13]  <- 3
data$item274[data$item274 == 14]  <- 4
data$item274[data$item274 == 15]  <- 5

data$item275[data$item275 == 11]  <- 1
data$item275[data$item275 == 12]  <- 2
data$item275[data$item275 == 13]  <- 3
data$item275[data$item275 == 14]  <- 4
data$item275[data$item275 == 15]  <- 5

data$item276[data$item276 == 11]  <- 1
data$item276[data$item276 == 12]  <- 2
data$item276[data$item276 == 13]  <- 3
data$item276[data$item276 == 14]  <- 4
data$item276[data$item276 == 15]  <- 5

data$item277[data$item277 == 11]  <- 1
data$item277[data$item277 == 12]  <- 2
data$item277[data$item277 == 13]  <- 3
data$item277[data$item277 == 14]  <- 4
data$item277[data$item277 == 15]  <- 5

data$item278[data$item278 == 11]  <- 1
data$item278[data$item278 == 12]  <- 2
data$item278[data$item278 == 13]  <- 3
data$item278[data$item278 == 14]  <- 4
data$item278[data$item278 == 15]  <- 5

data$item279[data$item279 == 11]  <- 1
data$item279[data$item279 == 12]  <- 2
data$item279[data$item279 == 13]  <- 3
data$item279[data$item279 == 14]  <- 4
data$item279[data$item279 == 15]  <- 5

data$item280[data$item280 == 11]  <- 1
data$item280[data$item280 == 12]  <- 2
data$item280[data$item280 == 13]  <- 3
data$item280[data$item280 == 14]  <- 4
data$item280[data$item280 == 15]  <- 5

data$item281[data$item281 == 11]  <- 1
data$item281[data$item281 == 12]  <- 2
data$item281[data$item281 == 13]  <- 3
data$item281[data$item281 == 14]  <- 4
data$item281[data$item281 == 15]  <- 5

data$item282[data$item282 == 11]  <- 1
data$item282[data$item282 == 12]  <- 2
data$item282[data$item282 == 13]  <- 3
data$item282[data$item282 == 14]  <- 4
data$item282[data$item282 == 15]  <- 5

data$item283[data$item283 == 11]  <- 1
data$item283[data$item283 == 12]  <- 2
data$item283[data$item283 == 13]  <- 3
data$item283[data$item283 == 14]  <- 4
data$item283[data$item283 == 15]  <- 5

data$item284[data$item284 == 11]  <- 1
data$item284[data$item284 == 12]  <- 2
data$item284[data$item284 == 13]  <- 3
data$item284[data$item284 == 14]  <- 4
data$item284[data$item284 == 15]  <- 5

data$item285[data$item285 == 11]  <- 1
data$item285[data$item285 == 12]  <- 2
data$item285[data$item285 == 13]  <- 3
data$item285[data$item285 == 14]  <- 4
data$item285[data$item285 == 15]  <- 5

data$item286[data$item286 == 11]  <- 1
data$item286[data$item286 == 12]  <- 2
data$item286[data$item286 == 13]  <- 3
data$item286[data$item286 == 14]  <- 4
data$item286[data$item286 == 15]  <- 5

data$item287[data$item287 == 11]  <- 1
data$item287[data$item287 == 12]  <- 2
data$item287[data$item287 == 13]  <- 3
data$item287[data$item287 == 14]  <- 4
data$item287[data$item287 == 15]  <- 5

data$item288[data$item288 == 9]   <- 1
data$item288[data$item288 == 10]  <- 2
data$item288[data$item288 == 11]  <- 3
data$item288[data$item288 == 12]  <- 4
data$item288[data$item288 == 13]  <- 5

data$item289[data$item289 == 11]  <- 1
data$item289[data$item289 == 12]  <- 2
data$item289[data$item289 == 13]  <- 3
data$item289[data$item289 == 14]  <- 4
data$item289[data$item289 == 15]  <- 5

data$item290[data$item290 == 6]  <- 1
data$item290[data$item290 == 7]  <- 2
data$item290[data$item290 == 8]  <- 3
data$item290[data$item290 == 9]  <- 4
data$item290[data$item290 == 10] <- 5

data$item291[data$item291 == 6]  <- 1
data$item291[data$item291 == 7]  <- 2
data$item291[data$item291 == 8]  <- 3
data$item291[data$item291 == 9]  <- 4
data$item291[data$item291 == 10] <- 5

data$item292[data$item292 == 6]  <- 1
data$item292[data$item292 == 7]  <- 2
data$item292[data$item292 == 8]  <- 3
data$item292[data$item292 == 9]  <- 4
data$item292[data$item292 == 10] <- 5

data$item293[data$item293 == 6]  <- 1
data$item293[data$item293 == 7]  <- 2
data$item293[data$item293 == 8]  <- 3
data$item293[data$item293 == 9]  <- 4
data$item293[data$item293 == 10] <- 5

data$item294[data$item294 == 6]  <- 1
data$item294[data$item294 == 7]  <- 2
data$item294[data$item294 == 8]  <- 3
data$item294[data$item294 == 9]  <- 4
data$item294[data$item294 == 10] <- 5

data$item295[data$item295 == 6]  <- 1
data$item295[data$item295 == 7]  <- 2
data$item295[data$item295 == 8]  <- 3
data$item295[data$item295 == 9]  <- 4
data$item295[data$item295 == 10] <- 5

data$item296[data$item296 == 11]  <- 1
data$item296[data$item296 == 12]  <- 2
data$item296[data$item296 == 13]  <- 3
data$item296[data$item296 == 14]  <- 4
data$item296[data$item296 == 15]  <- 5

data$item297[data$item297 == 4]  <- 1
data$item297[data$item297 == 5]  <- 2
data$item297[data$item297 == 6]  <- 3
data$item297[data$item297 == 7]  <- 4
data$item297[data$item297 == 8]  <- 5

data$item298[data$item298 == 11]  <- 1
data$item298[data$item298 == 12]  <- 2
data$item298[data$item298 == 13]  <- 3
data$item298[data$item298 == 14]  <- 4
data$item298[data$item298 == 15]  <- 5

data$item299[data$item299 == 11]  <- 1
data$item299[data$item299 == 12]  <- 2
data$item299[data$item299 == 13]  <- 3
data$item299[data$item299 == 14]  <- 4
data$item299[data$item299 == 15]  <- 5

data$item300[data$item300 == 11]  <- 1
data$item300[data$item300 == 12]  <- 2
data$item300[data$item300 == 13]  <- 3
data$item300[data$item300 == 14]  <- 4
data$item300[data$item300 == 15]  <- 5

data$item301[data$item301 == 11]  <- 1
data$item301[data$item301 == 12]  <- 2
data$item301[data$item301 == 13]  <- 3
data$item301[data$item301 == 14]  <- 4
data$item301[data$item301 == 15]  <- 5

data$item302[data$item302 == 11]  <- 1
data$item302[data$item302 == 12]  <- 2
data$item302[data$item302 == 13]  <- 3
data$item302[data$item302 == 14]  <- 4
data$item302[data$item302 == 15]  <- 5

data$item303[data$item303 == 11]  <- 1
data$item303[data$item303 == 12]  <- 2
data$item303[data$item303 == 13]  <- 3
data$item303[data$item303 == 14]  <- 4
data$item303[data$item303 == 15]  <- 5

data$item304[data$item304 == 11]  <- 1
data$item304[data$item304 == 12]  <- 2
data$item304[data$item304 == 13]  <- 3
data$item304[data$item304 == 14]  <- 4
data$item304[data$item304 == 15]  <- 5

data$item305[data$item305 == 6]  <- 1
data$item305[data$item305 == 7]  <- 2
data$item305[data$item305 == 8]  <- 3
data$item305[data$item305 == 9]  <- 4
data$item305[data$item305 == 10] <- 5

data$item306[data$item306 == 6]  <- 1
data$item306[data$item306 == 7]  <- 2
data$item306[data$item306 == 8]  <- 3
data$item306[data$item306 == 9]  <- 4
data$item306[data$item306 == 10] <- 5

data$item307[data$item307 == 6]  <- 1
data$item307[data$item307 == 7]  <- 2
data$item307[data$item307 == 8]  <- 3
data$item307[data$item307 == 9]  <- 4
data$item307[data$item307 == 10] <- 5

## Attention check

data$item309[data$item309 == 16]  <- 1
data$item309[data$item309 == 17]  <- 2
data$item309[data$item309 == 18]  <- 3
data$item309[data$item309 == 19]  <- 4
data$item309[data$item309 == 20]  <- 5

data$item310[data$item310 == 6]  <- 1
data$item310[data$item310 == 7]  <- 2
data$item310[data$item310 == 8]  <- 3
data$item310[data$item310 == 9]  <- 4
data$item310[data$item310 == 10] <- 5

data$item311[data$item311 == 6]  <- 1
data$item311[data$item311 == 7]  <- 2
data$item311[data$item311 == 8]  <- 3
data$item311[data$item311 == 9]  <- 4
data$item311[data$item311 == 10] <- 5

data$item312[data$item312 == 6]  <- 1
data$item312[data$item312 == 7]  <- 2
data$item312[data$item312 == 8]  <- 3
data$item312[data$item312 == 9]  <- 4
data$item312[data$item312 == 10] <- 5

data$item313[data$item313 == 6]  <- 1
data$item313[data$item313 == 7]  <- 2
data$item313[data$item313 == 8]  <- 3
data$item313[data$item313 == 9]  <- 4
data$item313[data$item313 == 10] <- 5

data$item314[data$item314 == 6]  <- 1
data$item314[data$item314 == 7]  <- 2
data$item314[data$item314 == 8]  <- 3
data$item314[data$item314 == 9]  <- 4
data$item314[data$item314 == 10] <- 5

data$item315[data$item315 == 6]  <- 1
data$item315[data$item315 == 7]  <- 2
data$item315[data$item315 == 8]  <- 3
data$item315[data$item315 == 9]  <- 4
data$item315[data$item315 == 10] <- 5

data$item316[data$item316 == 16]  <- 1
data$item316[data$item316 == 17]  <- 2
data$item316[data$item316 == 18]  <- 3
data$item316[data$item316 == 19]  <- 4
data$item316[data$item316 == 20]  <- 5

data$item317[data$item317 == 6]  <- 1
data$item317[data$item317 == 7]  <- 2
data$item317[data$item317 == 8]  <- 3
data$item317[data$item317 == 9]  <- 4
data$item317[data$item317 == 10] <- 5

data$item318[data$item318 == 6]  <- 1
data$item318[data$item318 == 7]  <- 2
data$item318[data$item318 == 8]  <- 3
data$item318[data$item318 == 9]  <- 4
data$item318[data$item318 == 10] <- 5

data$item319[data$item319 == 6]  <- 1
data$item319[data$item319 == 7]  <- 2
data$item319[data$item319 == 8]  <- 3
data$item319[data$item319 == 9]  <- 4
data$item319[data$item319 == 10] <- 5

data$item320[data$item320 == 11] <- 1
data$item320[data$item320 == 12] <- 2
data$item320[data$item320 == 13] <- 3
data$item320[data$item320 == 14] <- 4
data$item320[data$item320 == 15] <- 5

data$item321[data$item321 == 11] <- 1
data$item321[data$item321 == 12] <- 2
data$item321[data$item321 == 13] <- 3
data$item321[data$item321 == 14] <- 4
data$item321[data$item321 == 15] <- 5

data$item322[data$item322 == 11] <- 1
data$item322[data$item322 == 12] <- 2
data$item322[data$item322 == 13] <- 3
data$item322[data$item322 == 14] <- 4
data$item322[data$item322 == 15] <- 5

data$item323[data$item323 == 11] <- 1
data$item323[data$item323 == 12] <- 2
data$item323[data$item323 == 13] <- 3
data$item323[data$item323 == 14] <- 4
data$item323[data$item323 == 15] <- 5

data$item324[data$item324 == 11] <- 1
data$item324[data$item324 == 12] <- 2
data$item324[data$item324 == 13] <- 3
data$item324[data$item324 == 14] <- 4
data$item324[data$item324 == 15] <- 5

data$item325[data$item325 == 11] <- 1
data$item325[data$item325 == 12] <- 2
data$item325[data$item325 == 13] <- 3
data$item325[data$item325 == 14] <- 4
data$item325[data$item325 == 15] <- 5

data$item326[data$item326 == 11] <- 1
data$item326[data$item326 == 12] <- 2
data$item326[data$item326 == 13] <- 3
data$item326[data$item326 == 14] <- 4
data$item326[data$item326 == 15] <- 5

data$item327[data$item327 == 11] <- 1
data$item327[data$item327 == 12] <- 2
data$item327[data$item327 == 13] <- 3
data$item327[data$item327 == 14] <- 4
data$item327[data$item327 == 15] <- 5

data$item328[data$item328 == 6]  <- 1
data$item328[data$item328 == 7]  <- 2
data$item328[data$item328 == 8]  <- 3
data$item328[data$item328 == 9]  <- 4
data$item328[data$item328 == 10] <- 5

data$item329[data$item329 == 11] <- 1
data$item329[data$item329 == 12] <- 2
data$item329[data$item329 == 13] <- 3
data$item329[data$item329 == 14] <- 4
data$item329[data$item329 == 15] <- 5

data$item330[data$item330 == 11] <- 1
data$item330[data$item330 == 12] <- 2
data$item330[data$item330 == 13] <- 3
data$item330[data$item330 == 14] <- 4
data$item330[data$item330 == 15] <- 5

data$item331[data$item331 == 6]  <- 1
data$item331[data$item331 == 7]  <- 2
data$item331[data$item331 == 8]  <- 3
data$item331[data$item331 == 9]  <- 4
data$item331[data$item331 == 10] <- 5

data$item332[data$item332 == 11] <- 1
data$item332[data$item332 == 12] <- 2
data$item332[data$item332 == 13] <- 3
data$item332[data$item332 == 14] <- 4
data$item332[data$item332 == 15] <- 5

data$item333[data$item333 == 11] <- 1
data$item333[data$item333 == 12] <- 2
data$item333[data$item333 == 13] <- 3
data$item333[data$item333 == 14] <- 4
data$item333[data$item333 == 15] <- 5

data$item334[data$item334 == 11] <- 1
data$item334[data$item334 == 12] <- 2
data$item334[data$item334 == 13] <- 3
data$item334[data$item334 == 14] <- 4
data$item334[data$item334 == 15] <- 5

data$item335[data$item335 == 11] <- 1
data$item335[data$item335 == 12] <- 2
data$item335[data$item335 == 13] <- 3
data$item335[data$item335 == 14] <- 4
data$item335[data$item335 == 15] <- 5

data$item336[data$item336 == 11] <- 1
data$item336[data$item336 == 12] <- 2
data$item336[data$item336 == 13] <- 3
data$item336[data$item336 == 14] <- 4
data$item336[data$item336 == 15] <- 5

data$item337[data$item337 == 18] <- 1
data$item337[data$item337 == 19] <- 2
data$item337[data$item337 == 20] <- 3
data$item337[data$item337 == 21] <- 4
data$item337[data$item337 == 22] <- 5

data$item338[data$item338 == 11] <- 1
data$item338[data$item338 == 12] <- 2
data$item338[data$item338 == 13] <- 3
data$item338[data$item338 == 14] <- 4
data$item338[data$item338 == 15] <- 5

data$item339[data$item339 == 11] <- 1
data$item339[data$item339 == 12] <- 2
data$item339[data$item339 == 13] <- 3
data$item339[data$item339 == 14] <- 4
data$item339[data$item339 == 15] <- 5

data$item340[data$item340 == 11] <- 1
data$item340[data$item340 == 12] <- 2
data$item340[data$item340 == 13] <- 3
data$item340[data$item340 == 14] <- 4
data$item340[data$item340 == 15] <- 5

data$item341[data$item341 == 11] <- 1
data$item341[data$item341 == 12] <- 2
data$item341[data$item341 == 13] <- 3
data$item341[data$item341 == 14] <- 4
data$item341[data$item341 == 15] <- 5

data$item342[data$item342 == 11] <- 1
data$item342[data$item342 == 12] <- 2
data$item342[data$item342 == 13] <- 3
data$item342[data$item342 == 14] <- 4
data$item342[data$item342 == 15] <- 5

data$item343[data$item343 == 11] <- 1
data$item343[data$item343 == 12] <- 2
data$item343[data$item343 == 13] <- 3
data$item343[data$item343 == 14] <- 4
data$item343[data$item343 == 15] <- 5

data$item344[data$item344 == 11] <- 1
data$item344[data$item344 == 12] <- 2
data$item344[data$item344 == 13] <- 3
data$item344[data$item344 == 14] <- 4
data$item344[data$item344 == 15] <- 5

data$item345[data$item345 == 11] <- 1
data$item345[data$item345 == 12] <- 2
data$item345[data$item345 == 13] <- 3
data$item345[data$item345 == 14] <- 4
data$item345[data$item345 == 15] <- 5

data$item346[data$item346 == 11] <- 1
data$item346[data$item346 == 12] <- 2
data$item346[data$item346 == 13] <- 3
data$item346[data$item346 == 14] <- 4
data$item346[data$item346 == 15] <- 5

data$item347[data$item347 == 11] <- 1
data$item347[data$item347 == 12] <- 2
data$item347[data$item347 == 13] <- 3
data$item347[data$item347 == 14] <- 4
data$item347[data$item347 == 15] <- 5

data$item348[data$item348 == 11] <- 1
data$item348[data$item348 == 12] <- 2
data$item348[data$item348 == 13] <- 3
data$item348[data$item348 == 14] <- 4
data$item348[data$item348 == 15] <- 5

data$item349[data$item349 == 11] <- 1
data$item349[data$item349 == 12] <- 2
data$item349[data$item349 == 13] <- 3
data$item349[data$item349 == 14] <- 4
data$item349[data$item349 == 15] <- 5

data$item350[data$item350 == 11] <- 1
data$item350[data$item350 == 12] <- 2
data$item350[data$item350 == 13] <- 3
data$item350[data$item350 == 14] <- 4
data$item350[data$item350 == 15] <- 5

data$item351[data$item351 == 11] <- 1
data$item351[data$item351 == 12] <- 2
data$item351[data$item351 == 13] <- 3
data$item351[data$item351 == 14] <- 4
data$item351[data$item351 == 15] <- 5

data$item352[data$item352 == 11] <- 1
data$item352[data$item352 == 12] <- 2
data$item352[data$item352 == 13] <- 3
data$item352[data$item352 == 14] <- 4
data$item352[data$item352 == 15] <- 5

data$item353[data$item353 == 11] <- 1
data$item353[data$item353 == 12] <- 2
data$item353[data$item353 == 13] <- 3
data$item353[data$item353 == 14] <- 4
data$item353[data$item353 == 15] <- 5

data$item354[data$item354 == 21] <- 1
data$item354[data$item354 == 22] <- 2
data$item354[data$item354 == 23] <- 3
data$item354[data$item354 == 24] <- 4
data$item354[data$item354 == 25] <- 5

data$item355[data$item355 == 11] <- 1
data$item355[data$item355 == 12] <- 2
data$item355[data$item355 == 13] <- 3
data$item355[data$item355 == 14] <- 4
data$item355[data$item355 == 15] <- 5

data$item356[data$item356 == 11] <- 1
data$item356[data$item356 == 12] <- 2
data$item356[data$item356 == 13] <- 3
data$item356[data$item356 == 14] <- 4
data$item356[data$item356 == 15] <- 5

data$item357[data$item357 == 11] <- 1
data$item357[data$item357 == 12] <- 2
data$item357[data$item357 == 13] <- 3
data$item357[data$item357 == 14] <- 4
data$item357[data$item357 == 15] <- 5

data$item358[data$item358 == 11] <- 1
data$item358[data$item358 == 12] <- 2
data$item358[data$item358 == 13] <- 3
data$item358[data$item358 == 14] <- 4
data$item358[data$item358 == 15] <- 5

data$item359[data$item359 == 11] <- 1
data$item359[data$item359 == 12] <- 2
data$item359[data$item359 == 13] <- 3
data$item359[data$item359 == 14] <- 4
data$item359[data$item359 == 15] <- 5

data$item360[data$item360 == 11] <- 1
data$item360[data$item360 == 12] <- 2
data$item360[data$item360 == 13] <- 3
data$item360[data$item360 == 14] <- 4
data$item360[data$item360 == 15] <- 5

data$item361[data$item361 == 11] <- 1
data$item361[data$item361 == 12] <- 2
data$item361[data$item361 == 13] <- 3
data$item361[data$item361 == 14] <- 4
data$item361[data$item361 == 15] <- 5

data$item362[data$item362 == 11] <- 1
data$item362[data$item362 == 12] <- 2
data$item362[data$item362 == 13] <- 3
data$item362[data$item362 == 14] <- 4
data$item362[data$item362 == 15] <- 5

data$item363[data$item363 == 11] <- 1
data$item363[data$item363 == 12] <- 2
data$item363[data$item363 == 13] <- 3
data$item363[data$item363 == 14] <- 4
data$item363[data$item363 == 15] <- 5

data$item364[data$item364 == 11] <- 1
data$item364[data$item364 == 12] <- 2
data$item364[data$item364 == 13] <- 3
data$item364[data$item364 == 14] <- 4
data$item364[data$item364 == 15] <- 5

data$item365[data$item365 == 11] <- 1
data$item365[data$item365 == 12] <- 2
data$item365[data$item365 == 13] <- 3
data$item365[data$item365 == 14] <- 4
data$item365[data$item365 == 15] <- 5

data$item366[data$item366 == 11] <- 1
data$item366[data$item366 == 12] <- 2
data$item366[data$item366 == 13] <- 3
data$item366[data$item366 == 14] <- 4
data$item366[data$item366 == 15] <- 5

data$item367[data$item367 == 11] <- 1
data$item367[data$item367 == 12] <- 2
data$item367[data$item367 == 13] <- 3
data$item367[data$item367 == 14] <- 4
data$item367[data$item367 == 15] <- 5

data$item368[data$item368 == 11] <- 1
data$item368[data$item368 == 12] <- 2
data$item368[data$item368 == 13] <- 3
data$item368[data$item368 == 14] <- 4
data$item368[data$item368 == 15] <- 5

data$item369[data$item369 == 11] <- 1
data$item369[data$item369 == 12] <- 2
data$item369[data$item369 == 13] <- 3
data$item369[data$item369 == 14] <- 4
data$item369[data$item369 == 15] <- 5

data$item370[data$item370 == 11] <- 1
data$item370[data$item370 == 12] <- 2
data$item370[data$item370 == 13] <- 3
data$item370[data$item370 == 14] <- 4
data$item370[data$item370 == 15] <- 5

data$item371[data$item371 == 11] <- 1
data$item371[data$item371 == 12] <- 2
data$item371[data$item371 == 13] <- 3
data$item371[data$item371 == 14] <- 4
data$item371[data$item371 == 15] <- 5

data$item372[data$item372 == 11] <- 1
data$item372[data$item372 == 12] <- 2
data$item372[data$item372 == 13] <- 3
data$item372[data$item372 == 14] <- 4
data$item372[data$item372 == 15] <- 5

write.csv(psych::describe(data[18:372]), "checkingrecodes.csv")

```

## Materials

```{r interrater}
interrater <- read.csv("interrater.csv")

library(irr)

kappa <- kappam.fleiss(interrater)
```

Each free-field job title was placed into one of 14 possible O\*NET job families classifications. 60 of these ratings were performed by all 3 author raters, with a resulting Kappa of `r round(kappa$value,2)` [@landis1977measurement].

### Characteristics, Demands, and Resources

We used 98 statements taken from O\*NET ["activity" and "context" classifications](https://www.O\*NETonline.org/find/descriptor/result/4.A.1.b.3). We retained 41 "work activity" classifications which O\*NET groups into categories of "Information Input" (5 statements), "Interacting with Others" (17 statements), "Mental Processes" (10 statements) and "Work Output" (9 statements). 57 "work context" statements grouped into "Interpersonal Relationships" (14 statements), "Physical Work Conditions" (30 statements), and "Structural Job Characteristics" (13 statements).

These "descriptors" often have unique response categories ([see here for example](https://www.O\*NETonline.org/find/descriptor/result/4.C.1.c.2)). We retained the O\*NET wording to capture characteristics of relevance for each respondent. Subsequent to these self evaluations, each respondent who agreed that the element had *at least some relevance* to their job was also asked to rate that element in terms of, 1) ...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) ...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) ...this aspect of your job is a hinderance that can inhibit personal growth, learning, and work goal attainment.

# Results

## Low Variability Demands and Resources

The below graphs present the resources, challenges, and hindrances that are *largely agreed on* as indexed by (relatively) low standard deviations.

> Note. The "zero" standard deviations are likely one person, *n*'s should also go on these graphs if they're retained.

```{r resourceslowsd}

labels <- read.csv("truncatedlabels.csv")

resource <- as.data.frame(t(data[118:202]))

resource$description <- labels[c(118:202),1]
resource$mean <- round(rowMeans(resource[1:nrow(data)], na.rm=TRUE),2)
resource$sd   <- round(apply(resource[1:nrow(data)], 1, sd, na.rm=TRUE),2)

resource <- resource[,-145]   ## attention check
#resource <- resource[ which(resource$sd > 0), ]

sortresource <- resource[order(resource$sd),]

topresource <- head(sortresource, 10)

topresource <- topresource[tail(names(topresource),3)]

library(ggplot2)

ggplot(topresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Agreed Upon as a Resource") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))

```

```{r challengesagree}

labels <- read.csv("truncatedlabels.csv")

challenge <- as.data.frame(t(data[288:372]))

challenge$description <- labels[c(288:372),1]
challenge$mean <- round(rowMeans(challenge[1:nrow(data)], na.rm=TRUE),2)
challenge$sd   <- round(apply(challenge[1:nrow(data)], 1, sd, na.rm=TRUE),2)

challenge <- challenge[,-308]   ## attention check
#challenge <- challenge[ which(challenge$sd > 0), ]

sortchallenge <- challenge[order(challenge$sd),]

topchallenge <- head(sortchallenge, 10)

topchallenge <- topchallenge[tail(names(topchallenge),3)]

library(ggplot2)

ggplot(topchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Agreed Upon as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))

```

```{r hindrancesagree}

labels <- read.csv("truncatedlabels.csv")

hindrance <- as.data.frame(t(data[203:287]))

hindrance$description <- labels[c(203:287),1]
hindrance$mean <- round(rowMeans(hindrance[1:nrow(data)], na.rm=TRUE),2)
hindrance$sd   <- round(apply(hindrance[1:nrow(data)], 1, sd, na.rm=TRUE),2)

hindrance <- hindrance[,-248]   ## attention check
#hindrance <- hindrance[ which(hindrance$sd > 0), ]

sorthindrance <- hindrance[order(hindrance$sd),]

tophindrance <- head(sorthindrance, 10)

tophindrance <- tophindrance[tail(names(tophindrance),3)]

library(ggplot2)

ggplot(tophindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Agreed upon as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))

```

As can be seen by the graphs, there is considerable disagreement regarding the degree to which job elements are considered *hindrances*, with the 10 elements showing the greatest agreement still ranging in standard deviations from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`. What is widely seen as a resource and challenge tends to be more universally agreed upon (range of lowest 10 resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 10 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`.

## High Variability Demands and Resources

The below graphs present the resources, challenges, and hindrances that are *largely disagreed on* as indexed by (relatively) high standard deviations (these are the 10 characteristics with the greatest variability in rating).

```{r resourceshisd}

labels <- read.csv("truncatedlabels.csv")

resource <- as.data.frame(t(data[118:202]))

resource$description <- labels[c(118:202),1]
resource$mean <- round(rowMeans(resource[1:nrow(data)], na.rm=TRUE),2)
resource$sd   <- round(apply(resource[1:nrow(data)], 1, sd, na.rm=TRUE),2)

resource <- resource[,-145]   ## attention check
resource <- resource[ which(resource$sd > 0), ]

sortresource <- resource[order(-resource$sd),]

topresource <- head(sortresource, 10)

topresource <- topresource[tail(names(topresource),3)]

library(ggplot2)

ggplot(topresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed Upon as a Resource") + 
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))

```

```{r challengeshighsd}

labels <- read.csv("truncatedlabels.csv")

challenge <- as.data.frame(t(data[288:372]))

challenge$description <- labels[c(288:372),1]
challenge$mean <- round(rowMeans(challenge[1:nrow(data)], na.rm=TRUE),2)
challenge$sd   <- round(apply(challenge[1:nrow(data)], 1, sd, na.rm=TRUE),2)

challenge <- challenge[,-308]   ## attention check
challenge <- challenge[ which(challenge$sd > 0), ]

sortchallenge <- challenge[order(-challenge$sd),]

topchallenge <- head(sortchallenge, 10)

topchallenge <- topchallenge[tail(names(topchallenge),3)]

library(ggplot2)

ggplot(topchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed Upon as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))

```

```{r hindranceshighsd}

labels <- read.csv("truncatedlabels.csv")

hindrance <- as.data.frame(t(data[203:287]))

hindrance$description <- labels[c(203:287),1]
hindrance$mean <- round(rowMeans(hindrance[1:nrow(data)], na.rm=TRUE),2)
hindrance$sd   <- round(apply(hindrance[1:nrow(data)], 1, sd, na.rm=TRUE),2)

hindrance <- hindrance[,-248]   ## attention check
hindrance <- hindrance[ which(hindrance$sd > 0), ]

sorthindrance <- hindrance[order(-hindrance$sd),]

tophindrance <- head(sorthindrance, 10)

tophindrance <- tophindrance[tail(names(tophindrance),3)]

library(ggplot2)

ggplot(tophindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed upon as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))

```

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2021-12-01 jobcats.R

@@ -1,0 +1,58 @@
+## Job classifications
+
+data <- read.csv("C:\\Users\\kulasj\\Downloads\\workers.csv")
+
+library(ggplot2)
+
+ggplot(data, aes(O.Net.Job.Family.Categories))+
+  geom_histogram(stat="count") + coord_flip()
+
+
+## Combining categories
+
+data$O.Net.Job.Family.Categories[data$O.Net.Job.Family.Categories == "Transportation and Material Moving"] <- "Physical Labor"
+data$O.Net.Job.Family.Categories[data$O.Net.Job.Family.Categories == "Protective Service"] <- "Physical Labor"
+data$O.Net.Job.Family.Categories[data$O.Net.Job.Family.Categories == "Production"] <- "Physical Labor"
+data$O.Net.Job.Family.Categories[data$O.Net.Job.Family.Categories == "Personal Care and Service"] <- "Physical Labor"
+data$O.Net.Job.Family.Categories[data$O.Net.Job.Family.Categories == "Installation Maintenance and Repair"] <- "Physical Labor"
+data$O.Net.Job.Family.Categories[data$O.Net.Job.Family.Categories == "Food Preparation and Serving Related"] <- "Physical Labor"
+data$O.Net.Job.Family.Categories[data$O.Net.Job.Family.Categories == "Farming Fishing and Forestry"] <- "Physical Labor"
+data$O.Net.Job.Family.Categories[data$O.Net.Job.Family.Categories == "Construction and Extraction"] <- "Physical Labor"
+data$O.Net.Job.Family.Categories[data$O.Net.Job.Family.Categories == "Building and Grounds Cleaning and Maintenance"] <- "Physical Labor"
+
+## with Alicia 12/1
+data$O.Net.Job.Family.Categories[data$O.Net.Job.Family.Categories == "Architecture and Engineering"] <- "Computer & Engineering"
+data$O.Net.Job.Family.Categories[data$O.Net.Job.Family.Categories == "Computer and Mathematical"] <- "Computer & Engineering"
+
+data$O.Net.Job.Family.Categories[data$O.Net.Job.Family.Categories == "Life Physical and Social Science"] <- "Education, Science & Health"
+data$O.Net.Job.Family.Categories[data$O.Net.Job.Family.Categories == "Educational Instruction and Library"] <- "Education, Science & Health"
[…]

### 2021-12-01 Submission.tex
initial repo creation

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Job Demands-Resources model components through the lens of O*NET classifications},
  pdfauthor={Alicia Stachowski1, Renata Garcia Prieto Palacios Roji2, \& John Kulas2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{O*NET JD-R}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi

\title{Job Demands-Resources model components through the lens of O*NET classifications}
\author{Alicia Stachowski\textsuperscript{1}, Renata Garcia Prieto Palacios Roji\textsuperscript{2}, \& John Kulas\textsuperscript{2}}
\date{}

\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Wisconsin - Stout\\\textsuperscript{2} Montclair State University}

\abstract{
O*NET work characteristics were rated in terms of relevance, perception of demand, and perception as resource. All the results of this current study match the stress-appraisal stuff. Next steps: 1) discuss results within stress-appraisal framework (Lazarus \& Bookman), 2) different literature on challenge and hindrance demands. Job Demands Resources theory that says resources and demands are relatively universal is NOT consistent with these findings. JDR neglects the other 2 literatures. Analytically pull O*Net descriptors that reflect universal demands/resources (e.g., autonomy) and see how much variability there is on those. Maybe forget about cross-walk thing. May actually want to start with this: \url{https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit\#gid=1041061499}.

We want to also group items by O*NET categories so there's not so many (that makes ANOVAs more viable)
}

\begin{document}
\maketitle

In an attempt to integrate the O*NET taxonomy within the orientation of the Job Demands-Resources (Bakker et al., 2003; Bakker \& Demerouti, 2017; Demerouti et al., 2001), a series of evaluations were made that used: 1) O*NET terminology (both descriptor and response option), 2) JD-R influenced ratings of demand, challenge, or hindrance. The outcome of this integration is a cross-walk between the Department of Labor classifications and the I-O literature steeped JD-R. While O*Net provides thorough documentation of information associated with job analyses, one of the remaining limitations is its lack of connection to theory. Given the popularity of the Job Demands-Resources Theory (JD-R; Demerouti et al., 2001) in exploring questions related to everything from motivation to job design, we aim to explore the intersection between perceptions of job demands and resources, and the broad set of job characteristics provided on O*Net. In an attempt to integrate the O*Net taxonomy within the orientation of the JD-R framework (Bakker et al., 2003; Bakker \& Demerouti, 2017; Demerouti et al., 2001), a series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance. Prior to a description of results, a brief overview of both the JD-R theory and O*Net is provided.

\hypertarget{the-job-demands-resources-theory}{%
\subsection{The Job demands-Resources Theory}\label{the-job-demands-resources-theory}}

The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model (Demerouti et al., 2001). One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands. \emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001). In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; Demerouti et al. (2001)).
Cognitively, the perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; Bakker \& Demerouti, 2014). Pertinent to the current study, demanding job characteristics are frequently often associated with negative outcomes (e.g., Bakker et al., 2003), whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation (Bakker et al., 2007).

\hypertarget{onet-resource}{%
\subsection{O*Net Resource}\label{onet-resource}}

Originally, the Advisory Panel for the Dictionary of Occupational Titles recommended a system that would \enquote{\ldots promote the effective education, training, counseling, and employment of the American workforce. It should accomplish its purpose by providing a database system that identified, defines, classifies, and describes occupations in the economy in an accessible and flexible manner} (Dictionary of Occupational Titles (US) and Service (1993), p.~6). The result was the now commonly used O*NET. The Occupational Information Network (O*NET; onetonline.org) contains a comprehensive description of occupations (Peterson et al., 2001). This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated. In fact, there was a call to work with experienced I/O psychologists over the summer to update the content for the \href{https://www.onetonline.org/link/summary/19-3032.00}{Industrial and Organizational Psychologist listing on O*Net}. These data, and the tools provided for free on the website (e.g., Career Exploration Tools, \enquote{My Next Move for Veterans}, \enquote{My Next Move}, Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice, and also employers with information with which to craft job descriptions and help employees determine what skills are needed for promotion.

\hypertarget{current-study}{%
\subsection{Current Study}\label{current-study}}

Interestingly, we have not yet integrated this practical and accessible resource within the JD-R framework. This paper aims to provide such a crosswalk or integration of the theory and practical occupations-focused data on O*Net. Several broad research questions are examined across jobs:

\begin{quote}
\emph{Research Question 1}: Which O*Net job characteristics are consistently rated as job resources?
\end{quote}

\begin{quote}
\emph{Research Question 2}: Which O*Net job characteristics are consistently rated as challenge demands?
\end{quote}

\begin{quote}
\emph{Research Question 3}: Which O*Net job characteristics are consistently rated as hinderance demands?
\end{quote}

The other distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework. In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., (Bakker \& Sanz-Vergel, 2013); {[}cavanaugh2000empirical{]}; (Gerich, 2017); (Podsakoff et al., 2007); (Webster et al., 2011)).

Thus, a fourth question of interest explores just that possibility:

\begin{quote}
\emph{Research Question 4}: Which O*Net job characteristics show wide variability in assigned JD-R classification of resource, challenge, or hinderance.
\end{quote}

\hypertarget{alternatively-alicias-jdr-vs-stress-model-predictions}{%
\subsection{ALTERNATIVELY, Alicia's JDR vs stress model predictions}\label{alternatively-alicias-jdr-vs-stress-model-predictions}}

Objective vs.~Subjective Nature of Demands and Resources: The Role of Appraisal

Searle and Auton (2015) note that the majority of the research on workplace demands is based on apriori classifications of demands. However, the stress experience, or process, described early on by Lazarus and Folkman (1984) is grounded in the assumption that individual appraisals of stressors/demands vary. Their transactional theory or stress and coping states that people continuously appraise stimuli in their environments. An appraisal is the cognitive process whereby meaning is assigned to a stimulus. If a stimulus is appraised as a stressor (threat, challenge, potentially harmful), emotional distress leads to coping of some kind. This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes is not appraised as favorable (Lazarus \& Folkman, 1984). The stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.

We next consider the (limited) empirical evidence on this topic. First, some relatively recent research suggests that job demands and resources may not be universally appraised or assigned as such. Starting with job demands, Webster et al. (2011), for example, studied workload, role ambiguity, and role conflict demands, and found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hinderance to different degrees. While their study did include resources, it nonetheless points to individual difference on how people perceive stressors at work. Although part of a much larger study on retirement, Sonnega et al. (2018) compared self-reported (subjective) ratings of degree of physical demand, stress, and need for intense concentration from the Health and Retirement Study with objective ratings from O*Net. Correlations physical demand (r = .52), stress (r = .10), and need for intense concentration (r = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than assumed. Next considering resources, Schmitz et al. (2019) captured subjective and objective resources in their study of retirement also. Correlations of composite variables for the resources of autonomy (r = .12), recognition of work (r = .07), decision freedom (r = .08), and advancement (r = -.01), while significant, certainly do not reflect high levels of overlap.

We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees. Downes et al. (2021) meta-analysis addresses this reality in depth, although it is beyond the scope of this project.

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

Of the 785 Prolific panel individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses ({\textbf{???}}). Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current SIOP sample. 13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.

Ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53). The survey offered a free-field gender identity category, although the sample predominantly self-identified as female (52.58\%) or male (46.83\%).

\hypertarget{materials}{%
\subsection{Materials}\label{materials}}

Each free-field job title was placed into one of 14 possible O*NET job families classifications. 60 of these ratings were performed by all 3 author raters, with a resulting Kappa of 0.53 (Landis \& Koch, 1977).

\hypertarget{characteristics-demands-and-resources}{%
\subsubsection{Characteristics, Demands, and Resources}\label{characteristics-demands-and-resources}}

We used 98 statements taken from O*NET \href{https://www.O*NETonline.org/find/descriptor/result/4.A.1.b.3}{\enquote{activity} and \enquote{context} classifications}. We retained 41 \enquote{work activity} classifications which O*NET groups into categories of \enquote{Information Input} (5 statements), \enquote{Interacting with Others} (17 statements), \enquote{Mental Processes} (10 statements) and \enquote{Work Output} (9 statements). 57 \enquote{work context} statements grouped into \enquote{Interpersonal Relationships} (14 statements), \enquote{Physical Work Conditions} (30 statements), and \enquote{Structural Job Characteristics} (13 statements).

These \enquote{descriptors} often have unique response categories (\href{https://www.O*NETonline.org/find/descriptor/result/4.C.1.c.2}{see here for example}). We retained the O*NET wording to capture characteristics of relevance for each respondent. Subsequent to these self evaluations, each respondent who agreed that the element had \emph{at least some relevance} to their job was also asked to rate that element in terms of, 1) \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) \ldots this aspect of your job is a hinderance that can inhibit personal growth, learning, and work goal attainment.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{low-variability-demands-and-resources}{%
\subsection{Low Variability Demands and Resources}\label{low-variability-demands-and-resources}}

The below graphs present the resources, challenges, and hindrances that are \emph{largely agreed on} as indexed by (relatively) low standard deviations.

\begin{quote}
Note. The \enquote{zero} standard deviations are likely one person, \emph{n}'s should also go on these graphs if they're retained.
\end{quote}

\includegraphics{Submission_files/figure-latex/resourceslowsd-1.pdf}

\includegraphics{Submission_files/figure-latex/challengesagree-1.pdf}

\includegraphics{Submission_files/figure-latex/hindrancesagree-1.pdf}

As can be seen by the graphs, there is considerable disagreement regarding the degree to which job elements are considered \emph{hindrances}, with the 10 elements showing the greatest agreement still ranging in standard deviations from 0 to 1.18. What is widely seen as a resource and challenge tends to be more universally agreed upon (range of lowest 10 resource standard deviations is 0 to 0.88 and the range of lowest 10 challenge standard deviations is 0 to 0.87.

\hypertarget{high-variability-demands-and-resources}{%
\subsection{High Variability Demands and Resources}\label{high-variability-demands-and-resources}}

The below graphs present the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations (these are the 10 characteristics with the greatest variability in rating).

\includegraphics{Submission_files/figure-latex/resourceshisd-1.pdf}

\includegraphics{Submission_files/figure-latex/challengeshighsd-1.pdf}

\includegraphics{Submission_files/figure-latex/hindranceshighsd-1.pdf}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-bakker2014job}{}%
Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.

\leavevmode\hypertarget{ref-bakker2017job}{}%
Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.

\leavevmode\hypertarget{ref-bakker2007job}{}%
Bakker, A. B., Hakanen, J. J., Demerouti, E., \& Xanthopoulou, D. (2007). Job resources boost work engagement, particularly when job demands are high. \emph{Journal of Educational Psychology}, \emph{99}(2), 274.

\leavevmode\hypertarget{ref-bakker2013weekly}{}%
Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.

\leavevmode\hypertarget{ref-bakker2003dual}{}%
Bakker, A., Demerouti, E., \& Schaufeli, W. (2003). Dual processes at work in a call centre: An application of the job demands--resources model. \emph{European Journal of Work and Organizational Psychology}, \emph{12}(4), 393--417.

\leavevmode\hypertarget{ref-demerouti2001job}{}%
Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.

\leavevmode\hypertarget{ref-advisory1993new}{}%
Dictionary of Occupational Titles (US), A. P. for the, \& Service, U. S. E. (1993). \emph{The new dot: A database of occupational titles for the twenty-first century}. US Department of Labor, Employment; Training Administration, US~\ldots.

\leavevmode\hypertarget{ref-downes2021incorporating}{}%
Downes, P. E., Reeves, C. J., McCormick, B. W., Boswell, W. R., \& Butts, M. M. (2021). Incorporating job demand variability into job demands theory: A meta-analysis. \emph{Journal of Management}, \emph{47}(6), 1630--1656.

\leavevmode\hypertarget{ref-gerich2017relevance}{}%
Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.

\leavevmode\hypertarget{ref-landis1977measurement}{}%
Landis, J. R., \& Koch, G. G. (1977). The measurement of observer agreement for categorical data. \emph{Biometrics}, 159--174.

\leavevmode\hypertarget{ref-lazarus1984stress}{}%
Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.

\leavevmode\hypertarget{ref-peterson2001understanding}{}%
Peterson, N. G., Mumford, M. D., Borman, W. C., Jeanneret, P. R., Fleishman, E. A., Levin, K. Y., Campion, M. A., Mayfield, M. S., Morgeson, F. P., Pearlman, K., \& others. (2001). Understanding work using the occupational information network (o* net): Implications for practice and research. \emph{Personnel Psychology}, \emph{54}(2), 451--492.

\leavevmode\hypertarget{ref-podsakoff2007differential}{}%
Podsakoff, N. P., LePine, J. A., \& LePine, M. A. (2007). Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis. \emph{Journal of Applied Psychology}, \emph{92}(2), 438.

\leavevmode\hypertarget{ref-schmitz_interpreting_2019}{}%
Schmitz, L. L., McCluney, C. L., Sonnega, A., \& Hicken, M. T. (2019). Interpreting Subjective and Objective Measures of Job Resources: The Importance of Sociodemographic Context. \emph{International Journal of Environmental Research and Public Health}, \emph{16}(17), 3058. \url{https://doi.org/10.3390/ijerph16173058}

\leavevmode\hypertarget{ref-searle2015merits}{}%
Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.

\leavevmode\hypertarget{ref-sonnega_comparison_2018}{}%
Sonnega, A., Helppie-McFall, B., Hudomiet, P., Willis, R. J., \& Fisher, G. G. (2018). A Comparison of Subjective and Objective Job Demands and Fit With Personal Resources as Predictors of Retirement Timing in a National U.S. Sample. \emph{Work, Aging and Retirement}, \emph{4}(1), 37--51. \url{https://doi.org/10.1093/workar/wax016}

\leavevmode\hypertarget{ref-webster2011extending}{}%
Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.

\endgroup

\end{document}

### 2021-12-09 Submission.Rmd
initial repo creation
Intro editing...

--- 2021-12-01 JDR_3_Crosswalk.Rmd
@@
 
-In an attempt to integrate the O\*NET taxonomy within the orientation of the Job Demands-Resources  [@demerouti2001job; @bakker2003dual; @bakker2017job], a series of evaluations were made that used: 1) O\*NET terminology (both descriptor and response option), 2) JD-R influenced ratings of demand, challenge, or hindrance.
-The outcome of this integration is a cross-walk between the Department of Labor classifications and the I-O literature steeped JD-R.
-While O\*Net provides thorough documentation of information associated with job analyses, one of the remaining limitations is its lack of connection to theory.
 Given the popularity of the Job Demands-Resources Theory [JD-R; @demerouti2001job] in exploring questions related to everything from motivation to job design, we aim to explore the intersection between perceptions of job demands and resources, and the broad set of job characteristics provided on O\*Net.
-In an attempt to integrate the O\*Net taxonomy within the orientation of the JD-R framework [@demerouti2001job; @bakker2003dual; @bakker2017job], a series of evaluations were made that used: 1) direct O\*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance.
-Prior to a description of results, a brief overview of both the JD-R theory and O\*Net is provided.
+A series of evaluations were made that used: 1) direct O\*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance.
+Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O\*Net is provided.
 
@@
 Pertinent to the current study, demanding job characteristics are frequently often associated with negative outcomes [e.g., @bakker2003dual], whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job].
+
+## Objective vs. Subjective Nature of Demands and Resources: The Role of Appraisal
+
+@searle2015merits note that the majority of the research on workplace demands is based on apriori classifications of demands.
+However, the stress experience, or process, described early on by @lazarus1984stress is grounded in the assumption that individual appraisals of stressors/demands vary.
+Their transactional theory or stress and coping states that people continuously appraise stimuli in their environments.
+An appraisal is the cognitive process whereby meaning is assigned to a stimulus.
+If a stimulus is appraised as a stressor (threat, challenge, potentially harmful), emotional distress leads to coping of some kind.
+This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes is not appraised as favorable [@lazarus1984stress].
+The stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.
+
+We next consider the (limited) empirical evidence on this topic.
+First, some relatively recent research suggests that job demands and resources may not be universally appraised or assigned as such.
+Starting with job demands, @webster2011extending, for example, studied workload, role ambiguity, and role conflict demands, and found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hinderance to different degrees.
+While their study did include resources, it nonetheless points to individual difference on how people perceive stressors at work.
+Although part of a much larger study on retirement, @sonnega_comparison_2018 compared self-reported (subjective) ratings of degree of physical demand, stress, and need for intense concentration from the Health and Retirement Study with objective ratings from O*Net.
+Correlations physical demand (r = .52), stress (r = .10), and need for intense concentration (r = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than assumed.
+Next considering resources, @schmitz_interpreting_2019 captured subjective and objective resources in their study of retirement also.
+Correlations of composite variables for the resources of autonomy (r = .12), recognition of work (r = .07), decision freedom (r = .08), and advancement (r = -.01), while significant, certainly do not reflect high levels of overlap.
+
+We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees.
+@downes2021incorporating meta-analysis addresses this reality in depth, although it is beyond the scope of this project.
 
@@
 
-Interestingly, we have not yet integrated this practical and accessible resource within the JD-R framework.
-This paper aims to provide such a crosswalk or integration of the theory and practical occupations-focused data on O\*Net.
-Several broad research questions are examined across jobs:
+This paper aims to provide an integration of the theory and practical occupations-focused data on O\*Net. Several broad research questions are examined across jobs:
 
@@
 >*Research Question 4*: Which O\*Net job characteristics show wide variability in assigned JD-R classification of resource, challenge, or hinderance.
-
-## ALTERNATIVELY, Alicia's JDR vs stress model predictions
-
-Objective vs. Subjective Nature of Demands and Resources: The Role of Appraisal
-
-  @searle2015merits note that the majority of the research on workplace demands is based on apriori classifications of demands.
-However, the stress experience, or process, described early on by @lazarus1984stress is grounded in the assumption that individual appraisals of stressors/demands vary.
-Their transactional theory or stress and coping states that people continuously appraise stimuli in their environments.
-An appraisal is the cognitive process whereby meaning is assigned to a stimulus.
-If a stimulus is appraised as a stressor (threat, challenge, potentially harmful), emotional distress leads to coping of some kind.
-This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes is not appraised as favorable [@lazarus1984stress].
-The stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.
-
-  We next consider the (limited) empirical evidence on this topic.
-First, some relatively recent research suggests that job demands and resources may not be universally appraised or assigned as such.
-Starting with job demands, @webster2011extending, for example, studied workload, role ambiguity, and role conflict demands, and found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hinderance to different degrees.
-While their study did include resources, it nonetheless points to individual difference on how people perceive stressors at work.
-Although part of a much larger study on retirement, @sonnega_comparison_2018 compared self-reported (subjective) ratings of degree of physical demand, stress, and need for intense concentration from the Health and Retirement Study with objective ratings from O*Net.
-Correlations physical demand (r = .52), stress (r = .10), and need for intense concentration (r = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than assumed.
-Next considering resources, @schmitz_interpreting_2019 captured subjective and objective resources in their study of retirement also.
-Correlations of composite variables for the resources of autonomy (r = .12), recognition of work (r = .07), decision freedom (r = .08), and advancement (r = -.01), while significant, certainly do not reflect high levels of overlap.
-
-  We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees.
-@downes2021incorporating meta-analysis addresses this reality in depth, although it is beyond the scope of this project.
 

### 2022-01-26 Submission.Rmd
Edits after first meeting of the semester

@@
 abstract: |
-  O\*NET work characteristics were rated in terms of relevance, perception of demand, and perception as resource.
+  O\*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource.
 All the results of this current study match the stress-appraisal stuff.
@@
 
->*Research Question 4*: Which O\*Net job characteristics show wide variability in assigned JD-R classification of resource, challenge, or hinderance.
+>*Research Question 4*: Does the **type of work** reported explain variability in the categorization of work characteristics into challenges, hindrances, and resources?
 

### 2022-01-26 Submission.tex
Edits after first meeting of the semester

@@
 \abstract{
-O*NET work characteristics were rated in terms of relevance, perception of demand, and perception as resource.
+O*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource.
 All the results of this current study match the stress-appraisal stuff.
@@
 
-In an attempt to integrate the O*NET taxonomy within the orientation of the Job Demands-Resources (Bakker et al., 2003; Bakker \& Demerouti, 2017; Demerouti et al., 2001), a series of evaluations were made that used: 1) O*NET terminology (both descriptor and response option), 2) JD-R influenced ratings of demand, challenge, or hindrance.
-The outcome of this integration is a cross-walk between the Department of Labor classifications and the I-O literature steeped JD-R.
-While O*Net provides thorough documentation of information associated with job analyses, one of the remaining limitations is its lack of connection to theory.
 Given the popularity of the Job Demands-Resources Theory (JD-R; Demerouti et al., 2001) in exploring questions related to everything from motivation to job design, we aim to explore the intersection between perceptions of job demands and resources, and the broad set of job characteristics provided on O*Net.
-In an attempt to integrate the O*Net taxonomy within the orientation of the JD-R framework (Bakker et al., 2003; Bakker \& Demerouti, 2017; Demerouti et al., 2001), a series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance.
-Prior to a description of results, a brief overview of both the JD-R theory and O*Net is provided.
+A series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance.
+Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O*Net is provided.
 
@@
 
-\hypertarget{onet-resource}{%
-\subsection{O*Net Resource}\label{onet-resource}}
-
-Originally, the Advisory Panel for the Dictionary of Occupational Titles recommended a system that would \enquote{\ldots promote the effective education, training, counseling, and employment of the American workforce.
-It should accomplish its purpose by providing a database system that identified, defines, classifies, and describes occupations in the economy in an accessible and flexible manner} (Dictionary of Occupational Titles (US) and Service (1993), p.~6).
-The result was the now commonly used O*NET.
-The Occupational Information Network (O*NET; onetonline.org) contains a comprehensive description of occupations (Peterson et al., 2001).
-This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated.
-In fact, there was a call to work with experienced I/O psychologists over the summer to update the content for the \href{https://www.onetonline.org/link/summary/19-3032.00}{Industrial and Organizational Psychologist listing on O*Net}.
-These data, and the tools provided for free on the website (e.g., Career Exploration Tools, \enquote{My Next Move for Veterans}, \enquote{My Next Move}, Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice, and also employers with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
-
-\hypertarget{current-study}{%
-\subsection{Current Study}\label{current-study}}
-
-Interestingly, we have not yet integrated this practical and accessible resource within the JD-R framework.
-This paper aims to provide such a crosswalk or integration of the theory and practical occupations-focused data on O*Net.
-Several broad research questions are examined across jobs:
-
-\begin{quote}
-\emph{Research Question 1}: Which O*Net job characteristics are consistently rated as job resources?
-\end{quote}
-
-\begin{quote}
-\emph{Research Question 2}: Which O*Net job characteristics are consistently rated as challenge demands?
-\end{quote}
-
-\begin{quote}
-\emph{Research Question 3}: Which O*Net job characteristics are consistently rated as hinderance demands?
-\end{quote}
-
-The other distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework.
-In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., (Bakker \& Sanz-Vergel, 2013); {[}cavanaugh2000empirical{]}; (Gerich, 2017); (Podsakoff et al., 2007); (Webster et al., 2011)).
-
-Thus, a fourth question of interest explores just that possibility:
-
-\begin{quote}
-\emph{Research Question 4}: Which O*Net job characteristics show wide variability in assigned JD-R classification of resource, challenge, or hinderance.
-\end{quote}
-
-\hypertarget{alternatively-alicias-jdr-vs-stress-model-predictions}{%
-\subsection{ALTERNATIVELY, Alicia's JDR vs stress model predictions}\label{alternatively-alicias-jdr-vs-stress-model-predictions}}
-
-Objective vs.~Subjective Nature of Demands and Resources: The Role of Appraisal
+\hypertarget{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisal}{%
+\subsection{Objective vs.~Subjective Nature of Demands and Resources: The Role of Appraisal}\label{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisal}}
 
@@
 (2021) meta-analysis addresses this reality in depth, although it is beyond the scope of this project.
+
+\hypertarget{onet-resource}{%
+\subsection{O*Net Resource}\label{onet-resource}}
+
+Originally, the Advisory Panel for the Dictionary of Occupational Titles recommended a system that would \enquote{\ldots promote the effective education, training, counseling, and employment of the American workforce.
+It should accomplish its purpose by providing a database system that identified, defines, classifies, and describes occupations in the economy in an accessible and flexible manner} (Dictionary of Occupational Titles (US) and Service (1993), p.~6).
+The result was the now commonly used O*NET.
+The Occupational Information Network (O*NET; onetonline.org) contains a comprehensive description of occupations (Peterson et al., 2001).
+This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated.
+In fact, there was a call to work with experienced I/O psychologists over the summer to update the content for the \href{https://www.onetonline.org/link/summary/19-3032.00}{Industrial and Organizational Psychologist listing on O*Net}.
+These data, and the tools provided for free on the website (e.g., Career Exploration Tools, \enquote{My Next Move for Veterans}, \enquote{My Next Move}, Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice, and also employers with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
+
+\hypertarget{current-study}{%
+\subsection{Current Study}\label{current-study}}
+
+This paper aims to provide an integration of the theory and practical occupations-focused data on O*Net. Several broad research questions are examined across jobs:
+
+\begin{quote}
+\emph{Research Question 1}: Which O*Net job characteristics are consistently rated as job resources?
+\end{quote}
+
+\begin{quote}
+\emph{Research Question 2}: Which O*Net job characteristics are consistently rated as challenge demands?
+\end{quote}
+
+\begin{quote}
+\emph{Research Question 3}: Which O*Net job characteristics are consistently rated as hinderance demands?
+\end{quote}
+
+The other distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework.
+In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., (Bakker \& Sanz-Vergel, 2013); {[}cavanaugh2000empirical{]}; (Gerich, 2017); (Podsakoff et al., 2007); (Webster et al., 2011)).
+
+Thus, a fourth question of interest explores just that possibility:
+
+\begin{quote}
+\emph{Research Question 4}: Which O*Net job characteristics show wide variability in assigned JD-R classification of resource, challenge, or hinderance.
+\end{quote}
 
@@
 Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
-
-\leavevmode\hypertarget{ref-bakker2017job}{}%
-Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
 

### 2022-01-26 jobcats.R

@@ -1,6 +1,6 @@
 ## Job classifications
 
-data <- read.csv("C:\\Users\\kulasj\\Downloads\\workers.csv")
+data <- read.csv("workers.csv")
 
 library(ggplot2)
 
@@ -36,6 +36,8 @@ data$O.Net.Job.Family.Categories[data$O.Net.Job.Family.Categories == "Healthcare
 data$O.Net.Job.Family.Categories[data$O.Net.Job.Family.Categories == "Arts Design Entertainment Sports Media"] <- "Other"
 data$O.Net.Job.Family.Categories[data$O.Net.Job.Family.Categories == "Military Specific"] <- "Other"
 
+
+#3 in plot all categories, combined and standalone 
 
 ggplot(data, aes(O.Net.Job.Family.Categories))+
   geom_histogram(stat="count") + coord_flip()

### 2022-02-01 Submission.Rmd
Small edits to intro section

@@
 Given the popularity of the Job Demands-Resources Theory [JD-R; @demerouti2001job] in exploring questions related to everything from motivation to job design, we aim to explore the intersection between perceptions of job demands and resources, and the broad set of job characteristics provided on O\*Net.
-A series of evaluations were made that used: 1) direct O\*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance.
+A series of evaluations were made that used: 1) direct O\*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers.
 Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O\*Net is provided.
@@
 *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; @demerouti2001job).
-Cognitively, the perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation [resulting from resources; @bakker2014job].
-Pertinent to the current study, demanding job characteristics are frequently often associated with negative outcomes [e.g., @bakker2003dual], whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job].
+In contrast, *demands* include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; @demerouti2001job).
+Cognitively, the perception of an element of ones job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation [resulting from resources; @bakker2014job].
+Pertinent to the current study, demanding job characteristics are frequently associated with negative outcomes [e.g., @bakker2003dual], whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job].
 
@@
 However, the stress experience, or process, described early on by @lazarus1984stress is grounded in the assumption that individual appraisals of stressors/demands vary.
-Their transactional theory or stress and coping states that people continuously appraise stimuli in their environments.
+Their transactional theory of stress and coping states that people continuously appraise stimuli in their environments.
 An appraisal is the cognitive process whereby meaning is assigned to a stimulus.
@@
 First, some relatively recent research suggests that job demands and resources may not be universally appraised or assigned as such.
-Starting with job demands, @webster2011extending, for example, studied workload, role ambiguity, and role conflict demands, and found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hinderance to different degrees.
-While their study did include resources, it nonetheless points to individual difference on how people perceive stressors at work.
+Starting with job demands, @webster2011extending, for example, studied workload, role ambiguity, and role conflict demands, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees.
+While their study did include resources, it nonetheless points to individual differences on how people perceive stressors at work.
 Although part of a much larger study on retirement, @sonnega_comparison_2018 compared self-reported (subjective) ratings of degree of physical demand, stress, and need for intense concentration from the Health and Retirement Study with objective ratings from O*Net.
 Correlations physical demand (r = .52), stress (r = .10), and need for intense concentration (r = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than assumed.
-Next considering resources, @schmitz_interpreting_2019 captured subjective and objective resources in their study of retirement also.
+Next considering resources, @schmitz_interpreting_2019 also captured subjective and objective resources in their study of retirement.
 Correlations of composite variables for the resources of autonomy (r = .12), recognition of work (r = .07), decision freedom (r = .08), and advancement (r = -.01), while significant, certainly do not reflect high levels of overlap.
+
+**NOTE** is this -0.01 significant?
 
@@
 Originally, the Advisory Panel for the Dictionary of Occupational Titles recommended a system that would “…promote the effective education, training, counseling, and employment of the American workforce.
-It should accomplish its purpose by providing a database system that identified, defines, classifies, and describes occupations in the economy in an accessible and flexible manner” (@advisory1993new, p.
+It should accomplish its purpose by providing a database system that identifies, defines, classifies, and describes occupations in the economy in an accessible and flexible manner” (@advisory1993new, p.
 6).
@@
 In fact, there was a call to work with experienced I/O psychologists over the summer to update the content for the [Industrial and Organizational Psychologist listing on O\*Net](https://www.onetonline.org/link/summary/19-3032.00).
-These data, and the tools provided for free on the website (e.g., Career Exploration Tools, “My Next Move for Veterans”, “My Next Move”, Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice, and also employers with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
+These data, and the tools provided for free on the website (e.g., Career Exploration Tools, “My Next Move for Veterans”, “My Next Move”, Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
+It is also useful to employers by providing them with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
 
@@
 
-The other distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework.
+The other distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework depending on *job classification*.
 In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., [@bakker2013weekly]; [cavanaugh2000empirical]; [@gerich2017relevance]; [@podsakoff2007differential]; [@webster2011extending]).

### 2022-02-01 Submission.tex
Small edits to intro section

@@
   man]{apa6}
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{amssymb,amsmath}
 \usepackage{ifxetex,ifluatex}
@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage{graphicx,grffile}
+\usepackage{graphicx}
 \makeatletter
@@
 % \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+%   {\begin{landscape}\centering\begin{threeparttable}}
+%   {\end{threeparttable}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
 
@@
 \else
-  \usepackage[shorthands=off,main=english]{babel}
+  \usepackage[main=english]{babel}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
 \fi
+\ifluatex
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 
-Given the popularity of the Job Demands-Resources Theory (JD-R; Demerouti et al., 2001) in exploring questions related to everything from motivation to job design, we aim to explore the intersection between perceptions of job demands and resources, and the broad set of job characteristics provided on O*Net.
+Given the popularity of the Job Demands-Resources Theory {[}JD-R; Demerouti et al.
+(2001){]} in exploring questions related to everything from motivation to job design, we aim to explore the intersection between perceptions of job demands and resources, and the broad set of job characteristics provided on O*Net.
 A series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance.
@@
 (2001)).
-Cognitively, the perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; Bakker \& Demerouti, 2014).
-Pertinent to the current study, demanding job characteristics are frequently often associated with negative outcomes (e.g., Bakker et al., 2003), whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation (Bakker et al., 2007).
+Cognitively, the perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation {[}resulting from resources; A.
+B.
+Bakker and Demerouti (2014){]}.
+Pertinent to the current study, demanding job characteristics are frequently often associated with negative outcomes (e.g., A.
+Bakker et al., 2003), whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation (A.
+B.
+Bakker et al., 2007).
 
@@
 
-Originally, the Advisory Panel for the Dictionary of Occupational Titles recommended a system that would \enquote{\ldots promote the effective education, training, counseling, and employment of the American workforce.
-It should accomplish its purpose by providing a database system that identified, defines, classifies, and describes occupations in the economy in an accessible and flexible manner} (Dictionary of Occupational Titles (US) and Service (1993), p.~6).
+Originally, the Advisory Panel for the Dictionary of Occupational Titles recommended a system that would ``\ldots promote the effective education, training, counseling, and employment of the American workforce.
+It should accomplish its purpose by providing a database system that identified, defines, classifies, and describes occupations in the economy in an accessible and flexible manner'' (Dictionary of Occupational Titles (US) and Service (1993), p.~6).
 The result was the now commonly used O*NET.
@@
 In fact, there was a call to work with experienced I/O psychologists over the summer to update the content for the \href{https://www.onetonline.org/link/summary/19-3032.00}{Industrial and Organizational Psychologist listing on O*Net}.
-These data, and the tools provided for free on the website (e.g., Career Exploration Tools, \enquote{My Next Move for Veterans}, \enquote{My Next Move}, Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice, and also employers with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
+These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move for Veterans,'' ``My Next Move,'' Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice, and also employers with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
 
@@
 The other distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework.
-In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., (Bakker \& Sanz-Vergel, 2013); {[}cavanaugh2000empirical{]}; (Gerich, 2017); (Podsakoff et al., 2007); (Webster et al., 2011)).
+In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., (A.
+B.
+Bakker \& Sanz-Vergel, 2013); {[}cavanaugh2000empirical{]}; (Gerich, 2017); (Podsakoff et al., 2007); (Webster et al., 2011)).
 
@@
 \begin{quote}
-\emph{Research Question 4}: Which O*Net job characteristics show wide variability in assigned JD-R classification of resource, challenge, or hinderance.
+\emph{Research Question 4}: Does the \textbf{type of work} reported explain variability in the categorization of work characteristics into challenges, hindrances, and resources?
 \end{quote}
@@
 
-Of the 785 Prolific panel individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses ({\textbf{???}}).
+Of the 785 Prolific panel individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (\textbf{R-careless?}).
 Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current SIOP sample.
@@
 
-We used 98 statements taken from O*NET \href{https://www.O*NETonline.org/find/descriptor/result/4.A.1.b.3}{\enquote{activity} and \enquote{context} classifications}.
-We retained 41 \enquote{work activity} classifications which O*NET groups into categories of \enquote{Information Input} (5 statements), \enquote{Interacting with Others} (17 statements), \enquote{Mental Processes} (10 statements) and \enquote{Work Output} (9 statements).
-57 \enquote{work context} statements grouped into \enquote{Interpersonal Relationships} (14 statements), \enquote{Physical Work Conditions} (30 statements), and \enquote{Structural Job Characteristics} (13 statements).
+We used 98 statements taken from O*NET \href{https://www.O*NETonline.org/find/descriptor/result/4.A.1.b.3}{``activity'' and ``context'' classifications}.
+We retained 41 ``work activity'' classifications which O*NET groups into categories of ``Information Input'' (5 statements), ``Interacting with Others'' (17 statements), ``Mental Processes'' (10 statements) and ``Work Output'' (9 statements).
+57 ``work context'' statements grouped into ``Interpersonal Relationships'' (14 statements), ``Physical Work Conditions'' (30 statements), and ``Structural Job Characteristics'' (13 statements).
 
-These \enquote{descriptors} often have unique response categories (\href{https://www.O*NETonline.org/find/descriptor/result/4.C.1.c.2}{see here for example}).
+These ``descriptors'' often have unique response categories (\href{https://www.O*NETonline.org/find/descriptor/result/4.C.1.c.2}{see here for example}).
 We retained the O*NET wording to capture characteristics of relevance for each respondent.
@@
 \begin{quote}
-Note. The \enquote{zero} standard deviations are likely one person, \emph{n}'s should also go on these graphs if they're retained.
+Note. The ``zero'' standard deviations are likely one person, \emph{n}'s should also go on these graphs if they're retained.
 \end{quote}
@@
 \hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
 \leavevmode\hypertarget{ref-bakker2014job}{}%
@@
 (1993).
-\emph{The new dot: A database of occupational titles for the twenty-first century}.
+\emph{The new DOT: A database of occupational titles for the twenty-first century}.
 US Department of Labor, Employment; Training Administration, US~\ldots.
@@
 (2001).
-Understanding work using the occupational information network (o* net): Implications for practice and research.
+Understanding work using the occupational information network (o* NET): Implications for practice and research.
 \emph{Personnel Psychology}, \emph{54}(2), 451--492.
@@
 (2019).
-Interpreting Subjective and Objective Measures of Job Resources: The Importance of Sociodemographic Context.
+Interpreting {Subjective} and {Objective} {Measures} of {Job} {Resources}: {The} {Importance} of {Sociodemographic} {Context}.
 \emph{International Journal of Environmental Research and Public Health}, \emph{16}(17), 3058.
@@
 (2018).
-A Comparison of Subjective and Objective Job Demands and Fit With Personal Resources as Predictors of Retirement Timing in a National U.S.
-Sample.
+A {Comparison} of {Subjective} and {Objective} {Job} {Demands} and {Fit} {With} {Personal} {Resources} as {Predictors} of {Retirement} {Timing} in a {National} {U}.{S}.
+{Sample}.
 \emph{Work, Aging and Retirement}, \emph{4}(1), 37--51.
@@
 
+\end{CSLReferences}
+
 \endgroup

### 2022-03-09 Submission.Rmd
study 1 and study 2

@@
 
-## Current Study
+## Study 1
+
+Look at the [google sheet](https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit#gid=1041061499) and document the extent to which job characteristics that have been consistently cited in the literature as demands or resources end up being consistently or variably experienced as demands or resources.
+Then Study 2 can further extend to other job characteristics that are within the O\*Net system.
+
+## Study 2
 
@@
 60 of these ratings were performed by all 3 author raters, with a resulting Kappa of `r round(kappa$value,2)` [@landis1977measurement].
+We then further collapsed these 14 categories into 8 essentially equal frequency job categories.
 

### 2022-03-09 Submission.tex
study 1 and study 2

@@
   man]{apa6}
+\title{Job Demands-Resources model components through the lens of O*NET classifications}
+\author{Alicia Stachowski\textsuperscript{1}, Renata Garcia Prieto Palacios Roji\textsuperscript{2}, \& John Kulas\textsuperscript{2}}
+\date{}
+
 \usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
 \fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 % Manuscript styling
@@
 % \newenvironment{ltable}
-%   {\begin{landscape}\centering\begin{threeparttable}}
-%   {\end{threeparttable}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
+%   {\begin{landscape}\begin{center}\begin{threeparttable}}
+%   {\end{threeparttable}\end{center}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
@@
 \usepackage{csquotes}
-\ifxetex
+\ifXeTeX
   % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
@@
 \fi
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-
-\title{Job Demands-Resources model components through the lens of O*NET classifications}
-\author{Alicia Stachowski\textsuperscript{1}, Renata Garcia Prieto Palacios Roji\textsuperscript{2}, \& John Kulas\textsuperscript{2}}
-\date{}
 
@@
 (2001){]} in exploring questions related to everything from motivation to job design, we aim to explore the intersection between perceptions of job demands and resources, and the broad set of job characteristics provided on O*Net.
-A series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance.
+A series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers.
 Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O*Net is provided.
@@
 \emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; Demerouti et al.
+In contrast, \emph{demands} include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; Demerouti et al.
 (2001)).
-Cognitively, the perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation {[}resulting from resources; A.
+Cognitively, the perception of an element of ones job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation {[}resulting from resources; A.
 B.
 Bakker and Demerouti (2014){]}.
-Pertinent to the current study, demanding job characteristics are frequently often associated with negative outcomes (e.g., A.
+Pertinent to the current study, demanding job characteristics are frequently associated with negative outcomes (e.g., A.
 Bakker et al., 2003), whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation (A.
@@
 However, the stress experience, or process, described early on by Lazarus and Folkman (1984) is grounded in the assumption that individual appraisals of stressors/demands vary.
-Their transactional theory or stress and coping states that people continuously appraise stimuli in their environments.
+Their transactional theory of stress and coping states that people continuously appraise stimuli in their environments.
 An appraisal is the cognitive process whereby meaning is assigned to a stimulus.
@@
 Starting with job demands, Webster et al.
-(2011), for example, studied workload, role ambiguity, and role conflict demands, and found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hinderance to different degrees.
-While their study did include resources, it nonetheless points to individual difference on how people perceive stressors at work.
+(2011), for example, studied workload, role ambiguity, and role conflict demands, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees.
+While their study did include resources, it nonetheless points to individual differences on how people perceive stressors at work.
 Although part of a much larger study on retirement, Sonnega et al.
@@
 Next considering resources, Schmitz et al.
-(2019) captured subjective and objective resources in their study of retirement also.
+(2019) also captured subjective and objective resources in their study of retirement.
 Correlations of composite variables for the resources of autonomy (r = .12), recognition of work (r = .07), decision freedom (r = .08), and advancement (r = -.01), while significant, certainly do not reflect high levels of overlap.
+
+\textbf{NOTE} is this -0.01 significant?
 
@@
 Originally, the Advisory Panel for the Dictionary of Occupational Titles recommended a system that would ``\ldots promote the effective education, training, counseling, and employment of the American workforce.
-It should accomplish its purpose by providing a database system that identified, defines, classifies, and describes occupations in the economy in an accessible and flexible manner'' (Dictionary of Occupational Titles (US) and Service (1993), p.~6).
+It should accomplish its purpose by providing a database system that identifies, defines, classifies, and describes occupations in the economy in an accessible and flexible manner'' (Dictionary of Occupational Titles (US) and Service (1993), p.~6).
 The result was the now commonly used O*NET.
@@
 In fact, there was a call to work with experienced I/O psychologists over the summer to update the content for the \href{https://www.onetonline.org/link/summary/19-3032.00}{Industrial and Organizational Psychologist listing on O*Net}.
-These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move for Veterans,'' ``My Next Move,'' Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice, and also employers with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
+These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move for Veterans,'' ``My Next Move,'' Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
+It is also useful to employers by providing them with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
 
-\hypertarget{current-study}{%
-\subsection{Current Study}\label{current-study}}
+\hypertarget{study-1}{%
+\subsection{Study 1}\label{study-1}}
+
+Look at the \href{https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit\#gid=1041061499}{google sheet} and document the extent to which job characteristics that have been consistently cited in the literature as demands or resources end up being consistently or variably experienced as demands or resources.
+Then Study 2 can further extend to other job characteristics that are within the O*Net system.
+
+\hypertarget{study-2}{%
+\subsection{Study 2}\label{study-2}}
 
@@
 
-The other distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework.
+The other distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework depending on \emph{job classification}.
 In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., (A.
@@
 60 of these ratings were performed by all 3 author raters, with a resulting Kappa of 0.53 (Landis \& Koch, 1977).
+We then further collapsed these 14 categories into 8 essentially equal frequency job categories.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-bakker2014job}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
 Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
 
-\leavevmode\hypertarget{ref-bakker2007job}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2007job}{}}%
 Bakker, A.
@@
 
-\leavevmode\hypertarget{ref-bakker2013weekly}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
 Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
 
-\leavevmode\hypertarget{ref-bakker2003dual}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2003dual}{}}%
 Bakker, A., Demerouti, E., \& Schaufeli, W.
@@
 
-\leavevmode\hypertarget{ref-demerouti2001job}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
 Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
 
-\leavevmode\hypertarget{ref-advisory1993new}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-advisory1993new}{}}%
 Dictionary of Occupational Titles (US), A.
@@
 
-\leavevmode\hypertarget{ref-downes2021incorporating}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-downes2021incorporating}{}}%
 Downes, P.
@@
 
-\leavevmode\hypertarget{ref-gerich2017relevance}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
 Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
 
-\leavevmode\hypertarget{ref-landis1977measurement}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-landis1977measurement}{}}%
 Landis, J. R., \& Koch, G. G. (1977). The measurement of observer agreement for categorical data. \emph{Biometrics}, 159--174.
 
-\leavevmode\hypertarget{ref-lazarus1984stress}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
 Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
 
-\leavevmode\hypertarget{ref-peterson2001understanding}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
 Peterson, N.
@@
 S., Morgeson, F.
-P., Pearlman, K., \& others.
+P., Pearlman, K.others.
 (2001).
@@
 
-\leavevmode\hypertarget{ref-podsakoff2007differential}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-podsakoff2007differential}{}}%
 Podsakoff, N.
@@
 
-\leavevmode\hypertarget{ref-schmitz_interpreting_2019}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-schmitz_interpreting_2019}{}}%
 Schmitz, L.
@@
 
-\leavevmode\hypertarget{ref-searle2015merits}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-searle2015merits}{}}%
 Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.
 
-\leavevmode\hypertarget{ref-sonnega_comparison_2018}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-sonnega_comparison_2018}{}}%
 Sonnega, A., Helppie-McFall, B., Hudomiet, P., Willis, R.
@@
 
-\leavevmode\hypertarget{ref-webster2011extending}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
 Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.

### 2022-03-16 Submission.Rmd
updating introduction

@@
 Given the popularity of the Job Demands-Resources Theory [JD-R; @demerouti2001job] in exploring questions related to everything from motivation to job design, we aim to explore the intersection between perceptions of job demands and resources, and the broad set of job characteristics provided on O\*Net.
-A series of evaluations were made that used: 1) direct O\*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers.
+Across two studies, a series of evaluations were made that used: 1) direct O\*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers.
 Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O\*Net is provided.
@@
 Next considering resources, @schmitz_interpreting_2019 also captured subjective and objective resources in their study of retirement.
-Correlations of composite variables for the resources of autonomy (r = .12), recognition of work (r = .07), decision freedom (r = .08), and advancement (r = -.01), while significant, certainly do not reflect high levels of overlap.
-
-**NOTE** is this -0.01 significant?
+Correlations of composite variables for the resources of autonomy (r = .12.
+p > .01), recognition of work (r = .07, p > .01), and decision freedom (r = .08, p > .01), while significant, certainly do not reflect high levels of overlap.
 
@@
 Look at the [google sheet](https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit#gid=1041061499) and document the extent to which job characteristics that have been consistently cited in the literature as demands or resources end up being consistently or variably experienced as demands or resources.
-Then Study 2 can further extend to other job characteristics that are within the O\*Net system.
+Study 1 aims to provide an integration of the theory and practical occupations-focused data on O\*Net.
+Several broad research questions are examined across jobs:
+
+>*Research Question 1*: Which O\*Net job characteristics are consistently rated as job resources?
+
+>*Research Question 2*: Which O\*Net job characteristics are consistently rated as challenge demands?
+
+>*Research Question 3*: Which O\*Net job characteristics are consistently rated as hinderance demands?
 
@@
 
-This paper aims to provide an integration of the theory and practical occupations-focused data on O\*Net. Several broad research questions are examined across jobs:
-
->*Research Question 1*: Which O\*Net job characteristics are consistently rated as job resources?
-
->*Research Question 2*: Which O\*Net job characteristics are consistently rated as challenge demands?
-
->*Research Question 3*: Which O\*Net job characteristics are consistently rated as hinderance demands?
+While Study 1 explored the above questions across jobs, Study 2 further extends to other job characteristics that are within the O\*Net system, specifically, job classification.
 
@@
 
-Thus, a fourth question of interest explores just that possibility:
+Thus, Study 2 focuses on a fourth question of interest.
 

### 2022-03-16 Submission.tex
updating introduction

@@
   man]{apa6}
-\title{Job Demands-Resources model components through the lens of O*NET classifications}
-\author{Alicia Stachowski\textsuperscript{1}, Renata Garcia Prieto Palacios Roji\textsuperscript{2}, \& John Kulas\textsuperscript{2}}
-\date{}
-
 \usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{iftex}
-\ifPDFTeX
+\usepackage{ifxetex,ifluatex}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
   \usepackage[T1]{fontenc}
@@
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 % Manuscript styling
@@
 
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
 % \usepackage{etoolbox}
@@
 \usepackage{csquotes}
-\ifXeTeX
+\ifxetex
   % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
@@
 \fi
-\ifLuaTeX
+\ifluatex
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
+\title{Job Demands-Resources model components through the lens of O*NET classifications}
+\author{Alicia Stachowski\textsuperscript{1}, Renata Garcia Prieto Palacios Roji\textsuperscript{2}, \& John Kulas\textsuperscript{2}}
+\date{}
+
+\authornote{
+
+Correspondence concerning this article should be addressed to Alicia Stachowski, Menomenie, WI. E-mail: \href{mailto:stachowskia@uwstout.edu}{\nolinkurl{stachowskia@uwstout.edu}}
+
+}
 
@@
 (2001){]} in exploring questions related to everything from motivation to job design, we aim to explore the intersection between perceptions of job demands and resources, and the broad set of job characteristics provided on O*Net.
-A series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers.
+Across two studies, a series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers.
 Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O*Net is provided.
@@
 (2019) also captured subjective and objective resources in their study of retirement.
-Correlations of composite variables for the resources of autonomy (r = .12), recognition of work (r = .07), decision freedom (r = .08), and advancement (r = -.01), while significant, certainly do not reflect high levels of overlap.
-
-\textbf{NOTE} is this -0.01 significant?
+Correlations of composite variables for the resources of autonomy (r = .12.
+p \textgreater{} .01), recognition of work (r = .07, p \textgreater{} .01), and decision freedom (r = .08, p \textgreater{} .01), while significant, certainly do not reflect high levels of overlap.
 
@@
 Look at the \href{https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit\#gid=1041061499}{google sheet} and document the extent to which job characteristics that have been consistently cited in the literature as demands or resources end up being consistently or variably experienced as demands or resources.
-Then Study 2 can further extend to other job characteristics that are within the O*Net system.
-
-\hypertarget{study-2}{%
-\subsection{Study 2}\label{study-2}}
-
-This paper aims to provide an integration of the theory and practical occupations-focused data on O*Net. Several broad research questions are examined across jobs:
+Study 1 aims to provide an integration of the theory and practical occupations-focused data on O*Net.
+Several broad research questions are examined across jobs:
 
@@
 
+\hypertarget{study-2}{%
+\subsection{Study 2}\label{study-2}}
+
+While Study 1 explored the above questions across jobs, Study 2 further extends to other job characteristics that are within the O*Net system, specifically, job classification.
+
 The other distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework depending on \emph{job classification}.
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
+\leavevmode\hypertarget{ref-bakker2014job}{}%
 Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2007job}{}}%
+\leavevmode\hypertarget{ref-bakker2007job}{}%
 Bakker, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
+\leavevmode\hypertarget{ref-bakker2013weekly}{}%
 Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2003dual}{}}%
+\leavevmode\hypertarget{ref-bakker2003dual}{}%
 Bakker, A., Demerouti, E., \& Schaufeli, W.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
+\leavevmode\hypertarget{ref-demerouti2001job}{}%
 Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
 
-\leavevmode\vadjust pre{\hypertarget{ref-advisory1993new}{}}%
+\leavevmode\hypertarget{ref-advisory1993new}{}%
 Dictionary of Occupational Titles (US), A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-downes2021incorporating}{}}%
+\leavevmode\hypertarget{ref-downes2021incorporating}{}%
 Downes, P.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
+\leavevmode\hypertarget{ref-gerich2017relevance}{}%
 Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
 
-\leavevmode\vadjust pre{\hypertarget{ref-landis1977measurement}{}}%
+\leavevmode\hypertarget{ref-landis1977measurement}{}%
 Landis, J. R., \& Koch, G. G. (1977). The measurement of observer agreement for categorical data. \emph{Biometrics}, 159--174.
 
-\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
+\leavevmode\hypertarget{ref-lazarus1984stress}{}%
 Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
 
-\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
+\leavevmode\hypertarget{ref-peterson2001understanding}{}%
 Peterson, N.
@@
 S., Morgeson, F.
-P., Pearlman, K.others.
+P., Pearlman, K., \& others.
 (2001).
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-podsakoff2007differential}{}}%
+\leavevmode\hypertarget{ref-podsakoff2007differential}{}%
 Podsakoff, N.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-schmitz_interpreting_2019}{}}%
+\leavevmode\hypertarget{ref-schmitz_interpreting_2019}{}%
 Schmitz, L.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-searle2015merits}{}}%
+\leavevmode\hypertarget{ref-searle2015merits}{}%
 Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.
 
-\leavevmode\vadjust pre{\hypertarget{ref-sonnega_comparison_2018}{}}%
+\leavevmode\hypertarget{ref-sonnega_comparison_2018}{}%
 Sonnega, A., Helppie-McFall, B., Hudomiet, P., Willis, R.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
+\leavevmode\hypertarget{ref-webster2011extending}{}%
 Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.

### 2022-03-21 Submission.Rmd
Study 2 description added

@@
 
-Given the popularity of the Job Demands-Resources Theory [JD-R; @demerouti2001job] in exploring questions related to everything from motivation to job design, we aim to explore the intersection between perceptions of job demands and resources, and the broad set of job characteristics provided on O\*Net.
+Given the popularity of the Job Demands-Resources Theory [JD-R; @demerouti2001job] in exploring questions related to everything from motivation to job design, we aim to explore the intersection between *perceptions* of job demands and resources, and the broad set of job characteristics provided on O\*Net.
+We aim to present evidence surrounding whether O\*Net job and task descriptors are simiarly rated as resources, challenge- or hindrance demands, and whether such ratings differ across job catories/classifications.
 Across two studies, a series of evaluations were made that used: 1) direct O\*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers.
@@
 
-While Study 1 explored the above questions across jobs, Study 2 further extends to other job characteristics that are within the O\*Net system, specifically, job classification.
-
-The other distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework depending on *job classification*.
-In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., [@bakker2013weekly]; [cavanaugh2000empirical]; [@gerich2017relevance]; [@podsakoff2007differential]; [@webster2011extending]).
-
+While Study 1 explored the above questions across jobs, Study 2 considers a potentially important moderator: job classification.
+There is a distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework depending on *job classification*.
+In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., [@bakker2013weekly]; [@cavanaugh2000empirical]; [@gerich2017relevance]; [@podsakoff2007differential]; [@webster2011extending]).
 Thus, Study 2 focuses on a fourth question of interest.

### 2022-03-21 Submission.tex
Study 2 description added

@@
 
-While Study 1 explored the above questions across jobs, Study 2 further extends to other job characteristics that are within the O*Net system, specifically, job classification.
-
-The other distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework depending on \emph{job classification}.
+While Study 1 explored the above questions across jobs, Study 2 considers a potentially important moderator: job classification.
+There is a distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework depending on \emph{job classification}.
 In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., (A.
 B.
-Bakker \& Sanz-Vergel, 2013); {[}cavanaugh2000empirical{]}; (Gerich, 2017); (Podsakoff et al., 2007); (Webster et al., 2011)).
-
+Bakker \& Sanz-Vergel, 2013); (Cavanaugh et al., 2000); (Gerich, 2017); (Podsakoff et al., 2007); (Webster et al., 2011)).
 Thus, Study 2 focuses on a fourth question of interest.
@@
 
+\leavevmode\hypertarget{ref-cavanaugh2000empirical}{}%
+Cavanaugh, M.
+A., Boswell, W.
+R., Roehling, M.
+V., \& Boudreau, J.
+W.
+(2000).
+An empirical examination of self-reported work stress among US managers.
+\emph{Journal of Applied Psychology}, \emph{85}(1), 65.
+
 \leavevmode\hypertarget{ref-demerouti2001job}{}%

### 2022-03-23 Submission.tex
Study 1 charts

--- 2022-03-09 Submission.tex
@@
 Given the popularity of the Job Demands-Resources Theory {[}JD-R; Demerouti et al.
-(2001){]} in exploring questions related to everything from motivation to job design, we aim to explore the intersection between perceptions of job demands and resources, and the broad set of job characteristics provided on O*Net.
-A series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers.
+(2001){]} in exploring questions related to everything from motivation to job design, we aim to explore the intersection between \emph{perceptions} of job demands and resources, and the broad set of job characteristics provided on O*Net.
+We aim to present evidence surrounding whether O*Net job and task descriptors are simiarly rated as resources, challenge- or hindrance demands, and whether such ratings differ across job catories/classifications.
+Across two studies, a series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers.
 Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O*Net is provided.
@@
 
-The other distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework depending on \emph{job classification}.
+\hypertarget{study-2}{%
+\subsection{Study 2}\label{study-2}}
+
+While Study 1 explored the above questions across jobs, Study 2 considers a potentially important moderator: job classification.
+There is a distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework depending on \emph{job classification}.
 In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., (A.
 B.
-Bakker \& Sanz-Vergel, 2013); {[}cavanaugh2000empirical{]}; (Gerich, 2017); (Podsakoff et al., 2007); (Webster et al., 2011)).
-
-Thus, a fourth question of interest explores just that possibility:
+Bakker \& Sanz-Vergel, 2013); (Cavanaugh et al., 2000); (Gerich, 2017); (Podsakoff et al., 2007); (Webster et al., 2011)).
+Thus, Study 2 focuses on a fourth question of interest.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
+Cavanaugh, M.
+A., Boswell, W.
+R., Roehling, M.
+V., \& Boudreau, J.
+W.
+(2000).
+An empirical examination of self-reported work stress among US managers.
+\emph{Journal of Applied Psychology}, \emph{85}(1), 65.
+
 \leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%

### 2022-03-23 study1.R

@@ -1,0 +1,1685 @@
+temp <- read.csv("initial_data_screen.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script
+
+x <- paste("item", sep="",1:404)
+y <- t(temp[2,])
+## decluttering Qualtrics excess
+data <- temp[-c(1:3),]                                           ## Getting rid of all 3 weird Qualtrics rows
+colnames(data) <- x
+
+incomplete <- read.csv("inprogress.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script
+
+data2 <- incomplete[-c(1:2),-c(10,12,16,113,199,285,371,379,400, 406:411)]                                          
+
+data3 <- as.data.frame(cbind(data2$V8,data2$V9,data2$V1,data2$V1,data2$V1,data2$V1,data2$V1,data2$V1,data2))
+
+colnames(data3) <- x
+
+rm(x, y, temp)       
+
+use <- rbind(data,data3)
+
+##########################################
+##########################################
+
+library(careless)
+use$careless_long <- longstring(use[18:399])
+use$missing <- rowSums(is.na(use[18:404])) 
+
+different <- use[ which(use$item18 == 2 | use$careless_long > 20 | use$missing > 200), ]
+
+attention <- use[which(use$item61 == 5 & use$item145 == 5 & use$item248 == 2 & use$item308 == 3), ]
+
+data <- data.frame(lapply(attention, function(x) as.numeric(as.character(x))))
+data <- data[,c(1:404)]
+
+###########################################
+###########################################
+
+data$item82[data$item82 == 8]  <- 1
+data$item82[data$item82 == 9]  <- 2
+data$item82[data$item82 == 10] <- 3
+data$item82[data$item82 == 11] <- 4
+data$item82[data$item82 == 12] <- 5
+
+data$item118[data$item118 == 9]  <- 1
+data$item118[data$item118 == 10] <- 2
+data$item118[data$item118 == 11] <- 3
+data$item118[data$item118 == 12] <- 4
+data$item118[data$item118 == 13] <- 5
+
[…]

### 2022-03-24 Submission.Rmd
Updated introduction

@@
 Given the popularity of the Job Demands-Resources Theory [JD-R; @demerouti2001job] in exploring questions related to everything from motivation to job design, we aim to explore the intersection between *perceptions* of job demands and resources, and the broad set of job characteristics provided on O\*Net.
-We aim to present evidence surrounding whether O\*Net job and task descriptors are simiarly rated as resources, challenge- or hindrance demands, and whether such ratings differ across job catories/classifications.
+This project makes three contributions.
+We aim to first explore whether ratings of of O\*Net item groupings align with the stated "resources" and "demands" presented in the job demands-resources theory.
+We then present evidence documenting whether O\*Net job and task descriptors are similarly rated as resources, challenge- or hindrance demands, and lastly, whether such ratings differ across job categories/classifications.
 Across two studies, a series of evaluations were made that used: 1) direct O\*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers.
@@
 
+Of greatest interest here are statements taken from O\*NET ["activity" and "context" classifications](https://www.O\*NETonline.org/find/descriptor/result/4.A.1.b.3) (e.g., items related to information input, interacting with others, physical work conditions, structural job characteristics).
+One of the first and basic questions is whether or not the categorical examples of "resources" and "demands" described in the Job Demands-Resources Theory [@demerouti2001job], for example, are generally deemed resources or demands as we objectively define them.
+The next logical question surrounds how "universal" such ratings are.
+For instance, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.
+A second study extends the findings from Study 1 to a potentially key moderator - job categories/classifications, examining whether ratings of resources, challenge- and hindrance demands differ by job classification.
+
 ## Study 1

### 2022-07-21 SIOP factor analysis.R
attempting FA in Anoka coffee shop

@@ -1,0 +1,25 @@
+
+data <- read.csv("recodedforsiop.csv")[,-1] ## line 1562 of "study1.R" script
+
+data$Structural <-      rowMeans(data[19:31], na.rm=TRUE)
+data$Physical <-        rowMeans(data[c(32:60,62)], na.rm=TRUE)
+data$Interpersonal <-   rowMeans(data[63:76], na.rm=TRUE)
+data$Information.I <-   rowMeans(data[77:81], na.rm=TRUE)
+data$Mental.P <-        rowMeans(data[82:91], na.rm=TRUE)
+data$WorkOutput <-      rowMeans(data[92:100], na.rm=TRUE)
+data$Interact.Others <- rowMeans(data[101:117], na.rm=TRUE)
+
+
+library(corrr)
+library(tidyr)
+
+res.cor <- correlate(data[c(405:411)], use="pairwise.complete.obs")
+res.cor %>% fashion()
+res.cor %>% rearrange(method="MDS", absolute=FALSE) %>% shave(upper=FALSE) %>% rplot()
+
+library(psych)
+forfa <- cor(data[c(19:60,62:117)], use="pairwise.complete.obs")
+fa.parallel(forfa, n.obs=568)
+
+efa <- fa(forfa, rotate="oblimin", nfactors=8, n.obs=568, scores=TRUE, alpha=.1)
+summary(efa)

### 2022-07-21 study1.R

@@ -1559,6 +1559,8 @@ data$item372[data$item372 == 13] <- 3
 data$item372[data$item372 == 14] <- 4
 data$item372[data$item372 == 15] <- 5
 
+forsiop <- write.csv(data, "recodedforsiop.csv")       ## saving above recodes so future scripts can be less dense (7/21/22 in Anoka)
+
 ###############################################
 ###############################################
 

### 2022-07-21 SIOP_Onet_FA.Rmd
First attempt at factor analysis - yay!

---
title             : "O*Net Factor Analysis Project"
shorttitle        : "SIOP_FA"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

# Methods

## Participants

## Material

## Procedure

# Results

Maybe try hierarchical which 2 overaching factors with the "dimensions" under each).

We are working on a factor analysis of the characteristics themselves. This is based on the larger number of items (97?) with an n of now 568.

We tried different numbers of factors based on a scree plot suggesting we start at 8 factors. We printed only those loadings at .3 or higher to begin. Very few items loaded on more than 1 factor, and most loaded at .3+ on one factor. A few were negative. Need to think carefully about interpretation by exploring what the items themselves are.

Next - tried a 2 factor solution, wondering if items in the "context" and "activity" categories loaded as expected based on Onet categories. Again, most items loaded at .3+. The physical items generally loaded on factor 1.

```{r scree plot}

data <- read.csv("recodedforsiop.csv")[,-1] ## line 1562 of "study1.R" script

data$Structural <-      rowMeans(data[19:31], na.rm=TRUE)
data$Physical <-        rowMeans(data[c(32:60,62)], na.rm=TRUE)
data$Interpersonal <-   rowMeans(data[63:76], na.rm=TRUE)
data$Information.I <-   rowMeans(data[77:81], na.rm=TRUE)
data$Mental.P <-        rowMeans(data[82:91], na.rm=TRUE)
data$WorkOutput <-      rowMeans(data[92:100], na.rm=TRUE)
data$Interact.Others <- rowMeans(data[101:117], na.rm=TRUE)

library(psych)
forfa <- cor(data[c(19:60,62:117)], use="pairwise.complete.obs")
fa.parallel(forfa, n.obs=568)
```

# Discussion

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2022-07-21 SIOP factor analysis.R

@@ -21,5 +21,31 @@ library(psych)
 forfa <- cor(data[c(19:60,62:117)], use="pairwise.complete.obs")
 fa.parallel(forfa, n.obs=568)
 
-efa <- fa(forfa, rotate="oblimin", nfactors=8, n.obs=568, scores=TRUE, alpha=.1)
+##Here's where we started - it appears that based on scree plot, 8 factors migth be appropriate.
+##Figure out how many factors - an option
+efa <- fa(data[c(19:60,62:117)], rotate="oblimin", nfactors=2, n.obs=568, scores=TRUE, alpha=.1) ## changed to data so can get factor scores
 summary(efa)
+
+together <- cbind(data, efa$scores)
+
+res.cor <- correlate(together[c(405:413)], use="pairwise.complete.obs")
+res.cor %>% fashion()
+res.cor %>% shave(upper=FALSE) %>% rplot()
+
+efa$loadings
+print(efa$loadings,cut=.3,digits=2)
+
+##Next, trying the 2 overarching factors we noted first:
+efa <- fa(forfa, rotate="oblimin", nfactors=2, n.obs=568, scores=TRUE, alpha=.1)
+summary(efa)
+
+efa$loadings
+print(efa$loadings,cut=.3,digits=2)
+
+## Try 7 factor solution next. 
+efa <- fa(forfa, rotate="oblimin", nfactors=7, n.obs=568, scores=TRUE, alpha=.1)
+summary(efa)
+
+efa$loadings
+print(efa$loadings,cut=.3,digits=2)
+

### 2022-07-21 SIOP_Onet_FA.Rmd
FA with 2, 7, 8, 9 factors

@@
   Enter author note here.
-
-abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
 
@@
 
+```{r eight_factorFA}
+##Here's where we started - it appears that based on scree plot, 8 factors might be appropriate.
+efa <- fa(data[c(19:60,62:117)], rotate="oblimin", nfactors=8, n.obs=568, scores=TRUE, alpha=.1) ## changed to data so can get factor scores
+summary(efa)
+
+together <- cbind(data, efa$scores)
+
+#res.cor <- correlate(together[c(405:413)], use="pairwise.complete.obs")
+#res.cor %>% fashion()
+#res.cor %>% shave(upper=FALSE) %>% rplot()
+
+efa$loadings
+print(efa$loadings,cut=.3,digits=2)
+```
+
+```{r two_factorFA}
+##Next, trying the 2 overarching factors we noted first:
+efa <- fa(forfa, rotate="oblimin", nfactors=2, n.obs=568, scores=TRUE, alpha=.1)
+summary(efa)
+
+efa$loadings
+print(efa$loadings,cut=.3,digits=2)
+```
+
+```{r seven_factorFA}
+## Try 7 factor solution next. 
+efa <- fa(forfa, rotate="oblimin", nfactors=7, n.obs=568, scores=TRUE, alpha=.1)
+summary(efa)
+
+efa$loadings
+print(efa$loadings,cut=.3,digits=2)
+```
+
+```{r nine_factorFA}
+## Try 9 factor solution next. 
+efa <- fa(forfa, rotate="oblimin", nfactors=9, n.obs=568, scores=TRUE, alpha=.1)
+summary(efa)
+
+efa$loadings
+print(efa$loadings,cut=.3,digits=2)
+```
 # Discussion

### 2022-07-21 SIOP factor analysis.R

@@ -21,5 +21,38 @@ library(psych)
 forfa <- cor(data[c(19:60,62:117)], use="pairwise.complete.obs")
 fa.parallel(forfa, n.obs=568)
 
-efa <- fa(forfa, rotate="oblimin", nfactors=8, n.obs=568, scores=TRUE, alpha=.1)
+##Here's where we started - it appears that based on scree plot, 8 factors might be appropriate.
+##Figure out how many factors - an option
+efa <- fa(data[c(19:60,62:117)], rotate="oblimin", nfactors=8, n.obs=568, scores=TRUE, alpha=.1) ## changed to data so can get factor scores
 summary(efa)
+
+together <- cbind(data, efa$scores)
+
+res.cor <- correlate(together[c(405:413)], use="pairwise.complete.obs")
+res.cor %>% fashion()
+res.cor %>% shave(upper=FALSE) %>% rplot()
+
+efa$loadings
+print(efa$loadings,cut=.3,digits=2)
+
+##Next, trying the 2 overarching factors we noted first:
+efa <- fa(forfa, rotate="oblimin", nfactors=2, n.obs=568, scores=TRUE, alpha=.1)
+summary(efa)
+
+efa$loadings
+print(efa$loadings,cut=.3,digits=2)
+
+## Try 7 factor solution next. 
+efa <- fa(forfa, rotate="oblimin", nfactors=7, n.obs=568, scores=TRUE, alpha=.1)
+summary(efa)
+
+efa$loadings
+print(efa$loadings,cut=.3,digits=2)
+
+## Try 9 factor solution next. 
+efa <- fa(forfa, rotate="oblimin", nfactors=9, n.obs=568, scores=TRUE, alpha=.1)
+summary(efa)
+
+efa$loadings
+print(efa$loadings,cut=.3,digits=2)
+

### 2022-07-25 SIOP factor analysis.R
Factor analysis update - all 4 options look ok. Need to think about naming factors based on what makes sense.

@@ -28,7 +28,7 @@ efa <- fa(data[c(19:60,62:117)], rotate="oblimin", nfactors=8, n.obs=568, scores
 =======
 ##Here's where we started - it appears that based on scree plot, 8 factors migth be appropriate.
 ##Figure out how many factors - an option
-efa <- fa(data[c(19:60,62:117)], rotate="oblimin", nfactors=2, n.obs=568, scores=TRUE, alpha=.1) ## changed to data so can get factor scores
+efa <- fa(data[c(19:60,62:117)], rotate="oblimin", nfactors=8, n.obs=568, scores=TRUE, alpha=.1) ## changed to data so can get factor scores
 >>>>>>> 69cdeaa28fdbafc29b5f0f9f68326640db2736a4
 summary(efa)
 

### 2022-07-28 SIOP factor analysis.R
subsetting data

@@ -1,5 +1,11 @@
 
-data <- read.csv("recodedforsiop.csv")[,-1] ## line 1562 of "study1.R" script
+dt <- read.csv("recodedforsiop.csv")[,-1] ## line 1562 of "study1.R" script
+
+set.seed(42)
+
+temp = sort(sample(nrow(dt), nrow(dt)*.5))
+data<-dt[temp,]
+cfa<-dt[-temp,]
 
 data$Structural <-      rowMeans(data[19:31], na.rm=TRUE)
 data$Physical <-        rowMeans(data[c(32:60,62)], na.rm=TRUE)
@@ -21,15 +27,13 @@ library(psych)
 forfa <- cor(data[c(19:60,62:117)], use="pairwise.complete.obs")
 fa.parallel(forfa, n.obs=568)
 
-<<<<<<< HEAD
 ##Here's where we started - it appears that based on scree plot, 8 factors might be appropriate.
 ##Figure out how many factors - an option
 efa <- fa(data[c(19:60,62:117)], rotate="oblimin", nfactors=8, n.obs=568, scores=TRUE, alpha=.1) ## changed to data so can get factor scores
-=======
+
 ##Here's where we started - it appears that based on scree plot, 8 factors migth be appropriate.
 ##Figure out how many factors - an option
 efa <- fa(data[c(19:60,62:117)], rotate="oblimin", nfactors=8, n.obs=568, scores=TRUE, alpha=.1) ## changed to data so can get factor scores
->>>>>>> 69cdeaa28fdbafc29b5f0f9f68326640db2736a4
 summary(efa)
 
 together <- cbind(data, efa$scores)
@@ -55,7 +59,6 @@ summary(efa)
 efa$loadings
 print(efa$loadings,cut=.3,digits=2)
 
-<<<<<<< HEAD
 ## Try 9 factor solution next. 
 efa <- fa(forfa, rotate="oblimin", nfactors=9, n.obs=568, scores=TRUE, alpha=.1)
 summary(efa)
@@ -63,5 +66,11 @@ summary(efa)
 efa$loadings
 print(efa$loadings,cut=.3,digits=2)
 
-=======
->>>>>>> 69cdeaa28fdbafc29b5f0f9f68326640db2736a4
+#This is for the whole dataset, not half.
+efa.whole <- fa(forfa, rotate="oblimin", nfactors=2, n.obs=568, scores=TRUE, alpha=.1)
[…]

### 2022-08-04 SIOP factor analysis.R
cluster analyses

@@ -23,9 +23,64 @@ res.cor <- correlate(data[c(405:411)], use="pairwise.complete.obs")
 res.cor %>% fashion()
 res.cor %>% rearrange(method="MDS", absolute=FALSE) %>% shave(upper=FALSE) %>% rplot()
 
+###############################
+## trying some cluster analyses
+cluster1 <- kmeans(data[,405:411], 2, nstart=20)
+cluster1
+
+cluster1$cluster <- as.factor(cluster1$cluster)
+
+library(ggplot2)
+ggplot(data, aes(Interact.Others, Interpersonal, color=cluster1$cluster)) + geom_point(size=5, alpha=.5)
+
+ggplot(data, aes(Structural, Interpersonal, color=cluster1$cluster)) + geom_point(size=5, alpha=.5)
+
+################################################################
+################################################################
+
+cluster2 <- kmeans(data[,c(19:60, 62:117)], 2, nstart=20)    ## item responses
+
+cluster2$cluster <- as.factor(cluster2$cluster)
+
+## Physical
+
+a <- ggplot(data, aes(Physical, Structural, color=cluster2$cluster)) + geom_point(size=5, alpha=.5) + theme(legend.position="none")
+
+b <- ggplot(data, aes(Physical, Interpersonal, color=cluster2$cluster)) + geom_point(size=5, alpha=.5) + theme(legend.position="none")
+
+c <- ggplot(data, aes(Physical, Information.I, color=cluster2$cluster)) + geom_point(size=5, alpha=.5) + theme(legend.position="none")
+
+d <- ggplot(data, aes(Physical, Mental.P, color=cluster2$cluster)) + geom_point(size=5, alpha=.5) + theme(legend.position="none")
+
+e <- ggplot(data, aes(Physical, WorkOutput, color=cluster2$cluster)) + geom_point(size=5, alpha=.5) + theme(legend.position="none")
+
+f <- ggplot(data, aes(Physical, Interact.Others, color=cluster2$cluster)) + geom_point(size=5, alpha=.5) + theme(legend.position="none")
+
+library(cowplot)
+plot_grid(a,b,c,d,e,f)
+
+## Interact.Others
+
+a <- ggplot(data, aes(Interact.Others, Structural, color=cluster2$cluster)) + geom_point(size=5, alpha=.5) + theme(legend.position="none")
+
[…]

### 2022-08-04 RelativeImportance_Onet_DVs.R
regressions - which dimensions predict outcomes

@@ -1,0 +1,137 @@
+data <- read.csv("SIOPcleaned.csv")      ## from "datacleaning.R" script
+
+## O*NET categories
+
+data$onet.resource.ii <- rowMeans(data[c(162:166)], na.rm=TRUE)
+data$onet.resource.mp <- rowMeans(data[c(167:176)], na.rm=TRUE)
+data$onet.resource.wo <- rowMeans(data[c(177:185)], na.rm=TRUE)
+data$onet.resource.io <- rowMeans(data[c(186:202)], na.rm=TRUE)
+data$onet.resource.ir <- rowMeans(data[c(149:161)], na.rm=TRUE)
+data$onet.resource.pc <- rowMeans(data[c(128:144,146:148)], na.rm=TRUE)
+data$onet.resource.sc <- rowMeans(data[c(118:127)], na.rm=TRUE)
+
+overall.resource <- rowMeans(data[c(118:144,147:202)], na.rm=TRUE)
+
+data$onet.hindrance.ii <- rowMeans(data[c(246:247,249:252)], na.rm=TRUE)
+data$onet.hindrance.mp <- rowMeans(data[c(252:261)], na.rm=TRUE)
+data$onet.hindrance.wo <- rowMeans(data[c(262:270)], na.rm=TRUE)
+data$onet.hindrance.io <- rowMeans(data[c(271:287)], na.rm=TRUE)
+data$onet.hindrance.ir <- rowMeans(data[c(233:245)], na.rm=TRUE)
+data$onet.hindrance.pc <- rowMeans(data[c(213:232)], na.rm=TRUE)
+data$onet.hindrance.sc <- rowMeans(data[c(203:212)], na.rm=TRUE)
+
+overall.hindrance <- rowMeans(data[c(203:247,249:287)], na.rm=TRUE)
+
+data$onet.challenge.ii <- rowMeans(data[c(332:336)], na.rm=TRUE)
+data$onet.challenge.mp <- rowMeans(data[c(337:346)], na.rm=TRUE)
+data$onet.challenge.wo <- rowMeans(data[c(347:355)], na.rm=TRUE)
+data$onet.challenge.io <- rowMeans(data[c(356:372)], na.rm=TRUE)
+data$onet.challenge.ir <- rowMeans(data[c(319:331)], na.rm=TRUE)
+data$onet.challenge.pc <- rowMeans(data[c(298:307,309:318)], na.rm=TRUE)
+data$onet.challenge.sc <- rowMeans(data[c(288:297)], na.rm=TRUE)
[…]

### 2022-08-13 RelativeImportance_Onet_DVs.R
Added scale interactions between resources and hindrances

@@ -5706,6 +5706,7 @@ process<-function(data,y="xxxxx",x="xxxxx",m="xxxxx",w="xxxxx",z="xxxxx",cov="xx
   invisible(resultms)
 }  
 process(activate=1)
+process(data=data, y="stress", x="overall.hindrance", w="overall.resource", model=1, jn=1, plot=1)
 
 #Do resources moderate the relationship between hindrances and stress such 
 #that more total resources weaken the relationship between
@@ -5713,7 +5714,6 @@ process(activate=1)
 data$overall.hindrance <- overall.hindrance
 data$overall.resource <- overall.resource
 data$overall.challenge <- overall.challenge
-process(data=data, y="stress", x="overall.hindrance", w="overall.resource", model=1, jn=1, plot=1)
 
 #Plot the interaction
 x<-c(1.6667, 2.2894, 3.2416, 1.6667, 2.2894, 3.2416, 1.6667, 2.2894, 3.2416)
@@ -5729,3 +5729,14 @@ legend("topleft", legend = legend.txt,cex=1,lty=c(1,3,6),lwd=c(2,3,2),
 lines(x[w==3.2983],y[w==3.2983],lwd=2,col="black")
 lines(x[w==3.7402],y[w==3.7402],lwd=3,lty=3,col="black")
 lines(x[w==4.2063],y[w==4.2063],lwd=2,lty=6,col="black")
+
+#explore the individual kinds of resources
+process(data=data, y="stress", x="overall.hindrance", w="onet.resource.ii", model=1, jn=1, plot=1)
+process(data=data, y="stress", x="overall.hindrance", w="onet.resource.mp", model=1, jn=1, plot=1)
+process(data=data, y="stress", x="overall.hindrance", w="onet.resource.ii", model=1, jn=1, plot=1)
+process(data=data, y="stress", x="overall.hindrance", w="onet.resource.wo", model=1, jn=1, plot=1)
+process(data=data, y="stress", x="overall.hindrance", w="onet.resource.io", model=1, jn=1, plot=1)
+process(data=data, y="stress", x="overall.hindrance", w="onet.resource.ir", model=1, jn=1, plot=1)
+process(data=data, y="stress", x="overall.hindrance", w="onet.resource.pc", model=1, jn=1, plot=1)
+process(data=data, y="stress", x="overall.hindrance", w="onet.resource.sc", model=1, jn=1, plot=1)
+

### 2022-08-15 SIOP_Onet_FA.Rmd
New .Rmd for JDR interaction

--- 2022-07-21 SIOP_Onet_FA.Rmd
@@
 
-abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
   <!-- https://tinyurl.com/ybremelq -->
@@
 
-bibliography      : ["r-references.bib"]
+bibliography      : ["r-references.bib", "SIOP_Onet_FA.bib", "jdr.bib", "jobdemands_resources_bibtex.bib"]
 
@@
 
+csl               : apa7.csl
 documentclass     : "apa6"
@@
 
+Given the popularity of the Job Demands-Resources Theory [JD-R; @demerouti2001job] in exploring questions related to everything from motivation to job design, we aim to explore the intersection between *perceptions* of job demands and resources, and the broad set of job characteristics provided on O\*Net.
+This project makes three contributions.
+We aim to first explore whether ratings of of O\*Net item groupings align with the stated "resources" and "demands" presented in the job demands-resources theory.
+We then present evidence documenting whether O\*Net job and task descriptors are similarly rated as resources, challenge- or hindrance demands, and lastly, whether such ratings differ across job categories/classifications.
+Across two studies, a series of evaluations were made that used: 1) direct O\*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers.
+Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O\*Net is provided.
+
+## The Job demands-Resources Theory
+
+The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model [@demerouti2001job].
+One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands.
+*Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
+In contrast, *demands* include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; @demerouti2001job).
+Cognitively, the perception of an element of ones job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation [resulting from resources; @bakker2014job].
+Pertinent to the current study, demanding job characteristics are frequently associated with negative outcomes [e.g., @bakker2003dual], whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job].
+
+## Objective vs. Subjective Nature of Demands and Resources: The Role of Appraisal
+
+@searle2015merits note that the majority of the research on workplace demands is based on apriori classifications of demands.
+However, the stress experience, or process, described early on by @lazarus1984stress is grounded in the assumption that individual appraisals of stressors/demands vary.
+Their transactional theory of stress and coping states that people continuously appraise stimuli in their environments.
+An appraisal is the cognitive process whereby meaning is assigned to a stimulus.
+If a stimulus is appraised as a stressor (threat, challenge, potentially harmful), emotional distress leads to coping of some kind.
+This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes is not appraised as favorable [@lazarus1984stress].
+The stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.
+
+We next consider the (limited) empirical evidence on this topic.
+First, some relatively recent research suggests that job demands and resources may not be universally appraised or assigned as such.
+Starting with job demands, @webster2011extending, for example, studied workload, role ambiguity, and role conflict demands, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees.
+While their study did include resources, it nonetheless points to individual differences on how people perceive stressors at work.
+Although part of a much larger study on retirement, @sonnega_comparison_2018 compared self-reported (subjective) ratings of degree of physical demand, stress, and need for intense concentration from the Health and Retirement Study with objective ratings from O*Net.
+Correlations physical demand (r = .52), stress (r = .10), and need for intense concentration (r = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than assumed.
+Next considering resources, @schmitz_interpreting_2019 also captured subjective and objective resources in their study of retirement.
+Correlations of composite variables for the resources of autonomy (r = .12.
+p > .01), recognition of work (r = .07, p > .01), and decision freedom (r = .08, p > .01), while significant, certainly do not reflect high levels of overlap.
+
+We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees.
+@downes2021incorporating meta-analysis addresses this reality in depth, although it is beyond the scope of this project.
+
+## O\*Net Resource
+
+Originally, the Advisory Panel for the Dictionary of Occupational Titles recommended a system that would “…promote the effective education, training, counseling, and employment of the American workforce.
+It should accomplish its purpose by providing a database system that identifies, defines, classifies, and describes occupations in the economy in an accessible and flexible manner” (@advisory1993new, p.
+6).
+The result was the now commonly used O\*NET.
+The Occupational Information Network (O\*NET; onetonline.org) contains a comprehensive description of occupations [@peterson2001understanding].
+This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated.
+In fact, there was a call to work with experienced I/O psychologists over the summer to update the content for the [Industrial and Organizational Psychologist listing on O\*Net](https://www.onetonline.org/link/summary/19-3032.00).
+These data, and the tools provided for free on the website (e.g., Career Exploration Tools, “My Next Move for Veterans”, “My Next Move”, Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
+It is also useful to employers by providing them with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
+
+Of greatest interest here are statements taken from O\*NET ["activity" and "context" classifications](https://www.O\*NETonline.org/find/descriptor/result/4.A.1.b.3) (e.g., items related to information input, interacting with others, physical work conditions, structural job characteristics).
+One of the first and basic questions is whether or not the categorical examples of "resources" and "demands" described in the Job Demands-Resources Theory [@demerouti2001job], for example, are generally deemed resources or demands as we objectively define them.
+The next logical question surrounds how "universal" such ratings are.
+For instance, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.
+A second study extends the findings from Study 1 to a potentially key moderator - job categories/classifications, examining whether ratings of resources, challenge- and hindrance demands differ by job classification.
+
 # Methods
@@
 
-## Material
+```{r getdata}
+
+data <- read.csv("SIOPcleaned.csv")      ## from "datacleaning.R" script
+
+## O*NET categories
+
+data$onet.resource.ii <- rowMeans(data[c(162:166)], na.rm=TRUE)
+data$onet.resource.mp <- rowMeans(data[c(167:176)], na.rm=TRUE)
+data$onet.resource.wo <- rowMeans(data[c(177:185)], na.rm=TRUE)
+data$onet.resource.io <- rowMeans(data[c(186:202)], na.rm=TRUE)
+data$onet.resource.ir <- rowMeans(data[c(149:161)], na.rm=TRUE)
+data$onet.resource.pc <- rowMeans(data[c(128:144,146:148)], na.rm=TRUE)
+data$onet.resource.sc <- rowMeans(data[c(118:127)], na.rm=TRUE)
+
+data$overall.resource <- rowMeans(data[c(118:144,147:202)], na.rm=TRUE)
+
+data$onet.hindrance.ii <- rowMeans(data[c(246:247,249:252)], na.rm=TRUE)
+data$onet.hindrance.mp <- rowMeans(data[c(252:261)], na.rm=TRUE)
+data$onet.hindrance.wo <- rowMeans(data[c(262:270)], na.rm=TRUE)
+data$onet.hindrance.io <- rowMeans(data[c(271:287)], na.rm=TRUE)
+data$onet.hindrance.ir <- rowMeans(data[c(233:245)], na.rm=TRUE)
+data$onet.hindrance.pc <- rowMeans(data[c(213:232)], na.rm=TRUE)
+data$onet.hindrance.sc <- rowMeans(data[c(203:212)], na.rm=TRUE)
+
+data$overall.hindrance <- rowMeans(data[c(203:247,249:287)], na.rm=TRUE)
+
+data$onet.challenge.ii <- rowMeans(data[c(332:336)], na.rm=TRUE)
+data$onet.challenge.mp <- rowMeans(data[c(337:346)], na.rm=TRUE)
+data$onet.challenge.wo <- rowMeans(data[c(347:355)], na.rm=TRUE)
+data$onet.challenge.io <- rowMeans(data[c(356:372)], na.rm=TRUE)
+data$onet.challenge.ir <- rowMeans(data[c(319:331)], na.rm=TRUE)
+data$onet.challenge.pc <- rowMeans(data[c(298:307,309:318)], na.rm=TRUE)
+data$onet.challenge.sc <- rowMeans(data[c(288:297)], na.rm=TRUE)
+
+data$overall.challenge <- rowMeans(data[c(288:307,309:372)], na.rm=TRUE)
+
+data$burnout      <- rowMeans(data[c(373:376)], na.rm=TRUE)
+data$stress       <- rowMeans(data[c(377:379)], na.rm=TRUE)
+data$engagement   <- rowMeans(data[c(380:399)], na.rm=TRUE)        ## added 10/12 because analyses too wonky with 3 subscales
+
+```
+
+There were `r nrow(data)` respondents.
+
+```{r PROCESS}
+
+#Next, try a moderated regression
+
+# PROCESS for R version 4.1.1
+# Written by Andrew F. Hayes
+# www.afhayes.com
+# www.processmacro.org
+# Copyright 2012-2022 by Andrew F. Hayes ALL RIGHTS RESERVED
+# PROCESS workshop schedule at http://haskayne.ucalgary.ca/CCRAM
+#
+# Distribution of this code in any form except through processmacro.org 
+# is prohibited without the permission of the copyright holder, as is
+# distribution after modification.
+#
+# THIS SOFTWARE IS PROVIDED AS IS, WITHOUT WARRANTY OF ANY KIND
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF
+# MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT
+# IN NO EVENT SHALL THE COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM
+# DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT
+# OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE
+# SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE
+# USE OF THIS SOFTWARE IMPLIES AGREEMENT WITH THESE TERMS
+#
+# To activate, run this script. It may take a few minutes. 
+# Patience is a virtue. This will produce a function called process.
+# The other functions it creates cannot be accessed by the user
+# but are used by the master process function.
+
+process.bcboot3<-function(databcbt,estmte,xp2,badend,priorlo,priorhi)
+{
+  databcbt<-as.matrix(sort(databcbt))
+  badlo<-0;badhi<-0
+  pv<-matrix(as.numeric(databcbt < estmte));
+  pv<-sum(pv)/nrow(databcbt);ppv<-pv;
+  if (pv > .5){ppv<-(1-pv)}
+  y5<-sqrt(-2*log(ppv))
+  p0<-(-.322232431088);p1<-(-1);p2<-(-.342242088547);p3<-(-.0204231210245)
+  p4<-(-.0000453642210148);q0<-(.0993484626060);q1<-(.588581570495)
+  q2<-(.531103462366);q3<-(.103537752850);q4<-(.0038560700634)
+  xp<-y5+((((y5*p4+p3)*y5+p2)*y5+p1)*y5+p0)/((((y5*q4+q3)*y5+q2)*y5+q1)*y5+q0)
+  if (pv <= .5){xp<-(-xp)}
+  cilow<-round(nrow(databcbt)*pnorm(2*xp-xp2))
+  cihigh<-trunc(nrow(databcbt)*pnorm(2*xp+xp2))+1
+  if (cilow < 1){cilow<-1;booterr<-1;badlo<-1}
+  if (cihigh > nrow(databcbt)){cihigh<-nrow(databcbt);booterr<-1;badhi<-1}
+  llcit<-databcbt[cilow,1]
+  ulcit<-databcbt[cihigh,1]
+  if ((badlo==1) & (llcit != priorlo)){priorlo<-llcit;badend<-c(badend,llcit)}
+  if ((badhi==1) & (ulcit != priorhi)){priorhi<-ulcit;badend<-c(badend,ulcit)}
+  bootse<-sd(databcbt)
+  cires<-as.matrix(c(bootse,llcit,ulcit))
+  cires<-list(cires,badend,priorlo,priorhi)
+  return(cires)
+}
+
+process.pboot3<-function(databcbt,lcval,hcval)
+{
+  databcbt<-as.matrix(sort(databcbt))
+  llcit<-databcbt[lcval,1]
+  ulcit<-databcbt[hcval,1]
+  bootse<-sd(databcbt)
+  cires<-as.matrix(c(bootse,llcit,ulcit))
+  return(cires)
+}
+
+process.llrtest3<-function(lm,y,x,b,basemod,iterate,converge)
+{
+  lm<-as.matrix(lm)
+  btemphld<-b
+  llrdat<-matrix(-999,nrow(x),(nrow(lm)-sum(lm)))
+  llrdf<-ncol(x)-ncol(llrdat)
+  llrcnt<-0
+  for (llri in (1:nrow(lm)))
+  {
+    if (lm[llri,1]==0){llrcnt<-llrcnt+1;llrdat[,llrcnt]<-x[,llri]}
+  }
+  LL2<-process.modelest(y,llrdat,2,0,xp2,5,iterate,converge)
+  b<-btemphld
+  pvchi<-(1-pchisq((LL2-basemod),df=llrdf))
+  fresult<-cbind((LL2-basemod),llrdf,pvchi)
+  return(fresult)
+}
+
+process.describ3<-function(descdatf,type=0,quantle=1)
+{
+  desctmp<-matrix(-999,(8-(4*type)),ncol(descdatf))
+  # mean, sd, min, max, 16th, 50th, 84th, dich toggle
+  for (jd in c(1:ncol(descdatf)))
+  {
+    descdat<-descdatf[,jd]
+    #get the mean, sd, minimum, and maximum */
+    desctmp[1,jd]<-mean(descdat)
+    desctmp[2,jd]<-sd(descdat)
+    desctmp[3,jd]<-min(descdat)
+    desctmp[4,jd]<-max(descdat)
+    if (type==0)
+    {
+      minwarn<-0;maxwarn<-0
+      tmp=as.numeric(descdat==desctmp[3,jd])+as.numeric(descdat==desctmp[4,jd])
+      desctmp[8,jd]<-as.numeric(sum(tmp)==length(tmp))
+      if (desctmp[3,jd]==desctmp[4,jd]){desctmp[8,jd]<-2}
+      descdat<-matrix(sort(descdat))
+      decval<-c(.16,.5,.84)
+      for (kd in c(1:3))
+      {
+        low<-trunc(decval[kd]*(length(descdat)+1))
+        lowdec<-decval[kd]*(length(descdat)+1)-low
+        value<-descdat[low,1]+(descdat[(low+1),1]-descdat[low,1])*lowdec
+        desctmp[(4+kd),jd]<-value
+      }
+      mnotev<-(1)
+      modvals<-matrix(desctmp[5:7,],ncol=ncol(descdatf))
+      if (quantle != 1)
+      {
+        desctmp[5,jd]<-desctmp[1,jd]-desctmp[2,jd]
+        desctmp[6,jd]<-desctmp[1,jd]
+        desctmp[7,jd]<-desctmp[1,jd]+desctmp[2,jd]
+        modvals<-matrix(desctmp[5:7,],ncol=ncol(descdatf))
+        mnotev<-(2)
+        if (modvals[1,1] < desctmp[3,1]){modvals[1,1]<-desctmp[3,1];minwarn<-1}
+        if (modvals[3,1] > desctmp[4,1]){modvals[3,1]<-desctmp[4,1];maxwarn<-1}
+      }
+      if (desctmp[8,jd]==1)
+      {modvals<-matrix(c(desctmp[3,1],desctmp[4,1]))
+      mnotev<-0;minwarn<-0;maxwarn<-0
+      }
+      descrtrn<-list(desctmp,modvals,minwarn,maxwarn,mnotev)
+    }
+  }
+  if (type==1)
+  {descrtrn<-list(desctmp)}
+  return(descrtrn)
+}
+
+process.ftest3<-function(lm,bcoef,cv=0,chr=0,brsq=0,skip=0,y,x)
+{
+  lmat2<-as.matrix(lm)
+  y<-as.matrix(y)
+  x<-as.matrix(x)
+  n<-nrow(y)
+  if (skip==0)
+  {
+    lmat2<-as.matrix(diag(as.numeric(lm)))
+    lmat3<-matrix(0,nrow(lmat2),1)
+    for (flp in c(1:ncol(lmat2)))
+    {
+      if (sum(lmat2[,flp])==1)
+      {lmat3<-cbind(as.matrix(lmat3),as.matrix(lmat2[,flp]))}
+    }
+    lmat2<-as.matrix(lmat3[,2:ncol(lmat3)])
+  }
+  fratio<-(t(t(lmat2)%*%bcoef)%*%solve(t(lmat2)%*%cv%*%lmat2)%*%((t(lmat2)%*%bcoef)))/ncol(lmat2)
+  pfr<-(1-pf(fratio,ncol(lmat2),(n-nrow(bcoef))))
+  fresult<-matrix(c(fratio,ncol(lmat2),(n-nrow(bcoef)),pfr),ncol=4)
+  if (chr==1)
+  {
+    lmat3<-as.matrix(1-rowSums(lmat2))
+    xfm<-matrix(0,n,sum(lmat3))
+    flpc<-1
+    for (flp in (1:nrow(lmat3)))
+    {
+      if (lmat3[flp,1]==1){xfm[,flpc]=x[,flp];flpc<-flpc+1}
+    }
+    bfm<-solve(t(xfm)%*%xfm)%*%t(xfm)%*%y
+    resid<-y-(xfm%*%bfm)
+    sstotal<-t(y-(sum(y)/n))%*%(y-(sum(y)/n))
+    ssresid<-t(resid)%*%resid
+    rsqch<-as.numeric(brsq)-((sstotal-ssresid)/sstotal)
+    fresult<-matrix(c(rsqch,fresult),ncol=5)
+  }
+  ftestout<-as.matrix(fresult)
+  return(ftestout)
+}
+
+#type1 for ols, type2 for logistic LLR, type3 for logistic bootstrapping
+process.modelest<-function(y,x,type,full,xp2,hc=5,iterate=100,converge=.00001)
+{
+  if (type==1)
+  {
+    invxtx<-solve(t(x)%*%x)
+    b<-invxtx%*%t(x)%*%y
+    modres<-b
+    if (full==1)
+    {
+      n1<-nrow(x)
+      dfres<-(n1-(ncol(x)))
+      sstotal<-t(y-(sum(y)/n1))%*%(y-(sum(y)/n1))
+      resid=y-x%*%b
+      ssresid<-sum(t(resid)%*%resid)       
+      r2<-(sstotal-ssresid)/sstotal
+      adjr2<-(1-((1-r2)*(n1-1)/(dfres)))
+      mse<-ssresid/(n1-ncol(x))
+      #HC covariance matrix
+      varb<-mse*invxtx
+      k3<-ncol(x)
+      xhc<-0
+      if (hc != 5)
+      {
+        xhc<-x
+        hat<-matrix(xhc[,1])
+        for (i3 in c(1:nrow(xhc)))
+        {
+          xhcm<-matrix(xhc[i3,])
+          hat[i3,1]<-t(xhcm)%*%invxtx%*%xhcm
+        }     
+        if ((hc==0) | (hc==1))
+        {
+          for (i3 in c(1:k3)){xhc[,i3]<-xhc[,i3]*resid}
+        }
+        if ((hc==3) | (hc==2))
+        {
+          for (i3 in c(1:k3))
+          {xhc[,i3]<-(resid/(1-hat)^(1/(4-hc)))*xhc[,i3]}
+        }
+        if (hc==4)
+        {
+          hcmn<-matrix(4,n1,2);hcmn[,2]<-(n1*hat)/k3
+          minr<-apply(hcmn,1,FUN=min)
+          for (i3 in c(1:k3))
+          {
+            xhc[,i3]<-(resid/(1-hat)^(minr/2))*xhc[,i3]
+          }
+        }
+        varb<-(invxtx%*%t(xhc)%*%xhc%*%invxtx)
+        if (hc==1){varb<-(n1/(n1-ncol(x)))*varb}
+      }
+      seb<-sqrt(diag(varb))
+      trat<-b/seb
+      p<-2*pt(-abs(trat),df=dfres)
+      tval<-sqrt(dfres* (exp((dfres-(5/6))*((xp2/(dfres-(2/3)+(.11/dfres)))*(xp2/(dfres-(2/3)+(.11/dfres)))))-1))
+      modres<-matrix(c(modres,seb, trat,p,(b-tval*seb),(b+tval*seb)),ncol=6)
+      modresl<-t(matrix(c("coeff","hclab","t","p","LLCI","ULCI")))
+      lmat<-diag(ncol(x));lmat<-lmat[,2:ncol(lmat)]
+      fratio<-(t(t(lmat)%*%b)%*%solve(t(lmat)%*%varb%*%lmat)%*%((t(lmat)%*%b)))/(ncol(x)-1)
+      pfr<-1-pf(fratio,(ncol(x)-1),dfres)
+      modsum=matrix(c(sqrt(r2),r2,mse,fratio,(ncol(x)-1),dfres,pfr))
+      modsuml=matrix(c("R","R-sq","MSE","hcflab","df1","df2", "p"))
+      modretrn<-list(modres,modresl,modsum,modsuml,b,varb,tval,resid)
+      return(modretrn)
+    }
+    if (full==0){return(modres)} 
+  }
+  #for logistic Y model
+  if ((type==2) | (type==3))
+  {
+    xlp<-x;ylp<-as.matrix(y)
+    pt2<-matrix((sum(ylp)/nrow(ylp)),nrow(ylp),1)
+    if ((type==2)|(type==3)) {LL3<-(ylp*log(pt2)+(1-ylp)*log(1-pt2))}    
+    LL3<-(-2*sum(LL3))
+    bt1<-matrix(0,ncol(xlp),1);LL1<-0
+    pt1<-matrix(0.5,nrow(ylp),1);pt1lp<-pt1
+    for (jjj in (1:iterate))
+    {
+      xlptmp<-t(xlp)
+      vecprb<-(pt1lp*(1-pt1lp))
+      for (kkk in (1:ncol(xlp))){xlptmp[kkk,]<-xlptmp[kkk,]*t(vecprb)}
+      b<-bt1+solve(xlptmp%*%xlp)%*%t(xlp)%*%(ylp-pt1lp)
+      if ((type==2) | (type==3))
+      {
+        xlpb<-xlp%*%b
+        xlpbt<-as.numeric(xlpb > -709.7)
+        xlpb709<-((1-xlpbt)*(-709.7))
+        xlpb<-((xlpb*xlpbt)+xlpb709)
+        pt1lp<-1/(1+exp(-(xlpb)))
+      }
+      itprob<-sum((pt1lp < .00000001) | (pt1lp > .9999999))
+      if (itprob > 0)
+      {
+        for (kkk in (1:nrow(pt1lp)))
+        {
+          if (pt1lp[kkk,1] > .9999999){pt1lp[kkk,1]<-.9999999}     
+          if (pt1lp[kkk,1] < .00000001){pt1lp[kkk,1]<-.00000001}     
+        }
+        itprob<-0
+      }
+      if (itprob==0)
+      {
+        if ((type==2)|(type==3)){LL<-(ylp*log(pt1lp)+(1-ylp)*log(1-pt1lp))}
+        LL2<-(-2*sum(LL))
+      }
+      if (abs(LL1-LL2) < converge)
+      {
+        if (full==1)
+        {
+          xlptmp<-t(xlp)
+          vecprb<-(pt1lp*(1-pt1lp))   
+          for (kkk in (1:ncol(xlp))){xlptmp[kkk,]<-xlptmp[kkk,]*t(vecprb)} 
+          varb<-solve(xlptmp%*%xlp)
+          seb<-matrix(sqrt(diag(varb)))
+        }
+        break
+      }
+      bt1<-b;LL1<-LL2
+    }
+    modres<-b
+    if (jjj > iterate)
+    {
+      itprob<-2
+      if (booting==0){iterrmod<-1}   
+      if (booting==1){bootiter==1}   
+      if (itprobtg==0)
+      {   
+        itprobtg<-1;errcode[errs,1]<-47;errs<-errs+1
+        if ((booting==0) & (full==1))
+        {
+          pt1lpc<-(pt1lp*(1-pt1lp))
+          vt1<-diag(pt1lpc)
+          varb<-solve(t(xlp)%*%vt1%*%xlp)
+          seb<-matrix(sqrt(diag(varb)))
+        }
+      }
+    }
+    if (full==1)
+    {
+      trat<-b/seb
+      dfres<-nrow(xlp)   
+      p<-2*(1-pnorm(abs(trat)))
+      modres<-cbind(modres,seb,trat,p) 
+      modres<-matrix(c(modres,(b-xp2*seb),(b+xp2*seb)),ncol=6)
+      pvchi<-(1-pchisq((LL3-LL2),df=(nrow(modres)-1)))
+      mcF<-(LL3-LL2)/LL3
+      cox<-1-exp(-(LL3-LL2)/nrow(xlp))
+      nagel<-cox/(1-exp(-(LL3)/nrow(xlp)))
+      modsum<-matrix(c(LL2,(LL3-LL2),(nrow(modres)-1),pvchi, mcF,cox,nagel))
+      modsuml<-matrix(c("-2LL","ModelLL", "df", "p", "McFadden", "CoxSnell", "Nagelkrk"))
+      modresl<-t(matrix(c("coeff","se","Z","p","LLCI","ULCI")))
+      modretrn<-list(modres,modresl,modsum,modsuml,b,varb,xp2)
+      return(modretrn)
+    }
+    if ((full==0) & (type==2)){return(LL2)} 
+    if ((full==0) & (type==3)){return(modres)}
+  }
+}
+
+process.dummy3<-function(dd)
+{
+  uq<-unique(dd)
+  uq<-matrix(unlist(uq[1]))
+  dummy<-matrix(0,nrow(dd),nrow(uq))
+  uq<-matrix(sort(uq))
+  uq2<-matrix(seq(1:nrow(uq)))
+  for (i in c(1:nrow(dd)))
+  {for (j in c(1:nrow(uq)))
+  {if (dd[i,1]==uq[j,1])
+  {dummy[i,uq2[j,1]]<-1}  
+  }
+  }
+  return(dummy)
+}
+
+process.makdummy<-function(dd,method,custcov=0,custcode=999)
+{
+  dd<-dd[order(dd[,2]),]
+  newrow<-dd[,1]
+  dd<-dd[,2]
+  dd<-as.data.frame(dd)
+  dummy<-process.dummy3(dd)
+  uq<-unique(dd);uq<-matrix(unlist(uq[1]))
+  criterrd<-0;errcode5<-0;errcode4<-0;errcode6<-0
+  nvls<-ncol(dummy)
+  nnvls<-colSums(dummy)
+  mnvls<-min(nnvls)
+  nnvls<-matrix(sort(uq))
+  conmat1<-1
+  if (mnvls < 2){errcode5<-1;criterrd<-1}
+  if (nvls > 9){errcode4<-1;criterrd<-1}
+  x<-0;dummat<-0
+  if (criterrd==0)
+  {
+    dumok<-1
+    if (method > 0)
+    {
+      x<-dummy[,2:ncol(dummy)]
+      nx<-ncol(x)
+      minus1<-matrix(-1,1,ncol(x))
+      if (method==4)
+      {
+        for (k in (1:nrow(dd)))
+        {shole<-sum(x[k,])
+        if (shole==0)
+        {x[k,]<-minus1}}
+      }
+      if ((method==2) | (method==3) | (method==5))
+      {
+        for (k in (1:nrow(dd)))
+        {shole<-sum(x[k,])
+        if (shole > 0)
+        {
+          for (i in (1:ncol(x)))
+          {if (x[k,i]==0){x[k,i]<-1} else{break}
+          }
+        }
+        }
+        if (method==3)
+        {
+          conmat1=c(-8,1,1,1,1,1,1,1,1,0,-7,1,1,1,1,1,1,1,0,0,-6,1,1,1,1,1,1,0,0,0,-5,1,1,1,1,1,0,0,0,0,-4,1,1,1,1,0,0,0,0,0,-3,1,1,1,0,0,0,0,0,0,-2,1,1,0,0,0,0,0,0,0,-1,1)
+          conmat1<-t(matrix(conmat1,9,8))
+          for (i in (1:8)){conmat1[i,]=conmat1[i,]/(10-i)}
+          conmat1<-t(conmat1[(10-nvls):8,(10-nvls):9])
+          for (k in (1:nrow(dd)))
+          {shole<-sum(x[k,]);x[k,]=conmat1[(shole+1),]}
+        }
+      }
+      if (method==5)
+      {
+        if (ncol(custcode) != (nvls*(nvls-1)))
+        {errcode6<-1}
+        if (ncol(custcode)==(nvls*(nvls-1)))
+        {
+          conmat1<-matrix(0,nvls,(nvls-1));cnt<-1
+          for (i in (1:nvls))
+          {
+            for (k in (1:(nvls-1)))
+            {conmat1[i,k]<-custcode[1,cnt];cnt<-cnt+1}
+          }
+          for (k in (1:nrow(dd))){x[k,]<-conmat1[(sum(x[k,])+1),]}   #check this
+        }
+      }
+      xskip<-1
+      dummat<-matrix(0,(nx+1),nx)
+      dummat[(2:nrow(dummat)),]<-diag(nx)
+      if (method==4){dummat[1,]<-minus1}
+      if (method==2)
+      {for (i in 2:nrow(dummat))
+      {for (j in (1:(i-1))){dummat[i,j]<-1}}
+      }
+      if (method==3){dummat<-conmat1}
+      if ((method==5) & (errcode6==0)){dummat<-conmat1}
+      dummat<-cbind(nnvls,dummat)
+    } 
+    x<-cbind(newrow,x)
+    x<-x[order(x[,1]),]
+  }
+  dummrn<-list(x,dummat,nvls,nnvls,errcode4,errcode5,errcode6)
+  return(dummrn)
+}
+
+process<-function(data,y="xxxxx",x="xxxxx",m="xxxxx",w="xxxxx",z="xxxxx",cov="xxxxx",
+                  model=999,converge=.00001,iterate=100,hc=5,jn=0,effsize=0,stand=0,xmtest=0,normal=0,
+                  mdichok=0,contrast=999,modelbt=0,matrices=0,covmy=0,covcoeff=0,boot=5000,mc=0,
+                  intprobe=0.1,plot=0,total=0,save=0,mcx=0,mcw=0,mcz=0,moments=0,progress=1,
+                  bmatrix=-999,wmatrix=-999,zmatrix=-999,wzmatrix=-999,cmatrix=-999,xcatcode=999,
+                  wcatcode=999,zcatcode=999,wmodval=999,zmodval=999,center=0,conf=95,seed=-999,
+                  decimals=9.4,maxboot=0,modelres=0,bc=0,outscreen=1,activate=0,describe=0,listmiss=0,
+                  linsum=-999)
+{
+
+  #all this is initiation of variables and matrices
+  ranseed<-0;
+  if (seed != -999)
+  {seed<-trunc(abs(seed));set.seed(seed)}
+  wnames<-w;znames<-z;mcerpt<-0;wiscov<-0;ziscov<-0;itprobtg<-0;
+  v2tag<-0;maxwwarn<-0;minwwarn<-0;maxzwarn<-0;minzwarn<-0
+  toomany<-0;wdich<-0;zdich<-0;wnotev<-0;znotev<-0;singlr<-0
+  nxpval<-1;nwpval<-1;nzpval<-1;errs<-1;notes<-1;criterr<-0
+  novar<-0;adjust<-0;ncs<-0;serial<-0;sobelok<-0;hasw<-0;ydich<-0;
+  hasz<-0;printw<-0;printz<-0;counterf<-0;wmodcust<-0;zmodcust<-0
+  booting<-0;bootiter<-0;iterrmod<-0;model<-trunc(model)
+  errcode<-matrix(0,100,1);notecode<-matrix(0,100,1)
+  iterate<-abs(trunc(iterate));converge=abs(converge);badend<-0;booterr<-0;
+  itprobtg<-0;v2tag<-0;maxwwarn<-0;minwwarn<-0;maxzwarn<-0
+  minzwarn<-0;toomany<-0;wdich<-0;zdich<-0;wnotev<-0;znotev<-0
+  nws<-0;nzs<-0;nms<-0;nys<-0;nxs<-0;maxresm<-9;bc<-as.numeric(bc==1);progress<-as.numeric(progress==1)
+  mcxok<-0;mcwok<-0;mczok<-0;xprod<-0;zprod<-0;wprod<-0;modcok<-0;alttotal=0;bc<-as.numeric(bc==1)
+  jn<-as.numeric(jn==1);effsize<-as.numeric(effsize==1);maxboots=abs(trunc(maxboot))
+  normal<-as.numeric(normal==1);xmtest<-as.numeric(xmtest==1);modelres<-as.numeric(modelres==1)
+  stand<-as.numeric(stand==1);outscreen<-as.numeric(outscreen==1);activate=as.numeric(activate==1)
+  describe<-as.numeric(describe==1);listmiss<-as.numeric(listmiss==1);
+  if (stand==1) {effsize<-1}
+  pstog<-0;sobelok<-0;mdichok=as.numeric(mdichok==1)
+  resultm<-matrix(99999,1,maxresm)
+
+  linsum<-t(matrix(linsum));
+  nlinsum<-ncol(linsum);
+  if (linsum[1,1]==-999){nlinsum<-0}
+
+  #contrast matrix
+  contrast<-matrix(contrast);
+  contrast<-t(contrast)
+  ncontr<-ncol(contrast)
+  if (contrast[1,1]==999) {ncontr<-1;contrast[1,1]<-0}
+  if (ncontr==1)
+  {
+    contrast<-trunc(contrast)
+    if ((contrast[1,1] > 2) | (contrast[1,1] < 0))
+    {ncontr<-1;contrast[1,1]<-0}
+  }
+  if (ncontr > 1)
+  {
+    contvec<-contrast;contrast[1,1]<-3
+    if (((model==2) | (model==3)) & (nms==0))
+    {
+      if (ncontr==4)
+      {
+        contvec<-t(matrix(contvec,2,2))
+        contrast[1,1]<-0;modcok<-1;wcontval<-matrix(contvec[,1]);zcontval<-matrix(contvec[,2])
+      }
+      if (ncontr !=4)
+      {
+        notecode[notes,1]<-19;notes<-notes+1
+        contrast[1,1]<-0
+      }
+    }
+  }
+  contrast<-contrast[1,1]
+  modelbt<-as.numeric(modelbt==1);matrices<-as.numeric(matrices==1)
+  covcoeff<-as.numeric(covcoeff==1);covmy<-trunc(covmy)
+  if ((covmy < 0) | (covmy > 2)) {covmy<-0} 
+  boot<-abs(trunc(boot));mc=abs(trunc(mc));hc=trunc(hc)
+  if ((intprobe < 0) | (intprobe > 1))
+  {intprobe<-0.10}
+  plot<-trunc(plot)
+  if ((plot < 0) | (plot > 2)) {plot<-0}
+  total<-as.numeric(total==1)
+  dototal<-0
+  saveboot<-as.numeric((save==1)|(save==3))
+  saveest<-as.numeric(save > 1)
+  if (saveest==1){intprobe=1}
+  if ((hc >=0) & (hc < 5)) {notecode[notes,1]=4;notes=notes+1}
+  if ((hc > 5) | (hc < 0)) {hc=5}
+  ####dont use these when y is dichotomous
+  hclab<-matrix(c("se(HC0)","se(HC1)","se(HC2)","se(HC3)","se(HC4)","se"))
+  hclab<-hclab[(hc+1),1]
+  hcflab<-matrix(c("F(HC0)","F(HC1)","F(HC2)","F(HC3)","F(HC4)","F"))
+  hcflab<-hcflab[(hc+1),1] 
+  mcw=trunc(mcw);mcz=trunc(mcz);mcx=trunc(mcx);
+  if ((mcx > 0) & (model==74)) {mcw=mcx}
+  if ((mcw > 0) & (model==74)) {mcx=mcw}
+  if ((mcx > 0) & (contrast > 0))
+  {notecode[notes,1]=28;notes=notes+1;contrast=0};
+  nxvls<-1;nmvls<-1;nwvls<-1;nzvls<-1
+  paths<-matrix(999);pathsw<-matrix(999);pathsz<-matrix(999);
+  pathswz<-matrix(999);pathsmod<-matrix(999);pathtype<-matrix(999);obscoeff<-999;
+  pathsdv=matrix(" ");quantile<-1;moments=as.numeric(moments==1)
+  if (moments==1){quantile<-0}
+  bmatrix=t(matrix(bmatrix));wmatrix=t(matrix(wmatrix));zmatrix=t(matrix(zmatrix));
+  wzmatrix=t(matrix(wzmatrix));cmatrix=t(matrix(cmatrix));xcatcode=t(matrix(xcatcode));
+  wcatcode=t(matrix(wcatcode));zcatcode=t(matrix(zcatcode));
+  needed<-0
+  decimals<-paste("%",decimals,"f",sep='')
+  if ((trunc(conf) >= 100) | (trunc(conf <= 50)))
+  {conf=95;notecode[notes,1]=2;notes=notes+1}
+  if ((model >= 0)  & (model < 4) & (modelbt==0)) {boot<-0;mc<-0;bc<-0;saveboot<-0}
+  if ((boot > 0) & (mc > 0)) {boot<-0;bc<-0}
+  if ((boot < 1000) & (boot > 0) & (mc==0)){boot=5000}
+  if ((mc < 1000) & (mc > 0) & (boot==0)){mc=5000}
+
+  #if ((model > 0) & (model < 4) & (boot = 98765) & (modelbt=1)) then;do;mc=0;boot=5000;end;
+  #if ((model > 0) & (model < 4) & ((boot = 98765) | (mc > 0))) then;do;boot=0;mc=0;bc=0;end;
+  #if ((boot = 98765) & (mc = 0)) then;do;boot=5000;end;
+
+  p0<- -.322232431088;p1<- -1;p2<- -.342242088547;p3<- -.0204231210245;
+  p4<- -.0000453642210148;q0<- .0993484626060;q1<- .588581570495;
+  q2<- .531103462366;q3<- .103537752850;q4<- .0038560700634;
+  priorlo<-(-9999999);priorhi<-9999999
+  alpha2<-(1-(conf/100))/2;cilm<-alpha2*2;y5<-sqrt(-2*log(alpha2));
+  xp2=(y5+((((y5*p4+p3)*y5+p2)*y5+p1)*y5+p0)/((((y5*q4+q3)*y5+q2)*y5+q1)*y5+q0))
+  medlb=matrix(c("   M1 :","   M2 :","   M3 :","   M4 :","   M5 :","   M6 :","   M7 :","   M8 :","   M9 :","  M10 :"))
+  medlb2=matrix(c("(M1)","(M2)","(M3)","(M4)","(M5)","(M6)","(M7)","(M8)","(M9)","(M10)"))
+  xlb=matrix(c("X1 :","X2 :","X3 :","X4 :","X5 :","X6 :","X7 :","X8 :","X9 :","X10:"))
+  highlbw=matrix(c("M1*W","M2*W","M3*W","M4*W","M5*W","M6*W","M7*W","M8*W","M9*W","M10*W"))
+  highlbz=matrix(c("M1*Z","M2*Z","M3*Z","M4*Z","M5*Z","M6*Z","M7*Z","M8*Z","M9*Z","M10*Z"))
+  highlbwz=matrix(c("M1*W*Z","M2*W*Z","M3*W*Z","M4*W*Z","M5*W*Z","M6*W*Z","M7*W*Z","M8*W*Z","M9*W*Z","M10*W*Z"))
+  highlbx=matrix(c("M1*X","M2*X","M3*X","M4*X","M5*X","M6*X","M7*X","M8*X","M9*X","M10*X"))
+  highlbbt=matrix(c("BOTH(M1)","BOTH(M2)","BOTH(M3)","BOTH(M4)","BOTH(M5)","BOTH(M6)","BOTH(M7)","BOTH(M8)","BOTH(M9)","BTH(M10)"))
+  skipwz=0
+  xnck=matrix(x);ynck=matrix(y);wnck=matrix(w);znck=matrix(z);mnck=matrix(m);cnck=matrix(cov)
+  if ((nrow(xnck)>1) | (nrow(ynck)>1) | (nrow(wnck)>1) | (nrow(znck)>1))
+  {errcode[errs,1]<-3;errs<-errs+1;criterr<-1}
+
+  validm=matrix(c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,0,0,1,1,0,0,0,0,
+                  0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,1,1,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1))
+  dim(validm)<-c(1,92)
+
+  # check for major errors in syntax
+  if (activate==1)
+  {errcode[errs,1]<-60;errs<-errs+1;criterr<-1}
+  if (criterr==0)
+  {
+    if ((model > 0) & (model < 93))
+    {
+      if (validm[1,model]==0)
+      {
+        errcode[errs,1]<-6;errs<-errs+1;criterr<-1
+      }
+    }
+    if (((model > 92) | (model < 0)) & (model != 999))
+    {errcode[errs,1]<-7;errs<-errs+1;criterr<-1}
+    if ((model==999) & (bmatrix[1,1]==-999))
+    {errcode[errs,1]<-24;errs<-errs+1;criterr<-1}
+    if ((model != 999) & (bmatrix[1,1] != -999))
+    {errcode[errs,1]<-25;errs<-errs+1;criterr<-1}
+    if (((model==74) | ((model > 0) & (model < 4))) & ((wmatrix[1,1] !=-999) | (zmatrix[1,1] != -999) | (wzmatrix[1,1] != -999)))
+    {errcode[errs,1]<-41;errs<-errs+1;criterr<-1}
+    if ((y=="xxxxx") | (x=="xxxxx"))
+    {errcode[errs,1]<-1;errs<-errs+1;criterr<-1}
+    if ((mnck[1,1]=="xxxxx") & (model > 3))
+    {errcode[errs,1]<-8;errs<-errs+1;criterr<-1}
+  } 
+  #end of check for major errors in syntax
+
+  #A loop reads data and does some other things
+
+  if (criterr==0)
+  {
+    #read y data
+    ytmp<-data[y];nys<-ncol(ytmp);needed<-nys
+    ynames<-matrix(y);n<-nrow(ytmp);varnames<-matrix(ynames)
+    dat<-ytmp
+    modelvar<-matrix(c(model,ynames))
+    if (model==999){modelvar[1,1]="CUSTOM"}
+
+    #read x data
+    xtmp<-data[x];
+    nxs<-ncol(xtmp);needed<-needed+nxs;
+    dat<-cbind(dat,xtmp)
+    xnames<-matrix(x);n<-nrow(xtmp);xcatlab<-xnames;
+    varnames<-matrix(c(varnames,xnames))
+    modelvar<-matrix(c(modelvar,xnames))
+    if (nxs==1){modelvlb<-matrix(c("Model :","    Y :","    X :"))}
+
+    #read m data
+    if (mnck[1,1] != "xxxxx")
+    {
+      mtmp<-data[m]
+      nms<-ncol(mtmp)
+      mnames<-matrix(m)
+      mprod<-matrix(0,1,nms)
+      n<-nrow(mtmp)
+      needed<-needed+nms
+      varnames<-matrix(c(varnames,mnames))
+      dat<-cbind(dat,mtmp)
+      modelvar<-matrix(c(modelvar,mnames))
+      x2m<-matrix(0,99,nms)
+      x2m<-matrix(0,99,nms)
+      x2y<-matrix(0,99,nms)
+      onem<-matrix(1,nms,1)
+      if ((nms > 1) & (nms < 11))
+      {modelvlb<-matrix(c(modelvlb,medlb[1:nms,1]))}
+      if (nms==1)
+      {modelvlb<-matrix(c(modelvlb,"    M :"))}
+      if ((nms > 0) & (model < 4)){errcode[errs,1]<-9;errs<-errs+1;criterr<-1}
+    }
+
+    #read w data
+    wlocatet<-0;wlocate<-0
+    if (w != "xxxxx")
+    {
+      wtmp<-data[w];nws=ncol(wtmp);n<-nrow(wtmp)
+      dat<-cbind(dat,wtmp)
+      wnames<-matrix(w);wcatlab<-wnames;
+      varnames<-matrix(c(varnames,wnames))
+      modelvar<-matrix(c(modelvar,wnames))
+      modelvlb<-matrix(c(modelvlb,"    W :"))
+      wlocate<-nrow(varnames)
+      if (model==74)
+      {
+        wlocatet<-1;
+        if (xnames != wnames)
+        {errcode[errs,1]<-45;errs<-errs+1;criterr<-1}
+      }     
+    }
+
+    #read z data
+    if (z != "xxxxx")
+    {
+      ztmp<-data[z];nzs<-ncol(ztmp);n<-nrow(ztmp);
+      dat<-cbind(dat,ztmp)
+      znames<-matrix(z);zcatlab<-znames;
+      varnames<-matrix(c(varnames,znames))
+      modelvar<-matrix(c(modelvar,znames))
+      modelvlb<-matrix(c(modelvlb,"    Z :"))
+    }
+
+    #read cov data
+    if (cnck[1,1] != "xxxxx")
+    {
+      ctmp<-data[cov];ncs<-ncol(ctmp);n<-nrow(ctmp);
+      dat<-cbind(dat,ctmp)
+      covnames<-matrix(cov);varnames<-matrix(c(varnames,covnames));  
+    }
+
+    if (((model==80) | (model==81)) & ((nms < 3) | (nms > 6)))
+    {errcode[errs,1]<-32;errs<-errs+1;criterr<-1}
+    if ((model==82) & (nms != 4))
+    {errcode[errs,1]<-33;errs<-errs+1;criterr<-1}
+    if (nms > 10)
+    {errcode[errs,1]<-37;errs<-errs+1;criterr<-1}
+    if (((model==6) | ((model > 82) & (model < 999))) & ((nms < 2) | (nms > 6)))
+    {errcode[errs,1]<-34;errs<-errs+1;criterr<-1}
+
+    #check for redundant variable names
+    match<-0;match2<-0;mcwzcov<-0
+    for (i in c(1:(nrow(varnames)-1)))
+    {
+      for (j in c((i+1):nrow(varnames)))
+      {
+        if (varnames[i]==varnames[j])
+        {
+          if (i < (nxs+nms+nys+1)){match2<-match2+1}
+          if ((wlocate==1) & (i==2) & (j==wlocate)){match2<-match2-1}
+          if ((wnames==znames) & ((nws > 0) | (nzs > 0))){match<-match2+1} 
+          if ((i < (nrow(varnames)-ncs+1)) & (j > (ncol(varnames)-ncs)))
+          {
+            if ((varnames[j]==wnames) & (mcw==0))
+            {match<-0;wiscov<-(j-(nrow(varnames)-ncs))}
+            if ((varnames[j]==wnames) & (mcw !=0)){mcwzcov<=0}
+            if ((varnames[j]==znames) & (mcz==0))
+            {match<-0;ziscov<-(j-nrow(varnames)-ncs)}
+            if ((varnames[j]==znames) & (mcz !=0)){mcwzcov<-0}
+          }
+        }
+      }
+    }  
+    if ((match2 > 0) | (match==1))
+    {errcode[errs,1]<-2;errs<-errs+1;criterr<-1}
+    if (mcwzcov==1)
+    {errcode[errs,1]<-50;errs<-errs+1;criterr<-1}
+
+    #check for factors
+    hello<-as.numeric(sapply(dat,is.factor))
+    nfacs<-sum(hello)
+    if (nfacs > 0){errcode[errs,1]<-53;errs<-errs+1;criterr<-1}
+
+    if (criterr==0)
+    {
+
+      #listwise deletion
+      ninit<-nrow(dat);rownum<-seq(1:nrow(dat));dat<-cbind(rownum,dat)
+      datms<-is.na(dat)
+      datms<-matrix(as.numeric(datms),nrow(datms))
+      datms<-matrix(rowSums(datms))
+      missrow<-0;
+      for (i in 1:ninit)
+      {if (datms[i,1] > 0){missrow<-cbind(missrow,i)}}
+      missrow<-matrix(missrow)
+      if (nrow(missrow) > 1)
+      {
+        missrow<-missrow[2:nrow(missrow)]
+        notecode[notes,1]<-29;
+        notes<-notes+1;
+      }
+      missrow<-t(matrix(missrow))
+      dat<-na.omit(dat);n<-nrow(dat);nmiss=ninit-n;
+      if (n < 5)
+      {errcode[errs,1]<-62;errs<-errs+1;criterr<-1}
+      if (criterr==0)
+        #startit
+      {
+        rownum<-dat[,1];dat<-dat[,2:ncol(dat)]
+        #extract the data back into vectors or matrices
+        ytmp=as.data.frame(dat[,1:nys])
+        desctmp2<-process.describ3(ytmp,0,quantile)
+        desctmp<-matrix(unlist(desctmp2[1]))
+        ysd<-desctmp[2,1];ovsd<-ysd;ydich<-0
+        if (desctmp[8,1]==2){errcode[errs,1]<-15;errs<-errs+1;criterr<-1;novar<-1}
+        if (desctmp[8,1]==1)
+        {
+          ydich<-1;
+          if (total==1){total<-0;notecode[notes,1]<-24;notes<-notes+1}
+          if (effsize==1){effsize<-0;notecode[notes,1]<-25;notes<-notes+1}
+          omx<-max(ytmp);omn<-min(ytmp)
+          ytmp<-matrix(as.numeric(ytmp==omx),ncol=nys)
+          dat[,1:nys]<-matrix(as.numeric(dat[,1:nys]==omx),ncol=nys)
+          rcd<-c(omn,omx,0,1);dim(rcd)<-c(2,2)
+        }
+        xtmp<-as.data.frame(dat[,(nys+1):(nys+nxs)])
+        desctmp2<-process.describ3(xtmp,0,quantile)
+        desctmp<-matrix(unlist(desctmp2[1]))
+        xsd<-desctmp[2,1]
+        if ((desctmp[8,1]==2) & (novar==0))
+        {errcode[errs,1]<-15;errs<-errs+1;criterr<-1;novar<-1}
+        xmodvals<-matrix(unlist(desctmp2[2]))
+        nxpval<-nrow(xmodvals)
+        xprobval<-as.matrix(xmodvals)
+        xdich<-desctmp[8,1]
+        if ((xdich==1) & (mcx > 0))
+        {mcx<-0;errcode[errs,1]<-52;errs<-errs+1;criterr<-1}
+        if ((model==74) & (xdich==1)){counterf==1}
+
+        #need to do m
+        if (nms > 0)
+        {
+          mtmp<-as.data.frame(dat[,(nys+nxs+1):(nys+nxs+nms)])
+          desctmp2<-process.describ3(mtmp,0,quantile)
+          desctmp<-matrix(unlist(desctmp2[1]),ncol=ncol(mtmp))
+          ovsd<-matrix(c(desctmp[2,],ysd))
+          zzzz<-rowSums(desctmp)
+          if ((zzzz[8]>0) & (mdichok != 1))
+          {errcode[errs,1]<-43;errs<-errs+1;criterr<-1}   
+          mmodvals<-matrix(unlist(desctmp2[2]),ncol=ncol(mtmp))
+          mprobval<-mmodvals
+
+        }
+
+        if (nws > 0)
+        {
+          wtmp<-as.data.frame(dat[,(nys+nxs+nms+1):(nys+nxs+nms+nws)])
+          desctmp2<-process.describ3(wtmp,0,quantile)
+          desctmp<-matrix(unlist(desctmp2[1]))
+          if ((desctmp[8,1]==2) & (novar==0))
+          {errcode[errs,1]<-15;errs<-errs+1;criterr<-1;novar<-1}
+          wmodvals<-matrix(unlist(desctmp2[2]))
+          wdich<-desctmp[8,1]
+          if ((wdich==1) & (mcw > 0))
+          {mcw<-0;errcode[errs,1]<-52;errs<-errs+1;criterr<-1}
+          wmin<-desctmp[3,1]
+          wmax<-desctmp[4,1] 
+          minwwarn<-matrix(unlist(desctmp2[3]));maxwwarn<-matrix(unlist(desctmp2[4]))
+          wnotev<-matrix(unlist(desctmp2[5]))
+          wmodval<-t(matrix(wmodval))
+          nwcontr<-ncol(wmodval)
+          if (wmodval[1,1] != 999)
+          {
+            wmodvals<-matrix(wmodval[1,1]);wmodcust<-1
+            if (nwcontr > 1){wmodvals<-t(wmodval)}
+            minwwarn<-0;maxwwarn<-0;wnotev<-0
+          }
+          wprobval<-as.matrix(wmodvals)
+          nwpval<-nrow(wmodvals)
+        }
+
+        if (nzs > 0)
+        {
+          ztmp<-as.data.frame(dat[,(nys+nxs+nms+nws+1):(nys+nxs+nms+nws+nzs)])
+          desctmp2<-process.describ3(ztmp,0,quantile)
+          desctmp<-matrix(unlist(desctmp2[1]))
+          if ((desctmp[8,1]==2) & (novar==0))
+          {errcode[errs,1]<-15;errs<-errs+1;criterr<-1;novar<-1}
+          zmodvals<-matrix(unlist(desctmp2[2]))
+          zdich<-desctmp[8,1]
+          if ((zdich==1) & (mcz > 0))
+          {mcz<-0;errcode[errs,1]<-52;errs<-errs+1;criterr<-1}
+          zmin<-desctmp[3,1]
+          zmax<-desctmp[4,1] 
+          minzwarn<-matrix(unlist(desctmp2[3]));maxzwarn<-matrix(unlist(desctmp2[4]));
+          znotev<-matrix(unlist(desctmp2[5]))
+          zmodval<-t(matrix(zmodval))
+          nzcontr<-ncol(zmodval)
+          if (zmodval[1,1] != 999)
+          {
+            zmodvals<-matrix(zmodval[1,1]);zmodcust<-1
+            if (nzcontr > 1){zmodvals<-t(zmodval)}
+            minzwarn<-0;maxzwarn<-0;znotev<-0
+          }
+          zprobval<-as.matrix(zmodvals)
+          nzpval<-nrow(zmodvals)
+        }
+        if (ncs > 0)
+        {
+          ctmp<-as.data.frame(dat[,(nys+nxs+nms+nws+nzs+1):(nys+nxs+nms+nws+nzs+ncs)])
+          covmean2<-process.describ3(ctmp,1,quantile)
+          covmeans<-matrix(unlist(covmean2[1]),ncol=ncs);covmeans<-matrix(covmeans[1,],nrow=1)
+        }
+        n<-nrow(ytmp)
+        ones<-matrix(1,n,1)
+        modresid<-matrix(9999,n,1)
+        #creat codes for categorical variables
+        if ((nws > 0) & (mcw > 0))
+        {
+          tmp<-cbind(rownum,wtmp[,1])
+          dumtmp<-process.makdummy(tmp,mcw,2,wcatcode)
+          wmodvals<-matrix(unlist(dumtmp[4]))
+          nwpval<-nrow(wmodvals)
+          errcode4<-unlist(dumtmp[5])
+          errcode5<-unlist(dumtmp[6])
+          errcode6<-unlist(dumtmp[7])
+          if (errcode4==1){errcode[errs,1]<-4;errs<-errs+1;criterr<-1}
+          if (errcode5==1){errcode[errs,1]<-5;errs<-errs+1;criterr<-1}
+          if (errcode6==1){errcode[errs,1]<-39;errs<-errs+1;criterr<-1}   
+          if (criterr==0)
+          {
+            nvls<-unlist(dumtmp[3])
+            nwvls<-nvls-1
+            minwwarn<-0;maxwwarn<-0;wnotev<-0
+            wtmp<-matrix(unlist(dumtmp[1]),ncol=(nwvls+1))
+            wtmp<-wtmp[,2:ncol(wtmp)];wtmp<-as.data.frame(wtmp)
+            wcatlab<-c("W1","W2","W3","W4","W5","W6","W7","W8","W9");wcatlab<-matrix(wcatlab)
+            mcwok<-1
+            dummatw<-matrix(unlist(dumtmp[2]),ncol=(nwvls+1),nrow=(nwvls+1))
+            wprobval<-dummatw[,2:ncol(dummatw)]
+            if (modcok==1)
+            {
+              wcontval<-matrix(-999,2,ncol(wprobval))
+              temp<-0
+              for (i in (1:2))
+              {
+                for (j in (1:nrow(dummatw)))
+                {
+                  if (contvec[i,1]==dummatw[j,1])
+                  {wcontval[i,]<-wprobval[j,];temp<-temp+1}
+                }
+              }
+              if (temp < 2)
+              {notecode[notes,1]<-20;notes<-notes+1;modcok<-0}
+            }
+            if (wmodval[1,1] != 999)
+            {notecode[notes,1]<-9;notes<-notes+1}
+          }
+        }
+        if ((nzs > 0) & (mcz > 0))
+        {
+          tmp<-cbind(rownum,ztmp[,1])
+          dumtmp<-process.makdummy(tmp,mcz,3,zcatcode)
+          zmodvals<-matrix(unlist(dumtmp[4]))
+          nzpval<-nrow(zmodvals)
+          errcode4<-unlist(dumtmp[5])
+          errcode5<-unlist(dumtmp[6])
+          errcode6<-unlist(dumtmp[7])
+          if (errcode4==1){errcode[errs,1]<-4;errs<-errs+1;criterr<-1}
+          if (errcode5==1){errcode[errs,1]<-5;errs<-errs+1;criterr<-1}
+          if (errcode6==1){errcode[errs,1]<-40;errs<-errs+1;criterr<-1}
+          if (criterr==0)
+          {
+            nvls<-unlist(dumtmp[3])
+            nzvls<-nvls-1
+            minzwarn<-0;maxzwarn<-0;znotev<-0
+            ztmp<-matrix(unlist(dumtmp[1]),ncol=(nzvls+1))
+            ztmp<-ztmp[,2:ncol(ztmp)];ztmp<-as.data.frame(ztmp)
+            zcatlab<-c("Z1","Z2","Z3","Z4","Z5","Z6","Z7","Z8","Z9");zcatlab=matrix(zcatlab)
+            mczok<-1
+            dummatz<-matrix(unlist(dumtmp[2]),ncol=(nzvls+1),nrow=(nzvls+1))
+            zprobval<-dummatz[,2:ncol(dummatz)]
+            if (modcok==1)
+            {
+              zcontval<-matrix(-999,2,ncol(zprobval))
+              temp<-0
+              for (i in (1:2))
+              {
+                for (j in (1:nrow(dummatz)))
+                {
+                  if (contvec[i,2]==dummatz[j,1])
+                  {zcontval[i,]<-zprobval[j,];temp<-temp+1}
+                }
+              }
+              if (temp < 2)
+              {notecode[notes,1]<-20;notes<-notes+1;modcok<-0}
+            }
+            if (zmodval[1,1] != 999)
+            {notecode[notes,1]<-10;notes<-notes+1}
+          }
+        }
+        if ((nxs > 0) & (mcx > 0))
+        {
+          tmp<-cbind(rownum,xtmp[,1])
+          dumtmp<-process.makdummy(tmp,mcx,1,xcatcode)
+          errcode4<-unlist(dumtmp[5])
+          errcode5<-unlist(dumtmp[6])
+          errcode6<-unlist(dumtmp[7])
+          if (errcode4==1){errcode[errs,1]<-4;errs<-errs+1;criterr<-1}
+          if (errcode5==1){errcode[errs,1]<-5;errs<-errs+1;criterr<-1}
+          if (errcode6==1){errcode[errs,1]<-38;errs<-errs+1;criterr<-1}
+          if (criterr==0)
+          {
+            nvls<-unlist(dumtmp[3])
+            nxvls<-nvls-1
+            xtmp<-matrix(unlist(dumtmp[1]),ncol=(nxvls+1))
+            xtmp<-xtmp[,2:ncol(xtmp)];xtmp<-as.data.frame(xtmp)
+            xcatlab<-c("X1","X2","X3","X4","X5","X6","X7","X8","X9");xcatlab=matrix(xcatlab)
+            xdich<-as.numeric(nvls==2)
+            mcxok<-1
+            dummatx<-matrix(unlist(dumtmp[2]),ncol=(nxvls+1),nrow=(nxvls+1))
+            xmodvals<-as.matrix(dummatx[,1])
+            nxpval<-nrow(xmodvals)
+          }
+        }
+        intlab<-matrix(" ",100,1)
+        for (i in c(1:100)){intlab[i,1]<-paste("Int_",i,sep='')}
+        bcmat<-matrix(0,needed,needed)
+        wcmat<-matrix(0,needed,needed)
+        zcmat<-matrix(0,needed,needed)
+        wzcmat<-matrix(0,needed,needed)
+        wsum<-0;zsum<-0;wzsum<-0
+      }
+    }
+
+  }
+  #endit
+
+  # End A loop reads data and does some other things
+
+  # Define model matrices for canned models
+  if ((criterr==0) & (model != 999))
+  { 
+    # X->MW, X->MZ, X->MWZ, M->YW, M->YZ, M->YWZ, X->YW, X->YZ, X->YWZ
+    modelmat<-
+      matrix(c(1,0,0,0,0,0,0,1,0,0,2,0,0,0,0,0,0,1,1,0,3,0,0,0,0,0,0,1,1,1,4,0,0,0,0,0,0,0,0,0,
+               5,0,0,0,0,0,0,1,0,0,6,0,0,0,0,0,0,0,0,0,7,1,0,0,0,0,0,0,0,0,8,1,0,0,0,0,0,1,0,0,
+               9,1,1,0,0,0,0,0,0,0,10,1,1,0,0,0,0,1,1,0,11,1,1,1,0,0,0,0,0,0,12,1,1,1,0,0,0,1,1,1,
+               13,1,1,1,0,0,0,1,0,0,14,0,0,0,1,0,0,0,0,0,15,0,0,0,1,0,0,1,0,0,16,0,0,0,1,1,0,0,0,0,
+               17,0,0,0,1,1,0,1,1,0,18,0,0,0,1,1,1,0,0,0,19,0,0,0,1,1,1,1,1,1,20,0,0,0,1,1,1,1,0,0,
+               21,1,0,0,0,1,0,0,0,0,22,1,0,0,0,1,0,1,0,0,23,0,0,0,0,0,0,0,0,0,24,0,0,0,0,0,0,0,0,0,
+               25,0,0,0,0,0,0,0,0,0,26,0,0,0,0,0,0,0,0,0,27,0,0,0,0,0,0,0,0,0,28,1,0,0,0,1,0,0,1,0,
+               29,1,0,0,0,1,0,1,1,0,30,0,0,0,0,0,0,0,0,0,31,0,0,0,0,0,0,0,0,0,32,0,0,0,0,0,0,0,0,0,
+               33,0,0,0,0,0,0,0,0,0,34,0,0,0,0,0,0,0,0,0,35,0,0,0,0,0,0,0,0,0,36,0,0,0,0,0,0,0,0,0,
+               37,0,0,0,0,0,0,0,0,0,38,0,0,0,0,0,0,0,0,0,39,0,0,0,0,0,0,0,0,0,40,0,0,0,0,0,0,0,0,0,
+               41,0,0,0,0,0,0,0,0,0,42,0,0,0,0,0,0,0,0,0,43,0,0,0,0,0,0,0,0,0,44,0,0,0,0,0,0,0,0,0,
+               45,0,0,0,0,0,0,0,0,0,46,0,0,0,0,0,0,0,0,0,47,0,0,0,0,0,0,0,0,0,48,0,0,0,0,0,0,0,0,0,
+               49,0,0,0,0,0,0,0,0,0,50,0,0,0,0,0,0,0,0,0,51,0,0,0,0,0,0,0,0,0,52,0,0,0,0,0,0,0,0,0,
+               53,0,0,0,0,0,0,0,0,0,54,0,0,0,0,0,0,0,0,0,55,0,0,0,0,0,0,0,0,0,56,0,0,0,0,0,0,0,0,0,
+               57,0,0,0,0,0,0,0,0,0,58,1,0,0,1,0,0,0,0,0,59,1,0,0,1,0,0,1,0,0,60,1,1,0,1,0,0,0,0,0,
+               61,1,1,0,1,0,0,1,0,0,62,1,1,0,1,0,0,0,1,0,63,1,1,0,1,0,0,1,1,0,64,1,0,0,1,1,0,0,0,0,
+               65,1,0,0,1,1,0,1,0,0,66,1,0,0,1,1,0,0,1,0,67,1,0,0,1,1,0,1,1,0,68,1,1,1,1,0,0,0,0,0,
+               69,1,1,1,1,0,0,1,1,1,70,1,0,0,1,1,1,0,0,0,71,1,0,0,1,1,1,1,1,1,72,1,1,1,1,1,1,0,0,0,
+               73,1,1,1,1,1,1,1,1,1,74,0,0,0,1,0,0,0,0,0,75,1,1,0,1,1,0,0,0,0,76,1,1,0,1,1,0,1,1,0,
+               77,0,0,0,0,0,0,0,0,0,78,0,0,0,0,0,0,0,0,0,79,0,0,0,0,0,0,0,0,0,80,0,0,0,0,0,0,0,0,0,
+               81,0,0,0,0,0,0,0,0,0,82,0,0,0,0,0,0,0,0,0,83,1,0,0,0,0,0,0,0,0,84,1,0,0,0,0,0,0,0,0,
+               85,1,0,0,0,0,0,1,0,0,86,1,0,0,0,0,0,1,0,0,87,0,0,0,1,0,0,0,0,0,88,0,0,0,1,0,0,0,0,0,
+               89,0,0,0,1,0,0,1,0,0,90,0,0,0,1,0,0,1,0,0,91,0,0,0,0,0,0,0,0,0,92,1,0,0,1,0,0,1,0,0))
+    dim(modelmat)<-c(10,92);modelmat=t(modelmat);
+    if (model > 0){tmp<-modelmat[model,2:ncol(modelmat)];tmp=t(matrix(tmp))}
+    if (model == 0){tmp<-matrix(0,1,9)}
+    if (model < 4) {bcmat[(nxs+1),1]<-1}
+    if ((model > 3) & (model != 6))
+    {bcmat[(nxs+1):(nxs+nms),1]<-onem
+    bcmat[nrow(bcmat),(nxs+1):(nxs+nms)]<-t(onem)
+    bcmat[nrow(bcmat),1]<-1}
+    if ((model==6) | ((model > 82) & (model < 93)))
+    {
+      for (j in c(2:nrow(bcmat)))
+      {for (i in c(1:(j-1)))
+      {bcmat[j,i]<-1}
+      }
+    } 
+    if (model==80)
+    {for (i in c(1:nms)){bcmat[(nrow(bcmat)-1),i]<-1}}
+    if (model==81)
+    {for (j in c(3:nrow(bcmat))){bcmat[j,2]<-1}}
+    if (model==82)
+    {bcmat[3,2]<-1;bcmat[5,4]<-1}
+    if (tmp[1,1]==1)
+    {
+      wcmat[(nxs+1):(nxs+nms),1]=onem;wprod<-1;xprod<-1
+      if ((model==83) | (model==86))
+      {onemsx<-onem
+      for (i in c(1:(nms-1))){onemsx[(i+1),1]<-0}
+      wcmat[(nxs+1):(nxs+nms),1]<-onemsx
+      } 
+    }
+    if (tmp[1,4]==1)
+    {
+      wcmat[nrow(wcmat),(nxs+1):(nxs+nms)]<-t(onem);wprod<-1;
+      if ((model==87) | (model==90))
+      {onemsx<-onem
+      for (i in c(1:(nms-1))){onemsx[i,1]=0}
+      wcmat[nrow(wcmat),(nxs+1):(nxs+nms)]=t(onemsx)
+      }
+    }
+    if (tmp[1,7]==1){wcmat[nrow(wcmat),1]<-1;wprod<-1;xprod<-1}
+    if (tmp[1,2]==1){zcmat[(nxs+1):(nxs+nms),1]<-onem;zprod<-1;xprod<-1}
+    if (tmp[1,5]==1){zcmat[nrow(zcmat),(nxs+1):(nxs+nms)]=t(onem);zprod<-1}
+    if (tmp[1,8]==1){zcmat[nrow(zcmat),1]<-1;zprod<-1;xprod<-1}
+    if (tmp[1,3]==1){wzcmat[(nxs+1):(nxs+nms),1]<-onem;xprod<-1;wprod<-1;zprod<-1}
+    if (tmp[1,6]==1){wzcmat[nrow(wzcmat),(nxs+1):(nxs+nms)]<-t(onem)}
+    if (tmp[1,9]==1){wzcmat[nrow(wzcmat),1]<-1;xprod<-1;wprod<-1;zprod<-1}
+    if ((model==91) | (model==92))
+    {
+      for (j in c(1:(nms-1)))
+      {for (i in c(1:j)){wcmat[(nxs+1+j),(nxs+i)]<-1}
+      }
+    }
+  }
+  #define and check covariates matrix
+  if (ncs > 0)
+  {
+    ccmat<-matrix(1,(nms+nys),ncs);ccmatoff<-ccmat
+    if (covmy==1){ccmat[nrow(ccmat),]<-matrix(0,1,ncs)}
+    if (covmy==2){ccmat[1:nms,]<-matrix(0,nms,ncs)}
+    if (cmatrix[1,1] != -999)
+    {if (ncol(cmatrix) != ((nms+nys)*ncs)){errcode[errs,1]<-29;errs<-errs+1;criterr<-1}
+      if (criterr==0)
+      {
+        tmp<-1;for (i in c(1:(nms+nys)))
+        {
+          for (j in c(1:ncs))
+          {ccmat[i,j]<-(1-as.numeric(cmatrix[1,tmp]==0));tmp<-tmp+1}
+        }
+        tmpcov<-colSums(ccmat);tmpcov<-as.numeric(tmpcov==0);tmpcov<-sum(tmpcov)
+        if (tmpcov !=0)
+        {errcode[errs,1]<-30;errs<-errs+1;criterr<-1}
+      }
+      if (covmy != 0){notecode[notes,1]<-1;notes<-notes+1}
+    } 
+  }
+
+  #Define matrices for custom models and do some error checking
+  if (criterr==0)
+  {
+    needed<-needed*(needed-1)/2;nopath<-0
+    if (bmatrix[1,1] != -999)
+    {tmp<-1
+    if ((ncol(bmatrix) != needed) | (sum(bmatrix)==0))
+    {errcode[errs,1]<-16;errs<-errs+1;criterr<-1} else {
+      for (i in c(2:nrow(bcmat)))
+      {for (j in c(1:(i-1)))
+      {bcmat[i,j]<-(1-as.numeric(bmatrix[1,tmp]==0));tmp<-tmp+1}        
+      } 
+    }
+    #check to make sure X affects something */
+    tmpcov<-sum(bcmat[,1])
+    if ((tmpcov==0) & (criterr==0))
+    {errcode[errs,1]<-22;errs<-errs+1;criterr<-1}
+    #check to make sure Y is affected by something */
+    tmpcov<-sum(bcmat[nrow(bcmat),])
+    if ((tmpcov==0) & (criterr==0))
+    {errcode[errs,1]<-23;errs<-errs+1;criterr<-1}
+    #check for dangling mediators
+    dm<-0
+    if (nms > 0)
+    {
+      for (i in c(1:nms))
+        tmpcov<-sum(bcmat[(nxs+i),]);tmpcov2<-sum(bcmat[,(nxs+i)])
+        {if (((tmpcov==0) | (tmpcov2==0)) & (dm==0) & (criterr==0))
+        {errcode[errs,1]<-26;errs<-errs+1;criterr<-1;dm<-1}       
+        }
+    }
+    }
+  }
+
+  #start b
+  if (criterr==0)
+  {
+    if (wmatrix[1,1] != -999)
+    {
+      tmp<-1
+      if (ncol(wmatrix) != needed)
+      {errcode[errs,1]<-17;errs<-errs+1;criterr<-1} else { 
+        modelvar[1,1]="CUSTOM"
+        for (i in (2:nrow(wcmat)))
+        {     
+          for (j in (1:(i-1)))       
+          {wcmat[i,j]<-(1-as.numeric(wmatrix[1,tmp]==0))
+          #dont allow to specify moderation of a path that doesnt exist
+          if ((wcmat[i,j]==1) & (bcmat[i,j]==0) & (nopath==0))
+          {errcode[errs,1]<-20;errs<-errs+1;criterr<-1;nopath<-1}   
+          tmp<-tmp+1
+          }
+        } 
+      }
+    }
+
+    if (zmatrix[1,1] != -999)
+    {
+      tmp<-1
+      if (ncol(zmatrix) != needed)
+      {errcode[errs,1]<-18;errs<-errs+1;criterr<-1} else {
+        modelvar[1,1]="CUSTOM"
+        if ((sum(wcmat)==0) & (model==999))
+        {errcode[errs,1]<-21;errs<-errs+1;criterr<-1}
+        for (i in (2:nrow(zcmat)))
+        {     
+          for (j in (1:(i-1)))       
+          {zcmat[i,j]<-(1-as.numeric(zmatrix[1,tmp]==0))
+          #dont allow to specify moderation of a path that doesnt exist
+          if ((zcmat[i,j]==1) & (bcmat[i,j]==0) & (nopath==0))
+          {errcode[errs,1]<-20;errs<-errs+1;criterr<-1;nopath<-1}   
+          tmp<-tmp+1
+          }
+        } 
+      }
+    }
+    tmp<-1
+    if (wzmatrix[1,1] != -999)
+    {
+      if (ncol(wzmatrix) != needed)
+      {errcode[errs,1]<-19;errs<-errs+1;criterr<-1}
+      modelvar[1,1]="CUSTOM"
+    } 
+    if (criterr==0)
+    {
+      for (i in (2:nrow(wzcmat)))
+      {
+        for (j in (1:(i-1)))
+        {
+          #set corresponding elements in W and Z for three way interaction
+          if (wzmatrix[1,1] != -999){wzcmat[i,j]<-(1-as.numeric(wzmatrix[1,tmp]==0))}
+          if (wzcmat[i,j]==1){wcmat[i,j]<-1;zcmat[i,j]<-1}       
+          #dont allow to specify moderation of a path that doesnt exist
+          if ((wzcmat[i,j]==1) & (bcmat[i,j]==0) & (nopath==0))
+          {errcode[errs,1]<-20;errs<-errs+1;criterr<-1;nopath<-1}
+          tmp<-tmp+1
+        }
+      }
+    }
+  }
+  # end B
+
+  if (criterr==0)
+  {
+    xprod<-(sum(wcmat[,1])+sum(zcmat[,1])+sum(wzcmat[,1]))
+    xprod<-as.numeric(xprod > 0)
+    wsum<-sum(wcmat)
+    wprod<-as.numeric(wsum > 0)
+    if (nms > 0)
+    {
+      for (i in c(1:nms))
+      {
+        tmp<-(sum(wcmat[,(1+i)])+sum(zcmat[,(1+i)])+sum(wzcmat[,(1+i)]))
+        mprod[1,i]<-as.numeric(tmp>0)
+      }
+    }
+    if ((wsum > 0) & (w=="xxxxx")){errcode[errs,1]<-11;errs<-errs+1;criterr<-1}
+    if ((wsum==0) & (w != "xxxxx")){errcode[errs,1]<-10;errs<-errs+1;criterr<-1}
+    zsum<-sum(zcmat)
+    zprod<-as.numeric(zsum > 0)
+    if ((zsum > 0) & (z=="xxxxx")){errcode[errs,1]<-13;errs<-errs+1;criterr<-1}
+    if ((zsum==0) & (z != "xxxxx")){errcode[errs,1]<-12;errs<-errs+1;criterr<-1}
+    if ((zsum > 0) & (wsum==0)){errcode[errs,1]<-35;errs<-errs+1;criterr<-1}
+  }
+  if ((criterr==0) & (nms > 1))
+  {
+    serchk<-bcmat[2:(nrow(bcmat)-1),2:ncol(bcmat)]
+    if (sum(serchk) > 0)
+    {serial<-1
+    if (nms > 6){errcode[errs,1]<-36;errs<-errs+1;criterr<-1}
+    }
+  }
+  #mean center if needed
+  if ((center > 0) & (criterr==0))
+  {
+    centvar<-matrix(c(" "))
+    if (criterr==0)
+    {
+      if ((center==1) | ((center==2) & (wdich==0)))
+      {
+        if ((wprod==1) & (mcwok==0) & (nwpval > 0))
+        {
+          for (i in c(1:nws))
+          {
+            wtmp[,i]<-wtmp[,i]-(sum(wtmp[,i])/n)
+            centvar<-cbind(centvar,wnames[1,i])
+          }
+          desctmp2<-process.describ3(wtmp,wmodcust,quantile)
+          desctmp<-matrix(unlist(desctmp2[1]))
+          wmin<-desctmp[3,1];wmax<-desctmp[4,1]
+          if (wmodcust==0)
+          {modvals<-matrix(unlist(desctmp2[2]))
+          wmodvals<-modvals;wprobval<-wmodvals}
+        }
+      }    
+      if ((center==1) | ((center==2) & (zdich==0)))
+      { 
+        if ((zprod==1) & (mczok==0) & (nzpval > 0))
+        {
+          for (i in c(1:nzs))
+          {
+            ztmp[,i]<-ztmp[,i]-(sum(ztmp[,i])/n)
+            centvar<-cbind(centvar,znames[1,i])
+          }
+          desctmp2<-process.describ3(ztmp,zmodcust,quantile)
+          desctmp<-matrix(unlist(desctmp2[1]))
+          zmin<-desctmp[3,1];zmax<-desctmp[4,1]
+          if (zmodcust==0)
+          {modvals<-matrix(unlist(desctmp2[2]))
+          zmodvals<-modvals;zprobval<-zmodvals}
+        }
+      }
+      if ((center==1) | ((center==2) & (xdich==0)))
+      {
+        if ((xprod==1) & (mcxok==0))
+        {
+          for (i in c(1:nxs))
+          {
+            xtmp[,i]<-xtmp[,i]-(sum(xtmp[,i])/n)
+            centvar<-cbind(centvar,xnames[1,i])
+          }
+          desctmp2<-process.describ3(xtmp,0,quantile)
+          modvals<-matrix(unlist(desctmp2[2]))
+          xmodvals<-modvals;xprobval<-as.matrix(xmodvals)
+        }
+      }
+      if (nms > 0)
+      {
+        for (i in c(1:nms))
+        {
+          if (mprod[1,i]==1)
+          {
+            mtmp[,i]<-mtmp[,i]-(sum(mtmp[,i])/n)
+            centvar<-cbind(centvar,mnames[i,1])
+          }
+        }
+        desctmp2<-process.describ3(mtmp,0,quantile)
+        modvals<-matrix(unlist(desctmp2[2]),ncol=ncol(mtmp))
+        mmodvals<-modvals;mprobval<-mmodvals;
+      }
+    }
+    if (ncol(centvar) > 1)
+    {notecode[notes,1]<-3;notes<-notes+1}
+  }
+  # Start D
+  #CONSTRUCT THE DATA MATRICES FOR EACH OF THE MODELS
+  if (criterr==0)
+  {
+    # The i loop is the dependent variable in the model matrices
+    # The j loop is the predictor variables in the model matrices
+    wsum<-sum(wcmat);zsum<-sum(zcmat);wzsum<-sum(wzcmat)
+    nump<-matrix(-999,1,(nys+nms));numint<-matrix(0,1,(nys+nms))
+    #DV
+    datcount<-1;
+    xtmpuse<-0;wtmpuse<-0;ztmpuse<-0;xwtmpus<-0;xztmpus<-0;wztmpus<-0;xwztmpu<-0;
+    xtmploc<- matrix(-999);wtmploc<- -999;xwtmplo<- -999;ztmploc<- -999
+    xztmplo<- -999;wztmplo<- -999;xwztmplo<- -999
+    vlabs<-" "
+    if (ncs > 0){ctmpuse<-matrix(0,1,ncs)}
+    if (nms > 0)
+    {
+      mtmpuse<-matrix(0,1,nms)
+      mwtmpus<-matrix(0,1,nms)
+      mztmpus<-matrix(0,1,nms)
+      mwztmpu<-matrix(0,1,nms)
+      mtmploc<-matrix(0,1,nms)
+      mwtmplo<-matrix(-999,nwvls,nms)
+      mztmplo<-matrix(-999,nzvls,nms)
+      mwztmplo<-matrix(-999,(nwvls*nzvls),nms)
+    }
+    if (ncs > 0){ctmploc<-matrix(0,1,ncs)}
+    fulldat<-matrix(1,n,1)
+    datindx<-matrix(-999,1000,(nms+nys))
+    wherew<-matrix(-999,2,(nms+nys));wherex<-matrix(-999,2,(nms+nys))
+    wherez<-matrix(-999,2,(nms+nys));wherexw<-matrix(-999,2,(nms+nys))
+    wherexz<-matrix(-999,2,(nms+nys));wherewz<-matrix(-999,2,(nms+nys))
+    wherexwz<-matrix(-999,2,(nms+nys))
+    if (nms > 0)
+    {
+      wherem<-matrix(-999,nms,(nms+nys))
+      wheremw<-matrix(-999,(nms*2),(nms+nys))
+      wheremz<-matrix(-999,(nms*2),(nms+nys))
+      wheremwz<-matrix(-999,(nms*2),(nms+nys))
+    }  
+    wzhigh<-matrix(0,1000,(((nms+1)*(nms+2))/2))
+    whigh<-matrix(0,1000,(((nms+1)*(nms+2))/2))
+    zhigh<-matrix(0,1000,(((nms+1)*(nms+2))/2))
+    fochigh<-matrix(0,1000,(((nms+1)*(nms+2))/2))
+    xcoefloc<-matrix(c(1,2,3,4,5,6,7,8,9))
+    intkey<-t(matrix(c(" ", " ", " ", " ", " ", " ", " ")))
+    wzhighct<-0;whighct<-0;zhighct<-0;foccnt<-0
+    if (nms > 0){mnames<-t(mnames)}
+    if (ncs > 0){covnames<-t(covnames)}
+    xtmp<-data.matrix(xtmp)
+
+    #START DV LOOP
+    for (i in (2:nrow(bcmat)))
+    {  
+      wdid<-0;zdid<-0;wzdid<-0;cntmp<-1;start<-1;
+      if (i < nrow(bcmat))
+      {outv<-mtmp[,(i-1)]  
+      modlabel<-matrix(c(mnames[1,(i-1)],"constant"))}
+      if (i==nrow(bcmat))
+      {outv<-ytmp;modlabel<-matrix(c(ynames,"constant"))}
+      # The j loop is the mediator
+      # START MED
+
+      for (j in (1:(i-1)))
+      {
+        foccnt<-foccnt+1
+        if ((j==1) & (bcmat[i,j]==1))
+        {
+          outv<-cbind(outv,xtmp)
+          modlabel<-matrix(c(modlabel,xcatlab[1:nxvls,1]))
+          if (xtmpuse==0)
+          {
+            fulldat<-matrix(c(fulldat,xtmp),nrow=n)
+            xtmpuse<-1
+            for (k4 in (datcount:(datcount+(nxvls-1))))
+            {xtmploc<-matrix(c(xtmploc,k4))}
+            xtmploc<-matrix(xtmploc[2:nrow(xtmploc),1])
+            datcount<-datcount+nxvls
+          }
+          datindx[start:(start+nrow(xtmploc)-1),(i-1)]<-xtmploc
+          wherex[1,(i-1)]<-start+1
+          wherex[2,(i-1)]<-start+nrow(xtmploc)-1+1
+          #do if (model = 74)
+          #end if
+          onebl<-matrix(1,nrow(xtmploc),1)
+          fochigh[(start+1):(start+nrow(xtmploc)),foccnt]<-onebl
+          start<-start+nrow(xtmploc)
+        }  
+        if ((j > 1) & (bcmat[i,j]==1))
+        {
+          outv<-cbind(outv,mtmp[,(j-1)])
+          modlabel<-matrix(c(modlabel,mnames[1,(j-1)]))
+          if (mtmpuse[1,(j-1)]==0)
+          {
+            fulldat<-matrix(c(fulldat,mtmp[,(j-1)]),nrow=n)
+            mtmpuse[1,(j-1)]<-1
+            mtmploc[1,(j-1)]<-datcount
+            datcount<-datcount+1
+          }
+          datindx[start:(start+nrow(mtmploc)-1),(i-1)]<-mtmploc[1,(j-1)]
+          wherem[(j-1),(i-1)]<-start+1
+          #onebl<-matrix(1,(nrow(mtmploc[1,(j-1)])),1)
+          #onebl<-matrix(1,mtmploc[1,(j-1)],1)
+          onebl<-1
+          #ttt<-nrow(mtmploc[1,(j-1)])+start-1
+          #fochigh[(start+1):(start+nrow(mtmploc[1,(j-1)])),foccnt]<-onebl
+          #fochigh[(start+1):(start+mtmploc[1,(j-1)]),foccnt]<-onebl
+          fochigh[(start+1):(start+1),foccnt]<-onebl
+          #start<-start+mtmploc[1,(j-1)]
+          start<-start+1
+        }
+      }
+      #END MED
+
+      #START W
+      if (wsum > 0)
+        wtmp<-data.matrix(wtmp)
+      {
+        for (j in c(1:(i-1)))
+        {
+          whighct<-whighct+1
+          if ((j==1) & (wcmat[i,j]==1))
+          {
+            if (wdid==0)
+            {
+              outv<-cbind(outv,wtmp)
+              if ((ncs > 0) & (wiscov > 0)){ccmatoff[(i-1),wiscov]<-0}
+              modlabel<-matrix(c(modlabel,wcatlab[1:nwvls,1]))
+              wdid<-1
+              if (wtmpuse==0)
+              {
+                fulldat<-matrix(c(fulldat,wtmp),nrow=n)
+                if ((ncs > 0) & (wiscov > 0)){ccmatoff[(i-1),wiscov]<-0}         
+                wtmpuse<-1
+                for (k4 in (datcount:(datcount+(nwvls-1))))
+                {wtmploc<-matrix(c(wtmploc,k4))}    
+                wtmploc<-matrix(wtmploc[2:nrow(wtmploc),1])
+                datcount<-datcount+nwvls
+              }
+            }     
+            datindx[start:(start+nrow(wtmploc)-1),(i-1)]<-wtmploc
+            wherew[1,(i-1)]<-start+1
+            wherew[2,(i-1)]<-start+nrow(wtmploc)-1+1
+            start<-start+nrow(wtmploc)
+            for (k1 in c(1:nxvls))
+            {
+              for (k2 in c(1:nwvls))
+              {
+                outv<-as.matrix(cbind(outv,(xtmp[,k1]*wtmp[,k2])))
+                if ((ncs > 0) & (wiscov > 0)){ccmatoff[(i-1),wiscov]<-0}          
+                modlabel<-matrix(c(modlabel,intlab[cntmp,1]))
+                intkeyt<-matrix(c(intlab[cntmp,1],":",xcatlab[k1,1],"x",wcatlab[k2,1]," "," "),ncol=7)
+                intkey<-rbind(intkey,intkeyt)
+                cntmp<-cntmp+1
+              }
+            }
+            if (xwtmpus==0)
+            {
+              fulldat<-matrix(c(fulldat,outv[,(ncol(outv)-(nxvls*nwvls)+1):ncol(outv)]),nrow=n)
+              xwtmpus<-1
+              if ((ncs > 0) & (wiscov > 0)){ccmatoff[(i-1),wiscov]<-0}
+              for (k4 in (datcount:(datcount+((nwvls*nxvls)-1))))
+              {xwtmplo<-matrix(c(xwtmplo,k4))}
+              xwtmplo<-matrix(xwtmplo[2:nrow(xwtmplo),1])
+              datcount<-datcount+(nxvls*nwvls)
+            }
+            datindx[start:(start+nrow(xwtmplo)-1),(i-1)]<-xwtmplo
+            wherexw[1,(i-1)]<-start+1
+            wherexw[2,(i-1)]<-start+nrow(xwtmplo)-1+1
+            onebl<-matrix(1,nrow(xwtmplo),1)
+            whigh[(start+1):(start+nrow(xwtmplo)),whighct]<-onebl
+            start<-start+nrow(xwtmplo)
+          }
+          if ((j > 1) & (wcmat[i,j]==1))
+          {
+            if ((wdid==0) & (model != 74))
+            {
+              outv<-cbind(outv,wtmp)
+              if ((ncs > 0) & (wiscov > 0)){ccmatoff[(i-1),wiscov]<-0}
+              modlabel<-matrix(c(modlabel,wcatlab[1:nwvls,1]))
+              wdid<-1
+              if (wtmpuse==0)
+              {
+                fulldat<-matrix(c(fulldat,wtmp),nrow=n)
+                if ((ncs > 0) & (wiscov > 0)){ccmatoff[(i-1),wiscov]<-0}
+                wtmpuse<-1
+                for (k4 in (datcount:(datcount+(nwvls-1))))
+                {wtmploc<-matrix(c(wtmploc,k4))}    
+                wtmploc<-matrix(wtmploc[2:nrow(wtmploc),1])
+                datcount<-datcount+nwvls
+              }
+              datindx[start:(start+nrow(wtmploc)-1),(i-1)]<-wtmploc
+              wherew[1,(i-1)]<-start+1
+              wherew[2,(i-1)]<-start+nrow(wtmploc)-1+1
+              start<-start+nrow(wtmploc)
+            }         
+            for (k2 in c(1:nwvls))
+            {
+              outv<-as.matrix(cbind(outv,(mtmp[,(j-1)]*wtmp[,k2])))
+              if ((ncs > 0) & (wiscov > 0)){ccmatoff[(i-1),wiscov]<-0}
+              modlabel<-matrix(c(modlabel,intlab[cntmp,1]))
+              intkeyt<-matrix(c(intlab[cntmp,1],":",mnames[1,(j-1)],"x",wcatlab[k2,1]," "," "),ncol=7)
+              intkey<-rbind(intkey,intkeyt)
+              cntmp<-cntmp+1
+            }
+            if (mwtmpus[1,(j-1)]==0)
+            {
+              fulldat<-matrix(c(fulldat,outv[,(ncol(outv)-nwvls+1):ncol(outv)]),nrow=n)
+              if ((ncs > 0) & (wiscov > 0)){ccmatoff[(i-1),wiscov]<-0}
+              mwtmpus[1,(j-1)]<-1
+              mw22<- -999
+              for (k4 in (datcount:(datcount+(nwvls-1))))
+              {mw22<-matrix(c(mw22,k4))}
+              mwtmplo[,(j-1)]=matrix(mw22[2:nrow(mw22),1])
+              datcount<-datcount+nwvls
+            }
+            datindx[start:(start+nrow(mwtmplo)-1),(i-1)]<-mwtmplo[,(j-1)]
+            wheremw[((2*j)-3),(i-1)]<-start+1
+            wheremw[((2*j)-2),(i-1)]<-start+nrow(mwtmplo)-1+1
+            onebl<-matrix(1,nrow(mwtmplo),1)
+            whigh[(start+1):(start+nrow(mwtmplo)),whighct]<-onebl
+            start<-start+nrow(mwtmplo)
+          }
+        }
+        }
+      #END W
+      #START Z
+      if (zsum > 0)
+        ztmp<-data.matrix(ztmp)
+      {
+        for (j in c(1:(i-1)))    
+        {
+          zhighct<-zhighct+1
+          if ((j==1) & (zcmat[i,j]==1))
+          {
+            if (zdid==0)
+            {
+              outv<-cbind(outv,ztmp)
+              if ((ncs > 0) & (ziscov > 0)){ccmatoff[(i-1),ziscov]<-0}         
+              modlabel<-matrix(c(modlabel,zcatlab[1:nzvls,1]))
+              zdid<-1
+              if (ztmpuse==0)
+              {
+                fulldat<-matrix(c(fulldat,ztmp),nrow=n)
+                if ((ncs > 0) & (ziscov > 0)){ccmatoff[(i-1),ziscov]<-0} 
+                ztmpuse<-1
+                for (k4 in (datcount:(datcount+(nzvls-1))))
+                {ztmploc<-matrix(c(ztmploc,k4))}      
+                ztmploc<-matrix(ztmploc[2:nrow(ztmploc),1])
+                datcount<-datcount+nzvls
+              }
+            }   
+            datindx[start:(start+nrow(ztmploc)-1),(i-1)]<-ztmploc
+            wherez[1,(i-1)]<-start+1
+            wherez[2,(i-1)]<-start+nrow(ztmploc)-1+1
+            start<-start+nrow(ztmploc)
+            for (k1 in c(1:nxvls))
+            {for (k2 in c(1:nzvls))
+            {        
+              outv=as.matrix(cbind(outv,(xtmp[,k1]*ztmp[,k2])))
+              if ((ncs > 0) & (ziscov > 0)){ccmatoff[(i-1),ziscov]<-0}
+              modlabel<-matrix(c(modlabel,intlab[cntmp,1]))
+              intkeyt<-matrix(c(intlab[cntmp,1],":",xcatlab[k1,1],"x",zcatlab[k2,1]," "," "),ncol=7)
+              intkey<-rbind(intkey,intkeyt)
+              cntmp<-cntmp+1
+            }
+            }
+            if (xztmpus==0)
+            {
+              fulldat<-matrix(c(fulldat,outv[,(ncol(outv)-(nxvls*nzvls)+1):ncol(outv)]),nrow=n)
+              if ((ncs > 0) & (ziscov > 0)){ccmatoff[(i-1),ziscov]<-0}
+              xztmpus<-1
+              for (k4 in (datcount:(datcount+((nzvls*nxvls)-1)))){xztmplo<-matrix(c(xztmplo,k4))}       
+              xztmplo<-matrix(xztmplo[2:nrow(xztmplo),1])
+              datcount<-datcount+(nxvls*nzvls)
+            }
+            datindx[start:(start+nrow(xztmplo)-1),(i-1)]<-xztmplo
+            wherexz[1,(i-1)]<-start+1
+            wherexz[2,(i-1)]<-start+nrow(xztmplo)-1+1
+            onebl<-matrix(1,nrow(xztmplo),1)
+            zhigh[(start+1):(start+nrow(xztmplo)),zhighct]<-onebl
+            start<-start+nrow(xztmplo)
+          }
+          if ((j > 1) & (zcmat[i,j]==1))
+          {
+            if (zdid==0)
+            {
+              outv<-cbind(outv,ztmp)
+              if ((ncs > 0) & (ziscov > 0)){ccmatoff[(i-1),ziscov]<-0}
+              modlabel<-matrix(c(modlabel,zcatlab[1:nzvls,1]))
+              zdid<-1
+              if (ztmpuse==0)
+              {
+                fulldat<-matrix(c(fulldat,ztmp),nrow=n)
+                if ((ncs > 0) & (ziscov > 0)){ccmatoff[(i-1),ziscov]<-0}
+                ztmpuse<-1
+                for (k4 in (datcount:(datcount+(nzvls-1))))
+                {ztmploc<-matrix(c(ztmploc,k4))}
+                ztmploc<-matrix(ztmploc[2:nrow(ztmploc),1])
+                datcount<-datcount+nzvls
+              }
+              datindx[start:(start+nrow(ztmploc)-1),(i-1)]<-ztmploc
+              wherez[1,(i-1)]<-start+1
+              wherez[2,(i-1)]<-start+nrow(ztmploc)-1+1
+              start<-start+nrow(ztmploc)
+            }    
+            for (k2 in (1:nzvls))
+            {
+              outv=as.matrix(cbind(outv,(mtmp[,(j-1)]*ztmp[,k2])))
+              if ((ncs > 0) & (ziscov > 0)){ccmatoff[(i-1),ziscov]<-0}
+              modlabel<-matrix(c(modlabel,intlab[cntmp,1]))
+              intkeyt<-matrix(c(intlab[cntmp,1],":", mnames[1,(j-1)],"x",zcatlab[k2,1]," "," "),ncol=7)
+              intkey<-rbind(intkey,intkeyt)
+              cntmp<-cntmp+1
+            }
+            if (mztmpus[1,(j-1)]==0)
+            {
+              fulldat<-matrix(c(fulldat,outv[,(ncol(outv)-nzvls+1):ncol(outv)]),nrow=n)
+              if ((ncs > 0) & (ziscov > 0)){ccmatoff[(i-1),ziscov]<-0}
+              mztmpus[1,(j-1)]<-1
+              mz22<- -999
+              for (k4 in (datcount:(datcount+(nzvls-1)))){mz22<-matrix(c(mz22,k4))}
+              mztmplo[,(j-1)]<-matrix(mz22[2:nrow(mz22),1])
+              datcount<-datcount+nzvls
+            }
+            datindx[start:(start+nrow(mztmplo)-1),(i-1)]<-mztmplo[,(j-1)]
+            wheremz[((2*j)-3),(i-1)]<-start+1
+            wheremz[((2*j)-2),(i-1)]<-start+nrow(mztmplo)-1+1
+            onebl<-matrix(1,nrow(mztmplo),1)
+            zhigh[(start+1):(start+nrow(mztmplo)),zhighct]<-onebl
+            start<-start+nrow(mztmplo)
+          }
+        }
+        }
+      #END Z
+
+      #START WZ
+      if (wzsum > 0)
+      {  
+        for (j in (1:(i-1)))
+        {
+          wzhighct<-wzhighct+1
+          if ((j==1) & (wzcmat[i,j]==1))
+          {
+            if (wzdid==0)
+            {
+              for (k1 in (1:nwvls))
+              {
+                for (k2 in (1:nzvls))
+                {
+                  outv<-as.matrix(cbind(outv,(wtmp[,k1]*ztmp[,k2]))) 
+                  if ((ncs > 0) & (ziscov > 0)){ccmatoff[(i-1),ziscov]<-0}
+                  if ((ncs > 0) & (wiscov > 0)){ccmatoff[(i-1),wiscov]<-0}
+                  modlabel<-matrix(c(modlabel,intlab[cntmp,1]))
+                  intkeyt<-matrix(c(intlab[cntmp,1],":",wcatlab[k1,1],"x",zcatlab[k2,1]," "," "),ncol=7)
+                  intkey<-rbind(intkey,intkeyt)
+                  cntmp<-cntmp+1
+                }
+              }
+              if (wztmpus==0)
+              {
+                fulldat<-matrix(c(fulldat,outv[,(ncol(outv)-(nwvls*nzvls)+1):ncol(outv)]),nrow=n)
+                if ((ncs > 0) & (ziscov > 0)){ccmatoff[(i-1),ziscov]<-0}  
+                if ((ncs > 0) & (wiscov > 0)){ccmatoff[(i-1),wiscov]<-0}
+                wztmpus<-1
+                for (k4 in (datcount:(datcount+((nwvls*nzvls)-1))))
+                {wztmplo<-matrix(c(wztmplo,k4))}   
+                wztmplo<-matrix(wztmplo[2:nrow(wztmplo),1])
+                datcount<-datcount+(nzvls*nwvls)
+              }
+              wzdid<-1         
+            }
+            datindx[start:(start+nrow(wztmplo)-1),(i-1)]<-wztmplo
+            wherewz[1,(i-1)]<-start+1
+            wherewz[2,(i-1)]<-start+nrow(wztmplo)-1+1
+            start<-start+nrow(wztmplo)
+            for (k1 in (1:nxvls))
+            {
+              for (k2 in (1:nwvls))
+              {
+                for (k3 in (1:nzvls))
+                {
+                  outv<-as.matrix(cbind(outv,(xtmp[,k1]*wtmp[,k2]*ztmp[,k3]))) 
+                  if ((ncs > 0) & (ziscov > 0)){ccmatoff[(i-1),ziscov]<-0}  
+                  if ((ncs > 0) & (wiscov > 0)){ccmatoff((i-1),wiscov)<-0}    
+                  modlabel<-matrix(c(modlabel,intlab[cntmp,1]))
+                  intkeyt<-matrix(c(intlab[cntmp,1],":",xcatlab[k1,1],"x",wcatlab[k2,1],"x",zcatlab[k3,1]),ncol=7)
+                  intkey<-rbind(intkey,intkeyt) 
+                  cntmp<-cntmp+1 
+                }
+              }
+            }
+            if (xwztmpu==0)
+            {
+              fulldat<-matrix(c(fulldat,outv[,(ncol(outv)-(nxvls*nwvls*nzvls)+1):ncol(outv)]),nrow=n)
+              if ((ncs > 0) & (ziscov > 0)){ccmatoff[(i-1),ziscov]<-0} 
+              if ((ncs > 0) & (wiscov > 0)){ccmatoff((i-1),wiscov)<-0}
+              xwztmpu<-1
+              for (k4 in (datcount:(datcount+((nzvls*nxvls*nwvls)-1))))
+              {xwztmplo<-matrix(c(xwztmplo,k4))}  
+              xwztmplo<-matrix(xwztmplo[2:nrow(xwztmplo),1])
+              datcount<-datcount+(nxvls*nzvls*nwvls)
+            }
+            datindx[start:(start+nrow(xwztmplo)-1),(i-1)]<-xwztmplo
+            wherexwz[1,(i-1)]<-start+1
+            wherexwz[2,(i-1)]<-start+nrow(xwztmplo)-1+1
+            onebl<-matrix(1,nrow(xwztmplo),1)
+            wzhigh[(start+1):(start+nrow(xwztmplo)),wzhighct]<-onebl
+            start<-start+nrow(xwztmplo)
+          }
+          if ((j > 1) & (wzcmat[i,j]==1))
+          {
+            if (wzdid==0)
+            {
+              for (k1 in (1:nwvls))
+              {
+                for (k2 in (1:nzvls))
+                {
+                  outv<-as.matrix(cbind(outv,(wtmp[,k1]*ztmp[,k2])))
+                  if ((ncs > 0) & (ziscov > 0)){ccmatoff[(i-1),ziscov]<-0}  
+                  if ((ncs > 0) & (wiscov > 0)){ccmatoff[(i-1),wiscov]<-0}
+                  modlabel<-matrix(c(modlabel,intlab[cntmp,1]))
+                  intkeyt<-matrix(c(intlab[cntmp,1],":",wcatlab[k1,1],"x",zcatlab[k2,1]," "," "),ncol=7)
+                  intkey<-rbind(intkey,intkeyt) 
+                  cntmp<-cntmp+1
+                }
+              }
+              if (wztmpus==0)
+              {
+                fulldat<-matrix(c(fulldat,outv[,(ncol(outv)-(nwvls*nzvls)+1):ncol(outv)]),nrow=n)
+                if ((ncs > 0) & (ziscov > 0)){ccmatoff[(i-1),ziscov]<-0}
+                if ((ncs > 0) & (wiscov > 0)){ccmatoff[(i-1),wiscov]<-0}
+                wztmpus<-1
+                for (k4 in (datcount:(datcount+((nwvls*nzvls)-1))))
+                {wztmplo<-matrix(c(wztmplo,k4))}    
+                wztmplo<-matrix(wztmplo[2:nrow(wztmplo),1])
+                datcount<-datcount+(nzvls*nwvls)
+              }
+              wzdid<-1
+              datindx[start:(start+nrow(wztmplo)-1),(i-1)]<-wztmplo
+              wherewz[1,(i-1)]<-start+1
+              wherewz[2,(i-1)]<-start+nrow(wztmplo)-1+1
+              start<-start+nrow(wztmplo)
+            }
+            for (k1 in (1:nwvls))
+            {
+              for (k2 in (1:nzvls))
+              {
+                outv<-as.matrix(cbind(outv,(mtmp[,(j-1)]*wtmp[,k1]*ztmp[,k2])))
+                if ((ncs > 0) & (ziscov > 0)){ccmatoff[(i-1),ziscov]<-0}  
+                if ((ncs > 0) & (wiscov > 0)){ccmatoff[(i-1),wiscov]<-0} 
+                modlabel<-matrix(c(modlabel,intlab[cntmp,1]))
+                intkeyt<-matrix(c(intlab[cntmp,1],":",mnames[1,(j-1)],"x",wcatlab[k1,1],"x",zcatlab[k2,1]),ncol=7)
+                intkey<-rbind(intkey,intkeyt) 
+                cntmp<-cntmp+1
+              }
+            }
+            if (mwztmpu[1,(j-1)]==0)
+            {
+              fulldat<-matrix(c(fulldat,outv[,(ncol(outv)-(nwvls*nzvls)+1):ncol(outv)]),nrow=n)
+              if ((ncs > 0) & (ziscov > 0)){ccmatoff[(i-1),ziscov]<-0} 
+              if ((ncs > 0) & (wiscov > 0)){ccmatoff[(i-1),wiscov]<-0}
+              mwztmpu[1,(j-1)]<-1
+              mz22<- -999
+              for (k4 in (datcount:(datcount+(nwvls*nzvls)-1)))
+              {mz22<-matrix(c(mz22,k4))}
+              mwztmplo[,(j-1)]<-matrix(mz22[2:nrow(mz22),1])
+              datcount<-datcount+(nwvls*nzvls)
+            }
+            datindx[start:(start+nrow(mwztmplo)-1),(i-1)]<-mwztmplo[,(j-1)]
+            wheremwz[((2*j)-3),(i-1)]<-start+1
+            wheremwz[((2*j)-2),(i-1)]<-start+nrow(mwztmplo)-1+1
+            onebl<-matrix(1,nrow(mwztmplo),1)
+            wzhigh[(start+1):(start+nrow(mwztmplo)),wzhighct]<-onebl
+            start<-start+nrow(mwztmplo)
+          }
+        }
+      }
+      #END WZ
+
+      #START COV
+      if (ncs > 0)
+      {  
+        ccmat<-ccmat*ccmatoff
+        for (j in c(1:ncs))
+        {
+          if (ccmat[(i-1),j]==1)
+          {
+            if (j==wiscov){ctmp[,j]<-wtmp}
+            if (j==ziscov){ctmp[,j]<-ztmp}
+            outv<-cbind(outv,ctmp[,j])
+            modlabel<-matrix(c(modlabel,covnames[1,j]))
+            if (ctmpuse[1,j]==0)
+            {
+              fulldat<-matrix(c(fulldat,ctmp[,j]),nrow=n)
+              ctmpuse[1,j]<-1
+              ctmploc[1,j]<-datcount
+              datcount<-datcount+1
+            }
+            datindx[start:(start+nrow(ctmploc)-1),(i-1)]<-ctmploc[1,j]
+            start<-start+1
+          }
+        }
+      }
+      #END COV
+
+      wdid<-0;zdid<-0;wzdid<-0
+      vlabs<-matrix(c(vlabs,modlabel[2:nrow(modlabel),1]))
+      numint[1,(i-1)]<-cntmp-1
+      nump[1,(i-1)]<-nrow(modlabel)-1
+
+    } 
+    #END DV LOOP
+    if ((modcok==1) & ((nms > 0) | (zcmat[2,1] != 1) | (mcx != 0)))
+    {notecode[notes,1]<-19;notes<-notes + 1;modcok<-0}
+    if (((serial==1) | (sum(numint)>0) | (nms==0)) & (mc > 0))
+    {notecode[notes,1]<-15;notes<-notes+1;boot<-mc;mc<-0}
+
+    if ((boot != 0) | (mc != 0))
+    {
+      bootsz<-boot
+      if (mc > 0){bootsz<-mc;saveboot<-0}
+      cilow<-0;cihigh<-bootsz+1
+      while ((cilow <=0) | (cihigh > bootsz))
+      {
+        cilow<-round(bootsz*(1-(conf/100))/2)
+        cihigh<-trunc((bootsz*(conf/100)+(bootsz*(1-(conf/100))/2)))+1
+        if ((cilow < 1) | (cihigh > bootsz))
+        {bootsz<-trunc((bootsz+1000)/1000)*1000;adjust<-1}
+      }
+      if (boot > 0){boot<-bootsz}
+      if (mc > 0){mc<-bootsz}
+      if ((adjust==1) & (boot > 0)){notecode[notes,1]<-8;notes<-notes+1}
+      if ((adjust==1) & (mc > 0)){notecode[notes,1]<-16;notes<-notes+1}
+    }
+    maxboot<-trunc(2*boot)
+    if (maxboots > maxboot){maxboot<-trunc(maxboots)}
+    #insert seed here  
+    if ((seed==-999) & (boot > 0) | (mc > 0))
+    {seed<-trunc(runif(1,1,1000000));set.seed(seed);ranseed<-1}
+    if (sum(numint) > 0){intkey<-matrix(intkey[2:nrow(intkey),],ncol=7)}
+    vlabs<-matrix(vlabs[2:nrow(vlabs),1])
+    fulldat<-as.data.frame(fulldat[,2:ncol(fulldat)])
+    fulldat<-data.matrix(fulldat)
+    fochigh<-fochigh[1:max(nump),]
+    whigh<-as.matrix(whigh[1:max(nump),])
+    zhigh<-as.matrix(zhigh[1:max(nump),])
+    wzhigh<-as.matrix(wzhigh[1:max(nump),])
+    coeffs<-fochigh+whigh+zhigh+wzhigh
+    bootloc<-matrix(0,max(nump),ncol(nump))
+
+    #Here is am deriving the locations in bootfile needed for indirect effects
+    if (nms > 0)
+    {
+      cntmp<-1
+      for (i in (1:ncol(nump)))
+      {for (j in (1:nump[1,i]))
+      {bootloc[j,i]<-cntmp;cntmp<-cntmp+1}
+      }
+      fochighb<-matrix(0,nrow(fochigh),ncol(fochigh))
+      whighb<-fochighb
+      zhighb<-fochighb
+      wzhighb<-fochighb
+      thetaxmb<-matrix(0,nrow(fochighb),nms)
+      thetaxyb<-matrix(0,nrow(fochighb),1)
+      pathsfoc<-matrix(0,nxvls,1)
+      cntmp<-1
+      for (i in (1:(nms+nys)))
+      {
+        for (j in (1:i))
+        {
+          fochighb[,cntmp]<-(fochigh[,cntmp]*bootloc[,i])
+          whighb[,cntmp]<-(whigh[,cntmp]*bootloc[,i])
+          zhighb[,cntmp]<-(zhigh[,cntmp]*bootloc[,i])
+          wzhighb[,cntmp]<-(wzhigh[,cntmp]*bootloc[,i])
+          coeffsb<-(fochighb+whighb+zhighb+wzhighb)
+          if ((i < (nms+nys)) & (j==1)){thetaxmb[,i]<-coeffsb[,cntmp]}
+          if ((i==(nms+nys)) & (j==1)){thetaxyb[,1]<-coeffsb[,cntmp]}
+          cntmp<-cntmp+1
+        }
+      }
+      thetamyb<-as.matrix(coeffsb[,(ncol(coeffsb)-nms+1):ncol(coeffsb)])
+      if (serial==1)
+      {thetammb<-matrix(0,nrow(coeffsb),((nms*(nms-1))/2))}
+      cntmp<-1
+      if ((nms > 1) & (serial==1))
+      {
+        for (i in (1:(nms-1)))
+        {
+          start<-((i+2)*(i+1))/2
+          for (j in (2:(nms-i+1)))
+          {
+            thetammb[,cntmp]<-coeffsb[,start]
+            start<-start+j+i-1
+            cntmp<-cntmp+1
+          }
+        } 
+      }
+    }
+
+    if ((total==1) & (sum(numint)==0))
+    {
+      dototal<-1
+      if ((sum(bcmat[,1]) != (nms+nys)) | (sum(bcmat[nrow(bcmat),]) != (nms+nys)))
+      {dototal<-0;alttotal<-1;notecode[notes,1]<-12;notes<-notes+1}
+      if (ncs > 0)
+      {
+        if ((sum(ccmat)) < (nrow(ccmat)*ncol(ccmat)))
+        {dototal<-0;alttotal<-1;notecode[notes,1]<-11;notes<-notes+1}
+      }
+    }
+  }
+  # End D
+  if ((criterr==0) & (ncs > 0))
+  {
+    tmperr<-sum(as.numeric(colSums(ccmat)==0))
+    if (sum(tmperr)!=0)
+    {errcode[errs,1]<-51;errs<-errs+1;criterr<-1}
+  }
+  if (outscreen==1)
+  {
+    cat("\n")
+    cat("********************* PROCESS for R Version 4.1.1 ********************* \n \n")
+    cat("           Written by Andrew F. Hayes, Ph.D.  www.afhayes.com              \n")
+    cat("   Documentation available in Hayes (2022). www.guilford.com/p/hayes3   \n \n")
+  }
+  if (criterr==0)
+  {
+    if ((stand==1) & (ydich==1)){stand<-0}
+    anymod2<-sum(wcmat+zcmat+wzcmat)
+    if ((anymod2 > 0) & (stand==1))
+    {notecode[notes,1]<-27;notes<-notes+1;stand<-0}
+    rownames(modelvar)<-modelvlb
+    colnames(modelvar)<-" "
+    funny<-1
+    if (outscreen==1)
+    {
+      cat("*********************************************************************** \n")
+      print(noquote(modelvar))
+      cat("\n")
+      if (ncs > 0)
+      {
+        cat("Covariates: \n")
+        covname2<-c("      ", covnames)
+        covname2<-t(noquote(covname2))  
+        write.table(covname2,quote=FALSE,row.names=FALSE,col.names=FALSE)
+        cat("\n")
+      }
+      cat("Sample size: ")
+      write.table(n,quote=FALSE,row.names=FALSE,col.names=FALSE)
+      cat("\n")
+      if (seed != -999)    
+      {if (ranseed==0)
+      {cat("Custom seed: ")}
+        if (ranseed==1)
+        {cat("Random seed: ")}
+        write.table(seed,quote=FALSE,row.names=FALSE,col.names=FALSE)
+        cat("\n")
+      }
+      maxresm<-9;
+      resultm<-matrix(99999,1,maxresm)  
+      if (describe==1)
+      {
+        means=apply(dat,2,mean);sdvec=apply(dat,2,sd);corall=cor(dat);
+        means<-rbind(t(matrix(means)),t(matrix(sdvec)))
+        means2<-noquote(matrix(sprintf(decimals,means),nrow=nrow(means)))
+        corall2<-noquote(matrix(sprintf(decimals,corall),nrow=nrow(corall)))
+        if (ncol(means) > 9)
+        {resultm<-matrix(99999,1,ncol(means));maxresm<-ncol(means)}
+        resultm2<-matrix(99999,2,maxresm)
+        resultm2[1:2,1:ncol(means)]<-means
+        resultm<-rbind(resultm,resultm2)
+        resultm2<-matrix(99999,ncol(corall),maxresm)
+        resultm2[1:ncol(corall),1:ncol(corall)]<-corall
+        resultm<-rbind(resultm,resultm2)
+        colnames(means2)<-varnames
+        colnames(corall2)<-varnames
+        rownames(corall2)<-varnames
+        rownames(means2)<-matrix(c("Mean","SD"))
+        if (outscreen==1)
+        {
+          cat("Variable means and standard deviations:\n")
+          print(means2,right=T)
+          cat("\n")
+          cat("Variable intercorrelations (Pearson's r):\n")
+          print(corall2,right=T)
+        }     
+      }
+
+      #resultm2<-matrix(99999,nrow(corall),maxresm)
+      #resultm2[1:nrow(corall),1:ncol(corall)]<-corall
+      #resultm<-rbind(resultm,resultm2)
+
+      if (mcxok==1)
+      {cat("Coding of categorical X variable for analysis: \n")
+        dummatx2<-noquote(matrix(sprintf(decimals,dummatx),nrow=nrow(dummatx)))
+        colnames(dummatx2)<-c(xnames,xcatlab[1:nxvls,1])
+        rownames(dummatx2)<-t(matrix(replicate((nxvls+1)," ")))
+        print(dummatx2,right=T)}
+      if (mcwok==1)
+      {cat("Coding of categorical W variable for analysis: \n")
+        dummatw2<-noquote(matrix(sprintf(decimals,dummatw),nrow=nrow(dummatw)))
+        colnames(dummatw2)<-c(wnames,t(wcatlab[1:nwvls,1]))
+        rownames(dummatw2)<-t(matrix(replicate((nwvls+1)," ")))
+        print(dummatw2,right=T)}
+      if (mczok==1)
+      {cat("Coding of categorical Z variable for analysis: \n")
+        dummatz2<-noquote(matrix(sprintf(decimals,dummatz),nrow=nrow(dummatz)))
+        colnames(dummatz2)<-c(znames,t(zcatlab[1:nzvls,1]))
+        rownames(dummatz2)<-t(matrix(replicate((nzvls+1)," ")))
+        print(dummatz2,right=T)}
+    }
+  } 
+  #START cycle through the models  
+  if (criterr==0)
+  {
+    outnames<-ynames
+    outvars<-ytmp
+    if (nms > 0)
+    {
+      outnames<-matrix(c(mnames,ynames))
+      outvars<-cbind(mtmp,ytmp)
+      indcov<-matrix(0,((nms*2)+(nms*(nxvls-1))),((nms*2)+(nms*(nxvls-1))))
+      mcsopath<-matrix(0,((nms*2)+(nms*(nxvls-1))),1)
+    }
+    labstart<-1
+    intstart<-1
+    start<-1
+    coeffmat<-matrix(0,1,6)
+    conseq<-"        "
+    dfmat<-0;coeffcol<-0;pathscnt<-1;pathscn2<-1
+
+    # START G LOOP
+    for (i in c(1:(nms+nys)))
+    {
+      if (outscreen==1)
+      {cat("\n*********************************************************************** \n")}
+      highf<-matrix(0,1,5);highf2<-highf
+      if ((i==(nms+nys)) & (ydich==1)){highf=matrix(0,1,3);highf2<-highf}
+      flabel<-" "   
+      y<-outvars[,i]
+      xindx<-datindx[1:(nump[1,i]-1),i]
+      x<-fulldat[,xindx]
+      x<-cbind(ones,x)
+      xsq<-t(x)%*%x
+      exsq<-eigen(xsq)
+      exsq<-matrix(unlist(exsq[1]))
+      zeroeig<-sum(as.numeric(exsq <= 0.000000000002))
+      if (outscreen==1)
+      {
+        cat("Outcome Variable: ")
+        write.table(outnames[i,1],quote=FALSE,row.names=FALSE,col.names=FALSE)
+        cat("\n")
+        if ((ydich==1) & (i==(nms+nys)))
+        {
+          cat("Coding of binary Y for logistic regression analysis:\n")
+          rcd<-noquote(matrix(sprintf(decimals,rcd),nrow=nrow(rcd)))
+          colnames(rcd)<-c(outnames[i,1], "Analysis")
+          rownames(rcd)<-t(matrix(replicate(nrow(rcd)," ")))
+          print(rcd,right=T)
+          cat("\n")
+        }
+      }
+      if (zeroeig > 0)
+      {
+        cat("\nSINGULAR OR NEAR SINGULAR DATA MATRIX.\n")
+        criterr<-1;errcode[errs,1]<-31;errs<-errs+1;
+      }    
+      means<-colSums(x)/n
+      vlabsm<-matrix(vlabs[labstart:(labstart+(nump[1,i]-1)),1])
+      #START E
+      if (criterr==0)
+      {
+        if ((ydich==0) | (i < (nms+nys)))
+        {
+          modoutz<-process.modelest(y,x,1,1,xp2,hc)
+          modres<-matrix(unlist(modoutz[1]),nrow=nump[1,i])
+          direff<-matrix(modres,nrow=ncol(x))
+          #modresl<-matrix(unlist(modoutz[2]))  
+          modsum<-matrix(unlist(modoutz[3]))
+          tval<-matrix(unlist(modoutz[7]))
+          resid<-matrix(unlist(modoutz[8]))
+          modresid<-cbind(modresid,resid)
+          brsq2<-modsum[2,1]
+          dfres<-modsum[6,1]
+          #for recording results
+          resultm2<-matrix(99999,1,maxresm)
+          resultm2[1,1:nrow(modsum)]<-t(modsum)
+          resultm<-rbind(resultm,resultm2)
+          resultm2<-matrix(99999,nrow(modres),maxresm)
+          resultm2[1:nrow(modres),1:ncol(modres)]<-modres
+          resultm<-rbind(resultm,resultm2)
+          #end recording results
+          modrest9<-modres
+          modres<-noquote(matrix(sprintf(decimals,modres),nrow=nump[1,i]))
+          modsum<-noquote(matrix(sprintf(decimals,modsum),nrow=1))
+          b<-matrix(unlist(modoutz[5]))
+          varb<-matrix(unlist(modoutz[6]),nrow=nump[1,i])
+          dfmatt<-matrix(modsum[1,6],nrow(modres),1)
+          modsuml<-matrix(c("R","R-sq","MSE",hcflab,"df1","df2", "p"))
+          modresl<-t(matrix(c("coeff",hclab,"t","p","LLCI","ULCI")))
+        }
+        if ((ydich==1) & (i==(nms+nys)))
+        {
+          modoutz<-process.modelest(y,x,2,1,xp2,5,iterate,converge)
+          modres<-matrix(unlist(modoutz[1]),nrow=nump[1,i])
+          direff<-matrix(modres,nrow=ncol(x))
+          modsum<-matrix(unlist(modoutz[3]))
+          basemod<-modsum[1,1]
+          basemodx<-basemod
+          tval<-matrix(unlist(modoutz[7]))
+          resultm2<-matrix(99999,1,maxresm)
+          resultm2[1,1:nrow(modsum)]<-t(modsum)
+          resultm<-rbind(resultm,resultm2)
+          resultm2<-matrix(99999,nrow(modres),maxresm)
+          resultm2[1:nrow(modres),1:ncol(modres)]<-modres
+          resultm<-rbind(resultm,resultm2)
+          modrest9<-modres
+          modres<-noquote(matrix(sprintf(decimals,modres),nrow=nump[1,i]))
+          modsum<-noquote(matrix(sprintf(decimals,modsum),nrow=1))
+          b<-matrix(unlist(modoutz[5]))
+          varb<-matrix(unlist(modoutz[6]),nrow=nump[1,i])
+          modsuml<-matrix(c("-2LL","ModelLL", "df", "p", "McFadden", "CoxSnell", "Nagelkrk"))
+          modresl<-t(matrix(c("coeff","se","Z","p","LLCI","ULCI")))
+          #modretrn<-list(modres,modresl,modsum,modsuml,b,varb,xp2)
+          dfmatt<-matrix(-999,nrow(modres),1)
+        } 
+        obscoeff<-cbind(obscoeff,t(b))
+        if (outscreen==1)
+        {
+          cat("Model Summary: \n")
+          colnames(modsum)<-modsuml;rownames(modsum)<-" "
+          print(modsum,right=T)
+          cat("\n")
+          cat("Model: \n")
+          rownames(modres)<-vlabsm;colnames(modres)<-modresl
+          print(modres,right=T)   
+          if ((ydich==1) & (i==(nms+nys)))
+          {
+            cat("\nThese results are expressed in a log-odds metric.\n")
+            notecode[notes,1]<-26;notes<-notes+1
+          }
+        }
+        coeffmat<-rbind(coeffmat,modres)
+        conseqt<-matrix(outnames[i,1],nrow(modres),1)
+        conseq<-matrix(c(conseq,conseqt))
+        dfmat<-rbind(dfmat,dfmatt)
+        labstart<-labstart+nump[1,i]
+
+        if (stand==1)
+        {
+          predsd<-matrix(0,nrow(modres),1)
+          stdmod<-as.numeric(modres[,1])/ovsd[i,1]
+          for (jd in c(1:ncol(x)))
+          {
+            predsd[jd,1]<-sd(x[,jd])
+          }
+          if ((wherex[1,i] != -999) & ((nxvls > 1) | (xdich==1)))    
+          {
+            sdmsone<-matrix(1,nxvls,1)
+            predsd[wherex[1,i]:wherex[2,i],1]<-sdmsone    
+            pstog<-1    
+          }
+          predsd[1,1]<-1
+          stdmod<-stdmod*predsd
+          stdmod<-matrix(stdmod[2:nrow(stdmod),1])
+          sdvlabs<-vlabsm[2:nrow(vlabsm),1]
+          if (outscreen==1){cat("\nStandardized coefficients:\n")}
+          resultm2<-matrix(99999,nrow(stdmod),maxresm)
+          resultm2[1:nrow(stdmod),1:ncol(stdmod)]<-stdmod
+          resultm<-rbind(resultm,resultm2)
+          stdmod<-noquote(matrix(sprintf(decimals,stdmod),nrow=(nump[1,i]-1)))
+          colnames(stdmod)<-"coeff"
+          rownames(stdmod)<-sdvlabs
+          if (outscreen==1)
+          {print(stdmod,right=T)}
+        }
+        if ((nms > 0) & (serial==0) & (sum(numint)==0) & ((normal==1) | (mc > 0)))
+        {
+          if (i < (nms+nys))
+          {
+            indcov[(((i-1)*nxvls)+1):(i*nxvls),(((i-1)*nxvls)+1):(i*nxvls)]<-varb[2:(1+nxvls),2:(1+nxvls)]
+            mcsopath[(((i-1)*nxvls)+1):(i*nxvls),1]<-matrix(modrest9[2:(1+nxvls),1])
+          }
+          if (i==(nms+nys))
+          {
+            atm<-ncol(wherem)
+            indcov[((nms*nxvls)+1):nrow(mcsopath),((nms*nxvls)+1):nrow(mcsopath)]<-varb[wherem[1,atm]:(wherem[1,atm]+nms-1),wherem[1,atm]:(wherem[1,atm]+nms-1)]
+            mcsopath[((nms*nxvls)+1):nrow(mcsopath),1]<-matrix(modrest9[wherem[1,atm]:(wherem[1,atm]+nms-1),1])
+            sobelok<-1          
+          }
+        }
+        obsdirfx<-matrix(0,1,nxvls);dirzes<-matrix(0,1,nxvls)    
+        if ((i ==(nms+nys)) & (bcmat[nrow(bcmat),1]==1))
+        {
+          direff<-matrix(direff[2:(1+nxvls),],nrow=nxvls)
+          obsdirfx=t(direff[,1])
+          direfflb<-modresl
+          direffl2<-vlabsm[2:(1+nxvls),]
+          lmat<-matrix(0,nrow(b),1)
+          lmat2<-matrix(1,nxvls,1)
+          lmat[2:(1+nxvls),1]<-lmat2
+          if (ydich != 1)
+          {
+            diromni<-process.ftest3(lmat,b,varb,1,brsq2,0,y,x)
+          }
+          if (ydich==1){diromni<-process.llrtest3(lmat,y,x,b,basemod,iterate,converge)}
+        }
+
+        if (numint[1,i] > 0)
+        {
+          if (outscreen==1)
+          {
+            cat("\nProduct terms key:\n")
+            intkeym<-matrix(intkey[intstart:(intstart+numint[1,i]-1),],ncol=7)
+            write.table(intkeym,quote=FALSE,row.names=FALSE,col.names=FALSE,sep = "  ")
+          }
+        }
+        if (covcoeff==1)
+        {
+          if (outscreen==1){cat("\nCovariance matrix of regression parameter estimates:\n")}
+          resultm2<-matrix(99999,nrow(varb),maxresm)
+          if (ncol(varb) <= maxresm)
+          {
+            resultm2[1:nrow(varb),1:ncol(varb)]<-varb
+            resultm<-rbind(resultm,resultm2)
+          }
+          if (ncol(varb) > maxresm)
+          {
+            resultmt<-matrix(99999,nrow(resultm),ncol(varb))
+            resultmt[1:nrow(resultm),1:ncol(resultm)]<-resultm
+            resultm<-resultmt
+            resultm2<-matrix(99999,nrow(varb),ncol(resultm))
+            resultm2[1:nrow(varb),1:ncol(varb)]<-varb
+            resultm<-rbind(resultm,resultm2)
+            maxresm<-ncol(resultm)
+          }
+          varbpr<-noquote(matrix(sprintf(decimals,varb),nrow=nump[1,i]))
+          rownames(varbpr)<-vlabsm;colnames(varbpr)<-vlabsm
+          if (outscreen==1)
+          {print(varbpr,right=T)}
+        }
+        #start X by M interaction */
+        if ((model != 74) & (xmtest==1) & (nms > 0))
+        {
+          r2tmp<-brsq2;btmp<-b;varbtmp<-varb
+          dfrestmp<-dfres
+          tvaltmp<-tval
+          xmtst<-matrix(0,nms,4)
+          xmtstlbc=matrix(c(hcflab,"df1","df2","p"))
+          if ((i==(nms+nys)) & (ydich==1))
+          {xmtst<-matrix(0,nms,3);xmtstlbc<-c("Chi-sq","df","p")
+          }
+          xmtstlb<-" ";xmtmat<-x;numxint<-0
+          if (i > 1)
+          {
+            for (xmint in (2:i))
+            {
+              x<-xmtmat
+              if ((bcmat[(i+1),xmint]==1) & (wzcmat[(i+1),xmint] != 1)) 
+              {
+                if (bcmat[(i+1),1]==0)
+                {
+                  x<-cbind(xmtmat,xtmp)
+                  if ((ydich==1) & (i==(nms+nys)))
+                  {
+                    LL2<-process.modelest(y,x,2,0,xp2,5,iterate,converge)
+                    basemodx<-LL2
+                  }
+                }
+                for (xmtlp1 in (1:nxvls))
+                {
+                  mtmpmns<-sum(mtmp[,(xmint-1)])/nrow(mtmp)
+                  x<-as.matrix(cbind(x,(xtmp[,xmtlp1]*((mtmp[,(xmint-1)])-mtmpmns))))
+                }
+                if ((i < (nms+nys)) | (ydich==0))
+                {
+                  modoutz<-process.modelest(y,x,1,1,xp2,hc)
+                  b<-matrix(unlist(modoutz[5]))
+                  varb<-matrix(unlist(modoutz[6]),nrow=nrow(b))
+                  lmat<-matrix(0,nrow(b),nxvls)
+                  lmattmp<-diag(nxvls)
+                  lmat[(nrow(lmat)-nxvls+1):nrow(lmat),]<-lmattmp
+                  fresult2<-process.ftest3(lmat,b,varb,0,0,1,y,x)
+                  numxint<-numxint+1
+                  xmtst[numxint,]<-fresult2
+                }
+                #right here
+                if ((i==(nms+nys)) & (ydich==1))
+                {
+                  LL2<-process.modelest(y,x,2,0,xp2,5,iterate,converge)
+                  chidfxm<-(basemodx-LL2)
+                  numxint<-numxint+1
+                  xmtst[numxint,1]<-chidfxm
+                  xmtst[numxint,3]<-(1-pchisq(chidfxm,df=nxvls))
+                }
+                xmtstlbt<-matrix(c(highlbx[(xmint-1),1]))
+                xmtstlb<-rbind(xmtstlb,xmtstlbt)     
+              }      
+            }
+          }
+          x<-xmtmat
+          if (numxint > 0)
+          {           
+            xmtstlb<-matrix(xmtstlb[(2:(numxint+1)),])
+            xmtst<-matrix(xmtst[1:numxint,],nrow=numxint)
+            if (nms==1){xmtstlb<-" "}
+            resultm2<-matrix(99999,nrow(xmtst),maxresm)
+            resultm2[1:nrow(xmtst),1:ncol(xmtst)]<-xmtst
+            resultm<-rbind(resultm,resultm2)
+            if ((i < (nms+nys)) | (ydich==0))
+            {
+              xmtst<-noquote(matrix(sprintf(decimals,xmtst),ncol=4))
+              colnames(xmtst)<-xmtstlbc
+              rownames(xmtst)<-xmtstlb
+              if (outscreen==1)
+              {cat("\nTest(s) of X by M interaction:\n")
+                print(xmtst,right=T)}
+            } 
+            if ((i==(nms+nys)) & (ydich==1))
+            {
+              xmtst<-noquote(matrix(sprintf(decimals,xmtst),ncol=3))
+              colnames(xmtst)<-xmtstlbc
+              rownames(xmtst)<-xmtstlb
+              if (outscreen==1)
+              {cat("\nLikelihood ratio test(s) of X by M interaction:\n")
+                print(xmtst,right=T)}
+            } 
+          }   
+          b<-btmp;varb<-varbtmp;dfres<-dfrestmp;tval<-tvaltmp;brsq2<-r2tmp
+        }
+        #end X by M interaction
+
+        #here is where we do F tests
+        #START F
+        if (criterr==0)
+        {
+          jj<-0
+          for (j in (start:((start+i)-1)))
+          {
+            dbint<-0
+            lmat<-whigh[1:nump[1,i],j]
+            lmat2<-wzhigh[1:nump[1,i],j]
+            if ((sum(lmat) > 0) & (sum(lmat2)==0)) 
+            {         
+              if ((i < (nms+nys)) | (ydich != 1))
+              {
+                fresult2<-process.ftest3(lmat,b,varb,chr=1,brsq2,0,y,x)
+                lmatdb<-lmat
+                dbint=dbint<-1
+              }
+              if ((ydich==1) & (i==(nms+nys)))
+              {                      
+                fresult2<-process.llrtest3(lmat,y,x,b,basemod,iterate,converge)
+                lmatdb<-lmat
+                dbint<-dbint+1
+              }
+              highf<-rbind(highf,fresult2)
+              highf2<-rbind(highf2,fresult2)
+              if (j==start){flabel<-matrix(c(flabel,"X*W"))}      
+              if (j > start)
+              {
+                if (nms > 1){flabel<-matrix(c(flabel,highlbw[jj,1]))}
+                if (nms==1){flabel<-matrix(c(flabel,"M*W"))}
+              }
+            }     
+            lmat<-zhigh[1:nump[1,i],j]
+            lmat2<-wzhigh[1:nump[1,i],j]
+            if ((sum(lmat) > 0) & (sum(lmat2)==0))
+            {
+              if ((i < (nms+nys)) | (ydich != 1))
+              {
+                fresult2<-process.ftest3(lmat,b,varb,chr=1,brsq2,0,y,x)
+                dbint<-dbint+1             
+              }
+              if ((ydich==1) & (i==(nms+nys)))
+              {
+                fresult2<-process.llrtest3(lmat,y,x,b,basemod,iterate,converge)
+                dbint<-dbint+1    
+              }
+              highf<-rbind(highf,fresult2)   
+              highf2<-rbind(highf2,fresult2)                
+              if (j==start){flabel<-matrix(c(flabel,"X*Z"))}
+              if (j > start)
+              {
+                if (nms > 1){flabel<-matrix(c(flabel,highlbz[jj,1]))}
+                if (nms==1){flabel<-matrix(c(flabel,"M*Z"))}
+              }
+            }
+            if (dbint==2)
+            {
+              lmatdb<-(lmatdb+lmat)
+              if ((ydich==1) & (i==(nms+nys)))
+              {fresult2<-process.llrtest3(lmatdb,y,x,b,basemod,iterate,converge)}       
+              if ((ydich != 1) | (i < (nms+nys)))
+              {
+                fresult2<-process.ftest3(lmatdb,b,varb,chr=1,brsq2,0,y,x)
+              }
+              dbint<-0 
+              highf<-rbind(highf,fresult2)
+              if ((jj==0) & (nms > 0)){flabel<-matrix(c(flabel,"BOTH(X)"))}  
+              if ((jj==0) & (nms==0)){flabel<-matrix(c(flabel,"BOTH"))}  
+              if ((jj > 0) & (nms==1)){flabel<-matrix(c(flabel,"BOTH(M)"))}  
+              if ((nms > 1) & (jj > 0)){flabel<-matrix(c(flabel,highlbbt[jj,1]))}         
+            } 
+            lmat2<-wzhigh[1:nump[1,i],j]
+            if (sum(lmat2) > 0)
+            {
+              if ((i < (nms+nys)) | (ydich != 1))
+              {
+                fresult2<-process.ftest3(lmat2,b,varb,chr=1,brsq2,0,y,x)
+              }
+              if ((ydich==1) & (i==(nms+nys)))
+              {fresult2<-process.llrtest3(lmat2,y,x,b,basemod,iterate,converge)}
+              highf<-rbind(highf,fresult2)
+              highf2<-rbind(highf2,fresult2)
+              if (j==start){flabel<-matrix(c(flabel,"X*W*Z"))}
+              if (j > start)
+              {
+                if (nms > 1){flabel<-matrix(c(flabel,highlbwz[jj,1]))}
+                if (nms==1){flabel<-matrix(c(flabel,"M*W*Z"))}
+              }
+            }
+            jj<-jj+1
+          }
+          start<-start+i
+          highfsz<-ncol(highf)
+        }
+        #END F
+
+        if (nrow(highf) > 1)
+        {
+          highf<-matrix(highf[2:nrow(highf),],ncol=highfsz)
+          highf2<-matrix(highf2[2:nrow(highf2),],ncol=highfsz)
+          flabel<-as.matrix(flabel[2:nrow(flabel),])
+          resultm2<-matrix(99999,nrow(highf),maxresm)
+          resultm2[1:nrow(highf),1:ncol(highf)]<-highf
+          resultm<-rbind(resultm,resultm2)
+          highf<-noquote(matrix(sprintf(decimals,highf),ncol=highfsz))
+          if (outscreen==1)
+          {
+            if ((i < (nms+nys)) | (ydich==0))
+            {      
+              cat("\nTest(s) of highest order unconditional interaction(s):\n")
+              colnames(highf)<-matrix(c("R2-chng",hcflab,"df1","df2","p"))
+              rownames(highf)<-flabel
+              print(highf,right=T)      
+            }
+            if ((ydich==1) & (i==(nms+nys)))
+            {
+              cat("\nLikelihood ratio test of highest order\n")
+              cat("unconditional interaction(s):\n")
+              colnames(highf)<-matrix(c("Chi-sq", "df","p"))
+              rownames(highf)<-flabel
+              print(highf,right=T)
+            }
+          }      
+          intpb<-as.matrix(highf2[,ncol(highf2)])
+        }
+        intstart<-intstart+numint[1,i]
+      }
+      #END E
+
+      #Start PROBEandPLOT
+      if (criterr==0)
+      {
+        threeway<-0;didprint<-0;didsome<-0;sigintct<-0
+        #Start R
+        for (jmed in (1:(nms+1)))
+        {
+          hasw<-0;hasz<-0;jnok<-0;nm1vls<-0;nm2vls<-0;panelgrp<-0
+          focpred4<-matrix(" ")
+          intprint<-0;modcat<-0    
+          #Start A
+          if (jmed <= i)
+          {
+            if ((jmed==1) & ((i+1)==nrow(bcmat)))
+            {pathscnt<-pathscnt+1} else {
+              paths<-cbind(paths,bcmat[(i+1),jmed])
+              pathsw<-cbind(pathsw,wcmat[(i+1),jmed])
+              pathsz<-cbind(pathsz,zcmat[(i+1),jmed])
+              pathswz<-cbind(pathswz,wzcmat[(i+1),jmed])
+              temp<-matrix(fochigh[,pathscnt]*bootloc[,i])
+              pathsfoc<-as.matrix(cbind(pathsfoc,pathsfoc[,1]))
+              if (jmed==1){pathtype<-cbind(pathtype,1)}
+              if ((i+1)==nrow(bcmat)){pathtype<-cbind(pathtype,3)}
+              if ((jmed > 1) & ((i+1) < nrow(bcmat))){pathtype<-cbind(pathtype,2)}
+              if ((jmed==1) & (nxvls > 1) & (bcmat[(i+1),jmed]==1))
+              {pathsfoc[,(pathscn2+1)]<-temp[2:(nxvls+1),1]}
+              if ((jmed > 1) | ((jmed==1) & (nxvls==1)))
+              {
+                temp<-matrix(apply(temp,2,max))  #column max
+                pathsfoc[1,(pathscn2+1)]<-temp
+              }
+              pathscnt<-pathscnt+1;pathscn2<-pathscn2+1
+              if (i <= nms){pathsdv<-matrix(c(pathsdv,mnames[1,i]))}
+              if (i > nms){pathsdv<-matrix(c(pathsdv,ynames))}
+            }
+            coeffcol<-coeffcol+1
+            probettt<-matrix(coeffs[1:nrow(b),coeffcol])
+            if ((jmed==1) & (bcmat[(i+1),jmed]==1))
+            {
+              omni<-matrix(0,nrow(probettt),nxvls)
+              omnitmp<-diag(nxvls)
+              omni[2:(1+nxvls),]<-omnitmp
+            }
+            if (sum(probettt) > 0)
+            {
+              probvarb<-matrix(999,sum(probettt),sum(probettt))
+              probcoef<-matrix(999,sum(probettt),1)
+              coefflp2<-1
+              for (coefflp in (1:nrow(probettt)))
+              {
+                if (probettt[coefflp,1]==1)
+                {
+                  probcoef[coefflp2,1]<-b[coefflp,1]
+                  coefflp2<-coefflp2+1
+                }
+              }
+              coefflp<-0;coefflp2<-0
+              for (iclp in (1:nrow(probettt)))
+              {
+                if (probettt[iclp,1]==1)
+                {
+                  coefflp<-coefflp+1
+                  coefflp2<-coefflp
+                  probvarb[coefflp,coefflp]<-varb[iclp,iclp]
+                  if (iclp < nrow(probettt))
+                  {
+                    for (jclp in ((iclp+1):nrow(probettt)))
+                    {       
+                      if (probettt[jclp,1]==1)
+                      {
+                        coefflp2<-coefflp2+1
+                        probvarb[coefflp,coefflp2]<-varb[iclp, jclp]
+                        probvarb[coefflp2,coefflp]<-varb[iclp, jclp]
+                      }
+                    }
+                  }
+                }
+              } 
+            } 
+          }
+          #End A
+          xprobval<-as.matrix(xmodvals)
+          if ((nxvls > 1) | (mcx > 0)){xprobval<-as.matrix(dummatx[,2:ncol(dummatx)])}
+          #Start B
+          if ((wcmat[(i+1),jmed]==1) & (zcmat[(i+1),jmed]==0))
+          {
+            numplps<-1;modvals<-wmodvals;probeval<-wmodvals;wheremv1<-wherexw
+            nm1vls<-nwvls;lpstsp<-t(matrix(c(1,1)));modcat<-0;jnmod<-wtmp;jnmodlab<-wnames
+            jnok<-1;jnmin<-wmin;jnmax<-wmax;wherejn1<-2
+            if (jmed==1)
+            {
+              wherejn3<-wherexw[1,i]
+              if (nxvls > 1){jnok<-0}
+            }
+            if (jmed > 1)
+            {
+              wherejn1<-wherem[(jmed-1),i]
+              wherejn3<-wheremw[((2*jmed)-3),i]
+            }
+            if (nwvls > 1)
+            {
+              probeval<-wprobval
+              lpstsp[1,2]<-ncol(probeval)
+              modcat<-1;jnok<-0
+            }
+            if (wdich==1){modcat<-1;jnok<-0}
+            problabs<-wnames
+            focpred3<-t(matrix(c(wnames,"(W)"))) 
+            hasw<-1
+            modgrph<-wnames;intprint<-1;sigintct<-sigintct+1;
+            printpbe<-intpb[sigintct,1]
+          }
+          #end B
+          #start C
+          if ((wcmat[(i+1),jmed]==0) & (zcmat[(i+1),jmed]==1))
+          {
+            numplps<-1;modvals<-zmodvals;probeval<-zmodvals;wheremv1<-wherexz
+            nm1vls<-nzvls;lpstsp<-t(matrix(c(1,1)));jnok<-1;jnmod<-ztmp;jnmin<-zmin;jnmax<-zmax
+            jnmodlab<-znames;wherejn1<-2
+            if (jmed==1)
+            { 
+              wherejn3<-wherexz[1,i]
+              if (nxvls > 1){jnok<-0}
+            }
+            if (jmed > 1){wherejn1<-wherem[(jmed-1),i];wherejn3<-wheremz[((2*jmed)-3),i]}
+            if (nzvls > 1)
+            {
+              probeval<-zprobval;lpstsp[1,2]<-ncol(probeval);modcat<-1;jnok<-0
+            }
+            if (zdich == 1){modcat<-1;jnok<-0}
+            problabs<-znames
+            focpred3<-t(matrix(c(znames,"(Z)"))) 
+            modgrph<-znames;hasz<-1;intprint<-1;sigintct<-sigintct+1;
+            printpbe<-intpb[sigintct,1]
+          }
+          # end C
+          # start D
+          if ((wzcmat[(i+1),jmed]==1) |  ((wcmat[(i+1),jmed]==1) & (zcmat[(i+1),jmed]==1)))
+          {
+            numplps<-2;probecnt<-1;intprint<-1
+            if (wzcmat[(i+1),jmed]==1)
+            {
+              sigintct<-sigintct+1;printpbe<-intpb[sigintct,1]
+            } else {
+              sigintct<-sigintct+2;printpbe<-min(intpb[(sigintct-1):sigintct,1])
+            } 
+            panelgrp<-1;hasw<-1;hasz<-1
+            modgrph<-wnames
+            lpstsp<-matrix(1,2,2)
+            wheremv1<-wherexw;nm1vls<-nwvls;wheremv2<-wherexz;nm2vls<-nzvls;jnok<-0
+            if (wzcmat[(i+1),jmed]==1){jnok<-1}
+            if (jmed > 1){mprobval<-mmodvals}
+            if (jmed==1){if (nxvls > 1){jnok<-0}}
+            if (nwvls > 1){lpstsp[1,2]<-ncol(wprobval);modcat<-1;jnok<-0}
+            if (zdich==1){modcat<-1;jnok<-0}
+            lpstsp[2,1]<-lpstsp[1,2]+1;lpstsp[2,2]<-lpstsp[1,2]+1
+            if (nzvls > 1)
+            {
+              lpstsp[2,1]<-lpstsp[1,2]+1
+              lpstsp[2,2]<-lpstsp[1,2]+ncol(zprobval)
+              jnok<-0
+            }
+            if (zdich==1){jnok<-0}
+            omni3<-matrix(0,nrow(b),(nxvls*nwvls),0)
+            if (jmed > 1){omni3<-matrix(0,nrow(b),nwvls)}
+            focpred3<-t(matrix(c(wnames,"(W)")))
+            focpred4<-t(matrix(c("      Moderator:", znames, "(Z)"))) 
+            modvals<-matrix(0,(nrow(wmodvals)*nrow(zmodvals)),2)
+            probeval<-matrix(0,(nrow(wmodvals)*nrow(zmodvals)),(ncol(wprobval)+ncol(zprobval)))
+            for (probei in (1:nrow(wmodvals)))
+            {
+              for (probej in (1:nrow(zmodvals)))
+              {
+                modvals[probecnt,1]<-wmodvals[probei,1]
+                probeval[probecnt,1:nwvls]<-wprobval[probei,]
+                modvals[probecnt,2]<-zmodvals[probej,1]
+                probeval[probecnt,(nwvls+1):(nwvls+nzvls)]<-zprobval[probej,]
+                probecnt<-probecnt+1
+              }
+            }
+            if (wzcmat[(i+1),jmed]==1)
+            {
+              numplps<-numplps+1
+              probprod<-matrix(0,1,(ncol(wprobval)*ncol(zprobval)))
+              lpstsp2<-t(matrix(c(1,1)))
+              lpstsp=rbind(lpstsp,lpstsp2)
+              lpstsp[3,1]<-lpstsp[2,2]+1
+              lpstsp[3,2]<-lpstsp[2,2]+ncol(probprod)
+              jnmod<-ztmp;jnmin<-zmin;jnmax<-zmax;jnmodlab<-znames
+              if (jmed == 1){wherejn1<-wherexw[1,i];wherejn3<-wherexwz[1,i]}
+              if (jmed > 1)
+              {
+                wherejn1<-wheremw[((2*jmed)-3),i]
+                wherejn3<-wheremwz[((2*jmed)-3),i]
+              }
+              for (probei in (1:nrow(wmodvals)))
+              {
+                for (probej in (1:nrow(zmodvals)))
+                {
+                  probtemp<-1
+                  for (probek in (1:ncol(wprobval)))
+                  {
+                    #probtemp<-cbind(probtemp,(wprobval[probei,probek]*zprobval[probej,]))
+                    probtemp<-cbind(probtemp,matrix((wprobval[probei,probek]*zprobval[probej,]),ncol=ncol(zprobval)))
+                  }
+                  probprod<-rbind(probprod,probtemp[1,2:ncol(probtemp)])
+                }
+              }
+              probprod<-probprod[2:nrow(probprod),]
+              probeval<-cbind(probeval,probprod)
+            }
+            problabs<-cbind(wnames,znames)
+          }
+          # end D
+          # start E
+          if (intprint==1)
+          {
+            focpred<-"Focal predictor:"
+            if (jmed==1)
+            {focpred<-cbind(focpred,xnames,"(X)");focplotv<-as.matrix(xmodvals)}
+            if (jmed >1)
+            {
+              if (nms > 1){focpred<-cbind(focpred,mnames[1,(jmed-1)], medlb2[(jmed-1),1])}
+              if (nms==1){focpred<-cbind(focpred,mnames[1,(jmed-1)], "(M)")}
+              focplotv<-as.matrix(mmodvals[,(jmed-1)],nrow=nrow(mmodvals))
+            }
+            focpred2<-cbind("      Moderator:",focpred3)
+            focpred<-rbind(focpred,focpred2)
+            if (ncol(focpred4) > 1){focpred<-rbind(focpred,focpred4);focpred4<-matrix(c(" "))}
+            if (outscreen==1)
+            {
+              if (((plot==1) | (plot==2)) | (printpbe <= intprobe))      
+              {cat("----------\n");write.table(focpred,quote=FALSE,row.names=FALSE,col.names=FALSE)}
+            }
+            foctmp<-matrix(1,nrow(modvals),1)
+            probexpl<-1
+            probeva2<-cbind(foctmp,probeval)
+            if ((jmed==1) & (nxs > 0) & (mcx > 0)){probexpl<-nxvls}
+            foctmp<-matrix(1,nrow(modvals),1)
+            modvals3<-matrix(0,1,(6+ncol(problabs)))
+            probrown<-matrix(0,nrow(probeval),1)
+            jtmp<-1
+            for (probei in (1:nrow(probeval))){probrown[probei,1]<-jtmp;jtmp<-jtmp+nxvls}
+            probrow<-999;modvarl<-problabs
+
+            # start F */ 
+            if ((plot==1) | (plot==2) | (nxvls > 1))
+            {
+              plotvals<-matrix(999,(nrow(modvals)*nrow(focplotv)),(ncol(modvals)+1))
+              for (ploti in (1:nrow(modvals)))
+              {
+                for (plotj in (1:nrow(focplotv)))
+                {
+                  plotvals[(((ploti-1)*nrow(focplotv))+plotj),2:ncol(plotvals)]<-modvals[ploti,]
+                  plotvals[(((ploti-1)*nrow(focplotv))+plotj),1]<-focplotv[plotj,1]
+                }
+              }
+              focpredn<-3
+              if (jmed==1)
+              {
+                if (nxvls > 1){focpredn<-(nxvls+1)}
+                if ((nxvls==1) & (xdich==1)){focpredn<-2}
+              }
+              meanmat<-diag(c(means))
+              onesmat<-matrix(1,nrow(meanmat),(nrow(probeval)*focpredn))
+              probeplt<-t(diag(means)%*%onesmat)
+              # start G
+              if (jmed==1)
+              {
+                if ((wcmat[(i+1),1]==1) | (zcmat[(i+1),1]==1))
+                {
+                  plotcnt<-1;iloops<-nwpval*nzpval;plotmx<-nxpval*nzpval
+                  if ((wcmat[(i+1),1]==1) & (zcmat[(i+1),1]==0))
+                  {iloops<-nwpval;plotmx<-nxpval}
+                  if ((wcmat[(i+1),1]==0) & (zcmat[(i+1),1]==1))
+                  {iloops<-nzpval;plotmx<-nxpval}     
+                  xestvals<-matrix(-999,(nxpval*iloops),ncol(xprobval))
+                  if (wcmat[(i+1),1]==1){westvals<-matrix(-999,nrow(xestvals),ncol(wprobval))} 
+                  if (zcmat[(i+1),1]==1){zestvals<-matrix(-999,nrow(xestvals),ncol(zprobval))}
+                  for (ploti in (1:iloops))
+                  {
+                    for (plotj in (1:nxpval))
+                    {xestvals[plotcnt,]<-xprobval[plotj,];plotcnt<-plotcnt+1}
+                  }
+                  plotcnt<-1;plotcnt1<-1;plotcnt2<-1;plotcntz<-1
+                  for (ploti in (1:(iloops*nxpval)))
+                  {
+                    if (wcmat[(i+1),1]==1){westvals[ploti,]=wprobval[plotcnt1,]}        
+                    if ((wcmat[(i+1),1]==0) & (zcmat[(i+1),1]==1))
+                    {zestvals[ploti,]<-zprobval[plotcnt1,]}   
+                    if ((wcmat[(i+1),1]==1) & (zcmat[(i+1),1]==1))
+                    {zestvals[ploti,]<-zprobval[plotcnt2,];plotcntz=plotcntz+1}
+                    plotcnt<-plotcnt+1
+                    if (plotcnt > plotmx){plotcnt<-1;plotcnt1<-plotcnt1+1}
+                    if (plotcntz > nxpval)
+                    {
+                      plotcnt2<-plotcnt2+1;plotcntz<-1
+                      if (plotcnt2 > nzpval){plotcnt2<-1} 
+                    }
+                  }
+                  probeplt[,2:(1+(ncol(xestvals)))]<-xestvals 
+                  if (wcmat[(i+1),1]==1)
+                  {probeplt[,wherew[1,i]:wherew[2,i]]<-westvals}            
+                  if (zcmat[(i+1),1]==1)
+                  {probeplt[,wherez[1,i]:wherez[2,i]]<-zestvals}  
+                }
+              }
+              # end G
+              # start H
+              if (jmed > 1)
+              {
+                if ((wcmat[(i+1),jmed]==1) | (zcmat[(i+1),jmed]==1))
+                {
+                  plotcnt<-1;iloops<-(nwpval*nzpval);plotmx<-(3*nzpval)
+                  if ((wcmat[(i+1),jmed]==1) & (zcmat[(i+1),jmed]==0))
+                  {iloops<-nwpval;plotmx<-3}
+                  if ((wcmat[(i+1),jmed]==0) & (zcmat[(i+1),jmed]==1))
+                  {iloops<-nzpval;plotmx<-3}
+                  mestvals<-matrix(-999,(3*iloops),1)
+                  if (wcmat[(i+1),jmed]==1)
+                  {westvals<-matrix(-999,nrow(mestvals),ncol(wprobval))}
+                  if (zcmat[(i+1),jmed]==1)
+                  {zestvals<-matrix(-999,nrow(mestvals),ncol(zprobval))}
+                  for (ploti in (1:iloops))
+                  {
+                    for (plotj in (1:3))
+                    {
+                      mestvals[plotcnt,]<-mprobval[plotj,(jmed-1)]
+                      plotcnt<-plotcnt+1
+                    }
+                  }
+                  plotcnt<-1;plotcnt1<-1;plotcnt2<-1;plotcntz<-1
+                  for (ploti in (1:(iloops*3)))
+                  {
+                    if (wcmat[(i+1),jmed]==1)
+                    {westvals[ploti,]<-wprobval[plotcnt1,]}     
+                    if ((wcmat[(i+1),jmed]==0) & (zcmat[(i+1),jmed]==1))
+                    {zestvals[ploti,]<-zprobval[plotcnt1,]}   
+                    if ((wcmat[(i+1),jmed]==1) & (zcmat[(i+1),jmed]==1))
+                    {zestvals[ploti,]<-zprobval[plotcnt2,];plotcntz<-plotcntz+1}
+                    plotcnt<-plotcnt+1
+                    if (plotcnt > plotmx){plotcnt<-1;plotcnt1<-plotcnt1+1}        
+                    if (plotcntz > 3)
+                    {
+                      plotcnt2<-plotcnt2+1;plotcntz<-1
+                      if (plotcnt2 > nzpval){plotcnt2<-1} 
+                    }
+                  }
+                  probeplt[,wherem[(jmed-1),i]]<-mestvals
+                  if (wcmat[(i+1),jmed]==1)
+                  {
+                    if (model != 74)
+                    {probeplt[,(wherew[1,i]):(wherew[2,i])]<-westvals}
+                    if (model==74)
+                    {probeplt[,(wherex[1,i]):(wherex[2,i])]<-westvals}
+                  }    
+                  if (zcmat[(i+1),jmed]==1)
+                  {probeplt[,(wherez[1,i]):(wherez[2,i])]<-zestvals}  
+                }
+              } 
+              # end H
+              # Here I am doing the multiplications to produce data for the plot
+              prodloop <-1
+              if (jmed==1){prodloop<-ncol(xestvals)}
+              if ((wcmat[(i+1),jmed])==1)
+              {
+                plotcnt<-0
+                for (ploti in (1:prodloop))
+                {
+                  for (plotj in (1:ncol(westvals)))
+                  {
+                    if (jmed==1)
+                    {probeplt[,(wherexw[1,i]+plotcnt)]<-(xestvals[,ploti]*westvals[,plotj])}
+                    if (jmed > 1)
+                    {probeplt[,(wheremw[((jmed*2)-3) ,i]+plotcnt)]<-(mestvals[,ploti]*westvals[,plotj])}
+                    plotcnt<-plotcnt+1
+                  }
+                } 
+              }
+              if ((zcmat[(i+1),jmed])==1)
+              {
+                plotcnt<-0
+                for (ploti in (1:prodloop))
+                {
+                  for (plotj in (1:ncol(zestvals)))
+                  {   
+                    if (jmed==1)
+                    {probeplt[,(wherexz[1,i]+plotcnt)]<-(xestvals[,ploti]*zestvals[,plotj])}    
+                    if (jmed > 1)
+                    {probeplt[,(wheremz[((jmed*2)-3),i]+plotcnt)]<-(mestvals[,ploti]*zestvals[,plotj])}
+                    plotcnt<-plotcnt+1
+                  }
+                } 
+              }
+              if ((wzcmat[(i+1),jmed])==1)
+              {
+                plotcnt<-0;threeway<-1
+                for (ploti in (1:ncol(westvals)))
+                {
+                  for (plotj in (1:ncol(zestvals)))
+                  {
+                    probeplt[,(wherewz[1,i]+plotcnt)]<-(westvals[,ploti]*zestvals[,plotj])
+                    plotcnt<-plotcnt+1
+                  }
+                }  
+                plotcnt<-0
+                for (plotk in (1:prodloop))
+                {
+                  for (ploti in (1:ncol(westvals)))
+                  {
+                    for (plotj in (1:ncol(zestvals)))
+                    {
+                      if (jmed==1)
+                      {probeplt[,(wherexwz[1,i]+plotcnt)]<-(xestvals[,plotk]*westvals[,ploti]*zestvals[,plotj])}          
+                      if (jmed > 1)
+                      {probeplt[,(wheremwz[((jmed*2)-3),i]+plotcnt)]<-(mestvals[,plotk]*westvals[,ploti]*zestvals[,plotj])}          
+                      plotcnt<-plotcnt+1
+                    }
+                  } 
+                }
+              }
+              # here is where we add holding constant products as needed
+              # start I
+              for (newplp in (1:i))
+              {  
+                if (newplp != jmed)
+                {  
+                  if (wcmat[(i+1),newplp]==1)
+                  {
+                    prodloop<-1
+                    if (newplp==1){prodloop<-nxvls}
+                    plotcnt<-0
+                    for (ploti in (1:prodloop))
+                    {
+                      for (plotj in (1:nwvls))
+                      {
+                        if (newplp==1)
+                        {probeplt[,(wherexw[1,i]+plotcnt)]<-probeplt[,(1+ploti)]*probeplt[,(wherew[1,i]+plotj-1)]}
+                        if (newplp > 1)
+                        {
+                          if (model != 74)
+                          {probeplt[,(wheremw[((newplp*2)-3) ,i]+plotcnt)]<-probeplt[,wherem[(newplp-1),i]]*probeplt[,(wherew[1,i]+plotj-1)]}
+                          if (model==74)
+                          {probeplt[,(wheremw[((newplp*2)-3) ,i]+plotcnt)]<-probeplt[,wherem[(newplp-1),i]]*probeplt[,(wherex[1,i]+plotj-1)]}           
+                        }
+                        plotcnt<-plotcnt+1
+                      }
+                    } 
+                  }  
+                  if (zcmat[(i+1),newplp]==1)
+                  {
+                    prodloop<-1
+                    if (newplp==1){prodloop<-nxvls}
+                    plotcnt<-0
+                    for (ploti in (1:prodloop))
+                    {
+                      for (plotj in (1:nzvls))
+                      {
+                        if (newplp==1)
+                        {probeplt[,(wherexz[1,i]+plotcnt)]<-probeplt[,(1+ploti)]*probeplt[,(wherez[1,i]+plotj-1)]}
+                        if (newplp > 1)
+                        {probeplt[,(wheremz[((newplp*2)-3),i]+plotcnt)]<-probeplt[,wherem[(newplp-1),i]]*probeplt[,(wherez[1,i]+plotj-1)]}
+                        plotcnt<-plotcnt+1
+                      }
+                    } 
+                  }
+                  if (wzcmat[(i+1),newplp]==1)
+                  {
+                    plotcnt<-0
+                    if (threeway==0)
+                    {
+                      for (ploti in (1:nwvls))
+                      {
+                        for (plotj in (1:nzvls))
+                        {
+                          probeplt[,(wherewz[1,i]+plotcnt)]<-probeplt[,(wherew[1,i]+ploti-1)]*probeplt[,(wherez[1,i]+plotj-1)]
+                          plotcnt<-plotcnt+1
+                        }
+                      }
+                    } 
+                    prodloop<-1
+                    if (newplp==1){prodloop<-nxvls}
+                    plotcnt<-0
+                    for (plotk in (1:prodloop))
+                    {
+                      for (ploti in (1:nwvls))
+                      {
+                        for (plotj in (1:nzvls))
+                        {
+                          if (newplp==1)
+                          {probeplt[,(wherexwz[1,i]+plotcnt)]<-probeplt[,(1+plotk)]*probeplt[,(wherew[1,i]+ploti-1)]*probeplt[,(wherez[1,i]+plotj-1)]}      
+                          if (newplp > 1)
+                          {probeplt[,(wheremwz[((newplp*2)-3),i]+plotcnt)]<-probeplt[,wherem[(newplp-1),i]]*probeplt[,(wherew[1,i]+ploti-1)]*probeplt[,(wherez[1,i]+plotj-1)]}      
+                          plotcnt<-plotcnt+1
+                        }
+                      } 
+                    }
+                  }      
+                }
+              }
+              #END I
+              predvals<-probeplt%*%b
+
+              if ((i==(nms+nys)) & (ydich==1))
+              {
+                predvalt<-as.numeric(predvals < 709.7)
+                prevalt7<-(1-predvalt)*(709.7)
+                predvals<-(predvals*predvalt)+prevalt7
+                expyhat<-exp(predvals)/(1+exp(predvals))
+              } 
+              sepred<-matrix(999,nrow(plotvals),3)
+              for (sei in (1:nrow(plotvals)))
+              {
+                ask<-as.matrix(probeplt[sei,],ncol=ncol(probeplt))       
+                sepred[sei,1]<-sqrt(t(ask)%*%varb%*%ask)
+                if ((i < (nms+nys)) | (ydich==0))
+                {
+                  sepred[sei,2]<-predvals[sei,1]-tval*sepred[sei,1]
+                  sepred[sei,3]<-predvals[sei,1]+tval*sepred[sei,1]
+                }
+                if ((i==(nms+nys)) & (ydich==1))
+                {
+                  sepred[sei,2]<-predvals[sei,1]-xp2*sepred[sei,1]
+                  sepred[sei,3]<-predvals[sei,1]+xp2*sepred[sei,1]
+                }
+              }
+              prevloc<-ncol(plotvals)+1
+              probeplt<-cbind(plotvals,predvals)
+              if (plot==2){probeplt<-cbind(probeplt,sepred)}
+              if ((i==(nms+nys)) & (ydich==1))
+              {probeplt<-cbind(probeplt,expyhat)}
+              didsome<-0
+            }
+            # END F
+
+            # here is the loop that is printing the conditional effects
+            # this does conditional two way interactions
+            # START J
+            if ((wzcmat[(i+1),jmed]==1) & (printpbe <= intprobe))
+            {
+              if (jmed==1)
+              {omnilp2<-nxvls*nwvls;omnitmp<-diag(omnilp2);omni3[wherexw[1,i]:wherexw[2,i],]<-omnitmp}  
+              if (jmed>1)
+              {omnilp2<-nwvls;omnitmp<-diag(omnilp2);omni3[wheremw[((jmed*2)-3),i]:wheremw[((jmed*2)-2),i],]<-omnitmp}
+              omnif<-matrix(0,1,4)
+              if ((i==(nms+nys)) & (ydich==1))
+              {omnif<-matrix(0,1,3)}
+              condeff3<-0
+              for (omnilp1 in (1:nrow(zprobval)))
+              {
+                for (omnilp in (1:omnilp2))
+                {
+                  if (jmed==1)
+                  {
+                    omni3[(wherexwz[1,i]+((omnilp-1)*nzvls)):(wherexwz[1,i]+((omnilp-1)*nzvls)+(nzvls-1)),omnilp]<-t(zprobval[omnilp1,])
+                  }
+                  if (jmed > 1)
+                  {
+                    omni3[(wheremwz[((jmed*2)-3),i]+((omnilp-1)*nzvls)):(wheremwz[((jmed*2)-3),i]+((omnilp-1)*nzvls)+(nzvls-1)),omnilp]<-t(zprobval[omnilp1,])
+                  }
+                }
+                condeff<-t(omni3)%*%b
+                condeff3<-rbind(condeff3,condeff)
+                fresult2<-process.ftest3(omni3,b,varb,chr=0,brsq2,1,y,x)
+
+                if ((i==(nms+nys)) & (ydich==1))
+                {
+                  fratio<-fresult2[1,1]*ncol(omni3)
+                  pfr<-(1-pchisq(fratio,df=ncol(omni3)))
+                  fresult2<-cbind(fratio,ncol(omni3),pfr)
+                }
+                omnif<-rbind(omnif,fresult2)
+              }
+              omnif<-matrix(omnif[2:nrow(omnif),],ncol=ncol(omnif))
+              clabtmp<-znames
+              condeff3<-matrix(condeff3[2:nrow(condeff3),],ncol=ncol(condeff3))
+              if ((nxvls*nwvls)==1)
+              {
+                omnif<-cbind(condeff3,omnif)
+                clabtmp<-cbind(clabtmp,"effect")
+              } 
+              omnif<-cbind(zmodvals,omnif)
+              if ((i < nms+nys) | (ydich==0))
+              {clabtmp<-c(clabtmp,hcflab,"df1","df2","p")}      
+              if ((i==(nms+nys)) & (ydich==1))
+              {clabtmp<-c(clabtmp,"Chi-sq","df","p")}
+              resultm2<-matrix(99999,nrow(omnif),maxresm)
+              resultm2[1:nrow(omnif),1:ncol(omnif)]<-omnif
+              resultm<-rbind(resultm,resultm2)
+              omnif2<-noquote(matrix(sprintf(decimals,omnif),nrow=nrow(omnif)))
+              colnames(omnif2)<-clabtmp
+              rownames(omnif2)<-t(matrix(replicate(nrow(omnif)," ")))
+              if (outscreen==1)
+              {
+                if (jmed==1)
+                {cat("\nTest of conditional X*W interaction at value(s) of Z:\n")
+                  print(omnif2,right=T)}
+                if (jmed > 1)
+                {cat("\nTest of conditional M*W interaction at value(s) of Z:\n")
+                  print(omnif2,right=T)}
+              }
+            }
+            # END J
+
+            # start O 
+            for (probei in (1:probexpl))
+            {
+              if (probexpl > 1)
+              {
+                foctmp<-matrix(0,nrow(modvals),probexpl)
+                foctmp[,probei]<-foctmp[,probei]+1
+                probtemp<-matrix(0,nrow(modvals),1)
+                for (probem in (1:numplps))
+                {for (probek in (1:nxvls))
+                {for (probej in (lpstsp[probem,1]:lpstsp[probem,2]))
+                {probtemp<-cbind(probtemp,foctmp[,probek]*probeval[,probej])}  
+                }
+                }
+                probeva2<-probtemp[,2:ncol(probtemp)]
+                probeva2<-cbind(foctmp,probeva2)
+              }    
+              probres<-probeva2%*%probcoef
+              probrese<-as.matrix(sqrt(diag(probeva2%*%probvarb%*%t(probeva2)))) 
+              tratio<-probres/probrese
+              if ((ydich==1) & (i==(nms+nys)))
+              {
+                p<-2*(1-pnorm(abs(tratio)))
+              } else {
+                p<-2*pt(-abs(tratio),df=dfres)
+              }
+              modvals2<-cbind(modvals,probres,probrese,tratio, p)
+              if ((i < nms+nys) | (ydich==0))
+              {
+                modvals2<-cbind(modvals2,(probres-as.numeric(tval)*probrese),(probres+as.numeric(tval)*probrese))   
+                problabs<-cbind(problabs,"effect",hclab,"t", "p", "LLCI", "ULCI")
+              }
+              if ((ydich==1) & (i==(nms+nys)))
+              {
+                modvals2<-cbind(modvals2,(probres-xp2*probrese),(probres+xp2*probrese))
+                problabs<-cbind(problabs,"effect","se","Z", "p", "LLCI", "ULCI")
+              }
+              # start L
+              if ((probexpl > 1) & (printpbe <= intprobe))
+              {
+                if (hasz==1){printz<-1}
+                if (hasw==1){printw<-1}
+                probrlab<-matrix(xcatlab[probei,1],nrow(modvals),1)
+                modvals3<-rbind(modvals3,modvals2)
+                probrow<-rbind(probrow,probrown)
+                probrown<-probrown+1
+                if (probei==probexpl)
+                {
+                  xproblab<-xcatlab[1:nxvls,1]
+                  probrow<-matrix(probrow[2:nrow(probrow),1])
+                  modvals3<-modvals3[2:nrow(modvals3),]
+                  #modvals3<-modvals3[order(modvals3[,1]),]
+                  modvals3<-modvals3[order(probrow[,1]),]
+                  start2<-1
+                  problabs<-problabs[1,(1+(ncol(modvarl))):ncol(problabs)]
+                  pstart<-1
+                  # start K
+                  for (probek in (1:nrow(probeval)))
+                  {
+                    endstart<-start2+(nxvls-1)
+                    temp<-modvals3[start2:endstart,(1+ncol(modvarl)):ncol(modvals3)]
+                    temp2<-t(modvals3[start2:start2,1:ncol(modvarl)])
+                    trnames<-t(modvarl)
+                    if (outscreen==1)
+                    {
+                      if (probek > 1){cat("----------\n")}
+                      if (probek==1)
+                      {
+                        cat("\nConditional effects of the focal predictor at values of the moderator(s):\n")
+                        if ((jmed==1) & (i ==(nms+nys)) & (nms > 0))
+                        {
+                          if (nxvls==1)
+                          {cat("\n(These are also the conditional direct effects of X on Y.)\n")}
+                          if (nxvls != 1)
+                          {cat("\n(These are also the relative conditional direct effects of X on Y.)\n")}
+                        }
+                        cat("\n")
+                      }
+                      cat("Moderator value(s):\n")
+                    }
+                    resultm2<-matrix(99999,nrow(temp2),maxresm)
+                    resultm2[1:nrow(temp2),1:ncol(temp2)]<-temp2
+                    resultm<-rbind(resultm,resultm2)
+                    temp2<-noquote(matrix(sprintf(decimals,temp2),nrow=nrow(temp2)))
+                    temp3<-matrix(temp2[1,1:ncol(temp2)])
+                    rownames(temp3)<-trnames
+                    colnames(temp3)<-" "
+                    if (outscreen==1)
+                    {print(temp3,right=TRUE,quote=FALSE)
+                      cat("\n")}
+                    #for (mdpntr in (1:ncol(temp2)))
+                    #{
+                    #write.table(temp2[1,mdpntr],quote=FALSE,row.names=trnames[mdpntr,1],col.names=FALSE)
+                    #}          
+                    resultm2<-matrix(99999,nrow(temp),maxresm)
+                    resultm2[1:nrow(temp),1:ncol(temp)]<-temp
+                    resultm<-rbind(resultm,resultm2)
+                    temp<-noquote(matrix(sprintf(decimals,temp),nrow=nrow(temp)))
+                    colnames(temp)<-problabs[1:ncol(temp)]
+                    rownames(temp)<-xproblab
+                    if (outscreen==1)
+                    {print(temp,right=T)}
+                    start2<-start2+nxvls
+                    didsome<-1
+                    if (jmed==1)
+                    {
+                      mod1val<-probeval[probek,1:nm1vls]
+                      for (omnilp in (1:nxvls))
+                      {
+                        omni[(wheremv1[1,i]+((omnilp-1)*nm1vls)):(wheremv1[1,i]+((omnilp-1)*nm1vls)+(nm1vls-1)),omnilp]<-t(mod1val)
+                        if (nm1vls < ncol(probeval))
+                        {
+                          mod2val<-probeval[probek,(nm1vls+1):(nm1vls+nm2vls)]
+                          omni[(wheremv2[1,i]+((omnilp-1)*nm2vls)):(wheremv2[1,i]+((omnilp-1)*nm2vls)+(nm2vls-1)),omnilp]<-t(mod2val)
+                          if ((nm1vls+nm2vls) < ncol(probeval))
+                          {
+                            intlen<-(nm1vls*nm2vls)
+                            modintvl<-probeval[probek,(nm1vls+nm2vls+1):ncol(probeval)]
+                            omni[(wherexwz[1,i]+((omnilp-1)*intlen)):(wherexwz[1,i]+((omnilp-1)*intlen)+(intlen-1)),omnilp]<-t(modintvl)
+                          }
+                        }
+                      }
+                      fresult2<-process.ftest3(omni,b,varb,0,brsq2,1,y,x)
+                      if ((i == (nms+nys)) & (ydich==1))
+                      {
+                        fratio<-fresult2[1,1]*nxvls
+                        pfr<-(1-pchisq(fratio,df=nxvls))
+                        fresult2<-cbind(fratio,nxvls,pfr)
+                      }
+                      resultm2<-matrix(99999,nrow(fresult2),maxresm)
+                      resultm2[1:nrow(fresult2),1:ncol(fresult2)]<-fresult2
+                      resultm<-rbind(resultm,resultm2)
+                      fresult2<-noquote(matrix(sprintf(decimals,fresult2),nrow=nrow(fresult2)))
+                      if (outscreen==1)
+                      {
+                        if (i < (nms + nys) | (ydich == 0))
+                        {
+                          cat("\nTest of equality of conditional means\n")            
+                          colnames(fresult2)<-c(hcflab,"df1","df2","p")
+                          rownames(fresult2)<-" "
+                          print(fresult2,right=T)
+                        }
+                        if ((i==(nms + nys)) & (ydich==1))
+                        {
+                          cat("\nTest of equality of conditional logits or probabilities\n")
+                          rownames(fresult2)<-" "
+                          colnames(fresult2)<-c("Chi-sq","df","p")
+                          print(fresult2,right=T)            
+                        }
+                      }
+                      probetmp<-probeplt[pstart:(pstart+nxvls),1]
+                      probetmp<-cbind(probetmp,probeplt[pstart:(pstart+nxvls),prevloc:ncol(probeplt)])
+                      pstart<-pstart+(nxvls+1)
+                      resultm2<-matrix(99999,nrow(probetmp),maxresm)
+                      resultm2[1:nrow(probetmp),1:ncol(probetmp)]<-probetmp
+                      resultm<-rbind(resultm,resultm2)
+                      probetmp<-noquote(matrix(sprintf(decimals,probetmp),nrow=nrow(probetmp)))
+                      if (outscreen==1)
+                      {
+                        if (i < ((nms + nys)) | (ydich==0))
+                        {   
+                          clabtmp<-cbind(xnames, outnames[i,1], hclab, "LLCI", "ULCI")
+                          cat("\nEstimated conditional means being compared:\n")
+                          colnames(probetmp)<-clabtmp[1:ncol(probetmp)]
+                          rownames(probetmp)<-t(matrix(replicate(nrow(probetmp)," ")))
+                          print(probetmp,right=T)
+                        }
+                        if ((i==(nms+nys)) & (ydich==1))
+                        {
+                          cat("\nEstimated conditional logits and probabilities:\n")
+                          clabtmp<-c(xnames, outnames[i,1], "prob")
+                          probetm2<-matrix(probetmp[,1:2],ncol=2)
+                          probetm2<-cbind(probetm2,probetmp[,ncol(probetmp)])
+                          probetm2<-noquote(probetm2)
+                          colnames(probetm2)<-clabtmp[1:ncol(probetm2)]
+                          rownames(probetm2)<-t(matrix(replicate(nrow(probetm2)," ")))
+                          print(probetm2,right=T)
+                        }
+                      }
+                    }
+                  }
+                  # end K
+                }
+              }
+              # end L
+              # start N
+              if ((probexpl==1) & (printpbe <= intprobe))
+              {
+                resultm2<-matrix(99999,nrow(modvals2),maxresm)
+                resultm2[1:nrow(modvals2),1:ncol(modvals2)]<-modvals2
+                resultm<-rbind(resultm,resultm2)
+                modva2<-noquote(matrix(sprintf(decimals,modvals2),nrow=nrow(modvals2)))
+                colnames(modva2)<-problabs[1:ncol(modva2)]
+                rownames(modva2)<-t(matrix(replicate(nrow(modva2)," ")))
+                if (outscreen==1)
+                {cat("\nConditional effects of the focal predictor at values of the moderator(s):\n")
+                  print(modva2,right=T)}
+                didsome<-1
+                if (hasz==1){printz<-1}
+                if (hasw==1){printw<-1}
+                # start M (JN method)
+                if ((jn==1) & (jnok==1))
+                {
+                  if (criterr==0)
+                  {
+                    dfres<-(n-nrow(b));
+                    roots<-as.matrix(99999)
+                    jncrit<-(dfres* (exp((dfres-(5/6))*((xp2/(dfres-(2/3)+(.11/dfres)))*(xp2/(dfres-(2/3)+(.11/dfres)))))-1))
+                    if ((i ==(nms+nys)) & (ydich==1)){jncrit<-xp2*xp2}
+                    jnb1<-b[wherejn1,1]
+                    jnb3<-b[wherejn3,1]
+                    jnsb1<-varb[wherejn1,wherejn1]
+                    jnsb3<-varb[wherejn3,wherejn3]
+                    jnsb1b3<-varb[wherejn1,wherejn3]
+                    ajn<-(jncrit*jnsb3)-(jnb3*jnb3)
+                    bjn<-2*((jncrit*jnsb1b3)-(jnb1*jnb3))
+                    cjn<-((jncrit*jnsb1)-(jnb1*jnb1))
+                    radarg<-(bjn*bjn)-(4*ajn*cjn)
+                    den<-2*ajn
+                    nrts<-0
+                    if ((radarg >= 0) & (den != 0))
+                    {
+                      x21<-(-bjn+sqrt(radarg))/den
+                      x22<-(-bjn-sqrt(radarg))/den
+                      if ((x21 >= jnmin) & (x21 <= jnmax))
+                      {nrts<-1;roots<-rbind(roots,x21)}
+                      if ((x22 >= jnmin) & (x22 <= jnmax))
+                      {nrts<-nrts+1;roots<-rbind(roots,x22)}
+                      roots<-cbind(roots,matrix(0,nrow(roots),2))
+                    }
+                    if (nrts > 0)
+                    {	                          
+                      roots<-matrix(roots[2:nrow(roots),1:3],ncol=3)
+                      roots[1,2]<-sum((as.numeric(jnmod < roots[1,1]))/n)*100
+                      roots[1,3]<-sum((as.numeric(jnmod > roots[1,1]))/n)*100
+                      if (nrow(roots)==2)
+                      {
+                        roots[2,2]<-sum((as.numeric(jnmod < roots[2,1]))/n)*100
+                        roots[2,3]<-sum((as.numeric(jnmod > roots[2,1]))/n)*100
+                      }
+                      roots2<-noquote(matrix(sprintf(decimals,roots),nrow=nrow(roots)))
+                      colnames(roots2)<-c("Value", "% below", "% above")
+                      rownames(roots2)<-t(matrix(replicate(nrow(roots)," ")))
+                      if (nrts==1){tmprts=matrix(99999,1,3);roots<-rbind(roots,tmprts)}
+                      if (outscreen==1)
+                      {cat("\nModerator value(s) defining Johnson-Neyman significance region(s):\n")
+                        print(roots2,right=T)}
+                    }
+                    if (nrts==0)
+                    {
+                      roots<-as.matrix(c(99999,99999))
+                      if (outscreen==1)
+                      {cat("\nThere are no statistical significance transition points within the observed\n")
+                        cat("range of the moderator found using the Johnson-Neyman method.\n")}
+                    }
+                    resultm2<-matrix(99999,nrow(roots),maxresm)
+                    resultm2[1:nrow(roots),1:ncol(roots)]<-roots
+                    resultm<-rbind(resultm,resultm2)
+                    jnvals<-matrix(0,23,7)
+                    for (jni in (0:(21-nrts)))
+                    {jnvals[(jni+1),1]<-jnmin+(jni*((jnmax-jnmin)/(21-nrts)))}
+                    if (nrts > 0)
+                    {
+                      for (jni in (1:nrts))
+                      {
+                        for (jnj in (2:nrow(jnvals)))
+                        {
+                          if ((roots[jni,1] > jnvals[(jnj-1),1]) & (roots[jni,1] < jnvals[jnj,1]))
+                          {
+                            jnvals[(jnj+1):(21+jni),1]<-jnvals[jnj:(20+jni),1]
+                            jnvals[jnj,1]<-roots[jni,1]
+                          }
+                        }
+                      }
+                    }
+                    jnvals<-jnvals[1:22,] 
+                    for (jni in (1:nrow(jnvals)))
+                    {
+                      jnvals[jni,2]<-jnb1+jnb3*jnvals[jni,1]
+                      jnvals[jni,3]<-sqrt(jnsb1+2*jnvals[jni,1]*jnsb1b3+(jnvals[jni,1]*jnvals[jni,1])*jnsb3)
+                      jnvals[jni,4]<-jnvals[jni,2]/jnvals[jni,3]
+                      jnvals[jni,5]<-2*pt(-abs(jnvals[jni,4]), df=dfres)
+                      jnvals[jni,6]<-jnvals[jni,2]-sqrt(jncrit)*jnvals[jni,3]
+                      jnvals[jni,7]<-jnvals[jni,2]+sqrt(jncrit)*jnvals[jni,3]
+                      if ((i==(nms + nys)) & (ydich==1))
+                      {
+                        jnvals[jni,5]<-2*(1-pnorm(abs(jnvals[jni,4])))
+                        jnvals[jni,6]<-jnvals[jni,2]-xp2*jnvals[jni,3]
+                        jnvals[jni,7]<-jnvals[jni,2]+xp2*jnvals[jni,3]
+                      }
+                    } 
+                    resultm2<-matrix(99999,nrow(jnvals),maxresm)
+                    resultm2[1:nrow(jnvals),1:ncol(jnvals)]<-jnvals
+                    resultm<-rbind(resultm,resultm2)
+                    jnvals2<-noquote(matrix(sprintf(decimals,jnvals),nrow=nrow(jnvals)))
+                    rownames(jnvals2)<-t(matrix(replicate(nrow(jnvals)," ")))
+                    if ((i < nms+nys) | (ydich==0))
+                    {colnames(jnvals2)<-c(jnmodlab,"effect", hclab, "t", "p", "LLCI", "ULCI")}          
+                    if ((i==(nms+nys)) & (ydich==1))
+                    {colnames(jnvals2)<-c(jnmodlab,"effect","se","Z", "p", "LLCI", "ULCI")}
+                    if (outscreen==1)
+                    {
+                      if (((wcmat[(i+1),jmed]==1) | (zcmat[(i+1),jmed]==1)) & (wzcmat[(i+1),jmed]==0))
+                      {cat("\nConditional effect of focal predictor at values of the moderator:\n");print(jnvals2,right=T)}          
+                      if ((jmed==1) & (wzcmat[(i+1),jmed]==1))
+                      {cat("\nConditional X*W interaction at values of the moderator Z:\n");print(jnvals2,right=T)}   
+                      if ((jmed > 1) & (wzcmat[(i+1),jmed]==1))
+                      {cat("\nConditional M*W interaction at values of the moderator Z:\n");print(jnvals2,right=T)} 
+                    }  
+                  }
+                }
+                # END M (JN method)
+              }
+              if ((i==(nms+nys)) & (jmed==1) & (bcmat[nrow(bcmat),1]==1))
+              {
+                if (probei==1)
+                {direfflb<-problabs;direff<-modvals2}
+                if (probei>1)
+                {direff<-rbind(direff,modvals2)}  
+              }
+              intprint<-0
+              #  This does the contrast for conditional effects */
+              if ((jmed==1) & (i==1) & (nms==0) & (modcok==1))
+              {
+                contvec2=matrix(1,2,1)
+                contvec2<-cbind(contvec2,wcontval,zcontval)
+                if (wzcmat[(i+1),jmed]==1)
+                {
+                  for (conti in (1:ncol(wcontval)))
+                  {
+                    for (contj in (1:ncol(zcontval)))
+                    {contvec2<-cbind(contvec2,wcontval[,conti]*zcontval[,contj])}
+                  }
+                }
+                conteff<-contvec2%*%probcoef
+                contdiff<-matrix(contvec2[1,]-contvec2[2,])
+                contse<-sqrt(t(contdiff)%*%probvarb%*%contdiff)
+                conteffd<-conteff[1,1]-conteff[2,1]
+                contvec=cbind(contvec,conteff)
+                contvecm<-contvec
+                resultm2<-matrix(99999,nrow(contvecm),maxresm)
+                resultm2[1:nrow(contvecm),1:ncol(contvecm)]<-contvecm
+                resultm<-rbind(resultm,resultm2)
+                contvecm<-noquote(matrix(sprintf(decimals,contvecm),nrow=nrow(contvecm)))
+                rownames(contvecm)<-c("Effect1:","Effect2:")
+                colnames(contvecm)<-problabs[1:3]
+                if (outscreen==1)
+                {cat("\nContrast between conditional effects of X:\n")
+                  print(contvecm,right=T)}
+                if (ydich==0)
+                {
+                  p<-2*pt(-abs(conteffd/contse),df=dfres)
+                  contvec<-cbind(conteffd,contse,conteffd/contse, p)
+                  contvec<-cbind(contvec,(conteffd-(tval*contse)))
+                  contvec<-cbind(contvec,(conteffd+(tval*contse)))
+                  contlabs<-c("Contrast", hclab, "t", "p", "LLCI", "ULCI")
+                }
+                if (ydich==1)
+                { 
+                  p<-2*(1-pnorm(abs(conteffd/contse)))
+                  contvec<-cbind(conteffd,contse,conteffd/contse, p)
+                  contvec<-cbind(contvec,(conteffd-(xp2*contse)))
+                  contvec<-cbind(contvec,(conteffd+(xp2*contse)))
+                  contlabs<-c("Contrast", "se", "Z", "p", "LLCI", "ULCI")
+                } 
+                resultm2<-matrix(99999,nrow(contvec),maxresm)
+                resultm2[1:nrow(contvec),1:ncol(contvec)]<-contvec
+                resultm<-rbind(resultm,resultm2)
+                contvec<-noquote(matrix(sprintf(decimals,contvec),nrow=nrow(contvec)))
+                colnames(contvec)<-contlabs
+                rownames(contvec)<-" "
+                if (outscreen==1)
+                {cat("\nTest of Effect1 minus Effect2\n")
+                  print(contvec,right=T)}
+              }
+            }
+            # end O
+
+            if ((plot==1) | (plot==2))
+            { 
+              datalabs<-cbind(t(focpred[,2]),outnames[i,1])
+              if (plot==2)
+              {datalabs<-c(datalabs,"se", "LLCI", "ULCI")}
+              if ((i==(nms+nys)) & (ydich==1))
+              {datalabs<-c(datalabs,"prob")}
+              resultm2<-matrix(99999,nrow(probeplt),maxresm)
+              resultm2[1:nrow(probeplt),1:ncol(probeplt)]<-probeplt
+              resultm<-rbind(resultm,resultm2)
+              probepnt<-noquote(matrix(sprintf(decimals,probeplt),nrow=nrow(probeplt)))
+              colnames(probepnt)<-datalabs
+              rownames(probepnt)<-t(matrix(replicate(nrow(probepnt)," ")))
+              if (outscreen==1)
+              {cat("\nData for visualizing the conditional effect of the focal predictor:\n")
+                print(probepnt,right=T)}
+            }    
+          }      
+          #End E
+        }
+        #End R
+      }
+      #End PROBEandPLOT
+
+      #linear sum
+      if ((i==(nms+nys)) & (model >= 0) & (model < 4) & (linsum[1,1] != -999))
+      {
+        lhyprob<-1;meansub<-0
+        if (((nlinsum==nrow(b)) | (nlinsum==(nrow(b)-ncs))))
+        {
+          if ((nlinsum ==(nrow(b)-ncs)) & (ncs > 0))
+          {
+            linsum<-cbind(linsum,covmeans)
+            meansub<-1
+          }
+          lhyprob<-0;hypest<-linsum%*%b
+          sehypest<-sqrt(linsum%*%varb%*%t(linsum))
+          phypest<-2*(pt((-abs(hypest/sehypest)),dfres))
+          hypest<-matrix(c(hypest,sehypest,(hypest/sehypest),phypest,(hypest-tval*sehypest),(hypest+tval*sehypest)),ncol=6)
+          resultm2<-matrix(99999,ncol(linsum),maxresm)
+          resultm2[,1]<-t(linsum)
+          resultm<-rbind(resultm,resultm2)
+          resultm2<-matrix(99999,1,maxresm)
+          resultm2[1,1:ncol(hypest)]<-hypest
+          resultm<-rbind(resultm,resultm2)
+          if (outscreen==1)
+          {
+            hyplabs<-c("Estimate",hclab,"t","p","LLCI","ULCI")
+            cat("\n----------\n")
+            cat("Linear Combination Estimate and Hypothesis Test\n")
+            linsumpt<-noquote(matrix(sprintf(decimals,linsum),ncol=1))
+            colnames(linsumpt)<-"weight"
+            rownames(linsumpt)<-vlabsm
+            cat("\nWeight vector:\n")
+            print(linsumpt,right=TRUE)
+            hypestpt<-noquote(matrix(sprintf(decimals,hypest),ncol=6))
+            colnames(hypestpt)<-hyplabs
+            rownames(hypestpt)<-" "
+            cat("\n")
+            print(hypestpt,right=TRUE)
+            if (meansub==1)
+            {cat("\nCovariate weight(s) set to the sample mean.\n")}
+          }
+        }
+        if (lhyprob==1){notecode[notes,1]<-30;notes<-notes + 1}
+      }
+    }
+    #END G LOOP
+    if ((criterr==0) & (dototal==1))
+    {
+      if (outscreen==1)
+      {
+        cat("\n************************ TOTAL EFFECT MODEL *************************** \n")
+        cat("Outcome Variable: ")
+        write.table(outnames[nrow(outnames),1],quote=FALSE,row.names=FALSE,col.names=FALSE)
+        cat("\n")
+      }
+      x<-xtmp
+      vlabsm<-matrix(c("constant",xcatlab[1:nxvls,1]))
+      if (ncs > 0)
+      {
+        x<-cbind(as.matrix(x),as.matrix(ctmp))
+        vlabsm<-matrix(c(vlabsm,t(covnames)))
+      }
+      x<-cbind(ones,x)
+      modoutz<-process.modelest(y,x,1,1,xp2,hc)
+      modsum<-matrix(unlist(modoutz[3]))
+      resultm2<-matrix(99999,1,maxresm)
+      resultm2[1,1:nrow(modsum)]<-t(modsum)
+      resultm<-rbind(resultm,resultm2)
+      modsum<-noquote(matrix(sprintf(decimals,modsum),nrow=1))
+      modres<-matrix(unlist(modoutz[1]),nrow=ncol(x))
+      toteff<-matrix(modres,nrow=ncol(x))
+      toteff<-matrix(toteff[2:(1+nxvls),],nrow=nxvls)
+      resultm2<-matrix(99999,nrow(modres),maxresm)
+      resultm2[1:nrow(modres),1:ncol(modres)]<-modres
+      resultm<-rbind(resultm,resultm2)
+      modres<-noquote(matrix(sprintf(decimals,modres),nrow=ncol(x)))
+      varb<-matrix(unlist(modoutz[6]),nrow=ncol(x))
+      brsq2<-modsum[1,2]
+      b<-matrix(unlist(modoutz[5]))
+      colnames(modsum)<-modsuml;rownames(modsum)<-" "
+      rownames(modres)<-vlabsm;colnames(modres)<-modresl
+      if (outscreen==1)
+      {
+        cat("Model Summary: \n")
+        print(modsum,right=T)
+        cat("\n")
+        cat("Model: \n")
+        print(modres,right=T)
+      }   
+      totefflb<-modresl
+      toteffl2<-vlabsm[2:(1+nxvls),]
+      lmat<-matrix(0,nrow(b),1)
+      lmat2<-matrix(1,nxvls,1)
+      lmat[2:(1+nxvls),1]<-lmat2
+      if (ydich != 1)
+      {totomni<-process.ftest3(lmat,b,varb,1,brsq2,0,y,x)} 
+      if (stand==1)
+      {
+        predsd<-matrix(0,nrow(modres),1)
+        stdmod<-as.numeric(modres[,1])/ovsd[nrow(ovsd),1]
+        for (jd in c(1:ncol(x)))
+        {predsd[jd,1]<-sd(x[,jd])}   
+        if ((wherex[1,ncol(wherex)] != -999) & ((nxvls > 1) | (xdich==1)))  
+        {  
+          sdmsone<-matrix(1,nxvls,1)
+          predsd[wherex[1,ncol(wherex)]:wherex[2,ncol(wherex)],1]<-sdmsone    
+          pstog<-1    
+        }
+        predsd[1,1]<-1
+        stdmod<-stdmod*predsd
+        stdmod<-matrix(stdmod[2:nrow(stdmod),1])
+        sdvlabs<-vlabsm[2:nrow(vlabsm),1]
+        resultm2<-matrix(99999,nrow(stdmod),maxresm)
+        resultm2[1:nrow(stdmod),1:ncol(stdmod)]<-stdmod
+        resultm<-rbind(resultm,resultm2)
+        stdmod<-noquote(matrix(sprintf(decimals,stdmod),(nrow(b)-1)))
+        colnames(stdmod)<-"coeff"
+        rownames(stdmod)<-sdvlabs
+        if (outscreen==1)
+        {cat("\nStandardized coefficients:\n")
+          print(stdmod,right=T)}
+      }
+
+      if (covcoeff==1)
+      {
+        varbpr<-noquote(matrix(sprintf(decimals,varb),nrow=nrow(b)))
+        rownames(varbpr)<-vlabsm;colnames(varbpr)<-vlabsm
+        if (outscreen==1)
+        {
+          cat("\nCovariance matrix of regression parameter estimates:\n")
+          print(varbpr,right=T)
+          resultm2<-matrix(99999,nrow(varb),maxresm)
+          if (ncol(varb) <= maxresm)
+          {
+            resultm2[1:nrow(varb),1:ncol(varb)]<-varb
+            resultm<-rbind(resultm,resultm2)
+          }
+          if (ncol(varb) > maxresm)
+          {
+            resultmt<-matrix(99999,nrow(resultm),ncol(varb))
+            resultmt[1:nrow(resultm),1:ncol(resultm)]<-resultm
+            resultm<-resultmt
+            resultm2<-matrix(99999,nrow(varb),ncol(resultm))
+            resultm2[1:nrow(varb),1:ncol(varb)]<-varb
+            resultm<-rbind(resultm,resultm2)
+            maxresm<-ncol(resultm)
+          }
+        }
+      } 
+    }
+  }
+  #END cycle through the models
+
+  if ((criterr==0) & (nms > 0) & (ydich==0) & (modelres==1))
+  {
+    modresid<-matrix(modresid[,2:ncol(modresid)],ncol=(ncol(modresid)-1))
+    corall<-cor(modresid)
+    resultm2<-matrix(99999,nrow(corall),maxresm)
+    resultm2[1:nrow(corall),1:ncol(corall)]<-corall
+    resultm<-rbind(resultm,resultm2)
+    corall2<-noquote(matrix(sprintf(decimals,corall),nrow=nrow(corall)))
+    colnames(corall2)<-outnames
+    rownames(corall2)<-outnames
+    if (outscreen==1)
+    {cat("\n*************** CORRELATIONS BETWEEN MODEL RESIDUALS **************** \n\n")
+      print(corall2,right=T)}
+  }
+
+  #DO BOOTSTRAPPING
+  if ((criterr==0) & (boot > 0))
+  { 
+    bootres<-matrix(-999,1,sum(nump))
+    bootdir<-obsdirfx
+    if (effsize==1){bootysd<-matrix(-999,1,1);bootxsd<-matrix(-999,1,1)}
+    badboot<-0;goodboot<-0;smallest<-1;booting<-1
+    j<-1
+    if (outscreen==1)
+    {
+      cat("\n*********************************************************************** \n")
+      if (progress==1)
+      {cat("Bootstrapping progress:\n")
+        bootprog<-txtProgressBar(min=0,max=boot,char=">",width=62,style=3)}
+      if (progress !=1){cat("Bootstrapping in progress. Please wait.\n");flush.console()}
+    }
+    while ((goodboot < boot) & (j <= maxboot))
+    {
+      if ((outscreen==1) & (progress==1)){setTxtProgressBar(bootprog,j)}   
+      nobootx<-1;modres2<-999;bad<-0;
+      v<-as.matrix(trunc(runif(n)*n)+1)
+      for (i in (1:(nms+nys)))
+      {
+        y<-as.matrix(outvars[v,i])
+        ynovar<-sum((y-(sum(y)/nrow(y)))*(y-(sum(y)/nrow(y))))
+        if (ynovar==0){bad<-1}
+        xindx<-datindx[1:(nump[1,i]-1),i]
+        hello<-0
+        x<-as.matrix(fulldat[v,xindx])
+        x<-cbind(ones,x)
+        xsq<-t(x)%*%x
+        exsq<-eigen(xsq)
+        exsq<-matrix(unlist(exsq[1]))
+        holymoly<-min(exsq)
+        zeroeig<-sum(as.numeric(exsq <= 0.000000000002))
+        bad<-bad+as.numeric(zeroeig > 0)
+        bad=bad+as.numeric(sd(y)==0)
+        if (bad==0)
+        {
+          if (holymoly < smallest){smallest<-holymoly}
+          if ((ydich==0) | (i < (nms+nys)))
+          {modrest<-process.modelest(y,x,type=1,full=0,xp2,hc)}
+          if ((ydich==1) & (i==(nms+nys)))
+          {modrest<-process.modelest(y,x,3,0,xp2,hc,iterate,converge)}
+          modres2<-as.matrix(c(modres2,modrest))
+          if (i==(nms+nys))
+          {
+            if (bcmat[(i+1),1]==1)
+            {bootdir<-rbind(bootdir,t(modrest[wherex[1,i]:wherex[2,i],1]))}             
+            if (bcmat[(i+1),1]==0)
+            {bootdir<-rbind(bootdir,dirzes)}         
+          }
+          if ((bcmat[(i+1),1]==1) & (nobootx==1) & (effsize==1))
+          {
+            nobootx<-0
+            xsdtemp<-sum((x[,2]-(sum(x[,2])/nrow(x)))*(x[,2]-(sum(x[,2])/nrow(x))))
+            xsdtemp<-sqrt(xsdtemp/(nrow(x)-1))
+          }
+        }
+      }
+      if (bad==0)
+      {
+        modres2<-t(modres2[2:nrow(modres2),])
+        #modres2<-matrix(modres2[,2:nrow(modres2),ncol=ncol(modres)-1)
+        bootres<-rbind(bootres,modres2)
+        if (effsize==1)
+        {
+          ysdtemp<-sd(y)
+          bootysd<-rbind(bootysd,ysdtemp)
+          bootxsd<-rbind(bootxsd,xsdtemp)
+        }
+        goodboot<-goodboot+1
+      }
+      if (bad != 0){badboot<-badboot+1}
+      j<-j+1
+    }
+    bootres<-as.matrix(bootres[2:nrow(bootres),])
+    if (effsize==1)
+    {
+      bootysd<-matrix(bootysd[2:nrow(bootysd),])
+      if (nrow(bootxsd) > 1){bootxsd<-matrix(bootxsd[2:nrow(bootxsd)])}
+    }
+    if (goodboot < (boot))
+    {boot<-0;modelbt<-0;notecode[notes,1]<-7;notes<-notes+1}
+    if (boot > 0)
+    {
+      if (effsize==1){bootysd<-rbind(ysd,bootysd);bootxsd<-rbind(xsd,bootxsd)}
+      if (saveboot==1)
+      {
+        savlabs<-matrix(" ",ncol(bootres))
+        for (i in c(1:ncol(bootres))){savlabs[i,1]<-paste("col",i,sep='')}
+        boots<-as.data.frame(bootres)
+        colnames(boots)<-savlabs
+        #assign("process.boots", boots, envir = .GlobalEnv)
+      }
+      if (modelbt==1)
+      {   
+        bootcim<-matrix(-99999,ncol(bootres),5)
+        bootcim[,2]<-t(colSums(bootres)/nrow(bootres))
+        bootcim[,1]<-as.numeric(coeffmat[2:nrow(coeffmat),1])
+        for (i in (1:ncol(bootres)))
+        { 
+          if (bc==0){bootcim[i,3:5]<-t(process.pboot3(bootres[,i],cilow,cihigh))}
+          if (bc==1)
+          {
+            bcbout<-process.bcboot3(bootres[,i],bootcim[i,1],xp2,badend,priorlo,priorhi)
+            bootcim[i,3:5]<-t(matrix(unlist(bcbout[1])))
+            badend<-unlist(bcbout[2]);priorlo<-unlist(bcbout[3]);priorhi<-unlist(bcbout[4])
+          }
+        }
+      } 
+    }
+
+    if (badboot > 0){notecode[notes,1]<-6;notes<-notes+1}
+    if ((outscreen==1) & (progress==1)){close(bootprog)}
+  }
+  #end of bootstrapping
+
+  #Here is for the indirect effects
+  if ((criterr==0) & (nms > 0))
+  {
+    paths<-matrix(paths[,2:ncol(paths)],nrow=nrow(paths))
+    pathsw<-matrix(pathsw[,2:ncol(pathsw)],nrow=nrow(pathsw))
+    pathsz<-matrix(pathsz[,2:ncol(pathsz)],nrow=nrow(pathsz))
+    pathswz<-matrix(pathswz[,2:ncol(pathswz)],nrow=nrow(pathswz))
+    pathsmod<-pathsw+pathsz+pathswz
+    pathsdv<-t(pathsdv[2:nrow(pathsdv),])
+    pathsfoc<-matrix(pathsfoc[,2:ncol(pathsfoc)],nrow=nrow(pathsfoc))
+    pathtype<-matrix(pathtype[,2:ncol(pathtype)],nrow=nrow(pathtype))
+    anymod<-as.numeric(sum(pathsmod) > 0)
+    obscoeff<-t(as.matrix(obscoeff[1,2:ncol(obscoeff)]))
+    if (outscreen==1)
+    {
+      if ((dototal==0) & (alttotal==0))
+      {cat("\n**************** DIRECT AND INDIRECT EFFECTS OF X ON Y ****************\n")}
+      if (alttotal==1)
+      {cat("\n************ TOTAL, DIRECT AND INDIRECT EFFECTS OF X ON Y ****************\n")}
+    }
+    if (dototal==1)
+    {
+      if (outscreen==1)
+      {cat("\n************ TOTAL, DIRECT, AND INDIRECT EFFECTS OF X ON Y ************\n")}   
+      totefflb[1,1]<-"effect"
+      if (counterf != 1)
+      {
+        if (effsize==1)
+        {
+          toteffsz<-toteff[,1]/ysd 
+          if ((xdich==1) | (mcx > 0)){totefflb<-cbind(totefflb,"c_ps")}
+          if ((xdich==0) & (mcx==0))
+          {toteffsz<-(toteffsz*xsd);totefflb<-cbind(totefflb,"c_cs")}     
+          toteff<-cbind(toteff,toteffsz)
+        }
+        resultm2<-matrix(99999,nrow(toteff),maxresm)
+        resultm2[1:nrow(toteff),1:ncol(toteff)]<-toteff
+        resultm<-rbind(resultm,resultm2)
+        toteff2<-noquote(matrix(sprintf(decimals,toteff),nrow=nrow(toteff)))
+        colnames(toteff2)<-totefflb
+        if (nxvls > 1)
+        {
+          rownames(toteff2)<-toteffl2
+          if (outscreen==1)
+          {cat("\nRelative total effects of X on Y:\n")
+            print(toteff2,right=T)}
+          clabtmp<-c("R2-chng", hcflab, "df1","df2","p")
+          resultm2<-matrix(99999,nrow(totomni),maxresm)
+          resultm2[1:nrow(totomni),1:ncol(totomni)]<-totomni
+          resultm<-rbind(resultm,resultm2)
+          totomni2<-noquote(matrix(sprintf(decimals,totomni),nrow=nrow(totomni)))
+          colnames(totomni2)<-clabtmp
+          rownames(totomni2)<-" "
+          if (outscreen==1)
+          {
+            cat("\nOmnibus test of total effect of X on Y:\n")
+            print(totomni2,right=T)
+            cat("----------\n")
+          }
+        }
+        if (nxvls < 2)
+        {
+          rownames(toteff2)<-" "
+          if (outscreen==1)
+          {cat("\nTotal effect of X on Y:\n")
+            print(toteff2,right=T)}
+        }
+      }
+    }
+    moddir<-wcmat[nrow(bcmat),1]+zcmat[nrow(bcmat),1]
+    if ((bcmat[nrow(bcmat),1]==1) & (counterf != 1))
+    {
+      if (ydich==1)
+      {
+        direfflb[,(ncol(direfflb)-5):ncol(direfflb)]<-t(matrix(c("Effect","se","Z","p","LLCI","ULCI")))
+      } 
+      if (moddir==0){direfflb[1,1]="effect"}
+      if ((effsize==1) & (moddir==0) & (anymod == 0))
+      {
+        direffsz<-direff[,1]/ysd
+        if ((xdich==1) | (mcx > 0)){direfflb<-cbind(direfflb,"c'_ps")}
+        if ((xdich==0) & (mcx==0))
+        {direffsz<-(direffsz*xsd);direfflb<-cbind(direfflb,"c'_cs")}    
+        direff<-cbind(direff,direffsz)
+      }
+      resultm2<-matrix(99999,nrow(direff),maxresm)
+      resultm2[1:nrow(direff),1:ncol(direff)]<-direff
+      resultm<-rbind(resultm,resultm2)
+      direff2<-noquote(matrix(sprintf(decimals,direff),nrow=nrow(direff)))
+      colnames(direff2)<-direfflb
+      if ((moddir==0) & (nxvls==1) & (outscreen==1))
+      {
+        rownames(direff2)<-" "
+        cat("\nDirect effect of X on Y:\n")
+        print(direff2,right=T)
+      }
+      if ((moddir==0) & (nxvls>1))  
+      {
+        rownames(direff2)<-direffl2
+        if (outscreen==1)
+        {cat("\nRelative direct effects of X on Y:\n")
+          print(direff2,right=T)} 
+        resultm2<-matrix(99999,nrow(diromni),maxresm)
+        resultm2[1:nrow(diromni),1:ncol(diromni)]<-diromni
+        resultm<-rbind(resultm,resultm2)
+        diromni2<-noquote(matrix(sprintf(decimals,diromni),nrow=nrow(diromni)))
+        rownames(diromni2)<-" "
+        if (ydich==0)
+        {  
+          colnames(diromni2)<-c("R2-chng", hcflab, "df1","df2","p")
+          if (outscreen==1)
+          {cat("\nOmnibus test of direct effect of X on Y:\n")
+            print(diromni2,right=T)}
+        }
+        if (ydich==1)
+        {  
+          colnames(diromni2)<-c("Chi-sq", "df", "p")
+          if (outscreen==1)
+          {cat("\nOmnibus likelihood ratio test of direct effect of X on Y:\n")
+            print(diromni2,right=T)}
+        }
+        if (outscreen==1)
+        {cat("\n----------\n")}
+      }
+      if ((moddir > 0) & (nxvls==1) & (outscreen==1))
+      {cat("\nConditional direct effect(s) of X on Y:\n")
+        rownames(direff2)<-t(matrix(replicate(nrow(direff2)," ")))
+        print(direff2,right=T)}
+      direffl4<-direffl2
+      if ((moddir > 0) & (nxvls>1))
+      {
+        direffl2=" "
+        for (i in (1:nxvls))
+        {
+          for (j in (1:(nrow(direff)/nxvls)))
+          {direffl2<-rbind(direffl2,xcatlab[i,1])}     
+        }
+        direffl2<-direffl2[2:nrow(direffl2),1]
+        rownames(direff2)<-direffl2
+        if (outscreen==1)
+        {cat("\nRelative conditional direct effect(s) of X on Y:\n")
+          print(direff2,right=T)}
+      }
+      direffl2<-direffl4    
+    }
+
+    if ((bcmat[nrow(bcmat),1]==0) & (counterf != 1) & (outscreen==1))
+    {cat("\nThe direct effect of X on Y is fixed to zero.\n")}
+
+    #Here is the start of the indirect effects
+    if (nms==1){indmark<-matrix(2);indsets<-t(matrix(c(1,2)))}
+    if (nms==2){indmark<-t(matrix(c(2,2,3)));indsets<-t(matrix(c(1,4,2,5,1,3,5)));thetam<-matrix(1)}
+    if (nms==3) 
+    {indmark<-t(matrix(c(2,2,2,3,3,3,4)))
+    indsets<-t(matrix(c(1,7,2,8,4,9,1,3,8,1,5,9,2,6,9,1,3,6,9)))
+    thetam<-t(matrix(c(1,2,3)))}
+    if (nms==4)
+    {indmark<-t(matrix(c(2,2,2,2,3,3,3,3,3,3,4,4,4,4,5)))
+    indsets<-t(matrix(c(1,11,2,12,4,13,7,14,1,3,12,1,5,13,1,8,14,2,6)))
+    indsets<-cbind(indsets,t(matrix(c(13,2,9,14,4,10,14,1,3,6,13,1,3,9,14,1,5,10,14,2,6,10,14,1,3,6,10,14))))
+    thetam<-t(matrix(c(1,2,4,3,5,6)))}
+    if (nms==5)
+    {indmark<-t(matrix(c(2,2,2,2,2,3,3,3,3,3,3,3,3,3,3,4,4,4,4,4,4,4,4,4,4,5,5,5,5,5,6)))
+    indsets<-t(matrix(c(1,16,2,17,4,18,7,19,11,20,1,3,17,1,5,18,1,8,19,1,12,20,2,6,18,2,9,19,2)))
+    indsets<-cbind(indsets,t(matrix(c(13,20,4,10,19,4,14,20,7,15,20,1,3,6,18,1,3,9,19,1,3,13,20,1,5,10))))
+    indsets<-cbind(indsets,t(matrix(c(19,1,5,14,20,1,8,15,20,2,6,10,19,2,6,14,20,2,9,15,20,4,10,15,20,1))))
+    indsets<-cbind(indsets,t(matrix(c(3,6,10,19,1,3,6,14,20,1,3,9,15,20,1,5,10,15,20,2,6,10,15,20,1,3))))
+    indsets<-cbind(indsets,t(matrix(c(6,10,15,20))))
+    thetam<-t(matrix(c(1,2,5,3,6,8,4,7,9,10)))}
+    if (nms==6)
+    {indmark<-t(matrix(c(2,2,2,2,2,2,3,3,3,3,3,3,3,3,3,3,3,3,3,3,3,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,4,5,5,5,5,5)))
+    indmark<-cbind(indmark,t(matrix(c(5,5,5,5,5,5,5,5,5,5,6,6,6,6,6,6,7))))
+    indsets<-t(matrix(c(1,22,2,23,4,24,7,25,11,26,16,27,1,3,23,1,5,24,1,8,25,1,12,26,1,17,27,2,6,24,2,9,25,2,13,26,2,18)))
+    indsets<-cbind(indsets,t(matrix(c(27,4,10,25,4,14,26,4,19,27,7,15,26,7,20,27,11,21,27,1,3,6,24,1,3,9,25,1,3,13,26,1,3))))
+    indsets<-cbind(indsets,t(matrix(c(18,27,1,5,10,25,1,5,14,26,1,5,19,27,1,8,15,26,1,8,20,27,1,12,21,27,2,6,10,25,2,6,14,26))))
+    indsets<-cbind(indsets,t(matrix(c(2,6,19,27,2,9,15,26,2,9,20,27,2,13,21,27,4,10,15,26,4,10,20,27,4,14,21,27,7,15,21,27))))
+    indsets<-cbind(indsets,t(matrix(c(1,3,6,10,25,1,3,6,14,26,1,3,6,19,27,1,3,9,15,26,1,3,9,20,27,1,3,13,21,27,1,5,10,15,26))))
+    indsets<-cbind(indsets,t(matrix(c(1,5,10,20,27,1,5,14,21,27,1,8,15,21,27,2,6,10,15,26,2,6,10,20,27,2,6,14,21,27,2,9,15))))
+    indsets<-cbind(indsets,t(matrix(c(21,27,4,10,15,21,27,1,3,6,10,15,26,1,3,6,10,20,27,1,3,6,14,21,27,1,3,9,15,21,27,1,5,10))))
+    indsets<-cbind(indsets,t(matrix(c(15,21,27,2,6,10,15,21,27,1,3,6,10,15,21,27))))
+    thetam<-t(matrix(c(1,2,6,3,7,10,4,8,11,13,5,9,12,14,15)))}
+    if (nms==7)
+    {indmark<-t(matrix(c(2,2,2,2,2,2,2)));indsets<-t(matrix(c(1,29,2,30,4,31,7,32,11,33,16,34,22,35)))}
+    if (nms==8)
+    {indmark<-t(matrix(c(2,2,2,2,2,2,2,2)));indsets<-t(matrix(c(1,37,2,38,4,39,7,40,11,41,16,42,22,43,29,44)))}
+    if (nms==9)
+    {indmark<-t(matrix(c(2,2,2,2,2,2,2,2,2)));indsets<-t(matrix(c(1,46,2,47,4,48,7,49,11,50,16,51,22,52,29,53,37,54)))}
+    if (nms==10)
+    {indmark<-t(matrix(c(2,2,2,2,2,2,2,2,2,2))) 
+    indsets<-t(matrix(c(1,56,2,57,4,58,7,59,11,60,16,61,22,62,29,63,37,64,46,65)))}
+    indlbl<-"Ind1"
+    for (indb in (2:90))
+    {indlbl<-cbind(indlbl,paste("Ind",indb,sep=''))}
+    indlbl<-matrix(indlbl)
+    cntname<-"(C1)"
+    for (indb in (2:105))
+    {cntname<-cbind(cntname,paste("(C",indb,")",sep=''))}
+    cntname<-matrix(cntname)
+    indmake<-matrix(0,ncol(indmark),(nms+2))
+    indmod<-matrix(999,ncol(indmark),1)
+    indmmm<-matrix(0,ncol(indmark),1)
+    indmmmt<-matrix(0,ncol(indmark),1)
+    start<-1;end<-0;nindfx<-0
+    indlocs<-matrix(999,nrow(thetaxmb),ncol(paths))
+    indkey<-matrix("      ",ncol(indmark),1+((max(indmark)*2)+1))
+    c1<-1;c2<-1;c3<-1
+    for (i in (1:ncol(paths)))
+    {
+      if (pathtype[1,i]==1){indlocs[,i]<-thetaxmb[,c1];c1<-(c1+1)}
+      if (pathtype[1,i]==3){indlocs[,i]<-thetamyb[,c2];c2<-(c2+1)}
+      if ((pathtype[1,i]==2) & (nms < 7) & (serial==1)){indlocs[,i]<-thetammb[,thetam[1,c3]];c3<-(c3+1)}
+    }
+    for (i in (1:ncol(indlocs)))
+    {
+      c1<-2
+      for (j in (2:nrow(indlocs)))
+      {
+        if (indlocs[j,i] != 0){indlocs[c1,i]<-indlocs[j,i];c1<-(c1+1)}
+      }
+      indlocs[1,i]<-(c1-2)
+    }
+    indlocs<-indlocs[1:max((indlocs[1,])+1),]
+    for (i in (1:ncol(indmark)))
+    { 
+      numget<-indmark[1,i];end<-end+numget;gotcha<-t(matrix(indsets[1,start:end]))
+      start<-end+1;ok<-1;temp<-0;repoman<-matrix(0,4,1)
+      for (j in (1:ncol(gotcha)))
+      {
+        if (paths[1,gotcha[1,j]]==0){ok<-0}
+        if (pathsmod[1,gotcha[1,j]] > 0)
+        {
+          temp<-1
+          temp2<-rbind(pathsw[1,gotcha[1,j]],pathsz[1,gotcha[1,j]],pathswz[1,gotcha[1,j]],0)
+          temp2<-matrix(temp2)
+          if ((temp2[1,1]==1) & (temp2[2,1]==1) & (temp2[3,1]==0)){temp2[4,1]<-1}
+          repoman<-repoman+temp2
+        }
+      }
+      temp<-0;tempmmm<-0;typemmm<-0
+      if ((repoman[1,1] > 0) & (repoman[2,1]==0))
+      {
+        temp<-1
+        if (repoman[1,1]==1){tempmmm<-1} 
+        if ((repoman[1,1] > 1) & ((wdich==1) | (mcw > 0)))
+        {
+          tempmmm<-12;typemmm<-mcw
+          if (wdich==1){typemmm<-1}
+        }
+        if ((repoman[1,1] > 1) & ((wdich==0) & (mcw==0))){tempmmm<-101} 
+      }
+      if ((repoman[1,1]==0) & (repoman[2,1] > 0))
+      {
+        temp<-2
+        if (repoman[2,1]==1){tempmmm<-2}
+        if ((repoman[2,1] > 1) & ((zdich==1) | (mcz > 0)))
+        {
+          tempmmm<-22;typemmm<-mcz
+          if (zdich==1){typemmm<-1}
+        }
+        if ((repoman[2,1] > 1) & ((zdich==0) & (mcw==0))){tempmmm<-102}
+      }
+      if ((repoman[1,1] > 0) & (repoman[2,1] > 0))
+      {
+        temp<-3
+        if ((repoman[1,1]==1) & (repoman[2,1]==1))
+        {
+          if (repoman[4,1]==1){tempmmm<-31}
+          if (repoman[3,1]==1){tempmmm<-41}
+        }
+      }
+      if ((repoman[1,1]==1) & (repoman[2,1]==1) & (repoman[3,1]==0) & (repoman[4,1]==0)){tempmmm<-51}
+      if (ok==1)
+      {
+        nindfx<-nindfx+1
+        indmake[nindfx,1]<-numget;indmod[nindfx,1]<-temp;indmmm[nindfx,1]<-tempmmm
+        indmmmt[nindfx,1]<-typemmm;indmake[nindfx,2:(1+numget)]<-gotcha;indkey[nindfx,1]<-xnames
+        for (j in (1:numget))
+        {
+          indkey[nindfx,(j*2+1)]<-pathsdv[1,gotcha[1,j]]
+          indkey[nindfx,(j*2)]<-"   ->   "
+        }
+      }
+    }
+    indkey<-matrix(indkey[1:nindfx,1:((max(indmake[,1])*2)+1)],nrow=nindfx)
+    indmake<-matrix(indmake[1:nindfx,1:(max(indmake[,1])+1)],ncol=(max(indmake[,1])+1))
+    indmod<-as.matrix(indmod[1:nrow(indmake),1])
+    indmmm<-as.matrix(indmmm[1:nrow(indmake),1])
+    indmmmt<-as.matrix(indmmmt[1:nrow(indmake),1])
+    ncpairs<-(((nindfx)*(nindfx-1))/2)
+    if (((contrast==1) | (contrast==2)) & (ncpairs > 105))
+    {contrast<-0;notecode[notes,1]<-13;notes<-notes+1}
+    if (contrast==3)
+    {
+      if (ncol(contvec) != nindfx)
+      {contrast<-0;notecode[notes,1]<-14;notes<-notes+1}
+    }
+
+    #This is for models with no moderator */
+    if (anymod==0)
+    {
+      if ((nms==1) & (contrast > 0)){contrast<-0}
+      efloop<-(((1-as.numeric(effsize==0))*2)+1)-((((mcx>0) | (xdich==1)))*(1-as.numeric(effsize==0)))
+      for (kk in (1:efloop))
+      {
+        if (boot==0)
+        {
+          bootres<-obscoeff
+          if (kk==1){totbtvec<-matrix(0,1,nxvls)}
+          indtab<-matrix(999);inddiff<-matrix(999);bootysd<-matrix(ysd);bootxsd<-matrix(xsd)
+        }    
+        if (boot > 0)
+        {
+          bootres<-rbind(obscoeff,bootres)
+          if (kk==1){totbtvec<-matrix(0,nrow(bootres),nxvls)}
+          indtab<-matrix(999,1,4);inddiff<-matrix(999,nrow(bootres))
+        }
+        indtotal<-matrix(0,nrow(bootres),1)
+        for (i in (1:nrow(indmake)))
+        {
+          for (j in (1:nxvls))
+          {
+            indtemp<-matrix(1,nrow(bootres),1)
+            for (k in (1:indmake[i,1]))
+            {
+              jtemp<-1
+              if ((j > 1) & (k==1)){jtemp<-j}
+              indtemp<-indtemp*bootres[,pathsfoc[jtemp,indmake[i,(k+1)]]]
+            }
+            if (kk==2){indtemp<-indtemp/bootysd}
+            if (kk==3){indtemp<-((bootxsd*indtemp)/bootysd)}
+            if (contrast != 0){inddiff<-cbind(inddiff,indtemp)}
+            if (nxvls==1){indtotal<-(indtotal+indtemp)}
+            indeff<-indtemp[1,1]
+            if (kk==1){totbtvec[,j]<-totbtvec[,j]+indtemp}
+            if (boot > 0)
+            {
+              if (bc==0){bcitmp<-process.pboot3(indtemp[2:nrow(indtemp),1],cilow,cihigh)}
+              if (bc==1)
+              {
+                bcbout<-process.bcboot3(indtemp[2:nrow(indtemp),1],indtemp[1,1],xp2,badend,priorlo,priorhi)
+                bcitmp<-matrix(unlist(bcbout[1]))
+                badend<-unlist(bcbout[2]);priorlo<-unlist(bcbout[3]);priorhi<-unlist(bcbout[4])
+              }
+              indeff<-cbind(indeff,t(bcitmp))
+            }
+            if (kk==1){indtabn<-rbind(indtab,indeff)}
+            indtab<-rbind(indtab,indeff)
+          }
+        }
+        indtab<-matrix(indtab[2:nrow(indtab),],nrow=(nrow(indtab)-1))
+        if (kk==1){indtabn<-matrix(indtabn[2:nrow(indtabn),],nrow=(nrow(indtabn)-1))}
+        rowlbs<-matrix(indlbl[1:nrow(indtab),1])
+        rowbls3<-rowlbs
+        if (mc > 0)
+        {
+          inddiff<-matrix(-999,mc,1)
+          indtab2<-matrix(-999,nrow(indtab),4)
+          indtab2[,1]<-indtab;indtab<-indtab2;mcct<-0
+          indtotal<-matrix(0,mc,1)
+          if (kk==1)
+          {
+            x1<-sqrt(-2*log(matrix(runif(mc*nrow(mcsopath)),mc,nrow(mcsopath))))*cos((2*3.14159265358979)*matrix(runif(mc*nrow(mcsopath)),mc,nrow(mcsopath)))
+            x1<-x1%*%chol(indcov)
+            for (ii in (1:nrow(x1))){x1[ii,]<-(x1[ii,]+t(mcsopath))}
+          }
+          for (ii in (1:nms))
+          {
+            tmpb<-x1[,((nms*nxvls)+ii)];tmpb2<-tmpb
+            if (nxvls > 1)
+            {
+              for (jj in (1:(nxvls-1)))
+              {tmpb2<-cbind(tmpb2,tmpb)}        
+            }
+            indtemp<-as.matrix(x1[,(((ii-1)*nxvls)+1):(ii*nxvls)]*tmpb2)
+            for (jj in (1:ncol(indtemp)))
+            {
+              if (kk==2){indtemp[,jj]<-indtemp[,jj]/ysd}
+              if (kk==3){indtemp[,jj]<-(xsd*indtemp[,jj])/ysd}
+              mcicon<-process.pboot3(indtemp[,jj],cilow,cihigh)
+              mcct<-mcct+1
+              indtab[mcct,2:4]<-t(mcicon)
+            }
+            if (nxvls==1)
+            {
+              indtotal<-indtotal+indtemp
+              if (contrast != 0){inddiff=cbind(inddiff,indtemp)}
+            }
+          }
+        }
+        if ((normal==1) & (sobelok==1))
+        {
+          sobelmat<-matrix(indtab[,1])
+          sobelmat<-cbind(sobelmat,(sobelmat/2),sobelmat,sobelmat)
+          for (ii in (1:nms))
+          {
+            se2b<-(indcov[((nms*nxvls)+ii),((nms*nxvls)+ii)])
+            bpath2<-(mcsopath[((nms*nxvls)+ii),1])^2
+            se2a<-matrix(diag(matrix(indcov[(((ii-1)*nxvls)+1):(ii*nxvls),(((ii-1)*nxvls)+1):(ii*nxvls)],nrow=nxvls)))
+            apath2<-matrix(mcsopath[(((ii-1)*nxvls)+1):(ii*nxvls),1])^2
+            sesobel<-sqrt(apath2*se2b+bpath2*se2a+se2a*se2b)
+            sobelmat[(((ii-1)*nxvls)+1):(ii*nxvls),2]<-sesobel
+          }
+          sobelmat[,3]<-sobelmat[,1]/sobelmat[,2]
+          sobelmat[,4]<-2*(1-pnorm(abs(sobelmat[,3])))
+        }
+        if (serial==0){rowlbs<-t(mnames)}
+        if ((nxvls==1) & (nms > 1))
+        {
+          rowlbs<-rbind("TOTAL",rowlbs)
+          indtemp<-indtotal[1,1]
+          if ((boot > 0) & (nxvls==1))
+          {
+            if (bc==0){bcitmp<-process.pboot3(indtotal[2:nrow(indtotal),1],cilow,cihigh)}
+            if (bc==1)
+            {
+              bcbout<-process.bcboot3(indtotal[2:nrow(indtotal),1],indtotal[1,1],xp2,badend,priorlo,priorhi)
+              bcitmp<-matrix(unlist(bcbout[1]))
+              badend<-unlist(bcbout[2]);priorlo<-unlist(bcbout[3]);priorhi<-unlist(bcbout[4])
+            }
+            indtemp<-cbind(indtemp,t(bcitmp))
+          }
+          if (mc > 0)
+          {
+            obtmc<-indtab[,1];indtemp<-sum(obtmc)
+            mcicon2<-process.pboot3(indtotal[,1],cilow,cihigh)
+            indtemp<-cbind(indtemp,t(mcicon2))
+          }
+          indtab<-rbind(indtemp,indtab)
+        }
+        bootlbs<-"Effect"
+        if (boot > 0){bootlbs<-c("Effect","BootSE","BootLLCI","BootULCI")}
+        if (mc > 0){bootlbs<-c("Effect","MC SE","MC LLCI","MC ULCI")}
+        if (nxvls==1)
+        {
+          if (contrast != 0)
+          {
+            inddiff<-matrix(inddiff[,2:ncol(inddiff)],nrow=nrow(inddiff))
+            if (mc > 0){inddiff=rbind(t(obtmc),inddiff)}
+            if (contrast==3)
+            {
+              inddifft<-matrix(inddiff%*%t(contvec))
+              indtemp<-inddifft[1,1]
+              if ((boot > 0) | (mc > 0))
+              {
+                if ((mc > 0) | ((boot > 0) & (bc==0)))
+                {bcicon<-process.pboot3(inddifft[2:nrow(inddifft),1],cilow,cihigh)}
+                if ((boot > 0) & (bc==1))
+                {
+                  bcbout<-process.bcboot3(inddifft[2:nrow(inddifft),1],inddifft[1,1],xp2,badend,priorlo,priorhi)
+                  bcicon<-matrix(unlist(bcbout[1]))
+                  badend<-unlist(bcbout[2]);priorlo<-unlist(bcbout[3]);priorhi<-unlist(bcbout[4])
+                }
+                indtemp<-cbind(indtemp,t(bcicon))
+              }
+              indtab<-rbind(indtab,indtemp)
+            }
+            if ((contrast==1) | (contrast==2))
+            {
+              conkey<-matrix(" ",1,4)
+              for (i in (1:(ncol(inddiff)-1)))
+              {     
+                for (j in ((i+1):ncol(inddiff)))
+                {           
+                  inddifft<-matrix(inddiff[,i]-inddiff[,j])
+                  if (contrast==2){inddifft<-matrix(abs(inddiff[,i])-abs(inddiff[,j]))}
+                  indtemp<-inddifft[1,1]
+                  conkeyt<-cbind(" ", rowlbs[(i+1),1]," minus  ",rowlbs[(j+1),1])
+                  conkey<-rbind(conkey,conkeyt)
+                  if ((boot > 0) | (mc > 0))
+                  {
+                    if ((mc > 0) | ((boot > 0) & (bc==0)))
+                    {bcitmp2<-process.pboot3(inddifft[2:nrow(inddifft),1],cilow,cihigh)}
+                    if ((boot > 0) & (bc==1))
+                    {
+                      bcbout<-process.bcboot3(inddifft[2:nrow(inddifft),1],inddifft[1,1],xp2,badend,priorlo,priorhi)
+                      bcitmp2<-matrix(unlist(bcbout[1]))
+                      badend<-unlist(bcbout[2]);priorlo<-unlist(bcbout[3]);priorhi<-unlist(bcbout[4])
+                    }
+                    indtemp<-cbind(indtemp,t(bcitmp2)) 
+                  }
+                  indtab<-rbind(indtab,indtemp)
+                }
+              }
+            }
+            if (contrast != 3)
+            {contlbs<-matrix(cntname[1:(((nindfx)*(nindfx-1))/2),1])}
+            if (contrast==3)
+            {contlbs<-matrix("(C1)")}    
+            rowlbs<-rbind(rowlbs,contlbs)
+          }
+          resultm2<-matrix(99999,nrow(indtab),maxresm)
+          resultm2[1:nrow(indtab),1:ncol(indtab)]<-indtab
+          resultm<-rbind(resultm,resultm2)
+          indtab5<-noquote(matrix(sprintf(decimals,indtab),nrow=nrow(indtab)))
+          colnames(indtab5)<-bootlbs
+          rownames(indtab5)<-rowlbs
+          if (outscreen==1)
+          {
+            if (kk==1)
+            {
+              cat("\nIndirect effect(s) of X on Y:\n")
+              print(indtab5,right=T)
+            }
+
+            if ((kk==2) & ((xdich==1) | (mcx > 0)))
+            {
+              cat("\nPartially standardized indirect effect(s) of X on Y:\n")
+              print(indtab5,right=T)
+            }
+            if (kk==3)
+            {
+              cat("\nCompletely standardized indirect effect(s) of X on Y:\n")
+              print(indtab5,right=T)
+            }
+          }
+          if ((normal==1) & (sobelok==1) & (kk==1))
+          {
+            sobellab<-c("Effect",hclab,"Z","p")
+            sobelrlb<-rowlbs
+            if (nms > 1){sobelrlb<-matrix(rowlbs[2:(1+nms),1])}
+            resultm2<-matrix(99999,nrow(sobelmat),maxresm)
+            resultm2[1:nrow(sobelmat),1:ncol(sobelmat)]<-sobelmat
+            resultm<-rbind(resultm,resultm2)
+            sobelmt2<-noquote(matrix(sprintf(decimals,sobelmat),nrow=nrow(sobelmat)))
+            rownames(sobelmt2)<-sobelrlb
+            colnames(sobelmt2)<-sobellab
+            if (outscreen==1)
+            {cat("\nNormal theory test for indirect effect(s):\n")
+              print(sobelmt2,right=T)}
+          }
+          if (contrast != 0)
+          {
+            if (((contrast==1) | (contrast==2)) & (kk==efloop))
+            {
+              conkey<-matrix(conkey[2:nrow(conkey),],nrow=(nrow(conkey)-1))
+              if (outscreen==1)
+              {cat("\nSpecific indirect effect contrast definition(s):\n")
+                write.table(conkey,quote=FALSE,row.names=contlbs,col.names=FALSE,sep = "  ")}
+            }
+            if ((contrast==3) & (kk=efloop))
+            {
+              crowlbs<-rowlbs[2:(nindfx+1),1]
+              contvect<-noquote(matrix(sprintf(decimals,contvec),nrow=1))
+              colnames(contvect)<-crowlbs
+              rownames(contvect)<-"(C1)"
+              if (outscreen==1)
+              {cat("\nSpecific indirect effect contrast weights:\n")
+                print(contvect,right=T)}
+            }
+            if ((contrast==2) & (kk==efloop) & (outscreen==1))
+            {cat("\nContrasts are differences between absolute values of indirect effects\n")}
+          }
+          if ((serial==1) & (kk==efloop))
+          {rowlbst<-matrix(rowlbs[2:nrow(rowlbs),1],nrow<-(nrow(rowlbs)-1))
+          if (outscreen==1)
+          {cat("\nIndirect effect key:\n")
+            write.table(indkey,quote=FALSE,row.names=rowbls3,col.names=FALSE,sep=" ")}}
+        }
+        if (nxvls > 1)
+        {
+          if (outscreen==1)
+          { 
+            if (kk==1){cat("\nRelative indirect effects of X on Y:\n")}
+            if (kk==2){cat("\nPartially standardized relative indirect effects of X on Y:\n")}
+            if (kk==3){cat("\nCompletely standardized relative indirect effects of X on Y:\n")}
+          }
+          for (i in (1:nrow(indmake)))
+          {
+            indtabsm<-indtab[(((i-1)*nxvls)+1):(nxvls*i),]
+            indkeyt<-indkey[i,]
+            if (outscreen==1)
+            {
+              cat("\n")
+              write.table(t(indkeyt),quote=FALSE,row.names=FALSE,col.names=FALSE,sep=" ")
+              cat("\n")
+            }
+            if (bcmat[nrow(bcmat),1]==0)
+            {direffl2<-xcatlab[1:nxvls,1]}
+            resultm2<-matrix(99999,nrow(indtabsm),maxresm)
+            resultm2[1:nrow(indtabsm),1:ncol(indtabsm)]<-indtabsm
+            resultm<-rbind(resultm,resultm2)
+            indtasm2<-noquote(matrix(sprintf(decimals,indtabsm),nrow=nrow(indtabsm)))
+            colnames(indtasm2)<-bootlbs
+            rownames(indtasm2)<-direffl2
+            if (outscreen==1)
+            {print(indtasm2,right=T)}
+            if ((normal==1) & (sobelok==1) & (kk==1))
+            {
+              sobelsm=sobelmat[(((i-1)*nxvls)+1):(nxvls*i),]
+              sobellab=c("Effect",hclab,"Z","p")
+              resultm2<-matrix(99999,nrow(sobelsm),maxresm)
+              resultm2[1:nrow(sobelsm),1:ncol(sobelsm)]<-sobelsm
+              resultm<-rbind(resultm,resultm2)
+              sobelsm2<-noquote(matrix(sprintf(decimals,sobelsm),nrow=nrow(sobelsm)))
+              colnames(sobelsm2)<-sobellab
+              rownames(sobelsm2)<-direffl2
+              if (outscreen==1)
+              {cat("\n   Normal theory test for relative indirect effects:\n")
+                print(sobelsm2,right=T)}
+            }
+          }
+        }
+        if ((effsize==1) & (boot > 0)){bootres=bootres[2:nrow(bootres),]}
+      }
+      if (alttotal==1)
+      {
+        altcnms<-"Effect"
+        totbtvec<-totbtvec+bootdir
+        alttotfx<-t(totbtvec[1,])
+        if (boot > 0)
+        {
+          alttotfx<-matrix(0,ncol(totbtvec),4)
+          alttotfx[,1]<-t(totbtvec[1,])
+          for (cec in (1:ncol(totbtvec)))
+          {
+            if (bc==0){bcitmp<-process.pboot3(totbtvec[2:nrow(totbtvec),cec],cilow,cihigh)}
+            if (bc==1)
+            {
+              bcbout<-process.bcboot3(totbtvec[2:nrow(totbtvec),cec],totbtvec[1,cec],xp2,badend,priorlo,priorhi)
+              bcitmp<-matrix(unlist(bcbout[1]))
+              badend<-unlist(bcbout[2]);priorlo<-unlist(bcbout[3]);priorhi<-unlist(bcbout[4])
+            }
+            alttotfx[cec,2:4]<-t(bcitmp)
+          }
+          altcnms<-c(altcnms,"BootSE","BootLLCI","BootULCI")
+        }
+        resultm2<-matrix(99999,nrow(alttotfx),maxresm)
+        resultm2[1:nrow(alttotfx),1:ncol(alttotfx)]<-alttotfx
+        resultm<-rbind(resultm,resultm2)
+        if (outscreen==1)
+        {
+          if (nxvls > 1)
+          {cat("----------\n")
+            cat("\nRelative total effects of X on Y (sum of direct and indirect effects):\n")
+            alttotfp<-noquote(matrix(sprintf(decimals,alttotfx),nrow=nrow(alttotfx)))
+            colnames(alttotfp)<-altcnms
+            rownames(alttotfp)<-direffl2
+            print(alttotfp,right=T)
+          }
+          if (nxvls==1)
+          {
+            cat("\nTotal effects of X on Y (sum of direct and indirect effects):\n")
+            alttotfp<-noquote(matrix(sprintf(decimals,alttotfx),nrow=nrow(alttotfx)))
+            colnames(alttotfp)<-altcnms
+            rownames(alttotfp)<-" "
+            print(alttotfp,right=T)
+          }
+        }
+      }
+
+    }
+    #this is the end of the no moderators loop */
+
+    if (anymod > 0)
+    {
+      if (boot==0){bootres<-obscoeff;indtab<-999}
+      if (boot > 0){bootres<-rbind(obscoeff,bootres);indtab<-matrix(999,1,4)}
+      if (sum(as.numeric(indmod > 0))==nrow(indmod))
+      {if (outscreen==1)
+      {
+        if (nxvls > 1)
+        {cat("\nRelative conditional indirect effects of X on Y:\n")}
+        if (nxvls==1)
+        {cat("\nConditional indirect effects of X on Y:\n")}
+      }
+      }
+      if (sum(as.numeric(indmod > 0)) < nrow(indmod))
+      {if (outscreen==1)
+      {
+        if (nxvls > 1)
+        {cat("\nRelative conditional and unconditional indirect effects of X on Y:\n")}
+        if (nxvls==1)
+        {cat("\nConditional and unconditional indirect effects of X on Y:\n")}
+      }
+      }
+      for (i in (1:nrow(indmake)))
+      {
+        indtab<-matrix(0,1,4)
+        indkeyt<-indkey[i,]
+        if (outscreen==1)
+        {
+          cat("\nINDIRECT EFFECT:\n\n")
+          write.table(t(indkeyt),quote=FALSE,row.names=FALSE,col.names=FALSE,sep=" ")
+          cat("\n")
+        }
+        if (indmod[i,1]==0)
+        {
+          for (j in (1:nxvls))
+          {
+            indtemp<-matrix(1,nrow(bootres),1)
+            for (k in (1:indmake[i,1]))
+            {
+              jtemp<-1
+              if ((j > 1) & (k==1)){jtemp<-j}       
+              indtemp<-indtemp*bootres[,pathsfoc[jtemp,indmake[i,(k+1)]]]
+            }
+            indeff<-indtemp[1,1]
+            if (boot > 0)
+            {
+              if (bc==0){bcitmp3<-process.pboot3(indtemp[2:nrow(indtemp),1],cilow,cihigh)}
+              if (bc==1)
+              {
+                bcbout<-process.bcboot3(indtemp[2:nrow(indtemp),1],indtemp[1,1],xp2,badend,priorlo,priorhi)
+                bcitmp3<-matrix(unlist(bcbout[1]))
+                badend<-unlist(bcbout[2]);priorlo<-unlist(bcbout[3]);priorhi<-unlist(bcbout[4])
+              }
+              indeff<-cbind(indeff,t(bcitmp3))
+            }  
+            indtab<-rbind(indtab,indeff)
+          }
+          indtab<-matrix(indtab[2:nrow(indtab),],ncol=ncol(indtab))
+          resultm2<-matrix(99999,nrow(indtab),maxresm)
+          resultm2[1:nrow(indtab),1:ncol(indtab)]<-indtab
+          resultm<-rbind(resultm,resultm2)
+          indtab10<-noquote(matrix(sprintf(decimals,indtab),nrow=nrow(indtab)))
+          if (nxvls > 1)
+          {rownames(indtab10)<-xcatlab[1:nxvls,1]}
+          if (nxvls==1)
+          {rownames(indtab10)<-" "}
+          colnames(indtab10)<-c("Effect","BootSE","BootLLCI","BootULCI")
+          if (outscreen==1)
+          {print(indtab10,right=T)}
+        }
+        # end of unmoderated
+        # start of moderated
+        if (indmod[i,1] > 0)
+        {
+          if (indmod[i,1]==1)
+          {indmodva<-wmodvals;indprova<-wprobval;condlbs<-wnames;printw<-1}
+          if (indmod[i,1]==2)
+          {indmodva<-zmodvals;indprova<-zprobval;condlbs<-znames;printz<-1}
+          if (indmod[i,1]==3)
+          {
+            cntmp<-1;printz<-1;printw<-1
+            indmodva<-matrix(999,(nrow(wmodvals)*nrow(zmodvals)),2)
+            for (k7 in (1:nrow(wmodvals)))
+            {
+              for (k8 in (1:nrow(zmodvals)))
+              {indmodva[cntmp,]<-cbind(wmodvals[k7,1],zmodvals[k8,1]);cntmp<-cntmp+1}
+            }
+            condlbs<-cbind(wnames,znames)
+          }
+          condres<-matrix(999,nrow(indmodva),1)
+          if (boot > 0)
+          {condres=matrix(999,nrow(indmodva),4)}  
+          condres<-cbind(indmodva,condres)
+
+          # Here is where the computations start
+          for (k4 in (1:nxvls))
+          {
+            imm3<-matrix(1,nrow(bootres),1);imm4<-matrix(1,nrow(bootres),1);indcontr<-0  
+            if (indmod[i,1]==3){tihsw<-wprobval;tihsz<-zprobval}
+            for (k1 in (1:nrow(indmodva)))
+            {
+              tucker2<-matrix(1,nrow(bootres),1)
+              imm2<-matrix(1,nrow(bootres),1)
+              wfirst<-0;zfirst<-0;immset<-0
+              for (k2 in (1:indmake[i,1]))
+              { 
+                colnumb<-indmake[i,(k2+1)]
+                if (k2==1)
+                {
+                  wbb<-matrix(0,nrow(bootres),(nwvls*nxvls))
+                  zbb<-matrix(0,nrow(bootres),(nzvls*nxvls))
+                  wzbb<-matrix(0,nrow(bootres),(nwvls*nzvls*nxvls))
+                }
+                if (k2 != 1)
+                {
+                  wbb<-matrix(0,nrow(bootres),nwvls)
+                  zbb<-matrix(0,nrow(bootres),nzvls)
+                  wzbb<-matrix(0,nrow(bootres),(nwvls*nzvls))
+                }
+                cnt<-1;tihs<-matrix(indlocs[2:((indlocs[1,colnumb])+1),colnumb])
+                if (k2==1)
+                {
+                  focbb<-matrix(tihs[1:nxvls,1]);focbb<-matrix(bootres[,focbb],ncol=nxvls)
+                  if (indmmm[i,1] > 0)
+                  {imm<-matrix(focbb[,k4]);condbb<-matrix(imm,ncol=ncol(imm))}
+                  focaddon<-matrix(0,1,nxvls);focaddon[1,k4]<-1;cnt<-cnt+nxvls;placeh<-nxvls
+                  if (indmod[i,1]==1)
+                  {
+                    tihsz<-matrix(0,nrow(wprobval),(nzvls*nxvls))
+                    tihswz<-matrix(0,nrow(wprobval),(nwvls*nzvls*nxvls))
+                    if (pathsw[1,colnumb]==1)
+                    {
+                      temp<-matrix(0,nrow(wprobval),(nxvls*nwvls))
+                      for (k5 in (1:nrow(wprobval)))
+                      {
+                        for (k6 in (1:nwvls))
+                        {temp[k5, (((k4-1)*nwvls)+k6)]<-wprobval[k5,k6]}
+                      }
+                      indprova<-cbind(temp,tihsz,tihswz)
+                    } else {
+                      indprova<-cbind(wprobval,tihsz,tihswz)}
+                  }
+                  if (indmod[i,1]==2)
+                  {
+                    tihsw<-matrix(0,nrow(zprobval),(nwvls*nxvls))
+                    tihswz<-matrix(0,nrow(zprobval),(nwvls*nzvls*nxvls))
+                    if (pathsz[1,colnumb]==1)
+                    {
+                      temp<-matrix(0,nrow(zprobval),(nxvls*nzvls))
+                      for (k5 in (1:nrow(zprobval)))
+                      {
+                        for (k6 in (1:nzvls))
+                        {temp[k5,(((k4-1)*nzvls)+k6)]<-zprobval[k5,k6]}  
+                      }
+                      indprova<-cbind(tihsw,temp,tihswz)
+                    } else {
+                      indprova<-cbind(tihsw,zprobval,tihswz)}
+                  }
+                  if (indmod[i,1]==3)
+                  {
+                    indprova<-matrix(0,(nrow(wprobval)*nrow(zprobval)),((ncol(wprobval)*nxvls)+(ncol(zprobval)*nxvls)+(nwvls*nzvls*nxvls)))
+                    cntemp<-1           
+                    for (k7 in (1:nrow(wprobval)))
+                    {
+                      for (k8 in (1:nrow(zprobval)))
+                      {
+                        temp<-(wprobval[k7,]*focaddon[1,k4])
+                        indprova[cntemp,(((k4-1)*nwvls)+1):(k4*(nwvls))]<-temp
+                        temp<-zprobval[k8,]*focaddon[1,k4]
+                        indprova[cntemp,((((k4-1)*nzvls)+1)+(nxvls*nwvls)):((((k4-1)*nzvls)+1)+(nxvls*nwvls)+(nzvls-1))]<-temp
+                        cntemp<-cntemp+1
+                      }
+                    }
+                    if (pathsz[1,colnumb]==0)
+                    {
+                      temp<-matrix(0,nrow(indprova),(ncol(zprobval)*nxvls))
+                      indprova[,((ncol(wprobval)*nxvls)+1):((ncol(wprobval)+ncol(zprobval))*nxvls)]<-temp
+                    }
+                    if (pathsw[1,colnumb]==0)
+                    {
+                      temp<-matrix(0,nrow(indprova),(ncol(wprobval)*nxvls))
+                      indprova[,1:(ncol(wprobval)*nxvls)]<-temp   
+                    }
+                    if (pathswz[1,colnumb]==1)
+                    {
+                      cntemp<-(ncol(wprobval)*nxvls)+(ncol(zprobval)*nxvls)+((k4-1)*ncol(wprobval)*ncol(zprobval))+1
+                      for (k7 in (1:ncol(wprobval)))
+                      {
+                        for (k8 in (1:ncol(zprobval)))
+                        {
+                          indprova[,cntemp]<-matrix(indprova[,((ncol(wprobval)*(k4-1))+k7)])*matrix(indprova[,((((k4-1)*ncol(zprobval))+k8)+(nxvls*ncol(wprobval)))])
+                          cntemp<-cntemp+1
+                        }
+                      }
+                    }
+                  }
+                }
+                if (k2 > 1)
+                {
+                  focbb<-tihs[1,1];focbb=matrix(bootres[,focbb])
+                  if (indmmm[i,1] > 0){imm<-matrix(focbb[,1]);condbb<-matrix(imm)}     
+                  focaddon<-matrix(1);cnt<-cnt+1;placeh<-1
+                  if (indmod[i,1]==1)
+                  {
+                    tihsz<-matrix(0,nrow(wprobval),nzvls)
+                    tihswz<-matrix(0,nrow(wprobval),(nwvls*nzvls))
+                    indprova<-cbind(wprobval,tihsz,tihswz)
+                  }
+                  if (indmod[i,1]==2)
+                  {
+                    tihsw<-matrix(0,nrow(zprobval),nwvls)
+                    tihswz<-matrix(0,nrow(zprobval),(nwvls*nzvls))
+                    indprova<-cbind(tihsw,zprobval,tihswz)
+                  }
+                  if (indmod[i,1]==3)
+                  {
+                    indprova<-matrix(0,(nrow(wprobval)*nrow(zprobval)),((ncol(wprobval)+ncol(zprobval))+(nwvls*nzvls)))
+                    cntemp<-1           
+                    for (k7 in (1:nrow(wprobval)))
+                    {
+                      for (k8 in (1:nrow(zprobval)))
+                      {
+                        indprova[cntemp,1:(ncol(wprobval)+ncol(zprobval))]<-cbind(t(matrix(wprobval[k7,])),t(matrix(zprobval[k8,])))
+                        cntemp<-cntemp+1
+                      }
+                    }
+                    if (pathsz[1,colnumb]==0)
+                    {
+                      temp<-matrix(0,nrow(indprova),ncol(zprobval))
+                      indprova[,(ncol(wprobval)+1):(ncol(wprobval)+ncol(zprobval))]<-temp
+                    }
+                    if (pathsw[1,colnumb]==0)
+                    {
+                      temp<-matrix(0,nrow(indprova),ncol(wprobval))
+                      indprova[,1:ncol(wprobval)]<-temp   
+                    }
+                    if (pathswz[1,colnumb]==1)
+                    {
+                      cntemp<-(ncol(wprobval)+ncol(zprobval)+1)
+                      for (k7 in (1:ncol(wprobval)))
+                      {
+                        for (k8 in (1:ncol(zprobval)))
+                        {
+                          indprova[,cntemp]<-matrix(indprova[,k7])*matrix(indprova[,(ncol(wprobval)+k8)])
+                          cntemp<-cntemp+1
+                        }
+                      }
+                    }
+                  }
+                }  
+                if (pathsw[1,colnumb]==1)
+                {
+                  wbb<-matrix(tihs[cnt:(cnt+(placeh*nwvls)-1),1])
+                  wbb<-matrix(bootres[,wbb],ncol=nrow(wbb))
+                  immlbs2<-matrix(wcatlab[1:nwvls,1])
+                  if (zfirst==0){wfirst<-1}              
+                  if ((indmmm[i,1]==1) | (indmmm[i,1]==31) | (indmmm[i,1]==51))
+                  {
+                    imm<-matrix(wbb[,1])
+                    for (k7 in (1:nwvls))
+                    {imm<-cbind(imm,wbb[,(((k4-1)*nwvls*(as.numeric(k2==1)))+k7)])}
+                    imm<-matrix(imm[,2:ncol(imm)],ncol=(ncol(imm)-1))               
+                  }
+                  if ((indmmm[i,1]==41) | (indmmm[i,1]==51))
+                  {
+                    condbb<-matrix(0,nrow(bootres),1)
+                    for (k7 in (1:nwvls))        
+                    {condbb<-cbind(condbb,wbb[,(((k4-1)*nwvls*(as.numeric(k2==1)))+k7)])}          
+                    condbb<-matrix(condbb[,2:ncol(condbb)],ncol=(ncol(condbb)-1))
+                  }    
+                  cnt<-cnt+(placeh*nwvls)
+                }
+                if (pathsz[1,colnumb]==1)
+                {
+                  zbb<-matrix(tihs[cnt:(cnt+(placeh*nzvls)-1),1])
+                  zbb<-matrix(bootres[,zbb],ncol=nrow(zbb))
+                  if (wfirst==0){zfirst<-1}
+                  if (indmmm[i,1] != 31){immlbs2<-matrix(zcatlab[1:nzvls,1])}
+                  if ((indmmm[i,1]==2) | (indmmm[i,1]==31) | (indmmm[i,1]==51))
+                  {
+                    if (indmmm[i,1]==2){imm<-matrix(zbb[,1])}
+                    for (k7 in (1:nzvls))
+                    {imm<-cbind(imm,zbb[,(((k4-1)*nzvls*(as.numeric(k2==1)))+k7)])}
+                    if ((indmmm[i,1]==2) | (indmmm[i,1]==51))
+                    {
+                      imm<-matrix(imm[,2:ncol(imm)],ncol=(ncol(imm)-1))  
+                      if (indmmm[i,1]==51){condbb<-cbind(condbb,imm)}
+                    }         
+                  }
+                  cnt<-cnt+(placeh*nzvls)
+                }
+                if (pathswz[1,colnumb]==1)
+                {
+                  wzbb<-matrix(tihs[cnt:(cnt+(placeh*nwvls*nzvls)-1),1])
+                  wzbb<-matrix(bootres[,wzbb],ncol=nrow(wzbb))
+                  if (indmmm[i,1]==41)
+                  {
+                    imm<-matrix(wzbb[,1])              
+                    for (k7 in (1:(nwvls*nzvls)))
+                    {imm<-cbind(imm,wzbb[,(((k4-1)*nzvls*nwvls*(as.numeric(k2==1)))+k7)])}
+                  }
+                  if (indmmm[i,1]==41)
+                  {
+                    imm<-matrix(imm[,2:ncol(imm)],ncol=(ncol(imm)-1))
+                    condbb<-cbind(condbb,imm[,(ncol(imm)-(nwvls*nzvls)+1):ncol(imm)]) 
+                  }
+                  cnt<-cnt+(placeh*nzvls*nwvls)
+                }
+                indprobe<-cbind(focaddon,t(matrix(indprova[k1,])))
+                tucker<-cbind(focbb,wbb,zbb,wzbb)
+                for (k3 in (1:ncol(indprobe)))
+                {tucker[,k3]<-matrix(tucker[,k3]*indprobe[1,k3])}
+                tucker2<-tucker2*matrix(rowSums(tucker))
+                if ((indmmm[i,1]==1) | (indmmm[i,1]==2) | (indmmm[i,1]==31) | (indmmm[i,1]==41) | (indmmm[i,1]==51))
+                {
+                  if (immset==1)
+                  {
+                    if ((ncol(imm2)==1) & (ncol(imm)==1)){imm2<-(matrix(imm2)*matrix(imm))}
+                    if ((indmmm[i,1]==41) | (indmmm[i,1]==51))
+                    {
+                      if ((ncol(condbb2) > 1) & (ncol(condbb) > 1))
+                      {
+                        condbb2t<-matrix(-999999,nrow(condbb2),(ncol(condbb2)*ncol(condbb)))
+                        k9<-1
+                        if (wfirst==1)
+                        {
+                          for (k7 in (1:ncol(condbb2)))
+                          {
+                            for (k8 in (1:ncol(condbb)))
+                            {condbb2t[,k9]<-(matrix(condbb2[,k7])*matrix(condbb[,k8]));k9<-k9+1}
+                          }
+                        }
+                        if (zfirst==1)
+                        {
+                          for (k7 in (1:ncol(condbb)))
+                          {
+                            for (k8 in (1:ncol(condbb2)))
+                            {condbb2t[,k9]<-(matrix(condbb[,k7])*matrix(condbb2[,k8]));k9<-k9+1}             
+                          }
+                        }
+                        condbb2<-matrix(condbb2t,ncol=ncol(condbb2t))            
+                      }
+                      if ((ncol(condbb2) > 1) & (ncol(condbb)==1))
+                      {
+                        for (k7 in (1:ncol(condbb2)))
+                        {condbb2[,k7]<-(matrix(condbb2[,k7])*matrix(condbb))}
+                      }
+                      if ((ncol(condbb2)==1) & (ncol(condbb) > 1))
+                      {
+                        for (k7 in (1:ncol(condbb)))
+                        {condbb[,k7]<-(matrix(condbb2)*matrix(condbb[,k7]))}
+                        condbb2<-matrix(condbb,ncol=ncol(condbb))
+                      }                 
+                    }
+                    if ((ncol(imm2) != 1) & (ncol(imm) != 1))
+                    {
+                      imm2t<-matrix(-999999,nrow(imm2),(ncol(imm2)*ncol(imm)))
+                      k9<-1
+                      if (wfirst==1)
+                      {
+                        for (k7 in (1:ncol(imm2)))
+                        {
+                          for (k8 in (1:ncol(imm)))
+                          {imm2t[,k9]<-(matrix(imm2[,k7])*matrix(imm[,k8]));k9<-k9+1}
+                        }
+                      }
+                      if (zfirst==1)
+                      {
+                        for (k7 in (1:ncol(imm)))
+                        {
+                          for (k8 in (1:ncol(imm2)))
+                          {imm2t[,k9]<-(matrix(imm[,k7])*matrix(imm2[,k8]));k9<-k9+1}
+                        }
+                      }
+                      imm2<-matrix(imm2t,ncol=ncol(imm2t))
+                    }
+                    if ((ncol(imm2) > 1) & (ncol(imm)==1))
+                    {
+                      for (k7 in (1:ncol(imm2)))
+                      {imm2[,k7]<-(matrix(imm2[,k7])*matrix(imm))}
+                    }
+                    if ((ncol(imm2)==1) & (ncol(imm) > 1))
+                    {
+                      for (k7 in (1:ncol(imm)))
+                      {imm[,k7]<-(matrix(imm2)*matrix(imm[,k7]))}
+                      imm2<-matrix(imm,ncol=ncol(imm))
+                    }
+                  }
+                  if (immset==0)
+                  {
+                    imm2<-matrix(imm,ncol=ncol(imm))
+                    if ((indmmm[i,1]==41) | (indmmm[i,1]==51))
+                    {condbb2<-matrix(condbb,ncol=ncol(condbb))}
+                    immset<-1
+                  }
+                }
+                # that is it for mmm loop */
+              }
+              # end of looping through paths: k2
+              indtemp<-tucker2[1,1]
+              if ((indmmm[i,1]==12) | (indmmm[i,1]==22))
+              {
+                imm3<-cbind(imm3,tucker2)
+                if (k1==nrow(indmodva))
+                {
+                  imm3<-matrix(imm3[,2:ncol(imm3)],ncol=(ncol(imm3)-1))
+                  immstop<-ncol(imm3)
+                  for (k8 in (2:immstop))
+                  {
+                    if (indmmmt[i,1]==1){imm3<-cbind(imm3,(imm3[,k8]-imm3[,1]))}
+                    if (indmmmt[i,1]==2){imm3=cbind(imm3,(imm3[,k8]-imm3[,(k8-1)]))}
+                    if (indmmmt[i,1]==3)
+                    {
+                      imm3<-cbind(imm3,((rowSums(imm3[,(k8:immstop)])/(immstop-k8+1))-imm3[,(k8-1)]))
+                    }
+                    if (indmmmt[i,1]==4)
+                    {imm3<-cbind(imm3,(imm3[,k8]-(rowSums(imm3[,1:immstop])/immstop)))}
+                  }
+                  if (indmmmt[i,1] < 5)
+                  {imm2<-matrix(imm3[,(immstop+1):ncol(imm3)],ncol=(ncol(imm3)-immstop))}
+                }
+              }      
+              if ((indmmm[i,1]>-1) & ((contrast==1) | (contrast==2)))
+              {
+                imm4<-cbind(imm4,tucker2)
+                if ((k1==nrow(indmodva)) & (k1 > 1))
+                {
+                  imm4<-matrix(imm4[,2:ncol(imm4)],ncol=(ncol(imm4)-1))
+                  immstop<-ncol(imm4)
+                  condcont<-matrix(-999,(immstop*(immstop-1)/2),6)              
+                  for (k8 in (1:(immstop-1)))
+                  {
+                    for (k9 in ((k8+1):immstop))
+                    {                   
+                      if (contrast==1){imm4<-cbind(imm4,matrix(imm4[,k9]-imm4[,k8]))}
+                      if (contrast==2){imm4<-cbind(imm4,matrix(abs(imm4[,k9])-abs(imm4[,k8])))}
+                      condcont[(ncol(imm4)-immstop),1]<-imm4[1,k9]
+                      condcont[(ncol(imm4)-immstop),2]<-imm4[1,k8]
+                    }
+                  }
+                  imm4<-matrix(imm4[,(immstop+1):ncol(imm4)],ncol=(ncol(imm4)-immstop))   
+                  for (k8 in (1:ncol(imm4)))
+                  {
+                    condcont[k8,3]<-imm4[1,k8]
+                    if (boot > 0)
+                    {
+                      if (bc==0){condcon3<-process.pboot3(imm4[2:nrow(imm4),k8],cilow,cihigh)}
+                      if (bc==1)
+                      {
+                        bcbout<-process.bcboot3(imm4[2:nrow(imm4),k8],imm4[1,k8],xp2,badend,priorlo,priorhi)
+                        condcon3<-matrix(unlist(bcbout[1]))
+                        badend<-unlist(bcbout[2]);priorlo<-unlist(bcbout[3]);priorhi<-unlist(bcbout[4])
+                      }
+                      condcont[k8,4:6]<-t(condcon3)  
+                    }
+                  }
+                  if (boot==0){condcont<-matrix(condcont[,1:3],ncol=3)}
+                  indcontr<-1
+                }
+              }
+              if (boot > 0)
+              {
+                if (bc==0){bcitmp11<-process.pboot3(tucker2[2:nrow(tucker2),1],cilow,cihigh)}
+                if (bc==1)
+                {
+                  bcbout<-process.bcboot3(tucker2[2:nrow(tucker2),1],tucker2[1,1],xp2,badend,priorlo,priorhi)
+                  bcitmp11<-matrix(unlist(bcbout[1]))
+                  badend<-unlist(bcbout[2]);priorlo<-unlist(bcbout[3]);priorhi<-unlist(bcbout[4])
+                }
+                indtemp<-cbind(indtemp,t(bcitmp11))  
+              }
+              condres[k1,(ncol(indmodva)+1):ncol(condres)]<-indtemp
+            }
+            # end of looping through indirect effects: k1
+            # Here is where the computations end
+            resultm2<-matrix(99999,nrow(condres),maxresm)
+            resultm2[1:nrow(condres),1:ncol(condres)]<-condres
+            resultm<-rbind(resultm,resultm2)
+            condresp<-noquote(matrix(sprintf(decimals,condres),nrow=nrow(condres)))
+            if (k4==1)
+            {
+              condlbs<-cbind(condlbs,"Effect")
+              if (boot > 0)
+              {condlbs<-cbind(condlbs,"BootSE","BootLLCI","BootULCI")}
+              condrlb<-t(matrix(replicate(nrow(condres)," ")))
+            }
+            if (nxvls > 1)
+            {condrlb<-matrix(xcatlab[k4,1],nrow(condres),1)}
+            colnames(condresp)<-condlbs
+            rownames(condresp)<-condrlb
+            if (outscreen==1)
+            {print(condresp,right=T)}
+            if (indmmm[i,1]==0){cat("\n")}
+            dichadj<-0;immcat<-0
+            if (indmmm[i,1] > 0)
+            {
+              if ((indmmm[i,1]==1) | (indmmm[i,1]==12) | (indmmm[i,1]==31))
+              {
+                if ((wdich==1) & (mcw==0))
+                {
+                  if (indmmm[i,1] != 12){imm2[,1]<-imm2[,1]*(wmax-wmin)}
+                  if (indmmm[i,1] != 31){dichadj<-1}
+                }           
+                if (((mcw==1) | (mcw==2)) & (indmmm[i,1] != 31)){immcat<-1}
+              }
+              if ((indmmm[i,1]==2) | (indmmm[i,1]==22) | (indmmm[i,1]==31))
+              {
+                if ((zdich==1) & (mcz==0))
+                {
+                  if (indmmm[i,1]==31)
+                  {
+                    imm2[,(nwvls+1):ncol(imm2)]<-matrix(imm2[,(nwvls+1):ncol(imm2)],ncol=(ncol(imm2)-nwvls))*(zmax-zmin)
+                  }
+                  if (indmmm[i,1]==2){imm2[,1]<-imm2[,1]*(zmax-zmin)}
+                  if (indmmm[i,1] != 31){dichadj<-1}
+                }
+                if (((mcz==1) | (mcz==2)) & (indmmm[i,1] != 31)){immcat<-1}
+              }
+              immtemp2<-t(matrix(imm2[1,],ncol=ncol(imm2)))
+              immtemp<-matrix(immtemp2,ncol=ncol(immtemp2))
+              immlbs<-"Index"
+              if (boot > 0)
+              {
+                immtemp<-matrix(0,1,3)
+                for (k7 in (1:ncol(imm2)))
+                {
+                  if (bc==0){immbtci<-process.pboot3(imm2[2:nrow(imm2),k7],cilow,cihigh)} 
+                  if (bc==1)
+                  {
+                    bcbout<-process.bcboot3(imm2[2:nrow(imm2),k7],imm2[1,k7],xp2,badend,priorlo,priorhi)
+                    immbtci<-matrix(unlist(bcbout[1]))
+                    badend<-unlist(bcbout[2]);priorlo<-unlist(bcbout[3]);priorhi<-unlist(bcbout[4])
+                  }
+                  immtemp<-rbind(immtemp,t(immbtci))
+                } 
+                immtemp<-matrix(immtemp[2:nrow(immtemp),],ncol=ncol(immtemp))
+                immtemp<-cbind(immtemp2,immtemp)
+                immlbs<-c(immlbs,"BootSE","BootLLCI","BootULCI")
+              }
+              resultm2<-matrix(99999,nrow(immtemp),maxresm)
+              resultm2[1:nrow(immtemp),1:ncol(immtemp)]<-immtemp
+              resultm<-rbind(resultm,resultm2)
+              immtempr<-noquote(matrix(sprintf(decimals,immtemp),nrow=nrow(immtemp)))
+              colnames(immtempr)<-immlbs        
+              if ((dichadj==0) & (immcat==0) & (indmmmt[i,1] != 5) & (indmmm[i,1] < 100))
+              {
+                if (indmmm[i,1] < 30)
+                {
+                  rownames(immtempr)<-immlbs2
+                  if (outscreen==1)
+                  {cat("\n     Index of moderated mediation:\n")
+                    print(immtempr,right=T)}
+                  if ((nxvls > 1) & (k4 < nxvls)){cat("\n")}
+                }
+                if (indmmm[i,1]==31)
+                {
+                  immlbs2<-rbind(immlbs2,matrix(zcatlab[1:nzvls,1]))
+                  rownames(immtempr)<-immlbs2
+                  if (outscreen==1)
+                  {cat("\n     Indices of partial moderated mediation:\n")
+                    print(immtempr,right=T)}
+                  if ((nxvls > 1) & (k4 < nxvls)){cat("\n")}
+                }
+                if ((nzvls==1) & (nwvls==1))
+                {
+                  if ((indmmm[i,1]==41) | (indmmm[i,1]==51))
+                  {
+                    for (k7 in (1:nwvls))
+                    {
+                      immlbs2<-zcatlab[1:nzvls,1]
+                      immtemp2<-matrix(immtemp[(((k7-1)*nzvls)+1):(((k7-1)*nzvls)+nzvls),],ncol=ncol(immtemp))
+                      #resultm2<-matrix(99999,nrow(immtemp2),maxresm)
+                      #resultm2[1:nrow(immtemp2),1:ncol(immtemp2)]<-immtemp2
+                      #print(resultm)
+                      #print(resultm2)
+                      #resultm<-rbind(resultm,resultm2)
+                      #print(resultm)     
+                      immtem2r<-noquote(matrix(sprintf(decimals,immtemp2),nrow=nrow(immtemp2)))
+                      colnames(immtem2r)<-immlbs
+                      if (nwvls > 1)
+                      {
+                        primodv<-cbind("Primary moderator:", wcatlab[k7,1])
+                        if (outscreen==1)
+                        {write.table(primodv,quote=FALSE,row.names=FALSE,col.names=FALSE)}
+                      }
+                      if (nzvls==1)
+                      {
+                        rownames(immtem2r)<-" "
+                        if (outscreen==1)
+                        {cat("\n     Index of moderated moderated mediation:\n")
+                          print(immtem2r,right=T)}
+                      } else {
+                        rownames(immtem2r)<-immlbs2
+                        if (outscreen==1)            
+                        {cat("\n     Indices of moderated moderated mediation:\n")
+                          print(immtem2r,right=T)}
+                      }
+                      cmmtemp<-matrix(0,nrow(zprobval),4)        
+                      for (k8 in (1:nrow(zprobval)))
+                      {
+                        bbst<-((nwvls+1)+((k7-1)*nzvls));bben<-((nwvls+1)+((k7-1)*nzvls)+(nzvls-1))
+                        condbb3<-matrix(condbb2[,bbst:bben],ncol=(bben-bbst+1))
+                        if (ncol(zprobval) > 1)
+                        {
+                          condbb3<-condbb3*diag(c(zprobval[k8,]))
+                        } else {
+                          condbb3<-condbb3*zprobval[k8,]
+                        }
+                        condbb3<-cbind(condbb2[,k7],condbb3)
+                        icmm<-matrix(rowSums(condbb3))
+                        cmmtemp[k8,1]<-icmm[1,1]
+                        if (boot > 0)
+                        {
+                          if (bc==0){cmmt3<-process.pboot3(icmm[2:nrow(icmm),1],cilow,cihigh)}
+                          if (bc==1)
+                          {
+                            bcbout<-process.bcboot3(icmm[2:nrow(icmm),1],icmm[1,1],xp2,badend,priorlo,priorhi)
+                            cmmt3<-matrix(unlist(bcbout[1]))
+                            badend<-unlist(bcbout[2]);priorlo<-unlist(bcbout[3]);priorhi<-unlist(bcbout[4])
+                          }
+                          cmmtemp[k8,2:4]<-t(cmmt3)
+                        }
+                        cmmlbs<-cbind(znames,t(matrix(immlbs)))
+                      }
+                      if (boot==0){cmmtemp<-matrix(cmmtemp[,1:1],ncol=1);cmmlbs<-cbind(znames,"Index")}                   
+                      cmmtemp<-cbind(zmodvals,cmmtemp)
+                      resultm2<-matrix(99999,nrow(cmmtemp),maxresm)
+                      resultm2[1:nrow(cmmtemp),1:ncol(cmmtemp)]<-cmmtemp
+                      resultm<-rbind(resultm,resultm2)
+                      cmmtempr<-noquote(matrix(sprintf(decimals,cmmtemp),nrow=nrow(cmmtemp)))
+                      #if (boot==0){cmmtempr<-matrix(cmmtemp[,1:2],ncol=2)}                   
+                      #cmmlbs<-cbind(znames,t(matrix(immlbs)))
+                      rownames(cmmtempr)<-t(matrix(replicate(nrow(cmmtempr)," ")))
+                      colnames(cmmtempr)<-cmmlbs
+                      if (outscreen==1)
+                      {cat("\n     Indices of conditional moderated mediation by W:\n")
+                        print(cmmtempr,right=T)}
+                    }
+                  }
+                }
+              }
+              if (((dichadj==1) | (immcat==1)) & (indmmm[i,1] < 30))
+              {
+                if (outscreen==1)
+                {
+                  cat("\n     Index of moderated mediation\n")
+                  cat("     (differences beween conditional indirect effects):\n")
+                  rownames(immtempr)<-immlbs2
+                  print(immtempr,right=T)
+                }
+              }
+            }
+            if (indcontr==1)
+            {
+              resultm2<-matrix(99999,nrow(condcont),maxresm)
+              resultm2[1:nrow(condcont),1:ncol(condcont)]<-condcont
+              resultm<-rbind(resultm,resultm2)
+              condcnt3<-noquote(matrix(sprintf(decimals,condcont),nrow=nrow(condcont))) 
+              condctlb<-c("Effect1","Effect2","Contrast","BootSE", "BootLLCI","BootULCI")
+              colnames(condcnt3)<-condctlb
+              rownames(condcnt3)<-t(matrix(replicate(nrow(condcnt3)," ")))
+              if (outscreen==1)
+              {
+                cat("\n     Pairwise contrasts between conditional indirect effects\n")
+                cat("     (Effect1 minus Effect2):\n")
+                print(condcnt3,right=T)
+              }
+            }
+            if (outscreen==1)
+            {cat("\n---\n")}
+          }
+        }
+        #end of moderated */
+      }
+    }
+    # This is the end of the moderated loop */
+  }
+
+  if ((criterr==0) & (saveboot==1))
+  {
+    if (boot > 0)
+    {
+      if (outscreen==1)
+      {
+        cat("\n*********************************************************************** \n")
+        conseq<-conseq[2:nrow(conseq),]
+        #cat("Bootstrap estimates were saved in a global dataframe named process.boots\n")
+        colslab<-cbind(savlabs,conseq,vlabs)
+        cat("\nMap of column names to model coefficients in bootstrap matrix:\n")
+        rownames(colslab)<-t(matrix(replicate(nrow(colslab)," ")))
+        colnames(colslab)<-c("name","Conseqnt","Antecdnt")
+        print(noquote(colslab),right=T)
+      }
+    }
+  }
+
+  #PRINT BOOTSTRAP RESULTS FOR MODEL PARAMETERS
+  if ((criterr==0) & (boot > 0) & (modelbt==1))
+  {
+    labstart<-1
+    if (outscreen==1)
+    {cat("\n********** BOOTSTRAP RESULTS FOR REGRESSION MODEL PARAMETERS **********\n\n")}
+    for (iboot in (1:(nms+nys)))
+    {
+      vlabsm<-matrix(vlabs[labstart:(labstart+(nump[1,iboot]-1)),1])
+      bootcimt<-matrix(bootcim[labstart:(labstart+(nump[1,iboot]-1)),],ncol=5)
+      resultm2<-matrix(99999,nrow(bootcimt),maxresm)
+      resultm2[1:nrow(bootcimt),1:ncol(bootcimt)]<-bootcimt
+      resultm<-rbind(resultm,resultm2)
+      bootcimt<-noquote(matrix(sprintf(decimals,bootcimt),ncol=5))
+      colnames(bootcimt)<-matrix(c("Coeff","BootMean","BootSE","BootLLCI","BootULCI"))
+      rownames(bootcimt)<-vlabsm
+      if (outscreen==1)
+      {
+        cat("Outcome variable: ")
+        write.table(outnames[iboot,1],quote=FALSE,row.names=FALSE,col.names=FALSE)
+        cat("\n")
+        print(bootcimt,right=T)
+      }
+      labstart<-labstart+nump[1,iboot]
+      if ((iboot < (nms+nys)) & (outscreen==1)){cat("----------\n")}
+    }
+  }
+
+  #print model matrices
+  if ((criterr==0) & (matrices==1) & (outscreen==1))
+  {
+    cat("\n********************* MODEL DEFINITION MATRICES *********************** \n \n")
+    cat("FROM variables are columns, TO variables are rows. \n \n")
+    temp2<-matrix("0",nrow(bcmat),ncol(bcmat))
+    for (i in c(2:nrow(bcmat)))
+    {for (j in c(1:(ncol(bcmat)-1)))
+    {if (bcmat[i,j]==1){temp2[i,j]<-"1"}
+      if (j >= i){temp2[i,j]<-" "}}
+    }
+    temp2<-as.matrix(noquote(temp2[2:nrow(bcmat),(1:(ncol(bcmat)-1))]))
+    if (nms > 0){cmatlabs<-c(xnames,mnames);rmatlabs<-c(mnames,ynames)}
+    if (nms==0){cmatlabs<-xnames;rmatlabs<-ynames}
+    colnames(temp2)<-cmatlabs
+    rownames(temp2)<-rmatlabs
+    cat("BMATRIX: Paths freely estimated (1) and fixed to zero (0): \n") 
+    print(temp2)
+    z<-0
+    if (sum(wcmat) !=0)
+    {
+      temp2<-matrix("0",nrow(wcmat),ncol(wcmat))
+      for (i in c(2:nrow(wcmat)))
+      {for (j in c(1:(ncol(wcmat)-1)))
+      {if (wcmat[i,j]==1){temp2[i,j]<-"1"}
+        if (j >= i){temp2[i,j]<-" "}}
+      }
+      temp2<-as.matrix(noquote(temp2[2:nrow(wcmat),(1:(ncol(wcmat)-1))]))
+      colnames(temp2)<-cmatlabs
+      rownames(temp2)<-rmatlabs
+      cat("\nWMATRIX: Paths moderated (1) and not moderated (0) by W: \n") 
+      print(temp2)
+    }
+    if (sum(zcmat) !=0)
+    {
+      temp2<-matrix("0",nrow(zcmat),ncol(zcmat))
+      for (i in c(2:nrow(zcmat)))
+      {for (j in c(1:(ncol(zcmat)-1)))
+      {if (zcmat[i,j]==1){temp2[i,j]<-"1"}
+        if (j >= i){temp2[i,j]<-" "}}
+      }
+      temp2<-as.matrix(noquote(temp2[2:nrow(zcmat),(1:(ncol(zcmat)-1))]))
+      colnames(temp2)<-cmatlabs
+      rownames(temp2)<-rmatlabs
+      cat("\nZMATRIX: Paths moderated (1) and not moderated (0) by Z: \n") 
+      print(temp2)
+    }
+    if (sum(wzcmat) !=0)
+    {
+      temp2<-matrix("0",nrow(wzcmat),ncol(wzcmat))
+      for (i in c(2:nrow(wzcmat)))
+      {for (j in c(1:(ncol(wzcmat)-1)))
+      {if (wzcmat[i,j]==1){temp2[i,j]<-"1"}
+        if (j >= i){temp2[i,j]<-" "}}
+      }
+      temp2<-as.matrix(noquote(temp2[2:nrow(wzcmat),(1:(ncol(wzcmat)-1))]))
+      colnames(temp2)<-cmatlabs
+      rownames(temp2)<-rmatlabs
+      cat("\nWZMATRIX: W moderated paths moderated (1) and not moderated (0) by Z: \n") 
+      print(temp2)
+    }
+    if (ncs > 0)
+    {colnames(ccmat)<-covnames
+    rownames(ccmat)<-rmatlabs
+    cat("\nCMATRIX: Covariates (columns) in (1) and not in (0) the models of M and Y (rows): \n")
+    print(ccmat)
+    }  
+  }
+  #end print model matrices
+
+  if (criterr==0)
+  {
+    resultm<-resultm[2:nrow(resultm),]
+    bocaj<-matrix(as.numeric(resultm==99999),nrow=nrow(resultm))
+    bocaj<-(colSums(bocaj)==nrow(resultm))
+    bocaj<-matrix(1-as.numeric(bocaj))
+    j<-1
+    for (i in (1:ncol(resultm)))
+    {if (bocaj[i,1]==1){j=j+1}}
+    resultm<-resultm[,1:(j-1)]
+    resultm[resultm==99999]<-NA
+  }
+  if ((outscreen==1) & (activate==0))
+  {cat("\n******************** ANALYSIS NOTES AND ERRORS ************************ \n")}
+  if (activate==1)
+  {cat("*********************************************************************** \n")}
+  if ((criterr==0) & (outscreen==1))
+  {
+    cat("\nLevel of confidence for all confidence intervals in output: ")
+    write.table(conf,quote=FALSE,row.names=FALSE,col.names=FALSE)
+    if (boot>0)
+    { 
+      if ((goodboot==boot) & (bc==0))
+      {
+        cat("\nNumber of bootstraps for percentile bootstrap confidence intervals: ")
+        write.table(boot,quote=FALSE,row.names=FALSE,col.names=FALSE)  
+      }
+      if ((goodboot==boot) & (bc==1))
+      {
+        cat("\nNumber of bootstraps for bias-corrected bootstrap confidence intervals: ")
+        write.table(boot,quote=FALSE,row.names=FALSE,col.names=FALSE)  
+      }
+      if (length(badend) > 1)
+      {
+        cat("\nWARNING: Bootstrap CI endpoints below are not trustworthy. Decrease confidence\n")
+        cat("or increase the number of bootstrap samples.\n")
+        badend<-matrix(badend);badend<-t(badend[2:nrow(badend),1])
+        badend<-noquote(matrix(sprintf(decimals,badend),nrow=nrow(badend)))
+        write.table(badend,quote=FALSE,row.names=FALSE,col.names=FALSE)
+      }
+    }
+    if (mc > 0)
+    {
+      cat("\nNumber of samples for Monte Carlo confidence intervals: ")
+      write.table(mc,quote=FALSE,row.names=FALSE,col.names=FALSE)  
+    }
+    if ((wnotev > 0) & (printw==1))
+    {
+      if (wnotev==1)
+      {cat("\nW values in conditional tables are the 16th, 50th, and 84th percentiles.\n")}
+      if ((wnotev==2) & (minwwarn==0) & (maxwwarn==0))
+      {cat("\nW values in conditional tables are the mean and +/- SD from the mean.\n")}  
+      if (minwwarn==1)
+      {cat("\nW values in conditional tables are the minimum, the mean, and 1 SD above the mean.\n")} 
+      if (maxwwarn==1)
+      {cat("\nW values in conditional tables are 1 SD below the mean, the mean, and the maximum.\n")}
+    }
+    if ((znotev > 0) & (printz==1))
+    {
+      if (znotev==1)
+      {cat("\nZ values in conditional tables are the 16th, 50th, and 84th percentiles.\n")}
+      if ((znotev==2) & (minzwarn==0) & (maxzwarn==0))
+      {cat("\nZ values in conditional tables are the mean and +/- SD from the mean.\n")}  
+      if (minzwarn==1)
+      {cat("\nZ values in conditional tables are the minimum, the mean, and 1 SD above the mean.\n")} 
+      if (maxzwarn==1)
+      {cat("\nZ values in conditional tables are 1 SD below the mean, the mean, and the maximum.\n")}
+    }
+    if (minwwarn > 0)
+    {cat("\nNOTE: One SD below the mean is below the minimum observed in the data for W,\n")
+      cat("      so the minimum measurement on W is used for conditioning instead.\n")}
+    if (maxwwarn > 0)
+    {cat("\nNOTE: One SD above the mean is above the maximum observed in the data for W,\n")
+      cat("      so the maximum measurement on W is used for conditioning instead.\n")}
+    if (minzwarn > 0)
+    {cat("\nNOTE: One SD below the mean is below the minimum observed in the data for Z,\n")
+      cat("      so the minimum measurement on Z is used for conditioning instead.\n")}
+    if (maxzwarn > 0)
+    {cat("\nNOTE: One SD above the mean is above the maximum observed in the data for Z,\n")
+      cat("      so the maximum measurement on Z is used for conditioning instead.\n")}
+    if (pstog==1)
+    {cat("\nNOTE: Standardized coefficients for dichotomous or multicategorical X are\n")
+      cat("      in partially standardized form.\n")}
+    for (i in c(1:100)) 
+    {
+      if (notecode[i,1]==1)
+      {cat(" \n")
+        cat("NOTE: COVMY is ignored when using CMATRIX option. \n")}
+      if (notecode[i,1]==2)
+      {cat(" \n")
+        cat("NOTE: Confidence level restricted to between 50 and 99.9999%. 95% confidence is provided in output. \n")}
+      if (notecode[i,1]==3)
+      {cat(" \n")
+        cat("NOTE: The following variables were mean centered prior to analysis: \n")
+        centvar<-c("      ", centvar)
+        centvar<-t(noquote(centvar))  
+        write.table(centvar,quote=FALSE,row.names=FALSE,col.names=FALSE)
+      }
+      if ((notecode[i,1]==4) & (ydich != 1))
+      {cat(" \n")
+        cat("NOTE: A heteroscedasticity consistent standard error and covariance matrix estimator was used. \n")}  
+      if (notecode[i,1]==6)
+      {cat(" \n")
+        cat("NOTE: Due to estimation problems, some bootstrap samples had to be replaced. \n")
+        cat("      The number of times this happened was: ")
+        write.table(badboot,quote=FALSE,row.names=FALSE,col.names=FALSE)}  
+      if (notecode[i,1]==7)
+      {cat(" \n")
+        cat("NOTE: The bootstrapping was not completed due to problematic bootstrap samples. \n")
+        cat("      Bootstrap confidence intervals are therefore suppressed.\n")}
+      if (notecode[i,1]==8)
+      {cat(" \n")
+        cat("NOTE: The number of bootstrap samples was adjusted upward given your desired confidence. \n")}  
+      if (notecode[i,1]==9)
+      {cat(" \n")
+        cat("NOTE: WMODVAL is ignored when W is specified as multicategorical. \n")}  
+      if (notecode[i,1]==10)
+      {cat(" \n")
+        cat("NOTE: ZMODVAL is ignored when Z is specified as multicategorical. \n")}
+      if (notecode[i,1]==11)
+      {cat(" \n")
+        cat("NOTE: Total effect model generated only when all covariates are specified\n")
+        cat("      in all models of M and Y.\n")}
+      if (notecode[i,1]==12)
+      {cat(" \n")
+        cat("NOTE: Total effect model generated only when X is freely estimated to\n")
+        cat("      affect each M and both X and M are freely estimated to affect Y.\n")}
+      if (notecode[i,1]==30)
+      {cat(" \n")
+        cat("NOTE: Your vector of linear hypothesis weights is of the wrong length for this model. \n")}  
+      if (notecode[i,1]==13)
+      {cat(" \n")
+        cat("NOTE: There are too many pairwise contrasts to conduct with this model. \n")}  
+      if (notecode[i,1]==14)
+      {cat(" \n")
+        cat("NOTE: The number of contrast weights must equal the number of indirect effects. \n")}  
+      if (notecode[i,1]==15)
+      {cat(" \n")
+        cat("NOTE: Monte Carlo confidence intervals not available for this model. \n")
+        cat("      Bootstrapping is used instead.\n")}
+      if (notecode[i,1]==16)
+      {cat(" \n")
+        cat("NOTE: The number of Monte Carlo samples was adjusted upward given your desired confidence. \n")}  
+      if (notecode[i,1]==19)
+      {cat(" \n")
+        cat("NOTE: Your contrast matrix is invalid or not applicable to this model. \n")}  
+      if (notecode[i,1]==20)
+      {cat(" \n")
+        cat("NOTE: One of the groups specified by your contrast matrix does not exist in the data. \n")}  
+      if (notecode[i,1]==24)
+      {cat(" \n")
+        cat("NOTE: Total effect model not available with dichotomous Y. \n")}
+      if (notecode[i,1]==25)
+      {cat(" \n")
+        cat("NOTE: STAND/EFFSIZE options not available with dichotomous Y. \n")}
+      if (notecode[i,1]==27)
+      {cat(" \n")
+        cat("NOTE: Standardized coefficients not available for models with moderators. \n")}
+      if (notecode[i,1]==28)
+      {cat(" \n")
+        cat("NOTE: The contrast option is not available with a multicategorical X. \n")}
+      if ((notecode[i,1]==29) & (listmiss==1))
+      {cat(" \n")
+        a<-missrow;conum<-ncol(missrow);allgood<-0;smremain<-12;largesti<-1;smallrow<-0;
+        if (conum > 12)
+        {
+          for (ii in c(1:12))
+          { 
+            check<-(conum/ii);
+            if (check==trunc(check))
+            {
+              check2<-conum/ii;aok<-ii
+              if (aok > 2){allgood<-1}
+            }
+            if (check != trunc(check))
+            {
+              remain<-conum-(ii*trunc(check))
+              if (remain <= smremain)
+              {smremain<-remain;largesti<-ii;smallrow<-trunc(conum/largesti)}
+            }
+          }
+          atemp<-a[1,1:(aok*check2)]
+          atemp<-matrix(atemp,nrow=check2,byrow=TRUE)
+          cat("NOTE: Missing data resulted in the deletion of the following row(s) of: \n")
+          cat("      data from the analysis: \n")
+          if (ncol(atemp) > 2)
+          {prmatrix(atemp, rowlab=rep("    ",nrow(atemp)),collab=rep("    ",ncol(atemp)))}
+          if (allgood==0)
+          {
+            atemp<-a[1,1:(smallrow*largesti)]
+            atemp<-matrix(atemp,nrow=smallrow,byrow=TRUE)
+            btemp<-matrix(a[1,((largesti*smallrow)+1):conum])
+            prmatrix(atemp,rowlab=rep("    ",nrow(atemp)),collab=rep("    ",ncol(atemp)))
+            prmatrix(btemp,rowlab=rep("    ",1),collab=rep("    ",ncol(btemp)))
+          }
+        }
+        if (conum <= 12)
+        {
+          cat("NOTE: Missing data resulted in the deletion of the following row(s) of: \n")
+          cat("      data from the analysis: \n")
+          prmatrix(a, rowlab=rep("    ",nrow(a)), collab=rep("    ",ncol(a)))
+        }
+
+      }
+    }
+    if ((nmiss > 0) & (listmiss==0))
+    {cat(" \n")
+      cat("NOTE: Some cases with missing data were deleted. The number of deleted cases was: ")
+      write.table(nmiss,quote=FALSE,row.names=FALSE,col.names=FALSE)}
+  }
+
+  # print errors
+  for (i in c(1:100)) 
+  {
+    if (errcode[i,1]==1)
+    {cat(" \n")
+      cat("ERROR: You must specify a Y and an X variable. \n")}  
+    if (errcode[i,1]==2)
+    {cat(" \n")
+      cat("ERROR: X, M, or Y variable used more than once or W and Z are the same variable. \n")}  
+    if (errcode[i,1]==3)
+    {cat(" \n")
+      cat("ERROR: You have specified more than one variable for W, Y, X, or Z. \n")} 
+    if (errcode[i,1]==4)
+    {cat(" \n")
+      cat("ERROR: A variable specified as multicategorical has more than nine categories. \n")} 
+    if (errcode[i,1]==5)
+    {cat(" \n")
+      cat("ERROR: One of the categories contains only a single case. \n")} 
+    if (errcode[i,1]==6)
+    {cat(" \n")
+      cat("ERROR: Invalid model number in this version of PROCESS. \n")}  
+    if (errcode[i,1]==7)
+    {cat(" \n")
+      cat("ERROR: Invalid model number. \n")}  
+    if (errcode[i,1]==8)
+    {cat(" \n")
+      cat("ERROR: You must specify an M variable for this model. \n")} 
+    if (errcode[i,1]==9)
+    {cat(" \n")
+      cat("ERROR: You have specified an M variable in a model that does not use it. \n")}
+    if (errcode[i,1]==10)
+    {cat(" \n")
+      cat("ERROR: You have specified a W variable in a model that does not use it. \n")}
+    if (errcode[i,1]==11)
+    {cat(" \n")
+      cat("ERROR: You have not specified a W variable in a model that requires it. \n")}
+    if (errcode[i,1]==12)
+    {cat(" \n")
+      cat("ERROR: You have specified a Z variable in a model that does not use it. \n")}
+    if (errcode[i,1]==13)
+    {cat(" \n")
+      cat("ERROR: You have not specified a Z variable in a model that requires it. \n")}
+    if (errcode[i,1]==15)
+    {cat(" \n")
+      cat("ERROR: One of your model variables exhibits no variation (it is a constant). \n")}
+    if (errcode[i,1]==16)
+    {cat(" \n")
+      cat("ERROR: BMATRIX is not the correct length or is otherwise invalid. \n")}
+    if (errcode[i,1]==17)
+    {cat(" \n")
+      cat("ERROR: WMATRIX is not the correct length or is otherwise invalid. \n")}
+    if (errcode[i,1]==18)
+    {cat(" \n")
+      cat("ERROR: ZMATRIX is not the correct length or is otherwise invalid. \n")}
+    if (errcode[i,1]==19)
+    {cat(" \n")
+      cat("ERROR: WZMATRIX is not the correct length or is otherwise invalid. \n")}
+    if (errcode[i,1]==20)
+    {cat(" \n")
+      cat("ERROR: A path fixed at zero cannot be moderated. \n")}
+    if (errcode[i,1]==60)
+    {cat(" \n")
+      cat("PROCESS is now ready for use.\n")
+      cat("Copyright 2022 by Andrew F. Hayes ALL RIGHTS RESERVED\n")
+      cat("Workshop schedule at http://haskayne.ucalgary.ca/CCRAM\n \n")}
+    if (errcode[i,1]==21)
+    {cat(" \n")
+      cat("ERROR: If only one moderator is specified, it must be specified as W. \n")}
+    if (errcode[i,1]==22)
+    {cat(" \n")
+      cat("ERROR: In BMATRIX, X must be specified to affect at least one variable. \n")}
+    if (errcode[i,1]==23)
+    {cat(" \n")
+      cat("ERROR: In BMATRIX, at least one variable must be specified to affect Y. \n")}
+    if (errcode[i,1]==24)
+    {cat(" \n")
+      cat("ERROR: You must specify a model number or a custom BMATRIX specification. \n")}  
+    if (errcode[i,1]==25)
+    {cat(" \n")
+      cat("ERROR: BMATRIX cannot be used in conjunction with a model number. \n")}
+    if (errcode[i,1]==26)
+    {cat(" \n")
+      cat("ERROR: Your model has a dangling mediator (all Ms must affect and be affected). \n")}
+    if (errcode[i,1]==29)
+    {cat(" \n")
+      cat("ERROR: CMATRIX is not the correct length or is otherwise invalid. \n")}  
+    if (errcode[i,1]==30)
+    {cat(" \n")
+      cat("ERROR: In CMATRIX, all covariates must be assigned to an M or a Y. \n")}
+    if ((errcode[i,1]==31) & (singlr==0))
+    {cat(" \n")
+      singlr<-1
+      cat("ERROR: A linear or near linear dependence (singularity) exists in the data. \n")}
+    if (errcode[i,1]==32)
+    {cat(" \n")
+      cat("ERROR: Models 80 and 81 require between 3 and 6 mediators. \n")}  
+    if (errcode[i,1]==33)
+    {cat(" \n")
+      cat("ERROR: Model 82 requires 4 mediators. \n")} 
+    if (errcode[i,1]==34)
+    {cat(" \n")
+      cat("ERROR: This model number requires between 2 and 6 mediators. \n")} 
+    if (errcode[i,1]==35)
+    {cat(" \n")
+      cat("ERROR: In a model with only one moderator, that moderator must be W. \n")}
+    if (errcode[i,1]==36)
+    {cat(" \n")
+      cat("ERROR: A serial mediation model cannot have more than 6 mediators. \n")}  
+    if (errcode[i,1]==37)
+    {cat(" \n")
+      cat("ERROR: No more than 10 mediators are allowed in a PROCESS command. \n")} 
+    if (errcode[i,1]==38)
+    {cat(" \n")
+      cat("ERROR: XCATCODE is not provided, not the correct length, or is otherwise invalid. \n")} 
+    if (errcode[i,1]==39)
+    {cat(" \n")
+      cat("ERROR: WCATCODE is not provided, not the correct length, or is otherwise invalid. \n")} 
+    if (errcode[i,1]==40)
+    {cat(" \n")
+      cat("ERROR: ZCATCODE is not provided, not the correct length, or is otherwise invalid. \n")} 
+    if (errcode[i,1]==41)
+    {cat(" \n")
+      cat("ERROR: Models 1, 2, and 3 cannot be customized. \n")}
+    if (errcode[i,1]==43)
+    {cat(" \n")
+      cat("ERROR: PROCESS does not allow dichotomous mediators. \n")}
+    if (errcode[i,1]==50)
+    {cat(" \n")
+      cat("ERROR: A multicategorical moderator cannot be specified as a covariate. \n")} 
+    if (errcode[i,1]==51)
+    {cat(" \n")
+      cat("ERROR: A variable you specified as a covariate is a moderator in all equations. \n")} 
+    if (errcode[i,1]==62)
+    {cat(" \n")
+      cat("ERROR: After listwise deletion of cases with missing data, too few cases remain. \n")} 
+    if ((errcode[i,1]==52) & (mcerpt==0))
+    {mcerpt<-1
+    cat(" \n")
+    cat("ERROR: A variable specified as multicategorical must have at least three categories. \n")}
+    if (errcode[i,1]==53)
+    {cat(" \n")
+      cat("ERROR: Variables declared as factors are not accepted by PROCESS.\n")}  
+  }
+  #if (saveboot==1)
+  #{resultm<-list(resultm,boots)}
+  #invisible(resultm)
+  resultms<-NULL
+  if ((saveboot==0) & (saveest==1)){resultms<-resultm}
+  if ((saveboot==1) & (saveest==0)){resultms<-boots}
+  if ((saveboot==1) & (saveest==1)){resultms<-(list(boots,resultm))}
+  invisible(resultms)
+}
+
+```
+
+### Participants
+
+* 568 respondents, 13.57% had been in their referent job less than 6 months, 19.20% between 6 months and a year, 49.12% between one and five years, 13.27% between 5 and 10 years, and 4.87% more than 10 years.
+* Ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53).
+* Gender: female (52.58%) or male (46.83%). 
+* Job classifications: International Standard Classification of Occupations (ISCO) via the package `labourR` [@R-labourR], and further categorized into “knowledge” (n = 320) versus “skilled” (n = 214) occupations with knowledge workers being identified via ISCO classifications of: 1) professionals, and 2) managers.
+
+The data for this study were collected through Prolific sample,18 or older and holding a full-time or part-time job.
+Participants were asked to think about their primary job while answering the survey, and upon completion each participant was compensated in the amount of six US dollars.
+
+# Materials
+
+We used 98 statements taken directly from O$^{*}$Net’s “activity” and “context” classifications.
+Each of the 98 descriptors has potentially unique response categories, but scaling was consistently 1 (low) to 5 (high).
+Subsequent to these self-evaluations, respondents were asked to rate elements in terms of 1) …this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) …this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) …this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
 
@@
 
+We used PROCESS for R Version 4.1.1 [@hayes2022] to assess the extent to which the relationship between demands and stress are moderated by resources.
+
 # Results
 
-Maybe try hierarchical which 2 overaching factors with the "dimensions" under each).
+```{r analyses, fig.cap="Interaction between hindrances and resources as predictors of stress"}
 
-We are working on a factor analysis of the characteristics themselves. This is based on the larger number of items (97?) with an n of now 568.
+process(activate=1)
+process(data=data, y="stress", x="overall.hindrance", w="overall.resource", model=1, jn=1, plot=1)
 
-We tried different numbers of factors based on a scree plot suggesting we start at 8 factors.
-We printed only those loadings at .3 or higher to begin.
-Very few items loaded on more than 1 factor, and most loaded at .3+ on one factor.
-A few were negative.
-Need to think carefully about interpretation by exploring what the items themselves are.
+#Do resources moderate the relationship between hindrances and stress such 
+#that more total resources weaken the relationship between
+#hindrances and stress?
 
-Next - tried a 2 factor solution, wondering if items in the "context" and "activity" categories loaded as expected based on Onet categories.
-Again, most items loaded at .3+.
-The physical items generally loaded on factor 1.
+#Plot the interaction
+x<-c(1.6667, 2.2894, 3.2416, 1.6667, 2.2894, 3.2416, 1.6667, 2.2894, 3.2416)
+w<-c(3.2983, 3.2983, 3.2983, 3.7402, 3.7402, 3.7402, 4.2063, 4.2063,4.2063)
+y<-c(2.6985, 2.8237, 3.0151, 2.7039, 2.7763, 2.8871, 2.7096, 2.7264, 2.7520)
+wmarker<-c(15,15,15,16,16,16,17,17,17)
+#par(mar=c(1,1,1,1))
+plot(y=y,x=x,cex=1.2,pch=wmarker,xlab="Resources (W)",
+     ylab="Stress (Y)")
+legend.txt<-c("Low Resources","Medium Resources", "High Resources")
+legend("topleft", legend = legend.txt,cex=1,lty=c(1,3,6),lwd=c(2,3,2),
+       pch=c(15,16,17))
+lines(x[w==3.2983],y[w==3.2983],lwd=2,col="black")
+lines(x[w==3.7402],y[w==3.7402],lwd=3,lty=3,col="black")
+lines(x[w==4.2063],y[w==4.2063],lwd=2,lty=6,col="black")
 
-```{r scree plot}
-
-data <- read.csv("recodedforsiop.csv")[,-1] ## line 1562 of "study1.R" script
-
-data$Structural <-      rowMeans(data[19:31], na.rm=TRUE)
-data$Physical <-        rowMeans(data[c(32:60,62)], na.rm=TRUE)
-data$Interpersonal <-   rowMeans(data[63:76], na.rm=TRUE)
-data$Information.I <-   rowMeans(data[77:81], na.rm=TRUE)
-data$Mental.P <-        rowMeans(data[82:91], na.rm=TRUE)
-data$WorkOutput <-      rowMeans(data[92:100], na.rm=TRUE)
-data$Interact.Others <- rowMeans(data[101:117], na.rm=TRUE)
-
-library(psych)
-forfa <- cor(data[c(19:60,62:117)], use="pairwise.complete.obs")
-fa.parallel(forfa, n.obs=568)
 ```

### 2022-08-15 SIOP_Onet_FA.Rmd
Updated Results section and next steps.

@@
 ---
-title             : "O*Net Factor Analysis Project"
-shorttitle        : "SIOP_FA"
+title             : "JD-R Theory: Using the Content of the O*Net"
+shorttitle        : "SIOP_Hindrances-Resources Interaction"
 
@@
 
-Given the popularity of the Job Demands-Resources Theory [JD-R; @demerouti2001job] in exploring questions related to everything from motivation to job design, we aim to explore the intersection between *perceptions* of job demands and resources, and the broad set of job characteristics provided on O\*Net.
-This project makes three contributions.
-We aim to first explore whether ratings of of O\*Net item groupings align with the stated "resources" and "demands" presented in the job demands-resources theory.
-We then present evidence documenting whether O\*Net job and task descriptors are similarly rated as resources, challenge- or hindrance demands, and lastly, whether such ratings differ across job categories/classifications.
-Across two studies, a series of evaluations were made that used: 1) direct O\*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers.
+The Job Demands-Resources Theory [JD-R; @demerouti2001job] has received wide support across contexts and varied research questions.
+We contribute to this literature by exploring the interaction between *perceptions* of job demands and resources on stress using the broad set of job characteristics provided on O\*Net.
+
+A series of evaluations were made that used: direct O\*Net terminology (both descriptor and response option), and JD-R influenced ratings of demand and hindrance stressors.
 Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O\*Net is provided.
@@
 
-The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model [@demerouti2001job].
+The job demands-resources theory is an expansion of the well-studied job demands-resources model [@demerouti2001job].
 One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands.
@@
 
+#Results
+A moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1.
+First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, F(3, 564) = 3.29, p = .020.
+The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, F(3, 564) = 3.51, p = .061.
+As can be seen in Figure 1, those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources.
+Upon exploring the interaction further, it was evident that this moderated effect happened at lower, but not higher levels of resources.
+
+Next steps:
+1)	Make a prettier graph using ggplot. Note the percentiles that we graphed. 
+2)	Or, could generate Johnson-Neyman Technique – shows specifically the range of W values that are significant. See p. 272 for visual and r-script. 
+Table example on p. 286: includes variables, symbol, coeff, SE, t, p; below that, rsquared, MSE and f-string.
+
 # Discussion

### 2022-08-18 SIOP2023/SIOP_PROCESS.tex
moving to folders and renaming .Rmd

--- 2022-03-23 Submission.tex
@@
 \documentclass[
-  english,
   man]{apa6}
-\title{Job Demands-Resources model components through the lens of O*NET classifications}
-\author{Alicia Stachowski\textsuperscript{1}, Renata Garcia Prieto Palacios Roji\textsuperscript{2}, \& John Kulas\textsuperscript{2}}
-\date{}
-
 \usepackage{amsmath,amssymb}
@@
 \hypersetup{
-  pdftitle={Job Demands-Resources model components through the lens of O*NET classifications},
-  pdfauthor={Alicia Stachowski1, Renata Garcia Prieto Palacios Roji2, \& John Kulas2},
+  pdftitle={JD-R Theory: Using the Content of the O*Net},
+  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
   pdflang={en-EN},
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\ifLuaTeX
+\usepackage[bidi=basic]{babel}
+\else
+\usepackage[bidi=default]{babel}
+\fi
+\babelprovide[main,import]{english}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
 % Manuscript styling
@@
 \makeatother
-\shorttitle{O*NET JD-R}
+
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
 \keywords{keywords\newline\indent Word count: X}
@@
 \makeatother
+\usepackage{lineno}
+
+\linenumbers
 \usepackage{csquotes}
-\ifXeTeX
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
 \ifLuaTeX
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Wisconsin - Stout\\\textsuperscript{2} Montclair State University}
+\title{JD-R Theory: Using the Content of the O*Net}
+\author{First Author\textsuperscript{1} \& Ernst-August Doelle\textsuperscript{1,2}}
+\date{}
 
-\abstract{
-O*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource.
-All the results of this current study match the stress-appraisal stuff.
-Next steps: 1) discuss results within stress-appraisal framework (Lazarus \& Bookman), 2) different literature on challenge and hindrance demands.
-Job Demands Resources theory that says resources and demands are relatively universal is NOT consistent with these findings.
-JDR neglects the other 2 literatures.
-Analytically pull O*Net descriptors that reflect universal demands/resources (e.g., autonomy) and see how much variability there is on those.
-Maybe forget about cross-walk thing.
-May actually want to start with this: \url{https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit\#gid=1041061499}.
+\shorttitle{SIOP\_Hindrances-Resources Interaction}
 
-We want to also group items by O*NET categories so there's not so many (that makes ANOVAs more viable)
+\authornote{
+
+Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+
+Enter author note here.
+
+The authors made the following contributions. First Author: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Ernst-August Doelle: Writing - Review \& Editing.
+
+Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
+
 }
+
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}
 
@@
 
-Given the popularity of the Job Demands-Resources Theory {[}JD-R; Demerouti et al.
-(2001){]} in exploring questions related to everything from motivation to job design, we aim to explore the intersection between \emph{perceptions} of job demands and resources, and the broad set of job characteristics provided on O*Net.
-We aim to present evidence surrounding whether O*Net job and task descriptors are simiarly rated as resources, challenge- or hindrance demands, and whether such ratings differ across job catories/classifications.
-Across two studies, a series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers.
+The Job Demands-Resources Theory {[}JD-R; Demerouti et al.
+(2001){]} has received wide support across contexts and varied research questions.
+We contribute to this literature by exploring the interaction between \emph{perceptions} of job demands and resources on stress using the broad set of job characteristics provided on O*Net.
+
+A series of evaluations were made that used: direct O*Net terminology (both descriptor and response option), and JD-R influenced ratings of demand and hindrance stressors.
 Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O*Net is provided.
@@
 
-The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model (Demerouti et al., 2001).
+The job demands-resources theory is an expansion of the well-studied job demands-resources model (Demerouti et al., 2001).
 One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands.
@@
 In fact, there was a call to work with experienced I/O psychologists over the summer to update the content for the \href{https://www.onetonline.org/link/summary/19-3032.00}{Industrial and Organizational Psychologist listing on O*Net}.
-These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move for Veterans,'' ``My Next Move,'' Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
+These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move for Veterans'', ``My Next Move'', Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
 It is also useful to employers by providing them with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
 
-\hypertarget{study-1}{%
-\subsection{Study 1}\label{study-1}}
+Of greatest interest here are statements taken from O*NET \href{https://www.O*NETonline.org/find/descriptor/result/4.A.1.b.3}{``activity'' and ``context'' classifications} (e.g., items related to information input, interacting with others, physical work conditions, structural job characteristics).
+One of the first and basic questions is whether or not the categorical examples of ``resources'' and ``demands'' described in the Job Demands-Resources Theory (Demerouti et al., 2001), for example, are generally deemed resources or demands as we objectively define them.
+The next logical question surrounds how ``universal'' such ratings are.
+For instance, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.
+A second study extends the findings from Study 1 to a potentially key moderator - job categories/classifications, examining whether ratings of resources, challenge- and hindrance demands differ by job classification.
 
-Look at the \href{https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit\#gid=1041061499}{google sheet} and document the extent to which job characteristics that have been consistently cited in the literature as demands or resources end up being consistently or variably experienced as demands or resources.
-Study 1 aims to provide an integration of the theory and practical occupations-focused data on O*Net.
-Several broad research questions are examined across jobs:
-
-\begin{quote}
-\emph{Research Question 1}: Which O*Net job characteristics are consistently rated as job resources?
-\end{quote}
-
-\begin{quote}
-\emph{Research Question 2}: Which O*Net job characteristics are consistently rated as challenge demands?
-\end{quote}
-
-\begin{quote}
-\emph{Research Question 3}: Which O*Net job characteristics are consistently rated as hinderance demands?
-\end{quote}
-
-\hypertarget{study-2}{%
-\subsection{Study 2}\label{study-2}}
-
-While Study 1 explored the above questions across jobs, Study 2 considers a potentially important moderator: job classification.
-There is a distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework depending on \emph{job classification}.
-In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., (A.
-B.
-Bakker \& Sanz-Vergel, 2013); (Cavanaugh et al., 2000); (Gerich, 2017); (Podsakoff et al., 2007); (Webster et al., 2011)).
-Thus, Study 2 focuses on a fourth question of interest.
-
-\begin{quote}
-\emph{Research Question 4}: Does the \textbf{type of work} reported explain variability in the categorization of work characteristics into challenges, hindrances, and resources?
-\end{quote}
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
 
@@
 
-Of the 785 Prolific panel individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (\textbf{R-careless?}).
-Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current SIOP sample.
-13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.
+There were 568 respondents.
 
+\hypertarget{participants-1}{%
+\subsubsection{Participants}\label{participants-1}}
+
+\begin{itemize}
+\tightlist
+\item
+  568 respondents, 13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.
+\item
   Ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53).
-The survey offered a free-field gender identity category, although the sample predominantly self-identified as female (52.58\%) or male (46.83\%).
+\item
+  Gender: female (52.58\%) or male (46.83\%).
+\item
+  Job classifications: International Standard Classification of Occupations (ISCO) via the package \texttt{labourR} (\textbf{R-labourR?}), and further categorized into ``knowledge'' (n = 320) versus ``skilled'' (n = 214) occupations with knowledge workers being identified via ISCO classifications of: 1) professionals, and 2) managers.
+\end{itemize}
+
+The data for this study were collected through Prolific sample,18 or older and holding a full-time or part-time job.
+Participants were asked to think about their primary job while answering the survey, and upon completion each participant was compensated in the amount of six US dollars.
 
 \hypertarget{materials}{%
-\subsection{Materials}\label{materials}}
+\section{Materials}\label{materials}}
 
-Each free-field job title was placed into one of 14 possible O*NET job families classifications.
-60 of these ratings were performed by all 3 author raters, with a resulting Kappa of 0.53 (Landis \& Koch, 1977).
-We then further collapsed these 14 categories into 8 essentially equal frequency job categories.
+We used 98 statements taken directly from O\(^{*}\)Net's ``activity'' and ``context'' classifications.
+Each of the 98 descriptors has potentially unique response categories, but scaling was consistently 1 (low) to 5 (high).
+Subsequent to these self-evaluations, respondents were asked to rate elements in terms of 1) \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
 
-\hypertarget{characteristics-demands-and-resources}{%
-\subsubsection{Characteristics, Demands, and Resources}\label{characteristics-demands-and-resources}}
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
 
-We used 98 statements taken from O*NET \href{https://www.O*NETonline.org/find/descriptor/result/4.A.1.b.3}{``activity'' and ``context'' classifications}.
-We retained 41 ``work activity'' classifications which O*NET groups into categories of ``Information Input'' (5 statements), ``Interacting with Others'' (17 statements), ``Mental Processes'' (10 statements) and ``Work Output'' (9 statements).
-57 ``work context'' statements grouped into ``Interpersonal Relationships'' (14 statements), ``Physical Work Conditions'' (30 statements), and ``Structural Job Characteristics'' (13 statements).
-
-These ``descriptors'' often have unique response categories (\href{https://www.O*NETonline.org/find/descriptor/result/4.C.1.c.2}{see here for example}).
-We retained the O*NET wording to capture characteristics of relevance for each respondent.
-Subsequent to these self evaluations, each respondent who agreed that the element had \emph{at least some relevance} to their job was also asked to rate that element in terms of, 1) \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) \ldots this aspect of your job is a hinderance that can inhibit personal growth, learning, and work goal attainment.
+We used PROCESS for R Version 4.1.1 (Hayes, 2022) to assess the extent to which the relationship between demands and stress are moderated by resources.
 
@@
 
-\hypertarget{low-variability-demands-and-resources}{%
-\subsection{Low Variability Demands and Resources}\label{low-variability-demands-and-resources}}
+\begin{verbatim}
+## 
+## ********************* PROCESS for R Version 4.1.1 ********************* 
+##  
+##            Written by Andrew F. Hayes, Ph.D.  www.afhayes.com              
+##    Documentation available in Hayes (2022). www.guilford.com/p/hayes3   
+##  
+## *********************************************************************** 
+##  
+## PROCESS is now ready for use.
+## Copyright 2022 by Andrew F. Hayes ALL RIGHTS RESERVED
+## Workshop schedule at http://haskayne.ucalgary.ca/CCRAM
+## 
+\end{verbatim}
 
-The below graphs present the resources, challenges, and hindrances that are \emph{largely agreed on} as indexed by (relatively) low standard deviations.
+\begin{verbatim}
+## 
+## ********************* PROCESS for R Version 4.1.1 ********************* 
+##  
+##            Written by Andrew F. Hayes, Ph.D.  www.afhayes.com              
+##    Documentation available in Hayes (2022). www.guilford.com/p/hayes3   
+##  
+## *********************************************************************** 
+##                          
+## Model : 1                
+##     Y : stress           
+##     X : overall.hindrance
+##     W : overall.resource 
+## 
+## Sample size: 568
+## 
+## 
+## *********************************************************************** 
+## Outcome Variable: stress
+## 
+## Model Summary: 
+##           R      R-sq       MSE         F       df1       df2         p
+##      0.1311    0.0172    0.7790    3.2876    3.0000  564.0000    0.0205
+## 
+## Model: 
+##                       coeff        se         t         p      LLCI      ULCI
+## constant             1.2688    1.0055    1.2618    0.2075   -0.7063    3.2439
+## overall.hindrance    0.8336    0.4031    2.0677    0.0391    0.0417    1.6254
+## overall.resource     0.3319    0.2518    1.3181    0.1880   -0.1627    0.8264
+## Int_1               -0.1918    0.1024   -1.8725    0.0616   -0.3929    0.0094
+## 
+## Product terms key:
+## Int_1  :  overall.hindrance  x  overall.resource      
+## 
+## Test(s) of highest order unconditional interaction(s):
+##       R2-chng         F       df1       df2         p
+## X*W    0.0061    3.5064    1.0000  564.0000    0.0616
+## ----------
+## Focal predictor: overall.hindrance (X)
+##       Moderator: overall.resource (W)
+## 
+## Conditional effects of the focal predictor at values of the moderator(s):
+##   overall.resource    effect        se         t         p      LLCI      ULCI
+##             3.2983    0.2010    0.0802    2.5065    0.0125    0.0435    0.3586
+##             3.7402    0.1163    0.0534    2.1759    0.0300    0.0113    0.2213
+##             4.2063    0.0269    0.0594    0.4535    0.6503   -0.0897    0.1435
+## 
+## Moderator value(s) defining Johnson-Neyman significance region(s):
+##       Value   % below   % above
+##      3.8196   55.6338   44.3662
+## 
+## Conditional effect of focal predictor at values of the moderator:
+##   overall.resource    effect        se         t         p      LLCI      ULCI
+##             1.0149    0.6389    0.3003    2.1276    0.0338    0.0491    1.2288
+##             1.2078    0.6020    0.2809    2.1433    0.0325    0.0503    1.1536
+##             1.4006    0.5650    0.2615    2.1608    0.0311    0.0514    1.0785
+##             1.5935    0.5280    0.2421    2.1807    0.0296    0.0524    1.0035
+##             1.7863    0.4910    0.2228    2.2034    0.0280    0.0533    0.9287
+##             1.9791    0.4540    0.2037    2.2293    0.0262    0.0540    0.8540
+##             2.1720    0.4170    0.1846    2.2592    0.0243    0.0545    0.7796
+##             2.3648    0.3801    0.1657    2.2937    0.0222    0.0546    0.7055
+##             2.5577    0.3431    0.1470    2.3336    0.0200    0.0543    0.6318
+##             2.7505    0.3061    0.1287    2.3791    0.0177    0.0534    0.5588
+##             2.9434    0.2691    0.1108    2.4292    0.0154    0.0515    0.4867
+##             3.1362    0.2321    0.0937    2.4784    0.0135    0.0482    0.4161
+##             3.3290    0.1951    0.0778    2.5085    0.0124    0.0423    0.3479
+##             3.5219    0.1582    0.0641    2.4667    0.0139    0.0322    0.2841
+##             3.7147    0.1212    0.0543    2.2306    0.0261    0.0145    0.2279
+##             3.8196    0.1011    0.0515    1.9642    0.0500    0.0000    0.2021
+##             3.9076    0.0842    0.0507    1.6605    0.0974   -0.0154    0.1838
+##             4.1004    0.0472    0.0545    0.8662    0.3867   -0.0599    0.1543
+##             4.2933    0.0102    0.0644    0.1589    0.8738   -0.1163    0.1368
+##             4.4861   -0.0267    0.0782   -0.3421    0.7324   -0.1803    0.1268
+##             4.6790   -0.0637    0.0941   -0.6773    0.4985   -0.2485    0.1211
+##             4.8718   -0.1007    0.1112   -0.9054    0.3656   -0.3192    0.1178
+## 
+## Data for visualizing the conditional effect of the focal predictor:
+##   overall.hindrance overall.resource    stress
+##              1.6667           3.2983    2.6985
+##              2.2894           3.2983    2.8237
+##              3.2416           3.2983    3.0151
+##              1.6667           3.7402    2.7039
+##              2.2894           3.7402    2.7763
+##              3.2416           3.7402    2.8871
+##              1.6667           4.2063    2.7096
+##              2.2894           4.2063    2.7264
+##              3.2416           4.2063    2.7520
+## 
+## ******************** ANALYSIS NOTES AND ERRORS ************************ 
+## 
+## Level of confidence for all confidence intervals in output: 95
+## 
+## W values in conditional tables are the 16th, 50th, and 84th percentiles.
+\end{verbatim}
 
-\begin{quote}
-Note. The ``zero'' standard deviations are likely one person, \emph{n}'s should also go on these graphs if they're retained.
-\end{quote}
+\begin{figure}
+\centering
+\includegraphics{SIOP_PROCESS_files/figure-latex/analyses-1.pdf}
+\caption{\label{fig:analyses}Interaction between hindrances and resources as predictors of stress}
+\end{figure}
 
-\includegraphics{Submission_files/figure-latex/resourceslowsd-1.pdf}
+\#Results
+A moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1.
+First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, F(3, 564) = 3.29, p = .020.
+The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, F(3, 564) = 3.51, p = .061.
+As can be seen in Figure 1, those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources.
+Upon exploring the interaction further, it was evident that this moderated effect happened at lower, but not higher levels of resources.
 
-\includegraphics{Submission_files/figure-latex/challengesagree-1.pdf}
+Next steps:
+1) Make a prettier graph using ggplot. Note the percentiles that we graphed.
+2) Or, could generate Johnson-Neyman Technique -- shows specifically the range of W values that are significant. See p.~272 for visual and r-script.
+Table example on p.~286: includes variables, symbol, coeff, SE, t, p; below that, rsquared, MSE and f-string.
 
-\includegraphics{Submission_files/figure-latex/hindrancesagree-1.pdf}
-
-As can be seen by the graphs, there is considerable disagreement regarding the degree to which job elements are considered \emph{hindrances}, with the 10 elements showing the greatest agreement still ranging in standard deviations from 0 to 1.18.
-What is widely seen as a resource and challenge tends to be more universally agreed upon (range of lowest 10 resource standard deviations is 0 to 0.88 and the range of lowest 10 challenge standard deviations is 0 to 0.87.
-
-\hypertarget{high-variability-demands-and-resources}{%
-\subsection{High Variability Demands and Resources}\label{high-variability-demands-and-resources}}
-
-The below graphs present the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations (these are the 10 characteristics with the greatest variability in rating).
-
-\includegraphics{Submission_files/figure-latex/resourceshisd-1.pdf}
-
-\includegraphics{Submission_files/figure-latex/challengeshighsd-1.pdf}
-
-\includegraphics{Submission_files/figure-latex/hindranceshighsd-1.pdf}
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
-Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
-
 \leavevmode\vadjust pre{\hypertarget{ref-bakker2003dual}{}}%
@@
 \emph{European Journal of Work and Organizational Psychology}, \emph{12}(4), 393--417.
-
-\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
-Cavanaugh, M.
-A., Boswell, W.
-R., Roehling, M.
-V., \& Boudreau, J.
-W.
-(2000).
-An empirical examination of self-reported work stress among US managers.
-\emph{Journal of Applied Psychology}, \emph{85}(1), 65.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
-Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
-
-\leavevmode\vadjust pre{\hypertarget{ref-landis1977measurement}{}}%
-Landis, J. R., \& Koch, G. G. (1977). The measurement of observer agreement for categorical data. \emph{Biometrics}, 159--174.
+\leavevmode\vadjust pre{\hypertarget{ref-hayes2022}{}}%
+Hayes, A. F. (2022). \emph{Introduction to mediation, moderation, and conditional process analysis: A regression-based approach} (3rd ed.). The Guilford Press.
 
@@
 \emph{Personnel Psychology}, \emph{54}(2), 451--492.
-
-\leavevmode\vadjust pre{\hypertarget{ref-podsakoff2007differential}{}}%
-Podsakoff, N.
-P., LePine, J.
-A., \& LePine, M.
-A.
-(2007).
-Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis.
-\emph{Journal of Applied Psychology}, \emph{92}(2), 438.
 

### 2022-08-18 SIOP2023/SIOP_PROCESS.Rmd
moving to folders and renaming .Rmd
sourcing process macro as separate script and results table

--- 2022-07-21 SIOP_Onet_FA.Rmd
@@
 
-bibliography      : ["r-references.bib"]
+bibliography      : ["r-references.bib", "SIOP_PROCESS.bib", "jdr.bib", "jobdemands_resources_bibtex.bib"]
 
@@
 
+The Job Demands-Resources Theory [JD-R; @demerouti2001job] has received wide support across contexts and varied research questions.
+We contribute to this literature by exploring the interaction between *perceptions* of job demands and resources on stress using the broad set of job characteristics provided on O\*Net.
+
+A series of evaluations were made that used: direct O\*Net terminology (both descriptor and response option), and JD-R influenced ratings of demand and hindrance stressors.
+Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O\*Net is provided.
+
+## The Job demands-Resources Theory
+
+The job demands-resources theory is an expansion of the well-studied job demands-resources model [@demerouti2001job].
+One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands.
+*Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
+In contrast, *demands* include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; @demerouti2001job).
+Cognitively, the perception of an element of ones job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation [resulting from resources; @bakker2014job].
+Pertinent to the current study, demanding job characteristics are frequently associated with negative outcomes [e.g., @bakker2003dual], whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job].
+
+## Objective vs. Subjective Nature of Demands and Resources: The Role of Appraisal
+
+@searle2015merits note that the majority of the research on workplace demands is based on apriori classifications of demands.
+However, the stress experience, or process, described early on by @lazarus1984stress is grounded in the assumption that individual appraisals of stressors/demands vary.
+Their transactional theory of stress and coping states that people continuously appraise stimuli in their environments.
+An appraisal is the cognitive process whereby meaning is assigned to a stimulus.
+If a stimulus is appraised as a stressor (threat, challenge, potentially harmful), emotional distress leads to coping of some kind.
+This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes is not appraised as favorable [@lazarus1984stress].
+The stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.
+
+We next consider the (limited) empirical evidence on this topic.
+First, some relatively recent research suggests that job demands and resources may not be universally appraised or assigned as such.
+Starting with job demands, @webster2011extending, for example, studied workload, role ambiguity, and role conflict demands, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees.
+While their study did include resources, it nonetheless points to individual differences on how people perceive stressors at work.
+Although part of a much larger study on retirement, @sonnega_comparison_2018 compared self-reported (subjective) ratings of degree of physical demand, stress, and need for intense concentration from the Health and Retirement Study with objective ratings from O*Net.
+Correlations physical demand (r = .52), stress (r = .10), and need for intense concentration (r = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than assumed.
+Next considering resources, @schmitz_interpreting_2019 also captured subjective and objective resources in their study of retirement.
+Correlations of composite variables for the resources of autonomy (r = .12.
+p > .01), recognition of work (r = .07, p > .01), and decision freedom (r = .08, p > .01), while significant, certainly do not reflect high levels of overlap.
+
+We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees.
+@downes2021incorporating meta-analysis addresses this reality in depth, although it is beyond the scope of this project.
+
+## O\*Net Resource
+
+Originally, the Advisory Panel for the Dictionary of Occupational Titles recommended a system that would “…promote the effective education, training, counseling, and employment of the American workforce.
+It should accomplish its purpose by providing a database system that identifies, defines, classifies, and describes occupations in the economy in an accessible and flexible manner” (@advisory1993new, p.
+6).
+The result was the now commonly used O\*NET.
+The Occupational Information Network (O\*NET; onetonline.org) contains a comprehensive description of occupations [@peterson2001understanding].
+This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated.
+In fact, there was a call to work with experienced I/O psychologists over the summer to update the content for the [Industrial and Organizational Psychologist listing on O\*Net](https://www.onetonline.org/link/summary/19-3032.00).
+These data, and the tools provided for free on the website (e.g., Career Exploration Tools, “My Next Move for Veterans”, “My Next Move”, Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
+It is also useful to employers by providing them with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
+
+Of greatest interest here are statements taken from O\*NET ["activity" and "context" classifications](https://www.O\*NETonline.org/find/descriptor/result/4.A.1.b.3) (e.g., items related to information input, interacting with others, physical work conditions, structural job characteristics).
+One of the first and basic questions is whether or not the categorical examples of "resources" and "demands" described in the Job Demands-Resources Theory [@demerouti2001job], for example, are generally deemed resources or demands as we objectively define them.
+The next logical question surrounds how "universal" such ratings are.
+For instance, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.
+A second study extends the findings from Study 1 to a potentially key moderator - job categories/classifications, examining whether ratings of resources, challenge- and hindrance demands differ by job classification.
+
 # Methods
@@
 
-## Material
+```{r getdata}
+
+data <- read.csv("SIOPcleaned.csv")      ## from "datacleaning.R" script
+
+## O*NET categories
+
+data$onet.resource.ii <- rowMeans(data[c(162:166)], na.rm=TRUE)
+data$onet.resource.mp <- rowMeans(data[c(167:176)], na.rm=TRUE)
+data$onet.resource.wo <- rowMeans(data[c(177:185)], na.rm=TRUE)
+data$onet.resource.io <- rowMeans(data[c(186:202)], na.rm=TRUE)
+data$onet.resource.ir <- rowMeans(data[c(149:161)], na.rm=TRUE)
+data$onet.resource.pc <- rowMeans(data[c(128:144,146:148)], na.rm=TRUE)
+data$onet.resource.sc <- rowMeans(data[c(118:127)], na.rm=TRUE)
+
+data$overall.resource <- rowMeans(data[c(118:144,147:202)], na.rm=TRUE)
+
+data$onet.hindrance.ii <- rowMeans(data[c(246:247,249:252)], na.rm=TRUE)
+data$onet.hindrance.mp <- rowMeans(data[c(252:261)], na.rm=TRUE)
+data$onet.hindrance.wo <- rowMeans(data[c(262:270)], na.rm=TRUE)
+data$onet.hindrance.io <- rowMeans(data[c(271:287)], na.rm=TRUE)
+data$onet.hindrance.ir <- rowMeans(data[c(233:245)], na.rm=TRUE)
+data$onet.hindrance.pc <- rowMeans(data[c(213:232)], na.rm=TRUE)
+data$onet.hindrance.sc <- rowMeans(data[c(203:212)], na.rm=TRUE)
+
+data$overall.hindrance <- rowMeans(data[c(203:247,249:287)], na.rm=TRUE)
+
+data$onet.challenge.ii <- rowMeans(data[c(332:336)], na.rm=TRUE)
+data$onet.challenge.mp <- rowMeans(data[c(337:346)], na.rm=TRUE)
+data$onet.challenge.wo <- rowMeans(data[c(347:355)], na.rm=TRUE)
+data$onet.challenge.io <- rowMeans(data[c(356:372)], na.rm=TRUE)
+data$onet.challenge.ir <- rowMeans(data[c(319:331)], na.rm=TRUE)
+data$onet.challenge.pc <- rowMeans(data[c(298:307,309:318)], na.rm=TRUE)
+data$onet.challenge.sc <- rowMeans(data[c(288:297)], na.rm=TRUE)
+
+data$overall.challenge <- rowMeans(data[c(288:307,309:372)], na.rm=TRUE)
+
+data$burnout      <- rowMeans(data[c(373:376)], na.rm=TRUE)
+data$stress       <- rowMeans(data[c(377:379)], na.rm=TRUE)
+data$engagement   <- rowMeans(data[c(380:399)], na.rm=TRUE)        ## added 10/12 because analyses too wonky with 3 subscales
+
+```
+
+There were `r nrow(data)` respondents.
+
+```{r PROCESS, include=FALSE}
+
+source("process.R", local = knitr::knit_global())
+
+```
+
+### Participants
+
+* 568 respondents, 13.57% had been in their referent job less than 6 months, 19.20% between 6 months and a year, 49.12% between one and five years, 13.27% between 5 and 10 years, and 4.87% more than 10 years.
+* Ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53).
+* Gender: female (52.58%) or male (46.83%). 
+* Job classifications: International Standard Classification of Occupations (ISCO) via the package `labourR` [@R-labourR], and further categorized into “knowledge” (n = 320) versus “skilled” (n = 214) occupations with knowledge workers being identified via ISCO classifications of: 1) professionals, and 2) managers.
+
+The data for this study were collected through Prolific sample,18 or older and holding a full-time or part-time job.
+Participants were asked to think about their primary job while answering the survey, and upon completion each participant was compensated in the amount of six US dollars.
+
+# Materials
+
+We used 98 statements taken directly from O$^{*}$Net’s “activity” and “context” classifications.
+Each of the 98 descriptors has potentially unique response categories, but scaling was consistently 1 (low) to 5 (high).
+Subsequent to these self-evaluations, respondents were asked to rate elements in terms of 1) …this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) …this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) …this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
 
@@
 
+We used PROCESS for R Version 4.1.1 [@hayes2022] to assess the extent to which the relationship between demands and stress are moderated by resources.
+
 # Results
 
-Maybe try hierarchical which 2 overaching factors with the "dimensions" under each).
+```{r analyses, fig.cap="Interaction between hindrances and resources as predictors of stress"}
 
-We are working on a factor analysis of the characteristics themselves. This is based on the larger number of items (97?) with an n of now 568.
+process(activate=1)
+results <- process(data=data, y="stress", x="overall.hindrance", w="overall.resource", model=1, jn=1, plot=1, save=2)
 
-We tried different numbers of factors based on a scree plot suggesting we start at 8 factors.
-We printed only those loadings at .3 or higher to begin.
-Very few items loaded on more than 1 factor, and most loaded at .3+ on one factor.
-A few were negative.
-Need to think carefully about interpretation by exploring what the items themselves are.
+#Do resources moderate the relationship between hindrances and stress such 
+#that more total resources weaken the relationship between
+#hindrances and stress?
 
-Next - tried a 2 factor solution, wondering if items in the "context" and "activity" categories loaded as expected based on Onet categories.
-Again, most items loaded at .3+.
-The physical items generally loaded on factor 1.
+#Plot the interaction
+x<-c(1.6667, 2.2894, 3.2416, 1.6667, 2.2894, 3.2416, 1.6667, 2.2894, 3.2416)
+w<-c(3.2983, 3.2983, 3.2983, 3.7402, 3.7402, 3.7402, 4.2063, 4.2063,4.2063)
+y<-c(2.6985, 2.8237, 3.0151, 2.7039, 2.7763, 2.8871, 2.7096, 2.7264, 2.7520)
+wmarker<-c(15,15,15,16,16,16,17,17,17)
+#par(mar=c(1,1,1,1))
+plot(y=y,x=x,cex=1.2,pch=wmarker,xlab="Resources (W)",
+     ylab="Stress (Y)")
+legend.txt<-c("Low Resources","Medium Resources", "High Resources")
+legend("topleft", legend = legend.txt,cex=1,lty=c(1,3,6),lwd=c(2,3,2),
+       pch=c(15,16,17))
+lines(x[w==3.2983],y[w==3.2983],lwd=2,col="black")
+lines(x[w==3.7402],y[w==3.7402],lwd=3,lty=3,col="black")
+lines(x[w==4.2063],y[w==4.2063],lwd=2,lty=6,col="black")
 
-```{r scree plot}
-
-data <- read.csv("recodedforsiop.csv")[,-1] ## line 1562 of "study1.R" script
-
-data$Structural <-      rowMeans(data[19:31], na.rm=TRUE)
-data$Physical <-        rowMeans(data[c(32:60,62)], na.rm=TRUE)
-data$Interpersonal <-   rowMeans(data[63:76], na.rm=TRUE)
-data$Information.I <-   rowMeans(data[77:81], na.rm=TRUE)
-data$Mental.P <-        rowMeans(data[82:91], na.rm=TRUE)
-data$WorkOutput <-      rowMeans(data[92:100], na.rm=TRUE)
-data$Interact.Others <- rowMeans(data[101:117], na.rm=TRUE)
-
-library(psych)
-forfa <- cor(data[c(19:60,62:117)], use="pairwise.complete.obs")
-fa.parallel(forfa, n.obs=568)
 ```
 
-```{r eight_factorFA}
-##Here's where we started - it appears that based on scree plot, 8 factors might be appropriate.
-efa <- fa(data[c(19:60,62:117)], rotate="oblimin", nfactors=8, n.obs=568, scores=TRUE, alpha=.1) ## changed to data so can get factor scores
-summary(efa)
+#Results
 
-together <- cbind(data, efa$scores)
+A moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1.
+First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, F(3, 564) = 3.29, p = .020.
+The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, F(3, 564) = 3.51, p = .061.
+As can be seen in Figure 1, those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources.
+Upon exploring the interaction further, it was evident that this moderated effect happened at lower, but not higher levels of resources.
 
-#res.cor <- correlate(together[c(405:413)], use="pairwise.complete.obs")
-#res.cor %>% fashion()
-#res.cor %>% shave(upper=FALSE) %>% rplot()
+```{r table}
 
-efa$loadings
-print(efa$loadings,cut=.3,digits=2)
+Component <- c("Constant", "Hindrance (X)", "Resource (W)", "Hindrance x Resource")
+coeff <- round(results[c(2:5),1],2)
+SE    <- round(results[c(2:5),2],2)
+t     <- round(results[c(2:5),3],2)
+p     <- round(results[c(2:5),4],2)
+
+table <- as.data.frame(cbind(Component, coeff, SE, t, p))
+
+papaja::apa_table(table,
+                  caption = "Results from a regression analysis examining the moderation of resources on the relationship between hindrance demands and stress",
+                  note = "R^2 etc here",
+                  landscape = FALSE,
+                  escape = TRUE)
+
 ```
 
-```{r two_factorFA}
-##Next, trying the 2 overarching factors we noted first:
-efa <- fa(forfa, rotate="oblimin", nfactors=2, n.obs=568, scores=TRUE, alpha=.1)
-summary(efa)
+Next steps:
+1)	Make a prettier graph using ggplot. Note the percentiles that we graphed. 
+2)	Or, could generate Johnson-Neyman Technique – shows specifically the range of W values that are significant. See p. 272 for visual and r-script. 
+Table example on p. 286: includes variables, symbol, coeff, SE, t, p; below that, rsquared, MSE and f-string.
 
-efa$loadings
-print(efa$loadings,cut=.3,digits=2)
-```
-
-```{r seven_factorFA}
-## Try 7 factor solution next. 
-efa <- fa(forfa, rotate="oblimin", nfactors=7, n.obs=568, scores=TRUE, alpha=.1)
-summary(efa)
-
-efa$loadings
-print(efa$loadings,cut=.3,digits=2)
-```
-
-```{r nine_factorFA}
-## Try 9 factor solution next. 
-efa <- fa(forfa, rotate="oblimin", nfactors=9, n.obs=568, scores=TRUE, alpha=.1)
-summary(efa)
-
-efa$loadings
-print(efa$loadings,cut=.3,digits=2)
-```
 # Discussion

### 2022-08-18 SIOP2023/SIOP_PROCESS.tex
sourcing process macro as separate script and results table

@@
 \#Results
+
 A moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1.
@@
 Upon exploring the interaction further, it was evident that this moderated effect happened at lower, but not higher levels of resources.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:table}Results from a regression analysis examining the moderation of resources on the relationship between hindrance demands and stress}
+
+\begin{tabular}{lllll}
+\toprule
+Component & \multicolumn{1}{c}{coeff} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{t} & \multicolumn{1}{c}{p}\\
+\midrule
+Constant & 1.27 & 1.01 & 1.26 & 0.21\\
+Hindrance (X) & 0.83 & 0.4 & 2.07 & 0.04\\
+Resource (W) & 0.33 & 0.25 & 1.32 & 0.19\\
+Hindrance x Resource & -0.19 & 0.1 & -1.87 & 0.06\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} R\textasciicircum{}2 etc here}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
 

### 2022-08-18 SIOP2023/SIOP.R

@@ -1,41 +1,0 @@
-## Looking at DV associations across tenure and maybe gender (possible SIOP submission)
-
-
-temp <- read.csv("initial_data_screen.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script
-
-x <- paste("item", sep="",1:404)
-y <- t(temp[2,])
-## decluttering Qualtrics excess
-data <- temp[-c(1:3),]                                           ## Getting rid of all 3 weird Qualtrics rows
-colnames(data) <- x
-
-incomplete <- read.csv("inprogress.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script
-
-data2 <- incomplete[-c(1:2),-c(10,12,16,113,199,285,371,379,400, 406:411)]                                          
-
-data3 <- as.data.frame(cbind(data2$V8,data2$V9,data2$V1,data2$V1,data2$V1,data2$V1,data2$V1,data2$V1,data2))
-
-colnames(data3) <- x
-
-rm(x, y, temp)       
-
-use <- rbind(data,data3)
-
-## STILL NEED FILE WITH BAD RESPONDENTS IDENTIFIED (E.G., Item_18=2, na > 200, longstring > 20, CARELESS CHECKS > 1)
-
-library(careless)
-use$careless_long <- longstring(use[18:399])
-use$missing <- rowSums(is.na(use[18:404])) 
-
-different <- use[ which(use$item18 == 2 | use$careless_long > 20 | use$missing > 200), ]
-
-attention <- use[which(use$item61 == 5 & use$item145 == 5 & use$item248 == 2 & use$item308 == 3), ]
-
-data <- data.frame(lapply(attention, function(x) as.numeric(as.character(x))))
-data <- data[,c(1:404)]
-
-numtot <- nrow(use)
-numkicked <- nrow(different)
-numvalid <- nrow(data)
-
-

### 2022-08-18 SIOP2023/SIOP_PROCESS.Rmd
Updated Introduction

@@
 The Job Demands-Resources Theory [JD-R; @demerouti2001job] has received wide support across contexts and varied research questions.
-We contribute to this literature by exploring the interaction between *perceptions* of job demands and resources on stress using the broad set of job characteristics provided on O\*Net.
+We add to this literature via two routes: by utilizing some of the job characteristics in the popular O\*Net, and by focusing on perceptions of all characteristics as demands/resources.
+Specifically, we explore the interaction between perceptions of job demands and resources on the outcome of stress across a wide range of occupations.
 
-A series of evaluations were made that used: direct O\*Net terminology (both descriptor and response option), and JD-R influenced ratings of demand and hindrance stressors.
-Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O\*Net is provided.
+Here, respondents made a series of evaluations that used: direct O\*Net terminology (both descriptor and response option), and JD-R influenced ratings of demand and hindrance stressors.
+Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O\*Net, is provided.
 
@@
 The job demands-resources theory is an expansion of the well-studied job demands-resources model [@demerouti2001job].
-One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands.
-*Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
-In contrast, *demands* include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; @demerouti2001job).
-Cognitively, the perception of an element of ones job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation [resulting from resources; @bakker2014job].
-Pertinent to the current study, demanding job characteristics are frequently associated with negative outcomes [e.g., @bakker2003dual], whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job].
+One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands, which are thoroughly documented by job in O\*Net.
+*Resources* are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
+*Demands*, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure; @demerouti2001job).
+Cognitively, the perception of an element of one's job as a resource or demand activates one of two unique processes: health impairment (resulting from demands) or motivation [resulting from resources; @bakker2014job].
+Demanding job characteristics are frequently associated with negative outcomes [e.g., @bakker2003dual], whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job].
+Our focus is on whether or not having more resources serves as a buffer to the demand-stress relationship.
+One of the stickier elements of this question surrounds the subjective nature of demands/resources, which we address next.
 
@@
 
-@searle2015merits note that the majority of the research on workplace demands is based on apriori classifications of demands.
+@searle2015merits note that much of our research on workplace demands is based on apriori classifications of demands.
 However, the stress experience, or process, described early on by @lazarus1984stress is grounded in the assumption that individual appraisals of stressors/demands vary.
@@
 p > .01), recognition of work (r = .07, p > .01), and decision freedom (r = .08, p > .01), while significant, certainly do not reflect high levels of overlap.
-
 We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees.
@@
 
-## O\*Net Resource
+Thus, while it is cleaner to be able to categorize job characteristics as *either* a demand or a resource, the above research suggests that individual appraisal is an important consideration.
+It is quite possible that one person experiences high work pressure (commonly cited as a demand in the literature) as a hindrance stressor and thus experiences strain, and another thrives in a fast-paced pressured role and would thus find the environment motivating.
+Here, we asked respondents to rate all of the job characterstics in terms of hindrances and resources.
+consider the here whether perceptions of demands (specifically hindrance demands) and stress is
+
+## Why use the O\*Net Resource?
 
@@
 A second study extends the findings from Study 1 to a potentially key moderator - job categories/classifications, examining whether ratings of resources, challenge- and hindrance demands differ by job classification.
+
+# Methods
+
+## Participants
 

### 2022-08-18 SIOP2023/SIOP_PROCESS.tex
Updated Introduction

@@
 \documentclass[
+  english,
   man]{apa6}
@@
 \usepackage{lmodern}
-\usepackage{iftex}
-\ifPDFTeX
+\usepackage{ifxetex,ifluatex}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
   \usepackage[T1]{fontenc}
@@
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-\ifLuaTeX
-\usepackage[bidi=basic]{babel}
-\else
-\usepackage[bidi=default]{babel}
-\fi
-\babelprovide[main,import]{english}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
 % Manuscript styling
@@
 \makeatother
-
-\usepackage{xpatch}
-\makeatletter
-\xapptocmd\appendix
-  {\xapptocmd\section
-    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
-    {}{\InnerPatchFailed}%
-  }
-{}{\PatchFailed}
+\shorttitle{SIOP\_Hindrances-Resources Interaction}
 \keywords{keywords\newline\indent Word count: X}
@@
 \usepackage{csquotes}
-\ifLuaTeX
+\ifxetex
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\else
+  \usepackage[main=english]{babel}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+\fi
+\ifluatex
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 \date{}
-
-\shorttitle{SIOP\_Hindrances-Resources Interaction}
 
@@
 In fact, there was a call to work with experienced I/O psychologists over the summer to update the content for the \href{https://www.onetonline.org/link/summary/19-3032.00}{Industrial and Organizational Psychologist listing on O*Net}.
-These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move for Veterans'', ``My Next Move'', Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
+These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move for Veterans,'' ``My Next Move,'' Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
 It is also useful to employers by providing them with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2003dual}{}}%
+\leavevmode\hypertarget{ref-bakker2003dual}{}%
 Bakker, A., Demerouti, E., \& Schaufeli, W.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-hayes2022}{}}%
+\leavevmode\hypertarget{ref-hayes2022}{}%
 Hayes, A. F. (2022). \emph{Introduction to mediation, moderation, and conditional process analysis: A regression-based approach} (3rd ed.). The Guilford Press.
 
-\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
+\leavevmode\hypertarget{ref-lazarus1984stress}{}%
 Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
 
-\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
+\leavevmode\hypertarget{ref-peterson2001understanding}{}%
 Peterson, N.

### 2022-08-18 SIOP2023/SIOP_PROCESS.Rmd
number formatting in table (2 decimals forced)

--- 2022-08-18 SIOP2023/SIOP_PROCESS.Rmd
@@
 Component <- c("Constant", "Hindrance (X)", "Resource (W)", "Hindrance x Resource")
-coeff <- round(results[c(2:5),1],2)
-SE    <- round(results[c(2:5),2],2)
-t     <- round(results[c(2:5),3],2)
-p     <- round(results[c(2:5),4],2)
+coeff <- format(round(results[c(2:5),1],2), nsmall=2)
+SE    <- format(round(results[c(2:5),2],2), nsmall=2)
+t     <- format(round(results[c(2:5),3],2), nsmall=2)
+p     <- format(round(results[c(2:5),4],2), nsmall=2)
 

### 2022-08-24 Submission.Rmd

@@
 
-## Study 1
+# Study 1
 
@@
 
->*Research Question 1*: Which O\*Net job characteristics are consistently rated as job resources?
-
->*Research Question 2*: Which O\*Net job characteristics are consistently rated as challenge demands?
-
->*Research Question 3*: Which O\*Net job characteristics are consistently rated as hinderance demands?
-
-## Study 2
-
-While Study 1 explored the above questions across jobs, Study 2 considers a potentially important moderator: job classification.
-There is a distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework depending on *job classification*.
-In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., [@bakker2013weekly]; [@cavanaugh2000empirical]; [@gerich2017relevance]; [@podsakoff2007differential]; [@webster2011extending]).
-Thus, Study 2 focuses on a fourth question of interest.
-
->*Research Question 4*: Does the **type of work** reported explain variability in the categorization of work characteristics into challenges, hindrances, and resources?
+>*Research Question 1*: Are literature-implicated resources consistently rated as job resources?
+
+>*Research Question 2*: Are literature-implicated challenges consistently rated as job challenges?
+
+>*Research Question 3*: Are literature-implicated hiderances consistently rated as job hinderances?
 
@@
 
-## Participants
-
-Of the `r nrow(use)` Prolific panel individuals who initially accessed the survey link, `r nrow(different)` indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses [@R-careless].
-Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of `r nrow(data)` respondents who constitute the current SIOP sample.
-`r round(a[1,3],2)`% had been in their referent job less than 6 months, `r round(a[2,3],1)`% between 6 months and a year, `r round(a[3,3],2)`% between one and five years, `r round(a[4,3],2)`% between 5 and 10 years, and `r round(a[5,3],2)`% more than 10 years.
-
-Ages ranged from 18 to 65 with an average of `r round(mean(data[,403], na.rm=TRUE),2)` years old (SD = `r round(sd(data[,403], na.rm=TRUE),2)`).
-The survey offered a free-field gender identity category, although the sample predominantly self-identified as female (`r round(b[2,3],2)`%) or male (`r round(b[5,3],2)`%).
-
 ```{r generalrecodes}
@@
 
+## Participants
+
+Of the `r nrow(use)` Prolific panel individuals who initially accessed the survey link, `r nrow(different)` indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses [@R-careless].
+Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of `r nrow(data)` respondents who constitute the current SIOP sample.
+`r round(a[1,3],2)`% had been in their referent job less than 6 months, `r round(a[2,3],1)`% between 6 months and a year, `r round(a[3,3],2)`% between one and five years, `r round(a[4,3],2)`% between 5 and 10 years, and `r round(a[5,3],2)`% more than 10 years.
+
+Ages ranged from 18 to 65 with an average of `r round(mean(data[,403], na.rm=TRUE),2)` years old (SD = `r round(sd(data[,403], na.rm=TRUE),2)`).
+The survey offered a free-field gender identity category, although the sample predominantly self-identified as female (`r round(b[2,3],2)`%) or male (`r round(b[5,3],2)`%).
+
+```{r litresources, fig.cap="Average and standard deviation of O*Net characteristics retained as indicators of Autonomy, Cohesion, Control, Participation, and Supervisor Support."}
+
+###############################################
+###############################################
+
+labels <- read.csv("truncatedlabels.csv")
+
+resource <- as.data.frame(t(data[118:202]))
+
+resource$description <- labels[c(118:202),1]
+resource$mean <- round(rowMeans(resource[1:nrow(data)], na.rm=TRUE),2)
+resource$sd   <- round(apply(resource[1:nrow(data)], 1, sd, na.rm=TRUE),2)
+
+resource <- resource[,-145]   ## attention check
+#resource <- resource[ which(resource$sd > 0), ]
+
+resource.control <- resource[ which(resource$description=='job structured for you, rather than allowing you to determine tasks, priorities, and goals' | resource$description=='regular work schedules'), ]
+resource.control$category <- "Control"
+
+resource.participation <- resource[ which(resource$description=='responsible for work outcomes and results of other workers' | resource$description=='responsibility for the health and safety of others' | resource$description=='developing specific goals and plans to prioritize, organize, and accomplish your work' | resource$description=='scheduling events, programs, and activities, as well as the work of others' | resource$description=='developing, designing, or creating new applications, ideas, relationships, systems, or products' | resource$description=='providing information to supervisors, co-workers, and subordinates by telephone, in written form, e-mail, or in person'), ]
+resource.participation$category <- "Participation"
+
+resource.sup.support <- resource[ which(resource$description=='providing guidance and expert advice to management or other groups on technical, systems-, or process-related topics' | resource$description=='identifying the educational needs of others, developing formal educational or training programs or classes, and teaching or instructing others'), ]
+resource.sup.support$category <- "Support"
+
+resource.autonomy <- resource[ which(resource$description=='decision making freedom, without supervision'), ]
+resource.autonomy$category <- "Autonomy"
+
+resource.cohesion <- resource[ which(resource$description=='work with others in a group or team' | resource$description=='getting members of a group to work together to accomplish tasks' | resource$description=='' | resource$description=='' | resource$description=='' | resource$description=='encouraging and building mutual trust, respect, and cooperation among team members'), ]
+resource.cohesion$category <- "Cohesion"
+
+notedresource <- rbind(resource.control, resource.participation, resource.sup.support, resource.autonomy, resource.cohesion)
+notedresource$RD <- "Resource"
+
+#########################################################
+#########################################################
+
+challenge <- as.data.frame(t(data[288:372]))
+
+challenge$description <- labels[c(288:372),1]
+challenge$mean <- round(rowMeans(challenge[1:nrow(data)], na.rm=TRUE),2)
+challenge$sd   <- round(apply(challenge[1:nrow(data)], 1, sd, na.rm=TRUE),2)
+
+challenge <- challenge[,-308]
+
+challenge.control <- challenge[ which(challenge$description=='job structured for you, rather than allowing you to determine tasks, priorities, and goals' | challenge$description=='regular work schedules'), ]
+challenge.control$category <- "Control"
+
+challenge.participation <- challenge[ which(challenge$description=='responsible for work outcomes and results of other workers' | challenge$description=='responsibility for the health and safety of others' | challenge$description=='developing specific goals and plans to prioritize, organize, and accomplish your work' | challenge$description=='scheduling events, programs, and activities, as well as the work of others' | challenge$description=='developing, designing, or creating new applications, ideas, relationships, systems, or products' | challenge$description=='providing information to supervisors, co-workers, and subordinates by telephone, in written form, e-mail, or in person'), ]
+challenge.participation$category <- "Participation"
+
+challenge.sup.support <- challenge[ which(challenge$description=='providing guidance and expert advice to management or other groups on technical, systems-, or process-related topics' | challenge$description=='identifying the educational needs of others, developing formal educational or training programs or classes, and teaching or instructing others'), ]
+challenge.sup.support$category <- "Support"
+
+#challenge.autonomy <- challenge[ which(challenge$description=='decision making freedom, without supervision'), ]
+#challenge.autonomy$category <- "Autonomy"
+
+challenge.cohesion <- challenge[ which(challenge$description=='work with others in a group or team' | challenge$description=='getting members of a group to work together to accomplish tasks' | challenge$description=='' | challenge$description=='' | challenge$description=='' | challenge$description=='encouraging and building mutual trust, respect, and cooperation among team members'), ]
+challenge.cohesion$category <- "Cohesion"
+
+notedchallenge <- rbind(challenge.control, challenge.participation, challenge.sup.support,  challenge.cohesion)     ## removed challenge.autonomy 8/24/22
+notedchallenge$RD <- "Challenge"
+
+############################################################
+############################################################
+
+hindrance <- as.data.frame(t(data[203:287]))
+
+hindrance$description <- labels[c(203:287),1]
+hindrance$mean <- round(rowMeans(hindrance[1:nrow(data)], na.rm=TRUE),2)
+hindrance$sd   <- round(apply(hindrance[1:nrow(data)], 1, sd, na.rm=TRUE),2)
+
+hindrance <- hindrance[,-248]   ## attention check
+#hindrance <- hindrance[ which(hindrance$sd > 0), ]
+
+hindrance.control <- hindrance[ which(hindrance$description=='job structured for you, rather than allowing you to determine tasks, priorities, and goals' | hindrance$description=='regular work schedules'), ]
+hindrance.control$category <- "Control"
+
+hindrance.participation <- hindrance[ which(hindrance$description=='responsible for work outcomes and results of other workers' | hindrance$description=='responsibility for the health and safety of others' | hindrance$description=='developing specific goals and plans to prioritize, organize, and accomplish your work' | hindrance$description=='scheduling events, programs, and activities, as well as the work of others' | hindrance$description=='developing, designing, or creating new applications, ideas, relationships, systems, or products' | hindrance$description=='providing information to supervisors, co-workers, and subordinates by telephone, in written form, e-mail, or in person'), ]
+hindrance.participation$category <- "Participation"
+
+hindrance.sup.support <- hindrance[ which(hindrance$description=='providing guidance and expert advice to management or other groups on technical, systems-, or process-related topics' | hindrance$description=='identifying the educational needs of others, developing formal educational or training programs or classes, and teaching or instructing others'), ]
+hindrance.sup.support$category <- "Support"
+
+hindrance.autonomy <- hindrance[ which(hindrance$description=='decision making freedom, without supervision'), ]
+hindrance.autonomy$category <- "Autonomy"
+
+hindrance.cohesion <- hindrance[ which(hindrance$description=='work with others in a group or team' | hindrance$description=='getting members of a group to work together to accomplish tasks' | hindrance$description=='' | hindrance$description=='' | hindrance$description=='' | hindrance$description=='encouraging and building mutual trust, respect, and cooperation among team members'), ]
+hindrance.cohesion$category <- "Cohesion"
+
+notedhindrance <- rbind(hindrance.control, hindrance.participation, hindrance.sup.support, hindrance.autonomy, hindrance.cohesion)
+notedhindrance$RD <- "Hindrance"
+
+###########################################################
+###########################################################  Name issue somehow above
+
+labels <- names(notedresource)
+colnames(notedchallenge) <- labels
+colnames(notedhindrance) <- labels
+
+together <- rbind(notedchallenge,notedhindrance,notedresource)
+
+############################################################
+############################################################
+
+library(ggplot2)
+library(dplyr)
+
+summarized <- together %>%                               # Summary by group using dplyr
+  group_by(category, RD) %>% 
+  summarize(mean = mean(mean),
+            sd = mean(sd))
+
+summarized$RD <- factor(summarized$RD, levels = c("Resource", "Challenge", "Hindrance"))
+
+ggplot(summarized, aes(x=category, y=mean, fill=RD)) + geom_bar(stat="identity", position=position_dodge()) + theme_bw() + xlab("") + ylab("Average Job Characteristic Rating") + coord_cartesian(ylim=c(1,5)) + scale_fill_brewer(palette="Blues") +
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.5, size=0.8, position=position_dodge(.9))
+
+```
+
+## Materials
+
+Looked through
+
+# Study 2
+
+While Study 1 explored the above questions across jobs, Study 2 considers a potentially important moderator: job classification.
+There is a distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework depending on *job classification*.
+In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., [@bakker2013weekly]; [@cavanaugh2000empirical]; [@gerich2017relevance]; [@podsakoff2007differential]; [@webster2011extending]).
+Thus, Study 2 focuses on a fourth question of interest.
+
+>*Research Question 4*: Does the **type of work** reported explain variability in the categorization of work characteristics into challenges, hindrances, and resources?
+
 ## Materials

### 2022-08-24 Submission.tex

@@
 \usepackage{csquotes}
-\ifXeTeX
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
 \ifLuaTeX
@@
 
+\title{Job Demands-Resources model components through the lens of O*NET classifications}
+\author{Alicia Stachowski\textsuperscript{1}, Renata Garcia Prieto Palacios Roji\textsuperscript{2}, \& John Kulas\textsuperscript{2}}
+\date{}
+
+\shorttitle{O*NET JD-R}
+
+\authornote{
+
+Correspondence concerning this article should be addressed to Alicia Stachowski, Menomenie, WI. E-mail: \href{mailto:stachowskia@uwstout.edu}{\nolinkurl{stachowskia@uwstout.edu}}
+
+}
+
 \affiliation{\vspace{0.5cm}\textsuperscript{1} University of Wisconsin - Stout\\\textsuperscript{2} Montclair State University}
 
-\abstract{
+\abstract{%
 O*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource.
@@
 (2001){]} in exploring questions related to everything from motivation to job design, we aim to explore the intersection between \emph{perceptions} of job demands and resources, and the broad set of job characteristics provided on O*Net.
-We aim to present evidence surrounding whether O*Net job and task descriptors are simiarly rated as resources, challenge- or hindrance demands, and whether such ratings differ across job catories/classifications.
+This project makes three contributions.
+We aim to first explore whether ratings of of O*Net item groupings align with the stated ``resources'' and ``demands'' presented in the job demands-resources theory.
+We then present evidence documenting whether O*Net job and task descriptors are similarly rated as resources, challenge- or hindrance demands, and lastly, whether such ratings differ across job categories/classifications.
 Across two studies, a series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers.
@@
 In fact, there was a call to work with experienced I/O psychologists over the summer to update the content for the \href{https://www.onetonline.org/link/summary/19-3032.00}{Industrial and Organizational Psychologist listing on O*Net}.
-These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move for Veterans,'' ``My Next Move,'' Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
+These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move for Veterans'', ``My Next Move'', Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
 It is also useful to employers by providing them with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
 
+Of greatest interest here are statements taken from O*NET \href{https://www.O*NETonline.org/find/descriptor/result/4.A.1.b.3}{``activity'' and ``context'' classifications} (e.g., items related to information input, interacting with others, physical work conditions, structural job characteristics).
+One of the first and basic questions is whether or not the categorical examples of ``resources'' and ``demands'' described in the Job Demands-Resources Theory (Demerouti et al., 2001), for example, are generally deemed resources or demands as we objectively define them.
+The next logical question surrounds how ``universal'' such ratings are.
+For instance, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.
+A second study extends the findings from Study 1 to a potentially key moderator - job categories/classifications, examining whether ratings of resources, challenge- and hindrance demands differ by job classification.
+
 \hypertarget{study-1}{%
-\subsection{Study 1}\label{study-1}}
+\section{Study 1}\label{study-1}}
 
@@
 \begin{quote}
-\emph{Research Question 1}: Which O*Net job characteristics are consistently rated as job resources?
+\emph{Research Question 1}: Are literature-implicated resources consistently rated as job resources?
 \end{quote}
@@
 \begin{quote}
-\emph{Research Question 2}: Which O*Net job characteristics are consistently rated as challenge demands?
+\emph{Research Question 2}: Are literature-implicated challenges consistently rated as job challenges?
 \end{quote}
@@
 \begin{quote}
-\emph{Research Question 3}: Which O*Net job characteristics are consistently rated as hinderance demands?
+\emph{Research Question 3}: Are literature-implicated hiderances consistently rated as job hinderances?
 \end{quote}
 
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
+Of the 785 Prolific panel individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (\textbf{R-careless?}).
+Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current SIOP sample.
+13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.
+
+Ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53).
+The survey offered a free-field gender identity category, although the sample predominantly self-identified as female (52.58\%) or male (46.83\%).
+
+\begin{figure}
+\centering
+\includegraphics{Submission_files/figure-latex/litresources-1.pdf}
+\caption{\label{fig:litresources}Average and standard deviation of O*Net characteristics retained as indicators of Autonomy, Cohesion, Control, Participation, and Supervisor Support.}
+\end{figure}
+
+\hypertarget{materials}{%
+\subsection{Materials}\label{materials}}
+
+Looked through
+
 \hypertarget{study-2}{%
-\subsection{Study 2}\label{study-2}}
+\section{Study 2}\label{study-2}}
 
@@
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-Of the 785 Prolific panel individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (\textbf{R-careless?}).
-Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current SIOP sample.
-13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.
-
-Ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53).
-The survey offered a free-field gender identity category, although the sample predominantly self-identified as female (52.58\%) or male (46.83\%).
-
-\hypertarget{materials}{%
-\subsection{Materials}\label{materials}}
+\hypertarget{materials-1}{%
+\subsection{Materials}\label{materials-1}}
 

### 2022-08-29 Submission_ResourceCount.Rmd
Creating new rmd for journal submission

---
title: "Submission_ResourceCount"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Next steps (thoughts from 8/24):
Want this to be a more traditional project: DVs engagement, burnout, stress. 
How to operationalize IVs of resources, challenges, hindrances. May want to only count it if they somewhat agree or strongly agree. Could do a count or a sum of these values. The moderator of job type may work well in this idea.

Want to include idea of item level things in terms of agreement. decreasing bar graphs relative to SD. Maybe we just present SD or SE. Thinking on SD, but ensure we have sufficient numbers of people responding to the item. 
Want to get a total count.

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2022-08-29 Submission.Rmd
sum of resource challenge hindrance

@@
 
-```{r generalrecodes}
-## Qualtrics data all messed up
-
-data$item82[data$item82 == 8]  <- 1
-data$item82[data$item82 == 9]  <- 2
-data$item82[data$item82 == 10] <- 3
-data$item82[data$item82 == 11] <- 4
-data$item82[data$item82 == 12] <- 5
-
-data$item118[data$item118 == 9]  <- 1
-data$item118[data$item118 == 10] <- 2
-data$item118[data$item118 == 11] <- 3
-data$item118[data$item118 == 12] <- 4
-data$item118[data$item118 == 13] <- 5
-
-data$item119[data$item119 == 11] <- 1
-data$item119[data$item119 == 12] <- 2
-data$item119[data$item119 == 13] <- 3
-data$item119[data$item119 == 14] <- 4
-data$item119[data$item119 == 15] <- 5
-
-data$item120[data$item120 == 6]  <- 1
-data$item120[data$item120 == 7]  <- 2
-data$item120[data$item120 == 8]  <- 3
-data$item120[data$item120 == 9]  <- 4
-data$item120[data$item120 == 10] <- 5
-
-data$item121[data$item121 == 6]  <- 1
-data$item121[data$item121 == 7]  <- 2
-data$item121[data$item121 == 8]  <- 3
-data$item121[data$item121 == 9]  <- 4
-data$item121[data$item121 == 10] <- 5
-
-data$item122[data$item122 == 6]  <- 1
-data$item122[data$item122 == 7]  <- 2
-data$item122[data$item122 == 8]  <- 3
-data$item122[data$item122 == 9]  <- 4
-data$item122[data$item122 == 10] <- 5
-
-data$item123[data$item123 == 6]  <- 1
-data$item123[data$item123 == 7]  <- 2
-data$item123[data$item123 == 8]  <- 3
-data$item123[data$item123 == 9]  <- 4
-data$item123[data$item123 == 10] <- 5
-
-data$item124[data$item124 == 6]  <- 1
-data$item124[data$item124 == 7]  <- 2
-data$item124[data$item124 == 8]  <- 3
-data$item124[data$item124 == 9]  <- 4
-data$item124[data$item124 == 10] <- 5
-
-data$item125[data$item125 == 6]  <- 1
-data$item125[data$item125 == 7]  <- 2
-data$item125[data$item125 == 8]  <- 3
-data$item125[data$item125 == 9]  <- 4
-data$item125[data$item125 == 10] <- 5
-
-data$item126[data$item126 == 11]  <- 1
-data$item126[data$item126 == 12]  <- 2
-data$item126[data$item126 == 13]  <- 3
-data$item126[data$item126 == 14]  <- 4
-data$item126[data$item126 == 15]  <- 5
-
-data$item127[data$item127 == 4]  <- 1
-data$item127[data$item127 == 5]  <- 2
-data$item127[data$item127 == 6]  <- 3
-data$item127[data$item127 == 7]  <- 4
-data$item127[data$item127 == 8]  <- 5
-
-data$item128[data$item128 == 11]  <- 1
-data$item128[data$item128 == 12]  <- 2
-data$item128[data$item128 == 13]  <- 3
-data$item128[data$item128 == 14]  <- 4
-data$item128[data$item128 == 15]  <- 5
-
-data$item129[data$item129 == 11]  <- 1
-data$item129[data$item129 == 12]  <- 2
-data$item129[data$item129 == 13]  <- 3
-data$item129[data$item129 == 14]  <- 4
-data$item129[data$item129 == 15]  <- 5
-
-data$item130[data$item130 == 11]  <- 1
-data$item130[data$item130 == 12]  <- 2
-data$item130[data$item130 == 13]  <- 3
-data$item130[data$item130 == 14]  <- 4
-data$item130[data$item130 == 15]  <- 5
-
-data$item131[data$item131 == 11]  <- 1
-data$item131[data$item131 == 12]  <- 2
-data$item131[data$item131 == 13]  <- 3
-data$item131[data$item131 == 14]  <- 4
-data$item131[data$item131 == 15]  <- 5
-
-data$item132[data$item132 == 11]  <- 1
-data$item132[data$item132 == 12]  <- 2
-data$item132[data$item132 == 13]  <- 3
-data$item132[data$item132 == 14]  <- 4
-data$item132[data$item132 == 15]  <- 5
-
-data$item133[data$item133 == 11]  <- 1
-data$item133[data$item133 == 12]  <- 2
-data$item133[data$item133 == 13]  <- 3
-data$item133[data$item133 == 14]  <- 4
-data$item133[data$item133 == 15]  <- 5
-
-data$item134[data$item134 == 11]  <- 1
-data$item134[data$item134 == 12]  <- 2
-data$item134[data$item134 == 13]  <- 3
-data$item134[data$item134 == 14]  <- 4
-data$item134[data$item134 == 15]  <- 5
-
-data$item135[data$item135 == 6]  <- 1
-data$item135[data$item135 == 7]  <- 2
-data$item135[data$item135 == 8]  <- 3
-data$item135[data$item135 == 9]  <- 4
-data$item135[data$item135 == 10] <- 5
-
-data$item136[data$item136 == 6]  <- 1
-data$item136[data$item136 == 7]  <- 2
-data$item136[data$item136 == 8]  <- 3
-data$item136[data$item136 == 9]  <- 4
-data$item136[data$item136 == 10] <- 5
-
-data$item137[data$item137 == 6]  <- 1
-data$item137[data$item137 == 7]  <- 2
-data$item137[data$item137 == 8]  <- 3
-data$item137[data$item137 == 9]  <- 4
-data$item137[data$item137 == 10] <- 5
-
-data$item138[data$item138 == 16]  <- 1
-data$item138[data$item138 == 17]  <- 2
-data$item138[data$item138 == 18]  <- 3
-data$item138[data$item138 == 19]  <- 4
-data$item138[data$item138 == 20]  <- 5
-
-data$item139[data$item139 == 6]  <- 1
-data$item139[data$item139 == 7]  <- 2
-data$item139[data$item139 == 8]  <- 3
-data$item139[data$item139 == 9]  <- 4
-data$item139[data$item139 == 10] <- 5
-
-data$item140[data$item140 == 6]  <- 1
-data$item140[data$item140 == 7]  <- 2
-data$item140[data$item140 == 8]  <- 3
-data$item140[data$item140 == 9]  <- 4
-data$item140[data$item140 == 10] <- 5
-
-data$item141[data$item141 == 6]  <- 1
-data$item141[data$item141 == 7]  <- 2
-data$item141[data$item141 == 8]  <- 3
-data$item141[data$item141 == 9]  <- 4
-data$item141[data$item141 == 10] <- 5
-
-data$item142[data$item142 == 6]  <- 1
-data$item142[data$item142 == 7]  <- 2
-data$item142[data$item142 == 8]  <- 3
-data$item142[data$item142 == 9]  <- 4
-data$item142[data$item142 == 10] <- 5
-
-data$item143[data$item143 == 6]  <- 1
-data$item143[data$item143 == 7]  <- 2
-data$item143[data$item143 == 8]  <- 3
-data$item143[data$item143 == 9]  <- 4
-data$item143[data$item143 == 10] <- 5
-
-data$item144[data$item144 == 6]  <- 1
-data$item144[data$item144 == 7]  <- 2
-data$item144[data$item144 == 8]  <- 3
-data$item144[data$item144 == 9]  <- 4
-data$item144[data$item144 == 10] <- 5
-
-## Attention check = 145
-
-data$item146[data$item146 == 16]  <- 1
-data$item146[data$item146 == 17]  <- 2
-data$item146[data$item146 == 18]  <- 3
-data$item146[data$item146 == 19]  <- 4
-data$item146[data$item146 == 20]  <- 5
-
-data$item147[data$item147 == 6]  <- 1
-data$item147[data$item147 == 7]  <- 2
-data$item147[data$item147 == 8]  <- 3
-data$item147[data$item147 == 9]  <- 4
-data$item147[data$item147 == 10] <- 5
-
-data$item148[data$item148 == 6]  <- 1
-data$item148[data$item148 == 7]  <- 2
-data$item148[data$item148 == 8]  <- 3
-data$item148[data$item148 == 9]  <- 4
-data$item148[data$item148 == 10] <- 5
-
-data$item149[data$item149 == 6]  <- 1
-data$item149[data$item149 == 7]  <- 2
-data$item149[data$item149 == 8]  <- 3
-data$item149[data$item149 == 9]  <- 4
-data$item149[data$item149 == 10] <- 5
-
-data$item150[data$item150 == 11]  <- 1
-data$item150[data$item150 == 12]  <- 2
-data$item150[data$item150 == 13]  <- 3
-data$item150[data$item150 == 14]  <- 4
-data$item150[data$item150 == 15]  <- 5
-
-data$item151[data$item151 == 11]  <- 1
-data$item151[data$item151 == 12]  <- 2
-data$item151[data$item151 == 13]  <- 3
-data$item151[data$item151 == 14]  <- 4
-data$item151[data$item151 == 15]  <- 5
-
-data$item152[data$item152 == 11]  <- 1
-data$item152[data$item152 == 12]  <- 2
-data$item152[data$item152 == 13]  <- 3
-data$item152[data$item152 == 14]  <- 4
-data$item152[data$item152 == 15]  <- 5
-
-data$item153[data$item153 == 11]  <- 1
-data$item153[data$item153 == 12]  <- 2
-data$item153[data$item153 == 13]  <- 3
-data$item153[data$item153 == 14]  <- 4
-data$item153[data$item153 == 15]  <- 5
-
-data$item154[data$item154 == 11]  <- 1
-data$item154[data$item154 == 12]  <- 2
-data$item154[data$item154 == 13]  <- 3
-data$item154[data$item154 == 14]  <- 4
-data$item154[data$item154 == 15]  <- 5
-
-data$item155[data$item155 == 11]  <- 1
-data$item155[data$item155 == 12]  <- 2
-data$item155[data$item155 == 13]  <- 3
-data$item155[data$item155 == 14]  <- 4
-data$item155[data$item155 == 15]  <- 5
-
-data$item156[data$item156 == 11]  <- 1
-data$item156[data$item156 == 12]  <- 2
-data$item156[data$item156 == 13]  <- 3
-data$item156[data$item156 == 14]  <- 4
-data$item156[data$item156 == 15]  <- 5
-
-data$item157[data$item157 == 11]  <- 1
-data$item157[data$item157 == 12]  <- 2
-data$item157[data$item157 == 13]  <- 3
-data$item157[data$item157 == 14]  <- 4
-data$item157[data$item157 == 15]  <- 5
-
-data$item158[data$item158 == 6]  <- 1
-data$item158[data$item158 == 7]  <- 2
-data$item158[data$item158 == 8]  <- 3
-data$item158[data$item158 == 9]  <- 4
-data$item158[data$item158 == 10] <- 5
-
-data$item159[data$item159 == 11]  <- 1
-data$item159[data$item159 == 12]  <- 2
-data$item159[data$item159 == 13]  <- 3
-data$item159[data$item159 == 14]  <- 4
-data$item159[data$item159 == 15]  <- 5
-
-data$item160[data$item160 == 11]  <- 1
-data$item160[data$item160 == 12]  <- 2
-data$item160[data$item160 == 13]  <- 3
-data$item160[data$item160 == 14]  <- 4
-data$item160[data$item160 == 15]  <- 5
-
-data$item161[data$item161 == 6]  <- 1
-data$item161[data$item161 == 7]  <- 2
-data$item161[data$item161 == 8]  <- 3
-data$item161[data$item161 == 9]  <- 4
-data$item161[data$item161 == 10] <- 5
-
-data$item162[data$item162 == 11]  <- 1
-data$item162[data$item162 == 12]  <- 2
-data$item162[data$item162 == 13]  <- 3
-data$item162[data$item162 == 14]  <- 4
-data$item162[data$item162 == 15]  <- 5
-
-data$item163[data$item163 == 11]  <- 1
-data$item163[data$item163 == 12]  <- 2
-data$item163[data$item163 == 13]  <- 3
-data$item163[data$item163 == 14]  <- 4
-data$item163[data$item163 == 15]  <- 5
-
-data$item164[data$item164 == 11]  <- 1
-data$item164[data$item164 == 12]  <- 2
-data$item164[data$item164 == 13]  <- 3
-data$item164[data$item164 == 14]  <- 4
-data$item164[data$item164 == 15]  <- 5
-
-data$item165[data$item165 == 11]  <- 1
-data$item165[data$item165 == 12]  <- 2
-data$item165[data$item165 == 13]  <- 3
-data$item165[data$item165 == 14]  <- 4
-data$item165[data$item165 == 15]  <- 5
-
-data$item166[data$item166 == 11]  <- 1
-data$item166[data$item166 == 12]  <- 2
-data$item166[data$item166 == 13]  <- 3
-data$item166[data$item166 == 14]  <- 4
-data$item166[data$item166 == 15]  <- 5
-
-data$item167[data$item167 == 18]  <- 1
-data$item167[data$item167 == 19]  <- 2
-data$item167[data$item167 == 20]  <- 3
-data$item167[data$item167 == 21]  <- 4
-data$item167[data$item167 == 22]  <- 5
-
-data$item168[data$item168 == 11]  <- 1
-data$item168[data$item168 == 12]  <- 2
-data$item168[data$item168 == 13]  <- 3
-data$item168[data$item168 == 14]  <- 4
-data$item168[data$item168 == 15]  <- 5
-
-data$item169[data$item169 == 11]  <- 1
-data$item169[data$item169 == 12]  <- 2
-data$item169[data$item169 == 13]  <- 3
-data$item169[data$item169 == 14]  <- 4
-data$item169[data$item169 == 15]  <- 5
-
-data$item170[data$item170 == 11]  <- 1
-data$item170[data$item170 == 12]  <- 2
-data$item170[data$item170 == 13]  <- 3
-data$item170[data$item170 == 14]  <- 4
-data$item170[data$item170 == 15]  <- 5
-
-data$item171[data$item171 == 11]  <- 1
-data$item171[data$item171 == 12]  <- 2
-data$item171[data$item171 == 13]  <- 3
-data$item171[data$item171 == 14]  <- 4
-data$item171[data$item171 == 15]  <- 5
-
-data$item172[data$item172 == 11]  <- 1
-data$item172[data$item172 == 12]  <- 2
-data$item172[data$item172 == 13]  <- 3
-data$item172[data$item172 == 14]  <- 4
-data$item172[data$item172 == 15]  <- 5
-
-data$item173[data$item173 == 11]  <- 1
-data$item173[data$item173 == 12]  <- 2
-data$item173[data$item173 == 13]  <- 3
-data$item173[data$item173 == 14]  <- 4
-data$item173[data$item173 == 15]  <- 5
-
-data$item174[data$item174 == 11]  <- 1
-data$item174[data$item174 == 12]  <- 2
-data$item174[data$item174 == 13]  <- 3
-data$item174[data$item174 == 14]  <- 4
-data$item174[data$item174 == 15]  <- 5
-
-data$item175[data$item175 == 11]  <- 1
-data$item175[data$item175 == 12]  <- 2
-data$item175[data$item175 == 13]  <- 3
-data$item175[data$item175 == 14]  <- 4
-data$item175[data$item175 == 15]  <- 5
-
-data$item176[data$item176 == 11]  <- 1
-data$item176[data$item176 == 12]  <- 2
-data$item176[data$item176 == 13]  <- 3
-data$item176[data$item176 == 14]  <- 4
-data$item176[data$item176 == 15]  <- 5
-
-data$item177[data$item177 == 11]  <- 1
-data$item177[data$item177 == 12]  <- 2
-data$item177[data$item177 == 13]  <- 3
-data$item177[data$item177 == 14]  <- 4
-data$item177[data$item177 == 15]  <- 5
-
-data$item178[data$item178 == 11]  <- 1
-data$item178[data$item178 == 12]  <- 2
-data$item178[data$item178 == 13]  <- 3
-data$item178[data$item178 == 14]  <- 4
-data$item178[data$item178 == 15]  <- 5
-
-data$item179[data$item179 == 11]  <- 1
-data$item179[data$item179 == 12]  <- 2
-data$item179[data$item179 == 13]  <- 3
-data$item179[data$item179 == 14]  <- 4
-data$item179[data$item179 == 15]  <- 5
-
-data$item180[data$item180 == 11]  <- 1
-data$item180[data$item180 == 12]  <- 2
-data$item180[data$item180 == 13]  <- 3
-data$item180[data$item180 == 14]  <- 4
-data$item180[data$item180 == 15]  <- 5
-
-data$item181[data$item181 == 11]  <- 1
-data$item181[data$item181 == 12]  <- 2
-data$item181[data$item181 == 13]  <- 3
-data$item181[data$item181 == 14]  <- 4
-data$item181[data$item181 == 15]  <- 5
-
-data$item182[data$item182 == 11]  <- 1
-data$item182[data$item182 == 12]  <- 2
-data$item182[data$item182 == 13]  <- 3
-data$item182[data$item182 == 14]  <- 4
-data$item182[data$item182 == 15]  <- 5
-
-data$item183[data$item183 == 11]  <- 1
-data$item183[data$item183 == 12]  <- 2
-data$item183[data$item183 == 13]  <- 3
-data$item183[data$item183 == 14]  <- 4
-data$item183[data$item183 == 15]  <- 5
-
-data$item184[data$item184 == 21]  <- 1
-data$item184[data$item184 == 22]  <- 2
-data$item184[data$item184 == 23]  <- 3
-data$item184[data$item184 == 24]  <- 4
-data$item184[data$item184 == 25]  <- 5
-
-data$item185[data$item185 == 11]  <- 1
-data$item185[data$item185 == 12]  <- 2
-data$item185[data$item185 == 13]  <- 3
-data$item185[data$item185 == 14]  <- 4
-data$item185[data$item185 == 15]  <- 5
-
-data$item186[data$item186 == 11]  <- 1
-data$item186[data$item186 == 12]  <- 2
-data$item186[data$item186 == 13]  <- 3
-data$item186[data$item186 == 14]  <- 4
-data$item186[data$item186 == 15]  <- 5
-
-data$item187[data$item187 == 11]  <- 1
-data$item187[data$item187 == 12]  <- 2
-data$item187[data$item187 == 13]  <- 3
-data$item187[data$item187 == 14]  <- 4
-data$item187[data$item187 == 15]  <- 5
-
-data$item188[data$item188 == 11]  <- 1
-data$item188[data$item188 == 12]  <- 2
-data$item188[data$item188 == 13]  <- 3
-data$item188[data$item188 == 14]  <- 4
-data$item188[data$item188 == 15]  <- 5
-
-data$item189[data$item189 == 11]  <- 1
-data$item189[data$item189 == 12]  <- 2
-data$item189[data$item189 == 13]  <- 3
-data$item189[data$item189 == 14]  <- 4
-data$item189[data$item189 == 15]  <- 5
-
-data$item190[data$item190 == 11]  <- 1
-data$item190[data$item190 == 12]  <- 2
-data$item190[data$item190 == 13]  <- 3
-data$item190[data$item190 == 14]  <- 4
-data$item190[data$item190 == 15]  <- 5
-
-data$item191[data$item191 == 11]  <- 1
-data$item191[data$item191 == 12]  <- 2
-data$item191[data$item191 == 13]  <- 3
-data$item191[data$item191 == 14]  <- 4
-data$item191[data$item191 == 15]  <- 5
-
-data$item192[data$item192 == 11]  <- 1
-data$item192[data$item192 == 12]  <- 2
-data$item192[data$item192 == 13]  <- 3
-data$item192[data$item192 == 14]  <- 4
-data$item192[data$item192 == 15]  <- 5
-
-data$item193[data$item193 == 11]  <- 1
-data$item193[data$item193 == 12]  <- 2
-data$item193[data$item193 == 13]  <- 3
-data$item193[data$item193 == 14]  <- 4
-data$item193[data$item193 == 15]  <- 5
-
-data$item194[data$item194 == 11]  <- 1
-data$item194[data$item194 == 12]  <- 2
-data$item194[data$item194 == 13]  <- 3
-data$item194[data$item194 == 14]  <- 4
-data$item194[data$item194 == 15]  <- 5
-
-data$item195[data$item195 == 11]  <- 1
-data$item195[data$item195 == 12]  <- 2
-data$item195[data$item195 == 13]  <- 3
-data$item195[data$item195 == 14]  <- 4
-data$item195[data$item195 == 15]  <- 5
-
-data$item196[data$item196 == 11]  <- 1
-data$item196[data$item196 == 12]  <- 2
-data$item196[data$item196 == 13]  <- 3
-data$item196[data$item196 == 14]  <- 4
-data$item196[data$item196 == 15]  <- 5
-
-data$item197[data$item197 == 11]  <- 1
-data$item197[data$item197 == 12]  <- 2
-data$item197[data$item197 == 13]  <- 3
-data$item197[data$item197 == 14]  <- 4
-data$item197[data$item197 == 15]  <- 5
-
-data$item198[data$item198 == 11]  <- 1
-data$item198[data$item198 == 12]  <- 2
-data$item198[data$item198 == 13]  <- 3
-data$item198[data$item198 == 14]  <- 4
-data$item198[data$item198 == 15]  <- 5
-
-data$item199[data$item199 == 11]  <- 1
-data$item199[data$item199 == 12]  <- 2
-data$item199[data$item199 == 13]  <- 3
-data$item199[data$item199 == 14]  <- 4
-data$item199[data$item199 == 15]  <- 5
-
-data$item200[data$item200 == 11]  <- 1
-data$item200[data$item200 == 12]  <- 2
-data$item200[data$item200 == 13]  <- 3
-data$item200[data$item200 == 14]  <- 4
-data$item200[data$item200 == 15]  <- 5
-
-data$item201[data$item201 == 11]  <- 1
-data$item201[data$item201 == 12]  <- 2
-data$item201[data$item201 == 13]  <- 3
-data$item201[data$item201 == 14]  <- 4
-data$item201[data$item201 == 15]  <- 5
-
-data$item202[data$item202 == 11]  <- 1
-data$item202[data$item202 == 12]  <- 2
-data$item202[data$item202 == 13]  <- 3
-data$item202[data$item202 == 14]  <- 4
-data$item202[data$item202 == 15]  <- 5
-
-data$item203[data$item203 == 9]   <- 1
-data$item203[data$item203 == 10]  <- 2
-data$item203[data$item203 == 11]  <- 3
-data$item203[data$item203 == 12]  <- 4
-data$item203[data$item203 == 13]  <- 5
-
-data$item204[data$item204 == 11]  <- 1
-data$item204[data$item204 == 12]  <- 2
-data$item204[data$item204 == 13]  <- 3
-data$item204[data$item204 == 14]  <- 4
-data$item204[data$item204 == 15]  <- 5
-
-data$item205[data$item205 == 6]  <- 1
-data$item205[data$item205 == 7]  <- 2
-data$item205[data$item205 == 8]  <- 3
-data$item205[data$item205 == 9]  <- 4
-data$item205[data$item205 == 10] <- 5
-
-data$item206[data$item206 == 6]  <- 1
-data$item206[data$item206 == 7]  <- 2
-data$item206[data$item206 == 8]  <- 3
-data$item206[data$item206 == 9]  <- 4
-data$item206[data$item206 == 10] <- 5
-
-data$item207[data$item207 == 6]  <- 1
-data$item207[data$item207 == 7]  <- 2
-data$item207[data$item207 == 8]  <- 3
-data$item207[data$item207 == 9]  <- 4
-data$item207[data$item207 == 10] <- 5
-
-data$item208[data$item208 == 6]  <- 1
-data$item208[data$item208 == 7]  <- 2
-data$item208[data$item208 == 8]  <- 3
-data$item208[data$item208 == 9]  <- 4
-data$item208[data$item208 == 10] <- 5
-
-data$item209[data$item209 == 6]  <- 1
-data$item209[data$item209 == 7]  <- 2
-data$item209[data$item209 == 8]  <- 3
-data$item209[data$item209 == 9]  <- 4
-data$item209[data$item209 == 10] <- 5
-
-data$item210[data$item210 == 6]  <- 1
-data$item210[data$item210 == 7]  <- 2
-data$item210[data$item210 == 8]  <- 3
-data$item210[data$item210 == 9]  <- 4
-data$item210[data$item210 == 10] <- 5
-
-data$item211[data$item211 == 11]  <- 1
-data$item211[data$item211 == 12]  <- 2
-data$item211[data$item211 == 13]  <- 3
-data$item211[data$item211 == 14]  <- 4
-data$item211[data$item211 == 15]  <- 5
-
-data$item212[data$item212 == 4]  <- 1
-data$item212[data$item212 == 5]  <- 2
-data$item212[data$item212 == 6]  <- 3
-data$item212[data$item212 == 7]  <- 4
-data$item212[data$item212 == 8]  <- 5
-
-data$item213[data$item213 == 11]  <- 1
-data$item213[data$item213 == 12]  <- 2
-data$item213[data$item213 == 13]  <- 3
-data$item213[data$item213 == 14]  <- 4
-data$item213[data$item213 == 15]  <- 5
-
-data$item214[data$item214 == 11]  <- 1
-data$item214[data$item214 == 12]  <- 2
-data$item214[data$item214 == 13]  <- 3
-data$item214[data$item214 == 14]  <- 4
-data$item214[data$item214 == 15]  <- 5
-
-data$item215[data$item215 == 11]  <- 1
-data$item215[data$item215 == 12]  <- 2
-data$item215[data$item215 == 13]  <- 3
-data$item215[data$item215 == 14]  <- 4
-data$item215[data$item215 == 15]  <- 5
-
-data$item216[data$item216 == 11]  <- 1
-data$item216[data$item216 == 12]  <- 2
-data$item216[data$item216 == 13]  <- 3
-data$item216[data$item216 == 14]  <- 4
-data$item216[data$item216 == 15]  <- 5
-
-data$item217[data$item217 == 11]  <- 1
-data$item217[data$item217 == 12]  <- 2
-data$item217[data$item217 == 13]  <- 3
-data$item217[data$item217 == 14]  <- 4
-data$item217[data$item217 == 15]  <- 5
-
-data$item218[data$item218 == 11]  <- 1
-data$item218[data$item218 == 12]  <- 2
-data$item218[data$item218 == 13]  <- 3
-data$item218[data$item218 == 14]  <- 4
-data$item218[data$item218 == 15]  <- 5
-
-data$item219[data$item219 == 11]  <- 1
-data$item219[data$item219 == 12]  <- 2
-data$item219[data$item219 == 13]  <- 3
-data$item219[data$item219 == 14]  <- 4
-data$item219[data$item219 == 15]  <- 5
-
-data$item220[data$item220 == 6]  <- 1
-data$item220[data$item220 == 7]  <- 2
-data$item220[data$item220 == 8]  <- 3
-data$item220[data$item220 == 9]  <- 4
-data$item220[data$item220 == 10] <- 5
-
-data$item221[data$item221 == 6]  <- 1
-data$item221[data$item221 == 7]  <- 2
-data$item221[data$item221 == 8]  <- 3
-data$item221[data$item221 == 9]  <- 4
-data$item221[data$item221 == 10] <- 5
-
-data$item222[data$item222 == 6]  <- 1
-data$item222[data$item222 == 7]  <- 2
-data$item222[data$item222 == 8]  <- 3
-data$item222[data$item222 == 9]  <- 4
-data$item222[data$item222 == 10] <- 5
-
-data$item223[data$item223 == 16] <- 1
-data$item223[data$item223 == 17] <- 2
-data$item223[data$item223 == 18] <- 3
-data$item223[data$item223 == 19] <- 4
-data$item223[data$item223 == 20] <- 5
-
-data$item224[data$item224 == 6]  <- 1
-data$item224[data$item224 == 7]  <- 2
-data$item224[data$item224 == 8]  <- 3
-data$item224[data$item224 == 9]  <- 4
-data$item224[data$item224 == 10] <- 5
-
-data$item225[data$item225 == 6]  <- 1
-data$item225[data$item225 == 7]  <- 2
-data$item225[data$item225 == 8]  <- 3
-data$item225[data$item225 == 9]  <- 4
-data$item225[data$item225 == 10] <- 5
-
-data$item226[data$item226 == 6]  <- 1
-data$item226[data$item226 == 7]  <- 2
-data$item226[data$item226 == 8]  <- 3
-data$item226[data$item226 == 9]  <- 4
-data$item226[data$item226 == 10] <- 5
-
-data$item227[data$item227 == 6]  <- 1
-data$item227[data$item227 == 7]  <- 2
-data$item227[data$item227 == 8]  <- 3
-data$item227[data$item227 == 9]  <- 4
-data$item227[data$item227 == 10] <- 5
-
-data$item228[data$item228 == 6]  <- 1
-data$item228[data$item228 == 7]  <- 2
-data$item228[data$item228 == 8]  <- 3
-data$item228[data$item228 == 9]  <- 4
-data$item228[data$item228 == 10] <- 5
-
-data$item229[data$item229 == 6]  <- 1
-data$item229[data$item229 == 7]  <- 2
-data$item229[data$item229 == 8]  <- 3
-data$item229[data$item229 == 9]  <- 4
-data$item229[data$item229 == 10] <- 5
-
-data$item230[data$item230 == 16] <- 1
-data$item230[data$item230 == 17] <- 2
-data$item230[data$item230 == 18] <- 3
-data$item230[data$item230 == 19] <- 4
-data$item230[data$item230 == 20] <- 5
-
-data$item231[data$item231 == 6]  <- 1
-data$item231[data$item231 == 7]  <- 2
-data$item231[data$item231 == 8]  <- 3
-data$item231[data$item231 == 9]  <- 4
-data$item231[data$item231 == 10] <- 5
-
-data$item232[data$item232 == 6]  <- 1
-data$item232[data$item232 == 7]  <- 2
-data$item232[data$item232 == 8]  <- 3
-data$item232[data$item232 == 9]  <- 4
-data$item232[data$item232 == 10] <- 5
-
-data$item233[data$item233 == 6]  <- 1
-data$item233[data$item233 == 7]  <- 2
-data$item233[data$item233 == 8]  <- 3
-data$item233[data$item233 == 9]  <- 4
-data$item233[data$item233 == 10] <- 5
-
-data$item234[data$item234 == 11]  <- 1
-data$item234[data$item234 == 12]  <- 2
-data$item234[data$item234 == 13]  <- 3
-data$item234[data$item234 == 14]  <- 4
-data$item234[data$item234 == 15]  <- 5
-
-data$item235[data$item235 == 11]  <- 1
-data$item235[data$item235 == 12]  <- 2
-data$item235[data$item235 == 13]  <- 3
-data$item235[data$item235 == 14]  <- 4
-data$item235[data$item235 == 15]  <- 5
-
-data$item236[data$item236 == 11]  <- 1
-data$item236[data$item236 == 12]  <- 2
-data$item236[data$item236 == 13]  <- 3
-data$item236[data$item236 == 14]  <- 4
-data$item236[data$item236 == 15]  <- 5
-
-data$item237[data$item237 == 11]  <- 1
-data$item237[data$item237 == 12]  <- 2
-data$item237[data$item237 == 13]  <- 3
-data$item237[data$item237 == 14]  <- 4
-data$item237[data$item237 == 15]  <- 5
-
-data$item238[data$item238 == 11]  <- 1
-data$item238[data$item238 == 12]  <- 2
-data$item238[data$item238 == 13]  <- 3
-data$item238[data$item238 == 14]  <- 4
-data$item238[data$item238 == 15]  <- 5
-
-data$item239[data$item239 == 11]  <- 1
-data$item239[data$item239 == 12]  <- 2
-data$item239[data$item239 == 13]  <- 3
-data$item239[data$item239 == 14]  <- 4
-data$item239[data$item239 == 15]  <- 5
-
-data$item240[data$item240 == 11]  <- 1
-data$item240[data$item240 == 12]  <- 2
-data$item240[data$item240 == 13]  <- 3
-data$item240[data$item240 == 14]  <- 4
-data$item240[data$item240 == 15]  <- 5
-
-data$item241[data$item241 == 11]  <- 1
-data$item241[data$item241 == 12]  <- 2
-data$item241[data$item241 == 13]  <- 3
-data$item241[data$item241 == 14]  <- 4
-data$item241[data$item241 == 15]  <- 5
-
-data$item242[data$item242 == 6]  <- 1
-data$item242[data$item242 == 7]  <- 2
-data$item242[data$item242 == 8]  <- 3
-data$item242[data$item242 == 9]  <- 4
-data$item242[data$item242 == 10] <- 5
-
-data$item243[data$item243 == 11]  <- 1
-data$item243[data$item243 == 12]  <- 2
-data$item243[data$item243 == 13]  <- 3
-data$item243[data$item243 == 14]  <- 4
-data$item243[data$item243 == 15]  <- 5
-
-data$item244[data$item244 == 11]  <- 1
-data$item244[data$item244 == 12]  <- 2
-data$item244[data$item244 == 13]  <- 3
-data$item244[data$item244 == 14]  <- 4
-data$item244[data$item244 == 15]  <- 5
-
-data$item245[data$item245 == 6]  <- 1
-data$item245[data$item245 == 7]  <- 2
-data$item245[data$item245 == 8]  <- 3
-data$item245[data$item245 == 9]  <- 4
-data$item245[data$item245 == 10] <- 5
-
-data$item246[data$item246 == 11]  <- 1
-data$item246[data$item246 == 12]  <- 2
-data$item246[data$item246 == 13]  <- 3
-data$item246[data$item246 == 14]  <- 4
-data$item246[data$item246 == 15]  <- 5
-
-data$item247[data$item247 == 11]  <- 1
-data$item247[data$item247 == 12]  <- 2
-data$item247[data$item247 == 13]  <- 3
-data$item247[data$item247 == 14]  <- 4
-data$item247[data$item247 == 15]  <- 5
-
-## Attention check
-
-data$item249[data$item249 == 11]  <- 1
-data$item249[data$item249 == 12]  <- 2
-data$item249[data$item249 == 13]  <- 3
-data$item249[data$item249 == 14]  <- 4
-data$item249[data$item249 == 15]  <- 5
-
-data$item250[data$item250 == 11]  <- 1
-data$item250[data$item250 == 12]  <- 2
-data$item250[data$item250 == 13]  <- 3
-data$item250[data$item250 == 14]  <- 4
-data$item250[data$item250 == 15]  <- 5
-
-data$item251[data$item251 == 11]  <- 1
-data$item251[data$item251 == 12]  <- 2
-data$item251[data$item251 == 13]  <- 3
-data$item251[data$item251 == 14]  <- 4
-data$item251[data$item251 == 15]  <- 5
-
-data$item252[data$item252 == 18]  <- 1
-data$item252[data$item252 == 19]  <- 2
-data$item252[data$item252 == 20]  <- 3
-data$item252[data$item252 == 21]  <- 4
-data$item252[data$item252 == 22]  <- 5
-
-data$item253[data$item253 == 11]  <- 1
-data$item253[data$item253 == 12]  <- 2
-data$item253[data$item253 == 13]  <- 3
-data$item253[data$item253 == 14]  <- 4
-data$item253[data$item253 == 15]  <- 5
-
-data$item254[data$item254 == 11]  <- 1
-data$item254[data$item254 == 12]  <- 2
-data$item254[data$item254 == 13]  <- 3
-data$item254[data$item254 == 14]  <- 4
-data$item254[data$item254 == 15]  <- 5
-
-data$item255[data$item255 == 11]  <- 1
-data$item255[data$item255 == 12]  <- 2
-data$item255[data$item255 == 13]  <- 3
-data$item255[data$item255 == 14]  <- 4
-data$item255[data$item255 == 15]  <- 5
-
-data$item256[data$item256 == 11]  <- 1
-data$item256[data$item256 == 12]  <- 2
-data$item256[data$item256 == 13]  <- 3
-data$item256[data$item256 == 14]  <- 4
-data$item256[data$item256 == 15]  <- 5
-
-data$item257[data$item257 == 11]  <- 1
-data$item257[data$item257 == 12]  <- 2
-data$item257[data$item257 == 13]  <- 3
-data$item257[data$item257 == 14]  <- 4
-data$item257[data$item257 == 15]  <- 5
-
-data$item258[data$item258 == 11]  <- 1
-data$item258[data$item258 == 12]  <- 2
-data$item258[data$item258 == 13]  <- 3
-data$item258[data$item258 == 14]  <- 4
-data$item258[data$item258 == 15]  <- 5
-
-data$item259[data$item259 == 11]  <- 1
-data$item259[data$item259 == 12]  <- 2
-data$item259[data$item259 == 13]  <- 3
-data$item259[data$item259 == 14]  <- 4
-data$item259[data$item259 == 15]  <- 5
-
-data$item260[data$item260 == 11]  <- 1
-data$item260[data$item260 == 12]  <- 2
-data$item260[data$item260 == 13]  <- 3
-data$item260[data$item260 == 14]  <- 4
-data$item260[data$item260 == 15]  <- 5
-
-data$item261[data$item261 == 11]  <- 1
-data$item261[data$item261 == 12]  <- 2
-data$item261[data$item261 == 13]  <- 3
-data$item261[data$item261 == 14]  <- 4
-data$item261[data$item261 == 15]  <- 5
-
-data$item262[data$item262 == 11]  <- 1
-data$item262[data$item262 == 12]  <- 2
-data$item262[data$item262 == 13]  <- 3
-data$item262[data$item262 == 14]  <- 4
-data$item262[data$item262 == 15]  <- 5
-
-data$item263[data$item263 == 11]  <- 1
-data$item263[data$item263 == 12]  <- 2
-data$item263[data$item263 == 13]  <- 3
-data$item263[data$item263 == 14]  <- 4
-data$item263[data$item263 == 15]  <- 5
-
-data$item264[data$item264 == 11]  <- 1
-data$item264[data$item264 == 12]  <- 2
-data$item264[data$item264 == 13]  <- 3
-data$item264[data$item264 == 14]  <- 4
-data$item264[data$item264 == 15]  <- 5
-
-data$item265[data$item265 == 11]  <- 1
-data$item265[data$item265 == 12]  <- 2
-data$item265[data$item265 == 13]  <- 3
-data$item265[data$item265 == 14]  <- 4
-data$item265[data$item265 == 15]  <- 5
-
-data$item266[data$item266 == 11]  <- 1
-data$item266[data$item266 == 12]  <- 2
-data$item266[data$item266 == 13]  <- 3
-data$item266[data$item266 == 14]  <- 4
-data$item266[data$item266 == 15]  <- 5
-
-data$item267[data$item267 == 11]  <- 1
-data$item267[data$item267 == 12]  <- 2
-data$item267[data$item267 == 13]  <- 3
-data$item267[data$item267 == 14]  <- 4
-data$item267[data$item267 == 15]  <- 5
-
-data$item268[data$item268 == 11]  <- 1
-data$item268[data$item268 == 12]  <- 2
-data$item268[data$item268 == 13]  <- 3
-data$item268[data$item268 == 14]  <- 4
-data$item268[data$item268 == 15]  <- 5
-
-data$item269[data$item269 == 21]  <- 1
-data$item269[data$item269 == 22]  <- 2
-data$item269[data$item269 == 23]  <- 3
-data$item269[data$item269 == 24]  <- 4
-data$item269[data$item269 == 25]  <- 5
-
-data$item270[data$item270 == 11]  <- 1
-data$item270[data$item270 == 12]  <- 2
-data$item270[data$item270 == 13]  <- 3
-data$item270[data$item270 == 14]  <- 4
-data$item270[data$item270 == 15]  <- 5
-
-data$item271[data$item271 == 11]  <- 1
-data$item271[data$item271 == 12]  <- 2
-data$item271[data$item271 == 13]  <- 3
-data$item271[data$item271 == 14]  <- 4
-data$item271[data$item271 == 15]  <- 5
-
-data$item272[data$item272 == 11]  <- 1
-data$item272[data$item272 == 12]  <- 2
-data$item272[data$item272 == 13]  <- 3
-data$item272[data$item272 == 14]  <- 4
-data$item272[data$item272 == 15]  <- 5
-
-data$item273[data$item273 == 11]  <- 1
-data$item273[data$item273 == 12]  <- 2
-data$item273[data$item273 == 13]  <- 3
-data$item273[data$item273 == 14]  <- 4
-data$item273[data$item273 == 15]  <- 5
-
-data$item274[data$item274 == 11]  <- 1
-data$item274[data$item274 == 12]  <- 2
-data$item274[data$item274 == 13]  <- 3
-data$item274[data$item274 == 14]  <- 4
-data$item274[data$item274 == 15]  <- 5
-
-data$item275[data$item275 == 11]  <- 1
-data$item275[data$item275 == 12]  <- 2
-data$item275[data$item275 == 13]  <- 3
-data$item275[data$item275 == 14]  <- 4
-data$item275[data$item275 == 15]  <- 5
-
-data$item276[data$item276 == 11]  <- 1
-data$item276[data$item276 == 12]  <- 2
-data$item276[data$item276 == 13]  <- 3
-data$item276[data$item276 == 14]  <- 4
-data$item276[data$item276 == 15]  <- 5
-
-data$item277[data$item277 == 11]  <- 1
-data$item277[data$item277 == 12]  <- 2
-data$item277[data$item277 == 13]  <- 3
-data$item277[data$item277 == 14]  <- 4
-data$item277[data$item277 == 15]  <- 5
-
-data$item278[data$item278 == 11]  <- 1
-data$item278[data$item278 == 12]  <- 2
-data$item278[data$item278 == 13]  <- 3
-data$item278[data$item278 == 14]  <- 4
-data$item278[data$item278 == 15]  <- 5
-
-data$item279[data$item279 == 11]  <- 1
-data$item279[data$item279 == 12]  <- 2
-data$item279[data$item279 == 13]  <- 3
-data$item279[data$item279 == 14]  <- 4
-data$item279[data$item279 == 15]  <- 5
-
-data$item280[data$item280 == 11]  <- 1
-data$item280[data$item280 == 12]  <- 2
-data$item280[data$item280 == 13]  <- 3
-data$item280[data$item280 == 14]  <- 4
-data$item280[data$item280 == 15]  <- 5
-
-data$item281[data$item281 == 11]  <- 1
-data$item281[data$item281 == 12]  <- 2
-data$item281[data$item281 == 13]  <- 3
-data$item281[data$item281 == 14]  <- 4
-data$item281[data$item281 == 15]  <- 5
-
-data$item282[data$item282 == 11]  <- 1
-data$item282[data$item282 == 12]  <- 2
-data$item282[data$item282 == 13]  <- 3
-data$item282[data$item282 == 14]  <- 4
-data$item282[data$item282 == 15]  <- 5
-
-data$item283[data$item283 == 11]  <- 1
-data$item283[data$item283 == 12]  <- 2
-data$item283[data$item283 == 13]  <- 3
-data$item283[data$item283 == 14]  <- 4
-data$item283[data$item283 == 15]  <- 5
-
-data$item284[data$item284 == 11]  <- 1
-data$item284[data$item284 == 12]  <- 2
-data$item284[data$item284 == 13]  <- 3
-data$item284[data$item284 == 14]  <- 4
-data$item284[data$item284 == 15]  <- 5
-
-data$item285[data$item285 == 11]  <- 1
-data$item285[data$item285 == 12]  <- 2
-data$item285[data$item285 == 13]  <- 3
-data$item285[data$item285 == 14]  <- 4
-data$item285[data$item285 == 15]  <- 5
-
-data$item286[data$item286 == 11]  <- 1
-data$item286[data$item286 == 12]  <- 2
-data$item286[data$item286 == 13]  <- 3
-data$item286[data$item286 == 14]  <- 4
-data$item286[data$item286 == 15]  <- 5
-
-data$item287[data$item287 == 11]  <- 1
-data$item287[data$item287 == 12]  <- 2
-data$item287[data$item287 == 13]  <- 3
-data$item287[data$item287 == 14]  <- 4
-data$item287[data$item287 == 15]  <- 5
-
-data$item288[data$item288 == 9]   <- 1
-data$item288[data$item288 == 10]  <- 2
-data$item288[data$item288 == 11]  <- 3
-data$item288[data$item288 == 12]  <- 4
-data$item288[data$item288 == 13]  <- 5
-
-data$item289[data$item289 == 11]  <- 1
-data$item289[data$item289 == 12]  <- 2
-data$item289[data$item289 == 13]  <- 3
-data$item289[data$item289 == 14]  <- 4
-data$item289[data$item289 == 15]  <- 5
-
-data$item290[data$item290 == 6]  <- 1
-data$item290[data$item290 == 7]  <- 2
-data$item290[data$item290 == 8]  <- 3
-data$item290[data$item290 == 9]  <- 4
-data$item290[data$item290 == 10] <- 5
-
-data$item291[data$item291 == 6]  <- 1
-data$item291[data$item291 == 7]  <- 2
-data$item291[data$item291 == 8]  <- 3
-data$item291[data$item291 == 9]  <- 4
-data$item291[data$item291 == 10] <- 5
-
-data$item292[data$item292 == 6]  <- 1
-data$item292[data$item292 == 7]  <- 2
-data$item292[data$item292 == 8]  <- 3
-data$item292[data$item292 == 9]  <- 4
-data$item292[data$item292 == 10] <- 5
-
-data$item293[data$item293 == 6]  <- 1
-data$item293[data$item293 == 7]  <- 2
-data$item293[data$item293 == 8]  <- 3
-data$item293[data$item293 == 9]  <- 4
-data$item293[data$item293 == 10] <- 5
-
-data$item294[data$item294 == 6]  <- 1
-data$item294[data$item294 == 7]  <- 2
-data$item294[data$item294 == 8]  <- 3
-data$item294[data$item294 == 9]  <- 4
-data$item294[data$item294 == 10] <- 5
-
-data$item295[data$item295 == 6]  <- 1
-data$item295[data$item295 == 7]  <- 2
-data$item295[data$item295 == 8]  <- 3
-data$item295[data$item295 == 9]  <- 4
-data$item295[data$item295 == 10] <- 5
-
-data$item296[data$item296 == 11]  <- 1
-data$item296[data$item296 == 12]  <- 2
-data$item296[data$item296 == 13]  <- 3
-data$item296[data$item296 == 14]  <- 4
-data$item296[data$item296 == 15]  <- 5
-
-data$item297[data$item297 == 4]  <- 1
-data$item297[data$item297 == 5]  <- 2
-data$item297[data$item297 == 6]  <- 3
-data$item297[data$item297 == 7]  <- 4
-data$item297[data$item297 == 8]  <- 5
-
-data$item298[data$item298 == 11]  <- 1
-data$item298[data$item298 == 12]  <- 2
-data$item298[data$item298 == 13]  <- 3
-data$item298[data$item298 == 14]  <- 4
-data$item298[data$item298 == 15]  <- 5
-
-data$item299[data$item299 == 11]  <- 1
-data$item299[data$item299 == 12]  <- 2
-data$item299[data$item299 == 13]  <- 3
-data$item299[data$item299 == 14]  <- 4
-data$item299[data$item299 == 15]  <- 5
-
-data$item300[data$item300 == 11]  <- 1
-data$item300[data$item300 == 12]  <- 2
-data$item300[data$item300 == 13]  <- 3
-data$item300[data$item300 == 14]  <- 4
-data$item300[data$item300 == 15]  <- 5
-
-data$item301[data$item301 == 11]  <- 1
-data$item301[data$item301 == 12]  <- 2
-data$item301[data$item301 == 13]  <- 3
-data$item301[data$item301 == 14]  <- 4
-data$item301[data$item301 == 15]  <- 5
-
-data$item302[data$item302 == 11]  <- 1
-data$item302[data$item302 == 12]  <- 2
-data$item302[data$item302 == 13]  <- 3
-data$item302[data$item302 == 14]  <- 4
-data$item302[data$item302 == 15]  <- 5
-
-data$item303[data$item303 == 11]  <- 1
-data$item303[data$item303 == 12]  <- 2
-data$item303[data$item303 == 13]  <- 3
-data$item303[data$item303 == 14]  <- 4
-data$item303[data$item303 == 15]  <- 5
-
-data$item304[data$item304 == 11]  <- 1
-data$item304[data$item304 == 12]  <- 2
-data$item304[data$item304 == 13]  <- 3
-data$item304[data$item304 == 14]  <- 4
-data$item304[data$item304 == 15]  <- 5
-
-data$item305[data$item305 == 6]  <- 1
-data$item305[data$item305 == 7]  <- 2
-data$item305[data$item305 == 8]  <- 3
-data$item305[data$item305 == 9]  <- 4
-data$item305[data$item305 == 10] <- 5
-
-data$item306[data$item306 == 6]  <- 1
-data$item306[data$item306 == 7]  <- 2
-data$item306[data$item306 == 8]  <- 3
-data$item306[data$item306 == 9]  <- 4
-data$item306[data$item306 == 10] <- 5
-
-data$item307[data$item307 == 6]  <- 1
-data$item307[data$item307 == 7]  <- 2
-data$item307[data$item307 == 8]  <- 3
-data$item307[data$item307 == 9]  <- 4
-data$item307[data$item307 == 10] <- 5
-
-## Attention check
-
-data$item309[data$item309 == 16]  <- 1
-data$item309[data$item309 == 17]  <- 2
-data$item309[data$item309 == 18]  <- 3
-data$item309[data$item309 == 19]  <- 4
-data$item309[data$item309 == 20]  <- 5
-
-data$item310[data$item310 == 6]  <- 1
-data$item310[data$item310 == 7]  <- 2
-data$item310[data$item310 == 8]  <- 3
-data$item310[data$item310 == 9]  <- 4
-data$item310[data$item310 == 10] <- 5
-
-data$item311[data$item311 == 6]  <- 1
-data$item311[data$item311 == 7]  <- 2
-data$item311[data$item311 == 8]  <- 3
-data$item311[data$item311 == 9]  <- 4
-data$item311[data$item311 == 10] <- 5
-
-data$item312[data$item312 == 6]  <- 1
-data$item312[data$item312 == 7]  <- 2
-data$item312[data$item312 == 8]  <- 3
-data$item312[data$item312 == 9]  <- 4
-data$item312[data$item312 == 10] <- 5
-
-data$item313[data$item313 == 6]  <- 1
-data$item313[data$item313 == 7]  <- 2
-data$item313[data$item313 == 8]  <- 3
-data$item313[data$item313 == 9]  <- 4
-data$item313[data$item313 == 10] <- 5
-
-data$item314[data$item314 == 6]  <- 1
-data$item314[data$item314 == 7]  <- 2
-data$item314[data$item314 == 8]  <- 3
-data$item314[data$item314 == 9]  <- 4
-data$item314[data$item314 == 10] <- 5
-
-data$item315[data$item315 == 6]  <- 1
-data$item315[data$item315 == 7]  <- 2
-data$item315[data$item315 == 8]  <- 3
-data$item315[data$item315 == 9]  <- 4
-data$item315[data$item315 == 10] <- 5
-
-data$item316[data$item316 == 16]  <- 1
-data$item316[data$item316 == 17]  <- 2
-data$item316[data$item316 == 18]  <- 3
-data$item316[data$item316 == 19]  <- 4
-data$item316[data$item316 == 20]  <- 5
-
-data$item317[data$item317 == 6]  <- 1
-data$item317[data$item317 == 7]  <- 2
-data$item317[data$item317 == 8]  <- 3
-data$item317[data$item317 == 9]  <- 4
-data$item317[data$item317 == 10] <- 5
-
-data$item318[data$item318 == 6]  <- 1
-data$item318[data$item318 == 7]  <- 2
-data$item318[data$item318 == 8]  <- 3
-data$item318[data$item318 == 9]  <- 4
-data$item318[data$item318 == 10] <- 5
-
-data$item319[data$item319 == 6]  <- 1
-data$item319[data$item319 == 7]  <- 2
-data$item319[data$item319 == 8]  <- 3
-data$item319[data$item319 == 9]  <- 4
-data$item319[data$item319 == 10] <- 5
-
-data$item320[data$item320 == 11] <- 1
-data$item320[data$item320 == 12] <- 2
-data$item320[data$item320 == 13] <- 3
-data$item320[data$item320 == 14] <- 4
-data$item320[data$item320 == 15] <- 5
-
-data$item321[data$item321 == 11] <- 1
-data$item321[data$item321 == 12] <- 2
-data$item321[data$item321 == 13] <- 3
-data$item321[data$item321 == 14] <- 4
-data$item321[data$item321 == 15] <- 5
-
-data$item322[data$item322 == 11] <- 1
-data$item322[data$item322 == 12] <- 2
-data$item322[data$item322 == 13] <- 3
-data$item322[data$item322 == 14] <- 4
-data$item322[data$item322 == 15] <- 5
-
-data$item323[data$item323 == 11] <- 1
-data$item323[data$item323 == 12] <- 2
-data$item323[data$item323 == 13] <- 3
-data$item323[data$item323 == 14] <- 4
-data$item323[data$item323 == 15] <- 5
-
-data$item324[data$item324 == 11] <- 1
-data$item324[data$item324 == 12] <- 2
-data$item324[data$item324 == 13] <- 3
-data$item324[data$item324 == 14] <- 4
-data$item324[data$item324 == 15] <- 5
-
-data$item325[data$item325 == 11] <- 1
-data$item325[data$item325 == 12] <- 2
-data$item325[data$item325 == 13] <- 3
-data$item325[data$item325 == 14] <- 4
-data$item325[data$item325 == 15] <- 5
-
-data$item326[data$item326 == 11] <- 1
-data$item326[data$item326 == 12] <- 2
-data$item326[data$item326 == 13] <- 3
-data$item326[data$item326 == 14] <- 4
-data$item326[data$item326 == 15] <- 5
-
-data$item327[data$item327 == 11] <- 1
-data$item327[data$item327 == 12] <- 2
-data$item327[data$item327 == 13] <- 3
-data$item327[data$item327 == 14] <- 4
-data$item327[data$item327 == 15] <- 5
-
-data$item328[data$item328 == 6]  <- 1
-data$item328[data$item328 == 7]  <- 2
-data$item328[data$item328 == 8]  <- 3
-data$item328[data$item328 == 9]  <- 4
-data$item328[data$item328 == 10] <- 5
-
-data$item329[data$item329 == 11] <- 1
-data$item329[data$item329 == 12] <- 2
-data$item329[data$item329 == 13] <- 3
-data$item329[data$item329 == 14] <- 4
-data$item329[data$item329 == 15] <- 5
-
-data$item330[data$item330 == 11] <- 1
-data$item330[data$item330 == 12] <- 2
-data$item330[data$item330 == 13] <- 3
-data$item330[data$item330 == 14] <- 4
-data$item330[data$item330 == 15] <- 5
-
-data$item331[data$item331 == 6]  <- 1
-data$item331[data$item331 == 7]  <- 2
-data$item331[data$item331 == 8]  <- 3
-data$item331[data$item331 == 9]  <- 4
-data$item331[data$item331 == 10] <- 5
-
-data$item332[data$item332 == 11] <- 1
-data$item332[data$item332 == 12] <- 2
-data$item332[data$item332 == 13] <- 3
-data$item332[data$item332 == 14] <- 4
-data$item332[data$item332 == 15] <- 5
-
-data$item333[data$item333 == 11] <- 1
-data$item333[data$item333 == 12] <- 2
-data$item333[data$item333 == 13] <- 3
-data$item333[data$item333 == 14] <- 4
-data$item333[data$item333 == 15] <- 5
-
-data$item334[data$item334 == 11] <- 1
-data$item334[data$item334 == 12] <- 2
-data$item334[data$item334 == 13] <- 3
-data$item334[data$item334 == 14] <- 4
-data$item334[data$item334 == 15] <- 5
-
-data$item335[data$item335 == 11] <- 1
-data$item335[data$item335 == 12] <- 2
-data$item335[data$item335 == 13] <- 3
-data$item335[data$item335 == 14] <- 4
-data$item335[data$item335 == 15] <- 5
-
-data$item336[data$item336 == 11] <- 1
-data$item336[data$item336 == 12] <- 2
-data$item336[data$item336 == 13] <- 3
-data$item336[data$item336 == 14] <- 4
-data$item336[data$item336 == 15] <- 5
-
-data$item337[data$item337 == 18] <- 1
-data$item337[data$item337 == 19] <- 2
-data$item337[data$item337 == 20] <- 3
-data$item337[data$item337 == 21] <- 4
-data$item337[data$item337 == 22] <- 5
-
-data$item338[data$item338 == 11] <- 1
-data$item338[data$item338 == 12] <- 2
-data$item338[data$item338 == 13] <- 3
-data$item338[data$item338 == 14] <- 4
-data$item338[data$item338 == 15] <- 5
-
-data$item339[data$item339 == 11] <- 1
-data$item339[data$item339 == 12] <- 2
-data$item339[data$item339 == 13] <- 3
-data$item339[data$item339 == 14] <- 4
-data$item339[data$item339 == 15] <- 5
-
-data$item340[data$item340 == 11] <- 1
-data$item340[data$item340 == 12] <- 2
-data$item340[data$item340 == 13] <- 3
-data$item340[data$item340 == 14] <- 4
-data$item340[data$item340 == 15] <- 5
-
-data$item341[data$item341 == 11] <- 1
-data$item341[data$item341 == 12] <- 2
-data$item341[data$item341 == 13] <- 3
-data$item341[data$item341 == 14] <- 4
-data$item341[data$item341 == 15] <- 5
-
-data$item342[data$item342 == 11] <- 1
-data$item342[data$item342 == 12] <- 2
-data$item342[data$item342 == 13] <- 3
-data$item342[data$item342 == 14] <- 4
-data$item342[data$item342 == 15] <- 5
-
-data$item343[data$item343 == 11] <- 1
-data$item343[data$item343 == 12] <- 2
-data$item343[data$item343 == 13] <- 3
-data$item343[data$item343 == 14] <- 4
-data$item343[data$item343 == 15] <- 5
-
-data$item344[data$item344 == 11] <- 1
-data$item344[data$item344 == 12] <- 2
-data$item344[data$item344 == 13] <- 3
-data$item344[data$item344 == 14] <- 4
-data$item344[data$item344 == 15] <- 5
-
-data$item345[data$item345 == 11] <- 1
-data$item345[data$item345 == 12] <- 2
-data$item345[data$item345 == 13] <- 3
-data$item345[data$item345 == 14] <- 4
-data$item345[data$item345 == 15] <- 5
-
-data$item346[data$item346 == 11] <- 1
-data$item346[data$item346 == 12] <- 2
-data$item346[data$item346 == 13] <- 3
-data$item346[data$item346 == 14] <- 4
-data$item346[data$item346 == 15] <- 5
-
-data$item347[data$item347 == 11] <- 1
-data$item347[data$item347 == 12] <- 2
-data$item347[data$item347 == 13] <- 3
-data$item347[data$item347 == 14] <- 4
-data$item347[data$item347 == 15] <- 5
-
-data$item348[data$item348 == 11] <- 1
-data$item348[data$item348 == 12] <- 2
-data$item348[data$item348 == 13] <- 3
-data$item348[data$item348 == 14] <- 4
-data$item348[data$item348 == 15] <- 5
-
-data$item349[data$item349 == 11] <- 1
-data$item349[data$item349 == 12] <- 2
-data$item349[data$item349 == 13] <- 3
-data$item349[data$item349 == 14] <- 4
-data$item349[data$item349 == 15] <- 5
-
-data$item350[data$item350 == 11] <- 1
-data$item350[data$item350 == 12] <- 2
-data$item350[data$item350 == 13] <- 3
-data$item350[data$item350 == 14] <- 4
-data$item350[data$item350 == 15] <- 5
-
-data$item351[data$item351 == 11] <- 1
-data$item351[data$item351 == 12] <- 2
-data$item351[data$item351 == 13] <- 3
-data$item351[data$item351 == 14] <- 4
-data$item351[data$item351 == 15] <- 5
-
-data$item352[data$item352 == 11] <- 1
-data$item352[data$item352 == 12] <- 2
-data$item352[data$item352 == 13] <- 3
-data$item352[data$item352 == 14] <- 4
-data$item352[data$item352 == 15] <- 5
-
-data$item353[data$item353 == 11] <- 1
-data$item353[data$item353 == 12] <- 2
-data$item353[data$item353 == 13] <- 3
-data$item353[data$item353 == 14] <- 4
-data$item353[data$item353 == 15] <- 5
-
-data$item354[data$item354 == 21] <- 1
-data$item354[data$item354 == 22] <- 2
-data$item354[data$item354 == 23] <- 3
-data$item354[data$item354 == 24] <- 4
-data$item354[data$item354 == 25] <- 5
-
-data$item355[data$item355 == 11] <- 1
-data$item355[data$item355 == 12] <- 2
-data$item355[data$item355 == 13] <- 3
-data$item355[data$item355 == 14] <- 4
-data$item355[data$item355 == 15] <- 5
-
-data$item356[data$item356 == 11] <- 1
-data$item356[data$item356 == 12] <- 2
-data$item356[data$item356 == 13] <- 3
-data$item356[data$item356 == 14] <- 4
-data$item356[data$item356 == 15] <- 5
-
-data$item357[data$item357 == 11] <- 1
-data$item357[data$item357 == 12] <- 2
-data$item357[data$item357 == 13] <- 3
-data$item357[data$item357 == 14] <- 4
-data$item357[data$item357 == 15] <- 5
-
-data$item358[data$item358 == 11] <- 1
-data$item358[data$item358 == 12] <- 2
-data$item358[data$item358 == 13] <- 3
-data$item358[data$item358 == 14] <- 4
-data$item358[data$item358 == 15] <- 5
-
-data$item359[data$item359 == 11] <- 1
-data$item359[data$item359 == 12] <- 2
-data$item359[data$item359 == 13] <- 3
-data$item359[data$item359 == 14] <- 4
-data$item359[data$item359 == 15] <- 5
-
-data$item360[data$item360 == 11] <- 1
-data$item360[data$item360 == 12] <- 2
-data$item360[data$item360 == 13] <- 3
-data$item360[data$item360 == 14] <- 4
-data$item360[data$item360 == 15] <- 5
-
-data$item361[data$item361 == 11] <- 1
-data$item361[data$item361 == 12] <- 2
-data$item361[data$item361 == 13] <- 3
-data$item361[data$item361 == 14] <- 4
-data$item361[data$item361 == 15] <- 5
-
-data$item362[data$item362 == 11] <- 1
-data$item362[data$item362 == 12] <- 2
-data$item362[data$item362 == 13] <- 3
-data$item362[data$item362 == 14] <- 4
-data$item362[data$item362 == 15] <- 5
-
-data$item363[data$item363 == 11] <- 1
-data$item363[data$item363 == 12] <- 2
-data$item363[data$item363 == 13] <- 3
-data$item363[data$item363 == 14] <- 4
-data$item363[data$item363 == 15] <- 5
-
-data$item364[data$item364 == 11] <- 1
-data$item364[data$item364 == 12] <- 2
-data$item364[data$item364 == 13] <- 3
-data$item364[data$item364 == 14] <- 4
-data$item364[data$item364 == 15] <- 5
-
-data$item365[data$item365 == 11] <- 1
-data$item365[data$item365 == 12] <- 2
-data$item365[data$item365 == 13] <- 3
-data$item365[data$item365 == 14] <- 4
-data$item365[data$item365 == 15] <- 5
-
-data$item366[data$item366 == 11] <- 1
-data$item366[data$item366 == 12] <- 2
-data$item366[data$item366 == 13] <- 3
-data$item366[data$item366 == 14] <- 4
-data$item366[data$item366 == 15] <- 5
-
-data$item367[data$item367 == 11] <- 1
-data$item367[data$item367 == 12] <- 2
-data$item367[data$item367 == 13] <- 3
-data$item367[data$item367 == 14] <- 4
-data$item367[data$item367 == 15] <- 5
-
-data$item368[data$item368 == 11] <- 1
-data$item368[data$item368 == 12] <- 2
-data$item368[data$item368 == 13] <- 3
-data$item368[data$item368 == 14] <- 4
-data$item368[data$item368 == 15] <- 5
-
-data$item369[data$item369 == 11] <- 1
-data$item369[data$item369 == 12] <- 2
-data$item369[data$item369 == 13] <- 3
-data$item369[data$item369 == 14] <- 4
-data$item369[data$item369 == 15] <- 5
-
-data$item370[data$item370 == 11] <- 1
-data$item370[data$item370 == 12] <- 2
-data$item370[data$item370 == 13] <- 3
-data$item370[data$item370 == 14] <- 4
-data$item370[data$item370 == 15] <- 5
-
-data$item371[data$item371 == 11] <- 1
-data$item371[data$item371 == 12] <- 2
-data$item371[data$item371 == 13] <- 3
-data$item371[data$item371 == 14] <- 4
-data$item371[data$item371 == 15] <- 5
-
-data$item372[data$item372 == 11] <- 1
-data$item372[data$item372 == 12] <- 2
-data$item372[data$item372 == 13] <- 3
-data$item372[data$item372 == 14] <- 4
-data$item372[data$item372 == 15] <- 5
-
-write.csv(psych::describe(data[18:372]), "checkingrecodes.csv")
+```{r generalrecodes, include=FALSE}
+
+source("recodescript.R", local = knitr::knit_global())
 

### 2022-08-29 Submission_ResourceCount.Rmd
sum of resource challenge hindrance

@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+```{r analysis-preferences, echo=FALSE}
+
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed, echo=FALSE, warning=FALSE, message=FALSE)
+
 ```
+
 Next steps (thoughts from 8/24):
@@
 
+```{r study1}
+
+temp <- read.csv("initial_data_screen.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script
+
+x <- paste("item", sep="",1:404)
+y <- t(temp[2,])
+                                        ## decluttering Qualtrics excess
+data <- temp[-c(1:3),]                                           ## Getting rid of all 3 weird Qualtrics rows
+colnames(data) <- x
+
+incomplete <- read.csv("inprogress.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script
+
+data2 <- incomplete[-c(1:2),-c(10,12,16,113,199,285,371,379,400, 406:411)]
+
+data3 <- as.data.frame(cbind(data2$V8,data2$V9,data2$V1,data2$V1,data2$V1,data2$V1,data2$V1,data2$V1,data2))
+
+colnames(data3) <- x
+
+rm(x, y, temp)
+
+use <- rbind(data,data3)
+
+## STILL NEED FILE WITH BAD RESPONDENTS IDENTIFIED (E.G., Item_18=2, na > 200, longstring > 20, CARELESS CHECKS > 1)
+
+library(careless)
+use$careless_long <- longstring(use[18:399])
+use$missing <- rowSums(is.na(use[18:404]))
+
+different <- use[ which(use$item18 == 2 | use$careless_long > 20 | use$missing > 200), ]
+
+attention <- use[which(use$item61 == 5 & use$item145 == 5 & use$item248 == 2 & use$item308 == 3), ]
+
+data <- data.frame(lapply(attention, function(x) as.numeric(as.character(x))))
+data <- data[,c(1:404)]
+
+numtot <- nrow(use)
+numkicked <- nrow(different)
+numvalid <- nrow(data)
+
 ```
 
-## Including Plots
+```{r demos}
 
-You can also embed plots, for example:
+a <- descr::freq(use$item401, plot=FALSE)
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+use$item402[use$item402 == "Female " | use$item402 == "female" | use$item402 == "FEMALE" | use$item402 == "Woman" | use$item402 == "Mujer" | use$item402 == "feminine" | use$item402 == "fEMALE" | use$item402 == "F" | use$item402 == "Femenale" | use$item402 == "feminino" | use$item402 == "female " | use$item402 == "Fem" | use$item402 == "Feminine" | use$item402 == "feminine" | use$item402 == "WOMAN" | use$item402 == "Femal" | use$item402 == "femenine" | use$item402 == "Femenine" | use$item402 == "femenino" | use$item402 == "woman"]  <- "Female"
+
+use$item402[use$item402 == "gerente" | use$item402 == "M" | use$item402 == "Make" | use$item402 == "Mal" | use$item402 == "male" | use$item402 == "MALE" | use$item402 == "male" | use$item402 == "Male" | use$item402 == "mals" | use$item402 == "man" | use$item402 == "masculine" | use$item402 == "Masculine" | use$item402 == "Man" | use$item402 == "mals " | use$item402 == "male " | use$item402 == "Male "]  <- "Male"
+
+b <- descr::freq(use$item402, plot=FALSE)
+
+##Job title
+library(labourR)
+
+#ESCO/ISCO classification using the labourR package
+#ISCO = International Standard Classification of Occupations
+
+attention$id <- 1:nrow(attention) #adds unique identifier to satisfy inane requirement of classify_occupation()
+
+ISCO <- classify_occupation(attention, text_col = 'item400', isco_level = 1)
+
+m3 <-merge(attention, ISCO, by.x = "id", by.y = "id", all.x = TRUE)
+
+c <- descr::freq(m3$preferredLabel, plot=FALSE)
+
+knowledge <- data[ which(m3$iscoGroup == "1" | m3$iscoGroup == "2"), ]
+service <- data[ which(m3$iscoGroup == "3" | m3$iscoGroup == "4" | m3$iscoGroup == "5" | m3$iscoGroup == "6" | m3$iscoGroup == "7" | m3$iscoGroup == "8" | m3$iscoGroup == "9"), ]
+
+data$item403[data$item403 == 2000]  <- 20
+
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+```{r generalrecodes, include=FALSE}
+
+source("recodescript.R", local = knitr::knit_global())
+
+```
+
+There were `r nrow(data)` retained respondents.
+
+```{r keeping45}
+
+## need to run "recodescript.R" prior to this if running chunk-by-chunk
+
+## variables of interest (resource, challenge, hindrance): 118:372
+
+library(dplyr)
+
+data22 <- data %>% 
+mutate_at(vars(118:372),
+function(x) recode(x,
+1==NA, 
+2==NA,
+3==NA,
+4==4,
+5==5))
+
+## attention checks: 145, 248, 308
+
+data22$resource <- rowSums(data22[c(118:144,146:202)], na.rm=TRUE)
+data22$hindrance <- rowSums(data22[c(203:247,249:287)], na.rm=TRUE)
+data22$challenge <- rowSums(data22[c(288:307,309:372)], na.rm=TRUE)
+
+cor(data22[405:407], use="all.obs")   ## something to be told with resources and challenges
+
+data22$burnout      <- rowMeans(data22[c(373:376)], na.rm=TRUE)
+data22$stress       <- rowMeans(data22[c(377:379)], na.rm=TRUE)
+data22$engagement   <- rowMeans(data22[c(380:399)], na.rm=TRUE)        ## probably need to recode some
+
+cor(data22[405:410], use="all.obs")   ## something to be told with resources and challenges
+
+```

### 2022-08-29 recodescript.R

@@ -1,0 +1,1527 @@
+## Qualtrics data all messed up
+
+data$item82[data$item82 == 8]  <- 1
+data$item82[data$item82 == 9]  <- 2
+data$item82[data$item82 == 10] <- 3
+data$item82[data$item82 == 11] <- 4
+data$item82[data$item82 == 12] <- 5
+
+data$item118[data$item118 == 9]  <- 1
+data$item118[data$item118 == 10] <- 2
+data$item118[data$item118 == 11] <- 3
+data$item118[data$item118 == 12] <- 4
+data$item118[data$item118 == 13] <- 5
+
+data$item119[data$item119 == 11] <- 1
+data$item119[data$item119 == 12] <- 2
+data$item119[data$item119 == 13] <- 3
+data$item119[data$item119 == 14] <- 4
+data$item119[data$item119 == 15] <- 5
+
+data$item120[data$item120 == 6]  <- 1
+data$item120[data$item120 == 7]  <- 2
+data$item120[data$item120 == 8]  <- 3
+data$item120[data$item120 == 9]  <- 4
+data$item120[data$item120 == 10] <- 5
+
+data$item121[data$item121 == 6]  <- 1
+data$item121[data$item121 == 7]  <- 2
+data$item121[data$item121 == 8]  <- 3
+data$item121[data$item121 == 9]  <- 4
+data$item121[data$item121 == 10] <- 5
+
+data$item122[data$item122 == 6]  <- 1
+data$item122[data$item122 == 7]  <- 2
+data$item122[data$item122 == 8]  <- 3
+data$item122[data$item122 == 9]  <- 4
+data$item122[data$item122 == 10] <- 5
+
+data$item123[data$item123 == 6]  <- 1
+data$item123[data$item123 == 7]  <- 2
+data$item123[data$item123 == 8]  <- 3
+data$item123[data$item123 == 9]  <- 4
+data$item123[data$item123 == 10] <- 5
+
+data$item124[data$item124 == 6]  <- 1
+data$item124[data$item124 == 7]  <- 2
+data$item124[data$item124 == 8]  <- 3
+data$item124[data$item124 == 9]  <- 4
+data$item124[data$item124 == 10] <- 5
+
+data$item125[data$item125 == 6]  <- 1
+data$item125[data$item125 == 7]  <- 2
+data$item125[data$item125 == 8]  <- 3
+data$item125[data$item125 == 9]  <- 4
+data$item125[data$item125 == 10] <- 5
+
[…]

### 2022-09-02 SIOP2023/SIOP_PROCESS.Rmd
Updated introduction. See notes near end of intro for next steps.

@@
 Specifically, we explore the interaction between perceptions of job demands and resources on the outcome of stress across a wide range of occupations.
-
 Here, respondents made a series of evaluations that used: direct O\*Net terminology (both descriptor and response option), and JD-R influenced ratings of demand and hindrance stressors.
@@
 *Demands*, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure; @demerouti2001job).
+
 Cognitively, the perception of an element of one's job as a resource or demand activates one of two unique processes: health impairment (resulting from demands) or motivation [resulting from resources; @bakker2014job].
@@
 @searle2015merits note that much of our research on workplace demands is based on apriori classifications of demands.
+For instance, we assume that generally, time pressure is a negative demand on an employee.
 However, the stress experience, or process, described early on by @lazarus1984stress is grounded in the assumption that individual appraisals of stressors/demands vary.
@@
 This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes is not appraised as favorable [@lazarus1984stress].
-The stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.
+As such, the stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.
 
-We next consider the (limited) empirical evidence on this topic.
-First, some relatively recent research suggests that job demands and resources may not be universally appraised or assigned as such.
-Starting with job demands, @webster2011extending, for example, studied workload, role ambiguity, and role conflict demands, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees.
-While their study did include resources, it nonetheless points to individual differences on how people perceive stressors at work.
-Although part of a much larger study on retirement, @sonnega_comparison_2018 compared self-reported (subjective) ratings of degree of physical demand, stress, and need for intense concentration from the Health and Retirement Study with objective ratings from O*Net.
-Correlations physical demand (r = .52), stress (r = .10), and need for intense concentration (r = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than assumed.
-Next considering resources, @schmitz_interpreting_2019 also captured subjective and objective resources in their study of retirement.
-Correlations of composite variables for the resources of autonomy (r = .12.
+We next consider the empirical evidence on the subjective nature of demands and resources.
+First, as hinted at above, some research suggests that job demands and resources may not be universally appraised or assigned as such.
+Starting with job demands, @webster2011extending  studied workload, role ambiguity, and role conflict demands, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being *both* a challenge and hindrance to different degrees.
+While their study not did include resources, it documents individual differences in how people perceive stressors at work.
+Although not the primary focus of their paper, @sonnega_comparison_2018 compared self-reported (subjective) ratings of degree of physical demand, stress, and need for intense concentration from the Health and Retirement Study with objective ratings from O*Net.
+Correlations physical demand (r = .52), stress (r = .10), and need for intense concentration (r = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than we tend to think.
+While the above two studies provide evidence for variability in perception of demands, @schmitz_interpreting_2019 captured subjective and objective resources in their study of retirement.
+Correlations of composite variables between subjective and objective measures for the resources of autonomy (r = .12.
 p > .01), recognition of work (r = .07, p > .01), and decision freedom (r = .08, p > .01), while significant, certainly do not reflect high levels of overlap.
@@
 It is quite possible that one person experiences high work pressure (commonly cited as a demand in the literature) as a hindrance stressor and thus experiences strain, and another thrives in a fast-paced pressured role and would thus find the environment motivating.
-Here, we asked respondents to rate all of the job characterstics in terms of hindrances and resources.
-consider the here whether perceptions of demands (specifically hindrance demands) and stress is
+Here, we asked respondents to rate all of the job characteristics in terms of hindrances, challenges, and resources.
 
-## Why use the O\*Net Resource?
+## Value of exploring the O\*Net Resource
 
-Originally, the Advisory Panel for the Dictionary of Occupational Titles recommended a system that would “…promote the effective education, training, counseling, and employment of the American workforce.
-It should accomplish its purpose by providing a database system that identifies, defines, classifies, and describes occupations in the economy in an accessible and flexible manner” (@advisory1993new, p.
-6).
-The result was the now commonly used O\*NET.
-The Occupational Information Network (O\*NET; onetonline.org) contains a comprehensive description of occupations [@peterson2001understanding].
+First, the Occupational Information Network (O\*NET; onetonline.org) contains a comprehensive description of occupations [@peterson2001understanding].
 This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated.
-In fact, there was a call to work with experienced I/O psychologists over the summer to update the content for the [Industrial and Organizational Psychologist listing on O\*Net](https://www.onetonline.org/link/summary/19-3032.00).
-These data, and the tools provided for free on the website (e.g., Career Exploration Tools, “My Next Move for Veterans”, “My Next Move”, Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
+These data, and the tools provided for free on the website (e.g., Career Exploration Tools, “My Next Move”, Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
 It is also useful to employers by providing them with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
+We utilized statements taken from O\*NET ["activity" and "context" classifications](https://www.O\*NETonline.org/find/descriptor/result/4.A.1.b.3) (e.g., items related to information input, interacting with others, physical work conditions, structural job characteristics).
 
-Of greatest interest here are statements taken from O\*NET ["activity" and "context" classifications](https://www.O\*NETonline.org/find/descriptor/result/4.A.1.b.3) (e.g., items related to information input, interacting with others, physical work conditions, structural job characteristics).
-One of the first and basic questions is whether or not the categorical examples of "resources" and "demands" described in the Job Demands-Resources Theory [@demerouti2001job], for example, are generally deemed resources or demands as we objectively define them.
-The next logical question surrounds how "universal" such ratings are.
-For instance, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.
-A second study extends the findings from Study 1 to a potentially key moderator - job categories/classifications, examining whether ratings of resources, challenge- and hindrance demands differ by job classification.
+# Current Study and Hypotheses
+
+These data were taken from a larger study on JD-R theory as it applies to O\*NET items.
+Our specific interest in the current study is in whether or not *perceptions* of hindrance demands are postitively related to perceived stress, and whether or not this relationship is moderated by perceived resources.
+The Job demands-Resources theory would suggest resources would buffer this relationship.
+We do have some existing evidence that this occurs with other outcomes.
+For example, Tadic et al.
+(2015) found that daily hindrance job demands were negatively related to both positive affect and engagement in a sample of primary school teachers.
+Daily job resources, in this sample, buffered the relationships between hindrances and affect and engagement.
+Here, we propose that perceived resources generally, as opposed to daily, would also buffer the relationship between perceived hindrance stressors and, in this, case, perceived stress.
+The following two predictions are made:
+
+*H1. There is a positive relationship between perceived hindrance stressors and stress.*
+
+*H2. The relationship between mean perceived hindrances and stress will be moderated by resources such that this relationship is diminished as perceived resources increase.*
+
+NOTES:
+Add: Challenge versus hindrance job demands and wellbeing: A diary study on the moderating role of job resources
+Add a correlation table to speak to H1. Reference H1 and H2 in the results section.
 
 # Methods
-
-## Participants
-
-# Methods
-
-## Participants
 
@@
 
-#Results
+Table 1 presents correlations among the study variables of interest.
 
-A moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1.
+To explore H2, a moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1.
 First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, F(3, 564) = 3.29, p = .020.
-The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, F(3, 564) = 3.51, p = .061.
+The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, F(3, 564) = 3.51, p = .061, providing tentative support for H2.
 As can be seen in Figure 1, those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources.
@@
 
-Next steps:
-1)	Make a prettier graph using ggplot. Note the percentiles that we graphed. 
-2)	Or, could generate Johnson-Neyman Technique – shows specifically the range of W values that are significant. See p. 272 for visual and r-script. 
-Table example on p. 286: includes variables, symbol, coeff, SE, t, p; below that, rsquared, MSE and f-string.
-
 # Discussion

### 2022-09-02 SIOP2023/SIOP_PROCESS.tex
number formatting in table (2 decimals forced)
Updated introduction. See notes near end of intro for next steps.

@@
 (2001){]} has received wide support across contexts and varied research questions.
-We contribute to this literature by exploring the interaction between \emph{perceptions} of job demands and resources on stress using the broad set of job characteristics provided on O*Net.
-
-A series of evaluations were made that used: direct O*Net terminology (both descriptor and response option), and JD-R influenced ratings of demand and hindrance stressors.
-Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O*Net is provided.
+We add to this literature via two routes: by utilizing some of the job characteristics in the popular O*Net, and by focusing on perceptions of all characteristics as demands/resources.
+Specifically, we explore the interaction between perceptions of job demands and resources on the outcome of stress across a wide range of occupations.
+Here, respondents made a series of evaluations that used: direct O*Net terminology (both descriptor and response option), and JD-R influenced ratings of demand and hindrance stressors.
+Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O*Net, is provided.
 
@@
 The job demands-resources theory is an expansion of the well-studied job demands-resources model (Demerouti et al., 2001).
-One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands.
-\emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
-In contrast, \emph{demands} include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; Demerouti et al.
+One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands, which are thoroughly documented by job in O*Net.
+\emph{Resources} are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
+\emph{Demands}, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure; Demerouti et al.
 (2001)).
-Cognitively, the perception of an element of ones job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation {[}resulting from resources; A.
+
+Cognitively, the perception of an element of one's job as a resource or demand activates one of two unique processes: health impairment (resulting from demands) or motivation {[}resulting from resources; A.
 B.
 Bakker and Demerouti (2014){]}.
-Pertinent to the current study, demanding job characteristics are frequently associated with negative outcomes (e.g., A.
+Demanding job characteristics are frequently associated with negative outcomes (e.g., A.
 Bakker et al., 2003), whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation (A.
@@
 Bakker et al., 2007).
+Our focus is on whether or not having more resources serves as a buffer to the demand-stress relationship.
+One of the stickier elements of this question surrounds the subjective nature of demands/resources, which we address next.
 
@@
 
-Searle and Auton (2015) note that the majority of the research on workplace demands is based on apriori classifications of demands.
+Searle and Auton (2015) note that much of our research on workplace demands is based on apriori classifications of demands.
+For instance, we assume that generally, time pressure is a negative demand on an employee.
 However, the stress experience, or process, described early on by Lazarus and Folkman (1984) is grounded in the assumption that individual appraisals of stressors/demands vary.
@@
 This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes is not appraised as favorable (Lazarus \& Folkman, 1984).
-The stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.
+As such, the stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.
 
-We next consider the (limited) empirical evidence on this topic.
-First, some relatively recent research suggests that job demands and resources may not be universally appraised or assigned as such.
+We next consider the empirical evidence on the subjective nature of demands and resources.
+First, as hinted at above, some research suggests that job demands and resources may not be universally appraised or assigned as such.
 Starting with job demands, Webster et al.
-(2011), for example, studied workload, role ambiguity, and role conflict demands, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees.
-While their study did include resources, it nonetheless points to individual differences on how people perceive stressors at work.
-Although part of a much larger study on retirement, Sonnega et al.
+(2011) studied workload, role ambiguity, and role conflict demands, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being \emph{both} a challenge and hindrance to different degrees.
+While their study not did include resources, it documents individual differences in how people perceive stressors at work.
+Although not the primary focus of their paper, Sonnega et al.
 (2018) compared self-reported (subjective) ratings of degree of physical demand, stress, and need for intense concentration from the Health and Retirement Study with objective ratings from O*Net.
-Correlations physical demand (r = .52), stress (r = .10), and need for intense concentration (r = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than assumed.
-Next considering resources, Schmitz et al.
-(2019) also captured subjective and objective resources in their study of retirement.
+Correlations physical demand (r = .52), stress (r = .10), and need for intense concentration (r = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than we tend to think.
+While the above two studies provide evidence for variability in perception of demands, Schmitz et al.
+(2019) captured subjective and objective resources in their study of retirement.
 Correlations of composite variables for the resources of autonomy (r = .12.
 p \textgreater{} .01), recognition of work (r = .07, p \textgreater{} .01), and decision freedom (r = .08, p \textgreater{} .01), while significant, certainly do not reflect high levels of overlap.
-
 We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees.
@@
 
-\hypertarget{onet-resource}{%
-\subsection{O*Net Resource}\label{onet-resource}}
+Thus, while it is cleaner to be able to categorize job characteristics as \emph{either} a demand or a resource, the above research suggests that individual appraisal is an important consideration.
+It is quite possible that one person experiences high work pressure (commonly cited as a demand in the literature) as a hindrance stressor and thus experiences strain, and another thrives in a fast-paced pressured role and would thus find the environment motivating.
+Here, we asked respondents to rate all of the job characterstics in terms of hindrances and resources.
+consider the here whether perceptions of demands (specifically hindrance demands) and stress is
+
+\hypertarget{why-use-the-onet-resource}{%
+\subsection{Why use the O*Net Resource?}\label{why-use-the-onet-resource}}
 
@@
 
+\hypertarget{methods-1}{%
+\section{Methods}\label{methods-1}}
+
+\hypertarget{participants-1}{%
+\subsection{Participants}\label{participants-1}}
+
 There were 568 respondents.
 
-\hypertarget{participants-1}{%
-\subsubsection{Participants}\label{participants-1}}
+\hypertarget{participants-2}{%
+\subsubsection{Participants}\label{participants-2}}
 
@@
 Constant & 1.27 & 1.01 & 1.26 & 0.21\\
-Hindrance (X) & 0.83 & 0.4 & 2.07 & 0.04\\
+Hindrance (X) & 0.83 & 0.40 & 2.07 & 0.04\\
 Resource (W) & 0.33 & 0.25 & 1.32 & 0.19\\
-Hindrance x Resource & -0.19 & 0.1 & -1.87 & 0.06\\
+Hindrance x Resource & -0.19 & 0.10 & -1.87 & 0.06\\
 \bottomrule

### 2022-09-05 Submission_ResourceCount.Rmd
Reflecting on engagement variable.
new siop project

@@
 title: "Submission_ResourceCount"
-output: pdf_document
+output:
+  pdf_document: 
+    latex_engine: xelatex
 ---
@@
 Want to get a total count.
+
+Alicia reflection 9/1/22: It actually appears that there may be more here with the engagement variable when reviewing the correlations.
+Knit and reflect more on the paper with that outcome being of focus.
+
+John-o:
+maybe use this as basis for another SIOP - extent to which resources and challenges are viewed similarly and also associations with engagement, burnout, etc...
+this operationalization is different than previous SIOP so could submit anew.
+Also would need a different approach to "similarity" - would need to look at item level
 
@@
 
+data22$item387 <- 7-data22$item387
 data22$burnout      <- rowMeans(data22[c(373:376)], na.rm=TRUE)
@@
 
-cor(data22[405:410], use="all.obs")   ## something to be told with resources and challenges
+```
+
+```{r correlation_table}
+r <- corx::corx(data22[,c(405:410)],                    
+                triangle = "lower",
+                stars = c(0.05, 0.01, 0.001),
+                describe = c(`$M$` = mean, `$SD$` = sd))
+
+papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table,
+                  landscape = TRUE,
+                  escape = FALSE)
+
+#cor(data22[405:410], use="all.obs")   ## something to be told with resources and challenges
 

### 2022-09-05 Submission_ResourceCount.tex
new siop project

--- 2022-08-18 SIOP2023/SIOP_PROCESS.tex
@@
 \documentclass[
-  english,
-  man]{apa6}
+]{article}
 \usepackage{amsmath,amssymb}
@@
 \hypersetup{
-  pdftitle={JD-R Theory: Using the Content of the O*Net},
-  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
+  pdftitle={Submission\_ResourceCount},
   hidelinks,
@@
 \urlstyle{same} % disable monospaced font for URLs
+\usepackage[margin=1in]{geometry}
 \usepackage{graphicx}
@@
 \setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-% Make \paragraph and \subparagraph free-standing
-\ifx\paragraph\undefined\else
-  \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-  \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-% Manuscript styling
-\usepackage{upgreek}
-\captionsetup{font=singlespacing,justification=justified}
-
-% Table formatting
-\usepackage{longtable}
-\usepackage{lscape}
-% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
-\usepackage{multirow}		% Table styling
-\usepackage{tabularx}		% Control Column width
-\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
-\usepackage{threeparttablex}            % Lets threeparttable work with longtable
-
-% Create new environments so endfloat can handle them
-% \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
-
-% Enables adjusting longtable caption width to table width
-% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
-\makeatletter
-\newcommand\LastLTentrywidth{1em}
-\newlength\longtablewidth
-\setlength{\longtablewidth}{1in}
-\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
-
-% \setlength{\parindent}{0.5in}
-% \setlength{\parskip}{0pt plus 0pt minus 0pt}
-
-% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
-% See https://github.com/crsh/papaja/issues/292
-\makeatletter
-\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-1em}%
-  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
-
-\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-\z@\relax}%
-  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-\makeatother
-
-% \usepackage{etoolbox}
-\makeatletter
-\patchcmd{\HyOrg@maketitle}
-  {\section{\normalfont\normalsize\abstractname}}
-  {\section*{\normalfont\normalsize\abstractname}}
-  {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
-  {\section{\protect\normalfont{\@title}}}
-  {\section*{\protect\normalfont{\@title}}}
-  {}{\typeout{Failed to patch title.}}
-\makeatother
-\shorttitle{SIOP\_Hindrances-Resources Interaction}
-\keywords{keywords\newline\indent Word count: X}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
-\usepackage{lineno}
-
-\linenumbers
-\usepackage{csquotes}
-\ifxetex
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
 \ifluatex
@@
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
-\title{JD-R Theory: Using the Content of the O*Net}
-\author{First Author\textsuperscript{1} \& Ernst-August Doelle\textsuperscript{1,2}}
-\date{}
-
-\authornote{
-
-Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-Enter author note here.
-
-The authors made the following contributions. First Author: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Ernst-August Doelle: Writing - Review \& Editing.
-
-Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
-
-}
-
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}
+\title{Submission\_ResourceCount}
+\author{}
+\date{\vspace{-2.5em}}
 
@@
 
-The Job Demands-Resources Theory {[}JD-R; Demerouti et al.
-(2001){]} has received wide support across contexts and varied research questions.
-We contribute to this literature by exploring the interaction between \emph{perceptions} of job demands and resources on stress using the broad set of job characteristics provided on O*Net.
+Next steps (thoughts from 8/24): Want this to be a more traditional
+project: DVs engagement, burnout, stress. How to operationalize IVs of
+resources, challenges, hindrances. May want to only count it if they
+somewhat agree or strongly agree. Could do a count or a sum of these
+values. The moderator of job type may work well in this idea.
 
-A series of evaluations were made that used: direct O*Net terminology (both descriptor and response option), and JD-R influenced ratings of demand and hindrance stressors.
-Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O*Net is provided.
+Want to include idea of item level things in terms of agreement.
+decreasing bar graphs relative to SD. Maybe we just present SD or SE.
+Thinking on SD, but ensure we have sufficient numbers of people
+responding to the item. Want to get a total count.
 
-\hypertarget{the-job-demands-resources-theory}{%
-\subsection{The Job demands-Resources Theory}\label{the-job-demands-resources-theory}}
+Alicia reflection 9/1/22: It actually appears that there may be more
+here with the engagement variable when reviewing the correlations. Knit
+and reflect more on the paper with that outcome being of focus.
 
-The job demands-resources theory is an expansion of the well-studied job demands-resources model (Demerouti et al., 2001).
-One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands.
-\emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
-In contrast, \emph{demands} include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; Demerouti et al.
-(2001)).
-Cognitively, the perception of an element of ones job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation {[}resulting from resources; A.
-B.
-Bakker and Demerouti (2014){]}.
-Pertinent to the current study, demanding job characteristics are frequently associated with negative outcomes (e.g., A.
-Bakker et al., 2003), whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation (A.
-B.
-Bakker et al., 2007).
+John-o: maybe use this as basis for another SIOP - extent to which
+resources and challenges are viewed similarly and also associations with
+engagement, burnout, etc\ldots{} this operationalization is different
+than previous SIOP so could submit anew. Also would need a different
+approach to ``similarity'' - would need to look at item level
 
-\hypertarget{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisal}{%
-\subsection{Objective vs.~Subjective Nature of Demands and Resources: The Role of Appraisal}\label{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisal}}
-
-Searle and Auton (2015) note that the majority of the research on workplace demands is based on apriori classifications of demands.
-However, the stress experience, or process, described early on by Lazarus and Folkman (1984) is grounded in the assumption that individual appraisals of stressors/demands vary.
-Their transactional theory of stress and coping states that people continuously appraise stimuli in their environments.
-An appraisal is the cognitive process whereby meaning is assigned to a stimulus.
-If a stimulus is appraised as a stressor (threat, challenge, potentially harmful), emotional distress leads to coping of some kind.
-This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes is not appraised as favorable (Lazarus \& Folkman, 1984).
-The stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.
-
-We next consider the (limited) empirical evidence on this topic.
-First, some relatively recent research suggests that job demands and resources may not be universally appraised or assigned as such.
-Starting with job demands, Webster et al.
-(2011), for example, studied workload, role ambiguity, and role conflict demands, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees.
-While their study did include resources, it nonetheless points to individual differences on how people perceive stressors at work.
-Although part of a much larger study on retirement, Sonnega et al.
-(2018) compared self-reported (subjective) ratings of degree of physical demand, stress, and need for intense concentration from the Health and Retirement Study with objective ratings from O*Net.
-Correlations physical demand (r = .52), stress (r = .10), and need for intense concentration (r = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than assumed.
-Next considering resources, Schmitz et al.
-(2019) also captured subjective and objective resources in their study of retirement.
-Correlations of composite variables for the resources of autonomy (r = .12.
-p \textgreater{} .01), recognition of work (r = .07, p \textgreater{} .01), and decision freedom (r = .08, p \textgreater{} .01), while significant, certainly do not reflect high levels of overlap.
-
-We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees.
-Downes et al.
-(2021) meta-analysis addresses this reality in depth, although it is beyond the scope of this project.
-
-\hypertarget{onet-resource}{%
-\subsection{O*Net Resource}\label{onet-resource}}
-
-Originally, the Advisory Panel for the Dictionary of Occupational Titles recommended a system that would ``\ldots promote the effective education, training, counseling, and employment of the American workforce.
-It should accomplish its purpose by providing a database system that identifies, defines, classifies, and describes occupations in the economy in an accessible and flexible manner'' (Dictionary of Occupational Titles (US) and Service (1993), p.~6).
-The result was the now commonly used O*NET.
-The Occupational Information Network (O*NET; onetonline.org) contains a comprehensive description of occupations (Peterson et al., 2001).
-This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated.
-In fact, there was a call to work with experienced I/O psychologists over the summer to update the content for the \href{https://www.onetonline.org/link/summary/19-3032.00}{Industrial and Organizational Psychologist listing on O*Net}.
-These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move for Veterans,'' ``My Next Move,'' Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
-It is also useful to employers by providing them with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
-
-Of greatest interest here are statements taken from O*NET \href{https://www.O*NETonline.org/find/descriptor/result/4.A.1.b.3}{``activity'' and ``context'' classifications} (e.g., items related to information input, interacting with others, physical work conditions, structural job characteristics).
-One of the first and basic questions is whether or not the categorical examples of ``resources'' and ``demands'' described in the Job Demands-Resources Theory (Demerouti et al., 2001), for example, are generally deemed resources or demands as we objectively define them.
-The next logical question surrounds how ``universal'' such ratings are.
-For instance, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.
-A second study extends the findings from Study 1 to a potentially key moderator - job categories/classifications, examining whether ratings of resources, challenge- and hindrance demands differ by job classification.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-There were 568 respondents.
-
-\hypertarget{participants-1}{%
-\subsubsection{Participants}\label{participants-1}}
-
-\begin{itemize}
-\tightlist
-\item
-  568 respondents, 13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.
-\item
-  Ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53).
-\item
-  Gender: female (52.58\%) or male (46.83\%).
-\item
-  Job classifications: International Standard Classification of Occupations (ISCO) via the package \texttt{labourR} (\textbf{R-labourR?}), and further categorized into ``knowledge'' (n = 320) versus ``skilled'' (n = 214) occupations with knowledge workers being identified via ISCO classifications of: 1) professionals, and 2) managers.
-\end{itemize}
-
-The data for this study were collected through Prolific sample,18 or older and holding a full-time or part-time job.
-Participants were asked to think about their primary job while answering the survey, and upon completion each participant was compensated in the amount of six US dollars.
-
-\hypertarget{materials}{%
-\section{Materials}\label{materials}}
-
-We used 98 statements taken directly from O\(^{*}\)Net's ``activity'' and ``context'' classifications.
-Each of the 98 descriptors has potentially unique response categories, but scaling was consistently 1 (low) to 5 (high).
-Subsequent to these self-evaluations, respondents were asked to rate elements in terms of 1) \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
-
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
-
-We used PROCESS for R Version 4.1.1 (Hayes, 2022) to assess the extent to which the relationship between demands and stress are moderated by resources.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
+There were 568 retained respondents.
 
 \begin{verbatim}
-## 
-## ********************* PROCESS for R Version 4.1.1 ********************* 
-##  
-##            Written by Andrew F. Hayes, Ph.D.  www.afhayes.com              
-##    Documentation available in Hayes (2022). www.guilford.com/p/hayes3   
-##  
-## *********************************************************************** 
-##  
-## PROCESS is now ready for use.
-## Copyright 2022 by Andrew F. Hayes ALL RIGHTS RESERVED
-## Workshop schedule at http://haskayne.ucalgary.ca/CCRAM
-## 
+##            resource hindrance challenge
+## resource  1.0000000 0.2255508 0.8622519
+## hindrance 0.2255508 1.0000000 0.2204752
+## challenge 0.8622519 0.2204752 1.0000000
 \end{verbatim}
 
-\begin{verbatim}
-## 
-## ********************* PROCESS for R Version 4.1.1 ********************* 
-##  
-##            Written by Andrew F. Hayes, Ph.D.  www.afhayes.com              
-##    Documentation available in Hayes (2022). www.guilford.com/p/hayes3   
-##  
-## *********************************************************************** 
-##                          
-## Model : 1                
-##     Y : stress           
-##     X : overall.hindrance
-##     W : overall.resource 
-## 
-## Sample size: 568
-## 
-## 
-## *********************************************************************** 
-## Outcome Variable: stress
-## 
-## Model Summary: 
-##           R      R-sq       MSE         F       df1       df2         p
-##      0.1311    0.0172    0.7790    3.2876    3.0000  564.0000    0.0205
-## 
-## Model: 
-##                       coeff        se         t         p      LLCI      ULCI
-## constant             1.2688    1.0055    1.2618    0.2075   -0.7063    3.2439
-## overall.hindrance    0.8336    0.4031    2.0677    0.0391    0.0417    1.6254
-## overall.resource     0.3319    0.2518    1.3181    0.1880   -0.1627    0.8264
-## Int_1               -0.1918    0.1024   -1.8725    0.0616   -0.3929    0.0094
-## 
-## Product terms key:
-## Int_1  :  overall.hindrance  x  overall.resource      
-## 
-## Test(s) of highest order unconditional interaction(s):
-##       R2-chng         F       df1       df2         p
-## X*W    0.0061    3.5064    1.0000  564.0000    0.0616
-## ----------
-## Focal predictor: overall.hindrance (X)
-##       Moderator: overall.resource (W)
-## 
-## Conditional effects of the focal predictor at values of the moderator(s):
-##   overall.resource    effect        se         t         p      LLCI      ULCI
-##             3.2983    0.2010    0.0802    2.5065    0.0125    0.0435    0.3586
-##             3.7402    0.1163    0.0534    2.1759    0.0300    0.0113    0.2213
-##             4.2063    0.0269    0.0594    0.4535    0.6503   -0.0897    0.1435
-## 
-## Moderator value(s) defining Johnson-Neyman significance region(s):
-##       Value   % below   % above
-##      3.8196   55.6338   44.3662
-## 
-## Conditional effect of focal predictor at values of the moderator:
-##   overall.resource    effect        se         t         p      LLCI      ULCI
-##             1.0149    0.6389    0.3003    2.1276    0.0338    0.0491    1.2288
-##             1.2078    0.6020    0.2809    2.1433    0.0325    0.0503    1.1536
-##             1.4006    0.5650    0.2615    2.1608    0.0311    0.0514    1.0785
-##             1.5935    0.5280    0.2421    2.1807    0.0296    0.0524    1.0035
-##             1.7863    0.4910    0.2228    2.2034    0.0280    0.0533    0.9287
-##             1.9791    0.4540    0.2037    2.2293    0.0262    0.0540    0.8540
-##             2.1720    0.4170    0.1846    2.2592    0.0243    0.0545    0.7796
-##             2.3648    0.3801    0.1657    2.2937    0.0222    0.0546    0.7055
-##             2.5577    0.3431    0.1470    2.3336    0.0200    0.0543    0.6318
-##             2.7505    0.3061    0.1287    2.3791    0.0177    0.0534    0.5588
-##             2.9434    0.2691    0.1108    2.4292    0.0154    0.0515    0.4867
-##             3.1362    0.2321    0.0937    2.4784    0.0135    0.0482    0.4161
-##             3.3290    0.1951    0.0778    2.5085    0.0124    0.0423    0.3479
-##             3.5219    0.1582    0.0641    2.4667    0.0139    0.0322    0.2841
-##             3.7147    0.1212    0.0543    2.2306    0.0261    0.0145    0.2279
-##             3.8196    0.1011    0.0515    1.9642    0.0500    0.0000    0.2021
-##             3.9076    0.0842    0.0507    1.6605    0.0974   -0.0154    0.1838
-##             4.1004    0.0472    0.0545    0.8662    0.3867   -0.0599    0.1543
-##             4.2933    0.0102    0.0644    0.1589    0.8738   -0.1163    0.1368
-##             4.4861   -0.0267    0.0782   -0.3421    0.7324   -0.1803    0.1268
-##             4.6790   -0.0637    0.0941   -0.6773    0.4985   -0.2485    0.1211
-##             4.8718   -0.1007    0.1112   -0.9054    0.3656   -0.3192    0.1178
-## 
-## Data for visualizing the conditional effect of the focal predictor:
-##   overall.hindrance overall.resource    stress
-##              1.6667           3.2983    2.6985
-##              2.2894           3.2983    2.8237
-##              3.2416           3.2983    3.0151
-##              1.6667           3.7402    2.7039
-##              2.2894           3.7402    2.7763
-##              3.2416           3.7402    2.8871
-##              1.6667           4.2063    2.7096
-##              2.2894           4.2063    2.7264
-##              3.2416           4.2063    2.7520
-## 
-## ******************** ANALYSIS NOTES AND ERRORS ************************ 
-## 
-## Level of confidence for all confidence intervals in output: 95
-## 
-## W values in conditional tables are the 16th, 50th, and 84th percentiles.
-\end{verbatim}
+\begin{lltable}
 
-\begin{figure}
-\centering
-\includegraphics{SIOP_PROCESS_files/figure-latex/analyses-1.pdf}
-\caption{\label{fig:analyses}Interaction between hindrances and resources as predictors of stress}
-\end{figure}
+\begin{longtable}{llllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:correlation_table}}\\
+\toprule
+ & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
+\midrule
+\endfirsthead
+\caption*{\normalfont{Table \ref{tab:correlation_table} continued}}\\
+\toprule
+ & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
+\midrule
+\endhead
+1. resource & - &  &  &  &  & 36.02 & 13.26\\
+2. hindrance & .23*** & - &  &  &  & 13.09 & 13.62\\
+3. challenge & .86*** & .22*** & - &  &  & 35.64 & 13.63\\
+4. burnout & .05 & .04 & .07 & - &  & 3.04 & 0.87\\
+5. stress & .06 & .09* & .08 & .70*** & - & 2.59 & 0.97\\
+6. engagement & .34*** & .01 & .31*** & -.35*** & -.30*** & 4.04 & 0.83\\
+\bottomrule
+\end{longtable}
 
-\#Results
-
-A moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1.
-First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, F(3, 564) = 3.29, p = .020.
-The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, F(3, 564) = 3.51, p = .061.
-As can be seen in Figure 1, those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources.
-Upon exploring the interaction further, it was evident that this moderated effect happened at lower, but not higher levels of resources.
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:table}Results from a regression analysis examining the moderation of resources on the relationship between hindrance demands and stress}
-
-\begin{tabular}{lllll}
-\toprule
-Component & \multicolumn{1}{c}{coeff} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{t} & \multicolumn{1}{c}{p}\\
-\midrule
-Constant & 1.27 & 1.01 & 1.26 & 0.21\\
-Hindrance (X) & 0.83 & 0.4 & 2.07 & 0.04\\
-Resource (W) & 0.33 & 0.25 & 1.32 & 0.19\\
-Hindrance x Resource & -0.19 & 0.1 & -1.87 & 0.06\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} R\textasciicircum{}2 etc here}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-Next steps:
-1) Make a prettier graph using ggplot. Note the percentiles that we graphed.
-2) Or, could generate Johnson-Neyman Technique -- shows specifically the range of W values that are significant. See p.~272 for visual and r-script.
-Table example on p.~286: includes variables, symbol, coeff, SE, t, p; below that, rsquared, MSE and f-string.
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-\newpage
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-bakker2014job}{}%
-Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
-
-\leavevmode\hypertarget{ref-bakker2007job}{}%
-Bakker, A.
-B., Hakanen, J.
-J., Demerouti, E., \& Xanthopoulou, D.
-(2007).
-Job resources boost work engagement, particularly when job demands are high.
-\emph{Journal of Educational Psychology}, \emph{99}(2), 274.
-
-\leavevmode\hypertarget{ref-bakker2003dual}{}%
-Bakker, A., Demerouti, E., \& Schaufeli, W.
-(2003).
-Dual processes at work in a call centre: An application of the job demands--resources model.
-\emph{European Journal of Work and Organizational Psychology}, \emph{12}(4), 393--417.
-
-\leavevmode\hypertarget{ref-demerouti2001job}{}%
-Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
-
-\leavevmode\hypertarget{ref-advisory1993new}{}%
-Dictionary of Occupational Titles (US), A.
-P.
-for the, \& Service, U.
-S.
-E.
-(1993).
-\emph{The new DOT: A database of occupational titles for the twenty-first century}.
-US Department of Labor, Employment; Training Administration, US~\ldots.
-
-\leavevmode\hypertarget{ref-downes2021incorporating}{}%
-Downes, P.
-E., Reeves, C.
-J., McCormick, B.
-W., Boswell, W.
-R., \& Butts, M.
-M.
-(2021).
-Incorporating job demand variability into job demands theory: A meta-analysis.
-\emph{Journal of Management}, \emph{47}(6), 1630--1656.
-
-\leavevmode\hypertarget{ref-hayes2022}{}%
-Hayes, A. F. (2022). \emph{Introduction to mediation, moderation, and conditional process analysis: A regression-based approach} (3rd ed.). The Guilford Press.
-
-\leavevmode\hypertarget{ref-lazarus1984stress}{}%
-Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
-
-\leavevmode\hypertarget{ref-peterson2001understanding}{}%
-Peterson, N.
-G., Mumford, M.
-D., Borman, W.
-C., Jeanneret, P.
-R., Fleishman, E.
-A., Levin, K.
-Y., Campion, M.
-A., Mayfield, M.
-S., Morgeson, F.
-P., Pearlman, K., \& others.
-(2001).
-Understanding work using the occupational information network (o* NET): Implications for practice and research.
-\emph{Personnel Psychology}, \emph{54}(2), 451--492.
-
-\leavevmode\hypertarget{ref-schmitz_interpreting_2019}{}%
-Schmitz, L.
-L., McCluney, C.
-L., Sonnega, A., \& Hicken, M.
-T.
-(2019).
-Interpreting {Subjective} and {Objective} {Measures} of {Job} {Resources}: {The} {Importance} of {Sociodemographic} {Context}.
-\emph{International Journal of Environmental Research and Public Health}, \emph{16}(17), 3058.
-\url{https://doi.org/10.3390/ijerph16173058}
-
-\leavevmode\hypertarget{ref-searle2015merits}{}%
-Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.
-
-\leavevmode\hypertarget{ref-sonnega_comparison_2018}{}%
-Sonnega, A., Helppie-McFall, B., Hudomiet, P., Willis, R.
-J., \& Fisher, G.
-G.
-(2018).
-A {Comparison} of {Subjective} and {Objective} {Job} {Demands} and {Fit} {With} {Personal} {Resources} as {Predictors} of {Retirement} {Timing} in a {National} {U}.{S}.
-{Sample}.
-\emph{Work, Aging and Retirement}, \emph{4}(1), 37--51.
-\url{https://doi.org/10.1093/workar/wax016}
-
-\leavevmode\hypertarget{ref-webster2011extending}{}%
-Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.
-
-\end{CSLReferences}
-
-\endgroup
+\end{lltable}
 

### 2022-09-12 SIOP2023/Counts/Submission_ResourceCount.Rmd
late pushes

--- 2022-09-05 Submission_ResourceCount.Rmd
@@
 
-```{r analysis-preferences, echo=FALSE}
+```{r setup, echo=FALSE}
 
 knitr::opts_chunk$set(cache.extra = knitr::rand_seed, echo=FALSE, warning=FALSE, message=FALSE)
+#knitr::opts_knit$set(root.dir=normalizePath('../'))
+knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
 
@@
 
-temp <- read.csv("initial_data_screen.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script
+temp <- read.csv("..//JDRJournalSubmission//initial_data_screen.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script
 
@@
 
-incomplete <- read.csv("inprogress.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script
+incomplete <- read.csv("..//JDRJournalSubmission//inprogress.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script
 
@@
 
-source("recodescript.R", local = knitr::knit_global())
+source("..//JDRJournalSubmission//recodescript.R", local = knitr::knit_global())
 
@@
 
-cor(data22[405:407], use="all.obs")   ## something to be told with resources and challenges
-
 data22$item387 <- 7-data22$item387
@@
 
+cor(data22[405:410], use="all.obs")   ## something to be told with resources and challenges
+
 ```
 
-```{r correlation_table}
+```{r matching}
+
+## Trying to figure out which characteristics have agreement
+
+## 145 & 248 (attention checks)
+
+data22$rh1  <- data22$item118 + data22$item203
+data22$rh2  <- data22$item119 + data22$item204
+data22$rh3  <- data22$item120 + data22$item205
+data22$rh4  <- data22$item121 + data22$item206
+data22$rh5  <- data22$item122 + data22$item207
+data22$rh6  <- data22$item123 + data22$item208
+data22$rh7  <- data22$item124 + data22$item209
+data22$rh8  <- data22$item125 + data22$item210
+data22$rh9  <- data22$item126 + data22$item211
+data22$rh10 <- data22$item127 + data22$item212
+
+```
+
+```{r correlation_table, eval=FALSE}
+
 r <- corx::corx(data22[,c(405:410)],                    
@@
 papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table,
-                  landscape = TRUE,
                   escape = FALSE)
@@
 ```
+
+```{r regressions}
+
+eng <- lm(engagement ~ hindrance + challenge + resource, data22)
+bur <- lm(burnout ~ hindrance + challenge + resource, data22)
+str <- lm(stress ~ hindrance + challenge + resource, data22)
+
+summary(eng)
+summary(bur)
+summary(str)
+```

### 2022-09-16 SIOP2023/Counts/Submission_ResourceCount.Rmd
one more
still need characteristic match (matching chunk)

@@
 ## 145 & 248 (attention checks)
+## maybe % match
 
@@
 data22$rh10 <- data22$item127 + data22$item212
+data22$rh11  <- data22$item128 + data22$item213
+data22$rh12  <- data22$item129 + data22$item214
+data22$rh13  <- data22$item130 + data22$item215
+data22$rh14  <- data22$item131 + data22$item216
+data22$rh15  <- data22$item132 + data22$item217
+data22$rh16  <- data22$item133 + data22$item218
+data22$rh17  <- data22$item134 + data22$item219
+data22$rh18  <- data22$item135 + data22$item220
+data22$rh19  <- data22$item136 + data22$item221
+data22$rh20  <- data22$item137 + data22$item222
+data22$rh21  <- data22$item138 + data22$item223
+data22$rh22  <- data22$item139 + data22$item224
+data22$rh23  <- data22$item140 + data22$item225
+data22$rh24  <- data22$item141 + data22$item226
+data22$rh25  <- data22$item142 + data22$item227
+data22$rh26  <- data22$item143 + data22$item228
+data22$rh27  <- data22$item144 + data22$item229
+
+data22$rh28  <- data22$item146 + data22$item230
+
+data22$rh29  <- data22$item147 + data22$item231
+data22$rh30  <- data22$item148 + data22$item232
+data22$rh31  <- data22$item149 + data22$item233
+data22$rh32  <- data22$item150 + data22$item234
+data22$rh33  <- data22$item151 + data22$item235
+data22$rh34  <- data22$item152 + data22$item236
+data22$rh35  <- data22$item153 + data22$item237
+data22$rh36  <- data22$item154 + data22$item238
+data22$rh37  <- data22$item155 + data22$item239
+data22$rh38  <- data22$item156 + data22$item240
+data22$rh39  <- data22$item157 + data22$item241
+data22$rh40  <- data22$item158 + data22$item242
+data22$rh41  <- data22$item159 + data22$item243
+data22$rh42  <- data22$item160 + data22$item244
+data22$rh43  <- data22$item161 + data22$item245
+data22$rh44  <- data22$item162 + data22$item246
+data22$rh45  <- data22$item163 + data22$item247
+
+data22$rh46  <- data22$item164 + data22$item249
+
+data22$rh47  <- data22$item165 + data22$item250
+data22$rh48  <- data22$item166 + data22$item251
+data22$rh49  <- data22$item167 + data22$item252
+data22$rh50  <- data22$item168 + data22$item253
+data22$rh51  <- data22$item169 + data22$item254
+data22$rh52  <- data22$item170 + data22$item255
+data22$rh53  <- data22$item171 + data22$item256
+data22$rh54  <- data22$item172 + data22$item257
+data22$rh55  <- data22$item173 + data22$item258
+data22$rh56  <- data22$item174 + data22$item259
+data22$rh57  <- data22$item175 + data22$item260
+data22$rh58  <- data22$item176 + data22$item261
+data22$rh59  <- data22$item177 + data22$item262
+data22$rh60  <- data22$item178 + data22$item263
+data22$rh61  <- data22$item179 + data22$item264
+data22$rh62  <- data22$item180 + data22$item265
+data22$rh63  <- data22$item181 + data22$item266
+data22$rh64  <- data22$item182 + data22$item267
+data22$rh65  <- data22$item183 + data22$item268
+data22$rh66  <- data22$item184 + data22$item269
+data22$rh67  <- data22$item185 + data22$item270
+data22$rh68  <- data22$item186 + data22$item271
+data22$rh69  <- data22$item187 + data22$item272
+data22$rh70  <- data22$item188 + data22$item273
+data22$rh71  <- data22$item189 + data22$item274
+data22$rh72  <- data22$item190 + data22$item275
+data22$rh73  <- data22$item191 + data22$item276
+data22$rh74  <- data22$item192 + data22$item277
+data22$rh75  <- data22$item193 + data22$item278
+data22$rh76  <- data22$item194 + data22$item279
+data22$rh77  <- data22$item195 + data22$item280
+data22$rh78  <- data22$item196 + data22$item281
+data22$rh79  <- data22$item197 + data22$item282
+data22$rh80  <- data22$item198 + data22$item283
+data22$rh81  <- data22$item199 + data22$item284
+data22$rh82  <- data22$item200 + data22$item285
+data22$rh83  <- data22$item201 + data22$item286
+data22$rh84  <- data22$item202 + data22$item287
+
+###### Resource-Challenge:
+
+data22$rc1  <- data22$item118 + data22$item288
+data22$rc2  <- data22$item119 + data22$item289
+data22$rc3  <- data22$item120 + data22$item290
+data22$rc4  <- data22$item121 + data22$item291
+data22$rc5  <- data22$item122 + data22$item292
+data22$rc6  <- data22$item123 + data22$item293
+data22$rc7  <- data22$item124 + data22$item294
+data22$rc8  <- data22$item125 + data22$item295
+data22$rc9  <- data22$item126 + data22$item296
+data22$rc10 <- data22$item127 + data22$item297
+data22$rc11  <- data22$item128 + data22$item298
+data22$rc12  <- data22$item129 + data22$item299
+data22$rc13  <- data22$item130 + data22$item300
+data22$rc14  <- data22$item131 + data22$item301
+data22$rc15  <- data22$item132 + data22$item302
+data22$rc16  <- data22$item133 + data22$item303
+data22$rc17  <- data22$item134 + data22$item304
+data22$rc18  <- data22$item135 + data22$item305
+data22$rc19  <- data22$item136 + data22$item306
+data22$rc20  <- data22$item137 + data22$item307
+
+data22$rc21  <- data22$item138 + data22$item309
+
+data22$rc22  <- data22$item139 + data22$item310
+data22$rc23  <- data22$item140 + data22$item311
+data22$rc24  <- data22$item141 + data22$item312
+data22$rc25  <- data22$item142 + data22$item313
+data22$rc26  <- data22$item143 + data22$item314
+data22$rc27  <- data22$item144 + data22$item315
+
+data22$rc28  <- data22$item146 + data22$item316
+
+data22$rc29  <- data22$item147 + data22$item317
+data22$rc30  <- data22$item148 + data22$item318
+data22$rc31  <- data22$item149 + data22$item319
+data22$rc32  <- data22$item150 + data22$item320
+data22$rc33  <- data22$item151 + data22$item321
+data22$rc34  <- data22$item152 + data22$item322
+data22$rc35  <- data22$item153 + data22$item323
+data22$rc36  <- data22$item154 + data22$item324
+data22$rc37  <- data22$item155 + data22$item325
+data22$rc38  <- data22$item156 + data22$item326
+data22$rc39  <- data22$item157 + data22$item327
+data22$rc40  <- data22$item158 + data22$item328
+data22$rc41  <- data22$item159 + data22$item329
+data22$rc42  <- data22$item160 + data22$item330
+data22$rc43  <- data22$item161 + data22$item331
+data22$rc44  <- data22$item162 + data22$item332
+data22$rc45  <- data22$item163 + data22$item333
+data22$rc46  <- data22$item164 + data22$item334
+data22$rc47  <- data22$item165 + data22$item335
+data22$rc48  <- data22$item166 + data22$item336
+data22$rc49  <- data22$item167 + data22$item337
+data22$rc50  <- data22$item168 + data22$item338
+data22$rc51  <- data22$item169 + data22$item339
+data22$rc52  <- data22$item170 + data22$item340
+data22$rc53  <- data22$item171 + data22$item341
+data22$rc54  <- data22$item172 + data22$item342
+data22$rc55  <- data22$item173 + data22$item343
+data22$rc56  <- data22$item174 + data22$item344
+data22$rc57  <- data22$item175 + data22$item345
+data22$rc58  <- data22$item176 + data22$item346
+data22$rc59  <- data22$item177 + data22$item347
+data22$rc60  <- data22$item178 + data22$item348
+data22$rc61  <- data22$item179 + data22$item349
+data22$rc62  <- data22$item180 + data22$item350
+data22$rc63  <- data22$item181 + data22$item351
+data22$rc64  <- data22$item182 + data22$item352
+data22$rc65  <- data22$item183 + data22$item353
+data22$rc66  <- data22$item184 + data22$item354
+data22$rc67  <- data22$item185 + data22$item355
+data22$rc68  <- data22$item186 + data22$item356
+data22$rc69  <- data22$item187 + data22$item357
+data22$rc70  <- data22$item188 + data22$item358
+data22$rc71  <- data22$item189 + data22$item359
+data22$rc72  <- data22$item190 + data22$item360
+data22$rc73  <- data22$item191 + data22$item361
+data22$rc74  <- data22$item192 + data22$item362
+data22$rc75  <- data22$item193 + data22$item363
+data22$rc76  <- data22$item194 + data22$item364
+data22$rc77  <- data22$item195 + data22$item365
+data22$rc78  <- data22$item196 + data22$item366
+data22$rc79  <- data22$item197 + data22$item367
+data22$rc80  <- data22$item198 + data22$item368
+data22$rc81  <- data22$item199 + data22$item369
+data22$rc82  <- data22$item200 + data22$item370
+data22$rc83  <- data22$item201 + data22$item371
+data22$rc84  <- data22$item202 + data22$item372
+
+####### Hindrance-Challenge
+
+data22$hc1  <- data22$item203 + data22$item288
+data22$hc2  <- data22$item204 + data22$item289
+data22$hc3  <- data22$item205 + data22$item290
+data22$hc4  <- data22$item206 + data22$item291
+data22$hc5  <- data22$item207 + data22$item292
+data22$hc6  <- data22$item208 + data22$item293
+data22$hc7  <- data22$item209 + data22$item294
+data22$hc8  <- data22$item210 + data22$item295
+data22$hc9  <- data22$item211 + data22$item296
+data22$hc10 <- data22$item212 + data22$item297
+data22$hc11  <- data22$item213 + data22$item298
+data22$hc12  <- data22$item214 + data22$item299
+data22$hc13  <- data22$item215 + data22$item300
+data22$hc14  <- data22$item216 + data22$item301
+data22$hc15  <- data22$item217 + data22$item302
+data22$hc16  <- data22$item218 + data22$item303
+data22$hc17  <- data22$item219 + data22$item304
+data22$hc18  <- data22$item220 + data22$item305
+data22$hc19  <- data22$item221 + data22$item306
+data22$hc20  <- data22$item222 + data22$item307
+
+data22$hc21  <- data22$item223 + data22$item309
+
+data22$hc22  <- data22$item224 + data22$item310
+data22$hc23  <- data22$item225 + data22$item311
+data22$hc24  <- data22$item226 + data22$item312
+data22$hc25  <- data22$item227 + data22$item313
+data22$hc26  <- data22$item228 + data22$item314
+data22$hc27  <- data22$item229 + data22$item315
+data22$hc28  <- data22$item230 + data22$item316
+data22$hc29  <- data22$item231 + data22$item317
+data22$hc30  <- data22$item232 + data22$item318
+data22$hc31  <- data22$item233 + data22$item319
+data22$hc32  <- data22$item234 + data22$item320
+data22$hc33  <- data22$item235 + data22$item321
+data22$hc34  <- data22$item236 + data22$item322
+data22$hc35  <- data22$item237 + data22$item323
+data22$hc36  <- data22$item238 + data22$item324
+data22$hc37  <- data22$item239 + data22$item325
+data22$hc38  <- data22$item240 + data22$item326
+data22$hc39  <- data22$item241 + data22$item327
+data22$hc40  <- data22$item242 + data22$item328
+data22$hc41  <- data22$item243 + data22$item329
+data22$hc42  <- data22$item244 + data22$item330
+data22$hc43  <- data22$item245 + data22$item331
+data22$hc44  <- data22$item246 + data22$item332
+data22$hc45  <- data22$item247 + data22$item333
+
+data22$hc46  <- data22$item249 + data22$item334
+
+data22$hc47  <- data22$item250 + data22$item335
+data22$hc48  <- data22$item251 + data22$item336
+data22$hc49  <- data22$item252 + data22$item337
+data22$hc50  <- data22$item253 + data22$item338
+data22$hc51  <- data22$item254 + data22$item339
+data22$hc52  <- data22$item255 + data22$item340
+data22$hc53  <- data22$item256 + data22$item341
+data22$hc54  <- data22$item257 + data22$item342
+data22$hc55  <- data22$item258 + data22$item343
+data22$hc56  <- data22$item259 + data22$item344
+data22$hc57  <- data22$item260 + data22$item345
+data22$hc58  <- data22$item261 + data22$item346
+data22$hc59  <- data22$item262 + data22$item347
+data22$hc60  <- data22$item263 + data22$item348
+data22$hc61  <- data22$item264 + data22$item349
+data22$hc62  <- data22$item265 + data22$item350
+data22$hc63  <- data22$item266 + data22$item351
+data22$hc64  <- data22$item267 + data22$item352
+data22$hc65  <- data22$item268 + data22$item353
+data22$hc66  <- data22$item269 + data22$item354
+data22$hc67  <- data22$item270 + data22$item355
+data22$hc68  <- data22$item271 + data22$item356
+data22$hc69  <- data22$item272 + data22$item357
+data22$hc70  <- data22$item273 + data22$item358
+data22$hc71  <- data22$item274 + data22$item359
+data22$hc72  <- data22$item275 + data22$item360
+data22$hc73  <- data22$item276 + data22$item361
+data22$hc74  <- data22$item277 + data22$item362
+data22$hc75  <- data22$item278 + data22$item363
+data22$hc76  <- data22$item279 + data22$item364
+data22$hc77  <- data22$item280 + data22$item365
+data22$hc78  <- data22$item281 + data22$item366
+data22$hc79  <- data22$item282 + data22$item367
+data22$hc80  <- data22$item283 + data22$item368
+data22$hc81  <- data22$item284 + data22$item369
+data22$hc82  <- data22$item285 + data22$item370
+data22$hc83  <- data22$item286 + data22$item371
+data22$hc84  <- data22$item287 + data22$item372
+
+isolated <- data22[,c(22:32, 42:50, 52:60, 62:65, 67:117,411:662)]  ## characteristic ratings scattered because we didn't ask for resource/demand ratings for characteristics such as "exposure to radiation" - 9/12/22
 
@@
 summary(str)
+
 ```

### 2022-09-16 SIOP2023/Counts/Submission_ResourceCount.Rmd
Updated introduction

@@
 ---
-title: "Submission_ResourceCount"
+title: "Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?"
 output:
@@
 
-Next steps (thoughts from 8/24):
-Want this to be a more traditional project: DVs engagement, burnout, stress. 
-How to operationalize IVs of resources, challenges, hindrances.
-May want to only count it if they somewhat agree or strongly agree.
-Could do a count or a sum of these values.
-The moderator of job type may work well in this idea.
+**Abstract**
 
-Want to include idea of item level things in terms of agreement.
-decreasing bar graphs relative to SD.
-Maybe we just present SD or SE.
-Thinking on SD, but ensure we have sufficient numbers of people responding to the item.
-Want to get a total count.
+The relationships among sum of perceived job resources, challenge- and hindrance demands and outcomes of organizational outcomes of engagement, stress, and burnout are explored.
+568 workers rated O*Net job characteristics in terms of relevance and perceptions as challenges, hindrances and resources.
+The findings are generally aligned with the job demands resource theory regarding associations between perceived resources, demands, and organizational outcomes of engagement, stress, and burnout.
 
-Alicia reflection 9/1/22: It actually appears that there may be more here with the engagement variable when reviewing the correlations.
-Knit and reflect more on the paper with that outcome being of focus.
+**Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?**
 
-John-o:
-maybe use this as basis for another SIOP - extent to which resources and challenges are viewed similarly and also associations with engagement, burnout, etc...
-this operationalization is different than previous SIOP so could submit anew.
-Also would need a different approach to "similarity" - would need to look at item level
+  A plethora of research applying the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker & Demerouti, 2017) underscore the importance of work characteristics on the experience of motivation and strain.
+However, much of our existing research on this topic assumes that certain characteristics are resources and others are generally considered demands.
+This study explores how individual perceptions of these work characteristics relate to engagement, stress, and burnout by asking respondents to indicate (of the characteristics that apply to their jobs) how much each is a resource, challenge, or hindrance demand.
+Amount of perceived resources, challenges, and hindrances can then be associated with engagement, stress, and burnout.
+
+**The Job Demands-Resources Theory**
+
+  The theoretical foundation for this study is the job demands-resources theory (Demerouti et al., 2001).
+Using this theory, we can model both work environment and job characteristics via job resources and demands.
+Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
+In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure; Demerouti et al., 2001).
+
+  The perception of a characteristic of one’s job as a resource or demand activates one of two unique processes: either health impairment or motivation Bakker & Demerouti, 2014).
+Demanding job characteristics are frequently associated with negative outcomes (e.g., health impairment process; Bakker et al., 2003), whereas job characteristics considered resources have been associated with positive organizational outcomes like engagement and motivation (Bakker et al., 2007).
+
+**An Added Complexity: Perception (Appraisal) of Work Characteristics Might Matter**
+
+  The above description speaks to one of two distinct processes being activated, presumably based on one’s assessment of how a work characteristics makes them feel (e.g., consider the different reactions employees may have to being nominated to give a speech at an upcoming company event).
+Thus, although some research on job demands in particular is based on a priori classifications of demands (Searle & Auton, 2015), the appraisal of any work characteristic as a demand or resource is quite subjective.
+The literature on the experience of stress explains how such individual differences in appraisal are possible.
+Specifically, the transactional theory of stress and coping states that people cognitively appraise stimuli in their environments on a continuous basis (Lazarus & Folkman, 1984).
+During this process, meaning is assigned to stimuli.
+If the above employee appraised the upcoming speech as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping (e.g., attempting to decline, asking for help in writing the speech).
+From that point, the cycle of appraisal continues based on the action to cope with the stressor (Lazarus & Folkman, 1984).
+
+**Could a Work Demand be Appraised Positively?: The Challenge-Hindrance Framework**
+
+  Although the word “stress” often connotes something negative, Selye (1936) defined stress generically as a response to change.
+For instance, the example above describes an employee who appraises being nominated to give a speech as a negative stressor.
+However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
+The terms associated with the two different appraisals of the stressor described here are challenge and hindrance demands (Cavanaugh et al., 2000) Specifically, challenge demands promote mastery, personal growth, and future gains.
+Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
+Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes (e.g., Cavanaugh et al., 2000).
+We will explore their associations with both positive and negative outcomes in this study.
+
+  Prior to proposing specific predictions, the empirical evidence on challenge and hindrance demands is very briefly shared below.
+To begin, the first logical question is whether employees actually distinguish between challenge and hindrance stressors, and research suggests that they can and do.
+For example, Bakker and Sanz-Vergel (2013) found that perceived work pressure can be classified as a hindrance demand, and emotional demands as a challenge demand.
+Webster et al.
+(2011) considered three common workplace demands including workload, role ambiguity, and role conflict.
+Interestingly, they found that while each could be appraised primarily as challenges or hindrances, employees could also simultaneously be perceived as being both a challenge and hindrance.
+
+  Having established that there can be individual differences in the appraisal of demands as challenges or resources, we next turn our attention to their association with organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and well-being.
+For example, Cavanaugh et al.
+(2000) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern with job satisfaction and job search behaviors in a sample of managers.
+However, Abbas and Raja (2019) found that challenge and hindrance stressors were both positively related to strain and turnover intentions.
+We also have some evidence that challenge-hinderance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford et al., 2010).
+The appraisal process also suggests theoretically that the perception of a job characteristic as a challenge or hindrance is a mediator.
+Gerich (2017), for instance, found that employee well-being was, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
+To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, Podsakoff et al.’s (2007) meta-analysis supported the original assertion of Cavanaugh et al.
+(2000) such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.
+
+**Current Study and Hypotheses**
+
+  The brief review above provides theoretical and empirical support for the connection between resources and positive organizational outcomes, and between demands and negative outcomes.
+Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement (“a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption”, Schaufeli et al., 2002), workplace stress (“an individual state characterized by a combination of high arousal and displeasure”, p.
+15, Pejtersen et al., 2010) and burnout (“the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work”, p.
+197; Kristensen et al., 2005).
+Utilizing the job demands-resources theory, transactional theory of stress, and the challenge-hindrance framework, we propose that the number of job characteristics appraised as “challenge demands” (i.e., promote mastery, personal growth, and future gains) would activate a positive state – that of engagement.
+In contrast, number of characteristics of one’s job appraised as a hindrance demand (i.e., inhibit growth, learning and goal achievement) would activate a negative state – here, stress.
+
+*Hypothesis 1a-1c*: Total number of resources are positively associated with engagement (1a), and negatively associated with stress (1b) and burnout (1c).
+*Hypothesis 2a-2c*: Total number of  challenge demands are positively associated with engagement (2a), and negatively associated with stress (2b) and burnout (2c).
+*Hypothesis 3a-3c*: Total number of hindrance demands are negatively associated with engagement (3a), and positively associated with stress (3b) and burnout (3c).
+
+	 In addition to exploring associations with our outcomes, we also sought to explore whether challenges are perceived as distinct from resources.
+Given the definitions of each (i.e.,  aspect of one’s job that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development [resource] vs.
+aspect of one’s job that can promote mastery, personal growth, or future gains [challenge]), we propose respondents may consider them both in the realm of a resource.
+
+*Hypothesis 4*: Characteristics perceived as challenges are also viewed as resources.
+
+	In addition to the above predictions, we consider, in an exploratory fashion, whether or not the pattern of correlations is similar across different job classifications.
+We expect to see the relationships to emerge similarly regardless of one’s type of work.
+For example, we expect that across jobs, total hindrance demands would be negatively related to engagement.
+
+*Method*
+
+  We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (Bakker & Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001), but from within the unifying framework of O*Net.
+Here, we focus on the relationship between O*Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S.
+workforce representative sample.
+
+*Participants*
+
+  A sample using a Prolific panel resulted in 785 individuals who initially accessed the survey link.
+Of those,112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes & Wilhelm, 2021).
+Additional screening using four embedded attention checks resulted in the retention of 568 respondents.
+A total of 13.57% had been in their job less than 6 months, 19.20% between 6 months and a year, 49.12% between one and five years, 13.27% between 5 and 10 years, and 4.87% more than 10 years.
+Reported ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53).
+Gender was captured via a free-field gender identity category, although the sample predominantly self-identified as female (52.58%) or male (46.83%).
+Jobs were classified into the International Standard Classification of Occupations (ISCO) via the package labourR (Kouretsis et al., 2020).
+Modify or omit?
+*Materials*
+
+  Characteristics, Demands, and Resources.
+Our analyses included items within O*Net’s classifications of “work activity”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context”: 5) Interpersonal Relationships (14 statements), 6) Physical Work Conditions (30 statements)1, and 7) Structural Job Characteristics (13 statements).
+  Other than minor grammatical editing (for example, changing “the” to “you”), we retained the O*Net wording for our item stems.
+We used O*Net’s response scales, several of which were unique across items, but all shared the same 1 to 5 scale options.
+Subsequent to providing ratings of whether or not an O*Net characteristic was relevant for the respondent’s work, each respondent who agreed that an element had at least some relevance to their job was also asked to rate that element in terms of, 1) .
+.
+.
+this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) .
+.
+.
+this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) .
+.
+.
+this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
+*Stress*. Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Obtained alpha was .85 in this sample.
+*Burnout*. Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Alpha was 0.85 in this sample.
+*Engagement*.
+The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample α’s of 0.68 (Absorption) and 0.80 (Vigor), and 0.90 (Dedication).
+For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).
+
+*Procedure*
+
+  Data were collected through Prolific, a data collection platform.
+An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
+Eligibility requirements included being 18+ and holding either a full-time or part-time job.
+Participants then voluntarily chose to respond to the survey.
+The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes.
+Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified.
+Thus, if a respondent indicated that 5 of the characteristics were not part of their job, they were not subsequently asked to rate the level of resource, challenge, or hindrance a given item presented to them.
+For items that were a part of their jobs, they were then asked to report how much a characteristic was a resource, and then how much each characteristic was a hindrance, and finally, how much each item was a challenge.
+Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
+
+*Results*
+
+  We used R (Version 4.0.3; R Core Team, 2020) and the R-packages careless (Version 1.1.3; Yentes & Wilhelm, 2021), labourR (Version 1.0.0; Kouretsis et al., 2020), papaja (Version 0.1.0.9997; Aust & Barth, 2020), and tinylabels (Barth, 2021) for all analyses.
+Our analyses are presented by characteristics of work that are rated in terms of being resources, challenge demands, and hindrance demands.
+Pearson correlation coefficients between characteristics classified as resources, challenges, and hindrances were obtained to investigate the associations among these characteristics.
+Correlations, means and standard deviations among all study variables are presented in Table 1.
+Results reveal a positive association between resources and engagement (r = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively).
+Challenge demands were positively associated with engagement (r = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
+Total hindrance stressors were not significantly associated with our outcomes (H3a-H3c).
+To further explore H1-H3, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
+First, regarding engagement (F(3, 564) = 26.41, p < .001), the total resources (beta = ??) was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table 2).
+Next, stress was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 2.47, p = .060 (see Table 3).
+Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 1.10, p = .349.
+See Table 4.
+
+  Our fourth prediction suggested a positive association between total resources and total challenge demands.
+Here, we observed a strong positive relationship, so much so that it could be argued that these two variables are capturing the same thing (r = .86), as fully 74% of the variability was shared.
+  In an exploratory fashion, we also considered whether or not the pattern of correlations described above was similar across job types.
 

### 2022-09-20 SIOP2023/Counts/Submission_ResourceCount.Rmd
inefficient recoeds

@@
 ---
-title: "Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?"
-output:
-  pdf_document: 
-    latex_engine: xelatex
+title             : "Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?"
+shorttitle        : "BiFactor Engagement"
+
+author: 
+  - name          : "John Kulas"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "1 Normal Ave, Montclair, NJ 07043"
+    email         : "kulasj@montclair.edu"
+  - name          : "Renata Garcia Prieto Palacios Roji"
+    affiliation   : "1"
+  - name          : "Casey Osorio-Duffoo"
+    affiliation   : "2"
+  - name          : "Morgan Russell"
+    affiliation   : "1"
+
+affiliation:
+  - id            : "1"
+    institution   : "Montclair State University"
+  - id            : "2"
+    institution   : "Harver"
+
+authornote: |
+  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+
+  Enter author note here.
+
+abstract: |
+  The most commonly referenced definition of attitudinal engagement implicates sub-dimensions of vigor, dedication, and absorption.
+The tripartite model of attitudes specifies cognitive, behavioral, and affective components.
+The current study documents the development and initial validation of a new measure of engagement that intentionally crosses the substantive and attitudinal elements.
+
+keywords          : "Engagement, engagement"
+wordcount         : "X"
+
+bibliography      : ["r-references.bib"]
+
+floatsintext      : no #change to yes if we want all tables to be put in-line rather than pushed to end of paper
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : no
+mask              : no
+draft             : no
+
+documentclass     : "apa6"
+classoption       : "man"
+output            : papaja::apa6_pdf
 ---
@@
 knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
+papaja::r_refs("r-references.bib")
 
@@
 
-data22 <- data %>% 
-mutate_at(vars(118:372),
-function(x) recode(x,
-1==NA, 
-2==NA,
-3==NA,
-4==4,
-5==5))
+# data22 <- data %>% 
+# mutate_at(vars(118:372),
+# function(x) recode(x,
+# 1==NA, 
+# 2==NA,
+# 3==NA,
+# 4==4,
+# 5==5))
 
@@
 
-data22$resource <- rowSums(data22[c(118:144,146:202)], na.rm=TRUE)
-data22$hindrance <- rowSums(data22[c(203:247,249:287)], na.rm=TRUE)
-data22$challenge <- rowSums(data22[c(288:307,309:372)], na.rm=TRUE)
+data$resource <- rowSums(data[c(118:144,146:202)], na.rm=TRUE)
+data$hindrance <- rowSums(data[c(203:247,249:287)], na.rm=TRUE)
+data$challenge <- rowSums(data[c(288:307,309:372)], na.rm=TRUE)
 
-data22$item387 <- 7-data22$item387
-data22$burnout      <- rowMeans(data22[c(373:376)], na.rm=TRUE)
-data22$stress       <- rowMeans(data22[c(377:379)], na.rm=TRUE)
-data22$engagement   <- rowMeans(data22[c(380:399)], na.rm=TRUE)        ## probably need to recode some
+data$item387 <- 7-data$item387
+data$burnout      <- rowMeans(data[c(373:376)], na.rm=TRUE)
+data$stress       <- rowMeans(data[c(377:379)], na.rm=TRUE)
+data$engagement   <- rowMeans(data[c(380:399)], na.rm=TRUE)        ## probably need to recode some
 
-cor(data22[405:410], use="all.obs")   ## something to be told with resources and challenges
+cor(data[405:410], use="all.obs")   ## something to be told with resources and challenges
 
@@
 
-data22$rh1  <- data22$item118 + data22$item203
-data22$rh2  <- data22$item119 + data22$item204
-data22$rh3  <- data22$item120 + data22$item205
-data22$rh4  <- data22$item121 + data22$item206
-data22$rh5  <- data22$item122 + data22$item207
-data22$rh6  <- data22$item123 + data22$item208
-data22$rh7  <- data22$item124 + data22$item209
-data22$rh8  <- data22$item125 + data22$item210
-data22$rh9  <- data22$item126 + data22$item211
-data22$rh10 <- data22$item127 + data22$item212
-data22$rh11  <- data22$item128 + data22$item213
-data22$rh12  <- data22$item129 + data22$item214
-data22$rh13  <- data22$item130 + data22$item215
-data22$rh14  <- data22$item131 + data22$item216
-data22$rh15  <- data22$item132 + data22$item217
-data22$rh16  <- data22$item133 + data22$item218
-data22$rh17  <- data22$item134 + data22$item219
-data22$rh18  <- data22$item135 + data22$item220
-data22$rh19  <- data22$item136 + data22$item221
-data22$rh20  <- data22$item137 + data22$item222
-data22$rh21  <- data22$item138 + data22$item223
-data22$rh22  <- data22$item139 + data22$item224
-data22$rh23  <- data22$item140 + data22$item225
-data22$rh24  <- data22$item141 + data22$item226
-data22$rh25  <- data22$item142 + data22$item227
-data22$rh26  <- data22$item143 + data22$item228
-data22$rh27  <- data22$item144 + data22$item229
+data$rh1[data$item118 > 3 & data$item203 > 3 & data$item22 >  1] <- 1        ## characteristic also both
+data$rh1[data$item22 == 1] <- NA                                             ## Not a characteristic
+data$rh1[(data$item118 < 4 | data$item203 < 4) & data$item22 >  1] <- 0      ## characteristic but not both
 
-data22$rh28  <- data22$item146 + data22$item230
+data$rh2[ data$item119 > 3 & data$item204 > 3 &  data$item23 >  1] <- 1        
+data$rh2[(data$item119 < 4 | data$item204 < 4) & data$item23 >  1] <- 0
+data$rh2[                                        data$item23 == 1] <- NA
 
-data22$rh29  <- data22$item147 + data22$item231
-data22$rh30  <- data22$item148 + data22$item232
-data22$rh31  <- data22$item149 + data22$item233
-data22$rh32  <- data22$item150 + data22$item234
-data22$rh33  <- data22$item151 + data22$item235
-data22$rh34  <- data22$item152 + data22$item236
-data22$rh35  <- data22$item153 + data22$item237
-data22$rh36  <- data22$item154 + data22$item238
-data22$rh37  <- data22$item155 + data22$item239
-data22$rh38  <- data22$item156 + data22$item240
-data22$rh39  <- data22$item157 + data22$item241
-data22$rh40  <- data22$item158 + data22$item242
-data22$rh41  <- data22$item159 + data22$item243
-data22$rh42  <- data22$item160 + data22$item244
-data22$rh43  <- data22$item161 + data22$item245
-data22$rh44  <- data22$item162 + data22$item246
-data22$rh45  <- data22$item163 + data22$item247
+data$rh3[ data$item120 > 3 & data$item205 > 3 &  data$item24 >  1] <- 1        
+data$rh3[(data$item120 < 4 | data$item205 < 4) & data$item24 >  1] <- 0
+data$rh3[                                        data$item24 == 1] <- NA
 
-data22$rh46  <- data22$item164 + data22$item249
+data$rh4[ data$item121 > 3 & data$item206 > 3 &  data$item25 >  1] <- 1        
+data$rh4[(data$item121 < 4 | data$item206 < 4) & data$item25 >  1] <- 0
+data$rh4[                                        data$item25 == 1] <- NA
 
-data22$rh47  <- data22$item165 + data22$item250
-data22$rh48  <- data22$item166 + data22$item251
-data22$rh49  <- data22$item167 + data22$item252
-data22$rh50  <- data22$item168 + data22$item253
-data22$rh51  <- data22$item169 + data22$item254
-data22$rh52  <- data22$item170 + data22$item255
-data22$rh53  <- data22$item171 + data22$item256
-data22$rh54  <- data22$item172 + data22$item257
-data22$rh55  <- data22$item173 + data22$item258
-data22$rh56  <- data22$item174 + data22$item259
-data22$rh57  <- data22$item175 + data22$item260
-data22$rh58  <- data22$item176 + data22$item261
-data22$rh59  <- data22$item177 + data22$item262
-data22$rh60  <- data22$item178 + data22$item263
-data22$rh61  <- data22$item179 + data22$item264
-data22$rh62  <- data22$item180 + data22$item265
-data22$rh63  <- data22$item181 + data22$item266
-data22$rh64  <- data22$item182 + data22$item267
-data22$rh65  <- data22$item183 + data22$item268
-data22$rh66  <- data22$item184 + data22$item269
-data22$rh67  <- data22$item185 + data22$item270
-data22$rh68  <- data22$item186 + data22$item271
-data22$rh69  <- data22$item187 + data22$item272
-data22$rh70  <- data22$item188 + data22$item273
-data22$rh71  <- data22$item189 + data22$item274
-data22$rh72  <- data22$item190 + data22$item275
-data22$rh73  <- data22$item191 + data22$item276
-data22$rh74  <- data22$item192 + data22$item277
-data22$rh75  <- data22$item193 + data22$item278
-data22$rh76  <- data22$item194 + data22$item279
-data22$rh77  <- data22$item195 + data22$item280
-data22$rh78  <- data22$item196 + data22$item281
-data22$rh79  <- data22$item197 + data22$item282
-data22$rh80  <- data22$item198 + data22$item283
-data22$rh81  <- data22$item199 + data22$item284
-data22$rh82  <- data22$item200 + data22$item285
-data22$rh83  <- data22$item201 + data22$item286
-data22$rh84  <- data22$item202 + data22$item287
+data$rh5[ data$item122 > 3 & data$item207 > 3 &  data$item26 >  1] <- 1        
+data$rh5[(data$item122 < 4 | data$item207 < 4) & data$item26 >  1] <- 0
+data$rh5[                                        data$item26 == 1] <- NA
+
+data$rh6[ data$item123 > 3 & data$item208 > 3 &  data$item27 >  1] <- 1        
+data$rh6[(data$item123 < 4 | data$item208 < 4) & data$item27 >  1] <- 0
+data$rh6[                                        data$item27 == 1] <- NA
+
+data$rh7[ data$item124 > 3 & data$item209 > 3 &  data$item28 >  1] <- 1        
+data$rh7[(data$item124 < 4 | data$item209 < 4) & data$item28 >  1] <- 0
+data$rh7[                                        data$item28 == 1] <- NA
+
+data$rh8[ data$item125 > 3 & data$item210 > 3 &  data$item29 >  1] <- 1        
+data$rh8[(data$item125 < 4 | data$item210 < 4) & data$item29 >  1] <- 0
+data$rh8[                                        data$item29 == 1] <- NA
+
+data$rh9[ data$item126 > 3 & data$item211 > 3 &  data$item30 >  1] <- 1        
+data$rh9[(data$item126 < 4 | data$item211 < 4) & data$item30 >  1] <- 0
+data$rh9[                                        data$item30 == 1] <- NA
+
+data$rh10[ data$item127 > 3 & data$item212 > 3 &  data$item31 >  1] <- 1        
+data$rh10[(data$item127 < 4 | data$item212 < 4) & data$item31 >  1] <- 0
+data$rh10[                                        data$item31 == 1] <- NA
+
+data$rh11[ data$item128 > 3 & data$item213 > 3 &  data$item32 >  1] <- 1        
+data$rh11[(data$item128 < 4 | data$item213 < 4) & data$item32 >  1] <- 0
+data$rh11[                                        data$item32 == 1] <- NA
+
+data$rh12[ data$item129 > 3 & data$item214 > 3 &  data$item42 >  1] <- 1        
+data$rh12[(data$item129 < 4 | data$item214 < 4) & data$item42 >  1] <- 0
+data$rh12[                                        data$item42 == 1] <- NA
+
+data$rh13[ data$item130 > 3 & data$item215 > 3 &  data$item43 >  1] <- 1        
+data$rh13[(data$item130 < 4 | data$item215 < 4) & data$item43 >  1] <- 0
+data$rh13[                                        data$item43 == 1] <- NA
+
+data$rh14[ data$item131 > 3 & data$item216 > 3 &  data$item44 >  1] <- 1        
+data$rh14[(data$item131 < 4 | data$item216 < 4) & data$item44 >  1] <- 0
+data$rh14[                                        data$item44 == 1] <- NA
+
+data$rh15[ data$item132 > 3 & data$item217 > 3 &  data$item45 >  1] <- 1        
+data$rh15[(data$item132 < 4 | data$item217 < 4) & data$item45 >  1] <- 0
+data$rh15[                                        data$item45 == 1] <- NA
+
+data$rh16[ data$item133 > 3 & data$item218 > 3 &  data$item46 >  1] <- 1        
+data$rh16[(data$item133 < 4 | data$item218 < 4) & data$item46 >  1] <- 0
+data$rh16[                                        data$item46 == 1] <- NA
+
+data$rh17[ data$item134 > 3 & data$item219 > 3 &  data$item47 >  1] <- 1        
+data$rh17[(data$item134 < 4 | data$item219 < 4) & data$item47 >  1] <- 0
+data$rh17[                                        data$item47 == 1] <- NA
+
+data$rh18[ data$item135 > 3 & data$item220 > 3 &  data$item48 >  1] <- 1        
+data$rh18[(data$item135 < 4 | data$item220 < 4) & data$item48 >  1] <- 0
+data$rh18[                                        data$item48 == 1] <- NA
+
+data$rh19[ data$item136 > 3 & data$item221 > 3 &  data$item49 >  1] <- 1        
+data$rh19[(data$item136 < 4 | data$item221 < 4) & data$item49 >  1] <- 0
+data$rh19[                                        data$item49 == 1] <- NA
+
+data$rh20[ data$item137 > 3 & data$item222 > 3 &  data$item50 >  1] <- 1        
+data$rh20[(data$item137 < 4 | data$item222 < 4) & data$item50 >  1] <- 0
+data$rh20[                                        data$item50 == 1] <- NA
+
+data$rh21[ data$item138 > 3 & data$item223 > 3 &  data$item52 >  1] <- 1        
+data$rh21[(data$item138 < 4 | data$item223 < 4) & data$item52 >  1] <- 0
+data$rh21[                                        data$item52 == 1] <- NA
+
+data$rh22[ data$item139 > 3 & data$item224 > 3 &  data$item53 >  1] <- 1        
+data$rh22[(data$item139 < 4 | data$item224 < 4) & data$item53 >  1] <- 0
+data$rh22[                                        data$item53 == 1] <- NA
+
+data$rh23[ data$item140 > 3 & data$item225 > 3 &  data$item54 >  1] <- 1        
+data$rh23[(data$item140 < 4 | data$item225 < 4) & data$item54 >  1] <- 0
+data$rh23[                                        data$item54 == 1] <- NA
+
+data$rh24[ data$item141 > 3 & data$item226 > 3 &  data$item55 >  1] <- 1        
+data$rh24[(data$item141 < 4 | data$item226 < 4) & data$item55 >  1] <- 0
+data$rh24[                                        data$item55 == 1] <- NA
+
+data$rh25[ data$item142 > 3 & data$item227 > 3 &  data$item56 >  1] <- 1        
+data$rh25[(data$item142 < 4 | data$item227 < 4) & data$item56 >  1] <- 0
+data$rh25[                                        data$item56 == 1] <- NA
+
+data$rh26[ data$item143 > 3 & data$item228 > 3 &  data$item57 >  1] <- 1        
+data$rh26[(data$item143 < 4 | data$item228 < 4) & data$item57 >  1] <- 0
+data$rh26[                                        data$item57 == 1] <- NA
+
+data$rh27[ data$item144 > 3 & data$item229 > 3 &  data$item58 >  1] <- 1        
+data$rh27[(data$item144 < 4 | data$item229 < 4) & data$item58 >  1] <- 0
+data$rh27[                                        data$item58 == 1] <- NA
+
+data$rh28[ data$item146 > 3 & data$item230 > 3 &  data$item59 >  1] <- 1        
+data$rh28[(data$item146 < 4 | data$item230 < 4) & data$item59 >  1] <- 0
+data$rh28[                                        data$item59 == 1] <- NA
+
+data$rh29[ data$item147 > 3 & data$item231 > 3 &  data$item60 >  1] <- 1        
+data$rh29[(data$item147 < 4 | data$item231 < 4) & data$item60 >  1] <- 0
+data$rh29[                                        data$item60 == 1] <- NA
+
+data$rh30[ data$item148 > 3 & data$item232 > 3 &  data$item62 >  1] <- 1        
+data$rh30[(data$item148 < 4 | data$item232 < 4) & data$item62 >  1] <- 0
+data$rh30[                                        data$item62 == 1] <- NA
+
+data$rh31[ data$item149 > 3 & data$item233 > 3 &  data$item63 >  1] <- 1        
+data$rh31[(data$item149 < 4 | data$item233 < 4) & data$item63 >  1] <- 0
+data$rh31[                                        data$item63 == 1] <- NA
+
+data$rh32[ data$item150 > 3 & data$item234 > 3 &  data$item64 >  1] <- 1        
+data$rh32[(data$item150 < 4 | data$item234 < 4) & data$item64 >  1] <- 0
+data$rh32[                                        data$item64 == 1] <- NA
+
+data$rh33[ data$item151 > 3 & data$item235 > 3 &  data$item65 >  1] <- 1        
+data$rh33[(data$item151 < 4 | data$item235 < 4) & data$item65 >  1] <- 0
+data$rh33[                                        data$item65 == 1] <- NA
+
+data$rh34[ data$item152 > 3 & data$item236 > 3 &  data$item67 >  1] <- 1        
+data$rh34[(data$item152 < 4 | data$item236 < 4) & data$item67 >  1] <- 0
+data$rh34[                                        data$item67 == 1] <- NA
+
+data$rh35[ data$item153 > 3 & data$item237 > 3 &  data$item68 >  1] <- 1        
+data$rh35[(data$item153 < 4 | data$item237 < 4) & data$item68 >  1] <- 0
+data$rh35[                                        data$item68 == 1] <- NA
+
+data$rh36[ data$item154 > 3 & data$item238 > 3 &  data$item69 >  1] <- 1        
+data$rh36[(data$item154 < 4 | data$item238 < 4) & data$item69 >  1] <- 0
+data$rh36[                                        data$item69 == 1] <- NA
+
+data$rh37[ data$item155 > 3 & data$item239 > 3 &  data$item70 >  1] <- 1        
+data$rh37[(data$item155 < 4 | data$item239 < 4) & data$item70 >  1] <- 0
+data$rh37[                                        data$item70 == 1] <- NA
+
+data$rh38[ data$item156 > 3 & data$item240 > 3 &  data$item71 >  1] <- 1        
+data$rh38[(data$item156 < 4 | data$item240 < 4) & data$item71 >  1] <- 0
+data$rh38[                                        data$item71 == 1] <- NA
+
+data$rh39[ data$item157 > 3 & data$item241 > 3 &  data$item72 >  1] <- 1        
+data$rh39[(data$item157 < 4 | data$item241 < 4) & data$item72 >  1] <- 0
+data$rh39[                                        data$item72 == 1] <- NA
+
+data$rh40[ data$item158 > 3 & data$item242 > 3 &  data$item73 >  1] <- 1        
+data$rh40[(data$item158 < 4 | data$item242 < 4) & data$item73 >  1] <- 0
+data$rh40[                                        data$item73 == 1] <- NA
+
+data$rh41[ data$item159 > 3 & data$item243 > 3 &  data$item74 >  1] <- 1        
+data$rh41[(data$item159 < 4 | data$item243 < 4) & data$item74 >  1] <- 0
+data$rh41[                                        data$item74 == 1] <- NA
+
+data$rh42[ data$item160 > 3 & data$item244 > 3 &  data$item75 >  1] <- 1        
+data$rh42[(data$item160 < 4 | data$item244 < 4) & data$item75 >  1] <- 0
+data$rh42[                                        data$item75 == 1] <- NA
+
+data$rh43[ data$item161 > 3 & data$item245 > 3 &  data$item76 >  1] <- 1        
+data$rh43[(data$item161 < 4 | data$item245 < 4) & data$item76 >  1] <- 0
+data$rh43[                                        data$item76 == 1] <- NA
+
+data$rh44[ data$item162 > 3 & data$item246 > 3 &  data$item77 >  1] <- 1        
+data$rh44[(data$item162 < 4 | data$item246 < 4) & data$item77 >  1] <- 0
+data$rh44[                                        data$item77 == 1] <- NA
+
+data$rh45[ data$item163 > 3 & data$item247 > 3 &  data$item78 >  1] <- 1        
+data$rh45[(data$item163 < 4 | data$item247 < 4) & data$item78 >  1] <- 0
+data$rh45[                                        data$item78 == 1] <- NA
+
+data$rh46[ data$item164 > 3 & data$item249 > 3 &  data$item79 >  1] <- 1        
+data$rh46[(data$item164 < 4 | data$item249 < 4) & data$item79 >  1] <- 0
+data$rh46[                                        data$item79 == 1] <- NA
+
+data$rh47[ data$item165 > 3 & data$item250 > 3 &  data$item80 >  1] <- 1        
+data$rh47[(data$item165 < 4 | data$item250 < 4) & data$item80 >  1] <- 0
+data$rh47[                                        data$item80 == 1] <- NA
+
+data$rh48[ data$item166 > 3 & data$item251 > 3 &  data$item81 >  1] <- 1        
+data$rh48[(data$item166 < 4 | data$item251 < 4) & data$item81 >  1] <- 0
+data$rh48[                                        data$item81 == 1] <- NA
+
+data$rh49[ data$item167 > 3 & data$item252 > 3 &  data$item82 >  1] <- 1        
+data$rh49[(data$item167 < 4 | data$item252 < 4) & data$item82 >  1] <- 0
+data$rh49[                                        data$item82 == 1] <- NA
+
+data$rh50[ data$item168 > 3 & data$item253 > 3 &  data$item83 >  1] <- 1        
+data$rh50[(data$item168 < 4 | data$item253 < 4) & data$item83 >  1] <- 0
+data$rh50[                                        data$item83 == 1] <- NA
+
+data$rh51[ data$item169 > 3 & data$item254 > 3 &  data$item84 >  1] <- 1        
+data$rh51[(data$item169 < 4 | data$item254 < 4) & data$item84 >  1] <- 0
+data$rh51[                                        data$item84 == 1] <- NA
+
+data$rh52[ data$item170 > 3 & data$item255 > 3 &  data$item85 >  1] <- 1        
+data$rh52[(data$item170 < 4 | data$item255 < 4) & data$item85 >  1] <- 0
+data$rh52[                                        data$item85 == 1] <- NA
+
+data$rh53[ data$item171 > 3 & data$item256 > 3 &  data$item86 >  1] <- 1        
+data$rh53[(data$item171 < 4 | data$item256 < 4) & data$item86 >  1] <- 0
+data$rh53[                                        data$item86 == 1] <- NA
+
+data$rh54[ data$item172 > 3 & data$item257 > 3 &  data$item87 >  1] <- 1        
+data$rh54[(data$item172 < 4 | data$item257 < 4) & data$item87 >  1] <- 0
+data$rh54[                                        data$item87 == 1] <- NA
+
+data$rh55[ data$item173 > 3 & data$item258 > 3 &  data$item88 >  1] <- 1        
+data$rh55[(data$item173 < 4 | data$item258 < 4) & data$item88 >  1] <- 0
+data$rh55[                                        data$item88 == 1] <- NA
+
+data$rh56[ data$item174 > 3 & data$item259 > 3 &  data$item89 >  1] <- 1        
+data$rh56[(data$item174 < 4 | data$item259 < 4) & data$item89 >  1] <- 0
+data$rh56[                                        data$item89 == 1] <- NA
+
+data$rh57[ data$item175 > 3 & data$item260 > 3 &  data$item90 >  1] <- 1        
+data$rh57[(data$item175 < 4 | data$item260 < 4) & data$item90 >  1] <- 0
+data$rh57[                                        data$item90 == 1] <- NA
+
+data$rh58[ data$item176 > 3 & data$item261 > 3 &  data$item91 >  1] <- 1        
+data$rh58[(data$item176 < 4 | data$item261 < 4) & data$item91 >  1] <- 0
+data$rh58[                                        data$item91 == 1] <- NA
+
+data$rh59[ data$item177 > 3 & data$item262 > 3 &  data$item92 >  1] <- 1        
+data$rh59[(data$item177 < 4 | data$item262 < 4) & data$item92 >  1] <- 0
+data$rh59[                                        data$item92 == 1] <- NA
+
+data$rh60[ data$item178 > 3 & data$item263 > 3 &  data$item93 >  1] <- 1        
+data$rh60[(data$item178 < 4 | data$item263 < 4) & data$item93 >  1] <- 0
+data$rh60[                                        data$item93 == 1] <- NA
+
+data$rh61[ data$item179 > 3 & data$item264 > 3 &  data$item94 >  1] <- 1        
+data$rh61[(data$item179 < 4 | data$item264 < 4) & data$item94 >  1] <- 0
+data$rh61[                                        data$item94 == 1] <- NA
+
+data$rh62[ data$item180 > 3 & data$item265 > 3 &  data$item95 >  1] <- 1        
+data$rh62[(data$item180 < 4 | data$item265 < 4) & data$item95 >  1] <- 0
+data$rh62[                                        data$item95 == 1] <- NA
+
+data$rh63[ data$item181 > 3 & data$item266 > 3 &  data$item96 >  1] <- 1        
+data$rh63[(data$item181 < 4 | data$item266 < 4) & data$item96 >  1] <- 0
+data$rh63[                                        data$item96 == 1] <- NA
+
+data$rh64[ data$item182 > 3 & data$item267 > 3 &  data$item97 >  1] <- 1        
+data$rh64[(data$item182 < 4 | data$item267 < 4) & data$item97 >  1] <- 0
+data$rh64[                                        data$item97 == 1] <- NA
+
+data$rh65[ data$item183 > 3 & data$item268 > 3 &  data$item98 >  1] <- 1        
+data$rh65[(data$item183 < 4 | data$item268 < 4) & data$item98 >  1] <- 0
+data$rh65[                                        data$item98 == 1] <- NA
+
+data$rh66[ data$item184 > 3 & data$item269 > 3 &  data$item99 >  1] <- 1        
+data$rh66[(data$item184 < 4 | data$item269 < 4) & data$item99 >  1] <- 0
+data$rh66[                                        data$item99 == 1] <- NA
+
+data$rh67[ data$item185 > 3 & data$item270 > 3 &  data$item100 >  1] <- 1        
+data$rh67[(data$item185 < 4 | data$item270 < 4) & data$item100 >  1] <- 0
+data$rh67[                                        data$item100 == 1] <- NA
+
+data$rh68[ data$item186 > 3 & data$item271 > 3 &  data$item101 >  1] <- 1        
+data$rh68[(data$item186 < 4 | data$item271 < 4) & data$item101 >  1] <- 0
+data$rh68[                                        data$item101 == 1] <- NA
+
+data$rh69[ data$item187 > 3 & data$item272 > 3 &  data$item102 >  1] <- 1        
+data$rh69[(data$item187 < 4 | data$item272 < 4) & data$item102 >  1] <- 0
+data$rh69[                                        data$item102 == 1] <- NA
+
+data$rh70[ data$item188 > 3 & data$item273 > 3 &  data$item103 >  1] <- 1        
+data$rh70[(data$item188 < 4 | data$item273 < 4) & data$item103 >  1] <- 0
+data$rh70[                                        data$item103 == 1] <- NA
+
+data$rh71[ data$item189 > 3 & data$item274 > 3 &  data$item104 >  1] <- 1        
+data$rh71[(data$item189 < 4 | data$item274 < 4) & data$item104 >  1] <- 0
+data$rh71[                                        data$item104 == 1] <- NA
+
+data$rh72[ data$item190 > 3 & data$item275 > 3 &  data$item105 >  1] <- 1        
+data$rh72[(data$item190 < 4 | data$item275 < 4) & data$item105 >  1] <- 0
+data$rh72[                                        data$item105 == 1] <- NA
+
+data$rh73[ data$item191 > 3 & data$item276 > 3 &  data$item106 >  1] <- 1        
+data$rh73[(data$item191 < 4 | data$item276 < 4) & data$item106 >  1] <- 0
+data$rh73[                                        data$item106 == 1] <- NA
+
+data$rh74[ data$item192 > 3 & data$item277 > 3 &  data$item107 >  1] <- 1        
+data$rh74[(data$item192 < 4 | data$item277 < 4) & data$item107 >  1] <- 0
+data$rh74[                                        data$item107 == 1] <- NA
+
+data$rh75[ data$item193 > 3 & data$item278 > 3 &  data$item108 >  1] <- 1        
+data$rh75[(data$item193 < 4 | data$item278 < 4) & data$item108 >  1] <- 0
+data$rh75[                                        data$item108 == 1] <- NA
+
+data$rh76[ data$item194 > 3 & data$item279 > 3 &  data$item109 >  1] <- 1        
+data$rh76[(data$item194 < 4 | data$item279 < 4) & data$item109 >  1] <- 0
+data$rh76[                                        data$item109 == 1] <- NA
+
+data$rh77[ data$item195 > 3 & data$item280 > 3 &  data$item110 >  1] <- 1        
+data$rh77[(data$item195 < 4 | data$item280 < 4) & data$item110 >  1] <- 0
+data$rh77[                                        data$item110 == 1] <- NA
+
+data$rh78[ data$item196 > 3 & data$item281 > 3 &  data$item111 >  1] <- 1        
+data$rh78[(data$item196 < 4 | data$item281 < 4) & data$item111 >  1] <- 0
+data$rh78[                                        data$item111 == 1] <- NA
+
+data$rh79[ data$item197 > 3 & data$item282 > 3 &  data$item112 >  1] <- 1        
+data$rh79[(data$item197 < 4 | data$item282 < 4) & data$item112 >  1] <- 0
+data$rh79[                                        data$item112 == 1] <- NA
+
+data$rh80[ data$item198 > 3 & data$item283 > 3 &  data$item113 >  1] <- 1        
+data$rh80[(data$item198 < 4 | data$item283 < 4) & data$item113 >  1] <- 0
+data$rh80[                                        data$item113 == 1] <- NA
+
+data$rh81[ data$item199 > 3 & data$item284 > 3 &  data$item114 >  1] <- 1        
+data$rh81[(data$item199 < 4 | data$item284 < 4) & data$item114 >  1] <- 0
+data$rh81[                                        data$item114 == 1] <- NA
+
+data$rh82[ data$item200 > 3 & data$item285 > 3 &  data$item115 >  1] <- 1        
+data$rh82[(data$item200 < 4 | data$item285 < 4) & data$item115 >  1] <- 0
+data$rh82[                                        data$item115 == 1] <- NA
+
+data$rh83[ data$item201 > 3 & data$item286 > 3 &  data$item116 >  1] <- 1        
+data$rh83[(data$item201 < 4 | data$item286 < 4) & data$item116 >  1] <- 0
+data$rh83[                                        data$item116 == 1] <- NA
+
+data$rh84[ data$item202 > 3 & data$item287 > 3 &  data$item117 >  1] <- 1        
+data$rh84[(data$item202 < 4 | data$item287 < 4) & data$item117 >  1] <- 0
+data$rh84[                                        data$item117 == 1] <- NA
 
@@
 
-data22$rc1  <- data22$item118 + data22$item288
-data22$rc2  <- data22$item119 + data22$item289
-data22$rc3  <- data22$item120 + data22$item290
-data22$rc4  <- data22$item121 + data22$item291
-data22$rc5  <- data22$item122 + data22$item292
-data22$rc6  <- data22$item123 + data22$item293
-data22$rc7  <- data22$item124 + data22$item294
-data22$rc8  <- data22$item125 + data22$item295
-data22$rc9  <- data22$item126 + data22$item296
-data22$rc10 <- data22$item127 + data22$item297
-data22$rc11  <- data22$item128 + data22$item298
-data22$rc12  <- data22$item129 + data22$item299
-data22$rc13  <- data22$item130 + data22$item300
-data22$rc14  <- data22$item131 + data22$item301
-data22$rc15  <- data22$item132 + data22$item302
-data22$rc16  <- data22$item133 + data22$item303
-data22$rc17  <- data22$item134 + data22$item304
-data22$rc18  <- data22$item135 + data22$item305
-data22$rc19  <- data22$item136 + data22$item306
-data22$rc20  <- data22$item137 + data22$item307
+data$rc1[ data$item118 > 3 & data$item288 > 3 &  data$item22 >  1] <- 1        
+data$rc1[(data$item118 < 4 | data$item288 < 4) & data$item22 >  1] <- 0
+data$rc1[                                        data$item22 == 1] <- NA
 
-data22$rc21  <- data22$item138 + data22$item309
+data$rc2[ data$item119 > 3 & data$item289 > 3 &  data$item23 >  1] <- 1        
+data$rc2[(data$item119 < 4 | data$item289 < 4) & data$item23 >  1] <- 0
+data$rc2[                                        data$item23 == 1] <- NA
 
-data22$rc22  <- data22$item139 + data22$item310
-data22$rc23  <- data22$item140 + data22$item311
-data22$rc24  <- data22$item141 + data22$item312
-data22$rc25  <- data22$item142 + data22$item313
-data22$rc26  <- data22$item143 + data22$item314
-data22$rc27  <- data22$item144 + data22$item315
+data$rc3[ data$item120 > 3 & data$item290 > 3 &  data$item24 >  1] <- 1        
+data$rc3[(data$item120 < 4 | data$item290 < 4) & data$item24 >  1] <- 0
+data$rc3[                                        data$item24 == 1] <- NA
 
-data22$rc28  <- data22$item146 + data22$item316
+data$rc4[ data$item121 > 3 & data$item291 > 3 &  data$item25 >  1] <- 1        
+data$rc4[(data$item121 < 4 | data$item291 < 4) & data$item25 >  1] <- 0
+data$rc4[                                        data$item25 == 1] <- NA
 
-data22$rc29  <- data22$item147 + data22$item317
-data22$rc30  <- data22$item148 + data22$item318
-data22$rc31  <- data22$item149 + data22$item319
-data22$rc32  <- data22$item150 + data22$item320
-data22$rc33  <- data22$item151 + data22$item321
-data22$rc34  <- data22$item152 + data22$item322
-data22$rc35  <- data22$item153 + data22$item323
-data22$rc36  <- data22$item154 + data22$item324
-data22$rc37  <- data22$item155 + data22$item325
-data22$rc38  <- data22$item156 + data22$item326
-data22$rc39  <- data22$item157 + data22$item327
-data22$rc40  <- data22$item158 + data22$item328
-data22$rc41  <- data22$item159 + data22$item329
-data22$rc42  <- data22$item160 + data22$item330
-data22$rc43  <- data22$item161 + data22$item331
-data22$rc44  <- data22$item162 + data22$item332
-data22$rc45  <- data22$item163 + data22$item333
-data22$rc46  <- data22$item164 + data22$item334
-data22$rc47  <- data22$item165 + data22$item335
-data22$rc48  <- data22$item166 + data22$item336
-data22$rc49  <- data22$item167 + data22$item337
-data22$rc50  <- data22$item168 + data22$item338
-data22$rc51  <- data22$item169 + data22$item339
-data22$rc52  <- data22$item170 + data22$item340
-data22$rc53  <- data22$item171 + data22$item341
-data22$rc54  <- data22$item172 + data22$item342
-data22$rc55  <- data22$item173 + data22$item343
-data22$rc56  <- data22$item174 + data22$item344
-data22$rc57  <- data22$item175 + data22$item345
-data22$rc58  <- data22$item176 + data22$item346
-data22$rc59  <- data22$item177 + data22$item347
-data22$rc60  <- data22$item178 + data22$item348
-data22$rc61  <- data22$item179 + data22$item349
-data22$rc62  <- data22$item180 + data22$item350
-data22$rc63  <- data22$item181 + data22$item351
-data22$rc64  <- data22$item182 + data22$item352
-data22$rc65  <- data22$item183 + data22$item353
-data22$rc66  <- data22$item184 + data22$item354
-data22$rc67  <- data22$item185 + data22$item355
-data22$rc68  <- data22$item186 + data22$item356
-data22$rc69  <- data22$item187 + data22$item357
-data22$rc70  <- data22$item188 + data22$item358
-data22$rc71  <- data22$item189 + data22$item359
-data22$rc72  <- data22$item190 + data22$item360
-data22$rc73  <- data22$item191 + data22$item361
-data22$rc74  <- data22$item192 + data22$item362
-data22$rc75  <- data22$item193 + data22$item363
-data22$rc76  <- data22$item194 + data22$item364
-data22$rc77  <- data22$item195 + data22$item365
-data22$rc78  <- data22$item196 + data22$item366
-data22$rc79  <- data22$item197 + data22$item367
-data22$rc80  <- data22$item198 + data22$item368
-data22$rc81  <- data22$item199 + data22$item369
-data22$rc82  <- data22$item200 + data22$item370
-data22$rc83  <- data22$item201 + data22$item371
-data22$rc84  <- data22$item202 + data22$item372
+data$rc5[ data$item122 > 3 & data$item292 > 3 &  data$item26 >  1] <- 1        
+data$rc5[(data$item122 < 4 | data$item292 < 4) & data$item26 >  1] <- 0
+data$rc5[                                        data$item26 == 1] <- NA
+
+data$rc6[ data$item123 > 3 & data$item293 > 3 &  data$item27 >  1] <- 1        
+data$rc6[(data$item123 < 4 | data$item293 < 4) & data$item27 >  1] <- 0
+data$rc6[                                        data$item27 == 1] <- NA
+
+data$rc7[ data$item124 > 3 & data$item294 > 3 &  data$item28 >  1] <- 1        
+data$rc7[(data$item124 < 4 | data$item294 < 4) & data$item28 >  1] <- 0
+data$rc7[                                        data$item28 == 1] <- NA
+
+data$rc8[ data$item125 > 3 & data$item295 > 3 &  data$item29 >  1] <- 1        
+data$rc8[(data$item125 < 4 | data$item295 < 4) & data$item29 >  1] <- 0
+data$rc8[                                        data$item29 == 1] <- NA
+
+data$rc9[ data$item126 > 3 & data$item296 > 3 &  data$item30 >  1] <- 1        
+data$rc9[(data$item126 < 4 | data$item296 < 4) & data$item30 >  1] <- 0
+data$rc9[                                        data$item30 == 1] <- NA
+
+data$rc10[ data$item127 > 3 & data$item297 > 3 &  data$item31 >  1] <- 1        
+data$rc10[(data$item127 < 4 | data$item297 < 4) & data$item31 >  1] <- 0
+data$rc10[                                        data$item31 == 1] <- NA
+
+data$rc11[ data$item128 > 3 & data$item298 > 3 &  data$item32 >  1] <- 1        
+data$rc11[(data$item128 < 4 | data$item298 < 4) & data$item32 >  1] <- 0
+data$rc11[                                        data$item32 == 1] <- NA
+
+data$rc12[ data$item129 > 3 & data$item299 > 3 &  data$item42 >  1] <- 1        
+data$rc12[(data$item129 < 4 | data$item299 < 4) & data$item42 >  1] <- 0
+data$rc12[                                        data$item42 == 1] <- NA
+
+data$rc13[ data$item130 > 3 & data$item300 > 3 &  data$item43 >  1] <- 1        
+data$rc13[(data$item130 < 4 | data$item300 < 4) & data$item43 >  1] <- 0
+data$rc13[                                        data$item43 == 1] <- NA
+
+data$rc14[ data$item131 > 3 & data$item301 > 3 &  data$item44 >  1] <- 1        
+data$rc14[(data$item131 < 4 | data$item301 < 4) & data$item44 >  1] <- 0
+data$rc14[                                        data$item44 == 1] <- NA
+
+data$rc15[ data$item132 > 3 & data$item302 > 3 &  data$item45 >  1] <- 1        
+data$rc15[(data$item132 < 4 | data$item302 < 4) & data$item45 >  1] <- 0
+data$rc15[                                        data$item45 == 1] <- NA
+
+data$rc16[ data$item133 > 3 & data$item303 > 3 &  data$item46 >  1] <- 1        
+data$rc16[(data$item133 < 4 | data$item303 < 4) & data$item46 >  1] <- 0
+data$rc16[                                        data$item46 == 1] <- NA
+
+data$rc17[ data$item134 > 3 & data$item304 > 3 &  data$item47 >  1] <- 1        
+data$rc17[(data$item134 < 4 | data$item304 < 4) & data$item47 >  1] <- 0
+data$rc17[                                        data$item47 == 1] <- NA
+
+data$rc18[ data$item135 > 3 & data$item305 > 3 &  data$item48 >  1] <- 1        
+data$rc18[(data$item135 < 4 | data$item305 < 4) & data$item48 >  1] <- 0
+data$rc18[                                        data$item48 == 1] <- NA
+
+data$rc19[ data$item136 > 3 & data$item306 > 3 &  data$item49 >  1] <- 1        
+data$rc19[(data$item136 < 4 | data$item306 < 4) & data$item49 >  1] <- 0
+data$rc19[                                        data$item49 == 1] <- NA
+
+data$rc20[ data$item137 > 3 & data$item307 > 3 &  data$item50 >  1] <- 1        
+data$rc20[(data$item137 < 4 | data$item307 < 4) & data$item50 >  1] <- 0
+data$rc20[                                        data$item50 == 1] <- NA
+
+data$rc21[ data$item138 > 3 & data$item309 > 3 &  data$item52 >  1] <- 1        
+data$rc21[(data$item138 < 4 | data$item309 < 4) & data$item52 >  1] <- 0
+data$rc21[                                        data$item52 == 1] <- NA
+
+data$rc22[ data$item139 > 3 & data$item310 > 3 &  data$item53 >  1] <- 1        
+data$rc22[(data$item139 < 4 | data$item310 < 4) & data$item53 >  1] <- 0
+data$rc22[                                        data$item53 == 1] <- NA
+
+data$rc23[ data$item140 > 3 & data$item311 > 3 &  data$item54 >  1] <- 1        
+data$rc23[(data$item140 < 4 | data$item311 < 4) & data$item54 >  1] <- 0
+data$rc23[                                        data$item54 == 1] <- NA
+
+data$rc24[ data$item141 > 3 & data$item312 > 3 &  data$item55 >  1] <- 1        
+data$rc24[(data$item141 < 4 | data$item312 < 4) & data$item55 >  1] <- 0
+data$rc24[                                        data$item55 == 1] <- NA
+
+data$rc25[ data$item142 > 3 & data$item313 > 3 &  data$item56 >  1] <- 1        
+data$rc25[(data$item142 < 4 | data$item313 < 4) & data$item56 >  1] <- 0
+data$rc25[                                        data$item56 == 1] <- NA
+
+data$rc26[ data$item143 > 3 & data$item314 > 3 &  data$item57 >  1] <- 1        
+data$rc26[(data$item143 < 4 | data$item314 < 4) & data$item57 >  1] <- 0
+data$rc26[                                        data$item57 == 1] <- NA
+
+data$rc27[ data$item144 > 3 & data$item315 > 3 &  data$item58 >  1] <- 1        
+data$rc27[(data$item144 < 4 | data$item315 < 4) & data$item58 >  1] <- 0
+data$rc27[                                        data$item58 == 1] <- NA
+
+data$rc28[ data$item146 > 3 & data$item316 > 3 &  data$item59 >  1] <- 1        
+data$rc28[(data$item146 < 4 | data$item316 < 4) & data$item59 >  1] <- 0
+data$rc28[                                        data$item59 == 1] <- NA
+
+data$rc29[ data$item147 > 3 & data$item317 > 3 &  data$item60 >  1] <- 1        
+data$rc29[(data$item147 < 4 | data$item317 < 4) & data$item60 >  1] <- 0
+data$rc29[                                        data$item60 == 1] <- NA
+
+data$rc30[ data$item148 > 3 & data$item318 > 3 &  data$item62 >  1] <- 1        
+data$rc30[(data$item148 < 4 | data$item318 < 4) & data$item62 >  1] <- 0
+data$rc30[                                        data$item62 == 1] <- NA
+
+data$rc31[ data$item149 > 3 & data$item319 > 3 &  data$item63 >  1] <- 1        
+data$rc31[(data$item149 < 4 | data$item319 < 4) & data$item63 >  1] <- 0
+data$rc31[                                        data$item63 == 1] <- NA
+
+data$rc32[ data$item150 > 3 & data$item320 > 3 &  data$item64 >  1] <- 1        
+data$rc32[(data$item150 < 4 | data$item320 < 4) & data$item64 >  1] <- 0
+data$rc32[                                        data$item64 == 1] <- NA
+
+data$rc33[ data$item151 > 3 & data$item321 > 3 &  data$item65 >  1] <- 1        
+data$rc33[(data$item151 < 4 | data$item321 < 4) & data$item65 >  1] <- 0
+data$rc33[                                        data$item65 == 1] <- NA
+
+data$rc34[ data$item152 > 3 & data$item322 > 3 &  data$item67 >  1] <- 1        
+data$rc34[(data$item152 < 4 | data$item322 < 4) & data$item67 >  1] <- 0
+data$rc34[                                        data$item67 == 1] <- NA
+
+data$rc35[ data$item153 > 3 & data$item323 > 3 &  data$item68 >  1] <- 1        
+data$rc35[(data$item153 < 4 | data$item323 < 4) & data$item68 >  1] <- 0
+data$rc35[                                        data$item68 == 1] <- NA
+
+data$rc36[ data$item154 > 3 & data$item324 > 3 &  data$item69 >  1] <- 1        
+data$rc36[(data$item154 < 4 | data$item324 < 4) & data$item69 >  1] <- 0
+data$rc36[                                        data$item69 == 1] <- NA
+
+data$rc37[ data$item155 > 3 & data$item325 > 3 &  data$item70 >  1] <- 1        
+data$rc37[(data$item155 < 4 | data$item325 < 4) & data$item70 >  1] <- 0
+data$rc37[                                        data$item70 == 1] <- NA
+
+data$rc38[ data$item156 > 3 & data$item326 > 3 &  data$item71 >  1] <- 1        
+data$rc38[(data$item156 < 4 | data$item326 < 4) & data$item71 >  1] <- 0
+data$rc38[                                        data$item71 == 1] <- NA
+
+data$rc39[ data$item157 > 3 & data$item327 > 3 &  data$item72 >  1] <- 1        
+data$rc39[(data$item157 < 4 | data$item327 < 4) & data$item72 >  1] <- 0
+data$rc39[                                        data$item72 == 1] <- NA
+
+data$rc40[ data$item158 > 3 & data$item328 > 3 &  data$item73 >  1] <- 1        
+data$rc40[(data$item158 < 4 | data$item328 < 4) & data$item73 >  1] <- 0
+data$rc40[                                        data$item73 == 1] <- NA
+
+data$rc41[ data$item159 > 3 & data$item329 > 3 &  data$item74 >  1] <- 1        
+data$rc41[(data$item159 < 4 | data$item329 < 4) & data$item74 >  1] <- 0
+data$rc41[                                        data$item74 == 1] <- NA
+
+data$rc42[ data$item160 > 3 & data$item330 > 3 &  data$item75 >  1] <- 1        
+data$rc42[(data$item160 < 4 | data$item330 < 4) & data$item75 >  1] <- 0
+data$rc42[                                        data$item75 == 1] <- NA
+
+data$rc43[ data$item161 > 3 & data$item331 > 3 &  data$item76 >  1] <- 1        
+data$rc43[(data$item161 < 4 | data$item331 < 4) & data$item76 >  1] <- 0
+data$rc43[                                        data$item76 == 1] <- NA
+
+data$rc44[ data$item162 > 3 & data$item332 > 3 &  data$item77 >  1] <- 1        
+data$rc44[(data$item162 < 4 | data$item332 < 4) & data$item77 >  1] <- 0
+data$rc44[                                        data$item77 == 1] <- NA
+
+data$rc45[ data$item163 > 3 & data$item333 > 3 &  data$item78 >  1] <- 1        
+data$rc45[(data$item163 < 4 | data$item333 < 4) & data$item78 >  1] <- 0
+data$rc45[                                        data$item78 == 1] <- NA
+
+data$rc46[ data$item164 > 3 & data$item334 > 3 &  data$item79 >  1] <- 1        
+data$rc46[(data$item164 < 4 | data$item334 < 4) & data$item79 >  1] <- 0
+data$rc46[                                        data$item79 == 1] <- NA
+
+data$rc47[ data$item165 > 3 & data$item335 > 3 &  data$item80 >  1] <- 1        
+data$rc47[(data$item165 < 4 | data$item335 < 4) & data$item80 >  1] <- 0
+data$rc47[                                        data$item80 == 1] <- NA
+
+data$rc48[ data$item166 > 3 & data$item336 > 3 &  data$item81 >  1] <- 1        
+data$rc48[(data$item166 < 4 | data$item336 < 4) & data$item81 >  1] <- 0
+data$rc48[                                        data$item81 == 1] <- NA
+
+data$rc49[ data$item167 > 3 & data$item337 > 3 &  data$item82 >  1] <- 1        
+data$rc49[(data$item167 < 4 | data$item337 < 4) & data$item82 >  1] <- 0
+data$rc49[                                        data$item82 == 1] <- NA
+
+data$rc50[ data$item168 > 3 & data$item338 > 3 &  data$item83 >  1] <- 1        
+data$rc50[(data$item168 < 4 | data$item338 < 4) & data$item83 >  1] <- 0
+data$rc50[                                        data$item83 == 1] <- NA
+
+data$rc51[ data$item169 > 3 & data$item339 > 3 &  data$item84 >  1] <- 1        
+data$rc51[(data$item169 < 4 | data$item339 < 4) & data$item84 >  1] <- 0
+data$rc51[                                        data$item84 == 1] <- NA
+
+data$rc52[ data$item170 > 3 & data$item340 > 3 &  data$item85 >  1] <- 1        
+data$rc52[(data$item170 < 4 | data$item340 < 4) & data$item85 >  1] <- 0
+data$rc52[                                        data$item85 == 1] <- NA
+
+data$rc53[ data$item171 > 3 & data$item341 > 3 &  data$item86 >  1] <- 1        
+data$rc53[(data$item171 < 4 | data$item341 < 4) & data$item86 >  1] <- 0
+data$rc53[                                        data$item86 == 1] <- NA
+
+data$rc54[ data$item172 > 3 & data$item342 > 3 &  data$item87 >  1] <- 1        
+data$rc54[(data$item172 < 4 | data$item342 < 4) & data$item87 >  1] <- 0
+data$rc54[                                        data$item87 == 1] <- NA
+
+data$rc55[ data$item173 > 3 & data$item343 > 3 &  data$item88 >  1] <- 1        
+data$rc55[(data$item173 < 4 | data$item343 < 4) & data$item88 >  1] <- 0
+data$rc55[                                        data$item88 == 1] <- NA
+
+data$rc56[ data$item174 > 3 & data$item344 > 3 &  data$item89 >  1] <- 1        
+data$rc56[(data$item174 < 4 | data$item344 < 4) & data$item89 >  1] <- 0
+data$rc56[                                        data$item89 == 1] <- NA
+
+data$rc57[ data$item175 > 3 & data$item345 > 3 &  data$item90 >  1] <- 1        
+data$rc57[(data$item175 < 4 | data$item345 < 4) & data$item90 >  1] <- 0
+data$rc57[                                        data$item90 == 1] <- NA
+
+data$rc58[ data$item176 > 3 & data$item346 > 3 &  data$item91 >  1] <- 1        
+data$rc58[(data$item176 < 4 | data$item346 < 4) & data$item91 >  1] <- 0
+data$rc58[                                        data$item91 == 1] <- NA
+
+data$rc59[ data$item177 > 3 & data$item347 > 3 &  data$item92 >  1] <- 1        
+data$rc59[(data$item177 < 4 | data$item347 < 4) & data$item92 >  1] <- 0
+data$rc59[                                        data$item92 == 1] <- NA
+
+data$rc60[ data$item178 > 3 & data$item348 > 3 &  data$item93 >  1] <- 1        
+data$rc60[(data$item178 < 4 | data$item348 < 4) & data$item93 >  1] <- 0
+data$rc60[                                        data$item93 == 1] <- NA
+
+data$rc61[ data$item179 > 3 & data$item349 > 3 &  data$item94 >  1] <- 1        
+data$rc61[(data$item179 < 4 | data$item349 < 4) & data$item94 >  1] <- 0
+data$rc61[                                        data$item94 == 1] <- NA
+
+data$rc62[ data$item180 > 3 & data$item350 > 3 &  data$item95 >  1] <- 1        
+data$rc62[(data$item180 < 4 | data$item350 < 4) & data$item95 >  1] <- 0
+data$rc62[                                        data$item95 == 1] <- NA
+
+data$rc63[ data$item181 > 3 & data$item351 > 3 &  data$item96 >  1] <- 1        
+data$rc63[(data$item181 < 4 | data$item351 < 4) & data$item96 >  1] <- 0
+data$rc63[                                        data$item96 == 1] <- NA
+
+data$rc64[ data$item182 > 3 & data$item352 > 3 &  data$item97 >  1] <- 1        
+data$rc64[(data$item182 < 4 | data$item352 < 4) & data$item97 >  1] <- 0
+data$rc64[                                        data$item97 == 1] <- NA
+
+data$rc65[ data$item183 > 3 & data$item353 > 3 &  data$item98 >  1] <- 1        
+data$rc65[(data$item183 < 4 | data$item353 < 4) & data$item98 >  1] <- 0
+data$rc65[                                        data$item98 == 1] <- NA
+
+data$rc66[ data$item184 > 3 & data$item354 > 3 &  data$item99 >  1] <- 1        
+data$rc66[(data$item184 < 4 | data$item354 < 4) & data$item99 >  1] <- 0
+data$rc66[                                        data$item99 == 1] <- NA
+
+data$rc67[ data$item185 > 3 & data$item355 > 3 &  data$item100 >  1] <- 1        
+data$rc67[(data$item185 < 4 | data$item355 < 4) & data$item100 >  1] <- 0
+data$rc67[                                        data$item100 == 1] <- NA
+
+data$rc68[ data$item186 > 3 & data$item356 > 3 &  data$item101 >  1] <- 1        
+data$rc68[(data$item186 < 4 | data$item356 < 4) & data$item101 >  1] <- 0
+data$rc68[                                        data$item101 == 1] <- NA
+
+data$rc69[ data$item187 > 3 & data$item357 > 3 &  data$item102 >  1] <- 1        
+data$rc69[(data$item187 < 4 | data$item357 < 4) & data$item102 >  1] <- 0
+data$rc69[                                        data$item102 == 1] <- NA
+
+data$rc70[ data$item188 > 3 & data$item358 > 3 &  data$item103 >  1] <- 1        
+data$rc70[(data$item188 < 4 | data$item358 < 4) & data$item103 >  1] <- 0
+data$rc70[                                        data$item103 == 1] <- NA
+
+data$rc71[ data$item189 > 3 & data$item359 > 3 &  data$item104 >  1] <- 1        
+data$rc71[(data$item189 < 4 | data$item359 < 4) & data$item104 >  1] <- 0
+data$rc71[                                        data$item104 == 1] <- NA
+
+data$rc72[ data$item190 > 3 & data$item360 > 3 &  data$item105 >  1] <- 1        
+data$rc72[(data$item190 < 4 | data$item360 < 4) & data$item105 >  1] <- 0
+data$rc72[                                        data$item105 == 1] <- NA
+
+data$rc73[ data$item191 > 3 & data$item361 > 3 &  data$item106 >  1] <- 1        
+data$rc73[(data$item191 < 4 | data$item361 < 4) & data$item106 >  1] <- 0
+data$rc73[                                        data$item106 == 1] <- NA
+
+data$rc74[ data$item192 > 3 & data$item362 > 3 &  data$item107 >  1] <- 1        
+data$rc74[(data$item192 < 4 | data$item362 < 4) & data$item107 >  1] <- 0
+data$rc74[                                        data$item107 == 1] <- NA
+
+data$rc75[ data$item193 > 3 & data$item363 > 3 &  data$item108 >  1] <- 1        
+data$rc75[(data$item193 < 4 | data$item363 < 4) & data$item108 >  1] <- 0
+data$rc75[                                        data$item108 == 1] <- NA
+
+data$rc76[ data$item194 > 3 & data$item364 > 3 &  data$item109 >  1] <- 1        
+data$rc76[(data$item194 < 4 | data$item364 < 4) & data$item109 >  1] <- 0
+data$rc76[                                        data$item109 == 1] <- NA
+
+data$rc77[ data$item195 > 3 & data$item365 > 3 &  data$item110 >  1] <- 1        
+data$rc77[(data$item195 < 4 | data$item365 < 4) & data$item110 >  1] <- 0
+data$rc77[                                        data$item110 == 1] <- NA
+
+data$rc78[ data$item196 > 3 & data$item366 > 3 &  data$item111 >  1] <- 1        
+data$rc78[(data$item196 < 4 | data$item366 < 4) & data$item111 >  1] <- 0
+data$rc78[                                        data$item111 == 1] <- NA
+
+data$rc79[ data$item197 > 3 & data$item367 > 3 &  data$item112 >  1] <- 1        
+data$rc79[(data$item197 < 4 | data$item367 < 4) & data$item112 >  1] <- 0
+data$rc79[                                        data$item112 == 1] <- NA
+
+data$rc80[ data$item198 > 3 & data$item368 > 3 &  data$item113 >  1] <- 1        
+data$rc80[(data$item198 < 4 | data$item368 < 4) & data$item113 >  1] <- 0
+data$rc80[                                        data$item113 == 1] <- NA
+
+data$rc81[ data$item199 > 3 & data$item369 > 3 &  data$item114 >  1] <- 1        
+data$rc81[(data$item199 < 4 | data$item369 < 4) & data$item114 >  1] <- 0
+data$rc81[                                        data$item114 == 1] <- NA
+
+data$rc82[ data$item200 > 3 & data$item370 > 3 &  data$item115 >  1] <- 1        
+data$rc82[(data$item200 < 4 | data$item370 < 4) & data$item115 >  1] <- 0
+data$rc82[                                        data$item115 == 1] <- NA
+
+data$rc83[ data$item201 > 3 & data$item371 > 3 &  data$item116 >  1] <- 1        
+data$rc83[(data$item201 < 4 | data$item371 < 4) & data$item116 >  1] <- 0
+data$rc83[                                        data$item116 == 1] <- NA
+
+data$rc84[ data$item202 > 3 & data$item372 > 3 &  data$item117 >  1] <- 1        
+data$rc84[(data$item202 < 4 | data$item372 < 4) & data$item117 >  1] <- 0
+data$rc84[                                        data$item117 == 1] <- NA
 
@@
 
-data22$hc1  <- data22$item203 + data22$item288
-data22$hc2  <- data22$item204 + data22$item289
-data22$hc3  <- data22$item205 + data22$item290
-data22$hc4  <- data22$item206 + data22$item291
-data22$hc5  <- data22$item207 + data22$item292
-data22$hc6  <- data22$item208 + data22$item293
-data22$hc7  <- data22$item209 + data22$item294
-data22$hc8  <- data22$item210 + data22$item295
-data22$hc9  <- data22$item211 + data22$item296
-data22$hc10 <- data22$item212 + data22$item297
-data22$hc11  <- data22$item213 + data22$item298
-data22$hc12  <- data22$item214 + data22$item299
-data22$hc13  <- data22$item215 + data22$item300
-data22$hc14  <- data22$item216 + data22$item301
-data22$hc15  <- data22$item217 + data22$item302
-data22$hc16  <- data22$item218 + data22$item303
-data22$hc17  <- data22$item219 + data22$item304
-data22$hc18  <- data22$item220 + data22$item305
-data22$hc19  <- data22$item221 + data22$item306
-data22$hc20  <- data22$item222 + data22$item307
+data$hc1[ data$item203 > 3 & data$item288 > 3 &  data$item22 >  1] <- 1        
+data$hc1[(data$item203 < 4 | data$item288 < 4) & data$item22 >  1] <- 0
+data$hc1[                                        data$item22 == 1] <- NA
 
-data22$hc21  <- data22$item223 + data22$item309
+data$hc2[ data$item204 > 3 & data$item289 > 3 &  data$item23 >  1] <- 1        
+data$hc2[(data$item204 < 4 | data$item289 < 4) & data$item23 >  1] <- 0
+data$hc2[                                        data$item23 == 1] <- NA
 
-data22$hc22  <- data22$item224 + data22$item310
-data22$hc23  <- data22$item225 + data22$item311
-data22$hc24  <- data22$item226 + data22$item312
-data22$hc25  <- data22$item227 + data22$item313
-data22$hc26  <- data22$item228 + data22$item314
-data22$hc27  <- data22$item229 + data22$item315
-data22$hc28  <- data22$item230 + data22$item316
-data22$hc29  <- data22$item231 + data22$item317
-data22$hc30  <- data22$item232 + data22$item318
-data22$hc31  <- data22$item233 + data22$item319
-data22$hc32  <- data22$item234 + data22$item320
-data22$hc33  <- data22$item235 + data22$item321
-data22$hc34  <- data22$item236 + data22$item322
-data22$hc35  <- data22$item237 + data22$item323
-data22$hc36  <- data22$item238 + data22$item324
-data22$hc37  <- data22$item239 + data22$item325
-data22$hc38  <- data22$item240 + data22$item326
-data22$hc39  <- data22$item241 + data22$item327
-data22$hc40  <- data22$item242 + data22$item328
-data22$hc41  <- data22$item243 + data22$item329
-data22$hc42  <- data22$item244 + data22$item330
-data22$hc43  <- data22$item245 + data22$item331
-data22$hc44  <- data22$item246 + data22$item332
-data22$hc45  <- data22$item247 + data22$item333
+data$hc3[ data$item205 > 3 & data$item290 > 3 &  data$item24 >  1] <- 1        
+data$hc3[(data$item205 < 4 | data$item290 < 4) & data$item24 >  1] <- 0
+data$hc3[                                        data$item24 == 1] <- NA
 
-data22$hc46  <- data22$item249 + data22$item334
+data$hc4[ data$item206 > 3 & data$item291 > 3 &  data$item25 >  1] <- 1        
+data$hc4[(data$item206 < 4 | data$item291 < 4) & data$item25 >  1] <- 0
+data$hc4[                                        data$item25 == 1] <- NA
 
-data22$hc47  <- data22$item250 + data22$item335
-data22$hc48  <- data22$item251 + data22$item336
-data22$hc49  <- data22$item252 + data22$item337
-data22$hc50  <- data22$item253 + data22$item338
-data22$hc51  <- data22$item254 + data22$item339
-data22$hc52  <- data22$item255 + data22$item340
-data22$hc53  <- data22$item256 + data22$item341
-data22$hc54  <- data22$item257 + data22$item342
-data22$hc55  <- data22$item258 + data22$item343
-data22$hc56  <- data22$item259 + data22$item344
-data22$hc57  <- data22$item260 + data22$item345
-data22$hc58  <- data22$item261 + data22$item346
-data22$hc59  <- data22$item262 + data22$item347
-data22$hc60  <- data22$item263 + data22$item348
-data22$hc61  <- data22$item264 + data22$item349
-data22$hc62  <- data22$item265 + data22$item350
-data22$hc63  <- data22$item266 + data22$item351
-data22$hc64  <- data22$item267 + data22$item352
-data22$hc65  <- data22$item268 + data22$item353
-data22$hc66  <- data22$item269 + data22$item354
-data22$hc67  <- data22$item270 + data22$item355
-data22$hc68  <- data22$item271 + data22$item356
-data22$hc69  <- data22$item272 + data22$item357
-data22$hc70  <- data22$item273 + data22$item358
-data22$hc71  <- data22$item274 + data22$item359
-data22$hc72  <- data22$item275 + data22$item360
-data22$hc73  <- data22$item276 + data22$item361
-data22$hc74  <- data22$item277 + data22$item362
-data22$hc75  <- data22$item278 + data22$item363
-data22$hc76  <- data22$item279 + data22$item364
-data22$hc77  <- data22$item280 + data22$item365
-data22$hc78  <- data22$item281 + data22$item366
-data22$hc79  <- data22$item282 + data22$item367
-data22$hc80  <- data22$item283 + data22$item368
-data22$hc81  <- data22$item284 + data22$item369
-data22$hc82  <- data22$item285 + data22$item370
-data22$hc83  <- data22$item286 + data22$item371
-data22$hc84  <- data22$item287 + data22$item372
+data$hc5[ data$item207 > 3 & data$item292 > 3 &  data$item26 >  1] <- 1        
+data$hc5[(data$item207 < 4 | data$item292 < 4) & data$item26 >  1] <- 0
+data$hc5[                                        data$item26 == 1] <- NA
 
-isolated <- data22[,c(22:32, 42:50, 52:60, 62:65, 67:117,411:662)]  ## characteristic ratings scattered because we didn't ask for resource/demand ratings for characteristics such as "exposure to radiation" - 9/12/22
+data$hc6[ data$item208 > 3 & data$item293 > 3 &  data$item27 >  1] <- 1        
+data$hc6[(data$item208 < 4 | data$item293 < 4) & data$item27 >  1] <- 0
+data$hc6[                                        data$item27 == 1] <- NA
+
+data$hc7[ data$item209 > 3 & data$item294 > 3 &  data$item28 >  1] <- 1        
+data$hc7[(data$item209 < 4 | data$item294 < 4) & data$item28 >  1] <- 0
+data$hc7[                                        data$item28 == 1] <- NA
+
+data$hc8[ data$item210 > 3 & data$item295 > 3 &  data$item29 >  1] <- 1        
+data$hc8[(data$item210 < 4 | data$item295 < 4) & data$item29 >  1] <- 0
+data$hc8[                                        data$item29 == 1] <- NA
+
+data$hc9[ data$item211 > 3 & data$item296 > 3 &  data$item30 >  1] <- 1        
+data$hc9[(data$item211 < 4 | data$item296 < 4) & data$item30 >  1] <- 0
+data$hc9[                                        data$item30 == 1] <- NA
+
+data$hc10[ data$item212 > 3 & data$item297 > 3 &  data$item31 >  1] <- 1        
+data$hc10[(data$item212 < 4 | data$item297 < 4) & data$item31 >  1] <- 0
+data$hc10[                                        data$item31 == 1] <- NA
+
+data$hc11[ data$item213 > 3 & data$item298 > 3 &  data$item32 >  1] <- 1        
+data$hc11[(data$item213 < 4 | data$item298 < 4) & data$item32 >  1] <- 0
+data$hc11[                                        data$item32 == 1] <- NA
+
+data$hc12[ data$item214 > 3 & data$item299 > 3 &  data$item42 >  1] <- 1        
+data$hc12[(data$item214 < 4 | data$item299 < 4) & data$item42 >  1] <- 0
+data$hc12[                                        data$item42 == 1] <- NA
+
+data$hc13[ data$item215 > 3 & data$item300 > 3 &  data$item43 >  1] <- 1        
+data$hc13[(data$item215 < 4 | data$item300 < 4) & data$item43 >  1] <- 0
+data$hc13[                                        data$item43 == 1] <- NA
+
+data$hc14[ data$item216 > 3 & data$item301 > 3 &  data$item44 >  1] <- 1        
+data$hc14[(data$item216 < 4 | data$item301 < 4) & data$item44 >  1] <- 0
+data$hc14[                                        data$item44 == 1] <- NA
+
+data$hc15[ data$item217 > 3 & data$item302 > 3 &  data$item45 >  1] <- 1        
+data$hc15[(data$item217 < 4 | data$item302 < 4) & data$item45 >  1] <- 0
+data$hc15[                                        data$item45 == 1] <- NA
+
+data$hc16[ data$item218 > 3 & data$item303 > 3 &  data$item46 >  1] <- 1        
+data$hc16[(data$item218 < 4 | data$item303 < 4) & data$item46 >  1] <- 0
+data$hc16[                                        data$item46 == 1] <- NA
+
+data$hc17[ data$item219 > 3 & data$item304 > 3 &  data$item47 >  1] <- 1        
+data$hc17[(data$item219 < 4 | data$item304 < 4) & data$item47 >  1] <- 0
+data$hc17[                                        data$item47 == 1] <- NA
+
+data$hc18[ data$item220 > 3 & data$item305 > 3 &  data$item48 >  1] <- 1        
+data$hc18[(data$item220 < 4 | data$item305 < 4) & data$item48 >  1] <- 0
+data$hc18[                                        data$item48 == 1] <- NA
+
+data$hc19[ data$item221 > 3 & data$item306 > 3 &  data$item49 >  1] <- 1        
+data$hc19[(data$item221 < 4 | data$item306 < 4) & data$item49 >  1] <- 0
+data$hc19[                                        data$item49 == 1] <- NA
+
+data$hc20[ data$item222 > 3 & data$item307 > 3 &  data$item50 >  1] <- 1        
+data$hc20[(data$item222 < 4 | data$item307 < 4) & data$item50 >  1] <- 0
+data$hc20[                                        data$item50 == 1] <- NA
+
+data$hc21[ data$item223 > 3 & data$item309 > 3 &  data$item52 >  1] <- 1        
+data$hc21[(data$item223 < 4 | data$item309 < 4) & data$item52 >  1] <- 0
+data$hc21[                                        data$item52 == 1] <- NA
+
+data$hc22[ data$item224 > 3 & data$item310 > 3 &  data$item53 >  1] <- 1        
+data$hc22[(data$item224 < 4 | data$item310 < 4) & data$item53 >  1] <- 0
+data$hc22[                                        data$item53 == 1] <- NA
+
+data$hc23[ data$item225 > 3 & data$item311 > 3 &  data$item54 >  1] <- 1        
+data$hc23[(data$item225 < 4 | data$item311 < 4) & data$item54 >  1] <- 0
+data$hc23[                                        data$item54 == 1] <- NA
+
+data$hc24[ data$item226 > 3 & data$item312 > 3 &  data$item55 >  1] <- 1        
+data$hc24[(data$item226 < 4 | data$item312 < 4) & data$item55 >  1] <- 0
+data$hc24[                                        data$item55 == 1] <- NA
+
+data$hc25[ data$item227 > 3 & data$item313 > 3 &  data$item56 >  1] <- 1        
+data$hc25[(data$item227 < 4 | data$item313 < 4) & data$item56 >  1] <- 0
+data$hc25[                                        data$item56 == 1] <- NA
+
+data$hc26[ data$item228 > 3 & data$item314 > 3 &  data$item57 >  1] <- 1        
+data$hc26[(data$item228 < 4 | data$item314 < 4) & data$item57 >  1] <- 0
+data$hc26[                                        data$item57 == 1] <- NA
+
+data$hc27[ data$item229 > 3 & data$item315 > 3 &  data$item58 >  1] <- 1        
+data$hc27[(data$item229 < 4 | data$item315 < 4) & data$item58 >  1] <- 0
+data$hc27[                                        data$item58 == 1] <- NA
+
+data$hc28[ data$item230 > 3 & data$item316 > 3 &  data$item59 >  1] <- 1        
+data$hc28[(data$item230 < 4 | data$item316 < 4) & data$item59 >  1] <- 0
+data$hc28[                                        data$item59 == 1] <- NA
+
+data$hc29[ data$item231 > 3 & data$item317 > 3 &  data$item60 >  1] <- 1        
+data$hc29[(data$item231 < 4 | data$item317 < 4) & data$item60 >  1] <- 0
+data$hc29[                                        data$item60 == 1] <- NA
+
+data$hc30[ data$item232 > 3 & data$item318 > 3 &  data$item62 >  1] <- 1        
+data$hc30[(data$item232 < 4 | data$item318 < 4) & data$item62 >  1] <- 0
+data$hc30[                                        data$item62 == 1] <- NA
+
+data$hc31[ data$item233 > 3 & data$item319 > 3 &  data$item63 >  1] <- 1        
+data$hc31[(data$item233 < 4 | data$item319 < 4) & data$item63 >  1] <- 0
+data$hc31[                                        data$item63 == 1] <- NA
+
+data$hc32[ data$item234 > 3 & data$item320 > 3 &  data$item64 >  1] <- 1        
+data$hc32[(data$item234 < 4 | data$item320 < 4) & data$item64 >  1] <- 0
+data$hc32[                                        data$item64 == 1] <- NA
+
+data$hc33[ data$item235 > 3 & data$item321 > 3 &  data$item65 >  1] <- 1        
+data$hc33[(data$item235 < 4 | data$item321 < 4) & data$item65 >  1] <- 0
+data$hc33[                                        data$item65 == 1] <- NA
+
+data$hc34[ data$item236 > 3 & data$item322 > 3 &  data$item67 >  1] <- 1        
+data$hc34[(data$item236 < 4 | data$item322 < 4) & data$item67 >  1] <- 0
+data$hc34[                                        data$item67 == 1] <- NA
+
+data$hc35[ data$item237 > 3 & data$item323 > 3 &  data$item68 >  1] <- 1        
+data$hc35[(data$item237 < 4 | data$item323 < 4) & data$item68 >  1] <- 0
+data$hc35[                                        data$item68 == 1] <- NA
+
+data$hc36[ data$item238 > 3 & data$item324 > 3 &  data$item69 >  1] <- 1        
+data$hc36[(data$item238 < 4 | data$item324 < 4) & data$item69 >  1] <- 0
+data$hc36[                                        data$item69 == 1] <- NA
+
+data$hc37[ data$item239 > 3 & data$item325 > 3 &  data$item70 >  1] <- 1        
+data$hc37[(data$item239 < 4 | data$item325 < 4) & data$item70 >  1] <- 0
+data$hc37[                                        data$item70 == 1] <- NA
+
+data$hc38[ data$item240 > 3 & data$item326 > 3 &  data$item71 >  1] <- 1        
+data$hc38[(data$item240 < 4 | data$item326 < 4) & data$item71 >  1] <- 0
+data$hc38[                                        data$item71 == 1] <- NA
+
+data$hc39[ data$item241 > 3 & data$item327 > 3 &  data$item72 >  1] <- 1        
+data$hc39[(data$item241 < 4 | data$item327 < 4) & data$item72 >  1] <- 0
+data$hc39[                                        data$item72 == 1] <- NA
+
+data$hc40[ data$item242 > 3 & data$item328 > 3 &  data$item73 >  1] <- 1        
+data$hc40[(data$item242 < 4 | data$item328 < 4) & data$item73 >  1] <- 0
+data$hc40[                                        data$item73 == 1] <- NA
+
+data$hc41[ data$item243 > 3 & data$item329 > 3 &  data$item74 >  1] <- 1        
+data$hc41[(data$item243 < 4 | data$item329 < 4) & data$item74 >  1] <- 0
+data$hc41[                                        data$item74 == 1] <- NA
+
+data$hc42[ data$item244 > 3 & data$item330 > 3 &  data$item75 >  1] <- 1        
+data$hc42[(data$item244 < 4 | data$item330 < 4) & data$item75 >  1] <- 0
+data$hc42[                                        data$item75 == 1] <- NA
+
+data$hc43[ data$item245 > 3 & data$item331 > 3 &  data$item76 >  1] <- 1        
+data$hc43[(data$item245 < 4 | data$item331 < 4) & data$item76 >  1] <- 0
+data$hc43[                                        data$item76 == 1] <- NA
+
+data$hc44[ data$item246 > 3 & data$item332 > 3 &  data$item77 >  1] <- 1        
+data$hc44[(data$item246 < 4 | data$item332 < 4) & data$item77 >  1] <- 0
+data$hc44[                                        data$item77 == 1] <- NA
+
+data$hc45[ data$item247 > 3 & data$item333 > 3 &  data$item78 >  1] <- 1        
+data$hc45[(data$item247 < 4 | data$item333 < 4) & data$item78 >  1] <- 0
+data$hc45[                                        data$item78 == 1] <- NA
+
+data$hc46[ data$item249 > 3 & data$item334 > 3 &  data$item79 >  1] <- 1        
+data$hc46[(data$item249 < 4 | data$item334 < 4) & data$item79 >  1] <- 0
+data$hc46[                                        data$item79 == 1] <- NA
+
+data$hc47[ data$item250 > 3 & data$item335 > 3 &  data$item80 >  1] <- 1        
+data$hc47[(data$item250 < 4 | data$item335 < 4) & data$item80 >  1] <- 0
+data$hc47[                                        data$item80 == 1] <- NA
+
+data$hc48[ data$item251 > 3 & data$item336 > 3 &  data$item81 >  1] <- 1        
+data$hc48[(data$item251 < 4 | data$item336 < 4) & data$item81 >  1] <- 0
+data$hc48[                                        data$item81 == 1] <- NA
+
+data$hc49[ data$item252 > 3 & data$item337 > 3 &  data$item82 >  1] <- 1        
+data$hc49[(data$item252 < 4 | data$item337 < 4) & data$item82 >  1] <- 0
+data$hc49[                                        data$item82 == 1] <- NA
+
+data$hc50[ data$item253 > 3 & data$item338 > 3 &  data$item83 >  1] <- 1        
+data$hc50[(data$item253 < 4 | data$item338 < 4) & data$item83 >  1] <- 0
+data$hc50[                                        data$item83 == 1] <- NA
+
+data$hc51[ data$item254 > 3 & data$item339 > 3 &  data$item84 >  1] <- 1        
+data$hc51[(data$item254 < 4 | data$item339 < 4) & data$item84 >  1] <- 0
+data$hc51[                                        data$item84 == 1] <- NA
+
+data$hc52[ data$item255 > 3 & data$item340 > 3 &  data$item85 >  1] <- 1        
+data$hc52[(data$item255 < 4 | data$item340 < 4) & data$item85 >  1] <- 0
+data$hc52[                                        data$item85 == 1] <- NA
+
+data$hc53[ data$item256 > 3 & data$item341 > 3 &  data$item86 >  1] <- 1        
+data$hc53[(data$item256 < 4 | data$item341 < 4) & data$item86 >  1] <- 0
+data$hc53[                                        data$item86 == 1] <- NA
+
+data$hc54[ data$item257 > 3 & data$item342 > 3 &  data$item87 >  1] <- 1        
+data$hc54[(data$item257 < 4 | data$item342 < 4) & data$item87 >  1] <- 0
+data$hc54[                                        data$item87 == 1] <- NA
+
+data$hc55[ data$item258 > 3 & data$item343 > 3 &  data$item88 >  1] <- 1        
+data$hc55[(data$item258 < 4 | data$item343 < 4) & data$item88 >  1] <- 0
+data$hc55[                                        data$item88 == 1] <- NA
+
+data$hc56[ data$item259 > 3 & data$item344 > 3 &  data$item89 >  1] <- 1        
+data$hc56[(data$item259 < 4 | data$item344 < 4) & data$item89 >  1] <- 0
+data$hc56[                                        data$item89 == 1] <- NA
+
+data$hc57[ data$item260 > 3 & data$item345 > 3 &  data$item90 >  1] <- 1        
+data$hc57[(data$item260 < 4 | data$item345 < 4) & data$item90 >  1] <- 0
+data$hc57[                                        data$item90 == 1] <- NA
+
+data$hc58[ data$item261 > 3 & data$item346 > 3 &  data$item91 >  1] <- 1        
+data$hc58[(data$item261 < 4 | data$item346 < 4) & data$item91 >  1] <- 0
+data$hc58[                                        data$item91 == 1] <- NA
+
+data$hc59[ data$item262 > 3 & data$item347 > 3 &  data$item92 >  1] <- 1        
+data$hc59[(data$item262 < 4 | data$item347 < 4) & data$item92 >  1] <- 0
+data$hc59[                                        data$item92 == 1] <- NA
+
+data$hc60[ data$item263 > 3 & data$item348 > 3 &  data$item93 >  1] <- 1        
+data$hc60[(data$item263 < 4 | data$item348 < 4) & data$item93 >  1] <- 0
+data$hc60[                                        data$item93 == 1] <- NA
+
+data$hc61[ data$item264 > 3 & data$item349 > 3 &  data$item94 >  1] <- 1        
+data$hc61[(data$item264 < 4 | data$item349 < 4) & data$item94 >  1] <- 0
+data$hc61[                                        data$item94 == 1] <- NA
+
+data$hc62[ data$item265 > 3 & data$item350 > 3 &  data$item95 >  1] <- 1        
+data$hc62[(data$item265 < 4 | data$item350 < 4) & data$item95 >  1] <- 0
+data$hc62[                                        data$item95 == 1] <- NA
+
+data$hc63[ data$item266 > 3 & data$item351 > 3 &  data$item96 >  1] <- 1        
+data$hc63[(data$item266 < 4 | data$item351 < 4) & data$item96 >  1] <- 0
+data$hc63[                                        data$item96 == 1] <- NA
+
+data$hc64[ data$item267 > 3 & data$item352 > 3 &  data$item97 >  1] <- 1        
+data$hc64[(data$item267 < 4 | data$item352 < 4) & data$item97 >  1] <- 0
+data$hc64[                                        data$item97 == 1] <- NA
+
+data$hc65[ data$item268 > 3 & data$item353 > 3 &  data$item98 >  1] <- 1        
+data$hc65[(data$item268 < 4 | data$item353 < 4) & data$item98 >  1] <- 0
+data$hc65[                                        data$item98 == 1] <- NA
+
+data$hc66[ data$item269 > 3 & data$item354 > 3 &  data$item99 >  1] <- 1        
+data$hc66[(data$item269 < 4 | data$item354 < 4) & data$item99 >  1] <- 0
+data$hc66[                                        data$item99 == 1] <- NA
+
+data$hc67[ data$item270 > 3 & data$item355 > 3 &  data$item100 >  1] <- 1        
+data$hc67[(data$item270 < 4 | data$item355 < 4) & data$item100 >  1] <- 0
+data$hc67[                                        data$item100 == 1] <- NA
+
+data$hc68[ data$item271 > 3 & data$item356 > 3 &  data$item101 >  1] <- 1        
+data$hc68[(data$item271 < 4 | data$item356 < 4) & data$item101 >  1] <- 0
+data$hc68[                                        data$item101 == 1] <- NA
+
+data$hc69[ data$item272 > 3 & data$item357 > 3 &  data$item102 >  1] <- 1        
+data$hc69[(data$item272 < 4 | data$item357 < 4) & data$item102 >  1] <- 0
+data$hc69[                                        data$item102 == 1] <- NA
+
+data$hc70[ data$item273 > 3 & data$item358 > 3 &  data$item103 >  1] <- 1        
+data$hc70[(data$item273 < 4 | data$item358 < 4) & data$item103 >  1] <- 0
+data$hc70[                                        data$item103 == 1] <- NA
+
+data$hc71[ data$item274 > 3 & data$item359 > 3 &  data$item104 >  1] <- 1        
+data$hc71[(data$item274 < 4 | data$item359 < 4) & data$item104 >  1] <- 0
+data$hc71[                                        data$item104 == 1] <- NA
+
+data$hc72[ data$item275 > 3 & data$item360 > 3 &  data$item105 >  1] <- 1        
+data$hc72[(data$item275 < 4 | data$item360 < 4) & data$item105 >  1] <- 0
+data$hc72[                                        data$item105 == 1] <- NA
+
+data$hc73[ data$item276 > 3 & data$item361 > 3 &  data$item106 >  1] <- 1        
+data$hc73[(data$item276 < 4 | data$item361 < 4) & data$item106 >  1] <- 0
+data$hc73[                                        data$item106 == 1] <- NA
+
+data$hc74[ data$item277 > 3 & data$item362 > 3 &  data$item107 >  1] <- 1        
+data$hc74[(data$item277 < 4 | data$item362 < 4) & data$item107 >  1] <- 0
+data$hc74[                                        data$item107 == 1] <- NA
+
+data$hc75[ data$item278 > 3 & data$item363 > 3 &  data$item108 >  1] <- 1        
+data$hc75[(data$item278 < 4 | data$item363 < 4) & data$item108 >  1] <- 0
+data$hc75[                                        data$item108 == 1] <- NA
+
+data$hc76[ data$item279 > 3 & data$item364 > 3 &  data$item109 >  1] <- 1        
+data$hc76[(data$item279 < 4 | data$item364 < 4) & data$item109 >  1] <- 0
+data$hc76[                                        data$item109 == 1] <- NA
+
+data$hc77[ data$item280 > 3 & data$item365 > 3 &  data$item110 >  1] <- 1        
+data$hc77[(data$item280 < 4 | data$item365 < 4) & data$item110 >  1] <- 0
+data$hc77[                                        data$item110 == 1] <- NA
+
+data$hc78[ data$item281 > 3 & data$item366 > 3 &  data$item111 >  1] <- 1        
+data$hc78[(data$item281 < 4 | data$item366 < 4) & data$item111 >  1] <- 0
+data$hc78[                                        data$item111 == 1] <- NA
+
+data$hc79[ data$item282 > 3 & data$item367 > 3 &  data$item112 >  1] <- 1        
+data$hc79[(data$item282 < 4 | data$item367 < 4) & data$item112 >  1] <- 0
+data$hc79[                                        data$item112 == 1] <- NA
+
+data$hc80[ data$item283 > 3 & data$item368 > 3 &  data$item113 >  1] <- 1        
+data$hc80[(data$item283 < 4 | data$item368 < 4) & data$item113 >  1] <- 0
+data$hc80[                                        data$item113 == 1] <- NA
+
+data$hc81[ data$item284 > 3 & data$item369 > 3 &  data$item114 >  1] <- 1        
+data$hc81[(data$item284 < 4 | data$item369 < 4) & data$item114 >  1] <- 0
+data$hc81[                                        data$item114 == 1] <- NA
+
+data$hc82[ data$item285 > 3 & data$item370 > 3 &  data$item115 >  1] <- 1        
+data$hc82[(data$item285 < 4 | data$item370 < 4) & data$item115 >  1] <- 0
+data$hc82[                                        data$item115 == 1] <- NA
+
+data$hc83[ data$item286 > 3 & data$item371 > 3 &  data$item116 >  1] <- 1        
+data$hc83[(data$item286 < 4 | data$item371 < 4) & data$item116 >  1] <- 0
+data$hc83[                                        data$item116 == 1] <- NA
+
+data$hc84[ data$item287 > 3 & data$item372 > 3 &  data$item117 >  1] <- 1        
+data$hc84[(data$item287 < 4 | data$item372 < 4) & data$item117 >  1] <- 0
+data$hc84[                                        data$item117 == 1] <- NA
+
+#isolated <- data[,c(22:32, 42:50, 52:60, 62:65, 67:117,411:662)]  ## characteristic ratings scattered because we didn't ask for resource/demand ratings for characteristics such as "exposure to radiation" - 9/12/22
 
@@
 
-r <- corx::corx(data22[,c(405:410)],                    
+r <- corx::corx(data[,c(405:410)],                    
                 triangle = "lower",
@@
 
-#cor(data22[405:410], use="all.obs")   ## something to be told with resources and challenges
+#cor(data[405:410], use="all.obs")   ## something to be told with resources and challenges
 
@@
 
-eng <- lm(engagement ~ hindrance + challenge + resource, data22)
-bur <- lm(burnout ~ hindrance + challenge + resource, data22)
-str <- lm(stress ~ hindrance + challenge + resource, data22)
+eng <- lm(engagement ~ hindrance + challenge + resource, data)
+bur <- lm(burnout ~ hindrance + challenge + resource, data)
+str <- lm(stress ~ hindrance + challenge + resource, data)
 

### 2022-09-20 SIOP2023/Counts/Submission_ResourceCount.tex
inefficient recoeds

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Engagement, engagement\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?},
  pdfauthor={John Kulas1, Renata Garcia Prieto Palacios Roji1, Casey Osorio-Duffoo2, \& Morgan Russell1},
  pdflang={en-EN},
  pdfkeywords={Engagement, engagement},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?}
\author{John Kulas\textsuperscript{1}, Renata Garcia Prieto Palacios Roji\textsuperscript{1}, Casey Osorio-Duffoo\textsuperscript{2}, \& Morgan Russell\textsuperscript{1}}
\date{}

\shorttitle{BiFactor Engagement}

\authornote{

Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

Correspondence concerning this article should be addressed to John Kulas, 1 Normal Ave, Montclair, NJ 07043. E-mail: \href{mailto:kulasj@montclair.edu}{\nolinkurl{kulasj@montclair.edu}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Montclair State University\\\textsuperscript{2} Harver}

\abstract{%
The most commonly referenced definition of attitudinal engagement implicates sub-dimensions of vigor, dedication, and absorption. The tripartite model of attitudes specifies cognitive, behavioral, and affective components. The current study documents the development and initial validation of a new measure of engagement that intentionally crosses the substantive and attitudinal elements.
}

\begin{document}
\maketitle

\textbf{Abstract}

The relationships among sum of perceived job resources, challenge- and hindrance demands and outcomes of organizational outcomes of engagement, stress, and burnout are explored. 568 workers rated O*Net job characteristics in terms of relevance and perceptions as challenges, hindrances and resources. The findings are generally aligned with the job demands resource theory regarding associations between perceived resources, demands, and organizational outcomes of engagement, stress, and burnout.

\textbf{Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?}

A plethora of research applying the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker \& Demerouti, 2017) underscore the importance of work characteristics on the experience of motivation and strain. However, much of our existing research on this topic assumes that certain characteristics are resources and others are generally considered demands. This study explores how individual perceptions of these work characteristics relate to engagement, stress, and burnout by asking respondents to indicate (of the characteristics that apply to their jobs) how much each is a resource, challenge, or hindrance demand. Amount of perceived resources, challenges, and hindrances can then be associated with engagement, stress, and burnout.

\textbf{The Job Demands-Resources Theory}

The theoretical foundation for this study is the job demands-resources theory (Demerouti et al., 2001). Using this theory, we can model both work environment and job characteristics via job resources and demands. Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001). In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure; Demerouti et al., 2001).

The perception of a characteristic of one's job as a resource or demand activates one of two unique processes: either health impairment or motivation Bakker \& Demerouti, 2014). Demanding job characteristics are frequently associated with negative outcomes (e.g., health impairment process; Bakker et al., 2003), whereas job characteristics considered resources have been associated with positive organizational outcomes like engagement and motivation (Bakker et al., 2007).

\textbf{An Added Complexity: Perception (Appraisal) of Work Characteristics Might Matter}

The above description speaks to one of two distinct processes being activated, presumably based on one's assessment of how a work characteristics makes them feel (e.g., consider the different reactions employees may have to being nominated to give a speech at an upcoming company event). Thus, although some research on job demands in particular is based on a priori classifications of demands (Searle \& Auton, 2015), the appraisal of any work characteristic as a demand or resource is quite subjective. The literature on the experience of stress explains how such individual differences in appraisal are possible. Specifically, the transactional theory of stress and coping states that people cognitively appraise stimuli in their environments on a continuous basis (Lazarus \& Folkman, 1984). During this process, meaning is assigned to stimuli. If the above employee appraised the upcoming speech as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping (e.g., attempting to decline, asking for help in writing the speech). From that point, the cycle of appraisal continues based on the action to cope with the stressor (Lazarus \& Folkman, 1984).

\textbf{Could a Work Demand be Appraised Positively?: The Challenge-Hindrance Framework}

Although the word ``stress'' often connotes something negative, Selye (1936) defined stress generically as a response to change. For instance, the example above describes an employee who appraises being nominated to give a speech as a negative stressor. However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired. The terms associated with the two different appraisals of the stressor described here are challenge and hindrance demands (Cavanaugh et al., 2000) Specifically, challenge demands promote mastery, personal growth, and future gains. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes (e.g., Cavanaugh et al., 2000). We will explore their associations with both positive and negative outcomes in this study.

Prior to proposing specific predictions, the empirical evidence on challenge and hindrance demands is very briefly shared below. To begin, the first logical question is whether employees actually distinguish between challenge and hindrance stressors, and research suggests that they can and do. For example, Bakker and Sanz-Vergel (2013) found that perceived work pressure can be classified as a hindrance demand, and emotional demands as a challenge demand. Webster et al.~(2011) considered three common workplace demands including workload, role ambiguity, and role conflict. Interestingly, they found that while each could be appraised primarily as challenges or hindrances, employees could also simultaneously be perceived as being both a challenge and hindrance.

Having established that there can be individual differences in the appraisal of demands as challenges or resources, we next turn our attention to their association with organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and well-being. For example, Cavanaugh et al.~(2000) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern with job satisfaction and job search behaviors in a sample of managers. However, Abbas and Raja (2019) found that challenge and hindrance stressors were both positively related to strain and turnover intentions. We also have some evidence that challenge-hinderance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford et al., 2010). The appraisal process also suggests theoretically that the perception of a job characteristic as a challenge or hindrance is a mediator. Gerich (2017), for instance, found that employee well-being was, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands. To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, Podsakoff et al.'s (2007) meta-analysis supported the original assertion of Cavanaugh et al.~(2000) such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.

\textbf{Current Study and Hypotheses}

The brief review above provides theoretical and empirical support for the connection between resources and positive organizational outcomes, and between demands and negative outcomes. Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement (``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption'', Schaufeli et al., 2002), workplace stress (``an individual state characterized by a combination of high arousal and displeasure'', p.~15, Pejtersen et al., 2010) and burnout (``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work'', p.~197; Kristensen et al., 2005). Utilizing the job demands-resources theory, transactional theory of stress, and the challenge-hindrance framework, we propose that the number of job characteristics appraised as ``challenge demands'' (i.e., promote mastery, personal growth, and future gains) would activate a positive state -- that of engagement. In contrast, number of characteristics of one's job appraised as a hindrance demand (i.e., inhibit growth, learning and goal achievement) would activate a negative state -- here, stress.

\emph{Hypothesis 1a-1c}: Total number of resources are positively associated with engagement (1a), and negatively associated with stress (1b) and burnout (1c).
\emph{Hypothesis 2a-2c}: Total number of challenge demands are positively associated with engagement (2a), and negatively associated with stress (2b) and burnout (2c).
\emph{Hypothesis 3a-3c}: Total number of hindrance demands are negatively associated with engagement (3a), and positively associated with stress (3b) and burnout (3c).

\begin{verbatim}
 In addition to exploring associations with our outcomes, we also sought to explore whether challenges are perceived as distinct from resources. Given the definitions of each (i.e.,  aspect of one’s job that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development [resource] vs. aspect of one’s job that can promote mastery, personal growth, or future gains [challenge]), we propose respondents may consider them both in the realm of a resource.

\end{verbatim}

\emph{Hypothesis 4}: Characteristics perceived as challenges are also viewed as resources.

\begin{verbatim}
In addition to the above predictions, we consider, in an exploratory fashion, whether or not the pattern of correlations is similar across different job classifications. We expect to see the relationships to emerge similarly regardless of one’s type of work. For example, we expect that across jobs, total hindrance demands would be negatively related to engagement.
\end{verbatim}

\emph{Method}

We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (Bakker \& Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001), but from within the unifying framework of O\emph{Net. Here, we focus on the relationship between O}Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S. workforce representative sample.

\emph{Participants}

A sample using a Prolific panel resulted in 785 individuals who initially accessed the survey link. Of those,112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021). Additional screening using four embedded attention checks resulted in the retention of 568 respondents. A total of 13.57\% had been in their job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years. Reported ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53). Gender was captured via a free-field gender identity category, although the sample predominantly self-identified as female (52.58\%) or male (46.83\%). Jobs were classified into the International Standard Classification of Occupations (ISCO) via the package labourR (Kouretsis et al., 2020). Modify or omit?
\emph{Materials}

Characteristics, Demands, and Resources. Our analyses included items within O\emph{Net's classifications of ``work activity'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'': 5) Interpersonal Relationships (14 statements), 6) Physical Work Conditions (30 statements)1, and 7) Structural Job Characteristics (13 statements).
Other than minor grammatical editing (for example, changing ``the'' to ``you''), we retained the O}Net wording for our item stems. We used O\emph{Net's response scales, several of which were unique across items, but all shared the same 1 to 5 scale options. Subsequent to providing ratings of whether or not an O}Net characteristic was relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was also asked to rate that element in terms of, 1) . . . this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) . . . this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) . . . this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
\emph{Stress}. Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Obtained alpha was .85 in this sample.
\emph{Burnout}. Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Alpha was 0.85 in this sample.
\emph{Engagement}. The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample α's of 0.68 (Absorption) and 0.80 (Vigor), and 0.90 (Dedication). For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).

\emph{Procedure}

Data were collected through Prolific, a data collection platform. An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information. Eligibility requirements included being 18+ and holding either a full-time or part-time job. Participants then voluntarily chose to respond to the survey. The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes. Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified. Thus, if a respondent indicated that 5 of the characteristics were not part of their job, they were not subsequently asked to rate the level of resource, challenge, or hindrance a given item presented to them. For items that were a part of their jobs, they were then asked to report how much a characteristic was a resource, and then how much each characteristic was a hindrance, and finally, how much each item was a challenge. Participants were compensated for their participation in this study in the amount of six dollars through Prolific.

\emph{Results}

We used R (Version 4.0.3; R Core Team, 2020) and the R-packages careless (Version 1.1.3; Yentes \& Wilhelm, 2021), labourR (Version 1.0.0; Kouretsis et al., 2020), papaja (Version 0.1.0.9997; Aust \& Barth, 2020), and tinylabels (Barth, 2021) for all analyses. Our analyses are presented by characteristics of work that are rated in terms of being resources, challenge demands, and hindrance demands. Pearson correlation coefficients between characteristics classified as resources, challenges, and hindrances were obtained to investigate the associations among these characteristics.
Correlations, means and standard deviations among all study variables are presented in Table 1. Results reveal a positive association between resources and engagement (r = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively). Challenge demands were positively associated with engagement (r = .31; H2a), but were unrelated to stress or burnout (H2b and H2c). Total hindrance stressors were not significantly associated with our outcomes (H3a-H3c). To further explore H1-H3, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands. First, regarding engagement (F(3, 564) = 26.41, p \textless{} .001), the total resources (beta = ??) was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table 2). Next, stress was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 2.47, p = .060 (see Table 3). Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 1.10, p = .349. See Table 4.

Our fourth prediction suggested a positive association between total resources and total challenge demands. Here, we observed a strong positive relationship, so much so that it could be argued that these two variables are capturing the same thing (r = .86), as fully 74\% of the variability was shared.
In an exploratory fashion, we also considered whether or not the pattern of correlations described above was similar across job types.

There were 568 retained respondents.

\begin{verbatim}
##              resource hindrance  challenge     burnout      stress engagement
## resource   1.00000000 0.4671740 0.94633436  0.07026188  0.08895664  0.3659061
## hindrance  0.46717398 1.0000000 0.46316538  0.10217550  0.14181731  0.0501684
## challenge  0.94633436 0.4631654 1.00000000  0.07838108  0.10674017  0.3358327
## burnout    0.07026188 0.1021755 0.07838108  1.00000000  0.69654076 -0.3549613
## stress     0.08895664 0.1418173 0.10674017  0.69654076  1.00000000 -0.2953456
## engagement 0.36590613 0.0501684 0.33583266 -0.35496125 -0.29534556  1.0000000
\end{verbatim}

\begin{verbatim}
## 
## Call:
## lm(formula = engagement ~ hindrance + challenge + resource, data = data)
## 
## Residuals:
##      Min       1Q   Median       3Q      Max 
## -2.28900 -0.48821  0.05198  0.53450  2.07255 
## 
## Coefficients:
##               Estimate Std. Error t value Pr(>|t|)    
## (Intercept)  3.0408396  0.1222467  24.875  < 2e-16 ***
## hindrance   -0.0022616  0.0006512  -3.473 0.000554 ***
## challenge   -0.0009931  0.0017269  -0.575 0.565461    
## resource     0.0073264  0.0017566   4.171 3.52e-05 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.763 on 564 degrees of freedom
## Multiple R-squared:  0.153,  Adjusted R-squared:  0.1485 
## F-statistic: 33.97 on 3 and 564 DF,  p-value: < 2.2e-16
\end{verbatim}

\begin{verbatim}
## 
## Call:
## lm(formula = burnout ~ hindrance + challenge + resource, data = data)
## 
## Residuals:
##      Min       1Q   Median       3Q      Max 
## -2.33223 -0.67843 -0.03482  0.63254  2.10197 
## 
## Coefficients:
##               Estimate Std. Error t value Pr(>|t|)    
## (Intercept)  2.7638017  0.1382398  19.993   <2e-16 ***
## hindrance    0.0013360  0.0007364   1.814   0.0702 .  
## challenge    0.0014508  0.0019529   0.743   0.4579    
## resource    -0.0009349  0.0019865  -0.471   0.6381    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.8628 on 564 degrees of freedom
## Multiple R-squared:  0.01206,    Adjusted R-squared:  0.006801 
## F-statistic: 2.294 on 3 and 564 DF,  p-value: 0.07694
\end{verbatim}

\begin{verbatim}
## 
## Call:
## lm(formula = stress ~ hindrance + challenge + resource, data = data)
## 
## Residuals:
##     Min      1Q  Median      3Q     Max 
## -1.8922 -0.7552 -0.1147  0.6988  2.6438 
## 
## Coefficients:
##               Estimate Std. Error t value Pr(>|t|)    
## (Intercept)  2.1772197  0.1541487  14.124  < 2e-16 ***
## hindrance    0.0021433  0.0008212   2.610  0.00929 ** 
## challenge    0.0032258  0.0021776   1.481  0.13907    
## resource    -0.0025593  0.0022151  -1.155  0.24842    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Residual standard error: 0.9621 on 564 degrees of freedom
## Multiple R-squared:  0.02457,    Adjusted R-squared:  0.01938 
## F-statistic: 4.735 on 3 and 564 DF,  p-value: 0.00285
\end{verbatim}

\end{document}

### 2022-09-23 SIOP2023/Counts/Submission_ResourceCount.Rmd
writing percents as .csv

--- 2022-09-16 SIOP2023/Counts/Submission_ResourceCount.Rmd
@@
 
-```{r matching}
+```{r matching, include=FALSE}
 
-## Trying to figure out which characteristics have agreement
+source("matching.R", local = knitr::knit_global())  ## adds 252 variables (count matches) to data object
 
-## 145 & 248 (attention checks)
-## maybe % match
+```
 
-data22$rh1  <- data22$item118 + data22$item203
-data22$rh2  <- data22$item119 + data22$item204
-data22$rh3  <- data22$item120 + data22$item205
-data22$rh4  <- data22$item121 + data22$item206
-data22$rh5  <- data22$item122 + data22$item207
-data22$rh6  <- data22$item123 + data22$item208
-data22$rh7  <- data22$item124 + data22$item209
-data22$rh8  <- data22$item125 + data22$item210
-data22$rh9  <- data22$item126 + data22$item211
-data22$rh10 <- data22$item127 + data22$item212
-data22$rh11  <- data22$item128 + data22$item213
-data22$rh12  <- data22$item129 + data22$item214
-data22$rh13  <- data22$item130 + data22$item215
-data22$rh14  <- data22$item131 + data22$item216
-data22$rh15  <- data22$item132 + data22$item217
-data22$rh16  <- data22$item133 + data22$item218
-data22$rh17  <- data22$item134 + data22$item219
-data22$rh18  <- data22$item135 + data22$item220
-data22$rh19  <- data22$item136 + data22$item221
-data22$rh20  <- data22$item137 + data22$item222
-data22$rh21  <- data22$item138 + data22$item223
-data22$rh22  <- data22$item139 + data22$item224
-data22$rh23  <- data22$item140 + data22$item225
-data22$rh24  <- data22$item141 + data22$item226
-data22$rh25  <- data22$item142 + data22$item227
-data22$rh26  <- data22$item143 + data22$item228
-data22$rh27  <- data22$item144 + data22$item229
+```{r rankings}
 
-data22$rh28  <- data22$item146 + data22$item230
-
-data22$rh29  <- data22$item147 + data22$item231
-data22$rh30  <- data22$item148 + data22$item232
-data22$rh31  <- data22$item149 + data22$item233
-data22$rh32  <- data22$item150 + data22$item234
-data22$rh33  <- data22$item151 + data22$item235
-data22$rh34  <- data22$item152 + data22$item236
-data22$rh35  <- data22$item153 + data22$item237
-data22$rh36  <- data22$item154 + data22$item238
-data22$rh37  <- data22$item155 + data22$item239
-data22$rh38  <- data22$item156 + data22$item240
-data22$rh39  <- data22$item157 + data22$item241
-data22$rh40  <- data22$item158 + data22$item242
-data22$rh41  <- data22$item159 + data22$item243
-data22$rh42  <- data22$item160 + data22$item244
-data22$rh43  <- data22$item161 + data22$item245
-data22$rh44  <- data22$item162 + data22$item246
-data22$rh45  <- data22$item163 + data22$item247
-
-data22$rh46  <- data22$item164 + data22$item249
-
-data22$rh47  <- data22$item165 + data22$item250
-data22$rh48  <- data22$item166 + data22$item251
-data22$rh49  <- data22$item167 + data22$item252
-data22$rh50  <- data22$item168 + data22$item253
-data22$rh51  <- data22$item169 + data22$item254
-data22$rh52  <- data22$item170 + data22$item255
-data22$rh53  <- data22$item171 + data22$item256
-data22$rh54  <- data22$item172 + data22$item257
-data22$rh55  <- data22$item173 + data22$item258
-data22$rh56  <- data22$item174 + data22$item259
-data22$rh57  <- data22$item175 + data22$item260
-data22$rh58  <- data22$item176 + data22$item261
-data22$rh59  <- data22$item177 + data22$item262
-data22$rh60  <- data22$item178 + data22$item263
-data22$rh61  <- data22$item179 + data22$item264
-data22$rh62  <- data22$item180 + data22$item265
-data22$rh63  <- data22$item181 + data22$item266
-data22$rh64  <- data22$item182 + data22$item267
-data22$rh65  <- data22$item183 + data22$item268
-data22$rh66  <- data22$item184 + data22$item269
-data22$rh67  <- data22$item185 + data22$item270
-data22$rh68  <- data22$item186 + data22$item271
-data22$rh69  <- data22$item187 + data22$item272
-data22$rh70  <- data22$item188 + data22$item273
-data22$rh71  <- data22$item189 + data22$item274
-data22$rh72  <- data22$item190 + data22$item275
-data22$rh73  <- data22$item191 + data22$item276
-data22$rh74  <- data22$item192 + data22$item277
-data22$rh75  <- data22$item193 + data22$item278
-data22$rh76  <- data22$item194 + data22$item279
-data22$rh77  <- data22$item195 + data22$item280
-data22$rh78  <- data22$item196 + data22$item281
-data22$rh79  <- data22$item197 + data22$item282
-data22$rh80  <- data22$item198 + data22$item283
-data22$rh81  <- data22$item199 + data22$item284
-data22$rh82  <- data22$item200 + data22$item285
-data22$rh83  <- data22$item201 + data22$item286
-data22$rh84  <- data22$item202 + data22$item287
-
-###### Resource-Challenge:
-
-data22$rc1  <- data22$item118 + data22$item288
-data22$rc2  <- data22$item119 + data22$item289
-data22$rc3  <- data22$item120 + data22$item290
-data22$rc4  <- data22$item121 + data22$item291
-data22$rc5  <- data22$item122 + data22$item292
-data22$rc6  <- data22$item123 + data22$item293
-data22$rc7  <- data22$item124 + data22$item294
-data22$rc8  <- data22$item125 + data22$item295
-data22$rc9  <- data22$item126 + data22$item296
-data22$rc10 <- data22$item127 + data22$item297
-data22$rc11  <- data22$item128 + data22$item298
-data22$rc12  <- data22$item129 + data22$item299
-data22$rc13  <- data22$item130 + data22$item300
-data22$rc14  <- data22$item131 + data22$item301
-data22$rc15  <- data22$item132 + data22$item302
-data22$rc16  <- data22$item133 + data22$item303
-data22$rc17  <- data22$item134 + data22$item304
-data22$rc18  <- data22$item135 + data22$item305
-data22$rc19  <- data22$item136 + data22$item306
-data22$rc20  <- data22$item137 + data22$item307
-
-data22$rc21  <- data22$item138 + data22$item309
-
-data22$rc22  <- data22$item139 + data22$item310
-data22$rc23  <- data22$item140 + data22$item311
-data22$rc24  <- data22$item141 + data22$item312
-data22$rc25  <- data22$item142 + data22$item313
-data22$rc26  <- data22$item143 + data22$item314
-data22$rc27  <- data22$item144 + data22$item315
-
-data22$rc28  <- data22$item146 + data22$item316
-
-data22$rc29  <- data22$item147 + data22$item317
-data22$rc30  <- data22$item148 + data22$item318
-data22$rc31  <- data22$item149 + data22$item319
-data22$rc32  <- data22$item150 + data22$item320
-data22$rc33  <- data22$item151 + data22$item321
-data22$rc34  <- data22$item152 + data22$item322
-data22$rc35  <- data22$item153 + data22$item323
-data22$rc36  <- data22$item154 + data22$item324
-data22$rc37  <- data22$item155 + data22$item325
-data22$rc38  <- data22$item156 + data22$item326
-data22$rc39  <- data22$item157 + data22$item327
-data22$rc40  <- data22$item158 + data22$item328
-data22$rc41  <- data22$item159 + data22$item329
-data22$rc42  <- data22$item160 + data22$item330
-data22$rc43  <- data22$item161 + data22$item331
-data22$rc44  <- data22$item162 + data22$item332
-data22$rc45  <- data22$item163 + data22$item333
-data22$rc46  <- data22$item164 + data22$item334
-data22$rc47  <- data22$item165 + data22$item335
-data22$rc48  <- data22$item166 + data22$item336
-data22$rc49  <- data22$item167 + data22$item337
-data22$rc50  <- data22$item168 + data22$item338
-data22$rc51  <- data22$item169 + data22$item339
-data22$rc52  <- data22$item170 + data22$item340
-data22$rc53  <- data22$item171 + data22$item341
-data22$rc54  <- data22$item172 + data22$item342
-data22$rc55  <- data22$item173 + data22$item343
-data22$rc56  <- data22$item174 + data22$item344
-data22$rc57  <- data22$item175 + data22$item345
-data22$rc58  <- data22$item176 + data22$item346
-data22$rc59  <- data22$item177 + data22$item347
-data22$rc60  <- data22$item178 + data22$item348
-data22$rc61  <- data22$item179 + data22$item349
-data22$rc62  <- data22$item180 + data22$item350
-data22$rc63  <- data22$item181 + data22$item351
-data22$rc64  <- data22$item182 + data22$item352
-data22$rc65  <- data22$item183 + data22$item353
-data22$rc66  <- data22$item184 + data22$item354
-data22$rc67  <- data22$item185 + data22$item355
-data22$rc68  <- data22$item186 + data22$item356
-data22$rc69  <- data22$item187 + data22$item357
-data22$rc70  <- data22$item188 + data22$item358
-data22$rc71  <- data22$item189 + data22$item359
-data22$rc72  <- data22$item190 + data22$item360
-data22$rc73  <- data22$item191 + data22$item361
-data22$rc74  <- data22$item192 + data22$item362
-data22$rc75  <- data22$item193 + data22$item363
-data22$rc76  <- data22$item194 + data22$item364
-data22$rc77  <- data22$item195 + data22$item365
-data22$rc78  <- data22$item196 + data22$item366
-data22$rc79  <- data22$item197 + data22$item367
-data22$rc80  <- data22$item198 + data22$item368
-data22$rc81  <- data22$item199 + data22$item369
-data22$rc82  <- data22$item200 + data22$item370
-data22$rc83  <- data22$item201 + data22$item371
-data22$rc84  <- data22$item202 + data22$item372
-
-####### Hindrance-Challenge
-
-data22$hc1  <- data22$item203 + data22$item288
-data22$hc2  <- data22$item204 + data22$item289
-data22$hc3  <- data22$item205 + data22$item290
-data22$hc4  <- data22$item206 + data22$item291
-data22$hc5  <- data22$item207 + data22$item292
-data22$hc6  <- data22$item208 + data22$item293
-data22$hc7  <- data22$item209 + data22$item294
-data22$hc8  <- data22$item210 + data22$item295
-data22$hc9  <- data22$item211 + data22$item296
-data22$hc10 <- data22$item212 + data22$item297
-data22$hc11  <- data22$item213 + data22$item298
-data22$hc12  <- data22$item214 + data22$item299
-data22$hc13  <- data22$item215 + data22$item300
-data22$hc14  <- data22$item216 + data22$item301
-data22$hc15  <- data22$item217 + data22$item302
-data22$hc16  <- data22$item218 + data22$item303
-data22$hc17  <- data22$item219 + data22$item304
-data22$hc18  <- data22$item220 + data22$item305
-data22$hc19  <- data22$item221 + data22$item306
-data22$hc20  <- data22$item222 + data22$item307
-
-data22$hc21  <- data22$item223 + data22$item309
-
-data22$hc22  <- data22$item224 + data22$item310
-data22$hc23  <- data22$item225 + data22$item311
-data22$hc24  <- data22$item226 + data22$item312
-data22$hc25  <- data22$item227 + data22$item313
-data22$hc26  <- data22$item228 + data22$item314
-data22$hc27  <- data22$item229 + data22$item315
-data22$hc28  <- data22$item230 + data22$item316
-data22$hc29  <- data22$item231 + data22$item317
-data22$hc30  <- data22$item232 + data22$item318
-data22$hc31  <- data22$item233 + data22$item319
-data22$hc32  <- data22$item234 + data22$item320
-data22$hc33  <- data22$item235 + data22$item321
-data22$hc34  <- data22$item236 + data22$item322
-data22$hc35  <- data22$item237 + data22$item323
-data22$hc36  <- data22$item238 + data22$item324
-data22$hc37  <- data22$item239 + data22$item325
-data22$hc38  <- data22$item240 + data22$item326
-data22$hc39  <- data22$item241 + data22$item327
-data22$hc40  <- data22$item242 + data22$item328
-data22$hc41  <- data22$item243 + data22$item329
-data22$hc42  <- data22$item244 + data22$item330
-data22$hc43  <- data22$item245 + data22$item331
-data22$hc44  <- data22$item246 + data22$item332
-data22$hc45  <- data22$item247 + data22$item333
-
-data22$hc46  <- data22$item249 + data22$item334
-
-data22$hc47  <- data22$item250 + data22$item335
-data22$hc48  <- data22$item251 + data22$item336
-data22$hc49  <- data22$item252 + data22$item337
-data22$hc50  <- data22$item253 + data22$item338
-data22$hc51  <- data22$item254 + data22$item339
-data22$hc52  <- data22$item255 + data22$item340
-data22$hc53  <- data22$item256 + data22$item341
-data22$hc54  <- data22$item257 + data22$item342
-data22$hc55  <- data22$item258 + data22$item343
-data22$hc56  <- data22$item259 + data22$item344
-data22$hc57  <- data22$item260 + data22$item345
-data22$hc58  <- data22$item261 + data22$item346
-data22$hc59  <- data22$item262 + data22$item347
-data22$hc60  <- data22$item263 + data22$item348
-data22$hc61  <- data22$item264 + data22$item349
-data22$hc62  <- data22$item265 + data22$item350
-data22$hc63  <- data22$item266 + data22$item351
-data22$hc64  <- data22$item267 + data22$item352
-data22$hc65  <- data22$item268 + data22$item353
-data22$hc66  <- data22$item269 + data22$item354
-data22$hc67  <- data22$item270 + data22$item355
-data22$hc68  <- data22$item271 + data22$item356
-data22$hc69  <- data22$item272 + data22$item357
-data22$hc70  <- data22$item273 + data22$item358
-data22$hc71  <- data22$item274 + data22$item359
-data22$hc72  <- data22$item275 + data22$item360
-data22$hc73  <- data22$item276 + data22$item361
-data22$hc74  <- data22$item277 + data22$item362
-data22$hc75  <- data22$item278 + data22$item363
-data22$hc76  <- data22$item279 + data22$item364
-data22$hc77  <- data22$item280 + data22$item365
-data22$hc78  <- data22$item281 + data22$item366
-data22$hc79  <- data22$item282 + data22$item367
-data22$hc80  <- data22$item283 + data22$item368
-data22$hc81  <- data22$item284 + data22$item369
-data22$hc82  <- data22$item285 + data22$item370
-data22$hc83  <- data22$item286 + data22$item371
-data22$hc84  <- data22$item287 + data22$item372
-
-isolated <- data22[,c(22:32, 42:50, 52:60, 62:65, 67:117,411:662)]  ## characteristic ratings scattered because we didn't ask for resource/demand ratings for characteristics such as "exposure to radiation" - 9/12/22
+write.csv(psych::describe(data[410:662]), "percents.csv")
 

### 2022-09-23 SIOP2023/Counts/matching.R

@@ -1,0 +1,1021 @@
+
+## Trying to figure out which characteristics have agreement
+
+## 145 & 248 (attention checks)
+## maybe % match
+
+
+data$rh1[data$item118 > 3 & data$item203 > 3 & data$item22 >  1] <- 1        ## characteristic also both
+data$rh1[data$item22 == 1] <- NA                                             ## Not a characteristic
+data$rh1[(data$item118 < 4 | data$item203 < 4) & data$item22 >  1] <- 0      ## characteristic but not both
+
+data$rh2[ data$item119 > 3 & data$item204 > 3 &  data$item23 >  1] <- 1        
+data$rh2[(data$item119 < 4 | data$item204 < 4) & data$item23 >  1] <- 0
+data$rh2[                                        data$item23 == 1] <- NA
+
+data$rh3[ data$item120 > 3 & data$item205 > 3 &  data$item24 >  1] <- 1        
+data$rh3[(data$item120 < 4 | data$item205 < 4) & data$item24 >  1] <- 0
+data$rh3[                                        data$item24 == 1] <- NA
+
+data$rh4[ data$item121 > 3 & data$item206 > 3 &  data$item25 >  1] <- 1        
+data$rh4[(data$item121 < 4 | data$item206 < 4) & data$item25 >  1] <- 0
+data$rh4[                                        data$item25 == 1] <- NA
+
+data$rh5[ data$item122 > 3 & data$item207 > 3 &  data$item26 >  1] <- 1        
+data$rh5[(data$item122 < 4 | data$item207 < 4) & data$item26 >  1] <- 0
+data$rh5[                                        data$item26 == 1] <- NA
+
+
+data$rh6[ data$item123 > 3 & data$item208 > 3 &  data$item27 >  1] <- 1        
+data$rh6[(data$item123 < 4 | data$item208 < 4) & data$item27 >  1] <- 0
+data$rh6[                                        data$item27 == 1] <- NA
+
+data$rh7[ data$item124 > 3 & data$item209 > 3 &  data$item28 >  1] <- 1        
+data$rh7[(data$item124 < 4 | data$item209 < 4) & data$item28 >  1] <- 0
+data$rh7[                                        data$item28 == 1] <- NA
+
+data$rh8[ data$item125 > 3 & data$item210 > 3 &  data$item29 >  1] <- 1        
+data$rh8[(data$item125 < 4 | data$item210 < 4) & data$item29 >  1] <- 0
[…]

### 2022-09-23 SIOP2023/Counts/Submission_ResourceCount.Rmd
using xelatex so .Rmd knits

@@
 ---
-title             : "Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?"
-shorttitle        : "BiFactor Engagement"
+title             : "The title"
+shorttitle        : "Title"
 
 author: 
-  - name          : "John Kulas"
+  - name          : "First Author"
     affiliation   : "1"
     corresponding : yes    # Define only one corresponding author
-    address       : "1 Normal Ave, Montclair, NJ 07043"
-    email         : "kulasj@montclair.edu"
-  - name          : "Renata Garcia Prieto Palacios Roji"
-    affiliation   : "1"
-  - name          : "Casey Osorio-Duffoo"
-    affiliation   : "2"
-  - name          : "Morgan Russell"
-    affiliation   : "1"
+    address       : "Postal address"
+    email         : "my@email.com"
+    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
+      - "Conceptualization"
+      - "Writing - Original Draft Preparation"
+      - "Writing - Review & Editing"
+  - name          : "Ernst-August Doelle"
+    affiliation   : "1,2"
+    role:
+      - "Writing - Review & Editing"
+      - "Supervision"
 
@@
   - id            : "1"
-    institution   : "Montclair State University"
+    institution   : "Wilhelm-Wundt-University"
   - id            : "2"
-    institution   : "Harver"
+    institution   : "Konstanz Business School"
 
@@
 abstract: |
-  The most commonly referenced definition of attitudinal engagement implicates sub-dimensions of vigor, dedication, and absorption.
-The tripartite model of attitudes specifies cognitive, behavioral, and affective components.
-The current study documents the development and initial validation of a new measure of engagement that intentionally crosses the substantive and attitudinal elements.
+  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
 
-keywords          : "Engagement, engagement"
+  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
+
+  One sentence clearly stating the **general problem** being addressed by  this particular study.
+
+  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
+
+  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
+
+  One or two sentences to put the results into a more **general context**.
+
+  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
+
+  <!-- https://tinyurl.com/ybremelq -->
+
+keywords          : "keywords"
 wordcount         : "X"
 
-bibliography      : ["r-references.bib"]
+bibliography      : "r-references.bib"
 
-floatsintext      : no #change to yes if we want all tables to be put in-line rather than pushed to end of paper
+floatsintext      : no
+linenumbers       : yes
+draft             : no
+mask              : no
+
 figurelist        : no
@@
 footnotelist      : no
-linenumbers       : no
-mask              : no
-draft             : no
 
-documentclass     : "apa6"
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            :
+  papaja::apa6_pdf:
+    latex_engine: xelatex
 ---
@@
 
-source("matching.R", local = knitr::knit_global())  ## adds 252 variables (count matches) to data object
+source("..\\JDRJournalSubmission\\SIOP2023\\Counts\\matching.R", local = knitr::knit_global())  ## adds 252 variables (count matches) to data object
 
@@
 
-write.csv(psych::describe(data[410:662]), "percents.csv")
+write.csv(psych::describe(data[411:662]), "..\\JDRJournalSubmission\\SIOP2023\\Counts\\percents.csv")   ## all together
+
+write.csv(psych::describe(data[411:494]), "..\\JDRJournalSubmission\\SIOP2023\\Counts\\resource_hind.csv")   ## 
+write.csv(psych::describe(data[495:578]), "..\\JDRJournalSubmission\\SIOP2023\\Counts\\resource_challenge.csv")
+write.csv(psych::describe(data[579:662]), "..\\JDRJournalSubmission\\SIOP2023\\Counts\\hind_challenge.csv")
 
@@
 
-```{r correlation_table, eval=FALSE}
+```{r correlation_table, eval=TRUE}
 
@@
 papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table,
+                  caption = "Focal variable correlations (counts data).",
                   escape = FALSE)

### 2022-09-23 SIOP2023/Counts/Submission_ResourceCount.tex
using xelatex so .Rmd knits

@@
 \usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={The title},
+  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 {}{\PatchFailed}
-\keywords{Engagement, engagement\newline\indent Word count: X}
+\keywords{keywords\newline\indent Word count: X}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 \makeatother
+\usepackage{lineno}
+
+\linenumbers
 \usepackage{csquotes}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?},
-  pdfauthor={John Kulas1, Renata Garcia Prieto Palacios Roji1, Casey Osorio-Duffoo2, \& Morgan Russell1},
-  pdflang={en-EN},
-  pdfkeywords={Engagement, engagement},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
 
-\title{Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?}
-\author{John Kulas\textsuperscript{1}, Renata Garcia Prieto Palacios Roji\textsuperscript{1}, Casey Osorio-Duffoo\textsuperscript{2}, \& Morgan Russell\textsuperscript{1}}
+\title{The title}
+\author{First Author\textsuperscript{1} \& Ernst-August Doelle\textsuperscript{1,2}}
 \date{}
 
-\shorttitle{BiFactor Engagement}
+\shorttitle{Title}
 
@@
 
-Correspondence concerning this article should be addressed to John Kulas, 1 Normal Ave, Montclair, NJ 07043. E-mail: \href{mailto:kulasj@montclair.edu}{\nolinkurl{kulasj@montclair.edu}}
+The authors made the following contributions.
+First Author: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Ernst-August Doelle: Writing - Review \& Editing, Supervision.
+
+Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Montclair State University\\\textsuperscript{2} Harver}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}
 
 \abstract{%
-The most commonly referenced definition of attitudinal engagement implicates sub-dimensions of vigor, dedication, and absorption.
-The tripartite model of attitudes specifies cognitive, behavioral, and affective components.
-The current study documents the development and initial validation of a new measure of engagement that intentionally crosses the substantive and attitudinal elements.
+One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
+
+Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
+
+One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
+
+One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
+
+Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
+
+One or two sentences to put the results into a more \textbf{general context}.
+
+Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
 }
@@
 
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:correlation_table}Focal variable correlations (counts data).}
+
+\begin{tabular}{llllllll}
+\toprule
+ & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
+\midrule
+1. resource & - &  &  &  &  & 203.85 & 56.73\\
+2. hindrance & .47*** & - &  &  &  & 129.50 & 55.80\\
+3. challenge & .95*** & .46*** & - &  &  & 203.12 & 57.57\\
+4. burnout & .07 & .10* & .08 & - &  & 3.04 & 0.87\\
+5. stress & .09* & .14*** & .11* & .70*** & - & 2.59 & 0.97\\
+6. engagement & .37*** & .05 & .34*** & -.35*** & -.30*** & 4.04 & 0.83\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
 \begin{verbatim}

### 2022-09-23 SIOP2023/Counts/Submission_ResourceCount.Rmd
added histogram that is a percent match for characterstics that were part of one's job.

@@
 Here, we observed a strong positive relationship, so much so that it could be argued that these two variables are capturing the same thing (r = .86), as fully 74% of the variability was shared.
+  To illustrate this relationship further, we computed a percentage of matches within person for the subset of job characteristics respondents agreed were a part of their jobs (excluding those characteristics rated as not part of one's job).
+Figure ??
+shows the distribution of the proportion of matches by person.
+
   In an exploratory fashion, we also considered whether or not the pattern of correlations described above was similar across job types.
@@
 ```
+```{r match percents by person}
+#rc1 to rc 84
+
+data$match_rc_by_person <- rowSums(data[495:578], na.rm = TRUE)
+
+data$match_rc_by_person_NAs <- rowSums(is.na(data[495:578]))
+
+#This should be matches divided by 84 items minus nas
+data$percent_match_total_person <- (data$match_rc_by_person/(84 - data$match_rc_by_person_NAs))
+head(data$percent_match_total_person)
+
+hist(data$percent_match_total_person)
+```

### 2022-09-23 SIOP2023/Counts/Submission_ResourceCount.Rmd
Draft discussion added

@@
 Here, we observed a strong positive relationship, so much so that it could be argued that these two variables are capturing the same thing (r = .86), as fully 74% of the variability was shared.
+
   To illustrate this relationship further, we computed a percentage of matches within person for the subset of job characteristics respondents agreed were a part of their jobs (excluding those characteristics rated as not part of one's job).
@@
 ```
+
+*Discussion*
+
+The major goal of this paper was to further explore the relationships among total perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout.
+Additionally, we considered whether resources and challenge demands were perceived as distinct, and finally, whether the patterns were similar across job categories/types of work.
+The results suggest a positive relationship between both resources and engagement (H1a), and challenge demands and engagement (H2a).
+Employers would benefit from understanding that at leas the perception of having “more” resources and more challenge demands in a job is highly associated with reported engagement.
+While not a causal relationship, it points to the potential value of these kinds of employee support nonetheless.
+The other relationships with outcomes of stress and burnout were not supported, suggesting that the sheer number of resources, challenges, and hindrances are not significantly related to these negative outcomes.
+It is possible that rather than volume, categorically some demands are more related to these outcomes than others.
+ Further, total resources were highly associated challenge demands (supporting H4).
+We could even argue, given the magnitude of the correlation, that they are capturing the same thing (74% overlap with a correlation of .86).
+Need to also talk about our exploratory findings regarding patterns across job type
+Limitations and Future Directions
+As with any piece of research, the process and results have limitations, but also provide a variety of additional directions to pursue in the future.
+First, while a strength of this project, arguably, is the use of O*Net items, practical considerations limited the number of job characteristics we could include in our survey.
+Future study could consider additional or other O*Net items.
+We conceptualized resources and demands in terms of perceived total amounts.
+It may be the case that certain kinds of resources or challenges are more strongly associated with engagement than others, and such, future research could explore the importance of resources/challenges categorically.
+Further, our study was limited to three outcomes of interest.
+It would be especially interesting to explore additional outcomes (e.g., job satisfaction) as well, or whether volume of resources and demands operationalized in this way are related to other behaviors (e.g., turnover intention, perceived organizational support, commitment).

### 2022-09-23 SIOP2023/Counts/Submission_ResourceCount.Rmd
forgot to push from Caribou

@@
 
-*Method*
+# Method
 
@@
 
-*Participants*
+## Participants
 
@@
 
-*Procedure*
+## Procedure
 
@@
 
-*Results*
+# Results
 
@@
 Here, we observed a strong positive relationship, so much so that it could be argued that these two variables are capturing the same thing (r = .86), as fully 74% of the variability was shared.
-
-  To illustrate this relationship further, we computed a percentage of matches within person for the subset of job characteristics respondents agreed were a part of their jobs (excluding those characteristics rated as not part of one's job).
-Figure ??
-shows the distribution of the proportion of matches by person.
 
@@
 ```
-```{r match percents by person}
+
+## Alicia graphs
+
+```{r matchpercentsbyperson}
 #rc1 to rc 84
@@
 
-*Discussion*
+  To illustrate this relationship further, we computed a percentage of matches within person for the subset of job characteristics respondents agreed were a part of their jobs (excluding those characteristics rated as not part of one's job).
+Figure \@ref(fig:matchpercentsbyperson) shows the distribution of the proportion of matches by person.
+
+## Kulas graphs
+
+```{r percagree, fig.cap="Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance."}
+
+rc <- read.csv("resource_challenge.csv")
+rh <- read.csv("resource_hind.csv")
+ch <- read.csv("hind_challenge.csv")
+
+rc$type <- "Resource-Challenge"
+rh$type <- "Resource-Hindrance"
+ch$type <- "Challenge-Hindrance"
+
+forgraph <- rbind(rc,rh,ch)
+
+library(ggplot2)
+
+#ggplot(forgraph, aes(x = mean, fill = type)) +
+#  geom_density(alpha = .3) +
+#  xlab("Percent Agreement") + labs(fill = "Att/Engage\nInteraction")
+
+p <- ggplot(forgraph, aes(x = mean)) + geom_histogram()
+p + facet_wrap(~type, nrow=3)
+
+## lotsa variance in resource-challenge agreement. Next look for either content (O*Net category) or contextual (job) moderator
+
+```
+
+Figure \@ref(fig:percagree) shows that there was not much mutual agreement regarding characteristics viewed as both hindrances and resources or as challenges and hindrances.
+Alternatively, whether a characteristic was viewed as both a resource and a challenge had quite a bit of variability.
+
+```{r recchall, fig.cap="Resource and challenge agreement across ONet characteristic groupings (e.g., scales)."}
+
+rc$scale <- c(rep("Structural",10), rep("Physical", 20), rep("Interpersonal",13), rep("Information Input", 5), rep("Mental Processes", 10), rep("Work Output", 9), rep("Interact with Others", 17))
+
+ggplot(rc, aes(x=mean)) + geom_histogram() + facet_wrap(~scale, nrow=7)
+
+#ggplot(rc, aes(x = mean, fill = scale)) +
+#  geom_density(alpha = .3) +
+#  xlab("Percent Agreement") + labs(fill = "ONET grouping")
+
+```
+
+Figure \@ref(fig:recchall) explores the possibility of moderation by *type of characteristic rated* for the resource-challenge convergence.
+We categorized each characteristic by its ONet "scale" (one of seven), and the graph shows consistency across certain characteristics (for example, ) and non-convergence across other *types* of characteristics (for example, "Physical" characteristics).
+
+>Note. If we keep this, we should also look at type of job as a moderator (swap it in for/instead of ONet scale).
+
+# Discussion
 

### 2022-09-23 SIOP2023/Counts/Submission_ResourceCount.tex
forgot to push from Caribou

@@
 
-\emph{Method}
+\hypertarget{method}{%
+\section{Method}\label{method}}
 
@@
 
-\emph{Participants}
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
 
@@
 
-\emph{Procedure}
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
 
@@
 
-\emph{Results}
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
@@
 Here, we observed a strong positive relationship, so much so that it could be argued that these two variables are capturing the same thing (r = .86), as fully 74\% of the variability was shared.
+
 In an exploratory fashion, we also considered whether or not the pattern of correlations described above was similar across job types.
@@
 
+\hypertarget{alicia-graphs}{%
+\subsection{Alicia graphs}\label{alicia-graphs}}
+
+\begin{verbatim}
+## [1] 0.1830986 0.6231884 0.4528302 0.2068966 0.6415094 0.6666667
+\end{verbatim}
+
+\includegraphics{Submission_ResourceCount_files/figure-latex/matchpercentsbyperson-1.pdf}
+
+To illustrate this relationship further, we computed a percentage of matches within person for the subset of job characteristics respondents agreed were a part of their jobs (excluding those characteristics rated as not part of one's job).
+Figure \ref{fig:matchpercentsbyperson} shows the distribution of the proportion of matches by person.
+
+\hypertarget{kulas-graphs}{%
+\subsection{Kulas graphs}\label{kulas-graphs}}
+
+\begin{figure}
+\centering
+\includegraphics{Submission_ResourceCount_files/figure-latex/percagree-1.pdf}
+\caption{\label{fig:percagree}Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance.}
+\end{figure}
+
+Figure \ref{fig:percagree} shows that there was not much mutual agreement regarding characteristics viewed as both hindrances and resources or as challenges and hindrances.
+Alternatively, whether a characteristic was viewed as both a resource and a challenge had quite a bit of variability.
+
+\begin{figure}
+\centering
+\includegraphics{Submission_ResourceCount_files/figure-latex/recchall-1.pdf}
+\caption{\label{fig:recchall}Resource and challenge agreement across ONet characteristic groupings (e.g., scales).}
+\end{figure}
+
+Figure \ref{fig:recchall} explores the possibility of moderation by \emph{type of characteristic rated} for the resource-challenge convergence.
+We categorized each characteristic by its ONet ``scale'' (one of seven), and the graph shows consistency across certain characteristics (for example, ) and non-convergence across other \emph{types} of characteristics (for example, ``Physical'' characteristics).
+
+\begin{quote}
+Note. If we keep this, we should also look at type of job as a moderator (swap it in for/instead of ONet scale).
+\end{quote}
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+The major goal of this paper was to further explore the relationships among total perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout.
+Additionally, we considered whether resources and challenge demands were perceived as distinct, and finally, whether the patterns were similar across job categories/types of work.
+The results suggest a positive relationship between both resources and engagement (H1a), and challenge demands and engagement (H2a).
+Employers would benefit from understanding that at leas the perception of having ``more'' resources and more challenge demands in a job is highly associated with reported engagement.
+While not a causal relationship, it points to the potential value of these kinds of employee support nonetheless.
+The other relationships with outcomes of stress and burnout were not supported, suggesting that the sheer number of resources, challenges, and hindrances are not significantly related to these negative outcomes.
+It is possible that rather than volume, categorically some demands are more related to these outcomes than others.
+Further, total resources were highly associated challenge demands (supporting H4).
+We could even argue, given the magnitude of the correlation, that they are capturing the same thing (74\% overlap with a correlation of .86).
+Need to also talk about our exploratory findings regarding patterns across job type
+Limitations and Future Directions
+As with any piece of research, the process and results have limitations, but also provide a variety of additional directions to pursue in the future.
+First, while a strength of this project, arguably, is the use of O\emph{Net items, practical considerations limited the number of job characteristics we could include in our survey.
+Future study could consider additional or other O}Net items.
+We conceptualized resources and demands in terms of perceived total amounts.
+It may be the case that certain kinds of resources or challenges are more strongly associated with engagement than others, and such, future research could explore the importance of resources/challenges categorically.
+Further, our study was limited to three outcomes of interest.
+It would be especially interesting to explore additional outcomes (e.g., job satisfaction) as well, or whether volume of resources and demands operationalized in this way are related to other behaviors (e.g., turnover intention, perceived organizational support, commitment).
+
 \end{document}

### 2022-09-23 SIOP2023/Counts/graphing.R

@@ -1,0 +1,30 @@
+## need to run "Submission_ResourceCount.Rmd" chunks to load objects in environment prior to running the below (9/23/22)
+
+rc <- read.csv("resource_challenge.csv")
+rh <- read.csv("resource_hind.csv")
+ch <- read.csv("hind_challenge.csv")
+
+rc$type <- "Resource-Challenge"
+rh$type <- "Resource-Hindrance"
+ch$type <- "Challenge-Hindrance"
+
+forgraph <- rbind(rc,rh,ch)
+
+library(ggplot2)
+
+#ggplot(forgraph, aes(x = mean, fill = type)) +
+#  geom_density(alpha = .3) +
+#  xlab("Percent Agreement") + labs(fill = "Att/Engage\nInteraction") 
+
+p <- ggplot(forgraph, aes(x = mean)) + geom_histogram()
+p + facet_wrap(~type, nrow=3)
+
+## lotsa variance in resource-challenge agreement. Next look for either content (O*Net category) or contextual (job) moderator
+
+rc$scale <- c(rep("Structural",10), rep("Physical", 20), rep("Interpersonal",13), rep("Information Input", 5), rep("Mental Processes", 10), rep("Work Output", 9), rep("Interact with Others", 17)) 
+
+# ggplot(rc, aes(x=mean)) + geom_histogram() + facet_wrap(~scale, nrow=7)
+
+ggplot(rc, aes(x = mean, fill = scale)) +
+  geom_density(alpha = .3) +
+  xlab("Percent Agreement") + labs(fill = "ONET grouping") 

### 2022-09-24 SIOP2023/Counts/Submission_ResourceCount.Rmd
figure heights - correlation between resource and challenge now .95 (what happened)?

@@
 
-```{r percagree, fig.cap="Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance."}
+```{r percagree, fig.cap="Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance.", fig.height=10}
 
@@
 
-```{r recchall, fig.cap="Resource and challenge agreement across ONet characteristic groupings (e.g., scales)."}
+```{r recchall, fig.cap="Resource and challenge agreement across ONet characteristic groupings (e.g., scales).", fig.height=10}
 

### 2022-09-24 SIOP2023/Counts/Submission_ResourceCount.Rmd
fixed correlations (little wonky but needed to recreate `data22` object and also pull scale scores from `data22` into `data`)

@@
 
-# data22 <- data %>% 
-# mutate_at(vars(118:372),
-# function(x) recode(x,
-# 1==NA, 
-# 2==NA,
-# 3==NA,
-# 4==4,
-# 5==5))
+ data22 <- data %>% 
+ mutate_at(vars(118:372),
+ function(x) recode(x,
+ 1==NA, 
+ 2==NA,
+ 3==NA,
+ 4==4,
+ 5==5))
 
@@
 
-data$resource <- rowSums(data[c(118:144,146:202)], na.rm=TRUE)
-data$hindrance <- rowSums(data[c(203:247,249:287)], na.rm=TRUE)
-data$challenge <- rowSums(data[c(288:307,309:372)], na.rm=TRUE)
+data22$resource <- rowSums(data22[c(118:144,146:202)], na.rm=TRUE)
+data22$hindrance <- rowSums(data22[c(203:247,249:287)], na.rm=TRUE)
+data22$challenge <- rowSums(data22[c(288:307,309:372)], na.rm=TRUE)
 
-data$item387 <- 7-data$item387
-data$burnout      <- rowMeans(data[c(373:376)], na.rm=TRUE)
-data$stress       <- rowMeans(data[c(377:379)], na.rm=TRUE)
-data$engagement   <- rowMeans(data[c(380:399)], na.rm=TRUE)        ## probably need to recode some
+data22$item387 <- 7-data22$item387
+data22$burnout      <- rowMeans(data22[c(373:376)], na.rm=TRUE)
+data22$stress       <- rowMeans(data22[c(377:379)], na.rm=TRUE)
+data22$engagement   <- rowMeans(data22[c(380:399)], na.rm=TRUE)        ## probably need to recode some
 
-cor(data[405:410], use="all.obs")   ## something to be told with resources and challenges
+cor(data22[405:410], use="all.obs")   ## something to be told with resources and challenges
+
+## Peculiar, but repeating for normal datafile so column identifiers line-up
+
+data$resource <- rowSums(data22[c(118:144,146:202)], na.rm=TRUE)
+data$hindrance <- rowSums(data22[c(203:247,249:287)], na.rm=TRUE)
+data$challenge <- rowSums(data22[c(288:307,309:372)], na.rm=TRUE)
+
+data$burnout      <- rowMeans(data22[c(373:376)], na.rm=TRUE)
+data$stress       <- rowMeans(data22[c(377:379)], na.rm=TRUE)
+data$engagement   <- rowMeans(data22[c(380:399)], na.rm=TRUE)        ## probably need to recode some
 
@@
 
-r <- corx::corx(data[,c(405:410)],                    
+r <- corx::corx(data22[,c(405:410)],                    
                 triangle = "lower",
@@
 
-eng <- lm(engagement ~ hindrance + challenge + resource, data)
-bur <- lm(burnout ~ hindrance + challenge + resource, data)
-str <- lm(stress ~ hindrance + challenge + resource, data)
+eng <- lm(engagement ~ hindrance + challenge + resource, data22)
+bur <- lm(burnout ~ hindrance + challenge + resource, data22)
+str <- lm(stress ~ hindrance + challenge + resource, data22)
 

### 2022-09-24 SIOP2023/Counts/Submission_ResourceCount.tex
figure heights - correlation between resource and challenge now .95 (what happened)?
fixed correlations (little wonky but needed to recreate `data22` object and also pull scale scores from `data22` into `data`)

@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={The title},
-  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={The title},
+  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 \begin{verbatim}
-##              resource hindrance  challenge     burnout      stress engagement
-## resource   1.00000000 0.4671740 0.94633436  0.07026188  0.08895664  0.3659061
-## hindrance  0.46717398 1.0000000 0.46316538  0.10217550  0.14181731  0.0501684
-## challenge  0.94633436 0.4631654 1.00000000  0.07838108  0.10674017  0.3358327
-## burnout    0.07026188 0.1021755 0.07838108  1.00000000  0.69654076 -0.3549613
-## stress     0.08895664 0.1418173 0.10674017  0.69654076  1.00000000 -0.2953456
-## engagement 0.36590613 0.0501684 0.33583266 -0.35496125 -0.29534556  1.0000000
+##              resource   hindrance  challenge     burnout      stress
+## resource   1.00000000 0.225550803 0.86225195  0.04841544  0.05583466
+## hindrance  0.22555080 1.000000000 0.22047517  0.04101639  0.08980526
+## challenge  0.86225195 0.220475168 1.00000000  0.06790884  0.08057171
+## burnout    0.04841544 0.041016388 0.06790884  1.00000000  0.69654076
+## stress     0.05583466 0.089805265 0.08057171  0.69654076  1.00000000
+## engagement 0.34225837 0.009629535 0.31087164 -0.35496125 -0.29534556
+##              engagement
+## resource    0.342258369
+## hindrance   0.009629535
+## challenge   0.310871641
+## burnout    -0.354961254
+## stress     -0.295345559
+## engagement  1.000000000
 \end{verbatim}
@@
 \midrule
-1. resource & - &  &  &  &  & 203.85 & 56.73\\
-2. hindrance & .47*** & - &  &  &  & 129.50 & 55.80\\
-3. challenge & .95*** & .46*** & - &  &  & 203.12 & 57.57\\
-4. burnout & .07 & .10* & .08 & - &  & 3.04 & 0.87\\
-5. stress & .09* & .14*** & .11* & .70*** & - & 2.59 & 0.97\\
-6. engagement & .37*** & .05 & .34*** & -.35*** & -.30*** & 4.04 & 0.83\\
+1. resource & - &  &  &  &  & 36.02 & 13.26\\
+2. hindrance & .23*** & - &  &  &  & 13.09 & 13.62\\
+3. challenge & .86*** & .22*** & - &  &  & 35.64 & 13.63\\
+4. burnout & .05 & .04 & .07 & - &  & 3.04 & 0.87\\
+5. stress & .06 & .09* & .08 & .70*** & - & 2.59 & 0.97\\
+6. engagement & .34*** & .01 & .31*** & -.35*** & -.30*** & 4.04 & 0.83\\
 \bottomrule
@@
 ## Call:
-## lm(formula = engagement ~ hindrance + challenge + resource, data = data)
+## lm(formula = engagement ~ hindrance + challenge + resource, data = data22)
 ## 
@@
 ##      Min       1Q   Median       3Q      Max 
-## -2.28900 -0.48821  0.05198  0.53450  2.07255 
+## -2.40431 -0.50713  0.02842  0.55010  2.05201 
 ## 
@@
 ##              Estimate Std. Error t value Pr(>|t|)    
-## (Intercept)  3.0408396  0.1222467  24.875  < 2e-16 ***
-## hindrance   -0.0022616  0.0006512  -3.473 0.000554 ***
-## challenge   -0.0009931  0.0017269  -0.575 0.565461    
-## resource     0.0073264  0.0017566   4.171 3.52e-05 ***
+## (Intercept)  3.276423   0.096574  33.926  < 2e-16 ***
+## hindrance   -0.004436   0.002460  -1.803 0.071918 .  
+## challenge    0.004175   0.004728   0.883 0.377613    
+## resource     0.018672   0.004868   3.836 0.000139 ***
 ## ---
@@
 ## 
-## Residual standard error: 0.763 on 564 degrees of freedom
-## Multiple R-squared:  0.153,  Adjusted R-squared:  0.1485 
-## F-statistic: 33.97 on 3 and 564 DF,  p-value: < 2.2e-16
+## Residual standard error: 0.7763 on 564 degrees of freedom
+## Multiple R-squared:  0.1232, Adjusted R-squared:  0.1185 
+## F-statistic: 26.41 on 3 and 564 DF,  p-value: 5.394e-16
 \end{verbatim}
@@
 ## Call:
-## lm(formula = burnout ~ hindrance + challenge + resource, data = data)
+## lm(formula = burnout ~ hindrance + challenge + resource, data = data22)
 ## 
@@
 ##      Min       1Q   Median       3Q      Max 
-## -2.33223 -0.67843 -0.03482  0.63254  2.10197 
+## -2.23967 -0.64759 -0.04747  0.65173  2.10310 
 ## 
@@
 ##              Estimate Std. Error t value Pr(>|t|)    
-## (Intercept)  2.7638017  0.1382398  19.993   <2e-16 ***
-## hindrance    0.0013360  0.0007364   1.814   0.0702 .  
-## challenge    0.0014508  0.0019529   0.743   0.4579    
-## resource    -0.0009349  0.0019865  -0.471   0.6381    
+## (Intercept)  2.895053   0.107671  26.888   <2e-16 ***
+## hindrance    0.001843   0.002743   0.672    0.502    
+## challenge    0.006290   0.005271   1.193    0.233    
+## resource    -0.002843   0.005427  -0.524    0.601    
 ## ---
@@
 ## 
-## Residual standard error: 0.8628 on 564 degrees of freedom
-## Multiple R-squared:  0.01206,    Adjusted R-squared:  0.006801 
-## F-statistic: 2.294 on 3 and 564 DF,  p-value: 0.07694
+## Residual standard error: 0.8655 on 564 degrees of freedom
+## Multiple R-squared:  0.005808,   Adjusted R-squared:  0.0005199 
+## F-statistic: 1.098 on 3 and 564 DF,  p-value: 0.3493
 \end{verbatim}
@@
 ## Call:
-## lm(formula = stress ~ hindrance + challenge + resource, data = data)
+## lm(formula = stress ~ hindrance + challenge + resource, data = data22)
 ## 
@@
 ##     Min      1Q  Median      3Q     Max 
-## -1.8922 -0.7552 -0.1147  0.6988  2.6438 
+## -1.8841 -0.8038 -0.1523  0.7164  2.5693 
 ## 
@@
 ##              Estimate Std. Error t value Pr(>|t|)    
-## (Intercept)  2.1772197  0.1541487  14.124  < 2e-16 ***
-## hindrance    0.0021433  0.0008212   2.610  0.00929 ** 
-## challenge    0.0032258  0.0021776   1.481  0.13907    
-## resource    -0.0025593  0.0022151  -1.155  0.24842    
+## (Intercept)  2.383299   0.120392  19.796   <2e-16 ***
+## hindrance    0.005571   0.003067   1.816   0.0698 .  
+## challenge    0.008445   0.005894   1.433   0.1525    
+## resource    -0.004687   0.006068  -0.772   0.4402    
 ## ---
@@
 ## 
-## Residual standard error: 0.9621 on 564 degrees of freedom
-## Multiple R-squared:  0.02457,    Adjusted R-squared:  0.01938 
-## F-statistic: 4.735 on 3 and 564 DF,  p-value: 0.00285
+## Residual standard error: 0.9678 on 564 degrees of freedom
+## Multiple R-squared:  0.01299,    Adjusted R-squared:  0.007741 
+## F-statistic: 2.474 on 3 and 564 DF,  p-value: 0.06069
 \end{verbatim}

### 2022-09-24 SIOP2023/Counts/Submission_ResourceCount.Rmd
Alicia graph auto-number generate (added fig.cap)

@@
 
-```{r matchpercentsbyperson}
+```{r matchpercentsbyperson, fig.cap="Distribution of the proportion of matches by person."}
 #rc1 to rc 84
@@
 data$percent_match_total_person <- (data$match_rc_by_person/(84 - data$match_rc_by_person_NAs))
-head(data$percent_match_total_person)
+# head(data$percent_match_total_person)
 

### 2022-09-26 SIOP2023/Counts/Submission_ResourceCount.Rmd
ANOVA on summary data at Dunn Brothers

@@
 ---
-title             : "The title"
-shorttitle        : "Title"
+title             : "O*Net Category Demands and Resources: Integrative Characteristics"
+shorttitle        : "O*Net JDR"
 
 author: 
-  - name          : "First Author"
+  - name          : "John Kulas"
     affiliation   : "1"
     corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
-    email         : "my@email.com"
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-      - "Conceptualization"
-      - "Writing - Original Draft Preparation"
-      - "Writing - Review & Editing"
-  - name          : "Ernst-August Doelle"
-    affiliation   : "1,2"
-    role:
-      - "Writing - Review & Editing"
-      - "Supervision"
+    email         : "jtkulas@ergreports.com"
+  - name          : "Alicia Stachowski"
+    affiliation   : "2"
+  - name          : "Renata Garcia Prieto Palacios Roji"
+    affiliation   : "3"
 
@@
   - id            : "1"
-    institution   : "Wilhelm-Wundt-University"
+    institution   : "eRg"
   - id            : "2"
-    institution   : "Konstanz Business School"
+    institution   : "University of Wisconsin - Stout"
+  - id            : "3"
+    institution   : "PepsiCo"
 
@@
 
+```{r anova}
+
+## probably need to do with actual data (not summaries)
+
+oneway <- aov(mean ~ scale, rc)
+
+```
+
 >Note. If we keep this, we should also look at type of job as a moderator (swap it in for/instead of ONet scale).
+
+F ratio from psych describe object is $F_(6, 76)$ = `r summary(oneway)[[1]][1,4]`, *p* = `r summary(oneway)[[1]][1,5]`, although these should ideally be estimated from larger datafile instead of summary object.
 

### 2022-09-26 SIOP2023/Counts/Submission_ResourceCount.tex
Alicia graph auto-number generate (added fig.cap)
ANOVA on summary data at Dunn Brothers

@@
 \usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={O*Net Category Demands and Resources: Integrative Characteristics},
+  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata Garcia Prieto Palacios Roji3},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={The title},
-  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
 
-\title{The title}
-\author{First Author\textsuperscript{1} \& Ernst-August Doelle\textsuperscript{1,2}}
+\title{O*Net Category Demands and Resources: Integrative Characteristics}
+\author{John Kulas\textsuperscript{1}, Alicia Stachowski\textsuperscript{2}, \& Renata Garcia Prieto Palacios Roji\textsuperscript{3}}
 \date{}
 
-\shorttitle{Title}
+\shorttitle{O*Net JDR}
 
@@
 
-The authors made the following contributions.
-First Author: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Ernst-August Doelle: Writing - Review \& Editing, Supervision.
-
-Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
+Correspondence concerning this article should be addressed to John Kulas. E-mail: \href{mailto:jtkulas@ergreports.com}{\nolinkurl{jtkulas@ergreports.com}}
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} eRg\\\textsuperscript{2} University of Wisconsin - Stout\\\textsuperscript{3} PepsiCo}
 
@@
 
-\begin{verbatim}
-## [1] 0.1830986 0.6231884 0.4528302 0.2068966 0.6415094 0.6666667
-\end{verbatim}
-
+\begin{figure}
+\centering
 \includegraphics{Submission_ResourceCount_files/figure-latex/matchpercentsbyperson-1.pdf}
+\caption{\label{fig:matchpercentsbyperson}Distribution of the proportion of matches by person.}
+\end{figure}
 
@@
 
+F ratio from psych describe object is \(F_(6, 76)\) = 26.05, \emph{p} = 0.00, although these should ideally be estimated from larger datafile instead of summary object.
+
 \hypertarget{discussion}{%

### 2022-09-30 SIOP2023/Counts/Submission_ResourceCount.Rmd
ANOVA added

@@
 
-## probably need to do with actual data (not summaries)
+## Repeated measures ANOVA for resource_challenge
 
-oneway <- aov(mean ~ scale, rc)
+anova <- data[,c(495:578)]
+
+anova$Structural <- rowSums(anova[1:10], na.rm=TRUE)
+anova$Physical <- rowSums(anova[11:30], na.rm=TRUE)
+anova$Interpersonal <- rowSums(anova[31:43], na.rm=TRUE)
+anova$Information <- rowSums(anova[44:48], na.rm=TRUE)
+anova$Mental <- rowSums(anova[49:58], na.rm=TRUE)
+anova$Output <- rowSums(anova[59:67], na.rm=TRUE)
+anova$Interact <- rowSums(anova[68:84], na.rm=TRUE)
+
+library(tidyr)
+
+anova <- cbind(person = 1:nrow(anova), anova)  ## creating person identifier for ANOVA
+
+analysis <- gather(anova, scale, value, Structural:Interact)
+
+repmeas <- aov(value ~ factor(scale) + Error(factor(person)), data=analysis)
 
@@
 
-F ratio from psych describe object is $F_(6, 76)$ = `r summary(oneway)[[1]][1,4]`, *p* = `r summary(oneway)[[1]][1,5]`, although these should ideally be estimated from larger datafile instead of summary object.
+F ratio from a repeated measures ANOVA is $F_(6, 3,402)$ = 613.5, *p* < .001 (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001.
 

### 2022-09-30 SIOP2023/Counts/Submission_ResourceCount.tex
ANOVA added

@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={O*Net Category Demands and Resources: Integrative Characteristics},
-  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata Garcia Prieto Palacios Roji3},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={O*Net Category Demands and Resources: Integrative Characteristics},
+  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata Garcia Prieto Palacios Roji3},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 
-F ratio from psych describe object is \(F_(6, 76)\) = 26.05, \emph{p} = 0.00, although these should ideally be estimated from larger datafile instead of summary object.
+F ratio from a repeated measures ANOVA is \(F_(6, 3,402)\) = 613.5, \emph{p} \textless{} .001 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001.
 

### 2022-09-30 SIOP2023/Counts/graphing.R

@@ -28,3 +28,25 @@ rc$scale <- c(rep("Structural",10), rep("Physical", 20), rep("Interpersonal",13)
 ggplot(rc, aes(x = mean, fill = scale)) +
   geom_density(alpha = .3) +
   xlab("Percent Agreement") + labs(fill = "ONET grouping") 
+
+
+## Repeated measures ANOVA for resource_challenge
+
+anova <- data[,c(495:578)]
+
+anova$Structural <- rowSums(anova[1:10], na.rm=TRUE)
+anova$Physical <- rowSums(anova[11:30], na.rm=TRUE)
+anova$Interpersonal <- rowSums(anova[31:43], na.rm=TRUE)
+anova$Information <- rowSums(anova[44:48], na.rm=TRUE)
+anova$Mental <- rowSums(anova[49:58], na.rm=TRUE)
+anova$Output <- rowSums(anova[59:67], na.rm=TRUE)
+anova$Interact <- rowSums(anova[68:84], na.rm=TRUE)
+
+library(tidyr)
+
+anova <- cbind(person = 1:nrow(anova), anova)  ## creating person identifier for ANOVA
+
+analysis <- gather(anova, scale, value, Structural:Interact)
+
+repmeas <- aov(value ~ factor(scale) + Error(factor(person)), data=analysis)
+summary(repmeas)

### 2022-09-30 SIOP2023/Counts/Submission_ResourceCount.tex
sleeking down to 2 papers (1 DV focus, the other agreement focused)

--- 2022-09-26 SIOP2023/Counts/Submission_ResourceCount.tex
@@
 \hypersetup{
-  pdftitle={O*Net Category Demands and Resources: Integrative Characteristics},
+  pdftitle={Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?},
   pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata Garcia Prieto Palacios Roji3},
@@
 
-\title{O*Net Category Demands and Resources: Integrative Characteristics}
+\title{Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?}
 \author{John Kulas\textsuperscript{1}, Alicia Stachowski\textsuperscript{2}, \& Renata Garcia Prieto Palacios Roji\textsuperscript{3}}
@@
 
-Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-Enter author note here.
+The relationships among sum of perceived job resources, challenge- and hindrance demands and outcomes of organizational outcomes of engagement, stress, and burnout are explored.
+568 workers rated O*Net job characteristics in terms of relevance and perceptions as challenges, hindrances and resources.
+The findings are generally aligned with the job demands resource theory regarding associations between perceived resources, demands, and organizational outcomes of engagement, stress, and burnout.
 
@@
 
-\abstract{%
-One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
-
-Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
-
-One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
-
-One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
-
-Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
-
-One or two sentences to put the results into a more \textbf{general context}.
-
-Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
-}
-
 \begin{document}
 \maketitle
-
-\textbf{Abstract}
-
-The relationships among sum of perceived job resources, challenge- and hindrance demands and outcomes of organizational outcomes of engagement, stress, and burnout are explored.
-568 workers rated O*Net job characteristics in terms of relevance and perceptions as challenges, hindrances and resources.
-The findings are generally aligned with the job demands resource theory regarding associations between perceived resources, demands, and organizational outcomes of engagement, stress, and burnout.
-
-\textbf{Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?}
 
@@
 
-\textbf{The Job Demands-Resources Theory}
+\hypertarget{the-job-demands-resources-theory}{%
+\subsection{The Job Demands-Resources Theory}\label{the-job-demands-resources-theory}}
 
@@
 
-\textbf{An Added Complexity: Perception (Appraisal) of Work Characteristics Might Matter}
+\hypertarget{an-added-complexity-perception-appraisal-of-work-characteristics-might-matter}{%
+\subsection{An Added Complexity: Perception (Appraisal) of Work Characteristics Might Matter}\label{an-added-complexity-perception-appraisal-of-work-characteristics-might-matter}}
 
@@
 
-\textbf{Could a Work Demand be Appraised Positively?: The Challenge-Hindrance Framework}
+\hypertarget{could-a-work-demand-be-appraised-positively-the-challenge-hindrance-framework}{%
+\subsection{Could a Work Demand be Appraised Positively?: The Challenge-Hindrance Framework}\label{could-a-work-demand-be-appraised-positively-the-challenge-hindrance-framework}}
 
@@
 
-\textbf{Current Study and Hypotheses}
+\hypertarget{current-study-and-hypotheses}{%
+\subsection{Current Study and Hypotheses}\label{current-study-and-hypotheses}}
 
@@
 
+\begin{quote}
 \emph{Hypothesis 1a-1c}: Total number of resources are positively associated with engagement (1a), and negatively associated with stress (1b) and burnout (1c).
+\end{quote}
+
+\begin{quote}
 \emph{Hypothesis 2a-2c}: Total number of challenge demands are positively associated with engagement (2a), and negatively associated with stress (2b) and burnout (2c).
+\end{quote}
+
+\begin{quote}
 \emph{Hypothesis 3a-3c}: Total number of hindrance demands are negatively associated with engagement (3a), and positively associated with stress (3b) and burnout (3c).
-
-\begin{verbatim}
- In addition to exploring associations with our outcomes, we also sought to explore whether challenges are perceived as distinct from resources.
-Given the definitions of each (i.e.,  aspect of one’s job that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development [resource] vs.
-aspect of one’s job that can promote mastery, personal growth, or future gains [challenge]), we propose respondents may consider them both in the realm of a resource.
-
-\end{verbatim}
-
-\emph{Hypothesis 4}: Characteristics perceived as challenges are also viewed as resources.
-
-\begin{verbatim}
-In addition to the above predictions, we consider, in an exploratory fashion, whether or not the pattern of correlations is similar across different job classifications.
-We expect to see the relationships to emerge similarly regardless of one’s type of work.
-For example, we expect that across jobs, total hindrance demands would be negatively related to engagement.
-\end{verbatim}
+\end{quote}
 
@@
 Modify or omit?
-\emph{Materials}
+
+\hypertarget{materials}{%
+\subsection{Materials}\label{materials}}
 
@@
 Our analyses included items within O\emph{Net's classifications of ``work activity'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'': 5) Interpersonal Relationships (14 statements), 6) Physical Work Conditions (30 statements)1, and 7) Structural Job Characteristics (13 statements).
-Other than minor grammatical editing (for example, changing ``the'' to ``you''), we retained the O}Net wording for our item stems.
-We used O\emph{Net's response scales, several of which were unique across items, but all shared the same 1 to 5 scale options.
+Other than minor grammatical editing (for example, changing ``the'' to ``you''), we retained the O*Net wording for our item stems.
+We used O*Net's response scales, several of which were unique across items, but all shared the same 1 to 5 scale options.
 Subsequent to providing ratings of whether or not an O}Net characteristic was relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was also asked to rate that element in terms of, 1) .
@@
 this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
-\emph{Stress}. Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Obtained alpha was .85 in this sample.
-\emph{Burnout}. Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Alpha was 0.85 in this sample.
-\emph{Engagement}.
+
+\hypertarget{stress.-three-items-taken-from-the-copenhagen-psychosocial-questionnaire-burr-et-al.-2019.-obtained-alpha-was-.85-in-this-sample.}{%
+\paragraph{\texorpdfstring{\emph{Stress}.
+Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019).
+Obtained alpha was .85 in this sample.}{Stress.
+Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019).
+Obtained alpha was .85 in this sample.}}\label{stress.-three-items-taken-from-the-copenhagen-psychosocial-questionnaire-burr-et-al.-2019.-obtained-alpha-was-.85-in-this-sample.}}
+
+\hypertarget{burnout.-four-items-were-taken-from-the-copenhagen-psychosocial-questionnaire-burr-et-al.-2019.-alpha-was-0.85-in-this-sample.}{%
+\paragraph{\texorpdfstring{\emph{Burnout}.
+Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019).
+Alpha was 0.85 in this sample.}{Burnout.
+Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019).
+Alpha was 0.85 in this sample.}}\label{burnout.-four-items-were-taken-from-the-copenhagen-psychosocial-questionnaire-burr-et-al.-2019.-alpha-was-0.85-in-this-sample.}}
+
+\hypertarget{engagement.-the-18-item-engagement-measure-was-recently-developed-russell-et-al.-2022-with-the-authors-specifying-three-subscales-which-yielded-current-sample-ux3b1s-of-0.68-absorption-and-0.80-vigor-and-0.90-dedication.-for-the-purposes-of-the-current-study-we-focused-on-an-overall-engagement-score-18-item-aggregate-ux3b1-0.91.}{%
+\paragraph{\texorpdfstring{\emph{Engagement}.
 The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample α's of 0.68 (Absorption) and 0.80 (Vigor), and 0.90 (Dedication).
-For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).
+For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).}{Engagement.
+The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample α's of 0.68 (Absorption) and 0.80 (Vigor), and 0.90 (Dedication).
+For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).}}\label{engagement.-the-18-item-engagement-measure-was-recently-developed-russell-et-al.-2022-with-the-authors-specifying-three-subscales-which-yielded-current-sample-ux3b1s-of-0.68-absorption-and-0.80-vigor-and-0.90-dedication.-for-the-purposes-of-the-current-study-we-focused-on-an-overall-engagement-score-18-item-aggregate-ux3b1-0.91.}}
 
@@
 See Table 4.
-
-Our fourth prediction suggested a positive association between total resources and total challenge demands.
-Here, we observed a strong positive relationship, so much so that it could be argued that these two variables are capturing the same thing (r = .86), as fully 74\% of the variability was shared.
 
@@
 
-\hypertarget{alicia-graphs}{%
-\subsection{Alicia graphs}\label{alicia-graphs}}
-
-\begin{figure}
-\centering
-\includegraphics{Submission_ResourceCount_files/figure-latex/matchpercentsbyperson-1.pdf}
-\caption{\label{fig:matchpercentsbyperson}Distribution of the proportion of matches by person.}
-\end{figure}
-
-To illustrate this relationship further, we computed a percentage of matches within person for the subset of job characteristics respondents agreed were a part of their jobs (excluding those characteristics rated as not part of one's job).
-Figure \ref{fig:matchpercentsbyperson} shows the distribution of the proportion of matches by person.
-
-\hypertarget{kulas-graphs}{%
-\subsection{Kulas graphs}\label{kulas-graphs}}
-
-\begin{figure}
-\centering
-\includegraphics{Submission_ResourceCount_files/figure-latex/percagree-1.pdf}
-\caption{\label{fig:percagree}Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance.}
-\end{figure}
-
-Figure \ref{fig:percagree} shows that there was not much mutual agreement regarding characteristics viewed as both hindrances and resources or as challenges and hindrances.
-Alternatively, whether a characteristic was viewed as both a resource and a challenge had quite a bit of variability.
-
-\begin{figure}
-\centering
-\includegraphics{Submission_ResourceCount_files/figure-latex/recchall-1.pdf}
-\caption{\label{fig:recchall}Resource and challenge agreement across ONet characteristic groupings (e.g., scales).}
-\end{figure}
-
-Figure \ref{fig:recchall} explores the possibility of moderation by \emph{type of characteristic rated} for the resource-challenge convergence.
-We categorized each characteristic by its ONet ``scale'' (one of seven), and the graph shows consistency across certain characteristics (for example, ) and non-convergence across other \emph{types} of characteristics (for example, ``Physical'' characteristics).
-
-\begin{quote}
-Note. If we keep this, we should also look at type of job as a moderator (swap it in for/instead of ONet scale).
-\end{quote}
-
-F ratio from psych describe object is \(F_(6, 76)\) = 26.05, \emph{p} = 0.00, although these should ideally be estimated from larger datafile instead of summary object.
-
 \hypertarget{discussion}{%
@@
 Need to also talk about our exploratory findings regarding patterns across job type
-Limitations and Future Directions
+
+\hypertarget{limitations-and-future-directions}{%
+\subsection{Limitations and Future Directions}\label{limitations-and-future-directions}}
+
 As with any piece of research, the process and results have limitations, but also provide a variety of additional directions to pursue in the future.
-First, while a strength of this project, arguably, is the use of O\emph{Net items, practical considerations limited the number of job characteristics we could include in our survey.
-Future study could consider additional or other O}Net items.
+First, while a strength of this project, arguably, is the use of O*Net items, practical considerations limited the number of job characteristics we could include in our survey.
+Future study could consider additional or other O*Net items.
 We conceptualized resources and demands in terms of perceived total amounts.

### 2022-09-30 SIOP2023/Counts/Submission_ResourceCount.Rmd
updating formatting

--- 2022-09-26 SIOP2023/Counts/Submission_ResourceCount.Rmd
@@
 ---
-title             : "O*Net Category Demands and Resources: Integrative Characteristics"
+title             : "Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?"
 shorttitle        : "O*Net JDR"
@@
 authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
 
 abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
+  The relationships among sum of perceived job resources, challenge- and hindrance demands and outcomes of organizational outcomes of engagement, stress, and burnout are explored.
+568 workers rated O\*Net job characteristics in terms of relevance and perceptions as challenges, hindrances and resources.
+The findings are generally aligned with the job demands resource theory regarding associations between perceived resources, demands, and organizational outcomes of engagement, stress, and burnout.
 
@@
 
-bibliography      : "r-references.bib"
+bibliography      : ["r-references.bib", "jdr.bib", "jobdemands_resources_bibtex.bib"]
 
@@
 
-**Abstract**
-
-The relationships among sum of perceived job resources, challenge- and hindrance demands and outcomes of organizational outcomes of engagement, stress, and burnout are explored.
-568 workers rated O*Net job characteristics in terms of relevance and perceptions as challenges, hindrances and resources.
-The findings are generally aligned with the job demands resource theory regarding associations between perceived resources, demands, and organizational outcomes of engagement, stress, and burnout.
-
-**Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?**
-
-  A plethora of research applying the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker & Demerouti, 2017) underscore the importance of work characteristics on the experience of motivation and strain.
+  A plethora of research applying the job demands-resources model (@demerouti2001job) and job demands-resources theory (Bakker & Demerouti, 2017) underscore the importance of work characteristics on the experience of motivation and strain.
 However, much of our existing research on this topic assumes that certain characteristics are resources and others are generally considered demands.
@@
 
-**The Job Demands-Resources Theory**
+## The Job Demands-Resources Theory
 
-  The theoretical foundation for this study is the job demands-resources theory (Demerouti et al., 2001).
+  The theoretical foundation for this study is the job demands-resources theory (@demerouti2001job).
 Using this theory, we can model both work environment and job characteristics via job resources and demands.
-Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure; Demerouti et al., 2001).
+Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (@demerouti2001job).
+In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure; @demerouti2001job).
 
@@
 
-**An Added Complexity: Perception (Appraisal) of Work Characteristics Might Matter**
+## An Added Complexity: Perception (Appraisal) of Work Characteristics Might Matter
 
@@
 
-**Could a Work Demand be Appraised Positively?: The Challenge-Hindrance Framework**
+## Could a Work Demand be Appraised Positively?: The Challenge-Hindrance Framework
 
@@
 
-**Current Study and Hypotheses**
+## Current Study and Hypotheses
 
@@
 
-*Hypothesis 1a-1c*: Total number of resources are positively associated with engagement (1a), and negatively associated with stress (1b) and burnout (1c).
-*Hypothesis 2a-2c*: Total number of  challenge demands are positively associated with engagement (2a), and negatively associated with stress (2b) and burnout (2c).
-*Hypothesis 3a-3c*: Total number of hindrance demands are negatively associated with engagement (3a), and positively associated with stress (3b) and burnout (3c).
+> *Hypothesis 1a-1c*: Total number of resources are positively associated with engagement (1a), and negatively associated with stress (1b) and burnout (1c).
 
-	 In addition to exploring associations with our outcomes, we also sought to explore whether challenges are perceived as distinct from resources.
-Given the definitions of each (i.e.,  aspect of one’s job that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development [resource] vs.
-aspect of one’s job that can promote mastery, personal growth, or future gains [challenge]), we propose respondents may consider them both in the realm of a resource.
+> *Hypothesis 2a-2c*: Total number of  challenge demands are positively associated with engagement (2a), and negatively associated with stress (2b) and burnout (2c).
 
-*Hypothesis 4*: Characteristics perceived as challenges are also viewed as resources.
-
-	In addition to the above predictions, we consider, in an exploratory fashion, whether or not the pattern of correlations is similar across different job classifications.
-We expect to see the relationships to emerge similarly regardless of one’s type of work.
-For example, we expect that across jobs, total hindrance demands would be negatively related to engagement.
+> *Hypothesis 3a-3c*: Total number of hindrance demands are negatively associated with engagement (3a), and positively associated with stress (3b) and burnout (3c).
 
@@
 
-  We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (Bakker & Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001), but from within the unifying framework of O*Net.
-Here, we focus on the relationship between O*Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S.
+  We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (Bakker & Demerouti, 2017; Bakker et al., 2003; @demerouti2001job), but from within the unifying framework of O\*Net.
+Here, we focus on the relationship between O\*Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S.
 workforce representative sample.
@@
 Gender was captured via a free-field gender identity category, although the sample predominantly self-identified as female (52.58%) or male (46.83%).
-Jobs were classified into the International Standard Classification of Occupations (ISCO) via the package labourR (Kouretsis et al., 2020).
-Modify or omit?
-*Materials*
+
+## Materials
 
   Characteristics, Demands, and Resources.
-Our analyses included items within O*Net’s classifications of “work activity”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context”: 5) Interpersonal Relationships (14 statements), 6) Physical Work Conditions (30 statements)1, and 7) Structural Job Characteristics (13 statements).
-  Other than minor grammatical editing (for example, changing “the” to “you”), we retained the O*Net wording for our item stems.
-We used O*Net’s response scales, several of which were unique across items, but all shared the same 1 to 5 scale options.
-Subsequent to providing ratings of whether or not an O*Net characteristic was relevant for the respondent’s work, each respondent who agreed that an element had at least some relevance to their job was also asked to rate that element in terms of, 1) .
+Our analyses included items within O\*Net’s classifications of “work activity”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context”: 5) Interpersonal Relationships (14 statements), 6) Physical Work Conditions (30 statements)1, and 7) Structural Job Characteristics (13 statements).
+
+  Other than minor grammatical editing (for example, changing “the” to “you”), we retained the O\*Net wording for our item stems.
+We used O\*Net’s response scales, several of which were unique across items, but all shared the same 1 to 5 scale options.
+Subsequent to providing ratings of whether or not an O\*Net characteristic was relevant for the respondent’s work, each respondent who agreed that an element had at least some relevance to their job was also asked to rate that element in terms of, 1) .
 .
@@
 this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
-*Stress*. Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Obtained alpha was .85 in this sample.
-*Burnout*. Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Alpha was 0.85 in this sample.
-*Engagement*.
+
+> *Stress*. Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Obtained alpha was .85 in this sample.
+
+> *Burnout*. Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Alpha was 0.85 in this sample.
+
+>*Engagement*.
 The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample α’s of 0.68 (Absorption) and 0.80 (Vigor), and 0.90 (Dedication).
@@
   Correlations, means and standard deviations among all study variables are presented in Table 1.
-Results reveal a positive association between resources and engagement (r = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively).
-Challenge demands were positively associated with engagement (r = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
+Results reveal a positive association between resources and engagement (*r* = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively).
+Challenge demands were positively associated with engagement (*r* = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
 Total hindrance stressors were not significantly associated with our outcomes (H3a-H3c).
@@
 First, regarding engagement (F(3, 564) = 26.41, p < .001), the total resources (beta = ??) was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table 2).
-Next, stress was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 2.47, p = .060 (see Table 3).
-Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 1.10, p = .349.
+Next, stress was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 2.47, *p* = .060 (see Table 3).
+Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 1.10, *p* = .349.
 See Table 4.
 
-  Our fourth prediction suggested a positive association between total resources and total challenge demands.
-Here, we observed a strong positive relationship, so much so that it could be argued that these two variables are capturing the same thing (r = .86), as fully 74% of the variability was shared.
-
-  In an exploratory fashion, we also considered whether or not the pattern of correlations described above was similar across job types.
-
-```{r study1}
+```{r study1, include=FALSE}
 
@@
 
-There were `r nrow(data)` retained respondents.
-
 ```{r keeping45}
@@
 
-```{r correlation_table, eval=TRUE}
+```{r correlation_table, eval=TRUE, include=FALSE}
 
@@
 
-```{r regressions}
+```{r regressions, include=FALSE}
 
@@
 
-## Alicia graphs
-
-```{r matchpercentsbyperson, fig.cap="Distribution of the proportion of matches by person."}
-#rc1 to rc 84
-
-data$match_rc_by_person <- rowSums(data[495:578], na.rm = TRUE)
-
-data$match_rc_by_person_NAs <- rowSums(is.na(data[495:578]))
-
-#This should be matches divided by 84 items minus nas
-data$percent_match_total_person <- (data$match_rc_by_person/(84 - data$match_rc_by_person_NAs))
-# head(data$percent_match_total_person)
-
-hist(data$percent_match_total_person)
-```
-
-  To illustrate this relationship further, we computed a percentage of matches within person for the subset of job characteristics respondents agreed were a part of their jobs (excluding those characteristics rated as not part of one's job).
-Figure \@ref(fig:matchpercentsbyperson) shows the distribution of the proportion of matches by person.
-
-## Kulas graphs
-
-```{r percagree, fig.cap="Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance.", fig.height=10}
-
-rc <- read.csv("resource_challenge.csv")
-rh <- read.csv("resource_hind.csv")
-ch <- read.csv("hind_challenge.csv")
-
-rc$type <- "Resource-Challenge"
-rh$type <- "Resource-Hindrance"
-ch$type <- "Challenge-Hindrance"
-
-forgraph <- rbind(rc,rh,ch)
-
-library(ggplot2)
-
-#ggplot(forgraph, aes(x = mean, fill = type)) +
-#  geom_density(alpha = .3) +
-#  xlab("Percent Agreement") + labs(fill = "Att/Engage\nInteraction")
-
-p <- ggplot(forgraph, aes(x = mean)) + geom_histogram()
-p + facet_wrap(~type, nrow=3)
-
-## lotsa variance in resource-challenge agreement. Next look for either content (O*Net category) or contextual (job) moderator
-
-```
-
-Figure \@ref(fig:percagree) shows that there was not much mutual agreement regarding characteristics viewed as both hindrances and resources or as challenges and hindrances.
-Alternatively, whether a characteristic was viewed as both a resource and a challenge had quite a bit of variability.
-
-```{r recchall, fig.cap="Resource and challenge agreement across ONet characteristic groupings (e.g., scales).", fig.height=10}
-
-rc$scale <- c(rep("Structural",10), rep("Physical", 20), rep("Interpersonal",13), rep("Information Input", 5), rep("Mental Processes", 10), rep("Work Output", 9), rep("Interact with Others", 17))
-
-ggplot(rc, aes(x=mean)) + geom_histogram() + facet_wrap(~scale, nrow=7)
-
-#ggplot(rc, aes(x = mean, fill = scale)) +
-#  geom_density(alpha = .3) +
-#  xlab("Percent Agreement") + labs(fill = "ONET grouping")
-
-```
-
-Figure \@ref(fig:recchall) explores the possibility of moderation by *type of characteristic rated* for the resource-challenge convergence.
-We categorized each characteristic by its ONet "scale" (one of seven), and the graph shows consistency across certain characteristics (for example, ) and non-convergence across other *types* of characteristics (for example, "Physical" characteristics).
-
-```{r anova}
-
-## probably need to do with actual data (not summaries)
-
-oneway <- aov(mean ~ scale, rc)
-
-```
-
->Note. If we keep this, we should also look at type of job as a moderator (swap it in for/instead of ONet scale).
-
-F ratio from psych describe object is $F_(6, 76)$ = `r summary(oneway)[[1]][1,4]`, *p* = `r summary(oneway)[[1]][1,5]`, although these should ideally be estimated from larger datafile instead of summary object.
-
 # Discussion
@@
 The major goal of this paper was to further explore the relationships among total perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout.
-Additionally, we considered whether resources and challenge demands were perceived as distinct, and finally, whether the patterns were similar across job categories/types of work.
 The results suggest a positive relationship between both resources and engagement (H1a), and challenge demands and engagement (H2a).
-Employers would benefit from understanding that at leas the perception of having “more” resources and more challenge demands in a job is highly associated with reported engagement.
+Employers would benefit from understanding that at least the perception of having “more” resources and more challenge demands in a job is highly associated with reported engagement.
 While not a causal relationship, it points to the potential value of these kinds of employee support nonetheless.
@@
 It is possible that rather than volume, categorically some demands are more related to these outcomes than others.
- Further, total resources were highly associated challenge demands (supporting H4).
-We could even argue, given the magnitude of the correlation, that they are capturing the same thing (74% overlap with a correlation of .86).
-Need to also talk about our exploratory findings regarding patterns across job type
-Limitations and Future Directions
+
+## Limitations and Future Directions
+
 As with any piece of research, the process and results have limitations, but also provide a variety of additional directions to pursue in the future.
-First, while a strength of this project, arguably, is the use of O*Net items, practical considerations limited the number of job characteristics we could include in our survey.
-Future study could consider additional or other O*Net items.
+First, while a strength of this project, arguably, is the use of O\*Net items, practical considerations limited the number of job characteristics we could include in our survey.
+Future study could consider additional or other O\*Net items.
 We conceptualized resources and demands in terms of perceived total amounts.
@@
 It would be especially interesting to explore additional outcomes (e.g., job satisfaction) as well, or whether volume of resources and demands operationalized in this way are related to other behaviors (e.g., turnover intention, perceived organizational support, commitment).
+
+\newpage
+
+# References
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+<div id="refs" custom-style="Bibliography"></div>
+\endgroup

### 2022-09-30 SIOP2023/Counts/Submission_ResourceCount.tex
updating formatting

@@
 \fi
-\ifLuaTeX
-\usepackage[bidi=basic]{babel}
-\else
-\usepackage[bidi=default]{babel}
-\fi
-\babelprovide[main,import]{english}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
 % Manuscript styling
@@
 \makeatother
-
-\usepackage{xpatch}
-\makeatletter
-\xapptocmd\appendix
-  {\xapptocmd\section
-    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
-    {}{\InnerPatchFailed}%
-  }
-{}{\PatchFailed}
+\shorttitle{O*Net JDR}
 \keywords{keywords\newline\indent Word count: X}
@@
 \usepackage{csquotes}
-\ifLuaTeX
+\ifxetex
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\else
+  \usepackage[main=english]{babel}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+\fi
+\ifluatex
   \usepackage{selnolig}  % disable illegal ligatures
@@
 
-\shorttitle{O*Net JDR}
-
 \authornote{
-
-The relationships among sum of perceived job resources, challenge- and hindrance demands and outcomes of organizational outcomes of engagement, stress, and burnout are explored.
-568 workers rated O*Net job characteristics in terms of relevance and perceptions as challenges, hindrances and resources.
-The findings are generally aligned with the job demands resource theory regarding associations between perceived resources, demands, and organizational outcomes of engagement, stress, and burnout.
 
@@
 \affiliation{\vspace{0.5cm}\textsuperscript{1} eRg\\\textsuperscript{2} University of Wisconsin - Stout\\\textsuperscript{3} PepsiCo}
+
+\abstract{
+The relationships among sum of perceived job resources, challenge- and hindrance demands and outcomes of organizational outcomes of engagement, stress, and burnout are explored.
+568 workers rated O*Net job characteristics in terms of relevance and perceptions as challenges, hindrances and resources.
+The findings are generally aligned with the job demands resource theory regarding associations between perceived resources, demands, and organizational outcomes of engagement, stress, and burnout.
+}
 
@@
 The brief review above provides theoretical and empirical support for the connection between resources and positive organizational outcomes, and between demands and negative outcomes.
-Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement (``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption'', Schaufeli et al., 2002), workplace stress (``an individual state characterized by a combination of high arousal and displeasure'', p.~15, Pejtersen et al., 2010) and burnout (``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work'', p.~197; Kristensen et al., 2005).
+Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement (``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption,'' Schaufeli et al., 2002), workplace stress (``an individual state characterized by a combination of high arousal and displeasure,'' p.~15, Pejtersen et al., 2010) and burnout (``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work,'' p.~197; Kristensen et al., 2005).
 Utilizing the job demands-resources theory, transactional theory of stress, and the challenge-hindrance framework, we propose that the number of job characteristics appraised as ``challenge demands'' (i.e., promote mastery, personal growth, and future gains) would activate a positive state -- that of engagement.
@@
 
-We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (Bakker \& Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001), but from within the unifying framework of O\emph{Net.
-Here, we focus on the relationship between O}Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S.
+We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (Bakker \& Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001), but from within the unifying framework of O*Net.
+Here, we focus on the relationship between O*Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S.
 workforce representative sample.
@@
 Of those,112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021).
-Additional screening using four embedded attention checks resulted in the retention of 568 respondents.
+Additional screening using four embedded attention checks resulted in the retention of respondents.
 A total of 13.57\% had been in their job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.
@@
 Gender was captured via a free-field gender identity category, although the sample predominantly self-identified as female (52.58\%) or male (46.83\%).
-Jobs were classified into the International Standard Classification of Occupations (ISCO) via the package labourR (Kouretsis et al., 2020).
-Modify or omit?
 
@@
 Characteristics, Demands, and Resources.
-Our analyses included items within O\emph{Net's classifications of ``work activity'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'': 5) Interpersonal Relationships (14 statements), 6) Physical Work Conditions (30 statements)1, and 7) Structural Job Characteristics (13 statements).
+Our analyses included items within O*Net's classifications of ``work activity'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'': 5) Interpersonal Relationships (14 statements), 6) Physical Work Conditions (30 statements)1, and 7) Structural Job Characteristics (13 statements).
+
 Other than minor grammatical editing (for example, changing ``the'' to ``you''), we retained the O*Net wording for our item stems.
 We used O*Net's response scales, several of which were unique across items, but all shared the same 1 to 5 scale options.
-Subsequent to providing ratings of whether or not an O}Net characteristic was relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was also asked to rate that element in terms of, 1) .
+Subsequent to providing ratings of whether or not an O*Net characteristic was relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was also asked to rate that element in terms of, 1) .
 .
@@
 
-\hypertarget{stress.-three-items-taken-from-the-copenhagen-psychosocial-questionnaire-burr-et-al.-2019.-obtained-alpha-was-.85-in-this-sample.}{%
-\paragraph{\texorpdfstring{\emph{Stress}.
-Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019).
-Obtained alpha was .85 in this sample.}{Stress.
-Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019).
-Obtained alpha was .85 in this sample.}}\label{stress.-three-items-taken-from-the-copenhagen-psychosocial-questionnaire-burr-et-al.-2019.-obtained-alpha-was-.85-in-this-sample.}}
+\begin{quote}
+\emph{Stress}. Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Obtained alpha was .85 in this sample.
+\end{quote}
 
-\hypertarget{burnout.-four-items-were-taken-from-the-copenhagen-psychosocial-questionnaire-burr-et-al.-2019.-alpha-was-0.85-in-this-sample.}{%
-\paragraph{\texorpdfstring{\emph{Burnout}.
-Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019).
-Alpha was 0.85 in this sample.}{Burnout.
-Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019).
-Alpha was 0.85 in this sample.}}\label{burnout.-four-items-were-taken-from-the-copenhagen-psychosocial-questionnaire-burr-et-al.-2019.-alpha-was-0.85-in-this-sample.}}
+\begin{quote}
+\emph{Burnout}. Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Alpha was 0.85 in this sample.
+\end{quote}
 
-\hypertarget{engagement.-the-18-item-engagement-measure-was-recently-developed-russell-et-al.-2022-with-the-authors-specifying-three-subscales-which-yielded-current-sample-ux3b1s-of-0.68-absorption-and-0.80-vigor-and-0.90-dedication.-for-the-purposes-of-the-current-study-we-focused-on-an-overall-engagement-score-18-item-aggregate-ux3b1-0.91.}{%
-\paragraph{\texorpdfstring{\emph{Engagement}.
+\begin{quote}
+\emph{Engagement}.
 The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample α's of 0.68 (Absorption) and 0.80 (Vigor), and 0.90 (Dedication).
-For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).}{Engagement.
-The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample α's of 0.68 (Absorption) and 0.80 (Vigor), and 0.90 (Dedication).
-For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).}}\label{engagement.-the-18-item-engagement-measure-was-recently-developed-russell-et-al.-2022-with-the-authors-specifying-three-subscales-which-yielded-current-sample-ux3b1s-of-0.68-absorption-and-0.80-vigor-and-0.90-dedication.-for-the-purposes-of-the-current-study-we-focused-on-an-overall-engagement-score-18-item-aggregate-ux3b1-0.91.}}
+For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).
+\end{quote}
 
@@
 Correlations, means and standard deviations among all study variables are presented in Table 1.
-Results reveal a positive association between resources and engagement (r = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively).
-Challenge demands were positively associated with engagement (r = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
+Results reveal a positive association between resources and engagement (\emph{r} = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively).
+Challenge demands were positively associated with engagement (\emph{r} = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
 Total hindrance stressors were not significantly associated with our outcomes (H3a-H3c).
@@
 First, regarding engagement (F(3, 564) = 26.41, p \textless{} .001), the total resources (beta = ??) was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table 2).
-Next, stress was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 2.47, p = .060 (see Table 3).
-Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 1.10, p = .349.
+Next, stress was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 2.47, \emph{p} = .060 (see Table 3).
+Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 1.10, \emph{p} = .349.
 See Table 4.
-
-In an exploratory fashion, we also considered whether or not the pattern of correlations described above was similar across job types.
-
-There were 568 retained respondents.
 
@@
 
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:correlation_table}Focal variable correlations (counts data).}
-
-\begin{tabular}{llllllll}
-\toprule
- & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
-\midrule
-1. resource & - &  &  &  &  & 36.02 & 13.26\\
-2. hindrance & .23*** & - &  &  &  & 13.09 & 13.62\\
-3. challenge & .86*** & .22*** & - &  &  & 35.64 & 13.63\\
-4. burnout & .05 & .04 & .07 & - &  & 3.04 & 0.87\\
-5. stress & .06 & .09* & .08 & .70*** & - & 2.59 & 0.97\\
-6. engagement & .34*** & .01 & .31*** & -.35*** & -.30*** & 4.04 & 0.83\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{verbatim}
-## 
-## Call:
-## lm(formula = engagement ~ hindrance + challenge + resource, data = data22)
-## 
-## Residuals:
-##      Min       1Q   Median       3Q      Max 
-## -2.40431 -0.50713  0.02842  0.55010  2.05201 
-## 
-## Coefficients:
-##              Estimate Std. Error t value Pr(>|t|)    
-## (Intercept)  3.276423   0.096574  33.926  < 2e-16 ***
-## hindrance   -0.004436   0.002460  -1.803 0.071918 .  
-## challenge    0.004175   0.004728   0.883 0.377613    
-## resource     0.018672   0.004868   3.836 0.000139 ***
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-## 
-## Residual standard error: 0.7763 on 564 degrees of freedom
-## Multiple R-squared:  0.1232, Adjusted R-squared:  0.1185 
-## F-statistic: 26.41 on 3 and 564 DF,  p-value: 5.394e-16
-\end{verbatim}
-
-\begin{verbatim}
-## 
-## Call:
-## lm(formula = burnout ~ hindrance + challenge + resource, data = data22)
-## 
-## Residuals:
-##      Min       1Q   Median       3Q      Max 
-## -2.23967 -0.64759 -0.04747  0.65173  2.10310 
-## 
-## Coefficients:
-##              Estimate Std. Error t value Pr(>|t|)    
-## (Intercept)  2.895053   0.107671  26.888   <2e-16 ***
-## hindrance    0.001843   0.002743   0.672    0.502    
-## challenge    0.006290   0.005271   1.193    0.233    
-## resource    -0.002843   0.005427  -0.524    0.601    
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-## 
-## Residual standard error: 0.8655 on 564 degrees of freedom
-## Multiple R-squared:  0.005808,   Adjusted R-squared:  0.0005199 
-## F-statistic: 1.098 on 3 and 564 DF,  p-value: 0.3493
-\end{verbatim}
-
-\begin{verbatim}
-## 
-## Call:
-## lm(formula = stress ~ hindrance + challenge + resource, data = data22)
-## 
-## Residuals:
-##     Min      1Q  Median      3Q     Max 
-## -1.8841 -0.8038 -0.1523  0.7164  2.5693 
-## 
-## Coefficients:
-##              Estimate Std. Error t value Pr(>|t|)    
-## (Intercept)  2.383299   0.120392  19.796   <2e-16 ***
-## hindrance    0.005571   0.003067   1.816   0.0698 .  
-## challenge    0.008445   0.005894   1.433   0.1525    
-## resource    -0.004687   0.006068  -0.772   0.4402    
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-## 
-## Residual standard error: 0.9678 on 564 degrees of freedom
-## Multiple R-squared:  0.01299,    Adjusted R-squared:  0.007741 
-## F-statistic: 2.474 on 3 and 564 DF,  p-value: 0.06069
-\end{verbatim}
-
 \hypertarget{discussion}{%
@@
 The major goal of this paper was to further explore the relationships among total perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout.
-Additionally, we considered whether resources and challenge demands were perceived as distinct, and finally, whether the patterns were similar across job categories/types of work.
 The results suggest a positive relationship between both resources and engagement (H1a), and challenge demands and engagement (H2a).
-Employers would benefit from understanding that at leas the perception of having ``more'' resources and more challenge demands in a job is highly associated with reported engagement.
+Employers would benefit from understanding that at least the perception of having ``more'' resources and more challenge demands in a job is highly associated with reported engagement.
 While not a causal relationship, it points to the potential value of these kinds of employee support nonetheless.
@@
 It is possible that rather than volume, categorically some demands are more related to these outcomes than others.
-Further, total resources were highly associated challenge demands (supporting H4).
-We could even argue, given the magnitude of the correlation, that they are capturing the same thing (74\% overlap with a correlation of .86).
-Need to also talk about our exploratory findings regarding patterns across job type
 

### 2022-10-01 SIOP2023/Counts/Submission_ResourceCount.Rmd
updated references and tables in text and added to the end of the paper.

@@
 
-  A plethora of research applying the job demands-resources model (@demerouti2001job) and job demands-resources theory (Bakker & Demerouti, 2017) underscore the importance of work characteristics on the experience of motivation and strain.
+  A plethora of research applying the job demands-resources model (@demerouti2001job) and job demands-resources theory (@bakker2017job) underscore the importance of work characteristics on the experience of motivation and strain.
 However, much of our existing research on this topic assumes that certain characteristics are resources and others are generally considered demands.
@@
 
-  The perception of a characteristic of one’s job as a resource or demand activates one of two unique processes: either health impairment or motivation Bakker & Demerouti, 2014).
-Demanding job characteristics are frequently associated with negative outcomes (e.g., health impairment process; Bakker et al., 2003), whereas job characteristics considered resources have been associated with positive organizational outcomes like engagement and motivation (Bakker et al., 2007).
+  The perception of a characteristic of one’s job as a resource or demand activates one of two unique processes: either health impairment or motivation @bakker2014job.
+Demanding job characteristics are frequently associated with negative outcomes (e.g., health impairment process; @bakker2003dual), whereas job characteristics considered resources have been associated with positive organizational outcomes like engagement and motivation (@bakker2007job).
 
@@
   The above description speaks to one of two distinct processes being activated, presumably based on one’s assessment of how a work characteristics makes them feel (e.g., consider the different reactions employees may have to being nominated to give a speech at an upcoming company event).
-Thus, although some research on job demands in particular is based on a priori classifications of demands (Searle & Auton, 2015), the appraisal of any work characteristic as a demand or resource is quite subjective.
+Thus, although some research on job demands in particular is based on a priori classifications of demands (@searle2015merits), the appraisal of any work characteristic as a demand or resource is quite subjective.
 The literature on the experience of stress explains how such individual differences in appraisal are possible.
-Specifically, the transactional theory of stress and coping states that people cognitively appraise stimuli in their environments on a continuous basis (Lazarus & Folkman, 1984).
+Specifically, the transactional theory of stress and coping states that people cognitively appraise stimuli in their environments on a continuous basis (@lazarus1984stress).
 During this process, meaning is assigned to stimuli.
 If the above employee appraised the upcoming speech as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping (e.g., attempting to decline, asking for help in writing the speech).
-From that point, the cycle of appraisal continues based on the action to cope with the stressor (Lazarus & Folkman, 1984).
+From that point, the cycle of appraisal continues based on the action to cope with the stressor (@lazarus1984stress).
 
@@
 
-  Although the word “stress” often connotes something negative, Selye (1936) defined stress generically as a response to change.
+  Although the word “stress” often connotes something negative,@selye1936syndrome defined stress generically as a response to change.
 For instance, the example above describes an employee who appraises being nominated to give a speech as a negative stressor.
 However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
-The terms associated with the two different appraisals of the stressor described here are challenge and hindrance demands (Cavanaugh et al., 2000) Specifically, challenge demands promote mastery, personal growth, and future gains.
+The terms associated with the two different appraisals of the stressor described here are challenge and hindrance demands (@cavanaugh2000empirical) Specifically, challenge demands promote mastery, personal growth, and future gains.
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes (e.g., Cavanaugh et al., 2000).
+Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes (e.g., @cavanaugh2000empirical).
 We will explore their associations with both positive and negative outcomes in this study.
@@
 To begin, the first logical question is whether employees actually distinguish between challenge and hindrance stressors, and research suggests that they can and do.
-For example, Bakker and Sanz-Vergel (2013) found that perceived work pressure can be classified as a hindrance demand, and emotional demands as a challenge demand.
-Webster et al.
-(2011) considered three common workplace demands including workload, role ambiguity, and role conflict.
+For example, @bakker2013weekly found that perceived work pressure can be classified as a hindrance demand, and emotional demands as a challenge demand.
+@webster2011extending considered three common workplace demands including workload, role ambiguity, and role conflict.
 Interestingly, they found that while each could be appraised primarily as challenges or hindrances, employees could also simultaneously be perceived as being both a challenge and hindrance.
@@
   Having established that there can be individual differences in the appraisal of demands as challenges or resources, we next turn our attention to their association with organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and well-being.
-For example, Cavanaugh et al.
-(2000) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern with job satisfaction and job search behaviors in a sample of managers.
-However, Abbas and Raja (2019) found that challenge and hindrance stressors were both positively related to strain and turnover intentions.
-We also have some evidence that challenge-hinderance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford et al., 2010).
+For example, @cavanaugh2000empirical found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern with job satisfaction and job search behaviors in a sample of managers.
+However, @abbas2019challenge found that challenge and hindrance stressors were both positively related to strain and turnover intentions.
+We also have some evidence that challenge-hinderance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (@crawford2010linking).
 The appraisal process also suggests theoretically that the perception of a job characteristic as a challenge or hindrance is a mediator.
-Gerich (2017), for instance, found that employee well-being was, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
-To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, Podsakoff et al.’s (2007) meta-analysis supported the original assertion of Cavanaugh et al.
-(2000) such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.
+@gerich2017relevance, for instance, found that employee well-being was, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
+To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, @podsakoff2007differential meta-analysis supported the original assertion of @cavanaugh2000empirical such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.
 
@@
   The brief review above provides theoretical and empirical support for the connection between resources and positive organizational outcomes, and between demands and negative outcomes.
-Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement (“a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption”, Schaufeli et al., 2002), workplace stress (“an individual state characterized by a combination of high arousal and displeasure”, p.
-15, Pejtersen et al., 2010) and burnout (“the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work”, p.
-197; Kristensen et al., 2005).
+Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement (“a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption”, @schaufeli2002measurement), workplace stress (“an individual state characterized by a combination of high arousal and displeasure”, p.
+15, @pejtersen2010second) and burnout (“the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work”, p.
+197; @kristensen2005copenhagen).
 Utilizing the job demands-resources theory, transactional theory of stress, and the challenge-hindrance framework, we propose that the number of job characteristics appraised as “challenge demands” (i.e., promote mastery, personal growth, and future gains) would activate a positive state – that of engagement.
@@
 
-  We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (Bakker & Demerouti, 2017; Bakker et al., 2003; @demerouti2001job), but from within the unifying framework of O\*Net.
+  We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (@bakker2017job; @bakker2003dual; @demerouti2001job), but from within the unifying framework of O\*Net.
 Here, we focus on the relationship between O\*Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S.
@@
 
-> *Stress*. Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Obtained alpha was .85 in this sample.
+> *Stress*. Three items taken from the Copenhagen Psychosocial Questionnaire (@burr_third_2019). Obtained alpha was .85 in this sample.
 
-> *Burnout*. Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Alpha was 0.85 in this sample.
+> *Burnout*. Four items were taken from the Copenhagen Psychosocial Questionnaire (@burr_third_2019). Alpha was 0.85 in this sample.
 
 >*Engagement*.
-The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample α’s of 0.68 (Absorption) and 0.80 (Vigor), and 0.90 (Dedication).
-For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).
+The 18-item engagement measure was recently developed (@engage_2022), with the authors specifying three subscales which yielded current sample α’s of 0.68 (absorption) and 0.80 (vigor), and 0.90 (dedication).
+For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, alpha = 0.91).
 
@@
 Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
-
-# Results
-
-  We used R (Version 4.0.3; R Core Team, 2020) and the R-packages careless (Version 1.1.3; Yentes & Wilhelm, 2021), labourR (Version 1.0.0; Kouretsis et al., 2020), papaja (Version 0.1.0.9997; Aust & Barth, 2020), and tinylabels (Barth, 2021) for all analyses.
-Our analyses are presented by characteristics of work that are rated in terms of being resources, challenge demands, and hindrance demands.
-Pearson correlation coefficients between characteristics classified as resources, challenges, and hindrances were obtained to investigate the associations among these characteristics.
-  Correlations, means and standard deviations among all study variables are presented in Table 1.
-Results reveal a positive association between resources and engagement (*r* = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively).
-Challenge demands were positively associated with engagement (*r* = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
-Total hindrance stressors were not significantly associated with our outcomes (H3a-H3c).
-To further explore H1-H3, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
-First, regarding engagement (F(3, 564) = 26.41, p < .001), the total resources (beta = ??) was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table 2).
-Next, stress was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 2.47, *p* = .060 (see Table 3).
-Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 1.10, *p* = .349.
-See Table 4.
 
@@
 
-```{r keeping45}
+```{r keeping45, include=FALSE}
 
@@
 
-```{r correlation_table, eval=TRUE, include=FALSE}
+```{r correlation_table, eval=TRUE}
 
@@
 ```
+
+```{r regression_table_eng}
+library(papaja)
+apa_lm <- apa_print(eng)
+apa_table(
+  apa_lm$table
+  , caption = "Regression Predicting Engagement."
+)
+```
+
+```{r regression_table_str}
+library(papaja)
+apa_lm <- apa_print(str)
+apa_table(
+  apa_lm$table
+  , caption = "Regression Predicting Stress."
+)
+```
+
+```{r regression_table_bur}
+library(papaja)
+apa_lm <- apa_print(bur)
+apa_table(
+  apa_lm$table
+  , caption = "Regression Predicting Burnout."
+)
+```
+
+# Results
+
+  We used R (Version 4.0.3; @R-base) and the R-packages careless (Version 1.1.3; Yentes & Wilhelm, 2021), labourR (Version 1.0.0; Kouretsis et al., 2020), papaja (Version 0.1.0.9997; Aust & Barth, 2020), and tinylabels (Barth, 2021) for all analyses.
+Our analyses are presented by characteristics of work that are rated in terms of being resources, challenge demands, and hindrance demands.
+Pearson correlation coefficients between characteristics classified as resources, challenges, and hindrances were obtained to investigate the associations among these characteristics.
+  Correlations, means and standard deviations among all study variables are presented in Table \ref{tab:correlation_table}.
+Results reveal a positive association between resources and engagement (*r* = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively).
+Challenge demands were positively associated with engagement (*r* = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
+Total hindrance stressors were not significantly associated with our outcomes (H3a-H3c).
+To further explore H1-H3, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
+First, regarding engagement (F(3, 564) = 26.41, p < .001), the total resources was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table \ref{tab:regression_table_eng}).
+Next, stress was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 2.47, *p* = .060 (see Table \ref{tab:regression_table_str}).
+Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 1.10, *p* = .349.
+See Table \ref{tab:regression_table_bur}.
 

### 2022-10-01 SIOP2023/Counts/Submission_ResourceCount.tex
updated references and tables in text and added to the end of the paper.

@@
 \fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 
-A plethora of research applying the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker \& Demerouti, 2017) underscore the importance of work characteristics on the experience of motivation and strain.
+A plethora of research applying the job demands-resources model (Demerouti, Bakker, Nachreiner, and Schaufeli (2001)) and job demands-resources theory (A.
+B.
+Bakker and Demerouti (2017)) underscore the importance of work characteristics on the experience of motivation and strain.
 However, much of our existing research on this topic assumes that certain characteristics are resources and others are generally considered demands.
@@
 
-The theoretical foundation for this study is the job demands-resources theory (Demerouti et al., 2001).
+The theoretical foundation for this study is the job demands-resources theory (Demerouti, Bakker, Nachreiner, and Schaufeli (2001)).
 Using this theory, we can model both work environment and job characteristics via job resources and demands.
-Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure; Demerouti et al., 2001).
+Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti, Bakker, Nachreiner, and Schaufeli (2001)).
+In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure; Demerouti, Bakker, Nachreiner, and Schaufeli (2001)).
 
-The perception of a characteristic of one's job as a resource or demand activates one of two unique processes: either health impairment or motivation Bakker \& Demerouti, 2014).
-Demanding job characteristics are frequently associated with negative outcomes (e.g., health impairment process; Bakker et al., 2003), whereas job characteristics considered resources have been associated with positive organizational outcomes like engagement and motivation (Bakker et al., 2007).
+The perception of a characteristic of one's job as a resource or demand activates one of two unique processes: either health impairment or motivation A.
+B.
+Bakker and Demerouti (2014).
+Demanding job characteristics are frequently associated with negative outcomes (e.g., health impairment process; A.
+Bakker, Demerouti, and Schaufeli (2003)), whereas job characteristics considered resources have been associated with positive organizational outcomes like engagement and motivation (A.
+B.
+Bakker, Hakanen, Demerouti, and Xanthopoulou (2007)).
 
@@
 The above description speaks to one of two distinct processes being activated, presumably based on one's assessment of how a work characteristics makes them feel (e.g., consider the different reactions employees may have to being nominated to give a speech at an upcoming company event).
-Thus, although some research on job demands in particular is based on a priori classifications of demands (Searle \& Auton, 2015), the appraisal of any work characteristic as a demand or resource is quite subjective.
+Thus, although some research on job demands in particular is based on a priori classifications of demands (Searle and Auton (2015)), the appraisal of any work characteristic as a demand or resource is quite subjective.
 The literature on the experience of stress explains how such individual differences in appraisal are possible.
-Specifically, the transactional theory of stress and coping states that people cognitively appraise stimuli in their environments on a continuous basis (Lazarus \& Folkman, 1984).
+Specifically, the transactional theory of stress and coping states that people cognitively appraise stimuli in their environments on a continuous basis (Lazarus and Folkman (1984)).
 During this process, meaning is assigned to stimuli.
 If the above employee appraised the upcoming speech as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping (e.g., attempting to decline, asking for help in writing the speech).
-From that point, the cycle of appraisal continues based on the action to cope with the stressor (Lazarus \& Folkman, 1984).
+From that point, the cycle of appraisal continues based on the action to cope with the stressor (Lazarus and Folkman (1984)).
 
@@
 
-Although the word ``stress'' often connotes something negative, Selye (1936) defined stress generically as a response to change.
+Although the word ``stress'' often connotes something negative,Selye (1936) defined stress generically as a response to change.
 For instance, the example above describes an employee who appraises being nominated to give a speech as a negative stressor.
 However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
-The terms associated with the two different appraisals of the stressor described here are challenge and hindrance demands (Cavanaugh et al., 2000) Specifically, challenge demands promote mastery, personal growth, and future gains.
+The terms associated with the two different appraisals of the stressor described here are challenge and hindrance demands (Cavanaugh, Boswell, Roehling, and Boudreau (2000)) Specifically, challenge demands promote mastery, personal growth, and future gains.
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes (e.g., Cavanaugh et al., 2000).
+Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes (e.g., Cavanaugh, Boswell, Roehling, and Boudreau (2000)).
 We will explore their associations with both positive and negative outcomes in this study.
@@
 To begin, the first logical question is whether employees actually distinguish between challenge and hindrance stressors, and research suggests that they can and do.
-For example, Bakker and Sanz-Vergel (2013) found that perceived work pressure can be classified as a hindrance demand, and emotional demands as a challenge demand.
-Webster et al.~(2011) considered three common workplace demands including workload, role ambiguity, and role conflict.
+For example, A.
+B.
+Bakker and Sanz-Vergel (2013) found that perceived work pressure can be classified as a hindrance demand, and emotional demands as a challenge demand.
+Webster, Beehr, and Love (2011) considered three common workplace demands including workload, role ambiguity, and role conflict.
 Interestingly, they found that while each could be appraised primarily as challenges or hindrances, employees could also simultaneously be perceived as being both a challenge and hindrance.
@@
 Having established that there can be individual differences in the appraisal of demands as challenges or resources, we next turn our attention to their association with organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and well-being.
-For example, Cavanaugh et al.~(2000) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern with job satisfaction and job search behaviors in a sample of managers.
+For example, Cavanaugh, Boswell, Roehling, and Boudreau (2000) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern with job satisfaction and job search behaviors in a sample of managers.
 However, Abbas and Raja (2019) found that challenge and hindrance stressors were both positively related to strain and turnover intentions.
-We also have some evidence that challenge-hinderance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford et al., 2010).
+We also have some evidence that challenge-hinderance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford, LePine, and Rich (2010)).
 The appraisal process also suggests theoretically that the perception of a job characteristic as a challenge or hindrance is a mediator.
 Gerich (2017), for instance, found that employee well-being was, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
-To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, Podsakoff et al.'s (2007) meta-analysis supported the original assertion of Cavanaugh et al.~(2000) such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.
+To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, Podsakoff, LePine, and LePine (2007) meta-analysis supported the original assertion of Cavanaugh, Boswell, Roehling, and Boudreau (2000) such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.
 
@@
 The brief review above provides theoretical and empirical support for the connection between resources and positive organizational outcomes, and between demands and negative outcomes.
-Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement (``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption,'' Schaufeli et al., 2002), workplace stress (``an individual state characterized by a combination of high arousal and displeasure,'' p.~15, Pejtersen et al., 2010) and burnout (``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work,'' p.~197; Kristensen et al., 2005).
+Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement (``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption,'' Schaufeli, Salanova, González-Romá, and Bakker (2002)), workplace stress (``an individual state characterized by a combination of high arousal and displeasure,'' p.~15, Pejtersen, Kristensen, Borg, and Bjorner (2010)) and burnout (``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work,'' p.~197; Kristensen, Borritz, Villadsen, and Christensen (2005)).
 Utilizing the job demands-resources theory, transactional theory of stress, and the challenge-hindrance framework, we propose that the number of job characteristics appraised as ``challenge demands'' (i.e., promote mastery, personal growth, and future gains) would activate a positive state -- that of engagement.
@@
 
-We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (Bakker \& Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001), but from within the unifying framework of O*Net.
+We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (A.
+B.
+Bakker and Demerouti (2017); A.
+Bakker, Demerouti, and Schaufeli (2003); Demerouti, Bakker, Nachreiner, and Schaufeli (2001)), but from within the unifying framework of O*Net.
 Here, we focus on the relationship between O*Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S.
@@
 Of those,112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021).
-Additional screening using four embedded attention checks resulted in the retention of respondents.
+Additional screening using four embedded attention checks resulted in the retention of 568 respondents.
 A total of 13.57\% had been in their job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.
@@
 \begin{quote}
-\emph{Stress}. Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Obtained alpha was .85 in this sample.
+\emph{Stress}. Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al. (2019)). Obtained alpha was .85 in this sample.
 \end{quote}
@@
 \begin{quote}
-\emph{Burnout}. Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Alpha was 0.85 in this sample.
+\emph{Burnout}. Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al. (2019)). Alpha was 0.85 in this sample.
 \end{quote}
@@
 \emph{Engagement}.
-The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample α's of 0.68 (Absorption) and 0.80 (Vigor), and 0.90 (Dedication).
-For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).
+The 18-item engagement measure was recently developed (Russell, Ossorio Duffoo, Garcia Prieto Palacios Roji, and Kulas (2022)), with the authors specifying three subscales which yielded current sample α's of 0.68 (absorption) and 0.80 (vigor), and 0.90 (dedication).
+For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, alpha = 0.91).
 \end{quote}
@@
 
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:correlation_table}Focal variable correlations (counts data).}
+
+\begin{tabular}{llllllll}
+\toprule
+ & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
+\midrule
+1. resource & - &  &  &  &  & 36.02 & 13.26\\
+2. hindrance & .23*** & - &  &  &  & 13.09 & 13.62\\
+3. challenge & .86*** & .22*** & - &  &  & 35.64 & 13.63\\
+4. burnout & .05 & .04 & .07 & - &  & 3.04 & 0.87\\
+5. stress & .06 & .09* & .08 & .70*** & - & 2.59 & 0.97\\
+6. engagement & .34*** & .01 & .31*** & -.35*** & -.30*** & 4.04 & 0.83\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:regression_table_eng}Regression Predicting Engagement.}
+
+\begin{tabular}{lllll}
+\toprule
+Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(564)$} & \multicolumn{1}{c}{$p$}\\
+\midrule
+Intercept & 3.28 & {}[3.09, 3.47] & 33.93 & < .001\\
+Hindrance & 0.00 & {}[-0.01, 0.00] & -1.80 & .072\\
+Challenge & 0.00 & {}[-0.01, 0.01] & 0.88 & .378\\
+Resource & 0.02 & {}[0.01, 0.03] & 3.84 & < .001\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:regression_table_str}Regression Predicting Stress.}
+
+\begin{tabular}{lllll}
+\toprule
+Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(564)$} & \multicolumn{1}{c}{$p$}\\
+\midrule
+Intercept & 2.38 & {}[2.15, 2.62] & 19.80 & < .001\\
+Hindrance & 0.01 & {}[0.00, 0.01] & 1.82 & .070\\
+Challenge & 0.01 & {}[0.00, 0.02] & 1.43 & .152\\
+Resource & 0.00 & {}[-0.02, 0.01] & -0.77 & .440\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:regression_table_bur}Regression Predicting Burnout.}
+
+\begin{tabular}{lllll}
+\toprule
+Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(564)$} & \multicolumn{1}{c}{$p$}\\
+\midrule
+Intercept & 2.90 & {}[2.68, 3.11] & 26.89 & < .001\\
+Hindrance & 0.00 & {}[0.00, 0.01] & 0.67 & .502\\
+Challenge & 0.01 & {}[0.00, 0.02] & 1.19 & .233\\
+Resource & 0.00 & {}[-0.01, 0.01] & -0.52 & .601\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
 \hypertarget{results}{%
@@
 
-We used R (Version 4.0.3; R Core Team, 2020) and the R-packages careless (Version 1.1.3; Yentes \& Wilhelm, 2021), labourR (Version 1.0.0; Kouretsis et al., 2020), papaja (Version 0.1.0.9997; Aust \& Barth, 2020), and tinylabels (Barth, 2021) for all analyses.
+We used R (Version 4.0.3; (\textbf{Manual?})) and the R-packages careless (Version 1.1.3; Yentes \& Wilhelm, 2021), labourR (Version 1.0.0; Kouretsis et al., 2020), papaja (Version 0.1.0.9997; Aust \& Barth, 2020), and tinylabels (Barth, 2021) for all analyses.
 Our analyses are presented by characteristics of work that are rated in terms of being resources, challenge demands, and hindrance demands.
 Pearson correlation coefficients between characteristics classified as resources, challenges, and hindrances were obtained to investigate the associations among these characteristics.
-Correlations, means and standard deviations among all study variables are presented in Table 1.
+Correlations, means and standard deviations among all study variables are presented in Table \ref{tab:correlation_table}.
 Results reveal a positive association between resources and engagement (\emph{r} = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively).
@@
 To further explore H1-H3, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
-First, regarding engagement (F(3, 564) = 26.41, p \textless{} .001), the total resources (beta = ??) was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table 2).
-Next, stress was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 2.47, \emph{p} = .060 (see Table 3).
+First, regarding engagement (F(3, 564) = 26.41, p \textless{} .001), the total resources was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table \ref{tab:regression_table_eng}).
+Next, stress was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 2.47, \emph{p} = .060 (see Table \ref{tab:regression_table_str}).
 Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 1.10, \emph{p} = .349.
-See Table 4.
-
-\begin{verbatim}
-##              resource   hindrance  challenge     burnout      stress
-## resource   1.00000000 0.225550803 0.86225195  0.04841544  0.05583466
-## hindrance  0.22555080 1.000000000 0.22047517  0.04101639  0.08980526
-## challenge  0.86225195 0.220475168 1.00000000  0.06790884  0.08057171
-## burnout    0.04841544 0.041016388 0.06790884  1.00000000  0.69654076
-## stress     0.05583466 0.089805265 0.08057171  0.69654076  1.00000000
-## engagement 0.34225837 0.009629535 0.31087164 -0.35496125 -0.29534556
-##              engagement
-## resource    0.342258369
-## hindrance   0.009629535
-## challenge   0.310871641
-## burnout    -0.354961254
-## stress     -0.295345559
-## engagement  1.000000000
-\end{verbatim}
+See Table \ref{tab:regression_table_bur}.
 
@@
 
+\newpage
+
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-abbas2019challenge}{}%
+Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.
+
+\leavevmode\hypertarget{ref-bakker2014job}{}%
+Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
+
+\leavevmode\hypertarget{ref-bakker2017job}{}%
+Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
+
+\leavevmode\hypertarget{ref-bakker2007job}{}%
+Bakker, A.
+B., Hakanen, J.
+J., Demerouti, E., \& Xanthopoulou, D.
+(2007).
+Job resources boost work engagement, particularly when job demands are high.
+\emph{Journal of Educational Psychology}, \emph{99}(2), 274.
+
+\leavevmode\hypertarget{ref-bakker2013weekly}{}%
+Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
+
+\leavevmode\hypertarget{ref-bakker2003dual}{}%
+Bakker, A., Demerouti, E., \& Schaufeli, W.
+(2003).
+Dual processes at work in a call centre: An application of the job demands--resources model.
+\emph{European Journal of Work and Organizational Psychology}, \emph{12}(4), 393--417.
+
+\leavevmode\hypertarget{ref-burr_third_2019}{}%
+Burr, H., Berthelsen, H., Moncada, S., Nübling, M., Dupret, E., Demiral, Y., \ldots{} Pohrt, A.
+(2019).
+The {Third} {Version} of the {Copenhagen} {Psychosocial} {Questionnaire}.
+\emph{Safety and Health at Work}, \emph{10}(4), 482--503.
+\url{https://doi.org/10.1016/j.shaw.2019.10.002}
+
+\leavevmode\hypertarget{ref-cavanaugh2000empirical}{}%
+Cavanaugh, M.
+A., Boswell, W.
+R., Roehling, M.
+V., \& Boudreau, J.
+W.
+(2000).
+An empirical examination of self-reported work stress among US managers.
+\emph{Journal of Applied Psychology}, \emph{85}(1), 65.
+
+\leavevmode\hypertarget{ref-crawford2010linking}{}%
+Crawford, E.
+R., LePine, J.
+A., \& Rich, B.
+L.
+(2010).
+Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test.
+\emph{Journal of Applied Psychology}, \emph{95}(5), 834.
+
+\leavevmode\hypertarget{ref-demerouti2001job}{}%
+Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
+
+\leavevmode\hypertarget{ref-gerich2017relevance}{}%
+Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
+
+\leavevmode\hypertarget{ref-kristensen2005copenhagen}{}%
+Kristensen, T. S., Borritz, M., Villadsen, E., \& Christensen, K. B. (2005). The copenhagen burnout inventory: A new tool for the assessment of burnout. \emph{Work \& Stress}, \emph{19}(3), 192--207.
+
+\leavevmode\hypertarget{ref-lazarus1984stress}{}%
+Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
+
+\leavevmode\hypertarget{ref-pejtersen2010second}{}%
+Pejtersen, J.
+H., Kristensen, T.
+S., Borg, V., \& Bjorner, J.
+B.
+(2010).
+The second version of the copenhagen psychosocial questionnaire.
+\emph{Scandinavian Journal of Public Health}, \emph{38}(3\_suppl), 8--24.
+
+\leavevmode\hypertarget{ref-podsakoff2007differential}{}%
+Podsakoff, N.
+P., LePine, J.
+A., \& LePine, M.
+A.
+(2007).
+Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis.
+\emph{Journal of Applied Psychology}, \emph{92}(2), 438.
+
+\leavevmode\hypertarget{ref-engage_2022}{}%
+Russell, M., Ossorio Duffoo, C., Garcia Prieto Palacios Roji, R., \& Kulas, J. (2022). Development of an intentional bifactor measure of engagement. \emph{The seattle edition of SIOP}, 1--14. SIOP.
+
+\leavevmode\hypertarget{ref-schaufeli2002measurement}{}%
+Schaufeli, W.
+B., Salanova, M., González-Romá, V., \& Bakker, A.
+B.
+(2002).
+The measurement of engagement and burnout: A two sample confirmatory factor analytic approach.
+\emph{Journal of Happiness Studies}, \emph{3}(1), 71--92.
+
+\leavevmode\hypertarget{ref-searle2015merits}{}%
+Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.
+
+\leavevmode\hypertarget{ref-selye1936syndrome}{}%
+Selye, H. (1936). A syndrome produced by diverse nocuous agents. \emph{Nature}, \emph{138}(3479), 32--32.
+
+\leavevmode\hypertarget{ref-webster2011extending}{}%
+Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.
+
+\end{CSLReferences}
+
+\endgroup
+
 \end{document}

### 2022-10-03 SIOP2023/Counts/convergence.Rmd
intro stealing

--- 2022-10-01 SIOP2023/Counts/Submission_ResourceCount.Rmd
@@
 ---
-title             : "Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?"
-shorttitle        : "O*Net JDR"
+title             : "Demanding resources: Similarity of perceptions for challenge and resource characteristics"
+shorttitle        : "Demanding Resources"
 
@@
 authornote: |
+  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+
+  Enter author note here.
 
@@
   The relationships among sum of perceived job resources, challenge- and hindrance demands and outcomes of organizational outcomes of engagement, stress, and burnout are explored.
-568 workers rated O\*Net job characteristics in terms of relevance and perceptions as challenges, hindrances and resources.
+568 workers rated O*Net job characteristics in terms of relevance and perceptions as challenges, hindrances and resources.
 The findings are generally aligned with the job demands resource theory regarding associations between perceived resources, demands, and organizational outcomes of engagement, stress, and burnout.
@@
 
+csl               : "apa7.csl"
 classoption       : "man"
@@
 knitr::opts_chunk$set(cache.extra = knitr::rand_seed, echo=FALSE, warning=FALSE, message=FALSE)
+
 #knitr::opts_knit$set(root.dir=normalizePath('../'))
+
 knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
-papaja::r_refs("r-references.bib")
+
+library(papaja)
+
+#r_refs("r-references.bib")
+knitr::write_bib("r-references.bib")
 
@@
 
-> *Hypothesis 1a-1c*: Total number of resources are positively associated with engagement (1a), and negatively associated with stress (1b) and burnout (1c).
+	 In addition to exploring associations with our outcomes, we also sought to explore whether challenges are perceived as distinct from resources.
+Given the definitions of each (i.e.,  aspect of one’s job that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development [resource] vs.
+aspect of one’s job that can promote mastery, personal growth, or future gains [challenge]), we propose respondents may consider them both in the realm of a resource.
 
-> *Hypothesis 2a-2c*: Total number of  challenge demands are positively associated with engagement (2a), and negatively associated with stress (2b) and burnout (2c).
+*Hypothesis 4*: Characteristics perceived as challenges are also viewed as resources.
 
-> *Hypothesis 3a-3c*: Total number of hindrance demands are negatively associated with engagement (3a), and positively associated with stress (3b) and burnout (3c).
+	In addition to the above predictions, we consider, in an exploratory fashion, whether or not the pattern of correlations is similar across different job classifications.
+We expect to see the relationships to emerge similarly regardless of one’s type of work.
+For example, we expect that across jobs, total hindrance demands would be negatively related to engagement.
 
@@
 
-  We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (@bakker2017job; @bakker2003dual; @demerouti2001job), but from within the unifying framework of O\*Net.
-Here, we focus on the relationship between O\*Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S.
+  We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (Bakker & Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001), but from within the unifying framework of O*Net.
+Here, we focus on the relationship between O*Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S.
 workforce representative sample.
@@
 Gender was captured via a free-field gender identity category, although the sample predominantly self-identified as female (52.58%) or male (46.83%).
-
-## Materials
+Jobs were classified into the International Standard Classification of Occupations (ISCO) via the package labourR (Kouretsis et al., 2020).
+Modify or omit?
+*Materials*
 
   Characteristics, Demands, and Resources.
-Our analyses included items within O\*Net’s classifications of “work activity”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context”: 5) Interpersonal Relationships (14 statements), 6) Physical Work Conditions (30 statements)1, and 7) Structural Job Characteristics (13 statements).
-
-  Other than minor grammatical editing (for example, changing “the” to “you”), we retained the O\*Net wording for our item stems.
-We used O\*Net’s response scales, several of which were unique across items, but all shared the same 1 to 5 scale options.
-Subsequent to providing ratings of whether or not an O\*Net characteristic was relevant for the respondent’s work, each respondent who agreed that an element had at least some relevance to their job was also asked to rate that element in terms of, 1) .
+Our analyses included items within O*Net’s classifications of “work activity”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context”: 5) Interpersonal Relationships (14 statements), 6) Physical Work Conditions (30 statements)1, and 7) Structural Job Characteristics (13 statements).
+  Other than minor grammatical editing (for example, changing “the” to “you”), we retained the O*Net wording for our item stems.
+We used O*Net’s response scales, several of which were unique across items, but all shared the same 1 to 5 scale options.
+Subsequent to providing ratings of whether or not an O*Net characteristic was relevant for the respondent’s work, each respondent who agreed that an element had at least some relevance to their job was also asked to rate that element in terms of, 1) .
 .
@@
 this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
-
-> *Stress*. Three items taken from the Copenhagen Psychosocial Questionnaire (@burr_third_2019). Obtained alpha was .85 in this sample.
-
-> *Burnout*. Four items were taken from the Copenhagen Psychosocial Questionnaire (@burr_third_2019). Alpha was 0.85 in this sample.
-
->*Engagement*.
-The 18-item engagement measure was recently developed (@engage_2022), with the authors specifying three subscales which yielded current sample α’s of 0.68 (absorption) and 0.80 (vigor), and 0.90 (dedication).
-For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, alpha = 0.91).
+*Stress*. Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Obtained alpha was .85 in this sample.
+*Burnout*. Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Alpha was 0.85 in this sample.
+*Engagement*.
+The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample α’s of 0.68 (Absorption) and 0.80 (Vigor), and 0.90 (Dedication).
+For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).
 
@@
 
-```{r study1, include=FALSE}
+# Results
+
+We used `r cite_r("r-references.bib")` for all analyses.
+Our analyses are presented by characteristics of work that are rated in terms of being resources, challenge demands, and hindrance demands.
+Pearson correlation coefficients between characteristics classified as resources, challenges, and hindrances were obtained to investigate the associations among these characteristics.
+Correlations, means and standard deviations among all study variables are presented in Table 1.
+Results reveal a positive association between resources and engagement (r = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively).
+Challenge demands were positively associated with engagement (r = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
+Total hindrance stressors were not significantly associated with our outcomes (H3a-H3c).
+To further explore H1-H3, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
+First, regarding engagement (F(3, 564) = 26.41, p < .001), the total resources (beta = ??) was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table 2).
+Next, stress was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 2.47, p = .060 (see Table 3).
+Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 1.10, p = .349.
+See Table 4.
+
+  Our fourth prediction suggested a positive association between total resources and total challenge demands.
+Here, we observed a strong positive relationship, so much so that it could be argued that these two variables are capturing the same thing (r = .86), as fully 74% of the variability was shared.
+
+  In an exploratory fashion, we also considered whether or not the pattern of correlations described above was similar across job types.
+
+```{r study1}
 
@@
 library(careless)
+
 use$careless_long <- longstring(use[18:399])
@@
 
-```{r keeping45, include=FALSE}
+There were `r nrow(data)` retained respondents.
+
+```{r keeping45}
 
@@
 
-```{r correlation_table, eval=TRUE}
+## Resource, Challenge, and Hindrance Associations
 
-r <- corx::corx(data22[,c(405:410)],                    
-                triangle = "lower",
-                stars = c(0.05, 0.01, 0.001),
-                describe = c(`$M$` = mean, `$SD$` = sd))
+```{r percagree, fig.cap="Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance.", fig.height=10}
 
-papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table,
-                  caption = "Focal variable correlations (counts data).",
-                  escape = FALSE)
+rc <- read.csv("resource_challenge.csv")
+rh <- read.csv("resource_hind.csv")
+ch <- read.csv("hind_challenge.csv")
 
-#cor(data[405:410], use="all.obs")   ## something to be told with resources and challenges
+rc$type <- "Resource-Challenge"
+rh$type <- "Resource-Hindrance"
+ch$type <- "Challenge-Hindrance"
+
+forgraph <- rbind(rc,rh,ch)
+
+library(ggplot2)
+
+#ggplot(forgraph, aes(x = mean, fill = type)) +
+#  geom_density(alpha = .3) +
+#  xlab("Percent Agreement") + labs(fill = "Att/Engage\nInteraction")
+
+p <- ggplot(forgraph, aes(x = mean)) + geom_histogram()
+p + facet_wrap(~type, nrow=3)
+
+## lotsa variance in resource-challenge agreement. Next look for either content (O*Net category) or contextual (job) moderator
 
@@
 
-```{r regressions, include=FALSE}
+Figure \@ref(fig:percagree) shows that there was not much mutual agreement regarding characteristics viewed as both hindrances and resources ($\bar{X}$ = `r round(mean(rh$mean, na.rm=TRUE),2)`) or as challenges and hindrances
+($\bar{X}$ = `r round(mean(ch$mean, na.rm=TRUE),2)`).
+Alternatively, whether a characteristic was viewed as both a resource and a challenge exhibited greater consistency although also had quite a bit of variability ($\bar{X}$ = `r round(mean(rc$mean, na.rm=TRUE),2)`, *sd* = `r round(sd(rc$mean, na.rm=TRUE),2)`).
 
-eng <- lm(engagement ~ hindrance + challenge + resource, data22)
-bur <- lm(burnout ~ hindrance + challenge + resource, data22)
-str <- lm(stress ~ hindrance + challenge + resource, data22)
+```{r recchall, fig.cap="Resource and challenge agreement across ONet characteristic groupings (e.g., scales).", fig.height=10}
 
-summary(eng)
-summary(bur)
-summary(str)
+rc$scale <- c(rep("Structural",10), rep("Physical", 20), rep("Interpersonal",13), rep("Information Input", 5), rep("Mental Processes", 10), rep("Work Output", 9), rep("Interact with Others", 17))
+
+ggplot(rc, aes(x=mean)) + geom_histogram() + facet_wrap(~scale, nrow=7)
+
+#ggplot(rc, aes(x = mean, fill = scale)) +
+#  geom_density(alpha = .3) +
+#  xlab("Percent Agreement") + labs(fill = "ONET grouping")
 
@@
 
-```{r regression_table_eng}
-library(papaja)
-apa_lm <- apa_print(eng)
-apa_table(
-  apa_lm$table
-  , caption = "Regression Predicting Engagement."
-)
+Figure \@ref(fig:recchall) explores the possibility of moderation by *type of characteristic rated* for the resource-challenge convergence.
+We categorized each characteristic by its ONet "scale" (one of seven), and the graph shows consistency across certain characteristics (for example, ) and non-convergence across other *types* of characteristics (for example, "Physical" characteristics).
+
+```{r anova}
+
+## Repeated measures ANOVA for resource_challenge
+
+anova <- data[,c(495:578)]
+
+anova$Structural <- rowSums(anova[1:10], na.rm=TRUE)
+anova$Physical <- rowSums(anova[11:30], na.rm=TRUE)
+anova$Interpersonal <- rowSums(anova[31:43], na.rm=TRUE)
+anova$Information <- rowSums(anova[44:48], na.rm=TRUE)
+anova$Mental <- rowSums(anova[49:58], na.rm=TRUE)
+anova$Output <- rowSums(anova[59:67], na.rm=TRUE)
+anova$Interact <- rowSums(anova[68:84], na.rm=TRUE)
+
+library(tidyr)
+
+anova <- cbind(person = 1:nrow(anova), anova)  ## creating person identifier for ANOVA
+
+analysis <- gather(anova, scale, value, Structural:Interact)
+
+repmeas <- aov(value ~ factor(scale) + Error(factor(person)), data=analysis)
+
 ```
 
-```{r regression_table_str}
-library(papaja)
-apa_lm <- apa_print(str)
-apa_table(
-  apa_lm$table
-  , caption = "Regression Predicting Stress."
-)
-```
-
-```{r regression_table_bur}
-library(papaja)
-apa_lm <- apa_print(bur)
-apa_table(
-  apa_lm$table
-  , caption = "Regression Predicting Burnout."
-)
-```
-
-# Results
-
-  We used R (Version 4.0.3; @R-base) and the R-packages careless (Version 1.1.3; Yentes & Wilhelm, 2021), labourR (Version 1.0.0; Kouretsis et al., 2020), papaja (Version 0.1.0.9997; Aust & Barth, 2020), and tinylabels (Barth, 2021) for all analyses.
-Our analyses are presented by characteristics of work that are rated in terms of being resources, challenge demands, and hindrance demands.
-Pearson correlation coefficients between characteristics classified as resources, challenges, and hindrances were obtained to investigate the associations among these characteristics.
-  Correlations, means and standard deviations among all study variables are presented in Table \ref{tab:correlation_table}.
-Results reveal a positive association between resources and engagement (*r* = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively).
-Challenge demands were positively associated with engagement (*r* = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
-Total hindrance stressors were not significantly associated with our outcomes (H3a-H3c).
-To further explore H1-H3, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
-First, regarding engagement (F(3, 564) = 26.41, p < .001), the total resources was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table \ref{tab:regression_table_eng}).
-Next, stress was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 2.47, *p* = .060 (see Table \ref{tab:regression_table_str}).
-Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 1.10, *p* = .349.
-See Table \ref{tab:regression_table_bur}.
+F ratio from a repeated measures ANOVA is $F_(6, 3,402)$ = 613.5, *p* < .001 (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001.
 
@@
 The major goal of this paper was to further explore the relationships among total perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout.
+Additionally, we considered whether resources and challenge demands were perceived as distinct, and finally, whether the patterns were similar across job categories/types of work.
 The results suggest a positive relationship between both resources and engagement (H1a), and challenge demands and engagement (H2a).
-Employers would benefit from understanding that at least the perception of having “more” resources and more challenge demands in a job is highly associated with reported engagement.
+Employers would benefit from understanding that at leas the perception of having “more” resources and more challenge demands in a job is highly associated with reported engagement.
 While not a causal relationship, it points to the potential value of these kinds of employee support nonetheless.
@@
 It is possible that rather than volume, categorically some demands are more related to these outcomes than others.
+ Further, total resources were highly associated challenge demands (supporting H4).
+We could even argue, given the magnitude of the correlation, that they are capturing the same thing (74% overlap with a correlation of .86).
+Need to also talk about our exploratory findings regarding patterns across job type
 
@@
 As with any piece of research, the process and results have limitations, but also provide a variety of additional directions to pursue in the future.
-First, while a strength of this project, arguably, is the use of O\*Net items, practical considerations limited the number of job characteristics we could include in our survey.
-Future study could consider additional or other O\*Net items.
+First, while a strength of this project, arguably, is the use of O*Net items, practical considerations limited the number of job characteristics we could include in our survey.
+Future study could consider additional or other O*Net items.
 We conceptualized resources and demands in terms of perceived total amounts.
@@
 
-\newpage
-
 # References
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id="refs" custom-style="Bibliography"></div>
-\endgroup

### 2022-10-03 SIOP2023/Counts/Submission_ResourceCount.Rmd
Udpated references.

@@
 
-bibliography      : ["r-references.bib", "jdr.bib", "jobdemands_resources_bibtex.bib"]
+bibliography      : ["jobdemands_resources_bibtex.bib"]
 
@@
 
-  A plethora of research applying the job demands-resources model (@demerouti2001job) and job demands-resources theory (@bakker2017job) underscore the importance of work characteristics on the experience of motivation and strain.
+  A plethora of research applying the job demands-resources model [@demerouti2001job] and job demands-resources theory [@bakker2017job] underscore the importance of work characteristics on the experience of motivation and strain.
 However, much of our existing research on this topic assumes that certain characteristics are resources and others are generally considered demands.
@@
 
-  The theoretical foundation for this study is the job demands-resources theory (@demerouti2001job).
+  The theoretical foundation for this study is the job demands-resources theory [@demerouti2001job].
 Using this theory, we can model both work environment and job characteristics via job resources and demands.
-Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (@demerouti2001job).
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure; @demerouti2001job).
+Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
+In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [e.g., high work pressure; @demerouti2001job].
 
-  The perception of a characteristic of one’s job as a resource or demand activates one of two unique processes: either health impairment or motivation @bakker2014job.
-Demanding job characteristics are frequently associated with negative outcomes (e.g., health impairment process; @bakker2003dual), whereas job characteristics considered resources have been associated with positive organizational outcomes like engagement and motivation (@bakker2007job).
+  The perception of a characteristic of one’s job as a resource or demand activates one of two unique processes: either health impairment or motivation [@bakker2014job].
+Demanding job characteristics are frequently associated with negative outcomes [e.g., health impairment process; @bakker2003dual], whereas job characteristics considered resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job].
 
@@
   The above description speaks to one of two distinct processes being activated, presumably based on one’s assessment of how a work characteristics makes them feel (e.g., consider the different reactions employees may have to being nominated to give a speech at an upcoming company event).
-Thus, although some research on job demands in particular is based on a priori classifications of demands (@searle2015merits), the appraisal of any work characteristic as a demand or resource is quite subjective.
+Thus, although some research on job demands in particular is based on a priori classifications of demands [@searle2015merits], the appraisal of any work characteristic as a demand or resource is quite subjective.
 The literature on the experience of stress explains how such individual differences in appraisal are possible.
-Specifically, the transactional theory of stress and coping states that people cognitively appraise stimuli in their environments on a continuous basis (@lazarus1984stress).
+Specifically, the transactional theory of stress and coping states that people cognitively appraise stimuli in their environments on a continuous basis [@lazarus1984stress].
 During this process, meaning is assigned to stimuli.
 If the above employee appraised the upcoming speech as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping (e.g., attempting to decline, asking for help in writing the speech).
-From that point, the cycle of appraisal continues based on the action to cope with the stressor (@lazarus1984stress).
+From that point, the cycle of appraisal continues based on the action to cope with the stressor [@lazarus1984stress].
 
@@
 However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
-The terms associated with the two different appraisals of the stressor described here are challenge and hindrance demands (@cavanaugh2000empirical) Specifically, challenge demands promote mastery, personal growth, and future gains.
+The terms associated with the two different appraisals of the stressor described here are challenge and hindrance demands [@cavanaugh2000empirical] Specifically, challenge demands promote mastery, personal growth, and future gains.
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes (e.g., @cavanaugh2000empirical).
+Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes [e.g., @cavanaugh2000empirical].
 We will explore their associations with both positive and negative outcomes in this study.
@@
 However, @abbas2019challenge found that challenge and hindrance stressors were both positively related to strain and turnover intentions.
-We also have some evidence that challenge-hinderance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (@crawford2010linking).
+We also have some evidence that challenge-hinderance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement [@crawford2010linking].
 The appraisal process also suggests theoretically that the perception of a job characteristic as a challenge or hindrance is a mediator.
@@
   The brief review above provides theoretical and empirical support for the connection between resources and positive organizational outcomes, and between demands and negative outcomes.
-Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement (“a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption”, @schaufeli2002measurement), workplace stress (“an individual state characterized by a combination of high arousal and displeasure”, p.
-15, @pejtersen2010second) and burnout (“the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work”, p.
-197; @kristensen2005copenhagen).
+Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement [“a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption”, @schaufeli2002measurement], workplace stress [“an individual state characterized by a combination of high arousal and displeasure”, p.
+15, @pejtersen2010second] and burnout [“the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work”, p.
+197; @kristensen2005copenhagen].
 Utilizing the job demands-resources theory, transactional theory of stress, and the challenge-hindrance framework, we propose that the number of job characteristics appraised as “challenge demands” (i.e., promote mastery, personal growth, and future gains) would activate a positive state – that of engagement.
@@
 
-  We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (@bakker2017job; @bakker2003dual; @demerouti2001job), but from within the unifying framework of O\*Net.
+  We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model [@bakker2017job; @bakker2003dual; @demerouti2001job], but from within the unifying framework of O\*Net.
 Here, we focus on the relationship between O\*Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S.

### 2022-10-03 SIOP2023/Counts/Submission_ResourceCount.tex
Udpated references.

@@
 
-A plethora of research applying the job demands-resources model (Demerouti, Bakker, Nachreiner, and Schaufeli (2001)) and job demands-resources theory (A.
+A plethora of research applying the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (A.
 B.
-Bakker and Demerouti (2017)) underscore the importance of work characteristics on the experience of motivation and strain.
+Bakker \& Demerouti, 2017) underscore the importance of work characteristics on the experience of motivation and strain.
 However, much of our existing research on this topic assumes that certain characteristics are resources and others are generally considered demands.
@@
 
-The theoretical foundation for this study is the job demands-resources theory (Demerouti, Bakker, Nachreiner, and Schaufeli (2001)).
+The theoretical foundation for this study is the job demands-resources theory (Demerouti et al., 2001).
 Using this theory, we can model both work environment and job characteristics via job resources and demands.
-Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti, Bakker, Nachreiner, and Schaufeli (2001)).
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure; Demerouti, Bakker, Nachreiner, and Schaufeli (2001)).
+Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
+In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain {[}e.g., high work pressure; Demerouti et al.
+(2001){]}.
 
-The perception of a characteristic of one's job as a resource or demand activates one of two unique processes: either health impairment or motivation A.
+The perception of a characteristic of one's job as a resource or demand activates one of two unique processes: either health impairment or motivation (A.
 B.
-Bakker and Demerouti (2014).
-Demanding job characteristics are frequently associated with negative outcomes (e.g., health impairment process; A.
-Bakker, Demerouti, and Schaufeli (2003)), whereas job characteristics considered resources have been associated with positive organizational outcomes like engagement and motivation (A.
+Bakker \& Demerouti, 2014).
+Demanding job characteristics are frequently associated with negative outcomes {[}e.g., health impairment process; A.
+Bakker et al.
+(2003){]}, whereas job characteristics considered resources have been associated with positive organizational outcomes like engagement and motivation (A.
 B.
-Bakker, Hakanen, Demerouti, and Xanthopoulou (2007)).
+Bakker et al., 2007).
 
@@
 The above description speaks to one of two distinct processes being activated, presumably based on one's assessment of how a work characteristics makes them feel (e.g., consider the different reactions employees may have to being nominated to give a speech at an upcoming company event).
-Thus, although some research on job demands in particular is based on a priori classifications of demands (Searle and Auton (2015)), the appraisal of any work characteristic as a demand or resource is quite subjective.
+Thus, although some research on job demands in particular is based on a priori classifications of demands (Searle \& Auton, 2015), the appraisal of any work characteristic as a demand or resource is quite subjective.
 The literature on the experience of stress explains how such individual differences in appraisal are possible.
-Specifically, the transactional theory of stress and coping states that people cognitively appraise stimuli in their environments on a continuous basis (Lazarus and Folkman (1984)).
+Specifically, the transactional theory of stress and coping states that people cognitively appraise stimuli in their environments on a continuous basis (Lazarus \& Folkman, 1984).
 During this process, meaning is assigned to stimuli.
 If the above employee appraised the upcoming speech as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping (e.g., attempting to decline, asking for help in writing the speech).
-From that point, the cycle of appraisal continues based on the action to cope with the stressor (Lazarus and Folkman (1984)).
+From that point, the cycle of appraisal continues based on the action to cope with the stressor (Lazarus \& Folkman, 1984).
 
@@
 However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
-The terms associated with the two different appraisals of the stressor described here are challenge and hindrance demands (Cavanaugh, Boswell, Roehling, and Boudreau (2000)) Specifically, challenge demands promote mastery, personal growth, and future gains.
+The terms associated with the two different appraisals of the stressor described here are challenge and hindrance demands (Cavanaugh et al., 2000) Specifically, challenge demands promote mastery, personal growth, and future gains.
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes (e.g., Cavanaugh, Boswell, Roehling, and Boudreau (2000)).
+Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes (e.g., Cavanaugh et al., 2000).
 We will explore their associations with both positive and negative outcomes in this study.
@@
 Bakker and Sanz-Vergel (2013) found that perceived work pressure can be classified as a hindrance demand, and emotional demands as a challenge demand.
-Webster, Beehr, and Love (2011) considered three common workplace demands including workload, role ambiguity, and role conflict.
+Webster et al.
+(2011) considered three common workplace demands including workload, role ambiguity, and role conflict.
 Interestingly, they found that while each could be appraised primarily as challenges or hindrances, employees could also simultaneously be perceived as being both a challenge and hindrance.
@@
 Having established that there can be individual differences in the appraisal of demands as challenges or resources, we next turn our attention to their association with organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and well-being.
-For example, Cavanaugh, Boswell, Roehling, and Boudreau (2000) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern with job satisfaction and job search behaviors in a sample of managers.
+For example, Cavanaugh et al.
+(2000) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern with job satisfaction and job search behaviors in a sample of managers.
 However, Abbas and Raja (2019) found that challenge and hindrance stressors were both positively related to strain and turnover intentions.
-We also have some evidence that challenge-hinderance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford, LePine, and Rich (2010)).
+We also have some evidence that challenge-hinderance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford et al., 2010).
 The appraisal process also suggests theoretically that the perception of a job characteristic as a challenge or hindrance is a mediator.
 Gerich (2017), for instance, found that employee well-being was, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
-To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, Podsakoff, LePine, and LePine (2007) meta-analysis supported the original assertion of Cavanaugh, Boswell, Roehling, and Boudreau (2000) such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.
+To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, Podsakoff et al.
+(2007) meta-analysis supported the original assertion of Cavanaugh et al.
+(2000) such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.
 
@@
 The brief review above provides theoretical and empirical support for the connection between resources and positive organizational outcomes, and between demands and negative outcomes.
-Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement (``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption,'' Schaufeli, Salanova, González-Romá, and Bakker (2002)), workplace stress (``an individual state characterized by a combination of high arousal and displeasure,'' p.~15, Pejtersen, Kristensen, Borg, and Bjorner (2010)) and burnout (``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work,'' p.~197; Kristensen, Borritz, Villadsen, and Christensen (2005)).
+Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement ({``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption,''} Schaufeli et al., 2002), workplace stress ({``an individual state characterized by a combination of high arousal and displeasure,''} p.~15, Pejtersen et al., 2010) and burnout {[}``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work,'' p.~197; Kristensen et al.
+(2005){]}.
 Utilizing the job demands-resources theory, transactional theory of stress, and the challenge-hindrance framework, we propose that the number of job characteristics appraised as ``challenge demands'' (i.e., promote mastery, personal growth, and future gains) would activate a positive state -- that of engagement.
@@
 We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (A.
+Bakker et al., 2003; A.
 B.
-Bakker and Demerouti (2017); A.
-Bakker, Demerouti, and Schaufeli (2003); Demerouti, Bakker, Nachreiner, and Schaufeli (2001)), but from within the unifying framework of O*Net.
+Bakker \& Demerouti, 2017; Demerouti et al., 2001), but from within the unifying framework of O*Net.
 Here, we focus on the relationship between O*Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S.
@@
 \emph{Engagement}.
-The 18-item engagement measure was recently developed (Russell, Ossorio Duffoo, Garcia Prieto Palacios Roji, and Kulas (2022)), with the authors specifying three subscales which yielded current sample α's of 0.68 (absorption) and 0.80 (vigor), and 0.90 (dedication).
+The 18-item engagement measure was recently developed (Russell et al.
+(2022)), with the authors specifying three subscales which yielded current sample α's of 0.68 (absorption) and 0.80 (vigor), and 0.90 (dedication).
 For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, alpha = 0.91).
@@
 
-We used R (Version 4.0.3; (\textbf{Manual?})) and the R-packages careless (Version 1.1.3; Yentes \& Wilhelm, 2021), labourR (Version 1.0.0; Kouretsis et al., 2020), papaja (Version 0.1.0.9997; Aust \& Barth, 2020), and tinylabels (Barth, 2021) for all analyses.
+We used R (Version 4.0.3; R Core Team (2022)) and the R-packages careless (Version 1.1.3; Yentes \& Wilhelm, 2021), labourR (Version 1.0.0; Kouretsis et al., 2020), papaja (Version 0.1.0.9997; Aust \& Barth, 2020), and tinylabels (Barth, 2021) for all analyses.
 Our analyses are presented by characteristics of work that are rated in terms of being resources, challenge demands, and hindrance demands.
@@
 \leavevmode\hypertarget{ref-burr_third_2019}{}%
-Burr, H., Berthelsen, H., Moncada, S., Nübling, M., Dupret, E., Demiral, Y., \ldots{} Pohrt, A.
+Burr, H., Berthelsen, H., Moncada, S., Nübling, M., Dupret, E., Demiral, Y., Oudyk, J., Kristensen, T.
+S., Llorens, C., Navarro, A., Lincke, H.-J., Bocéréan, C., Sahan, C., Smith, P., \& Pohrt, A.
 (2019).
@@
 
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2022). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
+
 \leavevmode\hypertarget{ref-engage_2022}{}%
-Russell, M., Ossorio Duffoo, C., Garcia Prieto Palacios Roji, R., \& Kulas, J. (2022). Development of an intentional bifactor measure of engagement. \emph{The seattle edition of SIOP}, 1--14. SIOP.
+Russell, M., Ossorio Duffoo, C., Garcia Prieto Palacios Roji, R., \& Kulas, J. (2022). Development of an intentional bifactor measure of engagement. \emph{The Seattle Edition of SIOP}, 1--14.
 

### 2022-10-04 SIOP2023/Counts/convergence.tex

--- 2022-10-03 SIOP2023/Counts/Submission_ResourceCount.tex
@@
 \documentclass[
-  english,
   man]{apa6}
@@
 \usepackage{lmodern}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
 \hypersetup{
-  pdftitle={Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?},
+  pdftitle={Demanding resources: Similarity of perceptions for challenge and resource characteristics},
   pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata Garcia Prieto Palacios Roji3},
@@
 \fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\ifLuaTeX
+\usepackage[bidi=basic]{babel}
+\else
+\usepackage[bidi=default]{babel}
+\fi
+\babelprovide[main,import]{english}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
 % Manuscript styling
@@
 \makeatother
-\shorttitle{O*Net JDR}
+
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
 \keywords{keywords\newline\indent Word count: X}
@@
 \usepackage{csquotes}
-\ifxetex
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
-\title{Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?}
+\title{Demanding resources: Similarity of perceptions for challenge and resource characteristics}
 \author{John Kulas\textsuperscript{1}, Alicia Stachowski\textsuperscript{2}, \& Renata Garcia Prieto Palacios Roji\textsuperscript{3}}
@@
 
+\shorttitle{Demanding Resources}
+
 \authornote{
+
+Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+
+Enter author note here.
 
@@
 
-\abstract{
+\abstract{%
 The relationships among sum of perceived job resources, challenge- and hindrance demands and outcomes of organizational outcomes of engagement, stress, and burnout are explored.
@@
 
-A plethora of research applying the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (A.
+\begin{verbatim}
+## Warning: package 'tinylabels' was built under R version 4.1.3
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in knitr::write_bib("r-references.bib"): package(s) r-references.bib not
+## found
+\end{verbatim}
+
+A plethora of research applying the job demands-resources model (Demerouti et al.
+(2001)) and job demands-resources theory (A.
 B.
-Bakker \& Demerouti, 2017) underscore the importance of work characteristics on the experience of motivation and strain.
+Bakker and Demerouti (2017)) underscore the importance of work characteristics on the experience of motivation and strain.
 However, much of our existing research on this topic assumes that certain characteristics are resources and others are generally considered demands.
@@
 
-The theoretical foundation for this study is the job demands-resources theory (Demerouti et al., 2001).
+The theoretical foundation for this study is the job demands-resources theory (Demerouti et al.
+(2001)).
 Using this theory, we can model both work environment and job characteristics via job resources and demands.
-Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain {[}e.g., high work pressure; Demerouti et al.
-(2001){]}.
+Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al.
+(2001)).
+In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure; Demerouti et al.
+(2001)).
 
-The perception of a characteristic of one's job as a resource or demand activates one of two unique processes: either health impairment or motivation (A.
+The perception of a characteristic of one's job as a resource or demand activates one of two unique processes: either health impairment or motivation A.
 B.
-Bakker \& Demerouti, 2014).
-Demanding job characteristics are frequently associated with negative outcomes {[}e.g., health impairment process; A.
+Bakker and Demerouti (2014).
+Demanding job characteristics are frequently associated with negative outcomes (e.g., health impairment process; A.
 Bakker et al.
-(2003){]}, whereas job characteristics considered resources have been associated with positive organizational outcomes like engagement and motivation (A.
+(2003)), whereas job characteristics considered resources have been associated with positive organizational outcomes like engagement and motivation (A.
 B.
-Bakker et al., 2007).
+Bakker et al.
+(2007)).
 
@@
 However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
-The terms associated with the two different appraisals of the stressor described here are challenge and hindrance demands (Cavanaugh et al., 2000) Specifically, challenge demands promote mastery, personal growth, and future gains.
+The terms associated with the two different appraisals of the stressor described here are challenge and hindrance demands (Cavanaugh et al.
+(2000)) Specifically, challenge demands promote mastery, personal growth, and future gains.
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes (e.g., Cavanaugh et al., 2000).
+Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes (e.g., Cavanaugh et al.
+(2000)).
 We will explore their associations with both positive and negative outcomes in this study.
@@
 However, Abbas and Raja (2019) found that challenge and hindrance stressors were both positively related to strain and turnover intentions.
-We also have some evidence that challenge-hinderance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford et al., 2010).
+We also have some evidence that challenge-hinderance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford et al.
+(2010)).
 The appraisal process also suggests theoretically that the perception of a job characteristic as a challenge or hindrance is a mediator.
@@
 The brief review above provides theoretical and empirical support for the connection between resources and positive organizational outcomes, and between demands and negative outcomes.
-Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement ({``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption,''} Schaufeli et al., 2002), workplace stress ({``an individual state characterized by a combination of high arousal and displeasure,''} p.~15, Pejtersen et al., 2010) and burnout {[}``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work,'' p.~197; Kristensen et al.
-(2005){]}.
+Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement (``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption'', Schaufeli et al.
+(2002)), workplace stress (``an individual state characterized by a combination of high arousal and displeasure'', p.~15, Pejtersen et al.
+(2010)) and burnout (``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work'', p.~197; Kristensen et al.
+(2005)).
 Utilizing the job demands-resources theory, transactional theory of stress, and the challenge-hindrance framework, we propose that the number of job characteristics appraised as ``challenge demands'' (i.e., promote mastery, personal growth, and future gains) would activate a positive state -- that of engagement.
@@
 
-\begin{quote}
-\emph{Hypothesis 1a-1c}: Total number of resources are positively associated with engagement (1a), and negatively associated with stress (1b) and burnout (1c).
-\end{quote}
+\begin{verbatim}
+ In addition to exploring associations with our outcomes, we also sought to explore whether challenges are perceived as distinct from resources.
+Given the definitions of each (i.e.,  aspect of one’s job that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development [resource] vs.
+aspect of one’s job that can promote mastery, personal growth, or future gains [challenge]), we propose respondents may consider them both in the realm of a resource.
 
-\begin{quote}
-\emph{Hypothesis 2a-2c}: Total number of challenge demands are positively associated with engagement (2a), and negatively associated with stress (2b) and burnout (2c).
-\end{quote}
+\end{verbatim}
 
-\begin{quote}
-\emph{Hypothesis 3a-3c}: Total number of hindrance demands are negatively associated with engagement (3a), and positively associated with stress (3b) and burnout (3c).
-\end{quote}
+\emph{Hypothesis 4}: Characteristics perceived as challenges are also viewed as resources.
+
+\begin{verbatim}
+In addition to the above predictions, we consider, in an exploratory fashion, whether or not the pattern of correlations is similar across different job classifications.
+We expect to see the relationships to emerge similarly regardless of one’s type of work.
+For example, we expect that across jobs, total hindrance demands would be negatively related to engagement.
+\end{verbatim}
 
@@
 
-We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (A.
-Bakker et al., 2003; A.
-B.
-Bakker \& Demerouti, 2017; Demerouti et al., 2001), but from within the unifying framework of O*Net.
-Here, we focus on the relationship between O*Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S.
+We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (Bakker \& Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001), but from within the unifying framework of O\emph{Net.
+Here, we focus on the relationship between O}Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S.
 workforce representative sample.
@@
 Gender was captured via a free-field gender identity category, although the sample predominantly self-identified as female (52.58\%) or male (46.83\%).
-
-\hypertarget{materials}{%
-\subsection{Materials}\label{materials}}
+Jobs were classified into the International Standard Classification of Occupations (ISCO) via the package labourR (Kouretsis et al., 2020).
+Modify or omit?
+\emph{Materials}
 
 Characteristics, Demands, and Resources.
-Our analyses included items within O*Net's classifications of ``work activity'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'': 5) Interpersonal Relationships (14 statements), 6) Physical Work Conditions (30 statements)1, and 7) Structural Job Characteristics (13 statements).
-
-Other than minor grammatical editing (for example, changing ``the'' to ``you''), we retained the O*Net wording for our item stems.
-We used O*Net's response scales, several of which were unique across items, but all shared the same 1 to 5 scale options.
-Subsequent to providing ratings of whether or not an O*Net characteristic was relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was also asked to rate that element in terms of, 1) .
+Our analyses included items within O\emph{Net's classifications of ``work activity'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'': 5) Interpersonal Relationships (14 statements), 6) Physical Work Conditions (30 statements)1, and 7) Structural Job Characteristics (13 statements).
+Other than minor grammatical editing (for example, changing ``the'' to ``you''), we retained the O}Net wording for our item stems.
+We used O\emph{Net's response scales, several of which were unique across items, but all shared the same 1 to 5 scale options.
+Subsequent to providing ratings of whether or not an O}Net characteristic was relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was also asked to rate that element in terms of, 1) .
 .
@@
 this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
-
-\begin{quote}
-\emph{Stress}. Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al. (2019)). Obtained alpha was .85 in this sample.
-\end{quote}
-
-\begin{quote}
-\emph{Burnout}. Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al. (2019)). Alpha was 0.85 in this sample.
-\end{quote}
-
-\begin{quote}
+\emph{Stress}. Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Obtained alpha was .85 in this sample.
+\emph{Burnout}. Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Alpha was 0.85 in this sample.
 \emph{Engagement}.
-The 18-item engagement measure was recently developed (Russell et al.
-(2022)), with the authors specifying three subscales which yielded current sample α's of 0.68 (absorption) and 0.80 (vigor), and 0.90 (dedication).
-For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, alpha = 0.91).
-\end{quote}
+The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample α's of 0.68 (Absorption) and 0.80 (Vigor), and 0.90 (Dedication).
+For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).
 
@@
 
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:correlation_table}Focal variable correlations (counts data).}
-
-\begin{tabular}{llllllll}
-\toprule
- & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
-\midrule
-1. resource & - &  &  &  &  & 36.02 & 13.26\\
-2. hindrance & .23*** & - &  &  &  & 13.09 & 13.62\\
-3. challenge & .86*** & .22*** & - &  &  & 35.64 & 13.63\\
-4. burnout & .05 & .04 & .07 & - &  & 3.04 & 0.87\\
-5. stress & .06 & .09* & .08 & .70*** & - & 2.59 & 0.97\\
-6. engagement & .34*** & .01 & .31*** & -.35*** & -.30*** & 4.04 & 0.83\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:regression_table_eng}Regression Predicting Engagement.}
-
-\begin{tabular}{lllll}
-\toprule
-Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(564)$} & \multicolumn{1}{c}{$p$}\\
-\midrule
-Intercept & 3.28 & {}[3.09, 3.47] & 33.93 & < .001\\
-Hindrance & 0.00 & {}[-0.01, 0.00] & -1.80 & .072\\
-Challenge & 0.00 & {}[-0.01, 0.01] & 0.88 & .378\\
-Resource & 0.02 & {}[0.01, 0.03] & 3.84 & < .001\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:regression_table_str}Regression Predicting Stress.}
-
-\begin{tabular}{lllll}
-\toprule
-Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(564)$} & \multicolumn{1}{c}{$p$}\\
-\midrule
-Intercept & 2.38 & {}[2.15, 2.62] & 19.80 & < .001\\
-Hindrance & 0.01 & {}[0.00, 0.01] & 1.82 & .070\\
-Challenge & 0.01 & {}[0.00, 0.02] & 1.43 & .152\\
-Resource & 0.00 & {}[-0.02, 0.01] & -0.77 & .440\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:regression_table_bur}Regression Predicting Burnout.}
-
-\begin{tabular}{lllll}
-\toprule
-Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(564)$} & \multicolumn{1}{c}{$p$}\\
-\midrule
-Intercept & 2.90 & {}[2.68, 3.11] & 26.89 & < .001\\
-Hindrance & 0.00 & {}[0.00, 0.01] & 0.67 & .502\\
-Challenge & 0.01 & {}[0.00, 0.02] & 1.19 & .233\\
-Resource & 0.00 & {}[-0.01, 0.01] & -0.52 & .601\\
-\bottomrule
-\end{tabular}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
 \hypertarget{results}{%
@@
 
-We used R (Version 4.0.3; R Core Team (2022)) and the R-packages careless (Version 1.1.3; Yentes \& Wilhelm, 2021), labourR (Version 1.0.0; Kouretsis et al., 2020), papaja (Version 0.1.0.9997; Aust \& Barth, 2020), and tinylabels (Barth, 2021) for all analyses.
+We used R (Version 4.1.1; R Core Team, 2021) and the R-packages \emph{corrr} (Version 0.4.3; \textbf{R-corrr?}), \emph{lavaan} (Version 0.6.11; \textbf{R-lavaan?}), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2022), \emph{psych} (Version 2.1.9; \textbf{R-psych?}), \emph{tidyr} (Version 1.2.0; \textbf{R-tidyr?}), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all analyses.
 Our analyses are presented by characteristics of work that are rated in terms of being resources, challenge demands, and hindrance demands.
 Pearson correlation coefficients between characteristics classified as resources, challenges, and hindrances were obtained to investigate the associations among these characteristics.
-Correlations, means and standard deviations among all study variables are presented in Table \ref{tab:correlation_table}.
-Results reveal a positive association between resources and engagement (\emph{r} = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively).
-Challenge demands were positively associated with engagement (\emph{r} = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
+Correlations, means and standard deviations among all study variables are presented in Table 1.
+Results reveal a positive association between resources and engagement (r = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively).
+Challenge demands were positively associated with engagement (r = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
 Total hindrance stressors were not significantly associated with our outcomes (H3a-H3c).
 To further explore H1-H3, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
-First, regarding engagement (F(3, 564) = 26.41, p \textless{} .001), the total resources was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table \ref{tab:regression_table_eng}).
-Next, stress was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 2.47, \emph{p} = .060 (see Table \ref{tab:regression_table_str}).
-Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 1.10, \emph{p} = .349.
-See Table \ref{tab:regression_table_bur}.
+First, regarding engagement (F(3, 564) = 26.41, p \textless{} .001), the total resources (beta = ??) was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table 2).
+Next, stress was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 2.47, p = .060 (see Table 3).
+Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 1.10, p = .349.
+See Table 4.
+
+Our fourth prediction suggested a positive association between total resources and total challenge demands.
+Here, we observed a strong positive relationship, so much so that it could be argued that these two variables are capturing the same thing (r = .86), as fully 74\% of the variability was shared.
+
+In an exploratory fashion, we also considered whether or not the pattern of correlations described above was similar across job types.
+
+There were 568 retained respondents.
+
+\begin{verbatim}
+##              resource   hindrance  challenge     burnout      stress
+## resource   1.00000000 0.225550803 0.86225195  0.04841544  0.05583466
+## hindrance  0.22555080 1.000000000 0.22047517  0.04101639  0.08980526
+## challenge  0.86225195 0.220475168 1.00000000  0.06790884  0.08057171
+## burnout    0.04841544 0.041016388 0.06790884  1.00000000  0.69654076
+## stress     0.05583466 0.089805265 0.08057171  0.69654076  1.00000000
+## engagement 0.34225837 0.009629535 0.31087164 -0.35496125 -0.29534556
+##              engagement
+## resource    0.342258369
+## hindrance   0.009629535
+## challenge   0.310871641
+## burnout    -0.354961254
+## stress     -0.295345559
+## engagement  1.000000000
+\end{verbatim}
+
+\hypertarget{resource-challenge-and-hindrance-associations}{%
+\subsection{Resource, Challenge, and Hindrance Associations}\label{resource-challenge-and-hindrance-associations}}
+
+\begin{figure}
+\centering
+\includegraphics{convergence_files/figure-latex/percagree-1.pdf}
+\caption{\label{fig:percagree}Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance.}
+\end{figure}
+
+Figure \ref{fig:percagree} shows that there was not much mutual agreement regarding characteristics viewed as both hindrances and resources (\(\bar{X}\) = 0.14) or as challenges and hindrances
+(\(\bar{X}\) = 0.14).
+Alternatively, whether a characteristic was viewed as both a resource and a challenge exhibited greater consistency although also had quite a bit of variability (\(\bar{X}\) = 0.51, \emph{sd} = 0.21).
+
+\begin{figure}
+\centering
+\includegraphics{convergence_files/figure-latex/recchall-1.pdf}
+\caption{\label{fig:recchall}Resource and challenge agreement across ONet characteristic groupings (e.g., scales).}
+\end{figure}
+
+Figure \ref{fig:recchall} explores the possibility of moderation by \emph{type of characteristic rated} for the resource-challenge convergence.
+We categorized each characteristic by its ONet ``scale'' (one of seven), and the graph shows consistency across certain characteristics (for example, ) and non-convergence across other \emph{types} of characteristics (for example, ``Physical'' characteristics).
+
+F ratio from a repeated measures ANOVA is \(F_(6, 3,402)\) = 613.5, \emph{p} \textless{} .001 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001.
 
@@
 The major goal of this paper was to further explore the relationships among total perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout.
+Additionally, we considered whether resources and challenge demands were perceived as distinct, and finally, whether the patterns were similar across job categories/types of work.
 The results suggest a positive relationship between both resources and engagement (H1a), and challenge demands and engagement (H2a).
-Employers would benefit from understanding that at least the perception of having ``more'' resources and more challenge demands in a job is highly associated with reported engagement.
+Employers would benefit from understanding that at leas the perception of having ``more'' resources and more challenge demands in a job is highly associated with reported engagement.
 While not a causal relationship, it points to the potential value of these kinds of employee support nonetheless.
@@
 It is possible that rather than volume, categorically some demands are more related to these outcomes than others.
+Further, total resources were highly associated challenge demands (supporting H4).
+We could even argue, given the magnitude of the correlation, that they are capturing the same thing (74\% overlap with a correlation of .86).
+Need to also talk about our exploratory findings regarding patterns across job type
 
@@
 As with any piece of research, the process and results have limitations, but also provide a variety of additional directions to pursue in the future.
-First, while a strength of this project, arguably, is the use of O*Net items, practical considerations limited the number of job characteristics we could include in our survey.
-Future study could consider additional or other O*Net items.
+First, while a strength of this project, arguably, is the use of O\emph{Net items, practical considerations limited the number of job characteristics we could include in our survey.
+Future study could consider additional or other O}Net items.
 We conceptualized resources and demands in terms of perceived total amounts.
@@
 
-\newpage
-
 \hypertarget{references}{%
-\section{References}\label{references}}
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-abbas2019challenge}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-abbas2019challenge}{}}%
 Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.
 
-\leavevmode\hypertarget{ref-bakker2014job}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
+Aust, F., \& Barth, M. (2022). \emph{Papaja: Prepare american psychological association journal articles with r markdown}. \url{https://github.com/crsh/papaja}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
 Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
 
-\leavevmode\hypertarget{ref-bakker2017job}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
 Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
 
-\leavevmode\hypertarget{ref-bakker2007job}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2007job}{}}%
 Bakker, A.
@@
 
-\leavevmode\hypertarget{ref-burr_third_2019}{}%
-Burr, H., Berthelsen, H., Moncada, S., Nübling, M., Dupret, E., Demiral, Y., Oudyk, J., Kristensen, T.
-S., Llorens, C., Navarro, A., Lincke, H.-J., Bocéréan, C., Sahan, C., Smith, P., \& Pohrt, A.
-(2019).
-The {Third} {Version} of the {Copenhagen} {Psychosocial} {Questionnaire}.
-\emph{Safety and Health at Work}, \emph{10}(4), 482--503.
-\url{https://doi.org/10.1016/j.shaw.2019.10.002}
+\leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
+Barth, M. (2022). \emph{Tinylabels: Lightweight variable labels}. \url{https://github.com/mariusbarth/tinylabels}
 
-\leavevmode\hypertarget{ref-cavanaugh2000empirical}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
 Cavanaugh, M.
@@
 
-\leavevmode\hypertarget{ref-crawford2010linking}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-crawford2010linking}{}}%
 Crawford, E.
@@
 
-\leavevmode\hypertarget{ref-demerouti2001job}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
 Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
 
-\leavevmode\hypertarget{ref-gerich2017relevance}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
 Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
 
-\leavevmode\hypertarget{ref-kristensen2005copenhagen}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-kristensen2005copenhagen}{}}%
 Kristensen, T. S., Borritz, M., Villadsen, E., \& Christensen, K. B. (2005). The copenhagen burnout inventory: A new tool for the assessment of burnout. \emph{Work \& Stress}, \emph{19}(3), 192--207.
 
-\leavevmode\hypertarget{ref-lazarus1984stress}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
 Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
 
-\leavevmode\hypertarget{ref-pejtersen2010second}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-pejtersen2010second}{}}%
 Pejtersen, J.
@@
 
-\leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2022). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
+\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
+R Core Team. (2021). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
 
-\leavevmode\hypertarget{ref-engage_2022}{}%
-Russell, M., Ossorio Duffoo, C., Garcia Prieto Palacios Roji, R., \& Kulas, J. (2022). Development of an intentional bifactor measure of engagement. \emph{The Seattle Edition of SIOP}, 1--14.
-
-\leavevmode\hypertarget{ref-schaufeli2002measurement}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-schaufeli2002measurement}{}}%
 Schaufeli, W.
@@
 
-\leavevmode\hypertarget{ref-searle2015merits}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-searle2015merits}{}}%
 Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.
 
-\leavevmode\hypertarget{ref-selye1936syndrome}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-selye1936syndrome}{}}%
 Selye, H. (1936). A syndrome produced by diverse nocuous agents. \emph{Nature}, \emph{138}(3479), 32--32.
 
-\leavevmode\hypertarget{ref-webster2011extending}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
 Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.
@@
 
-\endgroup
-
 \end{document}

### 2022-10-05 SIOP2023/Counts/Submission_ResourceCount.tex
pushing from laptop

@@
 \usepackage{csquotes}
-\ifxetex
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 \date{}
+
+\shorttitle{O*Net JDR}
 
@@
 The brief review above provides theoretical and empirical support for the connection between resources and positive organizational outcomes, and between demands and negative outcomes.
-Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement ({``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption,''} Schaufeli et al., 2002), workplace stress ({``an individual state characterized by a combination of high arousal and displeasure,''} p.~15, Pejtersen et al., 2010) and burnout {[}``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work,'' p.~197; Kristensen et al.
+Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement (``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption,'' Schaufeli et al., 2002), workplace stress (``an individual state characterized by a combination of high arousal and displeasure,'' p.~15, Pejtersen et al., 2010) and burnout {[}``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work'', p.~197; Kristensen et al.
 (2005){]}.
@@
 
-\begin{tabular}{lllll}
+\begin{tabular}{llllll}
 \toprule
-Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(564)$} & \multicolumn{1}{c}{$p$}\\
+Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$\mathit{df}$} & \multicolumn{1}{c}{$p$}\\
 \midrule
-Intercept & 3.28 & {}[3.09, 3.47] & 33.93 & < .001\\
-Hindrance & 0.00 & {}[-0.01, 0.00] & -1.80 & .072\\
-Challenge & 0.00 & {}[-0.01, 0.01] & 0.88 & .378\\
-Resource & 0.02 & {}[0.01, 0.03] & 3.84 & < .001\\
+Intercept & 3.28 & {}[3.09, 3.47] & 33.93 & 564 & < .001\\
+Hindrance & 0.00 & {}[-0.01, 0.00] & -1.80 & 564 & .072\\
+Challenge & 0.00 & {}[-0.01, 0.01] & 0.88 & 564 & .378\\
+Resource & 0.02 & {}[0.01, 0.03] & 3.84 & 564 & < .001\\
 \bottomrule
@@
 
-\begin{tabular}{lllll}
+\begin{tabular}{llllll}
 \toprule
-Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(564)$} & \multicolumn{1}{c}{$p$}\\
+Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$\mathit{df}$} & \multicolumn{1}{c}{$p$}\\
 \midrule
-Intercept & 2.38 & {}[2.15, 2.62] & 19.80 & < .001\\
-Hindrance & 0.01 & {}[0.00, 0.01] & 1.82 & .070\\
-Challenge & 0.01 & {}[0.00, 0.02] & 1.43 & .152\\
-Resource & 0.00 & {}[-0.02, 0.01] & -0.77 & .440\\
+Intercept & 2.38 & {}[2.15, 2.62] & 19.80 & 564 & < .001\\
+Hindrance & 0.01 & {}[0.00, 0.01] & 1.82 & 564 & .070\\
+Challenge & 0.01 & {}[0.00, 0.02] & 1.43 & 564 & .152\\
+Resource & 0.00 & {}[-0.02, 0.01] & -0.77 & 564 & .440\\
 \bottomrule
@@
 
-\begin{tabular}{lllll}
+\begin{tabular}{llllll}
 \toprule
-Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(564)$} & \multicolumn{1}{c}{$p$}\\
+Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$\mathit{df}$} & \multicolumn{1}{c}{$p$}\\
 \midrule
-Intercept & 2.90 & {}[2.68, 3.11] & 26.89 & < .001\\
-Hindrance & 0.00 & {}[0.00, 0.01] & 0.67 & .502\\
-Challenge & 0.01 & {}[0.00, 0.02] & 1.19 & .233\\
-Resource & 0.00 & {}[-0.01, 0.01] & -0.52 & .601\\
+Intercept & 2.90 & {}[2.68, 3.11] & 26.89 & 564 & < .001\\
+Hindrance & 0.00 & {}[0.00, 0.01] & 0.67 & 564 & .502\\
+Challenge & 0.01 & {}[0.00, 0.02] & 1.19 & 564 & .233\\
+Resource & 0.00 & {}[-0.01, 0.01] & -0.52 & 564 & .601\\
 \bottomrule
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-abbas2019challenge}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-abbas2019challenge}{}}%
 Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.
 
-\leavevmode\hypertarget{ref-bakker2014job}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
 Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
 
-\leavevmode\hypertarget{ref-bakker2017job}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
 Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
 
-\leavevmode\hypertarget{ref-bakker2007job}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2007job}{}}%
 Bakker, A.
@@
 
-\leavevmode\hypertarget{ref-burr_third_2019}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-burr_third_2019}{}}%
 Burr, H., Berthelsen, H., Moncada, S., Nübling, M., Dupret, E., Demiral, Y., Oudyk, J., Kristensen, T.
@@
 
-\leavevmode\hypertarget{ref-cavanaugh2000empirical}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
 Cavanaugh, M.
@@
 
-\leavevmode\hypertarget{ref-R-base}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
 R Core Team. (2022). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
 
-\leavevmode\hypertarget{ref-engage_2022}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-engage_2022}{}}%
 Russell, M., Ossorio Duffoo, C., Garcia Prieto Palacios Roji, R., \& Kulas, J. (2022). Development of an intentional bifactor measure of engagement. \emph{The Seattle Edition of SIOP}, 1--14.
 
-\leavevmode\hypertarget{ref-schaufeli2002measurement}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-schaufeli2002measurement}{}}%
 Schaufeli, W.

### 2022-10-05 SIOP2023/Counts/convergence.Rmd
pushing from laptop

@@
 We used `r cite_r("r-references.bib")` for all analyses.
-Our analyses are presented by characteristics of work that are rated in terms of being resources, challenge demands, and hindrance demands.
-Pearson correlation coefficients between characteristics classified as resources, challenges, and hindrances were obtained to investigate the associations among these characteristics.
+Our analyses are presented by characteristics of work that are rated as being "relevant".
+Upon confirming that a work characteristic was present, respondents then also rated the extent to which that characteristic was percieved as a resources, challenge, and hindrance.
+
 Correlations, means and standard deviations among all study variables are presented in Table 1.

### 2022-10-06 SIOP2023/SIOP_PROCESS.tex
changed file type to word.

@@
 (2019) captured subjective and objective resources in their study of retirement.
-Correlations of composite variables for the resources of autonomy (r = .12.
+Correlations of composite variables between subjective and objective measures for the resources of autonomy (r = .12.
 p \textgreater{} .01), recognition of work (r = .07, p \textgreater{} .01), and decision freedom (r = .08, p \textgreater{} .01), while significant, certainly do not reflect high levels of overlap.
@@
 It is quite possible that one person experiences high work pressure (commonly cited as a demand in the literature) as a hindrance stressor and thus experiences strain, and another thrives in a fast-paced pressured role and would thus find the environment motivating.
-Here, we asked respondents to rate all of the job characterstics in terms of hindrances and resources.
-consider the here whether perceptions of demands (specifically hindrance demands) and stress is
+Here, we asked respondents to rate all of the job characteristics in terms of hindrances, challenges, and resources.
 
-\hypertarget{why-use-the-onet-resource}{%
-\subsection{Why use the O*Net Resource?}\label{why-use-the-onet-resource}}
+\hypertarget{value-of-exploring-the-onet-resource}{%
+\subsection{Value of exploring the O*Net Resource}\label{value-of-exploring-the-onet-resource}}
 
-Originally, the Advisory Panel for the Dictionary of Occupational Titles recommended a system that would ``\ldots promote the effective education, training, counseling, and employment of the American workforce.
-It should accomplish its purpose by providing a database system that identifies, defines, classifies, and describes occupations in the economy in an accessible and flexible manner'' (Dictionary of Occupational Titles (US) and Service (1993), p.~6).
-The result was the now commonly used O*NET.
-The Occupational Information Network (O*NET; onetonline.org) contains a comprehensive description of occupations (Peterson et al., 2001).
+First, the Occupational Information Network (O*NET; onetonline.org) contains a comprehensive description of occupations (Peterson et al., 2001).
 This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated.
-In fact, there was a call to work with experienced I/O psychologists over the summer to update the content for the \href{https://www.onetonline.org/link/summary/19-3032.00}{Industrial and Organizational Psychologist listing on O*Net}.
-These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move for Veterans,'' ``My Next Move,'' Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
+These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move,'' Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
 It is also useful to employers by providing them with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
+We utilized statements taken from O*NET \href{https://www.O*NETonline.org/find/descriptor/result/4.A.1.b.3}{``activity'' and ``context'' classifications} (e.g., items related to information input, interacting with others, physical work conditions, structural job characteristics).
 
-Of greatest interest here are statements taken from O*NET \href{https://www.O*NETonline.org/find/descriptor/result/4.A.1.b.3}{``activity'' and ``context'' classifications} (e.g., items related to information input, interacting with others, physical work conditions, structural job characteristics).
-One of the first and basic questions is whether or not the categorical examples of ``resources'' and ``demands'' described in the Job Demands-Resources Theory (Demerouti et al., 2001), for example, are generally deemed resources or demands as we objectively define them.
-The next logical question surrounds how ``universal'' such ratings are.
-For instance, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.
-A second study extends the findings from Study 1 to a potentially key moderator - job categories/classifications, examining whether ratings of resources, challenge- and hindrance demands differ by job classification.
+\hypertarget{current-study-and-hypotheses}{%
+\section{Current Study and Hypotheses}\label{current-study-and-hypotheses}}
+
+These data were taken from a larger study on JD-R theory as it applies to O*NET items.
+Our specific interest in the current study is in whether or not \emph{perceptions} of hindrance demands are postitively related to perceived stress, and whether or not this relationship is moderated by perceived resources.
+The Job demands-Resources theory would suggest resources would buffer this relationship.
+We do have some existing evidence that this occurs with other outcomes.
+For example, Tadic et al.~(2015) found that daily hindrance job demands were negatively related to both positive affect and engagement in a sample of primary school teachers.
+Daily job resources, in this sample, buffered the relationships between hindrances and affect and engagement.
+Here, we propose that perceived resources generally, as opposed to daily, would also buffer the relationship between perceived hindrance stressors and, in this, case, perceived stress.
+The following two predictions are made:
+
+\emph{H1. There is a positive relationship between perceived hindrance stressors and stress.}
+
+\emph{H2. The relationship between mean perceived hindrances and stress will be moderated by resources such that this relationship is diminished as perceived resources increase.}
+
+NOTES:
+Add: Challenge versus hindrance job demands and wellbeing: A diary study on the moderating role of job resources
+Add a correlation table to speak to H1. Reference H1 and H2 in the results section.
 
@@
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-\hypertarget{methods-1}{%
-\section{Methods}\label{methods-1}}
-
-\hypertarget{participants-1}{%
-\subsection{Participants}\label{participants-1}}
-
 There were 568 respondents.
 
-\hypertarget{participants-2}{%
-\subsubsection{Participants}\label{participants-2}}
+\hypertarget{participants}{%
+\subsubsection{Participants}\label{participants}}
 
@@
 
-\#Results
+Table 1 presents correlations among the study variables of interest.
 
-A moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1.
+To explore H2, a moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1.
 First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, F(3, 564) = 3.29, p = .020.
-The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, F(3, 564) = 3.51, p = .061.
+The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, F(3, 564) = 3.51, p = .061, providing tentative support for H2.
 As can be seen in Figure 1, those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources.
@@
 \end{table}
-
-Next steps:
-1) Make a prettier graph using ggplot. Note the percentiles that we graphed.
-2) Or, could generate Johnson-Neyman Technique -- shows specifically the range of W values that are significant. See p.~272 for visual and r-script.
-Table example on p.~286: includes variables, symbol, coeff, SE, t, p; below that, rsquared, MSE and f-string.
 
@@
 Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
-
-\leavevmode\hypertarget{ref-advisory1993new}{}%
-Dictionary of Occupational Titles (US), A.
-P.
-for the, \& Service, U.
-S.
-E.
-(1993).
-\emph{The new DOT: A database of occupational titles for the twenty-first century}.
-US Department of Labor, Employment; Training Administration, US~\ldots.
 

### 2022-10-06 SIOP2023/Counts/convergence.Rmd
methods & results

@@
 ---
-title             : "Demanding resources: Similarity of perceptions for challenge and resource characteristics"
+title             : "Demanding resources: Agreement of perceptions for challenge and resource characteristics"
 shorttitle        : "Demanding Resources"
@@
 abstract: |
-  The relationships among sum of perceived job resources, challenge- and hindrance demands and outcomes of organizational outcomes of engagement, stress, and burnout are explored.
-568 workers rated O*Net job characteristics in terms of relevance and perceptions as challenges, hindrances and resources.
-The findings are generally aligned with the job demands resource theory regarding associations between perceived resources, demands, and organizational outcomes of engagement, stress, and burnout.
+ 568 workers rated job characteristics in terms of relevance as well as perceptions as challenges, hindrances and resources.
+We find strong associations between characteristics such that what is viewed as a "resource" is also very often considered a "challenge".
+This agreement was moderated by the nature of the job characteristic.
 
@@
 
-bibliography      : ["r-references.bib", "jdr.bib", "jobdemands_resources_bibtex.bib"]
+bibliography      : ["r-references.bib", "jobdemands_resources_bibtex.bib"]
 
@@
 
-  The brief review above provides theoretical and empirical support for the connection between resources and positive organizational outcomes, and between demands and negative outcomes.
-Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement (“a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption”, @schaufeli2002measurement), workplace stress (“an individual state characterized by a combination of high arousal and displeasure”, p.
-15, @pejtersen2010second) and burnout (“the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work”, p.
-197; @kristensen2005copenhagen).
-Utilizing the job demands-resources theory, transactional theory of stress, and the challenge-hindrance framework, we propose that the number of job characteristics appraised as “challenge demands” (i.e., promote mastery, personal growth, and future gains) would activate a positive state – that of engagement.
-In contrast, number of characteristics of one’s job appraised as a hindrance demand (i.e., inhibit growth, learning and goal achievement) would activate a negative state – here, stress.
+We explored the agreement of perceptions of job characteristics as resources as well as demands (in the form of challenges and hindrances).
+Given the definitions of each (i.e.,  aspect of one’s job that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development [resource] vs.
+aspect of one’s job that can promote mastery, personal growth, or future gains [challenge]), we propose respondents may consider the same characteristic to be viewed as both a challenge as well as a resource.
+That is, we explore whether these perceptions are orthogonal, contradictory, or perhaps even complimentary.
+Utilizing the job demands-resources theory and the challenge-hindrance framework, we propose that job characteristics appraised as “challenge demands” (i.e., promote mastery, personal growth, and future gains) may also be viewed as job resources.
 
-	 In addition to exploring associations with our outcomes, we also sought to explore whether challenges are perceived as distinct from resources.
-Given the definitions of each (i.e.,  aspect of one’s job that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development [resource] vs.
-aspect of one’s job that can promote mastery, personal growth, or future gains [challenge]), we propose respondents may consider them both in the realm of a resource.
+*Hypothesis 1*: Characteristics perceived as challenges are also commonly viewed as resources.
 
-*Hypothesis 4*: Characteristics perceived as challenges are also viewed as resources.
+Although the same job characteristic may be percieved as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others.
+For example, a physically strenuous job requirement such as "carrying heavy objects" would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as "negotiating work schedules" may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge.
+O\*Net has different levels of abstraction with regard to the nature of job characteristic, we will be exploring a mid-level abstraction with seven different characteristic "scales".
 
-	In addition to the above predictions, we consider, in an exploratory fashion, whether or not the pattern of correlations is similar across different job classifications.
-We expect to see the relationships to emerge similarly regardless of one’s type of work.
-For example, we expect that across jobs, total hindrance demands would be negatively related to engagement.
+*Hypothesis 2*: The association between challenging and resourceful characteristics is moderated by type of characteristic.
 
@@
 
-  We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (Bakker & Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001), but from within the unifying framework of O*Net.
-Here, we focus on the relationship between O*Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S.
-workforce representative sample.
+We evaluate agreement across perceptions of present job characteristics regarding their characterization of resource, challenge, and hindrance (Bakker & Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001).
+To capture an effectively exhaustive list of characteristics that apply to, theoretically, *every* possible job, we consult the  unifying framework of O\*Net.
 
-## Participants
+## Materials
 
-  A sample using a Prolific panel resulted in 785 individuals who initially accessed the survey link.
-Of those,112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes & Wilhelm, 2021).
-Additional screening using four embedded attention checks resulted in the retention of 568 respondents.
-A total of 13.57% had been in their job less than 6 months, 19.20% between 6 months and a year, 49.12% between one and five years, 13.27% between 5 and 10 years, and 4.87% more than 10 years.
-Reported ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53).
-Gender was captured via a free-field gender identity category, although the sample predominantly self-identified as female (52.58%) or male (46.83%).
-Jobs were classified into the International Standard Classification of Occupations (ISCO) via the package labourR (Kouretsis et al., 2020).
-Modify or omit?
-*Materials*
+Our survey consisted of 98 items crafted from job characteristic descriptors located within O\*Net’s classification of “work activities”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context” groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
 
-  Characteristics, Demands, and Resources.
-Our analyses included items within O*Net’s classifications of “work activity”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context”: 5) Interpersonal Relationships (14 statements), 6) Physical Work Conditions (30 statements)1, and 7) Structural Job Characteristics (13 statements).
-  Other than minor grammatical editing (for example, changing “the” to “you”), we retained the O*Net wording for our item stems.
-We used O*Net’s response scales, several of which were unique across items, but all shared the same 1 to 5 scale options.
-Subsequent to providing ratings of whether or not an O*Net characteristic was relevant for the respondent’s work, each respondent who agreed that an element had at least some relevance to their job was also asked to rate that element in terms of, 1) .
+The O\*Net descriptors are written in a similar manner to a task statement presented within a job analysis.
+For example, the descriptor for "level of competition", which is an element of the "structural job characteristics" grouping, is *...to what extent does this job require the worker to compete or to be aware of competitive pressures?*.
+Other than minor grammatical editing (for example, changing “the worker” to “you”), we retained the O\*Net wording for our item stems.
+We also retained O\*Net’s response scales, several of which were unique across items, but all shared the same 1 to 5 scale options.
+Subsequent to providing ratings of whether or not each of the 98 O\*Net characteristics were relevant for the respondent’s work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) .
 .
@@
 this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
-*Stress*. Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Obtained alpha was .85 in this sample.
-*Burnout*. Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Alpha was 0.85 in this sample.
-*Engagement*.
-The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample α’s of 0.68 (Absorption) and 0.80 (Vigor), and 0.90 (Dedication).
-For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).
 
-## Procedure
+The total number of items on the survey was less than 392 (98 characteristics x 4 administrations), because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very little variance across respondents (one excluded characteristic, for example, was *...the extent to which thr worker is exposed to radiation on the job*).
 
-  Data were collected through Prolific, a data collection platform.
-An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
+## Participants
+
 Eligibility requirements included being 18+ and holding either a full-time or part-time job.
-Participants then voluntarily chose to respond to the survey.
-The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes.
-Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified.
-Thus, if a respondent indicated that 5 of the characteristics were not part of their job, they were not subsequently asked to rate the level of resource, challenge, or hindrance a given item presented to them.
-For items that were a part of their jobs, they were then asked to report how much a characteristic was a resource, and then how much each characteristic was a hindrance, and finally, how much each item was a challenge.
+Participants were asked to think about their primary job while answering the survey.
+We sampled from a Prolific panel, resulting in 785 individuals who initially accessed the survey link.
+Of those, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes & Wilhelm, 2021).
+Additional screening using four embedded attention checks resulted in the retention of 568 respondents.
+A total of 13.57% had been in their job less than 6 months, 19.20% between 6 months and a year, 49.12% between one and five years, 13.27% between 5 and 10 years, and 4.87% more than 10 years.
+Reported ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53).
+Gender was captured via a free-field gender identity category, although the sample predominantly self-identified as female (52.6%) or male (46.8%).
 Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
@@
 
-We used `r cite_r("r-references.bib")` for all analyses.
-Our analyses are presented by characteristics of work that are rated as being "relevant".
-Upon confirming that a work characteristic was present, respondents then also rated the extent to which that characteristic was percieved as a resources, challenge, and hindrance.
-
-Correlations, means and standard deviations among all study variables are presented in Table 1.
-Results reveal a positive association between resources and engagement (r = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively).
-Challenge demands were positively associated with engagement (r = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
-Total hindrance stressors were not significantly associated with our outcomes (H3a-H3c).
-To further explore H1-H3, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
-First, regarding engagement (F(3, 564) = 26.41, p < .001), the total resources (beta = ??) was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table 2).
-Next, stress was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 2.47, p = .060 (see Table 3).
-Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 1.10, p = .349.
-See Table 4.
-
-  Our fourth prediction suggested a positive association between total resources and total challenge demands.
-Here, we observed a strong positive relationship, so much so that it could be argued that these two variables are capturing the same thing (r = .86), as fully 74% of the variability was shared.
-
-  In an exploratory fashion, we also considered whether or not the pattern of correlations described above was similar across job types.
+All analyses are focused on characteristics of work that are rated as being "relevant".
+Upon confirming that a work characteristic was relevant, respondents then also rated the extent to which that characteristic was percieved as a resources, challenge, and hindrance.
 
@@
 data22$engagement   <- rowMeans(data22[c(380:399)], na.rm=TRUE)        ## probably need to recode some
-
-cor(data22[405:410], use="all.obs")   ## something to be told with resources and challenges
 
@@
 
+```{r cortab}
+
+r <- corx::corx(data22[,c(405:407)],                    
+                triangle = "lower",
+                stars = c(0.05, 0.01, 0.001),
+                describe = c(`$M$` = mean, `$SD$` = sd))
+
+papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table,
+                  caption = "Resource, challenge, and hindrance correlations (counts data).",
+                  escape = FALSE)
+
+#cor(data[405:410], use="all.obs")   ## something to be told with resources and challenges
+
+```
+
+Hypothesis 1 predicted a positive association between total resources and total challenge demands.
+Table \@ref(tab:cortab) shows a very high association between a characteristic being implicated as a resource as well as a challenge (*r* = .85).
+These associations, however, are only capturing the relationships between these demands and resources in *sheer volume*.
+That is, table \@ref(tab:cortab) operationalized each variable as the sheer number of resources, hindrances, or challenges that a respondent indicated were present within their job.
+This correlational analysis simply implies that workers who experience more resources also percieve greater challenges (with significant but muted associations between the other contrasts).
+
+>Note. Why is resource-hindrance association positive? Look at scatterplot if have time
+
 ```{r percagree, fig.cap="Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance.", fig.height=10}
@@
 
-Figure \@ref(fig:percagree) shows that there was not much mutual agreement regarding characteristics viewed as both hindrances and resources ($\bar{X}$ = `r round(mean(rh$mean, na.rm=TRUE),2)`) or as challenges and hindrances
+We next looked for convergence of perception at the level of each individual job characteristic.
+Here, we calculated the *percent of affirmative correspondence* between individual characteristic perceptions.
+That is, a respondent needed to agree that *...being in contact with others* was both a resource as well as a challenge in order to be implicated as affirmatively agreeing.
+We did this for each of the 84 individual characteristics that were rated as a resource, challenge, or demand and then computed an aggregate level of affirmative correspondence for each person.
+Figure \@ref(fig:percagree) presents the results of these correspondences, showing that there was not much mutual agreement regarding characteristics being viewed as both hindrances and resources ($\bar{X}$ = `r round(mean(rh$mean, na.rm=TRUE),2)`) or as challenges and hindrances
 ($\bar{X}$ = `r round(mean(ch$mean, na.rm=TRUE),2)`).
-Alternatively, whether a characteristic was viewed as both a resource and a challenge exhibited greater consistency although also had quite a bit of variability ($\bar{X}$ = `r round(mean(rc$mean, na.rm=TRUE),2)`, *sd* = `r round(sd(rc$mean, na.rm=TRUE),2)`).
+However, when a characteristic was viewed a resource, it was more likely to also be percieved as a challenge (although the correspondence also exhibited quite a bit of variability; $\bar{X}$ = `r round(mean(rc$mean, na.rm=TRUE),2)`, *sd* = `r round(sd(rc$mean, na.rm=TRUE),2)`).
 
@@
 Figure \@ref(fig:recchall) explores the possibility of moderation by *type of characteristic rated* for the resource-challenge convergence.
-We categorized each characteristic by its ONet "scale" (one of seven), and the graph shows consistency across certain characteristics (for example, ) and non-convergence across other *types* of characteristics (for example, "Physical" characteristics).
+Here we categorized each characteristic by its O\*Net "scale" (one of seven), and the graph shows greater consistency across certain characteristics (for example, *Mental Processes* or *Interacting with Others*) and less convergence across other *types* of job activities (for example, *Physical* characteristics).
+A repeated-measures ANOVA retaining these 7 scales as independent variables yielded a treatment effect of $F_(6, 3,402)$ = 613.5, *p* < .001 (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001.
 
@@
 
-F ratio from a repeated measures ANOVA is $F_(6, 3,402)$ = 613.5, *p* < .001 (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001.
+# Discussion
 
-# Discussion
+Important to look not only at demands, but also the nature of the demand.
+Similar to the eustress/distress distinction, it would seem as though demands should be thought of in a valenced manner (e.g., is it a "good" demand or a "bad" demand)[^bootsie].
+
+[^bootsie]: Beyond this SIOP presentation, we have further investigated differential associations of challenges and hindrances with "good" and "bad" outcomes, but have not confirmed meaningful differential associations within this current dataset.
 

### 2022-10-06 SIOP2023/Counts/convergence.tex
methods & results

@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Demanding resources: Similarity of perceptions for challenge and resource characteristics},
-  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata Garcia Prieto Palacios Roji3},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Demanding resources: Agreement of perceptions for challenge and resource characteristics},
+  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata Garcia Prieto Palacios Roji3},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
-\title{Demanding resources: Similarity of perceptions for challenge and resource characteristics}
+\title{Demanding resources: Agreement of perceptions for challenge and resource characteristics}
 \author{John Kulas\textsuperscript{1}, Alicia Stachowski\textsuperscript{2}, \& Renata Garcia Prieto Palacios Roji\textsuperscript{3}}
@@
 \abstract{%
-The relationships among sum of perceived job resources, challenge- and hindrance demands and outcomes of organizational outcomes of engagement, stress, and burnout are explored.
-568 workers rated O*Net job characteristics in terms of relevance and perceptions as challenges, hindrances and resources.
-The findings are generally aligned with the job demands resource theory regarding associations between perceived resources, demands, and organizational outcomes of engagement, stress, and burnout.
+568 workers rated job characteristics in terms of relevance as well as perceptions as challenges, hindrances and resources.
+We find strong associations between characteristics such that what is viewed as a ``resource'' is also very often considered a ``challenge''.
+This agreement was moderated by the nature of the job characteristic.
 }
@@
 \maketitle
-
-\begin{verbatim}
-## Warning: package 'tinylabels' was built under R version 4.1.3
-\end{verbatim}
 
@@
 
-The brief review above provides theoretical and empirical support for the connection between resources and positive organizational outcomes, and between demands and negative outcomes.
-Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement (``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption'', Schaufeli et al.
-(2002)), workplace stress (``an individual state characterized by a combination of high arousal and displeasure'', p.~15, Pejtersen et al.
-(2010)) and burnout (``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work'', p.~197; Kristensen et al.
-(2005)).
-Utilizing the job demands-resources theory, transactional theory of stress, and the challenge-hindrance framework, we propose that the number of job characteristics appraised as ``challenge demands'' (i.e., promote mastery, personal growth, and future gains) would activate a positive state -- that of engagement.
-In contrast, number of characteristics of one's job appraised as a hindrance demand (i.e., inhibit growth, learning and goal achievement) would activate a negative state -- here, stress.
+We explored the agreement of perceptions of job characteristics as resources as well as demands (in the form of challenges and hindrances).
+Given the definitions of each (i.e., aspect of one's job that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development {[}resource{]} vs.~aspect of one's job that can promote mastery, personal growth, or future gains {[}challenge{]}), we propose respondents may consider the same characteristic to be viewed as both a challenge as well as a resource.
+That is, we explore whether these perceptions are orthogonal, contradictory, or perhaps even complimentary.
+Utilizing the job demands-resources theory and the challenge-hindrance framework, we propose that job characteristics appraised as ``challenge demands'' (i.e., promote mastery, personal growth, and future gains) may also be viewed as job resources.
 
-\begin{verbatim}
- In addition to exploring associations with our outcomes, we also sought to explore whether challenges are perceived as distinct from resources.
-Given the definitions of each (i.e.,  aspect of one’s job that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development [resource] vs.
-aspect of one’s job that can promote mastery, personal growth, or future gains [challenge]), we propose respondents may consider them both in the realm of a resource.
+\emph{Hypothesis 1}: Characteristics perceived as challenges are also commonly viewed as resources.
 
-\end{verbatim}
+Although the same job characteristic may be percieved as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others.
+For example, a physically strenuous job requirement such as ``carrying heavy objects'' would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as ``negotiating work schedules'' may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge.
+O*Net has different levels of abstraction with regard to the nature of job characteristic, we will be exploring a mid-level abstraction with seven different characteristic ``scales''.
 
-\emph{Hypothesis 4}: Characteristics perceived as challenges are also viewed as resources.
-
-\begin{verbatim}
-In addition to the above predictions, we consider, in an exploratory fashion, whether or not the pattern of correlations is similar across different job classifications.
-We expect to see the relationships to emerge similarly regardless of one’s type of work.
-For example, we expect that across jobs, total hindrance demands would be negatively related to engagement.
-\end{verbatim}
+\emph{Hypothesis 2}: The association between challenging and resourceful characteristics is moderated by type of characteristic.
 
@@
 
-We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (Bakker \& Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001), but from within the unifying framework of O\emph{Net.
-Here, we focus on the relationship between O}Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S.
-workforce representative sample.
+We evaluate agreement across perceptions of present job characteristics regarding their characterization of resource, challenge, and hindrance (Bakker \& Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001).
+To capture an effectively exhaustive list of characteristics that apply to, theoretically, \emph{every} possible job, we consult the unifying framework of O*Net.
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+\hypertarget{materials}{%
+\subsection{Materials}\label{materials}}
 
-A sample using a Prolific panel resulted in 785 individuals who initially accessed the survey link.
-Of those,112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021).
-Additional screening using four embedded attention checks resulted in the retention of 568 respondents.
-A total of 13.57\% had been in their job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.
-Reported ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53).
-Gender was captured via a free-field gender identity category, although the sample predominantly self-identified as female (52.58\%) or male (46.83\%).
-Jobs were classified into the International Standard Classification of Occupations (ISCO) via the package labourR (Kouretsis et al., 2020).
-Modify or omit?
-\emph{Materials}
+Our survey consisted of 98 items crafted from job characteristic descriptors located within O*Net's classification of ``work activities'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'' groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
 
-Characteristics, Demands, and Resources.
-Our analyses included items within O\emph{Net's classifications of ``work activity'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'': 5) Interpersonal Relationships (14 statements), 6) Physical Work Conditions (30 statements)1, and 7) Structural Job Characteristics (13 statements).
-Other than minor grammatical editing (for example, changing ``the'' to ``you''), we retained the O}Net wording for our item stems.
-We used O\emph{Net's response scales, several of which were unique across items, but all shared the same 1 to 5 scale options.
-Subsequent to providing ratings of whether or not an O}Net characteristic was relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was also asked to rate that element in terms of, 1) .
+The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis.
+For example, the descriptor for ``level of competition'', which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?}.
+Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems.
+We also retained O*Net's response scales, several of which were unique across items, but all shared the same 1 to 5 scale options.
+Subsequent to providing ratings of whether or not each of the 98 O*Net characteristics were relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) .
 .
@@
 this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
-\emph{Stress}. Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Obtained alpha was .85 in this sample.
-\emph{Burnout}. Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Alpha was 0.85 in this sample.
-\emph{Engagement}.
-The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample α's of 0.68 (Absorption) and 0.80 (Vigor), and 0.90 (Dedication).
-For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).
 
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
+The total number of items on the survey was less than 392 (98 characteristics x 4 administrations), because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very little variance across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which thr worker is exposed to radiation on the job}).
 
-Data were collected through Prolific, a data collection platform.
-An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
 Eligibility requirements included being 18+ and holding either a full-time or part-time job.
-Participants then voluntarily chose to respond to the survey.
-The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes.
-Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified.
-Thus, if a respondent indicated that 5 of the characteristics were not part of their job, they were not subsequently asked to rate the level of resource, challenge, or hindrance a given item presented to them.
-For items that were a part of their jobs, they were then asked to report how much a characteristic was a resource, and then how much each characteristic was a hindrance, and finally, how much each item was a challenge.
+Participants were asked to think about their primary job while answering the survey.
+We sampled from a Prolific panel, resulting in 785 individuals who initially accessed the survey link.
+Of those, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021).
+Additional screening using four embedded attention checks resulted in the retention of 568 respondents.
+A total of 13.57\% had been in their job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.
+Reported ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53).
+Gender was captured via a free-field gender identity category, although the sample predominantly self-identified as female (52.6\%) or male (46.8\%).
 Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
@@
 
-We used R (Version 4.1.1; R Core Team, 2021) and the R-packages \emph{corrr} (Version 0.4.3; \textbf{R-corrr?}), \emph{lavaan} (Version 0.6.11; \textbf{R-lavaan?}), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2022), \emph{psych} (Version 2.1.9; \textbf{R-psych?}), \emph{tidyr} (Version 1.2.0; \textbf{R-tidyr?}), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all analyses.
-Our analyses are presented by characteristics of work that are rated in terms of being resources, challenge demands, and hindrance demands.
-Pearson correlation coefficients between characteristics classified as resources, challenges, and hindrances were obtained to investigate the associations among these characteristics.
-Correlations, means and standard deviations among all study variables are presented in Table 1.
-Results reveal a positive association between resources and engagement (r = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively).
-Challenge demands were positively associated with engagement (r = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
-Total hindrance stressors were not significantly associated with our outcomes (H3a-H3c).
-To further explore H1-H3, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
-First, regarding engagement (F(3, 564) = 26.41, p \textless{} .001), the total resources (beta = ??) was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table 2).
-Next, stress was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 2.47, p = .060 (see Table 3).
-Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 1.10, p = .349.
-See Table 4.
-
-Our fourth prediction suggested a positive association between total resources and total challenge demands.
-Here, we observed a strong positive relationship, so much so that it could be argued that these two variables are capturing the same thing (r = .86), as fully 74\% of the variability was shared.
-
-In an exploratory fashion, we also considered whether or not the pattern of correlations described above was similar across job types.
-
-There were 568 retained respondents.
-
-\begin{verbatim}
-##              resource   hindrance  challenge     burnout      stress
-## resource   1.00000000 0.225550803 0.86225195  0.04841544  0.05583466
-## hindrance  0.22555080 1.000000000 0.22047517  0.04101639  0.08980526
-## challenge  0.86225195 0.220475168 1.00000000  0.06790884  0.08057171
-## burnout    0.04841544 0.041016388 0.06790884  1.00000000  0.69654076
-## stress     0.05583466 0.089805265 0.08057171  0.69654076  1.00000000
-## engagement 0.34225837 0.009629535 0.31087164 -0.35496125 -0.29534556
-##              engagement
-## resource    0.342258369
-## hindrance   0.009629535
-## challenge   0.310871641
-## burnout    -0.354961254
-## stress     -0.295345559
-## engagement  1.000000000
-\end{verbatim}
+All analyses are focused on characteristics of work that are rated as being ``relevant''.
+Upon confirming that a work characteristic was relevant, respondents then also rated the extent to which that characteristic was percieved as a resources, challenge, and hindrance.
 
@@
 \subsection{Resource, Challenge, and Hindrance Associations}\label{resource-challenge-and-hindrance-associations}}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:cortab}Resource, challenge, and hindrance correlations (counts data).}
+
+\begin{tabular}{lllll}
+\toprule
+ & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
+\midrule
+1. resource & - &  & 36.02 & 13.26\\
+2. hindrance & .23*** & - & 13.09 & 13.62\\
+3. challenge & .86*** & .22*** & 35.64 & 13.63\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+Hypothesis 1 predicted a positive association between total resources and total challenge demands.
+Table \ref{tab:cortab} shows a very high association between a characteristic being implicated as a resource as well as a challenge (\emph{r} = .85).
+These associations, however, are only capturing the relationships between these demands and resources in \emph{sheer volume}.
+That is, table \ref{tab:cortab} operationalized each variable as the sheer number of resources, hindrances, or challenges that a respondent indicated were present within their job.
+This correlational analysis simply implies that workers who experience more resources also percieve greater challenges (with significant but muted associations between the other contrasts).
+
+\begin{quote}
+Note. Why is resource-hindrance association positive? Look at scatterplot if have time
+\end{quote}
 
@@
 
-Figure \ref{fig:percagree} shows that there was not much mutual agreement regarding characteristics viewed as both hindrances and resources (\(\bar{X}\) = 0.14) or as challenges and hindrances
+We next looked for convergence of perception at the level of each individual job characteristic.
+Here, we calculated the \emph{percent of affirmative correspondence} between individual characteristic perceptions.
+That is, a respondent needed to agree that \emph{\ldots being in contact with others} was both a resource as well as a challenge in order to be implicated as affirmatively agreeing.
+We did this for each of the 84 individual characteristics that were rated as a resource, challenge, or demand and then computed an aggregate level of affirmative correspondence for each person.
+Figure \ref{fig:percagree} presents the results of these correspondences, showing that there was not much mutual agreement regarding characteristics being viewed as both hindrances and resources (\(\bar{X}\) = 0.14) or as challenges and hindrances
 (\(\bar{X}\) = 0.14).
-Alternatively, whether a characteristic was viewed as both a resource and a challenge exhibited greater consistency although also had quite a bit of variability (\(\bar{X}\) = 0.51, \emph{sd} = 0.21).
+However, when a characteristic was viewed a resource, it was more likely to also be percieved as a challenge (although the correspondence also exhibited quite a bit of variability; \(\bar{X}\) = 0.51, \emph{sd} = 0.21).
 
@@
 Figure \ref{fig:recchall} explores the possibility of moderation by \emph{type of characteristic rated} for the resource-challenge convergence.
-We categorized each characteristic by its ONet ``scale'' (one of seven), and the graph shows consistency across certain characteristics (for example, ) and non-convergence across other \emph{types} of characteristics (for example, ``Physical'' characteristics).
-
-F ratio from a repeated measures ANOVA is \(F_(6, 3,402)\) = 613.5, \emph{p} \textless{} .001 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001.
+Here we categorized each characteristic by its O*Net ``scale'' (one of seven), and the graph shows greater consistency across certain characteristics (for example, \emph{Mental Processes} or \emph{Interacting with Others}) and less convergence across other \emph{types} of job activities (for example, \emph{Physical} characteristics).
+A repeated-measures ANOVA retaining these 7 scales as independent variables yielded a treatment effect of \(F_(6, 3,402)\) = 613.5, \emph{p} \textless{} .001 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001.
 
@@
 \section{Discussion}\label{discussion}}
+
+Important to look not only at demands, but also the nature of the demand.
+Similar to the eustress/distress distinction, it would seem as though demands should be thought of in a valenced manner (e.g., is it a ``good'' demand or a ``bad'' demand)\footnote{Beyond this SIOP presentation, we have further investigated differential associations of challenges and hindrances with ``good'' and ``bad'' outcomes, but have not confirmed meaningful differential associations within this current dataset.}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
-Aust, F., \& Barth, M. (2022). \emph{Papaja: Prepare american psychological association journal articles with r markdown}. \url{https://github.com/crsh/papaja}
-
 \leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
@@
 \emph{European Journal of Work and Organizational Psychology}, \emph{12}(4), 393--417.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
-Barth, M. (2022). \emph{Tinylabels: Lightweight variable labels}. \url{https://github.com/mariusbarth/tinylabels}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-kristensen2005copenhagen}{}}%
-Kristensen, T. S., Borritz, M., Villadsen, E., \& Christensen, K. B. (2005). The copenhagen burnout inventory: A new tool for the assessment of burnout. \emph{Work \& Stress}, \emph{19}(3), 192--207.
-
 \leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
 Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
-
-\leavevmode\vadjust pre{\hypertarget{ref-pejtersen2010second}{}}%
-Pejtersen, J.
-H., Kristensen, T.
-S., Borg, V., \& Bjorner, J.
-B.
-(2010).
-The second version of the copenhagen psychosocial questionnaire.
-\emph{Scandinavian Journal of Public Health}, \emph{38}(3\_suppl), 8--24.
 
@@
 \emph{Journal of Applied Psychology}, \emph{92}(2), 438.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
-R Core Team. (2021). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-schaufeli2002measurement}{}}%
-Schaufeli, W.
-B., Salanova, M., González-Romá, V., \& Bakker, A.
-B.
-(2002).
-The measurement of engagement and burnout: A two sample confirmatory factor analytic approach.
-\emph{Journal of Happiness Studies}, \emph{3}(1), 71--92.
 

### 2022-10-07 SIOP2023/Counts/convergence.tex
prior to Hudson

@@
   pdftitle={Demanding resources: Agreement of perceptions for challenge and resource characteristics},
-  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata Garcia Prieto Palacios Roji3},
+  pdfauthor={John Kulas1 \& Alicia Stachowski2},
   pdflang={en-EN},
@@
 \title{Demanding resources: Agreement of perceptions for challenge and resource characteristics}
-\author{John Kulas\textsuperscript{1}, Alicia Stachowski\textsuperscript{2}, \& Renata Garcia Prieto Palacios Roji\textsuperscript{3}}
+\author{John Kulas\textsuperscript{1} \& Alicia Stachowski\textsuperscript{2}}
 \date{}
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} eRg\\\textsuperscript{2} University of Wisconsin - Stout\\\textsuperscript{3} PepsiCo}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} eRg\\\textsuperscript{2} University of Wisconsin - Stout}
 
@@
 \maketitle
-
-\begin{verbatim}
-## Warning in knitr::write_bib("r-references.bib"): package(s) r-references.bib not
-## found
-\end{verbatim}
 
@@
 
-All analyses are focused on characteristics of work that are rated as being ``relevant''.
+All analyses are focused on characteristics of work that were rated as being ``relevant'' to the respondents' job.
 Upon confirming that a work characteristic was relevant, respondents then also rated the extent to which that characteristic was percieved as a resources, challenge, and hindrance.
@@
 
-Important to look not only at demands, but also the nature of the demand.
-Similar to the eustress/distress distinction, it would seem as though demands should be thought of in a valenced manner (e.g., is it a ``good'' demand or a ``bad'' demand)\footnote{Beyond this SIOP presentation, we have further investigated differential associations of challenges and hindrances with ``good'' and ``bad'' outcomes, but have not confirmed meaningful differential associations within this current dataset.}.
+Our findings highlight the importance of dissociating the \emph{nature} of job demands.
+Similar to the eustress/distress distinction (e.g., Selye, 1974), it would seem as though demands should be thought of in a valenced manner (e.g., is it a ``good'' demand or a ``bad'' demand)\footnote{Beyond this SIOP presentation, we have further investigated differential associations of challenges and hindrances with ``good'' and ``bad'' outcomes, but have not confirmed meaningful differential associations within this current dataset.}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-selye1974stress}{}}%
+Selye, H. (1974). \emph{Stress without distress}. Lippincott Williams \& Wilkins.
+
 \leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%

### 2022-10-07 SIOP2023/SIOP_PROCESS.Rmd
changed file type to word.
updated project 1

@@
 ---
-title             : "JD-R Theory: Using the Content of the O*Net"
+title             : "Testing the JD-R Theory: Using the Content of the O*Net"
 shorttitle        : "SIOP_Hindrances-Resources Interaction"
@@
 author: 
-  - name          : "First Author"
+  - name          : "Alicia A. Stachowski"
     affiliation   : "1"
@@
     address       : "Postal address"
-    email         : "my@email.com"
+    email         : "stachowskia@uwstout.edu"
     role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
@@
       - Writing - Review & Editing
-  - name          : "Ernst-August Doelle"
-    affiliation   : "1,2"
+  - name          : "John T. Kulas"
+    affiliation   : "2"
     role:
@@
   - id            : "1"
-    institution   : "Wilhelm-Wundt-University"
+    institution   : "University of Wisconsin - Stout"
   - id            : "2"
-    institution   : "Konstanz Business School"
+    institution   : "eRg"
 
@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_word
 ---
@@
 The Job Demands-Resources Theory [JD-R; @demerouti2001job] has received wide support across contexts and varied research questions.
-We add to this literature via two routes: by utilizing some of the job characteristics in the popular O\*Net, and by focusing on perceptions of all characteristics as demands/resources.
-Specifically, we explore the interaction between perceptions of job demands and resources on the outcome of stress across a wide range of occupations.
+We extend the literature by 1) exploring the interaction between *perceptions* of job demands and resources on the outcome of stress using job characteristics in the popular O\*Net and 2) by considering also the appraisal of demands as challenge or hindrance stressors.
 Here, respondents made a series of evaluations that used: direct O\*Net terminology (both descriptor and response option), and JD-R influenced ratings of demand and hindrance stressors.
@@
 Demanding job characteristics are frequently associated with negative outcomes [e.g., @bakker2003dual], whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job].
-Our focus is on whether or not having more resources serves as a buffer to the demand-stress relationship.
-One of the stickier elements of this question surrounds the subjective nature of demands/resources, which we address next.
+However, a related line of research emphasizes a distinction between two types of demands - that of "challenge" and "hindrance" demands, suggesting that employees may evaluate stressors in different ways.
 
 ## Objective vs. Subjective Nature of Demands and Resources: The Role of Appraisal
+
+The stress literature speaks to the key consideration of the way employees appraise situations or circumstances - in this case, our focus will be on work characteristics.
+The transactional theory of stress and coping suggests that people cognitively appraise stimuli in their environments on a continuous basis [@lazarus1984stress].
+For example, two employees both informed that they need to step in and assume the responsibilities of a coworker in their absence may react differently to this job demand.
+One may feel quite paralyzed by the added or novel tasks, while the other may embrace it as an exciting new challenge.
+The terms associated with the two different appraisals of the same stressor are "challenge" and "hindrance" demands [@cavanaugh2000empirical] Challenge demands promote mastery, personal growth, and future gains.
+Hindrance demands, by definition, inhibit growth, learning and goal achievement.
+Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes [e.g., @cavanaugh2000empirical].
+Our focus here will be on the connection between hindrance demands specifically, and their association with reported stress.
+More specifically, our interest here is whether or not the negative hindrance association we typically observe between demands and stress can be buffered by perceived resources.
 
@@
 These data were taken from a larger study on JD-R theory as it applies to O\*NET items.
-Our specific interest in the current study is in whether or not *perceptions* of hindrance demands are postitively related to perceived stress, and whether or not this relationship is moderated by perceived resources.
+Our specific interest in the current study is in whether or not perceptions of hindrance demands are postitively related to perceived stress, and whether or not this relationship is moderated by perceived resources.
 The Job demands-Resources theory would suggest resources would buffer this relationship.
-We do have some existing evidence that this occurs with other outcomes.
+In fact, a rather large body of empirical evidence supports this assertion [e.g., see @bakker2017job for a historical review].
+We do have some existing evidence that this occurs with other outcomes beyond stress.
 For example, Tadic et al.
@@
 *H2. The relationship between mean perceived hindrances and stress will be moderated by resources such that this relationship is diminished as perceived resources increase.*
-
-NOTES:
-Add: Challenge versus hindrance job demands and wellbeing: A diary study on the moderating role of job resources
-Add a correlation table to speak to H1. Reference H1 and H2 in the results section.
 
@@
 
-There were `r nrow(data)` respondents.
-
 ```{r PROCESS, include=FALSE}
@@
 
-* 568 respondents, 13.57% had been in their referent job less than 6 months, 19.20% between 6 months and a year, 49.12% between one and five years, 13.27% between 5 and 10 years, and 4.87% more than 10 years.
-* Ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53).
-* Gender: female (52.58%) or male (46.83%). 
-* Job classifications: International Standard Classification of Occupations (ISCO) via the package `labourR` [@R-labourR], and further categorized into “knowledge” (n = 320) versus “skilled” (n = 214) occupations with knowledge workers being identified via ISCO classifications of: 1) professionals, and 2) managers.
-
-The data for this study were collected through Prolific sample,18 or older and holding a full-time or part-time job.
-Participants were asked to think about their primary job while answering the survey, and upon completion each participant was compensated in the amount of six US dollars.
+There were a total of 568 respondents, of which 13.57% had been in their referent job less than 6 months, 19.20% between 6 months and a year, 49.12% between one and five years, 13.27% between 5 and 10 years, and 4.87% more than 10 years.Their ages ranged from 18 to 65 with an average of 28.18 years old (*SD* = 7.53).
+Over half, 52.58% identified as female, and 46.83% identified as male.
 
@@
 
-We used 98 statements taken directly from O$^{*}$Net’s “activity” and “context” classifications.
+> *Resources and Hindrances*.
+To guage resources and hindrances, we used 98 statements taken directly from O\*Net’s “activity” and “context” classifications.
 Each of the 98 descriptors has potentially unique response categories, but scaling was consistently 1 (low) to 5 (high).
-Subsequent to these self-evaluations, respondents were asked to rate elements in terms of 1) …this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) …this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) …this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
+Subsequent to these self-evaluations, respondents were asked to rate elements in terms of resources ("…this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development"), challenges, (…this aspect of your job is a challenge that can promote mastery, personal growth, or future gains") and hindrances ("…this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment").
+For each category (e.g., resources), a means was computed across items that applied to one's role, and thus, mean scores could range from 1 to 5.
+
+> *Stress*.
+Three items taken from the Copenhagen Psychosocial Questionnaire (@burr_third_2019) captured stress (e.g., "How often have you had problems relaxing because of your job?").
+Responses were made on a 5-point scale ranging from "not at all" to "all the time".
+Alpha was .85 in this sample.
 
@@
 
-We used PROCESS for R Version 4.1.1 [@hayes2022] to assess the extent to which the relationship between demands and stress are moderated by resources.
+The data presented here were part of a larger study on the Job-demands Resources Model using O\*Net.
+Data were collected through Prolific, a data collection platform.
+An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
+Eligibility requirements included being 18+ and holding either a full-time or part-time job.
+Participants then voluntarily chose to respond to the survey.
+The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes.
+Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified.
+Thus, if a respondent indicated that 5 of the characteristics were not part of their job, they were not subsequently asked to rate the level of resource, challenge, or hindrance a given item presented to them.
+For items that were a part of their jobs, they were then asked to report how much a characteristic was a resource, and then how much each characteristic was a hindrance, and finally, how much each item was a challenge.
+Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
 
@@
 #par(mar=c(1,1,1,1))
-plot(y=y,x=x,cex=1.2,pch=wmarker,xlab="Resources (W)",
-     ylab="Stress (Y)")
+plot(y=y,x=x,cex=1.2,pch=wmarker,xlab="Hindrances",
+     ylab="Stress")
 legend.txt<-c("Low Resources","Medium Resources", "High Resources")
@@
 
-Table 1 presents correlations among the study variables of interest.
+Following data cleaning and preparation, we computed correlations among the study variables.
+See Table 1.
+With regard to H1, which predicted a positive association between perceived hindrance stressors and stress, a positive relationship was observed, *r* = , *p* = .
+Thus, support was found for H1.
 
-To explore H2, a moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1.
-First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, F(3, 564) = 3.29, p = .020.
-The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, F(3, 564) = 3.51, p = .061, providing tentative support for H2.
+Next, to explore H2, a moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1 [@hayes2022].
+First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, F(3, 564) = 3.29, *p* = .020.
+The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, F(3, 564) = 3.51, *p* = .061, providing tentative support for H2.
 As can be seen in Figure 1, those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources.
-Upon exploring the interaction further, it was evident that this moderated effect happened at lower, but not higher levels of resources.
+As such, these results provide some evidence that the resources do moderate the relationship between hindrance stressors
 
@@
 
+The primary goal of this project was to further explore the role of perceived resources on the hindrance-stress relationship.
+As expected, the results suggest a positive relationship between perceived hindrances and stress (H1).
+While intuitive, it is important to replicate this finding before we explore the impact of perceived resources, which arguably, is something that employers may have more leverage to control than hindrance stressors.
+Second, the results serve to support the assertion that resources change the relationship between hindrances and stressors such that the connection between the two is dimished as resources increase (H2).
+While not hypothesized or presented above, the authors did run a regression on the challenge-stress relationship with resources as a moderator, with the assumption that resources wouldn't influence a direct relationship, and did find that to be the case.
+The Job-demands Resources Theory [JD-R; @demerouti2001job] suggests that resources would buffer the negative impact between demands and stress, and by extension, given the more traditional conceptualization of demands would be aligned with hindrance demands.
+
+These findings have implications worth considering.
+In a practical sense wihtin the workplace, they speak to the ever present need to ensure employees have sufficient resources.
+Our project focused on the characteristics of one's work specifically, and in line with the literature cited above, studied the ratings or perceptions of resources and demands to account for individual differences in the way employees appraise components of their work.
+From a academic research standpoint, these findings integrate three related literatures: the job-demands resources, stress appraisal, and challenge-hindrance framework to examine the experience of employees across jobs - specifically, the way that resources and hindrance demands interact on the experience of stress.
+Results align with what all three theories/frameworks would suggest.
+
+## Limitations and Future Directions
+
+Here, we note a number of limitations, but also provide additional directions for future research on this topic.
+First, while the use of O\*Net items is a strength of the paper, practical considerations limited the number of job characteristics we could include in our survey.
+Because our focus was on O*Net items and our procedure was time and effort intensive, we were unable to inquire about other forms of resources (e.g., supervisor or coworker support) or demands.
+Thus, future study could explore these sources of support as resources and perhaps even compare the importance of various types of resources and their role in reducing the influence of hindrance stressors.
+Is it overall perceptions of having more resources that makes up for hindrances, or could it be that certain resources carry more weight?
+Second, our focus here was on the outcome of stress, but it may also be of value to consider what the interaction between resources and hindrances looks like on other outcomes of interest in a work context (e.g., commitment, motivation, engagement, intent to quit).
+
 \newpage

### 2022-10-07 SIOP2023/Counts/convergence.Rmd

@@
     affiliation   : "2"
-  - name          : "Renata Garcia Prieto Palacios Roji"
-    affiliation   : "3"
 
@@
     institution   : "University of Wisconsin - Stout"
-  - id            : "3"
-    institution   : "PepsiCo"
 
@@
 
-#r_refs("r-references.bib")
-knitr::write_bib("r-references.bib")
+r_refs("r-references.bib")
+#knitr::write_bib("r-references.bib")
 
@@
 
-All analyses are focused on characteristics of work that are rated as being "relevant".
+All analyses are focused on characteristics of work that were rated as being "relevant" to the respondents' job.
 Upon confirming that a work characteristic was relevant, respondents then also rated the extent to which that characteristic was percieved as a resources, challenge, and hindrance.
@@
 
-Important to look not only at demands, but also the nature of the demand.
-Similar to the eustress/distress distinction, it would seem as though demands should be thought of in a valenced manner (e.g., is it a "good" demand or a "bad" demand)[^bootsie].
+Our findings highlight the importance of dissociating the *nature* of job demands.
+Similar to the eustress/distress distinction [e.g., @selye1974stress], it would seem as though demands should be thought of in a valenced manner (e.g., is it a "good" demand or a "bad" demand)[^bootsie].
 

### 2022-10-07 SIOP2023/Counts/convergence.Rmd
reviewed methods/results

@@
 We did this for each of the 84 individual characteristics that were rated as a resource, challenge, or demand and then computed an aggregate level of affirmative correspondence for each person.
-Figure \@ref(fig:percagree) presents the results of these correspondences, showing that there was not much mutual agreement regarding characteristics being viewed as both hindrances and resources ($\bar{X}$ = `r round(mean(rh$mean, na.rm=TRUE),2)`) or as challenges and hindrances
-($\bar{X}$ = `r round(mean(ch$mean, na.rm=TRUE),2)`).
-However, when a characteristic was viewed a resource, it was more likely to also be percieved as a challenge (although the correspondence also exhibited quite a bit of variability; $\bar{X}$ = `r round(mean(rc$mean, na.rm=TRUE),2)`, *sd* = `r round(sd(rc$mean, na.rm=TRUE),2)`).
+Figure \@ref(fig:percagree) presents the results of these correspondences, showing that there was not much mutual agreement regarding characteristics being viewed as both hindrances and resources (*M* = `r round(mean(rh$mean, na.rm=TRUE),2)`) or as challenges and hindrances
+(*M* = `r round(mean(ch$mean, na.rm=TRUE),2)`).
+However, when a characteristic was viewed a resource, it was more likely to also be percieved as a challenge (although the correspondence also exhibited quite a bit of variability; *M* = `r round(mean(rc$mean, na.rm=TRUE),2)`, *sd* = `r round(sd(rc$mean, na.rm=TRUE),2)`).
 

### 2022-10-07 SIOP2023/Counts/convergence.tex
reviewed methods/results

@@
 \usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Demanding resources: Agreement of perceptions for challenge and resource characteristics},
+  pdfauthor={John Kulas1 \& Alicia Stachowski2},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \makeatother
-
-\usepackage{xpatch}
-\makeatletter
-\xapptocmd\appendix
-  {\xapptocmd\section
-    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
-    {}{\InnerPatchFailed}%
-  }
-{}{\PatchFailed}
+\shorttitle{Demanding Resources}
 \keywords{keywords\newline\indent Word count: X}
@@
 \usepackage{csquotes}
-\ifLuaTeX
+\ifxetex
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\else
+  \usepackage[main=english]{babel}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+\fi
+\ifluatex
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={Demanding resources: Agreement of perceptions for challenge and resource characteristics},
-  pdfauthor={John Kulas1 \& Alicia Stachowski2},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 \date{}
-
-\shorttitle{Demanding Resources}
 
@@
 
-\abstract{%
+\abstract{
 568 workers rated job characteristics in terms of relevance as well as perceptions as challenges, hindrances and resources.
-We find strong associations between characteristics such that what is viewed as a ``resource'' is also very often considered a ``challenge''.
-This agreement was moderated by the nature of the job characteristic.
+We find strong associations between characteristics such that what is viewed as a ``resource'' is also very often considered a ``challenge.'' This agreement was moderated by the nature of the job characteristic.
 }
@@
 For example, a physically strenuous job requirement such as ``carrying heavy objects'' would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as ``negotiating work schedules'' may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge.
-O*Net has different levels of abstraction with regard to the nature of job characteristic, we will be exploring a mid-level abstraction with seven different characteristic ``scales''.
+O*Net has different levels of abstraction with regard to the nature of job characteristic, we will be exploring a mid-level abstraction with seven different characteristic ``scales.''
 
@@
 The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis.
-For example, the descriptor for ``level of competition'', which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?}.
+For example, the descriptor for ``level of competition,'' which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?}.
 Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems.
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-abbas2019challenge}{}}%
+\leavevmode\hypertarget{ref-abbas2019challenge}{}%
 Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
+\leavevmode\hypertarget{ref-bakker2014job}{}%
 Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
+\leavevmode\hypertarget{ref-bakker2017job}{}%
 Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2007job}{}}%
+\leavevmode\hypertarget{ref-bakker2007job}{}%
 Bakker, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
+\leavevmode\hypertarget{ref-cavanaugh2000empirical}{}%
 Cavanaugh, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-crawford2010linking}{}}%
+\leavevmode\hypertarget{ref-crawford2010linking}{}%
 Crawford, E.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
+\leavevmode\hypertarget{ref-demerouti2001job}{}%
 Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
 
-\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
+\leavevmode\hypertarget{ref-gerich2017relevance}{}%
 Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
 
-\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
+\leavevmode\hypertarget{ref-lazarus1984stress}{}%
 Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
 
-\leavevmode\vadjust pre{\hypertarget{ref-podsakoff2007differential}{}}%
+\leavevmode\hypertarget{ref-podsakoff2007differential}{}%
 Podsakoff, N.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-searle2015merits}{}}%
+\leavevmode\hypertarget{ref-searle2015merits}{}%
 Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.
 
-\leavevmode\vadjust pre{\hypertarget{ref-selye1936syndrome}{}}%
+\leavevmode\hypertarget{ref-selye1936syndrome}{}%
 Selye, H. (1936). A syndrome produced by diverse nocuous agents. \emph{Nature}, \emph{138}(3479), 32--32.
 
-\leavevmode\vadjust pre{\hypertarget{ref-selye1974stress}{}}%
+\leavevmode\hypertarget{ref-selye1974stress}{}%
 Selye, H. (1974). \emph{Stress without distress}. Lippincott Williams \& Wilkins.
 
-\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
+\leavevmode\hypertarget{ref-webster2011extending}{}%
 Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.

### 2022-10-07 SIOP2023/Counts/Submission_ResourceCount.Rmd

@@
 ---
-title             : "Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?"
-shorttitle        : "O*Net JDR"
+title             : "Perception of Work Demands and Resources: Does Volume Matter?"
+shorttitle        : "JDR Volume"
 
 author: 
-  - name          : "John Kulas"
+  - name          : "Alicia Stachowski"
     affiliation   : "1"
     corresponding : yes    # Define only one corresponding author
-    email         : "jtkulas@ergreports.com"
-  - name          : "Alicia Stachowski"
+    email         : "stachowskia@uwstout.edu"
+  - name          : "John Kulas"
     affiliation   : "2"
-  - name          : "Renata Garcia Prieto Palacios Roji"
-    affiliation   : "3"
 
@@
   - id            : "1"
+    institution   : "University of Wisconsin - Stout"
+  - id            : "2"
     institution   : "eRg"
-  - id            : "2"
-    institution   : "University of Wisconsin - Stout"
-  - id            : "3"
-    institution   : "PepsiCo"
 
@@
 
-  A plethora of research applying the job demands-resources model [@demerouti2001job] and job demands-resources theory [@bakker2017job] underscore the importance of work characteristics on the experience of motivation and strain.
+  A plethora of research applying the job demands-resources model [@demerouti2001job] and job demands-resources theory [@bakker2017job] underscores the importance of work characteristics on the experience of motivation and strain.
 However, much of our existing research on this topic assumes that certain characteristics are resources and others are generally considered demands.

### 2022-10-07 SIOP2023/Counts/Submission_ResourceCount.tex

@@
 \hypersetup{
-  pdftitle={Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?},
-  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata Garcia Prieto Palacios Roji3},
+  pdftitle={Perception of Work Demands and Resources: Does Volume Matter?},
+  pdfauthor={Alicia Stachowski1 \& John Kulas2},
   pdflang={en-EN},
@@
 
-\title{Perception of Work Demands and Resources: Does Volume Relate to Engagement, Stress, or Burnout?}
-\author{John Kulas\textsuperscript{1}, Alicia Stachowski\textsuperscript{2}, \& Renata Garcia Prieto Palacios Roji\textsuperscript{3}}
+\title{Perception of Work Demands and Resources: Does Volume Matter?}
+\author{Alicia Stachowski\textsuperscript{1} \& John Kulas\textsuperscript{2}}
 \date{}
 
-\shorttitle{O*Net JDR}
+\shorttitle{JDR Volume}
 
@@
 
-Correspondence concerning this article should be addressed to John Kulas. E-mail: \href{mailto:jtkulas@ergreports.com}{\nolinkurl{jtkulas@ergreports.com}}
+Correspondence concerning this article should be addressed to Alicia Stachowski. E-mail: \href{mailto:stachowskia@uwstout.edu}{\nolinkurl{stachowskia@uwstout.edu}}
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} eRg\\\textsuperscript{2} University of Wisconsin - Stout\\\textsuperscript{3} PepsiCo}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Wisconsin - Stout\\\textsuperscript{2} eRg}
 
@@
 
-A plethora of research applying the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (A.
-B.
-Bakker \& Demerouti, 2017) underscore the importance of work characteristics on the experience of motivation and strain.
+A plethora of research applying the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker \& Demerouti, 2017) underscores the importance of work characteristics on the experience of motivation and strain.
 However, much of our existing research on this topic assumes that certain characteristics are resources and others are generally considered demands.
@@
 
-The perception of a characteristic of one's job as a resource or demand activates one of two unique processes: either health impairment or motivation (A.
-B.
-Bakker \& Demerouti, 2014).
-Demanding job characteristics are frequently associated with negative outcomes {[}e.g., health impairment process; A.
-Bakker et al.
-(2003){]}, whereas job characteristics considered resources have been associated with positive organizational outcomes like engagement and motivation (A.
-B.
-Bakker et al., 2007).
+The perception of a characteristic of one's job as a resource or demand activates one of two unique processes: either health impairment or motivation (Bakker \& Demerouti, 2014).
+Demanding job characteristics are frequently associated with negative outcomes {[}e.g., health impairment process; Bakker et al.
+(2003){]}, whereas job characteristics considered resources have been associated with positive organizational outcomes like engagement and motivation (Bakker et al., 2007).
 
@@
 To begin, the first logical question is whether employees actually distinguish between challenge and hindrance stressors, and research suggests that they can and do.
-For example, A.
-B.
-Bakker and Sanz-Vergel (2013) found that perceived work pressure can be classified as a hindrance demand, and emotional demands as a challenge demand.
+For example, Bakker and Sanz-Vergel (2013) found that perceived work pressure can be classified as a hindrance demand, and emotional demands as a challenge demand.
 Webster et al.
@@
 
-We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (A.
-Bakker et al., 2003; A.
-B.
-Bakker \& Demerouti, 2017; Demerouti et al., 2001), but from within the unifying framework of O*Net.
+We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (Bakker et al., 2003; Bakker \& Demerouti, 2017; Demerouti et al., 2001), but from within the unifying framework of O*Net.
 Here, we focus on the relationship between O*Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2003dual}{}}%
+Bakker, A.
+B., Demerouti, E., \& Schaufeli, W.
+(2003).
+Dual processes at work in a call centre: An application of the job demands--resources model.
+\emph{European Journal of Work and Organizational Psychology}, \emph{12}(4), 393--417.
+
 \leavevmode\vadjust pre{\hypertarget{ref-bakker2007job}{}}%
@@
 Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2003dual}{}}%
-Bakker, A., Demerouti, E., \& Schaufeli, W.
-(2003).
-Dual processes at work in a call centre: An application of the job demands--resources model.
-\emph{European Journal of Work and Organizational Psychology}, \emph{12}(4), 393--417.
 

### 2022-10-07 SIOP2023/Counts/Submission_ResourceCount.Rmd
first full pass through (Kulas)

@@
     corresponding : yes    # Define only one corresponding author
+    address       : "Anytown, USA"
     email         : "stachowskia@uwstout.edu"
@@
 
-  A plethora of research applying the job demands-resources model [@demerouti2001job] and job demands-resources theory [@bakker2017job] underscores the importance of work characteristics on the experience of motivation and strain.
-However, much of our existing research on this topic assumes that certain characteristics are resources and others are generally considered demands.
-This study explores how individual perceptions of these work characteristics relate to engagement, stress, and burnout by asking respondents to indicate (of the characteristics that apply to their jobs) how much each is a resource, challenge, or hindrance demand.
-Amount of perceived resources, challenges, and hindrances can then be associated with engagement, stress, and burnout.
+A plethora of research applying the job demands-resources model [@demerouti2001job] and theory [@bakker2017job] underscores the importance of work characteristics on the experience of motivation and strain.
+However, much of our existing research on this topic assumes that certain characteristics are resources (for example, autonomy) while others (such as deadlines) are generally considered demands.
+This study explores how individual perceptions of work characteristics relate to work-related outcomes by asking respondents to indicate (of the characteristics that apply to their jobs) how much each is experienced to be a resource, challenge, or hindrance.
+That is, we allow for the circumstance that the same characteristic may be perceived by some to be a resource as well as a demand.
+We then evaluate associations between resources and demands as well as probing for subsequent associations with engagement, stress, and burnout.
 
@@
 The theoretical foundation for this study is the job demands-resources theory [@demerouti2001job].
-Using this theory, we can model both work environment and job characteristics via job resources and demands.
+This theory posits that the perception of a characteristic of one’s job as a resource or demand activates one of two unique processes: either health impairment or motivation [@bakker2014job].
+Demanding job characteristics are frequently associated with negative outcomes [e.g., health impairment, @bakker2003dual], whereas resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job].
 Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [e.g., high work pressure; @demerouti2001job].
+In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [e.g., high work pressure, @demerouti2001job].
 
-  The perception of a characteristic of one’s job as a resource or demand activates one of two unique processes: either health impairment or motivation [@bakker2014job].
-Demanding job characteristics are frequently associated with negative outcomes [e.g., health impairment process; @bakker2003dual], whereas job characteristics considered resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job].
+### An Added Complexity: Perception (Appraisal) of Work Characteristics Might Matter
 
-## An Added Complexity: Perception (Appraisal) of Work Characteristics Might Matter
-
-  The above description speaks to one of two distinct processes being activated, presumably based on one’s assessment of how a work characteristics makes them feel (e.g., consider the different reactions employees may have to being nominated to give a speech at an upcoming company event).
-Thus, although some research on job demands in particular is based on a priori classifications of demands [@searle2015merits], the appraisal of any work characteristic as a demand or resource is quite subjective.
+The above description speaks to one of two distinct processes being activated, presumably based on one’s appraisal of how a work characteristics makes them feel (e.g., consider the different reactions two different employees may have to being nominated to give a speech at an upcoming company event).
+Thus, although some research on job demands in particular is based on *a priori* classifications of demands [@searle2015merits], the appraisal of any work characteristic as a demand or resource is actually subjective.
 The literature on the experience of stress explains how such individual differences in appraisal are possible.
-Specifically, the transactional theory of stress and coping states that people cognitively appraise stimuli in their environments on a continuous basis [@lazarus1984stress].
+Specifically, the transactional theory of stress and coping states that people cognitively appraise stimuli in their environments on a continual basis [@lazarus1984stress].
 During this process, meaning is assigned to stimuli.
-If the above employee appraised the upcoming speech as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping (e.g., attempting to decline, asking for help in writing the speech).
+If our example fictional employee appraised the upcoming speech as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping (e.g., attempting to decline, asking for help in writing the speech).
 From that point, the cycle of appraisal continues based on the action to cope with the stressor [@lazarus1984stress].
 
-## Could a Work Demand be Appraised Positively?: The Challenge-Hindrance Framework
+### Could a Work Demand be Appraised Positively?: The Challenge-Hindrance Framework
 
-  Although the word “stress” often connotes something negative,@selye1936syndrome defined stress generically as a response to change.
+Although the word “stress” often connotes something negative, @selye1936syndrome defined stress generically as a response to change.
 For instance, the example above describes an employee who appraises being nominated to give a speech as a negative stressor.
 However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
-The terms associated with the two different appraisals of the stressor described here are challenge and hindrance demands [@cavanaugh2000empirical] Specifically, challenge demands promote mastery, personal growth, and future gains.
+The terms associated with the two different appraisals of the stressor described here can be accomodated within the context of the JDR theory as "challenge" and "hindrance" demands [@cavanaugh2000empirical] Specifically, challenge demands promote mastery, personal growth, and future gains.
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
@@
 @gerich2017relevance, for instance, found that employee well-being was, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
-To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, @podsakoff2007differential meta-analysis supported the original assertion of @cavanaugh2000empirical such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.
+To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, @podsakoff2007differential's meta-analysis supported the original assertion of @cavanaugh2000empirical such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.
 
@@
 15, @pejtersen2010second] and burnout [“the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work”, p.
-197; @kristensen2005copenhagen].
-Utilizing the job demands-resources theory, transactional theory of stress, and the challenge-hindrance framework, we propose that the number of job characteristics appraised as “challenge demands” (i.e., promote mastery, personal growth, and future gains) would activate a positive state – that of engagement.
-In contrast, number of characteristics of one’s job appraised as a hindrance demand (i.e., inhibit growth, learning and goal achievement) would activate a negative state – here, stress.
+197, @kristensen2005copenhagen].
+Utilizing the job demands-resources theory, the transactional theory of stress, and the challenge-hindrance framework, we propose that the number of job characteristics appraised as “challenge demands” (i.e., promote mastery, personal growth, and future gains) would activate a positive state – that of engagement.
+In contrast, number of characteristics of one’s job appraised as a hindrance demand (i.e., inhibit growth, learning and goal achievement) would activate a negative state – here, resulting in stress and/or burnout.
 
-> *Hypothesis 1a-1c*: Total number of resources are positively associated with engagement (1a), and negatively associated with stress (1b) and burnout (1c).
+> *Hypothesis 1a-1c*: A greater overall quantity of resources is positively associated with engagement (1a), and negatively associated with stress (1b) and burnout (1c)
 
-> *Hypothesis 2a-2c*: Total number of  challenge demands are positively associated with engagement (2a), and negatively associated with stress (2b) and burnout (2c).
+> *Hypothesis 2a-2c*: A greater overall quantity of challenge demands is positively associated with engagement (2a), and negatively associated with stress (2b) and burnout (2c).
 
-> *Hypothesis 3a-3c*: Total number of hindrance demands are negatively associated with engagement (3a), and positively associated with stress (3b) and burnout (3c).
+> *Hypothesis 3a-3c*: A greater overall quantity of hindrance demands is negatively associated with engagement (3a), and positively associated with stress (3b) and burnout (3c).
 
@@
 
-  We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model [@bakker2017job; @bakker2003dual; @demerouti2001job], but from within the unifying framework of O\*Net.
-Here, we focus on the relationship between O\*Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S.
-workforce representative sample.
+  We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model [@bakker2017job; @bakker2003dual; @demerouti2001job], but from within the comprehensive framework of O\*Net.
+Here, we focus on the relationship between O\*Net delineated job components and employee levels of job engagement, job stress, and burnout within a workforce representative sample.
 
@@
 
-  Characteristics, Demands, and Resources.
+### Characteristics, Demands, and Resources.
+
 Our analyses included items within O\*Net’s classifications of “work activity”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context”: 5) Interpersonal Relationships (14 statements), 6) Physical Work Conditions (30 statements)1, and 7) Structural Job Characteristics (13 statements).
@@
 
-> *Stress*. Three items taken from the Copenhagen Psychosocial Questionnaire (@burr_third_2019). Obtained alpha was .85 in this sample.
+### Stress.
 
-> *Burnout*. Four items were taken from the Copenhagen Psychosocial Questionnaire (@burr_third_2019). Alpha was 0.85 in this sample.
+Three items taken from the Copenhagen Psychosocial Questionnaire [@burr_third_2019]. Obtained alpha was .85 in this sample.
 
->*Engagement*.
-The 18-item engagement measure was recently developed (@engage_2022), with the authors specifying three subscales which yielded current sample α’s of 0.68 (absorption) and 0.80 (vigor), and 0.90 (dedication).
+### Burnout.
+
+Four items were taken from the Copenhagen Psychosocial Questionnaire [@burr_third_2019]. Alpha was 0.85 in this sample.
+
+### Engagement.
+
+The 18-item engagement measure was recently developed [@engage_2022], with the authors specifying three subscales which yielded current sample α’s of 0.68 (absorption) and 0.80 (vigor), and 0.90 (dedication).
 For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, alpha = 0.91).
@@
 
-  Data were collected through Prolific, a data collection platform.
 An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
@@
 To further explore H1-H3, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
-First, regarding engagement (F(3, 564) = 26.41, p < .001), the total resources was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table \ref{tab:regression_table_eng}).
-Next, stress was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 2.47, *p* = .060 (see Table \ref{tab:regression_table_str}).
-Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 1.10, *p* = .349.
+First, regarding engagement ($F_{(3, 564)}$ = 26.41, p < .001), the total resources was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table \ref{tab:regression_table_eng}).
+Next, stress was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$ = 2.47, *p* = .060 (see Table \ref{tab:regression_table_str}).
+Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$= 1.10, *p* = .349.
 See Table \ref{tab:regression_table_bur}.

### 2022-10-07 SIOP2023/Counts/Submission_ResourceCount.tex
first full pass through (Kulas)

@@
 
-Correspondence concerning this article should be addressed to Alicia Stachowski. E-mail: \href{mailto:stachowskia@uwstout.edu}{\nolinkurl{stachowskia@uwstout.edu}}
+Correspondence concerning this article should be addressed to Alicia Stachowski, Anytown, USA. E-mail: \href{mailto:stachowskia@uwstout.edu}{\nolinkurl{stachowskia@uwstout.edu}}
 
@@
 
-A plethora of research applying the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker \& Demerouti, 2017) underscores the importance of work characteristics on the experience of motivation and strain.
-However, much of our existing research on this topic assumes that certain characteristics are resources and others are generally considered demands.
-This study explores how individual perceptions of these work characteristics relate to engagement, stress, and burnout by asking respondents to indicate (of the characteristics that apply to their jobs) how much each is a resource, challenge, or hindrance demand.
-Amount of perceived resources, challenges, and hindrances can then be associated with engagement, stress, and burnout.
+A plethora of research applying the job demands-resources model (Demerouti et al., 2001) and theory (Bakker \& Demerouti, 2017) underscores the importance of work characteristics on the experience of motivation and strain.
+However, much of our existing research on this topic assumes that certain characteristics are resources (for example, autonomy) while others (such as deadlines) are generally considered demands.
+This study explores how individual perceptions of work characteristics relate to work-related outcomes by asking respondents to indicate (of the characteristics that apply to their jobs) how much each is experienced to be a resource, challenge, or hindrance.
+That is, we allow for the circumstance that the same characteristic may be perceived by some to be a resource as well as a demand.
+We then evaluate associations between resources and demands as well as probing for subsequent associations with engagement, stress, and burnout.
 
@@
 The theoretical foundation for this study is the job demands-resources theory (Demerouti et al., 2001).
-Using this theory, we can model both work environment and job characteristics via job resources and demands.
+This theory posits that the perception of a characteristic of one's job as a resource or demand activates one of two unique processes: either health impairment or motivation (Bakker \& Demerouti, 2014).
+Demanding job characteristics are frequently associated with negative outcomes (e.g., health impairment, Bakker et al., 2003), whereas resources have been associated with positive organizational outcomes like engagement and motivation (Bakker et al., 2007).
 Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain {[}e.g., high work pressure; Demerouti et al.
-(2001){]}.
-
-The perception of a characteristic of one's job as a resource or demand activates one of two unique processes: either health impairment or motivation (Bakker \& Demerouti, 2014).
-Demanding job characteristics are frequently associated with negative outcomes {[}e.g., health impairment process; Bakker et al.
-(2003){]}, whereas job characteristics considered resources have been associated with positive organizational outcomes like engagement and motivation (Bakker et al., 2007).
+In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure, Demerouti et al., 2001).
 
 \hypertarget{an-added-complexity-perception-appraisal-of-work-characteristics-might-matter}{%
-\subsection{An Added Complexity: Perception (Appraisal) of Work Characteristics Might Matter}\label{an-added-complexity-perception-appraisal-of-work-characteristics-might-matter}}
+\subsubsection{An Added Complexity: Perception (Appraisal) of Work Characteristics Might Matter}\label{an-added-complexity-perception-appraisal-of-work-characteristics-might-matter}}
 
-The above description speaks to one of two distinct processes being activated, presumably based on one's assessment of how a work characteristics makes them feel (e.g., consider the different reactions employees may have to being nominated to give a speech at an upcoming company event).
-Thus, although some research on job demands in particular is based on a priori classifications of demands (Searle \& Auton, 2015), the appraisal of any work characteristic as a demand or resource is quite subjective.
+The above description speaks to one of two distinct processes being activated, presumably based on one's appraisal of how a work characteristics makes them feel (e.g., consider the different reactions two different employees may have to being nominated to give a speech at an upcoming company event).
+Thus, although some research on job demands in particular is based on \emph{a priori} classifications of demands (Searle \& Auton, 2015), the appraisal of any work characteristic as a demand or resource is actually subjective.
 The literature on the experience of stress explains how such individual differences in appraisal are possible.
-Specifically, the transactional theory of stress and coping states that people cognitively appraise stimuli in their environments on a continuous basis (Lazarus \& Folkman, 1984).
+Specifically, the transactional theory of stress and coping states that people cognitively appraise stimuli in their environments on a continual basis (Lazarus \& Folkman, 1984).
 During this process, meaning is assigned to stimuli.
-If the above employee appraised the upcoming speech as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping (e.g., attempting to decline, asking for help in writing the speech).
+If our example fictional employee appraised the upcoming speech as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping (e.g., attempting to decline, asking for help in writing the speech).
 From that point, the cycle of appraisal continues based on the action to cope with the stressor (Lazarus \& Folkman, 1984).
@@
 \hypertarget{could-a-work-demand-be-appraised-positively-the-challenge-hindrance-framework}{%
-\subsection{Could a Work Demand be Appraised Positively?: The Challenge-Hindrance Framework}\label{could-a-work-demand-be-appraised-positively-the-challenge-hindrance-framework}}
+\subsubsection{Could a Work Demand be Appraised Positively?: The Challenge-Hindrance Framework}\label{could-a-work-demand-be-appraised-positively-the-challenge-hindrance-framework}}
 
-Although the word ``stress'' often connotes something negative,Selye (1936) defined stress generically as a response to change.
+Although the word ``stress'' often connotes something negative, Selye (1936) defined stress generically as a response to change.
 For instance, the example above describes an employee who appraises being nominated to give a speech as a negative stressor.
 However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
-The terms associated with the two different appraisals of the stressor described here are challenge and hindrance demands (Cavanaugh et al., 2000) Specifically, challenge demands promote mastery, personal growth, and future gains.
+The terms associated with the two different appraisals of the stressor described here can be accomodated within the context of the JDR theory as ``challenge'' and ``hindrance'' demands (Cavanaugh et al., 2000) Specifically, challenge demands promote mastery, personal growth, and future gains.
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
@@
 To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, Podsakoff et al.
-(2007) meta-analysis supported the original assertion of Cavanaugh et al.
+(2007)'s meta-analysis supported the original assertion of Cavanaugh et al.
 (2000) such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.
@@
 The brief review above provides theoretical and empirical support for the connection between resources and positive organizational outcomes, and between demands and negative outcomes.
-Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement (``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption,'' Schaufeli et al., 2002), workplace stress (``an individual state characterized by a combination of high arousal and displeasure,'' p.~15, Pejtersen et al., 2010) and burnout {[}``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work'', p.~197; Kristensen et al.
-(2005){]}.
-Utilizing the job demands-resources theory, transactional theory of stress, and the challenge-hindrance framework, we propose that the number of job characteristics appraised as ``challenge demands'' (i.e., promote mastery, personal growth, and future gains) would activate a positive state -- that of engagement.
-In contrast, number of characteristics of one's job appraised as a hindrance demand (i.e., inhibit growth, learning and goal achievement) would activate a negative state -- here, stress.
+Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement (``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption,'' Schaufeli et al., 2002), workplace stress (``an individual state characterized by a combination of high arousal and displeasure,'' p.~15, Pejtersen et al., 2010) and burnout (``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work,'' p.~197, Kristensen et al., 2005).
+Utilizing the job demands-resources theory, the transactional theory of stress, and the challenge-hindrance framework, we propose that the number of job characteristics appraised as ``challenge demands'' (i.e., promote mastery, personal growth, and future gains) would activate a positive state -- that of engagement.
+In contrast, number of characteristics of one's job appraised as a hindrance demand (i.e., inhibit growth, learning and goal achievement) would activate a negative state -- here, resulting in stress and/or burnout.
 
 \begin{quote}
-\emph{Hypothesis 1a-1c}: Total number of resources are positively associated with engagement (1a), and negatively associated with stress (1b) and burnout (1c).
+\emph{Hypothesis 1a-1c}: A greater overall quantity of resources is positively associated with engagement (1a), and negatively associated with stress (1b) and burnout (1c)
 \end{quote}
@@
 \begin{quote}
-\emph{Hypothesis 2a-2c}: Total number of challenge demands are positively associated with engagement (2a), and negatively associated with stress (2b) and burnout (2c).
+\emph{Hypothesis 2a-2c}: A greater overall quantity of challenge demands is positively associated with engagement (2a), and negatively associated with stress (2b) and burnout (2c).
 \end{quote}
@@
 \begin{quote}
-\emph{Hypothesis 3a-3c}: Total number of hindrance demands are negatively associated with engagement (3a), and positively associated with stress (3b) and burnout (3c).
+\emph{Hypothesis 3a-3c}: A greater overall quantity of hindrance demands is negatively associated with engagement (3a), and positively associated with stress (3b) and burnout (3c).
 \end{quote}
@@
 
-We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (Bakker et al., 2003; Bakker \& Demerouti, 2017; Demerouti et al., 2001), but from within the unifying framework of O*Net.
-Here, we focus on the relationship between O*Net delineated job components and employee levels of job engagement, job stress, and burnout with a U.S.
-workforce representative sample.
+We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model (Bakker et al., 2003; Bakker \& Demerouti, 2017; Demerouti et al., 2001), but from within the comprehensive framework of O*Net.
+Here, we focus on the relationship between O*Net delineated job components and employee levels of job engagement, job stress, and burnout within a workforce representative sample.
 
@@
 
-Characteristics, Demands, and Resources.
+\hypertarget{characteristics-demands-and-resources.}{%
+\subsubsection{Characteristics, Demands, and Resources.}\label{characteristics-demands-and-resources.}}
+
 Our analyses included items within O*Net's classifications of ``work activity'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'': 5) Interpersonal Relationships (14 statements), 6) Physical Work Conditions (30 statements)1, and 7) Structural Job Characteristics (13 statements).
@@
 
-\begin{quote}
-\emph{Stress}. Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al. (2019)). Obtained alpha was .85 in this sample.
-\end{quote}
+\hypertarget{stress.}{%
+\subsubsection{Stress.}\label{stress.}}
 
-\begin{quote}
-\emph{Burnout}. Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al. (2019)). Alpha was 0.85 in this sample.
-\end{quote}
+Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Obtained alpha was .85 in this sample.
 
-\begin{quote}
-\emph{Engagement}.
-The 18-item engagement measure was recently developed (Russell et al.
-(2022)), with the authors specifying three subscales which yielded current sample α's of 0.68 (absorption) and 0.80 (vigor), and 0.90 (dedication).
+\hypertarget{burnout.}{%
+\subsubsection{Burnout.}\label{burnout.}}
+
+Four items were taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019). Alpha was 0.85 in this sample.
+
+\hypertarget{engagement.}{%
+\subsubsection{Engagement.}\label{engagement.}}
+
+The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample α's of 0.68 (absorption) and 0.80 (vigor), and 0.90 (dedication).
 For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, alpha = 0.91).
-\end{quote}
 
@@
 
-Data were collected through Prolific, a data collection platform.
 An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
@@
 To further explore H1-H3, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
-First, regarding engagement (F(3, 564) = 26.41, p \textless{} .001), the total resources was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table \ref{tab:regression_table_eng}).
-Next, stress was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 2.47, \emph{p} = .060 (see Table \ref{tab:regression_table_str}).
-Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, F(3, 564) = 1.10, \emph{p} = .349.
+First, regarding engagement (\(F_{(3, 564)}\) = 26.41, p \textless{} .001), the total resources was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table \ref{tab:regression_table_eng}).
+Next, stress was not predicted by total resources, challenge, or hindrance demands, \(F_{(3, 564)}\) = 2.47, \emph{p} = .060 (see Table \ref{tab:regression_table_str}).
+Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, \(F_{(3, 564)}\)= 1.10, \emph{p} = .349.
 See Table \ref{tab:regression_table_bur}.

### 2022-10-07 SIOP2023/SIOP_PROCESS.Rmd
reviewed methods/results

@@
 
-bibliography      : ["r-references.bib", "SIOP_PROCESS.bib", "jdr.bib", "jobdemands_resources_bibtex.bib"]
+bibliography      : ["r-references.bib", "SIOP_PROCESS.bib", "jobdemands_resources_bibtex.bib"]
 
@@
 
-These data were taken from a larger study on JD-R theory as it applies to O\*NET items.
-Our specific interest in the current study is in whether or not perceptions of hindrance demands are postitively related to perceived stress, and whether or not this relationship is moderated by perceived resources.
+These data were taken from a larger study on JD-R theory as it applies to O\*NET items, particularly Proposition 3 of the JD-R model - that job resources can buffer the impact of job demands on strain.
+The interaction between job resources and demands has been heavily studied with regard to a range of outcomes.
+For example @bakker2010beyond found that resources (e.g., learning opportunities, autonomy, leader support) predicted both task enjoyment and organizational commitment even under conditions of high demands.
+Much of the research, however, has focused on stress/strain and burnout outcomes.
+For example, @bakker2005job found that job resources lessen the impact of demands on burnout in  a large sample of employees working in higher education, and @xanthopoulou2007job found similar patterns in a sample of home care organization employees.
+
+Our specific interest in the current study is in whether or not *perceptions* of hindrance demands are postitively related to perceived stress, and whether or not this relationship is moderated by perceived resources.
 The Job demands-Resources theory would suggest resources would buffer this relationship.
@@
 We do have some existing evidence that this occurs with other outcomes beyond stress.
-For example, Tadic et al.
-(2015) found that daily hindrance job demands were negatively related to both positive affect and engagement in a sample of primary school teachers.
+For example, @tadic2015challenge found that daily hindrance job demands were negatively related to both positive affect and engagement in a sample of primary school teachers.
 Daily job resources, in this sample, buffered the relationships between hindrances and affect and engagement.
@@
 
+We sampled from a Prolific panel, resulting in 785 individuals who initially 166 accessed the survey link.
+Of those, 112 indicated that they were not interested, had more 167 than 200 missing responses, or had 20 or more identical consecutive sequential responses 168 (Yentes & Wilhelm, 2021).
 There were a total of 568 respondents, of which 13.57% had been in their referent job less than 6 months, 19.20% between 6 months and a year, 49.12% between one and five years, 13.27% between 5 and 10 years, and 4.87% more than 10 years.Their ages ranged from 18 to 65 with an average of 28.18 years old (*SD* = 7.53).
@@
 
-The primary goal of this project was to further explore the role of perceived resources on the hindrance-stress relationship.
+The primary goal of this project was to further explore the role of perceived resources on the hindrance-stress relationship using O\*Net characteristics.
+While we have plentiful evidence that resources can buffer the effects of a variety of job demands on burnout, this project focuses on subjective experiences of resources and demands, focusing on demands rated as challenges and hindrances.
 As expected, the results suggest a positive relationship between perceived hindrances and stress (H1).
@@
 First, while the use of O\*Net items is a strength of the paper, practical considerations limited the number of job characteristics we could include in our survey.
-Because our focus was on O*Net items and our procedure was time and effort intensive, we were unable to inquire about other forms of resources (e.g., supervisor or coworker support) or demands.
-Thus, future study could explore these sources of support as resources and perhaps even compare the importance of various types of resources and their role in reducing the influence of hindrance stressors.
+Because our focus was on O\*Net items and our procedure was time and effort intensive, we were unable to inquire about other forms of resources (e.g., supervisor or coworker support) or demands.
+Thus, future study could explore these sources of support as resources and perhaps even compare the importance of various types of resources and their role in reducing the influence of hindrance stressors using O\*Net characteristics.
 Is it overall perceptions of having more resources that makes up for hindrances, or could it be that certain resources carry more weight?

### 2022-10-08 SIOP2023/SIOP_PROCESS.Rmd

@@
 While their study not did include resources, it documents individual differences in how people perceive stressors at work.
-Although not the primary focus of their paper, @sonnega_comparison_2018 compared self-reported (subjective) ratings of degree of physical demand, stress, and need for intense concentration from the Health and Retirement Study with objective ratings from O*Net.
-Correlations physical demand (r = .52), stress (r = .10), and need for intense concentration (r = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than we tend to think.
+Although not the primary focus of their paper, @sonnega_comparison_2018 compared self-reported (subjective) ratings of degree of physical demand, stress, and need for intense concentration from the Health and Retirement Study with objective ratings from O\*Net.
+Correlations physical demand (*r* = .52), stress (*r* = .10), and need for intense concentration (*r* = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than we tend to think.
 While the above two studies provide evidence for variability in perception of demands, @schmitz_interpreting_2019 captured subjective and objective resources in their study of retirement.
-Correlations of composite variables between subjective and objective measures for the resources of autonomy (r = .12.
-p > .01), recognition of work (r = .07, p > .01), and decision freedom (r = .08, p > .01), while significant, certainly do not reflect high levels of overlap.
+Correlations of composite variables between subjective and objective measures for the resources of autonomy (*r* = .12.
+p > .01), recognition of work (*r* = .07, p > .01), and decision freedom (*r* = .08, p > .01), while significant, certainly do not reflect high levels of overlap.
 We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees.
@@
 
-```{r getdata}
+```{r getdata, include = FALSE}
 
@@
 
-```{r analyses, fig.cap="Interaction between hindrances and resources as predictors of stress"}
-
+```{r process_interaction, include=FALSE}
 process(activate=1)
 results <- process(data=data, y="stress", x="overall.hindrance", w="overall.resource", model=1, jn=1, plot=1, save=2)
+```
+
+```{r analyses, fig.cap="Interaction between hindrances and resources as predictors of stress"}
 
@@
 As can be seen in Figure 1, those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources.
-As such, these results provide some evidence that the resources do moderate the relationship between hindrance stressors
+As such, these results provide some evidence that the resources do moderate the relationship between hindrance stressors.
 
@@
 While intuitive, it is important to replicate this finding before we explore the impact of perceived resources, which arguably, is something that employers may have more leverage to control than hindrance stressors.
-Second, the results serve to support the assertion that resources change the relationship between hindrances and stressors such that the connection between the two is dimished as resources increase (H2).
-While not hypothesized or presented above, the authors did run a regression on the challenge-stress relationship with resources as a moderator, with the assumption that resources wouldn't influence a direct relationship, and did find that to be the case.
-The Job-demands Resources Theory [JD-R; @demerouti2001job] suggests that resources would buffer the negative impact between demands and stress, and by extension, given the more traditional conceptualization of demands would be aligned with hindrance demands.
+Second, the results serve to support the assertion that resources change the relationship between hindrances and stressors such that the connection between the two is diminished as resources increase (H2).
+While not hypothesized or presented above, the authors did run a regression on the challenge hindrance-stress relationship with resources as a moderator, with the assumption that resources would not moderate the relationship.
+The findings, indeed, did not indicate a moderated relationship in this case.
+It appears that resources are of benefit particularly when demands are high.
+In particular, the Job-demands Resources Theory [JD-R; @demerouti2001job] suggests that resources would buffer the negative impact between demands and stress, and by extension, given the more traditional conceptualization of demands would be aligned with hindrance demands.
 
 These findings have implications worth considering.
-In a practical sense wihtin the workplace, they speak to the ever present need to ensure employees have sufficient resources.
+In a practical sense within the workplace, they speak to the ever present need to ensure employees have sufficient resources.
 Our project focused on the characteristics of one's work specifically, and in line with the literature cited above, studied the ratings or perceptions of resources and demands to account for individual differences in the way employees appraise components of their work.
@@
 Is it overall perceptions of having more resources that makes up for hindrances, or could it be that certain resources carry more weight?
-Second, our focus here was on the outcome of stress, but it may also be of value to consider what the interaction between resources and hindrances looks like on other outcomes of interest in a work context (e.g., commitment, motivation, engagement, intent to quit).
+Second, our focus here was on the outcome of stress, but it may also be of value to consider what the interaction between ratings of O\*Net characteristics as resources and hindrances looks like on other outcomes of interest in a work context (e.g., commitment, motivation, engagement, intent to quit).
 

### 2022-10-08 SIOP2023/SIOP_PROCESS.Rmd
correlation table Study 1

@@
 classoption       : "man"
-output            : papaja::apa6_word
+output            : papaja::apa6_pdf
 ---
@@
 
-> *Resources and Hindrances*.
+### Resources and Hindrances.
+
 To guage resources and hindrances, we used 98 statements taken directly from O\*Net’s “activity” and “context” classifications.
@@
 
-> *Stress*.
+### Stress.
+
 Three items taken from the Copenhagen Psychosocial Questionnaire (@burr_third_2019) captured stress (e.g., "How often have you had problems relaxing because of your job?").
@@
 
+```{r cortab}
+
+data_new <- data
+
+names(data_new)[names(data_new) == "stress"] <- "Stress"
+names(data_new)[names(data_new) == "overall.challenge"] <- "Challenge"
+names(data_new)[names(data_new) == "overall.hindrance"] <- "Hindrance"
+names(data_new)[names(data_new) == "overall.resource"] <- "Resource"
+
+r <- corx::corx(data_new, x =c("Stress", "Challenge", "Hindrance", "Resource"), y =c("Stress", "Challenge", "Hindrance", "Resource"),            
+                triangle = "lower",
+                stars = c(0.05, 0.01, 0.001),
+                describe = c(`$M$` = mean, `$SD$` = sd))
+
+papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table,
+                  caption = "Challenge, hindrance, and resource bivariate correlations with stress.",
+                  escape = FALSE)
+```
+
 Following data cleaning and preparation, we computed correlations among the study variables.
-See Table 1.
-With regard to H1, which predicted a positive association between perceived hindrance stressors and stress, a positive relationship was observed, *r* = , *p* = .
-Thus, support was found for H1.
-
-Next, to explore H2, a moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1 [@hayes2022].
-First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, F(3, 564) = 3.29, *p* = .020.
-The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, F(3, 564) = 3.51, *p* = .061, providing tentative support for H2.
-As can be seen in Figure 1, those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources.
-As such, these results provide some evidence that the resources do moderate the relationship between hindrance stressors.
+See Table \@ref(tab:cortab).
+With regard to H1, which predicted a positive association between perceived hindrance stressors and stress, a small positive relationship was observed, *r* = .09, *p* < .05.
+Thus, "weak" support was found for H1.
 
@@
 ```
+
+Next, to explore H2, a moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1 [@hayes2022, see Table \@ref(tab:table)].
+First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, F(3, 564) = 3.29, *p* = .020.
+The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, F(3, 564) = 3.51, *p* = .061, providing tentative support for H2.
+As can be seen in Figure 1, those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources.
+As such, these results provide some evidence that the resources do moderate the relationship between hindrance stressors.
 

### 2022-10-08 SIOP2023/SIOP_PROCESS.tex
correlation table Study 1

@@
 \hypersetup{
-  pdftitle={JD-R Theory: Using the Content of the O*Net},
-  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
+  pdftitle={Testing the JD-R Theory: Using the Content of the O*Net},
+  pdfauthor={Alicia A. Stachowski1 \& John T. Kulas2},
   pdflang={en-EN},
@@
 \makeatother
-\shorttitle{SIOP\_Hindrances-Resources Interaction}
+
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
 \keywords{keywords\newline\indent Word count: X}
@@
 \usepackage{csquotes}
-\ifxetex
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
-\title{JD-R Theory: Using the Content of the O*Net}
-\author{First Author\textsuperscript{1} \& Ernst-August Doelle\textsuperscript{1,2}}
+\title{Testing the JD-R Theory: Using the Content of the O*Net}
+\author{Alicia A. Stachowski\textsuperscript{1} \& John T. Kulas\textsuperscript{2}}
 \date{}
+
+\shorttitle{SIOP\_Hindrances-Resources Interaction}
 
@@
 
-The authors made the following contributions. First Author: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Ernst-August Doelle: Writing - Review \& Editing.
+The authors made the following contributions. Alicia A. Stachowski: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; John T. Kulas: Writing - Review \& Editing.
 
-Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
+Correspondence concerning this article should be addressed to Alicia A. Stachowski, Postal address. E-mail: \href{mailto:stachowskia@uwstout.edu}{\nolinkurl{stachowskia@uwstout.edu}}
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Wisconsin - Stout\\\textsuperscript{2} eRg}
 
@@
 (2001){]} has received wide support across contexts and varied research questions.
-We add to this literature via two routes: by utilizing some of the job characteristics in the popular O*Net, and by focusing on perceptions of all characteristics as demands/resources.
-Specifically, we explore the interaction between perceptions of job demands and resources on the outcome of stress across a wide range of occupations.
+We extend the literature by 1) exploring the interaction between \emph{perceptions} of job demands and resources on the outcome of stress using job characteristics in the popular O*Net and 2) by considering also the appraisal of demands as challenge or hindrance stressors.
 Here, respondents made a series of evaluations that used: direct O*Net terminology (both descriptor and response option), and JD-R influenced ratings of demand and hindrance stressors.
@@
 
-Cognitively, the perception of an element of one's job as a resource or demand activates one of two unique processes: health impairment (resulting from demands) or motivation {[}resulting from resources; A.
-B.
-Bakker and Demerouti (2014){]}.
-Demanding job characteristics are frequently associated with negative outcomes (e.g., A.
-Bakker et al., 2003), whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation (A.
-B.
-Bakker et al., 2007).
-Our focus is on whether or not having more resources serves as a buffer to the demand-stress relationship.
-One of the stickier elements of this question surrounds the subjective nature of demands/resources, which we address next.
+Cognitively, the perception of an element of one's job as a resource or demand activates one of two unique processes: health impairment (resulting from demands) or motivation {[}resulting from resources; Bakker and Demerouti (2014){]}.
+Demanding job characteristics are frequently associated with negative outcomes (e.g., Bakker et al., 2003), whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation (Bakker et al., 2007).
+However, a related line of research emphasizes a distinction between two types of demands - that of ``challenge'' and ``hindrance'' demands, suggesting that employees may evaluate stressors in different ways.
 
@@
 \subsection{Objective vs.~Subjective Nature of Demands and Resources: The Role of Appraisal}\label{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisal}}
+
+The stress literature speaks to the key consideration of the way employees appraise situations or circumstances - in this case, our focus will be on work characteristics.
+The transactional theory of stress and coping suggests that people cognitively appraise stimuli in their environments on a continuous basis (Lazarus \& Folkman, 1984).
+For example, two employees both informed that they need to step in and assume the responsibilities of a coworker in their absence may react differently to this job demand.
+One may feel quite paralyzed by the added or novel tasks, while the other may embrace it as an exciting new challenge.
+The terms associated with the two different appraisals of the same stressor are ``challenge'' and ``hindrance'' demands (Cavanaugh et al., 2000) Challenge demands promote mastery, personal growth, and future gains.
+Hindrance demands, by definition, inhibit growth, learning and goal achievement.
+Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes (e.g., Cavanaugh et al., 2000).
+Our focus here will be on the connection between hindrance demands specifically, and their association with reported stress.
+More specifically, our interest here is whether or not the negative hindrance association we typically observe between demands and stress can be buffered by perceived resources.
 
@@
 (2018) compared self-reported (subjective) ratings of degree of physical demand, stress, and need for intense concentration from the Health and Retirement Study with objective ratings from O*Net.
-Correlations physical demand (r = .52), stress (r = .10), and need for intense concentration (r = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than we tend to think.
+Correlations physical demand (\emph{r} = .52), stress (\emph{r} = .10), and need for intense concentration (\emph{r} = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than we tend to think.
 While the above two studies provide evidence for variability in perception of demands, Schmitz et al.
 (2019) captured subjective and objective resources in their study of retirement.
-Correlations of composite variables between subjective and objective measures for the resources of autonomy (r = .12.
-p \textgreater{} .01), recognition of work (r = .07, p \textgreater{} .01), and decision freedom (r = .08, p \textgreater{} .01), while significant, certainly do not reflect high levels of overlap.
+Correlations of composite variables between subjective and objective measures for the resources of autonomy (\emph{r} = .12.
+p \textgreater{} .01), recognition of work (\emph{r} = .07, p \textgreater{} .01), and decision freedom (\emph{r} = .08, p \textgreater{} .01), while significant, certainly do not reflect high levels of overlap.
 We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees.
@@
 This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated.
-These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move,'' Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
+These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move'', Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
 It is also useful to employers by providing them with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
@@
 
-These data were taken from a larger study on JD-R theory as it applies to O*NET items.
+These data were taken from a larger study on JD-R theory as it applies to O*NET items, particularly Proposition 3 of the JD-R model - that job resources can buffer the impact of job demands on strain.
+The interaction between job resources and demands has been heavily studied with regard to a range of outcomes.
+For example Bakker et al.
+(2010) found that resources (e.g., learning opportunities, autonomy, leader support) predicted both task enjoyment and organizational commitment even under conditions of high demands.
+Much of the research, however, has focused on stress/strain and burnout outcomes.
+For example, Bakker et al.
+(2005) found that job resources lessen the impact of demands on burnout in a large sample of employees working in higher education, and Xanthopoulou et al.
+(2007) found similar patterns in a sample of home care organization employees.
+
 Our specific interest in the current study is in whether or not \emph{perceptions} of hindrance demands are postitively related to perceived stress, and whether or not this relationship is moderated by perceived resources.
 The Job demands-Resources theory would suggest resources would buffer this relationship.
-We do have some existing evidence that this occurs with other outcomes.
-For example, Tadic et al.~(2015) found that daily hindrance job demands were negatively related to both positive affect and engagement in a sample of primary school teachers.
+In fact, a rather large body of empirical evidence supports this assertion (e.g., see Bakker \& Demerouti, 2017 for a historical review).
+We do have some existing evidence that this occurs with other outcomes beyond stress.
+For example, Tadić et al.
+(2015) found that daily hindrance job demands were negatively related to both positive affect and engagement in a sample of primary school teachers.
 Daily job resources, in this sample, buffered the relationships between hindrances and affect and engagement.
@@
 
-NOTES:
-Add: Challenge versus hindrance job demands and wellbeing: A diary study on the moderating role of job resources
-Add a correlation table to speak to H1. Reference H1 and H2 in the results section.
-
 \hypertarget{methods}{%
 \section{Methods}\label{methods}}
-
-There were 568 respondents.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
-  568 respondents, 13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.
-\item
-  Ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53).
-\item
-  Gender: female (52.58\%) or male (46.83\%).
-\item
-  Job classifications: International Standard Classification of Occupations (ISCO) via the package \texttt{labourR} (\textbf{R-labourR?}), and further categorized into ``knowledge'' (n = 320) versus ``skilled'' (n = 214) occupations with knowledge workers being identified via ISCO classifications of: 1) professionals, and 2) managers.
-\end{itemize}
-
-The data for this study were collected through Prolific sample,18 or older and holding a full-time or part-time job.
-Participants were asked to think about their primary job while answering the survey, and upon completion each participant was compensated in the amount of six US dollars.
+We sampled from a Prolific panel, resulting in 785 individuals who initially 166 accessed the survey link.
+Of those, 112 indicated that they were not interested, had more 167 than 200 missing responses, or had 20 or more identical consecutive sequential responses 168 (Yentes \& Wilhelm, 2021).
+There were a total of 568 respondents, of which 13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.Their ages ranged from 18 to 65 with an average of 28.18 years old (\emph{SD} = 7.53).
+Over half, 52.58\% identified as female, and 46.83\% identified as male.
 
@@
 
-We used 98 statements taken directly from O\(^{*}\)Net's ``activity'' and ``context'' classifications.
+\hypertarget{resources-and-hindrances.}{%
+\subsubsection{Resources and Hindrances.}\label{resources-and-hindrances.}}
+
+To guage resources and hindrances, we used 98 statements taken directly from O*Net's ``activity'' and ``context'' classifications.
 Each of the 98 descriptors has potentially unique response categories, but scaling was consistently 1 (low) to 5 (high).
-Subsequent to these self-evaluations, respondents were asked to rate elements in terms of 1) \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
+Subsequent to these self-evaluations, respondents were asked to rate elements in terms of resources (``\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development''), challenges, (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains'') and hindrances (``\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment'').
+For each category (e.g., resources), a means was computed across items that applied to one's role, and thus, mean scores could range from 1 to 5.
+
+\hypertarget{stress.}{%
+\subsubsection{Stress.}\label{stress.}}
+
+Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al.
+(2019)) captured stress (e.g., ``How often have you had problems relaxing because of your job?'').
+Responses were made on a 5-point scale ranging from ``not at all'' to ``all the time''.
+Alpha was .85 in this sample.
 
@@
 
-We used PROCESS for R Version 4.1.1 (Hayes, 2022) to assess the extent to which the relationship between demands and stress are moderated by resources.
+The data presented here were part of a larger study on the Job-demands Resources Model using O*Net.
+Data were collected through Prolific, a data collection platform.
+An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
+Eligibility requirements included being 18+ and holding either a full-time or part-time job.
+Participants then voluntarily chose to respond to the survey.
+The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes.
+Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified.
+Thus, if a respondent indicated that 5 of the characteristics were not part of their job, they were not subsequently asked to rate the level of resource, challenge, or hindrance a given item presented to them.
+For items that were a part of their jobs, they were then asked to report how much a characteristic was a resource, and then how much each characteristic was a hindrance, and finally, how much each item was a challenge.
+Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
 
@@
 \section{Results}\label{results}}
-
-\begin{verbatim}
-## 
-## ********************* PROCESS for R Version 4.1.1 ********************* 
-##  
-##            Written by Andrew F. Hayes, Ph.D.  www.afhayes.com              
-##    Documentation available in Hayes (2022). www.guilford.com/p/hayes3   
-##  
-## *********************************************************************** 
-##  
-## PROCESS is now ready for use.
-## Copyright 2022 by Andrew F. Hayes ALL RIGHTS RESERVED
-## Workshop schedule at http://haskayne.ucalgary.ca/CCRAM
-## 
-\end{verbatim}
-
-\begin{verbatim}
-## 
-## ********************* PROCESS for R Version 4.1.1 ********************* 
-##  
-##            Written by Andrew F. Hayes, Ph.D.  www.afhayes.com              
-##    Documentation available in Hayes (2022). www.guilford.com/p/hayes3   
-##  
-## *********************************************************************** 
-##                          
-## Model : 1                
-##     Y : stress           
-##     X : overall.hindrance
-##     W : overall.resource 
-## 
-## Sample size: 568
-## 
-## 
-## *********************************************************************** 
-## Outcome Variable: stress
-## 
-## Model Summary: 
-##           R      R-sq       MSE         F       df1       df2         p
-##      0.1311    0.0172    0.7790    3.2876    3.0000  564.0000    0.0205
-## 
-## Model: 
-##                       coeff        se         t         p      LLCI      ULCI
-## constant             1.2688    1.0055    1.2618    0.2075   -0.7063    3.2439
-## overall.hindrance    0.8336    0.4031    2.0677    0.0391    0.0417    1.6254
-## overall.resource     0.3319    0.2518    1.3181    0.1880   -0.1627    0.8264
-## Int_1               -0.1918    0.1024   -1.8725    0.0616   -0.3929    0.0094
-## 
-## Product terms key:
-## Int_1  :  overall.hindrance  x  overall.resource      
-## 
-## Test(s) of highest order unconditional interaction(s):
-##       R2-chng         F       df1       df2         p
-## X*W    0.0061    3.5064    1.0000  564.0000    0.0616
-## ----------
-## Focal predictor: overall.hindrance (X)
-##       Moderator: overall.resource (W)
-## 
-## Conditional effects of the focal predictor at values of the moderator(s):
-##   overall.resource    effect        se         t         p      LLCI      ULCI
-##             3.2983    0.2010    0.0802    2.5065    0.0125    0.0435    0.3586
-##             3.7402    0.1163    0.0534    2.1759    0.0300    0.0113    0.2213
-##             4.2063    0.0269    0.0594    0.4535    0.6503   -0.0897    0.1435
-## 
-## Moderator value(s) defining Johnson-Neyman significance region(s):
-##       Value   % below   % above
-##      3.8196   55.6338   44.3662
-## 
-## Conditional effect of focal predictor at values of the moderator:
-##   overall.resource    effect        se         t         p      LLCI      ULCI
-##             1.0149    0.6389    0.3003    2.1276    0.0338    0.0491    1.2288
-##             1.2078    0.6020    0.2809    2.1433    0.0325    0.0503    1.1536
-##             1.4006    0.5650    0.2615    2.1608    0.0311    0.0514    1.0785
-##             1.5935    0.5280    0.2421    2.1807    0.0296    0.0524    1.0035
-##             1.7863    0.4910    0.2228    2.2034    0.0280    0.0533    0.9287
-##             1.9791    0.4540    0.2037    2.2293    0.0262    0.0540    0.8540
-##             2.1720    0.4170    0.1846    2.2592    0.0243    0.0545    0.7796
-##             2.3648    0.3801    0.1657    2.2937    0.0222    0.0546    0.7055
-##             2.5577    0.3431    0.1470    2.3336    0.0200    0.0543    0.6318
-##             2.7505    0.3061    0.1287    2.3791    0.0177    0.0534    0.5588
-##             2.9434    0.2691    0.1108    2.4292    0.0154    0.0515    0.4867
-##             3.1362    0.2321    0.0937    2.4784    0.0135    0.0482    0.4161
-##             3.3290    0.1951    0.0778    2.5085    0.0124    0.0423    0.3479
-##             3.5219    0.1582    0.0641    2.4667    0.0139    0.0322    0.2841
-##             3.7147    0.1212    0.0543    2.2306    0.0261    0.0145    0.2279
-##             3.8196    0.1011    0.0515    1.9642    0.0500    0.0000    0.2021
-##             3.9076    0.0842    0.0507    1.6605    0.0974   -0.0154    0.1838
-##             4.1004    0.0472    0.0545    0.8662    0.3867   -0.0599    0.1543
-##             4.2933    0.0102    0.0644    0.1589    0.8738   -0.1163    0.1368
-##             4.4861   -0.0267    0.0782   -0.3421    0.7324   -0.1803    0.1268
-##             4.6790   -0.0637    0.0941   -0.6773    0.4985   -0.2485    0.1211
-##             4.8718   -0.1007    0.1112   -0.9054    0.3656   -0.3192    0.1178
-## 
-## Data for visualizing the conditional effect of the focal predictor:
-##   overall.hindrance overall.resource    stress
-##              1.6667           3.2983    2.6985
-##              2.2894           3.2983    2.8237
-##              3.2416           3.2983    3.0151
-##              1.6667           3.7402    2.7039
-##              2.2894           3.7402    2.7763
-##              3.2416           3.7402    2.8871
-##              1.6667           4.2063    2.7096
-##              2.2894           4.2063    2.7264
-##              3.2416           4.2063    2.7520
-## 
-## ******************** ANALYSIS NOTES AND ERRORS ************************ 
-## 
-## Level of confidence for all confidence intervals in output: 95
-## 
-## W values in conditional tables are the 16th, 50th, and 84th percentiles.
-\end{verbatim}
 
@@
 
-Table 1 presents correlations among the study variables of interest.
+\begin{table}[tbp]
 
-To explore H2, a moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1.
-First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, F(3, 564) = 3.29, p = .020.
-The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, F(3, 564) = 3.51, p = .061, providing tentative support for H2.
-As can be seen in Figure 1, those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources.
-Upon exploring the interaction further, it was evident that this moderated effect happened at lower, but not higher levels of resources.
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:cortab}Challenge, hindrance, and resource bivariate correlations with stress.}
+
+\begin{tabular}{llllll}
+\toprule
+ & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
+\midrule
+1. Stress & - &  &  & 2.81 & 0.89\\
+2. Challenge & -.05 & - &  & 3.73 & 0.48\\
+3. Hindrance & .09* & -.19*** & - & 2.40 & 0.75\\
+4. Resource & -.08 & .75*** & -.24*** & 3.73 & 0.47\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+Following data cleaning and preparation, we computed correlations among the study variables.
+See Table \ref{tab:cortab}.
+With regard to H1, which predicted a positive association between perceived hindrance stressors and stress, a small positive relationship was observed, \emph{r} = .09, \emph{p} \textless{} .05.
+Thus, ``weak'' support was found for H1.
 
@@
 
+Next, to explore H2, a moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1 (Hayes, 2022, see Table \ref{tab:table}).
+First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, F(3, 564) = 3.29, \emph{p} = .020.
+The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, F(3, 564) = 3.51, \emph{p} = .061, providing tentative support for H2.
+As can be seen in Figure 1, those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources.
+As such, these results provide some evidence that the resources do moderate the relationship between hindrance stressors.
+
 \hypertarget{discussion}{%
 \section{Discussion}\label{discussion}}
+
+The primary goal of this project was to further explore the role of perceived resources on the hindrance-stress relationship using O*Net characteristics.
+While we have plentiful evidence that resources can buffer the effects of a variety of job demands on burnout, this project focuses on subjective experiences of resources and demands, focusing on demands rated as challenges and hindrances.
+As expected, the results suggest a positive relationship between perceived hindrances and stress (H1).
+While intuitive, it is important to replicate this finding before we explore the impact of perceived resources, which arguably, is something that employers may have more leverage to control than hindrance stressors.
+Second, the results serve to support the assertion that resources change the relationship between hindrances and stressors such that the connection between the two is diminished as resources increase (H2).
+While not hypothesized or presented above, the authors did run a regression on the challenge hindrance-stress relationship with resources as a moderator, with the assumption that resources would not moderate the relationship.
+The findings, indeed, did not indicate a moderated relationship in this case.
+It appears that resources are of benefit particularly when demands are high.
+In particular, the Job-demands Resources Theory {[}JD-R; Demerouti et al.
+(2001){]} suggests that resources would buffer the negative impact between demands and stress, and by extension, given the more traditional conceptualization of demands would be aligned with hindrance demands.
+
+These findings have implications worth considering.
+In a practical sense within the workplace, they speak to the ever present need to ensure employees have sufficient resources.
+Our project focused on the characteristics of one's work specifically, and in line with the literature cited above, studied the ratings or perceptions of resources and demands to account for individual differences in the way employees appraise components of their work.
+From a academic research standpoint, these findings integrate three related literatures: the job-demands resources, stress appraisal, and challenge-hindrance framework to examine the experience of employees across jobs - specifically, the way that resources and hindrance demands interact on the experience of stress.
+Results align with what all three theories/frameworks would suggest.
+
+\hypertarget{limitations-and-future-directions}{%
+\subsection{Limitations and Future Directions}\label{limitations-and-future-directions}}
+
+Here, we note a number of limitations, but also provide additional directions for future research on this topic.
+First, while the use of O*Net items is a strength of the paper, practical considerations limited the number of job characteristics we could include in our survey.
+Because our focus was on O*Net items and our procedure was time and effort intensive, we were unable to inquire about other forms of resources (e.g., supervisor or coworker support) or demands.
+Thus, future study could explore these sources of support as resources and perhaps even compare the importance of various types of resources and their role in reducing the influence of hindrance stressors using O*Net characteristics.
+Is it overall perceptions of having more resources that makes up for hindrances, or could it be that certain resources carry more weight?
+Second, our focus here was on the outcome of stress, but it may also be of value to consider what the interaction between ratings of O*Net characteristics as resources and hindrances looks like on other outcomes of interest in a work context (e.g., commitment, motivation, engagement, intent to quit).
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-bakker2014job}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
 Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
 
-\leavevmode\hypertarget{ref-bakker2007job}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
+Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2005job}{}}%
+Bakker, A. B., Demerouti, E., \& Euwema, M. C. (2005). Job resources buffer the impact of job demands on burnout. \emph{Journal of Occupational Health Psychology}, \emph{10}(2), 170.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2003dual}{}}%
+Bakker, A.
+B., Demerouti, E., \& Schaufeli, W.
+(2003).
+Dual processes at work in a call centre: An application of the job demands--resources model.
+\emph{European Journal of Work and Organizational Psychology}, \emph{12}(4), 393--417.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2007job}{}}%
 Bakker, A.
@@
 
-\leavevmode\hypertarget{ref-bakker2003dual}{}%
-Bakker, A., Demerouti, E., \& Schaufeli, W.
-(2003).
-Dual processes at work in a call centre: An application of the job demands--resources model.
-\emph{European Journal of Work and Organizational Psychology}, \emph{12}(4), 393--417.
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2010beyond}{}}%
+Bakker, A. B., Van Veldhoven, M., \& Xanthopoulou, D. (2010). Beyond the demand-control model: Thriving on high job demands and resources. \emph{Journal of Personnel Psychology}, \emph{9}(1), 3.
 
-\leavevmode\hypertarget{ref-demerouti2001job}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-burr_third_2019}{}}%
+Burr, H., Berthelsen, H., Moncada, S., Nübling, M., Dupret, E., Demiral, Y., Oudyk, J., Kristensen, T.
+S., Llorens, C., Navarro, A., Lincke, H.-J., Bocéréan, C., Sahan, C., Smith, P., \& Pohrt, A.
+(2019).
+The {Third} {Version} of the {Copenhagen} {Psychosocial} {Questionnaire}.
+\emph{Safety and Health at Work}, \emph{10}(4), 482--503.
+\url{https://doi.org/10.1016/j.shaw.2019.10.002}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
+Cavanaugh, M.
+A., Boswell, W.
+R., Roehling, M.
+V., \& Boudreau, J.
+W.
+(2000).
+An empirical examination of self-reported work stress among US managers.
+\emph{Journal of Applied Psychology}, \emph{85}(1), 65.
+
+\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
 Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
 
-\leavevmode\hypertarget{ref-downes2021incorporating}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-downes2021incorporating}{}}%
 Downes, P.
@@
 
-\leavevmode\hypertarget{ref-hayes2022}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-hayes2022}{}}%
 Hayes, A. F. (2022). \emph{Introduction to mediation, moderation, and conditional process analysis: A regression-based approach} (3rd ed.). The Guilford Press.
 
-\leavevmode\hypertarget{ref-lazarus1984stress}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
 Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
 
-\leavevmode\hypertarget{ref-peterson2001understanding}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
 Peterson, N.
@@
 
-\leavevmode\hypertarget{ref-webster2011extending}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-tadic2015challenge}{}}%
+Tadić, M., Bakker, A.
+B., \& Oerlemans, W.
+G.
+(2015).
+Challenge versus hindrance job demands and well-being: A diary study on the moderating role of job resources.
+\emph{Journal of Occupational and Organizational Psychology}, \emph{88}(4), 702--725.
+
+\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
 Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.
+
+\leavevmode\vadjust pre{\hypertarget{ref-xanthopoulou2007job}{}}%
+Xanthopoulou, D., Bakker, A.
+B., Dollard, M.
+F., Demerouti, E., Schaufeli, W.
+B., Taris, T.
+W., \& Schreurs, P.
+J.
+(2007).
+When do job demands particularly predict burnout?
+The moderating role of job resources.
+\emph{Journal of Managerial Psychology}.
 

### 2022-10-08 SIOP2023/Counts/convergence.tex
possible references for #3

--- 2022-10-07 SIOP2023/Counts/convergence.tex
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={Demanding resources: Agreement of perceptions for challenge and resource characteristics},
-  pdfauthor={John Kulas1 \& Alicia Stachowski2},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
 
@@
 
+\begin{verbatim}
+## Warning: package 'tinylabels' was built under R version 4.1.3
+\end{verbatim}
+
 A plethora of research applying the job demands-resources model (Demerouti et al.
-(2001)) and job demands-resources theory (A.
-B.
-Bakker and Demerouti (2017)) underscore the importance of work characteristics on the experience of motivation and strain.
+(2001)) and job demands-resources theory (Bakker and Demerouti (2017)) underscore the importance of work characteristics on the experience of motivation and strain.
 However, much of our existing research on this topic assumes that certain characteristics are resources and others are generally considered demands.
@@
 
-The perception of a characteristic of one's job as a resource or demand activates one of two unique processes: either health impairment or motivation A.
-B.
-Bakker and Demerouti (2014).
-Demanding job characteristics are frequently associated with negative outcomes (e.g., health impairment process; A.
-Bakker et al.
-(2003)), whereas job characteristics considered resources have been associated with positive organizational outcomes like engagement and motivation (A.
-B.
-Bakker et al.
+The perception of a characteristic of one's job as a resource or demand activates one of two unique processes: either health impairment or motivation Bakker and Demerouti (2014).
+Demanding job characteristics are frequently associated with negative outcomes (e.g., health impairment process; Bakker et al.
+(2003)), whereas job characteristics considered resources have been associated with positive organizational outcomes like engagement and motivation (Bakker et al.
 (2007)).
@@
 We did this for each of the 84 individual characteristics that were rated as a resource, challenge, or demand and then computed an aggregate level of affirmative correspondence for each person.
-Figure \ref{fig:percagree} presents the results of these correspondences, showing that there was not much mutual agreement regarding characteristics being viewed as both hindrances and resources (\(\bar{X}\) = 0.14) or as challenges and hindrances
-(\(\bar{X}\) = 0.14).
-However, when a characteristic was viewed a resource, it was more likely to also be percieved as a challenge (although the correspondence also exhibited quite a bit of variability; \(\bar{X}\) = 0.51, \emph{sd} = 0.21).
+Figure \ref{fig:percagree} presents the results of these correspondences, showing that there was not much mutual agreement regarding characteristics being viewed as both hindrances and resources (\emph{M} = 0.14) or as challenges and hindrances
+(\emph{M} = 0.14).
+However, when a characteristic was viewed a resource, it was more likely to also be percieved as a challenge (although the correspondence also exhibited quite a bit of variability; \emph{M} = 0.51, \emph{sd} = 0.21).
 

### 2022-10-08 SIOP2023/Counts/Submission_ResourceCount.Rmd
minor edits - only 1/2-way through intro

@@
 ---
-title             : "Perception of Work Demands and Resources: Does Volume Matter?"
+title             : "Perception of Work Demands and Resources: Does Sheer Volume Matter?"
 shorttitle        : "JDR Volume"
@@
 This theory posits that the perception of a characteristic of one’s job as a resource or demand activates one of two unique processes: either health impairment or motivation [@bakker2014job].
-Demanding job characteristics are frequently associated with negative outcomes [e.g., health impairment, @bakker2003dual], whereas resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job].
-Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
+Demanding job characteristics are frequently associated with negative outcomes [@bakker2003dual], whereas resources have been associated with positive organizational outcomes such as engagement [@bakker2007job].
+Resources are commonly defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
 In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [e.g., high work pressure, @demerouti2001job].
@@
 From that point, the cycle of appraisal continues based on the action to cope with the stressor [@lazarus1984stress].
+[^comment]
+
+[^comment]: This sentence needs clarification - comprehension is ocluded.
 
@@
 
-Although the word “stress” often connotes something negative, @selye1936syndrome defined stress generically as a response to change.
-For instance, the example above describes an employee who appraises being nominated to give a speech as a negative stressor.
-However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
+Although the concept of *stress* often carries a negative connotation, the progenitor of this concept [@selye1936syndrome] took a less valenced perspective, defining stress less perjoratively as a simple response to change.
+For instance, the example given in the previous paragraph describes an employee who may appraise being nominated to give a speech as a negative stressor.
+However, another employee may appraise the nomination to do so as an exciting opportunity to share their experiences with their coworkers, or one in which they may be able to further prove their capabilities on a more visible platform.
 The terms associated with the two different appraisals of the stressor described here can be accomodated within the context of the JDR theory as "challenge" and "hindrance" demands [@cavanaugh2000empirical] Specifically, challenge demands promote mastery, personal growth, and future gains.
@@
 It is possible that rather than volume, categorically some demands are more related to these outcomes than others.
+The moderate association between hindrances and challenges (*r* = .22) also hints that some of these relationships may be driven by *job complexity* - that is, some jobs simply have more elements.
+With more job elements come increased opportunities for those elements to be percieved as resources, challenges, or hindrances.
 

### 2022-10-08 SIOP2023/Counts/Submission_ResourceCount.tex
minor edits - only 1/2-way through intro

@@
 \hypersetup{
-  pdftitle={Perception of Work Demands and Resources: Does Volume Matter?},
+  pdftitle={Perception of Work Demands and Resources: Does Sheer Volume Matter?},
   pdfauthor={Alicia Stachowski1 \& John Kulas2},
@@
 
-\title{Perception of Work Demands and Resources: Does Volume Matter?}
+\title{Perception of Work Demands and Resources: Does Sheer Volume Matter?}
 \author{Alicia Stachowski\textsuperscript{1} \& John Kulas\textsuperscript{2}}
@@
 This theory posits that the perception of a characteristic of one's job as a resource or demand activates one of two unique processes: either health impairment or motivation (Bakker \& Demerouti, 2014).
-Demanding job characteristics are frequently associated with negative outcomes (e.g., health impairment, Bakker et al., 2003), whereas resources have been associated with positive organizational outcomes like engagement and motivation (Bakker et al., 2007).
-Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
+Demanding job characteristics are frequently associated with negative outcomes (Bakker et al., 2003), whereas resources have been associated with positive organizational outcomes such as engagement (Bakker et al., 2007).
+Resources are commonly defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
 In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure, Demerouti et al., 2001).
@@
 From that point, the cycle of appraisal continues based on the action to cope with the stressor (Lazarus \& Folkman, 1984).
+\footnote{This sentence needs clarification - comprehension is ocluded.}
 
@@
 
-Although the word ``stress'' often connotes something negative, Selye (1936) defined stress generically as a response to change.
-For instance, the example above describes an employee who appraises being nominated to give a speech as a negative stressor.
-However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
+Although the concept of \emph{stress} often carries a negative connotation, the progenitor of this concept (Selye, 1936) took a less valenced perspective, defining stress less perjoratively as a simple response to change.
+For instance, the example given in the previous paragraph describes an employee who may appraise being nominated to give a speech as a negative stressor.
+However, another employee may appraise the nomination to do so as an exciting opportunity to share their experiences with their coworkers, or one in which they may be able to further prove their capabilities on a more visible platform.
 The terms associated with the two different appraisals of the stressor described here can be accomodated within the context of the JDR theory as ``challenge'' and ``hindrance'' demands (Cavanaugh et al., 2000) Specifically, challenge demands promote mastery, personal growth, and future gains.
@@
 It is possible that rather than volume, categorically some demands are more related to these outcomes than others.
+The moderate association between hindrances and challenges (\emph{r} = .22) also hints that some of these relationships may be driven by \emph{job complexity} - that is, some jobs simply have more elements.
+With more job elements come increased opportunities for those elements to be percieved as resources, challenges, or hindrances.
 

### 2022-10-10 SIOP2023/Counts/Submission_ResourceCount.Rmd
updated projects 1 and 2

@@
 568 workers rated O\*Net job characteristics in terms of relevance and perceptions as challenges, hindrances and resources.
-The findings are generally aligned with the job demands resource theory regarding associations between perceived resources, demands, and organizational outcomes of engagement, stress, and burnout.
+The findings showed a clear connection between resources, challenge demands, and job engagement, but the other associations did not suggest meaningful connections.
 
@@
 floatsintext      : no
-linenumbers       : yes
+linenumbers       : no
 draft             : no
@@
 During this process, meaning is assigned to stimuli.
-If our example fictional employee appraised the upcoming speech as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping (e.g., attempting to decline, asking for help in writing the speech).
-From that point, the cycle of appraisal continues based on the action to cope with the stressor [@lazarus1984stress].
-[^comment]
-
-[^comment]: This sentence needs clarification - comprehension is ocluded.
+If our example fictional employee appraised the upcoming speech as threatening, challenging, or possibly harmful (in contrast to positive or irrelevant), the resulting emotional distress initiates coping (e.g., attempting to decline, asking for help in writing the speech).
+From that point, a reassessment of the situation happens, and the cycle of appraisal continues based on the action to cope with the stressor [@lazarus1984stress].
+This theory of stress and coping speaks to the importance of how work demands are assessed by individuals, and it is not only possible, but quite likely that demands and resources do not fit cleanly into objective categories of "demands" and "resources".
 
@@
 Pearson correlation coefficients between characteristics classified as resources, challenges, and hindrances were obtained to investigate the associations among these characteristics.
+
 Correlations, means and standard deviations among all study variables are presented in Table \ref{tab:correlation_table}.
-Results reveal a positive association between resources and engagement (*r* = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively).
+The results reveal a positive association between resources and engagement (*r* = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively), although there is a very small, significant relationship between hindrance demands and stress (*r* = .09).
 Challenge demands were positively associated with engagement (*r* = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
@@
 
-The major goal of this paper was to further explore the relationships among total perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout.
+The major goal of this paper was to further explore the relationships among *total* perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout.
 The results suggest a positive relationship between both resources and engagement (H1a), and challenge demands and engagement (H2a).
@@
 The moderate association between hindrances and challenges (*r* = .22) also hints that some of these relationships may be driven by *job complexity* - that is, some jobs simply have more elements.
-With more job elements come increased opportunities for those elements to be percieved as resources, challenges, or hindrances.
+With more job elements come increased opportunities for those elements to be perceived as resources, challenges, or hindrances.
 
@@
 Future study could consider additional or other O\*Net items.
-We conceptualized resources and demands in terms of perceived total amounts.
+We intentionally conceptualized resources and demands in terms of perceived total amounts.
 It may be the case that certain kinds of resources or challenges are more strongly associated with engagement than others, and such, future research could explore the importance of resources/challenges categorically.
@@
 It would be especially interesting to explore additional outcomes (e.g., job satisfaction) as well, or whether volume of resources and demands operationalized in this way are related to other behaviors (e.g., turnover intention, perceived organizational support, commitment).
+Furthermore, while we found support for the prediction that resources and challenge demands would be positively related to engagement, it would be interesting to consider moderators of this relationship.
+For example, the Job Characteristics Theory @hackman1976motivation includes the key component of growth need strength in the connections between job characteristics (e.g., autonomy, skill variety) and critical states (e.g., experienced meaningfulness), and between critical states and personal and work outcomes.
+Perhaps this connection between engagement and challenge demands, for instance, is stronger for those with greater growth need strength.
+
+# Conclusion
+
+In sum, the major contribution of this project shows that number of O\*Net job characteristics rated as resources, challenge- and hindrance demands are associated with engagement, but not stress, and burnout.
+The findings showed a clear connection between resources, challenge demands, and job engagement, but the other associations did not suggest meaningful connections.
 

### 2022-10-10 SIOP2023/Counts/Submission_ResourceCount.tex
updated projects 1 and 2

@@
 \makeatother
-
-\usepackage{xpatch}
-\makeatletter
-\xapptocmd\appendix
-  {\xapptocmd\section
-    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
-    {}{\InnerPatchFailed}%
-  }
-{}{\PatchFailed}
+\shorttitle{JDR Volume}
 \keywords{keywords\newline\indent Word count: X}
@@
 \makeatother
-\usepackage{lineno}
-
-\linenumbers
 \usepackage{csquotes}
-\ifLuaTeX
+\ifxetex
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\else
+  \usepackage[main=english]{babel}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+\fi
+\ifluatex
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 \date{}
-
-\shorttitle{JDR Volume}
 
@@
 
-\abstract{%
+\abstract{
 The relationships among sum of perceived job resources, challenge- and hindrance demands and outcomes of organizational outcomes of engagement, stress, and burnout are explored.
 568 workers rated O*Net job characteristics in terms of relevance and perceptions as challenges, hindrances and resources.
-The findings are generally aligned with the job demands resource theory regarding associations between perceived resources, demands, and organizational outcomes of engagement, stress, and burnout.
+The findings showed a clear connection between resources, challenge demands, and job engagement, but the other associations did not suggest meaningful connections.
 }
@@
 During this process, meaning is assigned to stimuli.
-If our example fictional employee appraised the upcoming speech as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping (e.g., attempting to decline, asking for help in writing the speech).
-From that point, the cycle of appraisal continues based on the action to cope with the stressor (Lazarus \& Folkman, 1984).
-\footnote{This sentence needs clarification - comprehension is ocluded.}
+If our example fictional employee appraised the upcoming speech as threatening, challenging, or possibly harmful (in contrast to positive or irrelevant), the resulting emotional distress initiates coping (e.g., attempting to decline, asking for help in writing the speech).
+From that point, a reassessment of the situation happens, and the cycle of appraisal continues based on the action to cope with the stressor (Lazarus \& Folkman, 1984).
+This theory of stress and coping speaks to the importance of how work demands are assessed by individuals, and it is not only possible, but quite likely that demands and resources do not fit cleanly into objective categories of ``demands'' and ``resources.''
 
@@
 The brief review above provides theoretical and empirical support for the connection between resources and positive organizational outcomes, and between demands and negative outcomes.
-Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement (``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption,'' Schaufeli et al., 2002), workplace stress (``an individual state characterized by a combination of high arousal and displeasure,'' p.~15, Pejtersen et al., 2010) and burnout (``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work,'' p.~197, Kristensen et al., 2005).
+Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement ({``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption,''} Schaufeli et al., 2002), workplace stress ({``an individual state characterized by a combination of high arousal and displeasure,''} p.~15, Pejtersen et al., 2010) and burnout ({``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work,''} p.~197, Kristensen et al., 2005).
 Utilizing the job demands-resources theory, the transactional theory of stress, and the challenge-hindrance framework, we propose that the number of job characteristics appraised as ``challenge demands'' (i.e., promote mastery, personal growth, and future gains) would activate a positive state -- that of engagement.
@@
 
-\begin{tabular}{llllll}
+\begin{tabular}{lllll}
 \toprule
-Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$\mathit{df}$} & \multicolumn{1}{c}{$p$}\\
+Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(564)$} & \multicolumn{1}{c}{$p$}\\
 \midrule
-Intercept & 3.28 & {}[3.09, 3.47] & 33.93 & 564 & < .001\\
-Hindrance & 0.00 & {}[-0.01, 0.00] & -1.80 & 564 & .072\\
-Challenge & 0.00 & {}[-0.01, 0.01] & 0.88 & 564 & .378\\
-Resource & 0.02 & {}[0.01, 0.03] & 3.84 & 564 & < .001\\
+Intercept & 3.28 & {}[3.09, 3.47] & 33.93 & < .001\\
+Hindrance & 0.00 & {}[-0.01, 0.00] & -1.80 & .072\\
+Challenge & 0.00 & {}[-0.01, 0.01] & 0.88 & .378\\
+Resource & 0.02 & {}[0.01, 0.03] & 3.84 & < .001\\
 \bottomrule
@@
 
-\begin{tabular}{llllll}
+\begin{tabular}{lllll}
 \toprule
-Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$\mathit{df}$} & \multicolumn{1}{c}{$p$}\\
+Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(564)$} & \multicolumn{1}{c}{$p$}\\
 \midrule
-Intercept & 2.38 & {}[2.15, 2.62] & 19.80 & 564 & < .001\\
-Hindrance & 0.01 & {}[0.00, 0.01] & 1.82 & 564 & .070\\
-Challenge & 0.01 & {}[0.00, 0.02] & 1.43 & 564 & .152\\
-Resource & 0.00 & {}[-0.02, 0.01] & -0.77 & 564 & .440\\
+Intercept & 2.38 & {}[2.15, 2.62] & 19.80 & < .001\\
+Hindrance & 0.01 & {}[0.00, 0.01] & 1.82 & .070\\
+Challenge & 0.01 & {}[0.00, 0.02] & 1.43 & .152\\
+Resource & 0.00 & {}[-0.02, 0.01] & -0.77 & .440\\
 \bottomrule
@@
 
-\begin{tabular}{llllll}
+\begin{tabular}{lllll}
 \toprule
-Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$\mathit{df}$} & \multicolumn{1}{c}{$p$}\\
+Predictor & \multicolumn{1}{c}{$b$} & \multicolumn{1}{c}{95\% CI} & \multicolumn{1}{c}{$t(564)$} & \multicolumn{1}{c}{$p$}\\
 \midrule
-Intercept & 2.90 & {}[2.68, 3.11] & 26.89 & 564 & < .001\\
-Hindrance & 0.00 & {}[0.00, 0.01] & 0.67 & 564 & .502\\
-Challenge & 0.01 & {}[0.00, 0.02] & 1.19 & 564 & .233\\
-Resource & 0.00 & {}[-0.01, 0.01] & -0.52 & 564 & .601\\
+Intercept & 2.90 & {}[2.68, 3.11] & 26.89 & < .001\\
+Hindrance & 0.00 & {}[0.00, 0.01] & 0.67 & .502\\
+Challenge & 0.01 & {}[0.00, 0.02] & 1.19 & .233\\
+Resource & 0.00 & {}[-0.01, 0.01] & -0.52 & .601\\
 \bottomrule
@@
 Pearson correlation coefficients between characteristics classified as resources, challenges, and hindrances were obtained to investigate the associations among these characteristics.
+
 Correlations, means and standard deviations among all study variables are presented in Table \ref{tab:correlation_table}.
-Results reveal a positive association between resources and engagement (\emph{r} = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively).
+The results reveal a positive association between resources and engagement (\emph{r} = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively), although there is a very small, significant relationship between hindrance demands and stress (\emph{r} = .09).
 Challenge demands were positively associated with engagement (\emph{r} = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
@@
 
-The major goal of this paper was to further explore the relationships among total perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout.
+The major goal of this paper was to further explore the relationships among \emph{total} perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout.
 The results suggest a positive relationship between both resources and engagement (H1a), and challenge demands and engagement (H2a).
@@
 The moderate association between hindrances and challenges (\emph{r} = .22) also hints that some of these relationships may be driven by \emph{job complexity} - that is, some jobs simply have more elements.
-With more job elements come increased opportunities for those elements to be percieved as resources, challenges, or hindrances.
+With more job elements come increased opportunities for those elements to be perceived as resources, challenges, or hindrances.
 
@@
 Future study could consider additional or other O*Net items.
-We conceptualized resources and demands in terms of perceived total amounts.
+We intentionally conceptualized resources and demands in terms of perceived total amounts.
 It may be the case that certain kinds of resources or challenges are more strongly associated with engagement than others, and such, future research could explore the importance of resources/challenges categorically.
@@
 It would be especially interesting to explore additional outcomes (e.g., job satisfaction) as well, or whether volume of resources and demands operationalized in this way are related to other behaviors (e.g., turnover intention, perceived organizational support, commitment).
+Furthermore, while we found support for the prediction that resources and challenge demands would be positively related to engagement, it would be interesting to consider moderators of this relationship.
+For example, the Job Characteristics Theory (\textbf{hackman1976motivation?}) includes the key component of growth need strength in the connections between job characteristics (e.g., autonomy, skill variety) and critical states (e.g., experienced meaningfulness), and between critical states and personal and work outcomes.
+Perhaps this connection between engagement and challenge demands, for instance, is stronger for those with greater growth need strength.
+
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
+
+In sum, the major contribution of this project shows that number of O*Net job characteristics rated as resources, challenge- and hindrance demands are associated with engagement, but not stress, and burnout.
+The findings showed a clear connection between resources, challenge demands, and job engagement, but the other associations did not suggest meaningful connections.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-abbas2019challenge}{}}%
+\leavevmode\hypertarget{ref-abbas2019challenge}{}%
 Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
+\leavevmode\hypertarget{ref-bakker2014job}{}%
 Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
+\leavevmode\hypertarget{ref-bakker2017job}{}%
 Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2003dual}{}}%
+\leavevmode\hypertarget{ref-bakker2003dual}{}%
 Bakker, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2007job}{}}%
+\leavevmode\hypertarget{ref-bakker2007job}{}%
 Bakker, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
+\leavevmode\hypertarget{ref-bakker2013weekly}{}%
 Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
 
-\leavevmode\vadjust pre{\hypertarget{ref-burr_third_2019}{}}%
+\leavevmode\hypertarget{ref-burr_third_2019}{}%
 Burr, H., Berthelsen, H., Moncada, S., Nübling, M., Dupret, E., Demiral, Y., Oudyk, J., Kristensen, T.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
+\leavevmode\hypertarget{ref-demerouti2001job}{}%
 Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
 
-\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
+\leavevmode\hypertarget{ref-gerich2017relevance}{}%
 Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
 
-\leavevmode\vadjust pre{\hypertarget{ref-kristensen2005copenhagen}{}}%
+\leavevmode\hypertarget{ref-kristensen2005copenhagen}{}%
 Kristensen, T. S., Borritz, M., Villadsen, E., \& Christensen, K. B. (2005). The copenhagen burnout inventory: A new tool for the assessment of burnout. \emph{Work \& Stress}, \emph{19}(3), 192--207.
 
-\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
+\leavevmode\hypertarget{ref-lazarus1984stress}{}%
 Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
 
-\leavevmode\vadjust pre{\hypertarget{ref-pejtersen2010second}{}}%
+\leavevmode\hypertarget{ref-pejtersen2010second}{}%
 Pejtersen, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
+\leavevmode\hypertarget{ref-R-base}{}%
 R Core Team. (2022). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
 
-\leavevmode\vadjust pre{\hypertarget{ref-engage_2022}{}}%
+\leavevmode\hypertarget{ref-engage_2022}{}%
 Russell, M., Ossorio Duffoo, C., Garcia Prieto Palacios Roji, R., \& Kulas, J. (2022). Development of an intentional bifactor measure of engagement. \emph{The Seattle Edition of SIOP}, 1--14.
 
-\leavevmode\vadjust pre{\hypertarget{ref-schaufeli2002measurement}{}}%
+\leavevmode\hypertarget{ref-schaufeli2002measurement}{}%
 Schaufeli, W.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-searle2015merits}{}}%
+\leavevmode\hypertarget{ref-searle2015merits}{}%
 Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.
 
-\leavevmode\vadjust pre{\hypertarget{ref-selye1936syndrome}{}}%
+\leavevmode\hypertarget{ref-selye1936syndrome}{}%
 Selye, H. (1936). A syndrome produced by diverse nocuous agents. \emph{Nature}, \emph{138}(3479), 32--32.
 
-\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
+\leavevmode\hypertarget{ref-webster2011extending}{}%
 Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.

### 2022-10-10 SIOP2023/SIOP_PROCESS.tex
updated projects 1 and 2

@@
 This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated.
-These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move'', Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
+These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move,'' Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
 It is also useful to employers by providing them with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
@@
 Each of the 98 descriptors has potentially unique response categories, but scaling was consistently 1 (low) to 5 (high).
-Subsequent to these self-evaluations, respondents were asked to rate elements in terms of resources (``\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development''), challenges, (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains'') and hindrances (``\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment'').
+Subsequent to these self-evaluations, respondents were asked to rate elements in terms of resources (``\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development''), challenges, (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains``) and hindrances (''\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment").
 For each category (e.g., resources), a means was computed across items that applied to one's role, and thus, mean scores could range from 1 to 5.
@@
 (2019)) captured stress (e.g., ``How often have you had problems relaxing because of your job?'').
-Responses were made on a 5-point scale ranging from ``not at all'' to ``all the time''.
-Alpha was .85 in this sample.
+Responses were made on a 5-point scale ranging from ``not at all'' to ``all the time.'' Alpha was .85 in this sample.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
+\leavevmode\hypertarget{ref-bakker2014job}{}%
 Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
+\leavevmode\hypertarget{ref-bakker2017job}{}%
 Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2005job}{}}%
+\leavevmode\hypertarget{ref-bakker2005job}{}%
 Bakker, A. B., Demerouti, E., \& Euwema, M. C. (2005). Job resources buffer the impact of job demands on burnout. \emph{Journal of Occupational Health Psychology}, \emph{10}(2), 170.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2003dual}{}}%
+\leavevmode\hypertarget{ref-bakker2003dual}{}%
 Bakker, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2010beyond}{}}%
+\leavevmode\hypertarget{ref-bakker2010beyond}{}%
 Bakker, A. B., Van Veldhoven, M., \& Xanthopoulou, D. (2010). Beyond the demand-control model: Thriving on high job demands and resources. \emph{Journal of Personnel Psychology}, \emph{9}(1), 3.
 
-\leavevmode\vadjust pre{\hypertarget{ref-burr_third_2019}{}}%
+\leavevmode\hypertarget{ref-burr_third_2019}{}%
 Burr, H., Berthelsen, H., Moncada, S., Nübling, M., Dupret, E., Demiral, Y., Oudyk, J., Kristensen, T.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
+\leavevmode\hypertarget{ref-demerouti2001job}{}%
 Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
 
-\leavevmode\vadjust pre{\hypertarget{ref-downes2021incorporating}{}}%
+\leavevmode\hypertarget{ref-downes2021incorporating}{}%
 Downes, P.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-tadic2015challenge}{}}%
+\leavevmode\hypertarget{ref-tadic2015challenge}{}%
 Tadić, M., Bakker, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
+\leavevmode\hypertarget{ref-webster2011extending}{}%
 Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.
 
-\leavevmode\vadjust pre{\hypertarget{ref-xanthopoulou2007job}{}}%
+\leavevmode\hypertarget{ref-xanthopoulou2007job}{}%
 Xanthopoulou, D., Bakker, A.

### 2022-10-11 SIOP2023/SIOP_PROCESS.Rmd
updated projects 1 and 2
PROCESS for SIOP (just a couple of notes left - do we want to change "stress" to "strain" throughout?)

@@
 ---
-title             : "Testing the JD-R Theory: Using the Content of the O*Net"
-shorttitle        : "SIOP_Hindrances-Resources Interaction"
+title             : "Testing the JD-R theory via O*Net definitional specification"
+shorttitle        : "Hindrances-Resources Interaction"
 
@@
 footnotelist      : no
-linenumbers       : yes
+linenumbers       : no
 mask              : no
@@
 
-The Job Demands-Resources Theory [JD-R; @demerouti2001job] has received wide support across contexts and varied research questions.
-We extend the literature by 1) exploring the interaction between *perceptions* of job demands and resources on the outcome of stress using job characteristics in the popular O\*Net and 2) by considering also the appraisal of demands as challenge or hindrance stressors.
-Here, respondents made a series of evaluations that used: direct O\*Net terminology (both descriptor and response option), and JD-R influenced ratings of demand and hindrance stressors.
+The Job Demands-Resources Theory [JD-R, @demerouti2001job] has received wide support across contexts and varied research questions.
+We extend the literature by 1) exploring the interaction between job demands and resources on the experience of stress using O\*Net job characteristics and 2) considering also the appraisal of demands as challenge or hindrance stressors.
+Here, respondents made a series of evaluations that used: direct O\*Net terminology (both descriptor and response option), and JD-R influenced ratings of challenge and hindrance stressors.
 Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O\*Net, is provided.
 
-## The Job demands-Resources Theory
+## The Job Demands-Resources Theory
 
 The job demands-resources theory is an expansion of the well-studied job demands-resources model [@demerouti2001job].
-One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands, which are thoroughly documented by job in O\*Net.
-*Resources* are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
-*Demands*, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure; @demerouti2001job).
+One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics (which are thoroughly documented across many jobs within O\*Net) via *resources* and *demands*.
+Resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
+Demands, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure; @demerouti2001job).
 
-Cognitively, the perception of an element of one's job as a resource or demand activates one of two unique processes: health impairment (resulting from demands) or motivation [resulting from resources; @bakker2014job].
+Cognitively, the perception of an element of one's job as a resource or demand activates one of two unique processes: health impairment (resulting from demands) or motivation [resulting from resources, @bakker2014job].
 Demanding job characteristics are frequently associated with negative outcomes [e.g., @bakker2003dual], whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job].
-However, a related line of research emphasizes a distinction between two types of demands - that of "challenge" and "hindrance" demands, suggesting that employees may evaluate stressors in different ways.
+However, a related line of research emphasizes a further distinction between two types of demands - that of *challenge* and *hindrance* demands, suggesting that employees may evaluate stressors in different ways.
 
-## Objective vs. Subjective Nature of Demands and Resources: The Role of Appraisal
+## The Subjective Nature of Demands and Resources: The Role of Appraisal
 
@@
 
-@searle2015merits note that much of our research on workplace demands is based on apriori classifications of demands.
+@searle2015merits note that much of our research on workplace demands is based on *a priori* classifications of demands.
 For instance, we assume that generally, time pressure is a negative demand on an employee.
@@
 First, as hinted at above, some research suggests that job demands and resources may not be universally appraised or assigned as such.
-Starting with job demands, @webster2011extending  studied workload, role ambiguity, and role conflict demands, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being *both* a challenge and hindrance to different degrees.
-While their study not did include resources, it documents individual differences in how people perceive stressors at work.
-Although not the primary focus of their paper, @sonnega_comparison_2018 compared self-reported (subjective) ratings of degree of physical demand, stress, and need for intense concentration from the Health and Retirement Study with objective ratings from O\*Net.
+Starting with job demands, @webster2011extending  studied workload, role ambiguity, and role conflict, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being *both* a challenge and hindrance to different degrees.
+While their study not did include resources, it does document individual differences in how people may perceive stressors at work.
+
+>Although not the primary focus of their paper, @sonnega_comparison_2018 compared self-reported (subjective) ratings of the degree of physical demands, stress, and a need for intense concentration from the Health and Retirement Study with objective ratings from O\*Net.
 Correlations physical demand (*r* = .52), stress (*r* = .10), and need for intense concentration (*r* = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than we tend to think.
-While the above two studies provide evidence for variability in perception of demands, @schmitz_interpreting_2019 captured subjective and objective resources in their study of retirement.
-Correlations of composite variables between subjective and objective measures for the resources of autonomy (*r* = .12.
+
+While the above two studies provide evidence for variability in how workers view *demands*, @schmitz_interpreting_2019 went on to further capture subjective and objective *resources* in their study of retirement.
+
+>[Same as above]: Correlations of composite variables between subjective and objective measures for the resources of autonomy (*r* = .12.
 p > .01), recognition of work (*r* = .07, p > .01), and decision freedom (*r* = .08, p > .01), while significant, certainly do not reflect high levels of overlap.
+
 We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees.
-@downes2021incorporating meta-analysis addresses this reality in depth, although it is beyond the scope of this project.
+@downes2021incorporating meta-analysis addresses this reality in depth, although a broader current elaboration is beyond the scope of this SIOP presentation.
 
-Thus, while it is cleaner to be able to categorize job characteristics as *either* a demand or a resource, the above research suggests that individual appraisal is an important consideration.
+Thus, while it is cleaner to be able to categorize job characteristics as *either* a demand or a resource, the above research suggests that an individual's (perhaps unique) appraisal is at least occasionally an important consideration.
 It is quite possible that one person experiences high work pressure (commonly cited as a demand in the literature) as a hindrance stressor and thus experiences strain, and another thrives in a fast-paced pressured role and would thus find the environment motivating.
-Here, we asked respondents to rate all of the job characteristics in terms of hindrances, challenges, and resources.
+In order to account for this possibility of "non-exclusivity", we asked our respondents to rate all relevant job characteristics in terms of their status as hindrances, challenges, and resources.
 
-## Value of exploring the O\*Net Resource
+## Value of consulting O\*Net
 
-First, the Occupational Information Network (O\*NET; onetonline.org) contains a comprehensive description of occupations [@peterson2001understanding].
-This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated.
-These data, and the tools provided for free on the website (e.g., Career Exploration Tools, “My Next Move”, Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
-It is also useful to employers by providing them with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
-We utilized statements taken from O\*NET ["activity" and "context" classifications](https://www.O\*NETonline.org/find/descriptor/result/4.A.1.b.3) (e.g., items related to information input, interacting with others, physical work conditions, structural job characteristics).
+The Occupational Information Network (O\*NET; onetonline.org) contains a fairly comprehensive description of occupations [@peterson2001understanding].
+This widely accessed database houses hundreds of standardized and occupation-specific descriptors for the majority of occupations within the United States, and these descriptions are frequently updated.
+These data, and the tools provided for public consumption on the website (e.g., Career Exploration Tools, “My Next Move”, Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist interested or curious job-seekers discover the nature of work as well as skills and training typically required for different occupations.
+It is also often useful to employers by providing them with information that may be helpful in a job analysis context.
+For the current study, we focused on statements taken from O\*NET's ["activity" and "context" classifications](https://www.O\*NETonline.org/find/descriptor/result/4.A.1.b.3) (e.g., items related to characteristics of work such as how often a worker interacts with others or engages in physical labor).
+From a job analytic lens, these descriptors are written more broadly than a task statement, and would most likely be classified by most job analysts as "responsibilities".
 
@@
 
-These data were taken from a larger study on JD-R theory as it applies to O\*NET items, particularly Proposition 3 of the JD-R model - that job resources can buffer the impact of job demands on strain.
+The data we describe here represents a subset taken from a larger study on JD-R theory and its integration within the O\*NET framework.
+For SIOP, we specifically investigate Proposition 3 of the JD-R model - that job resources can buffer the impact of job demands on strain.
 The interaction between job resources and demands has been heavily studied with regard to a range of outcomes.
 For example @bakker2010beyond found that resources (e.g., learning opportunities, autonomy, leader support) predicted both task enjoyment and organizational commitment even under conditions of high demands.
+In fact, a rather large body of empirical evidence supports this assertion [e.g., see @bakker2017job for a historical review].
 Much of the research, however, has focused on stress/strain and burnout outcomes.
@@
 
-Our specific interest in the current study is in whether or not *perceptions* of hindrance demands are postitively related to perceived stress, and whether or not this relationship is moderated by perceived resources.
-The Job demands-Resources theory would suggest resources would buffer this relationship.
-In fact, a rather large body of empirical evidence supports this assertion [e.g., see @bakker2017job for a historical review].
+Our unique contribution in the current study is in whether or not *perceptions* of demands as hindrances or challenges are related to experienced stress, and whether or not this relationship is moderated by the presence of resources.
 We do have some existing evidence that this occurs with other outcomes beyond stress.
@@
 Daily job resources, in this sample, buffered the relationships between hindrances and affect and engagement.
-Here, we propose that perceived resources generally, as opposed to daily, would also buffer the relationship between perceived hindrance stressors and, in this, case, perceived stress.
+With the current investigation, we propose that greater perceived resources generally, as opposed to daily, would also buffer the relationship between perceived hindrance stressors and, in this, case, perceived stress.
 The following two predictions are made:
 
-*H1. There is a positive relationship between perceived hindrance stressors and stress.*
+>*H1*. There is a positive relationship between perceived hindrance stressors and stress.
 
-*H2. The relationship between mean perceived hindrances and stress will be moderated by resources such that this relationship is diminished as perceived resources increase.*
+>*H2*. The relationship between mean perceived hindrances and stress will be moderated by resources such that this relationship is diminished as perceived resources increase.
 
 # Methods
+
+Data were collected through Prolific, a data collection platform.
+An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
+Eligibility requirements included being 18+ and holding either a full-time or part-time job.
+Participants then voluntarily chose to respond to the survey.
+The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes.
+Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified.
+Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource, challenge, or hindrance for that characteristic.
+For characteristics that *were* implicated as being relevent for their job, they were then asked to report how much a characteristic was a resource, and then how much each characteristic was a hindrance, and finally, how much each item was a challenge.
+Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
 
@@
 
-### Participants
+## Participants
 
-We sampled from a Prolific panel, resulting in 785 individuals who initially 166 accessed the survey link.
-Of those, 112 indicated that they were not interested, had more 167 than 200 missing responses, or had 20 or more identical consecutive sequential responses 168 (Yentes & Wilhelm, 2021).
-There were a total of 568 respondents, of which 13.57% had been in their referent job less than 6 months, 19.20% between 6 months and a year, 49.12% between one and five years, 13.27% between 5 and 10 years, and 4.87% more than 10 years.Their ages ranged from 18 to 65 with an average of 28.18 years old (*SD* = 7.53).
-Over half, 52.58% identified as female, and 46.83% identified as male.
+785 individuals initially accessed the survey link.
+Of those 785, several indicated that they were not interested after learning more about the project, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses.
+Any individual respondent who fell into any of these three areas of concern was removed from the initial data frame, resulting in a final realized sample of 568.
+13.57% of these individuals had been in their referent job less than 6 months, 19.20% between 6 months and a year, 49.12% between one and five years, 13.27% between 5 and 10 years, and 4.87% more than 10 years.
+Their ages ranged from 18 to 65 with an average of 28.18 years old (*SD* = 7.53).
+Over half (52.58%) identified as female, and 46.83% identified as male.
 
@@
 Each of the 98 descriptors has potentially unique response categories, but scaling was consistently 1 (low) to 5 (high).
-Subsequent to these self-evaluations, respondents were asked to rate elements in terms of resources ("…this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development"), challenges, (…this aspect of your job is a challenge that can promote mastery, personal growth, or future gains") and hindrances ("…this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment").
-For each category (e.g., resources), a means was computed across items that applied to one's role, and thus, mean scores could range from 1 to 5.
+Subsequent to self-evaluations regarding whether or not the characteristic was applicable to one's job, the respondents were asked to rate germane elements in terms of it's experience as a resource ("…this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development"), challenge, (…this aspect of your job is a challenge that can promote mastery, personal growth, or future gains") as well as hindrance ("…this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment").
+For each category (e.g., resources), a mean score was computed that indicated the across items that applied to one's role, and thus, mean scores could range from 1 to 5.
 
@@
 
-Three items taken from the Copenhagen Psychosocial Questionnaire (@burr_third_2019) captured stress (e.g., "How often have you had problems relaxing because of your job?").
+Three items taken from the Copenhagen Psychosocial Questionnaire [@burr_third_2019] captured stress (an example item is: "How often have you had problems relaxing because of your job?").
 Responses were made on a 5-point scale ranging from "not at all" to "all the time".
 Alpha was .85 in this sample.
-
-## Procedure
-
-The data presented here were part of a larger study on the Job-demands Resources Model using O\*Net.
-Data were collected through Prolific, a data collection platform.
-An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
-Eligibility requirements included being 18+ and holding either a full-time or part-time job.
-Participants then voluntarily chose to respond to the survey.
-The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes.
-Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified.
-Thus, if a respondent indicated that 5 of the characteristics were not part of their job, they were not subsequently asked to rate the level of resource, challenge, or hindrance a given item presented to them.
-For items that were a part of their jobs, they were then asked to report how much a characteristic was a resource, and then how much each characteristic was a hindrance, and finally, how much each item was a challenge.
-Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
 
@@
                   caption = "Results from a regression analysis examining the moderation of resources on the relationship between hindrance demands and stress",
-                  note = "R^2 etc here",
+                  note = "$R^2$ here",
                   landscape = FALSE,
-                  escape = TRUE)
+                  escape = FALSE)
 
@@
 Next, to explore H2, a moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1 [@hayes2022, see Table \@ref(tab:table)].
-First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, F(3, 564) = 3.29, *p* = .020.
-The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, F(3, 564) = 3.51, *p* = .061, providing tentative support for H2.
-As can be seen in Figure 1, those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources.
-As such, these results provide some evidence that the resources do moderate the relationship between hindrance stressors.
+First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, $F_{(3, 564)}$ = 3.29, *p* = .020.
+The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, $F_{(3, 564)}$ = 3.51, *p* = .061, providing marginal support for H2.
+As can be seen in Figure \@ref(fig:analyses), those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources.
+As such, these results provide some evidence that resources may moderate the relationship between hindrance demands and subsequent levels of stress.
 
@@
 The primary goal of this project was to further explore the role of perceived resources on the hindrance-stress relationship using O\*Net characteristics.
-While we have plentiful evidence that resources can buffer the effects of a variety of job demands on burnout, this project focuses on subjective experiences of resources and demands, focusing on demands rated as challenges and hindrances.
+While we have plentiful evidence that resources can buffer the effects of a variety of job demands on burnout, this project focuses on subjective experiences of resources and demands, focusing on demands rated as challenges and hindrances, as well as focusing on the outcome of *stress*.
 As expected, the results suggest a positive relationship between perceived hindrances and stress (H1).
 While intuitive, it is important to replicate this finding before we explore the impact of perceived resources, which arguably, is something that employers may have more leverage to control than hindrance stressors.
-Second, the results serve to support the assertion that resources change the relationship between hindrances and stressors such that the connection between the two is diminished as resources increase (H2).
-While not hypothesized or presented above, the authors did run a regression on the challenge hindrance-stress relationship with resources as a moderator, with the assumption that resources would not moderate the relationship.
+
+Second, the results serve to support the assertion that resources change the relationship between hindrances and stress such that the connection between the two is diminished as resources increase (H2).
+While not hypothesized or presented above, the authors did also run a regression on the *challenge*-stress relationship with resources as a moderator, with the assumption that resources would not moderate the relationship.
 The findings, indeed, did not indicate a moderated relationship in this case.
-It appears that resources are of benefit particularly when demands are high.
-In particular, the Job-demands Resources Theory [JD-R; @demerouti2001job] suggests that resources would buffer the negative impact between demands and stress, and by extension, given the more traditional conceptualization of demands would be aligned with hindrance demands.
-
+It appears that resources are of benefit particularly when hindrances are present.
+In particular, the Job-demands Resources Theory [@demerouti2001job] suggests that resources would buffer the negative impact between demands and stress, and by extension, given the more traditional conceptualization of demands would be aligned with hindrance demands.
 These findings have implications worth considering.

### 2022-10-11 SIOP2023/SIOP_PROCESS.tex
PROCESS for SIOP (just a couple of notes left - do we want to change "stress" to "strain" throughout?)

--- 2022-10-08 SIOP2023/SIOP_PROCESS.tex
@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Testing the JD-R Theory: Using the Content of the O*Net},
-  pdfauthor={Alicia A. Stachowski1 \& John T. Kulas2},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \makeatother
-\usepackage{lineno}
-
-\linenumbers
 \usepackage{csquotes}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Testing the JD-R theory via O*Net definitional specification},
+  pdfauthor={Alicia A. Stachowski1 \& John T. Kulas2},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
-\title{Testing the JD-R Theory: Using the Content of the O*Net}
+\title{Testing the JD-R theory via O*Net definitional specification}
 \author{Alicia A. Stachowski\textsuperscript{1} \& John T. Kulas\textsuperscript{2}}
@@
 
-\shorttitle{SIOP\_Hindrances-Resources Interaction}
+\shorttitle{Hindrances-Resources Interaction}
 
@@
 
-The Job Demands-Resources Theory {[}JD-R; Demerouti et al.
-(2001){]} has received wide support across contexts and varied research questions.
-We extend the literature by 1) exploring the interaction between \emph{perceptions} of job demands and resources on the outcome of stress using job characteristics in the popular O*Net and 2) by considering also the appraisal of demands as challenge or hindrance stressors.
-Here, respondents made a series of evaluations that used: direct O*Net terminology (both descriptor and response option), and JD-R influenced ratings of demand and hindrance stressors.
+The Job Demands-Resources Theory (JD-R, Demerouti et al., 2001) has received wide support across contexts and varied research questions.
+We extend the literature by 1) exploring the interaction between job demands and resources on the experience of stress using O*Net job characteristics and 2) considering also the appraisal of demands as challenge or hindrance stressors.
+Here, respondents made a series of evaluations that used: direct O*Net terminology (both descriptor and response option), and JD-R influenced ratings of challenge and hindrance stressors.
 Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O*Net, is provided.
@@
 \hypertarget{the-job-demands-resources-theory}{%
-\subsection{The Job demands-Resources Theory}\label{the-job-demands-resources-theory}}
+\subsection{The Job Demands-Resources Theory}\label{the-job-demands-resources-theory}}
 
 The job demands-resources theory is an expansion of the well-studied job demands-resources model (Demerouti et al., 2001).
-One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands, which are thoroughly documented by job in O*Net.
-\emph{Resources} are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
-\emph{Demands}, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure; Demerouti et al.
+One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics (which are thoroughly documented across many jobs within O*Net) via \emph{resources} and \emph{demands}.
+Resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
+Demands, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure; Demerouti et al.
 (2001)).
 
-Cognitively, the perception of an element of one's job as a resource or demand activates one of two unique processes: health impairment (resulting from demands) or motivation {[}resulting from resources; Bakker and Demerouti (2014){]}.
+Cognitively, the perception of an element of one's job as a resource or demand activates one of two unique processes: health impairment (resulting from demands) or motivation (resulting from resources, Bakker \& Demerouti, 2014).
 Demanding job characteristics are frequently associated with negative outcomes (e.g., Bakker et al., 2003), whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation (Bakker et al., 2007).
-However, a related line of research emphasizes a distinction between two types of demands - that of ``challenge'' and ``hindrance'' demands, suggesting that employees may evaluate stressors in different ways.
+However, a related line of research emphasizes a further distinction between two types of demands - that of \emph{challenge} and \emph{hindrance} demands, suggesting that employees may evaluate stressors in different ways.
 
-\hypertarget{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisal}{%
-\subsection{Objective vs.~Subjective Nature of Demands and Resources: The Role of Appraisal}\label{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisal}}
+\hypertarget{the-subjective-nature-of-demands-and-resources-the-role-of-appraisal}{%
+\subsection{The Subjective Nature of Demands and Resources: The Role of Appraisal}\label{the-subjective-nature-of-demands-and-resources-the-role-of-appraisal}}
 
@@
 
-Searle and Auton (2015) note that much of our research on workplace demands is based on apriori classifications of demands.
+Searle and Auton (2015) note that much of our research on workplace demands is based on \emph{a priori} classifications of demands.
 For instance, we assume that generally, time pressure is a negative demand on an employee.
@@
 Starting with job demands, Webster et al.
-(2011) studied workload, role ambiguity, and role conflict demands, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being \emph{both} a challenge and hindrance to different degrees.
-While their study not did include resources, it documents individual differences in how people perceive stressors at work.
+(2011) studied workload, role ambiguity, and role conflict, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being \emph{both} a challenge and hindrance to different degrees.
+While their study not did include resources, it does document individual differences in how people may perceive stressors at work.
+
+\begin{quote}
 Although not the primary focus of their paper, Sonnega et al.
-(2018) compared self-reported (subjective) ratings of degree of physical demand, stress, and need for intense concentration from the Health and Retirement Study with objective ratings from O*Net.
+(2018) compared self-reported (subjective) ratings of the degree of physical demands, stress, and a need for intense concentration from the Health and Retirement Study with objective ratings from O*Net.
 Correlations physical demand (\emph{r} = .52), stress (\emph{r} = .10), and need for intense concentration (\emph{r} = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than we tend to think.
-While the above two studies provide evidence for variability in perception of demands, Schmitz et al.
-(2019) captured subjective and objective resources in their study of retirement.
-Correlations of composite variables between subjective and objective measures for the resources of autonomy (\emph{r} = .12.
+\end{quote}
+
+While the above two studies provide evidence for variability in how workers view \emph{demands}, Schmitz et al.
+(2019) went on to further capture subjective and objective \emph{resources} in their study of retirement.
+
+\begin{quote}
+{[}Same as above{]}: Correlations of composite variables between subjective and objective measures for the resources of autonomy (\emph{r} = .12.
 p \textgreater{} .01), recognition of work (\emph{r} = .07, p \textgreater{} .01), and decision freedom (\emph{r} = .08, p \textgreater{} .01), while significant, certainly do not reflect high levels of overlap.
+\end{quote}
+
 We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees.
 Downes et al.
-(2021) meta-analysis addresses this reality in depth, although it is beyond the scope of this project.
+(2021) meta-analysis addresses this reality in depth, although a broader current elaboration is beyond the scope of this SIOP presentation.
 
-Thus, while it is cleaner to be able to categorize job characteristics as \emph{either} a demand or a resource, the above research suggests that individual appraisal is an important consideration.
+Thus, while it is cleaner to be able to categorize job characteristics as \emph{either} a demand or a resource, the above research suggests that an individual's (perhaps unique) appraisal is at least occasionally an important consideration.
 It is quite possible that one person experiences high work pressure (commonly cited as a demand in the literature) as a hindrance stressor and thus experiences strain, and another thrives in a fast-paced pressured role and would thus find the environment motivating.
-Here, we asked respondents to rate all of the job characteristics in terms of hindrances, challenges, and resources.
+In order to account for this possibility of ``non-exclusivity'', we asked our respondents to rate all relevant job characteristics in terms of their status as hindrances, challenges, and resources.
 
-\hypertarget{value-of-exploring-the-onet-resource}{%
-\subsection{Value of exploring the O*Net Resource}\label{value-of-exploring-the-onet-resource}}
+\hypertarget{value-of-consulting-onet}{%
+\subsection{Value of consulting O*Net}\label{value-of-consulting-onet}}
 
-First, the Occupational Information Network (O*NET; onetonline.org) contains a comprehensive description of occupations (Peterson et al., 2001).
-This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated.
-These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move'', Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
-It is also useful to employers by providing them with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
-We utilized statements taken from O*NET \href{https://www.O*NETonline.org/find/descriptor/result/4.A.1.b.3}{``activity'' and ``context'' classifications} (e.g., items related to information input, interacting with others, physical work conditions, structural job characteristics).
+The Occupational Information Network (O*NET; onetonline.org) contains a fairly comprehensive description of occupations (Peterson et al., 2001).
+This widely accessed database houses hundreds of standardized and occupation-specific descriptors for the majority of occupations within the United States, and these descriptions are frequently updated.
+These data, and the tools provided for public consumption on the website (e.g., Career Exploration Tools, ``My Next Move'', Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist interested or curious job-seekers discover the nature of work as well as skills and training typically required for different occupations.
+It is also often useful to employers by providing them with information that may be helpful in a job analysis context.
+For the current study, we focused on statements taken from O*NET's \href{https://www.O*NETonline.org/find/descriptor/result/4.A.1.b.3}{``activity'' and ``context'' classifications} (e.g., items related to characteristics of work such as how often a worker interacts with others or engages in physical labor).
+From a job analytic lens, these descriptors are written more broadly than a task statement, and would most likely be classified by most job analysts as ``responsibilities''.
 
@@
 
-These data were taken from a larger study on JD-R theory as it applies to O*NET items, particularly Proposition 3 of the JD-R model - that job resources can buffer the impact of job demands on strain.
+The data we describe here represents a subset taken from a larger study on JD-R theory and its integration within the O*NET framework.
+For SIOP, we specifically investigate Proposition 3 of the JD-R model - that job resources can buffer the impact of job demands on strain.
 The interaction between job resources and demands has been heavily studied with regard to a range of outcomes.
@@
 (2010) found that resources (e.g., learning opportunities, autonomy, leader support) predicted both task enjoyment and organizational commitment even under conditions of high demands.
+In fact, a rather large body of empirical evidence supports this assertion (e.g., see Bakker \& Demerouti, 2017 for a historical review).
 Much of the research, however, has focused on stress/strain and burnout outcomes.
@@
 
-Our specific interest in the current study is in whether or not \emph{perceptions} of hindrance demands are postitively related to perceived stress, and whether or not this relationship is moderated by perceived resources.
-The Job demands-Resources theory would suggest resources would buffer this relationship.
-In fact, a rather large body of empirical evidence supports this assertion (e.g., see Bakker \& Demerouti, 2017 for a historical review).
+Our unique contribution in the current study is in whether or not \emph{perceptions} of demands as hindrances or challenges are related to experienced stress, and whether or not this relationship is moderated by the presence of resources.
 We do have some existing evidence that this occurs with other outcomes beyond stress.
@@
 Daily job resources, in this sample, buffered the relationships between hindrances and affect and engagement.
-Here, we propose that perceived resources generally, as opposed to daily, would also buffer the relationship between perceived hindrance stressors and, in this, case, perceived stress.
+With the current investigation, we propose that greater perceived resources generally, as opposed to daily, would also buffer the relationship between perceived hindrance stressors and, in this, case, perceived stress.
 The following two predictions are made:
 
-\emph{H1. There is a positive relationship between perceived hindrance stressors and stress.}
+\begin{quote}
+\emph{H1}. There is a positive relationship between perceived hindrance stressors and stress.
+\end{quote}
 
-\emph{H2. The relationship between mean perceived hindrances and stress will be moderated by resources such that this relationship is diminished as perceived resources increase.}
+\begin{quote}
+\emph{H2}. The relationship between mean perceived hindrances and stress will be moderated by resources such that this relationship is diminished as perceived resources increase.
+\end{quote}
 
@@
 
+Data were collected through Prolific, a data collection platform.
+An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
+Eligibility requirements included being 18+ and holding either a full-time or part-time job.
+Participants then voluntarily chose to respond to the survey.
+The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes.
+Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified.
+Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource, challenge, or hindrance for that characteristic.
+For characteristics that \emph{were} implicated as being relevent for their job, they were then asked to report how much a characteristic was a resource, and then how much each characteristic was a hindrance, and finally, how much each item was a challenge.
+Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
+
 \hypertarget{participants}{%
-\subsubsection{Participants}\label{participants}}
+\subsection{Participants}\label{participants}}
 
-We sampled from a Prolific panel, resulting in 785 individuals who initially 166 accessed the survey link.
-Of those, 112 indicated that they were not interested, had more 167 than 200 missing responses, or had 20 or more identical consecutive sequential responses 168 (Yentes \& Wilhelm, 2021).
-There were a total of 568 respondents, of which 13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.Their ages ranged from 18 to 65 with an average of 28.18 years old (\emph{SD} = 7.53).
-Over half, 52.58\% identified as female, and 46.83\% identified as male.
+785 individuals initially accessed the survey link.
+Of those 785, several indicated that they were not interested after learning more about the project, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses.
+Any individual respondent who fell into any of these three areas of concern was removed from the initial data frame, resulting in a final realized sample of 568.
+13.57\% of these individuals had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.
+Their ages ranged from 18 to 65 with an average of 28.18 years old (\emph{SD} = 7.53).
+Over half (52.58\%) identified as female, and 46.83\% identified as male.
 
@@
 Each of the 98 descriptors has potentially unique response categories, but scaling was consistently 1 (low) to 5 (high).
-Subsequent to these self-evaluations, respondents were asked to rate elements in terms of resources (``\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development''), challenges, (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains'') and hindrances (``\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment'').
-For each category (e.g., resources), a means was computed across items that applied to one's role, and thus, mean scores could range from 1 to 5.
+Subsequent to self-evaluations regarding whether or not the characteristic was applicable to one's job, the respondents were asked to rate germane elements in terms of it's experience as a resource (``\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development''), challenge, (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains'') as well as hindrance (``\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment'').
+For each category (e.g., resources), a mean score was computed that indicated the across items that applied to one's role, and thus, mean scores could range from 1 to 5.
 
@@
 
-Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al.
-(2019)) captured stress (e.g., ``How often have you had problems relaxing because of your job?'').
+Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019) captured stress (an example item is: ``How often have you had problems relaxing because of your job?'').
 Responses were made on a 5-point scale ranging from ``not at all'' to ``all the time''.
 Alpha was .85 in this sample.
-
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
-
-The data presented here were part of a larger study on the Job-demands Resources Model using O*Net.
-Data were collected through Prolific, a data collection platform.
-An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
-Eligibility requirements included being 18+ and holding either a full-time or part-time job.
-Participants then voluntarily chose to respond to the survey.
-The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes.
-Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified.
-Thus, if a respondent indicated that 5 of the characteristics were not part of their job, they were not subsequently asked to rate the level of resource, challenge, or hindrance a given item presented to them.
-For items that were a part of their jobs, they were then asked to report how much a characteristic was a resource, and then how much each characteristic was a hindrance, and finally, how much each item was a challenge.
-Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
 
@@
 \begin{tablenotes}[para]
-\normalsize{\textit{Note.} R\textasciicircum{}2 etc here}
+\normalsize{\textit{Note.} $R^2$ here}
 \end{tablenotes}
@@
 Next, to explore H2, a moderated regression including hindrances, resources, and the interaction between them was done using PROCESS, version 4.1.1 (Hayes, 2022, see Table \ref{tab:table}).
-First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, F(3, 564) = 3.29, \emph{p} = .020.
-The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, F(3, 564) = 3.51, \emph{p} = .061, providing tentative support for H2.
-As can be seen in Figure 1, those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources.
-As such, these results provide some evidence that the resources do moderate the relationship between hindrance stressors.
+First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, \(F_{(3, 564)}\) = 3.29, \emph{p} = .020.
+The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, \(F_{(3, 564)}\) = 3.51, \emph{p} = .061, providing marginal support for H2.
+As can be seen in Figure \ref{fig:analyses}, those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources.
+As such, these results provide some evidence that resources may moderate the relationship between hindrance demands and subsequent levels of stress.
 
@@
 The primary goal of this project was to further explore the role of perceived resources on the hindrance-stress relationship using O*Net characteristics.
-While we have plentiful evidence that resources can buffer the effects of a variety of job demands on burnout, this project focuses on subjective experiences of resources and demands, focusing on demands rated as challenges and hindrances.
+While we have plentiful evidence that resources can buffer the effects of a variety of job demands on burnout, this project focuses on subjective experiences of resources and demands, focusing on demands rated as challenges and hindrances, as well as focusing on the outcome of \emph{stress}.
 As expected, the results suggest a positive relationship between perceived hindrances and stress (H1).
 While intuitive, it is important to replicate this finding before we explore the impact of perceived resources, which arguably, is something that employers may have more leverage to control than hindrance stressors.
-Second, the results serve to support the assertion that resources change the relationship between hindrances and stressors such that the connection between the two is diminished as resources increase (H2).
-While not hypothesized or presented above, the authors did run a regression on the challenge hindrance-stress relationship with resources as a moderator, with the assumption that resources would not moderate the relationship.
+
+Second, the results serve to support the assertion that resources change the relationship between hindrances and stress such that the connection between the two is diminished as resources increase (H2).
+While not hypothesized or presented above, the authors did also run a regression on the \emph{challenge}-stress relationship with resources as a moderator, with the assumption that resources would not moderate the relationship.
 The findings, indeed, did not indicate a moderated relationship in this case.
-It appears that resources are of benefit particularly when demands are high.
-In particular, the Job-demands Resources Theory {[}JD-R; Demerouti et al.
-(2001){]} suggests that resources would buffer the negative impact between demands and stress, and by extension, given the more traditional conceptualization of demands would be aligned with hindrance demands.
-
+It appears that resources are of benefit particularly when hindrances are present.
+In particular, the Job-demands Resources Theory (Demerouti et al., 2001) suggests that resources would buffer the negative impact between demands and stress, and by extension, given the more traditional conceptualization of demands would be aligned with hindrance demands.
 These findings have implications worth considering.
@@
 S., Morgeson, F.
-P., Pearlman, K.others.
+P., Pearlman, K., et al.
 (2001).

### 2022-10-11 SIOP2023/Counts/convergence.Rmd
switching projects for bit

@@
 ---
-title             : "Demanding resources: Agreement of perceptions for challenge and resource characteristics"
+title             : "Demanding resources: Agreement across characteristics seen as both challenges and resources"
 shorttitle        : "Demanding Resources"
@@
 
-  A plethora of research applying the job demands-resources model (@demerouti2001job) and job demands-resources theory (@bakker2017job) underscore the importance of work characteristics on the experience of motivation and strain.
-However, much of our existing research on this topic assumes that certain characteristics are resources and others are generally considered demands.
-This study explores how individual perceptions of these work characteristics relate to engagement, stress, and burnout by asking respondents to indicate (of the characteristics that apply to their jobs) how much each is a resource, challenge, or hindrance demand.
-Amount of perceived resources, challenges, and hindrances can then be associated with engagement, stress, and burnout.
+An abundance of research applying the job demands-resources model [@demerouti2001job] and job demands-resources theory [@bakker2017job] underscores the importance of job characteristics on the experience of work.
+Resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
+Demands, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain [e.g., high work pressure, @demerouti2001job].
+These two categories of outcomes (e.g., "good" and "bad") are thought to occur via one of two different mechanisms: motivational (resulting from resources) or health impairment [resulting from demands, @bakker2014job].
+Much of our existing research on the JD-R assumes that certain characteristics (for example, autonomy) are resources and others (for example, time constraints) are generally considered demands.
+This study searches instead for circumstances that provide exception to this static dichotomy of job characteristic mutual exclusivity.
 
-## The Job Demands-Resources Theory
+## Could a Work Demand be Appraised "Positively"?: The Challenge-Hindrance Framework
 
-  The theoretical foundation for this study is the job demands-resources theory (@demerouti2001job).
-Using this theory, we can model both work environment and job characteristics via job resources and demands.
-Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (@demerouti2001job).
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure; @demerouti2001job).
+Although the word “stress” often carries a negative connotation, the "father" of the current concept, @selye1936syndrome, conceptualized stress much less perjoratively - rather thinking of it as a *response to change*.
+For instance, consider the different reactions two different employees may have to being nominated to give a speech at an upcoming company event.
+One may appraise the nomination as a negative stressor.
+However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
+Selye the physician would likely have labeled the two responses as subjective manifestations of "Distress", and "Eustress" [@selye1974stress].
+In modern I-O Psychology parlance (and more consistent with the JD-R framework), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a *challenge* while the other would appraise the demand as a *hindrance* [@cavanaugh2000empirical].
+According to @cavanaugh2000empirical, challenge demands promote mastery, personal growth, and future gains.
+Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
+Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes [e.g., @cavanaugh2000empirical].
 
-  The perception of a characteristic of one’s job as a resource or demand activates one of two unique processes: either health impairment or motivation @bakker2014job.
-Demanding job characteristics are frequently associated with negative outcomes (e.g., health impairment process; @bakker2003dual), whereas job characteristics considered resources have been associated with positive organizational outcomes like engagement and motivation (@bakker2007job).
-
-## An Added Complexity: Perception (Appraisal) of Work Characteristics Might Matter
-
-  The above description speaks to one of two distinct processes being activated, presumably based on one’s assessment of how a work characteristics makes them feel (e.g., consider the different reactions employees may have to being nominated to give a speech at an upcoming company event).
-Thus, although some research on job demands in particular is based on a priori classifications of demands (@searle2015merits), the appraisal of any work characteristic as a demand or resource is quite subjective.
-The literature on the experience of stress explains how such individual differences in appraisal are possible.
-Specifically, the transactional theory of stress and coping states that people cognitively appraise stimuli in their environments on a continuous basis (@lazarus1984stress).
-During this process, meaning is assigned to stimuli.
-If the above employee appraised the upcoming speech as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping (e.g., attempting to decline, asking for help in writing the speech).
-From that point, the cycle of appraisal continues based on the action to cope with the stressor (@lazarus1984stress).
-
-## Could a Work Demand be Appraised Positively?: The Challenge-Hindrance Framework
-
-  Although the word “stress” often connotes something negative,@selye1936syndrome defined stress generically as a response to change.
-For instance, the example above describes an employee who appraises being nominated to give a speech as a negative stressor.
-However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
-The terms associated with the two different appraisals of the stressor described here are challenge and hindrance demands (@cavanaugh2000empirical) Specifically, challenge demands promote mastery, personal growth, and future gains.
-Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes (e.g., @cavanaugh2000empirical).
-We will explore their associations with both positive and negative outcomes in this study.
-
-  Prior to proposing specific predictions, the empirical evidence on challenge and hindrance demands is very briefly shared below.
-To begin, the first logical question is whether employees actually distinguish between challenge and hindrance stressors, and research suggests that they can and do.
+Prior to proposing specific predictions regarding the current SIOP presentation, the empirical evidence on challenge and hindrance demands is very briefly shared below.
+To begin, the first logical question is whether employees actually distinguish between challenges and hindrances, and research suggests that they can and do.
 For example, @bakker2013weekly found that perceived work pressure can be classified as a hindrance demand, and emotional demands as a challenge demand.
@@
 Interestingly, they found that while each could be appraised primarily as challenges or hindrances, employees could also simultaneously be perceived as being both a challenge and hindrance.
-
-  Having established that there can be individual differences in the appraisal of demands as challenges or resources, we next turn our attention to their association with organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and well-being.
-For example, @cavanaugh2000empirical found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern with job satisfaction and job search behaviors in a sample of managers.
-However, @abbas2019challenge found that challenge and hindrance stressors were both positively related to strain and turnover intentions.
-We also have some evidence that challenge-hinderance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (@crawford2010linking).
-The appraisal process also suggests theoretically that the perception of a job characteristic as a challenge or hindrance is a mediator.
-@gerich2017relevance, for instance, found that employee well-being was, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
-To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, @podsakoff2007differential meta-analysis supported the original assertion of @cavanaugh2000empirical such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.
 
@@
 
-## Limitations and Future Directions
+We conceptualized resources and demands in terms of perceived total amounts.
 
-As with any piece of research, the process and results have limitations, but also provide a variety of additional directions to pursue in the future.
-First, while a strength of this project, arguably, is the use of O*Net items, practical considerations limited the number of job characteristics we could include in our survey.
-Future study could consider additional or other O*Net items.
-We conceptualized resources and demands in terms of perceived total amounts.
-It may be the case that certain kinds of resources or challenges are more strongly associated with engagement than others, and such, future research could explore the importance of resources/challenges categorically.
-Further, our study was limited to three outcomes of interest.
-It would be especially interesting to explore additional outcomes (e.g., job satisfaction) as well, or whether volume of resources and demands operationalized in this way are related to other behaviors (e.g., turnover intention, perceived organizational support, commitment).
+The dissociation of challenges and hindrances may be important moving forward.
+@cavanaugh2000empirical found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern with job satisfaction and job search behaviors in a sample of managers.
+However, @abbas2019challenge found that challenge and hindrance stressors were both positively related to strain and turnover intentions.
+We also have some evidence that challenge-hinderance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (@crawford2010linking).
+The appraisal process also suggests theoretically that the perception of a job characteristic as a challenge or hindrance is a mediator.
+@gerich2017relevance, for instance, found that employee well-being was, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
+To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, @podsakoff2007differential meta-analysis supported the original assertion of @cavanaugh2000empirical such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.
 

### 2022-10-11 SIOP2023/Counts/convergence.tex
switching projects for bit

@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Demanding resources: Agreement of perceptions for challenge and resource characteristics},
-  pdfauthor={John Kulas1 \& Alicia Stachowski2},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Demanding resources: Agreement across characteristics seen as both challenges and resources},
+  pdfauthor={John Kulas1 \& Alicia Stachowski2},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
-\title{Demanding resources: Agreement of perceptions for challenge and resource characteristics}
+\title{Demanding resources: Agreement across characteristics seen as both challenges and resources}
 \author{John Kulas\textsuperscript{1} \& Alicia Stachowski\textsuperscript{2}}
@@
 
-\begin{verbatim}
-## Warning: package 'tinylabels' was built under R version 4.1.3
-\end{verbatim}
-
-A plethora of research applying the job demands-resources model (Demerouti et al.
-(2001)) and job demands-resources theory (Bakker and Demerouti (2017)) underscore the importance of work characteristics on the experience of motivation and strain.
-However, much of our existing research on this topic assumes that certain characteristics are resources and others are generally considered demands.
-This study explores how individual perceptions of these work characteristics relate to engagement, stress, and burnout by asking respondents to indicate (of the characteristics that apply to their jobs) how much each is a resource, challenge, or hindrance demand.
-Amount of perceived resources, challenges, and hindrances can then be associated with engagement, stress, and burnout.
-
-\hypertarget{the-job-demands-resources-theory}{%
-\subsection{The Job Demands-Resources Theory}\label{the-job-demands-resources-theory}}
-
-The theoretical foundation for this study is the job demands-resources theory (Demerouti et al.
-(2001)).
-Using this theory, we can model both work environment and job characteristics via job resources and demands.
-Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al.
-(2001)).
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure; Demerouti et al.
-(2001)).
-
-The perception of a characteristic of one's job as a resource or demand activates one of two unique processes: either health impairment or motivation Bakker and Demerouti (2014).
-Demanding job characteristics are frequently associated with negative outcomes (e.g., health impairment process; Bakker et al.
-(2003)), whereas job characteristics considered resources have been associated with positive organizational outcomes like engagement and motivation (Bakker et al.
-(2007)).
-
-\hypertarget{an-added-complexity-perception-appraisal-of-work-characteristics-might-matter}{%
-\subsection{An Added Complexity: Perception (Appraisal) of Work Characteristics Might Matter}\label{an-added-complexity-perception-appraisal-of-work-characteristics-might-matter}}
-
-The above description speaks to one of two distinct processes being activated, presumably based on one's assessment of how a work characteristics makes them feel (e.g., consider the different reactions employees may have to being nominated to give a speech at an upcoming company event).
-Thus, although some research on job demands in particular is based on a priori classifications of demands (Searle and Auton (2015)), the appraisal of any work characteristic as a demand or resource is quite subjective.
-The literature on the experience of stress explains how such individual differences in appraisal are possible.
-Specifically, the transactional theory of stress and coping states that people cognitively appraise stimuli in their environments on a continuous basis (Lazarus and Folkman (1984)).
-During this process, meaning is assigned to stimuli.
-If the above employee appraised the upcoming speech as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping (e.g., attempting to decline, asking for help in writing the speech).
-From that point, the cycle of appraisal continues based on the action to cope with the stressor (Lazarus and Folkman (1984)).
+An abundance of research applying the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker \& Demerouti, 2017) underscores the importance of job characteristics on the experience of work.
+Resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
+Demands, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure, Demerouti et al., 2001).
+These two categories of outcomes (e.g., ``good'' and ``bad'') are thought to occur via one of two different mechanisms: motivational (resulting from resources) or health impairment (resulting from demands, Bakker \& Demerouti, 2014).
+Much of our existing research on the JD-R assumes that certain characteristics (for example, autonomy) are resources and others (for example, time constraints) are generally considered demands.
+This study searches instead for circumstances that provide exception to this static dichotomy of job characteristic mutual exclusivity.
 
 \hypertarget{could-a-work-demand-be-appraised-positively-the-challenge-hindrance-framework}{%
-\subsection{Could a Work Demand be Appraised Positively?: The Challenge-Hindrance Framework}\label{could-a-work-demand-be-appraised-positively-the-challenge-hindrance-framework}}
+\subsection{Could a Work Demand be Appraised ``Positively''?: The Challenge-Hindrance Framework}\label{could-a-work-demand-be-appraised-positively-the-challenge-hindrance-framework}}
 
-Although the word ``stress'' often connotes something negative,Selye (1936) defined stress generically as a response to change.
-For instance, the example above describes an employee who appraises being nominated to give a speech as a negative stressor.
+Although the word ``stress'' often carries a negative connotation, the ``father'' of the current concept, Selye (1936), conceptualized stress much less perjoratively - rather thinking of it as a \emph{response to change}.
+For instance, consider the different reactions two different employees may have to being nominated to give a speech at an upcoming company event.
+One may appraise the nomination as a negative stressor.
 However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
-The terms associated with the two different appraisals of the stressor described here are challenge and hindrance demands (Cavanaugh et al.
-(2000)) Specifically, challenge demands promote mastery, personal growth, and future gains.
+Selye the physician would likely have labeled the two responses as subjective manifestations of ``Distress'', and ``Eustress'' (Selye, 1974).
+In modern I-O Psychology parlance (and more consistent with the JD-R framework), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a \emph{challenge} while the other would appraise the demand as a \emph{hindrance} (Cavanaugh et al., 2000).
+According to Cavanaugh et al.
+(2000), challenge demands promote mastery, personal growth, and future gains.
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes (e.g., Cavanaugh et al.
-(2000)).
-We will explore their associations with both positive and negative outcomes in this study.
+Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes (e.g., Cavanaugh et al., 2000).
 
-Prior to proposing specific predictions, the empirical evidence on challenge and hindrance demands is very briefly shared below.
-To begin, the first logical question is whether employees actually distinguish between challenge and hindrance stressors, and research suggests that they can and do.
+Prior to proposing specific predictions regarding the current SIOP presentation, the empirical evidence on challenge and hindrance demands is very briefly shared below.
+To begin, the first logical question is whether employees actually distinguish between challenges and hindrances, and research suggests that they can and do.
 For example, Bakker and Sanz-Vergel (2013) found that perceived work pressure can be classified as a hindrance demand, and emotional demands as a challenge demand.
@@
 Interestingly, they found that while each could be appraised primarily as challenges or hindrances, employees could also simultaneously be perceived as being both a challenge and hindrance.
-
-Having established that there can be individual differences in the appraisal of demands as challenges or resources, we next turn our attention to their association with organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and well-being.
-For example, Cavanaugh et al.
-(2000) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern with job satisfaction and job search behaviors in a sample of managers.
-However, Abbas and Raja (2019) found that challenge and hindrance stressors were both positively related to strain and turnover intentions.
-We also have some evidence that challenge-hinderance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford et al.
-(2010)).
-The appraisal process also suggests theoretically that the perception of a job characteristic as a challenge or hindrance is a mediator.
-Gerich (2017), for instance, found that employee well-being was, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
-To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, Podsakoff et al.
-(2007) meta-analysis supported the original assertion of Cavanaugh et al.
-(2000) such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.
 
@@
 
-\hypertarget{limitations-and-future-directions}{%
-\subsection{Limitations and Future Directions}\label{limitations-and-future-directions}}
+We conceptualized resources and demands in terms of perceived total amounts.
 
-As with any piece of research, the process and results have limitations, but also provide a variety of additional directions to pursue in the future.
-First, while a strength of this project, arguably, is the use of O\emph{Net items, practical considerations limited the number of job characteristics we could include in our survey.
-Future study could consider additional or other O}Net items.
-We conceptualized resources and demands in terms of perceived total amounts.
-It may be the case that certain kinds of resources or challenges are more strongly associated with engagement than others, and such, future research could explore the importance of resources/challenges categorically.
-Further, our study was limited to three outcomes of interest.
-It would be especially interesting to explore additional outcomes (e.g., job satisfaction) as well, or whether volume of resources and demands operationalized in this way are related to other behaviors (e.g., turnover intention, perceived organizational support, commitment).
+The dissociation of challenges and hindrances may be important moving forward.
+Cavanaugh et al.
+(2000) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern with job satisfaction and job search behaviors in a sample of managers.
+However, Abbas and Raja (2019) found that challenge and hindrance stressors were both positively related to strain and turnover intentions.
+We also have some evidence that challenge-hinderance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford et al.
+(2010)).
+The appraisal process also suggests theoretically that the perception of a job characteristic as a challenge or hindrance is a mediator.
+Gerich (2017), for instance, found that employee well-being was, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
+To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, Podsakoff et al.
+(2007) meta-analysis supported the original assertion of Cavanaugh et al.
+(2000) such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.
 
@@
 Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2003dual}{}}%
-Bakker, A.
-B., Demerouti, E., \& Schaufeli, W.
-(2003).
-Dual processes at work in a call centre: An application of the job demands--resources model.
-\emph{European Journal of Work and Organizational Psychology}, \emph{12}(4), 393--417.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2007job}{}}%
-Bakker, A.
-B., Hakanen, J.
-J., Demerouti, E., \& Xanthopoulou, D.
-(2007).
-Job resources boost work engagement, particularly when job demands are high.
-\emph{Journal of Educational Psychology}, \emph{99}(2), 274.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
-Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
-
 \leavevmode\vadjust pre{\hypertarget{ref-podsakoff2007differential}{}}%
@@
 \emph{Journal of Applied Psychology}, \emph{92}(2), 438.
-
-\leavevmode\vadjust pre{\hypertarget{ref-searle2015merits}{}}%
-Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.
 

### 2022-10-11 SIOP2023/Counts/convergence.Rmd
caught a "hinderance"

@@
 However, @abbas2019challenge found that challenge and hindrance stressors were both positively related to strain and turnover intentions.
-We also have some evidence that challenge-hinderance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (@crawford2010linking).
+We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (@crawford2010linking).
 The appraisal process also suggests theoretically that the perception of a job characteristic as a challenge or hindrance is a mediator.

### 2022-10-12 SIOP2023/Counts/convergence.Rmd
push before meeting

@@
 
-The O\*Net descriptors are written in a similar manner to a task statement presented within a job analysis.
-For example, the descriptor for "level of competition", which is an element of the "structural job characteristics" grouping, is *...to what extent does this job require the worker to compete or to be aware of competitive pressures?*.
-Other than minor grammatical editing (for example, changing “the worker” to “you”), we retained the O\*Net wording for our item stems.
-We also retained O\*Net’s response scales, several of which were unique across items, but all shared the same 1 to 5 scale options.
+The O\*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to "responsibility" than task.
+For example, the descriptor for "level of competition", which is an element of the "structural job characteristics" grouping, is *...to what extent does this job require the worker to compete or to be aware of competitive pressures?* Other than minor grammatical editing (for example, changing “the worker” to “you”), we retained the O\*Net wording for our item stems.
+We also retained O\*Net’s response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
+It would likely NOT be considered controversial to referred to these as "effectively" Likert-type response scales.
+
+>put example response scale in
+
 Subsequent to providing ratings of whether or not each of the 98 O\*Net characteristics were relevant for the respondent’s work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) .
@@
 
-The total number of items on the survey was less than 392 (98 characteristics x 4 administrations), because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very little variance across respondents (one excluded characteristic, for example, was *...the extent to which thr worker is exposed to radiation on the job*).
+The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
 
@@
 
-Eligibility requirements included being 18+ and holding either a full-time or part-time job.
+Eligibility requirements included being 18 or older and holding either a full- or part-time job.
 Participants were asked to think about their primary job while answering the survey.
@@
 Hypothesis 1 predicted a positive association between total resources and total challenge demands.
-Table \@ref(tab:cortab) shows a very high association between a characteristic being implicated as a resource as well as a challenge (*r* = .85).
+Table \@ref(tab:cortab) shows a very high association between resources and challenges (*r* = .86).
 These associations, however, are only capturing the relationships between these demands and resources in *sheer volume*.
 That is, table \@ref(tab:cortab) operationalized each variable as the sheer number of resources, hindrances, or challenges that a respondent indicated were present within their job.
-This correlational analysis simply implies that workers who experience more resources also percieve greater challenges (with significant but muted associations between the other contrasts).
+This correlational analysis simply implies that workers who experience more resources also perceive greater challenges.
+The associations between resources and hindrances (*r* = .23) and challenges and hindrances (*r* = .22) were also significantly positive with moderate magnitude associations, suggesting that some of this "sheer volume" may be capturing job complexity (that is, the more complex the job, the more characteristics are relevant, and therefore the more likely it is to have *more* challenges as well as *more* hindrances as well as *more* resources).
+Although we did not address job complexity as a moderator in the current paper, we do plan to do so in future investigations.
+Also, take note of the average numbers of resources, challenges, and hindrances cited by our sample, where these respondents generally experienced fewer hindrances in their jobs (*M* = 13.09) than both resources and challenges.
 
->Note. Why is resource-hindrance association positive? Look at scatterplot if have time
+>Note. Should probably run a quick anova on these
 
-```{r percagree, fig.cap="Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance.", fig.height=10}
+```{r percagree, fig.cap="Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance).", fig.height=10}
 
@@
 
+### Convergence (same characteristic).
+
 We next looked for convergence of perception at the level of each individual job characteristic.
@@
 Here we categorized each characteristic by its O\*Net "scale" (one of seven), and the graph shows greater consistency across certain characteristics (for example, *Mental Processes* or *Interacting with Others*) and less convergence across other *types* of job activities (for example, *Physical* characteristics).
-A repeated-measures ANOVA retaining these 7 scales as independent variables yielded a treatment effect of $F_(6, 3,402)$ = 613.5, *p* < .001 (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001.
+A repeated-measures ANOVA retaining these 7 scales as independent variables yielded a treatment effect of $F_{(6, 3,402)}$ = 613.5, *p* < .001 (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001.
 

### 2022-10-12 SIOP2023/Counts/convergence.tex
push before meeting

@@
 
-The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis.
-For example, the descriptor for ``level of competition'', which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?}.
-Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems.
-We also retained O*Net's response scales, several of which were unique across items, but all shared the same 1 to 5 scale options.
+The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task.
+For example, the descriptor for ``level of competition'', which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems.
+We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
+It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.
+
+\begin{quote}
+put example response scale in
+\end{quote}
+
 Subsequent to providing ratings of whether or not each of the 98 O*Net characteristics were relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) .
@@
 
-The total number of items on the survey was less than 392 (98 characteristics x 4 administrations), because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very little variance across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which thr worker is exposed to radiation on the job}).
+The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
 
@@
 Hypothesis 1 predicted a positive association between total resources and total challenge demands.
-Table \ref{tab:cortab} shows a very high association between a characteristic being implicated as a resource as well as a challenge (\emph{r} = .85).
+Table \ref{tab:cortab} shows a very high association between resources and challenges (\emph{r} = .86).
 These associations, however, are only capturing the relationships between these demands and resources in \emph{sheer volume}.
 That is, table \ref{tab:cortab} operationalized each variable as the sheer number of resources, hindrances, or challenges that a respondent indicated were present within their job.
-This correlational analysis simply implies that workers who experience more resources also percieve greater challenges (with significant but muted associations between the other contrasts).
+This correlational analysis simply implies that workers who experience more resources also perceive greater challenges.
+The associations between resources and hindrances (\emph{r} = .23) and challenges and hindrances (\emph{r} = .22) were also significantly positive with moderate magnitude associations, suggesting that some of this ``sheer volume'' may be capturing job complexity (that is, the more complex the job, the more characteristics are relevant, and therefore the more likely it is to have \emph{more} challenges as well as \emph{more} hindrances as well as \emph{more} resources).
+Although we did not address job complexity as a moderator in the current paper, we do plan to do so in future investigations.
+Also, take note of the average numbers of resources, challenges, and hindrances cited by our sample, where these respondents generally experienced fewer hindrances in their jobs (\emph{M} = 13.09) than both resources and challenges.
 
 \begin{quote}
-Note. Why is resource-hindrance association positive? Look at scatterplot if have time
+Note. Should probably run a quick anova on these
 \end{quote}
@@
 \includegraphics{convergence_files/figure-latex/percagree-1.pdf}
-\caption{\label{fig:percagree}Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance.}
+\caption{\label{fig:percagree}Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance).}
 \end{figure}
+
+\hypertarget{convergence-same-characteristic.}{%
+\subsubsection{Convergence (same characteristic).}\label{convergence-same-characteristic.}}
 
@@
 Here we categorized each characteristic by its O*Net ``scale'' (one of seven), and the graph shows greater consistency across certain characteristics (for example, \emph{Mental Processes} or \emph{Interacting with Others}) and less convergence across other \emph{types} of job activities (for example, \emph{Physical} characteristics).
-A repeated-measures ANOVA retaining these 7 scales as independent variables yielded a treatment effect of \(F_(6, 3,402)\) = 613.5, \emph{p} \textless{} .001 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001.
+A repeated-measures ANOVA retaining these 7 scales as independent variables yielded a treatment effect of \(F_{(6, 3,402)}\) = 613.5, \emph{p} \textless{} .001 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001.
 
@@
 However, Abbas and Raja (2019) found that challenge and hindrance stressors were both positively related to strain and turnover intentions.
-We also have some evidence that challenge-hinderance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford et al.
+We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford et al.
 (2010)).

### 2022-10-12 SIOP2023/SIOP_PROCESS.Rmd
hopefully final, Alicia is going to export "SIOP_PROCESS.pdf" as a Word document

@@
 
+abstract: |
+  This project explored the role of resources on the demand-strain relationship through the lens of O\*Net derived job characteristics.
+When dissociating demands into challenges and hindrances, we did find tentative support for resources moderating the hindrance-strain relationship.
+
 keywords          : "keywords"
@@
 The Job Demands-Resources Theory [JD-R, @demerouti2001job] has received wide support across contexts and varied research questions.
-We extend the literature by 1) exploring the interaction between job demands and resources on the experience of stress using O\*Net job characteristics and 2) considering also the appraisal of demands as challenge or hindrance stressors.
+We extend the literature by 1) exploring the interaction between job demands and resources on the experience of strain using O\*Net job characteristics and 2) considering also the appraisal of demands as challenge or hindrance stressors.
 Here, respondents made a series of evaluations that used: direct O\*Net terminology (both descriptor and response option), and JD-R influenced ratings of challenge and hindrance stressors.
@@
 
-The stress literature speaks to the key consideration of the way employees appraise situations or circumstances - in this case, our focus will be on work characteristics.
+The stress/strain literature speaks to the key consideration of the way employees appraise situations or circumstances - in this case, our focus will be on work characteristics.
 The transactional theory of stress and coping suggests that people cognitively appraise stimuli in their environments on a continuous basis [@lazarus1984stress].
@@
 Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes [e.g., @cavanaugh2000empirical].
-Our focus here will be on the connection between hindrance demands specifically, and their association with reported stress.
-More specifically, our interest here is whether or not the negative hindrance association we typically observe between demands and stress can be buffered by perceived resources.
+Our focus here will be on the connection between hindrance demands specifically, and their association with reported strain.
+More specifically, our interest here is whether or not the negative hindrance association we typically observe between demands and strain can be buffered by perceived resources.
 
@@
 For instance, we assume that generally, time pressure is a negative demand on an employee.
-However, the stress experience, or process, described early on by @lazarus1984stress is grounded in the assumption that individual appraisals of stressors/demands vary.
+However, the stress/strain experience, or process, described early on by @lazarus1984stress is grounded in the assumption that individual appraisals of stressors/demands vary.
 Their transactional theory of stress and coping states that people continuously appraise stimuli in their environments.
@@
 If a stimulus is appraised as a stressor (threat, challenge, potentially harmful), emotional distress leads to coping of some kind.
-This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes is not appraised as favorable [@lazarus1984stress].
+This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes are not appraised as favorable [@lazarus1984stress].
 As such, the stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.
@@
 Starting with job demands, @webster2011extending  studied workload, role ambiguity, and role conflict, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being *both* a challenge and hindrance to different degrees.
-While their study not did include resources, it does document individual differences in how people may perceive stressors at work.
-
->Although not the primary focus of their paper, @sonnega_comparison_2018 compared self-reported (subjective) ratings of the degree of physical demands, stress, and a need for intense concentration from the Health and Retirement Study with objective ratings from O\*Net.
-Correlations physical demand (*r* = .52), stress (*r* = .10), and need for intense concentration (*r* = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than we tend to think.
+While their study did not include resources, it does document individual differences in how people may perceive stressors at work.
+Additionally, although not the primary focus of their paper, @sonnega_comparison_2018 compared self-reported (subjective) ratings of job demands with more objective ratings of the same characteristics, finding that perceptions of characteristics may be subject to a greater level of individual difference than we tend to think.
 
 While the above two studies provide evidence for variability in how workers view *demands*, @schmitz_interpreting_2019 went on to further capture subjective and objective *resources* in their study of retirement.
-
->[Same as above]: Correlations of composite variables between subjective and objective measures for the resources of autonomy (*r* = .12.
-p > .01), recognition of work (*r* = .07, p > .01), and decision freedom (*r* = .08, p > .01), while significant, certainly do not reflect high levels of overlap.
-
-We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees.
+They found only very small associations between subjective and objective measures for the "typically implicated" as resources variables of: 1) autonomy, 2) recognition of work, and 3) decision making freedom, again suggesting universal classification may not be appropriate.
 @downes2021incorporating meta-analysis addresses this reality in depth, although a broader current elaboration is beyond the scope of this SIOP presentation.
@@
 
-Our unique contribution in the current study is in whether or not *perceptions* of demands as hindrances or challenges are related to experienced stress, and whether or not this relationship is moderated by the presence of resources.
-We do have some existing evidence that this occurs with other outcomes beyond stress.
+Our unique contribution in the current study is in whether or not *perceptions* of demands as hindrances or challenges are related to experienced strain, and whether or not this relationship is moderated by the presence of resources.
+We do have some existing evidence that this occurs with other outcomes beyond strain.
 For example, @tadic2015challenge found that daily hindrance job demands were negatively related to both positive affect and engagement in a sample of primary school teachers.
 Daily job resources, in this sample, buffered the relationships between hindrances and affect and engagement.
-With the current investigation, we propose that greater perceived resources generally, as opposed to daily, would also buffer the relationship between perceived hindrance stressors and, in this, case, perceived stress.
+With the current investigation, we propose that greater perceived resources generally, as opposed to daily, would also buffer the relationship between perceived hindrance stressors and, in this, case, experienced strain.
 The following two predictions are made:
 
->*H1*. There is a positive relationship between perceived hindrance stressors and stress.
+>*H1*. There is a positive relationship between perceived hindrance stressors and strain.
 
->*H2*. The relationship between mean perceived hindrances and stress will be moderated by resources such that this relationship is diminished as perceived resources increase.
+>*H2*. The relationship between mean perceived hindrances and strain will be moderated by resources such that this relationship is diminished as perceived resources increase.
 
@@
 
-### Stress.
+### Strain.
 
-Three items taken from the Copenhagen Psychosocial Questionnaire [@burr_third_2019] captured stress (an example item is: "How often have you had problems relaxing because of your job?").
+Three items taken from the Copenhagen Psychosocial Questionnaire [@burr_third_2019] captured strain (an example item is: "How often have you had problems relaxing because of your job?").
 Responses were made on a 5-point scale ranging from "not at all" to "all the time".
@@
 See Table \@ref(tab:cortab).
-With regard to H1, which predicted a positive association between perceived hindrance stressors and stress, a small positive relationship was observed, *r* = .09, *p* < .05.
+With regard to H1, which predicted a positive association between perceived hindrance stressors and strain, a small positive relationship was observed, *r* = .09, *p* < .05.
 Thus, "weak" support was found for H1.
@@
 papaja::apa_table(table,
-                  caption = "Results from a regression analysis examining the moderation of resources on the relationship between hindrance demands and stress",
-                  note = "$R^2$ here",
+                  caption = "Results from a regression analysis examining the moderation of resources on the relationship between hindrance demands and strain",
+#                  note = "$R^2$ here",
                   landscape = FALSE,
@@
 First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, $F_{(3, 564)}$ = 3.29, *p* = .020.
-The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, $F_{(3, 564)}$ = 3.51, *p* = .061, providing marginal support for H2.
-As can be seen in Figure \@ref(fig:analyses), those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources.
-As such, these results provide some evidence that resources may moderate the relationship between hindrance demands and subsequent levels of stress.
+The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and strain was conditional on resources, $F_{(3, 564)}$ = 3.51, *p* = .061, providing marginal support for H2.
+As can be seen in Figure \@ref(fig:analyses), those with fewer resources show a much stronger positive relationship between hindrances and strain than those with more resources.
+As such, these results provide some evidence that resources may moderate the relationship between hindrance demands and subsequent levels of strain.
 
@@
 
-The primary goal of this project was to further explore the role of perceived resources on the hindrance-stress relationship using O\*Net characteristics.
-While we have plentiful evidence that resources can buffer the effects of a variety of job demands on burnout, this project focuses on subjective experiences of resources and demands, focusing on demands rated as challenges and hindrances, as well as focusing on the outcome of *stress*.
-As expected, the results suggest a positive relationship between perceived hindrances and stress (H1).
+The primary goal of this project was to further explore the role of perceived resources on the hindrance-strain relationship using O\*Net characteristics.
+While we have plentiful evidence that resources can buffer the effects of a variety of job demands on burnout, this project focuses on subjective experiences of resources and demands, focusing on demands rated as challenges and hindrances, as well as focusing on the outcome of *strain*.
+As expected, the results suggest a positive relationship between perceived hindrances and strain (H1).
 While intuitive, it is important to replicate this finding before we explore the impact of perceived resources, which arguably, is something that employers may have more leverage to control than hindrance stressors.
 
-Second, the results serve to support the assertion that resources change the relationship between hindrances and stress such that the connection between the two is diminished as resources increase (H2).
-While not hypothesized or presented above, the authors did also run a regression on the *challenge*-stress relationship with resources as a moderator, with the assumption that resources would not moderate the relationship.
+Second, the results serve to support the assertion that resources change the relationship between hindrances and strain such that the connection between the two is diminished as resources increase (H2).
+While not hypothesized or presented above, the authors did also run a regression on the *challenge*-strain relationship with resources as a moderator, with the assumption that resources would not moderate the relationship.
 The findings, indeed, did not indicate a moderated relationship in this case.
 It appears that resources are of benefit particularly when hindrances are present.
-In particular, the Job-demands Resources Theory [@demerouti2001job] suggests that resources would buffer the negative impact between demands and stress, and by extension, given the more traditional conceptualization of demands would be aligned with hindrance demands.
+In particular, the Job-demands Resources Theory [@demerouti2001job] suggests that resources would buffer the negative impact between demands and strain, and by extension, given the more traditional conceptualization of demands would be aligned with hindrance demands.
 These findings have implications worth considering.
@@
 Our project focused on the characteristics of one's work specifically, and in line with the literature cited above, studied the ratings or perceptions of resources and demands to account for individual differences in the way employees appraise components of their work.
-From a academic research standpoint, these findings integrate three related literatures: the job-demands resources, stress appraisal, and challenge-hindrance framework to examine the experience of employees across jobs - specifically, the way that resources and hindrance demands interact on the experience of stress.
+From a academic research standpoint, these findings integrate three related literatures: the job-demands resources, stress appraisal, and challenge-hindrance framework to examine the experience of employees across jobs - specifically, the way that resources and hindrance demands interact on the experience of strain.
 Results align with what all three theories/frameworks would suggest.
@@
 Is it overall perceptions of having more resources that makes up for hindrances, or could it be that certain resources carry more weight?
-Second, our focus here was on the outcome of stress, but it may also be of value to consider what the interaction between ratings of O\*Net characteristics as resources and hindrances looks like on other outcomes of interest in a work context (e.g., commitment, motivation, engagement, intent to quit).
+Second, our focus here was on the outcome of strain, but it may also be of value to consider what the interaction between ratings of O\*Net characteristics as resources and hindrances looks like on other outcomes of interest in a work context (e.g., commitment, motivation, engagement, intent to quit).
 

### 2022-10-12 SIOP2023/SIOP_PROCESS.tex
hopefully final, Alicia is going to export "SIOP_PROCESS.pdf" as a Word document

@@
 
+\abstract{%
+This project explored the role of resources on the demand-strain relationship through the lens of O*Net derived job characteristics.
+When dissociating demands into challenges and hindrances, we did find tentative support for resources moderating the hindrance-strain relationship.
+}
+
 \begin{document}
@@
 The Job Demands-Resources Theory (JD-R, Demerouti et al., 2001) has received wide support across contexts and varied research questions.
-We extend the literature by 1) exploring the interaction between job demands and resources on the experience of stress using O*Net job characteristics and 2) considering also the appraisal of demands as challenge or hindrance stressors.
+We extend the literature by 1) exploring the interaction between job demands and resources on the experience of strain using O*Net job characteristics and 2) considering also the appraisal of demands as challenge or hindrance stressors.
 Here, respondents made a series of evaluations that used: direct O*Net terminology (both descriptor and response option), and JD-R influenced ratings of challenge and hindrance stressors.
@@
 
-The stress literature speaks to the key consideration of the way employees appraise situations or circumstances - in this case, our focus will be on work characteristics.
+The stress/strain literature speaks to the key consideration of the way employees appraise situations or circumstances - in this case, our focus will be on work characteristics.
 The transactional theory of stress and coping suggests that people cognitively appraise stimuli in their environments on a continuous basis (Lazarus \& Folkman, 1984).
@@
 Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes (e.g., Cavanaugh et al., 2000).
-Our focus here will be on the connection between hindrance demands specifically, and their association with reported stress.
-More specifically, our interest here is whether or not the negative hindrance association we typically observe between demands and stress can be buffered by perceived resources.
+Our focus here will be on the connection between hindrance demands specifically, and their association with reported strain.
+More specifically, our interest here is whether or not the negative hindrance association we typically observe between demands and strain can be buffered by perceived resources.
 
@@
 For instance, we assume that generally, time pressure is a negative demand on an employee.
-However, the stress experience, or process, described early on by Lazarus and Folkman (1984) is grounded in the assumption that individual appraisals of stressors/demands vary.
+However, the stress/strain experience, or process, described early on by Lazarus and Folkman (1984) is grounded in the assumption that individual appraisals of stressors/demands vary.
 Their transactional theory of stress and coping states that people continuously appraise stimuli in their environments.
@@
 If a stimulus is appraised as a stressor (threat, challenge, potentially harmful), emotional distress leads to coping of some kind.
-This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes is not appraised as favorable (Lazarus \& Folkman, 1984).
+This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes are not appraised as favorable (Lazarus \& Folkman, 1984).
 As such, the stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.
@@
 (2011) studied workload, role ambiguity, and role conflict, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being \emph{both} a challenge and hindrance to different degrees.
-While their study not did include resources, it does document individual differences in how people may perceive stressors at work.
-
-\begin{quote}
-Although not the primary focus of their paper, Sonnega et al.
-(2018) compared self-reported (subjective) ratings of the degree of physical demands, stress, and a need for intense concentration from the Health and Retirement Study with objective ratings from O*Net.
-Correlations physical demand (\emph{r} = .52), stress (\emph{r} = .10), and need for intense concentration (\emph{r} = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than we tend to think.
-\end{quote}
+While their study did not include resources, it does document individual differences in how people may perceive stressors at work.
+Additionally, although not the primary focus of their paper, Sonnega et al.
+(2018) compared self-reported (subjective) ratings of job demands with more objective ratings of the same characteristics, finding that perceptions of characteristics may be subject to a greater level of individual difference than we tend to think.
 
@@
 (2019) went on to further capture subjective and objective \emph{resources} in their study of retirement.
-
-\begin{quote}
-{[}Same as above{]}: Correlations of composite variables between subjective and objective measures for the resources of autonomy (\emph{r} = .12.
-p \textgreater{} .01), recognition of work (\emph{r} = .07, p \textgreater{} .01), and decision freedom (\emph{r} = .08, p \textgreater{} .01), while significant, certainly do not reflect high levels of overlap.
-\end{quote}
-
-We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees.
+They found only very small associations between subjective and objective measures for the ``typically implicated'' as resources variables of: 1) autonomy, 2) recognition of work, and 3) decision making freedom, again suggesting universal classification may not be appropriate.
 Downes et al.
@@
 
-Our unique contribution in the current study is in whether or not \emph{perceptions} of demands as hindrances or challenges are related to experienced stress, and whether or not this relationship is moderated by the presence of resources.
-We do have some existing evidence that this occurs with other outcomes beyond stress.
+Our unique contribution in the current study is in whether or not \emph{perceptions} of demands as hindrances or challenges are related to experienced strain, and whether or not this relationship is moderated by the presence of resources.
+We do have some existing evidence that this occurs with other outcomes beyond strain.
 For example, Tadić et al.
@@
 Daily job resources, in this sample, buffered the relationships between hindrances and affect and engagement.
-With the current investigation, we propose that greater perceived resources generally, as opposed to daily, would also buffer the relationship between perceived hindrance stressors and, in this, case, perceived stress.
+With the current investigation, we propose that greater perceived resources generally, as opposed to daily, would also buffer the relationship between perceived hindrance stressors and, in this, case, experienced strain.
 The following two predictions are made:
@@
 \begin{quote}
-\emph{H1}. There is a positive relationship between perceived hindrance stressors and stress.
+\emph{H1}. There is a positive relationship between perceived hindrance stressors and strain.
 \end{quote}
@@
 \begin{quote}
-\emph{H2}. The relationship between mean perceived hindrances and stress will be moderated by resources such that this relationship is diminished as perceived resources increase.
+\emph{H2}. The relationship between mean perceived hindrances and strain will be moderated by resources such that this relationship is diminished as perceived resources increase.
 \end{quote}
@@
 
-\hypertarget{stress.}{%
-\subsubsection{Stress.}\label{stress.}}
+\hypertarget{strain.}{%
+\subsubsection{Strain.}\label{strain.}}
 
-Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019) captured stress (an example item is: ``How often have you had problems relaxing because of your job?'').
+Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019) captured strain (an example item is: ``How often have you had problems relaxing because of your job?'').
 Responses were made on a 5-point scale ranging from ``not at all'' to ``all the time''.
@@
 See Table \ref{tab:cortab}.
-With regard to H1, which predicted a positive association between perceived hindrance stressors and stress, a small positive relationship was observed, \emph{r} = .09, \emph{p} \textless{} .05.
+With regard to H1, which predicted a positive association between perceived hindrance stressors and strain, a small positive relationship was observed, \emph{r} = .09, \emph{p} \textless{} .05.
 Thus, ``weak'' support was found for H1.
@@
 
-\caption{\label{tab:table}Results from a regression analysis examining the moderation of resources on the relationship between hindrance demands and stress}
+\caption{\label{tab:table}Results from a regression analysis examining the moderation of resources on the relationship between hindrance demands and strain}
 
@@
 \bottomrule
-\addlinespace
 \end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} $R^2$ here}
-\end{tablenotes}
 
@@
 First, the overall regression model including mean hindrances, mean resources, and the interaction between the two variables was significant, \(F_{(3, 564)}\) = 3.29, \emph{p} = .020.
-The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and stress was conditional on resources, \(F_{(3, 564)}\) = 3.51, \emph{p} = .061, providing marginal support for H2.
-As can be seen in Figure \ref{fig:analyses}, those with fewer resources show a much stronger positive relationship between hindrances and stress than those with more resources.
-As such, these results provide some evidence that resources may moderate the relationship between hindrance demands and subsequent levels of stress.
+The interaction between hindrance and resources (uncentered) revealed that the relationship between hindrances and strain was conditional on resources, \(F_{(3, 564)}\) = 3.51, \emph{p} = .061, providing marginal support for H2.
+As can be seen in Figure \ref{fig:analyses}, those with fewer resources show a much stronger positive relationship between hindrances and strain than those with more resources.
+As such, these results provide some evidence that resources may moderate the relationship between hindrance demands and subsequent levels of strain.
 
@@
 
-The primary goal of this project was to further explore the role of perceived resources on the hindrance-stress relationship using O*Net characteristics.
-While we have plentiful evidence that resources can buffer the effects of a variety of job demands on burnout, this project focuses on subjective experiences of resources and demands, focusing on demands rated as challenges and hindrances, as well as focusing on the outcome of \emph{stress}.
-As expected, the results suggest a positive relationship between perceived hindrances and stress (H1).
+The primary goal of this project was to further explore the role of perceived resources on the hindrance-strain relationship using O*Net characteristics.
+While we have plentiful evidence that resources can buffer the effects of a variety of job demands on burnout, this project focuses on subjective experiences of resources and demands, focusing on demands rated as challenges and hindrances, as well as focusing on the outcome of \emph{strain}.
+As expected, the results suggest a positive relationship between perceived hindrances and strain (H1).
 While intuitive, it is important to replicate this finding before we explore the impact of perceived resources, which arguably, is something that employers may have more leverage to control than hindrance stressors.
 
-Second, the results serve to support the assertion that resources change the relationship between hindrances and stress such that the connection between the two is diminished as resources increase (H2).
-While not hypothesized or presented above, the authors did also run a regression on the \emph{challenge}-stress relationship with resources as a moderator, with the assumption that resources would not moderate the relationship.
+Second, the results serve to support the assertion that resources change the relationship between hindrances and strain such that the connection between the two is diminished as resources increase (H2).
+While not hypothesized or presented above, the authors did also run a regression on the \emph{challenge}-strain relationship with resources as a moderator, with the assumption that resources would not moderate the relationship.
 The findings, indeed, did not indicate a moderated relationship in this case.
 It appears that resources are of benefit particularly when hindrances are present.
-In particular, the Job-demands Resources Theory (Demerouti et al., 2001) suggests that resources would buffer the negative impact between demands and stress, and by extension, given the more traditional conceptualization of demands would be aligned with hindrance demands.
+In particular, the Job-demands Resources Theory (Demerouti et al., 2001) suggests that resources would buffer the negative impact between demands and strain, and by extension, given the more traditional conceptualization of demands would be aligned with hindrance demands.
 These findings have implications worth considering.
@@
 Is it overall perceptions of having more resources that makes up for hindrances, or could it be that certain resources carry more weight?
-Second, our focus here was on the outcome of stress, but it may also be of value to consider what the interaction between ratings of O*Net characteristics as resources and hindrances looks like on other outcomes of interest in a work context (e.g., commitment, motivation, engagement, intent to quit).
+Second, our focus here was on the outcome of strain, but it may also be of value to consider what the interaction between ratings of O*Net characteristics as resources and hindrances looks like on other outcomes of interest in a work context (e.g., commitment, motivation, engagement, intent to quit).
 

### 2022-10-12 SIOP2023/Counts/Submission_ResourceCount.tex
Hopefully final .pdf

--- 2022-10-08 SIOP2023/Counts/Submission_ResourceCount.tex
@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Perception of Work Demands and Resources: Does Sheer Volume Matter?},
-  pdfauthor={Alicia Stachowski1 \& John Kulas2},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Perception of Work Demands and Resources: Does Sheer Volume Matter?},
+  pdfauthor={Alicia Stachowski1 \& John Kulas2},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 \abstract{%
-The relationships among sum of perceived job resources, challenge- and hindrance demands and outcomes of organizational outcomes of engagement, stress, and burnout are explored.
-568 workers rated O*Net job characteristics in terms of relevance and perceptions as challenges, hindrances and resources.
-The findings are generally aligned with the job demands resource theory regarding associations between perceived resources, demands, and organizational outcomes of engagement, stress, and burnout.
+The relationships among total number of job resources, challenges, and hindrances and outcomes of engagement, stress, and burnout are explored.
+568 workers rated O*Net job characteristics in terms of relevance and interpretation of characteristics as challenges, hindrances and resources.
+The findings showed moderately strong connection between the presence of resources and challenge demands with job engagement.
 }
@@
 Thus, although some research on job demands in particular is based on \emph{a priori} classifications of demands (Searle \& Auton, 2015), the appraisal of any work characteristic as a demand or resource is actually subjective.
+
 The literature on the experience of stress explains how such individual differences in appraisal are possible.
@@
 During this process, meaning is assigned to stimuli.
-If our example fictional employee appraised the upcoming speech as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping (e.g., attempting to decline, asking for help in writing the speech).
-From that point, the cycle of appraisal continues based on the action to cope with the stressor (Lazarus \& Folkman, 1984).
-\footnote{This sentence needs clarification - comprehension is ocluded.}
+If our example fictional employee appraised the upcoming speech as threatening, challenging, or possibly harmful (in contrast to positive or irrelevant), the resulting emotional distress initiates coping (e.g., attempting to decline, asking for help in writing the speech).
+From that point, a reassessment of the situation happens, and the cycle of appraisal continues based on the action to cope with the stressor (Lazarus \& Folkman, 1984).
+This theory of stress and coping speaks to the importance of how work demands are assessed by individuals, and it is not only possible, but quite likely that demands and resources do not fit cleanly into objective categories of ``demands'' and ``resources''.
 
@@
 The brief review above provides theoretical and empirical support for the connection between resources and positive organizational outcomes, and between demands and negative outcomes.
-Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement (``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption,'' Schaufeli et al., 2002), workplace stress (``an individual state characterized by a combination of high arousal and displeasure,'' p.~15, Pejtersen et al., 2010) and burnout (``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work,'' p.~197, Kristensen et al., 2005).
+For this current study, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related to three organizational outcomes: engagement (``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption,'' Schaufeli et al., 2002), workplace stress (``an individual state characterized by a combination of high arousal and displeasure,'' p.~15, Pejtersen et al., 2010) and burnout (``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work,'' p.~197, Kristensen et al., 2005).
 Utilizing the job demands-resources theory, the transactional theory of stress, and the challenge-hindrance framework, we propose that the number of job characteristics appraised as ``challenge demands'' (i.e., promote mastery, personal growth, and future gains) would activate a positive state -- that of engagement.
@@
 
-The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample α's of 0.68 (absorption) and 0.80 (vigor), and 0.90 (dedication).
+The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample \(\alpha\)'s of 0.68 (absorption) and 0.80 (vigor), and 0.90 (dedication).
 For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, alpha = 0.91).
@@
 We used R (Version 4.0.3; R Core Team (2022)) and the R-packages careless (Version 1.1.3; Yentes \& Wilhelm, 2021), labourR (Version 1.0.0; Kouretsis et al., 2020), papaja (Version 0.1.0.9997; Aust \& Barth, 2020), and tinylabels (Barth, 2021) for all analyses.
-Our analyses are presented by characteristics of work that are rated in terms of being resources, challenge demands, and hindrance demands.
-Pearson correlation coefficients between characteristics classified as resources, challenges, and hindrances were obtained to investigate the associations among these characteristics.
+
 Correlations, means and standard deviations among all study variables are presented in Table \ref{tab:correlation_table}.
-Results reveal a positive association between resources and engagement (\emph{r} = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively).
-Challenge demands were positively associated with engagement (\emph{r} = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
-Total hindrance stressors were not significantly associated with our outcomes (H3a-H3c).
-To further explore H1-H3, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
-First, regarding engagement (\(F_{(3, 564)}\) = 26.41, p \textless{} .001), the total resources was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table \ref{tab:regression_table_eng}).
+The results reveal a positive association between resources and engagement (\emph{r} = .34; H1a), but a lack of meaningful association between resources and stress and burnout (H1b and H1c, respectively).
+Challenge demands were positively associated with engagement (\emph{r} = .31; H2a), but were similarly unrelated to stress or burnout (H2b and H2c).
+Total hindrance stressors were largely not significantly associated with our outcomes, although there was a small-moderate association with stress (H3b; \emph{r} = .09).
+
+To explore possible associations more comprehensively, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
+First, regarding engagement (\(F_{(3, 564)}\) = 26.41, p \textless{} .001), the total resources were predictive of engagement, but neither challenge nor hindrance demands predicted engagement (see Table \ref{tab:regression_table_eng}).
 Next, stress was not predicted by total resources, challenge, or hindrance demands, \(F_{(3, 564)}\) = 2.47, \emph{p} = .060 (see Table \ref{tab:regression_table_str}).
@@
 
-The major goal of this paper was to further explore the relationships among total perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout.
-The results suggest a positive relationship between both resources and engagement (H1a), and challenge demands and engagement (H2a).
+The major goal of this paper was to further explore the relationships among \emph{total} perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout.
+The results suggest a positive relationship between both resources and engagement (H1a) and challenge demands and engagement (H2a).
 Employers would benefit from understanding that at least the perception of having ``more'' resources and more challenge demands in a job is highly associated with reported engagement.
 While not a causal relationship, it points to the potential value of these kinds of employee support nonetheless.
-The other relationships with outcomes of stress and burnout were not supported, suggesting that the sheer number of resources, challenges, and hindrances are not significantly related to these negative outcomes.
-It is possible that rather than volume, categorically some demands are more related to these outcomes than others.
-The moderate association between hindrances and challenges (\emph{r} = .22) also hints that some of these relationships may be driven by \emph{job complexity} - that is, some jobs simply have more elements.
-With more job elements come increased opportunities for those elements to be percieved as resources, challenges, or hindrances.
+The other relationships with outcomes of stress and burnout were largely not supported, suggesting that the sheer number of resources, challenges, and hindrances are not significantly related to these negative outcomes.
+The caveat here is stress, which does exhibit a small significant association with the presence of hindrances.
+Note here that the total average number of hindrances implicated by our sample was low, so it is possible that a stronger association is hidden by a restriction of range.
 
@@
 
-As with any piece of research, the process and results have limitations, but also provide a variety of additional directions to pursue in the future.
+As with any piece of research, this project has limitations, but also provide a variety of additional directions to pursue in the future.
 First, while a strength of this project, arguably, is the use of O*Net items, practical considerations limited the number of job characteristics we could include in our survey.
 Future study could consider additional or other O*Net items.
-We conceptualized resources and demands in terms of perceived total amounts.
+We intentionally conceptualized resources and demands in terms of perceived total amounts.
 It may be the case that certain kinds of resources or challenges are more strongly associated with engagement than others, and such, future research could explore the importance of resources/challenges categorically.
-Further, our study was limited to three outcomes of interest.
+
+Our study was limited to three outcomes of interest.
 It would be especially interesting to explore additional outcomes (e.g., job satisfaction) as well, or whether volume of resources and demands operationalized in this way are related to other behaviors (e.g., turnover intention, perceived organizational support, commitment).
+Furthermore, while we found support for the prediction that resources and challenge demands would be positively related to engagement, it would be interesting to consider moderators of this relationship.
+For example, the Job Characteristics Theory (Hackman \& Oldham, 1976) includes the key component of growth need strength in the connections between job characteristics (e.g., autonomy, skill variety) and critical states (e.g., experienced meaningfulness), and between critical states and personal and work outcomes.
+Perhaps this connection between engagement and challenge demands, for instance, is stronger for those with greater growth need strength.
 
+It is also possible that rather than volume, categorically some demands are more related to these outcomes than others.
+The moderate association between hindrances and challenges (\emph{r} = .22) also hints that some of these relationships may be driven by \emph{job complexity} - that is, some jobs simply have more elements.
+With more job elements come increased opportunities for those elements to be perceived as resources, challenges, or hindrances.
 \newpage
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-hackman1976motivation}{}}%
+Hackman, J. R., \& Oldham, G. R. (1976). Motivation through the design of work: Test of a theory. \emph{Organizational Behavior and Human Performance}, \emph{16}(2), 250--279.
+
 \leavevmode\vadjust pre{\hypertarget{ref-kristensen2005copenhagen}{}}%

### 2022-10-12 SIOP2023/Counts/Submission_ResourceCount.tex
knitted papers to review in Word.

--- 2022-10-10 SIOP2023/Counts/Submission_ResourceCount.tex
@@
 \abstract{
-The relationships among sum of perceived job resources, challenge- and hindrance demands and outcomes of organizational outcomes of engagement, stress, and burnout are explored.
-568 workers rated O*Net job characteristics in terms of relevance and perceptions as challenges, hindrances and resources.
-The findings showed a clear connection between resources, challenge demands, and job engagement, but the other associations did not suggest meaningful connections.
+The relationships among total number of job resources, challenges, and hindrances and outcomes of engagement, stress, and burnout are explored.
+568 workers rated O*Net job characteristics in terms of relevance and interpretation of characteristics as challenges, hindrances and resources.
+The findings showed moderately strong connection between the presence of resources and challenge demands with job engagement.
 }
@@
 The brief review above provides theoretical and empirical support for the connection between resources and positive organizational outcomes, and between demands and negative outcomes.
-Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement ({``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption,''} Schaufeli et al., 2002), workplace stress ({``an individual state characterized by a combination of high arousal and displeasure,''} p.~15, Pejtersen et al., 2010) and burnout ({``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work,''} p.~197, Kristensen et al., 2005).
+For this current study, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related to three organizational outcomes: engagement ({``a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption,''} Schaufeli et al., 2002), workplace stress ({``an individual state characterized by a combination of high arousal and displeasure,''} p.~15, Pejtersen et al., 2010) and burnout ({``the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work,''} p.~197, Kristensen et al., 2005).
 Utilizing the job demands-resources theory, the transactional theory of stress, and the challenge-hindrance framework, we propose that the number of job characteristics appraised as ``challenge demands'' (i.e., promote mastery, personal growth, and future gains) would activate a positive state -- that of engagement.
@@
 We used R (Version 4.0.3; R Core Team (2022)) and the R-packages careless (Version 1.1.3; Yentes \& Wilhelm, 2021), labourR (Version 1.0.0; Kouretsis et al., 2020), papaja (Version 0.1.0.9997; Aust \& Barth, 2020), and tinylabels (Barth, 2021) for all analyses.
-Our analyses are presented by characteristics of work that are rated in terms of being resources, challenge demands, and hindrance demands.
-Pearson correlation coefficients between characteristics classified as resources, challenges, and hindrances were obtained to investigate the associations among these characteristics.
 
 Correlations, means and standard deviations among all study variables are presented in Table \ref{tab:correlation_table}.
-The results reveal a positive association between resources and engagement (\emph{r} = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively), although there is a very small, significant relationship between hindrance demands and stress (\emph{r} = .09).
-Challenge demands were positively associated with engagement (\emph{r} = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
-Total hindrance stressors were not significantly associated with our outcomes (H3a-H3c).
-To further explore H1-H3, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
-First, regarding engagement (\(F_{(3, 564)}\) = 26.41, p \textless{} .001), the total resources was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table \ref{tab:regression_table_eng}).
+The results reveal a positive association between resources and engagement (\emph{r} = .34; H1a), but a lack of meaningful association between resources and stress and burnout (H1b and H1c, respectively).
+Challenge demands were positively associated with engagement (\emph{r} = .31; H2a), but were similarly unrelated to stress or burnout (H2b and H2c).
+Total hindrance stressors were largely not significantly associated with our outcomes, although there was a small-moderate association with stress (H3b; \emph{r} = .09).
+
+To explore possible associations more comprehensively, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
+First, regarding engagement (\(F_{(3, 564)}\) = 26.41, p \textless{} .001), the total resources were predictive of engagement, but neither challenge nor hindrance demands predicted engagement (see Table \ref{tab:regression_table_eng}).
 Next, stress was not predicted by total resources, challenge, or hindrance demands, \(F_{(3, 564)}\) = 2.47, \emph{p} = .060 (see Table \ref{tab:regression_table_str}).
@@
 The major goal of this paper was to further explore the relationships among \emph{total} perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout.
-The results suggest a positive relationship between both resources and engagement (H1a), and challenge demands and engagement (H2a).
+The results suggest a positive relationship between both resources and engagement (H1a) and challenge demands and engagement (H2a).
 Employers would benefit from understanding that at least the perception of having ``more'' resources and more challenge demands in a job is highly associated with reported engagement.
 While not a causal relationship, it points to the potential value of these kinds of employee support nonetheless.
-The other relationships with outcomes of stress and burnout were not supported, suggesting that the sheer number of resources, challenges, and hindrances are not significantly related to these negative outcomes.
-It is possible that rather than volume, categorically some demands are more related to these outcomes than others.
-The moderate association between hindrances and challenges (\emph{r} = .22) also hints that some of these relationships may be driven by \emph{job complexity} - that is, some jobs simply have more elements.
-With more job elements come increased opportunities for those elements to be perceived as resources, challenges, or hindrances.
+The other relationships with outcomes of stress and burnout were largely not supported, suggesting that the sheer number of resources, challenges, and hindrances are not significantly related to these negative outcomes.
+The caveat here is stress, which does exhibit a small significant association with the presence of hindrances.
+Note here that the total average number of hindrances implicated by our sample was low, so it is possible that a stronger association is hidden by a restriction of range.
 
@@
 
-As with any piece of research, the process and results have limitations, but also provide a variety of additional directions to pursue in the future.
+As with any piece of research, this project has limitations, but also provide a variety of additional directions to pursue in the future.
 First, while a strength of this project, arguably, is the use of O*Net items, practical considerations limited the number of job characteristics we could include in our survey.
@@
 It may be the case that certain kinds of resources or challenges are more strongly associated with engagement than others, and such, future research could explore the importance of resources/challenges categorically.
-Further, our study was limited to three outcomes of interest.
+
+Our study was limited to three outcomes of interest.
 It would be especially interesting to explore additional outcomes (e.g., job satisfaction) as well, or whether volume of resources and demands operationalized in this way are related to other behaviors (e.g., turnover intention, perceived organizational support, commitment).
 Furthermore, while we found support for the prediction that resources and challenge demands would be positively related to engagement, it would be interesting to consider moderators of this relationship.
-For example, the Job Characteristics Theory (\textbf{hackman1976motivation?}) includes the key component of growth need strength in the connections between job characteristics (e.g., autonomy, skill variety) and critical states (e.g., experienced meaningfulness), and between critical states and personal and work outcomes.
+For example, the Job Characteristics Theory (Hackman \& Oldham, 1976) includes the key component of growth need strength in the connections between job characteristics (e.g., autonomy, skill variety) and critical states (e.g., experienced meaningfulness), and between critical states and personal and work outcomes.
 Perhaps this connection between engagement and challenge demands, for instance, is stronger for those with greater growth need strength.
 
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
-
-In sum, the major contribution of this project shows that number of O*Net job characteristics rated as resources, challenge- and hindrance demands are associated with engagement, but not stress, and burnout.
-The findings showed a clear connection between resources, challenge demands, and job engagement, but the other associations did not suggest meaningful connections.
-
+It is also possible that rather than volume, categorically some demands are more related to these outcomes than others.
+The moderate association between hindrances and challenges (\emph{r} = .22) also hints that some of these relationships may be driven by \emph{job complexity} - that is, some jobs simply have more elements.
+With more job elements come increased opportunities for those elements to be perceived as resources, challenges, or hindrances.
 \newpage
@@
 
+\leavevmode\hypertarget{ref-hackman1976motivation}{}%
+Hackman, J. R., \& Oldham, G. R. (1976). Motivation through the design of work: Test of a theory. \emph{Organizational Behavior and Human Performance}, \emph{16}(2), 250--279.
+
 \leavevmode\hypertarget{ref-kristensen2005copenhagen}{}%

### 2022-10-12 SIOP2023/Counts/convergence.Rmd
JDR #3

@@
 Much of our existing research on the JD-R assumes that certain characteristics (for example, autonomy) are resources and others (for example, time constraints) are generally considered demands.
-This study searches instead for circumstances that provide exception to this static dichotomy of job characteristic mutual exclusivity.
+This study searches instead for circumstances that provide exception to this mutually exclusive dichotomy of job characteristics.
 
@@
 To begin, the first logical question is whether employees actually distinguish between challenges and hindrances, and research suggests that they can and do.
-For example, @bakker2013weekly found that perceived work pressure can be classified as a hindrance demand, and emotional demands as a challenge demand.
-@webster2011extending considered three common workplace demands including workload, role ambiguity, and role conflict.
-Interestingly, they found that while each could be appraised primarily as challenges or hindrances, employees could also simultaneously be perceived as being both a challenge and hindrance.
+For example, @bakker2013weekly found that perceived work pressure can be classified as a hindrance demand, while the requirement to express emotions is a challenge demand.
+@webster2011extending also considered three common work characteristics including workload, role ambiguity, and role conflict.
+Interestingly, they found that while each could be identified *primarily* as a challenge or hindrance, employees could also appraise that a characteristic is simulataneously both a challenge and hindrance.
+
+Although it is cleaner to be able to categorize job characteristics as *either* a demand or a resource, the above research suggests that an individual's (perhaps unique) appraisal is at least occasionally an important consideration.
+It is quite possible that one person experiences high work pressure (commonly cited as a demand in the literature) as a hindrance stressor and thus experiences strain, and another thrives in a fast-paced pressured role and would thus find the environment motivating.
 
@@
 
-We explored the agreement of perceptions of job characteristics as resources as well as demands (in the form of challenges and hindrances).
-Given the definitions of each (i.e.,  aspect of one’s job that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development [resource] vs.
-aspect of one’s job that can promote mastery, personal growth, or future gains [challenge]), we propose respondents may consider the same characteristic to be viewed as both a challenge as well as a resource.
-That is, we explore whether these perceptions are orthogonal, contradictory, or perhaps even complimentary.
+We explored the extent to which perceptions of job characteristics converge upon being uniquely or concurrently experienced as resources and demands (in the form of challenges and hindrances).
+Our supposition is that respondents may consider the same objective job characteristic to be both challenging and resourceful - if not at the same moment, at least at different points in time or under differing circumstances.
+
+### Value of consulting O\*Net.
+
+The Occupational Information Network (O\*NET; onetonline.org) contains a fairly comprehensive description of occupations [@peterson2001understanding].
+This widely accessed database houses hundreds of standardized and occupation-specific descriptors for the majority of occupations within the United States, and these descriptions are frequently updated.
+These data, and the tools provided for public consumption on the website (e.g., Career Exploration Tools, “My Next Move”, Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist interested or curious job-seekers discover the nature of work as well as skills and training typically required for different occupations.
+It is also often useful to employers by providing them with information that may be helpful in a job analysis context.
+
+We asked our respondents to select job characteristics that were relevent to them from the broader comprehensive O\*Net list.
+We then asked these individuals to also rate those (relevant) characteristics in terms of their status as hindrances, challenges, and resources.
 Utilizing the job demands-resources theory and the challenge-hindrance framework, we propose that job characteristics appraised as “challenge demands” (i.e., promote mastery, personal growth, and future gains) may also be viewed as job resources.
@@
 For example, a physically strenuous job requirement such as "carrying heavy objects" would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as "negotiating work schedules" may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge.
-O\*Net has different levels of abstraction with regard to the nature of job characteristic, we will be exploring a mid-level abstraction with seven different characteristic "scales".
+O\*Net has different levels of abstraction with regard to the nature of job characteristic.
+We will be exploring a mid-level abstraction with seven different characteristic "scales".
 
@@
 
-We evaluate agreement across perceptions of present job characteristics regarding their characterization of resource, challenge, and hindrance (Bakker & Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001).
+We evaluate agreement across perceptions of job characteristics regarding their characterization as resource, challenge, and hindrance (Bakker & Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001).
 To capture an effectively exhaustive list of characteristics that apply to, theoretically, *every* possible job, we consult the  unifying framework of O\*Net.
@@
 
-Our survey consisted of 98 items crafted from job characteristic descriptors located within O\*Net’s classification of “work activities”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context” groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
+Our survey was informed by 98 statements taken from job characteristic descriptors located within O\*Net’s classification of “work activities”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context” groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
 
@@
 It would likely NOT be considered controversial to referred to these as "effectively" Likert-type response scales.
-
->put example response scale in
 
@@
 this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
-
 The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
@@
 
->Note. Should probably run a quick anova on these
-
 ```{r percagree, fig.cap="Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance).", fig.height=10}
@@
 Here we categorized each characteristic by its O\*Net "scale" (one of seven), and the graph shows greater consistency across certain characteristics (for example, *Mental Processes* or *Interacting with Others*) and less convergence across other *types* of job activities (for example, *Physical* characteristics).
-A repeated-measures ANOVA retaining these 7 scales as independent variables yielded a treatment effect of $F_{(6, 3,402)}$ = 613.5, *p* < .001 (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001.
+A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of $F_{(6, 3,402)}$ = 613.5, *p* < .001 (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001.
 
@@
 
-Our findings highlight the importance of dissociating the *nature* of job demands.
-Similar to the eustress/distress distinction [e.g., @selye1974stress], it would seem as though demands should be thought of in a valenced manner (e.g., is it a "good" demand or a "bad" demand)[^bootsie].
+The major goal of this paper was to further explore the relationships among perceptions of job characteristics as challenge demands, hindrance demands, and resources.
+Our findings perhaps most noteably highlight the importance of dissociating the *nature* of job demands.
+Similar to the eustress/distress distinction [e.g., @selye1974stress], it would seem as though demands should perhaps be thought of in a valenced manner (e.g., is it a "good" demand or a "bad" demand).
+We did not probe for dependent variable associations, however, @cavanaugh2000empirical found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite patterns in a sample of managers.
+We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (@crawford2010linking).
+@podsakoff2007differential's meta-analysis also found that challenge demands were positively related to job satisfaction and organizational commitment and negatively related to both turnover intentions and actual turnover, while hindrance demands again produced the opposite patterns of relationship.
+Although we did not probe for outcome associations, the current study does suggest that hindrance demands also operate in a manner different than challenge demands with regard to their association with resource appraisals.
 
-[^bootsie]: Beyond this SIOP presentation, we have further investigated differential associations of challenges and hindrances with "good" and "bad" outcomes, but have not confirmed meaningful differential associations within this current dataset.
-
-The major goal of this paper was to further explore the relationships among total perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout.
-Additionally, we considered whether resources and challenge demands were perceived as distinct, and finally, whether the patterns were similar across job categories/types of work.
-The results suggest a positive relationship between both resources and engagement (H1a), and challenge demands and engagement (H2a).
-Employers would benefit from understanding that at leas the perception of having “more” resources and more challenge demands in a job is highly associated with reported engagement.
-While not a causal relationship, it points to the potential value of these kinds of employee support nonetheless.
-The other relationships with outcomes of stress and burnout were not supported, suggesting that the sheer number of resources, challenges, and hindrances are not significantly related to these negative outcomes.
-It is possible that rather than volume, categorically some demands are more related to these outcomes than others.
- Further, total resources were highly associated challenge demands (supporting H4).
-We could even argue, given the magnitude of the correlation, that they are capturing the same thing (74% overlap with a correlation of .86).
-Need to also talk about our exploratory findings regarding patterns across job type
-
-We conceptualized resources and demands in terms of perceived total amounts.
-
-The dissociation of challenges and hindrances may be important moving forward.
-@cavanaugh2000empirical found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern with job satisfaction and job search behaviors in a sample of managers.
-However, @abbas2019challenge found that challenge and hindrance stressors were both positively related to strain and turnover intentions.
-We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (@crawford2010linking).
-The appraisal process also suggests theoretically that the perception of a job characteristic as a challenge or hindrance is a mediator.
-@gerich2017relevance, for instance, found that employee well-being was, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
-To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, @podsakoff2007differential meta-analysis supported the original assertion of @cavanaugh2000empirical such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.
+In terms of convergence of resource and challenge appraisals, there was quite a bit of variability (e.g., Figure \@ref(fig:percagree)), but that variability was partially explained by the nature of the characteristic being evaluated (e.g., Figure \@ref(fig:recchall)).
+Physical job characteristics such as, for example, the amount of "time spent bending or twisting the body" may be much more likely to be appraised as a challenging demand (but not a resource).
+Other *types* of job requirements, however, such as a mental process like, "scheduling work and activities" might reasonably be expected to exhibit greater convergence.
+We suspect that there are other moderators that help explain this association/ disassociation between challenges and resources, and would like to incorporate variables such as a respondents' personality in future investigations.
 

### 2022-10-12 SIOP2023/Counts/convergence.tex
JDR #3

@@
 To begin, the first logical question is whether employees actually distinguish between challenges and hindrances, and research suggests that they can and do.
-For example, Bakker and Sanz-Vergel (2013) found that perceived work pressure can be classified as a hindrance demand, and emotional demands as a challenge demand.
+For example, Bakker and Sanz-Vergel (2013) found that perceived work pressure can be classified as a hindrance demand, while the requirement to express emotions is a challenge demand.
 Webster et al.
-(2011) considered three common workplace demands including workload, role ambiguity, and role conflict.
-Interestingly, they found that while each could be appraised primarily as challenges or hindrances, employees could also simultaneously be perceived as being both a challenge and hindrance.
+(2011) also considered three common work characteristics including workload, role ambiguity, and role conflict.
+Interestingly, they found that while each could be identified \emph{primarily} as a challenge or hindrance, employees could also appraise that a characteristic is simulataneously both a challenge and hindrance.
+
+Although it is cleaner to be able to categorize job characteristics as \emph{either} a demand or a resource, the above research suggests that an individual's (perhaps unique) appraisal is at least occasionally an important consideration.
+It is quite possible that one person experiences high work pressure (commonly cited as a demand in the literature) as a hindrance stressor and thus experiences strain, and another thrives in a fast-paced pressured role and would thus find the environment motivating.
 
@@
 
-We explored the agreement of perceptions of job characteristics as resources as well as demands (in the form of challenges and hindrances).
-Given the definitions of each (i.e., aspect of one's job that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development {[}resource{]} vs.~aspect of one's job that can promote mastery, personal growth, or future gains {[}challenge{]}), we propose respondents may consider the same characteristic to be viewed as both a challenge as well as a resource.
-That is, we explore whether these perceptions are orthogonal, contradictory, or perhaps even complimentary.
+We explored the extent to which perceptions of job characteristics converge upon being uniquely or concurrently experienced as resources and demands (in the form of challenges and hindrances).
+Our supposition is that respondents may consider the same objective job characteristic to be both challenging and resourceful - if not at the same moment, at least at different points in time or under differing circumstances.
+
+\hypertarget{value-of-consulting-onet.}{%
+\subsubsection{Value of consulting O*Net.}\label{value-of-consulting-onet.}}
+
+The Occupational Information Network (O*NET; onetonline.org) contains a fairly comprehensive description of occupations (Peterson et al., 2001).
+This widely accessed database houses hundreds of standardized and occupation-specific descriptors for the majority of occupations within the United States, and these descriptions are frequently updated.
+These data, and the tools provided for public consumption on the website (e.g., Career Exploration Tools, ``My Next Move'', Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist interested or curious job-seekers discover the nature of work as well as skills and training typically required for different occupations.
+It is also often useful to employers by providing them with information that may be helpful in a job analysis context.
+
+We asked our respondents to select job characteristics that were relevent to them from the broader comprehensive O*Net list.
+We then asked these individuals to also rate those (relevant) characteristics in terms of their status as hindrances, challenges, and resources.
 Utilizing the job demands-resources theory and the challenge-hindrance framework, we propose that job characteristics appraised as ``challenge demands'' (i.e., promote mastery, personal growth, and future gains) may also be viewed as job resources.
@@
 For example, a physically strenuous job requirement such as ``carrying heavy objects'' would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as ``negotiating work schedules'' may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge.
-O*Net has different levels of abstraction with regard to the nature of job characteristic, we will be exploring a mid-level abstraction with seven different characteristic ``scales''.
+O*Net has different levels of abstraction with regard to the nature of job characteristic.
+We will be exploring a mid-level abstraction with seven different characteristic ``scales''.
 
@@
 
-We evaluate agreement across perceptions of present job characteristics regarding their characterization of resource, challenge, and hindrance (Bakker \& Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001).
+We evaluate agreement across perceptions of job characteristics regarding their characterization as resource, challenge, and hindrance (Bakker \& Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001).
 To capture an effectively exhaustive list of characteristics that apply to, theoretically, \emph{every} possible job, we consult the unifying framework of O*Net.
@@
 
-Our survey consisted of 98 items crafted from job characteristic descriptors located within O*Net's classification of ``work activities'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'' groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
+Our survey was informed by 98 statements taken from job characteristic descriptors located within O*Net's classification of ``work activities'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'' groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
 
@@
 It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.
-
-\begin{quote}
-put example response scale in
-\end{quote}
 
@@
 this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
-
 The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
@@
 
-\begin{quote}
-Note. Should probably run a quick anova on these
-\end{quote}
-
 \begin{figure}
@@
 Here we categorized each characteristic by its O*Net ``scale'' (one of seven), and the graph shows greater consistency across certain characteristics (for example, \emph{Mental Processes} or \emph{Interacting with Others}) and less convergence across other \emph{types} of job activities (for example, \emph{Physical} characteristics).
-A repeated-measures ANOVA retaining these 7 scales as independent variables yielded a treatment effect of \(F_{(6, 3,402)}\) = 613.5, \emph{p} \textless{} .001 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001.
+A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of \(F_{(6, 3,402)}\) = 613.5, \emph{p} \textless{} .001 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001.
 
@@
 
-Our findings highlight the importance of dissociating the \emph{nature} of job demands.
-Similar to the eustress/distress distinction (e.g., Selye, 1974), it would seem as though demands should be thought of in a valenced manner (e.g., is it a ``good'' demand or a ``bad'' demand)\footnote{Beyond this SIOP presentation, we have further investigated differential associations of challenges and hindrances with ``good'' and ``bad'' outcomes, but have not confirmed meaningful differential associations within this current dataset.}.
-
-The major goal of this paper was to further explore the relationships among total perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout.
-Additionally, we considered whether resources and challenge demands were perceived as distinct, and finally, whether the patterns were similar across job categories/types of work.
-The results suggest a positive relationship between both resources and engagement (H1a), and challenge demands and engagement (H2a).
-Employers would benefit from understanding that at leas the perception of having ``more'' resources and more challenge demands in a job is highly associated with reported engagement.
-While not a causal relationship, it points to the potential value of these kinds of employee support nonetheless.
-The other relationships with outcomes of stress and burnout were not supported, suggesting that the sheer number of resources, challenges, and hindrances are not significantly related to these negative outcomes.
-It is possible that rather than volume, categorically some demands are more related to these outcomes than others.
-Further, total resources were highly associated challenge demands (supporting H4).
-We could even argue, given the magnitude of the correlation, that they are capturing the same thing (74\% overlap with a correlation of .86).
-Need to also talk about our exploratory findings regarding patterns across job type
-
-We conceptualized resources and demands in terms of perceived total amounts.
-
-The dissociation of challenges and hindrances may be important moving forward.
-Cavanaugh et al.
-(2000) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern with job satisfaction and job search behaviors in a sample of managers.
-However, Abbas and Raja (2019) found that challenge and hindrance stressors were both positively related to strain and turnover intentions.
+The major goal of this paper was to further explore the relationships among perceptions of job characteristics as challenge demands, hindrance demands, and resources.
+Our findings perhaps most noteably highlight the importance of dissociating the \emph{nature} of job demands.
+Similar to the eustress/distress distinction (e.g., Selye, 1974), it would seem as though demands should perhaps be thought of in a valenced manner (e.g., is it a ``good'' demand or a ``bad'' demand).
+We did not probe for dependent variable associations, however, Cavanaugh et al.
+(2000) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite patterns in a sample of managers.
 We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford et al.
 (2010)).
-The appraisal process also suggests theoretically that the perception of a job characteristic as a challenge or hindrance is a mediator.
-Gerich (2017), for instance, found that employee well-being was, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
-To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, Podsakoff et al.
-(2007) meta-analysis supported the original assertion of Cavanaugh et al.
-(2000) such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.
+Podsakoff et al.
+(2007)'s meta-analysis also found that challenge demands were positively related to job satisfaction and organizational commitment and negatively related to both turnover intentions and actual turnover, while hindrance demands again produced the opposite patterns of relationship.
+Although we did not probe for outcome associations, the current study does suggest that hindrance demands also operate in a manner different than challenge demands with regard to their association with resource appraisals.
+
+In terms of convergence of resource and challenge appraisals, there was quite a bit of variability (e.g., Figure \ref{fig:percagree}), but that variability was partially explained by the nature of the characteristic being evaluated (e.g., Figure \ref{fig:recchall}).
+Physical job characteristics such as, for example, the amount of ``time spent bending or twisting the body'' may be much more likely to be appraised as a challenging demand (but not a resource).
+Other \emph{types} of job requirements, however, such as a mental process like, ``scheduling work and activities'' might reasonably be expected to exhibit greater convergence.
+We suspect that there are other moderators that help explain this association/ disassociation between challenges and resources, and would like to incorporate variables such as a respondents' personality in future investigations.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-abbas2019challenge}{}}%
-Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.
-
 \leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
-Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
+\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
+Peterson, N.
+G., Mumford, M.
+D., Borman, W.
+C., Jeanneret, P.
+R., Fleishman, E.
+A., Levin, K.
+Y., Campion, M.
+A., Mayfield, M.
+S., Morgeson, F.
+P., Pearlman, K., et al.
+(2001).
+Understanding work using the occupational information network (o* NET): Implications for practice and research.
+\emph{Personnel Psychology}, \emph{54}(2), 451--492.
 

### 2022-10-12 SIOP2023/Counts/convergence.tex
title change

@@
 \hypersetup{
-  pdftitle={Demanding resources: Agreement across characteristics seen as both challenges and resources},
+  pdftitle={Demanding resources: Converging characteristics of challenge and resource},
   pdfauthor={John Kulas1 \& Alicia Stachowski2},
@@
 
-\title{Demanding resources: Agreement across characteristics seen as both challenges and resources}
+\title{Demanding resources: Converging characteristics of challenge and resource}
 \author{John Kulas\textsuperscript{1} \& Alicia Stachowski\textsuperscript{2}}

### 2022-10-14 SIOP2023/Counts/Submission_ResourceCount.Rmd

@@
 abstract: |
-  The relationships among sum of perceived job resources, challenge- and hindrance demands and outcomes of organizational outcomes of engagement, stress, and burnout are explored.
-568 workers rated O\*Net job characteristics in terms of relevance and perceptions as challenges, hindrances and resources.
-The findings showed a clear connection between resources, challenge demands, and job engagement, but the other associations did not suggest meaningful connections.
+  The relationships among total number of job resources, challenges, and hindrances and outcomes of  engagement, stress, and burnout are explored.
+568 workers rated O\*Net job characteristics in terms of relevance and interpretation of characteristics as challenges, hindrances and resources.
+The findings showed moderately strong connection between the presence of resources and challenge demands with job engagement.
 
@@
 Thus, although some research on job demands in particular is based on *a priori* classifications of demands [@searle2015merits], the appraisal of any work characteristic as a demand or resource is actually subjective.
+
 The literature on the experience of stress explains how such individual differences in appraisal are possible.
@@
 The brief review above provides theoretical and empirical support for the connection between resources and positive organizational outcomes, and between demands and negative outcomes.
-Here, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related differently to three organizational outcomes: engagement [“a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption”, @schaufeli2002measurement], workplace stress [“an individual state characterized by a combination of high arousal and displeasure”, p.
+For this current study, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related to three organizational outcomes: engagement [“a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption”, @schaufeli2002measurement], workplace stress [“an individual state characterized by a combination of high arousal and displeasure”, p.
 15, @pejtersen2010second] and burnout [“the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work”, p.
@@
 
-The 18-item engagement measure was recently developed [@engage_2022], with the authors specifying three subscales which yielded current sample α’s of 0.68 (absorption) and 0.80 (vigor), and 0.90 (dedication).
+The 18-item engagement measure was recently developed [@engage_2022], with the authors specifying three subscales which yielded current sample $\alpha$’s of 0.68 (absorption) and 0.80 (vigor), and 0.90 (dedication).
 For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, alpha = 0.91).
@@
 We used R (Version 4.0.3; @R-base) and the R-packages careless (Version 1.1.3; Yentes & Wilhelm, 2021), labourR (Version 1.0.0; Kouretsis et al., 2020), papaja (Version 0.1.0.9997; Aust & Barth, 2020), and tinylabels (Barth, 2021) for all analyses.
-Our analyses are presented by characteristics of work that are rated in terms of being resources, challenge demands, and hindrance demands.
-Pearson correlation coefficients between characteristics classified as resources, challenges, and hindrances were obtained to investigate the associations among these characteristics.
 
 Correlations, means and standard deviations among all study variables are presented in Table \ref{tab:correlation_table}.
-The results reveal a positive association between resources and engagement (*r* = .34; H1a), but a lack of meaningful association between engagement and stress and burnout (H1b and H1c, respectively), although there is a very small, significant relationship between hindrance demands and stress (*r* = .09).
-Challenge demands were positively associated with engagement (*r* = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
-Total hindrance stressors were not significantly associated with our outcomes (H3a-H3c).
-To further explore H1-H3, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
-First, regarding engagement ($F_{(3, 564)}$ = 26.41, p < .001), the total resources was predictive of engagement, but total challenge nor hindrance demands predicted engagement (see Table \ref{tab:regression_table_eng}).
+The results reveal a positive association between resources and engagement (*r* = .34; H1a), but a lack of meaningful association between resources and stress and burnout (H1b and H1c, respectively).
+Challenge demands were positively associated with engagement (*r* = .31; H2a), but were similarly unrelated to stress or burnout (H2b and H2c).
+Total hindrance stressors were largely not significantly associated with our outcomes, although there was a small-moderate association with stress (H3b; *r* = .09).
+
+To explore possible associations more comprehensively, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
+First, regarding engagement ($F_{(3, 564)}$ = 26.41, p < .001), the total resources were predictive of engagement, but neither challenge nor hindrance demands predicted engagement (see Table \ref{tab:regression_table_eng}).
 Next, stress was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$ = 2.47, *p* = .060 (see Table \ref{tab:regression_table_str}).
@@
 The major goal of this paper was to further explore the relationships among *total* perceived challenge demands, hindrance demands, and resources and outcomes of engagement, stress, and burnout.
-The results suggest a positive relationship between both resources and engagement (H1a), and challenge demands and engagement (H2a).
+The results suggest a positive relationship between both resources and engagement (H1a) and challenge demands and engagement (H2a).
 Employers would benefit from understanding that at least the perception of having “more” resources and more challenge demands in a job is highly associated with reported engagement.
 While not a causal relationship, it points to the potential value of these kinds of employee support nonetheless.
-The other relationships with outcomes of stress and burnout were not supported, suggesting that the sheer number of resources, challenges, and hindrances are not significantly related to these negative outcomes.
-It is possible that rather than volume, categorically some demands are more related to these outcomes than others.
-The moderate association between hindrances and challenges (*r* = .22) also hints that some of these relationships may be driven by *job complexity* - that is, some jobs simply have more elements.
-With more job elements come increased opportunities for those elements to be perceived as resources, challenges, or hindrances.
+The other relationships with outcomes of stress and burnout were largely not supported, suggesting that the sheer number of resources, challenges, and hindrances are not significantly related to these negative outcomes.
+The caveat here is stress, which does exhibit a small significant association with the presence of hindrances.
+Note here that the total average number of hindrances implicated by our sample was low, so it is possible that a stronger association is hidden by a restriction of range.
 
@@
 
-As with any piece of research, the process and results have limitations, but also provide a variety of additional directions to pursue in the future.
+As with any piece of research, this project has limitations, but also provide a variety of additional directions to pursue in the future.
 First, while a strength of this project, arguably, is the use of O\*Net items, practical considerations limited the number of job characteristics we could include in our survey.
@@
 It may be the case that certain kinds of resources or challenges are more strongly associated with engagement than others, and such, future research could explore the importance of resources/challenges categorically.
-Further, our study was limited to three outcomes of interest.
+
+Our study was limited to three outcomes of interest.
 It would be especially interesting to explore additional outcomes (e.g., job satisfaction) as well, or whether volume of resources and demands operationalized in this way are related to other behaviors (e.g., turnover intention, perceived organizational support, commitment).
 Furthermore, while we found support for the prediction that resources and challenge demands would be positively related to engagement, it would be interesting to consider moderators of this relationship.
-For example, the Job Characteristics Theory @hackman1976motivation includes the key component of growth need strength in the connections between job characteristics (e.g., autonomy, skill variety) and critical states (e.g., experienced meaningfulness), and between critical states and personal and work outcomes.
+For example, the Job Characteristics Theory [@hackman1976motivation] includes the key component of growth need strength in the connections between job characteristics (e.g., autonomy, skill variety) and critical states (e.g., experienced meaningfulness), and between critical states and personal and work outcomes.
 Perhaps this connection between engagement and challenge demands, for instance, is stronger for those with greater growth need strength.
 
-# Conclusion
-
-In sum, the major contribution of this project shows that number of O\*Net job characteristics rated as resources, challenge- and hindrance demands are associated with engagement, but not stress, and burnout.
-The findings showed a clear connection between resources, challenge demands, and job engagement, but the other associations did not suggest meaningful connections.
-
+It is also possible that rather than volume, categorically some demands are more related to these outcomes than others.
+The moderate association between hindrances and challenges (*r* = .22) also hints that some of these relationships may be driven by *job complexity* - that is, some jobs simply have more elements.
+With more job elements come increased opportunities for those elements to be perceived as resources, challenges, or hindrances.
 \newpage

### 2022-10-14 SIOP2023/SIOP_PROCESS.tex

@@
 \usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Testing the JD-R theory via O*Net definitional specification},
+  pdfauthor={Alicia A. Stachowski1 \& John T. Kulas2},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \makeatother
-
-\usepackage{xpatch}
-\makeatletter
-\xapptocmd\appendix
-  {\xapptocmd\section
-    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
-    {}{\InnerPatchFailed}%
-  }
-{}{\PatchFailed}
+\shorttitle{Hindrances-Resources Interaction}
 \keywords{keywords\newline\indent Word count: X}
@@
 \usepackage{csquotes}
-\ifLuaTeX
+\ifxetex
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\else
+  \usepackage[main=english]{babel}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+\fi
+\ifluatex
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={Testing the JD-R theory via O*Net definitional specification},
-  pdfauthor={Alicia A. Stachowski1 \& John T. Kulas2},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 \date{}
-
-\shorttitle{Hindrances-Resources Interaction}
 
@@
 
-\abstract{%
+\abstract{
 This project explored the role of resources on the demand-strain relationship through the lens of O*Net derived job characteristics.
@@
 It is quite possible that one person experiences high work pressure (commonly cited as a demand in the literature) as a hindrance stressor and thus experiences strain, and another thrives in a fast-paced pressured role and would thus find the environment motivating.
-In order to account for this possibility of ``non-exclusivity'', we asked our respondents to rate all relevant job characteristics in terms of their status as hindrances, challenges, and resources.
+In order to account for this possibility of ``non-exclusivity,'' we asked our respondents to rate all relevant job characteristics in terms of their status as hindrances, challenges, and resources.
 
@@
 This widely accessed database houses hundreds of standardized and occupation-specific descriptors for the majority of occupations within the United States, and these descriptions are frequently updated.
-These data, and the tools provided for public consumption on the website (e.g., Career Exploration Tools, ``My Next Move'', Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist interested or curious job-seekers discover the nature of work as well as skills and training typically required for different occupations.
+These data, and the tools provided for public consumption on the website (e.g., Career Exploration Tools, ``My Next Move,'' Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist interested or curious job-seekers discover the nature of work as well as skills and training typically required for different occupations.
 It is also often useful to employers by providing them with information that may be helpful in a job analysis context.
 For the current study, we focused on statements taken from O*NET's \href{https://www.O*NETonline.org/find/descriptor/result/4.A.1.b.3}{``activity'' and ``context'' classifications} (e.g., items related to characteristics of work such as how often a worker interacts with others or engages in physical labor).
-From a job analytic lens, these descriptors are written more broadly than a task statement, and would most likely be classified by most job analysts as ``responsibilities''.
+From a job analytic lens, these descriptors are written more broadly than a task statement, and would most likely be classified by most job analysts as ``responsibilities.''
 
@@
 Each of the 98 descriptors has potentially unique response categories, but scaling was consistently 1 (low) to 5 (high).
-Subsequent to self-evaluations regarding whether or not the characteristic was applicable to one's job, the respondents were asked to rate germane elements in terms of it's experience as a resource (``\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development''), challenge, (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains'') as well as hindrance (``\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment'').
+Subsequent to self-evaluations regarding whether or not the characteristic was applicable to one's job, the respondents were asked to rate germane elements in terms of it's experience as a resource (``\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development''), challenge, (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains``) as well as hindrance (''\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment").
 For each category (e.g., resources), a mean score was computed that indicated the across items that applied to one's role, and thus, mean scores could range from 1 to 5.
@@
 Three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019) captured strain (an example item is: ``How often have you had problems relaxing because of your job?'').
-Responses were made on a 5-point scale ranging from ``not at all'' to ``all the time''.
-Alpha was .85 in this sample.
+Responses were made on a 5-point scale ranging from ``not at all'' to ``all the time.'' Alpha was .85 in this sample.
 
@@
 S., Morgeson, F.
-P., Pearlman, K., et al.
+P., Pearlman, K., \& others.
 (2001).

### 2022-10-14 copy of SIOP2023convergence.Rmd
getting worker categories into data object

--- 2022-10-12 SIOP2023/Counts/convergence.Rmd
@@
 ---
-title             : "Demanding resources: Agreement across characteristics seen as both challenges and resources"
+title             : "Demanding resources: Converging characteristics of challenge and resource"
 shorttitle        : "Demanding Resources"
@@
 
+```{r workcat}
+## Job classifications
+
+workers <- read.csv("workers.csv")             ## Probably need to revisit our coding - 10/14/22
+
+library(ggplot2)
+
+ggplot(workers, aes(O.Net.Job.Family.Categories))+
+  geom_histogram(stat="count") + coord_flip()
+
+## Combining categories
+
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Transportation and Material Moving"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Protective Service"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Production"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Personal Care and Service"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Installation Maintenance and Repair"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Food Preparation and Serving Related"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Farming Fishing and Forestry"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Construction and Extraction"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Building and Grounds Cleaning and Maintenance"] <- "Physical Labor"
+
+## with Alicia 12/1
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Architecture and Engineering"] <- "Computer & Engineering"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Computer and Mathematical"] <- "Computer & Engineering"
+
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Life Physical and Social Science"] <- "Education, Science & Health"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Educational Instruction and Library"] <- "Education, Science & Health"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Healthcare Practitioner and Technical"] <- "Education, Science & Health"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Community and Social Service"] <- "Education, Science & Health"
+
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Office and Administrative Support"] <- "Admin, Healthcare & Legal"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Legal"] <- "Admin, Healthcare & Legal"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Healthcare Support"] <- "Admin, Healthcare & Legal"
+
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Arts Design Entertainment Sports Media"] <- "Other"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Military Specific"] <- "Other"
+
+#3 in plot all categories, combined and standalone
+
+ggplot(workers, aes(O.Net.Job.Family.Categories)) +
+  geom_histogram(stat="count") + coord_flip()
+
+dataworker <- cbind(data,workers)    ## to repeat O*Net analyses
+                                     ## This gets worker info into convergence file
+
+```
+
 ```{r percagree, fig.cap="Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance).", fig.height=10}

### 2022-10-14 copy-of-SIOP2023convergence.tex
getting worker categories into data object

--- 2022-10-12 SIOP2023/Counts/convergence.tex
@@
 \usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Demanding resources: Converging characteristics of challenge and resource},
+  pdfauthor={John Kulas1 \& Alicia Stachowski2},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={Demanding resources: Converging characteristics of challenge and resource},
-  pdfauthor={John Kulas1 \& Alicia Stachowski2},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
 
@@
 
+\begin{verbatim}
+## Warning: package 'tinylabels' was built under R version 4.1.3
+\end{verbatim}
+
 An abundance of research applying the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker \& Demerouti, 2017) underscores the importance of job characteristics on the experience of work.
@@
 Demands, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure, Demerouti et al., 2001).
-These two categories of outcomes (e.g., ``good'' and ``bad'') are thought to occur via one of two different mechanisms: motivational (resulting from resources) or health impairment (resulting from demands, Bakker \& Demerouti, 2014).
+These two categories of outcomes (e.g., ``good'' and ``bad'') are thought to occur via one of two different mechanisms: motivational (resulting from resources) or health impairment (resulting from demands, \textbf{bakker2014job?}).
 Much of our existing research on the JD-R assumes that certain characteristics (for example, autonomy) are resources and others (for example, time constraints) are generally considered demands.
@@
 
-Although the word ``stress'' often carries a negative connotation, the ``father'' of the current concept, Selye (1936), conceptualized stress much less perjoratively - rather thinking of it as a \emph{response to change}.
+Although the word ``stress'' often carries a negative connotation, the ``father'' of the current concept, (\textbf{selye1936syndrome?}), conceptualized stress much less perjoratively - rather thinking of it as a \emph{response to change}.
 For instance, consider the different reactions two different employees may have to being nominated to give a speech at an upcoming company event.
@@
 However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
-Selye the physician would likely have labeled the two responses as subjective manifestations of ``Distress'', and ``Eustress'' (Selye, 1974).
-In modern I-O Psychology parlance (and more consistent with the JD-R framework), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a \emph{challenge} while the other would appraise the demand as a \emph{hindrance} (Cavanaugh et al., 2000).
-According to Cavanaugh et al.
-(2000), challenge demands promote mastery, personal growth, and future gains.
+Selye the physician would likely have labeled the two responses as subjective manifestations of ``Distress'', and ``Eustress'' (\textbf{selye1974stress?}).
+In modern I-O Psychology parlance (and more consistent with the JD-R framework), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a \emph{challenge} while the other would appraise the demand as a \emph{hindrance} (\textbf{cavanaugh2000empirical?}).
+According to (\textbf{cavanaugh2000empirical?}), challenge demands promote mastery, personal growth, and future gains.
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes (e.g., Cavanaugh et al., 2000).
+Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes (e.g., \textbf{cavanaugh2000empirical?}).
 
@@
 To begin, the first logical question is whether employees actually distinguish between challenges and hindrances, and research suggests that they can and do.
-For example, Bakker and Sanz-Vergel (2013) found that perceived work pressure can be classified as a hindrance demand, while the requirement to express emotions is a challenge demand.
-Webster et al.
-(2011) also considered three common work characteristics including workload, role ambiguity, and role conflict.
+For example, (\textbf{bakker2013weekly?}) found that perceived work pressure can be classified as a hindrance demand, while the requirement to express emotions is a challenge demand.
+(\textbf{webster2011extending?}) also considered three common work characteristics including workload, role ambiguity, and role conflict.
 Interestingly, they found that while each could be identified \emph{primarily} as a challenge or hindrance, employees could also appraise that a characteristic is simulataneously both a challenge and hindrance.
@@
 
-The Occupational Information Network (O*NET; onetonline.org) contains a fairly comprehensive description of occupations (Peterson et al., 2001).
+The Occupational Information Network (O*NET; onetonline.org) contains a fairly comprehensive description of occupations (\textbf{peterson2001understanding?}).
 This widely accessed database houses hundreds of standardized and occupation-specific descriptors for the majority of occupations within the United States, and these descriptions are frequently updated.
@@
 
+\includegraphics{copy-of-SIOP2023convergence_files/figure-latex/workcat-1.pdf} \includegraphics{copy-of-SIOP2023convergence_files/figure-latex/workcat-2.pdf}
+
 \begin{figure}
 \centering
-\includegraphics{convergence_files/figure-latex/percagree-1.pdf}
+\includegraphics{copy-of-SIOP2023convergence_files/figure-latex/percagree-1.pdf}
 \caption{\label{fig:percagree}Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance).}
@@
 \centering
-\includegraphics{convergence_files/figure-latex/recchall-1.pdf}
+\includegraphics{copy-of-SIOP2023convergence_files/figure-latex/recchall-1.pdf}
 \caption{\label{fig:recchall}Resource and challenge agreement across ONet characteristic groupings (e.g., scales).}
@@
 Our findings perhaps most noteably highlight the importance of dissociating the \emph{nature} of job demands.
-Similar to the eustress/distress distinction (e.g., Selye, 1974), it would seem as though demands should perhaps be thought of in a valenced manner (e.g., is it a ``good'' demand or a ``bad'' demand).
-We did not probe for dependent variable associations, however, Cavanaugh et al.
-(2000) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite patterns in a sample of managers.
+Similar to the eustress/distress distinction (e.g., \textbf{selye1974stress?}), it would seem as though demands should perhaps be thought of in a valenced manner (e.g., is it a ``good'' demand or a ``bad'' demand).
+We did not probe for dependent variable associations, however, (\textbf{cavanaugh2000empirical?}) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite patterns in a sample of managers.
 We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford et al.
 (2010)).
-Podsakoff et al.
-(2007)'s meta-analysis also found that challenge demands were positively related to job satisfaction and organizational commitment and negatively related to both turnover intentions and actual turnover, while hindrance demands again produced the opposite patterns of relationship.
+(\textbf{podsakoff2007differential?})'s meta-analysis also found that challenge demands were positively related to job satisfaction and organizational commitment and negatively related to both turnover intentions and actual turnover, while hindrance demands again produced the opposite patterns of relationship.
 Although we did not probe for outcome associations, the current study does suggest that hindrance demands also operate in a manner different than challenge demands with regard to their association with resource appraisals.
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
-Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
-
 \leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
 Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
-Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
-
-\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
-Cavanaugh, M.
-A., Boswell, W.
-R., Roehling, M.
-V., \& Boudreau, J.
-W.
-(2000).
-An empirical examination of self-reported work stress among US managers.
-\emph{Journal of Applied Psychology}, \emph{85}(1), 65.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
-Peterson, N.
-G., Mumford, M.
-D., Borman, W.
-C., Jeanneret, P.
-R., Fleishman, E.
-A., Levin, K.
-Y., Campion, M.
-A., Mayfield, M.
-S., Morgeson, F.
-P., Pearlman, K., et al.
-(2001).
-Understanding work using the occupational information network (o* NET): Implications for practice and research.
-\emph{Personnel Psychology}, \emph{54}(2), 451--492.
-
-\leavevmode\vadjust pre{\hypertarget{ref-podsakoff2007differential}{}}%
-Podsakoff, N.
-P., LePine, J.
-A., \& LePine, M.
-A.
-(2007).
-Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis.
-\emph{Journal of Applied Psychology}, \emph{92}(2), 438.
-
-\leavevmode\vadjust pre{\hypertarget{ref-selye1936syndrome}{}}%
-Selye, H. (1936). A syndrome produced by diverse nocuous agents. \emph{Nature}, \emph{138}(3479), 32--32.
-
-\leavevmode\vadjust pre{\hypertarget{ref-selye1974stress}{}}%
-Selye, H. (1974). \emph{Stress without distress}. Lippincott Williams \& Wilkins.
-
-\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
-Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.
-
 \end{CSLReferences}

### 2022-10-14 jobcats.R

@@ -1,6 +1,6 @@
 ## Job classifications
 
-data <- read.csv("workers.csv")
+data <- read.csv("workers.csv")             ## Probably need to revisit our coding - 10/14/22
 
 library(ggplot2)
 

### 2022-10-14 copy of SIOP2023convergence.Rmd
job cat graphs although looks like pulled from wrong object

@@
 
-```{r workcat}
-## Job classifications
-
-workers <- read.csv("workers.csv")             ## Probably need to revisit our coding - 10/14/22
-
-library(ggplot2)
-
-ggplot(workers, aes(O.Net.Job.Family.Categories))+
-  geom_histogram(stat="count") + coord_flip()
-
-## Combining categories
-
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Transportation and Material Moving"] <- "Physical Labor"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Protective Service"] <- "Physical Labor"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Production"] <- "Physical Labor"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Personal Care and Service"] <- "Physical Labor"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Installation Maintenance and Repair"] <- "Physical Labor"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Food Preparation and Serving Related"] <- "Physical Labor"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Farming Fishing and Forestry"] <- "Physical Labor"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Construction and Extraction"] <- "Physical Labor"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Building and Grounds Cleaning and Maintenance"] <- "Physical Labor"
-
-## with Alicia 12/1
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Architecture and Engineering"] <- "Computer & Engineering"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Computer and Mathematical"] <- "Computer & Engineering"
-
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Life Physical and Social Science"] <- "Education, Science & Health"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Educational Instruction and Library"] <- "Education, Science & Health"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Healthcare Practitioner and Technical"] <- "Education, Science & Health"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Community and Social Service"] <- "Education, Science & Health"
-
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Office and Administrative Support"] <- "Admin, Healthcare & Legal"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Legal"] <- "Admin, Healthcare & Legal"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Healthcare Support"] <- "Admin, Healthcare & Legal"
-
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Arts Design Entertainment Sports Media"] <- "Other"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Military Specific"] <- "Other"
-
-#3 in plot all categories, combined and standalone
-
-ggplot(workers, aes(O.Net.Job.Family.Categories)) +
-  geom_histogram(stat="count") + coord_flip()
-
-dataworker <- cbind(data,workers)    ## to repeat O*Net analyses
-                                     ## This gets worker info into convergence file
-
-```
-
 ```{r percagree, fig.cap="Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance).", fig.height=10}
@@
 
+```{r workcat, fig.cap="Percent agreement (resource and challenge) across O*Net occupational categories (probably need to revisit original coding).", fig.height=10}
+
+## Job classifications
+
+workers <- read.csv("workers.csv")             ## Probably need to revisit our coding - 10/14/22
+
+# ggplot(workers, aes(O.Net.Job.Family.Categories))+
+#   geom_histogram(stat="count") + coord_flip()
+
+## Combining categories
+
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Transportation and Material Moving"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Protective Service"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Production"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Personal Care and Service"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Installation Maintenance and Repair"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Food Preparation and Serving Related"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Farming Fishing and Forestry"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Construction and Extraction"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Building and Grounds Cleaning and Maintenance"] <- "Physical Labor"
+
+## with Alicia 12/1
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Architecture and Engineering"] <- "Computer & Engineering"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Computer and Mathematical"] <- "Computer & Engineering"
+
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Life Physical and Social Science"] <- "Education, Science & Health"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Educational Instruction and Library"] <- "Education, Science & Health"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Healthcare Practitioner and Technical"] <- "Education, Science & Health"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Community and Social Service"] <- "Education, Science & Health"
+
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Office and Administrative Support"] <- "Admin, Healthcare & Legal"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Legal"] <- "Admin, Healthcare & Legal"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Healthcare Support"] <- "Admin, Healthcare & Legal"
+
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Arts Design Entertainment Sports Media"] <- "Other"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Military Specific"] <- "Other"
+
+#3 in plot all categories, combined and standalone
+
+#ggplot(workers, aes(O.Net.Job.Family.Categories)) +
+#  geom_histogram(stat="count") + coord_flip()
+
+dataworker <- cbind(anova,workers)    ## to repeat O*Net analyses
+                                     ## This gets worker info into convergence file
+
+dataworker$overall <- rowMeans(dataworker[1:84], na.rm=TRUE)
+
+ggplot(dataworker, aes(x=overall)) + geom_histogram() + facet_wrap(~O.Net.Job.Family.Categories, nrow=8)
+
+```
+
 # Discussion

### 2022-10-14 copy-of-SIOP2023convergence.tex
job cat graphs although looks like pulled from wrong object

@@
 
-\includegraphics{copy-of-SIOP2023convergence_files/figure-latex/workcat-1.pdf} \includegraphics{copy-of-SIOP2023convergence_files/figure-latex/workcat-2.pdf}
-
 \begin{figure}
@@
 A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of \(F_{(6, 3,402)}\) = 613.5, \emph{p} \textless{} .001 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001.
+
+\begin{figure}
+\centering
+\includegraphics{copy-of-SIOP2023convergence_files/figure-latex/workcat-1.pdf}
+\caption{\label{fig:workcat}Percent agreement (resource and challenge) across O*Net occupational categories (probably need to revisit original coding).}
+\end{figure}
 

### 2022-10-28 copy of SIOP2023convergence.Rmd
old edits from desktop prior to Hudson meeting

@@
     affiliation   : "2"
+  - name          : "Renata García Prieto Palacios Roji"
+    affiliation   : "3"
 
@@
     institution   : "University of Wisconsin - Stout"
+  - id            : "3"
+    institution   : "PepsiCo"
 

### 2022-10-28 copy-of-SIOP2023convergence.tex
old edits from desktop prior to Hudson meeting

@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Demanding resources: Converging characteristics of challenge and resource},
-  pdfauthor={John Kulas1 \& Alicia Stachowski2},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Demanding resources: Converging characteristics of challenge and resource},
+  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata García Prieto Palacios Roji3},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
 \title{Demanding resources: Converging characteristics of challenge and resource}
-\author{John Kulas\textsuperscript{1} \& Alicia Stachowski\textsuperscript{2}}
+\author{John Kulas\textsuperscript{1}, Alicia Stachowski\textsuperscript{2}, \& Renata García Prieto Palacios Roji\textsuperscript{3}}
 \date{}
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} eRg\\\textsuperscript{2} University of Wisconsin - Stout}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} eRg\\\textsuperscript{2} University of Wisconsin - Stout\\\textsuperscript{3} PepsiCo}
 

### 2022-10-28 copy of SIOP2023convergence.Rmd
new jobcat specification with ANOVAs added (p. 10)

@@
 
-```{r workcat, fig.cap="Percent agreement (resource and challenge) across O*Net occupational categories (probably need to revisit original coding).", fig.height=10}
+```{r workcat, fig.cap="Percent agreement (resource and challenge) across O*Net occupational categories (previous was across 84 O/*Net items - this is across 568 individual workers).", fig.height=10}
 
@@
 
-dataworker <- cbind(anova,workers)    ## to repeat O*Net analyses
+forworkers2 <- anova[,c(2:85)]
+dataworker <- cbind(forworkers2,workers$O.Net.Job.Family.Categories)    ## to repeat O*Net analyses
                                      ## This gets worker info into convergence file
@@
 
-ggplot(dataworker, aes(x=overall)) + geom_histogram() + facet_wrap(~O.Net.Job.Family.Categories, nrow=8)
+names(dataworker)[names(dataworker) == 'workers$O.Net.Job.Family.Categories'] <- 'JobFamily'
+
+ggplot(dataworker, aes(x=overall)) + geom_histogram() + facet_wrap(~JobFamily, nrow=8)
+
+workeraov <- aov(overall ~ JobFamily, data=dataworker)
+
+library(lsr)  ## for eta squared
+effect.size <- etaSquared(workeraov)
 
 ```
+
+```{r tukey}
+
+# TukeyHSD(workeraov)  ## Tukeys for temp in paper; biggest contrast p = .099
+# psych::describeBy(dataworker$overall, dataworker$JobFamily) (took means from here because `TukeyHSD` only reports relative difference)
+
+library(car)
+
+levenes <- leveneTest(overall ~ JobFamily, data=dataworker)
+
+```
+
+As can be seen in Figure \@ref(fig:workcat), the moderation seen across O\*Net dimension was not paralleled across *job classification*.
+Here, there was wide variability in convergence, regardless of *type* of job.
+The omnibus ANOVA did breach statistical significance ($F_{(7, 560)}$ = `r summary(workeraov)[[1]][1,4]`, *p* = `r summary(workeraov)[[1]][1,5]`), however, the practical effect was very small ($\eta^2$ = `r effect.size[1,1]`).
+The only contrast approaching statistical significance via Tukey's HSD specification (*p* = .09) was the contrast between Physical Labor (*M* = 0.49) and Business and Financial Operations (*M* = 0.58).
+Additionally, a Levene's test for homogeneity of variance was non-significant (Levene's = `r levenes[1,2]`, *p* = `r levenes[1,3]`).
+[should be .6539 and .7112]
 

### 2022-10-28 copy-of-SIOP2023convergence.tex
new jobcat specification with ANOVAs added (p. 10)

@@
 \usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Demanding resources: Converging characteristics of challenge and resource},
+  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata García Prieto Palacios Roji3},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={Demanding resources: Converging characteristics of challenge and resource},
-  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata García Prieto Palacios Roji3},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
 
@@
 \maketitle
+
+\begin{verbatim}
+## Warning: package 'tinylabels' was built under R version 4.1.3
+\end{verbatim}
 
@@
 \includegraphics{copy-of-SIOP2023convergence_files/figure-latex/workcat-1.pdf}
-\caption{\label{fig:workcat}Percent agreement (resource and challenge) across O*Net occupational categories (probably need to revisit original coding).}
+\caption{\label{fig:workcat}Percent agreement (resource and challenge) across O\emph{Net occupational categories (previous was across 84 O/}Net items - this is across 568 individual workers).}
 \end{figure}
+
+As can be seen in Figure \ref{fig:workcat}, the moderation seen across O*Net dimension was not paralleled across \emph{job classification}.
+Here, there was wide variability in convergence, regardless of \emph{type} of job.
+The omnibus ANOVA did breach statistical significance (\(F_{(7, 560)}\) = 2.06, \emph{p} = 0.05), however, the practical effect was very small (\(\eta^2\) = 0.03).
+The only contrast approaching statistical significance via Tukey's HSD specification (\emph{p} = .09) was the contrast between Physical Labor (\emph{M} = 0.49) and Business and Financial Operations (\emph{M} = 0.58).
+Additionally, a Levene's test for homogeneity of variance was non-significant (Levene's = 0.65, \emph{p} = 0.71).
+{[}should be .6539 and .7112{]}
 

### 2022-10-28 copy of SIOP2023convergence.Rmd
note on "extent to which characteristic is present" variables being used as a moderator

@@
 
+## Maybe do third moderator
+
+We also have ratings of "...the extent to which this characteristic is present in your job".
+Currently we're just taking a binary yes/no approach, but it does make sense to look for moderation based on *the degree to which the characteristic is present*.
+This is probably a better/more appropriate moderator than either of the above two...
+
 # Discussion

### 2022-10-28 copy-of-SIOP2023convergence.tex
note on "extent to which characteristic is present" variables being used as a moderator

@@
 
+\hypertarget{maybe-do-third-moderator}{%
+\subsection{Maybe do third moderator}\label{maybe-do-third-moderator}}
+
+We also have ratings of ``\ldots the extent to which this characteristic is present in your job''.
+Currently we're just taking a binary yes/no approach, but it does make sense to look for moderation based on \emph{the degree to which the characteristic is present}.
+This is probably a better/more appropriate moderator than either of the above two\ldots{}
+
 \hypertarget{discussion}{%

### 2022-11-03 copy-of-SIOP2023convergence.tex
survey

@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Demanding resources: Converging characteristics of challenge and resource},
-  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata García Prieto Palacios Roji3},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Demanding resources: Converging characteristics of challenge and resource},
+  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata García Prieto Palacios Roji3},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 
-\begin{verbatim}
-## Warning: package 'tinylabels' was built under R version 4.1.3
-\end{verbatim}
-
 An abundance of research applying the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker \& Demerouti, 2017) underscores the importance of job characteristics on the experience of work.
@@
 Demands, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure, Demerouti et al., 2001).
-These two categories of outcomes (e.g., ``good'' and ``bad'') are thought to occur via one of two different mechanisms: motivational (resulting from resources) or health impairment (resulting from demands, \textbf{bakker2014job?}).
+These two categories of outcomes (e.g., ``good'' and ``bad'') are thought to occur via one of two different mechanisms: motivational (resulting from resources) or health impairment (resulting from demands, Bakker \& Demerouti, 2014).
 Much of our existing research on the JD-R assumes that certain characteristics (for example, autonomy) are resources and others (for example, time constraints) are generally considered demands.
@@
 
-Although the word ``stress'' often carries a negative connotation, the ``father'' of the current concept, (\textbf{selye1936syndrome?}), conceptualized stress much less perjoratively - rather thinking of it as a \emph{response to change}.
+Although the word ``stress'' often carries a negative connotation, the ``father'' of the current concept, Selye (1936), conceptualized stress much less perjoratively - rather thinking of it as a \emph{response to change}.
 For instance, consider the different reactions two different employees may have to being nominated to give a speech at an upcoming company event.
@@
 However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
-Selye the physician would likely have labeled the two responses as subjective manifestations of ``Distress'', and ``Eustress'' (\textbf{selye1974stress?}).
-In modern I-O Psychology parlance (and more consistent with the JD-R framework), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a \emph{challenge} while the other would appraise the demand as a \emph{hindrance} (\textbf{cavanaugh2000empirical?}).
-According to (\textbf{cavanaugh2000empirical?}), challenge demands promote mastery, personal growth, and future gains.
+Selye the physician would likely have labeled the two responses as subjective manifestations of ``Distress'', and ``Eustress'' (Selye, 1974).
+In modern I-O Psychology parlance (and more consistent with the JD-R framework), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a \emph{challenge} while the other would appraise the demand as a \emph{hindrance} (Cavanaugh et al., 2000).
+According to Cavanaugh et al.
+(2000), challenge demands promote mastery, personal growth, and future gains.
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes (e.g., \textbf{cavanaugh2000empirical?}).
+Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes (e.g., Cavanaugh et al., 2000).
 
@@
 To begin, the first logical question is whether employees actually distinguish between challenges and hindrances, and research suggests that they can and do.
-For example, (\textbf{bakker2013weekly?}) found that perceived work pressure can be classified as a hindrance demand, while the requirement to express emotions is a challenge demand.
-(\textbf{webster2011extending?}) also considered three common work characteristics including workload, role ambiguity, and role conflict.
+For example, Bakker and Sanz-Vergel (2013) found that perceived work pressure can be classified as a hindrance demand, while the requirement to express emotions is a challenge demand.
+Webster et al.
+(2011) also considered three common work characteristics including workload, role ambiguity, and role conflict.
 Interestingly, they found that while each could be identified \emph{primarily} as a challenge or hindrance, employees could also appraise that a characteristic is simulataneously both a challenge and hindrance.
@@
 
-The Occupational Information Network (O*NET; onetonline.org) contains a fairly comprehensive description of occupations (\textbf{peterson2001understanding?}).
+The Occupational Information Network (O*NET; onetonline.org) contains a fairly comprehensive description of occupations (Peterson et al., 2001).
 This widely accessed database houses hundreds of standardized and occupation-specific descriptors for the majority of occupations within the United States, and these descriptions are frequently updated.
@@
 \hypertarget{convergence-same-characteristic.}{%
-\subsubsection{Convergence (same characteristic).}\label{convergence-same-characteristic.}}
+\subsection{Convergence (same characteristic).}\label{convergence-same-characteristic.}}
 
@@
 \end{figure}
+
+\hypertarget{moderating-effects}{%
+\subsubsection{Moderating effects}\label{moderating-effects}}
 
@@
 \hypertarget{maybe-do-third-moderator}{%
-\subsection{Maybe do third moderator}\label{maybe-do-third-moderator}}
+\paragraph{Maybe do third moderator}\label{maybe-do-third-moderator}}
 
@@
 Our findings perhaps most noteably highlight the importance of dissociating the \emph{nature} of job demands.
-Similar to the eustress/distress distinction (e.g., \textbf{selye1974stress?}), it would seem as though demands should perhaps be thought of in a valenced manner (e.g., is it a ``good'' demand or a ``bad'' demand).
-We did not probe for dependent variable associations, however, (\textbf{cavanaugh2000empirical?}) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite patterns in a sample of managers.
+Similar to the eustress/distress distinction (e.g., Selye, 1974), it would seem as though demands should perhaps be thought of in a valenced manner (e.g., is it a ``good'' demand or a ``bad'' demand).
+We did not probe for dependent variable associations, however, Cavanaugh et al.
+(2000) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite patterns in a sample of managers.
 We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford et al.
 (2010)).
-(\textbf{podsakoff2007differential?})'s meta-analysis also found that challenge demands were positively related to job satisfaction and organizational commitment and negatively related to both turnover intentions and actual turnover, while hindrance demands again produced the opposite patterns of relationship.
+Podsakoff et al.
+(2007)'s meta-analysis also found that challenge demands were positively related to job satisfaction and organizational commitment and negatively related to both turnover intentions and actual turnover, while hindrance demands again produced the opposite patterns of relationship.
 Although we did not probe for outcome associations, the current study does suggest that hindrance demands also operate in a manner different than challenge demands with regard to their association with resource appraisals.
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
+Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
+
 \leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
 Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
+Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
+Cavanaugh, M.
+A., Boswell, W.
+R., Roehling, M.
+V., \& Boudreau, J.
+W.
+(2000).
+An empirical examination of self-reported work stress among US managers.
+\emph{Journal of Applied Psychology}, \emph{85}(1), 65.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
+Peterson, N.
+G., Mumford, M.
+D., Borman, W.
+C., Jeanneret, P.
+R., Fleishman, E.
+A., Levin, K.
+Y., Campion, M.
+A., Mayfield, M.
+S., Morgeson, F.
+P., Pearlman, K., et al.
+(2001).
+Understanding work using the occupational information network (o* NET): Implications for practice and research.
+\emph{Personnel Psychology}, \emph{54}(2), 451--492.
+
+\leavevmode\vadjust pre{\hypertarget{ref-podsakoff2007differential}{}}%
+Podsakoff, N.
+P., LePine, J.
+A., \& LePine, M.
+A.
+(2007).
+Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis.
+\emph{Journal of Applied Psychology}, \emph{92}(2), 438.
+
+\leavevmode\vadjust pre{\hypertarget{ref-selye1936syndrome}{}}%
+Selye, H. (1936). A syndrome produced by diverse nocuous agents. \emph{Nature}, \emph{138}(3479), 32--32.
+
+\leavevmode\vadjust pre{\hypertarget{ref-selye1974stress}{}}%
+Selye, H. (1974). \emph{Stress without distress}. Lippincott Williams \& Wilkins.
+
+\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
+Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.
+
 \end{CSLReferences}

### 2022-11-06 Submission.tex
sum of resource challenge hindrance
Created scale scores of onet items grouped into literature-based job resource and demand categories.

--- 2022-03-21 Submission.tex
@@
 Given the popularity of the Job Demands-Resources Theory {[}JD-R; Demerouti et al.
-(2001){]} in exploring questions related to everything from motivation to job design, we aim to explore the intersection between perceptions of job demands and resources, and the broad set of job characteristics provided on O*Net.
+(2001){]} in exploring questions related to everything from motivation to job design, we aim to explore the intersection between \emph{perceptions} of job demands and resources, and the broad set of job characteristics provided on O*Net.
+This project makes three contributions.
+We aim to first explore whether ratings of of O*Net item groupings align with the stated ``resources'' and ``demands'' presented in the job demands-resources theory.
+We then present evidence documenting whether O*Net job and task descriptors are similarly rated as resources, challenge- or hindrance demands, and lastly, whether such ratings differ across job categories/classifications.
 Across two studies, a series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers.
@@
 
+Of greatest interest here are statements taken from O*NET \href{https://www.O*NETonline.org/find/descriptor/result/4.A.1.b.3}{``activity'' and ``context'' classifications} (e.g., items related to information input, interacting with others, physical work conditions, structural job characteristics).
+One of the first and basic questions is whether or not the categorical examples of ``resources'' and ``demands'' described in the Job Demands-Resources Theory (Demerouti et al., 2001), for example, are generally deemed resources or demands as we objectively define them.
+The next logical question surrounds how ``universal'' such ratings are.
+For instance, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.
+A second study extends the findings from Study 1 to a potentially key moderator - job categories/classifications, examining whether ratings of resources, challenge- and hindrance demands differ by job classification.
+
 \hypertarget{study-1}{%
-\subsection{Study 1}\label{study-1}}
+\section{Study 1}\label{study-1}}
 

### 2022-11-06 plotscript_practice.R

@@ -1,0 +1,91 @@
+#Open the Submission .rmd
+#Run chunks up to the source recodes chunk and then use the data object
+#to create the ggplot
+
+#Demands (resources ratings)
+#These are the literature-based categories, and composites - means - of Onet item ratings
+data$resources_workpressure <- rowMeans(subset(data, select = c(item120, item121)), na.rm = TRUE)
+data$resources_phyworkload_wkover <- rowMeans(subset(data, select = c(item122, item137, item138,
+                                                                      item139, item141, item142,
+                                                                      item143)), na.rm = TRUE)
+data$resources_timepressure <- rowMeans(subset(data, select = c(item125, item126)), na.rm = TRUE)
+data$resources_recipientcontact <- rowMeans(subset(data, select = c(item149, item154, item157, 
+                                                                    item160, item186, item188, 
+                                                                    item192, item197, item200, 
+                                                                    item201, item151)), na.rm = TRUE)
+data$resources_phyenvironment <- rowMeans(subset(data, select = c(item128, item129,	item130, item132,
+                                                                  item133,item134,	item136,	item137,
+                                                                  item138,	item139,	item140,	item141,
+                                                                  item142,	item143,	item144,	item146,
+                                                                  item147,	item148,	item177,	item180,
+                                                                  item182,	item181,	item183)), na.rm = TRUE)
+data$resources_workshift <- rowMeans(subset(data, select = c(item127)), na.rm = TRUE)
+data$resources_emotionaldemands <- rowMeans(subset(data, select = c(item150, item155, item199)), na.rm = TRUE)
+
+#Demands (challenge ratings)
+#These are the literature-based categories, and composites - means - of Onet item ratings
+data$challenge_workpressure <- rowMeans(subset(data, select = c(item290, item291)), na.rm = TRUE)
+data$challenge_phyworkload_wkover <- rowMeans(subset(data, select = c(item292, item307, 
+                                                                      item309, item310,	item312,
+                                                                      item313,	item314)), na.rm = TRUE)
+data$challenge_timepressure <- rowMeans(subset(data, select = c(item295, item296)), na.rm = TRUE)
+data$challenge_recipientcontact <- rowMeans(subset(data, select = c(item319, item324, item327,
+                                                                    item330, item356, item358,
+                                                                    item362, item367, item370,
+                                                                    item371, item321)), na.rm = TRUE)
[…]

### 2022-11-07 plotscript_practice.R
bar graph - still need to double check and probably facet (also need to decide on autonomy item)

@@ -1,5 +1,5 @@
 #Open the Submission .rmd
-#Run chunks up to the source recodes chunk and then use the data object
+#Run chunks up to the source recodes chunk (named, `generalrecodes`), and then use the data object
 #to create the ggplot
 
 #Demands (resources ratings)
@@ -88,4 +88,32 @@ data$hindrance_participation <- rowMeans(subset(data, select = c(item242, item24
                                                                  item260,	item274,	item278,
                                                                  item287)), na.rm = TRUE)
 data$hindrance_teamcohesion <- rowMeans(subset(data, select = c(item245, item275, item276)), na.rm = TRUE)
-data$challenge_autonomy <- rowMeans(subset(data, select = c(item203, item257)), na.rm = TRUE)
+data$hindrance_autonomy <- rowMeans(subset(data, select = c(item203, item257)), na.rm = TRUE)
+
+library(tidyr)
+
+toplot <- gather(data, scale, value, resources_workpressure:hindrance_teamcohesion, factor_key=TRUE)
+
+library(stringr)
+toplot$type <- str_sub(toplot$scale, 1,6)
+toplot$onet <- str_sub(toplot$scale, 10,-1)
+
+toplot$type[toplot$type == "challe"] <- "Challenge"
+toplot$type[toplot$type == "hindra"] <- "Hindrance"
+toplot$type[toplot$type == "resour"] <- "Resource"       ## change `onet` later if want to keep graphs
+
+toplot$onet[toplot$onet == "teamcohesion"] <- "Team Cohesion"       
+toplot$onet[toplot$onet == "_teamcohesion"] <- "Team Cohesion"  
+toplot$onet[toplot$onet == "participation"] <- "Participation"       
+toplot$onet[toplot$onet == "_participation"] <- "Participation"  
+toplot$onet[toplot$onet == "jobcontrol"] <- "Job Control"       
+toplot$onet[toplot$onet == "_jobcontrol"] <- "Job Control"  
+toplot$onet[toplot$onet == "autonomy"] <- "Autonomy"       
+toplot$onet[toplot$onet == "_autonomy"] <- "Autonomy"  
+
+toplotgg <- ddply(toplot, c("type", "onet"), summarise, average = mean(value, na.rm=TRUE))
+
+ggplot(data=toplotgg, aes(x=onet, y=average, fill=type)) + 
+  geom_bar(stat="identity", position=position_dodge()) + coord_flip()
+
[…]

### 2022-11-09 plotscript_practice.R
added a table for the manuscript

@@ -90,6 +90,9 @@ data$hindrance_participation <- rowMeans(subset(data, select = c(item242, item24
 data$hindrance_teamcohesion <- rowMeans(subset(data, select = c(item245, item275, item276)), na.rm = TRUE)
 data$hindrance_autonomy <- rowMeans(subset(data, select = c(item203, item257)), na.rm = TRUE)
 
+#check the autonomy variables
+summary(data$hindrance_autonomy)
+
 library(tidyr)
 
 toplot <- gather(data, scale, value, resources_workpressure:hindrance_teamcohesion, factor_key=TRUE)

### 2022-11-11 copy-of-SIOP2023convergence.tex
maybe putting hold on convergence paper

@@
 \usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Demanding resources: Converging perceptions of challenge and resource characteristics},
+  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata García Prieto Palacios Roji3},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={Demanding resources: Converging characteristics of challenge and resource},
-  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata García Prieto Palacios Roji3},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
 
-\title{Demanding resources: Converging characteristics of challenge and resource}
+\title{Demanding resources: Converging perceptions of challenge and resource characteristics}
 \author{John Kulas\textsuperscript{1}, Alicia Stachowski\textsuperscript{2}, \& Renata García Prieto Palacios Roji\textsuperscript{3}}
@@
 This study searches instead for circumstances that provide exception to this mutually exclusive dichotomy of job characteristics.
+
+\begin{figure}
+\centering
+\includegraphics{copy-of-SIOP2023convergence_files/figure-latex/uhoh-1.pdf}
+\caption{\label{fig:uhoh}Maybe put a hold on this paper as wording of resource and challenge seems very similar}
+\end{figure}
+
+see Figure \ref{fig:uhoh}
 
@@
 S., Morgeson, F.
-P., Pearlman, K., et al.
+P., Pearlman, K.others.
 (2001).

### 2022-11-11 plotscript_practice.R
Added a draft manuscript and updated the graph

@@ -2,6 +2,9 @@
 #Run chunks up to the source recodes chunk (named, `generalrecodes`), and then use the data object
 #to create the ggplot
 
+library(ggplot2)
+library(plyr)
+
 #Demands (resources ratings)
 #These are the literature-based categories, and composites - means - of Onet item ratings
 data$resources_workpressure <- rowMeans(subset(data, select = c(item120, item121)), na.rm = TRUE)
@@ -14,12 +17,9 @@ data$resources_recipientcontact <- rowMeans(subset(data, select = c(item149, ite
                                                                     item192, item197, item200, 
                                                                     item201, item151)), na.rm = TRUE)
 data$resources_phyenvironment <- rowMeans(subset(data, select = c(item128, item129,	item130, item132,
-                                                                  item133,item134,	item136,	item137,
-                                                                  item138,	item139,	item140,	item141,
-                                                                  item142,	item143,	item144,	item146,
+                                                                  item133,item134,	item136,	item144,	item146,
                                                                   item147,	item148,	item177,	item180,
                                                                   item182,	item181,	item183)), na.rm = TRUE)
-data$resources_workshift <- rowMeans(subset(data, select = c(item127)), na.rm = TRUE)
 data$resources_emotionaldemands <- rowMeans(subset(data, select = c(item150, item155, item199)), na.rm = TRUE)
 
 #Demands (challenge ratings)
@@ -34,12 +34,9 @@ data$challenge_recipientcontact <- rowMeans(subset(data, select = c(item319, ite
                                                                     item362, item367, item370,
                                                                     item371, item321)), na.rm = TRUE)
 data$challenge_phyenvironment <- rowMeans(subset(data, select = c(item298, item299, item300, item302,
-                                                                  item303, item304,item306, item307,
-                                                                  item309, item310, item311, item312,
-                                                                  item313, item314, item315, item316,
+                                                                  item303, item304,item306, item315, item316,
                                                                   item317, item318, item347, item350,
                                                                   item352, item351, item353)), na.rm = TRUE)
[…]

### 2022-11-11 copy of SIOP2023convergence.Rmd
survey

@@
 ---
-title             : "Demanding resources: Converging characteristics of challenge and resource"
+title             : "Demanding resources: Converging perceptions of challenge and resource characteristics"
 shorttitle        : "Demanding Resources"
@@
 This study searches instead for circumstances that provide exception to this mutually exclusive dichotomy of job characteristics.
+
+```{r uhoh, fig.cap="Maybe put a hold on this paper as wording of resource and challenge seems very similar"}
+
+library(grid) 
+library(magick)
+figure <- image_read("uhoh.png")
+
+grid.raster(figure)
+
+```
+
+see Figure \ref{fig:uhoh}
 
@@
 
-### Convergence (same characteristic).
+## Convergence (same characteristic).
 
@@
 ```
-
-Figure \@ref(fig:recchall) explores the possibility of moderation by *type of characteristic rated* for the resource-challenge convergence.
-Here we categorized each characteristic by its O\*Net "scale" (one of seven), and the graph shows greater consistency across certain characteristics (for example, *Mental Processes* or *Interacting with Others*) and less convergence across other *types* of job activities (for example, *Physical* characteristics).
-A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of $F_{(6, 3,402)}$ = 613.5, *p* < .001 (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001.
 
@@
 ```
+
+### Moderating effects
+
+Figure \@ref(fig:recchall) explores the possibility of moderation by *type of characteristic rated* for the resource-challenge convergence.
+Here we categorized each characteristic by its O\*Net "scale" (one of seven), and the graph shows greater consistency across certain characteristics (for example, *Mental Processes* or *Interacting with Others*) and less convergence across other *types* of job activities (for example, *Physical* characteristics).
+A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of $F_{(6, 3,402)}$ = 613.5, *p* < .001 (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001.
 
@@
 
-## Maybe do third moderator
+#### Maybe do third moderator
 

### 2022-11-11 Submission.Rmd
udpated submission.rmd file with our new notes and predictions.

@@
 Several broad research questions are examined across jobs:
+
+>Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
+
+>Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
+
+Add a description here of the exploratory stuff.
 
@@
 
-## Materials
-
-Looked through
-
 # Study 2
-
-While Study 1 explored the above questions across jobs, Study 2 considers a potentially important moderator: job classification.
-There is a distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework depending on *job classification*.
-In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., [@bakker2013weekly]; [@cavanaugh2000empirical]; [@gerich2017relevance]; [@podsakoff2007differential]; [@webster2011extending]).
-Thus, Study 2 focuses on a fourth question of interest.
-
->*Research Question 4*: Does the **type of work** reported explain variability in the categorization of work characteristics into challenges, hindrances, and resources?
 
@@
 
+```{r scale-level-graphs eval = FALSE}
+#this is a placeholder for the scale level faceted graph found in plotscript_practice script file. 
+```
+
 \newpage

### 2022-11-11 Submission.tex
udpated submission.rmd file with our new notes and predictions.

@@
 
-Of the 785 Prolific panel individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (\textbf{R-careless?}).
+Of the 785 Prolific panel individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021).
 Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current SIOP sample.
@@
 
+\leavevmode\hypertarget{ref-R-careless}{}%
+Yentes, R. D., \& Wilhelm, F. (2021). \emph{Careless: Procedures for computing indices of careless responding}.
+
 \end{CSLReferences}

### 2022-11-11 plotscript_practice.R
updated practice plot

@@ -118,10 +118,10 @@ ggplot(data=toplotgg, aes(x=onet, y=average, fill=type)) +
 
 ## Probably want to change this to a facet: 3 different grids grouped by literature-described 1) resource, 2) hindrances, and 3) challenge
 
-library(dplyr)
-toplotgg %>% filter(row(toplotgg) == 8 & row(toplotgg)
-                    == 8 & row(toplotgg) == 27)
-
 toplotgg$facet <- c("d", "d", "d", "d", "d", "d", "r", "r", "r", "r",
                     "d", "d", "d", "d", "d", "d", "r", "r", "r", "r",
                     "d", "d", "d", "d", "d", "d", "r", "r", "r", "r")
+
+ggplot(data=toplotgg, aes(x=onet, y=average, fill=type)) + 
+  geom_bar(stat="identity", position=position_dodge()) + coord_flip() +
+  facet_wrap(~facet)

### 2022-11-11 Submission.Rmd
porting Word document notes into .Rmd

@@
 Maybe forget about cross-walk thing.
-May actually want to start with this: https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit#gid=1041061499.
+May actually want to start with this: https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit#gid=1041061499.[^foot1]
 
@@
 
+[^foot1]: Need to rewrite
+
 Given the popularity of the Job Demands-Resources Theory [JD-R; @demerouti2001job] in exploring questions related to everything from motivation to job design, we aim to explore the intersection between *perceptions* of job demands and resources, and the broad set of job characteristics provided on O\*Net.
@@
 We then present evidence documenting whether O\*Net job and task descriptors are similarly rated as resources, challenge- or hindrance demands, and lastly, whether such ratings differ across job categories/classifications.
+
 Across two studies, a series of evaluations were made that used: 1) direct O\*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers.
@@
 
-## The Job demands-Resources Theory
+## The Job demands-Resources Theory[^foot2]
+
+[^foot2]: Need to expand this section
 
@@
 In contrast, *demands* include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; @demerouti2001job).
+
 Cognitively, the perception of an element of ones job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation [resulting from resources; @bakker2014job].
@@
 
-## Objective vs. Subjective Nature of Demands and Resources: The Role of Appraisal
+**Add information on Challenge-Hindrance stuff - it's in the SIOP submission so should be able to copy/paste**
+
+## Objective vs. Subjective Nature of Demands and Resources: The Role of Appraisal[^foot3]
+
+[^foot3]: Look for more recent literature - this is currently a bit dated
 
@@
 
-# Study 1
+# Study 1[^foot4]
+
+[^foot4]: Need to delete all references to Study 1 and Study 2
 
@@
 
-```{r scale-level-graphs eval = FALSE}
+```{r scale-level-graphs, eval = FALSE}
 #this is a placeholder for the scale level faceted graph found in plotscript_practice script file. 

### 2022-11-11 Submission.tex
porting Word document notes into .Rmd

--- 2022-08-24 Submission.tex
@@
 Maybe forget about cross-walk thing.
-May actually want to start with this: \url{https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit\#gid=1041061499}.
+May actually want to start with this: \url{https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit\#gid=1041061499}.\footnote{Need to rewrite}
 
@@
 We then present evidence documenting whether O*Net job and task descriptors are similarly rated as resources, challenge- or hindrance demands, and lastly, whether such ratings differ across job categories/classifications.
+
 Across two studies, a series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers.
@@
 
-\hypertarget{the-job-demands-resources-theory}{%
-\subsection{The Job demands-Resources Theory}\label{the-job-demands-resources-theory}}
+\hypertarget{the-job-demands-resources-theoryfoot2}{%
+\subsection[The Job demands-Resources Theory]{\texorpdfstring{The Job demands-Resources Theory\footnote{Need to expand this section}}{The Job demands-Resources Theory}}\label{the-job-demands-resources-theoryfoot2}}
 
@@
 (2001)).
+
 Cognitively, the perception of an element of ones job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation {[}resulting from resources; A.
@@
 
-\hypertarget{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisal}{%
-\subsection{Objective vs.~Subjective Nature of Demands and Resources: The Role of Appraisal}\label{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisal}}
+\textbf{Add information on Challenge-Hindrance stuff - it's in the SIOP submission so should be able to copy/paste}
+
+\hypertarget{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisalfoot3}{%
+\subsection[Objective vs.~Subjective Nature of Demands and Resources: The Role of Appraisal]{\texorpdfstring{Objective vs.~Subjective Nature of Demands and Resources: The Role of Appraisal\footnote{Look for more recent literature - this is currently a bit dated}}{Objective vs.~Subjective Nature of Demands and Resources: The Role of Appraisal}}\label{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisalfoot3}}
 
@@
 
-\hypertarget{study-1}{%
-\section{Study 1}\label{study-1}}
+\hypertarget{study-1foot4}{%
+\section[Study 1]{\texorpdfstring{Study 1\footnote{Need to delete all references to Study 1 and Study 2}}{Study 1}}\label{study-1foot4}}
 
@@
 Several broad research questions are examined across jobs:
+
+\begin{quote}
+Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
+\end{quote}
+
+\begin{quote}
+Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
+\end{quote}
+
+Add a description here of the exploratory stuff.
 
@@
 
-\hypertarget{materials}{%
-\subsection{Materials}\label{materials}}
-
-Looked through
-
 \hypertarget{study-2}{%
@@
 
-While Study 1 explored the above questions across jobs, Study 2 considers a potentially important moderator: job classification.
-There is a distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework depending on \emph{job classification}.
-In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., (A.
-B.
-Bakker \& Sanz-Vergel, 2013); (Cavanaugh et al., 2000); (Gerich, 2017); (Podsakoff et al., 2007); (Webster et al., 2011)).
-Thus, Study 2 focuses on a fourth question of interest.
-
-\begin{quote}
-\emph{Research Question 4}: Does the \textbf{type of work} reported explain variability in the categorization of work characteristics into challenges, hindrances, and resources?
-\end{quote}
-
-\hypertarget{materials-1}{%
-\subsection{Materials}\label{materials-1}}
+\hypertarget{materials}{%
+\subsection{Materials}\label{materials}}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
-Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
-
 \leavevmode\vadjust pre{\hypertarget{ref-landis1977measurement}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-careless}{}}%
+Yentes, R. D., \& Wilhelm, F. (2021). \emph{Careless: Procedures for computing indices of careless responding}.
+
 \end{CSLReferences}

### 2022-11-13 plotscript_practice.R
Updated graphs.

@@ -4,6 +4,7 @@
 
 library(ggplot2)
 library(plyr)
+library(dplyr)
 
 #Demands (resources ratings)
 #These are the literature-based categories, and composites - means - of Onet item ratings
@@ -125,3 +126,12 @@ toplotgg$facet <- c("d", "d", "d", "d", "d", "d", "r", "r", "r", "r",
 ggplot(data=toplotgg, aes(x=onet, y=average, fill=type)) + 
   geom_bar(stat="identity", position=position_dodge()) + coord_flip() +
   facet_wrap(~facet)
+
+demandsplot <- filter(toplotgg, facet == "d")
+resourcesplot <- filter(toplotgg, facet == "r")
+
+ggplot(data=demandsplot, aes(x=onet, y=average, fill=type)) + 
+  geom_bar(stat="identity", position=position_dodge()) + coord_flip() 
+
+ggplot(data=resourcesplot, aes(x=onet, y=average, fill=type)) + 
+  geom_bar(stat="identity", position=position_dodge()) + coord_flip()

### 2022-11-18 Submission.Rmd
updating introduction section

@@
 
-[^foot1]: Need to rewrite
+Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlight the importance of work characteristics on the experience of motivation and strain, which clearly have an impact on job performance.
+In light of some of the recent debate surrounding the challenge-hindrance stressor framework [e.g., @mazzola2019should], we extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, and how they relate to two important organizational outcomes: engagement and stress.
+Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.
 
-Given the popularity of the Job Demands-Resources Theory [JD-R; @demerouti2001job] in exploring questions related to everything from motivation to job design, we aim to explore the intersection between *perceptions* of job demands and resources, and the broad set of job characteristics provided on O\*Net.
-This project makes three contributions.
-We aim to first explore whether ratings of of O\*Net item groupings align with the stated "resources" and "demands" presented in the job demands-resources theory.
-We then present evidence documenting whether O\*Net job and task descriptors are similarly rated as resources, challenge- or hindrance demands, and lastly, whether such ratings differ across job categories/classifications.
-
-Across two studies, a series of evaluations were made that used: 1) direct O\*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers.
-Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O\*Net is provided.
-
-## The Job demands-Resources Theory[^foot2]
-
-[^foot2]: Need to expand this section
+## The Job demands-Resources Theory
 
@@
 *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
-In contrast, *demands* include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; @demerouti2001job).
+In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; @demerouti2001job).
 
-Cognitively, the perception of an element of ones job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation [resulting from resources; @bakker2014job].
-Pertinent to the current study, demanding job characteristics are frequently associated with negative outcomes [e.g., @bakker2003dual], whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job].
+Cognitively, the perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources) [@bakker2014job].
+Pertinent to the current study, demanding job characteristics are frequently often associated with negative outcomes [e.g., @bakker2003dual], whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job].
 
-**Add information on Challenge-Hindrance stuff - it's in the SIOP submission so should be able to copy/paste**
+## The Essential Role of Appraisal
 
-## Objective vs. Subjective Nature of Demands and Resources: The Role of Appraisal[^foot3]
+As implied in the last paragraph, job context and characteristics are “assigned” or appraised as demands or resources.
+Although some research on job demands in particular is based on apriori classifications of demands [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand.
+The stress process speaks to how such individual difference in appraisal is possible.
+@lazarus1984stress presented the transactional theory of stress and coping, which states that people cognitively appraise stimuli in their environments on a continuous basis.
+Via this process, meaning is assigned to stimuli – if appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping.
+The cycle of appraisal then continues based on the action to cope with the stressor [@lazarus1984stress].
 
-[^foot3]: Look for more recent literature - this is currently a bit dated
+## The Challenge-hindrance Stressor Framework
 
-@searle2015merits note that the majority of the research on workplace demands is based on apriori classifications of demands.
-However, the stress experience, or process, described early on by @lazarus1984stress is grounded in the assumption that individual appraisals of stressors/demands vary.
-Their transactional theory of stress and coping states that people continuously appraise stimuli in their environments.
-An appraisal is the cognitive process whereby meaning is assigned to a stimulus.
-If a stimulus is appraised as a stressor (threat, challenge, potentially harmful), emotional distress leads to coping of some kind.
-This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes is not appraised as favorable [@lazarus1984stress].
-The stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.
+Although there is a tendency to attach a negative connotation to the word “stress”, @selye1936syndrome defined stress as a response to change, which is quite non-specific.
+We return to the employed public figure for this next section.
+It is quite probable that two employees would be called upon to serve as a spokesperson for their organization in a time of need.
+One may appraise the circumstance as an opportunity to positively influence others, while the other may plausibly feel paralyzed by the task.
+In fact, @bakker2017job call attention to different types of demands in their recent review of, and future directions, for work on the job-demands resources theory.
+The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor (@cavanaugh2000empirical).
+@cavanaugh2000empirical delineated between two forms of demands – that of *challenge* and *hindrance* demands.
+Challenge demands promote mastery, personal growth, and future gains – these stressors should lead to coping strategies that facilitate achievement.
+Stressors like time pressure and responsibility are considered challenge stressors/demands.
+hindrance demands, in contrast, inhibit growth, learning and goal achievement.
+Hindrance stressors (e.g., role conflict, role ambiguity, politics) are associated with negative job behaviors and attitudes.
+This particular distinction between challenges and hindrances has been of value in determining what demands are related to various outcomes, whereby challenge stressors are typically associated with positive outcomes, and hindrance stressors, negative outcomes (e.g., @cavanaugh2000empirical).
 
-We next consider the (limited) empirical evidence on this topic.
-First, some relatively recent research suggests that job demands and resources may not be universally appraised or assigned as such.
-Starting with job demands, @webster2011extending, for example, studied workload, role ambiguity, and role conflict demands, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees.
-While their study did include resources, it nonetheless points to individual differences on how people perceive stressors at work.
-Although part of a much larger study on retirement, @sonnega_comparison_2018 compared self-reported (subjective) ratings of degree of physical demand, stress, and need for intense concentration from the Health and Retirement Study with objective ratings from O*Net.
-Correlations physical demand (r = .52), stress (r = .10), and need for intense concentration (r = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than assumed.
-Next considering resources, @schmitz_interpreting_2019 also captured subjective and objective resources in their study of retirement.
-Correlations of composite variables for the resources of autonomy (r = .12.
-p > .01), recognition of work (r = .07, p > .01), and decision freedom (r = .08, p > .01), while significant, certainly do not reflect high levels of overlap.
+However, one of the key questions we need to ask as researchers pertains to the very basic consideration of appraisals.
+In fact, this is one of several issues raised by @ mazzola2019should in a recent review and meta-analysis of this framework.
+These authors cited the apriori assignment to stressors as a challenge or hindrance as a flawed assumption, suggesting that stressors are more likely to be a combination of both – challenge and hindrance appraisals.
+@lepine2022challenge, in a rebuttal to the @ mazzola2019should criticism, while acknowledging that the original challenge-hindrance stressor framework was based on the assertion that people tend to appraise specific work stressors ad challenges and other demands, noted that the appraisals likely served as a mediator.
 
-We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees.
-@downes2021incorporating meta-analysis addresses this reality in depth, although it is beyond the scope of this project.
+We next consider the empirical evidence on this topic.
+The first obvious question is whether people perceive demands as challenges vs.
+hindrances, or whether all demands are under a larger “demands” category.
+Evidence suggests the employees do, in fact, distinguish between challenge and hindrance stressors [e.g., @bakker2013weekly; @gerich2017relevance; @webster2011extending].
+For example, @bakker2013weekly found that perceived work pressure as a hindrance demand, and emotional demands as more of a challenge demand.
+@webster2011extending approached this question with three common workplace demands: workload, role ambiguity, and role conflict.
+They found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees.
+
+While their study did include resources, it nonetheless points to the possibility that demands might be differentially appraised and related to outcomes [e.g., @podsakoff2007differential].
+The challenge-hindrance framework has, in fact, been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and well-being.
+A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic.
+For example, @cavanaugh2000empirical, in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern.
+In contrast, @abbas2019challenge found that challenge and hindrance stressors were *both* positively related to strain and turnover intentions.
+We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with it [@crawford2010linking].
+Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety [@rodell2009can].
+Lastly, @gerich2017relevance concluded that employee well-being was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
+
+We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point.
+@podsakoff2007differential supported the original assertion of @cavanaugh2000empirical with regard to work outcomes such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover.
+The opposite pattern of relationship was observed for hindrance stressors.
+@ kim2020thriving, similarly, found evidence for the differential results via challenge and hindrance appraisals
 
@@
 
-# Study 1[^foot4]
-
-[^foot4]: Need to delete all references to Study 1 and Study 2
-
-Look at the [google sheet](https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit#gid=1041061499) and document the extent to which job characteristics that have been consistently cited in the literature as demands or resources end up being consistently or variably experienced as demands or resources.
-Study 1 aims to provide an integration of the theory and practical occupations-focused data on O\*Net.
-Several broad research questions are examined across jobs:
-
 >Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
@@
 
->*Research Question 3*: Are literature-implicated hiderances consistently rated as job hinderances?
+>*Research Question 3*: Are literature-implicated hiderances consistently rated as job hindrances?
 
@@
 We retained the O\*NET wording to capture characteristics of relevance for each respondent.
-Subsequent to these self evaluations, each respondent who agreed that the element had *at least some relevance* to their job was also asked to rate that element in terms of, 1) ...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) ...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) ...this aspect of your job is a hinderance that can inhibit personal growth, learning, and work goal attainment.
+Subsequent to these self evaluations, each respondent who agreed that the element had *at least some relevance* to their job was also asked to rate that element in terms of, 1) ...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) ...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) ...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
 

### 2022-11-18 Submission.tex
Updating the introduction

--- 2022-11-11 Submission.tex
@@
 Maybe forget about cross-walk thing.
-May actually want to start with this: \url{https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit\#gid=1041061499}.
+May actually want to start with this: \url{https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit\#gid=1041061499}.{[}\^{}foot1{]}
 
@@
 
-Given the popularity of the Job Demands-Resources Theory {[}JD-R; Demerouti et al.
-(2001){]} in exploring questions related to everything from motivation to job design, we aim to explore the intersection between \emph{perceptions} of job demands and resources, and the broad set of job characteristics provided on O*Net.
-This project makes three contributions.
-We aim to first explore whether ratings of of O*Net item groupings align with the stated ``resources'' and ``demands'' presented in the job demands-resources theory.
-We then present evidence documenting whether O*Net job and task descriptors are similarly rated as resources, challenge- or hindrance demands, and lastly, whether such ratings differ across job categories/classifications.
-Across two studies, a series of evaluations were made that used: 1) direct O*Net terminology (both descriptor and response option), and 2) JD-R influenced ratings of demand, challenge, or hindrance of different types of workers.
-Prior to a description of results, a brief overview of both the JD-R theory, the stress appraisal process, and O*Net is provided.
+Research on the job demands-resources model (Demerouti et al., 2001) and later job demands-resources theory (A.
+B.
+Bakker \& Demerouti, 2017) highlight the importance of work characteristics on the experience of motivation and strain, which clearly have an impact on job performance.
+In light of some of the recent debate surrounding the challenge-hindrance stressor framework (e.g., Mazzola \& Disselhorst, 2019), we extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, and how they relate to two important organizational outcomes: engagement and stress.
+Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.
 
@@
 \emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
-In contrast, \emph{demands} include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; Demerouti et al.
+In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; Demerouti et al.
 (2001)).
-Cognitively, the perception of an element of ones job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation {[}resulting from resources; A.
+
+Cognitively, the perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources) (A.
 B.
-Bakker and Demerouti (2014){]}.
-Pertinent to the current study, demanding job characteristics are frequently associated with negative outcomes (e.g., A.
+Bakker \& Demerouti, 2014).
+Pertinent to the current study, demanding job characteristics are frequently often associated with negative outcomes (e.g., A.
 Bakker et al., 2003), whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation (A.
@@
 
-\hypertarget{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisal}{%
-\subsection{Objective vs.~Subjective Nature of Demands and Resources: The Role of Appraisal}\label{objective-vs.-subjective-nature-of-demands-and-resources-the-role-of-appraisal}}
+\hypertarget{the-essential-role-of-appraisal}{%
+\subsection{The Essential Role of Appraisal}\label{the-essential-role-of-appraisal}}
 
-Searle and Auton (2015) note that the majority of the research on workplace demands is based on apriori classifications of demands.
-However, the stress experience, or process, described early on by Lazarus and Folkman (1984) is grounded in the assumption that individual appraisals of stressors/demands vary.
-Their transactional theory of stress and coping states that people continuously appraise stimuli in their environments.
-An appraisal is the cognitive process whereby meaning is assigned to a stimulus.
-If a stimulus is appraised as a stressor (threat, challenge, potentially harmful), emotional distress leads to coping of some kind.
-This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes is not appraised as favorable (Lazarus \& Folkman, 1984).
-The stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error.
+As implied in the last paragraph, job context and characteristics are ``assigned'' or appraised as demands or resources.
+Although some research on job demands in particular is based on apriori classifications of demands (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand.
+The stress process speaks to how such individual difference in appraisal is possible.
+Lazarus and Folkman (1984) presented the transactional theory of stress and coping, which states that people cognitively appraise stimuli in their environments on a continuous basis.
+Via this process, meaning is assigned to stimuli -- if appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping.
+The cycle of appraisal then continues based on the action to cope with the stressor (Lazarus \& Folkman, 1984).
 
-We next consider the (limited) empirical evidence on this topic.
-First, some relatively recent research suggests that job demands and resources may not be universally appraised or assigned as such.
-Starting with job demands, Webster et al.
-(2011), for example, studied workload, role ambiguity, and role conflict demands, and found that while each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees.
-While their study did include resources, it nonetheless points to individual differences on how people perceive stressors at work.
-Although part of a much larger study on retirement, Sonnega et al.
-(2018) compared self-reported (subjective) ratings of degree of physical demand, stress, and need for intense concentration from the Health and Retirement Study with objective ratings from O*Net.
-Correlations physical demand (r = .52), stress (r = .10), and need for intense concentration (r = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than assumed.
-Next considering resources, Schmitz et al.
-(2019) also captured subjective and objective resources in their study of retirement.
-Correlations of composite variables for the resources of autonomy (r = .12.
-p \textgreater{} .01), recognition of work (r = .07, p \textgreater{} .01), and decision freedom (r = .08, p \textgreater{} .01), while significant, certainly do not reflect high levels of overlap.
+\hypertarget{the-challenge-hindrance-stressor-framework}{%
+\subsection{The Challenge-hindrance Stressor Framework}\label{the-challenge-hindrance-stressor-framework}}
 
-We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees.
-Downes et al.
-(2021) meta-analysis addresses this reality in depth, although it is beyond the scope of this project.
+Although there is a tendency to attach a negative connotation to the word ``stress,'' Selye (1936) defined stress as a response to change, which is quite non-specific.
+We return to the employed public figure for this next section.
+It is quite probable that two employees would be called upon to serve as a spokesperson for their organization in a time of need.
+One may appraise the circumstance as an opportunity to positively influence others, while the other may plausibly feel paralyzed by the task.
+In fact, A.
+B.
+Bakker and Demerouti (2017) call attention to different types of demands in their recent review of, and future directions, for work on the job-demands resources theory.
+The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor (Cavanaugh et al.
+(2000)).
+Cavanaugh et al.
+(2000) delineated between two forms of demands -- that of \emph{challenge} and \emph{hindrance} demands.
+Challenge demands promote mastery, personal growth, and future gains -- these stressors should lead to coping strategies that facilitate achievement.
+Stressors like time pressure and responsibility are considered challenge stressors/demands.
+hindrance demands, in contrast, inhibit growth, learning and goal achievement.
+Hindrance stressors (e.g., role conflict, role ambiguity, politics) are associated with negative job behaviors and attitudes.
+This particular distinction between challenges and hindrances has been of value in determining what demands are related to various outcomes, whereby challenge stressors are typically associated with positive outcomes, and hindrance stressors, negative outcomes (e.g., Cavanaugh et al.
+(2000)).
+
+However, one of the key questions we need to ask as researchers pertains to the very basic consideration of appraisals.
+In fact, this is one of several issues raised by @ mazzola2019should in a recent review and meta-analysis of this framework.
+These authors cited the apriori assignment to stressors as a challenge or hindrance as a flawed assumption, suggesting that stressors are more likely to be a combination of both -- challenge and hindrance appraisals.
+LePine (2022), in a rebuttal to the @ mazzola2019should criticism, while acknowledging that the original challenge-hindrance stressor framework was based on the assertion that people tend to appraise specific work stressors ad challenges and other demands, noted that the appraisals likely served as a mediator.
+
+We next consider the empirical evidence on this topic.
+The first obvious question is whether people perceive demands as challenges vs.~hindrances, or whether all demands are under a larger ``demands'' category.
+Evidence suggests the employees do, in fact, distinguish between challenge and hindrance stressors (e.g., A.
+B.
+Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011).
+For example, A.
+B.
+Bakker and Sanz-Vergel (2013) found that perceived work pressure as a hindrance demand, and emotional demands as more of a challenge demand.
+Webster et al.
+(2011) approached this question with three common workplace demands: workload, role ambiguity, and role conflict.
+They found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees.
+
+While their study did include resources, it nonetheless points to the possibility that demands might be differentially appraised and related to outcomes (e.g., Podsakoff et al., 2007).
+The challenge-hindrance framework has, in fact, been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and well-being.
+A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic.
+For example, Cavanaugh et al.
+(2000), in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern.
+In contrast, Abbas and Raja (2019) found that challenge and hindrance stressors were \emph{both} positively related to strain and turnover intentions.
+We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with it (Crawford et al., 2010).
+Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety (Rodell \& Judge, 2009).
+Lastly, Gerich (2017) concluded that employee well-being was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
+
+We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point.
+Podsakoff et al.
+(2007) supported the original assertion of Cavanaugh et al.
+(2000) with regard to work outcomes such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover.
+The opposite pattern of relationship was observed for hindrance stressors.
+@ kim2020thriving, similarly, found evidence for the differential results via challenge and hindrance appraisals
 
@@
 
-\hypertarget{study-1}{%
-\section{Study 1}\label{study-1}}
+\begin{quote}
+Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
+\end{quote}
 
-Look at the \href{https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit\#gid=1041061499}{google sheet} and document the extent to which job characteristics that have been consistently cited in the literature as demands or resources end up being consistently or variably experienced as demands or resources.
-Study 1 aims to provide an integration of the theory and practical occupations-focused data on O*Net.
-Several broad research questions are examined across jobs:
+\begin{quote}
+Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
+\end{quote}
+
+Add a description here of the exploratory stuff.
 
@@
 \begin{quote}
-\emph{Research Question 3}: Are literature-implicated hiderances consistently rated as job hinderances?
+\emph{Research Question 3}: Are literature-implicated hiderances consistently rated as job hindrances?
 \end{quote}
@@
 
-Looked through
-
-\hypertarget{study-2}{%
-\section{Study 2}\label{study-2}}
-
-While Study 1 explored the above questions across jobs, Study 2 considers a potentially important moderator: job classification.
-There is a distinct possibility we expect we may observe is wide variability in the assignment of some job characteristics within the JD-R framework depending on \emph{job classification}.
-In fact, a growing body of evidence suggests people may not universally experience job characteristics as challenges or hinderances (e.g., (A.
-B.
-Bakker \& Sanz-Vergel, 2013); (Cavanaugh et al., 2000); (Gerich, 2017); (Podsakoff et al., 2007); (Webster et al., 2011)).
-Thus, Study 2 focuses on a fourth question of interest.
-
-\begin{quote}
-\emph{Research Question 4}: Does the \textbf{type of work} reported explain variability in the categorization of work characteristics into challenges, hindrances, and resources?
-\end{quote}
-
-\hypertarget{materials-1}{%
-\subsection{Materials}\label{materials-1}}
-
 Each free-field job title was placed into one of 14 possible O*NET job families classifications.
@@
 We retained the O*NET wording to capture characteristics of relevance for each respondent.
-Subsequent to these self evaluations, each respondent who agreed that the element had \emph{at least some relevance} to their job was also asked to rate that element in terms of, 1) \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) \ldots this aspect of your job is a hinderance that can inhibit personal growth, learning, and work goal attainment.
+Subsequent to these self evaluations, each respondent who agreed that the element had \emph{at least some relevance} to their job was also asked to rate that element in terms of, 1) \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-abbas2019challenge}{}%
+Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.
+
 \leavevmode\hypertarget{ref-bakker2014job}{}%
 Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
+
+\leavevmode\hypertarget{ref-bakker2017job}{}%
+Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
 
@@
 
+\leavevmode\hypertarget{ref-crawford2010linking}{}%
+Crawford, E.
+R., LePine, J.
+A., \& Rich, B.
+L.
+(2010).
+Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test.
+\emph{Journal of Applied Psychology}, \emph{95}(5), 834.
+
 \leavevmode\hypertarget{ref-demerouti2001job}{}%
@@
 
-\leavevmode\hypertarget{ref-downes2021incorporating}{}%
-Downes, P.
-E., Reeves, C.
-J., McCormick, B.
-W., Boswell, W.
-R., \& Butts, M.
-M.
-(2021).
-Incorporating job demand variability into job demands theory: A meta-analysis.
-\emph{Journal of Management}, \emph{47}(6), 1630--1656.
-
 \leavevmode\hypertarget{ref-gerich2017relevance}{}%
@@
 Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
+
+\leavevmode\hypertarget{ref-lepine2022challenge}{}%
+LePine, M. A. (2022). The challenge-hindrance stressor framework: An integrative conceptual review and path forward. \emph{Group \& Organization Management}, \emph{47}(2), 223--254.
+
+\leavevmode\hypertarget{ref-mazzola2019should}{}%
+Mazzola, J.
+J., \& Disselhorst, R.
+(2019).
+Should we be {``challenging''} employees?: A critical review and meta-analysis of the challenge-hindrance model of stress.
+\emph{Journal of Organizational Behavior}, \emph{40}(8), 949--961.
 
@@
 
-\leavevmode\hypertarget{ref-schmitz_interpreting_2019}{}%
-Schmitz, L.
-L., McCluney, C.
-L., Sonnega, A., \& Hicken, M.
-T.
-(2019).
-Interpreting {Subjective} and {Objective} {Measures} of {Job} {Resources}: {The} {Importance} of {Sociodemographic} {Context}.
-\emph{International Journal of Environmental Research and Public Health}, \emph{16}(17), 3058.
-\url{https://doi.org/10.3390/ijerph16173058}
+\leavevmode\hypertarget{ref-rodell2009can}{}%
+Rodell, J.
+B., \& Judge, T.
+A.
+(2009).
+Can {``good''} stressors spark {``bad''} behaviors?
+The mediating role of emotions in links of challenge and hindrance stressors with citizenship and counterproductive behaviors.
+\emph{Journal of Applied Psychology}, \emph{94}(6), 1438.
 
@@
 
-\leavevmode\hypertarget{ref-sonnega_comparison_2018}{}%
-Sonnega, A., Helppie-McFall, B., Hudomiet, P., Willis, R.
-J., \& Fisher, G.
-G.
-(2018).
-A {Comparison} of {Subjective} and {Objective} {Job} {Demands} and {Fit} {With} {Personal} {Resources} as {Predictors} of {Retirement} {Timing} in a {National} {U}.{S}.
-{Sample}.
-\emph{Work, Aging and Retirement}, \emph{4}(1), 37--51.
-\url{https://doi.org/10.1093/workar/wax016}
+\leavevmode\hypertarget{ref-selye1936syndrome}{}%
+Selye, H. (1936). A syndrome produced by diverse nocuous agents. \emph{Nature}, \emph{138}(3479), 32--32.
 

### 2022-11-18 Submission.Rmd
Updating the introduction
graphs

@@
 For instance, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.
-A second study extends the findings from Study 1 to a potentially key moderator - job categories/classifications, examining whether ratings of resources, challenge- and hindrance demands differ by job classification.
 
@@
 
-# Study 2
-
 ## Materials
@@
 
-```{r scale-level-graphs, eval = FALSE}
+```{r scalelevelgraphs, fig.cap="Average characteristic rating grouped by literature-implicated categorizations."}
+
 #this is a placeholder for the scale level faceted graph found in plotscript_practice script file. 
+#Open the Submission .rmd
+#Run chunks up to the source recodes chunk (named, `generalrecodes`), and then use the data object
+#to create the ggplot
+
+library(ggplot2)
+library(plyr)
+library(dplyr)
+
+#Demands (resources ratings)
+#These are the literature-based categories, and composites - means - of Onet item ratings
+data$resources_workpressure <- rowMeans(subset(data, select = c(item120, item121)), na.rm = TRUE)
+data$resources_phyworkload_wkover <- rowMeans(subset(data, select = c(item122, item137, item138,
+                                                                      item139, item141, item142,
+                                                                      item143)), na.rm = TRUE)
+data$resources_timepressure <- rowMeans(subset(data, select = c(item125, item126)), na.rm = TRUE)
+data$resources_recipientcontact <- rowMeans(subset(data, select = c(item149, item154, item157, 
+                                                                    item160, item186, item188, 
+                                                                    item192, item197, item200, 
+                                                                    item201, item151)), na.rm = TRUE)
+data$resources_phyenvironment <- rowMeans(subset(data, select = c(item128, item129,	item130, item132,
+                                                                  item133,item134,	item136,	item144,	item146,
+                                                                  item147,	item148,	item177,	item180,
+                                                                  item182,	item181,	item183)), na.rm = TRUE)
+data$resources_emotionaldemands <- rowMeans(subset(data, select = c(item150, item155, item199)), na.rm = TRUE)
+
+#Demands (challenge ratings)
+#These are the literature-based categories, and composites - means - of Onet item ratings
+data$challenge_workpressure <- rowMeans(subset(data, select = c(item290, item291)), na.rm = TRUE)
+data$challenge_phyworkload_wkover <- rowMeans(subset(data, select = c(item292, item307, 
+                                                                      item309, item310,	item312,
+                                                                      item313,	item314)), na.rm = TRUE)
+data$challenge_timepressure <- rowMeans(subset(data, select = c(item295, item296)), na.rm = TRUE)
+data$challenge_recipientcontact <- rowMeans(subset(data, select = c(item319, item324, item327,
+                                                                    item330, item356, item358,
+                                                                    item362, item367, item370,
+                                                                    item371, item321)), na.rm = TRUE)
+data$challenge_phyenvironment <- rowMeans(subset(data, select = c(item298, item299, item300, item302,
+                                                                  item303, item304,item306, item315, item316,
+                                                                  item317, item318, item347, item350,
+                                                                  item352, item351, item353)), na.rm = TRUE)
+data$challenge_emotionaldemands <- rowMeans(subset(data, select = c(item320, item325, item369)), na.rm = TRUE)
+
+#Demands (hindrance ratings)
+#These are the literature-based categories, and composites - means - of Onet item ratings
+data$hindrance_workpressure <- rowMeans(subset(data, select = c(item205, item206)), na.rm = TRUE)
+data$hindrance_phyworkload_wkover <- rowMeans(subset(data, select = c(item207, item222,item223,
+                                                                      item224, item226, item227,
+                                                                      item228)), na.rm = TRUE)
+data$hindrance_timepressure <- rowMeans(subset(data, select = c(item210, item211)), na.rm = TRUE)
+data$hindrance_recipientcontact <- rowMeans(subset(data, select = c(item233, item238, item241, 
+                                                                    item244, item271, item273,
+                                                                    item277,	item282,	item285,
+                                                                    item286, item235)), na.rm = TRUE)
+data$hindrance_phyenvironment <- rowMeans(subset(data, select = c(item213, item214, item215, item217,
+                                                                  item218, item219, item221, item229,
+                                                                  item230,	item231,	item232,	
+                                                                  item262, item265, item267, item266,
+                                                                  item286)), na.rm = TRUE)
+data$hindrance_emotionaldemands <- rowMeans(subset(data, select = c(item234, item239, item284)), na.rm = TRUE)
+
+#Resources (resource ratings)
+#These are the literature-based categories, and composites - means - of Onet item ratings
+data$resource_jobcontrol <- rowMeans(subset(data, select = c(item124, item127)), na.rm = TRUE)
+data$resource_participation <- rowMeans(subset(data, select = c(item158, item159,
+                                                                item172,	item174, item175,
+                                                                item189, item193, item202)), na.rm = TRUE)
+data$resource_teamcohesion <- rowMeans(subset(data, select = c(item161, item190, item191)), na.rm = TRUE)
+data$resource_autonomy <- rowMeans(subset(data, select = c(item118, item172)), na.rm = TRUE)
+
+#Resources (challenge ratings)
+#These are the literature-based categories, and composites - means - of Onet item ratings
+data$challenge_jobcontrol <- rowMeans(subset(data, select = c(item294, item297)), na.rm = TRUE)
+data$challenge_participation <- rowMeans(subset(data, select = c(item328, item329, item342,
+                                                                 item344, item345, item359, item363,
+                                                                 item372)), na.rm = TRUE)
+data$challenge_teamcohesion <- rowMeans(subset(data, select = c(item331, item360, item361)), na.rm = TRUE)
+data$challenge_autonomy <- rowMeans(subset(data, select = c(item288, item342)), na.rm = TRUE)
+
+#Resources (hindrance ratings)
+#These are the literature-based categories, and composites - means - of Onet item ratings
+data$hindrance_jobcontrol <- rowMeans(subset(data, select = c(item209, item212)), na.rm = TRUE)
+data$hindrance_participation <- rowMeans(subset(data, select = c(item242, item243, item257,	item259,
+                                                                 item260,	item274,	item278,
+                                                                 item287)), na.rm = TRUE)
+data$hindrance_teamcohesion <- rowMeans(subset(data, select = c(item245, item275, item276)), na.rm = TRUE)
+data$hindrance_autonomy <- rowMeans(subset(data, select = c(item203, item257)), na.rm = TRUE)
+
+#check the autonomy variables
+summary(data$hindrance_autonomy)
+summary(data$challenge_autonomy)
+summary(data$resource_autonomy)
+library(tidyr)
+
+toplot <- gather(data, scale, value, resources_workpressure:hindrance_autonomy, factor_key=TRUE)
+
+library(stringr)
+toplot$type <- str_sub(toplot$scale, 1,6)
+toplot$onet <- str_sub(toplot$scale, 10,-1)
+
+toplot$type[toplot$type == "challe"] <- "Challenge"
+toplot$type[toplot$type == "hindra"] <- "Hindrance"
+toplot$type[toplot$type == "resour"] <- "Resource"       ## change `onet` later if want to keep graphs
+
+toplot$onet[toplot$onet == "teamcohesion"] <- "Team Cohesion"       
+toplot$onet[toplot$onet == "_teamcohesion"] <- "Team Cohesion"  
+toplot$onet[toplot$onet == "participation"] <- "Participation"       
+toplot$onet[toplot$onet == "_participation"] <- "Participation"  
+toplot$onet[toplot$onet == "jobcontrol"] <- "Job Control"       
+toplot$onet[toplot$onet == "_jobcontrol"] <- "Job Control"  
+toplot$onet[toplot$onet == "autonomy"] <- "Autonomy"       
+toplot$onet[toplot$onet == "_autonomy"] <- "Autonomy"
+
+toplot$onet[toplot$onet == "_emotionaldemands"] <- "Emotional Demands"          ## added 11/18/22 (Hudson)  
+toplot$onet[toplot$onet == "_phyenvironment"] <- "Physical Environment"  
+toplot$onet[toplot$onet == "_phyworkload_wkover"] <- "Overwork"  
+toplot$onet[toplot$onet == "_recipientcontact"] <- "Recipient Contact"  
+toplot$onet[toplot$onet == "_timepressure"] <- "Time Pressure"  
+toplot$onet[toplot$onet == "_workpressure"] <- "Work Pressure"
+
+toplotgg <- ddply(toplot, c("type", "onet"), summarise, average = mean(value, na.rm=TRUE))
+
+table(toplot$onet)
+
+## Probably want to change this to a facet: 3 different grids grouped by literature-described 1) resource, 2) hindrances, and 3) challenge
+
+toplotgg$facet <- c("Lit Resource", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Demand",
+                    "Lit Resource", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Demand",
+                    "Lit Resource", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Demand")
+
+##############################################################
+##############################################################
+################    Plots
+
+demandsplot <- filter(toplotgg, facet == "Lit Demand")
+resourcesplot <- filter(toplotgg, facet == "Lit Resource")
+
+## Demands
+
+demandsplot$onet <- factor(demandsplot$onet, levels=c("Work Pressure", "Recipient Contact", "Emotional Demands", "Time Pressure", "Physical Environment", "Overwork"))
+
+a <- ggplot(data=demandsplot, aes(x=onet, y=average, fill=type)) + 
+  geom_bar(stat="identity", position=position_dodge(), color="black") + coord_flip(ylim=c(1,5)) + scale_fill_manual(values=c("#000000","#cccccc","#ffffff")) +
+  scale_x_discrete(labels=function(x){sub("\\s", "\n", x)}) +
+  theme(legend.title=element_blank(), legend.position="none",  panel.border = element_rect(colour = "black", fill=NA, size=.5), axis.title.x = element_blank(), axis.title.y = element_blank())
+
+## Resources
+
+resourcesplot$onet <- factor(resourcesplot$onet, levels=c("Team Cohesion", "Autonomy", "Participation", "Job Control"))
+
+b <- ggplot(data=resourcesplot, aes(x=onet, y=average, fill=type)) + 
+  geom_bar(stat="identity", position=position_dodge(), color="black") + coord_flip(ylim=c(1,5)) + scale_fill_manual(values=c("#000000","#cccccc","#ffffff")) +
+  scale_x_discrete(labels=function(x){sub("\\s", "\n", x)}) +
+  theme(legend.title=element_blank(), legend.position="bottom",  panel.border = element_rect(colour = "black", fill=NA, size=.5), axis.title.x = element_blank(), axis.title.y = element_blank())
+
+################################################################
+################################################################
+################################################################
+
+library("gridExtra")
+grid.arrange(a, b, ncol = 2, nrow = 1)
+
 ```
+
+see Figure \@ref(fig:scalelevelgraphs)
 

### 2022-11-18 Submission.tex
graphs

@@
 \date{}
+
+\shorttitle{O*NET JD-R}
 
@@
 
-\abstract{
+\abstract{%
 O*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource.
@@
 
-Although there is a tendency to attach a negative connotation to the word ``stress,'' Selye (1936) defined stress as a response to change, which is quite non-specific.
+Although there is a tendency to attach a negative connotation to the word ``stress'', Selye (1936) defined stress as a response to change, which is quite non-specific.
 We return to the employed public figure for this next section.
@@
 In fact, there was a call to work with experienced I/O psychologists over the summer to update the content for the \href{https://www.onetonline.org/link/summary/19-3032.00}{Industrial and Organizational Psychologist listing on O*Net}.
-These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move for Veterans,'' ``My Next Move,'' Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
+These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move for Veterans'', ``My Next Move'', Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
 It is also useful to employers by providing them with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
@@
 
+\begin{verbatim}
+##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max.    NA's 
+##   1.000   1.000   2.000   2.185   3.000   5.000       7
+\end{verbatim}
+
+\begin{verbatim}
+##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max.    NA's 
+##   1.000   4.000   4.500   4.202   5.000   5.000       7
+\end{verbatim}
+
+\begin{verbatim}
+##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max.    NA's 
+##   1.000   4.000   4.500   4.205   5.000   5.000       7
+\end{verbatim}
+
+\begin{verbatim}
+## 
+##             Autonomy    Emotional Demands          Job Control 
+##                 1704                 1704                 1704 
+##             Overwork        Participation Physical Environment 
+##                 1704                 1704                 1704 
+##    Recipient Contact        Team Cohesion        Time Pressure 
+##                 1704                 1704                 1704 
+##        Work Pressure 
+##                 1704
+\end{verbatim}
+
+\begin{figure}
+\centering
+\includegraphics{Submission_files/figure-latex/scalelevelgraphs-1.pdf}
+\caption{\label{fig:scalelevelgraphs}Average characteristic rating grouped by literature-implicated categorizations.}
+\end{figure}
+
+see Figure \ref{fig:scalelevelgraphs}
+
 \newpage
@@
 
-\leavevmode\hypertarget{ref-gerich2017relevance}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
 Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
 
-\leavevmode\hypertarget{ref-landis1977measurement}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-landis1977measurement}{}}%
 Landis, J. R., \& Koch, G. G. (1977). The measurement of observer agreement for categorical data. \emph{Biometrics}, 159--174.
 
-\leavevmode\hypertarget{ref-lazarus1984stress}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
 Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
 
-\leavevmode\hypertarget{ref-lepine2022challenge}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lepine2022challenge}{}}%
 LePine, M. A. (2022). The challenge-hindrance stressor framework: An integrative conceptual review and path forward. \emph{Group \& Organization Management}, \emph{47}(2), 223--254.
 
-\leavevmode\hypertarget{ref-mazzola2019should}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-mazzola2019should}{}}%
 Mazzola, J.
@@
 
-\leavevmode\hypertarget{ref-peterson2001understanding}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
 Peterson, N.
@@
 
-\leavevmode\hypertarget{ref-rodell2009can}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-rodell2009can}{}}%
 Rodell, J.
@@
 
-\leavevmode\hypertarget{ref-searle2015merits}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-searle2015merits}{}}%
 Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.
 
-\leavevmode\hypertarget{ref-selye1936syndrome}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-selye1936syndrome}{}}%
 Selye, H. (1936). A syndrome produced by diverse nocuous agents. \emph{Nature}, \emph{138}(3479), 32--32.
 
-\leavevmode\hypertarget{ref-webster2011extending}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
 Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.
 
-\leavevmode\hypertarget{ref-R-careless}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-careless}{}}%
 Yentes, R. D., \& Wilhelm, F. (2021). \emph{Careless: Procedures for computing indices of careless responding}.

### 2022-11-18 plotscript_practice.R

@@ -110,28 +110,53 @@ toplot$onet[toplot$onet == "_jobcontrol"] <- "Job Control"
 toplot$onet[toplot$onet == "autonomy"] <- "Autonomy"       
 toplot$onet[toplot$onet == "_autonomy"] <- "Autonomy"  
 
+toplot$onet[toplot$onet == "_emotionaldemands"] <- "Emotional Demands"          ## added 11/18/22 (Hudson)  
+toplot$onet[toplot$onet == "_phyenvironment"] <- "Physical Environment"  
+toplot$onet[toplot$onet == "_phyworkload_wkover"] <- "Overwork"  
+toplot$onet[toplot$onet == "_recipientcontact"] <- "Recipient Contact"  
+toplot$onet[toplot$onet == "_timepressure"] <- "Time Pressure"  
+toplot$onet[toplot$onet == "_workpressure"] <- "Work Pressure"  
+
 toplotgg <- ddply(toplot, c("type", "onet"), summarise, average = mean(value, na.rm=TRUE))
 
 table(toplot$onet)
 
-ggplot(data=toplotgg, aes(x=onet, y=average, fill=type)) + 
-  geom_bar(stat="identity", position=position_dodge()) + coord_flip()
-
 ## Probably want to change this to a facet: 3 different grids grouped by literature-described 1) resource, 2) hindrances, and 3) challenge
 
-toplotgg$facet <- c("d", "d", "d", "d", "d", "d", "r", "r", "r", "r",
-                    "d", "d", "d", "d", "d", "d", "r", "r", "r", "r",
-                    "d", "d", "d", "d", "d", "d", "r", "r", "r", "r")
+toplotgg$facet <- c("Lit Resource", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Demand",
+                    "Lit Resource", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Demand",
+                    "Lit Resource", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Demand", "Lit Resource", "Lit Demand", "Lit Demand")
 
-ggplot(data=toplotgg, aes(x=onet, y=average, fill=type)) + 
[…]

### 2022-12-02 Submission.Rmd
Updating content of introduction

@@
     email         : "stachowskia@uwstout.edu"
-  - name          : "Renata Garcia Prieto Palacios Roji"
-    affiliation   : "2"
   - name          : "John Kulas"
     affiliation   : "2"
+  - name          : "Renata Garcia Prieto Palacios Roji"
+    affiliation   : "3"
 
@@
   - id            : "2"
-    institution   : "Montclair State University"
+    institution   : "eRg"
+   - id            : "3"
+    institution   : "PepsiCo"
 
@@
 
-Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlight the importance of work characteristics on the experience of motivation and strain, which clearly have an impact on job performance.
-In light of some of the recent debate surrounding the challenge-hindrance stressor framework [e.g., @mazzola2019should], we extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, and how they relate to two important organizational outcomes: engagement and stress.
+Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlight the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance.
+However, much of our existing knowledge of the way this model functions is grounded in the assumption that characteristics are generally considered resources or generally considered demands.
+We build on the research of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands (@webster2011extending) or that appraisals may change over time (CITE HERE).
+We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, which a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
 Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.
@@
 
-As implied in the last paragraph, job context and characteristics are “assigned” or appraised as demands or resources.
-Although some research on job demands in particular is based on apriori classifications of demands [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand.
+As implied in the last paragraph, job context and characteristics are assigned or appraised as demands or resources.
+Although much of our research on job demands in particular is based on apriori classifications of demands [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand.
 The stress process speaks to how such individual difference in appraisal is possible.
 @lazarus1984stress presented the transactional theory of stress and coping, which states that people cognitively appraise stimuli in their environments on a continuous basis.
-Via this process, meaning is assigned to stimuli – if appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping.
+Via this process, meaning is assigned to stimuli based on potential for gain or loss.
+If appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping.
 The cycle of appraisal then continues based on the action to cope with the stressor [@lazarus1984stress].
@@
 In fact, @bakker2017job call attention to different types of demands in their recent review of, and future directions, for work on the job-demands resources theory.
+
 The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor (@cavanaugh2000empirical).
@@
 Stressors like time pressure and responsibility are considered challenge stressors/demands.
-hindrance demands, in contrast, inhibit growth, learning and goal achievement.
+Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
 Hindrance stressors (e.g., role conflict, role ambiguity, politics) are associated with negative job behaviors and attitudes.
@@
 However, one of the key questions we need to ask as researchers pertains to the very basic consideration of appraisals.
-In fact, this is one of several issues raised by @ mazzola2019should in a recent review and meta-analysis of this framework.
+In fact, this is one of several issues raised by @mazzola2019should in a recent review and meta-analysis of this framework.
 These authors cited the apriori assignment to stressors as a challenge or hindrance as a flawed assumption, suggesting that stressors are more likely to be a combination of both – challenge and hindrance appraisals.
@@
 The opposite pattern of relationship was observed for hindrance stressors.
-@ kim2020thriving, similarly, found evidence for the differential results via challenge and hindrance appraisals
+@kim2020thriving, similarly, found evidence for the differential results via challenge and hindrance appraisals.
 

### 2022-12-02 Submission.tex
Updating content of introduction

--- 2022-11-18 Submission.tex
@@
 \includegraphics{Submission_files/figure-latex/hindranceshighsd-1.pdf}
+
+\begin{verbatim}
+##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max.    NA's 
+##   1.000   1.000   2.000   2.185   3.000   5.000       7
+\end{verbatim}
+
+\begin{verbatim}
+##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max.    NA's 
+##   1.000   4.000   4.500   4.202   5.000   5.000       7
+\end{verbatim}
+
+\begin{verbatim}
+##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max.    NA's 
+##   1.000   4.000   4.500   4.205   5.000   5.000       7
+\end{verbatim}
+
+\begin{verbatim}
+## 
+##             Autonomy    Emotional Demands          Job Control 
+##                 1704                 1704                 1704 
+##             Overwork        Participation Physical Environment 
+##                 1704                 1704                 1704 
+##    Recipient Contact        Team Cohesion        Time Pressure 
+##                 1704                 1704                 1704 
+##        Work Pressure 
+##                 1704
+\end{verbatim}
+
+\begin{figure}
+\centering
+\includegraphics{Submission_files/figure-latex/scalelevelgraphs-1.pdf}
+\caption{\label{fig:scalelevelgraphs}Average characteristic rating grouped by literature-implicated categorizations.}
+\end{figure}
+
+see Figure \ref{fig:scalelevelgraphs}
 

### 2022-12-02 Submission.tex
Fixed the YAML

@@
   pdftitle={Job Demands-Resources model components through the lens of O*NET classifications},
-  pdfauthor={Alicia Stachowski1, Renata Garcia Prieto Palacios Roji2, \& John Kulas2},
+  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
   pdflang={en-EN},
@@
 \title{Job Demands-Resources model components through the lens of O*NET classifications}
-\author{Alicia Stachowski\textsuperscript{1}, Renata Garcia Prieto Palacios Roji\textsuperscript{2}, \& John Kulas\textsuperscript{2}}
+\author{Alicia Stachowski\textsuperscript{1}, John Kulas\textsuperscript{2}, \& Renata Garcia Prieto Palacios Roji\textsuperscript{3}}
 \date{}
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Wisconsin - Stout\\\textsuperscript{2} Montclair State University}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Wisconsin - Stout\\\textsuperscript{2} eRg\\\textsuperscript{3} PepsiCo}
 
@@
 B.
-Bakker \& Demerouti, 2017) highlight the importance of work characteristics on the experience of motivation and strain, which clearly have an impact on job performance.
-In light of some of the recent debate surrounding the challenge-hindrance stressor framework (e.g., Mazzola \& Disselhorst, 2019), we extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, and how they relate to two important organizational outcomes: engagement and stress.
+Bakker \& Demerouti, 2017) highlight the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance.
+However, much of our existing knowledge of the way this model functions is grounded in the assumption that characteristics are generally considered resources or generally considered demands.
+We build on the research of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands (Webster et al.
+(2011)) or that appraisals may change over time (CITE HERE).
+We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, which a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
 Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.
@@
 
-As implied in the last paragraph, job context and characteristics are ``assigned'' or appraised as demands or resources.
-Although some research on job demands in particular is based on apriori classifications of demands (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand.
+As implied in the last paragraph, job context and characteristics are assigned or appraised as demands or resources.
+Although much of our research on job demands in particular is based on apriori classifications of demands (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand.
 The stress process speaks to how such individual difference in appraisal is possible.
 Lazarus and Folkman (1984) presented the transactional theory of stress and coping, which states that people cognitively appraise stimuli in their environments on a continuous basis.
-Via this process, meaning is assigned to stimuli -- if appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping.
+Via this process, meaning is assigned to stimuli based on potential for gain or loss.
+If appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping.
 The cycle of appraisal then continues based on the action to cope with the stressor (Lazarus \& Folkman, 1984).
@@
 Bakker and Demerouti (2017) call attention to different types of demands in their recent review of, and future directions, for work on the job-demands resources theory.
+
 The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor (Cavanaugh et al.
@@
 However, one of the key questions we need to ask as researchers pertains to the very basic consideration of appraisals.
-In fact, this is one of several issues raised by @ mazzola2019should in a recent review and meta-analysis of this framework.
+In fact, this is one of several issues raised by Mazzola and Disselhorst (2019) in a recent review and meta-analysis of this framework.
 These authors cited the apriori assignment to stressors as a challenge or hindrance as a flawed assumption, suggesting that stressors are more likely to be a combination of both -- challenge and hindrance appraisals.
@@
 The opposite pattern of relationship was observed for hindrance stressors.
-@ kim2020thriving, similarly, found evidence for the differential results via challenge and hindrance appraisals
+Kim and Beehr (2020), similarly, found evidence for the differential results via challenge and hindrance appraisals.
 
@@
 
+\leavevmode\hypertarget{ref-kim2020thriving}{}%
+Kim, M., \& Beehr, T.
+A.
+(2020).
+Thriving on demand: Challenging work results in employee flourishing through appraisals and resources.
+\emph{International Journal of Stress Management}, \emph{27}(2), 111.
+
 \leavevmode\hypertarget{ref-landis1977measurement}{}%

### 2022-12-02 Submission.Rmd
Fixed the YAML
formatting mostly

@@
 
-We used 98 statements taken from O\*NET ["activity" and "context" classifications](https://www.O\*NETonline.org/find/descriptor/result/4.A.1.b.3).
+We used 98 statements taken from O\*NET ["activity" and "context" classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3).
 We retained 41 "work activity" classifications which O\*NET groups into categories of "Information Input" (5 statements), "Interacting with Others" (17 statements), "Mental Processes" (10 statements) and "Work Output" (9 statements).
@@
 
-These "descriptors" often have unique response categories ([see here for example](https://www.O\*NETonline.org/find/descriptor/result/4.C.1.c.2)).
+These "descriptors" often have unique response categories ([see here for example](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2)).
 We retained the O\*NET wording to capture characteristics of relevance for each respondent.
@@
 
-The below graphs present the resources, challenges, and hindrances that are *largely agreed on* as indexed by (relatively) low standard deviations.
-
-> Note. The "zero" standard deviations are likely one person, *n*'s should also go on these graphs if they're retained.
-
-```{r resourceslowsd}
+```{r resourcesagree, fig.cap="Characteristics most similarly viewed as resources (lowest standard deviations)."}
 
@@
 
-```{r challengesagree}
+```{r challengesagree, fig.cap="Characteristics most similarly viewed as challenges (lowest standard deviations)."}
 
@@
 
-```{r hindrancesagree}
+```{r hindrancesagree, fig.cap="Characteristics most similarly viewed as hindrances (lowest standard deviations)."}
 
@@
 
+Figures \@ref(fig:resourcesagree), \@ref(fig:challengesagree), and \@ref(fig:hindrancesagree) present the resources, challenges, and hindrances that are *largely agreed on* as indexed by (relatively) low standard deviations.[^caveat]
+
+[^caveat]: There were a few characteristics with standard deviations of "zero" but these were excluded from presenation as they were likely representing only one person (*n*'s should also go on these graphs if they're retained - Alicia's idea 12/2 was to use initial ratings as indicators of counts).
+
 As can be seen by the graphs, there is considerable disagreement regarding the degree to which job elements are considered *hindrances*, with the 10 elements showing the greatest agreement still ranging in standard deviations from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`.
@@
 
-The below graphs present the resources, challenges, and hindrances that are *largely disagreed on* as indexed by (relatively) high standard deviations (these are the 10 characteristics with the greatest variability in rating).
-
-```{r resourceshisd}
+```{r resourcesdisagree, fig.cap="Characteristics most *dis*similarly viewed as resources (highest standard deviations)."}
 
@@
 
-```{r challengeshighsd}
+```{r challengesdisagree, fig.cap="Characteristics most *dis*similarly viewed as challenges (highest standard deviations)."}
 
@@
 
-```{r hindranceshighsd}
+```{r hindrancesdisagree, fig.cap="Characteristics most *dis*similarly viewed as hindrances (highest standard deviations)."}
 
@@
 ```
+
+Figures \@ref(fig:resourcesdisagree), \@ref(fig:challengesdisagree), and \@ref(fig:hindrancesdisagree) present the resources, challenges, and hindrances that are *largely disagreed on* as indexed by (relatively) high standard deviations (these are the 10 characteristics with the greatest variability in rating).
 
@@
 #check the autonomy variables
-summary(data$hindrance_autonomy)
-summary(data$challenge_autonomy)
-summary(data$resource_autonomy)
+#summary(data$hindrance_autonomy)
+#summary(data$challenge_autonomy)
+#summary(data$resource_autonomy)
+
 library(tidyr)
@@
 
-table(toplot$onet)
+#table(toplot$onet)
 
@@
 
+# Discussion
+
+## Future directions
+
+There may be some practical utility to pursue training interventions aimed at *how* characteristics are appraised.
+Perhaps the clinical literature may be informative - for example, within cognitive behavioral therapeutic applications, the way in which situations are appraised can be a mechanism to help battle affective disorders such as depression.[^check] Given the current findings, where the same characteristic may be viewed similarly as both a demand and resource, it is possible that framing interventions may ameliorate negative outcomes of demands such as, for example, stress or strain.
+
+[^check]: Check on this - this is just speculative place-holding from 12/2 Hudson coffee discussion
+
+\newpage
+
 # References

### 2022-12-02 Submission.tex
formatting mostly

--- 2022-11-18 Submission.tex
@@
 
-We used 98 statements taken from O*NET \href{https://www.O*NETonline.org/find/descriptor/result/4.A.1.b.3}{``activity'' and ``context'' classifications}.
+We used 98 statements taken from O*NET \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{``activity'' and ``context'' classifications}.
 We retained 41 ``work activity'' classifications which O*NET groups into categories of ``Information Input'' (5 statements), ``Interacting with Others'' (17 statements), ``Mental Processes'' (10 statements) and ``Work Output'' (9 statements).
@@
 
-These ``descriptors'' often have unique response categories (\href{https://www.O*NETonline.org/find/descriptor/result/4.C.1.c.2}{see here for example}).
+These ``descriptors'' often have unique response categories (\href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{see here for example}).
 We retained the O*NET wording to capture characteristics of relevance for each respondent.
@@
 
-The below graphs present the resources, challenges, and hindrances that are \emph{largely agreed on} as indexed by (relatively) low standard deviations.
+\begin{figure}
+\centering
+\includegraphics{Submission_files/figure-latex/resourcesagree-1.pdf}
+\caption{\label{fig:resourcesagree}Characteristics most similarly viewed as resources (lowest standard deviations).}
+\end{figure}
 
-\begin{quote}
-Note. The ``zero'' standard deviations are likely one person, \emph{n}'s should also go on these graphs if they're retained.
-\end{quote}
+\begin{figure}
+\centering
+\includegraphics{Submission_files/figure-latex/challengesagree-1.pdf}
+\caption{\label{fig:challengesagree}Characteristics most similarly viewed as challenges (lowest standard deviations).}
+\end{figure}
 
-\includegraphics{Submission_files/figure-latex/resourceslowsd-1.pdf}
+\begin{figure}
+\centering
+\includegraphics{Submission_files/figure-latex/hindrancesagree-1.pdf}
+\caption{\label{fig:hindrancesagree}Characteristics most similarly viewed as hindrances (lowest standard deviations).}
+\end{figure}
 
-\includegraphics{Submission_files/figure-latex/challengesagree-1.pdf}
-
-\includegraphics{Submission_files/figure-latex/hindrancesagree-1.pdf}
+Figures \ref{fig:resourcesagree}, \ref{fig:challengesagree}, and \ref{fig:hindrancesagree} present the resources, challenges, and hindrances that are \emph{largely agreed on} as indexed by (relatively) low standard deviations.\footnote{There were a few characteristics with standard deviations of ``zero'' but these were excluded from presenation as they were likely representing only one person (\emph{n}'s should also go on these graphs if they're retained - Alicia's idea 12/2 was to use initial ratings as indicators of counts).}
 
@@
 
-The below graphs present the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations (these are the 10 characteristics with the greatest variability in rating).
+\begin{figure}
+\centering
+\includegraphics{Submission_files/figure-latex/resourcesdisagree-1.pdf}
+\caption{\label{fig:resourcesdisagree}Characteristics most \emph{dis}similarly viewed as resources (highest standard deviations).}
+\end{figure}
 
-\includegraphics{Submission_files/figure-latex/resourceshisd-1.pdf}
+\begin{figure}
+\centering
+\includegraphics{Submission_files/figure-latex/challengesdisagree-1.pdf}
+\caption{\label{fig:challengesdisagree}Characteristics most \emph{dis}similarly viewed as challenges (highest standard deviations).}
+\end{figure}
 
-\includegraphics{Submission_files/figure-latex/challengeshighsd-1.pdf}
+\begin{figure}
+\centering
+\includegraphics{Submission_files/figure-latex/hindrancesdisagree-1.pdf}
+\caption{\label{fig:hindrancesdisagree}Characteristics most \emph{dis}similarly viewed as hindrances (highest standard deviations).}
+\end{figure}
 
-\includegraphics{Submission_files/figure-latex/hindranceshighsd-1.pdf}
-
-\begin{verbatim}
-##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max.    NA's 
-##   1.000   1.000   2.000   2.185   3.000   5.000       7
-\end{verbatim}
-
-\begin{verbatim}
-##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max.    NA's 
-##   1.000   4.000   4.500   4.202   5.000   5.000       7
-\end{verbatim}
-
-\begin{verbatim}
-##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max.    NA's 
-##   1.000   4.000   4.500   4.205   5.000   5.000       7
-\end{verbatim}
-
-\begin{verbatim}
-## 
-##             Autonomy    Emotional Demands          Job Control 
-##                 1704                 1704                 1704 
-##             Overwork        Participation Physical Environment 
-##                 1704                 1704                 1704 
-##    Recipient Contact        Team Cohesion        Time Pressure 
-##                 1704                 1704                 1704 
-##        Work Pressure 
-##                 1704
-\end{verbatim}
+Figures \ref{fig:resourcesdisagree}, \ref{fig:challengesdisagree}, and \ref{fig:hindrancesdisagree} present the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations (these are the 10 characteristics with the greatest variability in rating).
 
@@
 see Figure \ref{fig:scalelevelgraphs}
+
+\newpage
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+\hypertarget{future-directions}{%
+\subsection{Future directions}\label{future-directions}}
+
+There may be some practical utility to pursue training interventions aimed at \emph{how} characteristics are appraised.
+Perhaps the clinical literature may be informative - for example, within cognitive behavioral therapeutic applications, the way in which situations are appraised can be a mechanism to help battle affective disorders such as depression.\footnote{Check on this - this is just speculative place-holding from 12/2 Hudson coffee discussion} Given the current findings, where the same characteristic may be viewed similarly as both a demand and resource, it is possible that framing interventions may ameliorate negative outcomes of demands such as, for example, stress or strain.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-kim2020thriving}{}}%
+Kim, M., \& Beehr, T.
+A.
+(2020).
+Thriving on demand: Challenging work results in employee flourishing through appraisals and resources.
+\emph{International Journal of Stress Management}, \emph{27}(2), 111.
+
 \leavevmode\vadjust pre{\hypertarget{ref-landis1977measurement}{}}%

### 2022-12-03 plotscript_practice.R
looking for n's

@@ -160,3 +160,8 @@ b <- ggplot(data=resourcesplot, aes(x=onet, y=average, fill=type)) +
 
 library("gridExtra")
 grid.arrange(a, b, ncol = 2, nrow = 1)
+
+#I am still thinking about which variables we want n's for, but
+#this might work.
+library(Hmisc)
+describe(data)

### 2022-12-03 Submission.Rmd
Updated Introduction

@@
 All the results of this current study match the stress-appraisal stuff.
-Next steps: 1) discuss results within stress-appraisal framework (Lazarus & Bookman), 2) different literature on challenge and hindrance demands.
+Next steps: 1) discuss results within stress-appraisal framework [@lazarus1984stress], 2) different literature on challenge and hindrance demands.
 Job Demands Resources theory that says resources and demands are relatively universal is NOT consistent with these findings.
@@
 However, much of our existing knowledge of the way this model functions is grounded in the assumption that characteristics are generally considered resources or generally considered demands.
-We build on the research of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands (@webster2011extending) or that appraisals may change over time (CITE HERE).
+We build on the research of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands (@webster2011extending) or that appraisals may change over time (@rosen2020challenges).
 We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, which a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
@@
 In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; @demerouti2001job).
-
 Cognitively, the perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources) [@bakker2014job].
-Pertinent to the current study, demanding job characteristics are frequently often associated with negative outcomes [e.g., @bakker2003dual], whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job].
+Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience depsite the typical apriori assignment of a characteristic as objectively a "demand" or "resource".
+We explore this further below.
 
@@
 
-As implied in the last paragraph, job context and characteristics are assigned or appraised as demands or resources.
+As described in the last paragraph, job context and characteristics are assigned or appraised as demands or resources.
 Although much of our research on job demands in particular is based on apriori classifications of demands [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand.
@@
 The cycle of appraisal then continues based on the action to cope with the stressor [@lazarus1984stress].
+Coping is considered a secondary appraisal and is the way that someone chooses to manage a stressor should an event or situation be deemed so.
+Although not suggested by the names, primary and secondary appraisals can happen simultaneously.
+For instance, available resources to cope with a stressor may influence an employee’s initial appraisal of a stressor (e.g., amount of time [resource] available to prepare for the speech may influence one’s primary appraisal of this ask).
 
@@
 Hindrance stressors (e.g., role conflict, role ambiguity, politics) are associated with negative job behaviors and attitudes.
-This particular distinction between challenges and hindrances has been of value in determining what demands are related to various outcomes, whereby challenge stressors are typically associated with positive outcomes, and hindrance stressors, negative outcomes (e.g., @cavanaugh2000empirical).
+This distinction between challenges and hindrances has been of value in determining which demands are related to various outcomes.
+The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes (e.g., @cavanaugh2000empirical).
 
-However, one of the key questions we need to ask as researchers pertains to the very basic consideration of appraisals.
-In fact, this is one of several issues raised by @mazzola2019should in a recent review and meta-analysis of this framework.
-These authors cited the apriori assignment to stressors as a challenge or hindrance as a flawed assumption, suggesting that stressors are more likely to be a combination of both – challenge and hindrance appraisals.
-@lepine2022challenge, in a rebuttal to the @ mazzola2019should criticism, while acknowledging that the original challenge-hindrance stressor framework was based on the assertion that people tend to appraise specific work stressors ad challenges and other demands, noted that the appraisals likely served as a mediator.
+Prior to considering the subsequent empirical work done on this topic, it is of value to explore *why* there is expected to be different outcomes associated with these forms of demands.
+@lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes.
+Similar to the job-demands resources theory [@bakker2017job], challenge and hindrance demands elicit two different paths or processes.
+First, challenge stressors typically result in a challenge appraisal, and both engagement is likely to happen as a result.
+Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing.
+The other side of the coin is that this energy may be depleted eventually, leading to strain.
+Hindrance stressors elicit a different process.
+Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing.
+This happens because resources are depleted via frustrations and other affectively negative reactions [@lepine2022challenge].
 
 We next consider the empirical evidence on this topic.
-The first obvious question is whether people perceive demands as challenges vs.
+The broadest, and perhaps first question, we should ask is whether people perceive demands as challenges vs.
 hindrances, or whether all demands are under a larger “demands” category.
@@
 They found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees.
+@kim2020thriving found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing.
+The opposite occurred when a demand was appraised as a hindrance – in those instances, the appraisal had a negative association with motivational resources.
 
-While their study did include resources, it nonetheless points to the possibility that demands might be differentially appraised and related to outcomes [e.g., @podsakoff2007differential].
-The challenge-hindrance framework has, in fact, been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and well-being.
+Having evidence that people can make a distinction between challenge and hindrance stressors, the next logical question is whether they do relate differentially to outcomes.
+The challenge-hindrance stressor framework has, in fact, been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and well-being.
 A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic.
 For example, @cavanaugh2000empirical, in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern.
+@chen2021daily found that daily challenge demands were positively related to cognitive wellbeing and work-family enrichment.
+Daily hindrance demands were negatively related to these outcomes.
 In contrast, @abbas2019challenge found that challenge and hindrance stressors were *both* positively related to strain and turnover intentions.
@@
 
-We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point.
-@podsakoff2007differential supported the original assertion of @cavanaugh2000empirical with regard to work outcomes such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover.
-The opposite pattern of relationship was observed for hindrance stressors.
+We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point, and a rich collection of them support differential associations across a variety of organizational outcomes.
+For example, both challenges and hindrances have been shown to positively predict strain (@lepine2005meta; @podsakoff2007differential; @webster2010toward).
+Many other outcomes are differentially related to challenges and hindrances, largely in the expected direction.
+For example, motivation, job satisfaction, commitment, and performance have been shown to positively relate to challenge stressors and negatively relate to hindrance stressor [@lepine2005meta].
+Turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance stressors [@podsakoff2007differential].
 @kim2020thriving, similarly, found evidence for the differential results via challenge and hindrance appraisals.
+
+@horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process described by @lazarus1984stress into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources into our study of the overarching JD-R model.
+In fact, @horan2020review state that “…stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p.
+3).
+In fact, @horan2020review suggest future research continue to move away from apriori classifications of stressors, as doing so can be problematic for theoretical and empirical reasons.
+Theoretically, apriori classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
+Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time (e.g., @searle2015merits).
+TRANSITION?
 
@@
 
+##Current Study and Hypotheses
+
 Of greatest interest here are statements taken from O\*NET ["activity" and "context" classifications](https://www.O\*NETonline.org/find/descriptor/result/4.A.1.b.3) (e.g., items related to information input, interacting with others, physical work conditions, structural job characteristics).
@@
 
-Add a description here of the exploratory stuff.
+Lastly, we propose three research that explicitly address a topic hinted at in the literature review above.
+Although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, there remains variability in these appraisals [@lepine2022challenge].
+@lepine2022challenge, in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal.
+We explore whether literature-implicated job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory [@bakker2017job]and challenge-hindrance stressor framework [@cavanaugh2000empirical].
 
@@
 
+So, what can be done about the findings that people experience both?
+@lepine2005meta and @podsakoff2007differential encourage organizations to incorporate strain-reducing activities like train and support to offset the negative effects of challenging job demands.
+
 There may be some practical utility to pursue training interventions aimed at *how* characteristics are appraised.

### 2022-12-03 Submission.tex
Updated Introduction

--- 2022-12-02 Submission.tex
@@
 All the results of this current study match the stress-appraisal stuff.
-Next steps: 1) discuss results within stress-appraisal framework (Lazarus \& Bookman), 2) different literature on challenge and hindrance demands.
+Next steps: 1) discuss results within stress-appraisal framework (Lazarus \& Folkman, 1984), 2) different literature on challenge and hindrance demands.
 Job Demands Resources theory that says resources and demands are relatively universal is NOT consistent with these findings.
@@
 
-Research on the job demands-resources model (Demerouti et al., 2001) and later job demands-resources theory (A.
-B.
-Bakker \& Demerouti, 2017) highlight the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance.
+Research on the job demands-resources model (Demerouti et al., 2001) and later job demands-resources theory (Bakker \& Demerouti, 2017) highlight the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance.
 However, much of our existing knowledge of the way this model functions is grounded in the assumption that characteristics are generally considered resources or generally considered demands.
 We build on the research of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands (Webster et al.
-(2011)) or that appraisals may change over time (CITE HERE).
+(2011)) or that appraisals may change over time ((\textbf{rosen2020challenges?})).
 We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, which a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
@@
 (2001)).
-
-Cognitively, the perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources) (A.
-B.
-Bakker \& Demerouti, 2014).
-Pertinent to the current study, demanding job characteristics are frequently often associated with negative outcomes (e.g., A.
-Bakker et al., 2003), whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation (A.
-B.
-Bakker et al., 2007).
+Cognitively, the perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources) (Bakker \& Demerouti, 2014).
+Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience depsite the typical apriori assignment of a characteristic as objectively a ``demand'' or ``resource.'' We explore this further below.
 
@@
 
-As implied in the last paragraph, job context and characteristics are assigned or appraised as demands or resources.
+As described in the last paragraph, job context and characteristics are assigned or appraised as demands or resources.
 Although much of our research on job demands in particular is based on apriori classifications of demands (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand.
@@
 The cycle of appraisal then continues based on the action to cope with the stressor (Lazarus \& Folkman, 1984).
+Coping is considered a secondary appraisal and is the way that someone chooses to manage a stressor should an event or situation be deemed so.
+Although not suggested by the names, primary and secondary appraisals can happen simultaneously.
+For instance, available resources to cope with a stressor may influence an employee's initial appraisal of a stressor (e.g., amount of time {[}resource{]} available to prepare for the speech may influence one's primary appraisal of this ask).
 
@@
 One may appraise the circumstance as an opportunity to positively influence others, while the other may plausibly feel paralyzed by the task.
-In fact, A.
-B.
-Bakker and Demerouti (2017) call attention to different types of demands in their recent review of, and future directions, for work on the job-demands resources theory.
+In fact, Bakker and Demerouti (2017) call attention to different types of demands in their recent review of, and future directions, for work on the job-demands resources theory.
 
@@
 Hindrance stressors (e.g., role conflict, role ambiguity, politics) are associated with negative job behaviors and attitudes.
-This particular distinction between challenges and hindrances has been of value in determining what demands are related to various outcomes, whereby challenge stressors are typically associated with positive outcomes, and hindrance stressors, negative outcomes (e.g., Cavanaugh et al.
+This distinction between challenges and hindrances has been of value in determining which demands are related to various outcomes.
+The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes (e.g., Cavanaugh et al.
 (2000)).
 
-However, one of the key questions we need to ask as researchers pertains to the very basic consideration of appraisals.
-In fact, this is one of several issues raised by Mazzola and Disselhorst (2019) in a recent review and meta-analysis of this framework.
-These authors cited the apriori assignment to stressors as a challenge or hindrance as a flawed assumption, suggesting that stressors are more likely to be a combination of both -- challenge and hindrance appraisals.
-LePine (2022), in a rebuttal to the @ mazzola2019should criticism, while acknowledging that the original challenge-hindrance stressor framework was based on the assertion that people tend to appraise specific work stressors ad challenges and other demands, noted that the appraisals likely served as a mediator.
+Prior to considering the subsequent empirical work done on this topic, it is of value to explore \emph{why} there is expected to be different outcomes associated with these forms of demands.
+M.
+A.
+LePine (2022) explain the mechanisms by which demands are related to performance and wellbeing outcomes.
+Similar to the job-demands resources theory (Bakker \& Demerouti, 2017), challenge and hindrance demands elicit two different paths or processes.
+First, challenge stressors typically result in a challenge appraisal, and both engagement is likely to happen as a result.
+Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing.
+The other side of the coin is that this energy may be depleted eventually, leading to strain.
+Hindrance stressors elicit a different process.
+Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing.
+This happens because resources are depleted via frustrations and other affectively negative reactions (M.
+A.
+LePine, 2022).
 
 We next consider the empirical evidence on this topic.
-The first obvious question is whether people perceive demands as challenges vs.~hindrances, or whether all demands are under a larger ``demands'' category.
-Evidence suggests the employees do, in fact, distinguish between challenge and hindrance stressors (e.g., A.
-B.
-Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011).
-For example, A.
-B.
-Bakker and Sanz-Vergel (2013) found that perceived work pressure as a hindrance demand, and emotional demands as more of a challenge demand.
+The broadest, and perhaps first question, we should ask is whether people perceive demands as challenges vs.~hindrances, or whether all demands are under a larger ``demands'' category.
+Evidence suggests the employees do, in fact, distinguish between challenge and hindrance stressors (e.g., Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011).
+For example, Bakker and Sanz-Vergel (2013) found that perceived work pressure as a hindrance demand, and emotional demands as more of a challenge demand.
 Webster et al.
@@
 They found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees.
+Kim and Beehr (2020) found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing.
+The opposite occurred when a demand was appraised as a hindrance -- in those instances, the appraisal had a negative association with motivational resources.
 
-While their study did include resources, it nonetheless points to the possibility that demands might be differentially appraised and related to outcomes (e.g., Podsakoff et al., 2007).
-The challenge-hindrance framework has, in fact, been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and well-being.
+Having evidence that people can make a distinction between challenge and hindrance stressors, the next logical question is whether they do relate differentially to outcomes.
+The challenge-hindrance stressor framework has, in fact, been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and well-being.
 A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic.
@@
 (2000), in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern.
+Chen et al.
+(2021) found that daily challenge demands were positively related to cognitive wellbeing and work-family enrichment.
+Daily hindrance demands were negatively related to these outcomes.
 In contrast, Abbas and Raja (2019) found that challenge and hindrance stressors were \emph{both} positively related to strain and turnover intentions.
@@
 
-We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point.
-Podsakoff et al.
-(2007) supported the original assertion of Cavanaugh et al.
-(2000) with regard to work outcomes such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover.
-The opposite pattern of relationship was observed for hindrance stressors.
+We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point, and a rich collection of them support differential associations across a variety of organizational outcomes.
+For example, both challenges and hindrances have been shown to positively predict strain (J.
+A.
+LePine et al.
+(2005); Podsakoff et al.
+(2007); Webster et al.
+(2010)).
+Many other outcomes are differentially related to challenges and hindrances, largely in the expected direction.
+For example, motivation, job satisfaction, commitment, and performance have been shown to positively relate to challenge stressors and negatively relate to hindrance stressor (J.
+A.
+LePine et al., 2005).
+Turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance stressors (Podsakoff et al., 2007).
 Kim and Beehr (2020), similarly, found evidence for the differential results via challenge and hindrance appraisals.
+
+Horan et al.
+(2020) and M.
+A.
+LePine (2022) specifically call out the need for additional research to incorporate the appraisal process described by Lazarus and Folkman (1984) into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources into our study of the overarching JD-R model.
+In fact, Horan et al.
+(2020) state that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3).
+In fact, Horan et al.
+(2020) suggest future research continue to move away from apriori classifications of stressors, as doing so can be problematic for theoretical and empirical reasons.
+Theoretically, apriori classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
+Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time (e.g., Searle and Auton (2015)).
+TRANSITION?
 
@@
 It is also useful to employers by providing them with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
+
+\#Current Study and Hypotheses
 
@@
 
-Add a description here of the exploratory stuff.
+Lastly, we propose three research that explicitly address a topic hinted at in the literature review above.
+Although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, there remains variability in these appraisals (M.
+A.
+LePine, 2022).
+M.
+A.
+LePine (2022), in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal.
+We explore whether literature-implicated job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory (Bakker \& Demerouti, 2017)and challenge-hindrance stressor framework (Cavanaugh et al., 2000).
 
@@
 see Figure \ref{fig:scalelevelgraphs}
+
+\newpage
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+\hypertarget{future-directions}{%
+\subsection{Future directions}\label{future-directions}}
+
+So, what can be done about the findings that people experience both?
+J.
+A.
+LePine et al.
+(2005) and Podsakoff et al.
+(2007) encourage organizations to incorporate strain-reducing activities like train and support to offset the negative effects of challenging job demands.
+
+There may be some practical utility to pursue training interventions aimed at \emph{how} characteristics are appraised.
+Perhaps the clinical literature may be informative - for example, within cognitive behavioral therapeutic applications, the way in which situations are appraised can be a mechanism to help battle affective disorders such as depression.\footnote{Check on this - this is just speculative place-holding from 12/2 Hudson coffee discussion} Given the current findings, where the same characteristic may be viewed similarly as both a demand and resource, it is possible that framing interventions may ameliorate negative outcomes of demands such as, for example, stress or strain.
 
@@
 
-\leavevmode\hypertarget{ref-bakker2007job}{}%
-Bakker, A.
-B., Hakanen, J.
-J., Demerouti, E., \& Xanthopoulou, D.
-(2007).
-Job resources boost work engagement, particularly when job demands are high.
-\emph{Journal of Educational Psychology}, \emph{99}(2), 274.
-
 \leavevmode\hypertarget{ref-bakker2013weekly}{}%
 Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
-
-\leavevmode\hypertarget{ref-bakker2003dual}{}%
-Bakker, A., Demerouti, E., \& Schaufeli, W.
-(2003).
-Dual processes at work in a call centre: An application of the job demands--resources model.
-\emph{European Journal of Work and Organizational Psychology}, \emph{12}(4), 393--417.
 
@@
 \emph{Journal of Applied Psychology}, \emph{85}(1), 65.
+
+\leavevmode\hypertarget{ref-chen2021daily}{}%
+Chen, H., Wang, H., Yuan, M., \& Xu, S. (2021). Daily challenge/hindrance demands and cognitive wellbeing: A multilevel moderated mediation model. \emph{Frontiers in Psychology}, \emph{12}, 616002.
 
@@
 
+\leavevmode\hypertarget{ref-horan2020review}{}%
+Horan, K.
+A., Nakahara, W.
+H., DiStaso, M.
+J., \& Jex, S.
+M.
+(2020).
+A review of the challenge-hindrance stress model: Recent advances, expanded paradigms, and recommendations for future research.
+\emph{Frontiers in Psychology}, \emph{11}, 560346.
+
 \leavevmode\hypertarget{ref-kim2020thriving}{}%
@@
 
+\leavevmode\hypertarget{ref-lepine2005meta}{}%
+LePine, J.
+A., Podsakoff, N.
+P., \& LePine, M.
+A.
+(2005).
+A meta-analytic test of the challenge stressor--hindrance stressor framework: An explanation for inconsistent relationships among stressors and performance.
+\emph{Academy of Management Journal}, \emph{48}(5), 764--775.
+
 \leavevmode\hypertarget{ref-lepine2022challenge}{}%
 LePine, M. A. (2022). The challenge-hindrance stressor framework: An integrative conceptual review and path forward. \emph{Group \& Organization Management}, \emph{47}(2), 223--254.
-
-\leavevmode\hypertarget{ref-mazzola2019should}{}%
-Mazzola, J.
-J., \& Disselhorst, R.
-(2019).
-Should we be {``challenging''} employees?: A critical review and meta-analysis of the challenge-hindrance model of stress.
-\emph{Journal of Organizational Behavior}, \emph{40}(8), 949--961.
 
@@
 
+\leavevmode\hypertarget{ref-webster2010toward}{}%
+Webster, J.
+R., Beehr, T.
+A., \& Christiansen, N.
+D.
+(2010).
+Toward a better understanding of the effects of hindrance and challenge stressors on work behavior.
+\emph{Journal of Vocational Behavior}, \emph{76}(1), 68--77.
+
 \leavevmode\hypertarget{ref-webster2011extending}{}%

### 2022-12-05 Submission.Rmd
See line 351 and triple check this code!!

@@
 #resource <- resource[ which(resource$sd > 0), ] 
+########################################################
+########################################################
+##Need to triple check all of this. 
+########################################################
+########################################################
+##checking the ns
+library(psych)
+resource_ns <- describe(data[c(118:144, 146:202)])
+#resource_ns
+#table(data$item161) # check one item to confirm ns - it is functioning correctly.
 
+resource <- cbind(resource, resource_ns$n)
+resource
 sortresource <- resource[order(resource$sd),]

### 2022-12-10 Submission.Rmd
I think this is just knitting the paper.

--- 2022-12-03 Submission.Rmd
@@
 However, much of our existing knowledge of the way this model functions is grounded in the assumption that characteristics are generally considered resources or generally considered demands.
-We build on the research of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands (@webster2011extending) or that appraisals may change over time (@rosen2020challenges).
+We build on the research of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges].
 We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, which a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
@@
 *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; @demerouti2001job).
+In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [e.g., high work pressure is frequently cited as a common demand; @demerouti2001job].
 Cognitively, the perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources) [@bakker2014job].
@@
 
-The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor (@cavanaugh2000empirical).
+The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor [@cavanaugh2000empirical].
 @cavanaugh2000empirical delineated between two forms of demands – that of *challenge* and *hindrance* demands.
@@
 This distinction between challenges and hindrances has been of value in determining which demands are related to various outcomes.
-The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes (e.g., @cavanaugh2000empirical).
+The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes [e.g., @cavanaugh2000empirical].
 
@@
 We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point, and a rich collection of them support differential associations across a variety of organizational outcomes.
-For example, both challenges and hindrances have been shown to positively predict strain (@lepine2005meta; @podsakoff2007differential; @webster2010toward).
+For example, both challenges and hindrances have been shown to positively predict strain [@lepine2005meta; @podsakoff2007differential; @webster2010toward].
 Many other outcomes are differentially related to challenges and hindrances, largely in the expected direction.
@@
 Theoretically, apriori classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
-Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time (e.g., @searle2015merits).
+Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time [e.g., @searle2015merits].
 TRANSITION?
@@
 Originally, the Advisory Panel for the Dictionary of Occupational Titles recommended a system that would “…promote the effective education, training, counseling, and employment of the American workforce.
-It should accomplish its purpose by providing a database system that identifies, defines, classifies, and describes occupations in the economy in an accessible and flexible manner” (@advisory1993new, p.
-6).
+It should accomplish its purpose by providing a database system that identifies, defines, classifies, and describes occupations in the economy in an accessible and flexible manner” [@advisory1993new, p.
+6].
 The result was the now commonly used O\*NET.
@@
 #resource <- resource[ which(resource$sd > 0), ] 
+########################################################
+########################################################
+##Need to triple check all of this. 
+########################################################
+########################################################
+##checking the ns
+#library(psych)
+#resource_ns <- describe(data[c(118:144, 146:202)])
+#resource_ns
+#table(data$item161) # check one item to confirm ns - it is functioning correctly.
 
+#resource <- cbind(resource, resource_ns$n)
+#resource
 sortresource <- resource[order(resource$sd),]

### 2022-12-10 Submission.tex
I think this is just knitting the paper.

@@
 However, much of our existing knowledge of the way this model functions is grounded in the assumption that characteristics are generally considered resources or generally considered demands.
-We build on the research of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands (Webster et al.
-(2011)) or that appraisals may change over time ((\textbf{rosen2020challenges?})).
+We build on the research of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020).
 We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, which a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
@@
 \emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; Demerouti et al.
-(2001)).
+In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain {[}e.g., high work pressure is frequently cited as a common demand; Demerouti et al.
+(2001){]}.
 Cognitively, the perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources) (Bakker \& Demerouti, 2014).
@@
 
-The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor (Cavanaugh et al.
-(2000)).
+The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor (Cavanaugh et al., 2000).
 Cavanaugh et al.
@@
 This distinction between challenges and hindrances has been of value in determining which demands are related to various outcomes.
-The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes (e.g., Cavanaugh et al.
-(2000)).
+The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes (e.g., Cavanaugh et al., 2000).
 
@@
 A.
-LePine et al.
-(2005); Podsakoff et al.
-(2007); Webster et al.
-(2010)).
+LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010).
 Many other outcomes are differentially related to challenges and hindrances, largely in the expected direction.
@@
 Theoretically, apriori classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
-Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time (e.g., Searle and Auton (2015)).
+Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time (e.g., Searle \& Auton, 2015).
 TRANSITION?
@@
 Originally, the Advisory Panel for the Dictionary of Occupational Titles recommended a system that would ``\ldots promote the effective education, training, counseling, and employment of the American workforce.
-It should accomplish its purpose by providing a database system that identifies, defines, classifies, and describes occupations in the economy in an accessible and flexible manner'' (Dictionary of Occupational Titles (US) and Service (1993), p.~6).
+It should accomplish its purpose by providing a database system that identifies, defines, classifies, and describes occupations in the economy in an accessible and flexible manner'' (Dictionary of Occupational Titles (US) \& Service, 1993, p.
+6).
 The result was the now commonly used O*NET.
@@
 
-\#Current Study and Hypotheses
+\#\#Current Study and Hypotheses
 
@@
 
+\leavevmode\hypertarget{ref-rosen2020challenges}{}%
+Rosen, C.
+C., Dimotakis, N., Cole, M.
+S., Taylor, S.
+G., Simon, L.
+S., Smith, T.
+A., \& Reina, C.
+S.
+(2020).
+When challenges hinder: An investigation of when and how challenge stressors impact employee outcomes.
+\emph{Journal of Applied Psychology}, \emph{105}(10), 1181.
+
 \leavevmode\hypertarget{ref-searle2015merits}{}%

### 2022-12-10 Submission.Rmd
on the fly edits

@@
 
+# Method
+
+We evaluate agreement across perceptions of job characteristics regarding their characterization as resource, challenge, and hindrance (Bakker & Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001).
+To capture an effectively exhaustive list of characteristics that apply to, theoretically, *every* possible job, we consult the  unifying framework of O\*Net.
+
+## Materials
+
+Our survey was informed by 98 statements taken from job characteristic descriptors located within O\*Net’s classification of “work activities”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context” groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
+
+The O\*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to "responsibility" than task.
+For example, the descriptor for "level of competition", which is an element of the "structural job characteristics" grouping, is *...to what extent does this job require the worker to compete or to be aware of competitive pressures?* Other than minor grammatical editing (for example, changing “the worker” to “you”), we retained the O\*Net wording for our item stems.
+We also retained O\*Net’s response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
+It would likely NOT be considered controversial to referred to these as "effectively" Likert-type response scales.
+
+Subsequent to providing ratings of whether or not each of the 98 O\*Net characteristics were relevant for the respondent’s work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) .
+.
+.
+this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) .
+.
+.
+this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) .
+.
+.
+this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
+The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
+
 ## Participants
@@
 Of the `r nrow(use)` Prolific panel individuals who initially accessed the survey link, `r nrow(different)` indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses [@R-careless].
-Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of `r nrow(data)` respondents who constitute the current SIOP sample.
-`r round(a[1,3],2)`% had been in their referent job less than 6 months, `r round(a[2,3],1)`% between 6 months and a year, `r round(a[3,3],2)`% between one and five years, `r round(a[4,3],2)`% between 5 and 10 years, and `r round(a[5,3],2)`% more than 10 years.
-
-Ages ranged from 18 to 65 with an average of `r round(mean(data[,403], na.rm=TRUE),2)` years old (SD = `r round(sd(data[,403], na.rm=TRUE),2)`).
+Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of `r nrow(data)` respondents who constitute the current sample.
+Regarding tenure, `r round(a[1,3],2)`% had been in their referent job less than 6 months, `r round(a[2,3],1)`% between 6 months and a year, `r round(a[3,3],2)`% between one and five years, `r round(a[4,3],2)`% between 5 and 10 years, and `r round(a[5,3],2)`% more than 10 years.
+Respondent ages ranged from 18 to 65 with an average of `r round(mean(data[,403], na.rm=TRUE),2)` years old (*SD* = `r round(sd(data[,403], na.rm=TRUE),2)`).
 The survey offered a free-field gender identity category, although the sample predominantly self-identified as female (`r round(b[2,3],2)`%) or male (`r round(b[5,3],2)`%).
@@
 
-Each free-field job title was placed into one of 14 possible O\*NET job families classifications.
-60 of these ratings were performed by all 3 author raters, with a resulting Kappa of `r round(kappa$value,2)` [@landis1977measurement].
-We then further collapsed these 14 categories into 8 essentially equal frequency job categories.
-
 ### Characteristics, Demands, and Resources
 
-We used 98 statements taken from O\*NET ["activity" and "context" classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3).
-We retained 41 "work activity" classifications which O\*NET groups into categories of "Information Input" (5 statements), "Interacting with Others" (17 statements), "Mental Processes" (10 statements) and "Work Output" (9 statements).
-57 "work context" statements grouped into "Interpersonal Relationships" (14 statements), "Physical Work Conditions" (30 statements), and "Structural Job Characteristics" (13 statements).
+We used 98 statements taken from O\*NET [activity and context classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3).
+We retained 41 work activity classifications which O\*NET groups into categories of information input (5 statements), interacting with others (17 statements), mental processes (10 statements) and work output (9 statements).
+Fifty-seven work context statements grouped into interpersonal relationships (14 statements), physical work conditions (30 statements), and structural job characteristics (13 statements).
 
-These "descriptors" often have unique response categories ([see here for example](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2)).
-We retained the O\*NET wording to capture characteristics of relevance for each respondent.
+These descriptors often have [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).
+For example, the statement "How responsible is the worker for work outcomes and results of other workers?" has response options ranging from *No responsibility* to *Very high responsibility*, while the statement, "How often do you use electronic mail in this job?" has options ranging from *Never* to *Every day*.
+We retained the essence of each O\*NET descriptor to capture characteristics of relevance for each respondent.
 Subsequent to these self evaluations, each respondent who agreed that the element had *at least some relevance* to their job was also asked to rate that element in terms of, 1) ...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) ...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) ...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.

### 2022-12-10 Submission.tex
on the fly edits

@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Job Demands-Resources model components through the lens of O*NET classifications},
-  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \usepackage{csquotes}
-\ifxetex
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Job Demands-Resources model components through the lens of O*NET classifications},
+  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 Cognitively, the perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources) (Bakker \& Demerouti, 2014).
-Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience depsite the typical apriori assignment of a characteristic as objectively a ``demand'' or ``resource.'' We explore this further below.
+Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience depsite the typical apriori assignment of a characteristic as objectively a ``demand'' or ``resource''.
+We explore this further below.
 
@@
 
+\hypertarget{method}{%
+\section{Method}\label{method}}
+
+We evaluate agreement across perceptions of job characteristics regarding their characterization as resource, challenge, and hindrance (Bakker \& Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001).
+To capture an effectively exhaustive list of characteristics that apply to, theoretically, \emph{every} possible job, we consult the unifying framework of O*Net.
+
+\hypertarget{materials}{%
+\subsection{Materials}\label{materials}}
+
+Our survey was informed by 98 statements taken from job characteristic descriptors located within O*Net's classification of ``work activities'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'' groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
+
+The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task.
+For example, the descriptor for ``level of competition'', which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems.
+We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
+It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.
+
+Subsequent to providing ratings of whether or not each of the 98 O*Net characteristics were relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) .
+.
+.
+this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) .
+.
+.
+this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) .
+.
+.
+this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
+The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
+
 \hypertarget{participants}{%
@@
 Of the 785 Prolific panel individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021).
-Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current SIOP sample.
-13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.
-
-Ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53).
+Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current sample.
+Regarding tenure, 13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.
+Respondent ages ranged from 18 to 65 with an average of 28.18 years old (\emph{SD} = 7.53).
 The survey offered a free-field gender identity category, although the sample predominantly self-identified as female (52.58\%) or male (46.83\%).
@@
 
-\hypertarget{materials}{%
-\subsection{Materials}\label{materials}}
-
-Each free-field job title was placed into one of 14 possible O*NET job families classifications.
-60 of these ratings were performed by all 3 author raters, with a resulting Kappa of 0.53 (Landis \& Koch, 1977).
-We then further collapsed these 14 categories into 8 essentially equal frequency job categories.
+\hypertarget{materials-1}{%
+\subsection{Materials}\label{materials-1}}
 
@@
 
-We used 98 statements taken from O*NET \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{``activity'' and ``context'' classifications}.
-We retained 41 ``work activity'' classifications which O*NET groups into categories of ``Information Input'' (5 statements), ``Interacting with Others'' (17 statements), ``Mental Processes'' (10 statements) and ``Work Output'' (9 statements).
-57 ``work context'' statements grouped into ``Interpersonal Relationships'' (14 statements), ``Physical Work Conditions'' (30 statements), and ``Structural Job Characteristics'' (13 statements).
+We used 98 statements taken from O*NET \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context classifications}.
+We retained 41 work activity classifications which O*NET groups into categories of information input (5 statements), interacting with others (17 statements), mental processes (10 statements) and work output (9 statements).
+Fifty-seven work context statements grouped into interpersonal relationships (14 statements), physical work conditions (30 statements), and structural job characteristics (13 statements).
 
-These ``descriptors'' often have unique response categories (\href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{see here for example}).
-We retained the O*NET wording to capture characteristics of relevance for each respondent.
+These descriptors often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}.
+For example, the statement ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{No responsibility} to \emph{Very high responsibility}, while the statement, ``How often do you use electronic mail in this job?'' has options ranging from \emph{Never} to \emph{Every day}.
+We retained the essence of each O*NET descriptor to capture characteristics of relevance for each respondent.
 Subsequent to these self evaluations, each respondent who agreed that the element had \emph{at least some relevance} to their job was also asked to rate that element in terms of, 1) \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-abbas2019challenge}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-abbas2019challenge}{}}%
 Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.
 
-\leavevmode\hypertarget{ref-bakker2014job}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
 Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
 
-\leavevmode\hypertarget{ref-bakker2017job}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
 Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
 
-\leavevmode\hypertarget{ref-bakker2013weekly}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
 Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
 
-\leavevmode\hypertarget{ref-cavanaugh2000empirical}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
 Cavanaugh, M.
@@
 
-\leavevmode\hypertarget{ref-chen2021daily}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-chen2021daily}{}}%
 Chen, H., Wang, H., Yuan, M., \& Xu, S. (2021). Daily challenge/hindrance demands and cognitive wellbeing: A multilevel moderated mediation model. \emph{Frontiers in Psychology}, \emph{12}, 616002.
 
-\leavevmode\hypertarget{ref-crawford2010linking}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-crawford2010linking}{}}%
 Crawford, E.
@@
 
-\leavevmode\hypertarget{ref-gerich2017relevance}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
 Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
 
-\leavevmode\hypertarget{ref-horan2020review}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-horan2020review}{}}%
 Horan, K.
@@
 
-\leavevmode\hypertarget{ref-kim2020thriving}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-kim2020thriving}{}}%
 Kim, M., \& Beehr, T.
@@
 
-\leavevmode\hypertarget{ref-landis1977measurement}{}%
-Landis, J. R., \& Koch, G. G. (1977). The measurement of observer agreement for categorical data. \emph{Biometrics}, 159--174.
-
-\leavevmode\hypertarget{ref-lazarus1984stress}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
 Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
 
-\leavevmode\hypertarget{ref-lepine2005meta}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lepine2005meta}{}}%
 LePine, J.
@@
 
-\leavevmode\hypertarget{ref-lepine2022challenge}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lepine2022challenge}{}}%
 LePine, M. A. (2022). The challenge-hindrance stressor framework: An integrative conceptual review and path forward. \emph{Group \& Organization Management}, \emph{47}(2), 223--254.
 
-\leavevmode\hypertarget{ref-peterson2001understanding}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
 Peterson, N.
@@
 S., Morgeson, F.
-P., Pearlman, K., \& others.
+P., Pearlman, K., et al.
 (2001).
@@
 
-\leavevmode\hypertarget{ref-rosen2020challenges}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-rosen2020challenges}{}}%
 Rosen, C.
@@
 
-\leavevmode\hypertarget{ref-searle2015merits}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-searle2015merits}{}}%
 Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.
 
-\leavevmode\hypertarget{ref-selye1936syndrome}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-selye1936syndrome}{}}%
 Selye, H. (1936). A syndrome produced by diverse nocuous agents. \emph{Nature}, \emph{138}(3479), 32--32.
 
-\leavevmode\hypertarget{ref-webster2010toward}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-webster2010toward}{}}%
 Webster, J.
@@
 
-\leavevmode\hypertarget{ref-webster2011extending}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
 Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.
 
-\leavevmode\hypertarget{ref-R-careless}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-careless}{}}%
 Yentes, R. D., \& Wilhelm, F. (2021). \emph{Careless: Procedures for computing indices of careless responding}.

### 2022-12-10 Submission.Rmd
methods edits

@@
 
+Data were collected through Prolific, a data collection platform.
+An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
+Eligibility requirements included being 18+ and holding either a full-time or part-time job.
+Participants then voluntarily chose to respond to the survey.
+The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes.
+Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified.
+Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource, challenge, or hindrance for that characteristic.
+For characteristics that *were* implicated as being relevent for their job, they were then asked to report how much a characteristic was a resource, and then how much each characteristic was a hindrance, and finally, how much each item was a challenge.
+Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
+
 We evaluate agreement across perceptions of job characteristics regarding their characterization as resource, challenge, and hindrance (Bakker & Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001).
@@
 
-Subsequent to providing ratings of whether or not each of the 98 O\*Net characteristics were relevant for the respondent’s work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) .
-.
-.
-this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) .
-.
-.
-this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) .
-.
-.
-this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
 The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
@@
 ```
+Subsequent to providing ratings of whether or not each of the 98 O\*Net characteristics were relevant for the respondent’s work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) .
+.
+.
+this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) .
+.
+.
+this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) .
+.
+.
+this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
 

### 2022-12-10 Submission.tex
methods edits

@@
 
+Data were collected through Prolific, a data collection platform.
+An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
+Eligibility requirements included being 18+ and holding either a full-time or part-time job.
+Participants then voluntarily chose to respond to the survey.
+The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes.
+Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified.
+Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource, challenge, or hindrance for that characteristic.
+For characteristics that \emph{were} implicated as being relevent for their job, they were then asked to report how much a characteristic was a resource, and then how much each characteristic was a hindrance, and finally, how much each item was a challenge.
+Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
+
 We evaluate agreement across perceptions of job characteristics regarding their characterization as resource, challenge, and hindrance (Bakker \& Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001).
@@
 
-Subsequent to providing ratings of whether or not each of the 98 O*Net characteristics were relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) .
-.
-.
-this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) .
-.
-.
-this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) .
-.
-.
-this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
 The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
@@
 \subsection{Materials}\label{materials-1}}
+
+Subsequent to providing ratings of whether or not each of the 98 O*Net characteristics were relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) .
+.
+.
+this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) .
+.
+.
+this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) .
+.
+.
+this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
 

### 2022-12-10 Submission.Rmd
on the fly edits

@@
 
-We evaluate agreement across perceptions of job characteristics regarding their characterization as resource, challenge, and hindrance (Bakker & Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001).
-To capture an effectively exhaustive list of characteristics that apply to, theoretically, *every* possible job, we consult the  unifying framework of O\*Net.
-
-## Materials
-
-Our survey was informed by 98 statements taken from job characteristic descriptors located within O\*Net’s classification of “work activities”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context” groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
-
-The O\*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to "responsibility" than task.
-For example, the descriptor for "level of competition", which is an element of the "structural job characteristics" grouping, is *...to what extent does this job require the worker to compete or to be aware of competitive pressures?* Other than minor grammatical editing (for example, changing “the worker” to “you”), we retained the O\*Net wording for our item stems.
-We also retained O\*Net’s response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
-It would likely NOT be considered controversial to referred to these as "effectively" Likert-type response scales.
-
-The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
-
 ## Participants
@@
 
-```{r interrater}
-interrater <- read.csv("interrater.csv")
+Our survey was informed by 98 statements taken from job characteristic descriptors located within O\*Net’s classification of “work activities”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context” groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
 
-library(irr)
+The O\*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to "responsibility" than task.
+For example, the descriptor for "level of competition", which is an element of the "structural job characteristics" grouping, is *...to what extent does this job require the worker to compete or to be aware of competitive pressures?* Other than minor grammatical editing (for example, changing “the worker” to “you”), we retained the O\*Net wording for our item stems.
+We also retained O\*Net’s response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
+It would likely NOT be considered controversial to referred to these as "effectively" Likert-type response scales.
 
-kappa <- kappam.fleiss(interrater)
-```
-Subsequent to providing ratings of whether or not each of the 98 O\*Net characteristics were relevant for the respondent’s work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) .
-.
-.
-this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) .
-.
-.
-this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) .
-.
-.
-this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
-
-### Characteristics, Demands, and Resources
+The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
 
@@
 # Results
+
+Outline:
+
+1. Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
+
+2. Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
+
+3. *Research Question 1*: Are literature-implicated resources consistently rated as job resources?
+
+4. *Research Question 2*: Are literature-implicated challenges consistently rated as job challenges?
+
+5. *Research Question 3*: Are literature-implicated hiderances consistently rated as job hindrances?
 

### 2022-12-10 Submission.tex
on the fly edits

@@
 
-We evaluate agreement across perceptions of job characteristics regarding their characterization as resource, challenge, and hindrance (Bakker \& Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001).
-To capture an effectively exhaustive list of characteristics that apply to, theoretically, \emph{every} possible job, we consult the unifying framework of O*Net.
-
-\hypertarget{materials}{%
-\subsection{Materials}\label{materials}}
-
-Our survey was informed by 98 statements taken from job characteristic descriptors located within O*Net's classification of ``work activities'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'' groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
-
-The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task.
-For example, the descriptor for ``level of competition'', which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems.
-We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
-It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.
-
-The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
-
 \hypertarget{participants}{%
@@
 
-\hypertarget{materials-1}{%
-\subsection{Materials}\label{materials-1}}
+\hypertarget{materials}{%
+\subsection{Materials}\label{materials}}
 
-Subsequent to providing ratings of whether or not each of the 98 O*Net characteristics were relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) .
-.
-.
-this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) .
-.
-.
-this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) .
-.
-.
-this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
+Our survey was informed by 98 statements taken from job characteristic descriptors located within O*Net's classification of ``work activities'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'' groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
 
-\hypertarget{characteristics-demands-and-resources}{%
-\subsubsection{Characteristics, Demands, and Resources}\label{characteristics-demands-and-resources}}
+The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task.
+For example, the descriptor for ``level of competition'', which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems.
+We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
+It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.
+
+The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
 
@@
 \section{Results}\label{results}}
+
+Outline:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
+\item
+  Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
+\item
+  \emph{Research Question 1}: Are literature-implicated resources consistently rated as job resources?
+\item
+  \emph{Research Question 2}: Are literature-implicated challenges consistently rated as job challenges?
+\item
+  \emph{Research Question 3}: Are literature-implicated hiderances consistently rated as job hindrances?
+\end{enumerate}
 

### 2022-12-15 Submission.Rmd
Updating introduction to incorporate Renata's feedback

@@
 Similar to the job-demands resources theory [@bakker2017job], challenge and hindrance demands elicit two different paths or processes.
-First, challenge stressors typically result in a challenge appraisal, and both engagement is likely to happen as a result.
+First, challenge stressors typically result in a challenge appraisal, and engagement is likely to happen as a result.
 Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing.
@@
 Having evidence that people can make a distinction between challenge and hindrance stressors, the next logical question is whether they do relate differentially to outcomes.
-The challenge-hindrance stressor framework has, in fact, been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and well-being.
+The challenge-hindrance stressor framework has, in fact, been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing.
 A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic.
@@
 Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety [@rodell2009can].
-Lastly, @gerich2017relevance concluded that employee well-being was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
+Lastly, @gerich2017relevance concluded that employee wellbeing was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
 
@@
 Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time [e.g., @searle2015merits].
-TRANSITION?
+THE TRANSITION NEEDED HERE COULD ADDRESS RENATA'S RECOMMENDATION TO TIE THIS LITERATURE BACK INTO THE JOB-DEMANDS RESOURCES MODEL.
 
@@
 
-##Current Study and Hypotheses
+## Current Study and Hypotheses
 

### 2022-12-17 Submission.Rmd
revisiting n's

@@
 
+```{r ncheck}
+
+## Use this chunk to figure out n issue - 12/16/22 w/ Alicia on Zoom
+
+## 12/16 looks like these sd's are non-zero but graphs have zeros - triple checking should be applied to graphs prior to this chunk
+
+resource <- resource[ which(resource$sd > 0), ] 
+########################################################
+########################################################
+##Need to triple check all of this. 
+########################################################
+########################################################
+##checking the ns
+#library(psych)
+resource_ns <- psych::describe(data[c(118:144, 146:202)])
+#resource_ns
+#table(data$item161) # check one item to confirm ns - it is functioning correctly.
+
+resource <- cbind(resource, resource_ns$n)
+resource
+
+```
+
 ```{r challengesagree, fig.cap="Characteristics most similarly viewed as challenges (lowest standard deviations)."}

### 2022-12-17 Submission.tex
revisiting n's

@@
 Similar to the job-demands resources theory (Bakker \& Demerouti, 2017), challenge and hindrance demands elicit two different paths or processes.
-First, challenge stressors typically result in a challenge appraisal, and both engagement is likely to happen as a result.
+First, challenge stressors typically result in a challenge appraisal, and engagement is likely to happen as a result.
 Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing.
@@
 Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety (Rodell \& Judge, 2009).
-Lastly, Gerich (2017) concluded that employee well-being was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
+Lastly, Gerich (2017) concluded that employee wellbeing was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
 
@@
 Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time (e.g., Searle \& Auton, 2015).
-TRANSITION?
+THE TRANSITION NEEDED HERE COULD ADDRESS RENATA'S RECOMMENDATION TO TIE THIS LITERATURE BACK INTO THE JOB-DEMANDS RESOURCES MODEL.
 
@@
 
-\#\#Current Study and Hypotheses
+\hypertarget{current-study-and-hypotheses}{%
+\subsection{Current Study and Hypotheses}\label{current-study-and-hypotheses}}
 
@@
 \end{figure}
+
+\begin{verbatim}
+##         V1 V2 V3 V4 V5 V6 V7 V8 V9 V10 V11 V12 V13 V14 V15 V16 V17 V18 V19 V20
+## item118  3  5  4  1  5  4  3  4  5   4   2   5   4  NA   2   5   5   4   4   5
+## item119  4  5  4  3  5  2  3  5  5  NA  NA   2  NA  NA  NA   5   5   4  NA  NA
+## item120  2  4  5  4  5  2  2  5  4   4   3   3   4   5   1   5   5   3  NA   5
+## item121  4  5  5  2  5  5  4  4  5   4   4   3   4   5   4   3   5   4   5   3
+## item122 NA  4 NA  4  3 NA NA  1  2   2   3   3  NA   3   4  NA   5  NA   4  NA
+## item123  4  4  3 NA NA  4 NA  2  5   3   4   3   2   4  NA  NA   1   4   2  NA
+## item124  4  5  4  4  2  4  3  2  5   2   5   5   3   2   3   5   1   4   2   1
+## item125  4  2  3 NA  2 NA NA  2  1   4   4   3   2   3   4   1   4  NA  NA   5
+## item126  3  4  2  3  5  5  2  3  4  NA   4   2  NA   5   2   1   5   3   5  NA
+## item127  3  4  3  4  2  5  2  3  4   4   4   1   5   5   2   1   5   4   4   4
+## item128  1 NA NA NA NA NA NA NA  2  NA  NA  NA  NA  NA   1  NA   4  NA  NA  NA
+## item129  4 NA NA  4 NA NA NA NA NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA
+## item130 NA NA NA NA NA NA NA NA NA   1  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA
+## item131  2  4  3  2  3  4  3  4  5   5   4  NA   5   4   5   3   5  NA  NA  NA
+## item132  4  2 NA NA NA NA NA  4 NA  NA   2  NA  NA  NA   1  NA  NA  NA   4   4
+## item133  3  1 NA NA NA NA NA NA NA   1  NA  NA   2  NA   3  NA  NA  NA  NA   1
+## item134 NA NA NA NA NA NA NA NA NA   4  NA   3   4  NA   4  NA  NA  NA  NA   1
+## item135  4  4  2  4  3  2  5  4  5   4   2   4   3   4   3   3   4   3   4   1
+## item136 NA NA NA NA NA NA NA  2  2   1   2   2   2  NA   2  NA  NA  NA  NA  NA
+## item137 NA  2 NA  4 NA NA NA NA  1   3   3  NA   2  NA   4  NA   4  NA  NA  NA
+## item138 NA  3 NA NA NA NA NA NA NA   4   4  NA   2  NA  NA  NA   4  NA  NA  NA
+## item139 NA  2 NA NA NA NA NA NA  4   3  NA   1   2  NA   2  NA   2  NA  NA  NA
+## item140  4  3 NA NA NA  3  2 NA  4   3  NA  NA   3  NA   4  NA   4  NA  NA   1
+## item141  3 NA  2  3  3  4  4  2 NA   5   3   3   4   2   4   3   1   2   4   1
+## item142  2  2 NA  4 NA  4 NA  4  3   4   3   3   5  NA   4   3   4  NA   3   1
+## item143  2  3 NA  3 NA NA  2 NA  1   4   4   3   4  NA   5   3   5  NA   3   1
+## item144  2  3 NA NA NA  4 NA  4  4   3  NA  NA   5  NA   5  NA   4   2   1   1
+## item146 NA NA NA NA NA NA NA NA NA   1   3  NA   1  NA   2  NA  NA  NA  NA   1
+## item147 NA NA NA NA NA NA NA  5 NA   5  NA  NA  NA   4  NA  NA  NA  NA  NA   4
+## item148 NA NA NA NA NA NA NA  5 NA   5  NA  NA  NA  NA  NA  NA   5  NA  NA   3
+## item149  2  4  4  3  3  5  2  4  5  NA   2   5   3   5   5   5   5   4   4   5
+## item150  3  4  4  3  5  4 NA  4  2   5   4   5   4   5   4   5   5   4   3   4
+## item151  2  4  3  2  3 NA  4  3  5   3   4   4   4   3  NA   4   5   4   5   5
+## item152  3  3 NA  4  3  4 NA  2  5  NA   1   2   1  NA  NA   4   1   4   5   5
+## item153  5  5  3  1  5  4  5  4 NA  NA   3   4  NA   5  NA   3   4   3   5  NA
+## item154  3  5  3  5  5  5  4  5  3   4   4   5   4   4   4   4   5   4   5   5
+## item155  1  3  3  4  4  4  2  3  2  NA   2   4   2   3   2   4   4   3   4   5
+## item156  3  4 NA  3  5  4 NA  3 NA  NA   3   2  NA  NA   4   4   5   4   5  NA
+## item157  3  4  4  1 NA  5 NA  5  4  NA   4   5  NA   5  NA   4   5   4  NA  NA
+## item158  2  4  4  3  5  4 NA  4  4   4   3   4   4  NA  NA   4   4   4   2   4
+## item159  2  3 NA  4  3 NA NA  5  3   4   3   3   3  NA   1   4   5   4   2   5
+## item160  4  5 NA  3  5  4  1  5  2  NA   4   3   5   4  NA   3   2   3   4  NA
+## item161 NA NA NA NA NA  5 NA NA NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA
+## item162  3  4 NA NA NA NA  1  5  5   2   5  NA   4   4   5  NA   4   4   2   3
+## item163  3  4  4  1  5  5  2  5  3   4   5   3   4   4   2   4   4   4   5   3
+## item164  4  4  4  5  5 NA  3  4  5   3   5  NA  NA  NA   3   3   4   4   5   4
+## item165  3  3 NA  3 NA NA NA  4  5   2  NA  NA  NA  NA   5  NA   4  NA  NA  NA
+## item166  4  4  4  2  5 NA NA  4  2   3  NA  NA  NA  NA   4  NA   4  NA  NA  NA
+## item167  3  4  4 NA  5  5  4  4 NA  NA   4   3  NA  NA  NA   5   5   4   5  NA
+## item168  2  4  4  4  5  5 NA  5  5  NA   4   5  NA   5   3   5   5   5   4  NA
+## item169  3  3  3  3  5  5  2  5  2   4  NA   5   2  NA  NA   5   4   4   4   3
+## item170  4  4  5  4  5 NA NA  5  5  NA  NA   5   5  NA  NA   5   5   3  NA  NA
+## item171  4  5  4  3  5  5  1  4  3  NA   4   5  NA   5   5   5   5   4   5  NA
+## item172  3  5  4  4  5  5  2  5  4   5   4   5   5   5  NA   4   5   4   5   3
+## item173  4  4  3  5  3  5  4  4  4  NA   5   4  NA   4   2   3   4   3   3   1
+## item174  3  4  4  1  5  4 NA  4 NA  NA   5   5   4  NA  NA   3   4   3   2  NA
+## item175  2  3  4  4  5 NA  5  4 NA   3   5   4  NA  NA  NA   4   4   5   3  NA
+## item176  4  5  4  2  5  4  3  4  2   4   5   5  NA   5  NA   5   5   4   4   4
+## item177  5 NA NA NA NA NA NA NA  1   4  NA  NA  NA  NA   5  NA   4  NA  NA  NA
+## item178  4  4  3 NA  3  4  2  4  1  NA   5   5   4   3   4  NA   4   3   4  NA
+## item179  4  3  3  2 NA NA  4  4  5  NA  NA  NA  NA  NA  NA  NA   4  NA  NA  NA
+## item180  3  3 NA  3 NA NA NA NA  4  NA  NA  NA   3  NA   5  NA   5  NA  NA   4
+## item181  4  4  3  4  5  5  1  4 NA  NA   4   4   3   5  NA   3   4   3  NA  NA
+## item182  4 NA NA  4 NA NA NA NA NA   3  NA  NA  NA  NA   4  NA  NA  NA  NA  NA
+## item183  3  2 NA NA NA NA NA NA  3   1  NA  NA   5  NA   2  NA   4  NA  NA   1
+## item184  3 NA NA NA NA NA NA NA NA  NA  NA  NA  NA  NA   5  NA   2  NA  NA  NA
+## item185  4 NA NA NA NA NA NA NA  4  NA  NA  NA  NA  NA   5  NA   4  NA  NA  NA
+## item186 NA  2  4  4  3  5 NA  4  2  NA   4   4   3  NA  NA   4   4   2  NA   5
+## item187  4  4  4  2  5  4 NA  4  4  NA   5   5  NA  NA   4  NA   5   2  NA  NA
+## item188  4  5  3  2  3  3  4  4  3  NA  NA   4  NA  NA  NA   4   5   4   5   5
+## item189  2  4  3  4  5  4  4  4  4  NA   5   4   3   5   4   4   5   4   5   4
+## item190  3  5  4  3  5  3 NA  4  2  NA   3   5  NA   4  NA   4   5   4   3   5
+## item191  3  4  4  4  5  4 NA  4  3   4   5   5  NA   5  NA   4   5   4   5   5
+## item192  5  5  4  2  5  4  2  4  2   4   5   5   5   5   5   4   4   4   5   5
+## item193  4  4  4  2  5 NA NA  4  2  NA   4   5  NA  NA   4   4   4   3  NA  NA
+## item194  4  4  4  4  5  5  3  5  5  NA   5   5   4   3  NA   5   5   4   4  NA
+## item195  3  4  3 NA  5 NA NA  5  5  NA  NA   5  NA  NA  NA   5   4   4  NA  NA
+## item196  4  5  2  4  3 NA  1  4  5  NA   5   5  NA  NA  NA   3   5   2   5  NA
+## item197  4  5  3 NA  3 NA NA NA  4  NA  NA   4   5  NA  NA   5   5   3   5   5
+## item198  2  4  3  5  5 NA NA  5  2  NA  NA   3  NA  NA  NA   4   4   3  NA  NA
+## item199  4  4  3  1  3 NA NA  3  5  NA  NA   4   4  NA  NA   3   4   2  NA   5
+## item200  4  4  3 NA NA NA NA NA NA  NA  NA  NA   3  NA  NA   3   2  NA  NA  NA
+## item201  4  4  4  3  5 NA NA  5 NA  NA  NA   4  NA  NA  NA   5   2   2  NA  NA
+## item202 NA  3  4  4  5  4 NA  5 NA  NA  NA   5  NA  NA  NA   3   5   2  NA  NA
+##         V21 V22 V23 V24 V25 V26 V27 V28 V29 V30 V31 V32 V33 V34 V35 V36 V37 V38
+## item118   4   5   4   4   5   4   5   3   5   4   4   4   3   4   5   5   5   5
+## item119   4   5   5  NA   5   3   5  NA   5   3   3   4   4   3  NA   4   5   4
+## item120   4   5   4   4   5   3   4  NA   5   4   2   4   4   3  NA   3   5   4
+## item121   4   5   5   4   5   4   5   5   5   5   5   4   5   4   4   3   5   5
+## item122   2   5   3   2  NA   3   4   5   5   5   5   2   4   4   4   3   2   4
+## item123   3   5   3   3  NA   3   5   4   5   3   2   4   5   4   5   4   3   2
+## item124   4   5   3  NA   5   2   1   4   5   2   3   4   3   4   5   4   2   4
+## item125   3   5   5   4  NA   4   1   4   5  NA   1   4   1   1  NA  NA   2   4
+## item126   3   5   5  NA   5   4   4   4   5   4   5   4   4   4  NA   3   3   4
+## item127   4   5   5   2   5   4   3   5   5   2   5   4   4   4   5   3   2   4
+## item128   1  NA   3   1  NA  NA   1   4  NA  NA  NA  NA  NA  NA  NA   2  NA   2
+## item129  NA  NA   1  NA  NA  NA  NA  NA  NA   4  NA  NA   2  NA  NA  NA   2   4
+## item130  NA  NA  NA  NA  NA  NA  NA  NA   2  NA  NA  NA  NA  NA  NA  NA  NA  NA
+## item131   4  NA   4   3  NA   3   3   4   4   4   3   4   1   4   4   3  NA   4
+## item132   2  NA  NA   2  NA  NA  NA  NA  NA  NA  NA  NA   5  NA  NA  NA  NA   2
+## item133   2  NA  NA  NA  NA  NA  NA  NA   5   3  NA  NA   4  NA  NA  NA  NA   2
+## item134   4  NA  NA  NA  NA  NA  NA  NA   2  NA  NA  NA   4  NA  NA  NA  NA   4
+## item135   4   5   3   2   3   3   2   4   5   4   3   2   2   4   3   4   2   3
+## item136   1  NA   4   1  NA   3   1  NA   3  NA  NA  NA   3  NA  NA   3  NA   1
+## item137   3  NA   3   4  NA   4   2   5   4   4  NA  NA   5  NA  NA   3  NA   1
+## item138   3  NA  NA   4  NA  NA  NA  NA   2  NA  NA  NA   4  NA  NA   3  NA   2
+## item139  NA  NA  NA   4  NA  NA  NA   5  NA  NA  NA  NA   5  NA  NA  NA  NA   2
+## item140   3   5   4   4  NA   4   2   5   4   4  NA   4   4   4   3   3  NA  NA
+## item141   2   5   2   5   2   4   3   5   4   3   4   4   3   4   1   3   2   3
+## item142   4   5   2   2   3   3   3   5   5   3  NA  NA   4  NA  NA   3   2   3
+## item143   4  NA   4   4  NA   3   4   4   5   4  NA   4   5   2  NA   3  NA   3
+## item144   2  NA   1   2  NA  NA  NA   4   3   4  NA  NA   5  NA  NA   3   1   4
+## item146   1  NA  NA   1  NA  NA   1  NA   4  NA  NA  NA  NA  NA  NA   3  NA   2
+## item147   4  NA  NA   5  NA  NA  NA  NA   5  NA  NA   2   3  NA  NA   3  NA  NA
+## item148   4  NA  NA  NA  NA  NA  NA  NA   5  NA  NA  NA  NA  NA  NA   3  NA  NA
+## item149   5   5   4   5   5  NA   4   4   5   4  NA   4   5   5  NA   4   5   2
+## item150   4   5   4   2   5  NA   4   3   5  NA   3   4   5   4  NA   4   5   5
+## item151   4   5   4   5  NA   3   4  NA   5   4   3   4  NA   3   5   3   4   4
+## item152   1  NA   3   4   3  NA   3  NA   1   4  NA  NA  NA  NA  NA   3   1   4
+## item153   4   5   5   4   3   4   5  NA   4  NA   5   5   3   5   4   3   3   5
+## item154   4   5   5   3   5   3   4  NA   5   5   4   4   5   5   5   3   4   5
+## item155   3   5   4   4   3  NA   2   2   2   3  NA   4   4   3  NA   4   2   5
+## item156   4   5   5  NA   3  NA   2  NA   4  NA  NA  NA   3   4  NA   3   2   5
+## item157   3   5   1  NA   5   3  NA  NA  NA   5   4   4   2   4   5   3   4   4
+## item158   4   5   5   4  NA  NA   4   3   4  NA   3   4  NA   4  NA   5   5   4
+## item159   5  NA  NA   5  NA  NA   2   4   5   5  NA  NA   5   3   4   5   3   4
+## item160   4   5   5  NA   3   4   5   2   4   4   4   5   4   4   4   3   3   4
+## item161  NA  NA  NA  NA  NA  NA  NA  NA  NA   3  NA  NA  NA  NA   4  NA  NA  NA
+## item162   3   5   4   2  NA  NA   4  NA   5   4  NA  NA   2   3   4   3   3   4
+## item163   4   5   5   5   5  NA   5   4   5   4  NA   4   4   3   5   4   3   4
+## item164   3   5   4   2  NA  NA   5  NA   4   4  NA   4   3   3  NA   3   3   4
+## item165   3  NA   4   5  NA  NA  NA  NA   5  NA  NA   4   2   4  NA   4  NA   5
+## item166   4  NA   2   4  NA  NA  NA  NA   4  NA  NA   5   4   4   4   4  NA   5
+## item167   4   5   5  NA  NA  NA   5  NA   4   3   3   4   3   4   5   4   4   4
+## item168   4   5   4  NA   5  NA   5  NA   4  NA  NA   5   5   4  NA  NA   3   5
+## item169   4  NA   5   5  NA  NA   4  NA   5   4   3   4  NA   4  NA   4   5   5
+## item170   4   5   5   4   5   4   5  NA   5   4   3   4   4   5  NA   4   4   4
+## item171   5   5   5   4  NA   3   5  NA   5   4   3   4   4   5  NA   4   5   5
+## item172   4   5   5  NA   5   4   4  NA   5   5   3   4   5   5   5   4   4   5
+## item173   3  NA   5  NA  NA   4   5  NA   4   3   5   4   3   3   5   4   3   5
+## item174   4  NA   1  NA   4   4   4  NA   4  NA   3   4   4   3  NA   3   3   4
+## item175   3  NA   1  NA   5   3  NA  NA   3  NA  NA   4   4   3  NA  NA  NA   5
+## item176   4   5   4   3   5   3   5  NA   4   5   3   4   4   4   5   4   5   4
+## item177   4  NA   1  NA  NA   3  NA   4   5  NA  NA   4  NA  NA  NA   3  NA  NA
+## item178   4  NA   5   5   5   4   5  NA   4   4   3  NA  NA   4   5   4   2   5
+## item179   4   5   5  NA  NA   4  NA  NA   4  NA  NA   4   4   4  NA  NA  NA   5
+## item180   4  NA   4   5  NA   3  NA   4   5   4  NA   2   5  NA  NA   3  NA   3
+## item181   4  NA   5   4   5   3   5  NA   3  NA   5   5   3   4   4   4   3   5
+## item182  NA  NA  NA  NA  NA  NA  NA   4  NA   4  NA  NA   4  NA  NA  NA  NA  NA
+## item183   1  NA  NA   4  NA  NA  NA   4   4   4  NA  NA   5  NA  NA   2   2   3
+## item184   4  NA   1   5  NA  NA  NA  NA  NA  NA  NA   4   3   4  NA   3  NA   4
+## item185  NA  NA  NA  NA  NA  NA  NA   4  NA  NA  NA   4  NA   1  NA   3  NA  NA
+## item186   5  NA  NA   3  NA  NA   3  NA   4  NA  NA  NA   4   3  NA   4  NA   5
+## item187   4  NA   4  NA   5   4   4  NA   2  NA  NA   4   4   3   5   4   4   5
+## item188   4  NA   3   4  NA   4   5  NA   5  NA  NA   4  NA   4  NA   4   4   4
+## item189   4   5   5   2   3   4   5   3   5   4   4   4   5   3  NA   4   4   5
+## item190   4   5   5   4   5  NA   5  NA   5  NA   4   4   5   3  NA   4   4   4
+## item191   4   4   5   3   5   3   5  NA   5  NA   3   4   5   3  NA   4   4   5
+## item192   4   5   5   3   5   3   5   4   4  NA   3   4   5   2  NA   4   4   5
+## item193   4  NA   3  NA   5  NA   4  NA   3  NA  NA   4   4   4  NA   3   4   4
+## item194   4  NA   5   4   5   3   4  NA   4   4  NA   4   5   4   5   4   4   4
+## item195   4  NA   1  NA  NA  NA  NA  NA  NA   4  NA   4  NA  NA  NA  NA   3   4
+## item196   4  NA   5  NA   3   3   5  NA  NA  NA   3   4   3  NA   4   3   2   4
+## item197   5  NA   2   4  NA  NA  NA  NA   4   4  NA  NA  NA  NA  NA   4   3   3
+## item198   4  NA   4   3  NA  NA   4  NA   2  NA  NA   4   4  NA  NA   4   4   4
+## item199   4  NA   4  NA  NA  NA   5  NA  NA   4  NA   4   4  NA  NA   3   5   5
+## item200   4  NA   1  NA  NA  NA   5  NA  NA  NA  NA  NA  NA  NA  NA  NA   3   2
+## item201   4  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA   5  NA  NA  NA  NA   3   3
+## item202   4  NA   4  NA   5  NA   3  NA  NA  NA  NA   4   5   4   5   5   5   4
+##         V39 V40 V41 V42 V43 V44 V45 V46 V47 V48 V49 V50 V51 V52 V53 V54 V55 V56
+## item118   5   4   4   3   5   4   4   4   4   5   2   3   5   4   4   4   4   2
+## item119   4   4   4   3   5   4   4   2   4  NA   2  NA   5  NA   4   4   3   4
+## item120   4   4   4   4   5   5   5   2   2   5   2  NA   4   5   3   4   4   5
+## item121   5   5   3   4   5   2   5   5   4   5   2   3   4   5   2   5   3   5
+## item122   3   3   2   2   3   4   4   5   5  NA   3   2   3   4  NA  NA   3   5
+## item123  NA   5   5   2   5  NA   2   4   4   4   2   3   5   5  NA  NA   3   4
+## item124   2   4   1   4   5   5   2   4   4   4   3   3   5   5   2   5   3   4
+## item125   2  NA  NA   2   5   3   3   2   5   5   5  NA   3   5   1   5   2   4
+## item126   5   5  NA   3   3   4   4   4   4   1   4   4   5   5   1   2   3   5
+## item127   5   4   4   3   1   2   3   4   5   1   4   3   5   5  NA   4   4   4
+## item128  NA  NA  NA   3  NA  NA  NA  NA   5  NA   4  NA  NA  NA   1  NA   2   1
+## item129  NA  NA   3  NA  NA   5  NA  NA   4  NA   3  NA   3  NA  NA  NA  NA  NA
+## item130  NA  NA  NA  NA  NA   1  NA  NA   4  NA   4  NA  NA  NA  NA  NA  NA  NA
+## item131  NA   3   5  NA   5  NA   5   5   4  NA   4   3  NA   5   1  NA   2   5
+## item132   3  NA  NA  NA   1  NA  NA  NA   4  NA   3  NA  NA   3  NA   3  NA  NA
+## item133  NA  NA   1  NA  NA   4  NA   4   4  NA   3  NA  NA   3  NA  NA  NA   1
+## item134  NA  NA  NA  NA  NA  NA  NA   1  NA  NA   5  NA  NA  NA  NA  NA  NA   4
+## item135   5   3   3   5   2   4   4   5   4   2   3   4   4   5   3   4   4   5
+## item136  NA  NA   2  NA  NA  NA  NA   1   2  NA   4  NA  NA  NA  NA  NA  NA  NA
+## item137   3  NA   2  NA  NA  NA  NA  NA   5  NA   5   2  NA  NA   3  NA  NA   4
+## item138  NA  NA  NA  NA  NA  NA  NA  NA   4  NA   5  NA  NA  NA  NA  NA  NA  NA
+## item139   1  NA   2  NA  NA  NA  NA  NA   5  NA   3  NA  NA  NA   2  NA  NA   4
+## item140   3   5   2  NA  NA   4   5  NA   4   1   2  NA  NA  NA  NA   3  NA   4
+## item141   3   3  NA  NA   5   4   3   5   4   2   4   3   3   4   3   3   3   5
+## item142   3  NA   3  NA  NA   3  NA   4   5   4   4   3  NA   3   2   3  NA   5
+## item143   3   4   4  NA  NA   4   2  NA   4   5   3  NA  NA   5  NA   3   1   4
+## item144  NA  NA   4  NA  NA   2  NA   4   5  NA   3  NA  NA  NA   2  NA   1   4
+## item146  NA  NA  NA  NA  NA  NA  NA  NA   4  NA   3  NA  NA  NA  NA  NA  NA   1
+## item147  NA  NA   5  NA  NA   2  NA  NA  NA  NA   4  NA  NA  NA  NA  NA  NA  NA
+## item148  NA  NA  NA  NA  NA   3  NA  NA  NA  NA   5  NA  NA  NA  NA  NA  NA  NA
+## item149   5   4   4   3  NA   4   5   5   5  NA  NA   4   4   5   3   4  NA   5
+## item150   5   5   5   3   5  NA   5   2   4   5   3  NA   4   5   2   4   2   5
+## item151   5   4   5   3   5   5   5   4   5  NA   5   4   4   4   2   4   2   4
+## item152   4   5   1   4  NA   2   2   2   5  NA   5   4   4   4   2  NA   1   4
+## item153   3   5   5   4   5  NA   5   4   3   4   3   4   3  NA   3   3   5  NA
+## item154   5   4  NA   5   5   4   5   4   5   3  NA   4   3   5   4   5  NA   4
+## item155   4   4   4   2  NA   1   3   2   5  NA  NA   4   4   4   3   3  NA   4
+## item156   3   5  NA  NA   4  NA   4   4  NA  NA   3   4   3   5   2   5   4   4
+## item157   5   5  NA   2  NA  NA   4   5  NA   4   3  NA   3   5   4   5   3   5
+## item158   5   5   3   5   5   4   4   1   4   4   3  NA   4   5   2   5  NA  NA
+## item159   3   3   4   3   1   2   4   1   4  NA   4   4   3   5   1  NA  NA   5
+## item160   5   4   5   4   5   5   5   2   4  NA   3   4   3   5   3   3   4   3
+## item161  NA  NA  NA  NA  NA   2  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA
+## item162  NA   3  NA   4   2   5   5   1   4   1   3  NA   3   5   3   5   2   4
+## item163   5   4  NA   2   5   5   5   4   4   4   3   4   3   5   2   5   4   4
+## item164   5   4  NA   5   3   5   5   2   4   4   3  NA  NA   5   1   5   4   4
+## item165  NA  NA  NA   2   1   4  NA  NA   4   3   3  NA  NA   5   5  NA   2   4
+## item166  NA   4  NA   5   1  NA   5  NA   4   3   2  NA  NA   5  NA   4  NA   4
+## item167  NA   5  NA   2   5   2   5   5   3   3   4   3   3   5  NA   5   3   4
+## item168   5   5  NA   4   5   2   5   5   4   5   5  NA   4   5   2   5   2   4
+## item169   5   5  NA   2   5  NA   5   4   5  NA   3  NA   5   5   2   5  NA   5
+## item170   5   5   5   5   5   2   4   5   4  NA   3  NA   4   5   4   4  NA   5
+## item171   5   5   3   2   4   4   5   5   5   5   4  NA   4   5   5   5   4   5
+## item172   5   5  NA   4   5   4   5   5   5   5   4   4   4   5   4   5  NA   5
+## item173   5   3  NA   4   2   3   5   1   3   5   4   4   3   5   2   5   4   5
+## item174  NA   4  NA   4   5   1   5   1   4   4   5  NA   2   5   2   3  NA   4
+## item175   5   5  NA  NA   5  NA   5   4   4   5   4   3  NA  NA  NA  NA   5   5
+## item176   5   4   4  NA   5   1   5   4   4   5   4   4   5   5   2   5   5   4
+## item177  NA  NA   4  NA   5  NA  NA  NA   3  NA   3  NA  NA  NA  NA  NA   2  NA
+## item178   5   4   4  NA   5   3   5   2  NA  NA  NA   4   4   5   3   5   5   4
+## item179  NA   5   5  NA  NA  NA  NA  NA   3  NA  NA  NA  NA   4   2  NA  NA   5
+## item180  NA  NA   5  NA  NA   3  NA  NA   5   5  NA  NA  NA  NA   1  NA  NA   4
+## item181   4   5  NA   2   5   3   4   5   5   5   3   4   3   4   1   5   5   5
+## item182  NA  NA  NA  NA  NA   4  NA  NA   2  NA   3  NA  NA  NA  NA  NA  NA  NA
+## item183   3  NA   5  NA  NA   4  NA  NA   5  NA   3  NA  NA  NA   2  NA  NA   4
+## item184  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA   4  NA  NA  NA  NA  NA  NA  NA
+## item185  NA  NA  NA  NA  NA   4  NA  NA   4  NA   3  NA  NA  NA  NA  NA  NA  NA
+## item186   5   5   4  NA   5   2  NA   2   5  NA   4  NA  NA  NA  NA  NA  NA   4
+## item187   5   4   5  NA   4  NA  NA   2   5  NA  NA  NA   4  NA   1   4  NA   4
+## item188  NA   4   5   5   5   5   5   2   4  NA  NA   4   4  NA  NA   5  NA   5
+## item189   5   4   4   3   3   5   5   4   4   4   4   4   4   5   2   5  NA   5
+## item190   5   5   5   4   3   1   5   4   5  NA   4   4   4   5   4   5   4   5
+## item191   5   5   5   2   5  NA   5   5   4   5   4   4   4   5   2   5   4   5
+## item192   5   5   5   5   5   3   5   5   4   5   4  NA   4   5   1   5   4   5
+## item193   5   5  NA   2   2  NA   5   2   4   5   3   3   4   5   3   5   3   4
+## item194   5   4   4   4   4  NA  NA   4   4  NA   3   4   4   5   2   5   3   4
+## item195   4   4  NA   4  NA  NA   5   1   4  NA   4  NA   4  NA   2   4  NA  NA
+## item196   4   4  NA  NA   5   4   5   2   3  NA   4   4   3   5   5   4   4   4
+## item197   5  NA   5  NA   5   5   3   4   5  NA   4   4   4  NA   1  NA  NA   4
+## item198  NA  NA  NA  NA   5   4   5   1   4  NA   3  NA  NA   5  NA   5  NA   4
+## item199   5  NA   5   2   2   2   5   4   5  NA  NA   4   4  NA   1   5  NA   4
+## item200  NA  NA   3  NA   5  NA  NA   5   4  NA  NA  NA  NA  NA  NA  NA  NA  NA
+## item201  NA  NA  NA   3  NA  NA  NA  NA   3  NA  NA  NA  NA  NA  NA   5   3  NA
+## item202   5   4  NA   5   1  NA  NA  NA   4  NA  NA  NA  NA  NA   2   4  NA   5
+##         V57 V58 V59 V60 V61 V62 V63 V64 V65 V66 V67 V68 V69 V70 V71 V72 V73 V74
+## item118   3   4   5   5   4   4   5   5   5   5   3   3   2   3   2   4   2   5
+## item119  NA   4   4   4   4   4  NA   4  NA  NA   5   4   4   3   1   3   5   5
+## item120  NA   4   3   3   4   3  NA   3  NA  NA   5   2   4   4   1   4   5   4
+## item121   5   5   3   5   3   5   5   3   5   5   5   4   4   5   4   4   4   5
+## item122   4   1   4   2  NA   4   4  NA   5   1   4   1   2   5   3   3   3   4
+## item123   4  NA   4   1   2  NA   5  NA  NA   5  NA   2   4  NA   3  NA   3   5
+## item124   5  NA   4   1   2   4   5   4   5   5   4   3   3   5   2   3   4   4
+## item125   4   1   2   4  NA   3   1  NA   5   5  NA  NA   2   1   1   2   3  NA
+## item126   5   5   4   4   3   4   4   2   5   5   5   4   4   4   4   4   5   5
+## item127   4   3   3   5   4   5   4   3   5   5   4   5   4   5   1   4   5   5
+## item128  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA   2   3  NA  NA
+## item129  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA   1   2   5
+## item130  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA   1   1  NA
+## item131  NA   4  NA  NA   5   4   4  NA   5   5  NA  NA   4   5   1   2   5   4
+## item132  NA   2  NA  NA  NA  NA  NA   2  NA  NA  NA  NA   3  NA  NA   4  NA  NA
+## item133   4   2  NA  NA   4  NA  NA  NA   5  NA  NA   1  NA  NA   1   3   2  NA
+## item134  NA   2  NA  NA   3  NA  NA  NA   5  NA  NA   1  NA  NA  NA   3  NA  NA
+## item135   4   4   2   3   3   5   1   4   5   5   4   5   4   4   5   4   2   4
+## item136   5   1  NA  NA  NA   3  NA  NA  NA  NA  NA  NA  NA  NA   3   4  NA  NA
+## item137   4  NA  NA  NA   4   4  NA  NA  NA  NA   4   1   4  NA   2   4  NA  NA
+## item138   4  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA   4  NA  NA   4  NA  NA
+## item139  NA  NA  NA  NA   4   4  NA  NA  NA  NA   3  NA   4  NA  NA   4  NA  NA
+## item140   4   1   1   1  NA   4   4  NA  NA  NA   4   2   3   5  NA   4   3  NA
+## item141   3   4   2   1   4   3   1   1   5   5   3   3   3   3   2   5   1   4
+## item142   4   5   2  NA   4   4  NA  NA   5   5   4   3   4  NA   2   5   1   4
+## item143   4   5   5   2   4   4   4  NA   5  NA   4   2   4   5   3   4   2   4
+## item144   5   5  NA  NA   3   4  NA  NA   5  NA   4   3   4  NA  NA   5  NA  NA
+## item146  NA  NA  NA  NA   1  NA  NA  NA  NA  NA   2  NA  NA  NA   2   2  NA  NA
+## item147   4  NA  NA  NA  NA   3  NA  NA  NA  NA   4  NA  NA  NA  NA   3  NA  NA
+## item148  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA   2  NA  NA
+## item149  NA   4   2   4   3   5  NA  NA  NA   5   5   4   4   4   3   5   5   5
+## item150   4   5   4   3   4   4   4   5   5   5   4   4   4   5   1   5   5   5
+## item151   3   5   4  NA   3   5   3  NA   5   5   5   1   4  NA  NA   5   4   5
+## item152  NA   4   4  NA   1   4  NA  NA   5   1   4   2   3   1   2   4   4   1
+## item153   5   4   4   4   5   3   4   3   5   5   5   3   4   5   4   5   5   5
+## item154   4   5   2   4   5   5  NA   4   5   5   5   3   4  NA   4   5   5   5
+## item155  NA   5   2   2   3   4  NA  NA  NA   5   1   4   3   4   3   4   5   3
+## item156   4   3   4   1   4   3   3   2   5   5   4   3   4   4  NA   4   4   3
+## item157  NA   4   3   5   4   3  NA   5  NA  NA   2   5  NA  NA   4   3   5   5
+## item158   4   5   2   3   4   4  NA  NA  NA   5   3   4   3  NA   1   4   4   5
+## item159   5  NA   3  NA  NA   4  NA   5  NA   5   4   4   4   5   1   5   4   5
+## item160  NA  NA   3   3   3  NA   2   2   5   5   5   2   4   5   3   3   4   5
+## item161  NA  NA  NA  NA  NA  NA  NA  NA   5  NA  NA  NA  NA  NA  NA  NA  NA  NA
+## item162  NA  NA  NA   2  NA   3  NA  NA  NA   5  NA   3   4  NA   1   2  NA   4
+## item163   5  NA   4   2   5   3   5   4   5   5   4   2   4   5   3   3   5   5
+## item164   4   5   3   2   4  NA   4   5   5   5   4   3   4   5   3   4   4   5
+## item165   3   5  NA   2  NA   4  NA  NA  NA  NA   4   3   4  NA   2   2  NA  NA
+## item166   4   5  NA   4   4   4  NA   5  NA  NA   4   3   3   5   1   4  NA  NA
+## item167   4   5   2   4   3  NA   4   5   5   5   3   3   4  NA   3   3   3   5
+## item168   4   5  NA   3   4   4   4   4   5   5   4   3   4   4   1   4   4   5
+## item169   4  NA   3   3   4   4  NA  NA   5   5   4   2   3   5   3   4   2   5
+## item170   4  NA   3   3   4   4  NA   4   4   5   5   4   4   5   2   5   3   4
+## item171   3   5   4   5   5   4   5   4  NA   5   3   5   4   5   3   4   5   5
+## item172   4  NA   4   4   4   4   4   5  NA   5   4   5   4   5   3   3   5   5
+## item173   4  NA   4   2   3  NA   4  NA   5  NA  NA   4   4   4   2   4   3   4
+## item174  NA  NA   4   2   4  NA  NA   3   5  NA   2   3  NA   5   1   4   4   5
+## item175  NA  NA   2   5   3  NA   4  NA  NA  NA   1   5  NA   5   1   3   2  NA
+## item176  NA   5   2   2   5   3   5   5   4   5   4   5   4   5   1   3   2  NA
+## item177  NA   5  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA   3  NA   3   4  NA  NA
+## item178  NA   4   4   2   2  NA   4   3   4  NA   4   4   4   4   4   4   2  NA
+## item179  NA   5  NA   2  NA   3   4   5  NA   5   4   3  NA   5   1   4  NA   5
+## item180   4   5   4  NA  NA   4  NA  NA  NA  NA   3  NA   3   4   2   5  NA  NA
+## item181  NA   5   4   3   4  NA   4   3   5  NA   4  NA   4   5   1   2   3   5
+## item182  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA   4   4  NA   5
+## item183   4   5  NA  NA  NA   4  NA  NA  NA  NA   4  NA   4  NA   2   3  NA  NA
+## item184  NA   5  NA  NA  NA  NA  NA  NA  NA  NA   3  NA   4  NA   2   4  NA  NA
+## item185   4   5  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA   4  NA   2   4  NA  NA
+## item186  NA   5   4  NA  NA   4  NA   4  NA  NA   5   5   4  NA   3   4   3  NA
+## item187  NA  NA   4  NA  NA   4  NA   5  NA  NA   4   5   4  NA   2   4   4   5
+## item188   4   5   4   4   2  NA   3  NA   4   5  NA   1   4  NA   2   3   4   5
+## item189   3   4   4   3   2   3   4   4   4   5   5   3   4   4   3   4   5   5
+## item190  NA  NA   4   4   5   5   4   5  NA   5   4   4   4   5   3   2   5   5
+## item191   4   5   2   4   5   5  NA   5   5   5   5   4   4   5   1   3   5   5
+## item192   4   5   2   4   5   5  NA   5   4   5   5   3   4   5   1   2   5   5
+## item193  NA  NA   1  NA  NA   4  NA   4   4   5  NA   4   4  NA   1   2   5   5
+## item194   3   5   2   2   4   4   4   5  NA   5   4   5   4   5   1   4   4   5
+## item195   5  NA   4   3   4  NA  NA  NA  NA   5   3  NA  NA  NA   2   5   4   4
+## item196   5  NA   4   1   2  NA  NA  NA   4   5   3   1   3   5   1   4   4   5
+## item197   4   5  NA  NA   2   5  NA   5   4  NA   5  NA   4  NA   1   3   5   4
+## item198  NA   5  NA  NA  NA  NA  NA  NA   4  NA  NA  NA   4  NA   1   4   4   4
+## item199  NA  NA   2  NA  NA   4  NA   4   5   5   3   2   3  NA   5   4   4   3
+## item200  NA   5  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA   4  NA   3   4  NA   5
+## item201  NA  NA   4  NA   4  NA  NA  NA  NA  NA  NA  NA  NA  NA   2   4   3  NA
+## item202  NA  NA   4   2  NA   4  NA   5  NA  NA   4   5   3  NA   2   4   4  NA
+##         V75 V76 V77 V78 V79 V80 V81 V82 V83 V84 V85 V86 V87 V88 V89 V90 V91 V92
+## item118   4   4   5   3   5   5   4   5   4   4  NA   4   5   1   3   2   4   3
+## item119   1  NA   4   3   4   5   3   4   4   4  NA   4   3   1   5  NA   4   5
+## item120   1   2   4   5   5   5  NA   3   4   5  NA   4   3   2   5   2   4   5
+## item121   5   5   4   5   5   5   5   4   5   5   3   5   4   4   5   5   4   5
+## item122  NA   1  NA   3   1  NA   4  NA   1   4   3   3   2   2   2  NA   2   4
+## item123   4   2   4   5   5   5   1  NA  NA   4   3   2   2   1   2   3   4   2
+## item124   1   4   4   5   2   5  NA   1   4   4   3   5   4   4   2   3   4   2
+## item125   4   1   4   1   3   5   5   1  NA  NA   3   4   3   5   1   1  NA   2
+## item126   4   4   4   5   5   5   2   1   4   4   2   4   2   4   5  NA   4   5
+## item127   1   4   4   2   5   5   3   1   2   4   3   4   4   5   5   3   3   5
+## item128   1  NA   3  NA   3  NA  NA  NA  NA   4   1   2  NA  NA  NA   1  NA  NA
+## item129  NA  NA   5   5   3  NA  NA  NA   4  NA  NA   2  NA  NA  NA  NA   3   5
+## item130  NA  NA   5   3  NA  NA  NA  NA  NA  NA   3  NA  NA  NA  NA  NA  NA   5
+## item131   4  NA   4   1   5   5   4  NA   4   4   1   5   3   1  NA   3   5  NA
+## item132  NA  NA   4  NA   4  NA  NA  NA  NA   5   2   1  NA  NA  NA  NA   3   5
+## item133   1  NA   5  NA   4  NA  NA  NA   2   5  NA   1  NA  NA  NA  NA  NA   5
+## item134   1  NA   5  NA   4  NA  NA  NA  NA   5  NA  NA  NA  NA  NA  NA  NA   4
+## item135   3   2   4   4   3   5   1   4   3   4   2   4   3   1   2   5   3   4
+## item136   1  NA   4  NA  NA   3  NA  NA  NA   3   1   2  NA   1  NA  NA   2   2
+## item137  NA  NA   3  NA  NA  NA  NA  NA   2   4   1  NA  NA  NA  NA   1   2   5
+## item138  NA  NA   3  NA  NA  NA  NA  NA  NA   4   1   4  NA  NA  NA  NA  NA   5
+## item139  NA  NA   3  NA  NA  NA  NA  NA  NA  NA   3   2  NA  NA  NA   1  NA   5
+## item140   1  NA   3  NA  NA   4   3  NA  NA   4   3   2  NA   1   2  NA  NA   5
+## item141   1   1   4   5   3   5   3   3   2   3  NA   4   3   1   1   4   2   4
+## item142   1   2   4   2   3   5  NA   3   4   4   3   4   3  NA  NA   2   4   4
+## item143   1  NA   4   2   5   5  NA  NA  NA   4   3   5   3   2  NA   3   3   5
+## item144  NA  NA   4   2  NA   3  NA  NA  NA   4   3   4  NA  NA  NA   2   3  NA
+## item146  NA  NA   4  NA  NA  NA  NA  NA  NA   4   1  NA  NA  NA  NA  NA  NA   4
+## item147  NA  NA   4  NA  NA   5  NA  NA  NA  NA   4   4  NA  NA  NA   3   3   5
+## item148  NA  NA   4  NA  NA  NA  NA  NA  NA  NA   4  NA  NA  NA  NA  NA  NA  NA
+## item149   4   5   4  NA   5  NA  NA   4   5   5   3   5   4   4   2   5   5   5
+## item150  NA   5   4  NA   5   5   5   3   4   5   3   5   4   4  NA   5   4   5
+## item151   4   3   4   3   5   5   3   4   4  NA   3   4  NA   4   5   3   5   5
+## item152  NA  NA   2  NA   5   4  NA   3  NA   5  NA   2  NA   4   2   4   2   2
+## item153   5   4   4  NA   5   5   4   3   4   4  NA   5   2   3   5   5   3   5
+## item154   5   4   4   1   5  NA  NA   4   4   4   4   4   4  NA   3   4   4   5
+## item155   3   2   3  NA   5  NA  NA   4   4   4   3   4   3   4   1   2   3   2
+## item156  NA   2   3  NA   5   5   2   1   4   4  NA  NA  NA   3   5   4   2   2
+## item157  NA  NA  NA  NA   5  NA  NA  NA  NA   5   3  NA  NA   5  NA  NA   4   2
+## item158   4   4   4  NA   5   5   1   3   4   2  NA   4   4   3   5   5   4   5
+## item159  NA   4   4  NA   5   5  NA  NA  NA   3   4   4  NA  NA   5   5   3   5
+## item160   3   4   3   5   5   5  NA   3   5   4  NA   5   3   5   5   3   5   5
+## item161  NA  NA  NA   1  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA  NA
+## item162  NA   2   4  NA   5   3  NA   2  NA   4  NA   5   4   2  NA   4   5   4
+## item163   5   4   4  NA   5   5   3   4   5   4   3   5   4   5   5   4   4   2
+## item164   4  NA   4  NA   5  NA   2   4   4   4  NA   5   4   5   5   4   2   2
+## item165  NA  NA   4   4  NA  NA   3  NA  NA  NA   4   5  NA  NA  NA   4   3   5
+## item166   4  NA   4  NA   4  NA  NA   3   4   5  NA   5   4   5   5  NA   3   4
+## item167   5  NA   4  NA   4  NA   3   4   4   5  NA   5   4   5   2  NA   3  NA
+## item168   5   5   4  NA   5   4  NA   5  NA   5  NA   5   5  NA   3  NA   4   2
+## item169  NA   3   4   5   5   4  NA  NA  NA   4  NA   4   4   5   3  NA   3   5
+## item170   5   5   4  NA   4   5   4   4  NA   3   3   4   3  NA   5  NA   3   4
+## item171   5   5   4  NA   5   5  NA   4   5   5  NA   4   5   5   5   4   4   4
+## item172   5   5   4   3   5   4   5   4   5   5  NA   4   5   5   5   5   4   4
+## item173   4   2   3  NA   5   5   3   3   4   4  NA   4   4   5   4  NA   2   1
+## item174   4   4   3  NA   5   5   3   3  NA   4  NA   5   3  NA  NA  NA   3  NA
+## item175   5   4   4  NA   5  NA  NA   5   5   5  NA   3   5   5  NA  NA   3  NA
+## item176   5   4   5  NA   5   5   4   4   4   5   5   5   5   5   5   4   4  NA
+## item177  NA  NA   5  NA  NA  NA  NA  NA  NA  NA   4   4  NA  NA  NA  NA  NA  NA
+## item178   5   2   4  NA   5   5   2   3   4   4  NA   3   2   5   5   4  NA   3
+## item179   4  NA   4  NA   5  NA  NA  NA  NA   5   4   4   4   5   5  NA  NA  NA
+## item180   1  NA   5  NA  NA   5  NA  NA   3   4   3   4  NA  NA  NA   4  NA   4
+## item181  NA   4   4  NA   5   5   4   3  NA   5  NA   5   5   5  NA   3   3   3
+## item182  NA  NA   5   5  NA  NA  NA  NA  NA  NA   3   3  NA  NA  NA  NA  NA   5
+## item183  NA  NA   5   3  NA  NA  NA  NA   3   2   4   3  NA  NA  NA   2  NA   5
+## item184  NA  NA   5   1  NA  NA   3  NA  NA  NA  NA   3   4   5  NA  NA  NA   4
+## item185  NA  NA   5  NA  NA  NA  NA  NA  NA  NA  NA   4  NA  NA  NA  NA  NA   4
+## item186  NA   2  NA  NA  NA   5   3  NA  NA   5  NA   3  NA  NA  NA   5  NA   4
+## item187   5   2   4  NA   5  NA  NA  NA   4   5  NA   4   3   5   5  NA   4   4
+## item188   4   5   4  NA  NA   5  NA   4   5   4  NA   4   3   5  NA  NA   3   4
+## item189   4   4   4   5   5   5   4   4   4   4   4   4   4   5   5   4   3   5
+## item190  NA   5   5  NA   4  NA   4   5   5   5  NA   4   4   5   5   5   4   4
+## item191   5   5   5  NA   5   5   5  NA   4   5   4   5   4   5   5   5   4   4
+## item192   5   5   5  NA   5   5   5   5   5   4   4   5   4   5   5   5   4   5
+## item193  NA  NA   4  NA   5   4   2  NA  NA   5  NA   4  NA  NA   5   5   4   4
+## item194   5  NA   4  NA   5  NA   3  NA   5   5  NA   4   4   5   5   5   2  NA
+## item195  NA   2   5  NA  NA  NA  NA   3  NA   3  NA   5  NA   3   5  NA   5  NA
+## item196   3   2   4  NA   4   5  NA  NA   4   4  NA   5   2   3   5  NA   2   5
+## item197  NA  NA   4   1  NA   5  NA  NA  NA   5  NA  NA  NA  NA  NA   4  NA   5
+## item198  NA  NA   4  NA   5  NA  NA   3  NA   5  NA   5   4   5  NA  NA   3   3
+## item199  NA  NA   2   1  NA  NA  NA   3  NA   4  NA   5   4  NA   3   4   2   5
+## item200  NA  NA   5  NA  NA  NA  NA   3   5  NA  NA   2   3   2  NA  NA   5   3
+## item201  NA  NA   4  NA  NA  NA  NA   2  NA  NA  NA  NA  NA  NA  NA  NA   3  NA
+## item202  NA  NA   4  NA  NA  NA  NA  NA   4   5  NA   4  NA   5  NA  NA   3  NA
+##         V93 V94 V95 V96 V97 V98 V99 V100 V101 V102 V103 V104 V105 V106 V107
+## item118   3   5   3   3   4   4   4    4    5    4    4    4    3    5    4
+## item119   4   5   3  NA   4  NA   3   NA   NA    4   NA   NA   NA   NA    4
+## item120   2   5   3  NA   4   4   4    2    5    5    4    4   NA   NA    5
+## item121   4   5   4   3   4   4   5    5    5    2    5    4    2    5    5
+## item122   1  NA   3   3  NA   2   3    5    5    3   NA    3   NA    3    5
+## item123  NA   5   5   3  NA   4   3    5   NA    3    4    4   NA    5    5
+## item124   3   4   4   3   5   4   2    4    5    2    2   NA    4    4    5
+## item125   2   4   4   3   3   4   3    5    5   NA   NA    4   NA    3    4
+## item126   2   5   5   3   5   2   4    4    5   NA    2    4   NA    3    5
+## item127   3   5   3   3   5   5   3    3    5    4    2    4    4    3    5
+## item128   2   3  NA   3   3  NA  NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item129   4   3  NA  NA  NA  NA  NA   NA   NA   NA   NA   NA    5   NA    3
+## item130   4   3  NA   3  NA  NA  NA    5   NA   NA   NA   NA   NA   NA   NA
+## item131   3   3   5   3   5   5   3   NA    5    3    4    4    3    3    3
+## item132   3  NA  NA   3  NA  NA  NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item133   3   3  NA   3   5  NA  NA    4   NA   NA   NA   NA    3   NA   NA
+## item134   3   3  NA  NA   5  NA  NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item135   4   4   4   3   4   2   3    4    5    3    4    4    5    3    3
+## item136   1   2   2   3   3   5  NA   NA   NA    2    1   NA    1   NA   NA
+## item137   3   1  NA   3   3   4  NA    5   NA    2   NA   NA    2   NA   NA
+## item138   3   1  NA   3  NA  NA  NA    4   NA   NA   NA   NA   NA   NA   NA
+## item139   3   1  NA   3  NA  NA  NA    4   NA    2   NA   NA    2   NA    4
+## item140   2   1   3   3   5   1   3    5    5    2   NA   NA    3    4   NA
+## item141   2  NA   4   3   2   1   3    1    5    2    2    2    3    3    4
+## item142   2   1  NA   3   3   1  NA    2   NA    2    2   NA    4    3    4
+## item143   4   5   4   3   5   1   3    5    5    3   NA    3    4    4   NA
+## item144   3   1  NA   3   5   1  NA    5   NA   NA   NA   NA    2    3   NA
+## item146   2   1  NA  NA   5  NA  NA    3   NA   NA   NA   NA   NA   NA   NA
+## item147   4   5  NA   3   5  NA  NA    4   NA   NA   NA   NA   NA   NA   NA
+## item148   4   5  NA   3   3   5  NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item149   4   4  NA  NA   5   5   4    5    5    4    4    2    5    5    4
+## item150   4   5   4   3   5   5   4    5    5    3    2    4    4    4    5
+## item151   2   4  NA   3   2   5   3   NA    5    5    2    4   NA    4    4
+## item152   2   3  NA  NA   1   3   3    5    4    2   NA    4    2    2    5
+## item153  NA  NA   4   3   5   3   3   NA    4    2    4    4    3    5    4
+## item154   4   3   4   3   5   4   4    5    4    1    2    4    5    2    4
+## item155   1   4  NA  NA   3   4   4    4    4    3    2    4    4    4    5
+## item156   3  NA  NA  NA   5   4   3    5    4   NA   NA    5   NA    3    4
+## item157  NA   2  NA   3   5   5  NA   NA   NA    4    4   NA   NA   NA   NA
+## item158   5   5   4   3   5   4   3   NA    5    3    3    5   NA    4    5
+## item159   5   5   5   3   2   4   3   NA   NA    5   NA    3    4    3    5
+## item160   3   3   4   3   5   4   3    3    5    3    3    4    1    4    4
+## item161  NA  NA  NA  NA  NA  NA  NA   NA   NA    3   NA   NA   NA   NA   NA
+## item162   4   5  NA   3   5   4  NA   NA   NA    5    4    4    3    4    4
+## item163   4   5   5   3   5   1   4   NA    5    5    4    5   NA    4    4
+## item164   4   5   4  NA   4   1   4    5   NA    4    2    5   NA    5    4
+## item165   5   5   4   3   3   1  NA    5   NA    5   NA   NA   NA    4    4
+## item166   5   5   4   3   3   5  NA   NA   NA    5   NA   NA    3    4    5
+## item167   5   5  NA   3   5   5  NA   NA    5   NA    3    5   NA    4    5
+## item168   4   5   5   3   4   5   4   NA   NA    5    4    3    5    5    5
+## item169   4   5   4   3   5   4   2   NA   NA    4    4    2   NA    4    5
+## item170   4   5   4   3   5   4  NA   NA    3    4    3    2    4    4    4
+## item171   5   5   4   3   3   4  NA    5    3    5    2    5    4    5    5
+## item172   5   5   5   3   5   5   4    5    5    5    3    5    5    5    5
+## item173   4   5   4   3   5   2   3   NA    1    3    2    3   NA    5    4
+## item174   4   5  NA   3   4   3  NA   NA    1   NA   NA    4    5    4   NA
+## item175  NA   5   5   3   4   4   4   NA   NA   NA   NA   NA   NA   NA   NA
+## item176   5   5   5   3   3   4   4    4   NA   NA    4    5    1    5    5
+## item177   5   5   3  NA   5  NA  NA   NA    4   NA   NA   NA   NA   NA    4
+## item178   4   5   4  NA   3   3   3    5    5   NA    2    5   NA    5    5
+## item179   4   5   4  NA   4   3  NA   NA    5    5   NA    3   NA    4   NA
+## item180   3   5   4  NA   4   2  NA    5    5    5   NA   NA    3    3    4
+## item181  NA  NA   5   3   5   2   4   NA    5    3    2    4    3    5    4
+## item182   4   4  NA  NA  NA  NA  NA    5   NA   NA   NA   NA   NA   NA   NA
+## item183   4   5   4  NA   3  NA  NA    5    5    3   NA   NA    5   NA   NA
+## item184   5   5   3   3   3  NA  NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item185   5   5  NA   3   2  NA  NA    5   NA   NA   NA   NA   NA   NA   NA
+## item186   4   5   4  NA   5   3  NA   NA   NA    5   NA   NA    4   NA    5
+## item187   3   5   4   3   4   4   3   NA    5    3    2    5    5   NA    5
+## item188   3   5   2   3  NA   5  NA    5    5    4   NA    5   NA    5    5
+## item189   5   5   3   3   2   4   3    4    4    3    2    4    3    5    4
+## item190   5   5   4   3   4   4   4    5    5    3    2    4    4    4    5
+## item191   5   5   4   3   5   4   5    5    4    3    2    5   NA    4    5
+## item192   5   5   4   3   5   3   3    5    4   NA    2    5   NA    4   NA
+## item193   4   5   4   3   2   4   3    5    3    3   NA    5   NA    4    5
+## item194   5   5   4   3   2   4   3    5    3   NA    1    4    4    4    5
+## item195   4   5  NA   3  NA  NA  NA   NA    2    4   NA   NA   NA    3    4
+## item196  NA   5   4   3   2   4   2   NA    5    3    2    5   NA    5    4
+## item197  NA   5  NA  NA   2   4  NA   NA    5    5   NA   NA   NA    3   NA
+## item198  NA   5   4  NA  NA   3   3   NA    5   NA   NA   NA   NA   NA   NA
+## item199  NA   5   2  NA  NA   3   3   NA    5   NA   NA    4    4   NA    5
+## item200  NA  NA  NA  NA  NA   3  NA   NA    5    5   NA    3   NA    5   NA
+## item201  NA   5  NA  NA  NA  NA  NA   NA    2    3   NA   NA   NA    3    4
+## item202   4   5   4   3  NA  NA  NA   NA    5   NA   NA   NA    5   NA    5
+##         V108 V109 V110 V111 V112 V113 V114 V115 V116 V117 V118 V119 V120 V121
+## item118    5    5    1    3    2    2    4    4    4    5    5    4    5    5
+## item119   NA    5    1    4    4    2   NA    5    2    4    4    4    5    3
+## item120   NA    5    1    4    5    3   NA    4    2    5    3    4    5    3
+## item121    5    5    1    5    5    5    4    5    1    5    5    5    5    3
+## item122   NA    3    1    4    2    1    5    5    3   NA    2    4    5   NA
+## item123    5    2   NA    3    4    2   NA    4    3    1    3   NA   NA    3
+## item124    5    1    1    5    5    2   NA    5    4    5    4    1    2    4
+## item125   NA    2    4    3    4    5    3    5    5    4    2    5   NA    3
+## item126    2    2   NA    4    5    5   NA    5    4    2    4    5    5    4
+## item127    1    4    4    4    5    2    5    4    2    3    4    5    5    4
+## item128   NA   NA   NA    1    1    1    1    2    1   NA    2    1   NA   NA
+## item129   NA    3   NA   NA    5   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item130   NA   NA   NA   NA   NA   NA    4   NA   NA   NA    3   NA   NA   NA
+## item131    1    2    1    3    4    5    5    4    2    3    4   NA   NA    3
+## item132   NA    2   NA   NA   NA   NA   NA   NA    2   NA   NA   NA   NA   NA
+## item133   NA    3   NA   NA    5   NA   NA   NA    3   NA    4    5    5    3
+## item134   NA    3   NA   NA    5   NA   NA    4    2   NA    4   NA    5   NA
+## item135    1    5    4    1    5    2    2    5    3    3    5    5    5    3
+## item136   NA   NA   NA   NA    2    1    2    3    1   NA    1    3    5   NA
+## item137   NA    2   NA   NA   NA    1    2    4   NA   NA   NA    1    5   NA
+## item138   NA   NA   NA   NA   NA    3   NA   NA   NA   NA   NA    3   NA   NA
+## item139   NA   NA   NA   NA   NA   NA    1   NA   NA   NA    1    1   NA   NA
+## item140   NA    4    4    3    5    1    3    4    2   NA   NA    4   NA    3
+## item141    3    3    4    2    2    4   NA    2    4    3    1    4    2    4
+## item142   NA    3    2    2    4    1    4    4    3   NA    3    4    4   NA
+## item143    3    3    4    4    1    1    3    5    4    3    4    5    5    3
+## item144    3    3    4   NA    4    5    3    5   NA   NA    4   NA    5   NA
+## item146   NA   NA   NA   NA    1   NA   NA    1    2   NA   NA    3    5   NA
+## item147    4   NA    5   NA   NA   NA    2   NA    2   NA    5    5   NA   NA
+## item148   NA   NA    5   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item149   NA   NA    5    4    5    5    4    5    3    3    5   NA    5    2
+## item150    3    5   NA    4    5    2    4    4    3    4    5    5    5    4
+## item151    3    5    5    4    5    4   NA    4    3    4    4    5    5    4
+## item152    1    1    4    2    1    5   NA    4    1    1    3    1    5    2
+## item153    5    3    4    5    5    1   NA   NA    5    4    4    5    5    5
+## item154    1   NA    5    3    5    5    3    5    2    4    3    5    5    2
+## item155   NA   NA    5    1    2    4    1    4    2    4    4   NA    5    2
+## item156   NA    5   NA    3    5    1   NA    5    4   NA    4    5    5    4
+## item157   NA    5   NA   NA    5   NA    2    5    4    4    5   NA    5   NA
+## item158   NA    5    2    4    4    5   NA    4    2    4    5    5    5    3
+## item159   NA    5    3   NA    2    5    3    4    2   NA    5    4    5   NA
+## item160    5    4   NA    3    5   NA    1    4    4    4    3    5    4    2
+## item161   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item162    4   NA    3    5    2    5    4    5    1    5    5   NA    5    3
+## item163    3    4    4    5    5    1    4    5    2    5    4    5    5    4
+## item164   NA    5   NA    5    5    1   NA    5    1    5    4   NA    5    4
+## item165   NA    4   NA    4   NA    1   NA    5    4   NA    4    5   NA   NA
+## item166   NA    5   NA    3    4   NA   NA    5    4   NA    4   NA   NA    3
+## item167   NA   NA   NA    4    4    1   NA    4    2    5    4   NA    5    3
+## item168    4    5   NA    4    4    1   NA    5    4    5    5   NA    5    4
+## item169   NA   NA   NA    4    4    5   NA    5    4    5    5   NA    5    3
+## item170   NA   NA   NA    5    4    5    2    5    5    5    5   NA    5    4
+## item171   NA    4   NA    5    5    4    4   NA    2    5    4   NA    5    4
+## item172    5    5   NA    5    5    5   NA    5    3    5    5    5    5    4
+## item173   NA    4   NA    5    5    5    3   NA    2    5    4   NA    5    3
+## item174   NA    5   NA    4    5   NA   NA    5    5    3    5   NA    5    4
+## item175   NA   NA   NA    5    5   NA   NA   NA    4    4    5   NA    5    5
+## item176   NA   NA   NA    4    4    5   NA    5    4    5    5    4    5    3
+## item177   NA   NA   NA   NA   NA   NA    4   NA    3   NA   NA    5   NA   NA
+## item178   NA    4    4    3    5    5   NA   NA    4    5    4   NA    5    3
+## item179   NA   NA   NA    4    2   NA   NA   NA    4    5    4   NA   NA   NA
+## item180   NA    2   NA    3    2    1    3    4    4   NA    4   NA    5   NA
+## item181    5    5    5    4    5    2   NA    5    4    5    5   NA    5    4
+## item182   NA   NA   NA   NA    2   NA    5   NA   NA   NA    4    5   NA   NA
+## item183   NA    3   NA    3    2    1    5    5   NA   NA    4   NA   NA   NA
+## item184   NA   NA   NA   NA   NA   NA   NA   NA    2   NA   NA   NA   NA   NA
+## item185   NA   NA   NA   NA    2   NA   NA   NA    3   NA   NA   NA   NA   NA
+## item186   NA    5   NA    4    5    5   NA   NA    5    3   NA   NA    5    5
+## item187   NA    5   NA    4    5   NA    2   NA    4    4    4    5    4    5
+## item188    5    5   NA    3    5    5   NA   NA    5    5   NA   NA    5    4
+## item189    4    5    5    3    5   NA   NA    4    4    5    3    5    5    4
+## item190   NA    5   NA    3    5    5    4    5    4    4    4    5    5    3
+## item191    5    5   NA    5    5    5    5    5    5    5    5    5    5    5
+## item192    5    5   NA    5    5    5    5    4    5    5    5    5    5    5
+## item193   NA    4   NA    5    5    5    2    5    5    5    4    5    5    3
+## item194   NA    4   NA    3    5    5   NA    5    4    4    4   NA    5    3
+## item195   NA    4   NA    4    5    4   NA   NA    4   NA   NA   NA   NA   NA
+## item196   NA    4    4    4    5    5   NA   NA    4   NA   NA    5    5    3
+## item197   NA   NA    5    3    5    4   NA    5    4    4   NA   NA    5   NA
+## item198   NA    3   NA    3    5    5   NA   NA    3    4    4   NA    5   NA
+## item199   NA   NA    5    3    5    5   NA    4   NA   NA    4   NA    5    3
+## item200    5   NA   NA   NA    5    5   NA   NA   NA   NA    2   NA    5    3
+## item201   NA   NA   NA    3    5   NA   NA   NA   NA   NA   NA   NA    5   NA
+## item202   NA    5   NA   NA    5   NA   NA   NA    4   NA    4   NA    5   NA
+##         V122 V123 V124 V125 V126 V127 V128 V129 V130 V131 V132 V133 V134 V135
+## item118    4    4    4    5    4    4    4    4    2    4    5    5    5    3
+## item119   NA    4    3    5    4    2    4    4    3    3    4    3    5    3
+## item120   NA    3    4    5    4    2    5    3    3    4    3    3    5    3
+## item121    5    5    4    5    4    2    5    4    4    4    5    4    5    4
+## item122    3    4    2    3    3    4    2    3    3    5    4    3    5    2
+## item123   NA    4   NA    4    4    4    4   NA    4    3    5   NA    5    3
+## item124    4   NA    3    1    3    4    5    2    2    4    5    3    5    3
+## item125    2   NA   NA   NA    3    4    3    1    3    3    3    3   NA    2
+## item126    4    4    4    3    4    4    5    3   NA    3    5    3    5    4
+## item127    2    4    4    4    4    4    3    4    2    4    5    3    5    3
+## item128   NA   NA   NA    1    3    4   NA   NA    3    3    2   NA   NA   NA
+## item129   NA   NA   NA   NA    3    4   NA   NA    4    4    2    3   NA   NA
+## item130   NA   NA   NA   NA   NA    4   NA   NA   NA    3   NA   NA   NA   NA
+## item131    4    1    5    4    3    4    3   NA    2    4    5    3    4    1
+## item132   NA    1   NA   NA   NA    4   NA   NA   NA   NA   NA    3    4   NA
+## item133   NA   NA   NA    2    3    4   NA   NA   NA   NA    4   NA   NA    2
+## item134   NA   NA   NA   NA    3    4   NA   NA   NA   NA    4   NA    4    2
+## item135    4    4    4    1    3    5    5    3    3    4    5    3    5    2
+## item136    1    2    1    1    1    4   NA   NA   NA    4    2    1    3    3
+## item137   NA   NA   NA    4   NA    4   NA   NA   NA    3   NA   NA    4   NA
+## item138   NA    2   NA    4   NA    2   NA   NA   NA    4   NA   NA    3   NA
+## item139   NA    4   NA    4   NA    2   NA   NA   NA   NA   NA   NA    4   NA
+## item140    2    4    1    5    3    2    2    2   NA    4    3    3    5   NA
+## item141    2   NA    4    3    3    2    2    3    4   NA    3    2    4    3
+## item142   NA    2    3    4    3    4    2   NA    4    4    3   NA    4    3
+## item143    3    4    2    5    3    4    4    3    4    4    2    4    5    3
+## item144   NA    4    2    3    3    4    2   NA    4    3   NA   NA    3    3
+## item146   NA   NA   NA   NA    1    4   NA   NA   NA    4   NA   NA   NA   NA
+## item147   NA   NA   NA   NA   NA    4   NA   NA   NA    4   NA   NA   NA   NA
+## item148   NA   NA   NA   NA   NA    2   NA   NA   NA   NA   NA   NA   NA   NA
+## item149   NA    4    4    5    5    2    4   NA   NA    4    5    5   NA    2
+## item150   NA    5    4    4    5    2    5    4   NA    4    5    4    5    3
+## item151   NA    4    3    4    5    2    5   NA    3    4    5    4    5    3
+## item152   NA    3    2   NA    4    4    4   NA   NA   NA    4    1    2    1
+## item153    5    4    4   NA    4    2    3    3    2    4    4    3   NA    3
+## item154   NA    4    3    5    4    2    5    5    3    3    4    3    4    1
+## item155   NA    4    3    4    4    2    5   NA   NA    5    4    3   NA    3
+## item156   NA    4    2   NA    4    2    3   NA   NA    3    4    4   NA    3
+## item157   NA   NA    3   NA    5    2    5    3   NA   NA    5    4   NA    4
+## item158   NA    4    4    3    4    2   NA   NA    3    4    5    3    5    4
+## item159   NA    4    2    2    4    4    4   NA   NA    5    3    3    5    5
+## item160   NA    5    4   NA    4    2    4   NA    4    4    4   NA   NA    4
+## item161    5   NA   NA   NA   NA   NA   NA   NA    4   NA   NA   NA   NA   NA
+## item162   NA   NA    4   NA    4    5    5   NA   NA    3    4    3    5    4
+## item163    5    4    4    4    4    4    5    5   NA    3    4    3   NA    4
+## item164    4   NA    4   NA    5    4    5    4   NA    3    5    3    5    4
+## item165   NA   NA    1    4   NA    4   NA   NA    2    4    2    3    5    4
+## item166   NA   NA    3   NA    4    4   NA   NA   NA    4    4    3    5    4
+## item167    4   NA    3   NA    4    2    5    4   NA    3    3    3   NA   NA
+## item168   NA    4    4    5    4    2    5    5   NA    5    5    4    5    3
+## item169   NA   NA    2   NA    4    4   NA   NA   NA    4    4    3    5    3
+## item170   NA    4    2    2    4    5    5   NA   NA    4    5    4    5    4
+## item171   NA    5    4    5    4    2    5    5   NA    4    5    4    5    4
+## item172   NA    4    4    5    4    4    5    5   NA    4    5    4    5    4
+## item173    4   NA    4   NA    4    4    4    5   NA    3    4    4   NA    4
+## item174   NA   NA    4   NA    4    2   NA   NA    4    4    5    3   NA    4
+## item175   NA    3    2    5    4    2   NA    5   NA    4    4    5    5   NA
+## item176   NA   NA    4    5    5    4    5    5   NA    4    4    5    5   NA
+## item177   NA   NA   NA   NA   NA    5   NA   NA   NA    4   NA    3   NA   NA
+## item178   NA   NA    4    5    5    5    4   NA   NA   NA    3    3    5   NA
+## item179   NA   NA    1   NA    5    2    4    4   NA    3    4    4   NA    4
+## item180   NA    4   NA    5   NA    2   NA   NA    3    5    3    4    5   NA
+## item181    4   NA    5    5    4    2    4    3   NA    5    3    5    5    4
+## item182   NA   NA   NA   NA    4    4   NA   NA    2   NA    1   NA   NA   NA
+## item183   NA    4   NA   NA   NA    4   NA   NA    4    4    2   NA    3   NA
+## item184   NA   NA   NA   NA   NA    2   NA   NA   NA    3   NA   NA   NA   NA
+## item185   NA   NA   NA   NA   NA    2   NA   NA    4    5   NA   NA   NA   NA
+## item186   NA    4    2    2    5    2    5   NA   NA    4    2   NA    5    5
+## item187   NA   NA    3    3    5    4    5    4   NA    4    5    4    5    5
+## item188   NA   NA    4   NA    5    4    5    3    2    4    4    4   NA    4
+## item189   NA   NA    4    5    5    2    4    4    2    5    5    4   NA    4
+## item190   NA   NA    4    5    5    4    5    5   NA    4    5    4   NA    4
+## item191   NA    4    4    3    5    5    5    4   NA    3    5    4   NA    5
+## item192   NA    4    4    3    5    5    5    4    3    4    5    4    4    4
+## item193   NA   NA    3   NA    5    4   NA   NA   NA    4    4    3    5    4
+## item194   NA   NA    3    2    5    2    5    4   NA    5    5    3    5    3
+## item195   NA   NA    4   NA   NA    4   NA   NA   NA    5    3   NA    3    4
+## item196   NA    4    5   NA    5    2    4   NA   NA    3    3    3    5    3
+## item197   NA    4    2    5    5    4    5   NA    2    5    4   NA    5    3
+## item198   NA   NA    3    4    5    5   NA    4   NA    5    4    4    5    4
+## item199   NA   NA    3    4    5    2    5   NA   NA    4    4    4   NA    3
+## item200   NA    4    3    3   NA    5    5   NA    3    4    4   NA   NA   NA
+## item201   NA   NA   NA   NA   NA    2   NA   NA    2   NA    4   NA   NA    4
+## item202   NA   NA    2   NA   NA    5   NA   NA    4    4    4    4    5   NA
+##         V136 V137 V138 V139 V140 V141 V142 V143 V144 V146 V147 V148 V149 V150
+## item118    5    3    4    4    3    3    3    4    2    4   NA    4    5    5
+## item119    4    3    2    4    4    3    4    4    2    4    3    1    4   NA
+## item120    4    3    2    4    4    4    4    4    4    5    4    4    4    5
+## item121    4    5    4    4    5    4    5    5    2    5    5    4    5    4
+## item122    3    3   NA    3    4    2    3    4    5    4    1    1    3    2
+## item123    3   NA    1    4    3    2   NA    4    4    4   NA    2    4    4
+## item124    1    4    4    2    4    3    3    2    4    4   NA    5    2    4
+## item125    2    5    2    3    3    4    5    2   NA    4    3    3    3    1
+## item126    3    5    2    5    5    3    4    4    3    5   NA    4    4    1
+## item127    3    5    2    4    2    4    5    4    4    5    2    4    4    2
+## item128   NA   NA   NA    2    3   NA   NA    3   NA   NA    3    3   NA    1
+## item129   NA   NA   NA    2    4   NA   NA    2    2   NA   NA   NA   NA   NA
+## item130   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item131    4    5   NA    2    5    3    5    4   NA    5    3    5    4   NA
+## item132    3   NA   NA   NA   NA   NA   NA    4    1   NA   NA   NA   NA    3
+## item133    4   NA   NA    2    4   NA   NA    3   NA    5    2    1   NA   NA
+## item134   NA   NA   NA   NA    4   NA   NA    3   NA   NA    2   NA   NA   NA
+## item135    3    1    2    4    2    1    2    4    4    4    2    5    3    1
+## item136   NA   NA   NA    1    2   NA   NA    4    2    2   NA    1   NA    2
+## item137   NA   NA   NA   NA   NA    1   NA    3    3    4    1   NA   NA    3
+## item138   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    3
+## item139   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    1   NA    3
+## item140   NA   NA   NA    2   NA    1   NA    4    3    4    1   NA   NA    1
+## item141    4    3    2    3    3   NA    3    2    3    5    1    2    3    2
+## item142    4    3   NA    3    2    1   NA    1    3    4    1    3   NA    2
+## item143   NA   NA   NA    3    2    2   NA    4    2    4    3    5    4    3
+## item144   NA    3   NA    3    1    1   NA   NA   NA    4    3   NA   NA    2
+## item146   NA   NA   NA   NA   NA    1    1    3   NA    5    1    1   NA    1
+## item147    4   NA   NA   NA   NA   NA   NA    2   NA    5    3    5   NA   NA
+## item148   NA   NA   NA   NA   NA   NA   NA    2   NA   NA   NA    4   NA   NA
+## item149    4   NA    2    4    5    3    2    4    3    4    5    5   NA    3
+## item150    4    4    4    4    5    5    2    4    3    4    4    4    4    5
+## item151    4    4    2    5    5    3    2    4    1    5    4    3    4    5
+## item152    1    4    1    5    4    2    1   NA    2   NA    4    1   NA    4
+## item153    4    5    3    5    5   NA    5    1    3    5    3    5    4    4
+## item154    4    5    1    4    5    4    5    4    3   NA    5    4    3    4
+## item155    3   NA    1    4    4    3    3    4    2    4    4    5   NA    4
+## item156    2    3   NA    4    5    3    3    2    2   NA    3    4   NA    3
+## item157    4   NA    3    5    5    4   NA    4    3    5   NA    3   NA    4
+## item158    3   NA    4    4    4    3   NA    4    3    5    4    4    3    4
+## item159   NA   NA   NA   NA   NA    2   NA    5    2    5    3    5    3    2
+## item160    5    4    2    4    5    1    4    3    3    5    2    4    4    4
+## item161   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item162    4    3    1    3    4    4   NA    4    4    4   NA    4    4    4
+## item163    4    4    4    5    4   NA    5    3    2    4   NA    5    5    4
+## item164    4    3    4    4    4    4    5    4    3    4    3    3    4    4
+## item165   NA   NA   NA    3    4    5   NA    4    4    5    3    3    4    4
+## item166    3   NA    2    4    4    3    4    5    3    5    3    4    4    4
+## item167    4   NA    4    5    4   NA    5    4    5    5   NA    4    4    4
+## item168    3    5    4    3    4   NA    4    5    4    5   NA    4    4   NA
+## item169    3    5   NA    5    5   NA    5    4    4    5    4   NA    4   NA
+## item170   NA   NA   NA    5    4   NA    5    4    3    5   NA   NA    4    3
+## item171    4   NA    4    4    5   NA    5    5    1    5    5    5    4    5
+## item172    5    5    4    5    5   NA    5    5    4    5   NA    5    4    5
+## item173    4   NA    4    3    4    2    4    4    3    4    3   NA    4    4
+## item174    3   NA    2    4    4   NA    4    4    4    4    4    3   NA   NA
+## item175   NA   NA    4    4    3   NA    5    3    2    4   NA   NA   NA    4
+## item176    3    5    5    5    4    5    5    4    4    4   NA    5    5    4
+## item177   NA   NA   NA    3   NA    2   NA   NA    2    5    2    3   NA   NA
+## item178    4    5    4    4    4    2    4    4    2    5    2    4    3    4
+## item179   NA   NA   NA   NA   NA    3   NA    3    4    4   NA    2   NA    3
+## item180   NA   NA   NA   NA   NA    2   NA    3    3    4    3    4    3    3
+## item181    5    5    5    4    5    3    5    3    4    4   NA   NA    5    4
+## item182   NA   NA   NA   NA    3   NA   NA    2    3   NA   NA   NA   NA   NA
+## item183   NA   NA   NA   NA   NA   NA   NA   NA    2    4   NA   NA   NA    2
+## item184   NA   NA   NA   NA   NA   NA   NA   NA   NA    5    3   NA   NA    4
+## item185   NA   NA   NA   NA   NA    2   NA   NA   NA    4   NA   NA   NA   NA
+## item186   NA   NA   NA    4    4   NA    5    5   NA   NA   NA   NA    3    4
+## item187    4   NA    4    5    4    5    5    5    3    4   NA   NA    4    5
+## item188    4    5   NA    5    4    4    5    4    4    4    4   NA    5   NA
+## item189    4    5    1    5    5    4    4    4   NA    4    4    5    4    5
+## item190    5    5    4    5    4    5    3    4    3    5    5    5    3    5
+## item191    4    5    5    5    5    5    5    5    3    5    5    5    3    5
+## item192    4   NA    5    5    4    5    5    5    2    5    5    5    3    5
+## item193    4    5   NA    5    4    4   NA    4    4    5    4    5   NA   NA
+## item194    5    5    4    4    4   NA    4    4    3    5    4    5    4    5
+## item195   NA   NA   NA    4    4    4   NA    5    4   NA   NA   NA   NA   NA
+## item196   NA    5    2    5    3    3    4    2    3    5    1   NA   NA    5
+## item197   NA    3   NA   NA    5    4    4    3    2    5    4   NA   NA    5
+## item198    4    5    4    4    5   NA    4    4    3    5   NA   NA   NA    5
+## item199   NA    5   NA    5    5    4    4    4    4    4    4   NA   NA    5
+## item200   NA   NA   NA    4    4   NA   NA    4    1   NA   NA   NA   NA    4
+## item201   NA   NA   NA   NA    4   NA   NA    3    3    4   NA   NA    4   NA
+## item202   NA   NA   NA   NA    4   NA   NA    5    1    4   NA   NA   NA   NA
+##         V151 V152 V153 V154 V155 V156 V157 V158 V159 V160 V161 V162 V163 V164
+## item118    4    4    5    4    4    4    5    3    4    5    5    4    4    1
+## item119    4    4    5    3    5    5    5    3   NA   NA    3    4   NA    5
+## item120    5    4    2    3    5    4    5    3    4    5    2    4    4    5
+## item121    4    4    5    4    5    4    5    3    5    4    5    3    2    5
+## item122    1    5    5    3    4    2    3    4    4    4    5    4   NA    4
+## item123    4    2   NA    3    4    2    3   NA    3    5    4    1    1   NA
+## item124    1    4    1    3    4    4    4    4    3    2    3    4    4    3
+## item125   NA    4   NA   NA    5    4    4    2   NA    4    5    5   NA   NA
+## item126    3    4    2   NA    5    4    5    4    5    5    5    5    5    5
+## item127    2    5    3    4    4    3    3    5    4    2    5    2    4    4
+## item128   NA    2   NA    1    2    4   NA   NA    2    5    1    5   NA   NA
+## item129    2   NA   NA    5    2    2   NA   NA   NA    4   NA   NA   NA   NA
+## item130    2   NA   NA    2   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item131    2   NA    3    2    4    4    3   NA    2    4    3    4   NA   NA
+## item132    2   NA   NA    3    2    2   NA   NA   NA    3   NA   NA   NA   NA
+## item133   NA   NA   NA    2    2    2   NA   NA   NA    5   NA   NA   NA   NA
+## item134   NA   NA   NA    2    3    3   NA   NA   NA    4   NA   NA   NA   NA
+## item135    2    4    5    2    3    2    3    4    4    4    3    5    1    5
+## item136    1    2   NA    2    1    1    3   NA    1    4    1    5   NA   NA
+## item137   NA   NA   NA    3    4    2   NA    2   NA    5    1    4    1   NA
+## item138   NA   NA   NA    1    3    3   NA    3    3    4   NA   NA   NA   NA
+## item139   NA   NA   NA    1   NA   NA    3   NA   NA    4   NA    5   NA    1
+## item140   NA    2    3   NA    4    3    3    3    2    4    3    3    1    3
+## item141    1    2    3    2    3    4    3    4    2    4    1    4    3    1
+## item142    1    2   NA    5    3    4    3   NA    2    4    2    3   NA    2
+## item143    1    2    4    2    4    4    4    4    4    5    5    5   NA    3
+## item144   NA    4   NA    5    4    1   NA   NA   NA    5   NA    4   NA    4
+## item146    1   NA   NA    4    2    2   NA   NA   NA    3   NA    4   NA   NA
+## item147    1   NA   NA    3   NA    5    4   NA   NA    5   NA    3   NA    4
+## item148    1   NA   NA    3   NA   NA   NA   NA   NA    5   NA    4   NA   NA
+## item149    2    4    5    4    4    2    5    4    5    5    4    5    1    5
+## item150    4    5    4    5    5    4    5    3    4    5    4    4    4    5
+## item151   NA    5    4    5    5    4    5    4    5    5    4    3   NA    3
+## item152   NA    2    2    5    4    1   NA    2    4    3   NA   NA    1    1
+## item153    2    4    3    5    4    5    4   NA    3    5    4    3    5   NA
+## item154    4    4    4    5    5    4    5    4    4    5    3    5    1   NA
+## item155    2    4    2    1    5    2    3    4    4    4    2    4    1    3
+## item156    2    5    4    4    4    4    5    1    3    4    3    2    4   NA
+## item157    4   NA    4    4   NA   NA    5   NA   NA    4    4    4    1    2
+## item158    4    4    4   NA    4    4    4    3    4    5    5    4    2    5
+## item159    4   NA    3    2    4    4    5    2   NA    5    3    5   NA   NA
+## item160    1    4    4    5    4    4    5    4    3    5    3   NA    3    4
+## item161   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item162    4    4    3    5    5    4    5    2    5    5    3    3   NA    5
+## item163   NA    5    4    3    5    4    5    1    5    4    4    4    4    4
+## item164    4    4    4    4    5    2    5   NA    4    4    4    4   NA    3
+## item165    4   NA   NA    3    5   NA    5   NA   NA    5    4   NA   NA    2
+## item166    4   NA    4    4    5   NA    5   NA   NA    5    4    5   NA    2
+## item167    4    5    5    3    4    4    5   NA   NA    5    3   NA    4    3
+## item168    4    5    5    5    5   NA    5   NA    4    4    5    4    4    5
+## item169    4    5    2    3    5    4    4    4    5    5    3    5   NA    4
+## item170    4    5    4    2    5    4    4   NA    5    5    4    4    3    4
+## item171    5    5    5    3    5    4    4   NA    5    5    4    5    4    5
+## item172    5    5    5    4    5    5    4   NA    4    5    5    5    4    4
+## item173    5    5    3    2    5    3    5   NA    4    4    5    5   NA   NA
+## item174   NA   NA    3    5    5    4    5    4    3    5    4    3   NA    5
+## item175   NA    3    5    5    5    4    5    4    4    4    5    4    5    5
+## item176   NA    3    5    5    5    5    5    4    4    5    5   NA    4    5
+## item177    4   NA   NA    5    5   NA    4   NA   NA    4    4    1   NA   NA
+## item178    4    4    3    5    5    4    3   NA    5    4    3    4    4   NA
+## item179   NA   NA   NA    5    4   NA    5   NA   NA    5    4    3   NA   NA
+## item180   NA    2   NA    5    4   NA    3    3   NA    5    3    2   NA    3
+## item181    4    5    5    2    5    4    5    4    4    5    5    5   NA   NA
+## item182   NA   NA   NA    5    5    4   NA   NA   NA    5    4   NA   NA   NA
+## item183   NA   NA   NA    5    5    3   NA   NA   NA    5   NA    4   NA   NA
+## item184   NA   NA   NA    5   NA   NA    5   NA   NA    5    5   NA   NA    2
+## item185   NA   NA   NA    2   NA   NA    5   NA   NA    5    5    4   NA    2
+## item186    4   NA    4    5   NA    4    5   NA   NA    5    3    4   NA   NA
+## item187    5   NA    4    5    5    5    5   NA    5    5    4   NA    2    5
+## item188    5    5    4    5    5    5    5    4    5    5    4    5   NA   NA
+## item189    5    5    3    4    5    4    5    4    4    4    3    4    2    5
+## item190    4    5    5    5    5    5    5   NA    4    5    4    4    3    5
+## item191    4   NA    5    3    5    5    5   NA    5    5    5    5    3    5
+## item192    4    5    5    5    5    4    5   NA    5    5    4    3    4    5
+## item193   NA   NA    3    5    5    4    5   NA    4    5    4    1   NA   NA
+## item194    2    4    5    5    5    4    5   NA    3    5    4    5    4    2
+## item195   NA    5    4    3   NA   NA    5    4   NA    5    4    5   NA    5
+## item196    4    5    1    4    5    4    4   NA   NA    5    4    3   NA   NA
+## item197   NA    5   NA    3    5    5    5    3   NA    5   NA   NA   NA    5
+## item198   NA   NA    2    3   NA    4    5   NA    4    5    4    4   NA   NA
+## item199    4    3    2    3    5    3    5   NA    5    5    2    5   NA    5
+## item200   NA   NA    4    2    4    3    4    3    4   NA    3    4    2    5
+## item201   NA   NA    5    4    5    3   NA   NA   NA   NA    4    2   NA   NA
+## item202   NA   NA    5    4   NA   NA    5   NA   NA    5    4    4   NA   NA
+##         V165 V166 V167 V168 V169 V170 V171 V172 V173 V174 V175 V176 V177 V178
+## item118    4    5    4    4    5    4    5    3    3    4    4    1    2    5
+## item119    4    4    4    4    4    4    5   NA    4    3   NA    3    2    4
+## item120    3    5    4    3    4    4    4   NA    4    4    4    4    2    5
+## item121    4    5    4    5    5    4    5    5    4    5    5    5    3    5
+## item122    4    3    3    2    3    4    4    3    2    3    2    5    3    4
+## item123    4    4    5    4    4    4    4    4    2    3    2    2    4    5
+## item124    5    3    2    2    4    4    5    4    5    3    4    1    2    5
+## item125    2    4    4   NA    2    4    4    3    2    3    3    3    4    4
+## item126    3    4    5    4    4    4    5    5    3    2    1    5    4    4
+## item127   NA    3    4    3    2    4    5    4    4    4    2    1    4    5
+## item128   NA    2    4   NA    2    5    1   NA   NA    2    4    2    2   NA
+## item129   NA   NA    3   NA    2    4   NA   NA   NA   NA    5    5   NA   NA
+## item130   NA   NA    4    3   NA    4   NA   NA   NA   NA    5   NA   NA   NA
+## item131   NA    5    3    4    4    4    4    5    4    4   NA   NA    4    5
+## item132   NA    3    3    3    2    4    2   NA    2    2    3   NA   NA   NA
+## item133   NA   NA    4    3    2    4    4   NA   NA    2    2    3   NA    1
+## item134   NA   NA    4   NA   NA    4    4   NA   NA    2   NA   NA   NA   NA
+## item135   NA    4    4    4    4    3    4    4    2    3    4    4    3    5
+## item136   NA    2    3   NA    1    4    1   NA   NA    1    1    1   NA   NA
+## item137   NA    1    4    1   NA   NA    1    3   NA    3    2    5   NA   NA
+## item138   NA   NA    4    3   NA    4    3   NA   NA    3   NA   NA   NA   NA
+## item139   NA    1    4    1   NA   NA    3   NA   NA    2    2    2    3   NA
+## item140   NA   NA    4    1   NA   NA   NA    3    1    3    2    5    3    5
+## item141   NA    5    4    1    3    4   NA    5    4    3    4    5    3    5
+## item142   NA    4    4    1    2    4    3    3    4    3    3    5    3    5
+## item143    3    4    4    1    4    4    5    5    3    4    4    5    3   NA
+## item144   NA   NA    4    1   NA    4    2   NA   NA    3    4    5   NA   NA
+## item146   NA   NA    4    1   NA   NA    1   NA   NA    1   NA    5   NA   NA
+## item147   NA   NA    5    5   NA   NA    4   NA    5   NA    3    5    4   NA
+## item148   NA   NA    5    5   NA   NA    4   NA    1   NA   NA   NA    4   NA
+## item149   NA   NA    4    4    4    4    5    4    3    3    4    5    4    5
+## item150    3    3    5    3    5    4    5    3    4    4    5   NA    4    5
+## item151    4   NA    4    4   NA    4    4    4    2    3    3    5    3    5
+## item152   NA   NA    3   NA    2    4    1    5    1    3    2    5    1    1
+## item153    3    4    5    3    2    5    3    5    5    4   NA    3    3    5
+## item154    3    4    5    4    4    5    5    4    2    4    1    5    2    3
+## item155   NA   NA    3    1    1    4    4    4    2    3    2    5    2    3
+## item156   NA    2    4    4    2    4    4    2    1    3    3    1    4    5
+## item157   NA    4    5   NA    3    4   NA   NA   NA    3   NA   NA   NA   NA
+## item158    3    4    5   NA    4    4    4    3    3    4    4   NA    4    5
+## item159   NA    4    5    3    3    4   NA    4    4    3    4    3    5    5
+## item160    3    2    5    3    4    4   NA    5    4    4    4    3    3    5
+## item161   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item162    2    3    5    2    5    4    4   NA    2    4    5   NA    4    5
+## item163    3    3    5    4    4    4    5    4    5    4    5    3    4    5
+## item164    3    3    4    4    5    4    4   NA    2    4    5   NA    4    5
+## item165   NA    4    5   NA    4    4    4   NA    3    3    5   NA    4    5
+## item166    5   NA    5    4    4    4    5   NA    2    3   NA   NA    4    5
+## item167    4    3    5    4    4    4    5    1    4    3   NA   NA   NA    5
+## item168    5    4    5    4    5    4   NA    3    5    3   NA    4   NA    5
+## item169   NA    4    4    4    5    4    5    2    5    4   NA    4    4    5
+## item170    5    4    5    3    4    4    5    3    4    4   NA   NA    4    5
+## item171    5    3    5    4    5    4    5    2    5    4    5   NA    4    5
+## item172    5    3    5    5    4    4    4    4    4    4   NA    4   NA    5
+## item173    4    5    5   NA    1    4    4   NA    5    3    3   NA    4    5
+## item174    5    5    5   NA   NA    4    5    2    2    4    3   NA    4   NA
+## item175    5    4    5   NA    4    4    4   NA   NA    3   NA   NA   NA    5
+## item176    5    5    5    4    4    5    5    4    5    4   NA    5    4    5
+## item177    3   NA    4    3    5    4    3   NA   NA    3    4   NA   NA   NA
+## item178    3   NA    4   NA    4    4    4    3    4    3   NA   NA    4    5
+## item179   NA    5    5   NA    2    4    5   NA    3    3   NA   NA   NA    5
+## item180    3   NA    4    3   NA    4    5   NA    2    3    4    5    3   NA
+## item181    5    4    5    4    4    4    4    5    5    4    3   NA    3    5
+## item182   NA   NA    4    3    1    4    4   NA   NA   NA   NA    5   NA   NA
+## item183   NA   NA    5    3   NA   NA    5   NA   NA    2    2    5    3    5
+## item184   NA    2    5    3   NA    4    4   NA   NA    3    3   NA    3    5
+## item185   NA   NA    5    4   NA    4    4   NA   NA    3    3    5    3    5
+## item186   NA   NA    5   NA   NA    4    4    4   NA    3   NA   NA    4    5
+## item187    4    4    5    4    4    4    5   NA    3    4   NA   NA    4    5
+## item188   NA   NA    5    4    4    4    5    3    4    4   NA    4    4    5
+## item189    5    4    5    4    5    4    4    4    5    4    4   NA    4    5
+## item190    5    5    5    4    5    4    5    3    5    4    4    5    5    5
+## item191    5    5    5    5    4    4    5    4    4    4    3    3    5    5
+## item192    5    5    5    4    4    4    4    4    5    4   NA   NA    5   NA
+## item193    5    5    5    4    5    4    4   NA    4    4   NA   NA    4    5
+## item194    4    4    5    3    4    4    5    4    2    4   NA   NA    4    5
+## item195   NA   NA    5    4   NA    4    5   NA    5    3   NA   NA   NA    5
+## item196   NA    4    5    4    4    4    4    3    4    3   NA   NA    3    5
+## item197   NA   NA    3   NA    4    4   NA   NA   NA    3    4    4   NA   NA
+## item198    4    5    5   NA    4    4    5   NA    3    3   NA   NA    4   NA
+## item199   NA   NA    4    4    4    4    5   NA    1    4   NA   NA    4    4
+## item200   NA   NA    4   NA   NA    4   NA    4   NA    4   NA    4    3   NA
+## item201   NA   NA    4   NA    4    4    4   NA    2    4   NA   NA    3    5
+## item202   NA    5    5   NA    4    4   NA    3    1    4   NA    1    4   NA
+##         V179 V180 V181 V182 V183 V184 V185 V186 V187 V188 V189 V190 V191 V192
+## item118    4    5    5    4    4    5    5    2    4    2    4    4    2    4
+## item119    3    4    4    4    3    1    3   NA    4    4    4    3   NA    3
+## item120    3    1    4    4    4    4    4   NA    4    4    3    4    3   NA
+## item121    5    5    3    5    5    5    5    5    5    5    5    4    5    5
+## item122    3    5    4    2    5    5   NA    3    3    1    4    4    2    4
+## item123    2   NA    4    4    2    5    5    4   NA    4    4   NA    2    2
+## item124    2    3    4    2    4    3    2   NA    2    2    4   NA    1    3
+## item125    1    5    3    2    2    5   NA    2    4    3    4   NA    3    2
+## item126    4   NA    4    4   NA    5    3    5    5    4    4    4    2    4
+## item127    5    5    5    3    4    5    2    4    2    4    3    5    3    3
+## item128   NA   NA    4   NA   NA   NA   NA   NA   NA    1    4   NA   NA   NA
+## item129   NA   NA    1   NA   NA   NA    1   NA    3   NA    4   NA   NA   NA
+## item130   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    4   NA   NA   NA
+## item131    5    5    4    3   NA    2    2    5    4    3    3    3    5   NA
+## item132   NA   NA    4   NA    5   NA   NA   NA   NA    2    3   NA    1   NA
+## item133   NA   NA    4   NA   NA    1    1   NA    4   NA    3   NA   NA   NA
+## item134   NA   NA    4   NA   NA    1   NA   NA   NA   NA    3   NA   NA   NA
+## item135    5    5    4    3    5    1    3    4    3    1    3    3    3    2
+## item136   NA   NA    4    4   NA   NA    1   NA    1    1    2   NA    1   NA
+## item137   NA   NA    4   NA   NA   NA   NA   NA   NA   NA    2    3    3   NA
+## item138   NA   NA    4   NA   NA   NA   NA    4   NA    4    2    3    3   NA
+## item139   NA   NA    4   NA   NA   NA   NA   NA    3   NA    3   NA    2   NA
+## item140   NA   NA    4    2   NA    1    1    1   NA    1    3    4    2   NA
+## item141    5    5    3    2    4    3    1    4    3    1    3    4    3    3
+## item142   NA    5    4    2    2    3    1   NA    4    3    3    3    2   NA
+## item143    1    5    4    4    1    3    2    5    4    3    4    2    4    2
+## item144   NA   NA    1    2   NA    3    1   NA    3    3    3   NA   NA   NA
+## item146   NA   NA    3   NA   NA   NA   NA   NA   NA   NA    3   NA   NA   NA
+## item147   NA   NA    4    2   NA   NA   NA   NA   NA   NA    4    4   NA   NA
+## item148   NA   NA    3   NA   NA   NA   NA   NA   NA   NA    4    4   NA   NA
+## item149    5    5   NA    3    5    2    4    5    4    3    4    3    4    4
+## item150    3   NA    4    4    3    4    5    4    4    4    4    1    4    3
+## item151    5    5    1   NA    5    5    5    5    4    4    3   NA    3   NA
+## item152    4    1   NA    3    4    3    3    1    3    1    2   NA    2   NA
+## item153    5    4   NA    3    3    5    1    5    5    3    4    4    3    2
+## item154    4    5    5    4    4    5    4    5    4    3    4    4    4    3
+## item155    4    3   NA    4    4    3    3    5    4    3    3    3    4    2
+## item156    3    4   NA    4   NA    5    2   NA   NA    3    4    3    2   NA
+## item157    5   NA   NA    4    5    4    5   NA    5    4    5    2   NA    1
+## item158    5   NA    3    4    4    5    4   NA    4    4    4   NA    5    4
+## item159    2    5    4   NA   NA   NA   NA    4    4    4    5    5    5   NA
+## item160    5    5    4    3    4    3    4    5    4    3    4    3    3    3
+## item161   NA   NA   NA   NA    3   NA   NA    5   NA   NA   NA   NA   NA   NA
+## item162   NA    1    4    4    5    3    2   NA    5    4    5    4    5   NA
+## item163    4    5    3    4   NA    5    4    5    5    4    5    5    5    4
+## item164    3    5    2    4   NA    3    4    5    5    4    5    5    5   NA
+## item165    1   NA    4   NA   NA    3   NA   NA   NA   NA    5    4    4   NA
+## item166    1   NA    4   NA    5    3    3   NA    5    4    4    5    5   NA
+## item167    4   NA    3    4   NA    4    5    5    5    4    4    4   NA    1
+## item168    5   NA    3    4    5    5    4    4    4    5    4   NA    5   NA
+## item169    5    5    4    3   NA    4   NA    5    5    5    5   NA    4   NA
+## item170    4    5    4   NA    3    5    4    5    5    5    3    4   NA    3
+## item171    4    5    4    4    5    5    5    5    5    5    4    5    5    4
+## item172    5    1    4    4    4    5    5    5    5    4    4    4    5    3
+## item173    4    1    1    5   NA   NA    3    5    5    4    3    3   NA    4
+## item174    4   NA    1    4   NA    4    3   NA    5    4    4   NA    4   NA
+## item175   NA   NA   NA    4   NA   NA   NA   NA    4    4    3   NA   NA    3
+## item176    4    4    3    4    3   NA    5    5    5    5    5    4    5    5
+## item177   NA    4    4    2   NA   NA   NA   NA   NA   NA    4    3   NA   NA
+## item178    4    1   NA    4   NA   NA    2    5    5    3    5   NA    2    4
+## item179   NA   NA    2    4   NA   NA   NA   NA    5    5    5    4   NA    4
+## item180   NA    5    4    2   NA   NA   NA    4    5   NA    5    4    3   NA
+## item181   NA   NA   NA    5   NA    4    2    5    5    3    4   NA   NA    5
+## item182   NA   NA    4   NA   NA   NA   NA   NA    4   NA    5   NA    3   NA
+## item183   NA   NA    3   NA   NA   NA    1    2    4   NA    3   NA    3   NA
+## item184   NA   NA    3   NA   NA   NA   NA   NA    5   NA    3   NA   NA   NA
+## item185   NA   NA    3   NA   NA   NA   NA   NA    5   NA    5    4   NA   NA
+## item186   NA   NA    4    4    4   NA   NA    5    5    5    4   NA    5   NA
+## item187   NA   NA   NA    4    4   NA    3    5    4    5    5    4    5   NA
+## item188    5    5    1    3   NA    5    5    5    5    5    3   NA    3   NA
+## item189    5    4    2    4    2    5    4    5    5    4    5    3    4    3
+## item190    5    4    5    4   NA   NA    4    5    5    4    5   NA    5    3
+## item191    4    3    5    4   NA    5    5    5    5    4    4    3    5    3
+## item192    4    5    5    4   NA    5    5    5    5    5    4   NA    5    3
+## item193    4   NA    3    4    2   NA   NA   NA    4    5    5    4    5    4
+## item194    4   NA    3    4    1    3    5   NA    5    5    5    4    4   NA
+## item195   NA   NA   NA    4   NA   NA   NA   NA    5    5    3   NA   NA   NA
+## item196    4   NA   NA    3    1    4    2    5    5    4    4   NA    1    4
+## item197    5   NA   NA   NA    5   NA   NA    4    5    4   NA   NA    2   NA
+## item198    5   NA   NA    4   NA   NA   NA   NA   NA    4    5   NA   NA    3
+## item199    4   NA   NA    3   NA   NA   NA    5    5    4    3   NA    4   NA
+## item200   NA   NA   NA   NA   NA    5    4   NA    4    4    3   NA    4   NA
+## item201   NA   NA   NA   NA   NA   NA   NA   NA   NA    4    3   NA   NA   NA
+## item202   NA   NA   NA    4    5   NA   NA   NA   NA    4    5    4    5    2
+##         V193 V194 V195 V196 V197 V198 V199 V200 V201 V202 V203 V204 V205 V206
+## item118    2    4    5    3    4    5    4    4    5    3    2    4    2    5
+## item119   NA    4    4    4    4   NA    4   NA    5    3    1    4   NA    4
+## item120    3    4    3    4    5   NA    4   NA    5    4    4    4   NA    5
+## item121    4    3    5    4    4    5    4    4    5    4    3    5    2    5
+## item122    4    4    4    3    4    3    4    2    4    4    3    4    4    2
+## item123    2    4    5    4    4    5   NA   NA    3    4    4    4    2   NA
+## item124    3    5    3    4    4    2    4    4   NA    3    1    3    2    3
+## item125    2   NA    4    3    4    3    5   NA    5    3    2    3    4    3
+## item126    4    3    5    4    4    5    4    4    5    4    3    4    4    5
+## item127    2    4    5    4    4    4    4    4    5    3    3    4    2    5
+## item128   NA    1    4    3    5    3    2    1   NA   NA    1    3    2   NA
+## item129   NA   NA    4    3    4   NA    3   NA   NA   NA    3   NA   NA   NA
+## item130   NA   NA   NA    3   NA    4    3   NA   NA   NA   NA   NA   NA   NA
+## item131   NA    3    4   NA    3    3    3    1    5    4    4    4    3    3
+## item132   NA   NA    1    3   NA   NA    3    1   NA   NA   NA   NA   NA   NA
+## item133   NA    2   NA    3    1    2    3   NA   NA   NA    3    4   NA    2
+## item134   NA   NA    3    3    2    3    3   NA   NA   NA   NA    3   NA    2
+## item135    2    4    5    3    3    3    4    3    5    4    4    3    4    2
+## item136   NA    1    1    3    1    2    2    1   NA    2    1    4   NA   NA
+## item137   NA    2   NA    3    1    2    2    1    1    3    1    2    2    2
+## item138   NA    4   NA    3   NA    4    2   NA   NA    3   NA    4    2   NA
+## item139   NA   NA   NA    3   NA    4    2   NA   NA    3    1   NA    2   NA
+## item140    2    2    1    3    4    3    4    3    3    3    1    4    3    1
+## item141    2    4    5    3    3    2    3    1    5    2   NA    3   NA    1
+## item142    2    2    1    3    3    3    3    1    3    4    3    3    3    1
+## item143    3    2    5    4    4    4    3    4    5    4    3    4    5    1
+## item144   NA    3   NA    3    2    3    3    1   NA    4    3    4    2    1
+## item146   NA   NA   NA    3   NA   NA    3   NA   NA   NA    3   NA   NA   NA
+## item147   NA    2   NA    3   NA    5    5   NA   NA   NA    4    4   NA    4
+## item148   NA   NA   NA   NA    4   NA   NA   NA   NA   NA   NA    3   NA    4
+## item149   NA    4    5    3    4    4    4    5    4    5    5    4    4    5
+## item150   NA    5    3    4    3    5    4   NA    4    2   NA    4    4    5
+## item151   NA    4    5   NA    4    4    4   NA    5    5    5    4    4    4
+## item152   NA    4    3    3    3    1    4   NA   NA    1    4    3   NA    1
+## item153    4    5    5    3    5    4    5    4    5   NA    4    2    4    4
+## item154   NA    4   NA    4    5    5    4    4    3    2    4    5    4    4
+## item155   NA    5    5    4    2    1    4    1    1    2    2    2    1    5
+## item156    2    5   NA    4    3    2    4    3   NA   NA    3    1   NA    5
+## item157   NA    4    5    4    4    3    4   NA    4    4   NA    4   NA    5
+## item158   NA    5    3    4    4    5    4    3    5    3    4    4   NA    5
+## item159   NA    5    3    4    5    5    3    3    5    4    5    3    1    5
+## item160   NA    4    5    4    3    2    4   NA    4    2   NA    4    2    5
+## item161   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item162   NA    3    5    5    4    4    4   NA   NA   NA    3    3   NA    5
+## item163    2    4    5    5    4    4    4   NA    5    3    4    2    4    5
+## item164    4    5    3    5    5    3    5    4    5    2    4    2    4    5
+## item165   NA    4   NA    5    4    5    4   NA    5    4    4    4    2    4
+## item166   NA   NA   NA    5    4    5    4   NA    5    4    4    3   NA    5
+## item167    4    4    4    4    4    5    5   NA    5   NA    3    3   NA    5
+## item168    2    5    5    5    4    5    5   NA    5   NA   NA    4    2    5
+## item169   NA    4    4    4    4    5    4   NA    1   NA    5    5    4    5
+## item170    4    5    4    4    5    5    5   NA    4   NA    5    3    5    5
+## item171   NA    5    5    5    4    5    5   NA    5   NA    5    4    4    5
+## item172    2    5    5    5    5    4    4   NA    3   NA    5    4    4    5
+## item173    4    4    4    4    5    4    3    4   NA   NA    4    3    3    5
+## item174   NA    4    3    4    4    3    3   NA   NA   NA   NA    3    2    4
+## item175   NA    5    4    4    4    4   NA   NA   NA   NA   NA    2    4    5
+## item176    2    3    5    5    4    5    4   NA    5   NA    5    4    4    5
+## item177   NA   NA   NA    4    4    4    4   NA   NA   NA   NA    2   NA   NA
+## item178   NA   NA   NA    4    4    4    3    4    5   NA   NA    4    4    5
+## item179   NA    2    5    4    4    5    4   NA    5   NA   NA    2   NA    5
+## item180   NA   NA    5    4    2    4    3   NA   NA    4    5    4    4   NA
+## item181    4   NA    5    4    5    5    4   NA    5    5   NA    2    5    5
+## item182   NA   NA   NA    4    2    5    3   NA   NA   NA    5    4   NA   NA
+## item183   NA   NA   NA    4    2    4    3    4   NA    5    4    2    4    2
+## item184   NA   NA   NA    4    4    5    4   NA    5   NA   NA    3    2    4
+## item185   NA   NA   NA    4    4    5    4   NA   NA   NA    4    4   NA    4
+## item186   NA    5    4    4    5    5    4   NA   NA   NA   NA   NA   NA    5
+## item187   NA    4   NA    4    5    5    4   NA   NA   NA    4    4    2    5
+## item188   NA    4    5    3    4    4    5   NA    3   NA    3    2    4    5
+## item189   NA    4    4    4    5    4    5   NA    4    4    3    4    4    5
+## item190    2    4    4    5    3    5    4   NA    4   NA    5    5    5    5
+## item191    2    4    5    5    4    5    4    5    5    4   NA    5    5    5
+## item192   NA    4    5    4    5    4    4    5    4    5    5    4    4    5
+## item193   NA    3    5    5    4    4    4   NA   NA   NA   NA    2    4    5
+## item194    2    3    5    4    5    4    5   NA    5   NA    4    2    4    5
+## item195   NA    2   NA    4    4    4    5    3   NA   NA   NA    4   NA    5
+## item196   NA    3    4    4    4    4    4    4   NA   NA    3    4   NA    5
+## item197   NA    3    5    3    3    4    5   NA   NA    5    3    4    4    5
+## item198   NA    3   NA    4    4    5    4   NA    5   NA   NA    4    4    5
+## item199   NA    4    4    4    3    4    4   NA    3   NA    4    5   NA    4
+## item200   NA    4    5    3    4    3    5   NA   NA   NA   NA    2    5    3
+## item201   NA    5   NA    3    4   NA   NA   NA   NA   NA   NA    2   NA    5
+## item202   NA    4   NA    4    4   NA    4   NA   NA   NA   NA    4    4    4
+##         V207 V208 V209 V210 V211 V212 V213 V214 V215 V216 V217 V218 V219 V220
+## item118    3    4    4    4    4    2    5    4    5    1    2    2    5    4
+## item119    4    4   NA    4    5    4    4    4    5    4    3    2    5    4
+## item120    4    4    3    2    4    4    4    4    5    4    4    1    5    4
+## item121    5    4    4    4    5    5    5    5    5    5    5    4    5    4
+## item122    3    2    3    2    5    1    4    4    2    2    3    3    5    3
+## item123    4    4   NA    2    4    2   NA    3    3    4    4    2    5    4
+## item124    1    4    3    4    4    5    2    2    2    1    2    2    3    2
+## item125    3    4    3   NA   NA    4   NA    3    3    3   NA    4    5   NA
+## item126    2    4    3    4    4    2    2    4    3    4    5    4    5    4
+## item127    4    4    4    3    4    2    5    2    3    1    3    4    5    4
+## item128    1   NA   NA   NA   NA   NA    3   NA   NA   NA    1   NA   NA    3
+## item129    2   NA   NA    2   NA   NA    3   NA   NA   NA   NA   NA   NA    3
+## item130    3   NA   NA   NA   NA    1   NA   NA   NA   NA   NA   NA   NA   NA
+## item131    4    4    5    4    5    1    4   NA   NA    5    4    3    5    3
+## item132    1    4   NA    2   NA    1    3    3   NA   NA    2   NA   NA   NA
+## item133   NA    1   NA   NA   NA    5    2   NA   NA   NA    3   NA   NA    3
+## item134    2    1   NA   NA   NA    5    2   NA   NA   NA    3   NA   NA    3
+## item135    3    4    1    4    4    4    3    4    4    5    4    4    5    3
+## item136    1    4   NA    2   NA    1    1   NA    2   NA    1   NA    1    3
+## item137    2   NA   NA   NA   NA    4    3   NA   NA   NA   NA    2    1    3
+## item138    2   NA   NA   NA   NA    4    3   NA   NA   NA   NA   NA   NA   NA
+## item139   NA   NA   NA   NA   NA    4    2   NA   NA   NA   NA   NA    1   NA
+## item140    3   NA   NA   NA   NA    4    2    4   NA    4    3    2    3   NA
+## item141    3    5    5    2    5    4    2    3    3    4    3    2    4    3
+## item142    3    4   NA    1   NA    4    2    3   NA    4    3    3    4    3
+## item143    5    2   NA    4   NA    4    4   NA   NA    5   NA    3    5    3
+## item144    4    1   NA    4   NA    1    3   NA   NA   NA   NA   NA    4   NA
+## item146    1   NA   NA   NA   NA    1    1   NA   NA   NA    2   NA   NA   NA
+## item147    4   NA   NA    4   NA    5    5   NA    3   NA    5   NA    5    5
+## item148    4   NA   NA   NA   NA    4   NA   NA   NA   NA    5   NA    5    5
+## item149    4    4   NA    4   NA    5    3    4    4    5    4    4    5    5
+## item150    5    4    5    5   NA    4    5    4    4    5    4    4    5    4
+## item151   NA    3    5    4   NA    1    5    3    4    5    4    3    5    5
+## item152    3    4   NA    2   NA    1    1    4    3    4    2    1    5   NA
+## item153    4    5    5    4    5    1    5    5    4    5    5    5    5    5
+## item154    5    5    2    5   NA    4    5    5    4   NA    5    2    5    5
+## item155    5    5   NA    2   NA    1    2    4    3    4    4    1    5    4
+## item156    4    5   NA    2   NA    1   NA    4    3    2    3    3    5   NA
+## item157    3    4    3   NA   NA    4    5   NA   NA   NA    5   NA   NA   NA
+## item158    3    4    1    4   NA    4    2    5    5    5    4    4    5    4
+## item159    4   NA   NA    3   NA    4    3   NA    3   NA    5    4    5    3
+## item160    4    4    3    4   NA    2    4    4    4    5    4    3    5    3
+## item161   NA   NA   NA   NA    4   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item162    5    2   NA   NA   NA    5    5    3   NA   NA    5    3    5    4
+## item163    5    2    4    4    5    5    5    4    5    5    4    4    5    4
+## item164    5    5   NA    2   NA    1    5    4    4    5    4    4    5    4
+## item165    5   NA   NA   NA   NA    4    5   NA   NA   NA    4   NA    5    5
+## item166    4   NA   NA    4   NA    4    5    4    4    5    4    4    5    5
+## item167    5    4   NA    4   NA    4    5    4    3   NA    4    4    5    4
+## item168   NA    4    4    4   NA    4    4    4    5   NA    5    5    5    5
+## item169    3    4   NA    5   NA   NA    4    4    4    4    5    4    5   NA
+## item170   NA    4   NA    4   NA    4    4    4    4    5    4    4    5    5
+## item171    5    5    4    5   NA   NA    5    4    4    5    5    5    5    5
+## item172    5    4    5    5    5    4    5    4    4   NA    4    5    5    5
+## item173    5    1   NA    4   NA   NA    5    4    4    5    4    5    5    5
+## item174   NA    5    4   NA   NA   NA    4    3    3   NA    4    5   NA    5
+## item175   NA    5    2    2   NA   NA    3    3   NA   NA   NA   NA   NA    5
+## item176    5    2    5    2    5    5    5    4    4    5    5    5   NA    5
+## item177    4   NA   NA   NA   NA   NA    3   NA   NA   NA    4   NA   NA    2
+## item178   NA    4    5    4    5   NA   NA    3    4    4    4    4    5    2
+## item179    3   NA   NA   NA   NA    5    5   NA   NA   NA    5   NA   NA    5
+## item180    4   NA   NA   NA   NA    5    4   NA   NA    2   NA   NA    4    3
+## item181    5    4    4    4    5    3    5    4    4    5   NA    4    5    3
+## item182    3   NA   NA   NA   NA    4    3   NA    4   NA   NA   NA   NA   NA
+## item183    2   NA   NA   NA   NA    5    2   NA   NA   NA   NA   NA   NA    3
+## item184    4   NA   NA   NA    4   NA    4   NA   NA   NA   NA   NA    5    3
+## item185    5   NA   NA   NA   NA    1    5   NA   NA   NA   NA   NA   NA    3
+## item186    4   NA   NA    3   NA    5   NA    4    3   NA    5    5    5   NA
+## item187   NA    3    3    4   NA   NA    4    4   NA   NA    5    5    5   NA
+## item188   NA    4    4    5    4   NA    3   NA    5    3    4    4    5   NA
+## item189   NA    4    4    4   NA    1    5    5    4    4    4    3    5    3
+## item190    5    4    5    5   NA    5    5    4    4   NA    4    4    5    5
+## item191    4   NA   NA    5   NA    5    5    5    4   NA    5    5    5    5
+## item192   NA    4    5    4   NA    5    5    5    4   NA    5    3    5    5
+## item193    5    4   NA    4   NA    5    4    4   NA   NA    4    5    5    5
+## item194    4    4    5    5    4   NA    5    4    3   NA    4    4    5    5
+## item195   NA    4   NA   NA   NA    5    3   NA   NA   NA    5    5   NA    5
+## item196    4    4    5    2   NA   NA    4    4    3    5    3    4    5   NA
+## item197   NA   NA   NA    4   NA   NA   NA   NA    3    5    3    3    5   NA
+## item198   NA   NA    2    4   NA    4    4    4   NA   NA    4    4    5    5
+## item199    2   NA   NA    2   NA    4   NA    4    4    4    4    4    5   NA
+## item200   NA    4   NA   NA   NA   NA   NA   NA   NA    5    3   NA   NA   NA
+## item201   NA    4    1   NA   NA   NA   NA    4   NA   NA    4    4    5    5
+## item202    5    4   NA   NA   NA   NA   NA    4   NA   NA    5   NA    5   NA
+##         V221 V222 V223 V224 V225 V226 V227 V228 V229 V230 V231 V232 V233 V234
+## item118    4    5    2    3    5    5    4    4    5    4    4    4    5    4
+## item119    5    5    2   NA    4    5    4    5   NA    5   NA    4    5    4
+## item120    5    5    3    3    4    5    4    5    3    5    4    4    5    4
+## item121    4    4    2    4    4    5    5    5    5    5    5    5    5    5
+## item122    3    3    4    4    3    5    2    3    1    1    4    1    2    1
+## item123    4    2   NA   NA    4    5    5   NA    3   NA   NA   NA    5    4
+## item124    5    5    3    2    4    4    1    4    5    4    3    3    2    4
+## item125    5    4    4   NA    4    4    4    5    2    4    4    1    1    4
+## item126    5    4    4    5    4    5    5    5   NA    5    4    4    5    5
+## item127    5    2    2    5    4    4    4    3    5    3    5    4    5    5
+## item128   NA    5   NA   NA    1   NA    2   NA   NA   NA    3   NA   NA    2
+## item129   NA    2   NA   NA   NA   NA    4   NA   NA    3   NA   NA   NA   NA
+## item130   NA   NA   NA   NA   NA   NA    4   NA   NA   NA   NA   NA   NA   NA
+## item131    1    3    2    5    5    4    3    4   NA    4    3    4    3    4
+## item132   NA    2   NA   NA   NA   NA    2   NA   NA   NA   NA   NA   NA    2
+## item133    1   NA   NA   NA   NA   NA    4   NA   NA   NA   NA   NA   NA   NA
+## item134   NA   NA   NA   NA   NA    5    4   NA   NA   NA   NA   NA   NA   NA
+## item135    1    5    2    4    4    5    4    1    2    1    3    3    4    3
+## item136   NA    2   NA   NA    1   NA    1   NA   NA   NA   NA   NA   NA    1
+## item137    1    1   NA   NA   NA    4    2   NA    3   NA   NA   NA   NA    2
+## item138   NA    3   NA   NA   NA   NA    4   NA   NA   NA   NA   NA   NA   NA
+## item139   NA    2   NA   NA   NA   NA    3   NA   NA   NA    3   NA   NA   NA
+## item140    1    2    4    3    4    4    2   NA    2   NA   NA    2   NA    2
+## item141    1   NA    3    3    3   NA    4    3    2    4    3    2    3    3
+## item142    1    2   NA    3    3    4    4    4    2    2   NA   NA   NA   NA
+## item143    1    4   NA    4    4   NA    5    3    4   NA    4    2    3    4
+## item144   NA    2   NA   NA   NA    5    4    3   NA    1    3   NA   NA   NA
+## item146   NA   NA   NA   NA   NA   NA    2   NA   NA   NA   NA   NA   NA    1
+## item147   NA    4   NA   NA   NA    5    5   NA   NA   NA   NA   NA   NA   NA
+## item148   NA   NA   NA   NA   NA   NA    5   NA   NA   NA   NA   NA   NA   NA
+## item149    1    5   NA    5   NA    5    5    5    1    5    5    3    5    4
+## item150    5    4    4    5    4    5    5    5   NA    4   NA    4    5    5
+## item151    5    5    4    5    4    5    5    5   NA    5    4   NA    4    4
+## item152    5    4    3    4    3    4    4    3   NA    1   NA   NA    1    1
+## item153    1   NA    4    5    4    4    4    5    3    4    4    4    5    5
+## item154    5    2    4    5   NA    5    5    4   NA    5    4    4    4    3
+## item155    5    4   NA    4   NA    5    2    4    1    2    4    1    2    2
+## item156    1   NA    2    4    3    4    2    3    2    3   NA    4    5    4
+## item157   NA   NA    1    5    4   NA    4   NA   NA    3   NA    4   NA    4
+## item158    5    5   NA    2    4    5    4    5   NA    1    5    4    5    3
+## item159    1    5   NA   NA    5    5    5    3   NA   NA    4   NA    4   NA
+## item160    1    3    1    4    4    4    4    5   NA    4    4    3    5    4
+## item161   NA   NA   NA   NA   NA   NA   NA   NA    2   NA   NA   NA   NA   NA
+## item162    5    4    2    3    4    5    5    3   NA    3   NA   NA    4    4
+## item163    5    4    3    4    4    5    5    5    5    4    4    5    5    4
+## item164    5    5    5    4    4    5    5    5    5    4    4    5    5    4
+## item165    5    4    4   NA   NA    5    4   NA   NA   NA   NA   NA   NA    4
+## item166    5    5    3   NA   NA    5    5    5   NA   NA    4   NA    4    4
+## item167    5    4   NA    5   NA    5    4    5    5    4    5    5    5    4
+## item168    5    5   NA    5   NA    5    4   NA   NA    5    5    5    5    5
+## item169    5    4    4    5    4    5    5    3   NA    4    5    5    5    3
+## item170    5    2    4   NA    4    5    5    5    5    4    5    4    5    4
+## item171    5    5    3    5    5    5    5    5    5    5    5    5    5    5
+## item172    5    5    4    4    5    5    5    4    3    5    5    5    5    5
+## item173    5    3    4    3    4   NA    5   NA    5    3    5    5    5    4
+## item174    5    4    3    4   NA   NA    4    3   NA    5   NA    4    5    4
+## item175    5   NA    2   NA    4   NA    5   NA    5   NA    5    5   NA    4
+## item176    5    5    5    5    5    5    4    5    5    5    5    5    5    5
+## item177    1    2   NA   NA    3    5    4   NA   NA   NA    4   NA   NA    1
+## item178    5    4    2    4    4    4    5    5    5    3    4    5    5    3
+## item179   NA    3    3    4   NA   NA    5   NA   NA   NA    5    4   NA    4
+## item180    1    1   NA   NA   NA    5    4   NA   NA   NA    3   NA    3    2
+## item181    5    2    4    5    5   NA    4    5    5    5    5    4    5    5
+## item182   NA   NA   NA   NA   NA   NA    5   NA   NA   NA   NA   NA   NA   NA
+## item183   NA    1   NA   NA   NA    5    4   NA   NA   NA   NA   NA   NA   NA
+## item184   NA    2   NA   NA   NA   NA    4   NA   NA   NA    4   NA    3    3
+## item185   NA    2   NA   NA   NA   NA    5   NA   NA   NA   NA   NA   NA   NA
+## item186    5    3    4   NA   NA    5    5    5   NA    3   NA    4    5    4
+## item187    5    5   NA    4    5    5    5   NA   NA    4   NA    5    5    4
+## item188    5   NA    4    5    4   NA    5   NA   NA    5    4    2    5    4
+## item189    5    4    4    4    4    5    4    5    2    4    5    4    5    4
+## item190    5    5   NA    5    5    5    4    4   NA    5    5    4    5    5
+## item191    5    5   NA    5    5    5    5   NA   NA    5    5    5    5    5
+## item192    5    5   NA    5    4    5    5   NA   NA    5    5    5    5    5
+## item193    5    3    4    5    4    5    4   NA   NA   NA   NA    4    5    4
+## item194    5    5    4    4    5    5    4    3    4    3    4    5    4    4
+## item195   NA    4   NA   NA    4   NA    5   NA   NA   NA   NA   NA    5    4
+## item196    5    4    4    5    4    4    4   NA   NA    3    4    3    5    4
+## item197    5    5    4    5    4    5    4   NA   NA    3   NA   NA   NA    4
+## item198    5   NA   NA    5   NA    4    4    3    2    4    4    4    5    4
+## item199   NA    4    4    5    3    5    5    4   NA    2    5    2    5    3
+## item200   NA   NA   NA   NA   NA    3    5   NA   NA    2   NA    4    4    3
+## item201   NA   NA   NA   NA   NA   NA    4   NA   NA   NA   NA   NA    5    2
+## item202   NA    5   NA   NA   NA    5    4   NA   NA   NA   NA    4    5    4
+##         V235 V236 V237 V238 V239 V240 V241 V242 V243 V244 V245 V246 V247 V248
+## item118    5    4    5    5    4    5    1    5    4    4   NA    5    5    4
+## item119    3    4   NA    4    2    4   NA    5    4   NA   NA    4    4    4
+## item120    3    3    3    5    1    3    1    5    4    2   NA    5    4    4
+## item121    3    5    5    5    5    3    5    5    5    2    5    5    4    5
+## item122    5    3    3    5    1    1    4    4    4    2    5    5    5    4
+## item123    5    4   NA   NA   NA   NA   NA    5    5    2    5    5    5    5
+## item124    1    4    5    5    1    2    4    5    3    2    3    2    4    4
+## item125    5    3    3    4   NA   NA   NA    4    4    1    3    2    1    5
+## item126    5    5    5    5    4   NA   NA    5    4    2    4    4   NA    4
+## item127    5    5    5    4    1    2    5    5    4    2    5    3    3    3
+## item128   NA    1   NA   NA   NA   NA    1   NA   NA   NA   NA   NA   NA    2
+## item129   NA   NA   NA   NA   NA   NA   NA   NA    1   NA   NA   NA   NA   NA
+## item130   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item131    4    3   NA    5    1    2   NA    4    5    4    3   NA    5    2
+## item132    1   NA   NA    3   NA   NA   NA   NA    4   NA   NA   NA    4   NA
+## item133    1   NA   NA   NA   NA   NA    1    4    4   NA   NA   NA    3   NA
+## item134   NA   NA   NA   NA   NA   NA    2   NA    4   NA   NA   NA    2   NA
+## item135    4    3    3    5    1    4    2    4    5    3    3    3    5    4
+## item136    3   NA   NA    3   NA    1    1    1    5   NA   NA   NA    5   NA
+## item137    1   NA   NA   NA   NA   NA   NA    1   NA    2    1   NA    5   NA
+## item138   NA   NA   NA   NA   NA   NA    4    1   NA   NA    2   NA   NA   NA
+## item139    2   NA   NA   NA   NA   NA   NA   NA    5   NA   NA   NA   NA   NA
+## item140    5   NA   NA   NA    1    4    4    2    5    2    4   NA    5   NA
+## item141    5    3    3    5    1    1    5    2    5    1   NA    3   NA    3
+## item142    1    3   NA    5   NA    1    3    2    5    3    5    3    5   NA
+## item143    5   NA   NA   NA   NA    4   NA    5    4    3    5   NA    5    3
+## item144   NA   NA   NA    4   NA    3   NA   NA    5    3   NA   NA    5   NA
+## item146   NA   NA   NA   NA   NA   NA    1    1   NA   NA   NA   NA    2   NA
+## item147   NA   NA   NA    3   NA    1   NA   NA    4    2   NA   NA   NA   NA
+## item148   NA   NA   NA   NA   NA    1   NA   NA   NA   NA   NA   NA   NA   NA
+## item149    5    4   NA   NA    1    4    4    4    5    4    5    5   NA   NA
+## item150    4    3   NA    5    4    4    4    5    5    4    5    5    5    4
+## item151    5   NA   NA    5    4    5    4    5    5    3    5    5    5    4
+## item152    4   NA   NA    4    1   NA    3    4    2    3    5   NA   NA   NA
+## item153    5    5    3    5    1    2   NA    5    4    3    5    5    2    4
+## item154    4    4   NA    5   NA    5    3    5    5    4    5    5    5    4
+## item155    4    3   NA   NA    1    5    2    5    4    2    5    3   NA   NA
+## item156    1   NA   NA    5    1    2   NA    5    4    4   NA    5   NA    2
+## item157    4    5   NA    4    4    4    4    5    5    4   NA    3    5   NA
+## item158    3    4   NA    5    4    4    4    5    5    2   NA    5    4    4
+## item159    2   NA   NA    4   NA    4    5    4    5    1    4    4    4    4
+## item160    5    4   NA    5    1    2    1    5    4    3    4    5    3    4
+## item161   NA   NA    3   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item162    4    4   NA    5   NA    3   NA    5    4    2   NA    5    4    5
+## item163    5    5    3    5    1    5   NA    5    5    2    5    5    4    5
+## item164    4    5    5    5    1    5   NA    5    4   NA   NA    5    4    5
+## item165    4   NA   NA   NA   NA    4    5    5    4   NA   NA   NA    4   NA
+## item166    2    5    3   NA   NA    4    3    5    4   NA   NA   NA    4   NA
+## item167   NA    5    5    4   NA    4   NA    5    4   NA   NA    5    4   NA
+## item168    5    5    5    5    1    4   NA    5    5   NA   NA    5    2   NA
+## item169    3   NA   NA    5    1   NA    3    5    3   NA   NA    5    2    5
+## item170    5    5   NA    5    1    4   NA    5    5   NA    5   NA    1    5
+## item171    4    5    5    5    1    5   NA    5    4   NA    5    5    4    5
+## item172    5    5    5    5    5    4   NA    5    5    4    5    5    3    5
+## item173    3    5    3    4   NA   NA   NA    5    3    1   NA    5    3    5
+## item174    5    3   NA    4   NA   NA   NA    5    4   NA   NA   NA    4   NA
+## item175    5    5    3   NA   NA   NA   NA    5    5   NA   NA   NA    2    5
+## item176    5    5    3    5    5    4   NA    5    5   NA    5    5    5    5
+## item177    1   NA   NA   NA   NA   NA   NA    5   NA   NA    5   NA    1   NA
+## item178    5    5    5    4    1    3   NA    5    4   NA   NA    5    3    5
+## item179    3    5   NA   NA   NA   NA   NA    5   NA   NA   NA   NA    4   NA
+## item180    3   NA   NA   NA   NA    4   NA    2    4    2    3   NA    4   NA
+## item181    5    5    5    5    1    4   NA    5    4    1   NA    5    3    5
+## item182    1   NA   NA   NA   NA   NA   NA    5   NA   NA   NA   NA    4   NA
+## item183    1   NA   NA   NA   NA   NA    4    2    4    3    3   NA    5   NA
+## item184    4   NA   NA   NA   NA   NA   NA   NA   NA   NA    4   NA   NA   NA
+## item185    2   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item186    4   NA   NA   NA    4    4   NA    4    5   NA    5   NA    5   NA
+## item187    5    4   NA    4   NA    4   NA    5    5    4    5   NA    5   NA
+## item188    5   NA   NA    5    4    4   NA    5    4   NA   NA   NA    5    4
+## item189    2    5   NA    5    4    3   NA    5    4    3    5    5    2    5
+## item190    5    5   NA    5   NA    5    5    5    5    4    5    5   NA    4
+## item191    5    5   NA    5    4    5    5    5    5    4    5    5   NA   NA
+## item192    5    5   NA    5    4    5    5    5    5   NA    5    5    5    5
+## item193    5    3   NA   NA   NA    4   NA    5    5   NA   NA    5   NA   NA
+## item194    4    5   NA    4   NA    4   NA    5    4   NA    5    5    5   NA
+## item195    5   NA    5    5    4   NA   NA    5    5   NA   NA   NA    3   NA
+## item196    2    5    5    4    1   NA   NA    5    4   NA   NA    5    4    4
+## item197    5   NA   NA    4   NA    4   NA    2    5    3    3   NA    5   NA
+## item198    4    4   NA    4   NA   NA   NA    5   NA   NA   NA   NA   NA    5
+## item199    4   NA   NA    5   NA   NA   NA   NA    2    3    5   NA   NA    3
+## item200    5   NA   NA    5   NA   NA   NA   NA   NA    4    5   NA    4   NA
+## item201    4   NA   NA   NA   NA   NA   NA    5    4   NA    5   NA   NA   NA
+## item202    5   NA   NA   NA   NA    4   NA    4    5   NA    5   NA    5   NA
+##         V249 V250 V251 V252 V253 V254 V255 V256 V257 V258 V259 V260 V261 V262
+## item118    4    5    1    5    4    5    5    4    5    3    4    4    2    4
+## item119    3    5   NA   NA    4    5    4   NA    4    4    4    3    2    2
+## item120    4    5    3   NA    4    4    5   NA    5    3    4    3    4    2
+## item121    2    5    4    5    4    5    3    4    4    4    5    3    5    5
+## item122    5    2    3   NA    1    1    2    4    5    3    4    2    1    5
+## item123    1   NA    5    4    4   NA    3   NA   NA   NA    4   NA    4    4
+## item124    4    2    4    3    4    1    5   NA    4    4    5    1    2    5
+## item125    3   NA    5   NA    4    1    2   NA    1    3    5    2    3    2
+## item126    2    4    3   NA    5    4    5    4    4    3    5    2    4   NA
+## item127    4    4    5    5    5    4    2    5    5    4    5    2    2    4
+## item128   NA   NA    1   NA   NA   NA   NA   NA   NA    4    5   NA   NA   NA
+## item129   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    5   NA   NA   NA
+## item130   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item131   NA   NA    5    3   NA    3    2    1    5    4    5    3   NA    4
+## item132   NA   NA    1    3   NA   NA   NA    1   NA   NA    5   NA   NA   NA
+## item133   NA   NA   NA    3    2   NA   NA   NA   NA   NA    5   NA   NA   NA
+## item134    4   NA   NA    3    2   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item135    1    2    4    4    4    4    1    2    3    4    5    5    1    4
+## item136   NA   NA    5    2   NA   NA   NA    1   NA   NA   NA   NA    5   NA
+## item137   NA   NA   NA   NA   NA   NA   NA   NA    3    4    2   NA    3   NA
+## item138   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item139   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    2   NA   NA   NA
+## item140    4   NA    4    4    2   NA   NA    3    1    5    2   NA    3    5
+## item141    3    2    5   NA    1    3    3    4    4    3    2    3    2    3
+## item142    2   NA    1    3    1    3   NA    2    2    4    2    3    3    3
+## item143    3   NA    4   NA    3   NA   NA    4    2   NA    4    3    5    5
+## item144    3   NA   NA    3   NA   NA   NA    1    1    3    2    3    3   NA
+## item146   NA   NA   NA   NA   NA   NA   NA    1   NA   NA   NA   NA   NA   NA
+## item147   NA   NA   NA   NA   NA   NA   NA    4   NA    3   NA   NA   NA   NA
+## item148   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item149    3    5    5    4    5    4    1   NA    4   NA    5   NA    5    3
+## item150    4    5    1    5    4    5    5   NA    3    4    5    4    5    4
+## item151    4    4    5    5    4    4    5   NA    3    4    5    5    4    3
+## item152    4   NA    4   NA   NA   NA    4   NA   NA    4    1   NA    2    2
+## item153    2    4    5    3    5    3    3    4    5    4    5    3    5    5
+## item154    4    5    4    5    4    4    5    4    4   NA    1    5    5    5
+## item155    4    5    4    5    4    4    5   NA    1   NA    1   NA    2    4
+## item156    3    4    5   NA    5    4   NA   NA    5    3    3   NA    4   NA
+## item157    5   NA   NA   NA    5    3   NA   NA    1   NA    5    4    4    5
+## item158    4    5    4   NA    5    4    3   NA    4    4    5    4    4   NA
+## item159    5    5    1   NA    4    3   NA    4    3    4    5    3    5    5
+## item160    4    4    5    3    5    3    4   NA    5    3    5    4    5    5
+## item161   NA   NA   NA   NA   NA   NA   NA    4   NA   NA   NA   NA   NA   NA
+## item162    2    5   NA   NA    4    4    5   NA    3   NA    1   NA    3   NA
+## item163    3    4    5   NA    5    4    5    5    4    4    4    5    5    4
+## item164    4    4   NA   NA    4    5    5   NA    4    4    3    5    5    4
+## item165    4   NA   NA   NA    4   NA    3   NA   NA   NA    1    3   NA   NA
+## item166    3    5   NA   NA    5   NA    3   NA    3    4    4    4   NA   NA
+## item167    4    5   NA   NA    5    4    4   NA    3   NA    4    3    5    5
+## item168    4    5   NA   NA    4    5    5   NA    4   NA    5    5    5    5
+## item169    4    5    3   NA    4    5    5   NA    3   NA    4    3    5    5
+## item170    5    5    3   NA    5    5    5   NA    4   NA    5    4    4    4
+## item171    3    5    3    5    4    5    5   NA    4    5    5    5    5    5
+## item172    3    5    4   NA    5    4    5    5    5    4    5    5    5    5
+## item173    3    5   NA    3    4    4    4   NA   NA   NA    5    3    5    4
+## item174    4    5   NA   NA    4    2    5   NA    5   NA    5   NA   NA    4
+## item175    5    5   NA   NA    4   NA    5   NA   NA   NA    5    5   NA   NA
+## item176    3    5    5   NA    4    5    5   NA    1   NA    5    5    5    5
+## item177    4   NA    5   NA   NA   NA   NA    3   NA   NA   NA   NA   NA   NA
+## item178    5    2    5   NA    4    3    3   NA   NA    4    5   NA    4    4
+## item179    4    4   NA   NA   NA   NA    3    4   NA   NA   NA    3   NA   NA
+## item180    3   NA   NA   NA    4   NA   NA    4   NA   NA    5   NA   NA   NA
+## item181    4    4    5   NA    4    3    4    5    5    4    5    3    5    5
+## item182   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item183   NA   NA   NA    3   NA   NA   NA   NA   NA    4    5   NA   NA   NA
+## item184   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item185   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item186   NA    5    4   NA   NA    3    5   NA    4    3   NA   NA   NA    4
+## item187    4    5    3   NA    4    5    4   NA   NA   NA    5   NA    3    5
+## item188    5    4    5   NA    5    4    5   NA    4    3    5    5    4   NA
+## item189    3    5    5   NA    5    3    4    4    5    4    5    4    5    5
+## item190    4    5   NA   NA    5    4    5   NA    4    4    5    5    5    4
+## item191    3    5    3    5    5    5    5   NA   NA    5    5    5    5    4
+## item192    2    5    4    5    4    5    5    5    5    5    5    5    5    5
+## item193    3    5   NA   NA    4    4    5   NA   NA   NA    5    4    5    5
+## item194    5    4    5    4    4    4    4   NA   NA    4    5    3    5   NA
+## item195    4    5   NA   NA    4    4    4   NA   NA   NA    5   NA    4   NA
+## item196    3    2    5   NA    4    4    3   NA    5    4    5    2    5    4
+## item197   NA   NA    5    5   NA    4   NA   NA    3   NA    5   NA    3    4
+## item198    3    5    3   NA    5    5    4   NA   NA   NA    4   NA   NA   NA
+## item199    4    5    4    5    5    5    4   NA    3   NA    5   NA    2    4
+## item200    4   NA    5   NA   NA   NA    4   NA   NA   NA    5   NA   NA   NA
+## item201    3    5   NA   NA   NA    4   NA   NA   NA   NA    3   NA   NA   NA
+## item202    4    5   NA   NA   NA    5   NA   NA   NA   NA   NA   NA    5   NA
+##         V263 V264 V265 V266 V267 V268 V269 V270 V271 V272 V273 V274 V275 V276
+## item118    5    4    2    3    4    2    4    4    5    3    5    5    5    3
+## item119    4    4    4   NA   NA    3   NA    4    5    4    5   NA   NA    4
+## item120    4    3    4    2    5    3    4    4    5    3    4   NA    5    3
+## item121    5    4    5    4    5    4    5    5    5    4    4    5    5    5
+## item122    2    3    3    2    3    4   NA    3    1    3    4    1    2    2
+## item123    3   NA    4    4   NA    4    4    4   NA    3   NA    2    4    5
+## item124    3    5    4    3    2    4    2    4    1    2   NA    1    2    3
+## item125    3    3    4    4    4    3   NA    3   NA    4   NA    3    4   NA
+## item126    4    3    5    2    2    3    3    3    4    4   NA    5    4    4
+## item127    4    3    4    5    4    3    4    3    4    4    3    4    5    4
+## item128   NA    2   NA   NA   NA    3   NA    1   NA    3    1   NA   NA   NA
+## item129   NA    2   NA    2   NA   NA   NA   NA   NA   NA   NA   NA    2   NA
+## item130   NA    2   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item131    2    3   NA    5   NA    3    5    4    5    2    3    4    5    3
+## item132   NA    3   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item133   NA    2   NA   NA   NA    2   NA   NA   NA   NA   NA   NA   NA   NA
+## item134    2    3   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item135    2    3    2    3    3    3    3    3    2    2    2    4    2    3
+## item136   NA    1   NA   NA   NA    4    1    3   NA   NA   NA   NA   NA   NA
+## item137   NA    1   NA    2   NA   NA   NA    3   NA   NA   NA   NA   NA   NA
+## item138   NA    3   NA    3   NA   NA   NA    4   NA   NA   NA   NA   NA   NA
+## item139   NA    1   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item140   NA    1   NA    2   NA    3    3    4   NA   NA    3    1    1   NA
+## item141    2    3    2    4    4    2    3    4    1    2   NA    4    5    1
+## item142    2    3    2    5   NA    3    4    3   NA   NA    3    3    2   NA
+## item143   NA    3    4    4   NA    3    5    3    4    2    4   NA    5   NA
+## item144   NA    3    3    4   NA    4   NA   NA   NA   NA   NA   NA   NA   NA
+## item146   NA    1   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item147   NA    3    4    5   NA    3   NA    4   NA   NA   NA   NA   NA    1
+## item148   NA   NA   NA    5   NA   NA   NA    4   NA   NA   NA   NA   NA   NA
+## item149    3    3    4    3    2    4    4    4    4    2    4    4   NA    3
+## item150    3    4    4    2   NA    3    3    4   NA    2   NA    4   NA    5
+## item151    3    4    5   NA    2    2    5    5    4    3    4    4    5    5
+## item152   NA    2   NA    1   NA   NA   NA    5    4    4    1    2    1    2
+## item153    3    4    4    1    5    4    4    3    4    2   NA    5    5    4
+## item154    3    4   NA    4    4    4    5    5    4    2    5    5   NA    4
+## item155    4    2    5    3    2    3    3    4    4    2    4    2   NA    4
+## item156   NA   NA   NA   NA    5    3   NA    3    4    2   NA    3   NA   NA
+## item157   NA    2   NA    2   NA   NA    3   NA   NA    2   NA   NA   NA    5
+## item158    3    4    5   NA    4    3    4    5   NA   NA   NA    4   NA    4
+## item159   NA    4    4    2   NA    2    4    5   NA    2   NA    3   NA    1
+## item160    3    4   NA    3    5    2   NA    5    4    2   NA    4    4    4
+## item161    3   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    2   NA
+## item162    4    4    4    5   NA    3    4    4   NA    3   NA    3    4    5
+## item163    4    4    4    3    5    4    5    4    5    4   NA    4    5    5
+## item164    4    4    4    4    5    3    4    3    5    4   NA    3   NA    5
+## item165   NA    4    5    5   NA    2    4    3   NA    2   NA   NA    4    4
+## item166    3    4    4    5   NA    3    4    3   NA    3   NA   NA    3    4
+## item167    4    4   NA    3    4    3    5    3    5    4   NA    3   NA    5
+## item168    4    4   NA    4   NA    3    4    4   NA    4   NA    4    5    5
+## item169    4    3    5    4    5    2    4    4    5    4   NA    3    5    5
+## item170    3    4    5   NA    5    4    4    5   NA    4   NA    4    2    5
+## item171    3    5    3    3    5    3    5    5    5    5    5   NA    5    5
+## item172    4    5    4    4    5    2    4    5    5    5   NA    5    5    4
+## item173    4    3    3    5    5    3    5    4    5    5   NA   NA    4    5
+## item174    3    4    4    2   NA   NA    2    4   NA    4   NA   NA   NA    3
+## item175    2    4    4    2   NA   NA    5    4   NA   NA   NA   NA   NA    5
+## item176    3    4    5    3    4    4    5    5    5    4   NA   NA    4    5
+## item177    3   NA   NA    3   NA    3   NA    5   NA   NA   NA   NA   NA   NA
+## item178    5    4   NA    4   NA    2    4    5    5    5   NA    5    5   NA
+## item179    3    3    4    5   NA    3    4    4   NA    4   NA   NA   NA    5
+## item180   NA    3    4    1   NA    3    5    5   NA    3    3   NA    5   NA
+## item181    4    3    3    2    5    3    5   NA   NA    5   NA    4    5    5
+## item182   NA    3   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item183   NA    3    4   NA   NA    4   NA   NA   NA    3   NA   NA   NA   NA
+## item184   NA    3   NA    3   NA    5    3    5   NA    3   NA   NA    3   NA
+## item185   NA   NA   NA   NA   NA    3    3    5   NA    4   NA   NA   NA   NA
+## item186    3    3    4    3    5    4    4    4   NA    4   NA    4   NA   NA
+## item187    3    4    5    4    5   NA    4    4   NA    4   NA   NA   NA   NA
+## item188    3    4    4   NA    5   NA    4    4    5    4   NA    4    5    5
+## item189    4    4    5    4    5    3    5    3    5    4    5    4   NA    3
+## item190    4    5    5    5   NA   NA    5    4   NA    4    5   NA   NA    4
+## item191    3    5    4    3    4    4    5    4   NA    3    5   NA   NA    4
+## item192    3    5    4    4    5    4    4    4   NA    4    5    4    5    5
+## item193    4    5    5   NA   NA   NA    4    4   NA   NA   NA   NA   NA   NA
+## item194    4    5    4    2    5    3    5    4   NA    4    3    5    5    4
+## item195    4   NA    2   NA   NA   NA   NA    4   NA   NA    3   NA    4    4
+## item196    4    4   NA    2    5   NA    2    4    4   NA   NA   NA    5    3
+## item197    2    3    5   NA   NA   NA   NA    4    4   NA    4    2   NA    3
+## item198    3    4   NA    3   NA   NA    4   NA   NA   NA    5   NA   NA    5
+## item199    3    4    4    3    4   NA    3    4    5    5    4    4   NA    3
+## item200   NA   NA    4   NA   NA   NA   NA    5   NA    5    5   NA    5    4
+## item201   NA    4    5   NA   NA   NA   NA    3   NA   NA   NA   NA    3   NA
+## item202    4   NA    5   NA   NA   NA   NA    5   NA   NA   NA   NA    4   NA
+##         V277 V278 V279 V280 V281 V282 V283 V284 V285 V286 V287 V288 V289 V290
+## item118    4    5    2    1    5    5    2    2    4    2    5    3    5    2
+## item119    2   NA    2   NA    5   NA    3   NA    4    2    5    4   NA    4
+## item120    2   NA    5    2    5   NA    2   NA    3    2    5    4    4    4
+## item121    4    3    5    4    5    5    4    5    4    3    5    5    4    2
+## item122    1   NA    1    1    3    5    2    4    4    4    4    3    5   NA
+## item123    2   NA    3    4    4    5   NA    5    4    4    4    4    4   NA
+## item124    4    4    1   NA    5    5    4    3    3   NA    5    2    5    5
+## item125   NA   NA    3    1    3    5   NA    2    4    1    5   NA    3   NA
+## item126    2    4    4    2    4    5    2   NA    3    2    4    2    5    5
+## item127    2    3    4    1    4    5    4    5    4    1    3    4    5    1
+## item128   NA   NA   NA    1    2   NA   NA   NA    1    1   NA    1   NA    4
+## item129   NA    1   NA   NA    2   NA   NA   NA    2    1    3   NA   NA   NA
+## item130   NA   NA   NA   NA   NA    5   NA   NA   NA   NA   NA   NA   NA   NA
+## item131    4    3    4    1    2    5    3    3    5    4   NA    5   NA    1
+## item132   NA   NA   NA    1   NA    5    4   NA    1   NA   NA    1   NA   NA
+## item133   NA   NA    4   NA    2    5   NA   NA    1    2    1    1    4    1
+## item134   NA   NA   NA   NA    2    5   NA   NA    2    3   NA    2    4   NA
+## item135    4    3    4    1    3    5    4    4    5    3    3    4    5    2
+## item136    1    1   NA    1    2    5    3   NA    1    1   NA    1   NA   NA
+## item137   NA   NA   NA    1    1    5   NA   NA    2    3    2    2   NA   NA
+## item138   NA   NA   NA    1    3    5   NA   NA   NA    3   NA    2   NA   NA
+## item139   NA   NA   NA    1    1    5   NA   NA    1   NA   NA   NA   NA   NA
+## item140    2   NA   NA    1    1    5    3    4    2    4    2    2   NA   NA
+## item141    1    3    5    1    1    1    4    5    5    2    3    4    5    2
+## item142   NA    3    3    1    1    1    3    3    3    4    4    4    5    3
+## item143    2    3   NA    1    1    5    2    4    4    5    3    5    5   NA
+## item144   NA   NA    3    1    1   NA    3   NA    4    5    3    4    4    2
+## item146   NA   NA   NA   NA   NA    5   NA   NA    1    1    1    1   NA    1
+## item147   NA   NA    5    4   NA    5   NA   NA    3   NA   NA   NA    5    5
+## item148   NA   NA   NA    4   NA    5   NA   NA   NA   NA   NA   NA   NA   NA
+## item149    4    4    3    5    5   NA    4    5    5    4    3    5   NA    4
+## item150    4    4    5    5    5    5    4    5    4    5   NA    4    5   NA
+## item151    5    2    4   NA    5    5    4    3    3    5    3    4    4    4
+## item152    2    1   NA   NA    3   NA   NA    3    2    2    1    1   NA    4
+## item153    5    3    5   NA    3    5    4    4    4    5    5    4    5    2
+## item154    5    4    3    5    5    5    3    3    4    5   NA    4   NA    5
+## item155    3    1    3    5    5   NA    2    4    2    2    2    1   NA    5
+## item156   NA    3    2    5    4    5    4   NA    4   NA   NA   NA    5   NA
+## item157    4    2    5   NA    5    5   NA   NA    4    4   NA    5    4    5
+## item158    5   NA    3    4    5    5    2    5    3    4   NA    3    4    4
+## item159   NA    2    5    4    3    5    2   NA    2    1    3    4   NA    5
+## item160    4    3    5    2    3    5    4    3    4    4    3    4    5    4
+## item161   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    2   NA   NA   NA
+## item162    5   NA    4    3    3    5   NA    5    4    2    3   NA   NA   NA
+## item163    4    3    4    5    4    5    3    5    4    1    4    4    4    5
+## item164    4    3    4    5    4    5    4    4    4    1    3   NA   NA   NA
+## item165    4   NA   NA    5    4    5    3   NA    4   NA   NA    2   NA   NA
+## item166    4   NA   NA    4    4    5   NA   NA    4   NA   NA    5   NA   NA
+## item167    4    3   NA    4    3   NA   NA    3    5    2   NA    5   NA   NA
+## item168    4    5    5    4    4    5    4    4    4    5   NA    5    5   NA
+## item169    5    2    5    2    4   NA    3   NA    3    3   NA    3   NA    5
+## item170    2    4    5    5    4    5   NA   NA    3    4    4    4    5    5
+## item171    5    5    5    5    5    5    4    5    5    5   NA    5    5    5
+## item172    5    5    4    5    5    5   NA    5    4    5    5    5    5   NA
+## item173    5    3    4    4    4    5    4   NA    4    4    4    3    5    3
+## item174    5    2    4    5    4    5    4   NA    3    5   NA    4    5   NA
+## item175    4    4   NA   NA    5    5    2   NA    4    4   NA    5    5   NA
+## item176    5    4    5   NA    5    5    4    5    5    3    5    5    5    5
+## item177   NA   NA   NA    2   NA    5    3   NA    3   NA   NA   NA    4   NA
+## item178    4    3    5    3    3    5    4    4    4    3    5    4    5    3
+## item179    5    1    4    4    5    5    2   NA    4   NA   NA   NA    5   NA
+## item180   NA   NA   NA    1    4    5    2   NA    3    5   NA    2   NA   NA
+## item181    5    5    5    2    4   NA    4    5    5    4   NA    3    5   NA
+## item182   NA   NA    3    2   NA    5   NA   NA   NA   NA    3   NA   NA   NA
+## item183   NA   NA    3    2   NA    5    2   NA    4    5   NA   NA   NA   NA
+## item184   NA   NA   NA   NA    4    5   NA   NA    4   NA   NA    3   NA   NA
+## item185   NA   NA   NA    5   NA    5   NA   NA    2   NA   NA    3   NA   NA
+## item186    5    4    4    5    4    5   NA   NA    3    5   NA    4   NA    4
+## item187    4    5    4    5    5    5   NA   NA    4    3   NA    5    5   NA
+## item188    4    2    5   NA    5   NA    3    5    4    5   NA    3    4    4
+## item189    3    3    5    3    4    5    3    5    2    5   NA    4    5    5
+## item190    3    5    5    5    5    5    3    5    3    4   NA    5    5   NA
+## item191    5    5    5    5    5    5    3    5    4    4   NA    5    5   NA
+## item192    4    5    5    5    5    5    3    5    3    4    5    5    5   NA
+## item193    5    4    5   NA    5    5   NA   NA    3    5   NA    5    4   NA
+## item194    4    3    5   NA    5   NA    3    4    4    4   NA    4    5    4
+## item195    4   NA    5   NA    4    5   NA   NA    3    4   NA   NA   NA   NA
+## item196    3    2    4   NA    3    5    4    3    4    4   NA    2    5    5
+## item197    5    2   NA   NA    5   NA   NA   NA    3    5   NA    3   NA   NA
+## item198    3    3    5   NA    5    5    4   NA    4   NA   NA    4    5   NA
+## item199    3    1    4    5    5   NA   NA   NA    3    2    3    4   NA    4
+## item200   NA    3   NA   NA    5   NA   NA   NA    3    3   NA   NA   NA   NA
+## item201   NA   NA   NA   NA    4   NA   NA   NA    2    4   NA   NA   NA    5
+## item202    5    5    4   NA    5   NA   NA   NA    4    3   NA    5    5   NA
+##         V291 V292 V293 V294 V295 V296 V297 V298 V299 V300 V301 V302 V303 V304
+## item118    5    4    5    3    5    4    3    4    5    4    4    5    5    4
+## item119    5    4    4    3    4   NA    2    4    5    4    4    5    5   NA
+## item120    5    3    3    3    4   NA    2    5    4    4    3    4    5    5
+## item121    5    2    4    3    5    4    3    5    5    5    4    5    5    5
+## item122    3    2    3    4    2    1    1    5    4    3    3    4    5    4
+## item123    4    3    3    4    3   NA    1    4    4    4    4    4    5    5
+## item124    5    3    4    4    4   NA    3    2    4    4    3    3    4    3
+## item125    3   NA    3    4    4    4    3    4    5    4    3    4    3    4
+## item126    4   NA    4    4    5   NA    1    4    4    5    4    4    5    5
+## item127    4    4    4    4    2    4    4    5    4    5    3    5    5    5
+## item128   NA   NA   NA    2    1    2    1    4    3   NA    3   NA   NA   NA
+## item129    4   NA   NA   NA    1   NA   NA   NA    3   NA   NA    4   NA   NA
+## item130   NA   NA   NA   NA   NA   NA   NA   NA    3   NA   NA   NA   NA   NA
+## item131    4    3    2    2    2    3    3    5    4    5    3    5    5    5
+## item132   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item133    3    3    5   NA    2   NA   NA   NA    5   NA    3    4   NA   NA
+## item134    3   NA   NA   NA   NA   NA   NA   NA    5   NA    3    4   NA   NA
+## item135    4    4    4    2    4    2    1    5    3    5    4    2    4    4
+## item136    2   NA    2    2   NA   NA    1    4    3   NA   NA   NA   NA    1
+## item137    2    4    1    3   NA    1    1    1    3   NA   NA   NA   NA   NA
+## item138   NA    4   NA    4   NA   NA    1   NA    3   NA   NA   NA   NA   NA
+## item139   NA    4   NA   NA   NA   NA    1   NA    3   NA    3   NA   NA   NA
+## item140    3    4   NA    4   NA    2    1    2    3   NA    3    3   NA   NA
+## item141    3   NA    1    4    1   NA    3    4    3    5    3    5    4    4
+## item142    2    5    1    3   NA    3    2    3    3    4    3    4   NA   NA
+## item143    4   NA    3    4    1    4    1    4    3    5    3    3   NA   NA
+## item144    3    5    3    4   NA    4    1    3    3   NA    3   NA   NA   NA
+## item146    2   NA   NA    2   NA    2   NA    2    4   NA   NA   NA   NA   NA
+## item147    4   NA   NA    4   NA   NA    5   NA    4   NA   NA   NA   NA   NA
+## item148   NA   NA   NA   NA   NA   NA    5   NA   NA   NA   NA   NA   NA   NA
+## item149    4   NA   NA    3    4    4    4    5    4    5    4    4    5    5
+## item150    5    3    4    4    4    3    5    5    4    4    5    4    5    5
+## item151    5    5    5    2    3    5   NA    4    4    5    4    4    5    5
+## item152    5   NA    2    1    1    4    1    4    4    4   NA   NA    5    5
+## item153    5    4    4    4    1   NA    3    5    4    5    4    4    5    5
+## item154    5   NA    4    3    4   NA    1    4    3    5    4    4    5    5
+## item155    5   NA   NA    4    2    4    5    5    4    5    3    4    5    1
+## item156    3    5   NA    5    4   NA    3    5    3    5   NA    4    4   NA
+## item157    5    5    5    2    2    4    3    4    5    4   NA    5    5    3
+## item158    5    3    4    4    5    4    3    5    5    4    3    4    5    5
+## item159    5    5   NA    5    4    4    2    5    4    5    3    4    3    5
+## item160    4    5    4    4    3    4    3    5    3    5    4    5    5    5
+## item161   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item162    5    4    4    4    2    4    3    5    4    1    5    5   NA   NA
+## item163    5    4    4    3    3    4    3    5    5    5    4    4    5    5
+## item164    5    4   NA    4    4    3    3    5    5    3    4    4    5    5
+## item165   NA    5    5    4   NA    4    3    4    4    1    4    4   NA   NA
+## item166    5    3    5    3   NA    4    3    5    4   NA    4    5   NA    5
+## item167    5   NA   NA    3   NA   NA   NA    5    4    3    5    4    5    4
+## item168    5    4    4    3   NA   NA    3    4    4    3    5    4   NA    5
+## item169    5    4    4    2   NA    3    3    5    4    4    4    5    5    5
+## item170    5    4    4    4    5    5    2    5    4    4    4    4    5    5
+## item171    5    3    4    4    5    4    4    5    4    5    4    5    5    5
+## item172    5    4    4    4    4   NA    4    5    4    4    4    4    5    5
+## item173    5    3    5    4    4   NA    4    5    4    4    3    4    5    5
+## item174    5    5    5    4    3   NA    4   NA    5    5    3    4    5    4
+## item175    5    4    5    3   NA   NA   NA   NA    4   NA    4    4   NA   NA
+## item176    5    5    5    4    4   NA    3    5    4    4    4    5    5    5
+## item177   NA   NA   NA    2   NA    3    3   NA    3    3    4    5   NA   NA
+## item178    5    5    5    4    3   NA   NA    5    4    4    3    4   NA    4
+## item179   NA   NA   NA    4   NA   NA   NA    5    4    3   NA    5   NA   NA
+## item180   NA   NA    3    4   NA    4    2    4    4    5   NA   NA   NA   NA
+## item181    5    5    5    3    4   NA   NA    4    4    5    4    4   NA    5
+## item182   NA   NA   NA   NA   NA   NA   NA   NA    3   NA   NA   NA   NA   NA
+## item183   NA    5    3    3   NA    4    2    2    4   NA   NA   NA   NA   NA
+## item184   NA   NA    3    3   NA   NA   NA    5    4   NA    4   NA   NA    5
+## item185   NA   NA   NA    3   NA   NA    2   NA    4   NA   NA   NA   NA   NA
+## item186   NA    5   NA    4    4   NA    4    5    4    4   NA    5   NA    5
+## item187    4    5    4    5    4    5    4    4    4    4    5    5    5    5
+## item188    5    5    4    3    5   NA    4    5    4    5    5    5    5    5
+## item189    5   NA    4    5    4    3    4    5    4    5    4    4    5    5
+## item190    4   NA    4    3    3    4    4    5    5    5    5    4    5    5
+## item191    5   NA    4    4    5    5    5    5    5    5    5    5    5    5
+## item192    5   NA    4    5    5    4    5    4    5    5    5    5    5    5
+## item193    5   NA    4   NA    4    4    5    4    5    4    5    5    5    5
+## item194    5    4   NA    5    4    4    3    4    5    5    5    4    5    4
+## item195    5    3   NA    5    3   NA   NA   NA    5    5    4    4    5   NA
+## item196    5    4    4    4    4   NA    3    4    5    5    4    4    5    5
+## item197    5    5    5    5   NA    4   NA    5    5   NA    3    5   NA   NA
+## item198    5   NA    4    3    4    3   NA   NA    4    4   NA    4    5   NA
+## item199    4   NA    3    3    2    4    3    5    5    5    3    5    5    5
+## item200    4   NA    5    5   NA   NA    2    4    4    4   NA    4   NA    5
+## item201   NA   NA   NA   NA    5   NA   NA   NA    3    5   NA    5   NA   NA
+## item202   NA   NA    3    4    4   NA    4    5    5    4   NA    4    5    5
+##         V305 V306 V307 V308 V309 V310 V311 V312 V313 V314 V315 V316 V317 V318
+## item118    4    4    5    4    3    4    4    2    4    4    4    5    5    5
+## item119    4    4    3   NA   NA    4    3    2    2    5    3   NA    5    5
+## item120    4    4    1    3    3   NA    4    2    2    4    4    4    5    5
+## item121    5    5    5    4    2    4    4    3    4    5    4    3    5    5
+## item122    1    4    1    5    4    3    3    5    2   NA    2    1    4    3
+## item123    4    5    1    4    2   NA    4    2    4    4    4    1    4    4
+## item124    3    5    1    4    3    5    3    4    4    5    2    4    2    4
+## item125    4    4   NA    2    4    1    2    1    2    1    2   NA    1    5
+## item126    4    5    1    5    2    5    3    4    2    5    3    2    4    5
+## item127    5    5    3    2    2    4    3    5    3    4    3    1    4    4
+## item128   NA   NA   NA   NA   NA    2    3   NA   NA   NA   NA   NA    2   NA
+## item129   NA    3   NA   NA   NA   NA    4   NA    3   NA   NA   NA   NA   NA
+## item130   NA   NA   NA   NA   NA   NA   NA   NA    3   NA   NA   NA   NA   NA
+## item131    1    4    1    5    4    3    3   NA    2    4    4    3    4    4
+## item132   NA   NA   NA   NA   NA   NA    2   NA    4    3   NA   NA   NA   NA
+## item133   NA   NA   NA   NA   NA   NA    3   NA    4    1   NA   NA    4   NA
+## item134   NA   NA   NA   NA   NA   NA    3   NA   NA    2   NA    3    4   NA
+## item135    1    5    1    1    3    2    4    4    4    3    3    1    1    2
+## item136    3    1   NA   NA   NA   NA   NA   NA    1   NA   NA   NA    1   NA
+## item137   NA   NA   NA    3   NA    1    4   NA    1   NA   NA   NA   NA   NA
+## item138   NA   NA   NA   NA   NA   NA   NA   NA    3   NA   NA   NA   NA   NA
+## item139   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item140   NA   NA   NA    5    3   NA    5   NA   NA   NA    2   NA    3    3
+## item141    1    4    1    5    4    3   NA    5   NA    3    3    3    4    3
+## item142    3    3   NA   NA   NA    2    5    4    3    4   NA    1    4    2
+## item143   NA    4   NA    5   NA    3    2    3    4    4    4    4   NA    4
+## item144    1    3   NA   NA   NA    3    5    1    4   NA   NA    1    4    2
+## item146   NA   NA   NA   NA   NA    1    3   NA   NA   NA   NA   NA   NA   NA
+## item147    5   NA   NA   NA   NA    2    2   NA    4   NA   NA    3    4   NA
+## item148   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    3   NA   NA
+## item149    4    5    1    1    3    5    4    3    4    5   NA    4    4    4
+## item150    4    5    1    5    2    4    4    3    4    5    5    4    4    5
+## item151    4    3   NA    5    2    3    3    3    5    5    5    5    5    5
+## item152   NA    3   NA    1    2    1    3    4    5    4   NA    4    1    2
+## item153    5    5    3    4    3    5    2    4    1    5    5    3    4    5
+## item154    4    5   NA   NA    3    5    3    4    5    5    5   NA    4    5
+## item155    4    3    3    4    3    2    2    2    5    4   NA    4    3    4
+## item156   NA    5    3    1    3   NA   NA    4   NA    2    4    3    4    5
+## item157   NA    3    3   NA   NA    4    5   NA    5    4   NA    4   NA   NA
+## item158    4    4   NA   NA    4   NA    3    3    5    5    4    5    4    4
+## item159    5    3   NA    5    4    4    3    2    5    2    4    3   NA    3
+## item160    3    5    3   NA    4    4    3    5    4    4    3    4    4    4
+## item161   NA   NA   NA    1   NA   NA   NA   NA   NA   NA   NA    1   NA   NA
+## item162    4   NA   NA   NA   NA    4    2   NA    3    4    4   NA    5    3
+## item163    4    4    3    5    4    4    2    5    4    5    4    5    5    5
+## item164    4    3    3    5    3    5    1   NA    4    4    4   NA    5    3
+## item165    4   NA   NA   NA   NA    5    2   NA    4    4    3    4    4   NA
+## item166    2   NA    3    4    2    5    3   NA   NA    5    4    4    4   NA
+## item167    4   NA    3   NA    3    4   NA   NA   NA    5    4    4    4    5
+## item168    5    3    3   NA    3    5    4    3   NA    4    4    5    4    5
+## item169    4    4    3    5    4    4    4    4   NA    3    4    4    5    5
+## item170    5   NA    3    5    3   NA    4    4    4    4    5    4    5    4
+## item171    4    4    3    5    3    5    3    3    5    5    5    5    5    5
+## item172    5    4    3    5    3   NA    2    4    4    5    5    5    5    5
+## item173   NA   NA   NA    4    3    5    2    4   NA    3    4    4    5    5
+## item174    5    4    3    5    3   NA    2    3    4    4    5   NA    5    5
+## item175   NA   NA   NA   NA    3   NA    2   NA   NA    5    4   NA    5    4
+## item176    4    5    3    5    3    5    2   NA    5    5    5    5    5    5
+## item177   NA   NA   NA   NA   NA   NA    1   NA    4   NA   NA   NA    5   NA
+## item178    4    4    3    5    3    5   NA    4   NA    5    3    3    4    5
+## item179    5   NA   NA   NA   NA   NA   NA   NA    2   NA   NA   NA   NA   NA
+## item180    1   NA   NA   NA   NA   NA    3   NA    2    4   NA   NA   NA   NA
+## item181    4    5    3    5    2    5    2    5   NA    4    4    3    5    5
+## item182   NA   NA   NA   NA   NA   NA    2   NA   NA   NA   NA   NA   NA   NA
+## item183   NA    3   NA   NA   NA    3    4   NA    2   NA   NA   NA   NA   NA
+## item184   NA   NA   NA   NA   NA    5   NA   NA    4   NA   NA   NA   NA   NA
+## item185   NA   NA   NA   NA   NA   NA    2   NA    4   NA   NA   NA   NA   NA
+## item186   NA    3   NA    4    2   NA    4    4   NA   NA   NA    4    5   NA
+## item187    4    4   NA    4    4    5    4    3   NA    5    5   NA   NA    4
+## item188    5    4    3    5    2    4    3   NA   NA    5    5    3    5    5
+## item189    4    4    3    4    4    4    4    4    2    5    5    3    3    5
+## item190    5    5   NA   NA    2    5    4   NA    4    5    5   NA    4    5
+## item191    5    5   NA   NA    3   NA    4   NA    4    5    5    3    5    5
+## item192    5    5   NA    5    2    5    4    4    4    5    5   NA    5    5
+## item193    4   NA   NA   NA    4   NA    3    3    4    5    5   NA    4    5
+## item194    2    5    3    5    2    5    3    3    4    4    4    5    4    5
+## item195   NA   NA   NA   NA   NA    4    2   NA    4   NA    4    3    4    4
+## item196    3    4   NA   NA    3    5    2    5   NA    3    2    2    3    5
+## item197   NA   NA   NA   NA   NA   NA    4    4    4    4    4    4    3   NA
+## item198   NA   NA   NA    3   NA   NA    2   NA   NA   NA    5    4   NA    5
+## item199   NA    4   NA   NA    3   NA    3    3    2    5    5    4    4    4
+## item200   NA   NA    3   NA    3   NA    4   NA    2    5   NA    3    4   NA
+## item201   NA   NA   NA   NA   NA   NA    4    5   NA    4    5   NA   NA    4
+## item202    4   NA    3    5    2   NA    2    3   NA    5    5   NA   NA   NA
+##         V319 V320 V321 V322 V323 V324 V325 V326 V327 V328 V329 V330 V331 V332
+## item118    4    4    5    3   NA    3    4    1    5    4    4    3    4    5
+## item119   NA   NA    5   NA   NA    4   NA    1    5    4    3    4    2    4
+## item120   NA    4    5   NA   NA    2   NA    1    4    3    3    5    4    4
+## item121    2    5    5   NA    5    4    3    5    5    4    4    5    4    5
+## item122   NA    3    2   NA    3    2    1    1   NA    3    2    3    1    2
+## item123    2    4    3   NA    4    3   NA    5    5   NA    1    4    3    4
+## item124    4    3    1    4   NA    4    4   NA    4    1    1    2    4    2
+## item125    1    4   NA   NA    2    1   NA    1   NA    4    3    3    3    2
+## item126    3    4    2   NA    4    4   NA    4    5    5    3    4    2    4
+## item127    5    5    3    4    4    2    4    4    4    5    5    4    4    3
+## item128   NA    2   NA   NA   NA    2   NA   NA    5   NA    1    2   NA   NA
+## item129   NA    4    1   NA   NA    2   NA   NA   NA   NA   NA   NA   NA    2
+## item130   NA    2   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item131   NA   NA    3    3    3   NA    5   NA   NA    3    5    4   NA    3
+## item132   NA    4    1   NA   NA   NA   NA    4    5    3   NA   NA   NA   NA
+## item133   NA    3   NA   NA   NA   NA   NA    5    5    1   NA    4   NA   NA
+## item134   NA    4   NA   NA   NA   NA   NA    5    4    1   NA   NA   NA    3
+## item135    3    5    5    4    3    3    4    5    5    3    5    3    4    3
+## item136   NA   NA   NA   NA   NA    2    1    1    3   NA    1    2   NA   NA
+## item137   NA    2   NA   NA   NA    3   NA   NA    4   NA   NA    1   NA   NA
+## item138   NA   NA   NA   NA   NA   NA   NA   NA    3   NA   NA   NA   NA   NA
+## item139   NA    3   NA   NA   NA   NA   NA   NA    3   NA   NA   NA   NA   NA
+## item140   NA    4   NA   NA   NA    2   NA    1    4   NA    1    3   NA    3
+## item141    2    4    2    1    2    3    1    5    4    5   NA    2    3    3
+## item142    3    5    2    3   NA    3   NA    4    4   NA    3    3   NA   NA
+## item143    4    3    3   NA    3    3   NA    5    5    5    4    2   NA    3
+## item144    2    3   NA   NA   NA    3   NA    4    4   NA    4    3   NA   NA
+## item146   NA   NA   NA   NA   NA   NA   NA   NA    3   NA    1    2   NA   NA
+## item147   NA    5   NA   NA   NA   NA   NA   NA    5   NA    4    4   NA   NA
+## item148   NA    3   NA   NA   NA    3   NA   NA   NA   NA    4   NA   NA   NA
+## item149    4    4    5   NA    4    4   NA    5    5    5    5    5    4    4
+## item150    4    4    5   NA   NA    4    3    2    4    5    5    4    4    4
+## item151    4    3    4   NA    3    4   NA    5    5    3   NA    3    4    4
+## item152    1   NA    3    2    1    4   NA    2    5   NA   NA    3    2    4
+## item153    5    5    2    4    4   NA    2    5   NA    5    4    2    3    5
+## item154    4    5    5   NA    4    4    2    5    4    5    4    4    3    4
+## item155    3    3    3   NA    2    3   NA    5    4    3    4    4    2    3
+## item156    5   NA    3   NA    4    3   NA    5    3    3    4    2   NA    3
+## item157   NA   NA    5   NA   NA    4    2   NA   NA    4   NA    4    3    3
+## item158   NA    4    5   NA   NA    3   NA    4   NA    5    5    4    4    4
+## item159   NA    5    5   NA    3    4   NA   NA    4   NA   NA    4   NA    3
+## item160    4    5    4    4    4    3    1    5    3    3    4    3    3    3
+## item161   NA   NA   NA    2   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item162   NA    5    4   NA   NA    3   NA    5    5    4    4    3   NA    4
+## item163   NA    5    5   NA    4    3   NA    5    5    5    5    4    4    5
+## item164   NA    4    5   NA    4    4   NA    5    5    4   NA    4    5    4
+## item165   NA    5   NA   NA   NA   NA   NA    5    5   NA    5    3    2   NA
+## item166   NA    5    4   NA   NA   NA   NA    5    4   NA   NA    2    3   NA
+## item167   NA    5    5   NA    4   NA    1    5    4    5   NA    4    4    4
+## item168   NA    5    5   NA    4   NA    3    5    5    5   NA    4    4    5
+## item169    4    4    4   NA    5    3   NA    5    5   NA   NA    4   NA    3
+## item170   NA    5    5   NA   NA    3    2    5    5    5    5    4   NA    4
+## item171   NA    5    5   NA   NA    4   NA    5    5    5    5    5    4    4
+## item172    4    5    5   NA    5    4   NA    5    5    5   NA    4    4    4
+## item173   NA    5    3   NA   NA    3    1    5   NA    4   NA    3    4    4
+## item174   NA    4    4   NA   NA    4   NA    5    5    5    4    3    3    3
+## item175   NA    5    5   NA   NA   NA   NA    5    5    5   NA    3    4   NA
+## item176   NA    5    5   NA    5    5    2    5    5    5   NA    4    5    4
+## item177   NA   NA   NA   NA   NA   NA   NA    5   NA   NA    4   NA   NA   NA
+## item178   NA    3    3   NA    4    3    1    5    3   NA   NA    3    5    3
+## item179   NA    5   NA   NA   NA   NA    2    5    3   NA   NA    4    3    4
+## item180   NA    3   NA   NA   NA    2   NA    5    5   NA    2    2   NA   NA
+## item181    5    5    4   NA    5    3    5    5   NA    5    4    4    4    4
+## item182   NA    3   NA   NA   NA   NA   NA   NA    5   NA   NA   NA   NA   NA
+## item183   NA    2   NA   NA   NA    2   NA   NA    5   NA    3    2   NA   NA
+## item184   NA    5    3   NA   NA   NA   NA    5    4   NA   NA    3    2    3
+## item185   NA    3   NA   NA   NA   NA   NA    5    3   NA   NA   NA   NA   NA
+## item186   NA    3   NA   NA    3    3   NA   NA    3   NA   NA    5   NA   NA
+## item187   NA    4    5   NA    4   NA   NA   NA    4    4   NA    5    3    3
+## item188   NA    2    5   NA    4   NA   NA    5    4    3   NA    3   NA    4
+## item189    5    5    4   NA    4    2    4    5    4    5    5    4    4    4
+## item190    5    5    5   NA    4    4   NA    5    4    5    5    4    5    4
+## item191    4    5    5   NA    4    4    4    5    4    5    5    5    5    4
+## item192    4    5    5   NA    5    4    4    5    5    5    5    5    5    4
+## item193   NA    5    5   NA   NA    4   NA    5    5    5    5    5    3   NA
+## item194   NA    5    5    2    4    4    5    5    4    5    4    4    2    4
+## item195   NA   NA    3   NA   NA    4   NA    5    4   NA   NA    3   NA    4
+## item196    4    3    2    4    3    2    2    5    5    3    4    4   NA    3
+## item197   NA   NA   NA   NA   NA    3   NA    5    4   NA   NA    2   NA   NA
+## item198   NA    5    4   NA   NA    4   NA   NA    4    5   NA    3   NA    4
+## item199   NA    4    3    4    3    4   NA   NA    4    3   NA    5   NA    3
+## item200   NA   NA   NA   NA   NA    4   NA    5    4   NA   NA    3   NA    4
+## item201   NA   NA    5   NA   NA    4   NA   NA    4    4   NA    3   NA   NA
+## item202   NA    5    5   NA   NA   NA    4   NA    4    5   NA    5   NA    3
+##         V333 V334 V335 V336 V337 V338 V339 V340 V341 V342 V343 V344 V345 V346
+## item118    5    5    4    4    4    2    5    5    4    5    2    4    3    5
+## item119    3    5    3    4    4    3    5    5    4    4    1    4   NA    4
+## item120    3    5    3    2    4    2    5    4    4    1    2    5   NA    4
+## item121    3    4    4    4    3    4    5    4    5    4    2    4    4    4
+## item122    4   NA    2    4    2    2    1    3    4    1    2    2    5    4
+## item123    4    4    2    4    2    3    5   NA   NA    1    2    5    4    4
+## item124    4    1    3    4    2    2    3    1   NA    5    4    3    4    3
+## item125    2    2    2   NA    2    2   NA   NA   NA    3    4    3   NA   NA
+## item126    4    3    4    4    4    2    5    4    5    1    4    3    5    4
+## item127    4    2    3    4    2    2    2    4    5    2    4    4    5    4
+## item128   NA   NA    3   NA    2   NA   NA   NA   NA   NA    4    2   NA   NA
+## item129   NA   NA    2   NA   NA   NA   NA    1   NA   NA   NA    3   NA    1
+## item130   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item131    2    3    4    5    2    4    1    4    5   NA    5    3    3    1
+## item132   NA    3    3   NA   NA   NA   NA   NA    2   NA   NA    4   NA   NA
+## item133    4   NA    5   NA   NA   NA   NA   NA    3   NA   NA    4    3    1
+## item134   NA   NA    5   NA   NA   NA   NA   NA    4   NA   NA    3    1   NA
+## item135    4    5    1    2    2    4    2    3    5    1    4    5    4    1
+## item136   NA   NA    5   NA    3   NA   NA   NA    2   NA   NA    2    1   NA
+## item137    2   NA    4   NA   NA   NA   NA   NA    3   NA    3    1    3   NA
+## item138   NA   NA   NA    4   NA   NA   NA   NA    5   NA   NA   NA    3   NA
+## item139   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item140    2   NA    4    4   NA   NA   NA   NA    3   NA    3    1    2    2
+## item141    2    3    5    5    2    2    1    3    2    1    3    4    2    1
+## item142   NA    3    5    4   NA    3   NA   NA    5   NA    3    3    1    1
+## item143   NA    3    1    4    2    3    3   NA    4   NA    3    4    5   NA
+## item144   NA   NA   NA   NA   NA   NA   NA   NA    4   NA   NA    3    5    1
+## item146   NA   NA   NA   NA   NA   NA   NA   NA    5   NA    5   NA   NA   NA
+## item147    4   NA    3   NA   NA   NA   NA   NA    5   NA    5   NA    5   NA
+## item148   NA   NA   NA   NA   NA   NA   NA   NA    5   NA    3    2    5    2
+## item149    4    5    5    4    3    4    5   NA    5    1    3    3    4    1
+## item150    3    5    4    3    2    4    5    5    4    4    4    4   NA    2
+## item151    4    5    4    4    4    3    5    5    5    1   NA    3    5    5
+## item152   NA    4    3    2    3   NA    1    1    3    1    4    2   NA   NA
+## item153    4    3    5    5    2    3    4    5    5    2    4    5    5    5
+## item154    4    5    3    1   NA    4    5    5    5    1    4    1    4    3
+## item155    4    5    3    4    2    3    1   NA    4    1    4    3    4    4
+## item156   NA   NA    1   NA    2    3    5    5    3    1    4    4   NA    3
+## item157   NA    5    3    2   NA    4    5    3    3    4   NA   NA   NA    4
+## item158    3    5    3    5    1    3    5    5    5    1   NA    3    1    4
+## item159    3   NA    3    5    1   NA    2    5    5    1    4    3    1    4
+## item160   NA    5    2    1    2    3    4    5    4    4    3    4    3    4
+## item161   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item162    4    4    3   NA   NA    3    5   NA    3    1   NA    5    4    2
+## item163    4    4    4    5    2    4    5    5    5    1    4    3    4    2
+## item164    4   NA    2    5    2    4    4   NA    4    1    3    3    5    2
+## item165    4   NA    4   NA   NA   NA   NA   NA    5   NA    4    4   NA    3
+## item166   NA   NA    3    5   NA    4    4   NA    4   NA    4    5    4    4
+## item167    4   NA    4    3   NA    4    5    3    4    1    2    4   NA    3
+## item168   NA    5    4    4   NA    4    4    5    3    1    3   NA    5    5
+## item169   NA   NA    4    4   NA   NA    4    4    3    1   NA   NA   NA    3
+## item170    4   NA    5    4    2    3    5    5    5   NA    4    5    3    4
+## item171    4    5    5    4    3    4    5    4    5    5    4    5    5    4
+## item172   NA    5    5    4    3    4    4    5    4    5    3    4    5    3
+## item173    4    4    4   NA    2    5    5    2    5    5    3    2    4    4
+## item174   NA    5    3    4   NA   NA    5    5    4    5   NA   NA   NA    4
+## item175   NA   NA    3   NA   NA    5   NA    3    3    5    4   NA    4    4
+## item176    4    5    4    5    1    5    4    5    3    5    3    5    5    4
+## item177   NA   NA    2    3   NA   NA   NA   NA    3   NA    4    4   NA   NA
+## item178    4   NA    5    3    2    4    5    3    5   NA   NA    3    4    5
+## item179   NA   NA    2    5    2    4   NA   NA    5    5   NA    4    4    5
+## item180   NA   NA    1    5   NA   NA    3   NA    4   NA    5    4    3   NA
+## item181    4   NA    2    5    3    5    5    5    5    4    5   NA    5    5
+## item182   NA   NA    1    5   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item183   NA   NA    1   NA   NA   NA   NA    3    4   NA    3    4    2    4
+## item184   NA   NA   NA    5   NA   NA   NA   NA    5   NA    5   NA   NA   NA
+## item185   NA   NA   NA    5   NA   NA   NA   NA   NA   NA    4    3   NA   NA
+## item186   NA   NA    3   NA   NA   NA   NA    5    4   NA    4   NA   NA    4
+## item187   NA   NA    3    4   NA    4    5    5    4   NA    4   NA   NA    5
+## item188   NA   NA    4    5    3    4    5    5    4    1    4    4    4    4
+## item189    3    5    4    4    4    4    5    4    5    4    3    4    5    5
+## item190   NA   NA    4    5    3    4    5    5    5    1    5    5   NA    5
+## item191   NA    5    5    4    3    5    5    5    5    5    5   NA    4    5
+## item192   NA    5    5    4    1    4    5    5    5    5    4    4   NA    5
+## item193   NA   NA    4    4    3   NA    5   NA    5   NA    3   NA   NA    5
+## item194   NA   NA    4    5    4    5    5    5    5    5    4    5    5    5
+## item195   NA   NA    4    5   NA   NA    5   NA   NA   NA   NA    5    4    4
+## item196    4   NA    2    5   NA   NA    5    5    5    5   NA    4    4    5
+## item197   NA   NA    4    5   NA   NA    5    5    4   NA   NA    4    3   NA
+## item198   NA    4    2    5    4    5    5   NA    3    5   NA    4   NA    4
+## item199   NA   NA    4    5    4   NA    1   NA    5   NA   NA    5   NA    3
+## item200   NA   NA    5    5    4   NA    2   NA   NA   NA   NA   NA    4    4
+## item201   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    4
+## item202   NA   NA   NA    4   NA   NA    5   NA    5   NA   NA   NA   NA   NA
+##         V347 V348 V349 V350 V351 V352 V353 V354 V355 V356 V357 V358 V359 V360
+## item118    4    5    3    3    2    5   NA    3    5    5    5    3    5    2
+## item119    4    3   NA    3    5    4   NA   NA    5    4    3    4    4    2
+## item120    4    3   NA    3    5    4   NA    4    5    5    5    4    3   NA
+## item121    4    5    4    4    5    4    4    4    5    4    2    5    5    5
+## item122    3    5    3    3    4    4    1    1    5    5    1    4   NA    4
+## item123    5    4   NA   NA    4    4    1    5    5   NA    3    3   NA    4
+## item124    4    5    3    3    5    4   NA    2    5    5    2    4    1    3
+## item125   NA    2   NA    4    5   NA    3    1    5   NA    1    4   NA    1
+## item126    4    5    3    4    5    5    4    4    5   NA    4    3    5    4
+## item127    5    5    4    4    3    5    3    4    5    4    1    5    3    4
+## item128    4   NA   NA    4   NA   NA   NA   NA   NA   NA    1    4   NA    2
+## item129   NA   NA   NA   NA   NA    4   NA   NA   NA   NA   NA   NA   NA   NA
+## item130   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item131    5    5    3   NA    1   NA    4   NA   NA   NA    3    5    3   NA
+## item132   NA   NA   NA   NA   NA    2   NA   NA   NA   NA    3    4   NA   NA
+## item133   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item134   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item135    5    5    4    4    4    4    3    1    5    3    2    4    2    4
+## item136    3    3   NA    4    1    2    1    1   NA    5    1    5   NA    2
+## item137    2   NA   NA    4   NA   NA   NA   NA   NA    4    1   NA   NA   NA
+## item138   NA   NA   NA   NA   NA   NA    3   NA   NA    3    1   NA   NA   NA
+## item139    2   NA   NA    4   NA   NA    1   NA   NA   NA   NA   NA   NA   NA
+## item140    3   NA   NA    4    4   NA    3    1   NA    2    1    2   NA   NA
+## item141    4    4    4   NA    1    3    1    1    4    2    3    3   NA    2
+## item142    4    5    3    4    1    2    1   NA    3    3    1    2   NA    1
+## item143    4    5   NA    4    5    4    3    1   NA   NA    3    5    3   NA
+## item144    4    5   NA    4   NA    3   NA   NA   NA   NA    1    3   NA   NA
+## item146   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item147    5   NA   NA    4   NA    4    1   NA   NA    5    2   NA   NA   NA
+## item148    4   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item149    5    4    4    5    5    5    4   NA   NA    5    3    3    5    4
+## item150    4    5    4   NA    5    5    4    4    5   NA    4    2    5    4
+## item151    4    4    4    4    5    5   NA   NA   NA    5    4    4    3    4
+## item152    4    4    4   NA   NA    2   NA   NA   NA    3    2    3   NA    1
+## item153    4    5    4   NA    5    5    3   NA    5    3    3    2    5    2
+## item154    4    5    4    5    5    5    5   NA    5    1    4    4    4    2
+## item155    4    3    4    4    4    4    1   NA   NA    1    2    3    4    4
+## item156    3   NA   NA   NA    3    2    4   NA   NA    1    3    4   NA    3
+## item157    2    2    5   NA    5   NA   NA   NA    5   NA    4   NA    4   NA
+## item158    5    4    4   NA    5    4    4    2    5    5    5    2    5    2
+## item159    5    5    5    4    5    4    3   NA    5    5    4    4   NA   NA
+## item160    4    5    4   NA    5    4    4   NA    5    3    3   NA    3    4
+## item161   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item162    2    3    4    4    5    4    3   NA    5    5    4    2    5    1
+## item163    4    4    4    4    5    4    5    5    5    4    5    4    5    4
+## item164    4    4   NA    4    5    5    4    5    5    4    5    3    5    3
+## item165    2    2    3    4    5    4    5   NA   NA    5    5    2   NA   NA
+## item166    4    5    3    4    5    4    4   NA    5    4    4   NA    3   NA
+## item167    3    5   NA    4    5    4    4    4    5    3    5   NA    5   NA
+## item168    4    5    3    4    5    5    5   NA    5   NA    5   NA    5    4
+## item169    5    5    3    4    5    5    4   NA    5    5    4   NA    3    4
+## item170    5    5    3    4    5    5    4   NA    5    5    5   NA    4   NA
+## item171    5    5    3    4    5    5    5    5    5    5    4    4    5    3
+## item172    4    5    4    4    5    5   NA    4    5    5    5    3    5    5
+## item173    4    4   NA    4    5    4    5    2    5    5    4    3    5    2
+## item174    3    2    4   NA    5    5   NA   NA   NA    5    4    3    3   NA
+## item175   NA   NA   NA   NA    5   NA   NA   NA    5   NA    5   NA    5   NA
+## item176    5    4    3    4    5   NA    5   NA    5    5    5    5    5    5
+## item177   NA   NA   NA   NA   NA    4   NA   NA   NA    3    4   NA   NA   NA
+## item178    4    5   NA    4    5   NA    4   NA   NA    4    3    5    3    4
+## item179   NA   NA   NA   NA    5    4   NA   NA   NA    4    4   NA   NA   NA
+## item180    4   NA   NA    5   NA    4    3    1   NA    4    2    2   NA   NA
+## item181    2    4   NA    4    5    4    4   NA    5    5    4    2    5    4
+## item182   NA   NA   NA   NA   NA    4   NA   NA   NA   NA   NA   NA   NA   NA
+## item183    4    4   NA    4   NA    2   NA   NA   NA    1    4   NA   NA   NA
+## item184   NA   NA   NA   NA    5    4   NA   NA   NA   NA    3   NA   NA   NA
+## item185   NA   NA   NA   NA    5    4   NA   NA   NA    3    4   NA   NA   NA
+## item186    5    4    4   NA    5    4    4    1   NA    5    4    4   NA   NA
+## item187    4    5    4   NA    5    4    4   NA   NA    5    5   NA    5   NA
+## item188    4    3    5    4    5    5   NA   NA   NA    5    3    3    3    5
+## item189    4    5    3   NA    5    5    5   NA    5    5    4    2    5    4
+## item190    4    5    3   NA    5    5    5   NA    5    5    4   NA    5    4
+## item191    5    5    4    5    5    5    4   NA    5    5    4    4    5   NA
+## item192    4    4   NA    5    5    5    4   NA    5    5    4    2    5    4
+## item193    4    5    4   NA    5    5    4   NA   NA    5    4    3    5    4
+## item194    2    5   NA   NA    5    4    5    4    4    4    4    2    5    4
+## item195   NA   NA    4   NA    5    4   NA   NA   NA    5    4    4    4   NA
+## item196    4   NA    3    4    5    4    4    2   NA    5    3    4    4    2
+## item197    3    4   NA    4    5    5   NA   NA   NA    5    3    3    3    3
+## item198   NA   NA    3   NA    5    5    5   NA    5    5    4    3    5   NA
+## item199    4    5    3    4    5    4   NA   NA   NA    4    5    4    4    2
+## item200   NA   NA   NA   NA    5    4   NA   NA   NA    5   NA    2   NA   NA
+## item201   NA   NA    4   NA    5   NA   NA   NA   NA    5    5    4    5   NA
+## item202    3   NA    4   NA    5    4   NA   NA   NA    5    5    3    5   NA
+##         V361 V362 V363 V364 V365 V366 V367 V368 V369 V370 V371 V372 V373 V374
+## item118    4    4    1    4    3    5    5    2    2    4    4    2    5    5
+## item119    3    4    1    3    4    5    4    3    3    3    4    1    4    4
+## item120    3    4    1    4    5    4    5    2    3    3    5   NA    4    4
+## item121    5    5    5    5    5    5    5    4    5    5    5    3    3    5
+## item122   NA   NA   NA    3    3    3   NA    3    4    5    5    2    1    4
+## item123   NA    3   NA   NA    4    5    4    4    1    4    4   NA    4    5
+## item124    4    4    1    2    4    4    1    4    3    2    4    2    3    4
+## item125    4    3    4    4    3    3    5    2    5    3    5    3   NA    3
+## item126    4    4    4    4    4    5    4    4    4    5    4    3    2    5
+## item127    4    5    2    3    4    5    4    4    4    4    5    2    2    5
+## item128   NA   NA   NA    1    3    3   NA    2   NA   NA   NA   NA   NA   NA
+## item129   NA   NA   NA   NA   NA    3   NA   NA   NA   NA    4   NA   NA   NA
+## item130   NA   NA   NA   NA   NA    3   NA   NA   NA   NA   NA   NA   NA   NA
+## item131    5   NA   NA   NA    3   NA    5    3    3   NA    4    3    4    3
+## item132   NA    3   NA   NA   NA    3   NA   NA   NA    3    5   NA   NA    3
+## item133   NA   NA   NA   NA   NA    3   NA   NA   NA   NA    4   NA   NA   NA
+## item134   NA   NA   NA   NA   NA    3   NA   NA   NA   NA    4   NA   NA   NA
+## item135    3    4    2    1    4    4    1    2    3    4    4    2    4    4
+## item136   NA    2   NA   NA    2   NA   NA   NA   NA   NA    1    2    2   NA
+## item137   NA   NA   NA   NA   NA   NA   NA   NA   NA    3    2    1   NA    3
+## item138   NA   NA   NA   NA   NA    3   NA   NA   NA   NA   NA   NA   NA   NA
+## item139   NA   NA   NA   NA   NA    3   NA   NA   NA    3   NA    3   NA   NA
+## item140    3    3   NA   NA   NA    3   NA    5    3    3    4    3   NA    2
+## item141    3    5    1    3    1    2    5    5    5    3    3   NA    3    3
+## item142   NA    3   NA   NA    4    3   NA    2    3   NA    4    3   NA    3
+## item143    3    5   NA   NA    3    3    1    5   NA   NA   NA    3    4    4
+## item144   NA    1   NA   NA    4    4   NA   NA   NA   NA    4    2   NA   NA
+## item146   NA    2   NA   NA   NA    3   NA   NA   NA   NA   NA   NA   NA   NA
+## item147   NA    4   NA   NA   NA    4   NA   NA   NA    3    5   NA   NA    5
+## item148   NA   NA   NA   NA   NA    4   NA   NA   NA   NA   NA   NA   NA    5
+## item149    4    5   NA    1    5   NA   NA    3    5    5    5    4    4    5
+## item150    4    5    4   NA    4    5    4    2    4    4    3    4    5    5
+## item151    3    5    3    4    5    5    4    2   NA    5    5    4    5    4
+## item152   NA   NA    2    2    3   NA   NA    4   NA    5    4    2    4   NA
+## item153    5    5    5    3    4    4    5    4    5    4    5   NA    3    5
+## item154    5    5    5    2    5    4    5    4    4    5    5    3    4    5
+## item155    3    3   NA    2    4   NA   NA    5    1    5    4    2    4    5
+## item156   NA   NA    4   NA   NA   NA   NA    1    4    5    5   NA    3    5
+## item157   NA   NA    5   NA    3    5    5   NA   NA   NA    3    3    4    5
+## item158   NA    5    5   NA    4    5    4    4    3    4   NA    3   NA    5
+## item159   NA    5   NA    3    3    4   NA   NA   NA    4   NA    4   NA    5
+## item160    3    4    2    3    5    3    4    2    4    4    5   NA    4    5
+## item161   NA   NA   NA    1   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item162    1    5   NA   NA    3    5    1    5    4    5    5    1    3    5
+## item163    4    4    2    4    4    4    5    5    4    5    5   NA    5    5
+## item164    3    4   NA    4    4    5    5    1    5    5    5   NA    4    5
+## item165   NA    5   NA   NA    3    4   NA   NA    5    5    5   NA   NA    5
+## item166   NA    5   NA    4    3    5    5   NA    5   NA    5   NA   NA    5
+## item167    3    3    2    4    3    4    5   NA    4   NA    5   NA    5    5
+## item168    5    4   NA    4    3    5    5    1    3   NA    5   NA    4    5
+## item169    3    5    2    3    4    5    4   NA    3   NA    5    3    3    5
+## item170   NA    5   NA    4    4    4    4   NA    5   NA    5    3   NA   NA
+## item171    4    4    4    4    5    5    5    3    4   NA    5   NA   NA    5
+## item172    5    5    5    4    3    4    5    2    3    5    5   NA    4    5
+## item173    3    3   NA    4    2    5    5    3    5   NA    5   NA    2    5
+## item174    4    4   NA   NA    3    5    4    3   NA   NA   NA   NA   NA    5
+## item175   NA    5   NA   NA   NA    4    5   NA    5   NA    5   NA   NA    4
+## item176    5    5    4    4    4    5    5   NA    4    5    5   NA    5    5
+## item177   NA    5   NA   NA   NA    4   NA   NA   NA   NA   NA    1   NA    5
+## item178   NA    3    2    4    3    4    5   NA   NA   NA    5   NA    3    4
+## item179   NA    4   NA   NA    3    5   NA   NA   NA   NA    5   NA   NA    5
+## item180   NA    5   NA   NA    3    3   NA   NA   NA   NA    3    3   NA    5
+## item181    4    4   NA    3    3    4    5    4    5    5    5    3    2    5
+## item182   NA   NA   NA   NA   NA    3   NA   NA   NA   NA    5   NA   NA   NA
+## item183   NA    1   NA   NA    3    3   NA   NA   NA   NA    5    3   NA   NA
+## item184   NA    5   NA   NA   NA    4   NA   NA   NA   NA    3   NA   NA    5
+## item185   NA    5   NA   NA   NA    4   NA   NA   NA   NA    3   NA   NA   NA
+## item186   NA    4   NA   NA   NA    5   NA   NA   NA   NA    5    4   NA   NA
+## item187    3    5   NA    4   NA    5    4   NA   NA    5    4    4    4    4
+## item188    4    4    2    4    5   NA    4    4   NA    5    5   NA    4    4
+## item189    4    4    2    4    5    4    4    2    4    5    5    2    4    5
+## item190    4    5    4   NA    4    5    4    2   NA    5    4    2    5    5
+## item191    4    5    4    4    5    5    4    3    5    5    5    4    3    3
+## item192    4    5    4    4    5    4   NA    1    4   NA    5    4    3    4
+## item193   NA    4    4    4    5    5    4    2    3   NA    5   NA   NA   NA
+## item194    3    3    2    4    5    5    5    4    4   NA    5   NA    5    5
+## item195    3    5   NA   NA    3    5    4    3   NA   NA    5   NA   NA    4
+## item196    3    3    2    3    5    3   NA    5    4    5    5   NA    1    5
+## item197   NA   NA    2   NA    5    4   NA    5   NA   NA    5    4   NA    4
+## item198    3   NA    2    4    3    4    4    4   NA   NA    5   NA   NA    5
+## item199   NA    3    2    4    5    5   NA    1   NA    4    5    4   NA    5
+## item200   NA    3   NA    4    3   NA   NA   NA   NA    5    5   NA   NA   NA
+## item201    4   NA   NA   NA   NA   NA    4   NA    2   NA   NA   NA   NA   NA
+## item202   NA    4    2    3   NA   NA    4   NA   NA   NA   NA   NA   NA    5
+##         V375 V376 V377 V378 V379 V380 V381 V382 V383 V384 V385 V386 V387 V388
+## item118    5    4    5    4    4    4    4    5    5    5    5   NA    3    5
+## item119    5    1   NA    4   NA    4   NA    5    4    4    3    3    4   NA
+## item120    4    2    2    4   NA    4    3    5    5    4    2    3    4   NA
+## item121    5    5    5    5    5    3    3    5    5    4    5    3    5    5
+## item122   NA    3    2    3    4    3   NA   NA    3    3    3    2    4   NA
+## item123    5   NA    4    3    4    3    4    5    4    3    4    3    5   NA
+## item124    3    5    5    1    2    4    4    4    2    4    5    3    3    4
+## item125    4    1    4    1    3    3   NA   NA    4    4    1    3    4    3
+## item126    4    2    5    4    5    2    3    2    4    4    2    4    5    3
+## item127    3    2    3    4    5    2    3    2    4    3    1    4    2    4
+## item128   NA   NA    3    1   NA   NA   NA   NA   NA    3    3   NA   NA   NA
+## item129   NA   NA   NA   NA   NA    1    1   NA   NA   NA    3   NA   NA   NA
+## item130   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item131    1    5   NA    4   NA    3   NA    5    4   NA    3    3    2    5
+## item132   NA   NA    5    4    4    3   NA   NA    3   NA    3    3   NA   NA
+## item133   NA   NA    4   NA   NA    3    2   NA   NA   NA    1   NA   NA   NA
+## item134   NA   NA    4   NA   NA    3    2   NA   NA   NA    3   NA   NA   NA
+## item135    1    4    1    2    4    4    4    4    5    3    3    3    3    3
+## item136   NA    1    4    5   NA    1   NA   NA   NA   NA    1   NA   NA   NA
+## item137   NA   NA    2    4   NA   NA    3   NA   NA   NA    1    3   NA   NA
+## item138   NA   NA    1    4   NA   NA   NA   NA   NA   NA    2   NA   NA   NA
+## item139   NA   NA    1    3   NA   NA   NA   NA    4   NA    2   NA   NA   NA
+## item140    3    2    1    4   NA    3    4   NA    3   NA    2    3   NA   NA
+## item141    1    3    5   NA    5    3    4    4    2   NA   NA    3    5    4
+## item142   NA   NA    2    5   NA    3   NA   NA   NA   NA    1    3   NA   NA
+## item143   NA   NA    5    4   NA    2    1    4    4    3    2    2   NA    5
+## item144   NA   NA   NA    4   NA   NA   NA   NA    5   NA    3   NA   NA   NA
+## item146   NA   NA    3    5   NA   NA    2   NA   NA    4    1   NA   NA   NA
+## item147   NA   NA    1    5   NA    2    1   NA   NA   NA   NA   NA   NA   NA
+## item148   NA   NA   NA   NA   NA   NA    1   NA   NA   NA   NA   NA   NA   NA
+## item149   NA   NA    5    5    5    4   NA    5   NA   NA    4    3   NA   NA
+## item150    5   NA   NA    5    4    4    4    5    5    4    5    3    2    4
+## item151    4   NA    5   NA    5    4    1    5    5    4    2    4    4   NA
+## item152    4   NA    3    5    5    3    3   NA   NA    4    1    3    5   NA
+## item153    4    5    5    4    5    5    5    4    4    4    5    3    5    4
+## item154    5    4    2    5    4    5   NA    5    5    4    5    3   NA   NA
+## item155   NA   NA    2    5    5    4   NA    4   NA   NA    4    4   NA   NA
+## item156    5   NA    5   NA    5    4   NA    4    4    4    5    3    4   NA
+## item157    4   NA    2   NA    5    4    4    5   NA    4   NA    3   NA   NA
+## item158    5   NA   NA    5    4    4    4    3    5    4    5    3    4    4
+## item159    4   NA   NA    5    4    4    2    2    4    4    3   NA   NA    4
+## item160    4    4    5    3    5    4    4    3    4    4    5    3    5   NA
+## item161   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item162   NA   NA    4    5   NA    4   NA    4    5    4    3    3   NA    5
+## item163    5    4    5    4    5    4   NA    5    5    4    5    3   NA    5
+## item164    5    4    5    5    4    4    2    4    5    3    5    3   NA    5
+## item165   NA   NA   NA    4   NA    4   NA   NA   NA    4   NA    3   NA   NA
+## item166   NA   NA   NA    4   NA    4    4    4   NA    4   NA    3   NA    5
+## item167    5    4    4    5    5    4    2    4    5    4   NA    3    3    5
+## item168    5    5    2    4    4    4    4    4    5    4    5    3    3    4
+## item169    5    3    2   NA    5    4   NA    4    4    4   NA    3   NA   NA
+## item170    5   NA   NA    4    2    4    4    4    5    4    5    3   NA    5
+## item171    5    4   NA    4    5    4    4    5    5    4    5    4    4    5
+## item172    5    5    3    5    5    4    4    5    5    4    5    4    5    4
+## item173    5    4    4    4    5    4   NA    5    5    4    5    3   NA    5
+## item174    4   NA   NA   NA    2    3    4    4    4    4    4    4   NA    4
+## item175    4   NA   NA   NA   NA   NA   NA    4    5    5    5   NA   NA    5
+## item176    5    5    2    4    3    4    4    3    5    4    5    4    5    5
+## item177   NA   NA    3    5   NA   NA   NA   NA   NA    4   NA   NA   NA   NA
+## item178   NA    4    5    4    4   NA    3    4    5    4   NA    4    2    5
+## item179   NA   NA    5   NA   NA    4   NA    4    4    4   NA    4   NA    4
+## item180   NA   NA    4    4   NA    2   NA   NA   NA    4    1   NA   NA    4
+## item181    4    5    5   NA    3    2    1    4    5    4    4    4   NA    5
+## item182   NA   NA    4    4   NA    2   NA   NA   NA   NA   NA   NA   NA   NA
+## item183   NA   NA    2    5   NA    2   NA   NA   NA   NA    3   NA   NA   NA
+## item184   NA   NA    2    4   NA   NA   NA   NA    4   NA   NA   NA   NA   NA
+## item185   NA   NA    2    4   NA    2   NA    4   NA   NA   NA   NA   NA   NA
+## item186   NA   NA   NA    5    5    4    4   NA    4   NA   NA   NA    1   NA
+## item187    5    4   NA    5    2    4    4    3    5    4   NA    4    1    4
+## item188    5    1    5   NA    5    4    1    5    5    4    5    5    1   NA
+## item189    5    4    5    2    5    4    4    4   NA    4    5    4    4    4
+## item190    5    4   NA    5   NA    4   NA    4    5    4    5    4    4    4
+## item191    5    4    5    5   NA    4    5    4    5    4   NA    4    5    4
+## item192    5    5    5    5    5    4    5    4    5    4    5    4    4    4
+## item193    5   NA    5    2   NA    4   NA    5    4    4    5    4   NA   NA
+## item194    5    3    1    4   NA    4    4    4    4    4    4    4    4    5
+## item195    4   NA   NA   NA   NA    3   NA    3    5    4    4   NA   NA   NA
+## item196    4    3    3   NA    5    3   NA    5    5    4    3    4   NA    5
+## item197    4   NA    3   NA    5    3   NA   NA    5   NA    4   NA   NA   NA
+## item198    5    2    2    4   NA    3    4    4    5    4   NA   NA   NA    3
+## item199    5   NA    1   NA    5    4   NA    4    5    4   NA    4   NA   NA
+## item200   NA   NA    5   NA   NA    3   NA   NA    4   NA    5   NA    5   NA
+## item201    4   NA   NA   NA   NA    2   NA    2    5    4   NA   NA   NA   NA
+## item202    5   NA   NA   NA   NA    4    4    3    5    4   NA   NA   NA   NA
+##         V389 V390 V391 V392 V393 V394 V395 V396 V397 V398 V399 V400 V401 V402
+## item118    5    5    5    4    5    4    4    3    5    4    5    5    5    1
+## item119   NA    5    5   NA    4    4    4    2    5    4    3   NA    5   NA
+## item120    4    5    5    4    4    4    2    5    5    4    4   NA    4   NA
+## item121    5    5    5    4    5    5    5    5    5    3    4    3    4    4
+## item122    5    4    3    3    2    4    4    5    1    4    5    1    2    2
+## item123   NA   NA    4   NA    4    5    5   NA    3    3   NA    4    4    4
+## item124    1    3    5    2    1    5    5    4    2    5    3    4    2    2
+## item125   NA   NA    3   NA   NA   NA   NA    3    1    3   NA    1   NA    3
+## item126    5    4    4    4    3    4    5    4    4    5    5    3    4   NA
+## item127    4    4    5    3    1    5    5    5    2    5    1    3    3    2
+## item128   NA    2    2    3    1   NA    1   NA   NA    4   NA   NA   NA    4
+## item129   NA    2   NA   NA   NA   NA   NA   NA   NA    4   NA   NA   NA    2
+## item130   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item131    4    2    4    3    3    5    1    4    5   NA    1   NA    5    3
+## item132   NA   NA   NA   NA   NA   NA    1   NA   NA   NA   NA    2    2   NA
+## item133    1    3    2    3   NA   NA    4   NA   NA   NA   NA   NA   NA    4
+## item134   NA    3    4   NA   NA   NA   NA   NA   NA    3   NA   NA   NA    2
+## item135    5    3    2    3    1    3    1    3    4    4    4    3    2    4
+## item136   NA    3    1   NA    1   NA    1   NA    1   NA   NA    1    1   NA
+## item137    1   NA    2    3   NA   NA    1   NA    1   NA   NA   NA   NA   NA
+## item138   NA   NA   NA    3   NA   NA    5   NA   NA   NA   NA   NA   NA   NA
+## item139   NA   NA    2    3   NA    3   NA   NA    1   NA   NA   NA   NA   NA
+## item140   NA    2    2    3   NA   NA   NA   NA   NA    5    2    1   NA    2
+## item141    4    1    4    3    3    4    1    3    2    4    4    2    3    2
+## item142    4    1    4    3    3    2    1    2    2    3    1   NA    2    2
+## item143   NA   NA    4    3    3    3    4   NA    3    1   NA    2    1    2
+## item144    1    1    4    3    3    3   NA   NA    2   NA   NA   NA   NA    3
+## item146   NA   NA    2   NA    1   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item147   NA   NA    5    4    4   NA   NA   NA   NA   NA   NA   NA    4   NA
+## item148   NA   NA    4    4   NA   NA   NA   NA   NA   NA   NA   NA    2   NA
+## item149    5    5    4    4    3    5    5    4    5    5    5   NA    5    2
+## item150    4    4    5    4    4    5    5    3    5    5    4   NA    5   NA
+## item151    4    4    1    4    2    5    5    2    5    5   NA    4    4    3
+## item152    3    4    2    3    1    4    4    3    4   NA   NA    4    1    3
+## item153    5    4    4    4    5    5    4    4    5    5    5    4    3    2
+## item154    5    4    5    4    4    5    5    5    5    4    5   NA    5   NA
+## item155    4    4    4    4    3    5    4   NA    5    4    2   NA    1    4
+## item156    5    4    2    4    4    5   NA    4    5    5   NA   NA    2   NA
+## item157    5    5    4    4    3   NA    5    4    5   NA   NA   NA    3   NA
+## item158    5    5    5    4    4    5    5    4    4    5    5    5    5    2
+## item159    5    5    3    4    4    5   NA   NA    4    5   NA   NA    5   NA
+## item160    4    5    4    4    4    5    3    4    5    4    3    4    3    2
+## item161   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    3   NA    5
+## item162    2    5    4    4    4    5    5    5   NA    3    1    4    4    3
+## item163    5    5    4    4    4    5    5    5    5    4    4    4    4   NA
+## item164    5    5    4   NA    4    5    5    5    5    3    5    5    4   NA
+## item165   NA   NA    2    4    4    3   NA    4   NA   NA   NA    4    4   NA
+## item166    3   NA    5    4    4    5    5    4    5   NA    5   NA    4   NA
+## item167    5    5    4   NA    4   NA    5    3    5   NA    3   NA    5   NA
+## item168    5    5    5    4    5    5    5   NA    5   NA    5    4    5   NA
+## item169    5    5    5    4    5    5    5    5    5    2    5    2    3   NA
+## item170    5    5    5    4    5    5    5    4    5    5    5    4    4   NA
+## item171    5    5    4    4    5    5    5    5    5    5    4    4    5   NA
+## item172    5    5    4    4    5    5    5    4    5    5    5    4    5    3
+## item173    2    5    3    3    4    5    5    5    5    3    5    4    3   NA
+## item174   NA    5    4    4    3    5    5    3    4    3    3   NA    4   NA
+## item175    1    5   NA   NA    4    5    5    4    5    5    5    5    5   NA
+## item176    5    5    4    4    5    5    5    5    5    5    5    4    5   NA
+## item177   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item178    4    5    4    4    2    5    5    4    5   NA    4    2    2   NA
+## item179    2   NA    4    4    4    5   NA    4    5    4    3   NA    3   NA
+## item180   NA    5    4    2   NA   NA   NA   NA    3   NA   NA    3   NA    4
+## item181    5    2    4    4    5    5    3    5    5    3    5    5    4   NA
+## item182   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item183   NA    2    3    3   NA   NA    1   NA    3   NA   NA   NA   NA    2
+## item184   NA    2   NA   NA   NA    5   NA   NA   NA   NA   NA    4    2   NA
+## item185   NA    2   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    2   NA
+## item186    5    4   NA    4    4    5   NA   NA    4   NA   NA   NA    2   NA
+## item187    5    5    4    4    4    5    5    4    4    3    3   NA    3   NA
+## item188   NA    5    4   NA    3    5    5    4    5    3    2    4    5    4
+## item189    5    5    4    4    4    5    3    5    4    4    4   NA    5    4
+## item190    5    5    4   NA    4    5    5   NA    5    4    5   NA    5   NA
+## item191    5    5    4    4    4    5    4    5    5    4    5   NA    5   NA
+## item192    5    5    4    4    3    5    3    4    5    5    5   NA    5   NA
+## item193    5    5    4    4    5    5    5    4    5    5   NA   NA    5   NA
+## item194    5    5    4    4    4    5    5    4    5    5    4   NA    3   NA
+## item195   NA    5   NA   NA    4   NA   NA    5    5    5   NA    3    4   NA
+## item196    5    5    3    4    2    5    4    4    5    5    4    2    2   NA
+## item197    2    5    3    4    3    5    5    2    4   NA   NA   NA    2    4
+## item198   NA    5    4   NA    5    4   NA    4    5   NA    5   NA    4   NA
+## item199    4    5    4   NA    4    5    5    3    5   NA   NA    2    3    2
+## item200   NA   NA   NA   NA   NA    5    4   NA    5   NA   NA   NA    1   NA
+## item201   NA    5   NA   NA   NA   NA   NA   NA    5   NA   NA   NA    4   NA
+## item202    5    5   NA    4    3   NA   NA   NA    4    5    5   NA    5   NA
+##         V403 V404 V405 V406 V407 V408 V409 V410 V411 V412 V413 V414 V415 V416
+## item118    4    4    3    4    4    5    4    1    4    5    5    4    4    5
+## item119    4    4    4    4    2    3    4    1    4    4    3    4    3    3
+## item120    3    4    3    5    3    4    2   NA    4    4    4    4    4    2
+## item121    3    4    5    5    4    5    5    1    4    3    5    5    5    4
+## item122    2    4    5    5    2   NA    4    1    4    4    4    4    1   NA
+## item123   NA   NA    5    5    3    2    5   NA    3    3    3    4   NA    3
+## item124    2    4    5    5    4    4    4    1    4    5    4    5    5    1
+## item125   NA    2    3    4    2   NA    4   NA    1    5    5    4    4   NA
+## item126    3    3    3    4    3    1    5    1    3    3    3    3    4    3
+## item127    4    3    5    4    4    2    2    1    4    4    4    4    2    3
+## item128    1   NA    3   NA   NA    1    4    1    1    3   NA    5   NA   NA
+## item129   NA   NA   NA    1    2   NA   NA    1   NA    3   NA   NA   NA   NA
+## item130   NA   NA   NA   NA   NA   NA    4    1   NA   NA   NA   NA   NA   NA
+## item131    4    3   NA    5    2   NA    4    1    4    3    3    5    1    2
+## item132   NA   NA   NA   NA   NA    3    5    1   NA   NA   NA   NA   NA   NA
+## item133   NA   NA   NA    1    2   NA    5    1   NA   NA   NA   NA   NA   NA
+## item134   NA   NA   NA    2   NA   NA    5    1   NA   NA   NA   NA   NA   NA
+## item135    2    4    5    2    4    2    4    1    3    3    4    5    4    2
+## item136    1   NA    5    1    2    1    2    1   NA   NA   NA    5    1   NA
+## item137    1   NA   NA   NA    2   NA    2    1   NA   NA   NA   NA   NA   NA
+## item138    2   NA   NA    1    3   NA    4    1   NA   NA   NA   NA   NA   NA
+## item139    2   NA   NA   NA   NA   NA    2    1   NA   NA   NA   NA   NA   NA
+## item140    2    3    5    2    2    1    4    1    4   NA    4    4   NA    2
+## item141    3    2    5    4    3    2    4    1    3    3    3    4    1    2
+## item142    3   NA    5    4    3   NA    2    1    3    3   NA   NA   NA   NA
+## item143    4    4    5    2    2    3    5    1    2    3   NA    5    1    3
+## item144    4   NA    4    4    3   NA   NA    1    3   NA   NA   NA   NA   NA
+## item146   NA   NA   NA   NA   NA    2    2    1   NA   NA   NA   NA   NA   NA
+## item147   NA   NA   NA   NA   NA    3    5    1   NA   NA   NA   NA   NA   NA
+## item148   NA   NA   NA   NA   NA   NA    4    1   NA   NA   NA   NA   NA   NA
+## item149    4    5    4    4    4   NA    5   NA    4    3    4    5    4    3
+## item150    4    4    4    4    4    4    5    1    4    3    4    5    5    2
+## item151    5    4    3   NA    3    4    5    1    4    4    4   NA    4    3
+## item152    2    2    5    2    3   NA    4   NA    2   NA    3    4    3    2
+## item153    3    3    4    5    4    3    5    1    4    4    4    5    2    2
+## item154    5    4    5    4    4    5    5    1    4    5    4    4    4    4
+## item155    2    2    5    2    4   NA    5   NA    4    5    3    4    2    3
+## item156   NA    3    3    5    4    3    5    1    4    5    4    5    4    3
+## item157    5   NA    5    3    4    4   NA   NA    4    4   NA   NA    4    3
+## item158    3    4    5    2    4    5    4    1    4    4   NA    4    4    2
+## item159   NA   NA    5    2    4   NA    5    1    4   NA    3    4    1    2
+## item160    4    3    3    4    3    5    5    1    4    5    3    4    3    3
+## item161   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item162    4   NA    4    4    3    3    4    1    4    3    4    4   NA    3
+## item163    4    4    4    4    3    5    5    1    4    3    4    5    4    3
+## item164    4    4    4    4    3    5    5    1    4    3    4    5    4    3
+## item165    3   NA    5    2   NA   NA    5    1   NA    3   NA    5   NA   NA
+## item166    3   NA    5    4   NA    5    4    1   NA    3   NA    4   NA    3
+## item167    4    4    4    4    3    5    4    1   NA    3    4    4    4    3
+## item168    4    4    4    4    4    4    5    1   NA    3    5    5    5    4
+## item169    4    4    5    4    3    3   NA    1    4    3    5   NA    4    3
+## item170    3   NA    5    2    4   NA    5    1    4    4   NA    4    3    3
+## item171    5    5    5    4    4    5    5    1    4    5    4    5    5    4
+## item172    4    4    5    4    4    4    5    1    4    5   NA    4    5    5
+## item173    4    4    4    1    2    5    4    1    4    5    4    5    3    2
+## item174    4    3    5   NA    3    3    5    1    3    3   NA   NA    4    3
+## item175    3    4    5   NA    3    5   NA    1    4    4   NA    5    5    3
+## item176    4    5    4    5    4    5    4    1    4    5   NA    5    3    4
+## item177    3   NA    3    2   NA   NA    4    1   NA    3   NA   NA   NA   NA
+## item178    4   NA    4    2    3    2    2    1   NA    3    4    4    2    2
+## item179   NA   NA    5   NA   NA    4    5    1   NA    3   NA    5   NA   NA
+## item180    4   NA    5    4   NA   NA    5    1   NA   NA   NA    5   NA   NA
+## item181    3    4    5   NA    3    4    5    1   NA    5    3    4    4   NA
+## item182   NA   NA   NA   NA   NA   NA    5    1   NA   NA   NA   NA   NA   NA
+## item183    4   NA    4   NA   NA   NA    4    1   NA   NA   NA   NA   NA   NA
+## item184   NA   NA    3   NA   NA   NA    5   NA   NA    5   NA   NA   NA    1
+## item185   NA   NA    3   NA   NA   NA    4    1   NA   NA   NA   NA   NA   NA
+## item186    4   NA    5    1    4   NA    2   NA   NA   NA    3    5    4   NA
+## item187    3   NA    5    2    4   NA    4    1   NA    3    4   NA    4    2
+## item188    5    5    5    4    4    5    3    1   NA    3    3   NA    3    2
+## item189    4    4    4    4    4    5    5    1    4    3    4    5    5    2
+## item190    4    5    4    5    4    5    4    1    4    4    5   NA    5    4
+## item191    4    5    4    4    4    4    5    2    4    4   NA    4    5    4
+## item192    4    5    5   NA    4    4    5    1    4    3   NA    4    4    5
+## item193   NA   NA    4    4    4   NA   NA    1    4    4   NA   NA    5    3
+## item194    3    4    5    4    3    5    4   NA    4   NA    3    4    3    3
+## item195    3   NA    4    5    3   NA   NA    1    4   NA   NA   NA    3    3
+## item196    3    4    5    4    4    2    4   NA    4    4    3    5    2    2
+## item197    4   NA    5    2    4   NA    3   NA    3   NA    3   NA   NA    3
+## item198    3   NA    4    4    4    5    4   NA    4   NA   NA    5    3    3
+## item199    4    3    5    4    4   NA    2   NA    3   NA    4    5    2    3
+## item200   NA   NA   NA   NA    3    4    3    1   NA   NA   NA   NA    2    3
+## item201   NA   NA    5    3    3   NA    4   NA   NA   NA   NA   NA    4    4
+## item202   NA   NA    5    5    3   NA   NA   NA    3   NA   NA   NA    3    4
+##         V417 V418 V419 V420 V421 V422 V423 V424 V425 V426 V427 V428 V429 V430
+## item118    4    5   NA    4    4    4    5    2    4    4    1    4    5    4
+## item119    3    5   NA    4    4    4    5    3    4    4   NA    3    5    4
+## item120    3    3    1    3    4    3   NA    3    4    2    4    4    5    5
+## item121    4    4    5    3    5    4    5    4    5    5    4    4    5    5
+## item122    4    1    1    2    2    2    4    2    4    2    2    3    1    1
+## item123    4    2   NA    4    3   NA    1   NA   NA   NA    4    3    5    3
+## item124    4    3   NA    3    2    3    4   NA    5    1    4    4    1    2
+## item125    4   NA   NA    3    2    5    1    2   NA   NA    3    3    5   NA
+## item126    4    3   NA    4    4    4    5    3    3    4    4    4    1    4
+## item127    4    4    1    2    4    5    5    3    5    4    4    4    5    3
+## item128    2   NA   NA   NA   NA   NA   NA    2    3   NA   NA    2   NA   NA
+## item129   NA   NA   NA   NA   NA   NA   NA    2   NA   NA   NA   NA   NA    1
+## item130   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item131    4    3    3    3    4   NA    5    2    4    3    4    3   NA    5
+## item132    4   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    1
+## item133   NA   NA    1    3   NA   NA   NA    1    4   NA   NA   NA   NA    1
+## item134   NA   NA   NA    3   NA   NA   NA    1    4   NA   NA   NA   NA    2
+## item135    4    3    3    4    4    2    4    1    3    4    4    3    1    2
+## item136   NA    1   NA   NA   NA   NA   NA    1    3   NA   NA    2   NA    1
+## item137    2   NA   NA   NA   NA   NA    3    1    3   NA    2    2   NA   NA
+## item138    2   NA   NA   NA   NA   NA   NA   NA    3   NA    3   NA   NA   NA
+## item139    2   NA   NA   NA   NA   NA    4   NA    3   NA    2   NA   NA   NA
+## item140    2    3    1    3   NA   NA    3    3    3    1    2    3   NA    2
+## item141    2    3    1    3    3    4    5   NA    3    1    2    3    1    4
+## item142    2   NA    1    3    1   NA    4    3    3   NA    4    3   NA    2
+## item143    4    3    3    4   NA   NA    4    3    3   NA    4    3    1   NA
+## item144    4   NA    2    2   NA   NA    1    4    3   NA    4   NA   NA   NA
+## item146    3   NA    1   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    1
+## item147   NA   NA   NA   NA   NA   NA   NA    4    3   NA   NA    4   NA   NA
+## item148   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item149    4    4   NA    4    5    5   NA    3   NA    4    4    4    5    4
+## item150    4    4    1    4    4    4   NA    3    4    5    4    4    5    5
+## item151    4    4    3    5    2   NA    5    1    3    4    4    3   NA    4
+## item152    3    4   NA    2   NA    2    4    1   NA    4    2   NA    5    1
+## item153    4    4    5    3    5    5    5    3    3    1    3    3    3    5
+## item154    4    4    3    4    4   NA    3    4    4    4    4    4    5    5
+## item155    4    5   NA    4    1    4   NA    3   NA    4    4    4    5    2
+## item156    4    3    4    3    5   NA    4    4    3    1   NA   NA    3    3
+## item157    4    4   NA    4   NA    2    5    4   NA   NA    5    4    5    3
+## item158    4    3    3    4    4    5    4    4    4    4    5    3    5    4
+## item159    4   NA    2    2    5   NA    4    4    5   NA    5    4   NA   NA
+## item160    4    4    4    5    4    5    5    4    3    1    4    3    5    4
+## item161   NA   NA   NA   NA   NA   NA    3   NA   NA   NA   NA   NA   NA   NA
+## item162    2    4   NA    3   NA   NA    3    3    4   NA    5    4    1    1
+## item163    3    4    4    4    5    4    5    3    4    5    5    4    5    5
+## item164    3    3    4    2    4   NA    5    3    3    5    5    3    5    4
+## item165    3    2    4   NA   NA   NA   NA    4    3    5   NA    4   NA   NA
+## item166    3    3    4   NA    5    3    5    3   NA    4    4    4    3    5
+## item167   NA    4   NA    4    4    3    5    3   NA   NA    5    3    5    4
+## item168   NA    5   NA    4    5   NA    5   NA    4   NA    5    4    5    5
+## item169   NA   NA    4    3    5   NA    4    3    4    4    4    3    5    4
+## item170    4    5   NA    5    4   NA    5    3    4    5    5    4    5    5
+## item171    4    5   NA    4    5    4    5    4    3    5    5    4    5    5
+## item172    4    5   NA    5    4   NA    5    4    4   NA    5    4    5    5
+## item173    4    2    4    3    3   NA    5   NA    4    3   NA    4    1    4
+## item174    4    1    4    3   NA   NA    3   NA    5    4    5    4    1    4
+## item175   NA   NA   NA    5   NA   NA    5   NA    5   NA    5    4    5    3
+## item176    4    5    4    5    5    5    5    4    4   NA    5    3    5    5
+## item177   NA   NA   NA   NA   NA   NA   NA    3   NA   NA   NA   NA   NA   NA
+## item178    3   NA    4    4   NA    4    5   NA    5    1    3    3    1    4
+## item179   NA    5   NA    3   NA   NA   NA   NA   NA   NA   NA    4   NA   NA
+## item180    4   NA   NA   NA   NA    2    2    3    3   NA   NA   NA    5   NA
+## item181    4    4    4    4    5    5    5   NA    3    3    4    3    4    4
+## item182   NA   NA   NA   NA   NA   NA   NA    3   NA   NA   NA   NA   NA    1
+## item183    3   NA    3   NA   NA   NA   NA    3    3   NA   NA   NA   NA    2
+## item184   NA   NA   NA   NA   NA    4   NA   NA    3   NA   NA   NA   NA   NA
+## item185   NA   NA   NA   NA   NA    4   NA   NA    3   NA   NA   NA   NA   NA
+## item186   NA   NA   NA    3   NA   NA    5    4    4    4    4   NA   NA    3
+## item187    4   NA   NA    4   NA    1    5   NA    4    4    5   NA    5    4
+## item188   NA    3   NA    5   NA   NA    5    3    4    5    4    3   NA    5
+## item189    4    5    3    5    4    5    3    4    3    5    5    4    2    5
+## item190    4    3   NA    5    4    3   NA    4    3   NA    4    4    5    5
+## item191    4    5   NA    5    4    5    5    4    4    4    5    4    5    5
+## item192    4    5   NA    5   NA    5    4    4    4    4    5    4    5    5
+## item193    4   NA   NA    5   NA   NA   NA   NA    4    4    4    4    5    4
+## item194    4    3    3    4   NA    5    4   NA    4    4    3    4    5    3
+## item195    4   NA   NA    4   NA   NA    5   NA    3   NA   NA    3    5    4
+## item196    4    2    4    2    3   NA    5    4    3    1    3    4    1    5
+## item197   NA    2    3    2   NA    2    5    1    3    4    4    3   NA    2
+## item198    4   NA   NA   NA   NA    4   NA   NA    3    5   NA    4    4    5
+## item199    3    2   NA    2   NA   NA    5    1    3    5    4    4   NA    5
+## item200    3   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    5
+## item201   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    3    5    5
+## item202   NA   NA   NA   NA   NA   NA    4   NA    4    4    5   NA    5    5
+##         V431 V432 V433 V434 V435 V436 V437 V438 V439 V440 V441 V442 V443 V444
+## item118    2    5    5    5    4    5    5    5    5    5    5    5    5    5
+## item119    3    4    5    4    4    4   NA    3    3    3    5   NA    3    4
+## item120    4    4    5    3    4    5    5    3    3    4    4   NA    5    4
+## item121    5    5    5    5    4    5    5    5    5    5    5    5    5    4
+## item122   NA    4    1    2    3    5    4   NA   NA    3    3    4    4    2
+## item123    2    5    4    3    3   NA    5   NA   NA   NA    4   NA    5    2
+## item124    1    4    2    2    4    5    3    1    2    5    4   NA    5    3
+## item125   NA   NA    4    4    3    5    3    5    4    5    4   NA    3    1
+## item126    4    4    1    3    4   NA   NA    2    3    5    5    5   NA    4
+## item127    5    4    5    4    4    5    5    4    1    5    5    5    1    5
+## item128    1    5    1   NA   NA   NA   NA   NA   NA   NA   NA   NA    2    3
+## item129   NA   NA    1   NA    3    5   NA   NA   NA    5   NA   NA   NA   NA
+## item130   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item131    5    2   NA    1    4    5    5    5    4    3    5   NA   NA    2
+## item132    5   NA    1   NA    3    5   NA    1   NA   NA   NA    4    1   NA
+## item133   NA   NA    3   NA    3    5    3   NA   NA    1   NA   NA    1   NA
+## item134   NA   NA    3   NA    3    5    3   NA   NA   NA   NA   NA    1   NA
+## item135    3    4    2    3    3    5    5    3    3    5    3    4    4    4
+## item136    1    4    2    2   NA   NA   NA    1    1    1    2    4    4   NA
+## item137    3    3    1   NA   NA   NA    3   NA   NA   NA   NA    5   NA    2
+## item138   NA    5    4   NA   NA    5    5   NA   NA   NA   NA    4   NA   NA
+## item139   NA    2    2   NA    3   NA    3   NA   NA   NA   NA   NA    4   NA
+## item140   NA    5   NA    2    3    5    3   NA   NA   NA    2    4    5    4
+## item141    3    4   NA    2    3    3    3    5    3    5    3   NA   NA    5
+## item142    3    4    4    1    3    3    3   NA   NA    5   NA    5    3    5
+## item143    4    5    1    1    3    2    4   NA    3    5    3    5    3    4
+## item144   NA    1    5   NA    3   NA    3   NA   NA    3   NA    4    3    3
+## item146   NA   NA    1   NA   NA   NA    4   NA   NA   NA   NA   NA    1   NA
+## item147    3    4   NA    3    3    3   NA   NA    4    5   NA    5   NA   NA
+## item148   NA    4   NA   NA   NA    4   NA   NA   NA   NA   NA   NA   NA   NA
+## item149    4    4    2   NA    4   NA    5    4   NA   NA    5    5    5    5
+## item150    5    5    5    4    4    2    5    4   NA    4    5   NA    5    4
+## item151    4    4    5   NA    4    3    4    3    4   NA    5   NA    5    4
+## item152    2    5    4   NA    4    4    5   NA    3   NA    2   NA    5    2
+## item153    5   NA    4    4    4    2   NA    5    4   NA    5   NA   NA    4
+## item154    2    2    4    5    4    4    5    5    5    5    5    5    5    4
+## item155    2   NA    4   NA    4   NA    4    2   NA   NA    3    5    5    2
+## item156    2    4   NA    2    3    4   NA    4    4   NA   NA   NA   NA    5
+## item157    4   NA    4    5    4   NA   NA    5    4   NA    4   NA    5    4
+## item158    5    4    5    3    4    3    5    5   NA   NA    5   NA    5    3
+## item159    5    5    1   NA    3    4    5   NA    5   NA   NA    5    3    3
+## item160    4    4    5    3    4    4   NA    5    4   NA    5   NA    3    4
+## item161   NA   NA   NA   NA   NA   NA   NA   NA    4   NA   NA    3   NA   NA
+## item162    5    5    1    4    4    5   NA    5   NA    5   NA    2    4    3
+## item163    5    3    2    4    4    4    5    5    5    4    5    3    5    3
+## item164    5    4   NA    4    4    5    5    5    4   NA    5    5    4    2
+## item165   NA   NA   NA    4    4   NA   NA   NA   NA   NA   NA    4    4   NA
+## item166   NA   NA   NA    5    4   NA    5   NA   NA   NA   NA    5    4   NA
+## item167    5    1   NA    4    4   NA   NA    5   NA   NA    5   NA    5   NA
+## item168    5    4    4    4    4   NA    5    4   NA   NA    5   NA    5   NA
+## item169    5    1   NA    4    4   NA   NA    4    4   NA    5   NA    5    4
+## item170    4    3    5    3    4    5   NA    5   NA   NA    5    5    5   NA
+## item171    5    5    4    5    4    5    5    5    4   NA    5   NA    5    4
+## item172    5    4    5    4    4    5    5    5    5   NA    5   NA    5    3
+## item173    5   NA    1    4    4    5   NA    5    4   NA    5   NA    5   NA
+## item174    2   NA    5    3    4    4    3    4   NA   NA    3   NA    5   NA
+## item175    5   NA    4   NA    4    5   NA    4   NA   NA    4   NA    4   NA
+## item176    5   NA    1    4    5    5    5    5    5   NA    5   NA    4    5
+## item177   NA   NA   NA   NA    3    5    4   NA   NA   NA   NA   NA    5   NA
+## item178    5    3   NA    4    3    5   NA   NA    4    3   NA   NA    5   NA
+## item179   NA   NA   NA    4    4   NA   NA    3   NA   NA   NA   NA   NA   NA
+## item180   NA    1    1    2    3    5    5   NA    3    5   NA    2    4    1
+## item181    5   NA   NA    4    4    5   NA    5    5   NA    5   NA    5    5
+## item182   NA   NA    1   NA   NA    5   NA   NA   NA   NA   NA   NA   NA   NA
+## item183   NA   NA    4   NA    3    5    5   NA    3   NA   NA   NA    5    1
+## item184   NA   NA   NA    4   NA    5    5   NA   NA   NA   NA   NA   NA   NA
+## item185   NA   NA   NA   NA   NA   NA    5   NA   NA   NA   NA   NA   NA   NA
+## item186    4    3    4   NA   NA   NA    4   NA    5    4   NA   NA   NA   NA
+## item187    4    4   NA    3    3   NA    5   NA   NA    4   NA   NA    4    4
+## item188    4   NA    5    3    5   NA   NA    3    4   NA   NA   NA    5    5
+## item189    4    3    5    5    5    5    4    4    4    5    4    5   NA    5
+## item190    4    5    4    4    5   NA    5    5   NA    5    5   NA    5    5
+## item191    5    5    5    3    5    5    5    4   NA    4    5   NA    5    5
+## item192    5    5    5    4    5    5    5    4   NA   NA    5   NA    5    5
+## item193    5    5    4    3    5    5    4   NA   NA   NA   NA   NA    5   NA
+## item194    5   NA   NA    5    4    5    5    4    4   NA   NA   NA   NA    4
+## item195   NA   NA    5   NA    3    5   NA   NA   NA   NA   NA   NA    5   NA
+## item196    5   NA    5   NA    4    5   NA   NA    4   NA    4   NA    5    4
+## item197    4   NA    5   NA   NA   NA    4   NA    4    5   NA   NA    5    2
+## item198   NA   NA    4    3   NA   NA    4    5   NA   NA   NA   NA    5    3
+## item199   NA   NA    4    2    4    4    4   NA   NA   NA   NA   NA    5   NA
+## item200   NA   NA    5   NA   NA    3   NA    4   NA   NA   NA   NA    5   NA
+## item201   NA   NA    5   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item202    5   NA    2   NA   NA    5   NA   NA   NA    5    5   NA    5   NA
+##         V445 V446 V447 V448 V449 V450 V451 V452 V453 V454 V455 V456 V457 V458
+## item118    5    5    4    5    4    5    5    4    4   NA    4    5    4    4
+## item119    5    5    4    4    4   NA    5    3    3    5    4    4    2    5
+## item120    5    5    5    4    2    4    5    5    4    5    4    3    2    5
+## item121    5    5    5    5    4    5    5    5    5    5    4    5    5    5
+## item122    2    1    5   NA    4   NA    5    5    2    3    3    4   NA    5
+## item123    2    5    5    4    4    1    5   NA    3    3    4    5    2    5
+## item124    2    5    1    5    5    2    5    3    3   NA    4    3    1    5
+## item125   NA    1    2    2   NA    2   NA    3    5    3    3    5    3   NA
+## item126    4    5    2    4    3    4    5    5    4    4    4    5   NA    5
+## item127    4    5    3    5    4    4    5    5    4    3    4    4    5    4
+## item128   NA   NA    5   NA   NA    4   NA   NA   NA   NA   NA    3   NA   NA
+## item129   NA   NA   NA   NA   NA    5   NA   NA   NA   NA   NA    5   NA   NA
+## item130   NA   NA   NA   NA   NA    4   NA   NA   NA   NA   NA   NA   NA   NA
+## item131   NA   NA   NA    3   NA    5    5    3    4    3    3   NA    4    3
+## item132   NA   NA   NA   NA   NA    4    5   NA   NA   NA    3   NA   NA    3
+## item133   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    4   NA   NA
+## item134   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    4   NA   NA
+## item135    4    1    4    1    5    5    5    4    3    3    3    3    4    4
+## item136   NA    1   NA   NA    4    4   NA   NA    1   NA    4    3    1    2
+## item137   NA   NA   NA   NA    4    4   NA   NA   NA   NA   NA    3   NA   NA
+## item138   NA   NA   NA   NA   NA    4   NA   NA   NA   NA   NA   NA   NA   NA
+## item139   NA   NA   NA   NA    3    4   NA   NA   NA   NA   NA    3   NA   NA
+## item140   NA   NA   NA   NA    2    2   NA    5   NA    3   NA    3    4    2
+## item141    4    1    1    2    2    2    3    5    2    2    1    5    4    4
+## item142    4   NA    2   NA    4    4    3   NA    3   NA   NA    5   NA    4
+## item143    3    1   NA    1    4    4    3    3    3    3    3    5    4    4
+## item144    3   NA    5   NA    4    3   NA   NA   NA   NA   NA    5   NA   NA
+## item146   NA   NA   NA   NA   NA    2   NA   NA   NA   NA   NA    3   NA   NA
+## item147   NA   NA   NA   NA   NA    5   NA   NA   NA   NA   NA   NA   NA   NA
+## item148   NA   NA    5   NA   NA    4   NA   NA   NA   NA   NA   NA   NA   NA
+## item149    5    5    4    5    5    5   NA    5    4    3    4    5    4    4
+## item150    4    5    4    5    4    5    5    4    4    4    4   NA   NA    5
+## item151    4    1    3    4    4   NA    5    5    5    5    4    3    4    4
+## item152    4   NA   NA   NA    4    1   NA    4    1    2    4    4    1    4
+## item153    5    3    3    5    3   NA    5    5    3    3    4    3   NA    4
+## item154    4    1    3    5    5    5   NA    5    4    4    4    3    1    4
+## item155    4    1    3    4    5    3   NA    3    3    3    4    4    1    5
+## item156    4    5    4    4    5    2    5    4    3   NA   NA    3   NA    5
+## item157    4    5    4    5    5   NA    5   NA    3    3    5   NA    2    5
+## item158    4    3    4    5    5    4    5   NA    4    5    4   NA   NA    5
+## item159   NA   NA    3   NA    5    5   NA   NA   NA    5   NA    5   NA    5
+## item160    4    3    3    4    4    1    5    5    4    5    4    3   NA    5
+## item161   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    3   NA   NA
+## item162    3    5    3    4   NA    4   NA   NA   NA   NA    4   NA   NA    4
+## item163    4    5    2    4    5    5    5    5    4    5    4    4   NA    4
+## item164    4    5    2    3    5    4    5    5    4   NA    4   NA   NA    4
+## item165    3   NA    3   NA    4    5    5   NA   NA   NA    4    3   NA   NA
+## item166    4    5    4   NA    5    5    5   NA    4   NA    5    3   NA   NA
+## item167    4    5    4    3    5    4   NA    5    5   NA    4   NA   NA   NA
+## item168    4    5    4    5    5    4    5   NA    5   NA    4   NA   NA    5
+## item169    4    3    4    3    3    4   NA    5    5   NA   NA    5   NA    5
+## item170    4    5    4    5    5    3   NA   NA    4   NA    4    5   NA    5
+## item171    5    5    4    5    5    5    5    5    5    5    4    3   NA    5
+## item172    5    5    5    5    5    5    5    4    5    5    4    4   NA    5
+## item173    3    5    3    4    2   NA   NA    5    5   NA    4   NA   NA    5
+## item174    4    5    5   NA    4    2    5   NA    5    5    4   NA   NA    5
+## item175    5    5    3   NA    4    3    5   NA   NA   NA    4   NA   NA    5
+## item176    4    5    4    5    4    5    5    5    5    5    4   NA    5    5
+## item177    3   NA    3   NA    1    5   NA   NA   NA   NA   NA   NA    2    3
+## item178    3    1    3    4    1    2   NA   NA    4    5    3    5   NA    5
+## item179   NA   NA   NA   NA   NA    5    5   NA   NA   NA   NA   NA   NA    5
+## item180   NA   NA   NA   NA    4    5   NA   NA   NA   NA   NA    5    2    4
+## item181    4    5   NA    5   NA   NA    5    5    5    5    4    4   NA    5
+## item182   NA   NA   NA   NA   NA    4   NA   NA   NA   NA   NA    5   NA   NA
+## item183   NA   NA   NA   NA    4    4   NA   NA   NA   NA   NA    4   NA   NA
+## item184   NA   NA   NA   NA   NA    5   NA   NA   NA   NA   NA   NA   NA   NA
+## item185   NA   NA   NA   NA   NA    5   NA   NA   NA   NA   NA   NA   NA   NA
+## item186    4   NA    2   NA    5    2   NA    5   NA    5    3    5   NA    5
+## item187   NA   NA   NA    5    5    4    5   NA    5   NA    4    3   NA    5
+## item188    5    1   NA   NA    4   NA    5    5    5    5   NA   NA   NA    5
+## item189    5    5    2    5    4    4    5    4    4    5    4    3    3    5
+## item190    5    5    5    5    5    5   NA    5    5   NA    4   NA   NA    5
+## item191    5    5    1    5    5    5   NA    5    5    5    4   NA   NA    5
+## item192    4    5   NA    5    5    5   NA    4    5    5    4   NA    5    5
+## item193    4    5    2    4    5    4   NA   NA    5   NA    5    3   NA    5
+## item194    5    5    2    4    5    2    5   NA    5    5    4   NA   NA    5
+## item195    4   NA    5   NA    2   NA    5   NA   NA   NA   NA   NA   NA    5
+## item196    4   NA    5    3    2   NA    5    5    3    5    4   NA   NA    5
+## item197   NA   NA    1   NA    5   NA   NA    5    4   NA   NA   NA    4   NA
+## item198    3    5   NA    3    5    4   NA    4    5   NA   NA   NA   NA    5
+## item199    3   NA    1    5    2    1   NA    5    4   NA   NA    3   NA    5
+## item200    4   NA    1   NA    2   NA    5   NA   NA   NA    4   NA   NA   NA
+## item201   NA   NA   NA    4   NA   NA   NA   NA    5   NA   NA   NA   NA    5
+## item202    4   NA   NA    5    5   NA   NA    3    5   NA    3   NA   NA    5
+##         V459 V460 V461 V462 V463 V464 V465 V466 V467 V468 V469 V470 V471 V472
+## item118    3    4    4    5    4    4    4    5    3    2    5    5    5    2
+## item119    5    3    5   NA    5    2    5   NA    5    2    4    3    5    3
+## item120    4    3    5   NA    5    2    5   NA    5    2    3    3    5   NA
+## item121    4    5    5    5    5    2    5    5    5    2    5    2    5    4
+## item122    3    2    4    1    5   NA    4    5    4    2    1   NA    2    2
+## item123    3    2    4    2    5    2    4    4   NA    2    4    5    4    2
+## item124    4    2    5    2    5    4    5    5    2    2    1    2    4    4
+## item125    1    4    4    3    5   NA    2   NA    3    3   NA   NA   NA    3
+## item126    3    4    5    5    5    2    5   NA    5    2    4    2    4    3
+## item127    4    2    5    5    5    2    3    5    2    3    3    3    4    4
+## item128   NA   NA    2    1    4   NA   NA    1   NA    4   NA   NA    2   NA
+## item129   NA   NA    2   NA    3   NA   NA   NA   NA   NA    4   NA   NA    3
+## item130   NA   NA    4   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item131   NA    4    4   NA    5    5    4   NA    5    3    3    3    4    4
+## item132   NA    1    5   NA   NA   NA    4    1   NA    3   NA   NA   NA   NA
+## item133   NA   NA    3   NA   NA    3    4    2   NA   NA    3   NA   NA    4
+## item134   NA   NA    4   NA   NA   NA   NA    2   NA   NA   NA   NA    4   NA
+## item135    3    4    4    3    3    3    2    5    4    2    4    4    5    4
+## item136    1    1    5   NA    3   NA    1    1    1    3   NA   NA    2    3
+## item137   NA    1    2   NA   NA   NA    3    4   NA    3   NA   NA    2   NA
+## item138   NA   NA    4   NA   NA   NA    2   NA   NA    3   NA   NA    4   NA
+## item139   NA    1   NA   NA   NA    2    3   NA   NA    3   NA   NA    4   NA
+## item140    1   NA    4   NA    5   NA    3    4    5    2   NA   NA    2   NA
+## item141    3    5    5    3    3    3    3    5   NA    3    2    3    4    4
+## item142    3    2    4   NA    3    2    4    5    5    3    2   NA    4   NA
+## item143   NA    5    2   NA    5    2    4    3    5    3   NA    4    5   NA
+## item144    1   NA    4    3    3   NA    4   NA    4    2    2   NA    5   NA
+## item146   NA   NA   NA   NA   NA   NA   NA    1   NA   NA   NA   NA   NA   NA
+## item147   NA   NA    4   NA    5   NA   NA   NA   NA    3   NA   NA    5   NA
+## item148   NA   NA    5   NA   NA   NA   NA   NA   NA   NA   NA   NA    5   NA
+## item149    3    3    3    5    5    3    5   NA    4    2    4    4    5    3
+## item150    4    3    4    4    5    4    5    5    4    4    3    5    5   NA
+## item151    5    4    4    5    5    4    4    5    3    3    4   NA    5    4
+## item152    1    2    1   NA    3    1    4   NA    4    3   NA   NA    2    4
+## item153    5    5    4    5    5    3    5    5    1    3    5    3    5    4
+## item154    3    4    4    5    5    4    4    5    4    3    5    5    5    4
+## item155    4    1    2    3    3    1    4   NA    3    4    4    4    4    2
+## item156    1    5    4    5    5    3    4   NA   NA    4    4    4    2   NA
+## item157   NA    3    5   NA    5    4    2   NA   NA    4   NA    5    4   NA
+## item158    2    2    5   NA    5    4    4    5    4    2    4    4    5    4
+## item159    5    5    4    4    4    2   NA    5    5    2   NA   NA    5   NA
+## item160    1    5    5    5    5    3    3    5    2    3    5    3    5   NA
+## item161   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    3
+## item162    5    5    4   NA    5    3    1    5    5    3   NA    4    4   NA
+## item163    3    5    4    5    5    4    5    5   NA    2    3    5    4    3
+## item164    2    5    4    4    5    3    5   NA   NA    3    3    5    4    2
+## item165    1    5    4   NA    5   NA   NA   NA    5    3    3    2    2   NA
+## item166    4    3    5    5    5    2    4   NA   NA    4    3    3    2    3
+## item167    3   NA    4    4    5   NA    5   NA   NA    3    4    5    2    4
+## item168    3    3    4    5    5    4    5   NA   NA    2   NA    5    5   NA
+## item169    3    5    5    5    5   NA    4    5   NA    3    4    5    5    4
+## item170    4    5    5   NA    5    4    5    5    4    3    3    5    5    2
+## item171    3    5    5    5    5    4    5    4    5    4    4    4    5    3
+## item172    5    5    4    5    5    4    5    5    5    3    4    5    5    4
+## item173    4    5    4    5    5    3    4    5   NA    2    3    5    2   NA
+## item174    3    5    5   NA    5    4    5    5   NA    3    4    3    5   NA
+## item175    4    4    4   NA    5   NA    3    5   NA   NA   NA    5    5   NA
+## item176    5    5    5   NA    5    3    5    5   NA    4    4    5    4   NA
+## item177   NA   NA   NA   NA    5   NA   NA   NA   NA   NA   NA   NA    4   NA
+## item178    2    3   NA    4    5    4    4    5   NA   NA    3    5    4    1
+## item179   NA    5    4   NA    5   NA   NA   NA   NA   NA   NA    5    5   NA
+## item180   NA    5    4   NA    5   NA   NA    5    2    3   NA   NA    5   NA
+## item181    1    5    5    5    5    2    5    5    5    3    4    5    5    3
+## item182   NA   NA    5   NA    3   NA   NA    3   NA   NA    2   NA   NA   NA
+## item183    1   NA    5   NA    3    3    4    5    3    4    2   NA    5   NA
+## item184   NA   NA   NA   NA    5   NA   NA   NA   NA   NA   NA   NA    2   NA
+## item185   NA   NA   NA   NA    5   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item186   NA    4    4   NA    5    4    5   NA   NA   NA   NA    3    5   NA
+## item187    2    3    4    5    5    4    5   NA    3    3    4    5    5   NA
+## item188    3    4    5    5    5    4    5   NA    4   NA    4    5    5    3
+## item189    3    5    4    5    5    3    4   NA    4    3    4    3    5    2
+## item190    3    5    5   NA    5    2    5   NA    4    3   NA    5    5   NA
+## item191    4    4    5    5    5    4    5   NA    5    3   NA    5    5    4
+## item192    2    4    5    5    5    5    5   NA    5    4    3    5    5    2
+## item193    3    3    4   NA    5    3    5   NA   NA    2   NA    4    5   NA
+## item194    4    5    5    5    5    3    5   NA   NA    4    4    5    5   NA
+## item195    3    5    4    5    5    4    5    5   NA    3    4   NA    2   NA
+## item196    3    5    4    5    5    2    4    5   NA    3    2   NA    4   NA
+## item197    4    3   NA    4    5    4    3    5    5    3    5   NA    5   NA
+## item198    4    3    4   NA    5   NA    5   NA    2   NA   NA    4    4   NA
+## item199    3    2    5   NA    3    2    4    3    3    3    4    4    4   NA
+## item200   NA    2    4   NA    5   NA    5    4    3    4    5   NA    2    4
+## item201   NA   NA   NA   NA    5   NA   NA   NA    5   NA   NA   NA    5   NA
+## item202    3    3    5   NA    5    4    5   NA   NA    3   NA    5    5   NA
+##         V473 V474 V475 V476 V477 V478 V479 V480 V481 V482 V483 V484 V485 V486
+## item118    5    5    4    2    3    5    4    4    4    4    4    5    5    4
+## item119    5    4    4    2    4   NA    4    4    2   NA    5    5    4    5
+## item120    5    5    4    3    4    2    4    4    3    2    5    4    3    4
+## item121    5    5    4    2    4    4    3    5    4    4    5    5    3    5
+## item122    4    3    3   NA    5    2    4    3    1    2    4   NA    1    4
+## item123    5    4    3    3    3   NA    4    4   NA    3    4    5    3    4
+## item124    3    4    2    4    2    5    4    3    3    4    4    2    3    4
+## item125    1    4    1    4    4    4    1   NA   NA    3    3    4   NA    4
+## item126    5    3    4    4    5    4   NA    4    4    2    5    4    3    4
+## item127    5    4    2    2    3    2    4    3    3    2    5    3    3    3
+## item128    1   NA   NA    3   NA   NA    4    3   NA   NA    2   NA   NA   NA
+## item129   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    3   NA    2   NA
+## item130   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item131    5    5    3   NA    4   NA    3    3    3    2    5    3   NA    4
+## item132   NA    1   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item133   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    2   NA   NA   NA
+## item134   NA   NA   NA   NA   NA   NA   NA    3   NA   NA   NA   NA   NA   NA
+## item135    5    5    4    3    2    3    4    4    4    2    4    5    2    4
+## item136   NA    2   NA   NA   NA   NA   NA    2   NA    2   NA   NA    1   NA
+## item137    3   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    3   NA   NA
+## item138   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    5   NA   NA   NA
+## item139   NA    1   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item140   NA   NA   NA   NA   NA   NA   NA   NA    2   NA    4   NA   NA   NA
+## item141    3    4    3    3    3    3    3    3    3    2    5    3    2    4
+## item142    3    3    3   NA   NA   NA    3   NA   NA   NA    1    3    3   NA
+## item143    3    4   NA   NA    4   NA    3   NA    3    3    3    3   NA    3
+## item144   NA    2   NA   NA   NA   NA    4   NA   NA   NA    2    3   NA   NA
+## item146   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item147   NA    3   NA   NA   NA   NA    4   NA   NA   NA   NA   NA   NA   NA
+## item148   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item149    5    4    4    4    4    5    4    4    4    5    5    5    4    4
+## item150    5    4    4    2    4    4    4    4    4    4    5    5    4    3
+## item151    3    1    4    1    3    4    4    4    4    2    4    5    3    4
+## item152    3   NA    3   NA    3    1    4    2    3    1    4    4    1    3
+## item153    4    4    4    4    5    4   NA    3    3    2    5    4    3    3
+## item154    5    4    4    4    5    4    4    3    4    4    5    5    3    3
+## item155    3    1    4    5    3    2    4    4    4    3    4    4    2    3
+## item156    3    3    4   NA   NA    3    4    3    3   NA    4    4    2    4
+## item157   NA   NA    2    4   NA   NA    5    3   NA    5    5   NA    5   NA
+## item158    5    4    4    5   NA    4    4    4    3    3    5    5    4    4
+## item159    5    4    4   NA   NA   NA    4   NA   NA   NA    5    2    3   NA
+## item160    4    3    3    3    5    4   NA    4    3    3    5    4    3    4
+## item161   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item162    4    4    4    3   NA   NA    4   NA    3    2    5    5    3   NA
+## item163    5    5    4    3    4    4    4    4    4    3    5    4    5    4
+## item164    5    4    4    3    5    3   NA    4    4    4    5   NA    5    4
+## item165    3    4    4   NA    5   NA    2   NA   NA    4    5    5    4   NA
+## item166    5    4    4   NA    4   NA    1   NA   NA    4    5   NA    4   NA
+## item167    5    4    4    5    4   NA   NA    4    4    3    5    5    5    3
+## item168    5    3    5    4   NA    5    5   NA    3    4    5    5    5    4
+## item169    5    4    4    3    5    5    4    4   NA    4    5    4    3    5
+## item170    5    4    4    4    5   NA    4    4    3    5    5   NA    5   NA
+## item171    5    4    5    5    5    4    5    4    4    4    5    5    5    5
+## item172    5    4    5    3    5    4    5    5    4    4    5    5    5    5
+## item173    3    2    4    5    2    2    3    5    4    5    5    5    3    1
+## item174    5    4    5    2   NA    2   NA    4   NA   NA    5    3    3    1
+## item175    4    5    4    5   NA   NA   NA   NA    4    5    5    5    5   NA
+## item176    5    4    5    4    5    5    4    4    4    4    5    5    5    1
+## item177    2    1   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item178    5    4    4    1    4    2   NA    4    2    3    4    3   NA    1
+## item179   NA    4   NA    1   NA   NA   NA    3   NA    3    4    5    4   NA
+## item180    4    3    3   NA    5   NA   NA   NA   NA   NA    3    3    3   NA
+## item181    5    5    3    2    5    4   NA    3    3    4    5    5    3    1
+## item182   NA   NA   NA   NA   NA   NA   NA    4   NA   NA   NA   NA   NA   NA
+## item183   NA    3   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    3   NA
+## item184   NA   NA   NA   NA   NA   NA   NA   NA   NA    3   NA    5   NA   NA
+## item185   NA    4   NA   NA   NA   NA   NA   NA   NA    3   NA   NA   NA   NA
+## item186   NA   NA   NA   NA    2   NA   NA   NA   NA    3   NA    4    4    1
+## item187    5    4   NA    2   NA    4    4   NA    3    4    5   NA    5   NA
+## item188    4    4    5   NA    5    4   NA    4    4    3    5    5    5    1
+## item189    5    4    5    4    4    4   NA    4    4    4    5    4    4    5
+## item190    5    5    5    3   NA    5    4    5    3    4    5    4    5    5
+## item191    5    5    5    4    4    5    4    4   NA    5    5    5    5    5
+## item192    5    4    5    5    4    5   NA    4    3    5    5    5    5    1
+## item193    5    4    5    2   NA    5    4    4    4    3    4    4    3   NA
+## item194    5    5    4    5   NA    4    4    4    4    3    5    4    5    1
+## item195    5   NA    5    5   NA    4   NA    4   NA   NA    5    5    3    1
+## item196    5    4    4   NA   NA    3   NA    4    2   NA    5    4    2    5
+## item197    5   NA    4   NA   NA   NA   NA    4    3   NA    3   NA   NA   NA
+## item198    5   NA    5   NA   NA   NA   NA   NA    4    2    5    5    4    1
+## item199    5   NA    5    3    5   NA    4   NA   NA    3    5    5    4    5
+## item200    5   NA    4   NA   NA   NA   NA   NA   NA   NA   NA   NA    3   NA
+## item201    5   NA   NA   NA   NA   NA   NA    4   NA   NA    4   NA    4   NA
+## item202    5   NA   NA    3   NA   NA   NA   NA   NA   NA    5   NA    4   NA
+##         V487 V488 V489 V490 V491 V492 V493 V494 V495 V496 V497 V498 V499 V500
+## item118    1    5    4    5    3    5    4    4    4    4   NA    5    4    4
+## item119    1    5    4    1    4   NA    4   NA   NA    4   NA    4    3    4
+## item120    4    4    3    3    4    5    4    5    3    4    5    4    4    4
+## item121    5    4    4    2    5    5    5    5    5    4    5    5    2    5
+## item122    2    4    5    2    4   NA    5    4    4    3    3    4   NA   NA
+## item123    4    2    4   NA    5   NA    2   NA    5    4   NA    4    2    4
+## item124    2    2    4    4    4    5    3    4    2    4   NA    2    4    5
+## item125   NA   NA    5    5    3   NA    4    2   NA    1    5    3   NA   NA
+## item126    4   NA    4    3    2    4    4    5    3    2    5    2    4    5
+## item127    4    2    3    2    4    4    2    5    2    4    5    4    1    5
+## item128   NA    1   NA   NA   NA   NA   NA   NA   NA   NA   NA    2   NA   NA
+## item129   NA   NA   NA   NA    4   NA    2   NA   NA   NA   NA   NA   NA   NA
+## item130   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item131   NA    3    4   NA   NA   NA    5   NA    2   NA   NA    3   NA   NA
+## item132   NA   NA   NA    2    4   NA    4    1    2   NA    3   NA   NA   NA
+## item133   NA    3   NA   NA    5   NA    2   NA   NA   NA   NA   NA   NA    3
+## item134   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    3
+## item135    2    4    4    3    4    1    3    1    5    1    4    1    1    5
+## item136    1   NA    5   NA    5   NA    2   NA    3   NA   NA   NA   NA   NA
+## item137   NA    2    4   NA    3   NA   NA   NA   NA   NA   NA    1   NA   NA
+## item138   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item139   NA   NA   NA   NA   NA   NA   NA   NA    2   NA   NA    1   NA   NA
+## item140    1    2    5    3    4    1    4   NA    4    3   NA   NA    1   NA
+## item141    3   NA    5    4    4    1    4    1    1    5    5   NA    1    3
+## item142    3    2    4    3    3   NA    3   NA    3    3   NA    1    1    3
+## item143    3    4    4    4    4    4    5    4    4    5   NA    3    4    4
+## item144    2    4    3    3    3   NA   NA   NA    2   NA   NA    2   NA   NA
+## item146    1    1    3   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item147   NA   NA   NA   NA   NA   NA   NA   NA    5   NA   NA    1   NA   NA
+## item148   NA   NA   NA   NA   NA   NA   NA   NA    5   NA   NA   NA   NA   NA
+## item149    4    4    4   NA    4    1    5    5    5    3   NA   NA    4    5
+## item150    4    4    3   NA    3    4    5    1    4    4   NA    4    4    5
+## item151    4    5    5    4    5    4    4    5   NA    4   NA   NA    3    4
+## item152    1    5    5   NA    4   NA   NA    4    5   NA   NA   NA    1   NA
+## item153    5   NA    4    4    2    5    5    4    3    5    5    3    5    3
+## item154    4    5    4    4    4    5    3    1    4    3    4    4    3    4
+## item155    2    5    5   NA    4    3    4    4    4    4   NA   NA    4    5
+## item156    4    3    2   NA    4   NA    3    4    3   NA   NA   NA    2    4
+## item157   NA   NA    4   NA   NA   NA    2   NA    4    3   NA   NA   NA    5
+## item158    1    4    4    3    5    2    4   NA    4    4   NA    4    4    4
+## item159    3    4    4   NA    3   NA   NA   NA    5    1   NA    3   NA   NA
+## item160    4    3    5    3    4    2    2    3    3    5   NA   NA    4    3
+## item161   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    4   NA    3   NA
+## item162    4    4    3   NA    3    1    4   NA   NA    4   NA    3    2   NA
+## item163    5    4    3   NA    4    4    4    4    4    4    5    4    4    4
+## item164    4    4    3    4    4    4    4    5    4    4    5    3    4    5
+## item165    5   NA    3   NA   NA   NA   NA   NA   NA   NA   NA    2   NA   NA
+## item166    2   NA    3   NA   NA   NA   NA    5    4   NA   NA    4   NA   NA
+## item167    4   NA    4    4   NA    4    5    5   NA   NA   NA    4   NA   NA
+## item168    5   NA    4    4   NA    4    2   NA   NA    3   NA    4    5    5
+## item169    4    4    4    4    5    4    5    5    4    3   NA   NA   NA   NA
+## item170    3    5    4   NA    3   NA    2   NA   NA    3   NA    5   NA   NA
+## item171    5    4    4    4    3    4    5    5    5    4   NA    4    5    5
+## item172    5    5    4    4    4    4    5    5    4    4   NA    5    4    5
+## item173    2   NA    5    4   NA    4    2    5    4    2    5   NA    4    4
+## item174    2   NA   NA   NA   NA   NA    3   NA   NA    4   NA    3   NA    5
+## item175   NA   NA   NA    5   NA    5   NA   NA   NA   NA   NA    4    4    5
+## item176    5    5    4    4    3    5    5    3    5    4    5    5    3    5
+## item177   NA    4   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item178    4   NA    4    4    4   NA    5    5    4   NA    5   NA   NA    5
+## item179    4   NA   NA   NA   NA    4   NA   NA   NA   NA   NA   NA   NA   NA
+## item180    3    4    5   NA    4   NA    2   NA   NA   NA   NA    3   NA   NA
+## item181    5    4    4    4   NA    5    5   NA   NA    5    5   NA   NA    5
+## item182   NA   NA   NA   NA    5   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item183    1    4    4   NA    5   NA   NA   NA    3   NA   NA    3   NA   NA
+## item184   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item185   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item186   NA    5    4   NA    4   NA    2   NA    5    1   NA   NA   NA   NA
+## item187   NA    5    3    4   NA   NA    4   NA    3    4   NA   NA    4    5
+## item188    4   NA    4    4   NA    5    4    5   NA    4   NA    4    3    5
+## item189    4   NA    4    4    4    4    2    5    3    4    5    5    3    4
+## item190    4    5    4    4   NA   NA    5    3   NA    4   NA    4    4    4
+## item191    4   NA    4   NA    5   NA    5   NA    5    4    4    5    5    5
+## item192    5    5    4    3    4    5    5   NA    5    5    4    4    2    5
+## item193   NA    4    3   NA   NA   NA    3   NA   NA   NA   NA    5    4    5
+## item194    4    5    2   NA   NA   NA    4   NA   NA    4   NA   NA    3    5
+## item195    5    4   NA   NA   NA   NA    2   NA   NA    4   NA   NA    4   NA
+## item196    5   NA    5    3   NA    2    5    4    3   NA    5   NA    3    5
+## item197    2    5    4    3    4   NA    2    4    5    4   NA    3    3    5
+## item198    4   NA   NA    4   NA   NA   NA   NA   NA   NA   NA   NA    4   NA
+## item199    2    5    5   NA    4   NA    2    5    5   NA   NA   NA    4   NA
+## item200    4   NA   NA   NA   NA   NA    4   NA   NA   NA   NA    5   NA   NA
+## item201   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item202   NA   NA   NA   NA   NA   NA    4   NA   NA   NA   NA   NA   NA    5
+##         V501 V502 V503 V504 V505 V506 V507 V508 V509 V510 V511 V512 V513 V514
+## item118    4    5    4    3    4    4    5    3    5    2    4    5    4    5
+## item119   NA   NA    3    3    5    4    4   NA    4   NA    4    4    4    4
+## item120   NA    4    4    4    5    3    4    2    4    4    4    5    5    5
+## item121    5    4    4    5    5    2    5    2    5    4    4    5    5    5
+## item122    5    1    3    5    4    1    2    2    3    1    3    3    5    1
+## item123   NA    2    4    5    4   NA    2   NA    4   NA    3    4   NA    4
+## item124    4    1    3    3    4    3    4    3    3    2    2    2    1    1
+## item125    5    1    4    4    5    1    5    2    3    1    3   NA    5    2
+## item126    4    4    4    5    4   NA    4    2    4    2    3    4    5    3
+## item127    4    4    5    4    5    3    4    3    4    3    2    4    5    4
+## item128   NA   NA    3   NA   NA   NA   NA   NA   NA   NA   NA    2    2    3
+## item129   NA   NA    3   NA   NA   NA   NA   NA   NA   NA    3    2   NA    3
+## item130   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item131    4   NA    4    5    2    4    5    5    3    1    3    3   NA    4
+## item132   NA   NA    4    2   NA   NA   NA   NA   NA   NA   NA    3   NA    4
+## item133   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    3    3   NA    5
+## item134   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    3   NA   NA   NA
+## item135    1    4    4    4    2    1    4    2    4    2    4    3    4    4
+## item136    1    1    4   NA   NA   NA   NA   NA   NA   NA    3    2   NA   NA
+## item137   NA   NA    4    4   NA   NA   NA   NA   NA   NA    3   NA    2   NA
+## item138   NA   NA    3   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item139   NA   NA    4   NA   NA   NA   NA   NA   NA   NA    3   NA    2   NA
+## item140   NA   NA    4    4    2   NA   NA   NA    2    1    3   NA    4    1
+## item141    1    3    5    5    1   NA    2    5    3    1    3    2   NA    3
+## item142   NA   NA    4    5    1   NA   NA   NA   NA    1    3    2    4    3
+## item143    1   NA    3    3   NA   NA    2    4    3   NA    3   NA    5    5
+## item144   NA   NA    4    3   NA   NA   NA   NA   NA   NA    3   NA   NA   NA
+## item146   NA   NA    5   NA   NA   NA   NA   NA   NA   NA    4    4   NA   NA
+## item147   NA   NA    3    5   NA   NA   NA   NA   NA   NA   NA    5    5    5
+## item148   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    5    4
+## item149    1    5    3    5    4    2    4    2    5    4   NA    4    4    5
+## item150   NA    5    4    3    4    5    4    1    4    4   NA    4    5    5
+## item151    1    5    5    5    5    5    4    3    5    5    4    4    4    5
+## item152    1    4    3    3    3    3    2   NA    2    1    4    4   NA    1
+## item153    4    1    5    5    5    5    5    4    5    4   NA    5    5    3
+## item154    4    5    3    4    4    4   NA    1    5    4   NA    5    5    5
+## item155    1    4    3    3    4    4    2    2    5    2   NA    4    5    2
+## item156    1   NA    3   NA    5    3   NA    4    4   NA   NA    5   NA    2
+## item157   NA   NA    3    3    4   NA   NA   NA    3   NA   NA    5   NA    5
+## item158    4    4    4    3    4    4    4    3    3   NA   NA    5    5    5
+## item159    1    5    2    5    4    5   NA    1    3    4   NA    4    5    5
+## item160    4    2    5    4    5    5    5    4    5   NA    3    5    4    4
+## item161    4   NA   NA   NA   NA   NA   NA   NA   NA   NA    4   NA   NA   NA
+## item162   NA   NA    5    1    4    5    5   NA    3   NA    4    5    5    5
+## item163   NA    4    4    4    5    5    4    3    4   NA    4    5    5    5
+## item164   NA    4    4   NA    5    5    4   NA    3   NA    4    5   NA    5
+## item165   NA   NA    3    4   NA   NA    4   NA    3   NA   NA    3   NA    4
+## item166   NA   NA    4    4    5    4    4   NA    4   NA   NA    5   NA    4
+## item167   NA   NA    3   NA    5    2    5    4    4    4   NA    5   NA    3
+## item168   NA   NA    3    3    4    5    2   NA    4   NA   NA    5   NA    5
+## item169   NA   NA    4    5    4    5    5    3    3   NA    4    5   NA    4
+## item170   NA   NA    3    5    5    5   NA   NA    3   NA    4    5    5    4
+## item171   NA   NA    4    5    5    5    5   NA    5   NA    4    5   NA    5
+## item172    5    5    3    5    4    5    2   NA    5    4    4    5    5    5
+## item173    4   NA    4   NA    5    1    5    4    5    3   NA    4   NA    4
+## item174   NA    4    2   NA    4    2   NA    3    3   NA   NA   NA    4    3
+## item175   NA    4    2   NA    4    4    5   NA    4   NA   NA   NA   NA    4
+## item176   NA    5    4    5    4    3    5   NA    5    5   NA    4    5    5
+## item177   NA   NA    2   NA   NA    3   NA   NA   NA   NA   NA   NA    5    2
+## item178    4   NA    4    5   NA    4    5    4    4    4   NA    4   NA    5
+## item179   NA   NA    4   NA    5   NA    2   NA    3   NA   NA   NA   NA    4
+## item180   NA   NA    4   NA   NA   NA    4   NA    3   NA   NA   NA    5    4
+## item181    5   NA    5    5    5   NA    5    5    4    5   NA    5    4    3
+## item182   NA   NA    3   NA   NA   NA   NA   NA    3   NA    3   NA   NA   NA
+## item183   NA   NA    4   NA   NA   NA   NA   NA    3   NA   NA   NA    5   NA
+## item184   NA   NA    2    4   NA   NA    2   NA   NA   NA   NA   NA   NA    2
+## item185   NA   NA    2    4   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item186    1   NA    2    4   NA    4   NA   NA   NA   NA   NA   NA    5   NA
+## item187   NA   NA    3    4    4    4    4   NA    3   NA   NA    4    5    4
+## item188   NA   NA    5    3    4    4    4    3    3   NA    4    5    4    5
+## item189   NA    4    5    5    5    4    4    3    4    5   NA    5    5    5
+## item190   NA    5    2    5    4    5   NA    2    5   NA   NA    5    5    5
+## item191   NA    5    2    5    5    5    4    5    5   NA   NA    5    5    5
+## item192   NA    5    3    5    5    4    4    5    5    5   NA    5    5    4
+## item193   NA    5    3    5    4    4    5    2   NA   NA   NA    5    5    4
+## item194   NA   NA    3    5    5   NA    4    2    4   NA   NA    4    4    4
+## item195    4   NA    2   NA    4    3   NA   NA   NA   NA    4    5    5    4
+## item196    4   NA    3    5    5   NA   NA    4    4    4   NA    4   NA    2
+## item197   NA    4    5    3    2   NA   NA    3   NA    4    4   NA    4   NA
+## item198   NA   NA    3    3    5   NA    4   NA    3   NA   NA    5    5    3
+## item199   NA    5    3    2    4   NA    2   NA    3   NA   NA    5    4   NA
+## item200   NA   NA    3   NA   NA    3   NA   NA   NA   NA    4   NA   NA   NA
+## item201   NA   NA   NA   NA    4    3   NA   NA   NA   NA   NA    5   NA   NA
+## item202   NA   NA    2   NA    4    4   NA   NA   NA   NA   NA   NA   NA    2
+##         V515 V516 V517 V518 V519 V520 V521 V522 V523 V524 V525 V526 V527 V528
+## item118    4    5    5    4    2    4    5    4    5    3    5    4    3    4
+## item119    4    5    3    3    4    4    4   NA   NA    3    5    5    3    4
+## item120    4    5    3    1    5    5    4    4    1    3    5    5    3    4
+## item121    4    5    5    1    5    5    5    2    5    5    5    5    5    5
+## item122    2    5    5   NA    5    2    1    2    3    4    2    2    3    3
+## item123    4    2    5    5    5    4    5   NA    4    4   NA    2    3    3
+## item124    2    1    1    1    1    2    5   NA    4    5    1    4    3    2
+## item125   NA    1    1    1    1    2    1    1   NA    3    1    1    3    2
+## item126    3    2    3    4    5    3    5    4   NA   NA    1    3    5    4
+## item127    4    1    5    4    5    4    5    4    4    2    1    2    5    4
+## item128   NA    2    1   NA    5   NA   NA    1   NA   NA   NA    1    3   NA
+## item129    1   NA   NA   NA    3   NA   NA   NA    3   NA    1    3   NA   NA
+## item130   NA   NA   NA   NA    5   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item131    1    5    5   NA   NA    3    3   NA    3    3   NA    5    3    4
+## item132   NA    1   NA   NA    5   NA   NA    1   NA   NA   NA    1   NA    3
+## item133   NA    1   NA   NA   NA    3   NA    1    3    3    1    2   NA    3
+## item134   NA    3    1   NA    2   NA   NA    1   NA    3    1   NA   NA   NA
+## item135    3    4    1    4    2    4    5    1    4    4    1    4    4    3
+## item136   NA    1    2    1    4    1    1    1   NA   NA   NA    1   NA    1
+## item137   NA    1    1   NA   NA    1    1   NA   NA    1    1   NA   NA   NA
+## item138   NA    3    1   NA    4    2   NA   NA   NA    1   NA   NA   NA   NA
+## item139   NA    5   NA   NA    5   NA   NA   NA   NA   NA    1   NA   NA   NA
+## item140   NA    5    3   NA    2    2    1    4   NA    4    1   NA    3    3
+## item141    3    4    2    4    1    1    1    5    3    3    1    5    3    2
+## item142    3    1    2    4    5    1    1   NA    3    3    1    3   NA    3
+## item143   NA    5    4    5    1    2    1    5    1    4    4    4    3    2
+## item144    3    2    1    4    2    1    1   NA    1    3    1    3    3   NA
+## item146   NA    1   NA   NA    4   NA   NA    1   NA   NA    1   NA   NA   NA
+## item147   NA    5   NA   NA    2   NA    1   NA   NA   NA   NA    5    5   NA
+## item148   NA   NA   NA   NA    5   NA    1   NA   NA   NA   NA   NA   NA   NA
+## item149    5    5    5   NA    5    3    5    4   NA   NA   NA    5    5    5
+## item150    4    5    5    5    2    4    5   NA    4   NA   NA    5    5    5
+## item151    4    5    5   NA    5    5    5    5    5    3    5    4    5    4
+## item152    2    1    1   NA    5    4    5    5    4    1   NA    1    4    4
+## item153    4    4    5    4   NA    3    3    5    3    3    5    4    5    5
+## item154    4    2    5    5    3    3    5    4    5    4   NA    5    4    5
+## item155    4    4    1   NA    3    4    5    3   NA   NA   NA    2    5    5
+## item156    4    4    2    4    1    3    3    5   NA    3   NA    3    3    3
+## item157    4    5    4    5    1    5   NA   NA   NA   NA    5   NA    3    5
+## item158    4    5    5    3    5    5    5    4   NA   NA   NA    4    3    4
+## item159   NA    4    4   NA    5    4    5   NA   NA   NA    5    4    5    4
+## item160    4    3    3    4    2    3    3    5    5   NA    5    5    3    4
+## item161   NA   NA   NA   NA   NA   NA   NA    5   NA   NA    5   NA   NA   NA
+## item162   NA    5    5    1    5    5   NA    3    1    3    5    4   NA    4
+## item163    4    5    5    5    5    5    4    5    4    4   NA    4   NA    4
+## item164    3    5    5    3    5    4    4    1    4    4    5    5    5    4
+## item165   NA    2    5   NA    2    4    4   NA   NA   NA   NA    4    5    3
+## item166   NA    5    5    4    2    4    5   NA   NA   NA    5   NA    5    3
+## item167   NA    5    5    5    2    4    3   NA   NA   NA   NA   NA    5    5
+## item168   NA    5    5    5    2    4    5   NA   NA    5   NA    5    5    5
+## item169    4    5    5   NA    1    3    4   NA    4   NA   NA    4    5    4
+## item170    4    5    5    4    5    5    5   NA   NA    3    5    4    5    4
+## item171    4    5    5    5    5    4    5   NA   NA    4   NA    5    5    5
+## item172    4    5    5    5    5    4    5    4   NA    4    5    5    5    5
+## item173    3    4   NA    5   NA    4   NA   NA   NA   NA   NA    4    5    4
+## item174    3    4    5    2    2    4    5   NA   NA   NA   NA    4    3    3
+## item175    4    5   NA    5    3    4   NA   NA   NA   NA   NA    5    4    5
+## item176    4    5    5    5    1    5    5   NA    4    3   NA    4    5    5
+## item177   NA   NA   NA   NA    5   NA   NA   NA   NA   NA   NA   NA   NA    3
+## item178    4    5    4   NA    5    4    4    4    3   NA   NA    3    3    3
+## item179   NA    5   NA    4   NA   NA   NA    1   NA   NA   NA   NA    5    4
+## item180   NA    4   NA    5   NA    3   NA    5   NA    4   NA    4   NA    2
+## item181    3    5    5    5    3    5    4    5   NA   NA    5    4    5    5
+## item182   NA   NA   NA   NA    4   NA   NA   NA   NA   NA    5   NA   NA   NA
+## item183   NA    2    2   NA    5   NA   NA   NA   NA    2    2   NA   NA    2
+## item184   NA    1   NA    3    5   NA    4   NA   NA   NA   NA   NA   NA   NA
+## item185   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    5   NA
+## item186    3   NA    3   NA    2    2    5    1   NA   NA   NA    4   NA   NA
+## item187    3    5    5   NA    2    5    5    2   NA    4   NA    5    5    4
+## item188    4    5    5    5    2    5    5    4    5   NA    5    4    5    5
+## item189    4    5    5    5    2    5    5    5   NA    3   NA    5    5    5
+## item190    4    5    4    5    2    5    5    3   NA   NA   NA    5    5    5
+## item191    4    5    4   NA    2    5    5    5   NA    4   NA    5    5    5
+## item192    4    5    5    5    3    5    5    5    5    4   NA    5    5    4
+## item193    4    5    5   NA    2    5    5   NA   NA   NA   NA    4    5    5
+## item194    3    5    2    4    2    4    4    4   NA   NA   NA    4    3    3
+## item195    3    4   NA   NA    4    4   NA   NA   NA   NA   NA   NA    5    5
+## item196    4    5    2    1    2    5    3    5   NA   NA   NA    2    5    3
+## item197    3    5    4   NA    2    3    5    4    5    4    5    4   NA    3
+## item198   NA    5   NA    5    2    4    5    1   NA   NA   NA    5    5    3
+## item199    2    4    1   NA    3    5    5    4   NA   NA    5    1    5    5
+## item200    4    4    2   NA    2    4   NA   NA    5   NA    4   NA   NA    4
+## item201    3    5    5   NA    2    3   NA   NA   NA   NA   NA    3    5    5
+## item202   NA    5    5    1    4    4    5    1   NA    5   NA    5    5    4
+##         V529 V530 V531 V532 V533 V534 V535 V536 V537 V538 V539 V540 V541 V542
+## item118    5    5    4    4    5    4    4   NA   NA    3    2    5    1    5
+## item119    5    5    4    2    5   NA    3   NA   NA    4    4    5   NA    5
+## item120    5    5    3    3    5   NA    3   NA    4    4    3    5   NA    5
+## item121    4    5    5    5    5    2    5    2    5    5    3    4    1    5
+## item122    2    5    1    3    5    3   NA   NA    1    1    3    4    3    1
+## item123    5    5    2   NA    5    2   NA   NA    4    4    3    3    3    1
+## item124    4    5    1    3    3    4    2   NA    1    3    3    3    4    1
+## item125    2    5   NA    2   NA    2   NA   NA    1    4    3    3    3    1
+## item126    2    5    1   NA    4    2    4   NA    2    4    4    3   NA    5
+## item127    5    5    4    4    4    4    3    4    4    4    3    2    4    5
+## item128    2   NA   NA    2   NA    2   NA   NA   NA   NA    4   NA    1    1
+## item129   NA    3   NA   NA   NA   NA   NA   NA   NA   NA   NA    3   NA   NA
+## item130   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    4   NA   NA
+## item131    1    4    4   NA    3    2    3    3    1    3    3   NA    4    1
+## item132    1   NA   NA    4   NA   NA   NA   NA   NA   NA   NA   NA   NA    1
+## item133    1    4   NA   NA   NA   NA   NA   NA   NA   NA    3    4   NA   NA
+## item134    1    4   NA   NA   NA   NA   NA   NA   NA    4   NA    4   NA   NA
+## item135    4    4    2    2    2    2    3    4    1    1    3    4    2    5
+## item136   NA    2    1    1    2   NA    1    2   NA   NA    4    3    2    1
+## item137   NA    2   NA    1   NA   NA   NA   NA   NA    1   NA    2    1    1
+## item138   NA    4   NA   NA   NA   NA   NA   NA   NA    2   NA    3   NA   NA
+## item139   NA   NA   NA    1    2   NA   NA   NA   NA   NA   NA    2    1    1
+## item140    3    4   NA    4    2   NA   NA    1    1    4    3    2    1    1
+## item141    5    5    4    2    2    3    3    2    1    2    2    2    3    1
+## item142    5    5    4    2    2    2    3    2   NA    4    2    4    3    1
+## item143    5    3    4    3   NA    3   NA    4    3    4   NA    4    3    1
+## item144    2    3   NA    1   NA    3   NA    1   NA    4   NA    4    4    1
+## item146   NA    4   NA    2   NA   NA   NA   NA   NA   NA   NA    4   NA   NA
+## item147   NA   NA   NA    4   NA   NA   NA   NA   NA    4   NA    4    4   NA
+## item148   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    3   NA   NA
+## item149    5   NA    4    4    3    3    5    4   NA    5    3    4    2    1
+## item150    3    5    4   NA    5    4    5   NA   NA    5    4    4    4    5
+## item151    3    5   NA    2    5   NA   NA    3    5    4    2    3    3    5
+## item152    1    3   NA    5    5   NA    4    4   NA    4    2   NA    1   NA
+## item153    5    5    3   NA    5    1    5    4    3    5    3   NA   NA    5
+## item154    1    5    4    5    5    4    5    4    4    5    2    3    1    5
+## item155    1   NA    3    5    5    2    4    4   NA    4    4    3    1    5
+## item156    1    5    1   NA    5    2    3    3    2    5    3   NA   NA    5
+## item157    2    5    4   NA   NA    1    5   NA   NA    5    5   NA   NA    5
+## item158    5    5    3    2    5    4   NA   NA   NA    4    3    5    4    5
+## item159    5    5   NA    4    5    3    5    4   NA    5    4    4    4   NA
+## item160    5    5    3    1    3    2    3    3   NA    2    3   NA   NA    5
+## item161   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item162    3    5    4   NA   NA   NA   NA   NA    4    4    3    5   NA    5
+## item163    5    5   NA   NA    5    2    5   NA    5    5    4    5    4    5
+## item164    5    5    4   NA    3    3    5   NA    5    4    4    5   NA    5
+## item165    2    5   NA    1   NA   NA   NA   NA   NA    5    3    5   NA    3
+## item166    4    4    4    4   NA   NA   NA   NA   NA    4    3    5   NA    5
+## item167    4    5    4    4   NA   NA    5   NA    4    4    3   NA   NA    5
+## item168    5    5    5    4   NA    4    5   NA   NA    3    4    5   NA    5
+## item169    5    5    3   NA    5    3    5   NA    5    5    3    3   NA    5
+## item170    5    5   NA   NA    5    2   NA   NA    2    4    3    4    4    5
+## item171    5    5    5   NA    5    4    5   NA    4    4    3    5    3    5
+## item172    5    5    4    5    5    3    5   NA   NA    5    3    5    4    5
+## item173    4    5    5   NA    5    3   NA    3    4    4    4    4   NA    5
+## item174    5    5    4   NA    5    3    5    4    1    2    4   NA   NA    5
+## item175   NA    5    5   NA   NA    5   NA   NA   NA    1    3   NA   NA    5
+## item176    5    5    4    5    5    3    4   NA    5    5    5    5   NA    5
+## item177    4    5   NA   NA   NA    4   NA   NA   NA   NA    3    4    1   NA
+## item178    5    5   NA   NA    5    2   NA    4    2    5    4   NA   NA    5
+## item179    5    5    4    1   NA    3   NA   NA   NA   NA    5   NA   NA   NA
+## item180    4    5   NA    2   NA   NA   NA    3   NA    3    4    4    1    2
+## item181    5    5    5   NA    5    3   NA   NA    5    5    3   NA   NA    5
+## item182   NA   NA   NA   NA   NA    2   NA   NA   NA   NA    2    4    1   NA
+## item183    2    5   NA    2   NA    3   NA   NA   NA    4    4    2    3    2
+## item184   NA    5   NA    2   NA   NA   NA   NA   NA   NA   NA    4   NA    3
+## item185    1    5   NA    2   NA   NA   NA   NA   NA   NA    3    4   NA    3
+## item186   NA    4   NA   NA    5   NA    5    5   NA    2    4   NA   NA    5
+## item187    5    5   NA   NA    5    2    5   NA   NA    5    3    3   NA    5
+## item188    5    5    4   NA    5    3    5   NA    5    4    4    3   NA    5
+## item189    5    5    3    3    5    2    5    3    5    4    4    4   NA    5
+## item190    4    5    4   NA    5    4    5    5    5    5    5    4    5    5
+## item191    5    5    4   NA    5    4    5   NA   NA    5    5    4    5    5
+## item192    5    5    4   NA    5    4    5    5    4    4    4    4    5    5
+## item193    5    5   NA   NA    5    4    5   NA   NA   NA    5    4    4    5
+## item194    3    5    4   NA    4    3    5   NA   NA    5   NA    4    2    5
+## item195    5    4    5   NA   NA    3   NA   NA   NA   NA   NA   NA   NA    5
+## item196    4    4    2   NA    4    2    3   NA    4    2    4   NA   NA    5
+## item197    5    4   NA   NA    5   NA   NA    5   NA    2    5    3    4   NA
+## item198    5    5   NA   NA    4    4   NA   NA   NA   NA    4    3   NA    5
+## item199    4    5   NA    2    5    4    4   NA   NA    4    4    3    4   NA
+## item200   NA    5   NA   NA   NA   NA   NA   NA   NA   NA    5    4    4   NA
+## item201    1    5   NA   NA    5   NA   NA   NA   NA   NA    4   NA   NA   NA
+## item202    5    5    3   NA    5    4    5   NA   NA    5    5    4   NA   NA
+##         V543 V544 V545 V546 V547 V548 V549 V550 V551 V552 V553 V554 V555 V556
+## item118    5    4    4    4    2    2    5    5    4    4    4    3    5    2
+## item119    5    2    5    5    3   NA   NA    3   NA    4    4   NA    5   NA
+## item120    4    2    4    5    3    2    4   NA    3    4    4   NA    5   NA
+## item121    5    2    4    3    5    4    4    5    5    4    4    4    5    3
+## item122    3    2    3    5    3   NA    5    1    3    2   NA   NA    4    3
+## item123   NA    4    3    5   NA    3    3    1    3    3    2   NA   NA   NA
+## item124    5    4    5    3    2    1    4    1    3    4    2   NA    4    4
+## item125   NA   NA    2   NA    3    2   NA   NA   NA    3    4   NA    1   NA
+## item126    4    3    4    5    4    2   NA    3    4    2    4   NA    3   NA
+## item127    5    3    4    4    4    4    4    4    4    4    4    4    3    3
+## item128   NA   NA    1   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item129   NA   NA   NA    2    3   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item130   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item131    4   NA   NA    5    3    2   NA    4    3    4   NA   NA    4   NA
+## item132   NA    3   NA   NA   NA    2   NA   NA   NA   NA   NA   NA   NA   NA
+## item133    2    3   NA   NA   NA   NA    3   NA   NA   NA   NA   NA   NA    1
+## item134   NA   NA   NA   NA   NA   NA   NA    4   NA   NA   NA   NA   NA    1
+## item135    2    3    4    4    3    2    4    4    3    2    2    2    3    1
+## item136    1   NA   NA   NA   NA   NA   NA    1   NA    1   NA    2    1    1
+## item137    4   NA   NA   NA    3   NA   NA   NA   NA    1   NA    2   NA    1
+## item138   NA   NA   NA   NA    3   NA   NA   NA   NA    1   NA   NA   NA   NA
+## item139    2   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA    2   NA    1
+## item140    1    3    4   NA    3   NA   NA   NA   NA    2    1   NA    4    1
+## item141    5    3    5    5    3    2    3    1    3    4    2    2    3   NA
+## item142    5    3    3    2    3    2    4    1   NA    5   NA    2    3    1
+## item143    5    3   NA   NA    3    3   NA    2    3    4    3    2    4    1
+## item144    3    3    4   NA    3    2    5   NA   NA    3   NA    2   NA   NA
+## item146    4   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item147    5   NA   NA   NA   NA   NA   NA    3   NA   NA   NA   NA   NA   NA
+## item148   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item149    4    4    5    3    4    4   NA    4    4    4    4   NA   NA    1
+## item150    5    4    3    4    4   NA   NA   NA    4    4    4   NA    5   NA
+## item151    4    3    4    4    4   NA    4    4    4    4    4   NA   NA   NA
+## item152    5    2   NA    2    1   NA   NA    1    4    1    1   NA   NA    1
+## item153    2    3    5    4    3    3   NA    3    4    4    4   NA    4   NA
+## item154    2    4    4    4    4    4   NA    4    5    5    2   NA    5    3
+## item155    5    2    4    3    4    4   NA    2    4    4    1   NA   NA    1
+## item156   NA    4    4   NA   NA    4   NA    2    4    2   NA   NA   NA   NA
+## item157   NA   NA   NA    5    4    4   NA    4    5    4   NA   NA   NA   NA
+## item158    5   NA    3    3    4    4   NA   NA    4    4   NA   NA   NA   NA
+## item159    5    3   NA    3    4   NA   NA   NA    3    5   NA    5    3   NA
+## item160    2    4    5    5    3    3   NA    4    4    4    4   NA   NA   NA
+## item161   NA    4   NA   NA   NA   NA    3   NA   NA   NA   NA    5   NA    3
+## item162    5   NA    1    5    3   NA   NA    5    4    3   NA   NA    5   NA
+## item163    5    4    3    4    4    4   NA    5    4    5    5   NA    5   NA
+## item164   NA    3    2    5   NA   NA   NA    5    4    5    5   NA    5   NA
+## item165   NA    3   NA   NA   NA   NA   NA   NA   NA    4   NA   NA   NA   NA
+## item166    5    4   NA   NA   NA   NA   NA   NA   NA    5   NA   NA   NA   NA
+## item167   NA    4   NA    5   NA   NA   NA   NA    4    4    5   NA    5   NA
+## item168   NA    3    3    5   NA    4   NA    4    5    5   NA   NA    5   NA
+## item169   NA    2    4    4    4   NA   NA   NA    4    4    5   NA   NA   NA
+## item170   NA    3   NA    4    4   NA   NA   NA    4    4    5   NA    5   NA
+## item171    5    4    4    4    5    4    5    5    4    5    5   NA    5    4
+## item172   NA    4    3    5    4    4   NA    4    4    4   NA   NA   NA    3
+## item173   NA    2   NA    4    3   NA   NA   NA    4    5   NA   NA    5   NA
+## item174   NA   NA   NA    4   NA   NA   NA    4    4    4    5   NA   NA   NA
+## item175   NA    4    2    3   NA   NA   NA   NA    4   NA   NA   NA   NA   NA
+## item176    5    5    3    5   NA    4    5   NA    4    5    5   NA    5   NA
+## item177    3   NA   NA   NA    3   NA   NA   NA    3   NA   NA   NA   NA   NA
+## item178   NA    4    3    3    3    4   NA   NA    4    3    3   NA    5   NA
+## item179   NA   NA   NA   NA    3   NA   NA   NA    4    4   NA   NA   NA   NA
+## item180    3   NA   NA   NA    3   NA    3   NA    4    2   NA   NA   NA    3
+## item181   NA    3   NA    5    3    3   NA   NA    5    5    5   NA    5   NA
+## item182   NA   NA   NA   NA   NA   NA   NA   NA   NA    4   NA   NA   NA   NA
+## item183    5    3   NA   NA    3   NA    4   NA   NA   NA   NA    2   NA    3
+## item184   NA   NA   NA   NA   NA   NA   NA   NA    3   NA   NA   NA   NA   NA
+## item185   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item186    3   NA   NA   NA    3   NA   NA   NA    4   NA   NA    5   NA   NA
+## item187    5   NA   NA    4    3    4   NA   NA    5    5   NA    5   NA   NA
+## item188   NA   NA    4    4    4   NA   NA    5    4    5    5   NA   NA   NA
+## item189    5    3    4    1    4   NA   NA    3    4    4    3    2    4   NA
+## item190    5    4   NA    2   NA    4   NA   NA    3    4    4   NA    5   NA
+## item191    5   NA   NA    3    5    3   NA    5    5    5    5   NA    5   NA
+## item192    5   NA    4    5    5    4   NA   NA    5    4    5   NA    5   NA
+## item193    5   NA    3   NA   NA   NA   NA   NA   NA    4   NA   NA   NA   NA
+## item194   NA    3    3    1    4    3   NA   NA    5    3    4    5   NA   NA
+## item195   NA   NA   NA    3   NA   NA   NA   NA    4    4   NA   NA   NA   NA
+## item196   NA   NA    4    3   NA    3   NA    2    4    3    3   NA    4   NA
+## item197    5   NA    2    5    5   NA    5   NA    4    4   NA    5   NA   NA
+## item198   NA   NA   NA    4   NA   NA   NA   NA    4    4   NA   NA   NA   NA
+## item199    5   NA    3   NA    4   NA   NA    4    4    3    2   NA   NA   NA
+## item200   NA   NA   NA   NA    3   NA   NA    1   NA    2    1   NA   NA   NA
+## item201   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item202   NA   NA   NA   NA   NA    5   NA   NA    5    4   NA    5   NA   NA
+##         V557 V558 V559 V560 V561 V562 V563 V564 V565 V566 V567 V568
+## item118    5    5    5    5    5    5    4    5    4    5    3    2
+## item119    3    5    5   NA    4    3    2    5    4    5   NA   NA
+## item120    4    5    3    3    5    4    3    4    4    3    3    3
+## item121    5    5    5    4    5    4    5    3    5    5    4    5
+## item122    1    1   NA    2    4   NA    3    2    3    4    4    4
+## item123   NA   NA   NA   NA    4    2    4   NA    3   NA    3    4
+## item124    4    1    2    1    3    1    4    4    4    2    3    5
+## item125    5    1   NA   NA    5    1    4    4    3    2    3    2
+## item126    5    4    4    5    5    3    5    2    5    4    4    4
+## item127    4    5    4    5    4    1    4    5    5    5    3    3
+## item128   NA   NA   NA   NA   NA    1   NA   NA    1   NA   NA    2
+## item129   NA   NA   NA   NA    1   NA   NA   NA   NA   NA   NA   NA
+## item130   NA   NA   NA   NA   NA    4   NA   NA   NA   NA   NA   NA
+## item131   NA    4    3   NA    1    3    3    5    5    4    3    4
+## item132   NA   NA   NA   NA    1    3   NA   NA    3   NA   NA   NA
+## item133   NA   NA   NA   NA    1    3    3   NA    1   NA   NA    1
+## item134   NA   NA   NA   NA    3   NA   NA   NA    1   NA   NA    3
+## item135    3    5    4    4    2    4    3    3    5    2    4    3
+## item136    1   NA   NA    1   NA    1   NA   NA   NA    1    2    1
+## item137   NA    1   NA   NA    1    3   NA   NA    3   NA    3    3
+## item138   NA   NA   NA   NA    1   NA   NA   NA    4   NA    3    3
+## item139   NA    1   NA   NA   NA    3   NA   NA   NA   NA    3    2
+## item140   NA    1   NA    2   NA    2   NA    3    4    2    3    3
+## item141    2    1    3    2    3   NA    3    3    5    4    3    4
+## item142    2    1    3    3    3    3   NA   NA    5   NA    3    4
+## item143    3    4   NA    2    4    3   NA    3    3    4    4    4
+## item144    2    1   NA    1    3    3   NA   NA    4   NA    4    4
+## item146   NA   NA   NA   NA    1    2   NA   NA   NA   NA   NA   NA
+## item147   NA   NA   NA   NA    3    3   NA   NA    4   NA   NA    4
+## item148   NA   NA   NA   NA    3   NA   NA   NA   NA   NA   NA   NA
+## item149    3   NA    4    5    2    5    5    4    5    5   NA   NA
+## item150    4    5    4    4    5    5    4    4    5    5    3    5
+## item151    4    5   NA    1    3    4    4    3    4    4    5   NA
+## item152    2    3   NA    1    1    4    3   NA    2    1    2   NA
+## item153    3    4    5    5    4    3    4    4    4    5   NA   NA
+## item154    2    3    5    4    5    4    4    5    5    5   NA    4
+## item155    2   NA    4    3    1    4    4    4    2    4   NA   NA
+## item156    4    1    5    4    4   NA   NA   NA    4    5   NA   NA
+## item157   NA    5    5    2    5    3    4    4    4    4    4   NA
+## item158   NA    5    4    4    5    4    4    4    4    5    3    3
+## item159   NA    3    3    1    5    3    3    3    5    4    3    3
+## item160    4    5    3    3    3    2    4    4    4    5   NA   NA
+## item161   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA   NA
+## item162   NA    4    5    4    5    3   NA    3    5    5   NA    2
+## item163    3    4    4    3    5    4    5    4    5    5   NA    4
+## item164    3    4    3    2    5    3    4    3    5    5   NA    3
+## item165   NA    4   NA   NA   NA    4   NA   NA   NA    4   NA   NA
+## item166   NA    4   NA   NA   NA   NA    4   NA    5    5   NA   NA
+## item167    3    3   NA    4    5   NA    5   NA    5    5   NA   NA
+## item168   NA    5   NA    5    5    5   NA    3    5    5   NA   NA
+## item169   NA    4   NA   NA    5    2    5    3    4    5   NA   NA
+## item170   NA    4    4    2    5    4    5    3    4    5   NA   NA
+## item171   NA    5    4    5    5    4    5    4    5    5   NA    3
+## item172   NA    5    4    5    5    4    5    5    5    5    4    4
+## item173    3    4    5    5    5   NA    2    4    5    5   NA    2
+## item174   NA    4    4   NA    5   NA   NA    4   NA    4   NA   NA
+## item175   NA    4    4    4   NA   NA    4   NA   NA    4   NA   NA
+## item176   NA    4    4    4    5    1    4    5    5    5   NA    5
+## item177   NA   NA   NA   NA    3    1   NA   NA    4   NA   NA    2
+## item178    3    3   NA    4    5    1    4    3    4    5   NA   NA
+## item179   NA   NA   NA    4   NA   NA    4   NA   NA    5   NA   NA
+## item180   NA    3   NA    2   NA    1   NA   NA   NA    4    4    3
+## item181    4    4    5    5    5    1   NA    4    4    5    4    4
+## item182   NA   NA   NA   NA    4    3   NA   NA   NA   NA   NA    3
+## item183   NA    3   NA   NA    1    1   NA   NA   NA   NA    4    3
+## item184   NA   NA   NA   NA   NA    4   NA   NA   NA    4   NA    2
+## item185   NA   NA   NA   NA   NA    1   NA   NA   NA   NA   NA    2
+## item186   NA    4   NA   NA    5    5    2   NA    5    4   NA    4
+## item187   NA    5    4   NA    5    4    5    4    5    5   NA    4
+## item188    3    5    4   NA    5    4    5    3    4    5   NA   NA
+## item189    3    5    5    5    5    4    5    4    4    5    3    5
+## item190   NA    4    4   NA    5    4    5    4    5    5   NA    5
+## item191    5    5    4   NA    5    5    5    5    5    5    4    5
+## item192    4    5    5    4    5    5    5    5    5    5    5    5
+## item193   NA    4    5   NA    5    3    4    3    5    4   NA    5
+## item194    3    3    4    3   NA    2    5    3    5    4   NA    5
+## item195   NA    4   NA   NA    5   NA   NA   NA   NA   NA   NA   NA
+## item196    3    4    4   NA    5    1   NA    2    4    5   NA   NA
+## item197    3    4   NA   NA    4    4   NA   NA   NA    4    5   NA
+## item198   NA   NA    5   NA   NA    4   NA    4   NA    5   NA    5
+## item199    5    4   NA   NA    5    5   NA    4    4    4   NA    5
+## item200   NA   NA   NA   NA    4    5   NA   NA   NA    4   NA   NA
+## item201   NA   NA    4   NA    1   NA   NA   NA   NA   NA   NA   NA
+## item202   NA    5    5   NA   NA    3   NA    5    5    5   NA   NA
+##                                                                                                                                                                                                                       description
+## item118                                                                                                          decisions that affect other people, the financial resources, and/or the image and reputation of the organization
+## item119                                                                                                                       decisions impact on other people or the image or reputation or financial resources of your employer
+## item120                                                                                                                                                                                       being very exact or highly accurate
+## item121                                                                                                                                          repeating the same physical or mental activities over and over, without stopping
+## item122                                                                                                                                                                           compete or to be aware of competitive pressures
+## item123                                                                                                                                job structured for you, rather than allowing you to determine tasks, priorities, and goals
+## item124                                                                                                                                                                 pace is determined by the speed of equipment or machinery
+## item125                                                                                                                                                                                                  meeting strict deadlines
+## item126                                                                                                                                                                                                    regular work schedules
+## item127                                                                                                                                                                                           working in cramped work spaces
+## item128                                                                                                                                                                                  working in a closed vehicle or equipment
+## item129                                                                                                                                                                                  working in an open vehicle or equipment
+## item130                                                                                                                                                                  working indoors in environmentally controlled conditions
+## item131                                                                                                                                                               working indoors in non-controlled environmental conditions
+## item132                                                                                                                                                                                                          working outdoors
+## item133                                                                                                                                                                                             working outdoors, under cover
+## item134                                                                                                                                                                                  close physical proximity to other people
+## item135                                                                                                                                          working exposed to sounds and noise levels that are distracting or uncomfortable
+## item136                                                                                                                                                                                             bending or twisting your body
+## item137                                                                                                                                                                                         keeping or regaining your balance
+## item138                                                                                                                                                                                 kneeling, crouching, stooping or crawling
+## item139                                                                                                                                                                                                 making repetitive motions
+## item140                                                                                                                                                                                                                   sitting
+## item141                                                                                                                                                                                                                  standing
+## item142                                                                                                                                                   using your hands to handle, control, or feel objects, tools or controls
+## item143                                                                                                                                                                                                       walking and running
+## item144                                                                                                                                                                                                           attention check
+## item146                                                                                                                                                                            wearing common protective or safety equipment
+## item147                                                                                                                                                                        wearing specialized protective or safety equipment
+## item148                                                                                                                                                           contact with others (face-to-face, by telephone, or otherwise)
+## item149                                                                                                                                                                                                 coordinate or lead others
+## item150                                                                                                                                                                                work with external customers or the public
+## item151                                                                                                                                                                  deal with unpleasant, angry, or discourteous individuals
+## item152                                                                                                                                                                                                       use electronic mail
+## item153                                                                                                                                                                   have face-to-face discussions with individuals or teams
+## item154                                                                                                                                                                                      conflict situations you have to face
+## item155                                                                                                                                                                                                 written letters and memos
+## item156                                                                                                                                                                                                   perform public speaking
+## item157                                                                                                                                                                responsible for work outcomes and results of other workers
+## item158                                                                                                                                                                        responsibility for the health and safety of others
+## item159                                                                                                                                                                                                   telephone conversations
+## item160                                                                                                                                                                                       work with others in a group or team
+## item161                                                                                                                          estimating sizes, distances, and quantities; or determining time, costs, resources, or materials
+## item162                                                                                                                                       observing, receiving, and otherwise obtaining information from all relevant sources
+## item163                                                                            identifying information by categorizing, estimating, recognizing differences or similarities, and detecting changes in circumstances or events
+## item164                                                                                                               inspecting equipment, structures, or materials to identify the cause of errors or other problems or defects
+## item165                                                                                                             monitoring and reviewing information from materials, events, or the environment, to detect or assess problems
+## item166                                                                                          identifying the underlying principles, reasons, or facts of information by breaking down information or data into separate parts
+## item167                                                                                                                              establishing long-range objectives and specifying the strategies and actions to achieve them
+## item168                                                                                   using relevant information and individual judgment to determine whether events or processes comply with laws, regulations, or standards
+## item169                                                                                                                                                           assessing the value, importance, or quality of things or people
+## item170                                                                                                                               analyzing information and evaluating results to choose the best solution and solve problems
+## item171                                                                                                                                     developing specific goals and plans to prioritize, organize, and accomplish your work
+## item172                                                                                                                      compiling, coding, categorizing, calculating, tabulating, auditing, or verifying information or data
+## item173                                                                                                                                                scheduling events, programs, and activities, as well as the work of others
+## item174                                                                                                                           developing, designing, or creating new applications, ideas, relationships, systems, or products
+## item175                                                                                                                                                                 keeping up-to-date technically and applying new knowledge
+## item176                                                                                                                              using either control mechanisms or direct physical activity to operate machines or processes
+## item177                                                                                                             entering, transcribing, recording, storing, or maintaining information in written or electronic/magnetic form
+## item178 providing documentation, detailed instructions, drawings, or specifications to tell others about how devices, parts, equipment, or structures are to be fabricated, constructed, assembled, modified, maintained, or used
+## item179                                                                                                                  using hands and arms in handling, installing, positioning, and moving materials, and manipulating things
+## item180                                                                                                     using computers and computer systems to program, write software, set up functions, enter data, or process information
+## item181                                                                                                                                             running, maneuvering, navigating, or driving vehicles or mechanized equipment
+## item182                                                                                                             performing physical activities that require considerable use of your arms and legs and moving your whole body
+## item183                       servicing, repairing, calibrating, regulating, fine-tuning, or testing machines, devices, and equipment that operate primarily on the basis of electrical or electronic (not mechanical) principles
+## item184                                                 servicing, repairing, adjusting, and testing machines, devices, moving parts, and equipment that operate primarily on the basis of mechanical (not electronic) principles
+## item185                                                                          providing personal assistance, medical attention, emotional support, or other personal care to others such as coworkers, customers, or patients?
+## item186                                                                                   identifying the developmental needs of others and coaching, mentoring, or otherwise helping others to improve their knowledge or skills
+## item187                                                                        communicating with people outside the organization, representing the organization to customers, the public, government, and other external sources
+## item188                                                                                                    providing information to supervisors, co-workers, and subordinates by telephone, in written form, e-mail, or in person
+## item189                                                                                                                                                           getting members of a group to work together to accomplish tasks
+## item190                                                                                                                                        encouraging and building mutual trust, respect, and cooperation among team members
+## item191                                                                                                                 developing constructive and cooperative working relationships with others, and maintaining them over time
+## item192                                                                                                                                                                          providing guidance and direction to subordinates
+## item193                                                                                                                                                   translating or explaining what information means and how it can be used
+## item194                                                                                                                                                 monitoring and controlling resources and overseeing the spending of money
+## item195                                                                                                                 performing day-to-day administrative tasks such as maintaining information files and processing paperwork
+## item196                                                                                                                                                                 performing for people or dealing directly with the public
+## item197                                                                                                      providing guidance and expert advice to management or other groups on technical, systems-, or process-related topics
+## item198                                                                                                      handling complaints, settling disputes, and resolving grievances and conflicts, or otherwise negotiating with others
+## item199                                                                                                                                  convincing others to buy merchandise/goods or to otherwise change their minds or actions
+## item200                                                                                                                                                      recruiting, interviewing, selecting, hiring, and promoting employees
+## item201                                                                            identifying the educational needs of others, developing formal educational or training programs or classes, and teaching or instructing others
+## item202                                                                                                                                                                              decision making freedom, without supervision
+##         mean   sd resource_ns$n
+## item118 3.99 1.05           556
+## item119 3.80 0.99           451
+## item120 3.77 1.04           511
+## item121 4.34 0.91           567
+## item122 3.08 1.27           497
+## item123 3.57 1.12           433
+## item124 3.25 1.29           541
+## item125 3.09 1.29           429
+## item126 3.81 1.07           521
+## item127 3.69 1.14           566
+## item128 2.34 1.22           198
+## item129 2.88 1.22           132
+## item130 3.22 1.22            45
+## item131 3.55 1.17           445
+## item132 2.78 1.24           162
+## item133 2.84 1.30           195
+## item134 3.08 1.18           140
+## item135 3.30 1.19           567
+## item136 2.05 1.25           278
+## item137 2.51 1.22           226
+## item138 3.10 1.09           125
+## item139 2.58 1.20           141
+## item140 2.88 1.22           363
+## item141 3.01 1.23           526
+## item142 2.99 1.14           426
+## item143 3.45 1.14           449
+## item144 3.04 1.20           289
+## item146 2.27 1.34           123
+## item147 3.86 1.13           177
+## item148 3.78 1.22            79
+## item149 4.10 0.99           478
+## item150 4.14 0.88           509
+## item151 4.00 0.99           495
+## item152 2.84 1.36           409
+## item153 3.99 1.05           514
+## item154 4.08 1.02           521
+## item155 3.31 1.20           476
+## item156 3.51 1.14           399
+## item157 3.98 1.03           338
+## item158 3.99 0.93           476
+## item159 3.80 1.16           403
+## item160 3.77 1.01           512
+## item161 3.31 1.24            39
+## item162 3.75 1.15           412
+## item163 4.19 0.88           530
+## item164 4.04 0.97           482
+## item165 3.78 1.06           283
+## item166 4.02 0.90           346
+## item167 4.06 0.91           404
+## item168 4.30 0.88           434
+## item169 4.05 0.95           431
+## item170 4.22 0.87           445
+## item171 4.49 0.74           509
+## item172 4.48 0.70           517
+## item173 3.87 1.07           454
+## item174 3.83 1.02           376
+## item175 4.16 0.98           304
+## item176 4.41 0.88           502
+## item177 3.45 1.19           162
+## item178 3.84 1.03           437
+## item179 3.97 1.02           242
+## item180 3.50 1.16           286
+## item181 4.19 0.99           468
+## item182 3.57 1.19           105
+## item183 3.28 1.20           229
+## item184 3.68 1.10           145
+## item185 3.62 1.17           117
+## item186 3.99 1.00           294
+## item187 4.16 0.87           390
+## item188 4.16 0.94           425
+## item189 4.11 0.89           531
+## item190 4.39 0.79           464
+## item191 4.52 0.74           489
+## item192 4.47 0.81           506
+## item193 4.18 0.90           371
+## item194 4.08 0.93           467
+## item195 4.05 0.91           261
+## item196 3.75 1.11           434
+## item197 3.93 1.03           321
+## item198 4.04 0.90           307
+## item199 3.81 1.09           380
+## item200 3.79 1.07           212
+## item201 3.87 1.04           159
+## item202 4.20 0.97           260
+\end{verbatim}
 

### 2022-12-19 Submission.Rmd
figured out zero sd's. We were reading in the "truncated labels" .csv file improperly (labels were misaligned with variables)

--- 2022-12-15 Submission.Rmd
@@
 
-labels <- read.csv("truncatedlabels.csv")
+labels <- read.csv("truncatedlabels.csv", header=FALSE)  ## Changed on 12/19 to fix zero sd issues
 
@@
 
-resource <- resource[,-145]   ## attention check
-#resource <- resource[ which(resource$sd > 0), ]
+resource <- resource[-28,]   ## attention check
 
@@
 
-challenge <- challenge[,-308]
+challenge <- challenge[-21,]
 
@@
 
-hindrance <- hindrance[,-248]   ## attention check
-#hindrance <- hindrance[ which(hindrance$sd > 0), ]
+hindrance <- hindrance[-46,]   ## attention check = 248
 
@@
 
-labels <- read.csv("truncatedlabels.csv")
-
-resource <- as.data.frame(t(data[118:202]))
-
-resource$description <- labels[c(118:202),1]
-resource$mean <- round(rowMeans(resource[1:nrow(data)], na.rm=TRUE),2)
-resource$sd   <- round(apply(resource[1:nrow(data)], 1, sd, na.rm=TRUE),2)
-
-resource <- resource[,-145]   ## attention check
-#resource <- resource[ which(resource$sd > 0), ] 
-########################################################
-########################################################
-##Need to triple check all of this. 
-########################################################
-########################################################
-##checking the ns
-#library(psych)
-#resource_ns <- describe(data[c(118:144, 146:202)])
-#resource_ns
-#table(data$item161) # check one item to confirm ns - it is functioning correctly.
-
-#resource <- cbind(resource, resource_ns$n)
-#resource
 sortresource <- resource[order(resource$sd),]
@@
 
-labels <- read.csv("truncatedlabels.csv")
-
-challenge <- as.data.frame(t(data[288:372]))
-
-challenge$description <- labels[c(288:372),1]
-challenge$mean <- round(rowMeans(challenge[1:nrow(data)], na.rm=TRUE),2)
-challenge$sd   <- round(apply(challenge[1:nrow(data)], 1, sd, na.rm=TRUE),2)
-
-challenge <- challenge[,-308]   ## attention check
-#challenge <- challenge[ which(challenge$sd > 0), ]
-
 sortchallenge <- challenge[order(challenge$sd),]
@@
 ```{r hindrancesagree, fig.cap="Characteristics most similarly viewed as hindrances (lowest standard deviations)."}
-
-labels <- read.csv("truncatedlabels.csv")
-
-hindrance <- as.data.frame(t(data[203:287]))
-
-hindrance$description <- labels[c(203:287),1]
-hindrance$mean <- round(rowMeans(hindrance[1:nrow(data)], na.rm=TRUE),2)
-hindrance$sd   <- round(apply(hindrance[1:nrow(data)], 1, sd, na.rm=TRUE),2)
-
-hindrance <- hindrance[,-248]   ## attention check
-#hindrance <- hindrance[ which(hindrance$sd > 0), ]
 
@@
 
-labels <- read.csv("truncatedlabels.csv")
-
-resource <- as.data.frame(t(data[118:202]))
-
-resource$description <- labels[c(118:202),1]
-resource$mean <- round(rowMeans(resource[1:nrow(data)], na.rm=TRUE),2)
-resource$sd   <- round(apply(resource[1:nrow(data)], 1, sd, na.rm=TRUE),2)
-
-resource <- resource[,-145]   ## attention check
 resource <- resource[ which(resource$sd > 0), ]
@@
 
-labels <- read.csv("truncatedlabels.csv")
-
-challenge <- as.data.frame(t(data[288:372]))
-
-challenge$description <- labels[c(288:372),1]
-challenge$mean <- round(rowMeans(challenge[1:nrow(data)], na.rm=TRUE),2)
-challenge$sd   <- round(apply(challenge[1:nrow(data)], 1, sd, na.rm=TRUE),2)
-
-challenge <- challenge[,-308]   ## attention check
-challenge <- challenge[ which(challenge$sd > 0), ]
-
 sortchallenge <- challenge[order(-challenge$sd),]
@@
 ```{r hindrancesdisagree, fig.cap="Characteristics most *dis*similarly viewed as hindrances (highest standard deviations)."}
-
-labels <- read.csv("truncatedlabels.csv")
-
-hindrance <- as.data.frame(t(data[203:287]))
-
-hindrance$description <- labels[c(203:287),1]
-hindrance$mean <- round(rowMeans(hindrance[1:nrow(data)], na.rm=TRUE),2)
-hindrance$sd   <- round(apply(hindrance[1:nrow(data)], 1, sd, na.rm=TRUE),2)
-
-hindrance <- hindrance[,-248]   ## attention check
-hindrance <- hindrance[ which(hindrance$sd > 0), ]
 

### 2022-12-19 Submission.tex
figured out zero sd's. We were reading in the "truncated labels" .csv file improperly (labels were misaligned with variables)

--- 2022-12-10 Submission.tex
@@
 
-As can be seen by the graphs, there is considerable disagreement regarding the degree to which job elements are considered \emph{hindrances}, with the 10 elements showing the greatest agreement still ranging in standard deviations from 0 to 1.18.
-What is widely seen as a resource and challenge tends to be more universally agreed upon (range of lowest 10 resource standard deviations is 0 to 0.88 and the range of lowest 10 challenge standard deviations is 0 to 0.87.
+As can be seen by the graphs, there is considerable disagreement regarding the degree to which job elements are considered \emph{hindrances}, with the 10 elements showing the greatest agreement still ranging in standard deviations from 1.12 to 1.19.
+What is widely seen as a resource and challenge tends to be more universally agreed upon (range of lowest 10 resource standard deviations is 0.70 to 0.88 and the range of lowest 10 challenge standard deviations is 0.79 to 0.87.
 

### 2022-12-19 Submission.Rmd
results section notes

@@
 
+> Maybe just do a histogram of standard deviations (overall) or perhaps also by O\*Net dimensions (aim to do this 12/21 in St. Cloud)
+
 2. Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
+
+> Maybe just put correlations in here - SIOP matrix (challenge, hindrance, resource) - would be most interesting by O\*Net dimension.
 
@@
 
-5. *Research Question 3*: Are literature-implicated hiderances consistently rated as job hindrances?
+5. *Research Question 3*: Are literature-implicated hindrances consistently rated as job hindrances?
+
+> New graph presents these but need an inferential - maybe ANOVAs
 

### 2022-12-19 Submission.tex
results section notes

@@
 \def\labelenumi{\arabic{enumi}.}
+\tightlist
 \item
   Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
+\end{enumerate}
+
+\begin{quote}
+Maybe just do a histogram of standard deviations (overall) or perhaps also by O*Net dimensions (aim to do this 12/21 in St.~Cloud)
+\end{quote}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
 \item
   Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
+\end{enumerate}
+
+\begin{quote}
+Maybe just put correlations in here - SIOP matrix (challenge, hindrance, resource) - would be most interesting by O*Net dimension.
+\end{quote}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{2}
 \item
@@
 \item
-  \emph{Research Question 3}: Are literature-implicated hiderances consistently rated as job hindrances?
+  \emph{Research Question 3}: Are literature-implicated hidrances consistently rated as job hindrances?
 \end{enumerate}
+
+\begin{quote}
+New graph presents these but need an inferential - maybe ANOVAs
+\end{quote}
 

### 2022-12-21 Submission.Rmd
bartletts test and histograms

@@
 
+## Standard deviations of perceptions
+
+```{r overallhist, fig.cap="Frequency distribution of standard deviations across characteristics deemed resources, challenges, and demands."}
+
+## resource$sd
+
+toplotresource <- resource
+toplotchallenge <- challenge
+toplothindrance <- hindrance
+
+toplotresource$RD <- "Resource"
+toplotchallenge$RD <- "Challenge"
+toplothindrance$RD <- "Hindrance"
+
+toplottogether <- rbind(toplotresource,toplotchallenge,toplothindrance)
+
+library(ggplot2)
+#ggplot(resource, aes(x=sd)) + geom_histogram()
+ggplot(toplottogether, aes(x=sd)) + geom_histogram() + facet_grid(RD ~ .)
+
+lookie <- stats::bartlett.test(sd ~ RD, toplottogether)
+
+```
+
+Figure \@ref(fig:overallhist) presents standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand.
+As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's $K^2$ = `r lookie$statistic[[1]]`, *p* = `r lookie$p.value` ).
+
 ## Low Variability Demands and Resources

### 2022-12-21 Submission.tex
bartletts test and histograms

@@
 \item
-  \emph{Research Question 3}: Are literature-implicated hidrances consistently rated as job hindrances?
+  \emph{Research Question 3}: Are literature-implicated hindrances consistently rated as job hindrances?
 \end{enumerate}
@@
 \end{quote}
+
+\hypertarget{standard-deviations-of-perceptions}{%
+\subsection{Standard deviations of perceptions}\label{standard-deviations-of-perceptions}}
+
+\begin{figure}
+\centering
+\includegraphics{Submission_files/figure-latex/overallhist-1.pdf}
+\caption{\label{fig:overallhist}Frequency distribution of standard deviations across characteristics deemed resources, challenges, and demands.}
+\end{figure}
+
+Figure \ref{fig:overallhist} presents standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand.
+As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's \(K^2\) = 76.83, \emph{p} = 0.00 ).
 

### 2022-12-26 Submission.Rmd
correlations (big table in as placeholder for now)

@@
 
+## Correlations
+
+```{r cortab}
+
+data_new <- data
+
+## O*NET categories
+
+data_new$onet.resource.ii <- rowMeans(data_new[c(162:166)], na.rm=TRUE)
+data_new$onet.resource.mp <- rowMeans(data_new[c(167:176)], na.rm=TRUE)
+data_new$onet.resource.wo <- rowMeans(data_new[c(177:185)], na.rm=TRUE)
+data_new$onet.resource.io <- rowMeans(data_new[c(186:202)], na.rm=TRUE)
+data_new$onet.resource.ir <- rowMeans(data_new[c(149:161)], na.rm=TRUE)
+data_new$onet.resource.pc <- rowMeans(data_new[c(128:144,146:148)], na.rm=TRUE)
+data_new$onet.resource.sc <- rowMeans(data_new[c(118:127)], na.rm=TRUE)
+
+data_new$overall.resource <- rowMeans(data_new[c(118:144,146:202)], na.rm=TRUE)
+
+data_new$onet.hindrance.ii <- rowMeans(data_new[c(246:247,249:252)], na.rm=TRUE)
+data_new$onet.hindrance.mp <- rowMeans(data_new[c(252:261)], na.rm=TRUE)
+data_new$onet.hindrance.wo <- rowMeans(data_new[c(262:270)], na.rm=TRUE)
+data_new$onet.hindrance.io <- rowMeans(data_new[c(271:287)], na.rm=TRUE)
+data_new$onet.hindrance.ir <- rowMeans(data_new[c(233:245)], na.rm=TRUE)
+data_new$onet.hindrance.pc <- rowMeans(data_new[c(213:232)], na.rm=TRUE)
+data_new$onet.hindrance.sc <- rowMeans(data_new[c(203:212)], na.rm=TRUE)
+
+data_new$overall.hindrance <- rowMeans(data_new[c(203:247,249:287)], na.rm=TRUE)
+
+data_new$onet.challenge.ii <- rowMeans(data_new[c(332:336)], na.rm=TRUE)
+data_new$onet.challenge.mp <- rowMeans(data_new[c(337:346)], na.rm=TRUE)
+data_new$onet.challenge.wo <- rowMeans(data_new[c(347:355)], na.rm=TRUE)
+data_new$onet.challenge.io <- rowMeans(data_new[c(356:372)], na.rm=TRUE)
+data_new$onet.challenge.ir <- rowMeans(data_new[c(319:331)], na.rm=TRUE)
+data_new$onet.challenge.pc <- rowMeans(data_new[c(298:307,309:318)], na.rm=TRUE)
+data_new$onet.challenge.sc <- rowMeans(data_new[c(288:297)], na.rm=TRUE)
+
+data_new$overall.challenge <- rowMeans(data_new[c(288:307,309:372)], na.rm=TRUE)
+
+data_new$burnout      <- rowMeans(data_new[c(373:376)], na.rm=TRUE)
+data_new$stress       <- rowMeans(data_new[c(377:379)], na.rm=TRUE)
+data_new$engagement   <- rowMeans(data_new[c(380:399)], na.rm=TRUE)        ## added 10/12 because analyses too wonky with 3 subscales
+
+names(data_new)[names(data_new) == "stress"] <- "Stress"
+names(data_new)[names(data_new) == "overall.challenge"] <- "Challenge"
+names(data_new)[names(data_new) == "overall.hindrance"] <- "Hindrance"
+names(data_new)[names(data_new) == "overall.resource"] <- "Resource"
+
+## Was originally overall: "Challenge", "Hindrance", "Resource"
+
+r <- corx::corx(data_new, x =c("onet.resource.ii", "onet.resource.mp", "onet.resource.wo",  "onet.resource.io", "onet.resource.ir", "onet.resource.pc", "onet.resource.sc", "onet.challenge.ii", "onet.challenge.mp", "onet.challenge.wo",  "onet.challenge.io", "onet.challenge.ir", "onet.challenge.pc", "onet.challenge.sc","onet.hindrance.ii", "onet.hindrance.mp", "onet.hindrance.wo", "onet.hindrance.io", "onet.hindrance.ir", "onet.hindrance.pc", "onet.hindrance.sc"), y =c("onet.resource.ii", "onet.resource.mp", "onet.resource.wo",  "onet.resource.io", "onet.resource.ir", "onet.resource.pc", "onet.resource.sc", "onet.challenge.ii", "onet.challenge.mp", "onet.challenge.wo", "onet.challenge.io", "onet.challenge.ir", "onet.challenge.pc", "onet.challenge.sc","onet.hindrance.ii", "onet.hindrance.mp", "onet.hindrance.wo", "onet.hindrance.io", "onet.hindrance.ir", "onet.hindrance.pc", "onet.hindrance.sc"),
+                triangle = "lower",
+                stars = c(0.05, 0.01, 0.001),
+                describe = c(`$M$` = mean, `$SD$` = sd))
+
+papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table,
+                  caption = "Challenge, hindrance, and resource bivariate correlations.",
+                  escape = FALSE, 
+                  font_size = "small", 
+                  landscape = TRUE)
+```
+
 ```{r scalelevelgraphs, fig.cap="Average characteristic rating grouped by literature-implicated categorizations."}

### 2022-12-27 SIOP2023/Counts/counts_poster.Rmd
changed file location

--- 2022-10-14 SIOP2023/Counts/Submission_ResourceCount.Rmd
@@
 ---
-title             : "Perception of Work Demands and Resources: Does Sheer Volume Matter?"
-shorttitle        : "JDR Volume"
-
+title: 'Perception of Work Demands and Resources: Does Sheer Volume Matter?'
 author:
-  - name          : "Alicia Stachowski"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Anytown, USA"
-    email         : "stachowskia@uwstout.edu"
-  - name          : "John Kulas"
-    affiliation   : "2"
-
+  - name: Alicia Stachowski
+    affil: 1
+  - name: John Kulas
+    affil: 2
 affiliation:
-  - id            : "1"
-    institution   : "University of Wisconsin - Stout"
-  - id            : "2"
-    institution   : "eRg"
-
-authornote: |
-
-abstract: |
-  The relationships among total number of job resources, challenges, and hindrances and outcomes of  engagement, stress, and burnout are explored.
-568 workers rated O\*Net job characteristics in terms of relevance and interpretation of characteristics as challenges, hindrances and resources.
-The findings showed moderately strong connection between the presence of resources and challenge demands with job engagement.
-
-keywords          : "keywords"
-wordcount         : "X"
-
-bibliography      : ["jobdemands_resources_bibtex.bib"]
-
-floatsintext      : no
-linenumbers       : no
-draft             : no
-mask              : no
-
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-
-csl               : "apa7.csl"
-classoption       : "man"
-output            :
-  papaja::apa6_pdf:
-    latex_engine: xelatex
+  - num: 1
+    address: University of Wisconsin - Stout
+  - num: 2
+    address: eRg
+column_numbers: 3
+#logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
+#logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
+output: 
+  posterdown::posterdown_html:
+    self_contained: false
+bibliography: jobdemands_resources_bibtex.bib
 ---
 
-```{r setup, echo=FALSE}
-
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed, echo=FALSE, warning=FALSE, message=FALSE)
-#knitr::opts_knit$set(root.dir=normalizePath('../'))
-knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
-papaja::r_refs("r-references.bib")
-
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE)
 ```
 
+# Introduction
 A plethora of research applying the job demands-resources model [@demerouti2001job] and theory [@bakker2017job] underscores the importance of work characteristics on the experience of motivation and strain.
@@
 
-# Method
+# Methods
 
@@
 
+# Results
+
 ```{r study1, include=FALSE}
-
 temp <- read.csv("..//JDRJournalSubmission//initial_data_screen.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script
@@
 With more job elements come increased opportunities for those elements to be perceived as resources, challenges, or hindrances.
-\newpage
+
+# Conclusion
+
+Add one!
+
+```{r, include=FALSE}
+knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
+```
 
 # References
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id="refs" custom-style="Bibliography"></div>
-\endgroup

### 2022-12-27 SIOP2023/Counts/counts_poster.Rmd
finding data: knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
Draft of the poster ready. Need to 1) hide references, 2) add polish in terms of color, logos etc., and 3) cut 1 paragraph to get it to 3 columns.

@@
 knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
 ```
@@
 # Introduction
-A plethora of research applying the job demands-resources model [@demerouti2001job] and theory [@bakker2017job] underscores the importance of work characteristics on the experience of motivation and strain.
-However, much of our existing research on this topic assumes that certain characteristics are resources (for example, autonomy) while others (such as deadlines) are generally considered demands.
-This study explores how individual perceptions of work characteristics relate to work-related outcomes by asking respondents to indicate (of the characteristics that apply to their jobs) how much each is experienced to be a resource, challenge, or hindrance.
-That is, we allow for the circumstance that the same characteristic may be perceived by some to be a resource as well as a demand.
-We then evaluate associations between resources and demands as well as probing for subsequent associations with engagement, stress, and burnout.
 
-## The Job Demands-Resources Theory
-
-The theoretical foundation for this study is the job demands-resources theory [@demerouti2001job].
-This theory posits that the perception of a characteristic of one’s job as a resource or demand activates one of two unique processes: either health impairment or motivation [@bakker2014job].
-Demanding job characteristics are frequently associated with negative outcomes [@bakker2003dual], whereas resources have been associated with positive organizational outcomes such as engagement [@bakker2007job].
-Resources are commonly defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [e.g., high work pressure, @demerouti2001job].
-
-### An Added Complexity: Perception (Appraisal) of Work Characteristics Might Matter
-
-The above description speaks to one of two distinct processes being activated, presumably based on one’s appraisal of how a work characteristics makes them feel (e.g., consider the different reactions two different employees may have to being nominated to give a speech at an upcoming company event).
-Thus, although some research on job demands in particular is based on *a priori* classifications of demands [@searle2015merits], the appraisal of any work characteristic as a demand or resource is actually subjective.
-
-The literature on the experience of stress explains how such individual differences in appraisal are possible.
-Specifically, the transactional theory of stress and coping states that people cognitively appraise stimuli in their environments on a continual basis [@lazarus1984stress].
-During this process, meaning is assigned to stimuli.
-If our example fictional employee appraised the upcoming speech as threatening, challenging, or possibly harmful (in contrast to positive or irrelevant), the resulting emotional distress initiates coping (e.g., attempting to decline, asking for help in writing the speech).
-From that point, a reassessment of the situation happens, and the cycle of appraisal continues based on the action to cope with the stressor [@lazarus1984stress].
-This theory of stress and coping speaks to the importance of how work demands are assessed by individuals, and it is not only possible, but quite likely that demands and resources do not fit cleanly into objective categories of "demands" and "resources".
-
-### Could a Work Demand be Appraised Positively?: The Challenge-Hindrance Framework
-
-Although the concept of *stress* often carries a negative connotation, the progenitor of this concept [@selye1936syndrome] took a less valenced perspective, defining stress less perjoratively as a simple response to change.
-For instance, the example given in the previous paragraph describes an employee who may appraise being nominated to give a speech as a negative stressor.
-However, another employee may appraise the nomination to do so as an exciting opportunity to share their experiences with their coworkers, or one in which they may be able to further prove their capabilities on a more visible platform.
-The terms associated with the two different appraisals of the stressor described here can be accomodated within the context of the JDR theory as "challenge" and "hindrance" demands [@cavanaugh2000empirical] Specifically, challenge demands promote mastery, personal growth, and future gains.
-Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes [e.g., @cavanaugh2000empirical].
-We will explore their associations with both positive and negative outcomes in this study.
-
-Prior to proposing specific predictions, the empirical evidence on challenge and hindrance demands is very briefly shared below.
-To begin, the first logical question is whether employees actually distinguish between challenge and hindrance stressors, and research suggests that they can and do.
-For example, @bakker2013weekly found that perceived work pressure can be classified as a hindrance demand, and emotional demands as a challenge demand.
-@webster2011extending considered three common workplace demands including workload, role ambiguity, and role conflict.
-Interestingly, they found that while each could be appraised primarily as challenges or hindrances, employees could also simultaneously be perceived as being both a challenge and hindrance.
-
-Having established that there can be individual differences in the appraisal of demands as challenges or resources, we next turn our attention to their association with organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and well-being.
-For example, @cavanaugh2000empirical found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern with job satisfaction and job search behaviors in a sample of managers.
-However, @abbas2019challenge found that challenge and hindrance stressors were both positively related to strain and turnover intentions.
-We also have some evidence that challenge-hinderance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement [@crawford2010linking].
-The appraisal process also suggests theoretically that the perception of a job characteristic as a challenge or hindrance is a mediator.
-@gerich2017relevance, for instance, found that employee well-being was, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
-To provide further evidence of the distinction between challenge and hindrance appraisals on work-related outcomes, @podsakoff2007differential's meta-analysis supported the original assertion of @cavanaugh2000empirical such that challenge stressors were positively related to job satisfaction and organizational commitment, and negatively related to both turnover intentions and actual turnover, while hindrance stressors produced the opposite pattern of relationships.
-
-## Current Study and Hypotheses
-
-The brief review above provides theoretical and empirical support for the connection between resources and positive organizational outcomes, and between demands and negative outcomes.
-For this current study, we explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related to three organizational outcomes: engagement [“a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption”, @schaufeli2002measurement], workplace stress [“an individual state characterized by a combination of high arousal and displeasure”, p.
+We explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related to three organizational outcomes: engagement [“a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption”, @schaufeli2002measurement], workplace stress [“an individual state characterized by a combination of high arousal and displeasure”, p.
 15, @pejtersen2010second] and burnout [“the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work”, p.
 197, @kristensen2005copenhagen].
-Utilizing the job demands-resources theory, the transactional theory of stress, and the challenge-hindrance framework, we propose that the number of job characteristics appraised as “challenge demands” (i.e., promote mastery, personal growth, and future gains) would activate a positive state – that of engagement.
-In contrast, number of characteristics of one’s job appraised as a hindrance demand (i.e., inhibit growth, learning and goal achievement) would activate a negative state – here, resulting in stress and/or burnout.
+
+Predictions are grounded in three intersecting theories:
+1.
+First, the job demands-resources theory [@demerouti2001job] posits that the perception of a characteristic of one’s job as a resource or demand activates one of two unique processes: either health impairment or motivation [@bakker2014job],
+2. The transactional theory of stress and coping states speaks to the importance of how work demands are assessed by individuals [@lazarus1984stress], and
+3.
+The challenge-hindrance framework [@cavanaugh2000empirical], which connects the above theories by distinguishing between challenge and hindrance appraisals of demands.
+*Challenge demands* promote mastery, personal growth, and future gains, whereas *hindrance demands* inhibit growth, learning and goal achievement.
+
+Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes [e.g., @cavanaugh2000empirical].
+Thus:
 
@@
 
-We evaluate relationships between the predictors and proximal outcomes of the Job Demands-Resources model [@bakker2017job; @bakker2003dual; @demerouti2001job], but from within the comprehensive framework of O\*Net.
-Here, we focus on the relationship between O\*Net delineated job components and employee levels of job engagement, job stress, and burnout within a workforce representative sample.
+## Participants, Procedure, & Materials
 
-## Participants
+A Prolific panel sample initially resulted in 785 respondents, of which 568 were retained after cleaning.
+13.57% had been in their job <6 months, 19.20% 6-12 months, 49.12% 1-5 years, 13.27% 5-10 year, and 4.87% >10 years.
+Mean age was 28.18 years (*SD* = 7.53).
+Self-identified gender was largely female (52.58%) or male (46.83%).
 
-  A sample using a Prolific panel resulted in 785 individuals who initially accessed the survey link.
-Of those,112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes & Wilhelm, 2021).
-Additional screening using four embedded attention checks resulted in the retention of 568 respondents.
-A total of 13.57% had been in their job less than 6 months, 19.20% between 6 months and a year, 49.12% between one and five years, 13.27% between 5 and 10 years, and 4.87% more than 10 years.
-Reported ages ranged from 18 to 65 with an average of 28.18 years old (SD = 7.53).
-Gender was captured via a free-field gender identity category, although the sample predominantly self-identified as female (52.58%) or male (46.83%).
-
-## Materials
+An email was sent to eligible participants in the Prolific respondent pool (those 18+ holding either a full-time or part-time job).
+The 40-45 minute survey was conducted via Qualtrics and asked to think about their primary job.
+The items they were presented with depended on the job characteristics they initially specified.
+They were asked to report how much a characteristic was a resource, and then how much each characteristic was a hindrance, and finally, how much each item was a challenge.
+Participants were compensated six dollars.
 
 ### Characteristics, Demands, and Resources. 
-
-Our analyses included items within O\*Net’s classifications of “work activity”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context”: 5) Interpersonal Relationships (14 statements), 6) Physical Work Conditions (30 statements)1, and 7) Structural Job Characteristics (13 statements).
-
-Other than minor grammatical editing (for example, changing “the” to “you”), we retained the O\*Net wording for our item stems.
+Our analyses included items within O\*Net’s classifications of “work activity” and "work context" items.
 We used O\*Net’s response scales, several of which were unique across items, but all shared the same 1 to 5 scale options.
-Subsequent to providing ratings of whether or not an O\*Net characteristic was relevant for the respondent’s work, each respondent who agreed that an element had at least some relevance to their job was also asked to rate that element in terms of, 1) .
+Subsequent to providing ratings of whether or not a characteristic was relevant, each respondent was also asked to rate that element in terms of, 1) .
 .
@@
 
-### Stress.
-
-Three items taken from the Copenhagen Psychosocial Questionnaire [@burr_third_2019]. Obtained alpha was .85 in this sample.
-
-### Burnout.
-
-Four items were taken from the Copenhagen Psychosocial Questionnaire [@burr_third_2019]. Alpha was 0.85 in this sample.
-
-### Engagement.
-
-The 18-item engagement measure was recently developed [@engage_2022], with the authors specifying three subscales which yielded current sample $\alpha$’s of 0.68 (absorption) and 0.80 (vigor), and 0.90 (dedication).
+### Outcomes of Stress, Burnout, and Engagement. 
+Three items taken from the Copenhagen Psychosocial Questionnaire [@burr_third_2019] to capture stress.
+Obtained alpha was .85 in this sample.
+Four items were taken from the Copenhagen Psychosocial Questionnaire [@burr_third_2019] to capture burnout.
+Alpha was 0.85 in this sample.
+The 18-item engagement measure was recently developed [@engage_2022] to capture engagement.
 For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, alpha = 0.91).
 
-## Procedure
-
-An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
-Eligibility requirements included being 18+ and holding either a full-time or part-time job.
-Participants then voluntarily chose to respond to the survey.
-The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes.
-Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified.
-Thus, if a respondent indicated that 5 of the characteristics were not part of their job, they were not subsequently asked to rate the level of resource, challenge, or hindrance a given item presented to them.
-For items that were a part of their jobs, they were then asked to report how much a characteristic was a resource, and then how much each characteristic was a hindrance, and finally, how much each item was a challenge.
-Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
-
 # Results
-
-```{r study1, include=FALSE}
+```{r study1, include=FALSE, message = FALSE, warning = FALSE}
 temp <- read.csv("..//JDRJournalSubmission//initial_data_screen.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script
@@
 
-```{r rankings}
+```{r rankings, warnings = FALSE, include = FALSE, eval = FALSE}
 
@@
 
-# Results
-
-We used R (Version 4.0.3; @R-base) and the R-packages careless (Version 1.1.3; Yentes & Wilhelm, 2021), labourR (Version 1.0.0; Kouretsis et al., 2020), papaja (Version 0.1.0.9997; Aust & Barth, 2020), and tinylabels (Barth, 2021) for all analyses.
-
 Correlations, means and standard deviations among all study variables are presented in Table \ref{tab:correlation_table}.
@@
 
-To explore possible associations more comprehensively, we conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
+We also conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
 First, regarding engagement ($F_{(3, 564)}$ = 26.41, p < .001), the total resources were predictive of engagement, but neither challenge nor hindrance demands predicted engagement (see Table \ref{tab:regression_table_eng}).
@@
 While not a causal relationship, it points to the potential value of these kinds of employee support nonetheless.
-The other relationships with outcomes of stress and burnout were largely not supported, suggesting that the sheer number of resources, challenges, and hindrances are not significantly related to these negative outcomes.
-The caveat here is stress, which does exhibit a small significant association with the presence of hindrances.
-Note here that the total average number of hindrances implicated by our sample was low, so it is possible that a stronger association is hidden by a restriction of range.
 
-## Limitations and Future Directions
-
-As with any piece of research, this project has limitations, but also provide a variety of additional directions to pursue in the future.
-First, while a strength of this project, arguably, is the use of O\*Net items, practical considerations limited the number of job characteristics we could include in our survey.
 Future study could consider additional or other O\*Net items.
@@
 It may be the case that certain kinds of resources or challenges are more strongly associated with engagement than others, and such, future research could explore the importance of resources/challenges categorically.
+It would be especially interesting to explore additional outcomes (e.g., job satisfaction) as well, or whether volume of resources and demands operationalized in this way are related to other behaviors (e.g., turnover intention, perceived organizational support, commitment).
+It is also possible that categorically some demands are more related to these outcomes than others.
+The moderate association between hindrances and challenges (*r* = .22) also hints that some of these relationships may be driven by *job complexity*.
 
-Our study was limited to three outcomes of interest.
-It would be especially interesting to explore additional outcomes (e.g., job satisfaction) as well, or whether volume of resources and demands operationalized in this way are related to other behaviors (e.g., turnover intention, perceived organizational support, commitment).
-Furthermore, while we found support for the prediction that resources and challenge demands would be positively related to engagement, it would be interesting to consider moderators of this relationship.
-For example, the Job Characteristics Theory [@hackman1976motivation] includes the key component of growth need strength in the connections between job characteristics (e.g., autonomy, skill variety) and critical states (e.g., experienced meaningfulness), and between critical states and personal and work outcomes.
-Perhaps this connection between engagement and challenge demands, for instance, is stronger for those with greater growth need strength.
-
-It is also possible that rather than volume, categorically some demands are more related to these outcomes than others.
-The moderate association between hindrances and challenges (*r* = .22) also hints that some of these relationships may be driven by *job complexity* - that is, some jobs simply have more elements.
-With more job elements come increased opportunities for those elements to be perceived as resources, challenges, or hindrances.
-
-# Conclusion
-
-Add one!
-
-```{r, include=FALSE}
+```{r bib, eval=FALSE}
 knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
 ```
-
-# References

### 2023-01-02 SIOP2023/Counts/counts_poster.Rmd
error edits

@@
 column_numbers: 3
+primary_colour: "#313ab3"
+secondary_colour: "#B4B5B4"
+accent_colour: "#111c2c"
 #logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
@@
     self_contained: false
+csl               : "apa7.csl"
 bibliography: jobdemands_resources_bibtex.bib
+suppress-bibliography: true 
+link-citations: true
 ---
@@
 knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
+
+library(tinylabels) ## because of warning on later chunk
+
 ```
@@
 
-### Characteristics, Demands, and Resources. 
+## Characteristics, Demands, and Resources. 
 Our analyses included items within O\*Net’s classifications of “work activity” and "work context" items.
@@
 
-### Outcomes of Stress, Burnout, and Engagement. 
+## Outcomes of Stress, Burnout, and Engagement. 
 Three items taken from the Copenhagen Psychosocial Questionnaire [@burr_third_2019] to capture stress.
@@
 
-```{r correlation_table, eval=TRUE}
+```{r correlationtable, warning=FALSE}
 
@@
 
-#cor(data[405:410], use="all.obs")   ## something to be told with resources and challenges
+# cor(data[405:410], use="all.obs")   ## something to be told with resources and challenges
 
@@
 
-```{r regression_table_eng}
+```{r regressiontableeng}
 library(papaja)
@@
 
-```{r regression_table_str}
+```{r regressiontablestr}
 library(papaja)
@@
 
-```{r regression_table_bur}
+```{r regressiontablebur}
 library(papaja)
@@
 
-Correlations, means and standard deviations among all study variables are presented in Table \ref{tab:correlation_table}.
+Correlations, means and standard deviations among all study variables are presented in Table \@ref(tab:correlationtable).
 The results reveal a positive association between resources and engagement (*r* = .34; H1a), but a lack of meaningful association between resources and stress and burnout (H1b and H1c, respectively).
@@
 We also conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
-First, regarding engagement ($F_{(3, 564)}$ = 26.41, p < .001), the total resources were predictive of engagement, but neither challenge nor hindrance demands predicted engagement (see Table \ref{tab:regression_table_eng}).
-Next, stress was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$ = 2.47, *p* = .060 (see Table \ref{tab:regression_table_str}).
+First, regarding engagement ($F_{(3, 564)}$ = 26.41, p < .001), the total resources were predictive of engagement, but neither challenge nor hindrance demands predicted engagement (see Table \@ref(tab:regressiontableeng).
+Next, stress was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$ = 2.47, *p* = .060 [see Table \@ref(tab:regressiontablestr)].
 Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$= 1.10, *p* = .349.
-See Table \ref{tab:regression_table_bur}.
+See Table \@ref(tab:regressiontablebur).
 

### 2023-01-02 SIOP2023/Counts/counts_poster.Rmd
Udpating Poster

@@
 link-citations: true
+affiliation_textsize: "50pt"
+body_textsize: "50px"
+title_textsize:	"75pt"	
+author_textsize:	"50pt"
+#logoleft_name	"Figures/posterdownlogo.png"	Location of the image to use.
+#logoright_name	"Figures/posterdownlogo.png"	Location of the image to use.
 ---
@@
 
-We explored whether the amount or volume of perceived resources and demands (in the form of challenges and hindrances) would be related to three organizational outcomes: engagement [“a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption”, @schaufeli2002measurement], workplace stress [“an individual state characterized by a combination of high arousal and displeasure”, p.
+Using the the job demands-resources theory [@demerouti2001job], transactional theory of stress and coping [@lazarus1984stress], and  the challenge-hindrance framework [@cavanaugh2000empirical], we explored whether the amount or volume of perceived resources and demands would be related to three organizational outcomes: engagement [“a positive affective experience defined as a fulfilling, work-related state of mind characterized by vigor, dedication, and absorption”, @schaufeli2002measurement], workplace stress [“an individual state characterized by a combination of high arousal and displeasure”, p.
 15, @pejtersen2010second] and burnout [“the degree of physical and psychological fatigue and exhaustion that is perceived by the person as related to his/her work”, p.
 197, @kristensen2005copenhagen].
-
-Predictions are grounded in three intersecting theories:
-1.
-First, the job demands-resources theory [@demerouti2001job] posits that the perception of a characteristic of one’s job as a resource or demand activates one of two unique processes: either health impairment or motivation [@bakker2014job],
-2. The transactional theory of stress and coping states speaks to the importance of how work demands are assessed by individuals [@lazarus1984stress], and
-3.
-The challenge-hindrance framework [@cavanaugh2000empirical], which connects the above theories by distinguishing between challenge and hindrance appraisals of demands.
-*Challenge demands* promote mastery, personal growth, and future gains, whereas *hindrance demands* inhibit growth, learning and goal achievement.
 
@@
 
-## Participants, Procedure, & Materials
+**Participants, Procedure, & Materials**
 
@@
 
-An email was sent to eligible participants in the Prolific respondent pool (those 18+ holding either a full-time or part-time job).
-The 40-45 minute survey was conducted via Qualtrics and asked to think about their primary job.
-The items they were presented with depended on the job characteristics they initially specified.
-They were asked to report how much a characteristic was a resource, and then how much each characteristic was a hindrance, and finally, how much each item was a challenge.
+An email was sent to eligible Prolific respondents (those 18+ holding either a full-time or part-time job).
+A ~45 minute survey asked to think about their primary job.
+The items presented depended on the job characteristics they initially specified.
+Respondents were asked to report 1) how much a characteristic was a resource, 2) how much each characteristic was a hindrance, 3) how much each item was a challenge.
 Participants were compensated six dollars.
 
-## Characteristics, Demands, and Resources. 
-Our analyses included items within O\*Net’s classifications of “work activity” and "work context" items.
-We used O\*Net’s response scales, several of which were unique across items, but all shared the same 1 to 5 scale options.
-Subsequent to providing ratings of whether or not a characteristic was relevant, each respondent was also asked to rate that element in terms of, 1) .
+**Characteristics, Demands, and Resources**.
+
+Items within O\*Net’s classifications of “work activity” and "work context" items were used here.
+We used O\*Net’s response scales, which all shared the same 1 to 5 scale options.
+Subsequent to providing ratings of whether or not a characteristic was relevant, respondents rated items in terms of, 1) .
 .
@@
 
-## Outcomes of Stress, Burnout, and Engagement. 
+**Outcomes of Stress, Burnout, and Engagement**.
+
 Three items taken from the Copenhagen Psychosocial Questionnaire [@burr_third_2019] to capture stress.
@@
 
-Correlations, means and standard deviations among all study variables are presented in Table \@ref(tab:correlationtable).
-The results reveal a positive association between resources and engagement (*r* = .34; H1a), but a lack of meaningful association between resources and stress and burnout (H1b and H1c, respectively).
-Challenge demands were positively associated with engagement (*r* = .31; H2a), but were similarly unrelated to stress or burnout (H2b and H2c).
+Correlations, means and standard deviations are presented in Table \@ref(tab:correlationtable).
+The results reveal a positive association between resources and engagement (*r* = .34; H1a), but a lack of meaningful association between resources and stress (H1b) and burnout (H1c).
+Challenge demands were positively associated with engagement (*r* = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
 Total hindrance stressors were largely not significantly associated with our outcomes, although there was a small-moderate association with stress (H3b; *r* = .09).
@@
 We also conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
-First, regarding engagement ($F_{(3, 564)}$ = 26.41, p < .001), the total resources were predictive of engagement, but neither challenge nor hindrance demands predicted engagement (see Table \@ref(tab:regressiontableeng).
-Next, stress was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$ = 2.47, *p* = .060 [see Table \@ref(tab:regressiontablestr)].
+The total resources were predictive of engagement ($F_{(3, 564)}$ = 26.41, p < .001), but neither challenge nor hindrance demands predicted engagement (see Table \@ref(tab:regressiontableeng).
+Stress was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$ = 2.47, *p* = .060 [see Table \@ref(tab:regressiontablestr)].
 Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$= 1.10, *p* = .349.
@@
 While not a causal relationship, it points to the potential value of these kinds of employee support nonetheless.
-
-Future study could consider additional or other O\*Net items.
-We intentionally conceptualized resources and demands in terms of perceived total amounts.
-It may be the case that certain kinds of resources or challenges are more strongly associated with engagement than others, and such, future research could explore the importance of resources/challenges categorically.
-It would be especially interesting to explore additional outcomes (e.g., job satisfaction) as well, or whether volume of resources and demands operationalized in this way are related to other behaviors (e.g., turnover intention, perceived organizational support, commitment).
-It is also possible that categorically some demands are more related to these outcomes than others.
-The moderate association between hindrances and challenges (*r* = .22) also hints that some of these relationships may be driven by *job complexity*.
+Future study could consider additional or other O\*Net items, *kinds* of resources or challenges, additional outcomes (e.g., job satisfaction), or whether volume of resources and demands operationalized in this way are related to other behaviors.
 

### 2023-01-03 SIOP2023/Counts/counts_poster.Rmd
tinkering

@@
 secondary_colour: "#B4B5B4"
-accent_colour: "#111c2c"
+accent_colour: "#FF0000"
 #logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
-#logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
+logoleft_name: http&#58;//career.iresearchnet.com/wp-content/uploads/2015/01/Occupational-Information-Network-300x300.png
 output: 
@@
 library(tinylabels) ## because of warning on later chunk
+
+```
+
+```{css, echo=FALSE}
+
+/*                         https://www.w3schools.com/css/css3_images.asp                  */
+
+.logo_left {
+  position: absolute;
+  top: 0px;
+  left: 0px;
+  width: 550px;         
+  height: 540px;
+}
+
+.logo_right {
+  position: absolute;
+  top: 20px;
+  left: 3250px;
+  width: 700px;          
+  height: 440px;
+}
+
+p.caption {
+  font-size: 0.8em;         /* This sets figure caption font size */
+  text-align: left
+}
 

### 2023-01-17 Submission.Rmd
freeze glitch changes

@@
 
-```{r litresources, fig.cap="Average and standard deviation of O*Net characteristics retained as indicators of Autonomy, Cohesion, Control, Participation, and Supervisor Support."}
+```{r litresources}
 
 ###############################################
-###############################################
+############################################### include & eval=FALSE on 1/16/23 because of new figure which replaced this older attempt
+
+### ACTUALLY, just commented out the graph because other code chunks needed for subsequent commands - 1/17/23 , fig.cap="Average and standard deviation of O*Net characteristics retained as indicators of Autonomy, Cohesion, Control, Participation, and Supervisor Support."
 
@@
 
-ggplot(summarized, aes(x=category, y=mean, fill=RD)) + geom_bar(stat="identity", position=position_dodge()) + theme_bw() + xlab("") + ylab("Average Job Characteristic Rating") + coord_cartesian(ylim=c(1,5)) + scale_fill_brewer(palette="Blues") +
-  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.5, size=0.8, position=position_dodge(.9))
+#ggplot(summarized, aes(x=category, y=mean, fill=RD)) + geom_bar(stat="identity", position=position_dodge()) + theme_bw() + xlab("") + ylab("Average Job Characteristic Rating") + coord_cartesian(ylim=c(1,5)) + scale_fill_brewer(palette="Blues") +
+#  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.5, size=0.8, position=position_dodge(.9))
 
@@
 We used 98 statements taken from O\*NET [activity and context classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3).
-We retained 41 work activity classifications which O\*NET groups into categories of information input (5 statements), interacting with others (17 statements), mental processes (10 statements) and work output (9 statements).
-Fifty-seven work context statements grouped into interpersonal relationships (14 statements), physical work conditions (30 statements), and structural job characteristics (13 statements).
+We retained 41 work activity classifications which O\*NET groups into categories of information input (5 statements; Where and how are the information and data gained that are needed to perform this job?), interacting with others (17 statements; What interactions with other persons or supervisory activities occur while performing this job?), mental processes (10 statements; What processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (9 statements; What physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
+Fifty-seven work context statements grouped into interpersonal relationships (14 statements; This category describes the context of the job in terms of human interaction processes), physical work conditions (30 statements; This category describes the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (13 statements; This category involves the relationships or interactions between the worker and the structural characteristics of the job).
 
@@
 
-> Maybe just do a histogram of standard deviations (overall) or perhaps also by O\*Net dimensions (aim to do this 12/21 in St. Cloud)
+> Done - Figure \@ref(fig:overallhist)
+
+> NOT DONE: Combine current graphs 2 $\rightarrow$ 8 into only 2 graphs (put resources, challenges, and demands on same graph; Kulas do this)
 
@@
 
-> Maybe just put correlations in here - SIOP matrix (challenge, hindrance, resource) - would be most interesting by O\*Net dimension.
+> Done (at O\*Net dimension level) - Table \@ref(tab:cortab).
 
@@
 
-> New graph presents these but need an inferential - maybe ANOVAs
+> Alicia can you present "what this means" and what is being presented in Figure \@ref(fig:scalelevelgraphs) more clearly - also possibly add ANOVAs
 
@@
                   font_size = "small", 
-                  landscape = TRUE)
+                  landscape = TRUE,
+                  note = "The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)")
 ```

### 2023-01-17 Submission.tex
correlations (big table in as placeholder for now)
freeze glitch changes

@@
 
-\begin{figure}
-\centering
-\includegraphics{Submission_files/figure-latex/litresources-1.pdf}
-\caption{\label{fig:litresources}Average and standard deviation of O*Net characteristics retained as indicators of Autonomy, Cohesion, Control, Participation, and Supervisor Support.}
-\end{figure}
-
 \hypertarget{materials}{%
@@
 We used 98 statements taken from O*NET \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context classifications}.
-We retained 41 work activity classifications which O*NET groups into categories of information input (5 statements), interacting with others (17 statements), mental processes (10 statements) and work output (9 statements).
-Fifty-seven work context statements grouped into interpersonal relationships (14 statements), physical work conditions (30 statements), and structural job characteristics (13 statements).
+We retained 41 work activity classifications which O*NET groups into categories of information input (5 statements; Where and how are the information and data gained that are needed to perform this job?), interacting with others (17 statements; What interactions with other persons or supervisory activities occur while performing this job?), mental processes (10 statements; What processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (9 statements; What physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
+Fifty-seven work context statements grouped into interpersonal relationships (14 statements; This category describes the context of the job in terms of human interaction processes), physical work conditions (30 statements; This category describes the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (13 statements; This category involves the relationships or interactions between the worker and the structural characteristics of the job).
 
@@
 \begin{quote}
-Maybe just do a histogram of standard deviations (overall) or perhaps also by O*Net dimensions (aim to do this 12/21 in St.~Cloud)
+Done - Figure \ref{fig:overallhist}
+\end{quote}
+
+\begin{quote}
+NOT DONE: Combine current graphs 2 \(\rightarrow\) 8 into only 2 graphs (put resources, challenges, and demands on same graph; Kulas do this)
 \end{quote}
@@
 \begin{quote}
-Maybe just put correlations in here - SIOP matrix (challenge, hindrance, resource) - would be most interesting by O*Net dimension.
+Done (at O*Net dimension level) - Table \ref{tab:cortab}.
 \end{quote}
@@
 \begin{quote}
-New graph presents these but need an inferential - maybe ANOVAs
+Alicia can you present ``what this means'' and what is being presented in Figure \ref{fig:scalelevelgraphs} more clearly - also possibly add ANOVAs
 \end{quote}
@@
 Figures \ref{fig:resourcesdisagree}, \ref{fig:challengesdisagree}, and \ref{fig:hindrancesdisagree} present the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations (these are the 10 characteristics with the greatest variability in rating).
+
+\hypertarget{correlations}{%
+\subsection{Correlations}\label{correlations}}
+
+\begin{lltable}
+
+\begin{TableNotes}[para]
+\normalsize{\textit{Note.} The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)}
+\end{TableNotes}
+
+\small{
+
+\begin{longtable}{lllllllllllllllllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:cortab}Challenge, hindrance, and resource bivariate correlations.}\\
+\toprule
+ & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{6} & \multicolumn{1}{c}{7} & \multicolumn{1}{c}{8} & \multicolumn{1}{c}{9} & \multicolumn{1}{c}{10} & \multicolumn{1}{c}{11} & \multicolumn{1}{c}{12} & \multicolumn{1}{c}{13} & \multicolumn{1}{c}{14} & \multicolumn{1}{c}{15} & \multicolumn{1}{c}{16} & \multicolumn{1}{c}{17} & \multicolumn{1}{c}{18} & \multicolumn{1}{c}{19} & \multicolumn{1}{c}{20} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
+\midrule
+\endfirsthead
+\caption*{\normalfont{Table \ref{tab:cortab} continued}}\\
+\toprule
+ & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{6} & \multicolumn{1}{c}{7} & \multicolumn{1}{c}{8} & \multicolumn{1}{c}{9} & \multicolumn{1}{c}{10} & \multicolumn{1}{c}{11} & \multicolumn{1}{c}{12} & \multicolumn{1}{c}{13} & \multicolumn{1}{c}{14} & \multicolumn{1}{c}{15} & \multicolumn{1}{c}{16} & \multicolumn{1}{c}{17} & \multicolumn{1}{c}{18} & \multicolumn{1}{c}{19} & \multicolumn{1}{c}{20} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
+\midrule
+\endhead
+1. onet.resource.ii & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
+2. onet.resource.mp & .61*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.19 & 0.60\\
+3. onet.resource.wo & .46*** & .50*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.79 & 0.84\\
+4. onet.resource.io & .49*** & .64*** & .45*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.10 & 0.60\\
+5. onet.resource.ir & .46*** & .55*** & .37*** & .60*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.80 & 0.61\\
+6. onet.resource.pc & .19*** & .15*** & .32*** & .18*** & .37*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 2.99 & 0.77\\
+7. onet.resource.sc & .43*** & .46*** & .41*** & .45*** & .48*** & .37*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.61\\
+8. onet.challenge.ii & .62*** & .49*** & .37*** & .41*** & .33*** & .08 & .33*** & - &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
+9. onet.challenge.mp & .47*** & .63*** & .42*** & .50*** & .41*** & .09* & .38*** & .65*** & - &  &  &  &  &  &  &  &  &  &  &  & 4.20 & 0.64\\
+10. onet.challenge.wo & .34*** & .39*** & .64*** & .34*** & .30*** & .29*** & .38*** & .45*** & .49*** & - &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.88\\
+11. onet.challenge.io & .34*** & .48*** & .33*** & .65*** & .48*** & .13** & .40*** & .50*** & .68*** & .43*** & - &  &  &  &  &  &  &  &  &  & 4.07 & 0.64\\
+12. onet.challenge.ir & .32*** & .40*** & .26*** & .48*** & .63*** & .23*** & .39*** & .46*** & .60*** & .39*** & .70*** & - &  &  &  &  &  &  &  &  & 3.85 & 0.63\\
+13. onet.challenge.pc & .12** & .08 & .21*** & .13** & .26*** & .66*** & .29*** & .14** & .12** & .33*** & .20*** & .31*** & - &  &  &  &  &  &  &  & 2.85 & 0.79\\
+14. onet.challenge.sc & .27*** & .31*** & .28*** & .38*** & .40*** & .27*** & .62*** & .36*** & .41*** & .38*** & .51*** & .45*** & .40*** & - &  &  &  &  &  &  & 3.66 & 0.59\\
+15. onet.hindrance.ii & -.26*** & -.26*** & -.17*** & -.24*** & -.18*** & -.02 & -.08 & -.27*** & -.26*** & -.10* & -.19*** & -.16*** & .06 & -.10* & - &  &  &  &  &  & 2.15 & 1.01\\
+16. onet.hindrance.mp & -.23*** & -.30*** & -.17*** & -.22*** & -.15*** & .05 & -.07 & -.22*** & -.27*** & -.10* & -.18*** & -.15*** & .12** & -.06 & .86*** & - &  &  &  &  & 2.10 & 1.05\\
+17. onet.hindrance.wo & -.21*** & -.25*** & -.22*** & -.22*** & -.06 & -.02 & -.12** & -.14** & -.21*** & -.23*** & -.15*** & -.09* & .05 & -.10* & .66*** & .69*** & - &  &  &  & 2.31 & 1.02\\
+18.
+onet.hindrance.io & -.22*** & -.27*** & -.14*** & -.29*** & -.18*** & -.01 & -.10* & -.21*** & -.25*** & -.10* & -.27*** & -.19*** & .07 & -.10* & .79*** & .86*** & .69*** & - &  &  & 2.23 & 1.03\\
+19.
+onet.hindrance.ir & -.22*** & -.24*** & -.15*** & -.24*** & -.25*** & -.06 & -.11** & -.19*** & -.21*** & -.08* & -.20*** & -.23*** & .04 & -.12** & .79*** & .80*** & .61*** & .82*** & - &  & 2.35 & 0.89\\
+20. onet.hindrance.pc & -.04 & -.08* & -.09* & -.11** & -.10* & -.16*** & -.13** & -.03 & -.04 & -.06 & -.08* & -.10* & -.04 & -.13** & .38*** & .33*** & .47*** & .35*** & .47*** & - & 2.66 & 0.83\\
+21.
+onet.hindrance.sc & -.13** & -.15*** & -.13** & -.19*** & -.13** & -.09* & -.23*** & -.12** & -.10* & -.05 & -.16*** & -.12** & -.01 & -.17*** & .62*** & .62*** & .56*** & .64*** & .66*** & .45*** & 2.64 & 0.80\\
+\bottomrule
+\addlinespace
+\insertTableNotes
+\end{longtable}
+
+}
+
+\end{lltable}
 

### 2023-01-28 Submission.Rmd
6 graphs into 2 figures

@@
 
-topresource <- head(sortresource, 10)
+topresource <- head(sortresource, 8)    ## changed for combined plot (1/28/23)
 
@@
 
-ggplot(topresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
+a <- ggplot(topresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
   scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Agreed Upon as a Resource") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))
@@
 
-topchallenge <- head(sortchallenge, 10)
+topchallenge <- head(sortchallenge, 8)    ## changed for combined plot (1/28/23)
 
@@
 
-library(ggplot2)
-
-ggplot(topchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
+b <- ggplot(topchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
   scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Agreed Upon as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))
@@
 
-tophindrance <- head(sorthindrance, 10)
+tophindrance <- head(sorthindrance, 8)  ## changed for combined plot (1/28/23)
 
@@
 
-library(ggplot2)
-
-ggplot(tophindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
-  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Agreed upon as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
+c <- ggplot(tophindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
+  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Agreed upon as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))
 
@@
 
-Figures \@ref(fig:resourcesagree), \@ref(fig:challengesagree), and \@ref(fig:hindrancesagree) present the resources, challenges, and hindrances that are *largely agreed on* as indexed by (relatively) low standard deviations.[^caveat]
+Figure \@ref(fig:combinegraphs) presents resources, challenges, and hindrances that are *largely agreed on* as indexed by (relatively) low standard deviations.[^caveat] There are only 8 characteristics presented per perceived category because of limited space.
+All sortable ratings are available in the online resources.
 
@@
 
-As can be seen by the graphs, there is considerable disagreement regarding the degree to which job elements are considered *hindrances*, with the 10 elements showing the greatest agreement still ranging in standard deviations from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`.
-What is widely seen as a resource and challenge tends to be more universally agreed upon (range of lowest 10 resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 10 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`.
+```{r combinegraphs, fig.cap="Characteristics percieved most similarly (lowest standard deviations).", fig.height=10}
+
+library(gridExtra)
+grid.arrange(a, b, c, nrow = 3)
+
+```
+
+As can be seen by the graphs, there is considerable disagreement regarding the degree to which job elements are considered *hindrances*, with the 8 elements showing the greatest agreement still ranging in standard deviations from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`.
+What is widely seen as a resource and challenge tends to be more universally agreed upon (range of lowest 8 resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`.
 
@@
 
-topresource <- head(sortresource, 10)
+topresource <- head(sortresource, 8)
 
@@
 
-library(ggplot2)
-
-ggplot(topresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
+d <- ggplot(topresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
   scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed Upon as a Resource") + 
@@
 
-topchallenge <- head(sortchallenge, 10)
+topchallenge <- head(sortchallenge, 8)
 
@@
 
-library(ggplot2)
-
-ggplot(topchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
+e <- ggplot(topchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
   scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed Upon as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
@@
 
-tophindrance <- head(sorthindrance, 10)
+tophindrance <- head(sorthindrance, 8)
 
@@
 
-library(ggplot2)
-
-ggplot(tophindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
+f <- ggplot(tophindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
   scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed upon as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
@@
 
-Figures \@ref(fig:resourcesdisagree), \@ref(fig:challengesdisagree), and \@ref(fig:hindrancesdisagree) present the resources, challenges, and hindrances that are *largely disagreed on* as indexed by (relatively) high standard deviations (these are the 10 characteristics with the greatest variability in rating).
+```{r combinegraphs2, fig.cap="Characteristics percieved most *DIS*similarly (lowest standard deviations).", fig.height=10}
+
+library(gridExtra)
+grid.arrange(d, e, f, nrow = 3)
+
+```
+
+Figure \@ref(fig:combinegraphs2) presents the resources, challenges, and hindrances that are *largely disagreed on* as indexed by (relatively) high standard deviations (these are the 8 characteristics with the greatest variability in rating).
 

### 2023-01-28 Submission.tex
6 graphs into 2 figures

@@
 \usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Job Demands-Resources model components through the lens of O*NET classifications},
+  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={Job Demands-Resources model components through the lens of O*NET classifications},
-  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics{Submission_files/figure-latex/resourcesagree-1.pdf}
-\caption{\label{fig:resourcesagree}Characteristics most similarly viewed as resources (lowest standard deviations).}
-\end{figure}
+Figure \ref{fig:combinegraphs} presents resources, challenges, and hindrances that are \emph{largely agreed on} as indexed by (relatively) low standard deviations.\footnote{There were a few characteristics with standard deviations of ``zero'' but these were excluded from presenation as they were likely representing only one person (\emph{n}'s should also go on these graphs if they're retained - Alicia's idea 12/2 was to use initial ratings as indicators of counts).} There are only 8 characteristics presented per perceived category because of limited space.
+All sortable ratings are available in the online resources.
 
@@
 \centering
-\includegraphics{Submission_files/figure-latex/challengesagree-1.pdf}
-\caption{\label{fig:challengesagree}Characteristics most similarly viewed as challenges (lowest standard deviations).}
+\includegraphics{Submission_files/figure-latex/combinegraphs-1.pdf}
+\caption{\label{fig:combinegraphs}Characteristics percieved most similarly (lowest standard deviations).}
 \end{figure}
 
-\begin{figure}
-\centering
-\includegraphics{Submission_files/figure-latex/hindrancesagree-1.pdf}
-\caption{\label{fig:hindrancesagree}Characteristics most similarly viewed as hindrances (lowest standard deviations).}
-\end{figure}
-
-Figures \ref{fig:resourcesagree}, \ref{fig:challengesagree}, and \ref{fig:hindrancesagree} present the resources, challenges, and hindrances that are \emph{largely agreed on} as indexed by (relatively) low standard deviations.\footnote{There were a few characteristics with standard deviations of ``zero'' but these were excluded from presenation as they were likely representing only one person (\emph{n}'s should also go on these graphs if they're retained - Alicia's idea 12/2 was to use initial ratings as indicators of counts).}
-
-As can be seen by the graphs, there is considerable disagreement regarding the degree to which job elements are considered \emph{hindrances}, with the 10 elements showing the greatest agreement still ranging in standard deviations from 1.12 to 1.19.
-What is widely seen as a resource and challenge tends to be more universally agreed upon (range of lowest 10 resource standard deviations is 0.70 to 0.88 and the range of lowest 10 challenge standard deviations is 0.79 to 0.87.
+As can be seen by the graphs, there is considerable disagreement regarding the degree to which job elements are considered \emph{hindrances}, with the 8 elements showing the greatest agreement still ranging in standard deviations from 1.12 to 1.16.
+What is widely seen as a resource and challenge tends to be more universally agreed upon (range of lowest 8 resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86.
 
@@
 \centering
-\includegraphics{Submission_files/figure-latex/resourcesdisagree-1.pdf}
-\caption{\label{fig:resourcesdisagree}Characteristics most \emph{dis}similarly viewed as resources (highest standard deviations).}
+\includegraphics{Submission_files/figure-latex/combinegraphs2-1.pdf}
+\caption{\label{fig:combinegraphs2}Characteristics percieved most \emph{DIS}similarly (lowest standard deviations).}
 \end{figure}
 
-\begin{figure}
-\centering
-\includegraphics{Submission_files/figure-latex/challengesdisagree-1.pdf}
-\caption{\label{fig:challengesdisagree}Characteristics most \emph{dis}similarly viewed as challenges (highest standard deviations).}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{Submission_files/figure-latex/hindrancesdisagree-1.pdf}
-\caption{\label{fig:hindrancesdisagree}Characteristics most \emph{dis}similarly viewed as hindrances (highest standard deviations).}
-\end{figure}
-
-Figures \ref{fig:resourcesdisagree}, \ref{fig:challengesdisagree}, and \ref{fig:hindrancesdisagree} present the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations (these are the 10 characteristics with the greatest variability in rating).
+Figure \ref{fig:combinegraphs2} presents the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations (these are the 8 characteristics with the greatest variability in rating).
 

### 2023-01-28 Submission.Rmd
Updates to Figures and description of Figure 4.

@@
 
-Lastly, we propose three research that explicitly address a topic hinted at in the literature review above.
+Lastly, we propose three research questions that explicitly address a topic discussed above.
 Although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, there remains variability in these appraisals [@lepine2022challenge].
 @lepine2022challenge, in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal.
-We explore whether literature-implicated job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory [@bakker2017job]and challenge-hindrance stressor framework [@cavanaugh2000empirical].
+We explore whether literature-implicated job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory [@bakker2017job] and challenge-hindrance stressor framework [@cavanaugh2000empirical].
 
@@
 
->*Research Question 2*: Are literature-implicated challenges consistently rated as job challenges?
-
->*Research Question 3*: Are literature-implicated hiderances consistently rated as job hindrances?
+>*Research Question 2*: Are literature-implicated demands consistently rated as job demands?
 
@@
 
-Of the `r nrow(use)` Prolific panel individuals who initially accessed the survey link, `r nrow(different)` indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses [@R-careless].
+Of the `r nrow(use)` individuals who initially accessed the survey link, `r nrow(different)` indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses [@R-careless].
 Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of `r nrow(data)` respondents who constitute the current sample.
@@
 
-Our survey was informed by 98 statements taken from job characteristic descriptors located within O\*Net’s classification of “work activities”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context” groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
-
-The O\*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to "responsibility" than task.
-For example, the descriptor for "level of competition", which is an element of the "structural job characteristics" grouping, is *...to what extent does this job require the worker to compete or to be aware of competitive pressures?* Other than minor grammatical editing (for example, changing “the worker” to “you”), we retained the O\*Net wording for our item stems.
-We also retained O\*Net’s response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
-It would likely NOT be considered controversial to referred to these as "effectively" Likert-type response scales.
-
-The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
-
 We used 98 statements taken from O\*NET [activity and context classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3).
@@
 For example, the statement "How responsible is the worker for work outcomes and results of other workers?" has response options ranging from *No responsibility* to *Very high responsibility*, while the statement, "How often do you use electronic mail in this job?" has options ranging from *Never* to *Every day*.
+The O\*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to "responsibility" than task.
+For example, the descriptor for "level of competition", which is an element of the "structural job characteristics" grouping, is *...to what extent does this job require the worker to compete or to be aware of competitive pressures?* Other than minor grammatical editing (for example, changing “the worker” to “you”), we retained the O\*Net wording for our item stems.
+We also retained O\*Net’s response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
+It would likely NOT be considered controversial to referred to these as "effectively" Likert-type response scales.
+
 We retained the essence of each O\*NET descriptor to capture characteristics of relevance for each respondent.
@@
 
+The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
+
 # Results
-
-Outline:
-
-1. Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
-
-> Done - Figure \@ref(fig:overallhist)
-
-> NOT DONE: Combine current graphs 2 $\rightarrow$ 8 into only 2 graphs (put resources, challenges, and demands on same graph; Kulas do this)
-
-2. Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
-
-> Done (at O\*Net dimension level) - Table \@ref(tab:cortab).
-
-3. *Research Question 1*: Are literature-implicated resources consistently rated as job resources?
-
-4. *Research Question 2*: Are literature-implicated challenges consistently rated as job challenges?
-
-5. *Research Question 3*: Are literature-implicated hindrances consistently rated as job hindrances?
-
-> Alicia can you present "what this means" and what is being presented in Figure \@ref(fig:scalelevelgraphs) more clearly - also possibly add ANOVAs
 
@@
 
+The first prediction asks whether job characteristics differ in variability/stability regarding
+subjective worker perception as a demand or resource.
 Figure \@ref(fig:overallhist) presents standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand.
@@
 
-[^caveat]: There were a few characteristics with standard deviations of "zero" but these were excluded from presenation as they were likely representing only one person (*n*'s should also go on these graphs if they're retained - Alicia's idea 12/2 was to use initial ratings as indicators of counts).
+[^caveat]: There were a few characteristics with standard deviations of "zero" but these were excluded from presentation as they were likely representing only one person (*n*'s should also go on these graphs if they're retained - Alicia's idea 12/2 was to use initial ratings as indicators of counts).
 
@@
 library(gridExtra)
-grid.arrange(a, b, c, nrow = 3)
+grid.arrange(b, c, a, nrow = 3)
 
@@
 library(gridExtra)
-grid.arrange(d, e, f, nrow = 3)
+grid.arrange(e, f, d, nrow = 3)
 
@@
 Figure \@ref(fig:combinegraphs2) presents the resources, challenges, and hindrances that are *largely disagreed on* as indexed by (relatively) high standard deviations (these are the 8 characteristics with the greatest variability in rating).
+In sum, these results provide some support for H1, particularly for hindrances, which are consistently viewed as "different".
 
 ## Correlations
+
+ADD THIS!
 
@@
 
+Figure 4 highs the average characteristic rating grouped by the literature implicated categories shown on the right.
+These categories are frequently presented in descriptions of the JD-R model and theory (cite).
+To answer these research questions, authors categorized items into the categories listed in the literature.
+For example, autonomy is frequently described as a resource.
+An O*Net item in the “autonomy” category is “How much decision making freedom, without supervision, does your job offer?”.
+Means for respondent-rated resources, challenges, and hindrances were then computed to explore whether literature-implicated resources and demands were consistently rated as such.
+The left side of Figure 8 shows literature-derived demands (e.g., work pressure).
+We do not see a clear pattern of high ratings as hindrances for these demands.
+In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much more variability in how employees rated what should objectively be "hindrances" at work.
+However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings.
+Here, the white bars representing resources are consistently higher.
+ADD ANOVAS HERE - one way repeated measures for each category (total of 10 analyses).
+describe pattern.
+In sum, these results provide ___ support for RQ 1 and 2.
+
+challenges
+
 see Figure \@ref(fig:scalelevelgraphs)

### 2023-01-28 Submission.tex
Updates to Figures and description of Figure 4.

@@
 \makeatother
-
-\usepackage{xpatch}
-\makeatletter
-\xapptocmd\appendix
-  {\xapptocmd\section
-    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
-    {}{\InnerPatchFailed}%
-  }
-{}{\PatchFailed}
+\shorttitle{O*NET JD-R}
 \keywords{keywords\newline\indent Word count: X}
@@
 \date{}
-
-\shorttitle{O*NET JD-R}
 
@@
 
-\abstract{%
+\abstract{
 O*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource.
@@
 Cognitively, the perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources) (Bakker \& Demerouti, 2014).
-Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience depsite the typical apriori assignment of a characteristic as objectively a ``demand'' or ``resource''.
-We explore this further below.
+Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience depsite the typical apriori assignment of a characteristic as objectively a ``demand'' or ``resource.'' We explore this further below.
 
@@
 
-Although there is a tendency to attach a negative connotation to the word ``stress'', Selye (1936) defined stress as a response to change, which is quite non-specific.
+Although there is a tendency to attach a negative connotation to the word ``stress,'' Selye (1936) defined stress as a response to change, which is quite non-specific.
 We return to the employed public figure for this next section.
@@
 The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task.
-For example, the descriptor for ``level of competition'', which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems.
+For example, the descriptor for ``level of competition,'' which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems.
 We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-abbas2019challenge}{}}%
+\leavevmode\hypertarget{ref-abbas2019challenge}{}%
 Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
+\leavevmode\hypertarget{ref-bakker2014job}{}%
 Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
+\leavevmode\hypertarget{ref-bakker2017job}{}%
 Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
+\leavevmode\hypertarget{ref-bakker2013weekly}{}%
 Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
 
-\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
+\leavevmode\hypertarget{ref-cavanaugh2000empirical}{}%
 Cavanaugh, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-chen2021daily}{}}%
+\leavevmode\hypertarget{ref-chen2021daily}{}%
 Chen, H., Wang, H., Yuan, M., \& Xu, S. (2021). Daily challenge/hindrance demands and cognitive wellbeing: A multilevel moderated mediation model. \emph{Frontiers in Psychology}, \emph{12}, 616002.
 
-\leavevmode\vadjust pre{\hypertarget{ref-crawford2010linking}{}}%
+\leavevmode\hypertarget{ref-crawford2010linking}{}%
 Crawford, E.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
+\leavevmode\hypertarget{ref-gerich2017relevance}{}%
 Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
 
-\leavevmode\vadjust pre{\hypertarget{ref-horan2020review}{}}%
+\leavevmode\hypertarget{ref-horan2020review}{}%
 Horan, K.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-kim2020thriving}{}}%
+\leavevmode\hypertarget{ref-kim2020thriving}{}%
 Kim, M., \& Beehr, T.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
+\leavevmode\hypertarget{ref-lazarus1984stress}{}%
 Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
 
-\leavevmode\vadjust pre{\hypertarget{ref-lepine2005meta}{}}%
+\leavevmode\hypertarget{ref-lepine2005meta}{}%
 LePine, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lepine2022challenge}{}}%
+\leavevmode\hypertarget{ref-lepine2022challenge}{}%
 LePine, M. A. (2022). The challenge-hindrance stressor framework: An integrative conceptual review and path forward. \emph{Group \& Organization Management}, \emph{47}(2), 223--254.
 
-\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
+\leavevmode\hypertarget{ref-peterson2001understanding}{}%
 Peterson, N.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-rodell2009can}{}}%
+\leavevmode\hypertarget{ref-rodell2009can}{}%
 Rodell, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-rosen2020challenges}{}}%
+\leavevmode\hypertarget{ref-rosen2020challenges}{}%
 Rosen, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-searle2015merits}{}}%
+\leavevmode\hypertarget{ref-searle2015merits}{}%
 Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.
 
-\leavevmode\vadjust pre{\hypertarget{ref-selye1936syndrome}{}}%
+\leavevmode\hypertarget{ref-selye1936syndrome}{}%
 Selye, H. (1936). A syndrome produced by diverse nocuous agents. \emph{Nature}, \emph{138}(3479), 32--32.
 
-\leavevmode\vadjust pre{\hypertarget{ref-webster2010toward}{}}%
+\leavevmode\hypertarget{ref-webster2010toward}{}%
 Webster, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
+\leavevmode\hypertarget{ref-webster2011extending}{}%
 Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-careless}{}}%
+\leavevmode\hypertarget{ref-R-careless}{}%
 Yentes, R. D., \& Wilhelm, F. (2021). \emph{Careless: Procedures for computing indices of careless responding}.

### 2023-01-28 Submission.Rmd
Updated Anovas and discussion

@@
 
+```{r ANOVAs}
+
+library(tidyr)
+
+foranova <- data
+foranova$subject <- 1:nrow(foranova)
+
+anova1 <- gather(foranova,type,score,resources_workpressure:hindrance_autonomy, factor_key=TRUE)
+
+## now need to isolate rows with targeted characteristics
+
+overwork <- anova1[ which(anova1$type=='resources_phyworkload_wkover' | anova1$type=='challenge_phyworkload_wkover' | anova1$type=='hindrance_phyworkload_wkover'), ]
+
+rstatix::anova_test(data=overwork,dv=score,wid=subject,within=type)
+
+## pairwise_t_test( value~time,paired=TRUE, p.adjust.method = "bonferroni" )
+
+# check <- overwork[,c(406:407)]
+# psych::describe.by(check, group=check$type)
+
+```
+
 \newpage
@@
 # Discussion
+NOTE: Add a table of the items (probably the full list and those we included in challenge, hindrance specifically). Could also have a column showing which items were used for Figure 4 categories. 
+Summary
+The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using a sample of items from O*Net.
+The findings broadly revealed that there was relatively more consistency in ratings resources and challenges characteristics, and far more variability in job characteristics rated as hindrance stressors.
+This finding lends additional evidence to Horan et al.’s (2020) conclusion that “...stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p.
+3).
+The research questions regarding the match between literature-implicated demand and resource categories and empirical ratings aligns with the consistency/variability we observed in H1.
+Interestingly, we consistently observed that job characteristics rated as resources were also rated highly as challenge stressors, which are not inherently negative in the way that hindrance stressors are.
+Lastly, we also found support for the prediction that job characteristics are not uniquely categorized as a resource or demand, but rather, some job  characteristics are rated highly as both a resource and a demand.
+Practical Implications
+The reality that there is more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging.
+These findings provide comforting support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees’ performance.
+Somewhat surprisingly, hindrances are rated more variably.
+As such, one important implication is that of frequent communication with employees regarding their perceptions of characteristics that limit their performance.
+ADD MORE
+Limitations and Future Directions
+•	Captured only a small number of job characteristics
+•	Part of that means we captured minimal “social” resources or interactions with one’s supervisor
+•	Should expand on the kinds of resources employees experience, as well as stressors
+•	Definition of resource, challenge, hindrance – question of distinction between resource and challenge (think about this one a little bit)
+
+Conclusion
+In sum, this endeavor explored the job-demands-resources literature from a unique lens, showing that there are far more individual differences in how employees perceive demands and resources than much of our current research suggests.
+While resources and challenges are more similarly experienced, hindrance demands show a wide amount of variability.
 

### 2023-01-31 Submission.tex
tuesday edits

--- 2023-01-28 Submission.tex
@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Job Demands-Resources model components through the lens of O*NET classifications},
-  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{248,248,248}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 \usepackage{graphicx}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Job Demands-Resources model components through the lens of O*NET classifications},
+  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 
-Lastly, we propose three research that explicitly address a topic hinted at in the literature review above.
+Lastly, we propose three research questions that explicitly address a topic discussed above.
 Although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, there remains variability in these appraisals (M.
@@
 LePine (2022), in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal.
-We explore whether literature-implicated job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory (Bakker \& Demerouti, 2017)and challenge-hindrance stressor framework (Cavanaugh et al., 2000).
+We explore whether literature-implicated job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory (Bakker \& Demerouti, 2017) and challenge-hindrance stressor framework (Cavanaugh et al., 2000).
 
@@
 \begin{quote}
-\emph{Research Question 2}: Are literature-implicated challenges consistently rated as job challenges?
-\end{quote}
-
-\begin{quote}
-\emph{Research Question 3}: Are literature-implicated hiderances consistently rated as job hindrances?
+\emph{Research Question 2}: Are literature-implicated demands consistently rated as job demands?
 \end{quote}
@@
 
-Of the 785 Prolific panel individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021).
+Of the 785 individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021).
 Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current sample.
@@
 
-Our survey was informed by 98 statements taken from job characteristic descriptors located within O*Net's classification of ``work activities'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'' groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
-
-The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task.
-For example, the descriptor for ``level of competition'', which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems.
-We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
-It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.
-
-The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
-
 We used 98 statements taken from O*NET \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context classifications}.
@@
 For example, the statement ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{No responsibility} to \emph{Very high responsibility}, while the statement, ``How often do you use electronic mail in this job?'' has options ranging from \emph{Never} to \emph{Every day}.
+The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task.
+For example, the descriptor for ``level of competition'', which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems.
+We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
+It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.
+
 We retained the essence of each O*NET descriptor to capture characteristics of relevance for each respondent.
@@
 
+The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
+
 \hypertarget{results}{%
 \section{Results}\label{results}}
-
-Outline:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
-\end{enumerate}
-
-\begin{quote}
-Done - Figure \ref{fig:overallhist}
-\end{quote}
-
-\begin{quote}
-NOT DONE: Combine current graphs 2 \(\rightarrow\) 8 into only 2 graphs (put resources, challenges, and demands on same graph; Kulas do this)
-\end{quote}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{1}
-\tightlist
-\item
-  Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
-\end{enumerate}
-
-\begin{quote}
-Done (at O*Net dimension level) - Table \ref{tab:cortab}.
-\end{quote}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{2}
-\item
-  \emph{Research Question 1}: Are literature-implicated resources consistently rated as job resources?
-\item
-  \emph{Research Question 2}: Are literature-implicated challenges consistently rated as job challenges?
-\item
-  \emph{Research Question 3}: Are literature-implicated hindrances consistently rated as job hindrances?
-\end{enumerate}
-
-\begin{quote}
-Alicia can you present ``what this means'' and what is being presented in Figure \ref{fig:scalelevelgraphs} more clearly - also possibly add ANOVAs
-\end{quote}
 
@@
 
+The first prediction asks whether job characteristics differ in variability/stability regarding
+subjective worker perception as a demand or resource.
 Figure \ref{fig:overallhist} presents standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand.
@@
 
-Figure \ref{fig:combinegraphs} presents resources, challenges, and hindrances that are \emph{largely agreed on} as indexed by (relatively) low standard deviations.\footnote{There were a few characteristics with standard deviations of ``zero'' but these were excluded from presenation as they were likely representing only one person (\emph{n}'s should also go on these graphs if they're retained - Alicia's idea 12/2 was to use initial ratings as indicators of counts).} There are only 8 characteristics presented per perceived category because of limited space.
+Figure \ref{fig:combinegraphs} presents resources, challenges, and hindrances that are \emph{largely agreed on} as indexed by (relatively) low standard deviations.\footnote{There were a few characteristics with standard deviations of ``zero'' but these were excluded from presentation as they were likely representing only one person (\emph{n}'s should also go on these graphs if they're retained - Alicia's idea 12/2 was to use initial ratings as indicators of counts).} There are only 8 characteristics presented per perceived category because of limited space.
 All sortable ratings are available in the online resources.
@@
 Figure \ref{fig:combinegraphs2} presents the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations (these are the 8 characteristics with the greatest variability in rating).
+In sum, these results provide some support for H1, particularly for hindrances, which are consistently viewed as ``different''.
 
@@
 \subsection{Correlations}\label{correlations}}
+
+ADD THIS!
 
@@
 
+Figure 4 highs the average characteristic rating grouped by the literature implicated categories shown on the right.
+These categories are frequently presented in descriptions of the JD-R model and theory (cite).
+To answer these research questions, authors categorized items into the categories listed in the literature.
+For example, autonomy is frequently described as a resource.
+An O*Net item in the ``autonomy'' category is ``How much decision making freedom, without supervision, does your job offer?''.
+Means for respondent-rated resources, challenges, and hindrances were then computed to explore whether literature-implicated resources and demands were consistently rated as such.
+The left side of Figure 8 shows literature-derived demands (e.g., work pressure).
+We do not see a clear pattern of high ratings as hindrances for these demands.
+In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much more variability in how employees rated what should objectively be ``hindrances'' at work.
+However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings.
+Here, the white bars representing resources are consistently higher.
+ADD ANOVAS HERE - one way repeated measures for each category (total of 10 analyses).
+describe pattern.
+In sum, these results provide \_\_\_ support for RQ 1 and 2.
+
+challenges
+
 see Figure \ref{fig:scalelevelgraphs}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{library}\NormalTok{(tidyr)}
+
+\NormalTok{foranova }\OtherTok{\textless{}{-}}\NormalTok{ data}
+\NormalTok{foranova}\SpecialCharTok{$}\NormalTok{subject }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\FunctionTok{nrow}\NormalTok{(foranova) }
+
+\NormalTok{anova1 }\OtherTok{\textless{}{-}} \FunctionTok{gather}\NormalTok{(foranova,type,score,resources\_workpressure}\SpecialCharTok{:}\NormalTok{hindrance\_autonomy, }\AttributeTok{factor\_key=}\ConstantTok{TRUE}\NormalTok{)}
+
+\DocumentationTok{\#\# now need to isolate rows with targeted characteristics}
+
+\NormalTok{overwork }\OtherTok{\textless{}{-}}\NormalTok{ anova1[ }\FunctionTok{which}\NormalTok{(anova1}\SpecialCharTok{$}\NormalTok{type}\SpecialCharTok{==}\StringTok{\textquotesingle{}resources\_phyworkload\_wkover\textquotesingle{}} \SpecialCharTok{|}\NormalTok{ anova1}\SpecialCharTok{$}\NormalTok{type}\SpecialCharTok{==}\StringTok{\textquotesingle{}challenge\_phyworkload\_wkover\textquotesingle{}} \SpecialCharTok{|}\NormalTok{ anova1}\SpecialCharTok{$}\NormalTok{type}\SpecialCharTok{==}\StringTok{\textquotesingle{}hindrance\_phyworkload\_wkover\textquotesingle{}}\NormalTok{), ]}
+
+\NormalTok{rstatix}\SpecialCharTok{::}\FunctionTok{anova\_test}\NormalTok{(}\AttributeTok{data=}\NormalTok{overwork,}\AttributeTok{dv=}\NormalTok{score,}\AttributeTok{wid=}\NormalTok{subject,}\AttributeTok{within=}\NormalTok{type) }
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## ANOVA Table (type III tests)
+## 
+## $ANOVA
+##   Effect DFn  DFd      F        p p<.05   ges
+## 1   type   2 1134 17.709 2.67e-08     * 0.017
+## 
+## $`Mauchly's Test for Sphericity`
+##   Effect     W        p p<.05
+## 1   type 0.694 1.29e-45     *
+## 
+## $`Sphericity Corrections`
+##   Effect   GGe       DF[GG]    p[GG] p[GG]<.05   HFe      DF[HF]    p[HF]
+## 1   type 0.766 1.53, 868.32 7.09e-07         * 0.767 1.53, 870.2 6.93e-07
+##   p[HF]<.05
+## 1         *
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{trying }\OtherTok{\textless{}{-}} \FunctionTok{aov}\NormalTok{(}\AttributeTok{formula =}\NormalTok{ score }\SpecialCharTok{\textasciitilde{}}\NormalTok{ type }\SpecialCharTok{+} \FunctionTok{Error}\NormalTok{(subject}\SpecialCharTok{/}\NormalTok{type), }\AttributeTok{data=}\NormalTok{overwork)}
+\FunctionTok{summary}\NormalTok{(trying)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## 
+## Error: subject
+##           Df Sum Sq Mean Sq F value Pr(>F)
+## Residuals  1  8.266   8.266               
+## 
+## Error: subject:type
+##      Df Sum Sq Mean Sq
+## type  2  15.04   7.519
+## 
+## Error: Within
+##             Df Sum Sq Mean Sq F value  Pr(>F)   
+## type         2    9.2   4.586   5.989 0.00256 **
+## Residuals 1698 1300.2   0.766                   
+## ---
+## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\DocumentationTok{\#\# pairwise\_t\_test( value\textasciitilde{}time,paired=TRUE, p.adjust.method = "bonferroni" ) }
+
+\CommentTok{\# check \textless{}{-} overwork[,c(406:407)]}
+\CommentTok{\# psych::describe.by(check, group=check$type)}
+\end{Highlighting}
+\end{Shaded}
 
@@
 \section{Discussion}\label{discussion}}
+
+NOTE: Add a table of the items (probably the full list and those we included in challenge, hindrance specifically). Could also have a column showing which items were used for Figure 4 categories.
+Summary
+The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using a sample of items from O*Net.
+The findings broadly revealed that there was relatively more consistency in ratings resources and challenges characteristics, and far more variability in job characteristics rated as hindrance stressors.
+This finding lends additional evidence to Horan et al.'s (2020) conclusion that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3).
+The research questions regarding the match between literature-implicated demand and resource categories and empirical ratings aligns with the consistency/variability we observed in H1.
+Interestingly, we consistently observed that job characteristics rated as resources were also rated highly as challenge stressors, which are not inherently negative in the way that hindrance stressors are.
+Lastly, we also found support for the prediction that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
+Practical Implications
+The reality that there is more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging.
+These findings provide comforting support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees' performance.
+Somewhat surprisingly, hindrances are rated more variably.
+As such, one important implication is that of frequent communication with employees regarding their perceptions of characteristics that limit their performance.
+ADD MORE
+Limitations and Future Directions
+• Captured only a small number of job characteristics
+• Part of that means we captured minimal ``social'' resources or interactions with one's supervisor
+• Should expand on the kinds of resources employees experience, as well as stressors
+• Definition of resource, challenge, hindrance -- question of distinction between resource and challenge (think about this one a little bit)
+
+Conclusion
+In sum, this endeavor explored the job-demands-resources literature from a unique lens, showing that there are far more individual differences in how employees perceive demands and resources than much of our current research suggests.
+While resources and challenges are more similarly experienced, hindrance demands show a wide amount of variability.
 

### 2023-02-04 Submission.Rmd
tuesday edits
small coffee shop edits - still verifying ANOVAs

@@
 ```{r setup, include = FALSE}
+
 library("papaja")
-r_refs("r-references.bib")
+
 ```
@@
 ```{r analysis-preferences}
+
 # Seed for random number generation
@@
 knitr::opts_chunk$set(cache.extra = knitr::rand_seed, echo=FALSE, warning=FALSE, message=FALSE)
+
 ```
@@
 
+## trying to replicate - doesn't work 1/31/23
+
+trying <- aov(formula = score ~ type + Error(subject/type), data=overwork)
+summary(trying)
+
+##write.csv(overwork, "checkingANOVAs.csv")
+
 ## pairwise_t_test( value~time,paired=TRUE, p.adjust.method = "bonferroni" )
@@
 # Discussion
+
 NOTE: Add a table of the items (probably the full list and those we included in challenge, hindrance specifically). Could also have a column showing which items were used for Figure 4 categories.
-Summary
+
+## Summary
+
 The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using a sample of items from O*Net.
@@
 Lastly, we also found support for the prediction that job characteristics are not uniquely categorized as a resource or demand, but rather, some job  characteristics are rated highly as both a resource and a demand.
-Practical Implications
+
+## Practical Implications
+
 The reality that there is more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging.
@@
 ADD MORE
-Limitations and Future Directions
-•	Captured only a small number of job characteristics
-•	Part of that means we captured minimal “social” resources or interactions with one’s supervisor
-•	Should expand on the kinds of resources employees experience, as well as stressors
-•	Definition of resource, challenge, hindrance – question of distinction between resource and challenge (think about this one a little bit)
 
-Conclusion
+## Limitations and Future Directions
+
++	Captured only a small number of job characteristics
++	Part of that means we captured minimal “social” resources or interactions with one’s supervisor
++	Should expand on the kinds of resources employees experience, as well as stressors
++	Definition of resource, challenge, hindrance – question of distinction between resource and challenge (think about this one a little bit)
+
+## Conclusion
+
 In sum, this endeavor explored the job-demands-resources literature from a unique lens, showing that there are far more individual differences in how employees perceive demands and resources than much of our current research suggests.
@@
 
+```{r}
+
+r_refs("r-references.bib")
+
+```
+
 \newpage

### 2023-02-04 Submission.tex
small coffee shop edits - still verifying ANOVAs

@@
 \usepackage{xcolor}
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{248,248,248}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{#1}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Job Demands-Resources model components through the lens of O*NET classifications},
+  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{library}\NormalTok{(tidyr)}
-
-\NormalTok{foranova }\OtherTok{\textless{}{-}}\NormalTok{ data}
-\NormalTok{foranova}\SpecialCharTok{$}\NormalTok{subject }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\FunctionTok{nrow}\NormalTok{(foranova) }
-
-\NormalTok{anova1 }\OtherTok{\textless{}{-}} \FunctionTok{gather}\NormalTok{(foranova,type,score,resources\_workpressure}\SpecialCharTok{:}\NormalTok{hindrance\_autonomy, }\AttributeTok{factor\_key=}\ConstantTok{TRUE}\NormalTok{)}
-
-\DocumentationTok{\#\# now need to isolate rows with targeted characteristics}
-
-\NormalTok{overwork }\OtherTok{\textless{}{-}}\NormalTok{ anova1[ }\FunctionTok{which}\NormalTok{(anova1}\SpecialCharTok{$}\NormalTok{type}\SpecialCharTok{==}\StringTok{\textquotesingle{}resources\_phyworkload\_wkover\textquotesingle{}} \SpecialCharTok{|}\NormalTok{ anova1}\SpecialCharTok{$}\NormalTok{type}\SpecialCharTok{==}\StringTok{\textquotesingle{}challenge\_phyworkload\_wkover\textquotesingle{}} \SpecialCharTok{|}\NormalTok{ anova1}\SpecialCharTok{$}\NormalTok{type}\SpecialCharTok{==}\StringTok{\textquotesingle{}hindrance\_phyworkload\_wkover\textquotesingle{}}\NormalTok{), ]}
-
-\NormalTok{rstatix}\SpecialCharTok{::}\FunctionTok{anova\_test}\NormalTok{(}\AttributeTok{data=}\NormalTok{overwork,}\AttributeTok{dv=}\NormalTok{score,}\AttributeTok{wid=}\NormalTok{subject,}\AttributeTok{within=}\NormalTok{type) }
-\end{Highlighting}
-\end{Shaded}
-
 \begin{verbatim}
@@
 \end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{trying }\OtherTok{\textless{}{-}} \FunctionTok{aov}\NormalTok{(}\AttributeTok{formula =}\NormalTok{ score }\SpecialCharTok{\textasciitilde{}}\NormalTok{ type }\SpecialCharTok{+} \FunctionTok{Error}\NormalTok{(subject}\SpecialCharTok{/}\NormalTok{type), }\AttributeTok{data=}\NormalTok{overwork)}
-\FunctionTok{summary}\NormalTok{(trying)}
-\end{Highlighting}
-\end{Shaded}
 
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\DocumentationTok{\#\# pairwise\_t\_test( value\textasciitilde{}time,paired=TRUE, p.adjust.method = "bonferroni" ) }
-
-\CommentTok{\# check \textless{}{-} overwork[,c(406:407)]}
-\CommentTok{\# psych::describe.by(check, group=check$type)}
-\end{Highlighting}
-\end{Shaded}
-
 \newpage
@@
 NOTE: Add a table of the items (probably the full list and those we included in challenge, hindrance specifically). Could also have a column showing which items were used for Figure 4 categories.
-Summary
+
+\hypertarget{summary}{%
+\subsection{Summary}\label{summary}}
+
 The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using a sample of items from O*Net.
@@
 Lastly, we also found support for the prediction that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
-Practical Implications
+
+\hypertarget{practical-implications}{%
+\subsection{Practical Implications}\label{practical-implications}}
+
 The reality that there is more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging.
@@
 ADD MORE
-Limitations and Future Directions
-• Captured only a small number of job characteristics
-• Part of that means we captured minimal ``social'' resources or interactions with one's supervisor
-• Should expand on the kinds of resources employees experience, as well as stressors
-• Definition of resource, challenge, hindrance -- question of distinction between resource and challenge (think about this one a little bit)
 
-Conclusion
+\hypertarget{limitations-and-future-directions}{%
+\subsection{Limitations and Future Directions}\label{limitations-and-future-directions}}
+
+\begin{itemize}
+\tightlist
+\item
+  Captured only a small number of job characteristics
+\item
+  Part of that means we captured minimal ``social'' resources or interactions with one's supervisor
+\item
+  Should expand on the kinds of resources employees experience, as well as stressors
+\item
+  Definition of resource, challenge, hindrance -- question of distinction between resource and challenge (think about this one a little bit)
+\end{itemize}
+
+\hypertarget{conclusion}{%
+\subsection{Conclusion}\label{conclusion}}
+
 In sum, this endeavor explored the job-demands-resources literature from a unique lens, showing that there are far more individual differences in how employees perceive demands and resources than much of our current research suggests.

### 2023-02-04 Submission.Rmd
ANOVA results added to body of paper (prior to Discussion section)

@@
 
-ADD THIS!
+Table \@ref(tab:cortab) highlights hypothesis 2.
+A large number of correlations are moderate.
+Challenge and hindrance demands are smaller in relationship but mostly negative.
+Challenge and resource are typically large.
+Only some are small (for example information input and physical challenges).
+For the most part there are strong associations between challenges and resources.
 
@@
 
-rstatix::anova_test(data=overwork,dv=score,wid=subject,within=type)
+phyenvir <- anova1[ which(anova1$type=='resources_phyenvironment' | anova1$type=='challenge_phyenvironment' | anova1$type=='hindrance_phyenvironment'), ]
 
-## trying to replicate - doesn't work 1/31/23
+timepress <- anova1[ which(anova1$type=='resources_timepressure' | anova1$type=='challenge_timepressure' | anova1$type=='hindrance_timepressure'), ]
 
-trying <- aov(formula = score ~ type + Error(subject/type), data=overwork)
-summary(trying)
+emodemand <- anova1[ which(anova1$type=='resources_emotionaldemands' | anova1$type=='challenge_emotionaldemands' | anova1$type=='hindrance_emotionaldemands'), ]
+
+recipcon <- anova1[ which(anova1$type=='resources_recipientcontact' | anova1$type=='challenge_recipientcontact' | anova1$type=='hindrance_recipientcontact'), ]
+
+workpress <- anova1[ which(anova1$type=='resources_workpressure' | anova1$type=='challenge_workpressure' | anova1$type=='hindrance_workpressure'), ]
+
+report1 <- rstatix::anova_test(data=overwork,dv=score,wid=subject,within=type, effect.size="pes") 
+report2 <- rstatix::anova_test(data=phyenvir,dv=score,wid=subject,within=type, effect.size="pes") 
+report3 <- rstatix::anova_test(data=timepress,dv=score,wid=subject,within=type, effect.size="pes") 
+report4 <- rstatix::anova_test(data=emodemand,dv=score,wid=subject,within=type, effect.size="pes") 
+report5 <- rstatix::anova_test(data=recipcon,dv=score,wid=subject,within=type, effect.size="pes") 
+report6 <- rstatix::anova_test(data=workpress,dv=score,wid=subject,within=type, effect.size="pes")
 
@@
 
-## pairwise_t_test( value~time,paired=TRUE, p.adjust.method = "bonferroni" )
+```
 
-# check <- overwork[,c(406:407)]
-# psych::describe.by(check, group=check$type)
-
-```
+The effect for `Overwork` was `r report1$ANOVA$F`, partial eta squared was `r report1$ANOVA$pes`
+The effect for `Physical Environment` was `r report2$ANOVA$F`, partial eta squared was `r report2$ANOVA$pes`
+The effect for `Time Pressure` was `r report3$ANOVA$F`, partial eta squared was `r report3$ANOVA$pes`
+The effect for `Emotional Demands` was `r report4$ANOVA$F`, partial eta squared was `r report4$ANOVA$pes`
+The effect for `Recipient Contact` was `r report5$ANOVA$F`, partial eta squared was `r report5$ANOVA$pes`
+The effect for `Work Pressure` was `r report6$ANOVA$F`, partial eta squared was `r report6$ANOVA$pes`
 

### 2023-02-04 Submission.tex
ANOVA results added to body of paper (prior to Discussion section)

@@
 
-ADD THIS!
+Table \ref{tab:cortab} highlights hypothesis 2.
+A large number of correlations are moderate.
+Challenge and hindrance demands are smaller in relationship but mostly negative.
+Challenge and resource are typically large.
+Only some are small (for example information input and physical challenges).
+For the most part there are strong associations between challenges and resources.
 
@@
 
-\begin{verbatim}
-## ANOVA Table (type III tests)
-## 
-## $ANOVA
-##   Effect DFn  DFd      F        p p<.05   ges
-## 1   type   2 1134 17.709 2.67e-08     * 0.017
-## 
-## $`Mauchly's Test for Sphericity`
-##   Effect     W        p p<.05
-## 1   type 0.694 1.29e-45     *
-## 
-## $`Sphericity Corrections`
-##   Effect   GGe       DF[GG]    p[GG] p[GG]<.05   HFe      DF[HF]    p[HF]
-## 1   type 0.766 1.53, 868.32 7.09e-07         * 0.767 1.53, 870.2 6.93e-07
-##   p[HF]<.05
-## 1         *
-\end{verbatim}
-
-\begin{verbatim}
-## 
-## Error: subject
-##           Df Sum Sq Mean Sq F value Pr(>F)
-## Residuals  1  8.266   8.266               
-## 
-## Error: subject:type
-##      Df Sum Sq Mean Sq
-## type  2  15.04   7.519
-## 
-## Error: Within
-##             Df Sum Sq Mean Sq F value  Pr(>F)   
-## type         2    9.2   4.586   5.989 0.00256 **
-## Residuals 1698 1300.2   0.766                   
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-\end{verbatim}
+The effect for \texttt{Overwork} was 17.71, partial eta squared was 0.03
+The effect for \texttt{Physical\ Environment} was 112.97, partial eta squared was 0.17
+The effect for \texttt{Time\ Pressure} was 82.22, partial eta squared was 0.13
+The effect for \texttt{Emotional\ Demands} was 393.43, partial eta squared was 0.42
+The effect for \texttt{Recipient\ Contact} was 1,031.73, partial eta squared was 0.65
+The effect for \texttt{Work\ Pressure} was 718.12, partial eta squared was 0.56
 

### 2023-02-04 Submission.Rmd
updated paper

@@
 Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time [e.g., @searle2015merits].
-THE TRANSITION NEEDED HERE COULD ADDRESS RENATA'S RECOMMENDATION TO TIE THIS LITERATURE BACK INTO THE JOB-DEMANDS RESOURCES MODEL.
 
@@
 
+NOTE: Add a table of the items (probably the full list and those we included in challenge, hindrance specifically). Could also have a column showing which items were used for Figure 4 categories.
+
 # Discussion
 
-NOTE: Add a table of the items (probably the full list and those we included in challenge, hindrance specifically). Could also have a column showing which items were used for Figure 4 categories.
-
-## Summary
-
-The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using a sample of items from O*Net.
-The findings broadly revealed that there was relatively more consistency in ratings resources and challenges characteristics, and far more variability in job characteristics rated as hindrance stressors.
+The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands (both challenge and hindrance), and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using a sample of items from O*Net.
+The findings broadly revealed that there was relatively more consistency in ratings of resources and challenges characteristics, and far more variability in job characteristics rated as hindrance stressors.
 This finding lends additional evidence to Horan et al.’s (2020) conclusion that “...stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p.
@@
 Interestingly, we consistently observed that job characteristics rated as resources were also rated highly as challenge stressors, which are not inherently negative in the way that hindrance stressors are.
-Lastly, we also found support for the prediction that job characteristics are not uniquely categorized as a resource or demand, but rather, some job  characteristics are rated highly as both a resource and a demand.
+Lastly, we also found support for the prediction that job characteristics are not uniquely categorized as a resource or demand, but rather, some job  characteristics are rated highly as both a resource and a demand (H2).
 
-## Practical Implications
+# Implications
 
+Theoretically, these findings support growing body of literature suggesting that perceptions of resources and demands, broadly, are not universal.
+There is individual difference in how employees experience the characteristics of their jobs.
+Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a “resource” or “demand”.
+These results have implications for managers as well.
 The reality that there is more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging.
@@
 As such, one important implication is that of frequent communication with employees regarding their perceptions of characteristics that limit their performance.
-ADD MORE
+@lepine2005meta and @podsakoff2007differential encourage organizations to incorporate strain-reducing activities like train and support to offset the negative effects of challenging job demands.
 
-## Limitations and Future Directions
+# Limitations and Future Directions
 
-+	Captured only a small number of job characteristics
-+	Part of that means we captured minimal “social” resources or interactions with one’s supervisor
-+	Should expand on the kinds of resources employees experience, as well as stressors
-+	Definition of resource, challenge, hindrance – question of distinction between resource and challenge (think about this one a little bit)
+As with all individual studies, this project was limited in scope, and as such, there are a number of avenues for future study worth exploring here.
+First, we captured only a small number of job characteristics given the nature of our research questions.
+Because we asked up to four questions about each characteristics, we were limited in the number of job characteristics we could reasonably include.
+Related to that, we intentionally worked within the O*Net database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources/demands.
+For example, we included minimal “social” resources or interactions with one’s supervisor, which the literature would suggest are important resources.
+Future study should explore this aspect of work.
+We also used the exact definitions of resource, challenge, and hindrance.
+It is possible that respondents did not distinguish between the challenge and resource definition as cleanly as we intended and so future research should explore this question differently.
+It would also be interesting to consider outcomes associated with subjective ratings.
+Lastly, there may be some practical utility to pursue training interventions aimed at *how* characteristics are appraised.
+Perhaps the clinical literature may be informative - for example, within cognitive behavioral therapeutic applications, the way in which situations are appraised can be a mechanism to help battle affective disorders such as depression.[^check] Given the current findings, where the same characteristic may be viewed similarly as both a demand and resource, it is possible that framing interventions may ameliorate negative outcomes of demands such as, for example, stress or strain.
 
-## Conclusion
+# Conclusion
 
@@
 While resources and challenges are more similarly experienced, hindrance demands show a wide amount of variability.
-
-## Future directions
-
-So, what can be done about the findings that people experience both?
-@lepine2005meta and @podsakoff2007differential encourage organizations to incorporate strain-reducing activities like train and support to offset the negative effects of challenging job demands.
-
-There may be some practical utility to pursue training interventions aimed at *how* characteristics are appraised.
-Perhaps the clinical literature may be informative - for example, within cognitive behavioral therapeutic applications, the way in which situations are appraised can be a mechanism to help battle affective disorders such as depression.[^check] Given the current findings, where the same characteristic may be viewed similarly as both a demand and resource, it is possible that framing interventions may ameliorate negative outcomes of demands such as, for example, stress or strain.
-
-[^check]: Check on this - this is just speculative place-holding from 12/2 Hudson coffee discussion
 

### 2023-02-04 Submission.tex
updated paper

@@
 Figure \ref{fig:combinegraphs2} presents the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations (these are the 8 characteristics with the greatest variability in rating).
-In sum, these results provide some support for H1, particularly for hindrances, which are consistently viewed as ``different''.
+In sum, these results provide some support for H1, particularly for hindrances, which are consistently viewed as ``different.''
 
@@
 For example, autonomy is frequently described as a resource.
-An O*Net item in the ``autonomy'' category is ``How much decision making freedom, without supervision, does your job offer?''.
-Means for respondent-rated resources, challenges, and hindrances were then computed to explore whether literature-implicated resources and demands were consistently rated as such.
+An O*Net item in the ``autonomy'' category is ``How much decision making freedom, without supervision, does your job offer?'' Means for respondent-rated resources, challenges, and hindrances were then computed to explore whether literature-implicated resources and demands were consistently rated as such.
 The left side of Figure 8 shows literature-derived demands (e.g., work pressure).
@@
 
+NOTE: Add a table of the items (probably the full list and those we included in challenge, hindrance specifically). Could also have a column showing which items were used for Figure 4 categories.
+
 \hypertarget{discussion}{%
@@
 
-NOTE: Add a table of the items (probably the full list and those we included in challenge, hindrance specifically). Could also have a column showing which items were used for Figure 4 categories.
-
-\hypertarget{summary}{%
-\subsection{Summary}\label{summary}}
-
-The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using a sample of items from O*Net.
-The findings broadly revealed that there was relatively more consistency in ratings resources and challenges characteristics, and far more variability in job characteristics rated as hindrance stressors.
+The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands (both challenge and hindrance), and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using a sample of items from O*Net.
+The findings broadly revealed that there was relatively more consistency in ratings of resources and challenges characteristics, and far more variability in job characteristics rated as hindrance stressors.
 This finding lends additional evidence to Horan et al.'s (2020) conclusion that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3).
@@
 Interestingly, we consistently observed that job characteristics rated as resources were also rated highly as challenge stressors, which are not inherently negative in the way that hindrance stressors are.
-Lastly, we also found support for the prediction that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
+Lastly, we also found support for the prediction that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand (H2).
 
-\hypertarget{practical-implications}{%
-\subsection{Practical Implications}\label{practical-implications}}
+\hypertarget{implications}{%
+\section{Implications}\label{implications}}
 
+Theoretically, these findings support growing body of literature suggesting that perceptions of resources and demands, broadly, are not universal.
+There is individual difference in how employees experience the characteristics of their jobs.
+Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a ``resource'' or ``demand.''
+These results have implications for managers as well.
 The reality that there is more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging.
@@
 As such, one important implication is that of frequent communication with employees regarding their perceptions of characteristics that limit their performance.
-ADD MORE
-
-\hypertarget{limitations-and-future-directions}{%
-\subsection{Limitations and Future Directions}\label{limitations-and-future-directions}}
-
-\begin{itemize}
-\tightlist
-\item
-  Captured only a small number of job characteristics
-\item
-  Part of that means we captured minimal ``social'' resources or interactions with one's supervisor
-\item
-  Should expand on the kinds of resources employees experience, as well as stressors
-\item
-  Definition of resource, challenge, hindrance -- question of distinction between resource and challenge (think about this one a little bit)
-\end{itemize}
-
-\hypertarget{conclusion}{%
-\subsection{Conclusion}\label{conclusion}}
-
-In sum, this endeavor explored the job-demands-resources literature from a unique lens, showing that there are far more individual differences in how employees perceive demands and resources than much of our current research suggests.
-While resources and challenges are more similarly experienced, hindrance demands show a wide amount of variability.
-
-\hypertarget{future-directions}{%
-\subsection{Future directions}\label{future-directions}}
-
-So, what can be done about the findings that people experience both?
 J.
@@
 
-There may be some practical utility to pursue training interventions aimed at \emph{how} characteristics are appraised.
-Perhaps the clinical literature may be informative - for example, within cognitive behavioral therapeutic applications, the way in which situations are appraised can be a mechanism to help battle affective disorders such as depression.\footnote{Check on this - this is just speculative place-holding from 12/2 Hudson coffee discussion} Given the current findings, where the same characteristic may be viewed similarly as both a demand and resource, it is possible that framing interventions may ameliorate negative outcomes of demands such as, for example, stress or strain.
+\hypertarget{limitations-and-future-directions}{%
+\section{Limitations and Future Directions}\label{limitations-and-future-directions}}
+
+As with all individual studies, this project was limited in scope, and as such, there are a number of avenues for future study worth exploring here.
+First, we captured only a small number of job characteristics given the nature of our research questions.
+Because we asked up to four questions about each characteristics, we were limited in the number of job characteristics we could reasonably include.
+Related to that, we intentionally worked within the O\emph{Net database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources/demands.
+For example, we included minimal ``social'' resources or interactions with one's supervisor, which the literature would suggest are important resources.
+Future study should explore this aspect of work.
+We also used the exact definitions of resource, challenge, and hindrance.
+It is possible that respondents did not distinguish between the challenge and resource definition as cleanly as we intended and so future research should explore this question differently.
+It would also be interesting to consider outcomes associated with subjective ratings.
+Lastly, there may be some practical utility to pursue training interventions aimed at }how* characteristics are appraised.
+Perhaps the clinical literature may be informative - for example, within cognitive behavioral therapeutic applications, the way in which situations are appraised can be a mechanism to help battle affective disorders such as depression.{[}\^{}check{]} Given the current findings, where the same characteristic may be viewed similarly as both a demand and resource, it is possible that framing interventions may ameliorate negative outcomes of demands such as, for example, stress or strain.
+
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
+
+In sum, this endeavor explored the job-demands-resources literature from a unique lens, showing that there are far more individual differences in how employees perceive demands and resources than much of our current research suggests.
+While resources and challenges are more similarly experienced, hindrance demands show a wide amount of variability.
 

### 2023-02-07 Submission.Rmd
Reviewed and edited up to the discussion section. We need to find the table of SDs and link to it as we indicate in the results section. The Excel table of items should also be referenced probably in the materials section.

@@
 ---
-title             : "Job Demands-Resources model components through the lens of O*NET classifications"
+title             : "Job Demands-Resources Model Components through the Lens of O*NET Classifications"
 shorttitle        : "O*NET JD-R"
@@
 abstract: |
-  O\*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource.
-All the results of this current study match the stress-appraisal stuff.
-Next steps: 1) discuss results within stress-appraisal framework [@lazarus1984stress], 2) different literature on challenge and hindrance demands.
-Job Demands Resources theory that says resources and demands are relatively universal is NOT consistent with these findings.
-JDR neglects the other 2 literatures.
-Analytically pull O*Net descriptors that reflect universal demands/resources (e.g., autonomy) and see how much variability there is on those.
-Maybe forget about cross-walk thing.
-May actually want to start with this: https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit#gid=1041061499.[^foot1]
-
-  We want to also group items by O\*NET categories so there's not so many (that makes ANOVAs more viable)
+  We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
+O*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource.
 
@@
 
-Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlight the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance.
-However, much of our existing knowledge of the way this model functions is grounded in the assumption that characteristics are generally considered resources or generally considered demands.
+Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlights the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance among other outcomes.
+However, much of our existing knowledge regarding the way this model functions is grounded in the assumption that job characteristics are generally considered resources or generally considered demands.
 We build on the research of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges].
-We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, which a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
+We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resources) in the workplace, with a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
 Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.
@@
 Cognitively, the perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources) [@bakker2014job].
-Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience depsite the typical apriori assignment of a characteristic as objectively a "demand" or "resource".
+Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience despite the typical apriori assignment of a characteristic as objectively a "demand" or "resource".
 We explore this further below.
@@
 As described in the last paragraph, job context and characteristics are assigned or appraised as demands or resources.
-Although much of our research on job demands in particular is based on apriori classifications of demands [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand.
+Although much of our research on job demands in particular is based on apriori classifications [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand.
 The stress process speaks to how such individual difference in appraisal is possible.
@@
 The cycle of appraisal then continues based on the action to cope with the stressor [@lazarus1984stress].
-Coping is considered a secondary appraisal and is the way that someone chooses to manage a stressor should an event or situation be deemed so.
+Coping is considered a secondary appraisal and is the way that someone chooses to manage a stressor.
 Although not suggested by the names, primary and secondary appraisals can happen simultaneously.
@@
 
-Although there is a tendency to attach a negative connotation to the word “stress”, @selye1936syndrome defined stress as a response to change, which is quite non-specific.
+Although there is a tendency to attach a negative connotation to the word “stress”, @selye1936syndrome defined stress as simple a response to change.
 We return to the employed public figure for this next section.
-It is quite probable that two employees would be called upon to serve as a spokesperson for their organization in a time of need.
-One may appraise the circumstance as an opportunity to positively influence others, while the other may plausibly feel paralyzed by the task.
-In fact, @bakker2017job call attention to different types of demands in their recent review of, and future directions, for work on the job-demands resources theory.
+Consider two employees be called upon to serve as spokespeople for their organization.
+One may appraise the circumstance as an opportunity to positively influence others, while the other may feel daunted by the task.
 
@@
 
-Prior to considering the subsequent empirical work done on this topic, it is of value to explore *why* there is expected to be different outcomes associated with these forms of demands.
+Prior to considering the subsequent empirical work on this topic, it is of value to explore *why* different outcomes are expected with these forms of demands.
 @lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes.
@@
 Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing.
-The other side of the coin is that this energy may be depleted eventually, leading to strain.
+Of note is that this energy may be depleted eventually, leading to strain.
 Hindrance stressors elicit a different process.
@@
 We next consider the empirical evidence on this topic.
-The broadest, and perhaps first question, we should ask is whether people perceive demands as challenges vs.
-hindrances, or whether all demands are under a larger “demands” category.
-Evidence suggests the employees do, in fact, distinguish between challenge and hindrance stressors [e.g., @bakker2013weekly; @gerich2017relevance; @webster2011extending].
-For example, @bakker2013weekly found that perceived work pressure as a hindrance demand, and emotional demands as more of a challenge demand.
+The first question we should ask is whether people distinguish between challenge vs.
+hindrance demands, or whether all demands are under a larger “demands” category.
+Evidence suggests the employees do, in fact, differentiate between challenge and hindrance stressors [e.g., @bakker2013weekly; @gerich2017relevance; @webster2011extending].
+For example, @bakker2013weekly found that work pressure was perceived as a hindrance demand, and emotional demands as more of a challenge demand.
 @webster2011extending approached this question with three common workplace demands: workload, role ambiguity, and role conflict.
-They found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees.
+They found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hindrance demands to different degrees.
+
+Appraisals are associated with different forms of coping, and subsequently, outcomes.
+The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing.
+A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic.
 @kim2020thriving found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing.
 The opposite occurred when a demand was appraised as a hindrance – in those instances, the appraisal had a negative association with motivational resources.
-
-Having evidence that people can make a distinction between challenge and hindrance stressors, the next logical question is whether they do relate differentially to outcomes.
-The challenge-hindrance stressor framework has, in fact, been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing.
-A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic.
-For example, @cavanaugh2000empirical, in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern.
+@cavanaugh2000empirical, in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern.
 @chen2021daily found that daily challenge demands were positively related to cognitive wellbeing and work-family enrichment.
@@
 
-We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point, and a rich collection of them support differential associations across a variety of organizational outcomes.
+We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point, and a rich collection of them support differential associations across a variety of organizational outcomes as well.
 For example, both challenges and hindrances have been shown to positively predict strain [@lepine2005meta; @podsakoff2007differential; @webster2010toward].
@@
 Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time [e.g., @searle2015merits].
-
-## O\*Net Resource
-
-Originally, the Advisory Panel for the Dictionary of Occupational Titles recommended a system that would “…promote the effective education, training, counseling, and employment of the American workforce.
-It should accomplish its purpose by providing a database system that identifies, defines, classifies, and describes occupations in the economy in an accessible and flexible manner” [@advisory1993new, p.
-6].
-The result was the now commonly used O\*NET.
-The Occupational Information Network (O\*NET; onetonline.org) contains a comprehensive description of occupations [@peterson2001understanding].
-This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated.
-In fact, there was a call to work with experienced I/O psychologists over the summer to update the content for the [Industrial and Organizational Psychologist listing on O\*Net](https://www.onetonline.org/link/summary/19-3032.00).
-These data, and the tools provided for free on the website (e.g., Career Exploration Tools, “My Next Move for Veterans”, “My Next Move”, Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
-It is also useful to employers by providing them with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
+TRANSITION NEEDED HERE.
+I DELETED THE ONET PARAGRAPH.
 
@@
 
-Of greatest interest here are statements taken from O\*NET ["activity" and "context" classifications](https://www.O\*NETonline.org/find/descriptor/result/4.A.1.b.3) (e.g., items related to information input, interacting with others, physical work conditions, structural job characteristics).
-One of the first and basic questions is whether or not the categorical examples of "resources" and "demands" described in the Job Demands-Resources Theory [@demerouti2001job], for example, are generally deemed resources or demands as we objectively define them.
-The next logical question surrounds how "universal" such ratings are.
-For instance, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.
+The integration of the literature above results in two primary predictions.
+The first addresses whether employees generally agree on their appraisals of job characteristics as resources or challenge or hindrance demands.
+For instance, although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, others have reported variability in these appraisals [@lepine2022challenge].
+@lepine2022challenge, in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal.
+Thus, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.
 
@@
 
-Lastly, we propose three research questions that explicitly address a topic discussed above.
-Although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, there remains variability in these appraisals [@lepine2022challenge].
-@lepine2022challenge, in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal.
-We explore whether literature-implicated job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory [@bakker2017job] and challenge-hindrance stressor framework [@cavanaugh2000empirical].
+We explore three research questions addressing whether our literature-implicated job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory [@bakker2017job] and challenge-hindrance stressor framework [@cavanaugh2000empirical].
 
@@
 
+The Occupational Information Network (O\*NET; onetonline.org) contains a comprehensive description of occupations [@peterson2001understanding].
+This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated.
 We used 98 statements taken from O\*NET [activity and context classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3).
@@
 # Results
-
-## Standard deviations of perceptions
 
@@
 
-The first prediction asks whether job characteristics differ in variability/stability regarding
-subjective worker perception as a demand or resource.
-Figure \@ref(fig:overallhist) presents standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand.
+The first prediction asks whether job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
+Figure \@ref(fig:overallhist) presents frequency distributions standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand.
 As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's $K^2$ = `r lookie$statistic[[1]]`, *p* = `r lookie$p.value` ).
-
-## Low Variability Demands and Resources
 
@@
 
-## High Variability Demands and Resources
-
 ```{r resourcesdisagree, fig.cap="Characteristics most *dis*similarly viewed as resources (highest standard deviations)."}
@@
 
-## Correlations
-
-Table \@ref(tab:cortab) highlights hypothesis 2.
-A large number of correlations are moderate.
-Challenge and hindrance demands are smaller in relationship but mostly negative.
-Challenge and resource are typically large.
-Only some are small (for example information input and physical challenges).
-For the most part there are strong associations between challenges and resources.
+The second prediction stated that job characteristics would not be uniquely categorized as a resource or demand.
+Table \@ref(tab:cortab) provides the correlations among the O\*Net item groupings by resource, challenge and hindrance demand.
+A large proportion of correlations are moderate.
+Challenge and hindrance demands are smaller in relationship, but mostly negative.
+Challenge and resource are strongly and positively related.
+These results provide support for H2 suggesting that there is overlap in how employees perceive job characteristics.
+Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.
 
@@
 
-Figure 4 highs the average characteristic rating grouped by the literature implicated categories shown on the right.
-These categories are frequently presented in descriptions of the JD-R model and theory (cite).
-To answer these research questions, authors categorized items into the categories listed in the literature.
+In addition to the two predictions, three related research questions were proposed.
+To answer these research questions, authors first categorized items into the categories listed in the JD-R literature.
 For example, autonomy is frequently described as a resource.
-An O*Net item in the “autonomy” category is “How much decision making freedom, without supervision, does your job offer?”.
-Means for respondent-rated resources, challenges, and hindrances were then computed to explore whether literature-implicated resources and demands were consistently rated as such.
-The left side of Figure 8 shows literature-derived demands (e.g., work pressure).
-We do not see a clear pattern of high ratings as hindrances for these demands.
+An O\*Net item in the autonomy category is, “How much decision making freedom, without supervision, does your job offer?”.
+Means for resources, challenges, and hindrances groupings were then computed to explore whether literature-implicated resources and demands were consistently rated as such.
+The left side of Figure 4 shows literature-derived demand categories (e.g., work pressure).
+Here, we do not see a clear pattern of high ratings as hindrances for these demands.
 In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much more variability in how employees rated what should objectively be "hindrances" at work.
 However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings.
-Here, the white bars representing resources are consistently higher.
+The white bars representing resources are consistently higher.
 ADD ANOVAS HERE - one way repeated measures for each category (total of 10 analyses).
@@
 In sum, these results provide ___ support for RQ 1 and 2.
-
-challenges
 

### 2023-02-07 Submission.Rmd
ANOVAs

@@
 
+## added 2/7/23 for online supplement materials
+
+resourcetemp <- sortresource[,c(569:571)]
+challengetemp <- sortchallenge[,c(569:571)]
+hindrancetemp <- sorthindrance[,c(569:571)]
+
+write.csv(resourcetemp, "sortresource.csv")
+write.csv(challengetemp, "sortchallenge.csv")
+write.csv(hindrancetemp, "sorthindrance.csv")
+
 ```
@@
 
+control <- anova1[ which(anova1$type=='resource_jobcontrol' | anova1$type=='challenge_jobcontrol' | anova1$type=='hindrance_jobcontrol'), ]
+
+particip <- anova1[ which(anova1$type=='resource_participation' | anova1$type=='challenge_participation' | anova1$type=='hindrance_participation'), ]
+
+teamcohe <- anova1[ which(anova1$type=='resource_teamcohesion' | anova1$type=='challenge_teamcohesion' | anova1$type=='hindrance_teamcohesion'), ]
+
+autonomy <- anova1[ which(anova1$type=='resource_autonomy' | anova1$type=='challenge_autonomy' | anova1$type=='hindrance_autonomy'), ]
+
+report7 <- rstatix::anova_test(data=control,dv=score,wid=subject,within=type, effect.size="pes") 
+report8 <- rstatix::anova_test(data=particip,dv=score,wid=subject,within=type, effect.size="pes") 
+report9 <- rstatix::anova_test(data=teamcohe,dv=score,wid=subject,within=type, effect.size="pes") 
+report10 <- rstatix::anova_test(data=autonomy,dv=score,wid=subject,within=type, effect.size="pes")
+
 ```
 
-The effect for `Overwork` was `r report1$ANOVA$F`, partial eta squared was `r report1$ANOVA$pes`
-The effect for `Physical Environment` was `r report2$ANOVA$F`, partial eta squared was `r report2$ANOVA$pes`
-The effect for `Time Pressure` was `r report3$ANOVA$F`, partial eta squared was `r report3$ANOVA$pes`
-The effect for `Emotional Demands` was `r report4$ANOVA$F`, partial eta squared was `r report4$ANOVA$pes`
-The effect for `Recipient Contact` was `r report5$ANOVA$F`, partial eta squared was `r report5$ANOVA$pes`
-The effect for `Work Pressure` was `r report6$ANOVA$F`, partial eta squared was `r report6$ANOVA$pes`
+Separate repeated-measures ANOVAs were conducted for each of these comparisons.
+
+## Literature-implicated demands
+
+The effect for `Overwork` was $F_{(`r report1$ANOVA$DFn`, `r report1$ANOVA$DFd`)}$ = `r report1$ANOVA$F`, partial eta squared $(\eta^2)$ was `r report1$ANOVA$pes`.
+The effect for `Physical Environment` was $F_{(`r report2$ANOVA$DFn`, `r report2$ANOVA$DFd`)}$ = `r report2$ANOVA$F` ($\eta^2$ = `r report2$ANOVA$pes`).
+The effect for `Time Pressure` was $F_{(`r report3$ANOVA$DFn`, `r report3$ANOVA$DFd`)}$ = `r report3$ANOVA$F` ($\eta^2$ = `r report3$ANOVA$pes`).
+The effect for `Emotional Demands` was $F_{(`r report4$ANOVA$DFn`, `r report4$ANOVA$DFd`)}$ = `r report4$ANOVA$F` ($\eta^2$ = `r report4$ANOVA$pes`).
+The effect for `Recipient Contact` was $F_{(`r report5$ANOVA$DFn`, `r report5$ANOVA$DFd`)}$ = `r report5$ANOVA$F` ($\eta^2$ = `r report5$ANOVA$pes`).
+The effect for `Work Pressure` was $F_{(`r report6$ANOVA$DFn`, `r report6$ANOVA$DFd`)}$ = `r report6$ANOVA$F` ($\eta^2$ = `r report6$ANOVA$pes`).
+
+## Literature-implicated resources
+
+The effect for `Job Control` was $F_{(`r report7$ANOVA$DFn`, `r report7$ANOVA$DFd`)}$ = `r report7$ANOVA$F` ($\eta^2$ = `r report7$ANOVA$pes`).
+The effect for `Participation` was $F_{(`r report8$ANOVA$DFn`, `r report8$ANOVA$DFd`)}$ = `r report8$ANOVA$F` ($\eta^2$ = `r report8$ANOVA$pes`).
+The effect for `Autonomy` was $F_{(`r report9$ANOVA$DFn`, `r report9$ANOVA$DFd`)}$ = `r report9$ANOVA$F` ($\eta^2$ = `r report9$ANOVA$pes`).
+The effect for `Team Cohesion` was $F_{(`r report10$ANOVA$DFn`, `r report10$ANOVA$DFd`)}$ = `r report10$ANOVA$F` ($\eta^2$ = `r report10$ANOVA$pes`).
 

### 2023-02-07 Submission.tex
ANOVAs

--- 2023-02-04 Submission.tex
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Job Demands-Resources Model Components through the Lens of O*NET Classifications},
+  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
-\title{Job Demands-Resources model components through the lens of O*NET classifications}
+\title{Job Demands-Resources Model Components through the Lens of O*NET Classifications}
 \author{Alicia Stachowski\textsuperscript{1}, John Kulas\textsuperscript{2}, \& Renata Garcia Prieto Palacios Roji\textsuperscript{3}}
@@
 \abstract{%
+We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
 O*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource.
-All the results of this current study match the stress-appraisal stuff.
-Next steps: 1) discuss results within stress-appraisal framework (Lazarus \& Folkman, 1984), 2) different literature on challenge and hindrance demands.
-Job Demands Resources theory that says resources and demands are relatively universal is NOT consistent with these findings.
-JDR neglects the other 2 literatures.
-Analytically pull O*Net descriptors that reflect universal demands/resources (e.g., autonomy) and see how much variability there is on those.
-Maybe forget about cross-walk thing.
-May actually want to start with this: \url{https://docs.google.com/spreadsheets/d/1ck-72dQ_c-Pl4Xba9W0r__OYo0znlEnV/edit\#gid=1041061499}.{[}\^{}foot1{]}
-
-We want to also group items by O*NET categories so there's not so many (that makes ANOVAs more viable)
 }
@@
 
-Research on the job demands-resources model (Demerouti et al., 2001) and later job demands-resources theory (Bakker \& Demerouti, 2017) highlight the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance.
-However, much of our existing knowledge of the way this model functions is grounded in the assumption that characteristics are generally considered resources or generally considered demands.
+Research on the job demands-resources model (Demerouti et al., 2001) and later job demands-resources theory (Bakker \& Demerouti, 2017) highlights the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance among other outcomes.
+However, much of our existing knowledge regarding the way this model functions is grounded in the assumption that job characteristics are generally considered resources or generally considered demands.
 We build on the research of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020).
-We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, which a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
+We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resources) in the workplace, with a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
 Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.
@@
 Cognitively, the perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources) (Bakker \& Demerouti, 2014).
-Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience depsite the typical apriori assignment of a characteristic as objectively a ``demand'' or ``resource''.
+Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience despite the typical apriori assignment of a characteristic as objectively a ``demand'' or ``resource''.
 We explore this further below.
@@
 As described in the last paragraph, job context and characteristics are assigned or appraised as demands or resources.
-Although much of our research on job demands in particular is based on apriori classifications of demands (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand.
+Although much of our research on job demands in particular is based on apriori classifications (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand.
 The stress process speaks to how such individual difference in appraisal is possible.
@@
 The cycle of appraisal then continues based on the action to cope with the stressor (Lazarus \& Folkman, 1984).
-Coping is considered a secondary appraisal and is the way that someone chooses to manage a stressor should an event or situation be deemed so.
+Coping is considered a secondary appraisal and is the way that someone chooses to manage a stressor.
 Although not suggested by the names, primary and secondary appraisals can happen simultaneously.
@@
 
-Although there is a tendency to attach a negative connotation to the word ``stress'', Selye (1936) defined stress as a response to change, which is quite non-specific.
+Although there is a tendency to attach a negative connotation to the word ``stress'', Selye (1936) defined stress as simple a response to change.
 We return to the employed public figure for this next section.
-It is quite probable that two employees would be called upon to serve as a spokesperson for their organization in a time of need.
-One may appraise the circumstance as an opportunity to positively influence others, while the other may plausibly feel paralyzed by the task.
-In fact, Bakker and Demerouti (2017) call attention to different types of demands in their recent review of, and future directions, for work on the job-demands resources theory.
+Consider two employees be called upon to serve as spokespeople for their organization.
+One may appraise the circumstance as an opportunity to positively influence others, while the other may feel daunted by the task.
 
@@
 
-Prior to considering the subsequent empirical work done on this topic, it is of value to explore \emph{why} there is expected to be different outcomes associated with these forms of demands.
+Prior to considering the subsequent empirical work on this topic, it is of value to explore \emph{why} different outcomes are expected with these forms of demands.
 M.
@@
 We next consider the empirical evidence on this topic.
-The broadest, and perhaps first question, we should ask is whether people perceive demands as challenges vs.~hindrances, or whether all demands are under a larger ``demands'' category.
-Evidence suggests the employees do, in fact, distinguish between challenge and hindrance stressors (e.g., Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011).
-For example, Bakker and Sanz-Vergel (2013) found that perceived work pressure as a hindrance demand, and emotional demands as more of a challenge demand.
+The first question we should ask is whether people distinguish between challenge vs.~hindrance demands, or whether all demands are under a larger ``demands'' category.
+Evidence suggests the employees do, in fact, differentiate between challenge and hindrance stressors (e.g., Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011).
+For example, Bakker and Sanz-Vergel (2013) found that work pressure was perceived as a hindrance demand, and emotional demands as more of a challenge demand.
 Webster et al.
 (2011) approached this question with three common workplace demands: workload, role ambiguity, and role conflict.
-They found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees.
+They found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hindrance demands to different degrees.
+
+Appraisals are associated with different forms of coping, and subsequently, outcomes.
+The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing.
+A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic.
 Kim and Beehr (2020) found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing.
 The opposite occurred when a demand was appraised as a hindrance -- in those instances, the appraisal had a negative association with motivational resources.
-
-Having evidence that people can make a distinction between challenge and hindrance stressors, the next logical question is whether they do relate differentially to outcomes.
-The challenge-hindrance stressor framework has, in fact, been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing.
-A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic.
-For example, Cavanaugh et al.
+Cavanaugh et al.
 (2000), in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern.
@@
 
-We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point, and a rich collection of them support differential associations across a variety of organizational outcomes.
+We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point, and a rich collection of them support differential associations across a variety of organizational outcomes as well.
 For example, both challenges and hindrances have been shown to positively predict strain (J.
@@
 Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time (e.g., Searle \& Auton, 2015).
-THE TRANSITION NEEDED HERE COULD ADDRESS RENATA'S RECOMMENDATION TO TIE THIS LITERATURE BACK INTO THE JOB-DEMANDS RESOURCES MODEL.
-
-\hypertarget{onet-resource}{%
-\subsection{O*Net Resource}\label{onet-resource}}
-
-Originally, the Advisory Panel for the Dictionary of Occupational Titles recommended a system that would ``\ldots promote the effective education, training, counseling, and employment of the American workforce.
-It should accomplish its purpose by providing a database system that identifies, defines, classifies, and describes occupations in the economy in an accessible and flexible manner'' (Dictionary of Occupational Titles (US) \& Service, 1993, p.
-6).
-The result was the now commonly used O*NET.
-The Occupational Information Network (O*NET; onetonline.org) contains a comprehensive description of occupations (Peterson et al., 2001).
-This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated.
-In fact, there was a call to work with experienced I/O psychologists over the summer to update the content for the \href{https://www.onetonline.org/link/summary/19-3032.00}{Industrial and Organizational Psychologist listing on O*Net}.
-These data, and the tools provided for free on the website (e.g., Career Exploration Tools, ``My Next Move for Veterans'', ``My Next Move'', Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist potential applicants discover the skills and training they need for the job of their choice.
-It is also useful to employers by providing them with information with which to craft job descriptions and help employees determine what skills are needed for promotion.
+TRANSITION NEEDED HERE.
+I DELETED THE ONET PARAGRAPH.
 
@@
 
-Of greatest interest here are statements taken from O*NET \href{https://www.O*NETonline.org/find/descriptor/result/4.A.1.b.3}{``activity'' and ``context'' classifications} (e.g., items related to information input, interacting with others, physical work conditions, structural job characteristics).
-One of the first and basic questions is whether or not the categorical examples of ``resources'' and ``demands'' described in the Job Demands-Resources Theory (Demerouti et al., 2001), for example, are generally deemed resources or demands as we objectively define them.
-The next logical question surrounds how ``universal'' such ratings are.
-For instance, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.
+The integration of the literature above results in two primary predictions.
+The first addresses whether employees generally agree on their appraisals of job characteristics as resources or challenge or hindrance demands.
+For instance, although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, others have reported variability in these appraisals (M.
+A.
+LePine, 2022).
+M.
+A.
+LePine (2022), in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal.
+Thus, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.
 
@@
 
-Lastly, we propose three research questions that explicitly address a topic discussed above.
-Although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, there remains variability in these appraisals (M.
-A.
-LePine, 2022).
-M.
-A.
-LePine (2022), in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal.
-We explore whether literature-implicated job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory (Bakker \& Demerouti, 2017) and challenge-hindrance stressor framework (Cavanaugh et al., 2000).
+We explore three research questions addressing whether our literature-implicated job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory (Bakker \& Demerouti, 2017) and challenge-hindrance stressor framework (Cavanaugh et al., 2000).
 
@@
 
+The Occupational Information Network (O*NET; onetonline.org) contains a comprehensive description of occupations (Peterson et al., 2001).
+This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated.
 We used 98 statements taken from O*NET \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context classifications}.
@@
 
-\hypertarget{standard-deviations-of-perceptions}{%
-\subsection{Standard deviations of perceptions}\label{standard-deviations-of-perceptions}}
-
 \begin{figure}
@@
 
-The first prediction asks whether job characteristics differ in variability/stability regarding
-subjective worker perception as a demand or resource.
-Figure \ref{fig:overallhist} presents standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand.
+The first prediction asks whether job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
+Figure \ref{fig:overallhist} presents frequency distributions standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand.
 As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's \(K^2\) = 76.83, \emph{p} = 0.00 ).
-
-\hypertarget{low-variability-demands-and-resources}{%
-\subsection{Low Variability Demands and Resources}\label{low-variability-demands-and-resources}}
 
@@
 
-\hypertarget{high-variability-demands-and-resources}{%
-\subsection{High Variability Demands and Resources}\label{high-variability-demands-and-resources}}
-
 \begin{figure}
@@
 
-\hypertarget{correlations}{%
-\subsection{Correlations}\label{correlations}}
-
-ADD THIS!
+The second prediction stated that job characteristics would not be uniquely categorized as a resource or demand.
+Table \ref{tab:cortab} provides the correlations among the O*Net item groupings by resource, challenge and hindrance demand.
+A large proportion of correlations are moderate.
+Challenge and hindrance demands are smaller in relationship, but mostly negative.
+Challenge and resource are strongly and positively related.
+These results provide support for H2 suggesting that there is overlap in how employees perceive job characteristics.
+Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.
 
@@
 
-Figure 4 highs the average characteristic rating grouped by the literature implicated categories shown on the right.
-These categories are frequently presented in descriptions of the JD-R model and theory (cite).
-To answer these research questions, authors categorized items into the categories listed in the literature.
+In addition to the two predictions, three related research questions were proposed.
+To answer these research questions, authors first categorized items into the categories listed in the JD-R literature.
 For example, autonomy is frequently described as a resource.
-An O*Net item in the ``autonomy'' category is ``How much decision making freedom, without supervision, does your job offer?''.
-Means for respondent-rated resources, challenges, and hindrances were then computed to explore whether literature-implicated resources and demands were consistently rated as such.
-The left side of Figure 8 shows literature-derived demands (e.g., work pressure).
-We do not see a clear pattern of high ratings as hindrances for these demands.
+An O*Net item in the autonomy category is, ``How much decision making freedom, without supervision, does your job offer?''.
+Means for resources, challenges, and hindrances groupings were then computed to explore whether literature-implicated resources and demands were consistently rated as such.
+The left side of Figure 4 shows literature-derived demand categories (e.g., work pressure).
+Here, we do not see a clear pattern of high ratings as hindrances for these demands.
 In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much more variability in how employees rated what should objectively be ``hindrances'' at work.
 However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings.
-Here, the white bars representing resources are consistently higher.
+The white bars representing resources are consistently higher.
 ADD ANOVAS HERE - one way repeated measures for each category (total of 10 analyses).
@@
 
-challenges
-
 see Figure \ref{fig:scalelevelgraphs}
 
-\begin{verbatim}
-## ANOVA Table (type III tests)
-## 
-## $ANOVA
-##   Effect DFn  DFd      F        p p<.05   ges
-## 1   type   2 1134 17.709 2.67e-08     * 0.017
-## 
-## $`Mauchly's Test for Sphericity`
-##   Effect     W        p p<.05
-## 1   type 0.694 1.29e-45     *
-## 
-## $`Sphericity Corrections`
-##   Effect   GGe       DF[GG]    p[GG] p[GG]<.05   HFe      DF[HF]    p[HF]
-## 1   type 0.766 1.53, 868.32 7.09e-07         * 0.767 1.53, 870.2 6.93e-07
-##   p[HF]<.05
-## 1         *
-\end{verbatim}
+Separate repeated-measures ANOVAs were conducted for each of these comparisons.
 
-\begin{verbatim}
-## 
-## Error: subject
-##           Df Sum Sq Mean Sq F value Pr(>F)
-## Residuals  1  8.266   8.266               
-## 
-## Error: subject:type
-##      Df Sum Sq Mean Sq
-## type  2  15.04   7.519
-## 
-## Error: Within
-##             Df Sum Sq Mean Sq F value  Pr(>F)   
-## type         2    9.2   4.586   5.989 0.00256 **
-## Residuals 1698 1300.2   0.766                   
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-\end{verbatim}
+\hypertarget{literature-implicated-demands}{%
+\subsection{Literature-implicated demands}\label{literature-implicated-demands}}
+
+The effect for \texttt{Overwork} was \(F_{(2, 1134)}\) = 17.71, partial eta squared \((\eta^2)\) was 0.03.
+The effect for \texttt{Physical\ Environment} was \(F_{(2, 1108)}\) = 112.97 (\(\eta^2\) = 0.17).
+The effect for \texttt{Time\ Pressure} was \(F_{(2, 1090)}\) = 82.22 (\(\eta^2\) = 0.13).
+The effect for \texttt{Emotional\ Demands} was \(F_{(2, 1098)}\) = 393.43 (\(\eta^2\) = 0.42).
+The effect for \texttt{Recipient\ Contact} was \(F_{(2, 1126)}\) = 1,031.73 (\(\eta^2\) = 0.65).
+The effect for \texttt{Work\ Pressure} was \(F_{(2, 1132)}\) = 718.12 (\(\eta^2\) = 0.56).
+
+\hypertarget{literature-implicated-resources}{%
+\subsection{Literature-implicated resources}\label{literature-implicated-resources}}
+
+The effect for \texttt{Job\ Control} was \(F_{(2, 1134)}\) = 52.78 (\(\eta^2\) = 0.08).
+The effect for \texttt{Participation} was \(F_{(2, 1124)}\) = 991.16 (\(\eta^2\) = 0.64).
+The effect for \texttt{Autonomy} was \(F_{(2, 1074)}\) = 951.90 (\(\eta^2\) = 0.64).
+The effect for \texttt{Team\ Cohesion} was \(F_{(2, 1120)}\) = 853.39 (\(\eta^2\) = 0.60).
 
 \newpage
+
+NOTE: Add a table of the items (probably the full list and those we included in challenge, hindrance specifically). Could also have a column showing which items were used for Figure 4 categories.
 
@@
 Interestingly, we consistently observed that job characteristics rated as resources were also rated highly as challenge stressors, which are not inherently negative in the way that hindrance stressors are.
-Lastly, we also found support for the prediction that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
+Lastly, we also found support for the prediction that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand (H2).
 
-\hypertarget{practical-implications}{%
-\subsection{Practical Implications}\label{practical-implications}}
+\hypertarget{implications}{%
+\section{Implications}\label{implications}}
 
+Theoretically, these findings support growing body of literature suggesting that perceptions of resources and demands, broadly, are not universal.
+There is individual difference in how employees experience the characteristics of their jobs.
+Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a ``resource'' or ``demand''.
+These results have implications for managers as well.
 The reality that there is more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-advisory1993new}{}}%
-Dictionary of Occupational Titles (US), A.
-P.
-for the, \& Service, U.
-S.
-E.
-(1993).
-\emph{The new DOT: A database of occupational titles for the twenty-first century}.
-US Department of Labor, Employment; Training Administration, US~\ldots.
-
 \leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%

### 2023-02-08 Submission.Rmd
Added draft abstract.

@@
 abstract: |
-  We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
-O*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource.
+  Much of our understanding of job demands and resources rests on the assumption that some aspects and components of one's job are resources and some are demanding.
+We build on a small but growing literature suggesting that individual differences may matter.
+The primary aims were to explore 1) whether there is variability in subjective ratings of job characteristics with respect to how much they served as resources and demands, and 2) whether or not there was a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
+O*NET work characteristics were rated by 568 employed respondents in terms of relevance, perception as a demand, and perception as a resource.
+The results suggest that job characteristics differ in variability/stability regarding subjective worker perceptions, particularly for hindrance demands which showed the most variability.
+Job characteristics were not uniquely categorized as a resource or demand as evidenced by correlations, and lastly, literature-implicated resources not consistently rated as job resources or demands.
 

### 2023-02-11 Submission.tex
added line numbers

@@
 \usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Job Demands-Resources Model Components through the Lens of O*NET Classifications},
+  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \makeatother
+\usepackage{lineno}
+
+\linenumbers
 \usepackage{csquotes}
-\ifLuaTeX
+\ifxetex
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\else
+  \usepackage[main=english]{babel}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+\fi
+\ifluatex
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={Job Demands-Resources Model Components through the Lens of O*NET Classifications},
-  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 
-\abstract{%
-We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resource) in the workplace, with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
-O*NET work characteristics were rated in terms of relevance, perception as a demand, and perception as a resource.
+\abstract{
+Much of our understanding of job demands and resources rests on the assumption that some aspects and components of one's job are resources and some are demanding.
+We build on a small but growing literature suggesting that individual differences may matter.
+The primary aims were to explore 1) whether there is variability in subjective ratings of job characteristics with respect to how much they served as resources and demands, and 2) whether or not there was a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
+O*NET work characteristics were rated by 568 employed respondents in terms of relevance, perception as a demand, and perception as a resource.
+The results suggest that job characteristics differ in variability/stability regarding subjective worker perceptions, particularly for hindrance demands which showed the most variability.
+Job characteristics were not uniquely categorized as a resource or demand as evidenced by correlations, and lastly, literature-implicated resources not consistently rated as job resources or demands.
 }
@@
 Cognitively, the perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources) (Bakker \& Demerouti, 2014).
-Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience despite the typical apriori assignment of a characteristic as objectively a ``demand'' or ``resource''.
-We explore this further below.
+Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience despite the typical apriori assignment of a characteristic as objectively a ``demand'' or ``resource.'' We explore this further below.
 
@@
 
-Although there is a tendency to attach a negative connotation to the word ``stress'', Selye (1936) defined stress as simple a response to change.
+Although there is a tendency to attach a negative connotation to the word ``stress,'' Selye (1936) defined stress as simple a response to change.
 We return to the employed public figure for this next section.
@@
 For example, autonomy is frequently described as a resource.
-An O*Net item in the autonomy category is, ``How much decision making freedom, without supervision, does your job offer?''.
-Means for resources, challenges, and hindrances groupings were then computed to explore whether literature-implicated resources and demands were consistently rated as such.
+An O*Net item in the autonomy category is, ``How much decision making freedom, without supervision, does your job offer?'' Means for resources, challenges, and hindrances groupings were then computed to explore whether literature-implicated resources and demands were consistently rated as such.
 The left side of Figure 4 shows literature-derived demand categories (e.g., work pressure).
@@
 There is individual difference in how employees experience the characteristics of their jobs.
-Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a ``resource'' or ``demand''.
+Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a ``resource'' or ``demand.''
 These results have implications for managers as well.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
+\leavevmode\hypertarget{ref-demerouti2001job}{}%
 Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
 
-\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
+\leavevmode\hypertarget{ref-gerich2017relevance}{}%
 Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
 
-\leavevmode\vadjust pre{\hypertarget{ref-horan2020review}{}}%
+\leavevmode\hypertarget{ref-horan2020review}{}%
 Horan, K.

### 2023-02-11 Submission.Rmd
added line numbers
added results explanation

@@
 footnotelist      : no
-linenumbers       : no
+linenumbers       : yes
 mask              : no
@@
 
+Repeated-measures ANOVAs were run for the group of literture-implicated demands first.
 The effect for `Overwork` was $F_{(`r report1$ANOVA$DFn`, `r report1$ANOVA$DFd`)}$ = `r report1$ANOVA$F`, partial eta squared $(\eta^2)$ was `r report1$ANOVA$pes`.
@@
 The effect for `Recipient Contact` was $F_{(`r report5$ANOVA$DFn`, `r report5$ANOVA$DFd`)}$ = `r report5$ANOVA$F` ($\eta^2$ = `r report5$ANOVA$pes`).
-The effect for `Work Pressure` was $F_{(`r report6$ANOVA$DFn`, `r report6$ANOVA$DFd`)}$ = `r report6$ANOVA$F` ($\eta^2$ = `r report6$ANOVA$pes`).
+The effect for `Work Pressure` was $F_{(`r report6$ANOVA$DFn`, `r report6$ANOVA$DFd`)}$ = `r report6$ANOVA$F` ($\eta^2$ = `r report6$ANOVA$pes`).In all cases, statistical significance was less then .001, indicating in all cases, what the literature implicates is a demand was rated as a resource (all means are above the midpoint).
+See the patten of white resource bars on the lefthand side of Figure 4.
+This is contrary to the expectation that ratings would match our assumption of what a resource constitutes.
+Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance.
 
@@
 
+Next, Repeated-measures ANOVAs were run for the group of literture-implicated resources (the right hand set of analyses presented in Figure 4).
 The effect for `Job Control` was $F_{(`r report7$ANOVA$DFn`, `r report7$ANOVA$DFd`)}$ = `r report7$ANOVA$F` ($\eta^2$ = `r report7$ANOVA$pes`).
@@
 The effect for `Autonomy` was $F_{(`r report9$ANOVA$DFn`, `r report9$ANOVA$DFd`)}$ = `r report9$ANOVA$F` ($\eta^2$ = `r report9$ANOVA$pes`).
-The effect for `Team Cohesion` was $F_{(`r report10$ANOVA$DFn`, `r report10$ANOVA$DFd`)}$ = `r report10$ANOVA$F` ($\eta^2$ = `r report10$ANOVA$pes`).
+The effect for `Team Cohesion` was $F_{(`r report10$ANOVA$DFn`, `r report10$ANOVA$DFd`)}$ = `r report10$ANOVA$F` ($\eta^2$ = `r report10$ANOVA$pes`).Similar to the demands analyses, statistical significance was less then .001 for all four category comparisons.
+Here, the pattern was as expected.
+Across categories, resources were rated the highest (see white bars representing resources in Figure 4).
 

### 2023-02-11 Submission.tex
added results explanation
Updating keywords

@@
   pdflang={en-EN},
-  pdfkeywords={keywords},
+  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resoures, job characteristics},
   hidelinks,
@@
 \shorttitle{O*NET JD-R}
-\keywords{keywords\newline\indent Word count: X}
+\keywords{O*Net, challenge-hindrance framework, job demands-resoures, job characteristics\newline\indent Word count: X}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 
-The effect for \texttt{Overwork} was \(F_{(2, 1134)}\) = 17.71, partial eta squared \((\eta^2)\) was 0.03.
+Repeated-measures ANOVAs were run for the group of literture-implicated demands first. The effect for \texttt{Overwork} was \(F_{(2, 1134)}\) = 17.71, partial eta squared \((\eta^2)\) was 0.03.
 The effect for \texttt{Physical\ Environment} was \(F_{(2, 1108)}\) = 112.97 (\(\eta^2\) = 0.17).
@@
 The effect for \texttt{Recipient\ Contact} was \(F_{(2, 1126)}\) = 1,031.73 (\(\eta^2\) = 0.65).
-The effect for \texttt{Work\ Pressure} was \(F_{(2, 1132)}\) = 718.12 (\(\eta^2\) = 0.56).
+The effect for \texttt{Work\ Pressure} was \(F_{(2, 1132)}\) = 718.12 (\(\eta^2\) = 0.56).In all cases, statistical significance was less then .001, indicating in all cases, what the literature implicates is a demand was rated as a resource (all means are above the midpoint).
+See the patten of white resource bars on the lefthand side of Figure 4.
+This is contrary to the expectation that ratings would match our assumption of what a resource constitutes.
+Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance.
 
@@
 
+Next, Repeated-measures ANOVAs were run for the group of literture-implicated resources (the right hand set of analyses presented in Figure 4).
 The effect for \texttt{Job\ Control} was \(F_{(2, 1134)}\) = 52.78 (\(\eta^2\) = 0.08).
@@
 The effect for \texttt{Autonomy} was \(F_{(2, 1074)}\) = 951.90 (\(\eta^2\) = 0.64).
-The effect for \texttt{Team\ Cohesion} was \(F_{(2, 1120)}\) = 853.39 (\(\eta^2\) = 0.60).
+The effect for \texttt{Team\ Cohesion} was \(F_{(2, 1120)}\) = 853.39 (\(\eta^2\) = 0.60).Similar to the demands analyses, statistical significance was less then .001 for all four category comparisons.
+Here, the pattern was as expected.
+Across categories, resources were rated the highest (see white bars representing resources in Figure 4).
 

### 2023-02-12 Submission.Rmd
Updated keywords
Updating keywords
Updated methods section.

@@
 abstract: |
-  Much of our understanding of job demands and resources rests on the assumption that some aspects and components of one's job are resources and some are demanding.
-We build on a small but growing literature suggesting that individual differences may matter.
+  Much of our understanding of job demands and resources rests on the assumption that some aspects and components of one's job are resources and some are demands.
+We build on a small but growing literature suggesting that individual differences may matter our perception of characteristics as demands and resources.
 The primary aims were to explore 1) whether there is variability in subjective ratings of job characteristics with respect to how much they served as resources and demands, and 2) whether or not there was a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
@@
 
-keywords          : "keywords"
+keywords         : "O*Net, challenge-hindrance framework, job demands-resoures, job characteristics"
 wordcount        : "X"
@@
 
-The integration of the literature above results in two primary predictions.
+The integration of the literature above results in two primary hypotheses.
 The first addresses whether employees generally agree on their appraisals of job characteristics as resources or challenge or hindrance demands.
@@
 
->Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
+>Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are viewed as both a resource and a demand.
 
-We explore three research questions addressing whether our literature-implicated job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory [@bakker2017job] and challenge-hindrance stressor framework [@cavanaugh2000empirical].
+Two exploratory questions further address whether our *literature-implicated* job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory [@bakker2017job] and challenge-hindrance stressor framework [@cavanaugh2000empirical].
 
@@
 # Method
-
-Data were collected through Prolific, a data collection platform.
-An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
-Eligibility requirements included being 18+ and holding either a full-time or part-time job.
-Participants then voluntarily chose to respond to the survey.
-The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes.
-Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified.
-Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource, challenge, or hindrance for that characteristic.
-For characteristics that *were* implicated as being relevent for their job, they were then asked to report how much a characteristic was a resource, and then how much each characteristic was a hindrance, and finally, how much each item was a challenge.
-Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
 
@@
 
-The Occupational Information Network (O\*NET; onetonline.org) contains a comprehensive description of occupations [@peterson2001understanding].
+The Occupational Information Network (O\*NET) contains a comprehensive description of occupations [@peterson2001understanding].
 This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated.
-We used 98 statements taken from O\*NET [activity and context classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3).
-We retained 41 work activity classifications which O\*NET groups into categories of information input (5 statements; Where and how are the information and data gained that are needed to perform this job?), interacting with others (17 statements; What interactions with other persons or supervisory activities occur while performing this job?), mental processes (10 statements; What processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (9 statements; What physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
-Fifty-seven work context statements grouped into interpersonal relationships (14 statements; This category describes the context of the job in terms of human interaction processes), physical work conditions (30 statements; This category describes the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (13 statements; This category involves the relationships or interactions between the worker and the structural characteristics of the job).
+We used 98 statements/questions from O\*NET [activity and context classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3).
+We retained work activity classifications which O\*NET groups into categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
+Work context statements were grouped into interpersonal relationships (i.e., this category describes the context of the job in terms of human interaction processes), physical work conditions (i.e., this category describes the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., this category involves the relationships or interactions between the worker and the structural characteristics of the job).
 
-These descriptors often have [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).
-For example, the statement "How responsible is the worker for work outcomes and results of other workers?" has response options ranging from *No responsibility* to *Very high responsibility*, while the statement, "How often do you use electronic mail in this job?" has options ranging from *Never* to *Every day*.
-The O\*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to "responsibility" than task.
-For example, the descriptor for "level of competition", which is an element of the "structural job characteristics" grouping, is *...to what extent does this job require the worker to compete or to be aware of competitive pressures?* Other than minor grammatical editing (for example, changing “the worker” to “you”), we retained the O\*Net wording for our item stems.
-We also retained O\*Net’s response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
+O\*NET collects information about these categories by periodically asking workers about these statements/questions, which often have [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).
+For example, "How responsible is the worker for work outcomes and results of other workers?" has response options ranging from *No responsibility* to *Very high responsibility*, while the question, "How often do you use electronic mail in this job?" has options ranging from *Never* to *Every day*.
+We retained O\*Net’s response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
 It would likely NOT be considered controversial to referred to these as "effectively" Likert-type response scales.
-
-We retained the essence of each O\*NET descriptor to capture characteristics of relevance for each respondent.
-Subsequent to these self evaluations, each respondent who agreed that the element had *at least some relevance* to their job was also asked to rate that element in terms of, 1) ...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) ...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) ...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
+Other than minor grammatical editing (for example, changing “the worker” to “you”), we also retained the O\*Net wording for our item stems (statements/questions).
 
 The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
+
+## Procedure
+
+Data were collected through Prolific, a data collection platform.
+An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
+Eligibility requirements included being 18+ and holding either a full-time or part-time job.
+Participants then voluntarily chose to respond to the survey.
+The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes.
+Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified.
+Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (i.e., ...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (i.e., ...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (i.e., ...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
+Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
 
@@
 
-The first prediction asks whether job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
+The first hypothesis asks whether job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
 Figure \@ref(fig:overallhist) presents frequency distributions standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand.
@@
 
-The second prediction stated that job characteristics would not be uniquely categorized as a resource or demand.
+The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand.
 Table \@ref(tab:cortab) provides the correlations among the O\*Net item groupings by resource, challenge and hindrance demand.
@@
 
-In addition to the two predictions, three related research questions were proposed.
+In addition to the two hypotheses, three related research questions were proposed.
 To answer these research questions, authors first categorized items into the categories listed in the JD-R literature.
@@
 The white bars representing resources are consistently higher.
-ADD ANOVAS HERE - one way repeated measures for each category (total of 10 analyses).
-describe pattern.
-In sum, these results provide ___ support for RQ 1 and 2.
-
-see Figure \@ref(fig:scalelevelgraphs)
+In sum, these results provide some support for RQ 1 and 2.
 
@@
 
-## Literature-implicated demands
-
 Repeated-measures ANOVAs were run for the group of literture-implicated demands first.
@@
 Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance.
-
-## Literature-implicated resources
 
@@
 
-The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands (both challenge and hindrance), and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using a sample of items from O*Net.
+The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands (both challenge and hindrance), and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using a sample of items from O\*Net.
 The findings broadly revealed that there was relatively more consistency in ratings of resources and challenges characteristics, and far more variability in job characteristics rated as hindrance stressors.
@@
 Interestingly, we consistently observed that job characteristics rated as resources were also rated highly as challenge stressors, which are not inherently negative in the way that hindrance stressors are.
-Lastly, we also found support for the prediction that job characteristics are not uniquely categorized as a resource or demand, but rather, some job  characteristics are rated highly as both a resource and a demand (H2).
+Lastly, we also found support for the hypothesis that job characteristics are not uniquely categorized as a resource or demand, but rather, some job  characteristics are rated highly as both a resource and a demand (H2).
 
-# Implications
+## Implications
 
@@
 
-# Limitations and Future Directions
+## Limitations and Future Directions
 
@@
 Because we asked up to four questions about each characteristics, we were limited in the number of job characteristics we could reasonably include.
-Related to that, we intentionally worked within the O*Net database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources/demands.
+Related to that, we intentionally worked within the O\*Net database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources/demands.
 For example, we included minimal “social” resources or interactions with one’s supervisor, which the literature would suggest are important resources.

### 2023-02-12 Submission.tex
Updated methods section.

@@
 \abstract{
-Much of our understanding of job demands and resources rests on the assumption that some aspects and components of one's job are resources and some are demanding.
-We build on a small but growing literature suggesting that individual differences may matter.
+Much of our understanding of job demands and resources rests on the assumption that some aspects and components of one's job are resources and some are demands.
+We build on a small but growing literature suggesting that individual differences may matter our perception of characteristics as demands and resources.
 The primary aims were to explore 1) whether there is variability in subjective ratings of job characteristics with respect to how much they served as resources and demands, and 2) whether or not there was a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
@@
 \begin{quote}
-Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
+Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are viewed as both a resource and a demand.
 \end{quote}
 
-We explore three research questions addressing whether our literature-implicated job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory (Bakker \& Demerouti, 2017) and challenge-hindrance stressor framework (Cavanaugh et al., 2000).
+Two exploratory questions further address whether our \emph{literature-implicated} job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory (Bakker \& Demerouti, 2017) and challenge-hindrance stressor framework (Cavanaugh et al., 2000).
 
@@
 \section{Method}\label{method}}
-
-Data were collected through Prolific, a data collection platform.
-An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
-Eligibility requirements included being 18+ and holding either a full-time or part-time job.
-Participants then voluntarily chose to respond to the survey.
-The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes.
-Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified.
-Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource, challenge, or hindrance for that characteristic.
-For characteristics that \emph{were} implicated as being relevent for their job, they were then asked to report how much a characteristic was a resource, and then how much each characteristic was a hindrance, and finally, how much each item was a challenge.
-Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
 
@@
 
-The Occupational Information Network (O*NET; onetonline.org) contains a comprehensive description of occupations (Peterson et al., 2001).
+The Occupational Information Network (O*NET) contains a comprehensive description of occupations (Peterson et al., 2001).
 This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated.
-We used 98 statements taken from O*NET \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context classifications}.
-We retained 41 work activity classifications which O*NET groups into categories of information input (5 statements; Where and how are the information and data gained that are needed to perform this job?), interacting with others (17 statements; What interactions with other persons or supervisory activities occur while performing this job?), mental processes (10 statements; What processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (9 statements; What physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
-Fifty-seven work context statements grouped into interpersonal relationships (14 statements; This category describes the context of the job in terms of human interaction processes), physical work conditions (30 statements; This category describes the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (13 statements; This category involves the relationships or interactions between the worker and the structural characteristics of the job).
+We used 98 statements/questions from O*NET \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context classifications}.
+We retained work activity classifications which O*NET groups into categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
+Work context statements were grouped into interpersonal relationships (i.e., this category describes the context of the job in terms of human interaction processes), physical work conditions (i.e., this category describes the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., this category involves the relationships or interactions between the worker and the structural characteristics of the job).
 
-These descriptors often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}.
-For example, the statement ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{No responsibility} to \emph{Very high responsibility}, while the statement, ``How often do you use electronic mail in this job?'' has options ranging from \emph{Never} to \emph{Every day}.
-The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task.
-For example, the descriptor for ``level of competition,'' which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems.
-We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
+O*NET collects information about these categories by periodically asking workers about these statements/questions, which often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}.
+For example, ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{No responsibility} to \emph{Very high responsibility}, while the question, ``How often do you use electronic mail in this job?'' has options ranging from \emph{Never} to \emph{Every day}.
+We retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
 It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.
-
-We retained the essence of each O*NET descriptor to capture characteristics of relevance for each respondent.
-Subsequent to these self evaluations, each respondent who agreed that the element had \emph{at least some relevance} to their job was also asked to rate that element in terms of, 1) \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
+Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we also retained the O*Net wording for our item stems (statements/questions).
 
 The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
+
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
+
+Data were collected through Prolific, a data collection platform.
+An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
+Eligibility requirements included being 18+ and holding either a full-time or part-time job.
+Participants then voluntarily chose to respond to the survey.
+The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes.
+Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified.
+Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (i.e., \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (i.e., \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (i.e., \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
+Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
 
@@
 
-The first prediction asks whether job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
+The first hypothesis asks whether job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
 Figure \ref{fig:overallhist} presents frequency distributions standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand.
@@
 
-The second prediction stated that job characteristics would not be uniquely categorized as a resource or demand.
+The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand.
 Table \ref{tab:cortab} provides the correlations among the O*Net item groupings by resource, challenge and hindrance demand.
@@
 The white bars representing resources are consistently higher.
-ADD ANOVAS HERE - one way repeated measures for each category (total of 10 analyses).
-describe pattern.
-In sum, these results provide \_\_\_ support for RQ 1 and 2.
-
-see Figure \ref{fig:scalelevelgraphs}
+In sum, these results provide some support for RQ 1 and 2.
 
 Separate repeated-measures ANOVAs were conducted for each of these comparisons.
-
-\hypertarget{literature-implicated-demands}{%
-\subsection{Literature-implicated demands}\label{literature-implicated-demands}}
 
@@
 Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance.
-
-\hypertarget{literature-implicated-resources}{%
-\subsection{Literature-implicated resources}\label{literature-implicated-resources}}
 
@@
 Interestingly, we consistently observed that job characteristics rated as resources were also rated highly as challenge stressors, which are not inherently negative in the way that hindrance stressors are.
-Lastly, we also found support for the prediction that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand (H2).
+Lastly, we also found support for the hypothesis that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand (H2).
 
 \hypertarget{implications}{%
-\section{Implications}\label{implications}}
+\subsection{Implications}\label{implications}}
 
@@
 \hypertarget{limitations-and-future-directions}{%
-\section{Limitations and Future Directions}\label{limitations-and-future-directions}}
+\subsection{Limitations and Future Directions}\label{limitations-and-future-directions}}
 
@@
 Because we asked up to four questions about each characteristics, we were limited in the number of job characteristics we could reasonably include.
-Related to that, we intentionally worked within the O\emph{Net database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources/demands.
+Related to that, we intentionally worked within the O*Net database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources/demands.
 For example, we included minimal ``social'' resources or interactions with one's supervisor, which the literature would suggest are important resources.
@@
 It would also be interesting to consider outcomes associated with subjective ratings.
-Lastly, there may be some practical utility to pursue training interventions aimed at }how* characteristics are appraised.
+Lastly, there may be some practical utility to pursue training interventions aimed at \emph{how} characteristics are appraised.
 Perhaps the clinical literature may be informative - for example, within cognitive behavioral therapeutic applications, the way in which situations are appraised can be a mechanism to help battle affective disorders such as depression.{[}\^{}check{]} Given the current findings, where the same characteristic may be viewed similarly as both a demand and resource, it is possible that framing interventions may ameliorate negative outcomes of demands such as, for example, stress or strain.

### 2023-02-13 Submission.Rmd
one more minor update
bartletts

@@
 Figure \@ref(fig:overallhist) presents frequency distributions standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand.
-As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's $K^2$ = `r lookie$statistic[[1]]`, *p* = `r lookie$p.value` ).
+As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's $\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* = `r lookie$p.value` ).
 
@@
 
-# Conclusion
+## Conclusion
 

### 2023-02-13 Submission.tex
bartletts

@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Job Demands-Resources Model Components through the Lens of O*NET Classifications},
-  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
-  pdflang={en-EN},
-  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resoures, job characteristics},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \makeatother
-\shorttitle{O*NET JD-R}
+
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
 \keywords{O*Net, challenge-hindrance framework, job demands-resoures, job characteristics\newline\indent Word count: X}
@@
 \usepackage{csquotes}
-\ifxetex
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Job Demands-Resources Model Components through the Lens of O*NET Classifications},
+  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
+  pdflang={en-EN},
+  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resoures, job characteristics},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 
-\abstract{
+\abstract{%
 Much of our understanding of job demands and resources rests on the assumption that some aspects and components of one's job are resources and some are demands.
@@
 Cognitively, the perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources) (Bakker \& Demerouti, 2014).
-Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience despite the typical apriori assignment of a characteristic as objectively a ``demand'' or ``resource.'' We explore this further below.
+Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience despite the typical apriori assignment of a characteristic as objectively a ``demand'' or ``resource''.
+We explore this further below.
 
@@
 
-Although there is a tendency to attach a negative connotation to the word ``stress,'' Selye (1936) defined stress as simple a response to change.
+Although there is a tendency to attach a negative connotation to the word ``stress'', Selye (1936) defined stress as simple a response to change.
 We return to the employed public figure for this next section.
@@
 Figure \ref{fig:overallhist} presents frequency distributions standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand.
-As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's \(K^2\) = 76.83, \emph{p} = 0.00 ).
+As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's \(\chi^2_{}\) = 76.83, \emph{p} = 0.00 ).
 
@@
 Figure \ref{fig:combinegraphs2} presents the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations (these are the 8 characteristics with the greatest variability in rating).
-In sum, these results provide some support for H1, particularly for hindrances, which are consistently viewed as ``different.''
+In sum, these results provide some support for H1, particularly for hindrances, which are consistently viewed as ``different''.
 
@@
 For example, autonomy is frequently described as a resource.
-An O*Net item in the autonomy category is, ``How much decision making freedom, without supervision, does your job offer?'' Means for resources, challenges, and hindrances groupings were then computed to explore whether literature-implicated resources and demands were consistently rated as such.
+An O*Net item in the autonomy category is, ``How much decision making freedom, without supervision, does your job offer?''.
+Means for resources, challenges, and hindrances groupings were then computed to explore whether literature-implicated resources and demands were consistently rated as such.
 The left side of Figure 4 shows literature-derived demand categories (e.g., work pressure).
@@
 There is individual difference in how employees experience the characteristics of their jobs.
-Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a ``resource'' or ``demand.''
+Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a ``resource'' or ``demand''.
 These results have implications for managers as well.
@@
 \hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
+\subsection{Conclusion}\label{conclusion}}
 
@@
 
-\leavevmode\hypertarget{ref-demerouti2001job}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
 Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
 
-\leavevmode\hypertarget{ref-gerich2017relevance}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
 Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
 
-\leavevmode\hypertarget{ref-horan2020review}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-horan2020review}{}}%
 Horan, K.
@@
 
-\leavevmode\hypertarget{ref-lazarus1984stress}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
 Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
 
-\leavevmode\hypertarget{ref-lepine2005meta}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lepine2005meta}{}}%
 LePine, J.

### 2023-02-14 SIOP2023/Counts/counts_poster.Rmd
working on logo size - they push each other off currently

--- 2023-01-02 SIOP2023/Counts/counts_poster.Rmd
@@
 secondary_colour: "#B4B5B4"
-accent_colour: "#111c2c"
-#logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
-#logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
+accent_colour: "#FF0000"
+logoright_name: 'Stoutlogo_2023.png'
+logoleft_name: "erg.png"
 output: 
@@
 link-citations: true
+floatsintext: yes
 affiliation_textsize: "50pt"
@@
 author_textsize:	"50pt"
+font_family: 'Helvetica'
+main_fontfamily: "Helvetica"
 #logoleft_name	"Figures/posterdownlogo.png"	Location of the image to use.
@@
 ```
+
+<style>
+.logo_left {
+ width: 10%;
+}
+.logo_right {
+ width: 10%;
+}
+</style>
 
@@
 
+Correlations, means and standard deviations are presented in Table \@ref(tab:correlationtable).
+The results reveal a positive association between resources and engagement (*r* = .34; H1a), but a lack of meaningful association between resources and stress (H1b) and burnout (H1c).
+Challenge demands were positively associated with engagement (*r* = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
+Total hindrance stressors were largely not significantly associated with our outcomes, although there was a small-moderate association with stress (H3b; *r* = .09).
+
 ```{r correlationtable, warning=FALSE}
@@
                  caption = "Focal variable correlations (counts data).",
+                 placement = "H",
+                 align = c('l','l','l','l','l','l','r','r'),
                  escape = FALSE)
@@
 
+We also conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
+The total resources were predictive of engagement ($F_{(3, 564)}$ = 26.41, p < .001), but neither challenge nor hindrance demands predicted engagement; see Table \@ref(tab:regressiontableeng).
+
 ```{r regressiontableeng}
@@
 apa_table(
-  apa_lm$table
-  , caption = "Regression Predicting Engagement."
+  apa_lm$table, 
+  caption = "Regression Predicting Engagement.",
+  align = c('l','r','r','r','r','r'),
+  placement = "H"
 )
 ```
+
+Stress was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$ = 2.47, *p* = .060; see Table \@ref(tab:regressiontablestr).
 
@@
 apa_table(
-  apa_lm$table
-  , caption = "Regression Predicting Stress."
+  apa_lm$table, 
+  placement = "H",
+  align = c('l','r','r','r','r','r'),
+  caption = "Regression Predicting Stress."
 )
 ```
+
+Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$= 1.10, *p* = .349. See Table \@ref(tab:regressiontablebur).
 
@@
 apa_table(
-  apa_lm$table
-  , caption = "Regression Predicting Burnout."
+  apa_lm$table, 
+  placement = "H",
+  align = c('l','r','r','r','r','r'),
+  caption = "Regression Predicting Burnout."
 )
 ```
-
-Correlations, means and standard deviations are presented in Table \@ref(tab:correlationtable).
-The results reveal a positive association between resources and engagement (*r* = .34; H1a), but a lack of meaningful association between resources and stress (H1b) and burnout (H1c).
-Challenge demands were positively associated with engagement (*r* = .31; H2a), but were unrelated to stress or burnout (H2b and H2c).
-Total hindrance stressors were largely not significantly associated with our outcomes, although there was a small-moderate association with stress (H3b; *r* = .09).
-
-We also conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
-The total resources were predictive of engagement ($F_{(3, 564)}$ = 26.41, p < .001), but neither challenge nor hindrance demands predicted engagement (see Table \@ref(tab:regressiontableeng).
-Stress was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$ = 2.47, *p* = .060 [see Table \@ref(tab:regressiontablestr)].
-Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$= 1.10, *p* = .349.
-See Table \@ref(tab:regressiontablebur).
 
@@
 
+![](SIOP.png){height=480px width=1340px}
+
 ```{r bib, eval=FALSE}

### 2023-02-14 SIOP2023/Counts/counts_poster.Rmd
Figured out title - title bar now good (had to decrease middle title container so left logo doesn't push right logo off screen)
formatting done - content should be double-checked

@@
 .logo_left {
- width: 10%;
+ width: 15%;
 }
 .logo_right {
- width: 10%;
+ width: 15%;
+}
+.poster_title{
+  padding-top: 5%;
+  width: 70%;
 }
@@
 While not a causal relationship, it points to the potential value of these kinds of employee support nonetheless.
+
+## Limitations & Future Directions
+
 Future study could consider additional or other O\*Net items, *kinds* of resources or challenges, additional outcomes (e.g., job satisfaction), or whether volume of resources and demands operationalized in this way are related to other behaviors.
+Finally, there was a moderate relationship between challenges and hindrances, which may be driven by job complexity – that is, some jobs simply have more elements.
+With more job elements come increased opportunities for those elements to be perceived as resources, challenges, or hindrances.
 
-![](SIOP.png){height=480px width=1340px}
-
+<center>
+![](SIOP.png){height=350px width=1080px}
+<center>
 ```{r bib, eval=FALSE}

### 2023-02-16 SIOP2023/Counts/counts_poster.Rmd
Made tiny edits to poster

@@
 affiliation_textsize: "50pt"
-body_textsize: "50px"
+body_textsize: "48px"
 title_textsize:	"75pt"	
@@
 papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table,
-                 caption = "Focal variable correlations (counts data).",
+                 caption = "Focal Variable Correlations (Counts Data)",
                  placement = "H",
@@
   apa_lm$table, 
-  caption = "Regression Predicting Engagement.",
+  caption = "Regression Predicting Engagement",
   align = c('l','r','r','r','r','r'),
@@
   align = c('l','r','r','r','r','r'),
-  caption = "Regression Predicting Stress."
+  caption = "Regression Predicting Stress"
 )
@@
   align = c('l','r','r','r','r','r'),
-  caption = "Regression Predicting Burnout."
+  caption = "Regression Predicting Burnout"
 )
@@
 ## Limitations & Future Directions 
-
 Future study could consider additional or other O\*Net items, *kinds* of resources or challenges, additional outcomes (e.g., job satisfaction), or whether volume of resources and demands operationalized in this way are related to other behaviors.
-Finally, there was a moderate relationship between challenges and hindrances, which may be driven by job complexity – that is, some jobs simply have more elements.
-With more job elements come increased opportunities for those elements to be perceived as resources, challenges, or hindrances.
+Finally, there was a moderate relationship between challenges and hindrances, which may be driven by job complexity.
+With more job elements comes increased opportunities for those elements to be perceived as resources, challenges, or hindrances.
 

### 2023-02-18 SIOP2023/Counts/counts_poster.Rmd
Updates to poster

@@
 ---
-title: 'Perception of Work Demands and Resources: Does Sheer Volume Matter?'
+title: 'Perception of Work Demands and Resources: <br />Does Sheer Volume Matter?'
 author:
@@
 .logo_left {
+ padding-top: 0%;
  width: 15%;
@@
 .logo_right {
+ padding-top: 0%;
  width: 15%;
@@
 
-Perhaps not surprisingly, challenge stressors are typically associated with positive outcomes, whereas hindrance stressors are associated with more negative outcomes [e.g., @cavanaugh2000empirical].
-Thus:
+> *Hypothesis 1a-1c*: Quantity of resources is positively associated with engagement (1a), and negatively associated with stress (1b) and burnout (1c)
 
-> *Hypothesis 1a-1c*: A greater overall quantity of resources is positively associated with engagement (1a), and negatively associated with stress (1b) and burnout (1c)
+> *Hypothesis 2a-2c*: Quantity of challenge demands is positively associated with engagement (2a), and negatively associated with stress (2b) and burnout (2c).
 
-> *Hypothesis 2a-2c*: A greater overall quantity of challenge demands is positively associated with engagement (2a), and negatively associated with stress (2b) and burnout (2c).
-
-> *Hypothesis 3a-3c*: A greater overall quantity of hindrance demands is negatively associated with engagement (3a), and positively associated with stress (3b) and burnout (3c).
+> *Hypothesis 3a-3c*: Quantity of hindrance demands is negatively associated with engagement (3a), and positively associated with stress (3b) and burnout (3c).
 
@@
 
-data22$resource <- rowSums(data22[c(118:144,146:202)], na.rm=TRUE)
-data22$hindrance <- rowSums(data22[c(203:247,249:287)], na.rm=TRUE)
-data22$challenge <- rowSums(data22[c(288:307,309:372)], na.rm=TRUE)
+data22$Resource <- rowSums(data22[c(118:144,146:202)], na.rm=TRUE)
+data22$Hindrance <- rowSums(data22[c(203:247,249:287)], na.rm=TRUE)
+data22$Challenge <- rowSums(data22[c(288:307,309:372)], na.rm=TRUE)
 
 data22$item387 <- 7-data22$item387
-data22$burnout      <- rowMeans(data22[c(373:376)], na.rm=TRUE)
-data22$stress       <- rowMeans(data22[c(377:379)], na.rm=TRUE)
-data22$engagement   <- rowMeans(data22[c(380:399)], na.rm=TRUE)        ## probably need to recode some
+data22$Burnout      <- rowMeans(data22[c(373:376)], na.rm=TRUE)
+data22$Stress       <- rowMeans(data22[c(377:379)], na.rm=TRUE)
+data22$Engagement   <- rowMeans(data22[c(380:399)], na.rm=TRUE)        ## probably need to recode some
 
@@
 
-data$resource <- rowSums(data22[c(118:144,146:202)], na.rm=TRUE)
-data$hindrance <- rowSums(data22[c(203:247,249:287)], na.rm=TRUE)
-data$challenge <- rowSums(data22[c(288:307,309:372)], na.rm=TRUE)
+data$Resource <- rowSums(data22[c(118:144,146:202)], na.rm=TRUE)
+data$Hindrance <- rowSums(data22[c(203:247,249:287)], na.rm=TRUE)
+data$Challenge <- rowSums(data22[c(288:307,309:372)], na.rm=TRUE)
 
-data$burnout      <- rowMeans(data22[c(373:376)], na.rm=TRUE)
-data$stress       <- rowMeans(data22[c(377:379)], na.rm=TRUE)
-data$engagement   <- rowMeans(data22[c(380:399)], na.rm=TRUE)        ## probably need to recode some
+data$Burnout      <- rowMeans(data22[c(373:376)], na.rm=TRUE)
+data$Stress       <- rowMeans(data22[c(377:379)], na.rm=TRUE)
+data$Engagement   <- rowMeans(data22[c(380:399)], na.rm=TRUE)        ## probably need to recode some
 
@@
 
-eng <- lm(engagement ~ hindrance + challenge + resource, data22)
-bur <- lm(burnout ~ hindrance + challenge + resource, data22)
-str <- lm(stress ~ hindrance + challenge + resource, data22)
+eng <- lm(Engagement ~ Hindrance + Challenge + Resource, data22)
+bur <- lm(Burnout ~ Hindrance + Challenge + Resource, data22)
+str <- lm(Stress ~ Hindrance + Challenge + Resource, data22)
 
@@
 
-## Limitations & Future Directions 
-Future study could consider additional or other O\*Net items, *kinds* of resources or challenges, additional outcomes (e.g., job satisfaction), or whether volume of resources and demands operationalized in this way are related to other behaviors.
-Finally, there was a moderate relationship between challenges and hindrances, which may be driven by job complexity.
-With more job elements comes increased opportunities for those elements to be perceived as resources, challenges, or hindrances.
+**Limitations & Future Directions.** 
+Future studies could consider additional or other O\*Net items, *kinds* of resources or challenges, additional outcomes (e.g., job satisfaction), or whether volume of resources and demands operationalized in this way are related to other behaviors.
+Finally, there was a moderate relationship between challenges and hindrances, which may be driven by job complexity - with more job elements comes increased opportunities for those elements to be perceived as resources, challenges, or hindrances.
 

### 2023-02-18 SIOP2023/Counts/counts_poster.Rmd
updated poster once more

@@
   posterdown::posterdown_html:
-    self_contained: false
+    self_contained: TRUE
+knit: pagedown::chrome_print
 csl               : "apa7.csl"
@@
 ```
-
 Stress was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$ = 2.47, *p* = .060; see Table \@ref(tab:regressiontablestr).

### 2023-02-21 Submission.Rmd
updating results section

@@
 
->Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
+>Hypothesis 1: Job characteristics differ in constancy regarding subjective worker perception as a demand or resource.
 
->Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are viewed as both a resource and a demand.
+>Hypothesis 2: Job characteristics are not exclusively categorized as a resource or demand, but rather, some job characteristics are viewed as both a resource and a demand.
 
-Two exploratory questions further address whether our *literature-implicated* job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory [@bakker2017job] and challenge-hindrance stressor framework [@cavanaugh2000empirical].
+Two exploratory questions further address whether our *literature-implicated* resources (e.g., autonomy) and demands are consistently rated as our research models suggest across the job-demands resources theory [@bakker2017job] and challenge-hindrance stressor framework [@cavanaugh2000empirical].
 
->*Research Question 1*: Are literature-implicated resources consistently rated as job resources?
+>*Research Question 1*: Do literature-implicated resources materialize as perceived resources?
 
->*Research Question 2*: Are literature-implicated demands consistently rated as job demands?
+>*Research Question 2*: Do literature-implicated demands materialize as job demands?
 
@@
 
-The Occupational Information Network (O\*NET) contains a comprehensive description of occupations [@peterson2001understanding].
-This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated.
-We used 98 statements/questions from O\*NET [activity and context classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3).
-We retained work activity classifications which O\*NET groups into categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
-Work context statements were grouped into interpersonal relationships (i.e., this category describes the context of the job in terms of human interaction processes), physical work conditions (i.e., this category describes the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., this category involves the relationships or interactions between the worker and the structural characteristics of the job).
+The Occupational Information Network (O\*Net) contains a comprehensive description of occupations [@peterson2001understanding].
+This widely accessed database houses hundreds of standardized and occupation-specific descriptors of most occupations in the US and these descriptions are continually updated.
+We retained 98 work [activity and context classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*Net groups into categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
+Work context statements were grouped into interpersonal relationships (i.e., the context of the job in terms of human interaction processes), physical work conditions (i.e., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., the relationships or interactions between the worker and the structural characteristics of the job).
 
-O\*NET collects information about these categories by periodically asking workers about these statements/questions, which often have [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).
+O\*Net collects information about these categories by periodically asking workers about these statements/questions, which often have [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).
 For example, "How responsible is the worker for work outcomes and results of other workers?" has response options ranging from *No responsibility* to *Very high responsibility*, while the question, "How often do you use electronic mail in this job?" has options ranging from *Never* to *Every day*.
-We retained O\*Net’s response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
-It would likely NOT be considered controversial to referred to these as "effectively" Likert-type response scales.
+We retained O\*Net’s response scales, all of which shared the same 5-point scale regardless of semantic label difference.
 Other than minor grammatical editing (for example, changing “the worker” to “you”), we also retained the O\*Net wording for our item stems (statements/questions).
-
-The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
 
@@
 Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (i.e., ...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (i.e., ...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (i.e., ...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
-Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
+The total number of items on the survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
 
@@
 
-The first hypothesis asks whether job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
-Figure \@ref(fig:overallhist) presents frequency distributions standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand.
-As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's $\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* = `r lookie$p.value` ).
+The first hypothesis asks whether job characteristics differ in constancy regarding subjective worker perception as a demand or resource.
 
@@
 In sum, these results provide some support for H1, particularly for hindrances, which are consistently viewed as "different".
+
+Figure \@ref(fig:overallhist) shows that hindrances tend to exhibit similar levels of variability across items.
+Challenges and resources, however, exhibit items that are rated more similary across people (note the spread of the challenge and resource histograms relative to the hindrance histogram).
+A Bartlett's test for homogeneity of variance confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* = `r lookie$p.value` ).
 

### 2023-02-21 Submission.tex
updating results section

--- 2023-02-12 Submission.tex
@@
 \begin{quote}
-Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
+Hypothesis 1: Job characteristics differ in constancy regarding subjective worker perception as a demand or resource.
 \end{quote}
@@
 \begin{quote}
-Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are viewed as both a resource and a demand.
+Hypothesis 2: Job characteristics are not exclusively categorized as a resource or demand, but rather, some job characteristics are viewed as both a resource and a demand.
 \end{quote}
 
-Two exploratory questions further address whether our \emph{literature-implicated} job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory (Bakker \& Demerouti, 2017) and challenge-hindrance stressor framework (Cavanaugh et al., 2000).
+Two exploratory questions further address whether our \emph{literature-implicated} resources (e.g., autonomy) and demands are consistently rated as our research models suggest across the job-demands resources theory (Bakker \& Demerouti, 2017) and challenge-hindrance stressor framework (Cavanaugh et al., 2000).
 
 \begin{quote}
-\emph{Research Question 1}: Are literature-implicated resources consistently rated as job resources?
+\emph{Research Question 1}: Do literature-implicated resources materialize as perceived resources?
 \end{quote}
@@
 \begin{quote}
-\emph{Research Question 2}: Are literature-implicated demands consistently rated as job demands?
+\emph{Research Question 2}: Do literature-implicated demands materialize as job demands?
 \end{quote}
@@
 
-The Occupational Information Network (O*NET) contains a comprehensive description of occupations (Peterson et al., 2001).
-This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated.
-We used 98 statements/questions from O*NET \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context classifications}.
-We retained work activity classifications which O*NET groups into categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
-Work context statements were grouped into interpersonal relationships (i.e., this category describes the context of the job in terms of human interaction processes), physical work conditions (i.e., this category describes the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., this category involves the relationships or interactions between the worker and the structural characteristics of the job).
+The Occupational Information Network (O*Net) contains a comprehensive description of occupations (Peterson et al., 2001).
+This widely accessed database houses hundreds of standardized and occupation-specific descriptors of most occupations in the US and these descriptions are continually updated.
+We retained 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context classifications} which O*Net groups into categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
+Work context statements were grouped into interpersonal relationships (i.e., the context of the job in terms of human interaction processes), physical work conditions (i.e., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., the relationships or interactions between the worker and the structural characteristics of the job).
 
-O*NET collects information about these categories by periodically asking workers about these statements/questions, which often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}.
+O*Net collects information about these categories by periodically asking workers about these statements/questions, which often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}.
 For example, ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{No responsibility} to \emph{Very high responsibility}, while the question, ``How often do you use electronic mail in this job?'' has options ranging from \emph{Never} to \emph{Every day}.
-We retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
-It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.
+We retained O*Net's response scales, all of which shared the same 5-point scale regardless of semantic label difference.
 Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we also retained the O*Net wording for our item stems (statements/questions).
-
-The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
 
@@
 Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (i.e., \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (i.e., \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (i.e., \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
-Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
+The total number of items on the survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
 
@@
 
-The first hypothesis asks whether job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
-Figure \ref{fig:overallhist} presents frequency distributions standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand.
-As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's \(K^2\) = 76.83, \emph{p} = 0.00 ).
+The first hypothesis asks whether job characteristics differ in constancy regarding subjective worker perception as a demand or resource.
 
@@
 In sum, these results provide some support for H1, particularly for hindrances, which are consistently viewed as ``different.''
+
+Figure \ref{fig:overallhist} shows that hindrances tend to exhibit similar levels of variability across items.
+Challenges and resources, however, exhibit items that are rated more similary across people (note the spread of the challenge and resource histograms relative to the hindrance histogram).
+A Bartlett's test for homogeneity of variance confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} = 0.00 ).
 

### 2023-02-22 Submission.Rmd
more edits to the results
saved changes
updating language for the results section

@@
 
-The first hypothesis asks whether job characteristics differ in constancy regarding subjective worker perception as a demand or resource.
-
 ```{r resourcesagree, fig.cap="Characteristics most similarly viewed as resources (lowest standard deviations)."}
@@
 
-Figure \@ref(fig:combinegraphs) presents resources, challenges, and hindrances that are *largely agreed on* as indexed by (relatively) low standard deviations.[^caveat] There are only 8 characteristics presented per perceived category because of limited space.
+H1 proposes that job characteristics differ in constancy regarding subjective worker perception as a demand or resource.
+We explore this hypothesis first by item, and then present a more holistic picture.
+First considering item-level characteristics, we present means and standard deviations visually, focusing on the items highest and lowest in variability.
+Figure \@ref(fig:combinegraphs) presents the top 8 resources, challenges, and hindrances characteristics that are *largely agreed on* as indexed by (relatively) low standard deviations.[^caveat] Note that the presentation is limited to 8 characteristics per perceived category only because of limited space.
 All sortable ratings are available in the online resources.
 
+Figures 2 and 3 present only a snapshot - full list available in online resources. 
 [^caveat]: There were a few characteristics with standard deviations of "zero" but these were excluded from presentation as they were likely representing only one person (*n*'s should also go on these graphs if they're retained - Alicia's idea 12/2 was to use initial ratings as indicators of counts).
@@
 
-As can be seen by the graphs, there is considerable disagreement regarding the degree to which job elements are considered *hindrances*, with the 8 elements showing the greatest agreement still ranging in standard deviations from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`.
-What is widely seen as a resource and challenge tends to be more universally agreed upon (range of lowest 8 resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`.
+As can be seen in the figures, what is widely seen as a resource and challenge tends to be somewhat agreed upon (range of lowest 8 resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`.
+However, there is considerable disagreement regarding the degree to which job elements are considered *hindrances*, with the 8 elements showing the greatest agreement still ranging in standard deviations from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`.
 
@@
 
-Figure \@ref(fig:combinegraphs2) presents the resources, challenges, and hindrances that are *largely disagreed on* as indexed by (relatively) high standard deviations (these are the 8 characteristics with the greatest variability in rating).
+Next, we explore the items with the highest variability in perceptions as resources, challenges, and hindrances.
+Figure \@ref(fig:combinegraphs2) presents the resources, challenges, and hindrances that are *largely disagreed on* as indexed by (relatively) high standard deviations.
+Stated another way, these are the 8 characteristics with the greatest variability in rating.
 In sum, these results provide some support for H1, particularly for hindrances, which are consistently viewed as "different".
 
+In addition to highlighting specific items, we also look at the pattern more holistically.
 Figure \@ref(fig:overallhist) shows that hindrances tend to exhibit similar levels of variability across items.

### 2023-02-22 Submission.tex
updating language for the results section

@@
 
-Figure \ref{fig:combinegraphs} presents resources, challenges, and hindrances that are \emph{largely agreed on} as indexed by (relatively) low standard deviations.\footnote{There were a few characteristics with standard deviations of ``zero'' but these were excluded from presentation as they were likely representing only one person (\emph{n}'s should also go on these graphs if they're retained - Alicia's idea 12/2 was to use initial ratings as indicators of counts).} There are only 8 characteristics presented per perceived category because of limited space.
+Figure \ref{fig:combinegraphs} presents resources, challenges, and hindrances that are \emph{largely agreed on} as indexed by (relatively) low standard deviations.{[}\^{}caveat{]} There are only 8 characteristics presented per perceived category because of limited space.
 All sortable ratings are available in the online resources.
+
+Figures 2 and 3 present only a snapshot - full list available in online resources.
+{[}\^{}caveat{]}: There were a few characteristics with standard deviations of ``zero'' but these were excluded from presentation as they were likely representing only one person (\emph{n}'s should also go on these graphs if they're retained - Alicia's idea 12/2 was to use initial ratings as indicators of counts).
 

### 2023-02-22 SIOP2023/Counts/counts_poster.Rmd
Updated poster spacing

--- 2023-02-18 SIOP2023/Counts/counts_poster.Rmd
@@
 affiliation_textsize: "50pt"
-body_textsize: "48px"
+body_textsize: "50px"
 title_textsize:	"75pt"	
@@
 
-We also conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
+<br />In addition to the above correlations, we also conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
 The total resources were predictive of engagement ($F_{(3, 564)}$ = 26.41, p < .001), but neither challenge nor hindrance demands predicted engagement; see Table \@ref(tab:regressiontableeng).

### 2023-02-24 SIOP2023/Counts/counts_poster.Rmd
final poster edits (prior to printing)

@@
 
-> *Hypothesis 1a-1c*: Quantity of resources is positively associated with engagement (1a), and negatively associated with stress (1b) and burnout (1c)
+> *Hypotheses 1a-1c*: Quantity of resources is positively associated with engagement (1a), and negatively associated with stress (1b) and burnout (1c)
 
-> *Hypothesis 2a-2c*: Quantity of challenge demands is positively associated with engagement (2a), and negatively associated with stress (2b) and burnout (2c).
+> *Hypotheses 2a-2c*: Quantity of challenge demands is positively associated with engagement (2a), and negatively associated with stress (2b) and burnout (2c).
 
-> *Hypothesis 3a-3c*: Quantity of hindrance demands is negatively associated with engagement (3a), and positively associated with stress (3b) and burnout (3c).
+> *Hypotheses 3a-3c*: Quantity of hindrance demands is negatively associated with engagement (3a), and positively associated with stress (3b) and burnout (3c).
 
@@
 
-Three items taken from the Copenhagen Psychosocial Questionnaire [@burr_third_2019] to capture stress.
-Obtained alpha was .85 in this sample.
+Three items taken from the Copenhagen Psychosocial Questionnaire [@burr_third_2019] capture stress.
+The obtained alpha was .85 in this sample.
 Four items were taken from the Copenhagen Psychosocial Questionnaire [@burr_third_2019] to capture burnout.
@@
 <br />In addition to the above correlations, we also conducted three regression analyses: regressing a) engagement, b) stress, and c) burnout separately onto total resources, challenge and hindrance demands.
-The total resources were predictive of engagement ($F_{(3, 564)}$ = 26.41, p < .001), but neither challenge nor hindrance demands predicted engagement; see Table \@ref(tab:regressiontableeng).
+The total resources were predictive of engagement ($F_{(3, 564)}$ = 26.41, p < .001, $R^2$ = .12), but neither challenge nor hindrance demands predicted engagement; see Table \@ref(tab:regressiontableeng).
 
@@
 
-Stress was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$ = 2.47, *p* = .060; see Table \@ref(tab:regressiontablestr).
+Stress was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$ = 2.47, *p* = .060, $R^2$ = .01; see Table \@ref(tab:regressiontablestr).
 
@@
 
-Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$= 1.10, *p* = .349. See Table \@ref(tab:regressiontablebur).
+Similarly, burnout was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$= 1.10, *p* = .349, $R^2$ = .01; See Table \@ref(tab:regressiontablebur).
 

### 2023-02-24 Submission.Rmd
got rid of "n" caveat regarding low SD items (2/22 check verified hundreds of ratings per item)

@@
 First considering item-level characteristics, we present means and standard deviations visually, focusing on the items highest and lowest in variability.
-Figure \@ref(fig:combinegraphs) presents the top 8 resources, challenges, and hindrances characteristics that are *largely agreed on* as indexed by (relatively) low standard deviations.[^caveat] Note that the presentation is limited to 8 characteristics per perceived category only because of limited space.
+Figure \@ref(fig:combinegraphs) presents the top 8 resources, challenges, and hindrances characteristics that are *largely agreed on* as indexed by (relatively) low standard deviations.
+Note that the presentation is limited to 8 characteristics per perceived category only because of limited space.
 All sortable ratings are available in the online resources.
@@
 Figures 2 and 3 present only a snapshot - full list available in online resources.
-[^caveat]: There were a few characteristics with standard deviations of "zero" but these were excluded from presentation as they were likely representing only one person (*n*'s should also go on these graphs if they're retained - Alicia's idea 12/2 was to use initial ratings as indicators of counts).
 

### 2023-02-24 Submission.tex
got rid of "n" caveat regarding low SD items (2/22 check verified hundreds of ratings per item)

@@
 
-The first hypothesis asks whether job characteristics differ in constancy regarding subjective worker perception as a demand or resource.
-
-Figure \ref{fig:combinegraphs} presents resources, challenges, and hindrances that are \emph{largely agreed on} as indexed by (relatively) low standard deviations.{[}\^{}caveat{]} There are only 8 characteristics presented per perceived category because of limited space.
+H1 proposes that job characteristics differ in constancy regarding subjective worker perception as a demand or resource.
+We explore this hypothesis first by item, and then present a more holistic picture.
+First considering item-level characteristics, we present means and standard deviations visually, focusing on the items highest and lowest in variability.
+Figure \ref{fig:combinegraphs} presents the top 8 resources, challenges, and hindrances characteristics that are \emph{largely agreed on} as indexed by (relatively) low standard deviations.
+Note that the presentation is limited to 8 characteristics per perceived category only because of limited space.
 All sortable ratings are available in the online resources.
@@
 Figures 2 and 3 present only a snapshot - full list available in online resources.
-{[}\^{}caveat{]}: There were a few characteristics with standard deviations of ``zero'' but these were excluded from presentation as they were likely representing only one person (\emph{n}'s should also go on these graphs if they're retained - Alicia's idea 12/2 was to use initial ratings as indicators of counts).
 
@@
 
-As can be seen by the graphs, there is considerable disagreement regarding the degree to which job elements are considered \emph{hindrances}, with the 8 elements showing the greatest agreement still ranging in standard deviations from 1.12 to 1.16.
-What is widely seen as a resource and challenge tends to be more universally agreed upon (range of lowest 8 resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86.
+As can be seen in the figures, what is widely seen as a resource and challenge tends to be somewhat agreed upon (range of lowest 8 resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86.
+However, there is considerable disagreement regarding the degree to which job elements are considered \emph{hindrances}, with the 8 elements showing the greatest agreement still ranging in standard deviations from 1.12 to 1.16.
 
@@
 
-Figure \ref{fig:combinegraphs2} presents the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations (these are the 8 characteristics with the greatest variability in rating).
-In sum, these results provide some support for H1, particularly for hindrances, which are consistently viewed as ``different.''
+Next, we explore the items with the highest variability in perceptions as resources, challenges, and hindrances.
+Figure \ref{fig:combinegraphs2} presents the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations.
+Stated another way, these are the 8 characteristics with the greatest variability in rating.
+In sum, these results provide some support for H1, particularly for hindrances, which are consistently viewed as ``different''.
 
+In addition to highlighting specific items, we also look at the pattern more holistically.
 Figure \ref{fig:overallhist} shows that hindrances tend to exhibit similar levels of variability across items.

### 2023-02-28 Submission.Rmd
Tuesday meeting updates (mostly results)

@@
 
->Hypothesis 1: Job characteristics differ in constancy regarding subjective worker perception as a demand or resource.
+>Hypothesis 1: Job characteristics differ in consistancy regarding subjective worker perception as a demand or resource.
 
@@
 The Occupational Information Network (O\*Net) contains a comprehensive description of occupations [@peterson2001understanding].
-This widely accessed database houses hundreds of standardized and occupation-specific descriptors of most occupations in the US and these descriptions are continually updated.
-We retained 98 work [activity and context classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*Net groups into categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
-Work context statements were grouped into interpersonal relationships (i.e., the context of the job in terms of human interaction processes), physical work conditions (i.e., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., the relationships or interactions between the worker and the structural characteristics of the job).
+This widely accessed database houses hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are continually updated.
+We retained 98 work [activity and context classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*Net groups into *activity* categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
+Work *context* statements are grouped into interpersonal relationships (i.e., the context of the job in terms of human interaction processes), physical work conditions (i.e., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., the relationships or interactions between the worker and the structural characteristics of the job).
 
-O\*Net collects information about these categories by periodically asking workers about these statements/questions, which often have [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).
+O\*Net collects information about these categories by periodically asking workers job characteristic statements/questions, which often have [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).
 For example, "How responsible is the worker for work outcomes and results of other workers?" has response options ranging from *No responsibility* to *Very high responsibility*, while the question, "How often do you use electronic mail in this job?" has options ranging from *Never* to *Every day*.
@@
 Eligibility requirements included being 18+ and holding either a full-time or part-time job.
-Participants then voluntarily chose to respond to the survey.
-The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes.
+Participants then voluntarily chose to respond to the online survey.
 Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified.
 Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (i.e., ...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (i.e., ...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (i.e., ...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
-The total number of items on the survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
+The total number of items on the survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
+Participants were compensated for their participation in this study estimated to require 45 minutes' time in the amount of six dollars through Prolific.
 
@@
 
-H1 proposes that job characteristics differ in constancy regarding subjective worker perception as a demand or resource.
+H1 proposes that job characteristics differ in consistancy regarding subjective worker perception as a demand or resource.
 We explore this hypothesis first by item, and then present a more holistic picture.
@@
 Challenge and resource are strongly and positively related.
-These results provide support for H2 suggesting that there is overlap in how employees perceive job characteristics.
+These results provide support for H2 suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is percieved as a *resource* being also percieved as a *challenge*.
 Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.
@@
 
-In addition to the two hypotheses, three related research questions were proposed.
-To answer these research questions, authors first categorized items into the categories listed in the JD-R literature.
+In addition to the two hypotheses, two related research questions were proposed.
+To answer these research questions, authors first categorized items into the JD-R elements listed in the JD-R literature.
 For example, autonomy is frequently described as a resource.
 An O\*Net item in the autonomy category is, “How much decision making freedom, without supervision, does your job offer?”.
-Means for resources, challenges, and hindrances groupings were then computed to explore whether literature-implicated resources and demands were consistently rated as such.
+This O\*Net item was therefore retained within the "autonomy" category.
+Means for resource, challenge, and hindrance groupings were then computed to explore whether literature-implicated resources and demands were evaluated as such.
 The left side of Figure 4 shows literature-derived demand categories (e.g., work pressure).
-Here, we do not see a clear pattern of high ratings as hindrances for these demands.
-In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much more variability in how employees rated what should objectively be "hindrances" at work.
+Here, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as "high" gray and black bars and "low" white bars).
+In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be "hindrances" at work.
 However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings.
@@
 
-\newpage
-
-NOTE: Add a table of the items (probably the full list and those we included in challenge, hindrance specifically). Could also have a column showing which items were used for Figure 4 categories.
-
 # Discussion

### 2023-02-28 Submission.tex
Tuesday meeting updates (mostly results)

@@
 \begin{quote}
-Hypothesis 1: Job characteristics differ in constancy regarding subjective worker perception as a demand or resource.
+Hypothesis 1: Job characteristics differ in consistancy regarding subjective worker perception as a demand or resource.
 \end{quote}
@@
 The Occupational Information Network (O*Net) contains a comprehensive description of occupations (Peterson et al., 2001).
-This widely accessed database houses hundreds of standardized and occupation-specific descriptors of most occupations in the US and these descriptions are continually updated.
-We retained 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context classifications} which O*Net groups into categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
-Work context statements were grouped into interpersonal relationships (i.e., the context of the job in terms of human interaction processes), physical work conditions (i.e., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., the relationships or interactions between the worker and the structural characteristics of the job).
+This widely accessed database houses hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are continually updated.
+We retained 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context classifications} which O*Net groups into \emph{activity} categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
+Work \emph{context} statements are grouped into interpersonal relationships (i.e., the context of the job in terms of human interaction processes), physical work conditions (i.e., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., the relationships or interactions between the worker and the structural characteristics of the job).
 
-O*Net collects information about these categories by periodically asking workers about these statements/questions, which often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}.
+O*Net collects information about these categories by periodically asking workers job characteristic statements/questions, which often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}.
 For example, ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{No responsibility} to \emph{Very high responsibility}, while the question, ``How often do you use electronic mail in this job?'' has options ranging from \emph{Never} to \emph{Every day}.
@@
 Eligibility requirements included being 18+ and holding either a full-time or part-time job.
-Participants then voluntarily chose to respond to the survey.
-The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes.
+Participants then voluntarily chose to respond to the online survey.
 Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified.
 Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (i.e., \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (i.e., \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (i.e., \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
-The total number of items on the survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
+The total number of items on the survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
+Participants were compensated for their participation in this study estimated to require 45 minutes' time in the amount of six dollars through Prolific.
 
@@
 Challenge and resource are strongly and positively related.
-These results provide support for H2 suggesting that there is overlap in how employees perceive job characteristics.
+These results provide support for H2 suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is percieved as a \emph{resource} being also percieved as a \emph{challenge}.
 Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.
@@
 
-In addition to the two hypotheses, three related research questions were proposed.
-To answer these research questions, authors first categorized items into the categories listed in the JD-R literature.
+In addition to the two hypotheses, two related research questions were proposed.
+To answer these research questions, authors first categorized items into the JD-R elements listed in the JD-R literature.
 For example, autonomy is frequently described as a resource.
 An O*Net item in the autonomy category is, ``How much decision making freedom, without supervision, does your job offer?''.
-Means for resources, challenges, and hindrances groupings were then computed to explore whether literature-implicated resources and demands were consistently rated as such.
+This O*Net item was therefore retained within the ``autonomy'' category.
+Means for resource, challenge, and hindrance groupings were then computed to explore whether literature-implicated resources and demands were evaluated as such.
 The left side of Figure 4 shows literature-derived demand categories (e.g., work pressure).
-Here, we do not see a clear pattern of high ratings as hindrances for these demands.
-In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much more variability in how employees rated what should objectively be ``hindrances'' at work.
+Here, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as ``high'' gray and black bars and ``low'' white bars).
+In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be ``hindrances'' at work.
 However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings.
@@
 Across categories, resources were rated the highest (see white bars representing resources in Figure 4).
-
-\newpage
-
-NOTE: Add a table of the items (probably the full list and those we included in challenge, hindrance specifically). Could also have a column showing which items were used for Figure 4 categories.
 

### 2023-02-28 Submission.Rmd
figures fixed w/ SD proper in text

@@
 
-```{r overallhist, fig.cap="Frequency distribution of standard deviations across characteristics deemed resources, challenges, and demands."}
-
-## resource$sd
-
-toplotresource <- resource
-toplotchallenge <- challenge
-toplothindrance <- hindrance
-
-toplotresource$RD <- "Resource"
-toplotchallenge$RD <- "Challenge"
-toplothindrance$RD <- "Hindrance"
-
-toplottogether <- rbind(toplotresource,toplotchallenge,toplothindrance)
-
-library(ggplot2)
-#ggplot(resource, aes(x=sd)) + geom_histogram()
-ggplot(toplottogether, aes(x=sd)) + geom_histogram() + facet_grid(RD ~ .)
-
-lookie <- stats::bartlett.test(sd ~ RD, toplottogether)
-
-```
-
 ```{r resourcesagree, fig.cap="Characteristics most similarly viewed as resources (lowest standard deviations)."}
@@
 
-H1 proposes that job characteristics differ in consistancy regarding subjective worker perception as a demand or resource.
-We explore this hypothesis first by item, and then present a more holistic picture.
-First considering item-level characteristics, we present means and standard deviations visually, focusing on the items highest and lowest in variability.
-Figure \@ref(fig:combinegraphs) presents the top 8 resources, challenges, and hindrances characteristics that are *largely agreed on* as indexed by (relatively) low standard deviations.
-Note that the presentation is limited to 8 characteristics per perceived category only because of limited space.
-All sortable ratings are available in the online resources.
-
-Figures 2 and 3 present only a snapshot - full list available in online resources.
-
 ```{r combinegraphs, fig.cap="Characteristics percieved most similarly (lowest standard deviations).", fig.height=10}
@@
 
-As can be seen in the figures, what is widely seen as a resource and challenge tends to be somewhat agreed upon (range of lowest 8 resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`.
-However, there is considerable disagreement regarding the degree to which job elements are considered *hindrances*, with the 8 elements showing the greatest agreement still ranging in standard deviations from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`.
-
 ```{r resourcesdisagree, fig.cap="Characteristics most *dis*similarly viewed as resources (highest standard deviations)."}
@@
 
-topresource <- head(sortresource, 8)
+bottomresource <- head(sortresource, 8)
 
-topresource <- topresource[tail(names(topresource),3)]
+bottomresource <- bottomresource[tail(names(bottomresource),3)]
 
-d <- ggplot(topresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
+d <- ggplot(bottomresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
   scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed Upon as a Resource") + 
@@
 
-topchallenge <- head(sortchallenge, 8)
+bottomchallenge <- head(sortchallenge, 8)
 
-topchallenge <- topchallenge[tail(names(topchallenge),3)]
+bottomchallenge <- bottomchallenge[tail(names(bottomchallenge),3)]
 
-e <- ggplot(topchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
+e <- ggplot(bottomchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
   scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed Upon as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
@@
 
-tophindrance <- head(sorthindrance, 8)
+bottomhindrance <- head(sorthindrance, 8)
 
-tophindrance <- tophindrance[tail(names(tophindrance),3)]
+bottomhindrance <- bottomhindrance[tail(names(bottomhindrance),3)]
 
-f <- ggplot(tophindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
+f <- ggplot(bottomhindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
   scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed upon as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
@@
 ```
+
+```{r overallhist, fig.cap="Frequency distribution of standard deviations across characteristics deemed resources, challenges, and demands."}
+
+## resource$sd
+
+toplotresource <- resource
+toplotchallenge <- challenge
+toplothindrance <- hindrance
+
+toplotresource$RD <- "Resource"
+toplotchallenge$RD <- "Challenge"
+toplothindrance$RD <- "Hindrance"
+
+toplottogether <- rbind(toplotresource,toplotchallenge,toplothindrance)
+
+library(ggplot2)
+#ggplot(resource, aes(x=sd)) + geom_histogram()
+ggplot(toplottogether, aes(x=sd)) + geom_histogram() + facet_grid(RD ~ .)
+
+lookie <- stats::bartlett.test(sd ~ RD, toplottogether)
+
+```
+
+H1 proposes that job characteristics differ in consistancy regarding subjective worker perception as a demand or resource.
+We explore this hypothesis first by item, and then present a more holistic picture.
+First considering item-level characteristics, we present means and standard deviations visually, focusing on the items highest and lowest in variability.
+Figure \@ref(fig:combinegraphs) presents the top 8 resources, challenges, and hindrances characteristics that are *largely agreed on* as indexed by (relatively) low standard deviations.
+Note that the presentation is limited to 8 characteristics per perceived category only because of limited space.
+All sortable ratings are available in the online resources.
+
+Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present only a snapshot - full list available in online resources.
+
+As can be seen in the figures, what is widely seen as a resource and challenge tends to be somewhat agreed upon (range of lowest 8 resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`.
+However, there is considerable disagreement regarding the degree to which job elements are considered hindrances, with the 8 elements showing the *greatest agreement* still ranging in standard deviations from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`.
 
@@
 
-```{r cortab}
+```{r cortab, results="asis"}
 
@@
                   escape = FALSE, 
-                  font_size = "small", 
+                  font_size = "small",  ## "tiny" smallest
+                  longtable = TRUE,
                   landscape = TRUE,
+#                  stub_indents = list(a=1:10, b = 11:21),
                   note = "The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)")
@@
 The findings broadly revealed that there was relatively more consistency in ratings of resources and challenges characteristics, and far more variability in job characteristics rated as hindrance stressors.
-This finding lends additional evidence to Horan et al.’s (2020) conclusion that “...stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p.
+This finding lends additional evidence to @horan2020review’s conclusion that “...stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p.
 3).
@@
 Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a “resource” or “demand”.
+
 These results have implications for managers as well.

### 2023-02-28 Submission.tex
figures fixed w/ SD proper in text

@@
 \centering
+\includegraphics{Submission_files/figure-latex/combinegraphs-1.pdf}
+\caption{\label{fig:combinegraphs}Characteristics percieved most similarly (lowest standard deviations).}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Submission_files/figure-latex/combinegraphs2-1.pdf}
+\caption{\label{fig:combinegraphs2}Characteristics percieved most \emph{DIS}similarly (lowest standard deviations).}
+\end{figure}
+
+\begin{figure}
+\centering
 \includegraphics{Submission_files/figure-latex/overallhist-1.pdf}
@@
 
-Figures 2 and 3 present only a snapshot - full list available in online resources.
-
-\begin{figure}
-\centering
-\includegraphics{Submission_files/figure-latex/combinegraphs-1.pdf}
-\caption{\label{fig:combinegraphs}Characteristics percieved most similarly (lowest standard deviations).}
-\end{figure}
+Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present only a snapshot - full list available in online resources.
 
@@
 However, there is considerable disagreement regarding the degree to which job elements are considered \emph{hindrances}, with the 8 elements showing the greatest agreement still ranging in standard deviations from 1.12 to 1.16.
-
-\begin{figure}
-\centering
-\includegraphics{Submission_files/figure-latex/combinegraphs2-1.pdf}
-\caption{\label{fig:combinegraphs2}Characteristics percieved most \emph{DIS}similarly (lowest standard deviations).}
-\end{figure}
 
@@
 The findings broadly revealed that there was relatively more consistency in ratings of resources and challenges characteristics, and far more variability in job characteristics rated as hindrance stressors.
-This finding lends additional evidence to Horan et al.'s (2020) conclusion that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3).
+This finding lends additional evidence to Horan et al.
+(2020)'s conclusion that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3).
 The research questions regarding the match between literature-implicated demand and resource categories and empirical ratings aligns with the consistency/variability we observed in H1.
@@
 Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a ``resource'' or ``demand''.
+
 These results have implications for managers as well.

### 2023-03-01 Submission.Rmd
hyptothesis 1 and figures good to go (Kulas perspective)

@@
 
-H1 proposes that job characteristics differ in consistancy regarding subjective worker perception as a demand or resource.
-We explore this hypothesis first by item, and then present a more holistic picture.
-First considering item-level characteristics, we present means and standard deviations visually, focusing on the items highest and lowest in variability.
-Figure \@ref(fig:combinegraphs) presents the top 8 resources, challenges, and hindrances characteristics that are *largely agreed on* as indexed by (relatively) low standard deviations.
-Note that the presentation is limited to 8 characteristics per perceived category only because of limited space.
-All sortable ratings are available in the online resources.
+H1 posits that static job characteristics are not necessarily always experienced similarly across workers - as hindrances, challenges, or resources.
+We explore this hypothesis first at the job characteristic level before presenting a broader perspective.
+Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present only extreme snapshots of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency.
+Figure \@ref(fig:combinegraphs) presents the resources, challenges, and hindrances characteristics that are *most consistently agreed on* as indexed by (relatively) low standard deviations, while Figure \@ref(fig:combinegraphs2) presents the characteristics with the greatest amount of *disagreement* across workers.
 
-Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present only a snapshot - full list available in online resources.
+ [^onlinelist]: A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
+The Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2)  presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).
 
-As can be seen in the figures, what is widely seen as a resource and challenge tends to be somewhat agreed upon (range of lowest 8 resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`.
-However, there is considerable disagreement regarding the degree to which job elements are considered hindrances, with the 8 elements showing the *greatest agreement* still ranging in standard deviations from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`.
+As can be seen in the figures, what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
+However, there is considerable less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`).
 
-Next, we explore the items with the highest variability in perceptions as resources, challenges, and hindrances.
-Figure \@ref(fig:combinegraphs2) presents the resources, challenges, and hindrances that are *largely disagreed on* as indexed by (relatively) high standard deviations.
-Stated another way, these are the 8 characteristics with the greatest variability in rating.
-In sum, these results provide some support for H1, particularly for hindrances, which are consistently viewed as "different".
-
-In addition to highlighting specific items, we also look at the pattern more holistically.
-Figure \@ref(fig:overallhist) shows that hindrances tend to exhibit similar levels of variability across items.
-Challenges and resources, however, exhibit items that are rated more similary across people (note the spread of the challenge and resource histograms relative to the hindrance histogram).
-A Bartlett's test for homogeneity of variance confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* = `r lookie$p.value` ).
+In addition to highlighting extremely agreed- or disagreed-upon items, Figure \@ref(fig:overallhist) presents our standard deviation indices across all rated items.
+Here, the Figure \@ref(fig:combinegraphs) discrepancies recieve illumination, with the *spread* of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively *bunched* levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
+Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
+This points to *hindrances*, in particular, as being likely amenable to future probing regarding moderating conditions.
+A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* = `r lookie$p.value` ).
+In sum, these results provide some collective support for H1, and  particularly so for hindrances, which are consistently viewed as "different".
 

### 2023-03-01 Submission.tex
hyptothesis 1 and figures good to go (Kulas perspective)

@@
 
-H1 proposes that job characteristics differ in consistancy regarding subjective worker perception as a demand or resource.
-We explore this hypothesis first by item, and then present a more holistic picture.
-First considering item-level characteristics, we present means and standard deviations visually, focusing on the items highest and lowest in variability.
-Figure \ref{fig:combinegraphs} presents the top 8 resources, challenges, and hindrances characteristics that are \emph{largely agreed on} as indexed by (relatively) low standard deviations.
-Note that the presentation is limited to 8 characteristics per perceived category only because of limited space.
-All sortable ratings are available in the online resources.
+H1 posits that static job characteristics are not necessarily always experienced similarly across workers - as hindrances, challenges, or resources.
+We explore this hypothesis first at the job characteristic level before presenting a broader perspective.
+Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present only extreme snapshots of characteristic variability in the form of the 8-most \emph{consistently rated} and \emph{inconsistently rated} resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
+The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency.
+Figure \ref{fig:combinegraphs} presents the resources, challenges, and hindrances characteristics that are \emph{most consistently agreed on} as indexed by (relatively) low standard deviations, while Figure \ref{fig:combinegraphs2} presents the characteristics with the greatest amount of \emph{disagreement} across workers.
 
-Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present only a snapshot - full list available in online resources.
+As can be seen in the figures, what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
+However, there is considerable less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16).
 
-As can be seen in the figures, what is widely seen as a resource and challenge tends to be somewhat agreed upon (range of lowest 8 resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86.
-However, there is considerable disagreement regarding the degree to which job elements are considered \emph{hindrances}, with the 8 elements showing the greatest agreement still ranging in standard deviations from 1.12 to 1.16.
-
-Next, we explore the items with the highest variability in perceptions as resources, challenges, and hindrances.
-Figure \ref{fig:combinegraphs2} presents the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations.
-Stated another way, these are the 8 characteristics with the greatest variability in rating.
-In sum, these results provide some support for H1, particularly for hindrances, which are consistently viewed as ``different''.
-
-In addition to highlighting specific items, we also look at the pattern more holistically.
-Figure \ref{fig:overallhist} shows that hindrances tend to exhibit similar levels of variability across items.
-Challenges and resources, however, exhibit items that are rated more similary across people (note the spread of the challenge and resource histograms relative to the hindrance histogram).
-A Bartlett's test for homogeneity of variance confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} = 0.00 ).
+In addition to highlighting extremely agreed- or disagreed-upon items, Figure \ref{fig:overallhist} presents our standard deviation indices across all rated items.
+Here, the Figure \ref{fig:combinegraphs} discrepancies recieve illumination, with the \emph{spread} of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively \emph{bunched} levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
+Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
+This points to \emph{hindrances}, in particular, as being likely amenable to future probing regarding moderating conditions.
+A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} = 0.00 ).
+In sum, these results provide some collective support for H1, and particularly so for hindrances, which are consistently viewed as ``different''.
 

### 2023-03-01 Submission.Rmd
edits made to RQ1 and RQ2.

@@
 
-In addition to the two hypotheses, two related research questions were proposed.
-To answer these research questions, authors first categorized items into the JD-R elements listed in the JD-R literature.
-For example, autonomy is frequently described as a resource.
-An O\*Net item in the autonomy category is, “How much decision making freedom, without supervision, does your job offer?”.
-This O\*Net item was therefore retained within the "autonomy" category.
-Means for resource, challenge, and hindrance groupings were then computed to explore whether literature-implicated resources and demands were evaluated as such.
-The left side of Figure 4 shows literature-derived demand categories (e.g., work pressure).
-Here, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as "high" gray and black bars and "low" white bars).
-In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be "hindrances" at work.
-However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings.
-The white bars representing resources are consistently higher.
-In sum, these results provide some support for RQ 1 and 2.
-
 ```{r ANOVAs}
@@
 
-Separate repeated-measures ANOVAs were conducted for each of these comparisons.
+In addition to the two hypotheses, two related research questions were proposed: 1) do literature-implicated resources materialize as perceived resources and 2) do literature-implicated demands materialize as perceived demands?
+To answer these questions, authors first categorized O\*Net items into the JD-R elements listed in the JD-R literature.
+For example, autonomy is frequently described as a resource in the JD-R literature.
+An O\*Net item in the autonomy category is, “How much decision making freedom, without supervision, does your job offer?”.
+This O\*Net item was therefore retained within the "autonomy" category.
+Mean ratings (of resource, challenge, and hindrances) were then computed to explore whether literature-implicated resources and demands were evaluated as such.
 
-Repeated-measures ANOVAs were run for the group of literture-implicated demands first.
+Repeated-measures ANOVAs were computed for the group of literature-implicated *resources* (see the right hand side of Figure 4).
+The effect for `Job Control` was $F_{(`r report7$ANOVA$DFn`, `r report7$ANOVA$DFd`)}$ = `r report7$ANOVA$F` ($\eta^2$ = `r report7$ANOVA$pes`).
+The effect for `Participation` was $F_{(`r report8$ANOVA$DFn`, `r report8$ANOVA$DFd`)}$ = `r report8$ANOVA$F` ($\eta^2$ = `r report8$ANOVA$pes`).
+The effect for `Autonomy` was $F_{(`r report9$ANOVA$DFn`, `r report9$ANOVA$DFd`)}$ = `r report9$ANOVA$F` ($\eta^2$ = `r report9$ANOVA$pes`).
+The effect for `Team Cohesion` was $F_{(`r report10$ANOVA$DFn`, `r report10$ANOVA$DFd`)}$ = `r report10$ANOVA$F` ($\eta^2$ = `r report10$ANOVA$pes`).Statistical significance was less then .001 for all four category comparisons.
+Here, the pattern was as expected.
+Across categories, resources were rated the highest (see white bars representing resources in Figure 4).
+However, as can be seen, mean challenge (which is a demand) was rated quite similarly and above the midpoint of 3 across JD-R categories.
+
+Next, repeated-measures ANOVAs were then run for the group of literature-implicated *demands*.
 The effect for `Overwork` was $F_{(`r report1$ANOVA$DFn`, `r report1$ANOVA$DFd`)}$ = `r report1$ANOVA$F`, partial eta squared $(\eta^2)$ was `r report1$ANOVA$pes`.
@@
 The effect for `Recipient Contact` was $F_{(`r report5$ANOVA$DFn`, `r report5$ANOVA$DFd`)}$ = `r report5$ANOVA$F` ($\eta^2$ = `r report5$ANOVA$pes`).
-The effect for `Work Pressure` was $F_{(`r report6$ANOVA$DFn`, `r report6$ANOVA$DFd`)}$ = `r report6$ANOVA$F` ($\eta^2$ = `r report6$ANOVA$pes`).In all cases, statistical significance was less then .001, indicating in all cases, what the literature implicates is a demand was rated as a resource (all means are above the midpoint).
-See the patten of white resource bars on the lefthand side of Figure 4.
+The effect for `Work Pressure` was $F_{(`r report6$ANOVA$DFn`, `r report6$ANOVA$DFd`)}$ = `r report6$ANOVA$F` ($\eta^2$ = `r report6$ANOVA$pes`).
+In all cases, statistical significance was less then .001, indicating that what the literature implicates is a demand was actually rated as a resource (all resource means are above the midpoint).
 This is contrary to the expectation that ratings would match our assumption of what a resource constitutes.
-Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance.
+Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance.See the pattern of white resource bars on the lefthand side of Figure 4.
 
-Next, Repeated-measures ANOVAs were run for the group of literture-implicated resources (the right hand set of analyses presented in Figure 4).
-The effect for `Job Control` was $F_{(`r report7$ANOVA$DFn`, `r report7$ANOVA$DFd`)}$ = `r report7$ANOVA$F` ($\eta^2$ = `r report7$ANOVA$pes`).
-The effect for `Participation` was $F_{(`r report8$ANOVA$DFn`, `r report8$ANOVA$DFd`)}$ = `r report8$ANOVA$F` ($\eta^2$ = `r report8$ANOVA$pes`).
-The effect for `Autonomy` was $F_{(`r report9$ANOVA$DFn`, `r report9$ANOVA$DFd`)}$ = `r report9$ANOVA$F` ($\eta^2$ = `r report9$ANOVA$pes`).
-The effect for `Team Cohesion` was $F_{(`r report10$ANOVA$DFn`, `r report10$ANOVA$DFd`)}$ = `r report10$ANOVA$F` ($\eta^2$ = `r report10$ANOVA$pes`).Similar to the demands analyses, statistical significance was less then .001 for all four category comparisons.
-Here, the pattern was as expected.
-Across categories, resources were rated the highest (see white bars representing resources in Figure 4).
+Figure 4 presents these comparisons visually.
+First exploring the right side of Figure 4, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings.
+The white bars representing resources are consistently higher.
+As described above, the left side of Figure 4 shows literature-derived demand categories (e.g., work pressure).
+However, in contrast, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as "high" gray and black bars and "low" white bars).
+In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be "hindrances" at work.
+In sum, these results provide some support for RQ 1 and 2.
 

### 2023-03-02 Submission.Rmd
updated RQ explanations again.

@@
 This O\*Net item was therefore retained within the "autonomy" category.
-Mean ratings (of resource, challenge, and hindrances) were then computed to explore whether literature-implicated resources and demands were evaluated as such.
+Mean ratings of the O\*Net items were then computed by element (e.g., all of the items representing autonomy) to explore whether literature-implicated resources and demands were evaluated as such.
 
-Repeated-measures ANOVAs were computed for the group of literature-implicated *resources* (see the right hand side of Figure 4).
+Repeated-measures ANOVAs were computed for the group of literature-implicated *resources* first (see the right hand side of Figure 4).
 The effect for `Job Control` was $F_{(`r report7$ANOVA$DFn`, `r report7$ANOVA$DFd`)}$ = `r report7$ANOVA$F` ($\eta^2$ = `r report7$ANOVA$pes`).
@@
 Next, repeated-measures ANOVAs were then run for the group of literature-implicated *demands*.
+See the left hand side of Figure 4.
 The effect for `Overwork` was $F_{(`r report1$ANOVA$DFn`, `r report1$ANOVA$DFd`)}$ = `r report1$ANOVA$F`, partial eta squared $(\eta^2)$ was `r report1$ANOVA$pes`.
@@
 The effect for `Work Pressure` was $F_{(`r report6$ANOVA$DFn`, `r report6$ANOVA$DFd`)}$ = `r report6$ANOVA$F` ($\eta^2$ = `r report6$ANOVA$pes`).
-In all cases, statistical significance was less then .001, indicating that what the literature implicates is a demand was actually rated as a resource (all resource means are above the midpoint).
-This is contrary to the expectation that ratings would match our assumption of what a resource constitutes.
-Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance.See the pattern of white resource bars on the lefthand side of Figure 4.
+In all cases, statistical significance was less then .001.
+However, the findings revealed that what the literature implicates as a demand was actually evaluated as a *resource* (all resource means are above the midpoint).
+This is contrary to the expectation that ratings would match our assumption of what a demand constitutes.
+Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance.
+See the pattern of white resource bars on the lefthand side of Figure 4.
 

### 2023-03-03 SIOP2023/Counts/counts_poster.Rmd
Poster size changed

@@
 floatsintext: yes
+poster_height: "36in"
+poster_width: "48in"
 affiliation_textsize: "50pt"
-body_textsize: "50px"
+body_textsize: "49px"
 title_textsize:	"75pt"	
@@
 
-Stress was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$ = 2.47, *p* = .060, $R^2$ = .01; see Table \@ref(tab:regressiontablestr).
+Stress was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$ = 2.47, *p* = .060, $R^2$ = .01; Table \@ref(tab:regressiontablestr).
 

### 2023-03-04 Submission.Rmd
correlation table

@@
 In addition to highlighting extremely agreed- or disagreed-upon items, Figure \@ref(fig:overallhist) presents our standard deviation indices across all rated items.
-Here, the Figure \@ref(fig:combinegraphs) discrepancies recieve illumination, with the *spread* of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively *bunched* levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
+Here, the Figure \@ref(fig:combinegraphs) discrepancies receive illumination, with the *spread* of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively *bunched* levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
 Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
@@
 Table \@ref(tab:cortab) provides the correlations among the O\*Net item groupings by resource, challenge and hindrance demand.
-A large proportion of correlations are moderate.
-Challenge and hindrance demands are smaller in relationship, but mostly negative.
+We would expect to see minimal correlations if job characteristics *were* uniquely categorized.
+Here, we do expected to see more than minimal correlations.
+First, the mean correlation within resource categories was __________, _________ within challenge categories, and __________ within hindrance categories.
+We would expect these to be the highest.
+The mean resource to challenge correlation was __________.
+The mean resource to hindrance correlation was __________.
+Finally, the mean challenge to hindrance correlation was ____________.
+These were expected to be moderate in size, but smaller than within the same category.
+In sum, Challenge and hindrance demands demonstrated smaller relationships, but mostly negative.
 Challenge and resource are strongly and positively related.
-These results provide support for H2 suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is percieved as a *resource* being also percieved as a *challenge*.
+These results provide support for H2, suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is perceived as a *resource* being also perceived as a *challenge*.
 Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.
@@
 r <- corx::corx(data_new, x =c("onet.resource.ii", "onet.resource.mp", "onet.resource.wo",  "onet.resource.io", "onet.resource.ir", "onet.resource.pc", "onet.resource.sc", "onet.challenge.ii", "onet.challenge.mp", "onet.challenge.wo",  "onet.challenge.io", "onet.challenge.ir", "onet.challenge.pc", "onet.challenge.sc","onet.hindrance.ii", "onet.hindrance.mp", "onet.hindrance.wo", "onet.hindrance.io", "onet.hindrance.ir", "onet.hindrance.pc", "onet.hindrance.sc"), y =c("onet.resource.ii", "onet.resource.mp", "onet.resource.wo",  "onet.resource.io", "onet.resource.ir", "onet.resource.pc", "onet.resource.sc", "onet.challenge.ii", "onet.challenge.mp", "onet.challenge.wo", "onet.challenge.io", "onet.challenge.ir", "onet.challenge.pc", "onet.challenge.sc","onet.hindrance.ii", "onet.hindrance.mp", "onet.hindrance.wo", "onet.hindrance.io", "onet.hindrance.ir", "onet.hindrance.pc", "onet.hindrance.sc"),
-                triangle = "lower",
-                stars = c(0.05, 0.01, 0.001),
+                triangle = "upper",
+  #              stars = c(0.05, 0.01, 0.001),
                 describe = c(`$M$` = mean, `$SD$` = sd))
@@
                   escape = FALSE, 
-                  font_size = "small",  ## "tiny" smallest
+                  font_size = "tiny",  ## "tiny" smallest
                   longtable = TRUE,
@@
 Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance.
-See the pattern of white resource bars on the lefthand side of Figure 4.
+See the pattern of white resource bars on the left hand side of Figure 4.
 

### 2023-03-04 Submission.tex
correlation table

@@
 \usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Job Demands-Resources Model Components through the Lens of O*NET Classifications},
+  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
+  pdflang={en-EN},
+  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resoures, job characteristics},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \makeatother
-
-\usepackage{xpatch}
-\makeatletter
-\xapptocmd\appendix
-  {\xapptocmd\section
-    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
-    {}{\InnerPatchFailed}%
-  }
-{}{\PatchFailed}
+\shorttitle{O*NET JD-R}
 \keywords{O*Net, challenge-hindrance framework, job demands-resoures, job characteristics\newline\indent Word count: X}
@@
 \usepackage{csquotes}
-\ifLuaTeX
+\ifxetex
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\else
+  \usepackage[main=english]{babel}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+\fi
+\ifluatex
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={Job Demands-Resources Model Components through the Lens of O*NET Classifications},
-  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
-  pdflang={en-EN},
-  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resoures, job characteristics},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 
-\abstract{%
+\abstract{
 Much of our understanding of job demands and resources rests on the assumption that some aspects and components of one's job are resources and some are demands.
@@
 In addition to highlighting extremely agreed- or disagreed-upon items, Figure \ref{fig:overallhist} presents our standard deviation indices across all rated items.
-Here, the Figure \ref{fig:combinegraphs} discrepancies recieve illumination, with the \emph{spread} of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively \emph{bunched} levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
+Here, the Figure \ref{fig:combinegraphs} discrepancies receive illumination, with the \emph{spread} of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively \emph{bunched} levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
 Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
@@
 A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} = 0.00 ).
-In sum, these results provide some collective support for H1, and particularly so for hindrances, which are consistently viewed as ``different''.
+In sum, these results provide some collective support for H1, and particularly so for hindrances, which are consistently viewed as ``different.''
 
@@
 Table \ref{tab:cortab} provides the correlations among the O*Net item groupings by resource, challenge and hindrance demand.
-A large proportion of correlations are moderate.
-Challenge and hindrance demands are smaller in relationship, but mostly negative.
+We would expect to see minimal correlations if job characteristics \emph{were} uniquely categorized.
+Here, we do expected to see more than minimal correlations.
+First, the mean correlation within resource categories was \_\_\_\_\_\_\_\_\_\_, \_\_\_\_\_\_\_\_\_ within challenge categories, and \_\_\_\_\_\_\_\_\_\_ within hindrance categories.
+We would expect these to be the highest.
+The mean resource to challenge correlation was \_\_\_\_\_\_\_\_\_\_.
+The mean resource to hindrance correlation was \_\_\_\_\_\_\_\_\_\_.
+Finally, the mean challenge to hindrance correlation was \_\_\_\_\_\_\_\_\_\_\_\_.
+These were expected to be moderate in size, but smaller than within the same category.
+In sum, Challenge and hindrance demands demonstrated smaller relationships, but mostly negative.
 Challenge and resource are strongly and positively related.
-These results provide support for H2 suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is percieved as a \emph{resource} being also percieved as a \emph{challenge}.
+These results provide support for H2, suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is perceived as a \emph{resource} being also perceived as a \emph{challenge}.
 Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.
@@
 
-\small{
+\tiny{
 
@@
 \endhead
-1. onet.resource.ii & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
-2. onet.resource.mp & .61*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.19 & 0.60\\
-3. onet.resource.wo & .46*** & .50*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.79 & 0.84\\
-4. onet.resource.io & .49*** & .64*** & .45*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.10 & 0.60\\
-5. onet.resource.ir & .46*** & .55*** & .37*** & .60*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.80 & 0.61\\
-6. onet.resource.pc & .19*** & .15*** & .32*** & .18*** & .37*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 2.99 & 0.77\\
-7. onet.resource.sc & .43*** & .46*** & .41*** & .45*** & .48*** & .37*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.61\\
-8. onet.challenge.ii & .62*** & .49*** & .37*** & .41*** & .33*** & .08 & .33*** & - &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
-9. onet.challenge.mp & .47*** & .63*** & .42*** & .50*** & .41*** & .09* & .38*** & .65*** & - &  &  &  &  &  &  &  &  &  &  &  & 4.20 & 0.64\\
-10. onet.challenge.wo & .34*** & .39*** & .64*** & .34*** & .30*** & .29*** & .38*** & .45*** & .49*** & - &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.88\\
-11. onet.challenge.io & .34*** & .48*** & .33*** & .65*** & .48*** & .13** & .40*** & .50*** & .68*** & .43*** & - &  &  &  &  &  &  &  &  &  & 4.07 & 0.64\\
-12. onet.challenge.ir & .32*** & .40*** & .26*** & .48*** & .63*** & .23*** & .39*** & .46*** & .60*** & .39*** & .70*** & - &  &  &  &  &  &  &  &  & 3.85 & 0.63\\
-13. onet.challenge.pc & .12** & .08 & .21*** & .13** & .26*** & .66*** & .29*** & .14** & .12** & .33*** & .20*** & .31*** & - &  &  &  &  &  &  &  & 2.85 & 0.79\\
-14. onet.challenge.sc & .27*** & .31*** & .28*** & .38*** & .40*** & .27*** & .62*** & .36*** & .41*** & .38*** & .51*** & .45*** & .40*** & - &  &  &  &  &  &  & 3.66 & 0.59\\
-15. onet.hindrance.ii & -.26*** & -.26*** & -.17*** & -.24*** & -.18*** & -.02 & -.08 & -.27*** & -.26*** & -.10* & -.19*** & -.16*** & .06 & -.10* & - &  &  &  &  &  & 2.15 & 1.01\\
-16. onet.hindrance.mp & -.23*** & -.30*** & -.17*** & -.22*** & -.15*** & .05 & -.07 & -.22*** & -.27*** & -.10* & -.18*** & -.15*** & .12** & -.06 & .86*** & - &  &  &  &  & 2.10 & 1.05\\
-17. onet.hindrance.wo & -.21*** & -.25*** & -.22*** & -.22*** & -.06 & -.02 & -.12** & -.14** & -.21*** & -.23*** & -.15*** & -.09* & .05 & -.10* & .66*** & .69*** & - &  &  &  & 2.31 & 1.02\\
-18.
-onet.hindrance.io & -.22*** & -.27*** & -.14*** & -.29*** & -.18*** & -.01 & -.10* & -.21*** & -.25*** & -.10* & -.27*** & -.19*** & .07 & -.10* & .79*** & .86*** & .69*** & - &  &  & 2.23 & 1.03\\
-19.
-onet.hindrance.ir & -.22*** & -.24*** & -.15*** & -.24*** & -.25*** & -.06 & -.11** & -.19*** & -.21*** & -.08* & -.20*** & -.23*** & .04 & -.12** & .79*** & .80*** & .61*** & .82*** & - &  & 2.35 & 0.89\\
-20. onet.hindrance.pc & -.04 & -.08* & -.09* & -.11** & -.10* & -.16*** & -.13** & -.03 & -.04 & -.06 & -.08* & -.10* & -.04 & -.13** & .38*** & .33*** & .47*** & .35*** & .47*** & - & 2.66 & 0.83\\
-21.
-onet.hindrance.sc & -.13** & -.15*** & -.13** & -.19*** & -.13** & -.09* & -.23*** & -.12** & -.10* & -.05 & -.16*** & -.12** & -.01 & -.17*** & .62*** & .62*** & .56*** & .64*** & .66*** & .45*** & 2.64 & 0.80\\
+1. onet.resource.ii & - & .61* & .46* & .49* & .46* & .19* & .43* & .62* & .47* & .34* & .34* & .32* & .12* & .27* & -.26* & -.23* & -.21* & -.22* & -.22* & -.04 & 3.98 & 0.80\\
+2. onet.resource.mp &  & - & .50* & .64* & .55* & .15* & .46* & .49* & .63* & .39* & .48* & .40* & .08 & .31* & -.26* & -.30* & -.25* & -.27* & -.24* & -.08* & 4.19 & 0.60\\
+3. onet.resource.wo &  &  & - & .45* & .37* & .32* & .41* & .37* & .42* & .64* & .33* & .26* & .21* & .28* & -.17* & -.17* & -.22* & -.14* & -.15* & -.09* & 3.79 & 0.84\\
+4. onet.resource.io &  &  &  & - & .60* & .18* & .45* & .41* & .50* & .34* & .65* & .48* & .13* & .38* & -.24* & -.22* & -.22* & -.29* & -.24* & -.11* & 4.10 & 0.60\\
+5. onet.resource.ir &  &  &  &  & - & .37* & .48* & .33* & .41* & .30* & .48* & .63* & .26* & .40* & -.18* & -.15* & -.06 & -.18* & -.25* & -.10* & 3.80 & 0.61\\
+6. onet.resource.pc &  &  &  &  &  & - & .37* & .08 & .09* & .29* & .13* & .23* & .66* & .27* & -.02 & .05 & -.02 & -.01 & -.06 & -.16* & 2.99 & 0.77\\
+7. onet.resource.sc &  &  &  &  &  &  & - & .33* & .38* & .38* & .40* & .39* & .29* & .62* & -.08 & -.07 & -.12* & -.10* & -.11* & -.13* & 3.65 & 0.61\\
+8. onet.challenge.ii &  &  &  &  &  &  &  & - & .65* & .45* & .50* & .46* & .14* & .36* & -.27* & -.22* & -.14* & -.21* & -.19* & -.03 & 3.98 & 0.80\\
+9. onet.challenge.mp &  &  &  &  &  &  &  &  & - & .49* & .68* & .60* & .12* & .41* & -.26* & -.27* & -.21* & -.25* & -.21* & -.04 & 4.20 & 0.64\\
+10. onet.challenge.wo &  &  &  &  &  &  &  &  &  & - & .43* & .39* & .33* & .38* & -.10* & -.10* & -.23* & -.10* & -.08* & -.06 & 3.65 & 0.88\\
+11. onet.challenge.io &  &  &  &  &  &  &  &  &  &  & - & .70* & .20* & .51* & -.19* & -.18* & -.15* & -.27* & -.20* & -.08* & 4.07 & 0.64\\
+12. onet.challenge.ir &  &  &  &  &  &  &  &  &  &  &  & - & .31* & .45* & -.16* & -.15* & -.09* & -.19* & -.23* & -.10* & 3.85 & 0.63\\
+13. onet.challenge.pc &  &  &  &  &  &  &  &  &  &  &  &  & - & .40* & .06 & .12* & .05 & .07 & .04 & -.04 & 2.85 & 0.79\\
+14. onet.challenge.sc &  &  &  &  &  &  &  &  &  &  &  &  &  & - & -.10* & -.06 & -.10* & -.10* & -.12* & -.13* & 3.66 & 0.59\\
+15. onet.hindrance.ii &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & .86* & .66* & .79* & .79* & .38* & 2.15 & 1.01\\
+16. onet.hindrance.mp &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & .69* & .86* & .80* & .33* & 2.10 & 1.05\\
+17. onet.hindrance.wo &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & .69* & .61* & .47* & 2.31 & 1.02\\
+18. onet.hindrance.io &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & .82* & .35* & 2.23 & 1.03\\
+19. onet.hindrance.ir &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & .47* & 2.35 & 0.89\\
+20. onet.hindrance.pc &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & 2.66 & 0.83\\
+21. onet.hindrance.sc &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 2.64 & 0.80\\
 \bottomrule
@@
 
-In addition to the two hypotheses, two related research questions were proposed.
-To answer these research questions, authors first categorized items into the JD-R elements listed in the JD-R literature.
-For example, autonomy is frequently described as a resource.
-An O*Net item in the autonomy category is, ``How much decision making freedom, without supervision, does your job offer?''.
-This O*Net item was therefore retained within the ``autonomy'' category.
-Means for resource, challenge, and hindrance groupings were then computed to explore whether literature-implicated resources and demands were evaluated as such.
-The left side of Figure 4 shows literature-derived demand categories (e.g., work pressure).
-Here, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as ``high'' gray and black bars and ``low'' white bars).
-In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be ``hindrances'' at work.
-However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings.
-The white bars representing resources are consistently higher.
-In sum, these results provide some support for RQ 1 and 2.
+In addition to the two hypotheses, two related research questions were proposed: 1) do literature-implicated resources materialize as perceived resources and 2) do literature-implicated demands materialize as perceived demands?
+To answer these questions, authors first categorized O*Net items into the JD-R elements listed in the JD-R literature.
+For example, autonomy is frequently described as a resource in the JD-R literature.
+An O*Net item in the autonomy category is, ``How much decision making freedom, without supervision, does your job offer?'' This O*Net item was therefore retained within the ``autonomy'' category.
+Mean ratings of the O*Net items were then computed by element (e.g., all of the items representing autonomy) to explore whether literature-implicated resources and demands were evaluated as such.
 
-Separate repeated-measures ANOVAs were conducted for each of these comparisons.
+Repeated-measures ANOVAs were computed for the group of literature-implicated \emph{resources} first (see the right hand side of Figure 4).
+The effect for \texttt{Job\ Control} was \(F_{(2, 1134)}\) = 52.78 (\(\eta^2\) = 0.08).
+The effect for \texttt{Participation} was \(F_{(2, 1124)}\) = 991.16 (\(\eta^2\) = 0.64).
+The effect for \texttt{Autonomy} was \(F_{(2, 1074)}\) = 951.90 (\(\eta^2\) = 0.64).
+The effect for \texttt{Team\ Cohesion} was \(F_{(2, 1120)}\) = 853.39 (\(\eta^2\) = 0.60).Statistical significance was less then .001 for all four category comparisons.
+Here, the pattern was as expected.
+Across categories, resources were rated the highest (see white bars representing resources in Figure 4).
+However, as can be seen, mean challenge (which is a demand) was rated quite similarly and above the midpoint of 3 across JD-R categories.
 
-Repeated-measures ANOVAs were run for the group of literture-implicated demands first. The effect for \texttt{Overwork} was \(F_{(2, 1134)}\) = 17.71, partial eta squared \((\eta^2)\) was 0.03.
+Next, repeated-measures ANOVAs were then run for the group of literature-implicated \emph{demands}.
+See the left hand side of Figure 4.
+The effect for \texttt{Overwork} was \(F_{(2, 1134)}\) = 17.71, partial eta squared \((\eta^2)\) was 0.03.
 The effect for \texttt{Physical\ Environment} was \(F_{(2, 1108)}\) = 112.97 (\(\eta^2\) = 0.17).
@@
 The effect for \texttt{Recipient\ Contact} was \(F_{(2, 1126)}\) = 1,031.73 (\(\eta^2\) = 0.65).
-The effect for \texttt{Work\ Pressure} was \(F_{(2, 1132)}\) = 718.12 (\(\eta^2\) = 0.56).In all cases, statistical significance was less then .001, indicating in all cases, what the literature implicates is a demand was rated as a resource (all means are above the midpoint).
-See the patten of white resource bars on the lefthand side of Figure 4.
-This is contrary to the expectation that ratings would match our assumption of what a resource constitutes.
+The effect for \texttt{Work\ Pressure} was \(F_{(2, 1132)}\) = 718.12 (\(\eta^2\) = 0.56).
+In all cases, statistical significance was less then .001.
+However, the findings revealed that what the literature implicates as a demand was actually evaluated as a \emph{resource} (all resource means are above the midpoint).
+This is contrary to the expectation that ratings would match our assumption of what a demand constitutes.
 Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance.
+See the pattern of white resource bars on the left hand side of Figure 4.
 
-Next, Repeated-measures ANOVAs were run for the group of literture-implicated resources (the right hand set of analyses presented in Figure 4).
-The effect for \texttt{Job\ Control} was \(F_{(2, 1134)}\) = 52.78 (\(\eta^2\) = 0.08).
-The effect for \texttt{Participation} was \(F_{(2, 1124)}\) = 991.16 (\(\eta^2\) = 0.64).
-The effect for \texttt{Autonomy} was \(F_{(2, 1074)}\) = 951.90 (\(\eta^2\) = 0.64).
-The effect for \texttt{Team\ Cohesion} was \(F_{(2, 1120)}\) = 853.39 (\(\eta^2\) = 0.60).Similar to the demands analyses, statistical significance was less then .001 for all four category comparisons.
-Here, the pattern was as expected.
-Across categories, resources were rated the highest (see white bars representing resources in Figure 4).
+Figure 4 presents these comparisons visually.
+First exploring the right side of Figure 4, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings.
+The white bars representing resources are consistently higher.
+As described above, the left side of Figure 4 shows literature-derived demand categories (e.g., work pressure).
+However, in contrast, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as ``high'' gray and black bars and ``low'' white bars).
+In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be ``hindrances'' at work.
+In sum, these results provide some support for RQ 1 and 2.
 
@@
 There is individual difference in how employees experience the characteristics of their jobs.
-Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a ``resource'' or ``demand''.
+Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a ``resource'' or ``demand.''
 

### 2023-03-04 correlations.R
hand entered correlations to help walk through Table 1 (Hudson public library)

@@ -1,0 +1,49 @@
+resources <- c(.61,.46,.49,.46,.19,.43,.5,.64,.55,.15,.46,.45,.37,.32,.41,.6,.18,.45,.37,.48,.37)
+
+challenges <- c(.65,.45,.5,.46,.14,.36,.49,.68,.60,.12,.41,.43,.39,.33,.38,.7,.2,.51,.31,.45,.4)
+
+hindrances <- c(.86,.66,.79,.79,.38,.69,.86,.8,.33,.69,.61,.47,.82,.35,.47,.62,.62,.56,.64,.66,.45)
+
+range(resources)
+mean(resources)
+sd(resources)
+
+range(challenges)
+mean(challenges)
+sd(challenges)
+
+range(hindrances)
+mean(hindrances)
+sd(hindrances)
+
+rcdiag <- c(.62,.63,.64,.65,.63,.66,.62)
+rhdiag <- c(26,30,22,29,25,16,23) ## all neg
+chdiag <- c(27,27,23,27,23,4,17) ## all neg
+
+rcoffdiag <- c(47,34,34,32,12,27,49,39,48,40,8,31,37,42,33,26,21,28,41,50,34,48,13,38,33,41,30,48,26,40,08,09,29,13,23,27,33,38,38,40,39,29)
+rhoffdiag <- c(23,21,22,22,04,13,26,25,27,24,08,15,17,17,14,15,09,13,24,22,22,24,11,19,18,15,06,18,10,13,02,-05,02,01,06,09,08,07,12,10,11,13)
+choffdiag <- c(22,14,21,19,03,12,26,21,25,21,04,10,10,10,10,08,06,05,19,18,15,20,08,16,16,15,09,19,10,12,-06,-12,-05,-07,-04,01,10,06,10,10,12,13)
+
+range(rcdiag)
+mean(rcdiag)
+sd(rcdiag)
+
+range(rhdiag)
+mean(rhdiag)
+sd(rhdiag)
+
+range(chdiag)
+mean(chdiag)
+sd(chdiag)
+
+range(rcoffdiag)
+mean(rcoffdiag)
+sd(rcoffdiag)
+
+range(rhoffdiag)
+mean(rhoffdiag)
+sd(rhoffdiag)
+
+range(choffdiag)
+mean(choffdiag)
+sd(choffdiag)

### 2023-03-04 Submission.Rmd
updating the results section

@@
 Here, we do expected to see more than minimal correlations.
-First, the mean correlation within resource categories was __________, _________ within challenge categories, and __________ within hindrance categories.
+First, the mean correlation within resource categories was .43 (*SD* = .13, range from .15 to .64), and challenge categories were similar (ranging from .12 to .70, *M* = .43, *SD* =.16).
+Hindrance categories had less differentiation across categories ranging from .33 to .86, *M* = .62, *SD* = .17.
+When people perceived hindrances, these seemed to be shared across different types of job activities, whereas challenges challenges and resources exhibited more differentiation.
 We would expect these to be the highest.
-The mean resource to challenge correlation was __________.
-The mean resource to hindrance correlation was __________.
-Finally, the mean challenge to hindrance correlation was ____________.
-These were expected to be moderate in size, but smaller than within the same category.
+
+The mean resource to challenge correlations within the same dimension ranged from .62 to .66, *M* = .64, *SD* = .02).
+The correlations between resources and challenges across dimensions ranged from .08 to .50, *M* = .32, *SD* = .12.
+The mean resource to hindrance correlations within the same dimension ranged from -.16 to -.30, *M* = -.24, *SD* = .05).
+The correlations between resources and hindrances across dimensions ranged from .05 to -.27, *M* = -.14, *SD* = .08.
+The mean challenge to hindrance correlations within the same dimension ranged from -.04 to -.27, *M* = -.21, *SD* = .08).
+The correlations between challenges to hindrances across dimensions ranged from .12 to -.26, *M* = -.11, *SD* = .09.
+Correlations were larger when what was being rated was the same type of characteristic.
 In sum, Challenge and hindrance demands demonstrated smaller relationships, but mostly negative.
@@
 r <- corx::corx(data_new, x =c("onet.resource.ii", "onet.resource.mp", "onet.resource.wo",  "onet.resource.io", "onet.resource.ir", "onet.resource.pc", "onet.resource.sc", "onet.challenge.ii", "onet.challenge.mp", "onet.challenge.wo",  "onet.challenge.io", "onet.challenge.ir", "onet.challenge.pc", "onet.challenge.sc","onet.hindrance.ii", "onet.hindrance.mp", "onet.hindrance.wo", "onet.hindrance.io", "onet.hindrance.ir", "onet.hindrance.pc", "onet.hindrance.sc"), y =c("onet.resource.ii", "onet.resource.mp", "onet.resource.wo",  "onet.resource.io", "onet.resource.ir", "onet.resource.pc", "onet.resource.sc", "onet.challenge.ii", "onet.challenge.mp", "onet.challenge.wo", "onet.challenge.io", "onet.challenge.ir", "onet.challenge.pc", "onet.challenge.sc","onet.hindrance.ii", "onet.hindrance.mp", "onet.hindrance.wo", "onet.hindrance.io", "onet.hindrance.ir", "onet.hindrance.pc", "onet.hindrance.sc"),
-                triangle = "upper",
+                triangle = "lower",
  #               stars = c(0.05, 0.01, 0.001),

### 2023-03-04 Submission.tex
updating the results section

@@
 Here, we do expected to see more than minimal correlations.
-First, the mean correlation within resource categories was \_\_\_\_\_\_\_\_\_\_, \_\_\_\_\_\_\_\_\_ within challenge categories, and \_\_\_\_\_\_\_\_\_\_ within hindrance categories.
+First, the mean correlation within resource categories was .43 (\emph{SD} = .13, range from .15 to .64), and challenge categories were similar (ranging from .12 to .70, \emph{M} = .43, \emph{SD} =.16).
+Hindrance categories had less differentiation across categories ranging from .33 to .86, \emph{M} = .62, \emph{SD} = .17.
+When people perceived hindrances, these seemed to be shared across different types of job activities, whereas challenges challenges and resources exhibited more differentiation.
 We would expect these to be the highest.
+
 The mean resource to challenge correlation was \_\_\_\_\_\_\_\_\_\_.
@@
 \endhead
-1. onet.resource.ii & - & .61* & .46* & .49* & .46* & .19* & .43* & .62* & .47* & .34* & .34* & .32* & .12* & .27* & -.26* & -.23* & -.21* & -.22* & -.22* & -.04 & 3.98 & 0.80\\
-2. onet.resource.mp &  & - & .50* & .64* & .55* & .15* & .46* & .49* & .63* & .39* & .48* & .40* & .08 & .31* & -.26* & -.30* & -.25* & -.27* & -.24* & -.08* & 4.19 & 0.60\\
-3. onet.resource.wo &  &  & - & .45* & .37* & .32* & .41* & .37* & .42* & .64* & .33* & .26* & .21* & .28* & -.17* & -.17* & -.22* & -.14* & -.15* & -.09* & 3.79 & 0.84\\
-4. onet.resource.io &  &  &  & - & .60* & .18* & .45* & .41* & .50* & .34* & .65* & .48* & .13* & .38* & -.24* & -.22* & -.22* & -.29* & -.24* & -.11* & 4.10 & 0.60\\
-5. onet.resource.ir &  &  &  &  & - & .37* & .48* & .33* & .41* & .30* & .48* & .63* & .26* & .40* & -.18* & -.15* & -.06 & -.18* & -.25* & -.10* & 3.80 & 0.61\\
-6. onet.resource.pc &  &  &  &  &  & - & .37* & .08 & .09* & .29* & .13* & .23* & .66* & .27* & -.02 & .05 & -.02 & -.01 & -.06 & -.16* & 2.99 & 0.77\\
-7. onet.resource.sc &  &  &  &  &  &  & - & .33* & .38* & .38* & .40* & .39* & .29* & .62* & -.08 & -.07 & -.12* & -.10* & -.11* & -.13* & 3.65 & 0.61\\
-8. onet.challenge.ii &  &  &  &  &  &  &  & - & .65* & .45* & .50* & .46* & .14* & .36* & -.27* & -.22* & -.14* & -.21* & -.19* & -.03 & 3.98 & 0.80\\
-9. onet.challenge.mp &  &  &  &  &  &  &  &  & - & .49* & .68* & .60* & .12* & .41* & -.26* & -.27* & -.21* & -.25* & -.21* & -.04 & 4.20 & 0.64\\
-10. onet.challenge.wo &  &  &  &  &  &  &  &  &  & - & .43* & .39* & .33* & .38* & -.10* & -.10* & -.23* & -.10* & -.08* & -.06 & 3.65 & 0.88\\
-11. onet.challenge.io &  &  &  &  &  &  &  &  &  &  & - & .70* & .20* & .51* & -.19* & -.18* & -.15* & -.27* & -.20* & -.08* & 4.07 & 0.64\\
-12. onet.challenge.ir &  &  &  &  &  &  &  &  &  &  &  & - & .31* & .45* & -.16* & -.15* & -.09* & -.19* & -.23* & -.10* & 3.85 & 0.63\\
-13. onet.challenge.pc &  &  &  &  &  &  &  &  &  &  &  &  & - & .40* & .06 & .12* & .05 & .07 & .04 & -.04 & 2.85 & 0.79\\
-14. onet.challenge.sc &  &  &  &  &  &  &  &  &  &  &  &  &  & - & -.10* & -.06 & -.10* & -.10* & -.12* & -.13* & 3.66 & 0.59\\
-15. onet.hindrance.ii &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & .86* & .66* & .79* & .79* & .38* & 2.15 & 1.01\\
-16. onet.hindrance.mp &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & .69* & .86* & .80* & .33* & 2.10 & 1.05\\
-17. onet.hindrance.wo &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & .69* & .61* & .47* & 2.31 & 1.02\\
-18. onet.hindrance.io &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & .82* & .35* & 2.23 & 1.03\\
-19. onet.hindrance.ir &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & .47* & 2.35 & 0.89\\
-20. onet.hindrance.pc &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & - & 2.66 & 0.83\\
-21. onet.hindrance.sc &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 2.64 & 0.80\\
+1. onet.resource.ii & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
+2. onet.resource.mp & .61* & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.19 & 0.60\\
+3. onet.resource.wo & .46* & .50* & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.79 & 0.84\\
+4. onet.resource.io & .49* & .64* & .45* & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.10 & 0.60\\
+5. onet.resource.ir & .46* & .55* & .37* & .60* & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.80 & 0.61\\
+6. onet.resource.pc & .19* & .15* & .32* & .18* & .37* & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 2.99 & 0.77\\
+7. onet.resource.sc & .43* & .46* & .41* & .45* & .48* & .37* & - &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.61\\
+8. onet.challenge.ii & .62* & .49* & .37* & .41* & .33* & .08 & .33* & - &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
+9. onet.challenge.mp & .47* & .63* & .42* & .50* & .41* & .09* & .38* & .65* & - &  &  &  &  &  &  &  &  &  &  &  & 4.20 & 0.64\\
+10. onet.challenge.wo & .34* & .39* & .64* & .34* & .30* & .29* & .38* & .45* & .49* & - &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.88\\
+11. onet.challenge.io & .34* & .48* & .33* & .65* & .48* & .13* & .40* & .50* & .68* & .43* & - &  &  &  &  &  &  &  &  &  & 4.07 & 0.64\\
+12. onet.challenge.ir & .32* & .40* & .26* & .48* & .63* & .23* & .39* & .46* & .60* & .39* & .70* & - &  &  &  &  &  &  &  &  & 3.85 & 0.63\\
+13. onet.challenge.pc & .12* & .08 & .21* & .13* & .26* & .66* & .29* & .14* & .12* & .33* & .20* & .31* & - &  &  &  &  &  &  &  & 2.85 & 0.79\\
+14. onet.challenge.sc & .27* & .31* & .28* & .38* & .40* & .27* & .62* & .36* & .41* & .38* & .51* & .45* & .40* & - &  &  &  &  &  &  & 3.66 & 0.59\\
+15. onet.hindrance.ii & -.26* & -.26* & -.17* & -.24* & -.18* & -.02 & -.08 & -.27* & -.26* & -.10* & -.19* & -.16* & .06 & -.10* & - &  &  &  &  &  & 2.15 & 1.01\\
+16. onet.hindrance.mp & -.23* & -.30* & -.17* & -.22* & -.15* & .05 & -.07 & -.22* & -.27* & -.10* & -.18* & -.15* & .12* & -.06 & .86* & - &  &  &  &  & 2.10 & 1.05\\
+17. onet.hindrance.wo & -.21* & -.25* & -.22* & -.22* & -.06 & -.02 & -.12* & -.14* & -.21* & -.23* & -.15* & -.09* & .05 & -.10* & .66* & .69* & - &  &  &  & 2.31 & 1.02\\
+18. onet.hindrance.io & -.22* & -.27* & -.14* & -.29* & -.18* & -.01 & -.10* & -.21* & -.25* & -.10* & -.27* & -.19* & .07 & -.10* & .79* & .86* & .69* & - &  &  & 2.23 & 1.03\\
+19. onet.hindrance.ir & -.22* & -.24* & -.15* & -.24* & -.25* & -.06 & -.11* & -.19* & -.21* & -.08* & -.20* & -.23* & .04 & -.12* & .79* & .80* & .61* & .82* & - &  & 2.35 & 0.89\\
+20. onet.hindrance.pc & -.04 & -.08* & -.09* & -.11* & -.10* & -.16* & -.13* & -.03 & -.04 & -.06 & -.08* & -.10* & -.04 & -.13* & .38* & .33* & .47* & .35* & .47* & - & 2.66 & 0.83\\
+21. onet.hindrance.sc & -.13* & -.15* & -.13* & -.19* & -.13* & -.09* & -.23* & -.12* & -.10* & -.05 & -.16* & -.12* & -.01 & -.17* & .62* & .62* & .56* & .64* & .66* & .45* & 2.64 & 0.80\\
 \bottomrule

### 2023-03-04 Submission.tex
updating results

@@
 
-The mean resource to challenge correlation was \_\_\_\_\_\_\_\_\_\_.
-The mean resource to hindrance correlation was \_\_\_\_\_\_\_\_\_\_.
-Finally, the mean challenge to hindrance correlation was \_\_\_\_\_\_\_\_\_\_\_\_.
-These were expected to be moderate in size, but smaller than within the same category.
+The mean resource to challenge correlations within the same dimension ranged from .62 to .66, \emph{M} = .64, \emph{SD} = .02).
+The correlations between resources and challenges across dimensions ranged from .08 to .50, \emph{M} = .32, \emph{SD} = .12.
+The mean resource to hindrance correlations within the same dimension ranged from -.16 to -.30, \emph{M} = -.24, \emph{SD} = .05).
+The correlations between resources and hindrances across dimensions ranged from .05 to -.27, \emph{M} = -.14, \emph{SD} = .08.
+The mean challenge to hindrance correlations within the same dimension ranged from -.04 to -.27, \emph{M} = -.21, \emph{SD} = .08).
+The correlations between challenges to hindrances across dimensions ranged from .12 to -.26, \emph{M} = -.11, \emph{SD} = .09.
+Correlations were larger when what was being rated was the same type of characteristic.
 In sum, Challenge and hindrance demands demonstrated smaller relationships, but mostly negative.

### 2023-03-04 Submission.Rmd
updated results

@@
 
-The mean resource to challenge correlations within the same dimension ranged from .62 to .66, *M* = .64, *SD* = .02).
-The correlations between resources and challenges across dimensions ranged from .08 to .50, *M* = .32, *SD* = .12.
+The mean resource to challenge correlations within the same dimension ranged from .62 to .66, *M* = .64, *SD* = .02; for example, the association between information input ratings as a resource and as a challenge was .62).
+The correlations between resources and challenges across dimensions (for example, the correlation between mental processes and work output was .42 and .39) ranged from .08 to .50, *M* = .32, *SD* = .12.
 The mean resource to hindrance correlations within the same dimension ranged from -.16 to -.30, *M* = -.24, *SD* = .05).
@@
 
+Figure 4 presents these comparisons visually.
+First exploring the right side of Figure 4, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings.
+The white bars representing resources are consistently higher.
+As described above, the left side of Figure 4 shows literature-derived demand categories (e.g., work pressure).
+However, in contrast, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as "high" gray and black bars and "low" white bars).
+In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be "hindrances" at work.
+
 Repeated-measures ANOVAs were computed for the group of literature-implicated *resources* first (see the right hand side of Figure 4).
@@
 The effect for `Autonomy` was $F_{(`r report9$ANOVA$DFn`, `r report9$ANOVA$DFd`)}$ = `r report9$ANOVA$F` ($\eta^2$ = `r report9$ANOVA$pes`).
-The effect for `Team Cohesion` was $F_{(`r report10$ANOVA$DFn`, `r report10$ANOVA$DFd`)}$ = `r report10$ANOVA$F` ($\eta^2$ = `r report10$ANOVA$pes`).Statistical significance was less then .001 for all four category comparisons.
+The effect for `Team Cohesion` was $F_{(`r report10$ANOVA$DFn`, `r report10$ANOVA$DFd`)}$ = `r report10$ANOVA$F` ($\eta^2$ = `r report10$ANOVA$pes`).
+Statistical significance was less then .001 for all four category comparisons.
 Here, the pattern was as expected.
@@
 See the pattern of white resource bars on the left hand side of Figure 4.
-
-Figure 4 presents these comparisons visually.
-First exploring the right side of Figure 4, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings.
-The white bars representing resources are consistently higher.
-As described above, the left side of Figure 4 shows literature-derived demand categories (e.g., work pressure).
-However, in contrast, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as "high" gray and black bars and "low" white bars).
-In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be "hindrances" at work.
 In sum, these results provide some support for RQ 1 and 2.

### 2023-03-04 Submission.tex
updated results one last time today

@@
 
-The mean resource to challenge correlations within the same dimension ranged from .62 to .66, \emph{M} = .64, \emph{SD} = .02).
-The correlations between resources and challenges across dimensions ranged from .08 to .50, \emph{M} = .32, \emph{SD} = .12.
+The mean resource to challenge correlations within the same dimension ranged from .62 to .66, \emph{M} = .64, \emph{SD} = .02; for example, the association between information input ratings as a resource and as a challenge was .62).
+The correlations between resources and challenges across dimensions (for example, the correlation between mental processes and work output was .42 and .39) ranged from .08 to .50, \emph{M} = .32, \emph{SD} = .12.
 The mean resource to hindrance correlations within the same dimension ranged from -.16 to -.30, \emph{M} = -.24, \emph{SD} = .05).
@@
 
+Figure 4 presents these comparisons visually.
+First exploring the right side of Figure 4, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings.
+The white bars representing resources are consistently higher.
+As described above, the left side of Figure 4 shows literature-derived demand categories (e.g., work pressure).
+However, in contrast, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as ``high'' gray and black bars and ``low'' white bars).
+In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be ``hindrances'' at work.
+
 Repeated-measures ANOVAs were computed for the group of literature-implicated \emph{resources} first (see the right hand side of Figure 4).
@@
 The effect for \texttt{Autonomy} was \(F_{(2, 1074)}\) = 951.90 (\(\eta^2\) = 0.64).
-The effect for \texttt{Team\ Cohesion} was \(F_{(2, 1120)}\) = 853.39 (\(\eta^2\) = 0.60).Statistical significance was less then .001 for all four category comparisons.
+The effect for \texttt{Team\ Cohesion} was \(F_{(2, 1120)}\) = 853.39 (\(\eta^2\) = 0.60).
+Statistical significance was less then .001 for all four category comparisons.
 Here, the pattern was as expected.
@@
 However, as can be seen, mean challenge (which is a demand) was rated quite similarly and above the midpoint of 3 across JD-R categories.
+In fact, the means were nearly identical for resource and challenge ratings for all for categories.
+The literature-implied category with the lowest resource rating also has the highest hindrance rating, so job control is positive and negative.
 
@@
 See the pattern of white resource bars on the left hand side of Figure 4.
-
-Figure 4 presents these comparisons visually.
-First exploring the right side of Figure 4, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings.
-The white bars representing resources are consistently higher.
-As described above, the left side of Figure 4 shows literature-derived demand categories (e.g., work pressure).
-However, in contrast, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as ``high'' gray and black bars and ``low'' white bars).
-In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be ``hindrances'' at work.
+In other words, demands are viewed as resources.
 In sum, these results provide some support for RQ 1 and 2.

### 2023-03-07 SIOP2023/Counts/counts_poster.Rmd

--- 2023-02-24 SIOP2023/Counts/counts_poster.Rmd
@@
   - num: 2
-    address: eRg
+    address: e`r fontawesome::fa("r-project")`g
 column_numbers: 3
@@
 
-Stress was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$ = 2.47, *p* = .060, $R^2$ = .01; see Table \@ref(tab:regressiontablestr).
+<br />
+<br />
+Stress was not predicted by total resources, challenge, or hindrance demands, $F_{(3, 564)}$ = 2.47, *p* = .060, $R^2$ = .01; Table \@ref(tab:regressiontablestr).
 

### 2023-03-11 Submission.Rmd
updated results one last time today
minor Saturday adds

@@
     corresponding : yes    # Define only one corresponding author
-    address       : "Menomenie, WI"
+    address       : "470M Harvey Hall, 721 3rd Street E, Menomenie, WI, 54751, USA"
     email         : "stachowskia@uwstout.edu"
   - name          : "John Kulas"
+    address       : "Minneapolis, MN"
     affiliation   : "2"
   - name          : "Renata Garcia Prieto Palacios Roji"
+    address       : "Dallas, TX"
     affiliation   : "3"
@@
   - id            : "1"
-    institution   : "University of Wisconsin - Stout"
+    institution   : "University of Wisconsin-Stout"
   - id            : "2"
@@
     institution   : "PepsiCo"
+
+authornote: |
+ Funding: This work was supported by the College of Humanities and Social Sciences, Montclair State University, Montclair, NJ.
 
@@
 See the pattern of white resource bars on the left hand side of Figure 4.
+In other words, demands are viewed as resources.
 In sum, these results provide some support for RQ 1 and 2.

### 2023-03-11 Submission.tex
minor Saturday adds

@@
 
+\shorttitle{O*NET JD-R}
+
 \authornote{
 
-Correspondence concerning this article should be addressed to Alicia Stachowski, Menomenie, WI. E-mail: \href{mailto:stachowskia@uwstout.edu}{\nolinkurl{stachowskia@uwstout.edu}}
+Funding: This work was supported by the College of Humanities and Social Sciences, Montclair State University, Montclair, NJ.
+
+Correspondence concerning this article should be addressed to Alicia Stachowski, 470M Harvey Hall, 721 3rd Street E, Menomenie, WI, 54751, USA.
+E-mail: \href{mailto:stachowskia@uwstout.edu}{\nolinkurl{stachowskia@uwstout.edu}}
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Wisconsin - Stout\\\textsuperscript{2} eRg\\\textsuperscript{3} PepsiCo}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Wisconsin-Stout\\\textsuperscript{2} eRg\\\textsuperscript{3} PepsiCo}
 
-\abstract{
+\abstract{%
 Much of our understanding of job demands and resources rests on the assumption that some aspects and components of one's job are resources and some are demands.
@@
 A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} = 0.00 ).
-In sum, these results provide some collective support for H1, and particularly so for hindrances, which are consistently viewed as ``different.''
+In sum, these results provide some collective support for H1, and particularly so for hindrances, which are consistently viewed as ``different''.
 
@@
 1. onet.resource.ii & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
-2. onet.resource.mp & .61* & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.19 & 0.60\\
-3. onet.resource.wo & .46* & .50* & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.79 & 0.84\\
-4. onet.resource.io & .49* & .64* & .45* & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.10 & 0.60\\
-5. onet.resource.ir & .46* & .55* & .37* & .60* & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.80 & 0.61\\
-6. onet.resource.pc & .19* & .15* & .32* & .18* & .37* & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 2.99 & 0.77\\
-7. onet.resource.sc & .43* & .46* & .41* & .45* & .48* & .37* & - &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.61\\
-8. onet.challenge.ii & .62* & .49* & .37* & .41* & .33* & .08 & .33* & - &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
-9. onet.challenge.mp & .47* & .63* & .42* & .50* & .41* & .09* & .38* & .65* & - &  &  &  &  &  &  &  &  &  &  &  & 4.20 & 0.64\\
-10. onet.challenge.wo & .34* & .39* & .64* & .34* & .30* & .29* & .38* & .45* & .49* & - &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.88\\
-11. onet.challenge.io & .34* & .48* & .33* & .65* & .48* & .13* & .40* & .50* & .68* & .43* & - &  &  &  &  &  &  &  &  &  & 4.07 & 0.64\\
-12. onet.challenge.ir & .32* & .40* & .26* & .48* & .63* & .23* & .39* & .46* & .60* & .39* & .70* & - &  &  &  &  &  &  &  &  & 3.85 & 0.63\\
-13. onet.challenge.pc & .12* & .08 & .21* & .13* & .26* & .66* & .29* & .14* & .12* & .33* & .20* & .31* & - &  &  &  &  &  &  &  & 2.85 & 0.79\\
-14. onet.challenge.sc & .27* & .31* & .28* & .38* & .40* & .27* & .62* & .36* & .41* & .38* & .51* & .45* & .40* & - &  &  &  &  &  &  & 3.66 & 0.59\\
-15. onet.hindrance.ii & -.26* & -.26* & -.17* & -.24* & -.18* & -.02 & -.08 & -.27* & -.26* & -.10* & -.19* & -.16* & .06 & -.10* & - &  &  &  &  &  & 2.15 & 1.01\\
-16. onet.hindrance.mp & -.23* & -.30* & -.17* & -.22* & -.15* & .05 & -.07 & -.22* & -.27* & -.10* & -.18* & -.15* & .12* & -.06 & .86* & - &  &  &  &  & 2.10 & 1.05\\
-17. onet.hindrance.wo & -.21* & -.25* & -.22* & -.22* & -.06 & -.02 & -.12* & -.14* & -.21* & -.23* & -.15* & -.09* & .05 & -.10* & .66* & .69* & - &  &  &  & 2.31 & 1.02\\
-18. onet.hindrance.io & -.22* & -.27* & -.14* & -.29* & -.18* & -.01 & -.10* & -.21* & -.25* & -.10* & -.27* & -.19* & .07 & -.10* & .79* & .86* & .69* & - &  &  & 2.23 & 1.03\\
-19. onet.hindrance.ir & -.22* & -.24* & -.15* & -.24* & -.25* & -.06 & -.11* & -.19* & -.21* & -.08* & -.20* & -.23* & .04 & -.12* & .79* & .80* & .61* & .82* & - &  & 2.35 & 0.89\\
-20. onet.hindrance.pc & -.04 & -.08* & -.09* & -.11* & -.10* & -.16* & -.13* & -.03 & -.04 & -.06 & -.08* & -.10* & -.04 & -.13* & .38* & .33* & .47* & .35* & .47* & - & 2.66 & 0.83\\
-21. onet.hindrance.sc & -.13* & -.15* & -.13* & -.19* & -.13* & -.09* & -.23* & -.12* & -.10* & -.05 & -.16* & -.12* & -.01 & -.17* & .62* & .62* & .56* & .64* & .66* & .45* & 2.64 & 0.80\\
+2. onet.resource.mp & .61*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.19 & 0.60\\
+3. onet.resource.wo & .46*** & .50*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.79 & 0.84\\
+4. onet.resource.io & .49*** & .64*** & .45*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.10 & 0.60\\
+5. onet.resource.ir & .46*** & .55*** & .37*** & .60*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.80 & 0.61\\
+6. onet.resource.pc & .19*** & .15*** & .32*** & .18*** & .37*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 2.99 & 0.77\\
+7. onet.resource.sc & .43*** & .46*** & .41*** & .45*** & .48*** & .37*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.61\\
+8. onet.challenge.ii & .62*** & .49*** & .37*** & .41*** & .33*** & .08 & .33*** & - &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
+9. onet.challenge.mp & .47*** & .63*** & .42*** & .50*** & .41*** & .09* & .38*** & .65*** & - &  &  &  &  &  &  &  &  &  &  &  & 4.20 & 0.64\\
+10. onet.challenge.wo & .34*** & .39*** & .64*** & .34*** & .30*** & .29*** & .38*** & .45*** & .49*** & - &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.88\\
+11. onet.challenge.io & .34*** & .48*** & .33*** & .65*** & .48*** & .13** & .40*** & .50*** & .68*** & .43*** & - &  &  &  &  &  &  &  &  &  & 4.07 & 0.64\\
+12. onet.challenge.ir & .32*** & .40*** & .26*** & .48*** & .63*** & .23*** & .39*** & .46*** & .60*** & .39*** & .70*** & - &  &  &  &  &  &  &  &  & 3.85 & 0.63\\
+13. onet.challenge.pc & .12** & .08 & .21*** & .13** & .26*** & .66*** & .29*** & .14** & .12** & .33*** & .20*** & .31*** & - &  &  &  &  &  &  &  & 2.85 & 0.79\\
+14. onet.challenge.sc & .27*** & .31*** & .28*** & .38*** & .40*** & .27*** & .62*** & .36*** & .41*** & .38*** & .51*** & .45*** & .40*** & - &  &  &  &  &  &  & 3.66 & 0.59\\
+15. onet.hindrance.ii & -.26*** & -.26*** & -.17*** & -.24*** & -.18*** & -.02 & -.08 & -.27*** & -.26*** & -.10* & -.19*** & -.16*** & .06 & -.10* & - &  &  &  &  &  & 2.15 & 1.01\\
+16. onet.hindrance.mp & -.23*** & -.30*** & -.17*** & -.22*** & -.15*** & .05 & -.07 & -.22*** & -.27*** & -.10* & -.18*** & -.15*** & .12** & -.06 & .86*** & - &  &  &  &  & 2.10 & 1.05\\
+17. onet.hindrance.wo & -.21*** & -.25*** & -.22*** & -.22*** & -.06 & -.02 & -.12** & -.14** & -.21*** & -.23*** & -.15*** & -.09* & .05 & -.10* & .66*** & .69*** & - &  &  &  & 2.31 & 1.02\\
+18.
+onet.hindrance.io & -.22*** & -.27*** & -.14*** & -.29*** & -.18*** & -.01 & -.10* & -.21*** & -.25*** & -.10* & -.27*** & -.19*** & .07 & -.10* & .79*** & .86*** & .69*** & - &  &  & 2.23 & 1.03\\
+19.
+onet.hindrance.ir & -.22*** & -.24*** & -.15*** & -.24*** & -.25*** & -.06 & -.11** & -.19*** & -.21*** & -.08* & -.20*** & -.23*** & .04 & -.12** & .79*** & .80*** & .61*** & .82*** & - &  & 2.35 & 0.89\\
+20. onet.hindrance.pc & -.04 & -.08* & -.09* & -.11** & -.10* & -.16*** & -.13** & -.03 & -.04 & -.06 & -.08* & -.10* & -.04 & -.13** & .38*** & .33*** & .47*** & .35*** & .47*** & - & 2.66 & 0.83\\
+21.
+onet.hindrance.sc & -.13** & -.15*** & -.13** & -.19*** & -.13** & -.09* & -.23*** & -.12** & -.10* & -.05 & -.16*** & -.12** & -.01 & -.17*** & .62*** & .62*** & .56*** & .64*** & .66*** & .45*** & 2.64 & 0.80\\
 \bottomrule
@@
 For example, autonomy is frequently described as a resource in the JD-R literature.
-An O*Net item in the autonomy category is, ``How much decision making freedom, without supervision, does your job offer?'' This O*Net item was therefore retained within the ``autonomy'' category.
+An O*Net item in the autonomy category is, ``How much decision making freedom, without supervision, does your job offer?''.
+This O*Net item was therefore retained within the ``autonomy'' category.
 Mean ratings of the O*Net items were then computed by element (e.g., all of the items representing autonomy) to explore whether literature-implicated resources and demands were evaluated as such.
@@
 There is individual difference in how employees experience the characteristics of their jobs.
-Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a ``resource'' or ``demand.''
+Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a ``resource'' or ``demand''.
 

### 2023-03-16 Submission.Rmd
Working on correlation table display issue

@@
                   note = "The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)")
+trial <- data_new[c(405:411, 413:419, 421:427)]
+library(apaTables)
+apa.cor.table(trial, filename = "cor.doc", show.conf.interval = FALSE, landscape = TRUE)
+
 ```

### 2023-03-16 Submission.tex
Working on correlation table display issue

--- 2023-03-04 Submission.tex
@@
 
-Correspondence concerning this article should be addressed to Alicia Stachowski, Menomenie, WI. E-mail: \href{mailto:stachowskia@uwstout.edu}{\nolinkurl{stachowskia@uwstout.edu}}
+Funding: This work was supported by the College of Humanities and Social Sciences, Montclair State University, Montclair, NJ.
+
+Correspondence concerning this article should be addressed to Alicia Stachowski, 470M Harvey Hall, 721 3rd Street E, Menomenie, WI, 54751, USA.
+E-mail: \href{mailto:stachowskia@uwstout.edu}{\nolinkurl{stachowskia@uwstout.edu}}
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Wisconsin - Stout\\\textsuperscript{2} eRg\\\textsuperscript{3} PepsiCo}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Wisconsin-Stout\\\textsuperscript{2} eRg\\\textsuperscript{3} PepsiCo}
 
@@
 
+The ability to suppress reporting of reporting confidence intervals has been deprecated in this version.
+The function argument show.conf.interval will be removed in a later version.
+
+Means, standard deviations, and correlations with confidence intervals
+
+Variable M SD 1 2 3\\
+1. onet.resource.ii 3.98 0.80
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\item
+  onet.resource.mp 4.19 0.60 .61**\\
+  {[}.55, .66{]}
+\item
+  onet.resource.wo 3.79 0.84 .46** .50**\\
+  {[}.40, .53{]} {[}.43, .56{]}
+\item
+  onet.resource.io 4.10 0.60 .49** .64** .45**\\
+  {[}.42, .55{]} {[}.59, .69{]} {[}.38, .51{]}
+\item
+  onet.resource.ir 3.80 0.61 .46** .55** .37**\\
+  {[}.40, .53{]} {[}.48, .60{]} {[}.30, .44{]}
+\item
+  onet.resource.pc 2.99 0.77 .19** .15** .32**\\
+  {[}.11, .27{]} {[}.07, .23{]} {[}.24, .39{]}
+\item
+  onet.resource.sc 3.65 0.61 .43** .46** .41**\\
+  {[}.36, .50{]} {[}.39, .52{]} {[}.34, .48{]}
+\item
+  onet.hindrance.ii 2.15 1.01 -.26** -.26** -.17**\\
+  {[}-.34, -.18{]} {[}-.34, -.18{]} {[}-.25, -.09{]}
+\item
+  onet.hindrance.mp 2.10 1.05 -.23** -.30** -.17**\\
+  {[}-.31, -.15{]} {[}-.38, -.22{]} {[}-.25, -.09{]}
+\item
+  onet.hindrance.wo 2.31 1.02 -.21** -.25** -.22**\\
+  {[}-.29, -.13{]} {[}-.33, -.17{]} {[}-.30, -.14{]}
+\item
+  onet.hindrance.io 2.23 1.03 -.22** -.27** -.14**\\
+  {[}-.30, -.14{]} {[}-.34, -.19{]} {[}-.22, -.06{]}
+\item
+  onet.hindrance.ir 2.35 0.89 -.22** -.24** -.15**\\
+  {[}-.30, -.14{]} {[}-.32, -.17{]} {[}-.23, -.07{]}
+\item
+  onet.hindrance.pc 2.66 0.83 -.04 -.08* -.09*\\
+  {[}-.12, .05{]} {[}-.17, -.00{]} {[}-.17, -.01{]}
+\item
+  onet.hindrance.sc 2.64 0.80 -.13** -.15** -.13**\\
+  {[}-.22, -.05{]} {[}-.23, -.06{]} {[}-.21, -.04{]}
+\item
+  onet.challenge.ii 3.98 0.80 .62** .49** .37**\\
+  {[}.56, .67{]} {[}.42, .55{]} {[}.30, .44{]}
+\item
+  onet.challenge.mp 4.20 0.64 .47** .63** .42**\\
+  {[}.40, .53{]} {[}.58, .68{]} {[}.35, .49{]}
+\item
+  onet.challenge.wo 3.65 0.88 .34** .39** .64**\\
+  {[}.26, .41{]} {[}.31, .45{]} {[}.58, .68{]}
+\item
+  onet.challenge.io 4.07 0.64 .34** .48** .33**\\
+  {[}.26, .41{]} {[}.41, .54{]} {[}.26, .41{]}
+\item
+  onet.challenge.ir 3.85 0.63 .32** .40** .26**\\
+  {[}.24, .39{]} {[}.33, .47{]} {[}.18, .34{]}
+\item
+  onet.challenge.pc 2.85 0.79 .12** .08 .21**\\
+  {[}.04, .21{]} {[}-.01, .16{]} {[}.13, .29{]}
+\item
+  onet.challenge.sc 3.66 0.59 .27** .31** .28**\\
+  {[}.19, .35{]} {[}.24, .39{]} {[}.20, .35{]}
+\end{enumerate}
+
+4 5 6 7 8 9
+
+.60**\\
+{[}.54, .65{]}
+
+.18** .37**\\
+{[}.10, .26{]} {[}.29, .43{]}
+
+.45** .48** .37**\\
+{[}.38, .51{]} {[}.42, .55{]} {[}.30, .44{]}
+
+-.24** -.18** -.02 -.08\\
+{[}-.32, -.16{]} {[}-.26, -.09{]} {[}-.10, .06{]} {[}-.16, .00{]}
+
+-.22** -.15** .05 -.07 .86**\\
+{[}-.29, -.14{]} {[}-.23, -.07{]} {[}-.03, .13{]} {[}-.16, .01{]} {[}.84, .88{]}
+
+-.22** -.06 -.02 -.12** .66** .69**\\
+{[}-.30, -.14{]} {[}-.15, .02{]} {[}-.11, .06{]} {[}-.20, -.04{]} {[}.61, .70{]} {[}.65, .73{]}
+
+-.29** -.18** -.01 -.10* .79** .86**\\
+{[}-.37, -.22{]} {[}-.26, -.10{]} {[}-.09, .08{]} {[}-.18, -.02{]} {[}.75, .82{]} {[}.84, .88{]}
+
+-.24** -.25** -.06 -.11** .79** .80**\\
+{[}-.32, -.16{]} {[}-.32, -.17{]} {[}-.14, .03{]} {[}-.19, -.03{]} {[}.75, .82{]} {[}.77, .83{]}
+
+-.11** -.10* -.16** -.13** .38** .33**\\
+{[}-.19, -.03{]} {[}-.18, -.02{]} {[}-.24, -.08{]} {[}-.21, -.05{]} {[}.31, .45{]} {[}.25, .40{]}
+
+-.19** -.13** -.09* -.23** .62** .62**\\
+{[}-.27, -.11{]} {[}-.21, -.04{]} {[}-.17, -.00{]} {[}-.31, -.15{]} {[}.56, .67{]} {[}.56, .66{]}
+
+.41** .33** .08 .33** -.27** -.22**\\
+{[}.33, .47{]} {[}.26, .41{]} {[}-.01, .16{]} {[}.25, .40{]} {[}-.34, -.19{]} {[}-.30, -.14{]}
+
+.50** .41** .09* .38** -.26** -.27**\\
+{[}.43, .56{]} {[}.34, .48{]} {[}.01, .17{]} {[}.30, .44{]} {[}-.33, -.18{]} {[}-.35, -.19{]}
+
+.34** .30** .29** .38** -.10* -.10*\\
+{[}.27, .41{]} {[}.22, .37{]} {[}.21, .36{]} {[}.31, .45{]} {[}-.19, -.02{]} {[}-.18, -.01{]}
+
+.65** .48** .13** .40** -.19** -.18**\\
+{[}.60, .70{]} {[}.42, .54{]} {[}.05, .21{]} {[}.33, .47{]} {[}-.27, -.11{]} {[}-.26, -.10{]}
+
+.48** .63** .23** .39** -.16** -.15**\\
+{[}.41, .54{]} {[}.58, .68{]} {[}.15, .30{]} {[}.32, .46{]} {[}-.24, -.07{]} {[}-.23, -.07{]}
+
+.13** .26** .66** .29** .06 .12**\\
+{[}.05, .21{]} {[}.18, .33{]} {[}.61, .71{]} {[}.21, .36{]} {[}-.03, .14{]} {[}.04, .21{]}
+
+.38** .40** .27** .62** -.10* -.06\\
+{[}.31, .45{]} {[}.33, .47{]} {[}.19, .34{]} {[}.56, .66{]} {[}-.18, -.02{]} {[}-.14, .03{]}
+
+10 11 12 13 14 15
+
+.69**\\
+{[}.65, .73{]}
+
+.61** .82**\\
+{[}.56, .66{]} {[}.80, .85{]}
+
+.47** .35** .47**\\
+{[}.41, .54{]} {[}.28, .42{]} {[}.40, .53{]}
+
+.56** .64** .66** .45**\\
+{[}.50, .61{]} {[}.58, .68{]} {[}.61, .71{]} {[}.39, .52{]}
+
+-.14** -.21** -.19** -.03 -.12**\\
+{[}-.22, -.05{]} {[}-.29, -.13{]} {[}-.27, -.10{]} {[}-.11, .06{]} {[}-.20, -.04{]}
+
+-.21** -.25** -.21** -.04 -.10* .65**\\
+{[}-.29, -.13{]} {[}-.33, -.17{]} {[}-.29, -.13{]} {[}-.13, .04{]} {[}-.19, -.02{]} {[}.59, .69{]}
+
+-.23** -.10* -.08* -.06 -.05 .45**\\
+{[}-.31, -.15{]} {[}-.18, -.02{]} {[}-.17, -.00{]} {[}-.14, .02{]} {[}-.14, .03{]} {[}.38, .51{]}
+
+-.15** -.27** -.20** -.08* -.16** .50**\\
+{[}-.23, -.06{]} {[}-.34, -.19{]} {[}-.28, -.12{]} {[}-.16, -.00{]} {[}-.24, -.08{]} {[}.44, .56{]}
+
+-.09* -.19** -.23** -.10* -.12** .46**\\
+{[}-.17, -.01{]} {[}-.27, -.11{]} {[}-.31, -.15{]} {[}-.18, -.02{]} {[}-.20, -.03{]} {[}.39, .52{]}
+
+.05 .07 .04 -.04 -.01 .14**\\
+{[}-.03, .14{]} {[}-.01, .15{]} {[}-.05, .12{]} {[}-.12, .04{]} {[}-.09, .07{]} {[}.06, .22{]}
+
+-.10* -.10* -.12** -.13** -.17** .36**\\
+{[}-.18, -.02{]} {[}-.18, -.01{]} {[}-.20, -.04{]} {[}-.21, -.05{]} {[}-.25, -.09{]} {[}.29, .43{]}
+
+16 17 18 19 20
+
+.49**\\
+{[}.42, .55{]}
+
+.68** .43**\\
+{[}.63, .72{]} {[}.36, .49{]}
+
+.60** .39** .70**\\
+{[}.54, .65{]} {[}.31, .45{]} {[}.65, .74{]}
+
+.12** .33** .20** .31**\\
+{[}.03, .20{]} {[}.25, .40{]} {[}.12, .28{]} {[}.24, .38{]}
+
+.41** .38** .51** .45** .40**\\
+{[}.34, .48{]} {[}.30, .45{]} {[}.45, .57{]} {[}.38, .51{]} {[}.33, .46{]}
+
+Note. M and SD are used to represent mean and standard deviation, respectively.
+Values in square brackets indicate the 95\% confidence interval.
+The confidence interval is a plausible range of population correlations
+that could have caused the sample correlation (Cumming, 2014).
+* indicates p \textless{} .05. ** indicates p \textless{} .01.
+
 \begin{figure}

### 2023-03-25 Submission.Rmd
coffee shop read-through

--- 2023-03-11 Submission.Rmd
@@
   Much of our understanding of job demands and resources rests on the assumption that some aspects and components of one's job are resources and some are demands.
-We build on a small but growing literature suggesting that individual differences may matter our perception of characteristics as demands and resources.
+We build on a small but growing literature suggesting that individual differences may matter in our perceptions of characteristics as demands and resources.
 The primary aims were to explore 1) whether there is variability in subjective ratings of job characteristics with respect to how much they served as resources and demands, and 2) whether or not there was a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
@@
 The results suggest that job characteristics differ in variability/stability regarding subjective worker perceptions, particularly for hindrance demands which showed the most variability.
-Job characteristics were not uniquely categorized as a resource or demand as evidenced by correlations, and lastly, literature-implicated resources not consistently rated as job resources or demands.
+Job characteristics were not uniquely categorized as a resource or demand, and literature-implicated resources were also implicated as being challenge, but not hindrance demands.
 
@@
 
-Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlights the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance among other outcomes.
+Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlights the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance, among other outcomes.
 However, much of our existing knowledge regarding the way this model functions is grounded in the assumption that job characteristics are generally considered resources or generally considered demands.
-We build on the research of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges].
+We build on the work of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges].
 We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resources) in the workplace, with a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
@@
 In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [e.g., high work pressure is frequently cited as a common demand; @demerouti2001job].
-Cognitively, the perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources) [@bakker2014job].
-Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience despite the typical apriori assignment of a characteristic as objectively a "demand" or "resource".
+Cognitively, the perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation [resulting from resources; @bakker2014job].
+Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience despite the typical *a priori* assignment of a characteristic as objectively a "demand" or "resource".
 We explore this further below.
@@
 
-As described in the last paragraph, job context and characteristics are assigned or appraised as demands or resources.
-Although much of our research on job demands in particular is based on apriori classifications [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand.
+As described above, job context and characteristics are assigned or appraised as demands or resources.
+Although much of our research on job demands in particular is based on *a priori* classifications [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand).
 The stress process speaks to how such individual difference in appraisal is possible.
@@
 Although not suggested by the names, primary and secondary appraisals can happen simultaneously.
-For instance, available resources to cope with a stressor may influence an employee’s initial appraisal of a stressor (e.g., amount of time [resource] available to prepare for the speech may influence one’s primary appraisal of this ask).
+For instance, available resources to cope with a stressor may influence an employee’s initial appraisal of a stressor (e.g., amount of time [resource] available to prepare for the speech may influence one’s primary appraisal of this task).
 
@@
 Although there is a tendency to attach a negative connotation to the word “stress”, @selye1936syndrome defined stress as simple a response to change.
-We return to the employed public figure for this next section.
+We return to the public figure for this next section.
 Consider two employees be called upon to serve as spokespeople for their organization.
@@
 
-The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor [@cavanaugh2000empirical].
+The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor [@cavanaugh2000empirical], in line with @lazarus1984stress.
 @cavanaugh2000empirical delineated between two forms of demands – that of *challenge* and *hindrance* demands.
@@
 @webster2011extending approached this question with three common workplace demands: workload, role ambiguity, and role conflict.
-They found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hindrance demands to different degrees.
+They found while that each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance demand to different degrees.
 
@@
 Many other outcomes are differentially related to challenges and hindrances, largely in the expected direction.
-For example, motivation, job satisfaction, commitment, and performance have been shown to positively relate to challenge stressors and negatively relate to hindrance stressor [@lepine2005meta].
+For example, motivation, job satisfaction, commitment, and performance have been shown to positively relate to challenge stressors and negatively relate to hindrance stressors [@lepine2005meta].
 Turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance stressors [@podsakoff2007differential].
@@
 3).
-In fact, @horan2020review suggest future research continue to move away from apriori classifications of stressors, as doing so can be problematic for theoretical and empirical reasons.
-Theoretically, apriori classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
+They go on to suggest future research continue to move away from *a priori* classifications of stressors, as doing so can be problematic for theoretical and empirical reasons.
+Theoretically, *a priori* classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
 Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time [e.g., @searle2015merits].
-TRANSITION NEEDED HERE.
-I DELETED THE ONET PARAGRAPH.
 
@@
 
-The integration of the literature above results in two primary hypotheses.
+The integration of the literature above culminates with two primary hypotheses.
 The first addresses whether employees generally agree on their appraisals of job characteristics as resources or challenge or hindrance demands.
-For instance, although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, others have reported variability in these appraisals [@lepine2022challenge].
+For instance, although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, others have reported variability in these appraisals [e.g., @lepine2022challenge].
 @lepine2022challenge, in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal.
@@
 This widely accessed database houses hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are continually updated.
-We retained 98 work [activity and context classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*Net groups into *activity* categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
+We retained 98 work [activity and context statements](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*Net groups into *activity* categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
 Work *context* statements are grouped into interpersonal relationships (i.e., the context of the job in terms of human interaction processes), physical work conditions (i.e., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., the relationships or interactions between the worker and the structural characteristics of the job).
 
-O\*Net collects information about these categories by periodically asking workers job characteristic statements/questions, which often have [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).
+O\*Net collects information about these categories by periodically asking workers job characteristic questions, which often have [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).
 For example, "How responsible is the worker for work outcomes and results of other workers?" has response options ranging from *No responsibility* to *Very high responsibility*, while the question, "How often do you use electronic mail in this job?" has options ranging from *Never* to *Every day*.
-We retained O\*Net’s response scales, all of which shared the same 5-point scale regardless of semantic label difference.
+We retained O\*Net’s response scales while asking for statement relevance, all of which shared the same 5-point scale regardless of semantic label difference.
 Other than minor grammatical editing (for example, changing “the worker” to “you”), we also retained the O\*Net wording for our item stems (statements/questions).
@@
 
-Data were collected through Prolific, a data collection platform.
+Data were collected through Prolific, an online data collection platform.
 An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
-Eligibility requirements included being 18+ and holding either a full-time or part-time job.
+Eligibility requirements included being 18 or older and holding either a full-time or part-time job.
 Participants then voluntarily chose to respond to the online survey.
-Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified.
+Participants were asked to think about their primary job, and the items they were presented with depended on the specific job characteristics they initially specified.
 Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (i.e., ...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (i.e., ...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (i.e., ...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
 The total number of items on the survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
-Participants were compensated for their participation in this study estimated to require 45 minutes' time in the amount of six dollars through Prolific.
+Participants were compensated for their participation in this study estimated to require 45 minutes' time in the amount of six US dollars through Prolific.
 
@@
 
-```{r combinegraphs2, fig.cap="Characteristics percieved most *DIS*similarly (lowest standard deviations).", fig.height=10}
+```{r combinegraphs2, fig.cap="Characteristics percieved most *DIS*similarly (largest standard deviations).", fig.height=10}
 
@@
 Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present only extreme snapshots of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency.
-Figure \@ref(fig:combinegraphs) presents the resources, challenges, and hindrances characteristics that are *most consistently agreed on* as indexed by (relatively) low standard deviations, while Figure \@ref(fig:combinegraphs2) presents the characteristics with the greatest amount of *disagreement* across workers.
+Figure \@ref(fig:combinegraphs) presents the resources, challenges, and hindrances that are *most consistently agreed on* as indexed by (relatively) low standard deviations, while Figure \@ref(fig:combinegraphs2) presents the characteristics with the greatest amount of *disagreement* across workers.
+The figures demonstrate that what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
+However, there is considerable less relative agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`).
 
@@
 
-As can be seen in the figures, what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
-However, there is considerable less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`).
-
 In addition to highlighting extremely agreed- or disagreed-upon items, Figure \@ref(fig:overallhist) presents our standard deviation indices across all rated items.
-Here, the Figure \@ref(fig:combinegraphs) discrepancies receive illumination, with the *spread* of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively *bunched* levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
+Here, the Figure \@ref(fig:combinegraphs) discrepancies receive greater context, with the *spread* of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively *bunched* levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
 Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
 This points to *hindrances*, in particular, as being likely amenable to future probing regarding moderating conditions.
-A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* = `r lookie$p.value` ).
-In sum, these results provide some collective support for H1, and  particularly so for hindrances, which are consistently viewed as "different".
+A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* < .01).
+In sum, these results provide some collective support for H1, and  particularly so for hindrances, which are consistently viewed "differently" across our raters.
 
 The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand.
-Table \@ref(tab:cortab) provides the correlations among the O\*Net item groupings by resource, challenge and hindrance demand.
+Table \@ref(tab:cortab) provides the correlations among the O\*Net "scale"-level groupings across ratings of resource, challenge, and hindrance.
 We would expect to see minimal correlations if job characteristics *were* uniquely categorized.
-Here, we do expected to see more than minimal correlations.
-First, the mean correlation within resource categories was .43 (*SD* = .13, range from .15 to .64), and challenge categories were similar (ranging from .12 to .70, *M* = .43, *SD* =.16).
-Hindrance categories had less differentiation across categories ranging from .33 to .86, *M* = .62, *SD* = .17.
-When people perceived hindrances, these seemed to be shared across different types of job activities, whereas challenges challenges and resources exhibited more differentiation.
-We would expect these to be the highest.
+First, the average correlation within all resource categories (variables 1 through 7 in Table \@ref(tab:cortab)) was .43 (*SD* = .13, range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16).
+Hindrance categories, however, had less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, *M* = .62, *SD* = .17.
+When people perceived hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.
 
-The mean resource to challenge correlations within the same dimension ranged from .62 to .66, *M* = .64, *SD* = .02; for example, the association between information input ratings as a resource and as a challenge was .62).
-The correlations between resources and challenges across dimensions (for example, the correlation between mental processes and work output was .42 and .39) ranged from .08 to .50, *M* = .32, *SD* = .12.
-The mean resource to hindrance correlations within the same dimension ranged from -.16 to -.30, *M* = -.24, *SD* = .05).
-The correlations between resources and hindrances across dimensions ranged from .05 to -.27, *M* = -.14, *SD* = .08.
+The mean resource to challenge correlations within the same dimension ranged from .62 to .66 (*M* = .64, *SD* = .02; for example, the association between information input ratings as a resource and as a challenge was .62).
+The correlations between resources and challenges *across* dimensions (for example, the correlation between mental processes and work output was .42 and .39) ranged from .08 to .50, *M* = .32, *SD* = .12.
+The resource-hindrance correlations within the same dimension ranged from -.16 to -.30, *M* = -.24, *SD* = .05), while the correlations between resources and hindrances *across* dimensions ranged from .05 to -.27, *M* = -.14, *SD* = .08.
 The mean challenge to hindrance correlations within the same dimension ranged from -.04 to -.27, *M* = -.21, *SD* = .08).
 The correlations between challenges to hindrances across dimensions ranged from .12 to -.26, *M* = -.11, *SD* = .09.
-Correlations were larger when what was being rated was the same type of characteristic.
-In sum, Challenge and hindrance demands demonstrated smaller relationships, but mostly negative.
-Challenge and resource are strongly and positively related.
+In summary, correlations were larger when what was being rated was the same type of characteristic.
+Challenge and hindrance demands demonstrated smaller relationships, but mostly negative.
+Challenges and resources within the same O\*Net dimensions are strongly and positively related.
 These results provide support for H2, suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is perceived as a *resource* being also perceived as a *challenge*.
@@
                   note = "The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)")
+trial <- data_new[c(405:411, 413:419, 421:427)]
+#library(apaTables)
+#apa.cor.table(trial, filename = "cor.doc", show.conf.interval = FALSE, landscape = TRUE)
+
 ```
@@
 In addition to the two hypotheses, two related research questions were proposed: 1) do literature-implicated resources materialize as perceived resources and 2) do literature-implicated demands materialize as perceived demands?
-To answer these questions, authors first categorized O\*Net items into the JD-R elements listed in the JD-R literature.
-For example, autonomy is frequently described as a resource in the JD-R literature.
+To answer these questions, authors first categorized O\*Net items into the elements listed in the JD-R literature.
+For example, autonomy is frequently described as a resource.
 An O\*Net item in the autonomy category is, “How much decision making freedom, without supervision, does your job offer?”.
@@
 
-Figure 4 presents these comparisons visually.
+Figure 4 presents these comparisons visually, where the bar lengths represent mean ratings within element category (e.g., the white bar represents mean O\*Net resource ratings for a given JD-R element).
 First exploring the right side of Figure 4, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings.
@@
 
-Repeated-measures ANOVAs were computed for the group of literature-implicated *resources* first (see the right hand side of Figure 4).
-The effect for `Job Control` was $F_{(`r report7$ANOVA$DFn`, `r report7$ANOVA$DFd`)}$ = `r report7$ANOVA$F` ($\eta^2$ = `r report7$ANOVA$pes`).
-The effect for `Participation` was $F_{(`r report8$ANOVA$DFn`, `r report8$ANOVA$DFd`)}$ = `r report8$ANOVA$F` ($\eta^2$ = `r report8$ANOVA$pes`).
-The effect for `Autonomy` was $F_{(`r report9$ANOVA$DFn`, `r report9$ANOVA$DFd`)}$ = `r report9$ANOVA$F` ($\eta^2$ = `r report9$ANOVA$pes`).
-The effect for `Team Cohesion` was $F_{(`r report10$ANOVA$DFn`, `r report10$ANOVA$DFd`)}$ = `r report10$ANOVA$F` ($\eta^2$ = `r report10$ANOVA$pes`).
+Repeated-measures ANOVAs were computed for the group of literature-implicated *resources* to further explain the patterns observed descriptively in Figure 4).
+The effect for Job Control was $F_{(`r report7$ANOVA$DFn`, `r report7$ANOVA$DFd`)}$ = `r report7$ANOVA$F` ($\eta^2$ = `r report7$ANOVA$pes`).
+The effect for Participation was $F_{(`r report8$ANOVA$DFn`, `r report8$ANOVA$DFd`)}$ = `r report8$ANOVA$F` ($\eta^2$ = `r report8$ANOVA$pes`).
+The effect for Autonomy was $F_{(`r report9$ANOVA$DFn`, `r report9$ANOVA$DFd`)}$ = `r report9$ANOVA$F` ($\eta^2$ = `r report9$ANOVA$pes`).
+The effect for Team Cohesion was $F_{(`r report10$ANOVA$DFn`, `r report10$ANOVA$DFd`)}$ = `r report10$ANOVA$F` ($\eta^2$ = `r report10$ANOVA$pes`).
 Statistical significance was less then .001 for all four category comparisons.
@@
 See the left hand side of Figure 4.
-The effect for `Overwork` was $F_{(`r report1$ANOVA$DFn`, `r report1$ANOVA$DFd`)}$ = `r report1$ANOVA$F`, partial eta squared $(\eta^2)$ was `r report1$ANOVA$pes`.
-The effect for `Physical Environment` was $F_{(`r report2$ANOVA$DFn`, `r report2$ANOVA$DFd`)}$ = `r report2$ANOVA$F` ($\eta^2$ = `r report2$ANOVA$pes`).
+The effect for Overwork was $F_{(`r report1$ANOVA$DFn`, `r report1$ANOVA$DFd`)}$ = `r report1$ANOVA$F`, $(\eta^2)$ was `r report1$ANOVA$pes`.
+The effect for Physical Environment was $F_{(`r report2$ANOVA$DFn`, `r report2$ANOVA$DFd`)}$ = `r report2$ANOVA$F` ($\eta^2$ = `r report2$ANOVA$pes`).
 The effect for `Time Pressure` was $F_{(`r report3$ANOVA$DFn`, `r report3$ANOVA$DFd`)}$ = `r report3$ANOVA$F` ($\eta^2$ = `r report3$ANOVA$pes`).
-The effect for `Emotional Demands` was $F_{(`r report4$ANOVA$DFn`, `r report4$ANOVA$DFd`)}$ = `r report4$ANOVA$F` ($\eta^2$ = `r report4$ANOVA$pes`).
-The effect for `Recipient Contact` was $F_{(`r report5$ANOVA$DFn`, `r report5$ANOVA$DFd`)}$ = `r report5$ANOVA$F` ($\eta^2$ = `r report5$ANOVA$pes`).
-The effect for `Work Pressure` was $F_{(`r report6$ANOVA$DFn`, `r report6$ANOVA$DFd`)}$ = `r report6$ANOVA$F` ($\eta^2$ = `r report6$ANOVA$pes`).
+The effect for Emotional Demands was $F_{(`r report4$ANOVA$DFn`, `r report4$ANOVA$DFd`)}$ = `r report4$ANOVA$F` ($\eta^2$ = `r report4$ANOVA$pes`).
+The effect for Recipient Contact was $F_{(`r report5$ANOVA$DFn`, `r report5$ANOVA$DFd`)}$ = `r report5$ANOVA$F` ($\eta^2$ = `r report5$ANOVA$pes`).
+The effect for Work Pressure was $F_{(`r report6$ANOVA$DFn`, `r report6$ANOVA$DFd`)}$ = `r report6$ANOVA$F` ($\eta^2$ = `r report6$ANOVA$pes`).
 In all cases, statistical significance was less then .001.
@@
 
-Theoretically, these findings support growing body of literature suggesting that perceptions of resources and demands, broadly, are not universal.
-There is individual difference in how employees experience the characteristics of their jobs.
+Theoretically, these findings support a growing body of literature suggesting that perceptions of resources and demands, broadly, are not universal.
+There are individual difference in how employees experience the characteristics of their jobs.
 Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a “resource” or “demand”.
@@
 These results have implications for managers as well.
-The reality that there is more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging.
-These findings provide comforting support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees’ performance.
+The reality that there are more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging.
+These findings provide support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees’ performance.
 Somewhat surprisingly, hindrances are rated more variably.
@@
 
-As with all individual studies, this project was limited in scope, and as such, there are a number of avenues for future study worth exploring here.
+As with all individual studies, this project was limited in scope, and as such, there are a number of avenues for future study worth exploring.
 First, we captured only a small number of job characteristics given the nature of our research questions.
-Because we asked up to four questions about each characteristics, we were limited in the number of job characteristics we could reasonably include.
+Because we asked up to four questions about each characteristic, we were limited in the number of job characteristics we could reasonably include.
 Related to that, we intentionally worked within the O\*Net database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources/demands.

### 2023-03-25 Submission.tex
coffee shop read-through

--- 2023-03-11 Submission.tex
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={Job Demands-Resources Model Components through the Lens of O*NET Classifications},
-  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
-  pdflang={en-EN},
-  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resoures, job characteristics},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
 
@@
 Much of our understanding of job demands and resources rests on the assumption that some aspects and components of one's job are resources and some are demands.
-We build on a small but growing literature suggesting that individual differences may matter our perception of characteristics as demands and resources.
+We build on a small but growing literature suggesting that individual differences may matter in our perceptions of characteristics as demands and resources.
 The primary aims were to explore 1) whether there is variability in subjective ratings of job characteristics with respect to how much they served as resources and demands, and 2) whether or not there was a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
@@
 The results suggest that job characteristics differ in variability/stability regarding subjective worker perceptions, particularly for hindrance demands which showed the most variability.
-Job characteristics were not uniquely categorized as a resource or demand as evidenced by correlations, and lastly, literature-implicated resources not consistently rated as job resources or demands.
+Job characteristics were not uniquely categorized as a resource or demand, and literature-implicated resources were also implicated as being challenge, but not hindrance demands.
 }
@@
 
-Research on the job demands-resources model (Demerouti et al., 2001) and later job demands-resources theory (Bakker \& Demerouti, 2017) highlights the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance among other outcomes.
+Research on the job demands-resources model (Demerouti et al., 2001) and later job demands-resources theory (Bakker \& Demerouti, 2017) highlights the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance, among other outcomes.
 However, much of our existing knowledge regarding the way this model functions is grounded in the assumption that job characteristics are generally considered resources or generally considered demands.
-We build on the research of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020).
+We build on the work of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020).
 We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resources) in the workplace, with a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
@@
 (2001){]}.
-Cognitively, the perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources) (Bakker \& Demerouti, 2014).
-Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience despite the typical apriori assignment of a characteristic as objectively a ``demand'' or ``resource''.
+Cognitively, the perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation {[}resulting from resources; Bakker and Demerouti (2014){]}.
+Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience despite the typical \emph{a priori} assignment of a characteristic as objectively a ``demand'' or ``resource''.
 We explore this further below.
@@
 
-As described in the last paragraph, job context and characteristics are assigned or appraised as demands or resources.
-Although much of our research on job demands in particular is based on apriori classifications (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand.
+As described above, job context and characteristics are assigned or appraised as demands or resources.
+Although much of our research on job demands in particular is based on \emph{a priori} classifications (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand).
 The stress process speaks to how such individual difference in appraisal is possible.
@@
 Although not suggested by the names, primary and secondary appraisals can happen simultaneously.
-For instance, available resources to cope with a stressor may influence an employee's initial appraisal of a stressor (e.g., amount of time {[}resource{]} available to prepare for the speech may influence one's primary appraisal of this ask).
+For instance, available resources to cope with a stressor may influence an employee's initial appraisal of a stressor (e.g., amount of time {[}resource{]} available to prepare for the speech may influence one's primary appraisal of this task).
 
@@
 Although there is a tendency to attach a negative connotation to the word ``stress'', Selye (1936) defined stress as simple a response to change.
-We return to the employed public figure for this next section.
+We return to the public figure for this next section.
 Consider two employees be called upon to serve as spokespeople for their organization.
@@
 
-The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor (Cavanaugh et al., 2000).
+The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor (Cavanaugh et al., 2000), in line with Lazarus and Folkman (1984).
 Cavanaugh et al.
@@
 (2011) approached this question with three common workplace demands: workload, role ambiguity, and role conflict.
-They found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hindrance demands to different degrees.
+They found while that each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance demand to different degrees.
 
@@
 Many other outcomes are differentially related to challenges and hindrances, largely in the expected direction.
-For example, motivation, job satisfaction, commitment, and performance have been shown to positively relate to challenge stressors and negatively relate to hindrance stressor (J.
+For example, motivation, job satisfaction, commitment, and performance have been shown to positively relate to challenge stressors and negatively relate to hindrance stressors (J.
 A.
@@
 (2020) state that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3).
-In fact, Horan et al.
-(2020) suggest future research continue to move away from apriori classifications of stressors, as doing so can be problematic for theoretical and empirical reasons.
-Theoretically, apriori classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
+They go on to suggest future research continue to move away from \emph{a priori} classifications of stressors, as doing so can be problematic for theoretical and empirical reasons.
+Theoretically, \emph{a priori} classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
 Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time (e.g., Searle \& Auton, 2015).
-TRANSITION NEEDED HERE.
-I DELETED THE ONET PARAGRAPH.
 
@@
 
-The integration of the literature above results in two primary hypotheses.
+The integration of the literature above culminates with two primary hypotheses.
 The first addresses whether employees generally agree on their appraisals of job characteristics as resources or challenge or hindrance demands.
-For instance, although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, others have reported variability in these appraisals (M.
+For instance, although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, others have reported variability in these appraisals (e.g., M.
 A.
@@
 This widely accessed database houses hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are continually updated.
-We retained 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context classifications} which O*Net groups into \emph{activity} categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
+We retained 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context statements} which O*Net groups into \emph{activity} categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
 Work \emph{context} statements are grouped into interpersonal relationships (i.e., the context of the job in terms of human interaction processes), physical work conditions (i.e., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., the relationships or interactions between the worker and the structural characteristics of the job).
 
-O*Net collects information about these categories by periodically asking workers job characteristic statements/questions, which often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}.
+O*Net collects information about these categories by periodically asking workers job characteristic questions, which often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}.
 For example, ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{No responsibility} to \emph{Very high responsibility}, while the question, ``How often do you use electronic mail in this job?'' has options ranging from \emph{Never} to \emph{Every day}.
-We retained O*Net's response scales, all of which shared the same 5-point scale regardless of semantic label difference.
+We retained O*Net's response scales while asking for statement relevance, all of which shared the same 5-point scale regardless of semantic label difference.
 Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we also retained the O*Net wording for our item stems (statements/questions).
@@
 
-Data were collected through Prolific, a data collection platform.
+Data were collected through Prolific, an online data collection platform.
 An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
-Eligibility requirements included being 18+ and holding either a full-time or part-time job.
+Eligibility requirements included being 18 or older and holding either a full-time or part-time job.
 Participants then voluntarily chose to respond to the online survey.
-Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified.
+Participants were asked to think about their primary job, and the items they were presented with depended on the specific job characteristics they initially specified.
 Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (i.e., \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (i.e., \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (i.e., \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
 The total number of items on the survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
-Participants were compensated for their participation in this study estimated to require 45 minutes' time in the amount of six dollars through Prolific.
+Participants were compensated for their participation in this study estimated to require 45 minutes' time in the amount of six US dollars through Prolific.
 
@@
 \includegraphics{Submission_files/figure-latex/combinegraphs2-1.pdf}
-\caption{\label{fig:combinegraphs2}Characteristics percieved most \emph{DIS}similarly (lowest standard deviations).}
+\caption{\label{fig:combinegraphs2}Characteristics percieved most \emph{DIS}similarly (largest standard deviations).}
 \end{figure}
@@
 The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency.
-Figure \ref{fig:combinegraphs} presents the resources, challenges, and hindrances characteristics that are \emph{most consistently agreed on} as indexed by (relatively) low standard deviations, while Figure \ref{fig:combinegraphs2} presents the characteristics with the greatest amount of \emph{disagreement} across workers.
-
-As can be seen in the figures, what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
-However, there is considerable less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16).
+Figure \ref{fig:combinegraphs} presents the resources, challenges, and hindrances that are \emph{most consistently agreed on} as indexed by (relatively) low standard deviations, while Figure \ref{fig:combinegraphs2} presents the characteristics with the greatest amount of \emph{disagreement} across workers.
+The figures demonstrate that what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
+However, there is considerable less relative agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16).
 
 In addition to highlighting extremely agreed- or disagreed-upon items, Figure \ref{fig:overallhist} presents our standard deviation indices across all rated items.
-Here, the Figure \ref{fig:combinegraphs} discrepancies receive illumination, with the \emph{spread} of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively \emph{bunched} levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
+Here, the Figure \ref{fig:combinegraphs} discrepancies receive greater context, with the \emph{spread} of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively \emph{bunched} levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
 Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
 This points to \emph{hindrances}, in particular, as being likely amenable to future probing regarding moderating conditions.
-A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} = 0.00 ).
-In sum, these results provide some collective support for H1, and particularly so for hindrances, which are consistently viewed as ``different''.
+A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} \textless{} .01).
+In sum, these results provide some collective support for H1, and particularly so for hindrances, which are consistently viewed ``differently'' across our raters.
 
 The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand.
-Table \ref{tab:cortab} provides the correlations among the O*Net item groupings by resource, challenge and hindrance demand.
+Table \ref{tab:cortab} provides the correlations among the O*Net ``scale''-level groupings across ratings of resource, challenge, and hindrance.
 We would expect to see minimal correlations if job characteristics \emph{were} uniquely categorized.
-Here, we do expected to see more than minimal correlations.
-First, the mean correlation within resource categories was .43 (\emph{SD} = .13, range from .15 to .64), and challenge categories were similar (ranging from .12 to .70, \emph{M} = .43, \emph{SD} =.16).
-Hindrance categories had less differentiation across categories ranging from .33 to .86, \emph{M} = .62, \emph{SD} = .17.
-When people perceived hindrances, these seemed to be shared across different types of job activities, whereas challenges challenges and resources exhibited more differentiation.
-We would expect these to be the highest.
+First, the average correlation within all resource categories (variables 1 through 7 in Table \ref{tab:cortab}) was .43 (\emph{SD} = .13, range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, \emph{M} = .43, \emph{SD} =.16).
+Hindrance categories, however, had less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, \emph{M} = .62, \emph{SD} = .17.
+When people perceived hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.
 
-The mean resource to challenge correlations within the same dimension ranged from .62 to .66, \emph{M} = .64, \emph{SD} = .02; for example, the association between information input ratings as a resource and as a challenge was .62).
-The correlations between resources and challenges across dimensions (for example, the correlation between mental processes and work output was .42 and .39) ranged from .08 to .50, \emph{M} = .32, \emph{SD} = .12.
-The mean resource to hindrance correlations within the same dimension ranged from -.16 to -.30, \emph{M} = -.24, \emph{SD} = .05).
-The correlations between resources and hindrances across dimensions ranged from .05 to -.27, \emph{M} = -.14, \emph{SD} = .08.
+The mean resource to challenge correlations within the same dimension ranged from .62 to .66 (\emph{M} = .64, \emph{SD} = .02; for example, the association between information input ratings as a resource and as a challenge was .62).
+The correlations between resources and challenges \emph{across} dimensions (for example, the correlation between mental processes and work output was .42 and .39) ranged from .08 to .50, \emph{M} = .32, \emph{SD} = .12.
+The resource-hindrance correlations within the same dimension ranged from -.16 to -.30, \emph{M} = -.24, \emph{SD} = .05), while the correlations between resources and hindrances \emph{across} dimensions ranged from .05 to -.27, \emph{M} = -.14, \emph{SD} = .08.
 The mean challenge to hindrance correlations within the same dimension ranged from -.04 to -.27, \emph{M} = -.21, \emph{SD} = .08).
 The correlations between challenges to hindrances across dimensions ranged from .12 to -.26, \emph{M} = -.11, \emph{SD} = .09.
-Correlations were larger when what was being rated was the same type of characteristic.
-In sum, Challenge and hindrance demands demonstrated smaller relationships, but mostly negative.
-Challenge and resource are strongly and positively related.
+In summary, correlations were larger when what was being rated was the same type of characteristic.
+Challenge and hindrance demands demonstrated smaller relationships, but mostly negative.
+Challenges and resources within the same O*Net dimensions are strongly and positively related.
 These results provide support for H2, suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is perceived as a \emph{resource} being also perceived as a \emph{challenge}.
@@
 1. onet.resource.ii & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
-2. onet.resource.mp & .61*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.19 & 0.60\\
-3. onet.resource.wo & .46*** & .50*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.79 & 0.84\\
-4. onet.resource.io & .49*** & .64*** & .45*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.10 & 0.60\\
-5. onet.resource.ir & .46*** & .55*** & .37*** & .60*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.80 & 0.61\\
-6. onet.resource.pc & .19*** & .15*** & .32*** & .18*** & .37*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 2.99 & 0.77\\
-7. onet.resource.sc & .43*** & .46*** & .41*** & .45*** & .48*** & .37*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.61\\
-8. onet.challenge.ii & .62*** & .49*** & .37*** & .41*** & .33*** & .08 & .33*** & - &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
-9. onet.challenge.mp & .47*** & .63*** & .42*** & .50*** & .41*** & .09* & .38*** & .65*** & - &  &  &  &  &  &  &  &  &  &  &  & 4.20 & 0.64\\
-10. onet.challenge.wo & .34*** & .39*** & .64*** & .34*** & .30*** & .29*** & .38*** & .45*** & .49*** & - &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.88\\
-11. onet.challenge.io & .34*** & .48*** & .33*** & .65*** & .48*** & .13** & .40*** & .50*** & .68*** & .43*** & - &  &  &  &  &  &  &  &  &  & 4.07 & 0.64\\
-12. onet.challenge.ir & .32*** & .40*** & .26*** & .48*** & .63*** & .23*** & .39*** & .46*** & .60*** & .39*** & .70*** & - &  &  &  &  &  &  &  &  & 3.85 & 0.63\\
-13. onet.challenge.pc & .12** & .08 & .21*** & .13** & .26*** & .66*** & .29*** & .14** & .12** & .33*** & .20*** & .31*** & - &  &  &  &  &  &  &  & 2.85 & 0.79\\
-14. onet.challenge.sc & .27*** & .31*** & .28*** & .38*** & .40*** & .27*** & .62*** & .36*** & .41*** & .38*** & .51*** & .45*** & .40*** & - &  &  &  &  &  &  & 3.66 & 0.59\\
-15. onet.hindrance.ii & -.26*** & -.26*** & -.17*** & -.24*** & -.18*** & -.02 & -.08 & -.27*** & -.26*** & -.10* & -.19*** & -.16*** & .06 & -.10* & - &  &  &  &  &  & 2.15 & 1.01\\
-16. onet.hindrance.mp & -.23*** & -.30*** & -.17*** & -.22*** & -.15*** & .05 & -.07 & -.22*** & -.27*** & -.10* & -.18*** & -.15*** & .12** & -.06 & .86*** & - &  &  &  &  & 2.10 & 1.05\\
-17. onet.hindrance.wo & -.21*** & -.25*** & -.22*** & -.22*** & -.06 & -.02 & -.12** & -.14** & -.21*** & -.23*** & -.15*** & -.09* & .05 & -.10* & .66*** & .69*** & - &  &  &  & 2.31 & 1.02\\
-18.
-onet.hindrance.io & -.22*** & -.27*** & -.14*** & -.29*** & -.18*** & -.01 & -.10* & -.21*** & -.25*** & -.10* & -.27*** & -.19*** & .07 & -.10* & .79*** & .86*** & .69*** & - &  &  & 2.23 & 1.03\\
-19.
-onet.hindrance.ir & -.22*** & -.24*** & -.15*** & -.24*** & -.25*** & -.06 & -.11** & -.19*** & -.21*** & -.08* & -.20*** & -.23*** & .04 & -.12** & .79*** & .80*** & .61*** & .82*** & - &  & 2.35 & 0.89\\
-20. onet.hindrance.pc & -.04 & -.08* & -.09* & -.11** & -.10* & -.16*** & -.13** & -.03 & -.04 & -.06 & -.08* & -.10* & -.04 & -.13** & .38*** & .33*** & .47*** & .35*** & .47*** & - & 2.66 & 0.83\\
-21.
-onet.hindrance.sc & -.13** & -.15*** & -.13** & -.19*** & -.13** & -.09* & -.23*** & -.12** & -.10* & -.05 & -.16*** & -.12** & -.01 & -.17*** & .62*** & .62*** & .56*** & .64*** & .66*** & .45*** & 2.64 & 0.80\\
+2. onet.resource.mp & .61* & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.19 & 0.60\\
+3. onet.resource.wo & .46* & .50* & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.79 & 0.84\\
+4. onet.resource.io & .49* & .64* & .45* & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.10 & 0.60\\
+5. onet.resource.ir & .46* & .55* & .37* & .60* & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.80 & 0.61\\
+6. onet.resource.pc & .19* & .15* & .32* & .18* & .37* & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 2.99 & 0.77\\
+7. onet.resource.sc & .43* & .46* & .41* & .45* & .48* & .37* & - &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.61\\
+8. onet.challenge.ii & .62* & .49* & .37* & .41* & .33* & .08 & .33* & - &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
+9. onet.challenge.mp & .47* & .63* & .42* & .50* & .41* & .09* & .38* & .65* & - &  &  &  &  &  &  &  &  &  &  &  & 4.20 & 0.64\\
+10. onet.challenge.wo & .34* & .39* & .64* & .34* & .30* & .29* & .38* & .45* & .49* & - &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.88\\
+11. onet.challenge.io & .34* & .48* & .33* & .65* & .48* & .13* & .40* & .50* & .68* & .43* & - &  &  &  &  &  &  &  &  &  & 4.07 & 0.64\\
+12. onet.challenge.ir & .32* & .40* & .26* & .48* & .63* & .23* & .39* & .46* & .60* & .39* & .70* & - &  &  &  &  &  &  &  &  & 3.85 & 0.63\\
+13. onet.challenge.pc & .12* & .08 & .21* & .13* & .26* & .66* & .29* & .14* & .12* & .33* & .20* & .31* & - &  &  &  &  &  &  &  & 2.85 & 0.79\\
+14. onet.challenge.sc & .27* & .31* & .28* & .38* & .40* & .27* & .62* & .36* & .41* & .38* & .51* & .45* & .40* & - &  &  &  &  &  &  & 3.66 & 0.59\\
+15. onet.hindrance.ii & -.26* & -.26* & -.17* & -.24* & -.18* & -.02 & -.08 & -.27* & -.26* & -.10* & -.19* & -.16* & .06 & -.10* & - &  &  &  &  &  & 2.15 & 1.01\\
+16. onet.hindrance.mp & -.23* & -.30* & -.17* & -.22* & -.15* & .05 & -.07 & -.22* & -.27* & -.10* & -.18* & -.15* & .12* & -.06 & .86* & - &  &  &  &  & 2.10 & 1.05\\
+17. onet.hindrance.wo & -.21* & -.25* & -.22* & -.22* & -.06 & -.02 & -.12* & -.14* & -.21* & -.23* & -.15* & -.09* & .05 & -.10* & .66* & .69* & - &  &  &  & 2.31 & 1.02\\
+18. onet.hindrance.io & -.22* & -.27* & -.14* & -.29* & -.18* & -.01 & -.10* & -.21* & -.25* & -.10* & -.27* & -.19* & .07 & -.10* & .79* & .86* & .69* & - &  &  & 2.23 & 1.03\\
+19. onet.hindrance.ir & -.22* & -.24* & -.15* & -.24* & -.25* & -.06 & -.11* & -.19* & -.21* & -.08* & -.20* & -.23* & .04 & -.12* & .79* & .80* & .61* & .82* & - &  & 2.35 & 0.89\\
+20. onet.hindrance.pc & -.04 & -.08* & -.09* & -.11* & -.10* & -.16* & -.13* & -.03 & -.04 & -.06 & -.08* & -.10* & -.04 & -.13* & .38* & .33* & .47* & .35* & .47* & - & 2.66 & 0.83\\
+21. onet.hindrance.sc & -.13* & -.15* & -.13* & -.19* & -.13* & -.09* & -.23* & -.12* & -.10* & -.05 & -.16* & -.12* & -.01 & -.17* & .62* & .62* & .56* & .64* & .66* & .45* & 2.64 & 0.80\\
 \bottomrule
@@
 In addition to the two hypotheses, two related research questions were proposed: 1) do literature-implicated resources materialize as perceived resources and 2) do literature-implicated demands materialize as perceived demands?
-To answer these questions, authors first categorized O*Net items into the JD-R elements listed in the JD-R literature.
-For example, autonomy is frequently described as a resource in the JD-R literature.
+To answer these questions, authors first categorized O*Net items into the elements listed in the JD-R literature.
+For example, autonomy is frequently described as a resource.
 An O*Net item in the autonomy category is, ``How much decision making freedom, without supervision, does your job offer?''.
@@
 
-Figure 4 presents these comparisons visually.
+Figure 4 presents these comparisons visually, where the bar lengths represent mean ratings within element category (e.g., the white bar represents mean O*Net resource ratings for a given JD-R element).
 First exploring the right side of Figure 4, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings.
@@
 
-Repeated-measures ANOVAs were computed for the group of literature-implicated \emph{resources} first (see the right hand side of Figure 4).
-The effect for \texttt{Job\ Control} was \(F_{(2, 1134)}\) = 52.78 (\(\eta^2\) = 0.08).
-The effect for \texttt{Participation} was \(F_{(2, 1124)}\) = 991.16 (\(\eta^2\) = 0.64).
-The effect for \texttt{Autonomy} was \(F_{(2, 1074)}\) = 951.90 (\(\eta^2\) = 0.64).
-The effect for \texttt{Team\ Cohesion} was \(F_{(2, 1120)}\) = 853.39 (\(\eta^2\) = 0.60).
+Repeated-measures ANOVAs were computed for the group of literature-implicated \emph{resources} to further explain the patterns observed descriptively in Figure 4).
+The effect for Job Control was \(F_{(2, 1134)}\) = 52.78 (\(\eta^2\) = 0.08).
+The effect for Participation was \(F_{(2, 1124)}\) = 991.16 (\(\eta^2\) = 0.64).
+The effect for Autonomy was \(F_{(2, 1074)}\) = 951.90 (\(\eta^2\) = 0.64).
+The effect for Team Cohesion was \(F_{(2, 1120)}\) = 853.39 (\(\eta^2\) = 0.60).
 Statistical significance was less then .001 for all four category comparisons.
@@
 See the left hand side of Figure 4.
-The effect for \texttt{Overwork} was \(F_{(2, 1134)}\) = 17.71, partial eta squared \((\eta^2)\) was 0.03.
-The effect for \texttt{Physical\ Environment} was \(F_{(2, 1108)}\) = 112.97 (\(\eta^2\) = 0.17).
+The effect for Overwork was \(F_{(2, 1134)}\) = 17.71, \((\eta^2)\) was 0.03.
+The effect for Physical Environment was \(F_{(2, 1108)}\) = 112.97 (\(\eta^2\) = 0.17).
 The effect for \texttt{Time\ Pressure} was \(F_{(2, 1090)}\) = 82.22 (\(\eta^2\) = 0.13).
-The effect for \texttt{Emotional\ Demands} was \(F_{(2, 1098)}\) = 393.43 (\(\eta^2\) = 0.42).
-The effect for \texttt{Recipient\ Contact} was \(F_{(2, 1126)}\) = 1,031.73 (\(\eta^2\) = 0.65).
-The effect for \texttt{Work\ Pressure} was \(F_{(2, 1132)}\) = 718.12 (\(\eta^2\) = 0.56).
+The effect for Emotional Demands was \(F_{(2, 1098)}\) = 393.43 (\(\eta^2\) = 0.42).
+The effect for Recipient Contact was \(F_{(2, 1126)}\) = 1,031.73 (\(\eta^2\) = 0.65).
+The effect for Work Pressure was \(F_{(2, 1132)}\) = 718.12 (\(\eta^2\) = 0.56).
 In all cases, statistical significance was less then .001.
@@
 
-Theoretically, these findings support growing body of literature suggesting that perceptions of resources and demands, broadly, are not universal.
-There is individual difference in how employees experience the characteristics of their jobs.
+Theoretically, these findings support a growing body of literature suggesting that perceptions of resources and demands, broadly, are not universal.
+There are individual difference in how employees experience the characteristics of their jobs.
 Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a ``resource'' or ``demand''.
@@
 These results have implications for managers as well.
-The reality that there is more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging.
-These findings provide comforting support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees' performance.
+The reality that there are more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging.
+These findings provide support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees' performance.
 Somewhat surprisingly, hindrances are rated more variably.
@@
 
-As with all individual studies, this project was limited in scope, and as such, there are a number of avenues for future study worth exploring here.
+As with all individual studies, this project was limited in scope, and as such, there are a number of avenues for future study worth exploring.
 First, we captured only a small number of job characteristics given the nature of our research questions.
-Because we asked up to four questions about each characteristics, we were limited in the number of job characteristics we could reasonably include.
+Because we asked up to four questions about each characteristic, we were limited in the number of job characteristics we could reasonably include.
 Related to that, we intentionally worked within the O*Net database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources/demands.

### 2023-03-28 Submission.Rmd
hopefully final edits

@@
 This widely accessed database houses hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are continually updated.
-We retained 98 work [activity and context statements](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*Net groups into *activity* categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
-Work *context* statements are grouped into interpersonal relationships (i.e., the context of the job in terms of human interaction processes), physical work conditions (i.e., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., the relationships or interactions between the worker and the structural characteristics of the job).
+We focused on 98 work [activity and context statements](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*Net groups into *activity* categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
+Work *context* statements are grouped into interpersonal relationships (e.g., the context of the job in terms of human interaction processes), physical work conditions (e.g., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (e.g., the relationships or interactions between the worker and the structural characteristics of the job).
 
 O\*Net collects information about these categories by periodically asking workers job characteristic questions, which often have [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).
-For example, "How responsible is the worker for work outcomes and results of other workers?" has response options ranging from *No responsibility* to *Very high responsibility*, while the question, "How often do you use electronic mail in this job?" has options ranging from *Never* to *Every day*.
+For example, "How responsible is the worker for work outcomes and results of other workers?" has response options ranging from *no responsibility* to *very high responsibility*, while the question, "How often do you use electronic mail in this job?" has options ranging from *never* to *every day*.
 We retained O\*Net’s response scales while asking for statement relevance, all of which shared the same 5-point scale regardless of semantic label difference.
-Other than minor grammatical editing (for example, changing “the worker” to “you”), we also retained the O\*Net wording for our item stems (statements/questions).
+Other than minor grammatical editing (for example, changing “the worker” to “you”), we also retained the O\*Net wording for our item stems.
 
@@
 Participants were asked to think about their primary job, and the items they were presented with depended on the specific job characteristics they initially specified.
-Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (i.e., ...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (i.e., ...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (i.e., ...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
+Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
 The total number of items on the survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
-Participants were compensated for their participation in this study estimated to require 45 minutes' time in the amount of six US dollars through Prolific.
+Participants were compensated for their participation in this study estimated to require 45 minutes' time in the amount of six dollars through Prolific.
 
@@
 The figures demonstrate that what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
-However, there is considerable less relative agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`).
+However, there is considerably less relative agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`).
 
@@
 A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* < .01).
-In sum, these results provide some collective support for H1, and  particularly so for hindrances, which are consistently viewed "differently" across our raters.
+In sum, these results provide some collective support for H1, and  particularly so for hindrances, which are differently experienced across our raters.
 
@@
 When people perceived hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.
+Taken with the Figure \@ref(fig:overallhist) takeaway, this hints that workers are likely either generally experiencing hindrances at work or they are not.
 
@@
 The correlations between resources and challenges *across* dimensions (for example, the correlation between mental processes and work output was .42 and .39) ranged from .08 to .50, *M* = .32, *SD* = .12.
-The resource-hindrance correlations within the same dimension ranged from -.16 to -.30, *M* = -.24, *SD* = .05), while the correlations between resources and hindrances *across* dimensions ranged from .05 to -.27, *M* = -.14, *SD* = .08.
-The mean challenge to hindrance correlations within the same dimension ranged from -.04 to -.27, *M* = -.21, *SD* = .08).
+The resource-hindrance correlations within the same dimension ranged from -.16 to -.30 (*M* = -.24, *SD* = .05), while the correlations between resources and hindrances *across* dimensions ranged from .05 to -.27, *M* = -.14, *SD* = .08.
+The mean challenge to hindrance correlations within the same dimension ranged from -.04 to -.27 (*M* = -.21, *SD* = .08).
 The correlations between challenges to hindrances across dimensions ranged from .12 to -.26, *M* = -.11, *SD* = .09.
@@
 For example, autonomy is frequently described as a resource.
-An O\*Net item in the autonomy category is, “How much decision making freedom, without supervision, does your job offer?”.
-This O\*Net item was therefore retained within the "autonomy" category.
+An O\*Net item is, “How much decision making freedom, without supervision, does your job offer?”.
+This O\*Net item was retained within the "autonomy" category.
 Mean ratings of the O\*Net items were then computed by element (e.g., all of the items representing autonomy) to explore whether literature-implicated resources and demands were evaluated as such.
@@
 Figure 4 presents these comparisons visually, where the bar lengths represent mean ratings within element category (e.g., the white bar represents mean O\*Net resource ratings for a given JD-R element).
-First exploring the right side of Figure 4, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings.
-The white bars representing resources are consistently higher.
+First exploring the right side of Figure 4, there is a pattern of the highest level ratings being those of literature-derived resources (e.g., job control).
 As described above, the left side of Figure 4 shows literature-derived demand categories (e.g., work pressure).
@@
 
-Repeated-measures ANOVAs were computed for the group of literature-implicated *resources* to further explain the patterns observed descriptively in Figure 4).
+Repeated-measures ANOVAs were computed to further explain each of the patterns observed descriptively in Figure 4.
 The effect for Job Control was $F_{(`r report7$ANOVA$DFn`, `r report7$ANOVA$DFd`)}$ = `r report7$ANOVA$F` ($\eta^2$ = `r report7$ANOVA$pes`).
@@
 The effect for Team Cohesion was $F_{(`r report10$ANOVA$DFn`, `r report10$ANOVA$DFd`)}$ = `r report10$ANOVA$F` ($\eta^2$ = `r report10$ANOVA$pes`).
-Statistical significance was less then .001 for all four category comparisons.
+Statistical significance was less than .001 for all four category comparisons.
 Here, the pattern was as expected.
@@
 
-Next, repeated-measures ANOVAs were then run for the group of literature-implicated *demands*.
-See the left hand side of Figure 4.
-The effect for Overwork was $F_{(`r report1$ANOVA$DFn`, `r report1$ANOVA$DFd`)}$ = `r report1$ANOVA$F`, $(\eta^2)$ was `r report1$ANOVA$pes`.
+Next, repeated-measures ANOVAs were also run for the group of literature-implicated *demands* (see the left hand side of Figure 4).
+The effect for Overwork was $F_{(`r report1$ANOVA$DFn`, `r report1$ANOVA$DFd`)}$ = `r report1$ANOVA$F` ($\eta^2$ was `r report1$ANOVA$pes`).
 The effect for Physical Environment was $F_{(`r report2$ANOVA$DFn`, `r report2$ANOVA$DFd`)}$ = `r report2$ANOVA$F` ($\eta^2$ = `r report2$ANOVA$pes`).
@@
 3).
-The research questions regarding the match between literature-implicated demand and resource categories and empirical ratings aligns with the consistency/variability we observed in H1.
-Interestingly, we consistently observed that job characteristics rated as resources were also rated highly as challenge stressors, which are not inherently negative in the way that hindrance stressors are.
 Lastly, we also found support for the hypothesis that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand (H2).
+Specifically, we consistently observed that job characteristics rated as resources were also rated viewed similarly as challenges.
 
@@
 
-Theoretically, these findings support a growing body of literature suggesting that perceptions of resources and demands, broadly, are not universal.
-There are individual difference in how employees experience the characteristics of their jobs.
 Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a “resource” or “demand”.
+Theoretically, however, our findings support a growing body of literature suggesting that perceptions of resources and demands, broadly, are not universal.
+There are individual differences in how employees experience the characteristics of their jobs.
 
-These results have implications for managers as well.
+These results have implications for practitioners as well, providing support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees’ performance.
 The reality that there are more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging.
-These findings provide support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees’ performance.
 Somewhat surprisingly, hindrances are rated more variably.
 As such, one important implication is that of frequent communication with employees regarding their perceptions of characteristics that limit their performance.
-@lepine2005meta and @podsakoff2007differential encourage organizations to incorporate strain-reducing activities like train and support to offset the negative effects of challenging job demands.
+@lepine2005meta and @podsakoff2007differential encourage organizations to incorporate strain-reducing activities like training and support to offset the negative effects of challenging job demands.
 

### 2023-03-28 Submission.tex
hopefully final edits

@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Job Demands-Resources Model Components through the Lens of O*NET Classifications},
+  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
+  pdflang={en-EN},
+  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resoures, job characteristics},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 This widely accessed database houses hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are continually updated.
-We retained 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context statements} which O*Net groups into \emph{activity} categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
-Work \emph{context} statements are grouped into interpersonal relationships (i.e., the context of the job in terms of human interaction processes), physical work conditions (i.e., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., the relationships or interactions between the worker and the structural characteristics of the job).
+We focused on 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context statements} which O*Net groups into \emph{activity} categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
+Work \emph{context} statements are grouped into interpersonal relationships (e.g., the context of the job in terms of human interaction processes), physical work conditions (e.g., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (e.g., the relationships or interactions between the worker and the structural characteristics of the job).
 
 O*Net collects information about these categories by periodically asking workers job characteristic questions, which often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}.
-For example, ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{No responsibility} to \emph{Very high responsibility}, while the question, ``How often do you use electronic mail in this job?'' has options ranging from \emph{Never} to \emph{Every day}.
+For example, ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{no responsibility} to \emph{very high responsibility}, while the question, ``How often do you use electronic mail in this job?'' has options ranging from \emph{never} to \emph{every day}.
 We retained O*Net's response scales while asking for statement relevance, all of which shared the same 5-point scale regardless of semantic label difference.
-Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we also retained the O*Net wording for our item stems (statements/questions).
+Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we also retained the O*Net wording for our item stems.
 
@@
 Participants were asked to think about their primary job, and the items they were presented with depended on the specific job characteristics they initially specified.
-Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (i.e., \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (i.e., \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (i.e., \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
+Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
 The total number of items on the survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
-Participants were compensated for their participation in this study estimated to require 45 minutes' time in the amount of six US dollars through Prolific.
+Participants were compensated for their participation in this study estimated to require 45 minutes' time in the amount of six dollars through Prolific.
 
@@
 The figures demonstrate that what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
-However, there is considerable less relative agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16).
+However, there is considerably less relative agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16).
 
@@
 A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} \textless{} .01).
-In sum, these results provide some collective support for H1, and particularly so for hindrances, which are consistently viewed ``differently'' across our raters.
+In sum, these results provide some collective support for H1, and particularly so for hindrances, which are differently experienced across our raters.
 
@@
 When people perceived hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.
+Taken with the Figure \ref{fig:overallhist} takeaway, this hints that workers are likely either generally experiencing hindrances at work or they are not.
 
@@
 The correlations between resources and challenges \emph{across} dimensions (for example, the correlation between mental processes and work output was .42 and .39) ranged from .08 to .50, \emph{M} = .32, \emph{SD} = .12.
-The resource-hindrance correlations within the same dimension ranged from -.16 to -.30, \emph{M} = -.24, \emph{SD} = .05), while the correlations between resources and hindrances \emph{across} dimensions ranged from .05 to -.27, \emph{M} = -.14, \emph{SD} = .08.
-The mean challenge to hindrance correlations within the same dimension ranged from -.04 to -.27, \emph{M} = -.21, \emph{SD} = .08).
+The resource-hindrance correlations within the same dimension ranged from -.16 to -.30 (\emph{M} = -.24, \emph{SD} = .05), while the correlations between resources and hindrances \emph{across} dimensions ranged from .05 to -.27, \emph{M} = -.14, \emph{SD} = .08.
+The mean challenge to hindrance correlations within the same dimension ranged from -.04 to -.27 (\emph{M} = -.21, \emph{SD} = .08).
 The correlations between challenges to hindrances across dimensions ranged from .12 to -.26, \emph{M} = -.11, \emph{SD} = .09.
@@
 For example, autonomy is frequently described as a resource.
-An O*Net item in the autonomy category is, ``How much decision making freedom, without supervision, does your job offer?''.
-This O*Net item was therefore retained within the ``autonomy'' category.
+An O*Net item is, ``How much decision making freedom, without supervision, does your job offer?''.
+This O*Net item was retained within the ``autonomy'' category.
 Mean ratings of the O*Net items were then computed by element (e.g., all of the items representing autonomy) to explore whether literature-implicated resources and demands were evaluated as such.
@@
 Figure 4 presents these comparisons visually, where the bar lengths represent mean ratings within element category (e.g., the white bar represents mean O*Net resource ratings for a given JD-R element).
-First exploring the right side of Figure 4, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings.
-The white bars representing resources are consistently higher.
+First exploring the right side of Figure 4, there is a pattern of the highest level ratings being those of literature-derived resources (e.g., job control).
 As described above, the left side of Figure 4 shows literature-derived demand categories (e.g., work pressure).
@@
 
-Repeated-measures ANOVAs were computed for the group of literature-implicated \emph{resources} to further explain the patterns observed descriptively in Figure 4).
-The effect for Job Control was \(F_{(2, 1134)}\) = 52.78 (\(\eta^2\) = 0.08).
+Repeated-measures ANOVAs were computed to further explain each of the patterns observed descriptively in Figure 4. The effect for Job Control was \(F_{(2, 1134)}\) = 52.78 (\(\eta^2\) = 0.08).
 The effect for Participation was \(F_{(2, 1124)}\) = 991.16 (\(\eta^2\) = 0.64).
@@
 The effect for Team Cohesion was \(F_{(2, 1120)}\) = 853.39 (\(\eta^2\) = 0.60).
-Statistical significance was less then .001 for all four category comparisons.
+Statistical significance was less than .001 for all four category comparisons.
 Here, the pattern was as expected.
@@
 
-Next, repeated-measures ANOVAs were then run for the group of literature-implicated \emph{demands}.
-See the left hand side of Figure 4.
-The effect for Overwork was \(F_{(2, 1134)}\) = 17.71, \((\eta^2)\) was 0.03.
+Next, repeated-measures ANOVAs were also run for the group of literature-implicated \emph{demands} (see the left hand side of Figure 4).
+The effect for Overwork was \(F_{(2, 1134)}\) = 17.71 (\(\eta^2\) was 0.03).
 The effect for Physical Environment was \(F_{(2, 1108)}\) = 112.97 (\(\eta^2\) = 0.17).
@@
 (2020)'s conclusion that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3).
-The research questions regarding the match between literature-implicated demand and resource categories and empirical ratings aligns with the consistency/variability we observed in H1.
-Interestingly, we consistently observed that job characteristics rated as resources were also rated highly as challenge stressors, which are not inherently negative in the way that hindrance stressors are.
 Lastly, we also found support for the hypothesis that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand (H2).
+Specifically, we consistently observed that job characteristics rated as resources were also rated viewed similarly as challenges.
 
@@
 
-Theoretically, these findings support a growing body of literature suggesting that perceptions of resources and demands, broadly, are not universal.
-There are individual difference in how employees experience the characteristics of their jobs.
 Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a ``resource'' or ``demand''.
+Theoretically, however, our findings support a growing body of literature suggesting that perceptions of resources and demands, broadly, are not universal.
+There are individual differences in how employees experience the characteristics of their jobs.
 
-These results have implications for managers as well.
+These results have implications for practitioners as well, providing support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees' performance.
 The reality that there are more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging.
-These findings provide support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees' performance.
 Somewhat surprisingly, hindrances are rated more variably.
@@
 (2005) and Podsakoff et al.
-(2007) encourage organizations to incorporate strain-reducing activities like train and support to offset the negative effects of challenging job demands.
+(2007) encourage organizations to incorporate strain-reducing activities like training and support to offset the negative effects of challenging job demands.
 

### 2023-03-28 Submission.Rmd
discussion edits

@@
 
-These results have implications for practitioners as well, providing support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees’ performance.
-The reality that there are more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging.
+These results have implications for practitioners as well, providing support for the idea that managers and supervisors can perhaps predict which characteristics are perceived as supportive to employees’ performance.
+The reality that there are more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is therefore in some ways encouraging.
 Somewhat surprisingly, hindrances are rated more variably.

### 2023-03-28 Submission.tex
discussion edits

@@
 
-These results have implications for practitioners as well, providing support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees' performance.
-The reality that there are more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging.
+These results have implications for practitioners as well, providing support for the idea that managers and supervisors can perhaps predict which characteristics are perceived as supportive to employees' performance.
+The reality that there are more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is therefore in some ways encouraging.
 Somewhat surprisingly, hindrances are rated more variably.

### 2023-03-31 Submission.Rmd
updating implications section

--- 2023-03-28 Submission.Rmd
@@
 
-Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a “resource” or “demand”.
-Theoretically, however, our findings support a growing body of literature suggesting that perceptions of resources and demands, broadly, are not universal.
-There are individual differences in how employees experience the characteristics of their jobs.
+The findings presented above have implications for both theory and practice.
+First, this research is couched within the well-studied job demands-resources theory [@demerouti2001job].We argue that while useful, additional emphasis should be placed on individual differences in perceptions of job characteristics.
+In fact, our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs [@webster2011extending].
+This finding aligns quite well with both the transactional theory of stress and coping, and the challenge-hindrance stressor framework, which collectively argue that employees perceive stimuli (i.e., job characteristics) uniquely [@lazarus1984stress], and thus, could appraise them as either a challenge or hindrance to their job performance [@cavanaugh2000empirical].
+Further, @cavanaugh2000empirical suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes [e.g., @cavanaugh2000empirical].
 
-These results have implications for practitioners as well, providing support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees’ performance.
-The reality that there are more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging.
-Somewhat surprisingly, hindrances are rated more variably.
-As such, one important implication is that of frequent communication with employees regarding their perceptions of characteristics that limit their performance.
-@lepine2005meta and @podsakoff2007differential encourage organizations to incorporate strain-reducing activities like training and support to offset the negative effects of challenging job demands.
+Differences in outcomes depending on whether or not an employee perceives a job characteristic to be a challenge or hindrance has practical implications.
+Our results suggest that what is generally seen as a resource and challenge tends to be somewhat agreed upon.
+As such, managers and supervisors can predict with some confidence which characteristics are perceived as supportive to employees’ performance.
+Somewhat surprisingly, hindrance demands are rated more variably and thus, it may be important to have conversations about job characteristics and expectations at multiple time points after hire.
+Specifically, having conversations with employees regarding their perceptions of characteristics that limit their performance is important.
+Such conversations could happen during an annual performance review or more informally.
+In addition, @lepine2005meta and @podsakoff2007differential encourage organizations to incorporate strain-reducing activities like training and support to offset the negative effects of challenging job demands, which may be associated with increased performance in the short term, but strain when prolonged.
 

### 2023-04-01 Submission.Rmd
finalized submission

@@
 
-The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands (both challenge and hindrance), and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using a sample of items from O\*Net.
-The findings broadly revealed that there was relatively more consistency in ratings of resources and challenges characteristics, and far more variability in job characteristics rated as hindrance stressors.
+The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands (both challenge and hindrance), and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using the comprehensive taxonomy provided by O\*Net.
+The findings broadly revealed that there was relatively more consistency in ratings of resource and challenge characteristics, and far more variability in job characteristics rated as hindrance stressors.
 This finding lends additional evidence to @horan2020review’s conclusion that “...stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p.
@@
 Lastly, we also found support for the hypothesis that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand (H2).
-Specifically, we consistently observed that job characteristics rated as resources were also rated viewed similarly as challenges.
+Specifically, we consistently observed a pattern of job characteristics seen as challenging also being cited as a resource.
 
@@
 The findings presented above have implications for both theory and practice.
-First, this research is couched within the well-studied job demands-resources theory [@demerouti2001job].We argue that while useful, additional emphasis should be placed on individual differences in perceptions of job characteristics.
+First, this research is couched within the well-studied job demands-resources theory [@demerouti2001job].
+We argue that while useful, additional emphasis should be placed on individual differences in perceptions of job characteristics.
 In fact, our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs [@webster2011extending].
@@
 Differences in outcomes depending on whether or not an employee perceives a job characteristic to be a challenge or hindrance has practical implications.
-Our results suggest that what is generally seen as a resource and challenge tends to be somewhat agreed upon.
-As such, managers and supervisors can predict with some confidence which characteristics are perceived as supportive to employees’ performance.
-Somewhat surprisingly, hindrance demands are rated more variably and thus, it may be important to have conversations about job characteristics and expectations at multiple time points after hire.
-Specifically, having conversations with employees regarding their perceptions of characteristics that limit their performance is important.
+Our results suggest that what is generally seen as a resource and challenge tends to be agreed upon moreso that what is seen a hindrance.
+In fact, hindrance demands are rated more variably and thus, it may be important to have conversations about job characteristics and expectations at multiple time points after hire.
+For example, having open conversations with employees regarding their subjective perceptions of characteristics that may be unique in limiting their performance or comfort.
 Such conversations could happen during an annual performance review or more informally.
 In addition, @lepine2005meta and @podsakoff2007differential encourage organizations to incorporate strain-reducing activities like training and support to offset the negative effects of challenging job demands, which may be associated with increased performance in the short term, but strain when prolonged.
+The current results suggest that these activities and training sessions would ideally be personalized.
 
@@
 As with all individual studies, this project was limited in scope, and as such, there are a number of avenues for future study worth exploring.
-First, we captured only a small number of job characteristics given the nature of our research questions.
-Because we asked up to four questions about each characteristic, we were limited in the number of job characteristics we could reasonably include.
+First, although we aggregated to both literature-derived as well as O\*Net groupings, essentially we were dealing with single-item scales.
+Although not ideal psychometrically, this provided a strong linkage to the established O\*Net framework.
 Related to that, we intentionally worked within the O\*Net database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources/demands.
-For example, we included minimal “social” resources or interactions with one’s supervisor, which the literature would suggest are important resources.
-Future study should explore this aspect of work.
-We also used the exact definitions of resource, challenge, and hindrance.
-It is possible that respondents did not distinguish between the challenge and resource definition as cleanly as we intended and so future research should explore this question differently.
-It would also be interesting to consider outcomes associated with subjective ratings.
+Therefore, to the extent that O\*Net is not an exhaustive repository, there are existing characteristics that we did not capture.
+For example, O\*Net also includes styles and values, which we did not sample.
+Future studies may want to expand to explore these additional aspects of work.
+
+We also retained the literature-derived definitions of resources, challenges, and hindrances [@demerouti2001job].
+Given the high associations observed between ratings of resource and challenge, it is possible that respondents did not distinguish between these definitions as cleanly as we intended.
+Future investigations may wish to explore the colloquial versus academic phrasing of these questions and how that may impact observed associations between resources and challenges.
+It would also be prudent to consider work-relevant outcomes associated with similar job characteristic ratings.
+
 Lastly, there may be some practical utility to pursue training interventions aimed at *how* characteristics are appraised.
-Perhaps the clinical literature may be informative - for example, within cognitive behavioral therapeutic applications, the way in which situations are appraised can be a mechanism to help battle affective disorders such as depression.[^check] Given the current findings, where the same characteristic may be viewed similarly as both a demand and resource, it is possible that framing interventions may ameliorate negative outcomes of demands such as, for example, stress or strain.
+Perhaps the clinical literature may be informative - for example, within cognitive behavioral therapeutic applications, the way in which situations are appraised can be a mechanism to help battle affective disorders such as depression.
+Given the current findings, where the same characteristic may be viewed similarly as both a demand and resource, it is possible that framing interventions may ameliorate negative outcomes of demands such as, for example, stress or strain.
 
-## Conclusion
-
-In sum, this endeavor explored the job-demands-resources literature from a unique lens, showing that there are far more individual differences in how employees perceive demands and resources than much of our current research suggests.
-While resources and challenges are more similarly experienced, hindrance demands show a wide amount of variability.
-
+In sum, this endeavor explored the job-demands-resources literature from a unique lens from within a universally accessible framework.
+We showed that there are far more individual differences in how employees perceive demands and resources than much of our current research suggests.
+While resources and challenges idiosyncratic more similarly experienced, what is experienced as a hindrance tends to be idiosyncratic.
 ```{r}

### 2023-04-01 Submission.tex
finalized submission

--- 2023-03-28 Submission.tex
@@
 \makeatother
-\usepackage{lineno}
-
-\linenumbers
 \usepackage{csquotes}
-\ifLuaTeX
+\ifxetex
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\else
+  \usepackage[main=english]{babel}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+\fi
+\ifluatex
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={Job Demands-Resources Model Components through the Lens of O*NET Classifications},
-  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
-  pdflang={en-EN},
-  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resoures, job characteristics},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 Cognitively, the perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation {[}resulting from resources; Bakker and Demerouti (2014){]}.
-Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience despite the typical \emph{a priori} assignment of a characteristic as objectively a ``demand'' or ``resource''.
-We explore this further below.
+Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience despite the typical \emph{a priori} assignment of a characteristic as objectively a ``demand'' or ``resource.'' We explore this further below.
 
@@
 
-Although there is a tendency to attach a negative connotation to the word ``stress'', Selye (1936) defined stress as simple a response to change.
+Although there is a tendency to attach a negative connotation to the word ``stress,'' Selye (1936) defined stress as simple a response to change.
 We return to the public figure for this next section.
@@
 For example, autonomy is frequently described as a resource.
-An O*Net item is, ``How much decision making freedom, without supervision, does your job offer?''.
-This O*Net item was retained within the ``autonomy'' category.
+An O*Net item is, ``How much decision making freedom, without supervision, does your job offer?'' This O*Net item was retained within the ``autonomy'' category.
 Mean ratings of the O*Net items were then computed by element (e.g., all of the items representing autonomy) to explore whether literature-implicated resources and demands were evaluated as such.
@@
 
-The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands (both challenge and hindrance), and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using a sample of items from O*Net.
-The findings broadly revealed that there was relatively more consistency in ratings of resources and challenges characteristics, and far more variability in job characteristics rated as hindrance stressors.
+The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands (both challenge and hindrance), and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using the comprehensive taxonomy provided by O*Net.
+The findings broadly revealed that there was relatively more consistency in ratings of resource and challenge characteristics, and far more variability in job characteristics rated as hindrance stressors.
 This finding lends additional evidence to Horan et al.
@@
 
-Much of our existing research on job demands and resources has been done from the perspective that job characteristics could be classified in advance as a ``resource'' or ``demand''.
-Theoretically, however, our findings support a growing body of literature suggesting that perceptions of resources and demands, broadly, are not universal.
-There are individual differences in how employees experience the characteristics of their jobs.
+The findings presented above have implications for both theory and practice.
+First, this research is couched within the well-studied job demands-resources theory (Demerouti et al., 2001).
+We argue that while useful, additional emphasis should be placed on individual differences in perceptions of job characteristics.
+In fact, our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs (Webster et al., 2011).
+This finding aligns quite well with both the transactional theory of stress and coping, and the challenge-hindrance stressor framework, which collectively argue that employees perceive stimuli (i.e., job characteristics) uniquely (Lazarus \& Folkman, 1984), and thus, could appraise them as either a challenge or hindrance to their job performance (Cavanaugh et al., 2000).
+Further, Cavanaugh et al.
+(2000) suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes (e.g., Cavanaugh et al., 2000).
 
-These results have implications for practitioners as well, providing support for the idea that managers and supervisors can predict which characteristics are perceived as supportive to employees' performance.
-The reality that there are more individual difference in what employees perceive to be a hindrance and less in what is perceived to be a resource or challenge stressor is in some ways encouraging.
-Somewhat surprisingly, hindrances are rated more variably.
-As such, one important implication is that of frequent communication with employees regarding their perceptions of characteristics that limit their performance.
-J.
+Differences in outcomes depending on whether or not an employee perceives a job characteristic to be a challenge or hindrance has practical implications.
+Our results suggest that what is generally seen as a resource and challenge tends to be agreed upon moreso that what is seen a hindrance.
+In fact, hindrance demands are rated more variably and thus, it may be important to have conversations about job characteristics and expectations at multiple time points after hire.
+For example, having open conversations with employees regarding their subjective perceptions of characteristics that may be unique in limiting their performance or comfort.
+Such conversations could happen during an annual performance review or more informally.
+In addition, J.
 A.
@@
 (2005) and Podsakoff et al.
-(2007) encourage organizations to incorporate strain-reducing activities like training and support to offset the negative effects of challenging job demands.
+(2007) encourage organizations to incorporate strain-reducing activities like training and support to offset the negative effects of challenging job demands, which may be associated with increased performance in the short term, but strain when prolonged.
+The current results suggest that these activities and training sessions would ideally be personalized.
 
@@
 As with all individual studies, this project was limited in scope, and as such, there are a number of avenues for future study worth exploring.
-First, we captured only a small number of job characteristics given the nature of our research questions.
-Because we asked up to four questions about each characteristic, we were limited in the number of job characteristics we could reasonably include.
+First, although we aggregated to both literature-derived as well as O*Net groupings, essentially we were dealing with single-item scales.
+Although not ideal psychometrically, this provided a strong linkage to the established O*Net framework.
 Related to that, we intentionally worked within the O*Net database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources/demands.
-For example, we included minimal ``social'' resources or interactions with one's supervisor, which the literature would suggest are important resources.
-Future study should explore this aspect of work.
-We also used the exact definitions of resource, challenge, and hindrance.
-It is possible that respondents did not distinguish between the challenge and resource definition as cleanly as we intended and so future research should explore this question differently.
-It would also be interesting to consider outcomes associated with subjective ratings.
+Therefore, to the extent that O*Net is not an exhaustive repository, there are existing characteristics that we did not capture.
+For example, O*Net also includes styles and values, which we did not sample.
+Future studies may want to expand to explore these additional aspects of work.
+
+We also retained the literature-derived definitions of resources, challenges, and hindrances (Demerouti et al., 2001).
+Given the high associations observed between ratings of resource and challenge, it is possible that respondents did not distinguish between these definitions as cleanly as we intended.
+Future investigations may wish to explore the colloquial versus academic phrasing of these questions and how that may impact observed associations between resources and challenges.
+It would also be prudent to consider work-relevant outcomes associated with similar job characteristic ratings.
+
 Lastly, there may be some practical utility to pursue training interventions aimed at \emph{how} characteristics are appraised.
-Perhaps the clinical literature may be informative - for example, within cognitive behavioral therapeutic applications, the way in which situations are appraised can be a mechanism to help battle affective disorders such as depression.{[}\^{}check{]} Given the current findings, where the same characteristic may be viewed similarly as both a demand and resource, it is possible that framing interventions may ameliorate negative outcomes of demands such as, for example, stress or strain.
+Perhaps the clinical literature may be informative - for example, within cognitive behavioral therapeutic applications, the way in which situations are appraised can be a mechanism to help battle affective disorders such as depression.
+Given the current findings, where the same characteristic may be viewed similarly as both a demand and resource, it is possible that framing interventions may ameliorate negative outcomes of demands such as, for example, stress or strain.
 
-\hypertarget{conclusion}{%
-\subsection{Conclusion}\label{conclusion}}
-
-In sum, this endeavor explored the job-demands-resources literature from a unique lens, showing that there are far more individual differences in how employees perceive demands and resources than much of our current research suggests.
-While resources and challenges are more similarly experienced, hindrance demands show a wide amount of variability.
+In sum, this endeavor explored the job-demands-resources literature from a unique lens from within a universally accessible framework.
+We showed that there are far more individual differences in how employees perceive demands and resources than much of our current research suggests.
+While resources and challenges idiosyncratic more similarly experienced, what is experienced as a hindrance tends to be idiosyncratic.
 

### 2023-04-04 Submission.tex
Submitting to JOHP

@@
   pdflang={en-EN},
-  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resoures, job characteristics},
+  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resources, job characteristics},
   hidelinks,
@@
 \shorttitle{O*NET JD-R}
-\keywords{O*Net, challenge-hindrance framework, job demands-resoures, job characteristics\newline\indent Word count: X}
+\keywords{O*Net, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: X}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}

### 2023-04-15 Submission.Rmd
Submitting to JOHP
masked for JOHP

@@
 
-keywords         : "O*Net, challenge-hindrance framework, job demands-resoures, job characteristics"
+keywords         : "O*Net, challenge-hindrance framework, job demands-resources, job characteristics"
 wordcount        : "X"
@@
 linenumbers       : no
-mask              : no
+mask              : yes
 draft             : no

### 2023-04-15 Submission.tex
masked for JOHP

@@
 \documentclass[
-  english,
-  man]{apa6}
+  man,mask]{apa6}
 \usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
   pdftitle={Job Demands-Resources Model Components through the Lens of O*NET Classifications},
-  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
   pdflang={en-EN},
@@
 \makeatother
-\shorttitle{O*NET JD-R}
+
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
 \keywords{O*Net, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: X}
@@
 Cognitively, the perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation {[}resulting from resources; Bakker and Demerouti (2014){]}.
-Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience despite the typical \emph{a priori} assignment of a characteristic as objectively a ``demand'' or ``resource.'' We explore this further below.
+Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience despite the typical \emph{a priori} assignment of a characteristic as objectively a ``demand'' or ``resource''.
+We explore this further below.
 
@@
 
-Although there is a tendency to attach a negative connotation to the word ``stress,'' Selye (1936) defined stress as simple a response to change.
+Although there is a tendency to attach a negative connotation to the word ``stress'', Selye (1936) defined stress as simple a response to change.
 We return to the public figure for this next section.
@@
 For example, autonomy is frequently described as a resource.
-An O*Net item is, ``How much decision making freedom, without supervision, does your job offer?'' This O*Net item was retained within the ``autonomy'' category.
+An O*Net item is, ``How much decision making freedom, without supervision, does your job offer?''.
+This O*Net item was retained within the ``autonomy'' category.
 Mean ratings of the O*Net items were then computed by element (e.g., all of the items representing autonomy) to explore whether literature-implicated resources and demands were evaluated as such.

### 2023-05-23 SIOP2024/SIOP2024convergence.Rmd
Reviewing convergence SIOP project to resubmit this fall. Need to look at moderator section note and add practical implications yet.

--- 2022-11-11 copy of SIOP2023convergence.Rmd
@@
 
-Although the word “stress” often carries a negative connotation, the "father" of the current concept, @selye1936syndrome, conceptualized stress much less perjoratively - rather thinking of it as a *response to change*.
+Although the word “stress” often carries a negative connotation, the "father" of the current concept, @selye1936syndrome, conceptualized stress much less pejoratively - rather thinking of it as a *response to change*.
 For instance, consider the different reactions two different employees may have to being nominated to give a speech at an upcoming company event.
@@
 However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
-Selye the physician would likely have labeled the two responses as subjective manifestations of "Distress", and "Eustress" [@selye1974stress].
+Selye the physician would likely have labeled the two responses as subjective manifestations of "distress", and "eustress" [@selye1974stress].
 In modern I-O Psychology parlance (and more consistent with the JD-R framework), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a *challenge* while the other would appraise the demand as a *hindrance* [@cavanaugh2000empirical].
@@
 @webster2011extending also considered three common work characteristics including workload, role ambiguity, and role conflict.
-Interestingly, they found that while each could be identified *primarily* as a challenge or hindrance, employees could also appraise that a characteristic is simulataneously both a challenge and hindrance.
+Interestingly, they found that while each could be identified *primarily* as a challenge or hindrance, employees could also appraise that a characteristic is simultaneously both a challenge and hindrance.
 
@@
 
-We asked our respondents to select job characteristics that were relevent to them from the broader comprehensive O\*Net list.
+We asked our respondents to select job characteristics that were relevant to them from the broader comprehensive O\*Net list.
 We then asked these individuals to also rate those (relevant) characteristics in terms of their status as hindrances, challenges, and resources.
@@
 
-Although the same job characteristic may be percieved as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others.
+Although the same job characteristic may be perceived as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others.
 For example, a physically strenuous job requirement such as "carrying heavy objects" would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as "negotiating work schedules" may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge.
-O\*Net has different levels of abstraction with regard to the nature of job characteristic.
-We will be exploring a mid-level abstraction with seven different characteristic "scales".
+O\*Net has different levels of abstraction with regard to the nature of job characteristics.
+We will be exploring a mid-level abstraction with seven different characteristic scales.
 
-*Hypothesis 2*: The association between challenging and resourceful characteristics is moderated by type of characteristic.
+*Research Question 1*: The association between challenging and resourceful characteristics is moderated by type of characteristic.
 
@@
 
-Subsequent to providing ratings of whether or not each of the 98 O\*Net characteristics were relevant for the respondent’s work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) .
+Subsequent to providing ratings of whether or not each of the 98 O\*Net characteristics were relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) .
 .
@@
 this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
-The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
+The total number of items on the survey was less than 392 (98 characteristics x 4 administrations - the first for relevance and the remaining 3 for resources, challenges, and hindrances) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
 
@@
 (*M* = `r round(mean(ch$mean, na.rm=TRUE),2)`).
-However, when a characteristic was viewed a resource, it was more likely to also be percieved as a challenge (although the correspondence also exhibited quite a bit of variability; *M* = `r round(mean(rc$mean, na.rm=TRUE),2)`, *sd* = `r round(sd(rc$mean, na.rm=TRUE),2)`).
+However, when a characteristic was viewed a resource, it was more likely to also be perceived as a challenge (although the correspondence also exhibited quite a bit of variability; *M* = `r round(mean(rc$mean, na.rm=TRUE),2)`, *sd* = `r round(sd(rc$mean, na.rm=TRUE),2)`).
 
@@
 The major goal of this paper was to further explore the relationships among perceptions of job characteristics as challenge demands, hindrance demands, and resources.
-Our findings perhaps most noteably highlight the importance of dissociating the *nature* of job demands.
+Our findings perhaps most notably highlight the importance of dissociating the *nature* of job demands.
 Similar to the eustress/distress distinction [e.g., @selye1974stress], it would seem as though demands should perhaps be thought of in a valenced manner (e.g., is it a "good" demand or a "bad" demand).

### 2023-05-31 SIOP2024/SIOP2024convergence.tex
.bib and .csl transfers to new root folder

--- 2022-11-11 copy-of-SIOP2023convergence.tex
@@
 \centering
-\includegraphics{copy-of-SIOP2023convergence_files/figure-latex/uhoh-1.pdf}
+\includegraphics{SIOP2024convergence_files/figure-latex/uhoh-1.pdf}
 \caption{\label{fig:uhoh}Maybe put a hold on this paper as wording of resource and challenge seems very similar}
@@
 
-Although the word ``stress'' often carries a negative connotation, the ``father'' of the current concept, Selye (1936), conceptualized stress much less perjoratively - rather thinking of it as a \emph{response to change}.
+Although the word ``stress'' often carries a negative connotation, the ``father'' of the current concept, Selye (1936), conceptualized stress much less pejoratively - rather thinking of it as a \emph{response to change}.
 For instance, consider the different reactions two different employees may have to being nominated to give a speech at an upcoming company event.
@@
 However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
-Selye the physician would likely have labeled the two responses as subjective manifestations of ``Distress'', and ``Eustress'' (Selye, 1974).
+Selye the physician would likely have labeled the two responses as subjective manifestations of ``distress'', and ``eustress'' (Selye, 1974).
 In modern I-O Psychology parlance (and more consistent with the JD-R framework), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a \emph{challenge} while the other would appraise the demand as a \emph{hindrance} (Cavanaugh et al., 2000).
@@
 (2011) also considered three common work characteristics including workload, role ambiguity, and role conflict.
-Interestingly, they found that while each could be identified \emph{primarily} as a challenge or hindrance, employees could also appraise that a characteristic is simulataneously both a challenge and hindrance.
+Interestingly, they found that while each could be identified \emph{primarily} as a challenge or hindrance, employees could also appraise that a characteristic is simultaneously both a challenge and hindrance.
 
@@
 
-We asked our respondents to select job characteristics that were relevent to them from the broader comprehensive O*Net list.
+We asked our respondents to select job characteristics that were relevant to them from the broader comprehensive O*Net list.
 We then asked these individuals to also rate those (relevant) characteristics in terms of their status as hindrances, challenges, and resources.
@@
 
-Although the same job characteristic may be percieved as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others.
+Although the same job characteristic may be perceived as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others.
 For example, a physically strenuous job requirement such as ``carrying heavy objects'' would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as ``negotiating work schedules'' may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge.
-O*Net has different levels of abstraction with regard to the nature of job characteristic.
-We will be exploring a mid-level abstraction with seven different characteristic ``scales''.
+O*Net has different levels of abstraction with regard to the nature of job characteristics.
+We will be exploring a mid-level abstraction with seven different characteristic scales.
 
-\emph{Hypothesis 2}: The association between challenging and resourceful characteristics is moderated by type of characteristic.
+\emph{Research Question 1}: The association between challenging and resourceful characteristics is moderated by type of characteristic.
 
@@
 this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
-The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
+The total number of items on the survey was less than 392 (98 characteristics x 4 administrations - the first for relevance and the remaining 3 for resources, challenges, and hindrances) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
 
@@
 \centering
-\includegraphics{copy-of-SIOP2023convergence_files/figure-latex/percagree-1.pdf}
+\includegraphics{SIOP2024convergence_files/figure-latex/percagree-1.pdf}
 \caption{\label{fig:percagree}Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance).}
@@
 (\emph{M} = 0.14).
-However, when a characteristic was viewed a resource, it was more likely to also be percieved as a challenge (although the correspondence also exhibited quite a bit of variability; \emph{M} = 0.51, \emph{sd} = 0.21).
+However, when a characteristic was viewed a resource, it was more likely to also be perceived as a challenge (although the correspondence also exhibited quite a bit of variability; \emph{M} = 0.51, \emph{sd} = 0.21).
 
@@
 \centering
-\includegraphics{copy-of-SIOP2023convergence_files/figure-latex/recchall-1.pdf}
+\includegraphics{SIOP2024convergence_files/figure-latex/recchall-1.pdf}
 \caption{\label{fig:recchall}Resource and challenge agreement across ONet characteristic groupings (e.g., scales).}
@@
 \centering
-\includegraphics{copy-of-SIOP2023convergence_files/figure-latex/workcat-1.pdf}
+\includegraphics{SIOP2024convergence_files/figure-latex/workcat-1.pdf}
 \caption{\label{fig:workcat}Percent agreement (resource and challenge) across O\emph{Net occupational categories (previous was across 84 O/}Net items - this is across 568 individual workers).}
@@
 The major goal of this paper was to further explore the relationships among perceptions of job characteristics as challenge demands, hindrance demands, and resources.
-Our findings perhaps most noteably highlight the importance of dissociating the \emph{nature} of job demands.
+Our findings perhaps most notably highlight the importance of dissociating the \emph{nature} of job demands.
 Similar to the eustress/distress distinction (e.g., Selye, 1974), it would seem as though demands should perhaps be thought of in a valenced manner (e.g., is it a ``good'' demand or a ``bad'' demand).

### 2023-06-01 SIOP2024/SIOP2024convergence.Rmd
Revising "story" for convergence project for SIOP. Unsure if we need the 3rd moderator idea in here, or if it's sufficient as is.

@@
 
-An abundance of research applying the job demands-resources model [@demerouti2001job] and job demands-resources theory [@bakker2017job] underscores the importance of job characteristics on the experience of work.
-Resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
-Demands, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain [e.g., high work pressure, @demerouti2001job].
-These two categories of outcomes (e.g., "good" and "bad") are thought to occur via one of two different mechanisms: motivational (resulting from resources) or health impairment [resulting from demands, @bakker2014job].
-Much of our existing research on the JD-R assumes that certain characteristics (for example, autonomy) are resources and others (for example, time constraints) are generally considered demands.
-This study searches instead for circumstances that provide exception to this mutually exclusive dichotomy of job characteristics.
-
-```{r uhoh, fig.cap="Maybe put a hold on this paper as wording of resource and challenge seems very similar"}
+```{r uhoh, fig.cap="Maybe put a hold on this paper as wording of resource and challenge seems very similar", fig.show='hide'}
 
@@
 ```
+The Occupational Information Network (O\*NET; onetonline.org) contains a reasonably comprehensive description of occupations [@peterson2001understanding] which subject matter experts inform via surveys.
+We utilize a set of O\*Net job context and activity statements contained in these surveys to explore a series of research questions about how people perceive resources, challenges, and hindrances within their jobs.
+There are a number of advantage to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.
 
-see Figure \ref{fig:uhoh}
-
-## Could a Work Demand be Appraised "Positively"?: The Challenge-Hindrance Framework
+## Not all Stressors are Equal: The Challenge-hindrance Framework
 
@@
 Selye the physician would likely have labeled the two responses as subjective manifestations of "distress", and "eustress" [@selye1974stress].
-In modern I-O Psychology parlance (and more consistent with the JD-R framework), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a *challenge* while the other would appraise the demand as a *hindrance* [@cavanaugh2000empirical].
+In modern I-O Psychology parlance (and more consistent with the job demands-resources model [@demerouti2001job] and job demands-resources theory [@bakker2017job]), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a *challenge* while the other would appraise the demand as a *hindrance* [@cavanaugh2000empirical].
 According to @cavanaugh2000empirical, challenge demands promote mastery, personal growth, and future gains.
@@
 
-Prior to proposing specific predictions regarding the current SIOP presentation, the empirical evidence on challenge and hindrance demands is very briefly shared below.
-To begin, the first logical question is whether employees actually distinguish between challenges and hindrances, and research suggests that they can and do.
+At the most broad level, we can question whether employees actually distinguish between challenges and hindrances as the theory describes.
+Research suggests that people can and do perceive them differently.
 For example, @bakker2013weekly found that perceived work pressure can be classified as a hindrance demand, while the requirement to express emotions is a challenge demand.
@@
 Interestingly, they found that while each could be identified *primarily* as a challenge or hindrance, employees could also appraise that a characteristic is simultaneously both a challenge and hindrance.
+However, this list of demands (workload, role ambiguity, and role conflict) is somewhat narrow.
+Using a very wide range of O\*Net job characteristics regarding job context and activities, we explore this question:
 
-Although it is cleaner to be able to categorize job characteristics as *either* a demand or a resource, the above research suggests that an individual's (perhaps unique) appraisal is at least occasionally an important consideration.
-It is quite possible that one person experiences high work pressure (commonly cited as a demand in the literature) as a hindrance stressor and thus experiences strain, and another thrives in a fast-paced pressured role and would thus find the environment motivating.
+*RQ1*: Do people distinguish between challenge and hindrance stressors?
 
-## Current Study and Hypotheses
+*Paired samples t-tests for challenge/hindrance by item?* - I like this first idea. could present it by the 7 different categories.
+*Could look*
+*Or percent agreement?* 
+*Maybe do item-level correlations between challenge/hindrance rating and present percent positively related, and negatively related (negative would be supportive, I think)*
 
-We explored the extent to which perceptions of job characteristics converge upon being uniquely or concurrently experienced as resources and demands (in the form of challenges and hindrances).
-Our supposition is that respondents may consider the same objective job characteristic to be both challenging and resourceful - if not at the same moment, at least at different points in time or under differing circumstances.
+The next question focuses on whether challenges (positive stressors per the definition above) might actually be positively related to resources.
+Per the job demands-resources theory [@bakker2017job] resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
+It stands to reason that a challenging demand may be considered a resource.
 
-### Value of consulting O\*Net.
+*RQ2*: Characteristics perceived as challenges are also commonly viewed as resources.
 
-The Occupational Information Network (O\*NET; onetonline.org) contains a fairly comprehensive description of occupations [@peterson2001understanding].
-This widely accessed database houses hundreds of standardized and occupation-specific descriptors for the majority of occupations within the United States, and these descriptions are frequently updated.
-These data, and the tools provided for public consumption on the website (e.g., Career Exploration Tools, “My Next Move”, Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist interested or curious job-seekers discover the nature of work as well as skills and training typically required for different occupations.
-It is also often useful to employers by providing them with information that may be helpful in a job analysis context.
-
-We asked our respondents to select job characteristics that were relevant to them from the broader comprehensive O\*Net list.
-We then asked these individuals to also rate those (relevant) characteristics in terms of their status as hindrances, challenges, and resources.
-Utilizing the job demands-resources theory and the challenge-hindrance framework, we propose that job characteristics appraised as “challenge demands” (i.e., promote mastery, personal growth, and future gains) may also be viewed as job resources.
-
-*Hypothesis 1*: Characteristics perceived as challenges are also commonly viewed as resources.
-
-Although the same job characteristic may be perceived as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others.
+Although we argue that the same job characteristic may be perceived as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others.
 For example, a physically strenuous job requirement such as "carrying heavy objects" would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as "negotiating work schedules" may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge.
@@
 
-*Research Question 1*: The association between challenging and resourceful characteristics is moderated by type of characteristic.
+*RQ3*: The association between challenging and resourceful characteristics is moderated by type of characteristic.
+
+#### Maybe do third moderator
+
+We also have ratings of "...the extent to which this characteristic is present in your job".
+Currently we're just taking a binary yes/no approach, but it does make sense to look for moderation based on *the degree to which the characteristic is present*.
+This is probably a better/more appropriate moderator than either of the above two...
 
@@
 To capture an effectively exhaustive list of characteristics that apply to, theoretically, *every* possible job, we consult the  unifying framework of O\*Net.
-
-## Materials
-
-Our survey was informed by 98 statements taken from job characteristic descriptors located within O\*Net’s classification of “work activities”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context” groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
-
-The O\*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to "responsibility" than task.
-For example, the descriptor for "level of competition", which is an element of the "structural job characteristics" grouping, is *...to what extent does this job require the worker to compete or to be aware of competitive pressures?* Other than minor grammatical editing (for example, changing “the worker” to “you”), we retained the O\*Net wording for our item stems.
-We also retained O\*Net’s response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
-It would likely NOT be considered controversial to referred to these as "effectively" Likert-type response scales.
-
-Subsequent to providing ratings of whether or not each of the 98 O\*Net characteristics were relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) .
-.
-.
-this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) .
-.
-.
-this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) .
-.
-.
-this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
-The total number of items on the survey was less than 392 (98 characteristics x 4 administrations - the first for relevance and the remaining 3 for resources, challenges, and hindrances) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
 
@@
 Gender was captured via a free-field gender identity category, although the sample predominantly self-identified as female (52.6%) or male (46.8%).
+
+## Materials
+
+Our survey was informed by 98 statements taken from job characteristic descriptors located within O\*Net’s classification of “work activities”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context” groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
+
+The O\*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to "responsibility" than task.
+For example, the descriptor for "level of competition", which is an element of the "structural job characteristics" grouping, is *...to what extent does this job require the worker to compete or to be aware of competitive pressures?* Other than minor grammatical editing (for example, changing “the worker” to “you”), we retained the O\*Net wording for our item stems.
+We also retained O\*Net’s response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
+It would likely NOT be considered controversial to referred to these as "effectively" Likert-type response scales.
+
+## Procedure
+
+Following IRB approval, respondents were recruited through Prolific.
+After providing consent, respondents provided ratings of whether or not each of the 98 O\*Net characteristics were relevant for the respondent's work.
+Subsequently, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of perception of resource, challenge, or hindrance.
+The total number of items on the survey was less than 392 (98 characteristics x 4 administrations - the first for relevance and the remaining 3 for resources, challenges, and hindrances) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
+Furthermore, not every respondent indicated that the same characteristics were relevant to them, therefore each respondent had a unique set of responses.
 Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
@@
 ```
-
 ## Convergence (same characteristic).
@@
 
-#### Maybe do third moderator
-
-We also have ratings of "...the extent to which this characteristic is present in your job".
-Currently we're just taking a binary yes/no approach, but it does make sense to look for moderation based on *the degree to which the characteristic is present*.
-This is probably a better/more appropriate moderator than either of the above two...
-
 # Discussion
@@
 Our findings perhaps most notably highlight the importance of dissociating the *nature* of job demands.
+
+IMPLICATION: Distinguishing between different kinds of work demands has implications for not only the employees themselves, but also teams they may be a part of, managers and the like.
+This is because demands appraised as a challenge promote mastery, personal growth, and future gains.
+Those appraised as a hindrance, in contrast, inhibit growth, learning and goal achievement.
+Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes [e.g., @cavanaugh2000empirical].
+
 Similar to the eustress/distress distinction [e.g., @selye1974stress], it would seem as though demands should perhaps be thought of in a valenced manner (e.g., is it a "good" demand or a "bad" demand).

### 2023-06-01 SIOP2024/SIOP2024convergence.tex
Revising "story" for convergence project for SIOP. Unsure if we need the 3rd moderator idea in here, or if it's sufficient as is.

@@
 
-\begin{verbatim}
-## Warning: package 'tinylabels' was built under R version 4.1.3
-\end{verbatim}
+The Occupational Information Network (O*NET; onetonline.org) contains a reasonably comprehensive description of occupations (Peterson et al., 2001) which subject matter experts inform via surveys.
+We utilize a set of O*Net job context and activity statements contained in these surveys to explore a series of research questions about how people perceive resources, challenges, and hindrances within their jobs.
+There are a number of advantage to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.
 
-An abundance of research applying the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker \& Demerouti, 2017) underscores the importance of job characteristics on the experience of work.
-Resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
-Demands, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure, Demerouti et al., 2001).
-These two categories of outcomes (e.g., ``good'' and ``bad'') are thought to occur via one of two different mechanisms: motivational (resulting from resources) or health impairment (resulting from demands, Bakker \& Demerouti, 2014).
-Much of our existing research on the JD-R assumes that certain characteristics (for example, autonomy) are resources and others (for example, time constraints) are generally considered demands.
-This study searches instead for circumstances that provide exception to this mutually exclusive dichotomy of job characteristics.
-
-\begin{figure}
-\centering
-\includegraphics{SIOP2024convergence_files/figure-latex/uhoh-1.pdf}
-\caption{\label{fig:uhoh}Maybe put a hold on this paper as wording of resource and challenge seems very similar}
-\end{figure}
-
-see Figure \ref{fig:uhoh}
-
-\hypertarget{could-a-work-demand-be-appraised-positively-the-challenge-hindrance-framework}{%
-\subsection{Could a Work Demand be Appraised ``Positively''?: The Challenge-Hindrance Framework}\label{could-a-work-demand-be-appraised-positively-the-challenge-hindrance-framework}}
+\hypertarget{not-all-stressors-are-equal-the-challenge-hindrance-framework}{%
+\subsection{Not all Stressors are Equal: The Challenge-hindrance Framework}\label{not-all-stressors-are-equal-the-challenge-hindrance-framework}}
 
@@
 However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
-Selye the physician would likely have labeled the two responses as subjective manifestations of ``distress'', and ``eustress'' (Selye, 1974).
-In modern I-O Psychology parlance (and more consistent with the JD-R framework), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a \emph{challenge} while the other would appraise the demand as a \emph{hindrance} (Cavanaugh et al., 2000).
+Selye the physician would likely have labeled the two responses as subjective manifestations of ``distress,'' and ``eustress'' (Selye, 1974).
+In modern I-O Psychology parlance (and more consistent with the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker \& Demerouti, 2017)), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a \emph{challenge} while the other would appraise the demand as a \emph{hindrance} (Cavanaugh et al., 2000).
 According to Cavanaugh et al.
@@
 
-Prior to proposing specific predictions regarding the current SIOP presentation, the empirical evidence on challenge and hindrance demands is very briefly shared below.
-To begin, the first logical question is whether employees actually distinguish between challenges and hindrances, and research suggests that they can and do.
+At the most broad level, we can question whether employees actually distinguish between challenges and hindrances as the theory describes.
+Research suggests that people can and do perceive them differently.
 For example, Bakker and Sanz-Vergel (2013) found that perceived work pressure can be classified as a hindrance demand, while the requirement to express emotions is a challenge demand.
@@
 Interestingly, they found that while each could be identified \emph{primarily} as a challenge or hindrance, employees could also appraise that a characteristic is simultaneously both a challenge and hindrance.
+However, this list of demands (workload, role ambiguity, and role conflict) is somewhat narrow.
+Using a very wide range of O*Net job characteristics regarding job context and activities, we explore this question:
 
-Although it is cleaner to be able to categorize job characteristics as \emph{either} a demand or a resource, the above research suggests that an individual's (perhaps unique) appraisal is at least occasionally an important consideration.
-It is quite possible that one person experiences high work pressure (commonly cited as a demand in the literature) as a hindrance stressor and thus experiences strain, and another thrives in a fast-paced pressured role and would thus find the environment motivating.
+\emph{RQ1}: Do people distinguish between challenge and hindrance stressors?
 
-\hypertarget{current-study-and-hypotheses}{%
-\subsection{Current Study and Hypotheses}\label{current-study-and-hypotheses}}
+\emph{Paired samples t-tests for challenge/hindrance by item?} - I like this first idea. could present it by the 7 different categories.
+\emph{Could look}
+\emph{Or percent agreement?}
+\emph{Maybe do item-level correlations between challenge/hindrance rating and present percent positively related, and negatively related (negative would be supportive, I think)}
 
-We explored the extent to which perceptions of job characteristics converge upon being uniquely or concurrently experienced as resources and demands (in the form of challenges and hindrances).
-Our supposition is that respondents may consider the same objective job characteristic to be both challenging and resourceful - if not at the same moment, at least at different points in time or under differing circumstances.
+The next question focuses on whether challenges (positive stressors per the definition above) might actually be positively related to resources.
+Per the job demands-resources theory (Bakker \& Demerouti, 2017) resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
+It stands to reason that a challenging demand may be considered a resource.
 
-\hypertarget{value-of-consulting-onet.}{%
-\subsubsection{Value of consulting O*Net.}\label{value-of-consulting-onet.}}
+\emph{RQ2}: Characteristics perceived as challenges are also commonly viewed as resources.
 
-The Occupational Information Network (O*NET; onetonline.org) contains a fairly comprehensive description of occupations (Peterson et al., 2001).
-This widely accessed database houses hundreds of standardized and occupation-specific descriptors for the majority of occupations within the United States, and these descriptions are frequently updated.
-These data, and the tools provided for public consumption on the website (e.g., Career Exploration Tools, ``My Next Move'', Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist interested or curious job-seekers discover the nature of work as well as skills and training typically required for different occupations.
-It is also often useful to employers by providing them with information that may be helpful in a job analysis context.
-
-We asked our respondents to select job characteristics that were relevant to them from the broader comprehensive O*Net list.
-We then asked these individuals to also rate those (relevant) characteristics in terms of their status as hindrances, challenges, and resources.
-Utilizing the job demands-resources theory and the challenge-hindrance framework, we propose that job characteristics appraised as ``challenge demands'' (i.e., promote mastery, personal growth, and future gains) may also be viewed as job resources.
-
-\emph{Hypothesis 1}: Characteristics perceived as challenges are also commonly viewed as resources.
-
-Although the same job characteristic may be perceived as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others.
+Although we argue that the same job characteristic may be perceived as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others.
 For example, a physically strenuous job requirement such as ``carrying heavy objects'' would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as ``negotiating work schedules'' may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge.
@@
 
-\emph{Research Question 1}: The association between challenging and resourceful characteristics is moderated by type of characteristic.
+\emph{RQ3}: The association between challenging and resourceful characteristics is moderated by type of characteristic.
+
+\hypertarget{maybe-do-third-moderator}{%
+\paragraph{Maybe do third moderator}\label{maybe-do-third-moderator}}
+
+We also have ratings of ``\ldots the extent to which this characteristic is present in your job.'' Currently we're just taking a binary yes/no approach, but it does make sense to look for moderation based on \emph{the degree to which the characteristic is present}.
+This is probably a better/more appropriate moderator than either of the above two\ldots{}
 
@@
 To capture an effectively exhaustive list of characteristics that apply to, theoretically, \emph{every} possible job, we consult the unifying framework of O*Net.
-
-\hypertarget{materials}{%
-\subsection{Materials}\label{materials}}
-
-Our survey was informed by 98 statements taken from job characteristic descriptors located within O*Net's classification of ``work activities'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'' groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
-
-The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task.
-For example, the descriptor for ``level of competition'', which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems.
-We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
-It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.
-
-Subsequent to providing ratings of whether or not each of the 98 O*Net characteristics were relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) .
-.
-.
-this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) .
-.
-.
-this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) .
-.
-.
-this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
-The total number of items on the survey was less than 392 (98 characteristics x 4 administrations - the first for relevance and the remaining 3 for resources, challenges, and hindrances) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
 
@@
 Gender was captured via a free-field gender identity category, although the sample predominantly self-identified as female (52.6\%) or male (46.8\%).
+
+\hypertarget{materials}{%
+\subsection{Materials}\label{materials}}
+
+Our survey was informed by 98 statements taken from job characteristic descriptors located within O*Net's classification of ``work activities'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'' groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
+
+The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task.
+For example, the descriptor for ``level of competition,'' which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems.
+We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
+It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.
+
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
+
+Following IRB approval, respondents were recruited through Prolific.
+After providing consent, respondents provided ratings of whether or not each of the 98 O*Net characteristics were relevant for the respondent's work.
+Subsequently, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of perception of resource, challenge, or hindrance.
+The total number of items on the survey was less than 392 (98 characteristics x 4 administrations - the first for relevance and the remaining 3 for resources, challenges, and hindrances) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
+Furthermore, not every respondent indicated that the same characteristics were relevant to them, therefore each respondent had a unique set of responses.
 Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
@@
 
-\hypertarget{maybe-do-third-moderator}{%
-\paragraph{Maybe do third moderator}\label{maybe-do-third-moderator}}
-
-We also have ratings of ``\ldots the extent to which this characteristic is present in your job''.
-Currently we're just taking a binary yes/no approach, but it does make sense to look for moderation based on \emph{the degree to which the characteristic is present}.
-This is probably a better/more appropriate moderator than either of the above two\ldots{}
-
 \hypertarget{discussion}{%
@@
 Our findings perhaps most notably highlight the importance of dissociating the \emph{nature} of job demands.
+
+IMPLICATION: Distinguishing between different kinds of work demands has implications for not only the employees themselves, but also teams they may be a part of, managers and the like.
+This is because demands appraised as a challenge promote mastery, personal growth, and future gains.
+Those appraised as a hindrance, in contrast, inhibit growth, learning and goal achievement.
+Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes (e.g., Cavanaugh et al., 2000).
+
 Similar to the eustress/distress distinction (e.g., Selye, 1974), it would seem as though demands should perhaps be thought of in a valenced manner (e.g., is it a ``good'' demand or a ``bad'' demand).
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
-Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
+\leavevmode\hypertarget{ref-bakker2017job}{}%
 Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
+\leavevmode\hypertarget{ref-bakker2013weekly}{}%
 Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
 
-\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
+\leavevmode\hypertarget{ref-cavanaugh2000empirical}{}%
 Cavanaugh, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
+\leavevmode\hypertarget{ref-demerouti2001job}{}%
 Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
 
-\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
+\leavevmode\hypertarget{ref-peterson2001understanding}{}%
 Peterson, N.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-selye1936syndrome}{}}%
+\leavevmode\hypertarget{ref-selye1936syndrome}{}%
 Selye, H. (1936). A syndrome produced by diverse nocuous agents. \emph{Nature}, \emph{138}(3479), 32--32.
 
-\leavevmode\vadjust pre{\hypertarget{ref-selye1974stress}{}}%
+\leavevmode\hypertarget{ref-selye1974stress}{}%
 Selye, H. (1974). \emph{Stress without distress}. Lippincott Williams \& Wilkins.
 
-\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
+\leavevmode\hypertarget{ref-webster2011extending}{}%
 Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.

### 2023-06-06 Submission.Rmd
Reviewing convergence SIOP project to resubmit this fall. Need to look at moderator section note and add practical implications yet.
doesn't knit with interact class - waiting on journal help

--- 2023-04-01 Submission.Rmd
@@
 
-keywords         : "O*Net, challenge-hindrance framework, job demands-resoures, job characteristics"
-wordcount        : "X"
+keywords         : "O*Net, challenge-hindrance framework, job demands-resources, job characteristics"
+wordcount        : "4,942"
 
@@
 csl               : apa7.csl
-documentclass     : "apa6"
-classoption       : "man"
+documentclass     : "interact"
+#classoption       : "man"
 output            : papaja::apa6_pdf
@@
 Eligibility requirements included being 18 or older and holding either a full-time or part-time job.
-Participants then voluntarily chose to respond to the online survey.
+Participants then voluntarily chose to respond to the online survey after reading an informed consent.
 Participants were asked to think about their primary job, and the items they were presented with depended on the specific job characteristics they initially specified.

### 2023-06-06 Submission.tex
Reviewing convergence SIOP project to resubmit this fall. Need to look at moderator section note and add practical implications yet.
updating for new journal submission

@@
 \documentclass[
-  man,mask]{apa6}
+  man]{interact}
 \usepackage{amsmath,amssymb}
@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Job Demands-Resources Model Components through the Lens of O*NET Classifications},
-  pdflang={en-EN},
-  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resources, job characteristics},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 {}{\PatchFailed}
-\keywords{O*Net, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: X}
+\keywords{O*Net, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: 4,942}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Job Demands-Resources Model Components through the Lens of O*NET Classifications},
+  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
+  pdflang={en-EN},
+  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resources, job characteristics},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 

### 2023-06-08 Submission.Rmd
anxiety LaTeX requirements (excluded correlation table)

@@
 author: 
-  - name          : "Alicia Stachowski"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "470M Harvey Hall, 721 3rd Street E, Menomenie, WI, 54751, USA"
-    email         : "stachowskia@uwstout.edu"
-  - name          : "John Kulas"
-    address       : "Minneapolis, MN"
-    affiliation   : "2"
-  - name          : "Renata Garcia Prieto Palacios Roji"
-    address       : "Dallas, TX"
-    affiliation   : "3"
-
-affiliation:
-  - id            : "1"
-    institution   : "University of Wisconsin-Stout"
-  - id            : "2"
-    institution   : "eRg"
-  - id            : "3"
-    institution   : "PepsiCo"
+  - Alicia Stachowski, University of Wisconsin, Stout
+  - John Kulas, eRg
+  - Renata Garcia Prieto Palacios Roji, PepsiCo
 
@@
 csl               : apa7.csl
-documentclass     : "interact"
+documentclass     : interact
 #classoption       : "man"
-output            : papaja::apa6_pdf
+output            : pdf_document
 ---
@@
 
-```{r analysis-preferences}
+```{r analysis-preferences, echo=FALSE, warning=FALSE, message=FALSE}
 
@@
 
-```{r cortab, results="asis"}
+```{r cortab, results="asis", eval=FALSE}
 

### 2023-06-12 Submission.tex
Changes for Anxiety, Stress, and Coping Journal submission

--- 2023-04-04 Submission.tex
@@
   english,
-  man]{apa6}
+  man]{interact}
 \usepackage{amsmath,amssymb}
@@
 \shorttitle{O*NET JD-R}
-\keywords{O*Net, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: X}
+\keywords{O*Net, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: 4,942}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}

### 2023-06-13 SIOP2024/SIOP2024convergence.Rmd
siop revisions working

@@
 
+*RQ1 is a good idea for A DIFFERENT PAPER. Do ICC(1,1)*
 *RQ1*: Do people distinguish between challenge and hindrance stressors?
@@
 
-*RQ2*: Characteristics perceived as challenges are also commonly viewed as resources.
-
+*RQ1*: Are job characteristics perceived as challenges are also commonly viewed as resources?  
 Although we argue that the same job characteristic may be perceived as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others.
@@
 
-*RQ3*: The association between challenging and resourceful characteristics is moderated by type of characteristic.
+*RQ2*: Is the association between challenge and resource characteristics moderated by type of characteristic?
 

### 2023-06-27 SIOP2024/SIOP2024_agreement.Rmd
updating siop submission

--- 2023-06-13 SIOP2024/SIOP2024convergence.Rmd
@@
 *RQ1*: Do people distinguish between challenge and hindrance stressors?
-
-*Paired samples t-tests for challenge/hindrance by item?* - I like this first idea. could present it by the 7 different categories.
-*Could look*
-*Or percent agreement?* 
-*Maybe do item-level correlations between challenge/hindrance rating and present percent positively related, and negatively related (negative would be supportive, I think)*
-
-The next question focuses on whether challenges (positive stressors per the definition above) might actually be positively related to resources.
-Per the job demands-resources theory [@bakker2017job] resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
-It stands to reason that a challenging demand may be considered a resource.
-
-*RQ1*: Are job characteristics perceived as challenges are also commonly viewed as resources?  
-Although we argue that the same job characteristic may be perceived as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others.
-For example, a physically strenuous job requirement such as "carrying heavy objects" would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as "negotiating work schedules" may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge.
-O\*Net has different levels of abstraction with regard to the nature of job characteristics.
-We will be exploring a mid-level abstraction with seven different characteristic scales.
-
-*RQ2*: Is the association between challenge and resource characteristics moderated by type of characteristic?
-
-#### Maybe do third moderator
-
-We also have ratings of "...the extent to which this characteristic is present in your job".
-Currently we're just taking a binary yes/no approach, but it does make sense to look for moderation based on *the degree to which the characteristic is present*.
-This is probably a better/more appropriate moderator than either of the above two...
 

### 2023-07-10 SIOP2024/SIOP2024convergence.tex
updating convergence paper
updating SIOP convergence project

@@
 \documentclass[
-  english,
   man]{apa6}
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Demanding resources: Converging perceptions of challenge and resource characteristics},
-  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata García Prieto Palacios Roji3},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx}
@@
 \makeatother
-\shorttitle{Demanding Resources}
+
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
 \keywords{keywords\newline\indent Word count: X}
@@
 \usepackage{csquotes}
-\ifxetex
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same}
+\hypersetup{
+  pdftitle={Demanding resources: Converging perceptions of challenge and resource characteristics},
+  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata García Prieto Palacios Roji3},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 \date{}
+
+\shorttitle{Demanding Resources}
 
@@
 
-\abstract{
+\abstract{%
 568 workers rated job characteristics in terms of relevance as well as perceptions as challenges, hindrances and resources.
-We find strong associations between characteristics such that what is viewed as a ``resource'' is also very often considered a ``challenge.'' This agreement was moderated by the nature of the job characteristic.
+We find strong associations between characteristics such that what is viewed as a ``resource'' is also very often considered a ``challenge''.
+This agreement was moderated by the nature of the job characteristic.
 }
@@
 However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
-Selye the physician would likely have labeled the two responses as subjective manifestations of ``distress,'' and ``eustress'' (Selye, 1974).
+Selye the physician would likely have labeled the two responses as subjective manifestations of ``distress'', and ``eustress'' (Selye, 1974).
 In modern I-O Psychology parlance (and more consistent with the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker \& Demerouti, 2017)), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a \emph{challenge} while the other would appraise the demand as a \emph{hindrance} (Cavanaugh et al., 2000).
@@
 
-\emph{RQ1}: Do people distinguish between challenge and hindrance stressors?
-
-\emph{Paired samples t-tests for challenge/hindrance by item?} - I like this first idea. could present it by the 7 different categories.
-\emph{Could look}
-\emph{Or percent agreement?}
-\emph{Maybe do item-level correlations between challenge/hindrance rating and present percent positively related, and negatively related (negative would be supportive, I think)}
-
 The next question focuses on whether challenges (positive stressors per the definition above) might actually be positively related to resources.
@@
 
-\emph{RQ2}: Characteristics perceived as challenges are also commonly viewed as resources.
+\emph{RQ1}: Do jobs with many resources also perceived to have many challenges?
 
@@
 
-\emph{RQ3}: The association between challenging and resourceful characteristics is moderated by type of characteristic.
+\emph{RQ2}: Is the association between challenge and resource characteristics moderated by type of characteristic?
 
@@
 
-We also have ratings of ``\ldots the extent to which this characteristic is present in your job.'' Currently we're just taking a binary yes/no approach, but it does make sense to look for moderation based on \emph{the degree to which the characteristic is present}.
+We also have ratings of ``\ldots the extent to which this characteristic is present in your job''.
+Currently we're just taking a binary yes/no approach, but it does make sense to look for moderation based on \emph{the degree to which the characteristic is present}.
 This is probably a better/more appropriate moderator than either of the above two\ldots{}
@@
 The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task.
-For example, the descriptor for ``level of competition,'' which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems.
+For example, the descriptor for ``level of competition'', which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems.
 We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
@@
 
-Hypothesis 1 predicted a positive association between total resources and total challenge demands.
+Research Question 1 explored whether jobs with many challenges have many resources?
+The total number of undifferentiated challenges and resources are positively related.
 Table \ref{tab:cortab} shows a very high association between resources and challenges (\emph{r} = .86).
@@
 
-\begin{figure}
-\centering
 \includegraphics{SIOP2024convergence_files/figure-latex/percagree-1.pdf}
-\caption{\label{fig:percagree}Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance).}
-\end{figure}
-
-\hypertarget{convergence-same-characteristic.}{%
-\subsection{Convergence (same characteristic).}\label{convergence-same-characteristic.}}
+\#\# Convergence (same characteristic)
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-bakker2017job}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
 Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
 
-\leavevmode\hypertarget{ref-bakker2013weekly}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
 Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
 
-\leavevmode\hypertarget{ref-cavanaugh2000empirical}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
 Cavanaugh, M.
@@
 
-\leavevmode\hypertarget{ref-demerouti2001job}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
 Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
 
-\leavevmode\hypertarget{ref-peterson2001understanding}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
 Peterson, N.
@@
 
-\leavevmode\hypertarget{ref-selye1936syndrome}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-selye1936syndrome}{}}%
 Selye, H. (1936). A syndrome produced by diverse nocuous agents. \emph{Nature}, \emph{138}(3479), 32--32.
 
-\leavevmode\hypertarget{ref-selye1974stress}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-selye1974stress}{}}%
 Selye, H. (1974). \emph{Stress without distress}. Lippincott Williams \& Wilkins.
 
-\leavevmode\hypertarget{ref-webster2011extending}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
 Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.

### 2023-07-10 SIOP2024/SIOP2024convergence.Rmd
SIOP Edits

@@
 The Occupational Information Network (O\*NET; onetonline.org) contains a reasonably comprehensive description of occupations [@peterson2001understanding] which subject matter experts inform via surveys.
-We utilize a set of O\*Net job context and activity statements contained in these surveys to explore a series of research questions about how people perceive resources, challenges, and hindrances within their jobs.
+We utilize a set of O\*NET job context and activity statements contained in these surveys to explore a series of research questions about how people perceive resources, challenges, and hindrances within their jobs.
 There are a number of advantage to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.
@@
 However, this list of demands (workload, role ambiguity, and role conflict) is somewhat narrow.
-Using a very wide range of O\*Net job characteristics regarding job context and activities, we explore this question:
-
-*RQ1 is a good idea for A DIFFERENT PAPER. Do ICC(1,1)*
-*RQ1*: Do people distinguish between challenge and hindrance stressors?
-
-*Paired samples t-tests for challenge/hindrance by item?* - I like this first idea. could present it by the 7 different categories.
-*Could look*
-*Or percent agreement?* 
-*Maybe do item-level correlations between challenge/hindrance rating and present percent positively related, and negatively related (negative would be supportive, I think)*
-
-The next question focuses on whether challenges (positive stressors per the definition above) might actually be positively related to resources.
+Using a very wide range of O\*NET job characteristics regarding job context and activities, we explore whether challenges (positive stressors per the definition above) might actually be positively related to resources.
 Per the job demands-resources theory [@bakker2017job] resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
@@
 
-*RQ1*: Are job characteristics perceived as challenges are also commonly viewed as resources?  
+*RQ1*: Do jobs with many resources also perceived to have many challenges?
+
 Although we argue that the same job characteristic may be perceived as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others.
 For example, a physically strenuous job requirement such as "carrying heavy objects" would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as "negotiating work schedules" may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge.
-O\*Net has different levels of abstraction with regard to the nature of job characteristics.
+O\*NET has different levels of abstraction with regard to the nature of job characteristics.
 We will be exploring a mid-level abstraction with seven different characteristic scales.
@@
 We evaluate agreement across perceptions of job characteristics regarding their characterization as resource, challenge, and hindrance (Bakker & Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001).
-To capture an effectively exhaustive list of characteristics that apply to, theoretically, *every* possible job, we consult the  unifying framework of O\*Net.
+To capture an effectively exhaustive list of characteristics that apply to, theoretically, *every* possible job, we consult the  unifying framework of O\*NET.
 
@@
 
-Our survey was informed by 98 statements taken from job characteristic descriptors located within O\*Net’s classification of “work activities”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context” groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
+Our survey was informed by 98 statements taken from job characteristic descriptors located within O\*NET’s classification of “work activities”: 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and “work context” groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
 
-The O\*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to "responsibility" than task.
-For example, the descriptor for "level of competition", which is an element of the "structural job characteristics" grouping, is *...to what extent does this job require the worker to compete or to be aware of competitive pressures?* Other than minor grammatical editing (for example, changing “the worker” to “you”), we retained the O\*Net wording for our item stems.
-We also retained O\*Net’s response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
+The O\*NET descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to "responsibility" than task.
+For example, the descriptor for "level of competition", which is an element of the "structural job characteristics" grouping, is *How often do you have to perform public speaking in this job??* Other than minor grammatical editing (for example, changing “the worker” to “you” where applicable), we retained the O\*NET wording for our item stems.
+We also retained O\*NET’s response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
 It would likely NOT be considered controversial to referred to these as "effectively" Likert-type response scales.
@@
 
-Following IRB approval, respondents were recruited through Prolific.
-After providing consent, respondents provided ratings of whether or not each of the 98 O\*Net characteristics were relevant for the respondent's work.
-Subsequently, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of perception of resource, challenge, or hindrance.
-The total number of items on the survey was less than 392 (98 characteristics x 4 administrations - the first for relevance and the remaining 3 for resources, challenges, and hindrances) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
-Furthermore, not every respondent indicated that the same characteristics were relevant to them, therefore each respondent had a unique set of responses.
+Respondents were recruited through Prolific.
+After providing consent, respondents provided ratings of whether or not each of the 98 O\*NET characteristics were relevant for the respondent's primary work role.
+Subsequently, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of perception of resource, challenge, and hindrance.
+The total number of items on the survey was less than 392 (98 characteristics x 4 administrations - the first for relevance and the remaining 3 for resources, challenges, and hindrances) because we did not ask for demand and resource evaluations for 14 O\*NET characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
+Furthermore, not every respondent indicated that the same characteristics were relevant to them.
+Therefore, each respondent had a unique set of administered items.
 Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
@@
 
-All analyses are focused on characteristics of work that were rated as being "relevant" to the respondents' job.
-Upon confirming that a work characteristic was relevant, respondents then also rated the extent to which that characteristic was percieved as a resources, challenge, and hindrance.
+All analyses are focused on characteristics of work that were rated as being "relevant" to the respondents' primary job.
+Upon confirming that a work characteristic was relevant, respondents then also rated the extent to which that characteristic was perceived as a resources, challenge, and hindrance.
 
@@
 
-## Resource, Challenge, and Hindrance Associations
-
 ```{r cortab}
@@
 
-Hypothesis 1 predicted a positive association between total resources and total challenge demands.
+## Resource, Challenge, and Hindrance Associations
+
+Research Question 1 explored whether jobs with many challenges have many resources.
+The total number of undifferentiated challenges and resources are positively related.
 Table \@ref(tab:cortab) shows a very high association between resources and challenges (*r* = .86).
 These associations, however, are only capturing the relationships between these demands and resources in *sheer volume*.
-That is, table \@ref(tab:cortab) operationalized each variable as the sheer number of resources, hindrances, or challenges that a respondent indicated were present within their job.
+That is, Table \@ref(tab:cortab) operationalized each variable as the sheer number of resources, hindrances, or challenges that a respondent indicated were present within their job.
 This correlational analysis simply implies that workers who experience more resources also perceive greater challenges.
@@
 Also, take note of the average numbers of resources, challenges, and hindrances cited by our sample, where these respondents generally experienced fewer hindrances in their jobs (*M* = 13.09) than both resources and challenges.
+
+## Convergence (same characteristic)
+
+We next looked for convergence of perception at the level of each individual job characteristic.
+Here, we calculated the *percent of affirmative correspondence* between individual characteristic perceptions.
+That is, a respondent needed to agree that *...being in contact with others* was both a resource as well as a challenge in order to be implicated as affirmatively agreeing.
+We did this for each of the 84 individual characteristics that were rated as a resource, challenge, or demand and then computed an aggregate level of affirmative correspondence for each person.
+Figure \@ref(fig:percagree) presents the results of these correspondences, showing that there was not much mutual agreement regarding characteristics being viewed as both hindrances and resources (*M* = `r round(mean(rh$mean, na.rm=TRUE),2)`) or as challenges and hindrances
+(*M* = `r round(mean(ch$mean, na.rm=TRUE),2)`).
+However, when a characteristic was viewed a resource, it was more likely to also be perceived as a challenge (although the correspondence also exhibited quite a bit of variability; *M* = `r round(mean(rc$mean, na.rm=TRUE),2)`, *sd* = `r round(sd(rc$mean, na.rm=TRUE),2)`).
 
@@
 
-## lotsa variance in resource-challenge agreement. Next look for either content (O*Net category) or contextual (job) moderator
+## lotsa variance in resource-challenge agreement. Next look for either content (O*NET category) or contextual (job) moderator
 
 ```
-## Convergence (same characteristic).
-
-We next looked for convergence of perception at the level of each individual job characteristic.
-Here, we calculated the *percent of affirmative correspondence* between individual characteristic perceptions.
-That is, a respondent needed to agree that *...being in contact with others* was both a resource as well as a challenge in order to be implicated as affirmatively agreeing.
-We did this for each of the 84 individual characteristics that were rated as a resource, challenge, or demand and then computed an aggregate level of affirmative correspondence for each person.
-Figure \@ref(fig:percagree) presents the results of these correspondences, showing that there was not much mutual agreement regarding characteristics being viewed as both hindrances and resources (*M* = `r round(mean(rh$mean, na.rm=TRUE),2)`) or as challenges and hindrances
-(*M* = `r round(mean(ch$mean, na.rm=TRUE),2)`).
-However, when a characteristic was viewed a resource, it was more likely to also be perceived as a challenge (although the correspondence also exhibited quite a bit of variability; *M* = `r round(mean(rc$mean, na.rm=TRUE),2)`, *sd* = `r round(sd(rc$mean, na.rm=TRUE),2)`).
 
@@
 Figure \@ref(fig:recchall) explores the possibility of moderation by *type of characteristic rated* for the resource-challenge convergence.
-Here we categorized each characteristic by its O\*Net "scale" (one of seven), and the graph shows greater consistency across certain characteristics (for example, *Mental Processes* or *Interacting with Others*) and less convergence across other *types* of job activities (for example, *Physical* characteristics).
+Here we categorized each characteristic by its O\*NET "scale" (one of seven), and the graph shows greater consistency across certain characteristics (for example, *Mental Processes* or *Interacting with Others*) and less convergence across other *types* of job activities (for example, *Physical* characteristics).
 A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of $F_{(6, 3,402)}$ = 613.5, *p* < .001 (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001.
 
-```{r workcat, fig.cap="Percent agreement (resource and challenge) across O*Net occupational categories (previous was across 84 O/*Net items - this is across 568 individual workers).", fig.height=10}
+```{r workcat, fig.cap="Percent agreement (resource and challenge) across O*NET occupational categories (previous was across 84 O/*Net items - this is across 568 individual workers).", fig.height=10}
 
@@
 forworkers2 <- anova[,c(2:85)]
-dataworker <- cbind(forworkers2,workers$O.Net.Job.Family.Categories)    ## to repeat O*Net analyses
+dataworker <- cbind(forworkers2,workers$O.Net.Job.Family.Categories)    ## to repeat O*NET analyses
                                      ## This gets worker info into convergence file
@@
 
-As can be seen in Figure \@ref(fig:workcat), the moderation seen across O\*Net dimension was not paralleled across *job classification*.
+As can be seen in Figure \@ref(fig:workcat), the moderation seen across O\*NET dimension was not paralleled across *job classification*.
 Here, there was wide variability in convergence, regardless of *type* of job.

### 2023-07-10 SIOP2024/SIOP2024convergence.tex
getting to knit (Starbucks)

@@
 \usepackage{amsmath,amssymb}
+\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math} % this also loads fontspec
+  \usepackage{unicode-math}
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-\usepackage{lmodern}
-\ifPDFTeX\else
-  % xetex/luatex font selection
 \fi
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same}
-\hypersetup{
-  pdftitle={Demanding resources: Converging perceptions of challenge and resource characteristics},
-  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata García Prieto Palacios Roji3},
-  pdflang={en-EN},
-  pdfkeywords={keywords},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
 
@@
 
+\begin{verbatim}
+## Warning: package 'tinylabels' was built under R version 4.1.3
+\end{verbatim}
+
 The Occupational Information Network (O*NET; onetonline.org) contains a reasonably comprehensive description of occupations (Peterson et al., 2001) which subject matter experts inform via surveys.
-We utilize a set of O*Net job context and activity statements contained in these surveys to explore a series of research questions about how people perceive resources, challenges, and hindrances within their jobs.
+We utilize a set of O*NET job context and activity statements contained in these surveys to explore a series of research questions about how people perceive resources, challenges, and hindrances within their jobs.
 There are a number of advantage to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.
@@
 However, this list of demands (workload, role ambiguity, and role conflict) is somewhat narrow.
-Using a very wide range of O*Net job characteristics regarding job context and activities, we explore this question:
-
-The next question focuses on whether challenges (positive stressors per the definition above) might actually be positively related to resources.
+Using a very wide range of O*NET job characteristics regarding job context and activities, we explore whether challenges (positive stressors per the definition above) might actually be positively related to resources.
 Per the job demands-resources theory (Bakker \& Demerouti, 2017) resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
@@
 For example, a physically strenuous job requirement such as ``carrying heavy objects'' would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as ``negotiating work schedules'' may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge.
-O*Net has different levels of abstraction with regard to the nature of job characteristics.
+O*NET has different levels of abstraction with regard to the nature of job characteristics.
 We will be exploring a mid-level abstraction with seven different characteristic scales.
@@
 We evaluate agreement across perceptions of job characteristics regarding their characterization as resource, challenge, and hindrance (Bakker \& Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001).
-To capture an effectively exhaustive list of characteristics that apply to, theoretically, \emph{every} possible job, we consult the unifying framework of O*Net.
+To capture an effectively exhaustive list of characteristics that apply to, theoretically, \emph{every} possible job, we consult the unifying framework of O*NET.
 
@@
 
-Our survey was informed by 98 statements taken from job characteristic descriptors located within O*Net's classification of ``work activities'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'' groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
+Our survey was informed by 98 statements taken from job characteristic descriptors located within O*NET's classification of ``work activities'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'' groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
 
-The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task.
-For example, the descriptor for ``level of competition'', which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems.
-We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
+The O*NET descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task.
+For example, the descriptor for ``level of competition'', which is an element of the ``structural job characteristics'' grouping, is \emph{How often do you have to perform public speaking in this job??} Other than minor grammatical editing (for example, changing ``the worker'' to ``you'' where applicable), we retained the O*NET wording for our item stems.
+We also retained O*NET's response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
 It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.
@@
 
-Following IRB approval, respondents were recruited through Prolific.
-After providing consent, respondents provided ratings of whether or not each of the 98 O*Net characteristics were relevant for the respondent's work.
-Subsequently, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of perception of resource, challenge, or hindrance.
-The total number of items on the survey was less than 392 (98 characteristics x 4 administrations - the first for relevance and the remaining 3 for resources, challenges, and hindrances) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
-Furthermore, not every respondent indicated that the same characteristics were relevant to them, therefore each respondent had a unique set of responses.
+Respondents were recruited through Prolific.
+After providing consent, respondents provided ratings of whether or not each of the 98 O*NET characteristics were relevant for the respondent's primary work role.
+Subsequently, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of perception of resource, challenge, and hindrance.
+The total number of items on the survey was less than 392 (98 characteristics x 4 administrations - the first for relevance and the remaining 3 for resources, challenges, and hindrances) because we did not ask for demand and resource evaluations for 14 O*NET characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
+Furthermore, not every respondent indicated that the same characteristics were relevant to them.
+Therefore, each respondent had a unique set of administered items.
 Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
@@
 
-All analyses are focused on characteristics of work that were rated as being ``relevant'' to the respondents' job.
-Upon confirming that a work characteristic was relevant, respondents then also rated the extent to which that characteristic was percieved as a resources, challenge, and hindrance.
-
-\hypertarget{resource-challenge-and-hindrance-associations}{%
-\subsection{Resource, Challenge, and Hindrance Associations}\label{resource-challenge-and-hindrance-associations}}
+All analyses are focused on characteristics of work that were rated as being ``relevant'' to the respondents' primary job.
+Upon confirming that a work characteristic was relevant, respondents then also rated the extent to which that characteristic was perceived as a resources, challenge, and hindrance.
 
@@
 
-Research Question 1 explored whether jobs with many challenges have many resources?
-The total number of undifferentiated challenges and resources are positively related.
-Table \ref{tab:cortab} shows a very high association between resources and challenges (\emph{r} = .86).
-These associations, however, are only capturing the relationships between these demands and resources in \emph{sheer volume}.
-That is, table \ref{tab:cortab} operationalized each variable as the sheer number of resources, hindrances, or challenges that a respondent indicated were present within their job.
-This correlational analysis simply implies that workers who experience more resources also perceive greater challenges.
-The associations between resources and hindrances (\emph{r} = .23) and challenges and hindrances (\emph{r} = .22) were also significantly positive with moderate magnitude associations, suggesting that some of this ``sheer volume'' may be capturing job complexity (that is, the more complex the job, the more characteristics are relevant, and therefore the more likely it is to have \emph{more} challenges as well as \emph{more} hindrances as well as \emph{more} resources).
-Although we did not address job complexity as a moderator in the current paper, we do plan to do so in future investigations.
-Also, take note of the average numbers of resources, challenges, and hindrances cited by our sample, where these respondents generally experienced fewer hindrances in their jobs (\emph{M} = 13.09) than both resources and challenges.
-
+\begin{figure}
+\centering
 \includegraphics{SIOP2024convergence_files/figure-latex/percagree-1.pdf}
-\#\# Convergence (same characteristic)
-
-We next looked for convergence of perception at the level of each individual job characteristic.
-Here, we calculated the \emph{percent of affirmative correspondence} between individual characteristic perceptions.
-That is, a respondent needed to agree that \emph{\ldots being in contact with others} was both a resource as well as a challenge in order to be implicated as affirmatively agreeing.
-We did this for each of the 84 individual characteristics that were rated as a resource, challenge, or demand and then computed an aggregate level of affirmative correspondence for each person.
-Figure \ref{fig:percagree} presents the results of these correspondences, showing that there was not much mutual agreement regarding characteristics being viewed as both hindrances and resources (\emph{M} = 0.14) or as challenges and hindrances
-(\emph{M} = 0.14).
-However, when a characteristic was viewed a resource, it was more likely to also be perceived as a challenge (although the correspondence also exhibited quite a bit of variability; \emph{M} = 0.51, \emph{sd} = 0.21).
+\caption{\label{fig:percagree}Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance).}
+\end{figure}
 
@@
 
+\hypertarget{resource-challenge-and-hindrance-associations}{%
+\subsection{Resource, Challenge, and Hindrance Associations}\label{resource-challenge-and-hindrance-associations}}
+
+Research Question 1 explored whether jobs with many challenges have many resources.
+The total number of undifferentiated challenges and resources are positively related.
+Table \ref{tab:cortab} shows a very high association between resources and challenges (\emph{r} = .86).
+These associations, however, are only capturing the relationships between these demands and resources in \emph{sheer volume}.
+That is, Table \ref{tab:cortab} operationalized each variable as the sheer number of resources, hindrances, or challenges that a respondent indicated were present within their job.
+This correlational analysis simply implies that workers who experience more resources also perceive greater challenges.
+The associations between resources and hindrances (\emph{r} = .23) and challenges and hindrances (\emph{r} = .22) were also significantly positive with moderate magnitude associations, suggesting that some of this ``sheer volume'' may be capturing job complexity (that is, the more complex the job, the more characteristics are relevant, and therefore the more likely it is to have \emph{more} challenges as well as \emph{more} hindrances as well as \emph{more} resources).
+Although we did not address job complexity as a moderator in the current paper, we do plan to do so in future investigations.
+Also, take note of the average numbers of resources, challenges, and hindrances cited by our sample, where these respondents generally experienced fewer hindrances in their jobs (\emph{M} = 13.09) than both resources and challenges.
+
+\hypertarget{convergence-same-characteristic}{%
+\subsection{Convergence (same characteristic)}\label{convergence-same-characteristic}}
+
+We next looked for convergence of perception at the level of each individual job characteristic.
+Here, we calculated the \emph{percent of affirmative correspondence} between individual characteristic perceptions.
+That is, a respondent needed to agree that \emph{\ldots being in contact with others} was both a resource as well as a challenge in order to be implicated as affirmatively agreeing.
+We did this for each of the 84 individual characteristics that were rated as a resource, challenge, or demand and then computed an aggregate level of affirmative correspondence for each person.
+Figure \ref{fig:percagree} presents the results of these correspondences, showing that there was not much mutual agreement regarding characteristics being viewed as both hindrances and resources (\emph{M} = 0.14) or as challenges and hindrances (\emph{M} = 0.14).
+However, when a characteristic was viewed a resource, it was more likely to also be perceived as a challenge (although the correspondence also exhibited quite a bit of variability; \emph{M} = 0.51, \emph{sd} = 0.21).
+
 \hypertarget{moderating-effects}{%
@@
 Figure \ref{fig:recchall} explores the possibility of moderation by \emph{type of characteristic rated} for the resource-challenge convergence.
-Here we categorized each characteristic by its O*Net ``scale'' (one of seven), and the graph shows greater consistency across certain characteristics (for example, \emph{Mental Processes} or \emph{Interacting with Others}) and less convergence across other \emph{types} of job activities (for example, \emph{Physical} characteristics).
+Here we categorized each characteristic by its O*NET ``scale'' (one of seven), and the graph shows greater consistency across certain characteristics (for example, \emph{Mental Processes} or \emph{Interacting with Others}) and less convergence across other \emph{types} of job activities (for example, \emph{Physical} characteristics).
 A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of \(F_{(6, 3,402)}\) = 613.5, \emph{p} \textless{} .001 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001.
@@
 \includegraphics{SIOP2024convergence_files/figure-latex/workcat-1.pdf}
-\caption{\label{fig:workcat}Percent agreement (resource and challenge) across O\emph{Net occupational categories (previous was across 84 O/}Net items - this is across 568 individual workers).}
+\caption{\label{fig:workcat}Percent agreement (resource and challenge) across O\emph{NET occupational categories (previous was across 84 O/}Net items - this is across 568 individual workers).}
 \end{figure}
 
-As can be seen in Figure \ref{fig:workcat}, the moderation seen across O*Net dimension was not paralleled across \emph{job classification}.
+As can be seen in Figure \ref{fig:workcat}, the moderation seen across O*NET dimension was not paralleled across \emph{job classification}.
 Here, there was wide variability in convergence, regardless of \emph{type} of job.

### 2023-07-10 SIOP2024/SIOP2024convergence.Rmd
getting to knit (Starbucks)
siop updates

@@
 
-## Resource, Challenge, and Hindrance Associations
-
-Research Question 1 explored whether jobs with many challenges have many resources.
-The total number of undifferentiated challenges and resources are positively related.
-Table \@ref(tab:cortab) shows a very high association between resources and challenges (*r* = .86).
-These associations, however, are only capturing the relationships between these demands and resources in *sheer volume*.
-That is, Table \@ref(tab:cortab) operationalized each variable as the sheer number of resources, hindrances, or challenges that a respondent indicated were present within their job.
-This correlational analysis simply implies that workers who experience more resources also perceive greater challenges.
-The associations between resources and hindrances (*r* = .23) and challenges and hindrances (*r* = .22) were also significantly positive with moderate magnitude associations, suggesting that some of this "sheer volume" may be capturing job complexity (that is, the more complex the job, the more characteristics are relevant, and therefore the more likely it is to have *more* challenges as well as *more* hindrances as well as *more* resources).
-Although we did not address job complexity as a moderator in the current paper, we do plan to do so in future investigations.
-Also, take note of the average numbers of resources, challenges, and hindrances cited by our sample, where these respondents generally experienced fewer hindrances in their jobs (*M* = 13.09) than both resources and challenges.
-
-## Convergence (same characteristic)
-
-We next looked for convergence of perception at the level of each individual job characteristic.
-Here, we calculated the *percent of affirmative correspondence* between individual characteristic perceptions.
-That is, a respondent needed to agree that *...being in contact with others* was both a resource as well as a challenge in order to be implicated as affirmatively agreeing.
-We did this for each of the 84 individual characteristics that were rated as a resource, challenge, or demand and then computed an aggregate level of affirmative correspondence for each person.
-Figure \@ref(fig:percagree) presents the results of these correspondences, showing that there was not much mutual agreement regarding characteristics being viewed as both hindrances and resources (*M* = `r round(mean(rh$mean, na.rm=TRUE),2)`) or as challenges and hindrances
-(*M* = `r round(mean(ch$mean, na.rm=TRUE),2)`).
-However, when a characteristic was viewed a resource, it was more likely to also be perceived as a challenge (although the correspondence also exhibited quite a bit of variability; *M* = `r round(mean(rc$mean, na.rm=TRUE),2)`, *sd* = `r round(sd(rc$mean, na.rm=TRUE),2)`).
-
 ```{r percagree, fig.cap="Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance).", fig.height=10}
@@
 forgraph <- rbind(rc,rh,ch)
+forgraph$type <- factor(forgraph$type, levels = c("Resource-Hindrance", "Challenge-Hindrance", "Resource-Challenge"))
 
@@
 
-repmeas <- aov(value ~ factor(scale) + Error(factor(person)), data=analysis)
+repmeas2 <- aov(value ~ factor(scale) + Error(factor(person)), data=analysis)
+
+library(ez)
+
+repmeas <- ezANOVA(data=analysis, dv=value, wid=person, within=.(scale), type=3, detailed=TRUE)
+repmeas
+# TukeyHSD(workeraov)  ## Tukeys for temp in paper; biggest contrast p = .099
+# psych::describeBy(dataworker$overall, dataworker$JobFamily) (took means from here because `TukeyHSD` only reports relative difference)
+
+TukeyHSD(repmeas2)
+library(car)
+
+#levenes <- leveneTest(value ~ scale, data=analysis)
 
 ```
+
+## Resource, Challenge, and Hindrance Associations
+
+Research Question 1 explored whether jobs with many challenges have many resources.
+The total number of undifferentiated challenges and resources are positively related.
+Table \@ref(tab:cortab) shows a very high association between resources and challenges (*r* = .86).
+These associations, however, are only capturing the relationships between these demands and resources in *sheer volume*.
+That is, Table \@ref(tab:cortab) operationalized each variable as the sheer number of resources, hindrances, or challenges that a respondent indicated were present within their job.
+This correlational analysis simply implies that workers who experience more resources also perceive greater challenges.
+The associations between resources and hindrances (*r* = .23) and challenges and hindrances (*r* = .22) were also significantly positive with moderate magnitude associations, suggesting that some of this "sheer volume" may be capturing job complexity (that is, the more complex the job, the more characteristics are relevant, and therefore the more likely it is to have *more* challenges as well as *more* hindrances as well as *more* resources).
+Although we did not address job complexity as a moderator in the current paper, we do plan to do so in future investigations.
+Also, take note of the average numbers of resources, challenges, and hindrances cited by our sample, where these respondents generally experienced fewer hindrances in their jobs (*M* = 13.09) than both resources and challenges.
+
+## Convergence (same characteristic)
+
+We next looked for convergence of perception at the level of each individual job characteristic.
+Here, we calculated the *percent of affirmative correspondence* between individual characteristic perceptions.
+That is, a respondent needed to agree that *...being in contact with others* was both a resource as well as a challenge in order to be implicated as affirmatively agreeing.
+We did this for each of the 84 individual characteristics that were rated as a resource, challenge, or demand and then computed an aggregate level of affirmative correspondence for each person.
+Figure \@ref(fig:percagree) presents the results of these correspondences, showing that there was not much mutual agreement regarding characteristics being viewed as both hindrances and resources (*M* = `r round(mean(rh$mean, na.rm=TRUE),2)`) or as challenges and hindrances (*M* = `r round(mean(ch$mean, na.rm=TRUE),2)`).
+However, when a characteristic was viewed a resource, it was more likely to also be perceived as a challenge (although the correspondence also exhibited quite a bit of variability; *M* = `r round(mean(rc$mean, na.rm=TRUE),2)`, *SD* = `r round(sd(rc$mean, na.rm=TRUE),2)`).
 
@@
 Here we categorized each characteristic by its O\*NET "scale" (one of seven), and the graph shows greater consistency across certain characteristics (for example, *Mental Processes* or *Interacting with Others*) and less convergence across other *types* of job activities (for example, *Physical* characteristics).
-A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of $F_{(6, 3,402)}$ = 613.5, *p* < .001 (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001.
+A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of $F_{(6, 3,402)}$ = 613.5, *p* < .001, $\eta^2_{p}$ = `r round(repmeas$ANOVA[2,9],2)` (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001.
+The only contrast approaching statistical significance via Tukey's HSD specification (*p* = .09) was the contrast between Physical Labor (*M* = 0.49) and Business and Financial Operations (*M* = 0.58).
 
-```{r workcat, fig.cap="Percent agreement (resource and challenge) across O*NET occupational categories (previous was across 84 O/*Net items - this is across 568 individual workers).", fig.height=10}
+```{r workcat, fig.cap="Percent agreement (resource and challenge) across O*NET occupational categories (previous was across 84 O/*Net items - this is across 568 individual workers).", fig.height=10, eval=FALSE}
 
@@
 
-```{r tukey}
+```{r tukey, eval=FALSE}
 
@@
 ```
-
-As can be seen in Figure \@ref(fig:workcat), the moderation seen across O\*NET dimension was not paralleled across *job classification*.
-Here, there was wide variability in convergence, regardless of *type* of job.
-The omnibus ANOVA did breach statistical significance ($F_{(7, 560)}$ = `r summary(workeraov)[[1]][1,4]`, *p* = `r summary(workeraov)[[1]][1,5]`), however, the practical effect was very small ($\eta^2$ = `r effect.size[1,1]`).
-The only contrast approaching statistical significance via Tukey's HSD specification (*p* = .09) was the contrast between Physical Labor (*M* = 0.49) and Business and Financial Operations (*M* = 0.58).
-Additionally, a Levene's test for homogeneity of variance was non-significant (Levene's = `r levenes[1,2]`, *p* = `r levenes[1,3]`).
-[should be .6539 and .7112]
 

### 2023-07-10 SIOP2024/SIOP2024convergence.tex
siop updates

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same}
+\hypersetup{
+  pdftitle={Demanding resources: Converging perceptions of challenge and resource characteristics},
+  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata García Prieto Palacios Roji3},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 Figure \ref{fig:percagree} presents the results of these correspondences, showing that there was not much mutual agreement regarding characteristics being viewed as both hindrances and resources (\emph{M} = 0.14) or as challenges and hindrances (\emph{M} = 0.14).
-However, when a characteristic was viewed a resource, it was more likely to also be perceived as a challenge (although the correspondence also exhibited quite a bit of variability; \emph{M} = 0.51, \emph{sd} = 0.21).
+However, when a characteristic was viewed a resource, it was more likely to also be perceived as a challenge (although the correspondence also exhibited quite a bit of variability; \emph{M} = 0.51, \emph{SD} = 0.21).
 
@@
 Here we categorized each characteristic by its O*NET ``scale'' (one of seven), and the graph shows greater consistency across certain characteristics (for example, \emph{Mental Processes} or \emph{Interacting with Others}) and less convergence across other \emph{types} of job activities (for example, \emph{Physical} characteristics).
-A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of \(F_{(6, 3,402)}\) = 613.5, \emph{p} \textless{} .001 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001.
-
-\begin{figure}
-\centering
-\includegraphics{SIOP2024convergence_files/figure-latex/workcat-1.pdf}
-\caption{\label{fig:workcat}Percent agreement (resource and challenge) across O\emph{NET occupational categories (previous was across 84 O/}Net items - this is across 568 individual workers).}
-\end{figure}
-
-As can be seen in Figure \ref{fig:workcat}, the moderation seen across O*NET dimension was not paralleled across \emph{job classification}.
-Here, there was wide variability in convergence, regardless of \emph{type} of job.
-The omnibus ANOVA did breach statistical significance (\(F_{(7, 560)}\) = 2.06, \emph{p} = 0.05), however, the practical effect was very small (\(\eta^2\) = 0.03).
+A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of \(F_{(6, 3,402)}\) = 613.5, \emph{p} \textless{} .001, \(\eta^2_{p}\) = 0.35 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001.
 The only contrast approaching statistical significance via Tukey's HSD specification (\emph{p} = .09) was the contrast between Physical Labor (\emph{M} = 0.49) and Business and Financial Operations (\emph{M} = 0.58).
-Additionally, a Levene's test for homogeneity of variance was non-significant (Levene's = 0.65, \emph{p} = 0.71).
-{[}should be .6539 and .7112{]}
+Additionally, a Levene's test for homogeneity of variance was non-significant (Levene's = , \emph{p} = .
 

### 2023-07-11 Submission.Rmd
old edits

@@
 author: 
-  - Alicia Stachowski, University of Wisconsin, Stout
-  - John Kulas, eRg
-  - Renata Garcia Prieto Palacios Roji, PepsiCo
+  -
 
@@
 We explore this hypothesis first at the job characteristic level before presenting a broader perspective.
-Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present only extreme snapshots of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency.
-Figure \@ref(fig:combinegraphs) presents the resources, challenges, and hindrances that are *most consistently agreed on* as indexed by (relatively) low standard deviations, while Figure \@ref(fig:combinegraphs2) presents the characteristics with the greatest amount of *disagreement* across workers.
+Figures 1 and 2 present only extreme snapshots of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency.
+Figure 1 presents the resources, challenges, and hindrances that are *most consistently agreed on* as indexed by (relatively) low standard deviations, while Figure 2 presents the characteristics with the greatest amount of *disagreement* across workers.
 The figures demonstrate that what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
@@
  [^onlinelist]: A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
-The Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2)  presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).
+The Figures 1 and 2  presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).
 
-In addition to highlighting extremely agreed- or disagreed-upon items, Figure \@ref(fig:overallhist) presents our standard deviation indices across all rated items.
-Here, the Figure \@ref(fig:combinegraphs) discrepancies receive greater context, with the *spread* of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively *bunched* levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
+In addition to highlighting extremely agreed- or disagreed-upon items, Figure 3 presents our standard deviation indices across all rated items.
+Here, the Figure 1 discrepancies receive greater context, with the *spread* of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively *bunched* levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
 Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
@@
 The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand.
-Table \@ref(tab:cortab) provides the correlations among the O\*Net "scale"-level groupings across ratings of resource, challenge, and hindrance.
+Table 1 provides the correlations among the O\*Net "scale"-level groupings across ratings of resource, challenge, and hindrance.
 We would expect to see minimal correlations if job characteristics *were* uniquely categorized.
-First, the average correlation within all resource categories (variables 1 through 7 in Table \@ref(tab:cortab)) was .43 (*SD* = .13, range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16).
+First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16).
 Hindrance categories, however, had less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, *M* = .62, *SD* = .17.
 When people perceived hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.
-Taken with the Figure \@ref(fig:overallhist) takeaway, this hints that workers are likely either generally experiencing hindrances at work or they are not.
+Taken with the Figure 3 takeaway, this hints that workers are likely either generally experiencing hindrances at work or they are not.
 

### 2023-07-11 SIOP2024/SIOP2024convergence.tex

@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same}
+\urlstyle{same} % disable monospaced font for URLs
 \hypersetup{
@@
 
+\begin{verbatim}
+## $ANOVA
+##        Effect DFn  DFd      SSn      SSd         F             p p<.05
+## 1 (Intercept)   1  567 68955.57 15304.71 2554.6258 3.565678e-212     *
+## 2       scale   6 3402 16058.68 14841.04  613.5199  0.000000e+00     *
+##         ges
+## 1 0.6958088
+## 2 0.3475572
+## 
+## $`Mauchly's Test for Sphericity`
+##   Effect         W             p p<.05
+## 2  scale 0.1909388 2.735968e-185     *
+## 
+## $`Sphericity Corrections`
+##   Effect       GGe p[GG] p[GG]<.05       HFe p[HF] p[HF]<.05
+## 2  scale 0.6049886     0         * 0.6093689     0         *
+\end{verbatim}
+
 \hypertarget{resource-challenge-and-hindrance-associations}{%
@@
 The only contrast approaching statistical significance via Tukey's HSD specification (\emph{p} = .09) was the contrast between Physical Labor (\emph{M} = 0.49) and Business and Financial Operations (\emph{M} = 0.58).
-Additionally, a Levene's test for homogeneity of variance was non-significant (Levene's = , \emph{p} = .
 

### 2023-07-11 SIOP2024/SIOP2024convergence.Rmd
siop updates
number of items per scale issue (will resolve next meeting)

@@
 
-TukeyHSD(repmeas2)
-library(car)
+library(datarium)
+library(tidyverse)
+library(ggpubr)
+library(rstatix)
 
-#levenes <- leveneTest(value ~ scale, data=analysis)
+tukeytest <- analysis %>% 
+  pairwise_t_test(value ~ scale, paired = TRUE, 
+                  p.adjust.method = "bonferroni"
+                  )  
+write.csv(tukeytest, "pairwisets.csv")
+psych::describe.by(analysis$value, analysis$scale)
 
@@
 
+>Note. This is all off because the "scales" have different numbers of items, so it's not appropriate to use sums as scale scores. Maybe revisit with means.
+
 Figure \@ref(fig:recchall) explores the possibility of moderation by *type of characteristic rated* for the resource-challenge convergence.
@@
 A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of $F_{(6, 3,402)}$ = 613.5, *p* < .001, $\eta^2_{p}$ = `r round(repmeas$ANOVA[2,9],2)` (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001.
-The only contrast approaching statistical significance via Tukey's HSD specification (*p* = .09) was the contrast between Physical Labor (*M* = 0.49) and Business and Financial Operations (*M* = 0.58).
+The only contrasts not broaching statistical significance via Bonferonni-corrected pairwise t-tests were Work Output vs.
+Physical Work Conditions (*t* = -2.31), Interpersonal Relationships vs.
+Mental Processes (*t* = .18), and Information Input vs.
+Physical Work Conditions (*t* = 1.64).
+The largest contrasts were Interacting with Others vs.
+Work Output (*t* = 36.09) and Information Input vs.
+Interacting with Others (*t* = -34.38) and Mental Processes (*t* = -34.10)
 

### 2023-07-11 SIOP2024/SIOP2024convergence.tex
number of items per scale issue (will resolve next meeting)

@@
 
+\begin{verbatim}
+## 
+##  Descriptive statistics by group 
+## group: Information
+##    vars   n mean   sd median trimmed  mad min max range skew kurtosis   se
+## X1    1 568 2.31 1.63      2    2.27 1.48   0   5     5 0.15    -1.07 0.07
+## ------------------------------------------------------------ 
+## group: Interact
+##    vars   n mean   sd median trimmed  mad min max range skew kurtosis   se
+## X1    1 568 7.57 4.21      7     7.5 4.45   0  17    17 0.13    -0.78 0.18
+## ------------------------------------------------------------ 
+## group: Interpersonal
+##    vars   n mean   sd median trimmed  mad min max range  skew kurtosis   se
+## X1    1 568 5.57 2.92      6     5.6 2.97   0  12    12 -0.06    -0.76 0.12
+## ------------------------------------------------------------ 
+## group: Mental
+##    vars   n mean  sd median trimmed  mad min max range  skew kurtosis   se
+## X1    1 568 5.55 2.9      6    5.66 2.97   0  10    10 -0.31    -0.92 0.12
+## ------------------------------------------------------------ 
+## group: Output
+##    vars   n mean   sd median trimmed  mad min max range skew kurtosis   se
+## X1    1 568 1.89 1.85      1     1.6 1.48   0   9     9  1.4     2.11 0.08
+## ------------------------------------------------------------ 
+## group: Physical
+##    vars   n mean   sd median trimmed  mad min max range skew kurtosis   se
+## X1    1 568 2.12 2.79      1    1.56 1.48   0  17    17 1.98     4.68 0.12
+## ------------------------------------------------------------ 
+## group: Structural
+##    vars   n mean   sd median trimmed  mad min max range skew kurtosis   se
+## X1    1 568 4.15 2.15      4    4.11 2.97   0  10    10  0.2    -0.52 0.09
+\end{verbatim}
+
 \hypertarget{resource-challenge-and-hindrance-associations}{%
@@
 
+\begin{quote}
+Note. This is all off because the ``scales'' have different numbers of items, so it's not appropriate to use sums as scale scores. Maybe revisit with means.
+\end{quote}
+
 Figure \ref{fig:recchall} explores the possibility of moderation by \emph{type of characteristic rated} for the resource-challenge convergence.
@@
 A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of \(F_{(6, 3,402)}\) = 613.5, \emph{p} \textless{} .001, \(\eta^2_{p}\) = 0.35 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001.
-The only contrast approaching statistical significance via Tukey's HSD specification (\emph{p} = .09) was the contrast between Physical Labor (\emph{M} = 0.49) and Business and Financial Operations (\emph{M} = 0.58).
+The only contrasts not broaching statistical significance via Bonferonni-corrected pairwise t-tests were Work Output vs.~Physical Work Conditions (\emph{t} = -2.31), Interpersonal Relationships vs.~Mental Processes (\emph{t} = .18), and Information Input vs.~Physical Work Conditions (\emph{t} = 1.64).
+The largest contrasts were Interacting with Others vs.~Work Output (\emph{t} = 36.09) and Information Input vs.~Interacting with Others (\emph{t} = -34.38) and Mental Processes (\emph{t} = -34.10)
 

### 2023-07-15 SIOP2024/SIOP2024convergence.Rmd
results done

@@
 
+#t-tests comparing resource, challenge, and hindrance proportions - sheer number of these things.
+
+#t comparing the sheer counts of resource and hindrance
+trechind <- t.test(data22$resource, data22$hindrance, paired = TRUE, alternative = "two.sided")
+
+#t comparing the sheer counts of resource and challenge
+trech <- t.test(data22$resource, data22$challenge, paired = TRUE, alternative = "two.sided")
+
+#t comparing the sheer counts of hindrance and challenge
+thich <- t.test(data22$hindrance, data22$challenge, paired = TRUE, alternative = "two.sided")
+
+library(lsr)
+
+drech <- cohensD(data22$resource, data22$challenge)
+dchhi <- cohensD(data22$hindrance, data22$challenge)
+drehi <- cohensD(data22$resource, data22$hindrance)
+
 ```
+
+The t-test between mean number of resources and hindrances suggests that respondents experienced more resources than hindrances, *t*(`r trechind$parameter`), = `r trechind$statistic`, *p* < .001, 95% CI = [`r trechind$conf.int[1]`, `r trechind$conf.int[2]`], *d* = `r drehi`.
+The t-test between mean number of resources and challenges suggests that respondents did not experience more resources than challenges, *t*(`r trech$parameter`), = `r trech$statistic`, *p* = .198, 95% CI = [`r trech$conf.int[1]`, `r trech$conf.int[2]`], *d* = `r drech`.
+The t-test between mean number of challenges and hindrances suggests that respondents experienced more challenges than hindrances, *t*(`r thich$parameter`), = `r thich$statistic`, *p* < .001, 95% CI = [`r thich$conf.int[1]`, `r thich$conf.int[2]`], *d* = `r dchhi`.
 
@@
 
-anova$Structural <- rowSums(anova[1:10], na.rm=TRUE)
-anova$Physical <- rowSums(anova[11:30], na.rm=TRUE)
-anova$Interpersonal <- rowSums(anova[31:43], na.rm=TRUE)
-anova$Information <- rowSums(anova[44:48], na.rm=TRUE)
-anova$Mental <- rowSums(anova[49:58], na.rm=TRUE)
-anova$Output <- rowSums(anova[59:67], na.rm=TRUE)
-anova$Interact <- rowSums(anova[68:84], na.rm=TRUE)
+anova$Structural <- rowMeans(anova[1:10], na.rm=TRUE)
+anova$Physical <- rowMeans(anova[11:30], na.rm=TRUE)
+anova$Interpersonal <- rowMeans(anova[31:43], na.rm=TRUE)
+anova$Information <- rowMeans(anova[44:48], na.rm=TRUE)
+anova$Mental <- rowMeans(anova[49:58], na.rm=TRUE)
+anova$Output <- rowMeans(anova[59:67], na.rm=TRUE)
+anova$Interact <- rowMeans(anova[68:84], na.rm=TRUE)
 
@@
 analysis <- gather(anova, scale, value, Structural:Interact)
+
+## 36 former "zeroes" got coded as NA when above scales were changed from rowSums to rowMeans - 7/15/23
+analysis$value[analysis$value == "NaN"] <- 0
+descr::freq(analysis$value)
 
@@
 A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of $F_{(6, 3,402)}$ = 613.5, *p* < .001, $\eta^2_{p}$ = `r round(repmeas$ANOVA[2,9],2)` (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001.
-The only contrasts not broaching statistical significance via Bonferonni-corrected pairwise t-tests were Work Output vs.
-Physical Work Conditions (*t* = -2.31), Interpersonal Relationships vs.
-Mental Processes (*t* = .18), and Information Input vs.
-Physical Work Conditions (*t* = 1.64).
-The largest contrasts were Interacting with Others vs.
-Work Output (*t* = 36.09) and Information Input vs.
-Interacting with Others (*t* = -34.38) and Mental Processes (*t* = -34.10)
+The only contrast not broaching statistical significance via Bonferonni-corrected pairwise t-tests was Work Output vs.
+Structural job characteristics (*t* = -1.10).
+The largest contrasts were Physical work conditions vs.
+Structural job characteristics (*t* = 25.14), Interpersonal relationships (*t* = -29.25), Mental processes (*t* = -33.84), and Interacting with others (*t* = -35.60)
 

### 2023-07-15 SIOP2024/SIOP2024convergence.tex
results done

--- 2023-07-10 SIOP2024/SIOP2024convergence.tex
@@
 
+The t-test between mean number of resources and hindrances suggests that respondents experienced more resources than hindrances, \emph{t}(567), = 32.67, \emph{p} \textless{} .001, 95\% CI = {[}21.55, 24.31{]}, \emph{d} = 1.71.
+The t-test between mean number of resources and challenges suggests that respondents did not experience more resources than challenges, \emph{t}(567), = 1.29, \emph{p} = .198, 95\% CI = {[}-0.20, 0.96{]}, \emph{d} = 0.03.
+The t-test between mean number of challenges and hindrances suggests that respondents experienced more challenges than hindrances, \emph{t}(567), = -31.58, \emph{p} \textless{} .001, 95\% CI = {[}-23.95, -21.15{]}, \emph{d} = 1.65.
+
 \begin{figure}
@@
 \end{figure}
+
+\includegraphics{SIOP2024convergence_files/figure-latex/anova-1.pdf}
+
+\begin{verbatim}
+## analysis$value 
+##                    Frequency   Percent
+## 0                        546  13.73239
+## 0.0526315789473684         1   0.02515
+## 0.0555555555555556         1   0.02515
+## 0.0588235294117647         3   0.07545
+## 0.0625                     1   0.02515
+## 0.0666666666666667         4   0.10060
+## 0.0714285714285714         2   0.05030
+## 0.0769230769230769         7   0.17606
+## 0.0833333333333333        14   0.35211
+## 0.0909090909090909        15   0.37726
+## 0.1                       21   0.52817
+## 0.111111111111111         28   0.70423
+## 0.125                     38   0.95573
+## 0.133333333333333          4   0.10060
+## 0.142857142857143         39   0.98089
+## 0.15                       1   0.02515
+## 0.153846153846154          4   0.10060
+## 0.157894736842105          1   0.02515
+## 0.166666666666667         41   1.03119
+## 0.176470588235294          2   0.05030
+## 0.181818181818182          9   0.22636
+## 0.1875                     3   0.07545
+## 0.2                       94   2.36419
+## 0.214285714285714          3   0.07545
+## 0.222222222222222         40   1.00604
+## 0.230769230769231          2   0.05030
+## 0.25                      84   2.11268
+## 0.266666666666667          2   0.05030
+## 0.272727272727273         13   0.32696
+## 0.277777777777778          1   0.02515
+## 0.285714285714286         45   1.13179
+## 0.294117647058824          2   0.05030
+## 0.3                       38   0.95573
+## 0.3125                     5   0.12575
+## 0.333333333333333        172   4.32596
+## 0.352941176470588          1   0.02515
+## 0.357142857142857          3   0.07545
+## 0.363636363636364         20   0.50302
+## 0.375                     40   1.00604
+## 0.384615384615385          5   0.12575
+## 0.4                      110   2.76660
+## 0.411764705882353          5   0.12575
+## 0.416666666666667         15   0.37726
+## 0.428571428571429         42   1.05634
+## 0.4375                     2   0.05030
+## 0.444444444444444         48   1.20724
+## 0.45                       1   0.02515
+## 0.454545454545455         19   0.47787
+## 0.461538461538462          4   0.10060
+## 0.466666666666667          2   0.05030
+## 0.470588235294118          2   0.05030
+## 0.5                      298   7.49497
+## 0.529411764705882          3   0.07545
+## 0.533333333333333          4   0.10060
+## 0.538461538461538          6   0.15091
+## 0.545454545454545         24   0.60362
+## 0.555555555555556         60   1.50905
+## 0.5625                     2   0.05030
+## 0.571428571428571         41   1.03119
+## 0.583333333333333         14   0.35211
+## 0.588235294117647          2   0.05030
+## 0.6                      117   2.94266
+## 0.611111111111111          2   0.05030
+## 0.615384615384615          5   0.12575
+## 0.625                     59   1.48390
+## 0.631578947368421          1   0.02515
+## 0.636363636363636         21   0.52817
+## 0.642857142857143          4   0.10060
+## 0.647058823529412          5   0.12575
+## 0.666666666666667        202   5.08048
+## 0.6875                     5   0.12575
+## 0.692307692307692          7   0.17606
+## 0.7                       46   1.15694
+## 0.705882352941177          4   0.10060
+## 0.714285714285714         38   0.95573
+## 0.727272727272727         29   0.72938
+## 0.733333333333333          6   0.15091
+## 0.75                     159   3.99899
+## 0.769230769230769         10   0.25151
+## 0.777777777777778         74   1.86117
+## 0.785714285714286          8   0.20121
+## 0.8                      125   3.14386
+## 0.8125                     1   0.02515
+## 0.818181818181818         20   0.50302
+## 0.823529411764706          3   0.07545
+## 0.833333333333333         59   1.48390
+## 0.846153846153846          3   0.07545
+## 0.857142857142857         38   0.95573
+## 0.866666666666667          7   0.17606
+## 0.875                     47   1.18209
+## 0.882352941176471          8   0.20121
+## 0.888888888888889         48   1.20724
+## 0.894736842105263          1   0.02515
+## 0.9                       50   1.25755
+## 0.909090909090909         16   0.40241
+## 0.916666666666667         15   0.37726
+## 0.923076923076923          4   0.10060
+## 0.928571428571429          9   0.22636
+## 0.933333333333333          8   0.20121
+## 0.9375                     5   0.12575
+## 0.941176470588235          8   0.20121
+## 1                        640  16.09658
+## Total                   3976 100.00000
+\end{verbatim}
+
+\begin{verbatim}
+## $ANOVA
+##        Effect DFn  DFd        SSn      SSd         F             p p<.05
+## 1 (Intercept)   1  567 1146.04761 171.5620 3787.6047 3.580669e-253     *
+## 2       scale   6 3402   92.90682 182.9607  287.9206 7.175910e-299     *
+##         ges
+## 1 0.7637413
+## 2 0.2076457
+## 
+## $`Mauchly's Test for Sphericity`
+##   Effect         W            p p<.05
+## 2  scale 0.4208255 6.425345e-91     *
+## 
+## $`Sphericity Corrections`
+##   Effect       GGe         p[GG] p[GG]<.05       HFe         p[HF] p[HF]<.05
+## 2  scale 0.7801204 6.574489e-234         * 0.7874087 4.617424e-236         *
+\end{verbatim}
+
+\begin{verbatim}
+## 
+##  Descriptive statistics by group 
+## group: Information
+##    vars   n mean   sd median trimmed  mad min max range  skew kurtosis   se
+## X1    1 568 0.62 0.38   0.67    0.65 0.49   0   1     1 -0.46    -1.27 0.02
+## ------------------------------------------------------------ 
+## group: Interact
+##    vars   n mean   sd median trimmed  mad min max range  skew kurtosis   se
+## X1    1 568 0.67 0.27   0.75     0.7 0.26   0   1     1 -0.83    -0.07 0.01
+## ------------------------------------------------------------ 
+## group: Interpersonal
+##    vars   n mean   sd median trimmed  mad min max range  skew kurtosis   se
+## X1    1 568 0.57 0.26    0.6    0.58 0.27   0   1     1 -0.36    -0.61 0.01
+## ------------------------------------------------------------ 
+## group: Mental
+##    vars   n mean   sd median trimmed  mad min max range  skew kurtosis   se
+## X1    1 568 0.71 0.29   0.78    0.75 0.33   0   1     1 -1.01     0.16 0.01
+## ------------------------------------------------------------ 
+## group: Output
+##    vars   n mean   sd median trimmed  mad min max range skew kurtosis   se
+## X1    1 568 0.48 0.37    0.5    0.48 0.49   0   1     1 0.07    -1.36 0.02
+## ------------------------------------------------------------ 
+## group: Physical
+##    vars   n mean   sd median trimmed  mad min max range skew kurtosis   se
+## X1    1 568 0.21 0.24   0.14    0.17 0.21   0   1     1 1.21     0.92 0.01
+## ------------------------------------------------------------ 
+## group: Structural
+##    vars   n mean   sd median trimmed  mad min max range skew kurtosis   se
+## X1    1 568  0.5 0.24    0.5     0.5 0.25   0   1     1 0.04    -0.62 0.01
+\end{verbatim}
 
@@
 
+\begin{quote}
+Note. This is all off because the ``scales'' have different numbers of items, so it's not appropriate to use sums as scale scores. Maybe revisit with means.
+\end{quote}
+
 Figure \ref{fig:recchall} explores the possibility of moderation by \emph{type of characteristic rated} for the resource-challenge convergence.
 Here we categorized each characteristic by its O*NET ``scale'' (one of seven), and the graph shows greater consistency across certain characteristics (for example, \emph{Mental Processes} or \emph{Interacting with Others}) and less convergence across other \emph{types} of job activities (for example, \emph{Physical} characteristics).
-A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of \(F_{(6, 3,402)}\) = 613.5, \emph{p} \textless{} .001, \(\eta^2_{p}\) = 0.35 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001.
-The only contrast approaching statistical significance via Tukey's HSD specification (\emph{p} = .09) was the contrast between Physical Labor (\emph{M} = 0.49) and Business and Financial Operations (\emph{M} = 0.58).
-Additionally, a Levene's test for homogeneity of variance was non-significant (Levene's = , \emph{p} = .
+A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of \(F_{(6, 3,402)}\) = 613.5, \emph{p} \textless{} .001, \(\eta^2_{p}\) = 0.21 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001.
+The only contrast not broaching statistical significance via Bonferonni-corrected pairwise t-tests was Work Output vs.~Structural job characteristics (\emph{t} = -1.10).
+The largest contrasts were Physical work conditions vs.~Structural job characteristics (\emph{t} = 25.14), Interpersonal relationships (\emph{t} = -29.25), Mental processes (\emph{t} = -33.84), and Interacting with others (\emph{t} = -35.60)
 

### 2023-07-18 SIOP2024/SIOP2024convergence.Rmd
editing output out
output editing

@@
 
-```{r anova}
+```{r anova, warning=FALSE, echo=FALSE}
 
@@
 analysis$value[analysis$value == "NaN"] <- 0
-descr::freq(analysis$value)
+#descr::freq(analysis$value)
 
@@
 repmeas <- ezANOVA(data=analysis, dv=value, wid=person, within=.(scale), type=3, detailed=TRUE)
-repmeas
+#repmeas
 # TukeyHSD(workeraov)  ## Tukeys for temp in paper; biggest contrast p = .099

### 2023-07-18 SIOP2024/SIOP2024convergence.tex
editing output out
output editing

@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Demanding resources: Converging perceptions of challenge and resource characteristics},
+  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata García Prieto Palacios Roji3},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 \end{figure}
-
-\includegraphics{SIOP2024convergence_files/figure-latex/anova-1.pdf}
-
-\begin{verbatim}
-## analysis$value 
-##                    Frequency   Percent
-## 0                        546  13.73239
-## 0.0526315789473684         1   0.02515
-## 0.0555555555555556         1   0.02515
-## 0.0588235294117647         3   0.07545
-## 0.0625                     1   0.02515
-## 0.0666666666666667         4   0.10060
-## 0.0714285714285714         2   0.05030
-## 0.0769230769230769         7   0.17606
-## 0.0833333333333333        14   0.35211
-## 0.0909090909090909        15   0.37726
-## 0.1                       21   0.52817
-## 0.111111111111111         28   0.70423
-## 0.125                     38   0.95573
-## 0.133333333333333          4   0.10060
-## 0.142857142857143         39   0.98089
-## 0.15                       1   0.02515
-## 0.153846153846154          4   0.10060
-## 0.157894736842105          1   0.02515
-## 0.166666666666667         41   1.03119
-## 0.176470588235294          2   0.05030
-## 0.181818181818182          9   0.22636
-## 0.1875                     3   0.07545
-## 0.2                       94   2.36419
-## 0.214285714285714          3   0.07545
-## 0.222222222222222         40   1.00604
-## 0.230769230769231          2   0.05030
-## 0.25                      84   2.11268
-## 0.266666666666667          2   0.05030
-## 0.272727272727273         13   0.32696
-## 0.277777777777778          1   0.02515
-## 0.285714285714286         45   1.13179
-## 0.294117647058824          2   0.05030
-## 0.3                       38   0.95573
-## 0.3125                     5   0.12575
-## 0.333333333333333        172   4.32596
-## 0.352941176470588          1   0.02515
-## 0.357142857142857          3   0.07545
-## 0.363636363636364         20   0.50302
-## 0.375                     40   1.00604
-## 0.384615384615385          5   0.12575
-## 0.4                      110   2.76660
-## 0.411764705882353          5   0.12575
-## 0.416666666666667         15   0.37726
-## 0.428571428571429         42   1.05634
-## 0.4375                     2   0.05030
-## 0.444444444444444         48   1.20724
-## 0.45                       1   0.02515
-## 0.454545454545455         19   0.47787
-## 0.461538461538462          4   0.10060
-## 0.466666666666667          2   0.05030
-## 0.470588235294118          2   0.05030
-## 0.5                      298   7.49497
-## 0.529411764705882          3   0.07545
-## 0.533333333333333          4   0.10060
-## 0.538461538461538          6   0.15091
-## 0.545454545454545         24   0.60362
-## 0.555555555555556         60   1.50905
-## 0.5625                     2   0.05030
-## 0.571428571428571         41   1.03119
-## 0.583333333333333         14   0.35211
-## 0.588235294117647          2   0.05030
-## 0.6                      117   2.94266
-## 0.611111111111111          2   0.05030
-## 0.615384615384615          5   0.12575
-## 0.625                     59   1.48390
-## 0.631578947368421          1   0.02515
-## 0.636363636363636         21   0.52817
-## 0.642857142857143          4   0.10060
-## 0.647058823529412          5   0.12575
-## 0.666666666666667        202   5.08048
-## 0.6875                     5   0.12575
-## 0.692307692307692          7   0.17606
-## 0.7                       46   1.15694
-## 0.705882352941177          4   0.10060
-## 0.714285714285714         38   0.95573
-## 0.727272727272727         29   0.72938
-## 0.733333333333333          6   0.15091
-## 0.75                     159   3.99899
-## 0.769230769230769         10   0.25151
-## 0.777777777777778         74   1.86117
-## 0.785714285714286          8   0.20121
-## 0.8                      125   3.14386
-## 0.8125                     1   0.02515
-## 0.818181818181818         20   0.50302
-## 0.823529411764706          3   0.07545
-## 0.833333333333333         59   1.48390
-## 0.846153846153846          3   0.07545
-## 0.857142857142857         38   0.95573
-## 0.866666666666667          7   0.17606
-## 0.875                     47   1.18209
-## 0.882352941176471          8   0.20121
-## 0.888888888888889         48   1.20724
-## 0.894736842105263          1   0.02515
-## 0.9                       50   1.25755
-## 0.909090909090909         16   0.40241
-## 0.916666666666667         15   0.37726
-## 0.923076923076923          4   0.10060
-## 0.928571428571429          9   0.22636
-## 0.933333333333333          8   0.20121
-## 0.9375                     5   0.12575
-## 0.941176470588235          8   0.20121
-## 1                        640  16.09658
-## Total                   3976 100.00000
-\end{verbatim}
-
-\begin{verbatim}
-## $ANOVA
-##        Effect DFn  DFd        SSn      SSd         F             p p<.05
-## 1 (Intercept)   1  567 1146.04761 171.5620 3787.6047 3.580669e-253     *
-## 2       scale   6 3402   92.90682 182.9607  287.9206 7.175910e-299     *
-##         ges
-## 1 0.7637413
-## 2 0.2076457
-## 
-## $`Mauchly's Test for Sphericity`
-##   Effect         W            p p<.05
-## 2  scale 0.4208255 6.425345e-91     *
-## 
-## $`Sphericity Corrections`
-##   Effect       GGe         p[GG] p[GG]<.05       HFe         p[HF] p[HF]<.05
-## 2  scale 0.7801204 6.574489e-234         * 0.7874087 4.617424e-236         *
-\end{verbatim}
 

### 2023-07-18 SIOP2024/SIOP2024convergence.Rmd
last bit

@@
 write.csv(tukeytest, "pairwisets.csv")
-psych::describe.by(analysis$value, analysis$scale)
+#psych::describe.by(analysis$value, analysis$scale)
 

### 2023-07-18 SIOP2024/SIOP2024convergence.tex
last bit

@@
 
-\begin{verbatim}
-## 
-##  Descriptive statistics by group 
-## group: Information
-##    vars   n mean   sd median trimmed  mad min max range  skew kurtosis   se
-## X1    1 568 0.62 0.38   0.67    0.65 0.49   0   1     1 -0.46    -1.27 0.02
-## ------------------------------------------------------------ 
-## group: Interact
-##    vars   n mean   sd median trimmed  mad min max range  skew kurtosis   se
-## X1    1 568 0.67 0.27   0.75     0.7 0.26   0   1     1 -0.83    -0.07 0.01
-## ------------------------------------------------------------ 
-## group: Interpersonal
-##    vars   n mean   sd median trimmed  mad min max range  skew kurtosis   se
-## X1    1 568 0.57 0.26    0.6    0.58 0.27   0   1     1 -0.36    -0.61 0.01
-## ------------------------------------------------------------ 
-## group: Mental
-##    vars   n mean   sd median trimmed  mad min max range  skew kurtosis   se
-## X1    1 568 0.71 0.29   0.78    0.75 0.33   0   1     1 -1.01     0.16 0.01
-## ------------------------------------------------------------ 
-## group: Output
-##    vars   n mean   sd median trimmed  mad min max range skew kurtosis   se
-## X1    1 568 0.48 0.37    0.5    0.48 0.49   0   1     1 0.07    -1.36 0.02
-## ------------------------------------------------------------ 
-## group: Physical
-##    vars   n mean   sd median trimmed  mad min max range skew kurtosis   se
-## X1    1 568 0.21 0.24   0.14    0.17 0.21   0   1     1 1.21     0.92 0.01
-## ------------------------------------------------------------ 
-## group: Structural
-##    vars   n mean   sd median trimmed  mad min max range skew kurtosis   se
-## X1    1 568  0.5 0.24    0.5     0.5 0.25   0   1     1 0.04    -0.62 0.01
-\end{verbatim}
-
 \hypertarget{resource-challenge-and-hindrance-associations}{%

### 2023-07-18 SIOP2024/SIOP2024_agreement.Rmd
Updating SIOP project

@@
 *RQ1*: Do people distinguish between challenge and hindrance stressors?
+#### Maybe do third moderator
+
+We also have ratings of "...the extent to which this characteristic is present in your job".
+Currently we're just taking a binary yes/no approach, but it does make sense to look for moderation based on *the degree to which the characteristic is present*.
+This is probably a better/more appropriate moderator than either of the above two...
 

### 2023-07-18 SIOP2024/SIOP2024convergence.Rmd
reference section
Updating SIOP project

@@
 abstract: |
- 568 workers rated job characteristics in terms of relevance as well as perceptions as challenges, hindrances and resources.
-We find strong associations between characteristics such that what is viewed as a "resource" is also very often considered a "challenge".
-This agreement was moderated by the nature of the job characteristic.
+ Using the Challenge-Hindrance Framework, 2 research questions were examined: are jobs with many resources also perceived to have many challenges, and 2) could that association be moderated by kind of job characteristic.
+A survey of 568 workers rated job characteristics in terms of relevance as well as perceptions as challenges, hindrances and resources using the common O\*NET classification of work activities and context.The findings point to high association between the number of resources and challenge demands employees experience, reasonable correspondence or agreement that a characteristic is a resource *and* challenge, and differences in this association by job characteristic category.
+More variability was observed when exploring associations between resources and hindrance stressors, and challenge/hindrance stressors.
 
@@
 There are a number of advantage to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.
+Here, we focus broadly on two research questions using these O\*NET items: 1) are jobs with many resources also perceived to have many challenges, and 2) could that association be moderated by kind of job characteristic (e.g., interacting with others vs.
+physical work characteristics)?
+A brief summary of the Challenge-hindrance Framework is presented prior to rationale for these specific questions.
 
@@
 
+We argue below that *perception* of something as a resource or demand matters.
 Although the word “stress” often carries a negative connotation, the "father" of the current concept, @selye1936syndrome, conceptualized stress much less pejoratively - rather thinking of it as a *response to change*.
@@
 
-*RQ1*: Do jobs with many resources also perceived to have many challenges?
+*RQ1*: Do employees who perceive many resources in their jobs also perceived many challenges?
 
@@
 
-*RQ2*: Is the association between challenge and resource characteristics moderated by type of characteristic?
-
-#### Maybe do third moderator
-
-We also have ratings of "...the extent to which this characteristic is present in your job".
-Currently we're just taking a binary yes/no approach, but it does make sense to look for moderation based on *the degree to which the characteristic is present*.
-This is probably a better/more appropriate moderator than either of the above two...
+*RQ2*: Is the association between resource and challenge characteristics moderated by type of characteristic?
 
@@
 
-The t-test between mean number of resources and hindrances suggests that respondents experienced more resources than hindrances, *t*(`r trechind$parameter`), = `r trechind$statistic`, *p* < .001, 95% CI = [`r trechind$conf.int[1]`, `r trechind$conf.int[2]`], *d* = `r drehi`.
-The t-test between mean number of resources and challenges suggests that respondents did not experience more resources than challenges, *t*(`r trech$parameter`), = `r trech$statistic`, *p* = .198, 95% CI = [`r trech$conf.int[1]`, `r trech$conf.int[2]`], *d* = `r drech`.
-The t-test between mean number of challenges and hindrances suggests that respondents experienced more challenges than hindrances, *t*(`r thich$parameter`), = `r thich$statistic`, *p* < .001, 95% CI = [`r thich$conf.int[1]`, `r thich$conf.int[2]`], *d* = `r dchhi`.
-
 ```{r percagree, fig.cap="Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance).", fig.height=10}
@@
 
-Research Question 1 explored whether jobs with many challenges have many resources.
-The total number of undifferentiated challenges and resources are positively related.
-Table \@ref(tab:cortab) shows a very high association between resources and challenges (*r* = .86).
-These associations, however, are only capturing the relationships between these demands and resources in *sheer volume*.
+Research Question 1 explored whether people who perceive many challenges in their work also report many resources.
+The results show that the total number of undifferentiated challenges and resources are positively related.
+In fact, table \@ref(tab:cortab) shows a very high association between resources and challenges (*r* = .86).
+This association, however, only captures the relationship between these demands and resources in *sheer volume*.
 That is, Table \@ref(tab:cortab) operationalized each variable as the sheer number of resources, hindrances, or challenges that a respondent indicated were present within their job.
-This correlational analysis simply implies that workers who experience more resources also perceive greater challenges.
-The associations between resources and hindrances (*r* = .23) and challenges and hindrances (*r* = .22) were also significantly positive with moderate magnitude associations, suggesting that some of this "sheer volume" may be capturing job complexity (that is, the more complex the job, the more characteristics are relevant, and therefore the more likely it is to have *more* challenges as well as *more* hindrances as well as *more* resources).
+This correlational analysis *does* imply that workers who experience more resources also perceive greater challenges.
+Although not explicitly part of the above research question, we also explored the associations between resources and hindrances (*r* = .23) and challenges and hindrances (*r* = .22), which were also significantly positive with moderate in magnitude, suggesting that some of this "sheer volume" may be capturing job complexity (that is, the more complex the job, the more characteristics are relevant, and therefore the more likely it is to have *more* challenges as well as *more* hindrances as well as *more* resources).
 Although we did not address job complexity as a moderator in the current paper, we do plan to do so in future investigations.
@@
 
-## Convergence (same characteristic)
+We further explored whether the mean number of resources, challenge- and hindrance demands were signficantly different from one another.
+Mirroring the results above, a paired-samples t-test between mean number of resources and challenges suggests that respondents did not experience more resources than challenges, *t*(`r trech$parameter`), = `r trech$statistic`, *p* = .198, 95% CI = [`r trech$conf.int[1]`, `r trech$conf.int[2]`], *d* = `r drech`.
+However, there was a significant difference between mean number of resources and hindrances, suggesting respondents experienced more resources than hindrances, *t*(`r trechind$parameter`), = `r trechind$statistic`, *p* < .001, 95% CI = [`r trechind$conf.int[1]`, `r trechind$conf.int[2]`], *d* = `r drehi`, and between mean number of challenges and hindrances suggests that respondents experienced more challenges than hindrances, *t*(`r thich$parameter`), = `r thich$statistic`, *p* < .001, 95% CI = [`r thich$conf.int[1]`, `r thich$conf.int[2]`], *d* = `r dchhi`.
+In sum, these findings highlight a pattern in which those who perceive or experience challenges in their work also perceive more resources, the implications of which will be explored further in the discussion.
 
-We next looked for convergence of perception at the level of each individual job characteristic.
+## Correspondence between Individual Job Characteristic Perceptions
+
+While interesting, we note above that the initial analyses explore this question through a very broad "sheer volume" lens.
+We next looked for convergence of perception at the level of each *individual job characteristic*.
 Here, we calculated the *percent of affirmative correspondence* between individual characteristic perceptions.
@@
 
-### Moderating effects
+## Is the association between resource and challenge characteristics moderated by type of characteristic?
 
->Note. This is all off because the "scales" have different numbers of items, so it's not appropriate to use sums as scale scores. Maybe revisit with means.
-
-Figure \@ref(fig:recchall) explores the possibility of moderation by *type of characteristic rated* for the resource-challenge convergence.
-Here we categorized each characteristic by its O\*NET "scale" (one of seven), and the graph shows greater consistency across certain characteristics (for example, *Mental Processes* or *Interacting with Others*) and less convergence across other *types* of job activities (for example, *Physical* characteristics).
-A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of $F_{(6, 3,402)}$ = 613.5, *p* < .001, $\eta^2_{p}$ = `r round(repmeas$ANOVA[2,9],2)` (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001.
+Figure \@ref(fig:recchall) explores the possibility of moderation by *type of characteristic rated* for the resource-challenge convergence (RQ2).
+Here, we categorized each characteristic by its O\*NET "scale" (one of seven), and the graph shows greater consistency across certain characteristics (for example, *Mental Processes* or *Interacting with Others*) and less convergence across other *types* of job activities (for example, *Physical* characteristics).
+A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of $F_{(6, 3,402)}$ = 613.5, *p* < .001, $\eta^2_{p}$ = `r round(repmeas$ANOVA[2,9],2)` (the subjects' effect was $F_{(567, 3402)}$ = 6.13, *p* < .001).
 The only contrast not broaching statistical significance via Bonferonni-corrected pairwise t-tests was Work Output vs.
@@
 The major goal of this paper was to further explore the relationships among perceptions of job characteristics as challenge demands, hindrance demands, and resources.
-Our findings perhaps most notably highlight the importance of dissociating the *nature* of job demands.
-
-IMPLICATION: Distinguishing between different kinds of work demands has implications for not only the employees themselves, but also teams they may be a part of, managers and the like.
-This is because demands appraised as a challenge promote mastery, personal growth, and future gains.
-Those appraised as a hindrance, in contrast, inhibit growth, learning and goal achievement.
-Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes [e.g., @cavanaugh2000empirical].
+Our findings suggest that there is an association between the number of resources and challenges employees perceive, and that this association does appear to be moderated by type of job characteristic.
+The results highlight the importance of dissociating the *nature* of job demands, as we did not see the same patterns across challenge and hindrance demands.
 
 Similar to the eustress/distress distinction [e.g., @selye1974stress], it would seem as though demands should perhaps be thought of in a valenced manner (e.g., is it a "good" demand or a "bad" demand).
-We did not probe for dependent variable associations, however, @cavanaugh2000empirical found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite patterns in a sample of managers.
-We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (@crawford2010linking).
-@podsakoff2007differential's meta-analysis also found that challenge demands were positively related to job satisfaction and organizational commitment and negatively related to both turnover intentions and actual turnover, while hindrance demands again produced the opposite patterns of relationship.
-Although we did not probe for outcome associations, the current study does suggest that hindrance demands also operate in a manner different than challenge demands with regard to their association with resource appraisals.
+Distinguishing between different kinds of work demands has implications for not only the employees themselves, but also teams they may be a part of, managers and the like.
+This is because demands appraised as a challenge promote mastery, personal growth, and future gains.
+Moreover, it was more likely that employees would also perceive these characterstics as *resources* within their jobs.
 
@@
 
+## Limitations & Future Directions  
+The findings above point to a number of additional avenues for this line of research.
+While our study focused on activity and content O\*NET statements, we were practically limited in the number of items that could be administered.
+As such, it would be of value to explore other, additional job characteristics, particularly in the relational realm (e.g., the "human" resources that are a major component of most work such as interacting with coworkers, one's relationship with a supervisor).
+Another important direction to consider will be that of job type.
+We explored one potential moderator - that of job characteristic category, but it is also quite possible that those in certain industries experience some job characteristics with more frequency and would naturally have more resources/challenges, for instance.
+Individual differences in person-job fit may also prove to be a useful addition, as would outcomes associated with resources and demands at work (e.g., job satisfaction, engagement, intent to turnover).
+
+## Conclusion  
+This study contributes to our understanding of the experience of different characteristics of work using the common O\*NET classification of work activities and context.
+The findings point to high association between the number of resources and challenge demands employees experience, reasonable correspondence or agreement that a characteristic is a resource *and* challenge, and differences in this association by job characteristic category.
+More variability was observed when exploring associations between resources and hindrance stressors, and challenge/hindrance stressors.
+The results speak strongly to the importance of perceptions of resources and demands at work given existing literature on the outcomes associated with such appraisals.
+
 # References

### 2023-07-18 SIOP2024/SIOP2024convergence.tex
reference section
Updating SIOP project

@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 \abstract{%
-568 workers rated job characteristics in terms of relevance as well as perceptions as challenges, hindrances and resources.
-We find strong associations between characteristics such that what is viewed as a ``resource'' is also very often considered a ``challenge''.
-This agreement was moderated by the nature of the job characteristic.
+Using the Challenge-Hindrance Framework, 2 research questions were examined: are jobs with many resources also perceived to have many challenges, and 2) could that association be moderated by kind of job characteristic.
+A survey of 568 workers rated job characteristics in terms of relevance as well as perceptions as challenges, hindrances and resources using the common O*NET classification of work activities and context.The findings point to high association between the number of resources and challenge demands employees experience, reasonable correspondence or agreement that a characteristic is a resource \emph{and} challenge, and differences in this association by job characteristic category.
+More variability was observed when exploring associations between resources and hindrance stressors, and challenge/hindrance stressors.
 }
@@
 There are a number of advantage to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.
+Here, we focus broadly on two research questions using these O*NET items: 1) are jobs with many resources also perceived to have many challenges, and 2) could that association be moderated by kind of job characteristic (e.g., interacting with others vs.~physical work characteristics)?
+A brief summary of the Challenge-hindrance Framework is presented prior to rationale for these specific questions.
 
@@
 
+We argue below that \emph{perception} of something as a resource or demand matters.
 Although the word ``stress'' often carries a negative connotation, the ``father'' of the current concept, Selye (1936), conceptualized stress much less pejoratively - rather thinking of it as a \emph{response to change}.
@@
 
-\emph{RQ1}: Do jobs with many resources also perceived to have many challenges?
+\emph{RQ1}: Do employees who perceive many resources in their jobs also perceived many challenges?
 
@@
 
-\emph{RQ2}: Is the association between challenge and resource characteristics moderated by type of characteristic?
-
-\hypertarget{maybe-do-third-moderator}{%
-\paragraph{Maybe do third moderator}\label{maybe-do-third-moderator}}
-
-We also have ratings of ``\ldots the extent to which this characteristic is present in your job''.
-Currently we're just taking a binary yes/no approach, but it does make sense to look for moderation based on \emph{the degree to which the characteristic is present}.
-This is probably a better/more appropriate moderator than either of the above two\ldots{}
+\emph{RQ2}: Is the association between resource and challenge characteristics moderated by type of characteristic?
 
@@
 
-The t-test between mean number of resources and hindrances suggests that respondents experienced more resources than hindrances, \emph{t}(567), = 32.67, \emph{p} \textless{} .001, 95\% CI = {[}21.55, 24.31{]}, \emph{d} = 1.71.
-The t-test between mean number of resources and challenges suggests that respondents did not experience more resources than challenges, \emph{t}(567), = 1.29, \emph{p} = .198, 95\% CI = {[}-0.20, 0.96{]}, \emph{d} = 0.03.
-The t-test between mean number of challenges and hindrances suggests that respondents experienced more challenges than hindrances, \emph{t}(567), = -31.58, \emph{p} \textless{} .001, 95\% CI = {[}-23.95, -21.15{]}, \emph{d} = 1.65.
-
 \begin{figure}
@@
 
-Research Question 1 explored whether jobs with many challenges have many resources.
-The total number of undifferentiated challenges and resources are positively related.
-Table \ref{tab:cortab} shows a very high association between resources and challenges (\emph{r} = .86).
-These associations, however, are only capturing the relationships between these demands and resources in \emph{sheer volume}.
+Research Question 1 explored whether people who perceive many challenges in their work also report many resources.
+The results show that the total number of undifferentiated challenges and resources are positively related.
+In fact, table \ref{tab:cortab} shows a very high association between resources and challenges (\emph{r} = .86).
+This association, however, only captures the relationship between these demands and resources in \emph{sheer volume}.
 That is, Table \ref{tab:cortab} operationalized each variable as the sheer number of resources, hindrances, or challenges that a respondent indicated were present within their job.
-This correlational analysis simply implies that workers who experience more resources also perceive greater challenges.
-The associations between resources and hindrances (\emph{r} = .23) and challenges and hindrances (\emph{r} = .22) were also significantly positive with moderate magnitude associations, suggesting that some of this ``sheer volume'' may be capturing job complexity (that is, the more complex the job, the more characteristics are relevant, and therefore the more likely it is to have \emph{more} challenges as well as \emph{more} hindrances as well as \emph{more} resources).
+This correlational analysis \emph{does} imply that workers who experience more resources also perceive greater challenges.
+Although not explicitly part of the above research question, we also explored the associations between resources and hindrances (\emph{r} = .23) and challenges and hindrances (\emph{r} = .22), which were also significantly positive with moderate in magnitude, suggesting that some of this ``sheer volume'' may be capturing job complexity (that is, the more complex the job, the more characteristics are relevant, and therefore the more likely it is to have \emph{more} challenges as well as \emph{more} hindrances as well as \emph{more} resources).
 Although we did not address job complexity as a moderator in the current paper, we do plan to do so in future investigations.
@@
 
-\hypertarget{convergence-same-characteristic}{%
-\subsection{Convergence (same characteristic)}\label{convergence-same-characteristic}}
+We further explored whether the mean number of resources, challenge- and hindrance demands were signficantly different from one another.
+Mirroring the results above, a paired-samples t-test between mean number of resources and challenges suggests that respondents did not experience more resources than challenges, \emph{t}(567), = 1.29, \emph{p} = .198, 95\% CI = {[}-0.20, 0.96{]}, \emph{d} = 0.03.
+However, there was a significant difference between mean number of resources and hindrances, suggesting respondents experienced more resources than hindrances, \emph{t}(567), = 32.67, \emph{p} \textless{} .001, 95\% CI = {[}21.55, 24.31{]}, \emph{d} = 1.71, and between mean number of challenges and hindrances suggests that respondents experienced more challenges than hindrances, \emph{t}(567), = -31.58, \emph{p} \textless{} .001, 95\% CI = {[}-23.95, -21.15{]}, \emph{d} = 1.65.
+In sum, these findings highlight a pattern in which those who perceive or experience challenges in their work also perceive more resources, the implications of which will be explored further in the discussion.
 
-We next looked for convergence of perception at the level of each individual job characteristic.
+\hypertarget{correspondence-between-individual-job-characteristic-perceptions}{%
+\subsection{Correspondence between Individual Job Characteristic Perceptions}\label{correspondence-between-individual-job-characteristic-perceptions}}
+
+While interesting, we note above that the initial analyses explore this question through a very broad ``sheer volume'' lens.
+We next looked for convergence of perception at the level of each \emph{individual job characteristic}.
 Here, we calculated the \emph{percent of affirmative correspondence} between individual characteristic perceptions.
@@
 
-\hypertarget{moderating-effects}{%
-\subsubsection{Moderating effects}\label{moderating-effects}}
+\hypertarget{is-the-association-between-resource-and-challenge-characteristics-moderated-by-type-of-characteristic}{%
+\subsection{Is the association between resource and challenge characteristics moderated by type of characteristic?}\label{is-the-association-between-resource-and-challenge-characteristics-moderated-by-type-of-characteristic}}
 
-\begin{quote}
-Note. This is all off because the ``scales'' have different numbers of items, so it's not appropriate to use sums as scale scores. Maybe revisit with means.
-\end{quote}
-
-Figure \ref{fig:recchall} explores the possibility of moderation by \emph{type of characteristic rated} for the resource-challenge convergence.
-Here we categorized each characteristic by its O*NET ``scale'' (one of seven), and the graph shows greater consistency across certain characteristics (for example, \emph{Mental Processes} or \emph{Interacting with Others}) and less convergence across other \emph{types} of job activities (for example, \emph{Physical} characteristics).
-A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of \(F_{(6, 3,402)}\) = 613.5, \emph{p} \textless{} .001, \(\eta^2_{p}\) = 0.21 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001.
+Figure \ref{fig:recchall} explores the possibility of moderation by \emph{type of characteristic rated} for the resource-challenge convergence (RQ2).
+Here, we categorized each characteristic by its O*NET ``scale'' (one of seven), and the graph shows greater consistency across certain characteristics (for example, \emph{Mental Processes} or \emph{Interacting with Others}) and less convergence across other \emph{types} of job activities (for example, \emph{Physical} characteristics).
+A repeated-measures ANOVA retaining these scales as 7 different levels of a within-subjects' independent variables yielded a treatment effect of \(F_{(6, 3,402)}\) = 613.5, \emph{p} \textless{} .001, \(\eta^2_{p}\) = 0.21 (the subjects' effect was \(F_{(567, 3402)}\) = 6.13, \emph{p} \textless{} .001).
 The only contrast not broaching statistical significance via Bonferonni-corrected pairwise t-tests was Work Output vs.~Structural job characteristics (\emph{t} = -1.10).
@@
 The major goal of this paper was to further explore the relationships among perceptions of job characteristics as challenge demands, hindrance demands, and resources.
-Our findings perhaps most notably highlight the importance of dissociating the \emph{nature} of job demands.
-
-IMPLICATION: Distinguishing between different kinds of work demands has implications for not only the employees themselves, but also teams they may be a part of, managers and the like.
-This is because demands appraised as a challenge promote mastery, personal growth, and future gains.
-Those appraised as a hindrance, in contrast, inhibit growth, learning and goal achievement.
-Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes (e.g., Cavanaugh et al., 2000).
+Our findings suggest that there is an association between the number of resources and challenges employees perceive, and that this association does appear to be moderated by type of job characteristic.
+The results highlight the importance of dissociating the \emph{nature} of job demands, as we did not see the same patterns across challenge and hindrance demands.
 
 Similar to the eustress/distress distinction (e.g., Selye, 1974), it would seem as though demands should perhaps be thought of in a valenced manner (e.g., is it a ``good'' demand or a ``bad'' demand).
-We did not probe for dependent variable associations, however, Cavanaugh et al.
-(2000) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite patterns in a sample of managers.
-We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford et al.
-(2010)).
-Podsakoff et al.
-(2007)'s meta-analysis also found that challenge demands were positively related to job satisfaction and organizational commitment and negatively related to both turnover intentions and actual turnover, while hindrance demands again produced the opposite patterns of relationship.
-Although we did not probe for outcome associations, the current study does suggest that hindrance demands also operate in a manner different than challenge demands with regard to their association with resource appraisals.
+Distinguishing between different kinds of work demands has implications for not only the employees themselves, but also teams they may be a part of, managers and the like.
+This is because demands appraised as a challenge promote mastery, personal growth, and future gains.
+Moreover, it was more likely that employees would also perceive these characterstics as \emph{resources} within their jobs.
 
@@
 We suspect that there are other moderators that help explain this association/ disassociation between challenges and resources, and would like to incorporate variables such as a respondents' personality in future investigations.
+
+\hypertarget{limitations-future-directions}{%
+\subsection{Limitations \& Future Directions}\label{limitations-future-directions}}
+
+The findings above point to a number of additional avenues for this line of research.
+While our study focused on activity and content O*NET statements, we were practically limited in the number of items that could be administered.
+As such, it would be of value to explore other, additional job characteristics, particularly in the relational realm (e.g., the ``human'' resources that are a major component of most work such as interacting with coworkers, one's relationship with a supervisor).
+Another important direction to consider will be that of job type.
+We explored one potential moderator - that of job characteristic category, but it is also quite possible that those in certain industries experience some job characteristics with more frequency and would naturally have more resources/challenges, for instance.
+Individual differences in person-job fit may also prove to be a useful addition, as would outcomes associated with resources and demands at work (e.g., job satisfaction, engagement, intent to turnover).
+
+\hypertarget{conclusion}{%
+\subsection{Conclusion}\label{conclusion}}
+
+This study contributes to our understanding of the experience of different characteristics of work using the common O*NET classification of work activities and context.
+The findings point to high association between the number of resources and challenge demands employees experience, reasonable correspondence or agreement that a characteristic is a resource \emph{and} challenge, and differences in this association by job characteristic category.
+More variability was observed when exploring associations between resources and hindrance stressors, and challenge/hindrance stressors.
+The results speak strongly to the importance of perceptions of resources and demands at work given existing literature on the outcomes associated with such appraisals.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-crawford2010linking}{}}%
-Crawford, E.
-R., LePine, J.
-A., \& Rich, B.
-L.
-(2010).
-Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test.
-\emph{Journal of Applied Psychology}, \emph{95}(5), 834.
-
 \leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-podsakoff2007differential}{}}%
-Podsakoff, N.
-P., LePine, J.
-A., \& LePine, M.
-A.
-(2007).
-Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis.
-\emph{Journal of Applied Psychology}, \emph{92}(2), 438.
-
 \leavevmode\vadjust pre{\hypertarget{ref-selye1936syndrome}{}}%

### 2023-07-25 SIOP2024/SIOP2024convergence.Rmd
updating siop project - need to work on intro

@@
 # References
+
+In terms of convergence of resource and challenge appraisals, there was quite a bit of variability (e.g., Figure \@ref(fig:percagree)), but that variability was partially explained by the nature of the characteristic being evaluated (e.g., Figure \@ref(fig:recchall)).
+Physical job characteristics such as, for example, the amount of "time spent bending or twisting the body" may be much more likely to be appraised as a challenging demand (but not a resource).
+Other *types* of job requirements, however, such as a mental process like, "scheduling work and activities" might reasonably be expected to exhibit greater convergence.
+We suspect that there are other moderators that help explain this association/ disassociation between challenges and resources, and would like to incorporate variables such as a respondents' personality in future investigations.
+
+# References
+
+Cut stuff:
+
+Similar to the eustress/distress distinction [e.g., @selye1974stress], it would seem as though demands should perhaps be thought of in a valenced manner (e.g., is it a "good" demand or a "bad" demand).
+We did not probe for dependent variable associations, however, @cavanaugh2000empirical found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite patterns in a sample of managers.
+We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (@crawford2010linking).
+@podsakoff2007differential's meta-analysis also found that challenge demands were positively related to job satisfaction and organizational commitment and negatively related to both turnover intentions and actual turnover, while hindrance demands again produced the opposite patterns of relationship.
+Although we did not probe for outcome associations, the current study does suggest that hindrance demands also operate in a manner different than challenge demands with regard to their association with resource appraisals.

### 2023-07-25 SIOP2024/SIOP2024convergence.tex
updating siop project - need to work on intro

@@
 \hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
+\section{References}\label{references}}
+
+In terms of convergence of resource and challenge appraisals, there was quite a bit of variability (e.g., Figure \ref{fig:percagree}), but that variability was partially explained by the nature of the characteristic being evaluated (e.g., Figure \ref{fig:recchall}).
+Physical job characteristics such as, for example, the amount of ``time spent bending or twisting the body'' may be much more likely to be appraised as a challenging demand (but not a resource).
+Other \emph{types} of job requirements, however, such as a mental process like, ``scheduling work and activities'' might reasonably be expected to exhibit greater convergence.
+We suspect that there are other moderators that help explain this association/ disassociation between challenges and resources, and would like to incorporate variables such as a respondents' personality in future investigations.
+
+\hypertarget{references-1}{%
+\section{References}\label{references-1}}
+
+Cut stuff:
+
+Similar to the eustress/distress distinction (e.g., Selye, 1974), it would seem as though demands should perhaps be thought of in a valenced manner (e.g., is it a ``good'' demand or a ``bad'' demand).
+We did not probe for dependent variable associations, however, Cavanaugh et al.
+(2000) found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite patterns in a sample of managers.
+We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with engagement (Crawford et al.
+(2010)).
+Podsakoff et al.
+(2007)'s meta-analysis also found that challenge demands were positively related to job satisfaction and organizational commitment and negatively related to both turnover intentions and actual turnover, while hindrance demands again produced the opposite patterns of relationship.
+Although we did not probe for outcome associations, the current study does suggest that hindrance demands also operate in a manner different than challenge demands with regard to their association with resource appraisals.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-crawford2010linking}{}}%
+Crawford, E.
+R., LePine, J.
+A., \& Rich, B.
+L.
+(2010).
+Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test.
+\emph{Journal of Applied Psychology}, \emph{95}(5), 834.
+
 \leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-podsakoff2007differential}{}}%
+Podsakoff, N.
+P., LePine, J.
+A., \& LePine, M.
+A.
+(2007).
+Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis.
+\emph{Journal of Applied Psychology}, \emph{92}(2), 438.
+
 \leavevmode\vadjust pre{\hypertarget{ref-selye1936syndrome}{}}%

### 2023-07-27 SIOP2024/SIOP2024_agreement.tex
Updated SIOP intro

--- 2022-11-11 copy-of-SIOP2023convergence.tex
@@
 
-\begin{verbatim}
-## Warning: package 'tinylabels' was built under R version 4.1.3
-\end{verbatim}
+The Occupational Information Network (O*NET; onetonline.org) contains a reasonably comprehensive description of occupations (Peterson et al., 2001) which subject matter experts inform via surveys.
+We utilize a set of O*Net job context and activity statements contained in these surveys to explore a series of research questions about how people perceive resources, challenges, and hindrances within their jobs.
+There are a number of advantage to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.
 
-An abundance of research applying the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker \& Demerouti, 2017) underscores the importance of job characteristics on the experience of work.
-Resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
-Demands, on the other hand, include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure, Demerouti et al., 2001).
-These two categories of outcomes (e.g., ``good'' and ``bad'') are thought to occur via one of two different mechanisms: motivational (resulting from resources) or health impairment (resulting from demands, Bakker \& Demerouti, 2014).
-Much of our existing research on the JD-R assumes that certain characteristics (for example, autonomy) are resources and others (for example, time constraints) are generally considered demands.
-This study searches instead for circumstances that provide exception to this mutually exclusive dichotomy of job characteristics.
+\hypertarget{not-all-stressors-are-equal-the-challenge-hindrance-framework}{%
+\subsection{Not all Stressors are Equal: The Challenge-hindrance Framework}\label{not-all-stressors-are-equal-the-challenge-hindrance-framework}}
 
-\begin{figure}
-\centering
-\includegraphics{copy-of-SIOP2023convergence_files/figure-latex/uhoh-1.pdf}
-\caption{\label{fig:uhoh}Maybe put a hold on this paper as wording of resource and challenge seems very similar}
-\end{figure}
-
-see Figure \ref{fig:uhoh}
-
-\hypertarget{could-a-work-demand-be-appraised-positively-the-challenge-hindrance-framework}{%
-\subsection{Could a Work Demand be Appraised ``Positively''?: The Challenge-Hindrance Framework}\label{could-a-work-demand-be-appraised-positively-the-challenge-hindrance-framework}}
-
-Although the word ``stress'' often carries a negative connotation, the ``father'' of the current concept, Selye (1936), conceptualized stress much less perjoratively - rather thinking of it as a \emph{response to change}.
+Although the word ``stress'' often carries a negative connotation, the ``father'' of the current concept, Selye (1936), conceptualized stress much less pejoratively - rather thinking of it as a \emph{response to change}.
 For instance, consider the different reactions two different employees may have to being nominated to give a speech at an upcoming company event.
@@
 However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
-Selye the physician would likely have labeled the two responses as subjective manifestations of ``Distress'', and ``Eustress'' (Selye, 1974).
-In modern I-O Psychology parlance (and more consistent with the JD-R framework), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a \emph{challenge} while the other would appraise the demand as a \emph{hindrance} (Cavanaugh et al., 2000).
+Selye the physician would likely have labeled the two responses as subjective manifestations of ``distress'', and ``eustress'' (Selye, 1974).
+In modern I-O Psychology parlance (and more consistent with the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker \& Demerouti, 2017)), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a \emph{challenge} while the other would appraise the demand as a \emph{hindrance} (Cavanaugh et al., 2000).
 According to Cavanaugh et al.
@@
 (2011) also considered three common work characteristics including workload, role ambiguity, and role conflict.
-Interestingly, they found that while each could be identified \emph{primarily} as a challenge or hindrance, employees could also appraise that a characteristic is simulataneously both a challenge and hindrance.
+Interestingly, they found that while each could be identified \emph{primarily} as a challenge or hindrance, employees could also appraise that a characteristic is simultaneously both a challenge and hindrance.
+However, this list of demands (workload, role ambiguity, and role conflict) is somewhat narrow.
+Using a very wide range of O*Net job characteristics regarding job context and activities, we explore this question:
 
-Although it is cleaner to be able to categorize job characteristics as \emph{either} a demand or a resource, the above research suggests that an individual's (perhaps unique) appraisal is at least occasionally an important consideration.
-It is quite possible that one person experiences high work pressure (commonly cited as a demand in the literature) as a hindrance stressor and thus experiences strain, and another thrives in a fast-paced pressured role and would thus find the environment motivating.
+\emph{RQ1 is a good idea for A DIFFERENT PAPER. Do ICC(1,1)}
+\emph{RQ1}: Do people distinguish between challenge and hindrance stressors?
+\#\#\#\# Maybe do third moderator
 
-\hypertarget{current-study-and-hypotheses}{%
-\subsection{Current Study and Hypotheses}\label{current-study-and-hypotheses}}
-
-We explored the extent to which perceptions of job characteristics converge upon being uniquely or concurrently experienced as resources and demands (in the form of challenges and hindrances).
-Our supposition is that respondents may consider the same objective job characteristic to be both challenging and resourceful - if not at the same moment, at least at different points in time or under differing circumstances.
-
-\hypertarget{value-of-consulting-onet.}{%
-\subsubsection{Value of consulting O*Net.}\label{value-of-consulting-onet.}}
-
-The Occupational Information Network (O*NET; onetonline.org) contains a fairly comprehensive description of occupations (Peterson et al., 2001).
-This widely accessed database houses hundreds of standardized and occupation-specific descriptors for the majority of occupations within the United States, and these descriptions are frequently updated.
-These data, and the tools provided for public consumption on the website (e.g., Career Exploration Tools, ``My Next Move'', Toolkit for Business) are frequently used by counselors, students, human resources departments, and researchers to assist interested or curious job-seekers discover the nature of work as well as skills and training typically required for different occupations.
-It is also often useful to employers by providing them with information that may be helpful in a job analysis context.
-
-We asked our respondents to select job characteristics that were relevent to them from the broader comprehensive O*Net list.
-We then asked these individuals to also rate those (relevant) characteristics in terms of their status as hindrances, challenges, and resources.
-Utilizing the job demands-resources theory and the challenge-hindrance framework, we propose that job characteristics appraised as ``challenge demands'' (i.e., promote mastery, personal growth, and future gains) may also be viewed as job resources.
-
-\emph{Hypothesis 1}: Characteristics perceived as challenges are also commonly viewed as resources.
-
-Although the same job characteristic may be percieved as both a challenge and a resource, it is also likely that some characteristics are less likely to be viewed as mutually complementary as others.
-For example, a physically strenuous job requirement such as ``carrying heavy objects'' would be less likely to be viewed both as a challenge and a resource whereas a structural characteristic such as ``negotiating work schedules'' may very well be viewed (likely in different circumstances) to be both a control-oriented resource as well as a challenge.
-O*Net has different levels of abstraction with regard to the nature of job characteristic.
-We will be exploring a mid-level abstraction with seven different characteristic ``scales''.
-
-\emph{Hypothesis 2}: The association between challenging and resourceful characteristics is moderated by type of characteristic.
+We also have ratings of ``\ldots the extent to which this characteristic is present in your job''.
+Currently we're just taking a binary yes/no approach, but it does make sense to look for moderation based on \emph{the degree to which the characteristic is present}.
+This is probably a better/more appropriate moderator than either of the above two\ldots{}
 
@@
 To capture an effectively exhaustive list of characteristics that apply to, theoretically, \emph{every} possible job, we consult the unifying framework of O*Net.
-
-\hypertarget{materials}{%
-\subsection{Materials}\label{materials}}
-
-Our survey was informed by 98 statements taken from job characteristic descriptors located within O*Net's classification of ``work activities'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'' groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
-
-The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task.
-For example, the descriptor for ``level of competition'', which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems.
-We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
-It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.
-
-Subsequent to providing ratings of whether or not each of the 98 O*Net characteristics were relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) .
-.
-.
-this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) .
-.
-.
-this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) .
-.
-.
-this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.
-The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
 
@@
 Gender was captured via a free-field gender identity category, although the sample predominantly self-identified as female (52.6\%) or male (46.8\%).
+
+\hypertarget{materials}{%
+\subsection{Materials}\label{materials}}
+
+Our survey was informed by 98 statements taken from job characteristic descriptors located within O*Net's classification of ``work activities'': 1) Information Input (5 statements), 2) Interacting with Others (17 statements), 3) Mental Processes (10 statements), and 4) Work Output (9 statements) and ``work context'' groupings: 1) Interpersonal Relationships (14 statements), 2) Physical Work Conditions (30 statements), and 3) Structural Job Characteristics (13 statements).
+
+The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task.
+For example, the descriptor for ``level of competition'', which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems.
+We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale.
+It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.
+
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
+
+Following IRB approval, respondents were recruited through Prolific.
+After providing consent, respondents provided ratings of whether or not each of the 98 O*Net characteristics were relevant for the respondent's work.
+Subsequently, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of perception of resource, challenge, or hindrance.
+The total number of items on the survey was less than 392 (98 characteristics x 4 administrations - the first for relevance and the remaining 3 for resources, challenges, and hindrances) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
+Furthermore, not every respondent indicated that the same characteristics were relevant to them, therefore each respondent had a unique set of responses.
 Participants were compensated for their participation in this study in the amount of six dollars through Prolific.
@@
 
-\begin{figure}
-\centering
-\includegraphics{copy-of-SIOP2023convergence_files/figure-latex/percagree-1.pdf}
-\caption{\label{fig:percagree}Percent convergence (characteristic rated consistently as, for example, both a resource and a hindrance).}
-\end{figure}
-
-\hypertarget{convergence-same-characteristic.}{%
-\subsection{Convergence (same characteristic).}\label{convergence-same-characteristic.}}
+\includegraphics{SIOP2024_agreement_files/figure-latex/percagree-1.pdf}
+\#\# Convergence (same characteristic).
 
@@
 \centering
-\includegraphics{copy-of-SIOP2023convergence_files/figure-latex/recchall-1.pdf}
+\includegraphics{SIOP2024_agreement_files/figure-latex/recchall-1.pdf}
 \caption{\label{fig:recchall}Resource and challenge agreement across ONet characteristic groupings (e.g., scales).}
@@
 \centering
-\includegraphics{copy-of-SIOP2023convergence_files/figure-latex/workcat-1.pdf}
+\includegraphics{SIOP2024_agreement_files/figure-latex/workcat-1.pdf}
 \caption{\label{fig:workcat}Percent agreement (resource and challenge) across O\emph{Net occupational categories (previous was across 84 O/}Net items - this is across 568 individual workers).}
@@
 The major goal of this paper was to further explore the relationships among perceptions of job characteristics as challenge demands, hindrance demands, and resources.
-Our findings perhaps most noteably highlight the importance of dissociating the \emph{nature} of job demands.
+Our findings perhaps most notably highlight the importance of dissociating the \emph{nature} of job demands.
+
+IMPLICATION: Distinguishing between different kinds of work demands has implications for not only the employees themselves, but also teams they may be a part of, managers and the like.
+This is because demands appraised as a challenge promote mastery, personal growth, and future gains.
+Those appraised as a hindrance, in contrast, inhibit growth, learning and goal achievement.
+Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes (e.g., Cavanaugh et al., 2000).
+
 Similar to the eustress/distress distinction (e.g., Selye, 1974), it would seem as though demands should perhaps be thought of in a valenced manner (e.g., is it a ``good'' demand or a ``bad'' demand).
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
-Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
-
 \leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%

### 2023-07-27 SIOP2024/SIOP2024convergence.Rmd
Updated SIOP intro

--- 2023-07-18 SIOP2024/SIOP2024convergence.Rmd
@@
 ---
-title             : "Demanding resources: Converging perceptions of challenge and resource characteristics"
+title             : "Demanding Resources: Converging Perceptions of Challenge and Resource Characteristics"
 shorttitle        : "Demanding Resources"
@@
 
-authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+#authornote: |
+#  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
 
-  Enter author note here.
+#  Enter author note here.
 
@@
 
-keywords          : "keywords"
-wordcount         : "X"
+#keywords          : "keywords"
+#wordcount         : "X"
 
@@
 The Occupational Information Network (O\*NET; onetonline.org) contains a reasonably comprehensive description of occupations [@peterson2001understanding] which subject matter experts inform via surveys.
-We utilize a set of O\*NET job context and activity statements contained in these surveys to explore a series of research questions about how people perceive resources, challenges, and hindrances within their jobs.
-There are a number of advantage to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.
-Here, we focus broadly on two research questions using these O\*NET items: 1) are jobs with many resources also perceived to have many challenges, and 2) could that association be moderated by kind of job characteristic (e.g., interacting with others vs.
+In the current study, we utilize a set of O\*NET job context and activity statements to explore two questions about how people perceive resources, challenges, and hindrances within their jobs.
+^[There are a number of advantages to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.] Here, we focus broadly on two research questions using these O\*NET items: 1) are jobs with many resources also perceived to have many challenges, and 2) could that association be moderated by kind of job characteristic (e.g., interacting with others vs.
 physical work characteristics)?
-A brief summary of the Challenge-hindrance Framework is presented prior to rationale for these specific questions.
-
-## Not all Stressors are Equal: The Challenge-hindrance Framework
+The basis for these questions comes out the stress literature [e.g., @lazarus1984stress].
 
@@
 Selye the physician would likely have labeled the two responses as subjective manifestations of "distress", and "eustress" [@selye1974stress].
-In modern I-O Psychology parlance (and more consistent with the job demands-resources model [@demerouti2001job] and job demands-resources theory [@bakker2017job]), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a *challenge* while the other would appraise the demand as a *hindrance* [@cavanaugh2000empirical].
+
+## Not all Stressors are Equal: The Challenge-hindrance Framework
+
+In modern I-O psychology parlance (and more consistent with the job demands-resources model [@demerouti2001job] and job demands-resources theory [@bakker2017job]), the two workers above would both be characterized as appraising the speaking opportunity as a job demand.
+However, as noted above, demands/stressors are subjective.
+Cavanaugh's (2000) challenge-hindrance stressor framework speaks directly to this reality, and suggests that the way we understand reactions to stressors requires consideration of how people *feel* about a given stressor.
+One of our above employees would be appraising the demand as a *challenge* while the other would appraise the demand as a *hindrance* [@cavanaugh2000empirical].
 According to @cavanaugh2000empirical, challenge demands promote mastery, personal growth, and future gains.
-Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
+Challenge stressors should lead to coping strategies that facilitate achievement and motivation [e.g., @kim2020thriving].
+Hindrance demands, in contrast, inhibit growth, learning and goal achievement (e.g., perception of role conflict, workplace politics).
 Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes [e.g., @cavanaugh2000empirical].
+
+@lepine2022challenge explain the mechanisms by which demands are related to these differential positive and negative outcomes.
+Similar to the job-demands resources theory [@bakker2017job], challenge and hindrance demands elicit two different paths or processes.
+Challenge stressors typically result in a challenge appraisal, and engagement is likely to happen as a result.
+Engagement is positively related to the positive outcomes described above: motivation, performance, growth, and wellbeing.
+Of note is that this energy may be depleted eventually, leading to strain.
+@rosen2020challenges, in fact, suggests that appraisals may change over time, which is probably expected when thinking about how workers experience continued stressors.
+Hindrance stressors elicit a different process.
+Rather than experiencing engagement, disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing.
+This is a result of depleted resources via frustrations and other affectively negative reactions [@lepine2022challenge].
+
+Recently, @horan2020review and @lepine2022challenge have both called out the need for additional research to incorporate the *appraisal process* described by @lazarus1984stress into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources into our study of the overarching job demands-resources model.
+In fact, @horan2020review state that “…stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p.
+3).
+In the current study, we build on the work of a growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources *and* demands [@webster2011extending].
+
+## Current Study and Research Questions
 
@@
 This is because demands appraised as a challenge promote mastery, personal growth, and future gains.
-Moreover, it was more likely that employees would also perceive these characterstics as *resources* within their jobs.
+Moreover, it was more likely that employees would also perceive these characteristics as *resources* within their jobs.
 

### 2023-07-27 SIOP2024/SIOP2024convergence.tex
Updated SIOP intro

--- 2023-07-18 SIOP2024/SIOP2024convergence.tex
@@
 {}{\PatchFailed}
-\keywords{keywords\newline\indent Word count: X}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
   pdflang={en-EN},
-  pdfkeywords={keywords},
   hidelinks,
@@
 \authornote{
-
-Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-Enter author note here.
 
@@
 The Occupational Information Network (O*NET; onetonline.org) contains a reasonably comprehensive description of occupations (Peterson et al., 2001) which subject matter experts inform via surveys.
-We utilize a set of O*NET job context and activity statements contained in these surveys to explore a series of research questions about how people perceive resources, challenges, and hindrances within their jobs.
-There are a number of advantage to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.
-Here, we focus broadly on two research questions using these O*NET items: 1) are jobs with many resources also perceived to have many challenges, and 2) could that association be moderated by kind of job characteristic (e.g., interacting with others vs.~physical work characteristics)?
-A brief summary of the Challenge-hindrance Framework is presented prior to rationale for these specific questions.
-
-\hypertarget{not-all-stressors-are-equal-the-challenge-hindrance-framework}{%
-\subsection{Not all Stressors are Equal: The Challenge-hindrance Framework}\label{not-all-stressors-are-equal-the-challenge-hindrance-framework}}
+In the current study, we utilize a set of O*NET job context and activity statements to explore two questions about how people perceive resources, challenges, and hindrances within their jobs.
+\footnote{There are a number of advantage to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.} Here, we focus broadly on two research questions using these O*NET items: 1) are jobs with many resources also perceived to have many challenges, and 2) could that association be moderated by kind of job characteristic (e.g., interacting with others vs.~physical work characteristics)?
+The basis for these questions comes out the stress literature (e.g., Lazarus \& Folkman, 1984).
 
@@
 Selye the physician would likely have labeled the two responses as subjective manifestations of ``distress'', and ``eustress'' (Selye, 1974).
-In modern I-O Psychology parlance (and more consistent with the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker \& Demerouti, 2017)), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a \emph{challenge} while the other would appraise the demand as a \emph{hindrance} (Cavanaugh et al., 2000).
+
+\hypertarget{not-all-stressors-are-equal-the-challenge-hindrance-framework}{%
+\subsection{Not all Stressors are Equal: The Challenge-hindrance Framework}\label{not-all-stressors-are-equal-the-challenge-hindrance-framework}}
+
+In modern I-O psychology parlance (and more consistent with the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker \& Demerouti, 2017)), the two workers above would both be characterized as appraising the speaking opportunity as a job demand.
+However, as noted above, demands/stressors are subjective.
+Cavanaugh's (2000) challenge-hindrance stressor framework speaks directly to this reality, and suggests that the way we understand reactions to stressors requires consideration of how people \emph{feel} about a given stressor.
+One of our above employees would be appraising the demand as a \emph{challenge} while the other would appraise the demand as a \emph{hindrance} (Cavanaugh et al., 2000).
 According to Cavanaugh et al.
 (2000), challenge demands promote mastery, personal growth, and future gains.
-Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
+Challenge stressors should lead to coping strategies that facilitate achievement and motivation (e.g., Kim \& Beehr, 2020).
+Hindrance demands, in contrast, inhibit growth, learning and goal achievement (e.g., perception of role conflict, workplace politics).
 Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes (e.g., Cavanaugh et al., 2000).
+
+LePine (2022) explain the mechanisms by which demands are related to these differential positive and negative outcomes.
+Similar to the job-demands resources theory (Bakker \& Demerouti, 2017), challenge and hindrance demands elicit two different paths or processes.
+Challenge stressors typically result in a challenge appraisal, and engagement is likely to happen as a result.
+Engagement is positively related to the positive outcomes described above: motivation, performance, growth, and wellbeing.
+Of note is that this energy may be depleted eventually, leading to strain.
+Rosen et al.
+(2020), in fact, suggests that appraisals may change over time, which is probably expected when thinking about how workers experience continued stressors.
+Hindrance stressors elicit a different process.
+Rather than experiencing engagemnet, disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing.
+This is a result of depleted resources via frustrations and other affectively negative reactions (LePine, 2022).
+
+Recently, Horan et al.
+(2020) and LePine (2022) have both called out the need for additional research to incorporate the \emph{appraisal process} described by Lazarus and Folkman (1984) into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources into our study of the overarching job demands-resources model.
+In fact, Horan et al.
+(2020) state that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3).
+In the current study, we build on the work of a growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources \emph{and} demands (Webster et al., 2011).
+
+\hypertarget{current-study-and-research-questions}{%
+\subsection{Current Study and Research Questions}\label{current-study-and-research-questions}}
 
@@
 This is because demands appraised as a challenge promote mastery, personal growth, and future gains.
-Moreover, it was more likely that employees would also perceive these characterstics as \emph{resources} within their jobs.
+Moreover, it was more likely that employees would also perceive these characteristics as \emph{resources} within their jobs.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-horan2020review}{}}%
+Horan, K.
+A., Nakahara, W.
+H., DiStaso, M.
+J., \& Jex, S.
+M.
+(2020).
+A review of the challenge-hindrance stress model: Recent advances, expanded paradigms, and recommendations for future research.
+\emph{Frontiers in Psychology}, \emph{11}, 560346.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kim2020thriving}{}}%
+Kim, M., \& Beehr, T.
+A.
+(2020).
+Thriving on demand: Challenging work results in employee flourishing through appraisals and resources.
+\emph{International Journal of Stress Management}, \emph{27}(2), 111.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
+Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lepine2022challenge}{}}%
+LePine, M. A. (2022). The challenge-hindrance stressor framework: An integrative conceptual review and path forward. \emph{Group \& Organization Management}, \emph{47}(2), 223--254.
+
 \leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-rosen2020challenges}{}}%
+Rosen, C.
+C., Dimotakis, N., Cole, M.
+S., Taylor, S.
+G., Simon, L.
+S., Smith, T.
+A., \& Reina, C.
+S.
+(2020).
+When challenges hinder: An investigation of when and how challenge stressors impact employee outcomes.
+\emph{Journal of Applied Psychology}, \emph{105}(10), 1181.
+
 \leavevmode\vadjust pre{\hypertarget{ref-selye1936syndrome}{}}%

### 2023-08-05 SIOP2024/SIOP2024convergence.tex
updating siop project

@@
 \documentclass[
-  man]{apa6}
+  jou]{apa6}
 \usepackage{amsmath,amssymb}
@@
 {}{\PatchFailed}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
+\usepackage{dblfloatfix}
+
 \usepackage{csquotes}
@@
 \hypersetup{
-  pdftitle={Demanding resources: Converging perceptions of challenge and resource characteristics},
+  pdftitle={Demanding Resources: Converging Perceptions of Challenge and Resource Characteristics},
   pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata García Prieto Palacios Roji3},
@@
 
-\title{Demanding resources: Converging perceptions of challenge and resource characteristics}
+\title{Demanding Resources: Converging Perceptions of Challenge and Resource Characteristics}
 \author{John Kulas\textsuperscript{1}, Alicia Stachowski\textsuperscript{2}, \& Renata García Prieto Palacios Roji\textsuperscript{3}}
@@
 In the current study, we utilize a set of O*NET job context and activity statements to explore two questions about how people perceive resources, challenges, and hindrances within their jobs.
-\footnote{There are a number of advantage to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.} Here, we focus broadly on two research questions using these O*NET items: 1) are jobs with many resources also perceived to have many challenges, and 2) could that association be moderated by kind of job characteristic (e.g., interacting with others vs.~physical work characteristics)?
+\footnote{There are a number of advantages to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.} Here, we focus broadly on two research questions using these O*NET items: 1) are jobs with many resources also perceived to have many challenges, and 2) could that association be moderated by kind of job characteristic (e.g., interacting with others vs.~physical work characteristics)?
 The basis for these questions comes out the stress literature (e.g., Lazarus \& Folkman, 1984).
@@
 Hindrance stressors elicit a different process.
-Rather than experiencing engagemnet, disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing.
+Rather than experiencing engagement, disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing.
 This is a result of depleted resources via frustrations and other affectively negative reactions (LePine, 2022).
@@
 \emph{RQ1}: Do employees who perceive many resources in their jobs also perceived many challenges?
+\emph{Amend the wording to fit the lead up}
 
@@
 
-\begin{table}[tbp]
+\begin{table*}[tbp]
 
@@
 
-\end{table}
+\end{table*}
 

### 2023-08-12 SIOP2024/SIOP2024convergence.Rmd
updating siop project

--- 2023-07-18 SIOP2024/SIOP2024convergence.Rmd
@@
 More variability was observed when exploring associations between resources and hindrance stressors, and challenge/hindrance stressors.
+**WORD LIMITS: Title (85 characters); Abstract (600 characters); Word limit (3,000; exclude tables, figures, references)**
 
-keywords          : "keywords"
-wordcount         : "X"
+#keywords          : "keywords"
+#wordcount         : "X"
 
@@
 ```
-The Occupational Information Network (O\*NET; onetonline.org) contains a reasonably comprehensive description of occupations [@peterson2001understanding] which subject matter experts inform via surveys.
-We utilize a set of O\*NET job context and activity statements contained in these surveys to explore a series of research questions about how people perceive resources, challenges, and hindrances within their jobs.
-There are a number of advantage to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.
-Here, we focus broadly on two research questions using these O\*NET items: 1) are jobs with many resources also perceived to have many challenges, and 2) could that association be moderated by kind of job characteristic (e.g., interacting with others vs.
-physical work characteristics)?
-A brief summary of the Challenge-hindrance Framework is presented prior to rationale for these specific questions.
+The Occupational Information Network ([O\*NET](onetonline.org)) contains a large yet non-exhaustive description of occupations [@peterson2001understanding] which subject matter experts inform via surveys.
+In the current study, we retain a set of O\*NET job context and activity statements to explore questions about how people perceive resources, challenges, and hindrances within their jobs.^[There are a number of advantages to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.] Here, we focus broadly on two research questions: 1) do challenging jobs tend to be resource-rich or -poor?, and 2) is that association be moderated by job characteristic (e.g., social vs.
+physical aspects of work)?
+
+Although the word *stress* often carries a negative connotation, the "father" of the current concept, @selye1936syndrome, conceptualized the construct much less pejoratively - simply presenting it as a *response to change*.
+Consider, for example, the responses two different employees may have to being nominated to give a presentation at an upcoming company event.
+One may appraise the nomination as a frightful task whereas another may appraise it as an exciting opportunity to share their experiences with their coworkers.
+Selye the physician would likely label the two responses as subjective manifestations of "distress" and "eustress" [@selye1974stress].
 
@@
 
-We argue below that *perception* of something as a resource or demand matters.
-Although the word “stress” often carries a negative connotation, the "father" of the current concept, @selye1936syndrome, conceptualized stress much less pejoratively - rather thinking of it as a *response to change*.
-For instance, consider the different reactions two different employees may have to being nominated to give a speech at an upcoming company event.
-One may appraise the nomination as a negative stressor.
-However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
-Selye the physician would likely have labeled the two responses as subjective manifestations of "distress", and "eustress" [@selye1974stress].
-In modern I-O Psychology parlance (and more consistent with the job demands-resources model [@demerouti2001job] and job demands-resources theory [@bakker2017job]), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a *challenge* while the other would appraise the demand as a *hindrance* [@cavanaugh2000empirical].
-According to @cavanaugh2000empirical, challenge demands promote mastery, personal growth, and future gains.
-Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
+In modern I-O psychology parlance, and more consistent with the job demands-resources model and job demands-resources theory [e.g., @bakker2017job; @demerouti2001job], the two workers would both be characterized as appraising the speaking opportunity as a job demand, which would be *stressful*.
+However, @cavanaugh2000empirical's challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people *feel* about a given stressor.
+One of our above employees would be appraising the demand as a *challenge* while the other would appraise the demand as a *hindrance* [@cavanaugh2000empirical].
+@horan2020review state that “…stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p.
+3).
+According to @cavanaugh2000empirical, challenge demands promote mastery, personal growth, and future gains - these should lead to coping strategies that facilitate achievement and motivation [e.g., @kim2020thriving].
+Hindrance demands (e.g., role conflict, workplace politics), in contrast, inhibit growth, learning and goal achievement.
 Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes [e.g., @cavanaugh2000empirical].
 
-At the most broad level, we can question whether employees actually distinguish between challenges and hindrances as the theory describes.
-Research suggests that people can and do perceive them differently.
-For example, @bakker2013weekly found that perceived work pressure can be classified as a hindrance demand, while the requirement to express emotions is a challenge demand.
+@lepine2022challenge explains the mechanisms by which demands are related to these differential positive and negative outcomes.
+Similar to the job-demands resources theory [@bakker2017job], challenge and hindrance demands elicit two different paths or processes.
+Challenge stressors typically result in a challenge appraisal, and engagement is likely to happen as a result.
+Of note, however, this energy may be depleted eventually, leading to strain.
+Hindrance stressors elicit a different process.
+Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing.
+This is a result of depleted resources via frustrations and other affectively negative reactions [@lepine2022challenge].
+
+Recently, @horan2020review,  @lepine2022challenge, and @mazzola2019should have all called out the need for additional research to incorporate the appraisal process into the challenge-hindrance stressor framework.
+In the current study, we build on the work of this growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources *and* demands [@webster2011extending].
+
+## Current Study and Research Questions
+
+At the broadest level, we can question whether employees actually distinguish between challenges and hindrances as the theory describes.
+Research suggests that people can and do.
+For example, @bakker2013weekly found that work pressure is classified as a hindrance demand, while the requirement to express emotions is a challenge demand.
 @webster2011extending also considered three common work characteristics including workload, role ambiguity, and role conflict.
 Interestingly, they found that while each could be identified *primarily* as a challenge or hindrance, employees could also appraise that a characteristic is simultaneously both a challenge and hindrance.
-However, this list of demands (workload, role ambiguity, and role conflict) is somewhat narrow.
-Using a very wide range of O\*NET job characteristics regarding job context and activities, we explore whether challenges (positive stressors per the definition above) might actually be positively related to resources.
+Here we note that this list of demands (workload, role ambiguity, and role conflict) is quite narrow.
+
+Using a very large set of O\*NET job characteristics, we explore whether challenges (positive stressors per the definition above) might actually be simultaneously viewed as resources.
 Per the job demands-resources theory [@bakker2017job] resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
-It stands to reason that a challenging demand may be considered a resource.
+It stands to reason that some challenging demands may also be appraised as resources.
 
-*RQ1*: Do employees who perceive many resources in their jobs also perceived many challenges?
+*RQ1*: Are challenging demands also appraised as resources?
 
@@
 
-Research Question 1 explored whether people who perceive many challenges in their work also report many resources.
+Research Question 1 explored whether challenging demands may also be commonly appraised as resources.
 The results show that the total number of undifferentiated challenges and resources are positively related.
@@
 Although we did not address job complexity as a moderator in the current paper, we do plan to do so in future investigations.
-Also, take note of the average numbers of resources, challenges, and hindrances cited by our sample, where these respondents generally experienced fewer hindrances in their jobs (*M* = 13.09) than both resources and challenges.
+Also, take note of the average numbers of resources, challenges, and hindrances cited by our sample, where these respondents generally experienced fewer hindrances in their jobs (*M* = 13.09) than both resources (*M* = 36.02) and challenges (*M* = 35.64).
 

### 2023-08-12 SIOP2024/SIOP2024convergence.tex

@@
 \documentclass[
-  jou]{apa6}
+  man]{apa6}
 \usepackage{amsmath,amssymb}
+\usepackage{lmodern}
 \usepackage{iftex}
@@
 {}{\PatchFailed}
-\usepackage{dblfloatfix}
-
+\DeclareDelayedFloatFlavor{ThreePartTable}{table}
+\DeclareDelayedFloatFlavor{lltable}{table}
+\DeclareDelayedFloatFlavor*{longtable}{table}
+\makeatletter
+\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
+\makeatother
 \usepackage{csquotes}
@@
 More variability was observed when exploring associations between resources and hindrance stressors, and challenge/hindrance stressors.
+\textbf{WORD LIMITS: Title (85 characters); Abstract (600 characters); Word limit (3,000; exclude tables, figures, references)}
 }
@@
 
-The Occupational Information Network (O*NET; onetonline.org) contains a reasonably comprehensive description of occupations (Peterson et al., 2001) which subject matter experts inform via surveys.
-In the current study, we utilize a set of O*NET job context and activity statements to explore two questions about how people perceive resources, challenges, and hindrances within their jobs.
-\footnote{There are a number of advantages to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.} Here, we focus broadly on two research questions using these O*NET items: 1) are jobs with many resources also perceived to have many challenges, and 2) could that association be moderated by kind of job characteristic (e.g., interacting with others vs.~physical work characteristics)?
-The basis for these questions comes out the stress literature (e.g., Lazarus \& Folkman, 1984).
+The Occupational Information Network (\href{onetonline.org}{O*NET}) contains a large yet non-exhaustive description of occupations (Peterson et al., 2001) which subject matter experts inform via surveys.
+In the current study, we retain a set of O*NET job context and activity statements to explore questions about how people perceive resources, challenges, and hindrances within their jobs.\footnote{There are a number of advantages to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.} Here, we focus broadly on two research questions: 1) do challenging jobs tend to be resource-rich or -poor?, and 2) is that association be moderated by job characteristic (e.g., social vs.~physical aspects of work)?
 
-We argue below that \emph{perception} of something as a resource or demand matters.
-Although the word ``stress'' often carries a negative connotation, the ``father'' of the current concept, Selye (1936), conceptualized stress much less pejoratively - rather thinking of it as a \emph{response to change}.
-For instance, consider the different reactions two different employees may have to being nominated to give a speech at an upcoming company event.
-One may appraise the nomination as a negative stressor.
-However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired.
-Selye the physician would likely have labeled the two responses as subjective manifestations of ``distress'', and ``eustress'' (Selye, 1974).
+Although the word \emph{stress} often carries a negative connotation, the ``father'' of the current concept, Selye (1936), conceptualized the construct much less pejoratively - simply presenting it as a \emph{response to change}.
+Consider, for example, the responses two different employees may have to being nominated to give a presentation at an upcoming company event.
+One may appraise the nomination as a frightful task whereas another may appraise it as an exciting opportunity to share their experiences with their coworkers.
+Selye the physician would likely label the two responses as subjective manifestations of ``distress'' and ``eustress'' (Selye, 1974).
 
@@
 
-In modern I-O psychology parlance (and more consistent with the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker \& Demerouti, 2017)), the two workers above would both be characterized as appraising the speaking opportunity as a job demand.
-However, as noted above, demands/stressors are subjective.
-Cavanaugh's (2000) challenge-hindrance stressor framework speaks directly to this reality, and suggests that the way we understand reactions to stressors requires consideration of how people \emph{feel} about a given stressor.
+In modern I-O psychology parlance, and more consistent with the job demands-resources model and job demands-resources theory (e.g., Bakker \& Demerouti, 2017; Demerouti et al., 2001), the two workers would both be characterized as appraising the speaking opportunity as a job demand, which would be \emph{stressful}.
+However, Cavanaugh et al.
+(2000)'s challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people \emph{feel} about a given stressor.
 One of our above employees would be appraising the demand as a \emph{challenge} while the other would appraise the demand as a \emph{hindrance} (Cavanaugh et al., 2000).
+Horan et al.
+(2020) state that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3).
 According to Cavanaugh et al.
-(2000), challenge demands promote mastery, personal growth, and future gains.
-Challenge stressors should lead to coping strategies that facilitate achievement and motivation (e.g., Kim \& Beehr, 2020).
-Hindrance demands, in contrast, inhibit growth, learning and goal achievement (e.g., perception of role conflict, workplace politics).
+(2000), challenge demands promote mastery, personal growth, and future gains - these should lead to coping strategies that facilitate achievement and motivation (e.g., Kim \& Beehr, 2020).
+Hindrance demands (e.g., role conflict, workplace politics), in contrast, inhibit growth, learning and goal achievement.
 Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes (e.g., Cavanaugh et al., 2000).
 
-LePine (2022) explain the mechanisms by which demands are related to these differential positive and negative outcomes.
+LePine (2022) explains the mechanisms by which demands are related to these differential positive and negative outcomes.
 Similar to the job-demands resources theory (Bakker \& Demerouti, 2017), challenge and hindrance demands elicit two different paths or processes.
 Challenge stressors typically result in a challenge appraisal, and engagement is likely to happen as a result.
-Engagement is positively related to the positive outcomes described above: motivation, performance, growth, and wellbeing.
-Of note is that this energy may be depleted eventually, leading to strain.
-Rosen et al.
-(2020), in fact, suggests that appraisals may change over time, which is probably expected when thinking about how workers experience continued stressors.
+Of note, however, this energy may be depleted eventually, leading to strain.
 Hindrance stressors elicit a different process.
-Rather than experiencing engagement, disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing.
+Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing.
 This is a result of depleted resources via frustrations and other affectively negative reactions (LePine, 2022).
@@
 Recently, Horan et al.
-(2020) and LePine (2022) have both called out the need for additional research to incorporate the \emph{appraisal process} described by Lazarus and Folkman (1984) into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources into our study of the overarching job demands-resources model.
-In fact, Horan et al.
-(2020) state that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3).
-In the current study, we build on the work of a growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources \emph{and} demands (Webster et al., 2011).
+(2020), LePine (2022), and Mazzola and Disselhorst (2019) have all called out the need for additional research to incorporate the appraisal process into the challenge-hindrance stressor framework.
+In the current study, we build on the work of this growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources \emph{and} demands (Webster et al., 2011).
 
@@
 
-At the most broad level, we can question whether employees actually distinguish between challenges and hindrances as the theory describes.
-Research suggests that people can and do perceive them differently.
-For example, Bakker and Sanz-Vergel (2013) found that perceived work pressure can be classified as a hindrance demand, while the requirement to express emotions is a challenge demand.
+At the broadest level, we can question whether employees actually distinguish between challenges and hindrances as the theory describes.
+Research suggests that people can and do.
+For example, Bakker and Sanz-Vergel (2013) found that work pressure is classified as a hindrance demand, while the requirement to express emotions is a challenge demand.
 Webster et al.
@@
 Interestingly, they found that while each could be identified \emph{primarily} as a challenge or hindrance, employees could also appraise that a characteristic is simultaneously both a challenge and hindrance.
-However, this list of demands (workload, role ambiguity, and role conflict) is somewhat narrow.
-Using a very wide range of O*NET job characteristics regarding job context and activities, we explore whether challenges (positive stressors per the definition above) might actually be positively related to resources.
+Here we note that this list of demands (workload, role ambiguity, and role conflict) is quite narrow.
+
+Using a very large set of O*NET job characteristics, we explore whether challenges (positive stressors per the definition above) might actually be simultaneously viewed as resources.
 Per the job demands-resources theory (Bakker \& Demerouti, 2017) resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
-It stands to reason that a challenging demand may be considered a resource.
+It stands to reason that some challenging demands may also be appraised as resources.
 
-\emph{RQ1}: Do employees who perceive many resources in their jobs also perceived many challenges?
-\emph{Amend the wording to fit the lead up}
+\emph{RQ1}: Are challenging demands also appraised as resources?
 
@@
 
-\begin{table*}[tbp]
+\begin{table}[tbp]
 
@@
 
-\end{table*}
+\end{table}
 
@@
 Although we did not address job complexity as a moderator in the current paper, we do plan to do so in future investigations.
-Also, take note of the average numbers of resources, challenges, and hindrances cited by our sample, where these respondents generally experienced fewer hindrances in their jobs (\emph{M} = 13.09) than both resources and challenges.
+Also, take note of the average numbers of resources, challenges, and hindrances cited by our sample, where these respondents generally experienced fewer hindrances in their jobs (\emph{M} = 13.09) than both resources (\emph{M} = 36.02) and challenges (\emph{M} = 35.64).
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
-Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
-
 \leavevmode\vadjust pre{\hypertarget{ref-lepine2022challenge}{}}%
 LePine, M. A. (2022). The challenge-hindrance stressor framework: An integrative conceptual review and path forward. \emph{Group \& Organization Management}, \emph{47}(2), 223--254.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mazzola2019should}{}}%
+Mazzola, J.
+J., \& Disselhorst, R.
+(2019).
+Should we be {``challenging''} employees?: A critical review and meta-analysis of the challenge-hindrance model of stress.
+\emph{Journal of Organizational Behavior}, \emph{40}(8), 949--961.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-rosen2020challenges}{}}%
-Rosen, C.
-C., Dimotakis, N., Cole, M.
-S., Taylor, S.
-G., Simon, L.
-S., Smith, T.
-A., \& Reina, C.
-S.
-(2020).
-When challenges hinder: An investigation of when and how challenge stressors impact employee outcomes.
-\emph{Journal of Applied Psychology}, \emph{105}(10), 1181.
-
 \leavevmode\vadjust pre{\hypertarget{ref-selye1936syndrome}{}}%

### 2023-12-12 Submission.Rmd
framing

@@
 ---
-title             : "Job Demands-Resources Model Components through the Lens of O*NET Classifications"
+title             : "Subjectivity of Job Demands and Resources through the comprehensive framework of O*NET"
 shorttitle        : "O*NET JD-R"
@@
 author: 
-  -
+  - name          : "Alicia Stachowski"
+    affiliation   : "2"
+    corresponding : yes    # Define only one corresponding author
+  - name          : "John Kulas"
+    affiliation   : "1"
+    email         : "jtkulas@ergreports.com"
+  - name          : "Renata García Prieto Palacios Roji"
+    affiliation   : "3"
+
+affiliation:
+  - id            : "1"
+    institution   : "eRg"
+  - id            : "2"
+    institution   : "University of Wisconsin - Stout"
+  - id            : "3"
+    institution   : "PepsiCo"
 
@@
 abstract: |
-  Much of our understanding of job demands and resources rests on the assumption that some aspects and components of one's job are resources and some are demands.
-We build on a small but growing literature suggesting that individual differences may matter in our perceptions of characteristics as demands and resources.
-The primary aims were to explore 1) whether there is variability in subjective ratings of job characteristics with respect to how much they served as resources and demands, and 2) whether or not there was a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
-O*NET work characteristics were rated by 568 employed respondents in terms of relevance, perception as a demand, and perception as a resource.
-The results suggest that job characteristics differ in variability/stability regarding subjective worker perceptions, particularly for hindrance demands which showed the most variability.
-Job characteristics were not uniquely categorized as a resource or demand, and literature-implicated resources were also implicated as being challenge, but not hindrance demands.
+  Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands.
+We build on an oppositional literature positing that *individual differences* matter in our perceptions of characteristics as demands and resources.
+Our primary aim was to document the degree of variability in subjective ratings of job characteristics with respect to interpretation as resource and demand.
+Secondarily, we quantify the degree to which perceptions match the literature-implicated resources/demands of job  characteristics.
+Procedurally, an exhaustive list of O\*NET work characteristics were rated by 568 employed respondents in terms of relevance, perception as a demand, and perception as a resource.
+Job characteristics were not commonly categorized as solely resource or demand - rather, job resources were also frequently viewed as challenging demands.
+**sentence about lit-implied demands/resources**.
+**sentence about implications for job design**.
 
@@
 
-csl               : apa7.csl
-documentclass     : interact
-#classoption       : "man"
-output            : pdf_document
+csl               : "apa7.csl"
+#documentclass     : "apa7" #interact
+classoption       : "jou"
+output            : papaja::apa6_pdf
+
 ---

### 2023-12-12 Submission.tex
framing

--- 2023-06-06 Submission.tex
@@
 \documentclass[
-  man]{interact}
+  jou,mask]{apa6}
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \keywords{O*Net, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: 4,942}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
+\usepackage{dblfloatfix}
+
 \usepackage{csquotes}
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
-  pdftitle={Job Demands-Resources Model Components through the Lens of O*NET Classifications},
-  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
+  pdftitle={Subjectivity of Job Demands and Resources through the comprehensive framework of O*NET},
   pdflang={en-EN},
@@
 
-\title{Job Demands-Resources Model Components through the Lens of O*NET Classifications}
-\author{Alicia Stachowski\textsuperscript{1}, John Kulas\textsuperscript{2}, \& Renata Garcia Prieto Palacios Roji\textsuperscript{3}}
+\title{Subjectivity of Job Demands and Resources through the comprehensive framework of O*NET}
+\author{Alicia Stachowski\textsuperscript{2}, John Kulas\textsuperscript{1}, \& Renata García Prieto Palacios Roji\textsuperscript{3}}
 \date{}
@@
 
-Correspondence concerning this article should be addressed to Alicia Stachowski, 470M Harvey Hall, 721 3rd Street E, Menomenie, WI, 54751, USA.
-E-mail: \href{mailto:stachowskia@uwstout.edu}{\nolinkurl{stachowskia@uwstout.edu}}
-
 }
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Wisconsin-Stout\\\textsuperscript{2} eRg\\\textsuperscript{3} PepsiCo}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} eRg\\\textsuperscript{2} University of Wisconsin - Stout\\\textsuperscript{3} PepsiCo}
 
 \abstract{%
-Much of our understanding of job demands and resources rests on the assumption that some aspects and components of one's job are resources and some are demands.
-We build on a small but growing literature suggesting that individual differences may matter in our perceptions of characteristics as demands and resources.
-The primary aims were to explore 1) whether there is variability in subjective ratings of job characteristics with respect to how much they served as resources and demands, and 2) whether or not there was a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
-O*NET work characteristics were rated by 568 employed respondents in terms of relevance, perception as a demand, and perception as a resource.
-The results suggest that job characteristics differ in variability/stability regarding subjective worker perceptions, particularly for hindrance demands which showed the most variability.
-Job characteristics were not uniquely categorized as a resource or demand, and literature-implicated resources were also implicated as being challenge, but not hindrance demands.
+Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands.
+We build on an oppositional literature positing that \emph{individual differences} matter in our perceptions of characteristics as demands and resources.
+Our primary aim was to document the degree of variability in subjective ratings of job characteristics with respect to interpretation as resource and demand.
+Secondarily, we quantify the degree to which perceptions match the literature-implicated resources/demands of job characteristics.
+Procedurally, an exhaustive list of O*NET work characteristics were rated by 568 employed respondents in terms of relevance, perception as a demand, and perception as a resource.
+Job characteristics were not commonly categorized as solely resource or demand - rather, job resources were also frequently viewed as challenging demands.
+\textbf{sentence about lit-implied demands/resources}.
+\textbf{sentence about implications for job design}.
 }
@@
 We explore this hypothesis first at the job characteristic level before presenting a broader perspective.
-Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present only extreme snapshots of characteristic variability in the form of the 8-most \emph{consistently rated} and \emph{inconsistently rated} resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
-The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency.
-Figure \ref{fig:combinegraphs} presents the resources, challenges, and hindrances that are \emph{most consistently agreed on} as indexed by (relatively) low standard deviations, while Figure \ref{fig:combinegraphs2} presents the characteristics with the greatest amount of \emph{disagreement} across workers.
+Figures 1 and 2 present only extreme snapshots of characteristic variability in the form of the 8-most \emph{consistently rated} and \emph{inconsistently rated} resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
+The Figures 1 and 2 presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency.
+Figure 1 presents the resources, challenges, and hindrances that are \emph{most consistently agreed on} as indexed by (relatively) low standard deviations, while Figure 2 presents the characteristics with the greatest amount of \emph{disagreement} across workers.
 The figures demonstrate that what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
@@
 
-In addition to highlighting extremely agreed- or disagreed-upon items, Figure \ref{fig:overallhist} presents our standard deviation indices across all rated items.
-Here, the Figure \ref{fig:combinegraphs} discrepancies receive greater context, with the \emph{spread} of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively \emph{bunched} levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
+In addition to highlighting extremely agreed- or disagreed-upon items, Figure 3 presents our standard deviation indices across all rated items.
+Here, the Figure 1 discrepancies receive greater context, with the \emph{spread} of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively \emph{bunched} levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
 Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
@@
 The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand.
-Table \ref{tab:cortab} provides the correlations among the O*Net ``scale''-level groupings across ratings of resource, challenge, and hindrance.
+Table 1 provides the correlations among the O*Net ``scale''-level groupings across ratings of resource, challenge, and hindrance.
 We would expect to see minimal correlations if job characteristics \emph{were} uniquely categorized.
-First, the average correlation within all resource categories (variables 1 through 7 in Table \ref{tab:cortab}) was .43 (\emph{SD} = .13, range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, \emph{M} = .43, \emph{SD} =.16).
+First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (\emph{SD} = .13, range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, \emph{M} = .43, \emph{SD} =.16).
 Hindrance categories, however, had less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, \emph{M} = .62, \emph{SD} = .17.
 When people perceived hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.
-Taken with the Figure \ref{fig:overallhist} takeaway, this hints that workers are likely either generally experiencing hindrances at work or they are not.
+Taken with the Figure 3 takeaway, this hints that workers are likely either generally experiencing hindrances at work or they are not.
 
@@
 Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.
-
-\begin{lltable}
-
-\begin{TableNotes}[para]
-\normalsize{\textit{Note.} The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)}
-\end{TableNotes}
-
-\tiny{
-
-\begin{longtable}{lllllllllllllllllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
-\caption{\label{tab:cortab}Challenge, hindrance, and resource bivariate correlations.}\\
-\toprule
- & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{6} & \multicolumn{1}{c}{7} & \multicolumn{1}{c}{8} & \multicolumn{1}{c}{9} & \multicolumn{1}{c}{10} & \multicolumn{1}{c}{11} & \multicolumn{1}{c}{12} & \multicolumn{1}{c}{13} & \multicolumn{1}{c}{14} & \multicolumn{1}{c}{15} & \multicolumn{1}{c}{16} & \multicolumn{1}{c}{17} & \multicolumn{1}{c}{18} & \multicolumn{1}{c}{19} & \multicolumn{1}{c}{20} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
-\midrule
-\endfirsthead
-\caption*{\normalfont{Table \ref{tab:cortab} continued}}\\
-\toprule
- & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{6} & \multicolumn{1}{c}{7} & \multicolumn{1}{c}{8} & \multicolumn{1}{c}{9} & \multicolumn{1}{c}{10} & \multicolumn{1}{c}{11} & \multicolumn{1}{c}{12} & \multicolumn{1}{c}{13} & \multicolumn{1}{c}{14} & \multicolumn{1}{c}{15} & \multicolumn{1}{c}{16} & \multicolumn{1}{c}{17} & \multicolumn{1}{c}{18} & \multicolumn{1}{c}{19} & \multicolumn{1}{c}{20} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
-\midrule
-\endhead
-1. onet.resource.ii & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
-2. onet.resource.mp & .61*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.19 & 0.60\\
-3. onet.resource.wo & .46*** & .50*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.79 & 0.84\\
-4. onet.resource.io & .49*** & .64*** & .45*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.10 & 0.60\\
-5. onet.resource.ir & .46*** & .55*** & .37*** & .60*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.80 & 0.61\\
-6. onet.resource.pc & .19*** & .15*** & .32*** & .18*** & .37*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 2.99 & 0.77\\
-7. onet.resource.sc & .43*** & .46*** & .41*** & .45*** & .48*** & .37*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.61\\
-8. onet.challenge.ii & .62*** & .49*** & .37*** & .41*** & .33*** & .08 & .33*** & - &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
-9. onet.challenge.mp & .47*** & .63*** & .42*** & .50*** & .41*** & .09* & .38*** & .65*** & - &  &  &  &  &  &  &  &  &  &  &  & 4.20 & 0.64\\
-10. onet.challenge.wo & .34*** & .39*** & .64*** & .34*** & .30*** & .29*** & .38*** & .45*** & .49*** & - &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.88\\
-11. onet.challenge.io & .34*** & .48*** & .33*** & .65*** & .48*** & .13** & .40*** & .50*** & .68*** & .43*** & - &  &  &  &  &  &  &  &  &  & 4.07 & 0.64\\
-12. onet.challenge.ir & .32*** & .40*** & .26*** & .48*** & .63*** & .23*** & .39*** & .46*** & .60*** & .39*** & .70*** & - &  &  &  &  &  &  &  &  & 3.85 & 0.63\\
-13. onet.challenge.pc & .12** & .08 & .21*** & .13** & .26*** & .66*** & .29*** & .14** & .12** & .33*** & .20*** & .31*** & - &  &  &  &  &  &  &  & 2.85 & 0.79\\
-14. onet.challenge.sc & .27*** & .31*** & .28*** & .38*** & .40*** & .27*** & .62*** & .36*** & .41*** & .38*** & .51*** & .45*** & .40*** & - &  &  &  &  &  &  & 3.66 & 0.59\\
-15. onet.hindrance.ii & -.26*** & -.26*** & -.17*** & -.24*** & -.18*** & -.02 & -.08 & -.27*** & -.26*** & -.10* & -.19*** & -.16*** & .06 & -.10* & - &  &  &  &  &  & 2.15 & 1.01\\
-16. onet.hindrance.mp & -.23*** & -.30*** & -.17*** & -.22*** & -.15*** & .05 & -.07 & -.22*** & -.27*** & -.10* & -.18*** & -.15*** & .12** & -.06 & .86*** & - &  &  &  &  & 2.10 & 1.05\\
-17. onet.hindrance.wo & -.21*** & -.25*** & -.22*** & -.22*** & -.06 & -.02 & -.12** & -.14** & -.21*** & -.23*** & -.15*** & -.09* & .05 & -.10* & .66*** & .69*** & - &  &  &  & 2.31 & 1.02\\
-18.
-onet.hindrance.io & -.22*** & -.27*** & -.14*** & -.29*** & -.18*** & -.01 & -.10* & -.21*** & -.25*** & -.10* & -.27*** & -.19*** & .07 & -.10* & .79*** & .86*** & .69*** & - &  &  & 2.23 & 1.03\\
-19.
-onet.hindrance.ir & -.22*** & -.24*** & -.15*** & -.24*** & -.25*** & -.06 & -.11** & -.19*** & -.21*** & -.08* & -.20*** & -.23*** & .04 & -.12** & .79*** & .80*** & .61*** & .82*** & - &  & 2.35 & 0.89\\
-20. onet.hindrance.pc & -.04 & -.08* & -.09* & -.11** & -.10* & -.16*** & -.13** & -.03 & -.04 & -.06 & -.08* & -.10* & -.04 & -.13** & .38*** & .33*** & .47*** & .35*** & .47*** & - & 2.66 & 0.83\\
-21.
-onet.hindrance.sc & -.13** & -.15*** & -.13** & -.19*** & -.13** & -.09* & -.23*** & -.12** & -.10* & -.05 & -.16*** & -.12** & -.01 & -.17*** & .62*** & .62*** & .56*** & .64*** & .66*** & .45*** & 2.64 & 0.80\\
-\bottomrule
-\addlinespace
-\insertTableNotes
-\end{longtable}
-
-}
-
-\end{lltable}
 

### 2023-12-26 Submission.Rmd
adding figure

@@
 #documentclass     : "apa7" #interact
-classoption       : "jou"
+classoption       : "man"
 output            : papaja::apa6_pdf
@@
 
+```{r reproduced, echo=FALSE, fig.cap="LePine (2022) revised challenge-stress-appraisal framework."}
+library(magick)
+library(grid)
+
+figure <- image_read("Reproduced_LepineFigure.png")
+
+grid.raster(figure)
+```
+
 Prior to considering the subsequent empirical work on this topic, it is of value to explore *why* different outcomes are expected with these forms of demands.
@@
 This happens because resources are depleted via frustrations and other affectively negative reactions [@lepine2022challenge].
+The theoretical associations that drive the current study's purpose are presented in Figure \@ref(fig:reproduced), which has been reproduced from @lepine2022challenge.
 

### 2023-12-26 Submission.tex
adding figure

@@
 \documentclass[
-  jou,mask]{apa6}
+  man,mask]{apa6}
 \usepackage{amsmath,amssymb}
@@
 \keywords{O*Net, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: 4,942}
-\usepackage{dblfloatfix}
-
+\DeclareDelayedFloatFlavor{ThreePartTable}{table}
+\DeclareDelayedFloatFlavor{lltable}{table}
+\DeclareDelayedFloatFlavor*{longtable}{table}
+\makeatletter
+\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
+\makeatother
 \usepackage{csquotes}
@@
 
+\begin{figure}
+\centering
+\includegraphics{Submission_files/figure-latex/reproduced-1.pdf}
+\caption{\label{fig:reproduced}LePine (2022) revised challenge-stress-appraisal framework.}
+\end{figure}
+
 Prior to considering the subsequent empirical work on this topic, it is of value to explore \emph{why} different outcomes are expected with these forms of demands.
@@
 LePine, 2022).
+The theoretical associations that drive the current study's purpose are presented in Figure \ref{fig:reproduced}, which has been reproduced from M.
+A.
+LePine (2022).
 

### 2023-12-26 Submission.Rmd
copyedited format
new abstract

--- 2023-12-12 Submission.Rmd
@@
   Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands.
-We build on an oppositional literature positing that *individual differences* matter in our perceptions of characteristics as demands and resources.
 Our primary aim was to document the degree of variability in subjective ratings of job characteristics with respect to interpretation as resource and demand.
 Secondarily, we quantify the degree to which perceptions match the literature-implicated resources/demands of job characteristics.
-Procedurally, an exhaustive list of O\*NET work characteristics were rated by 568 employed respondents in terms of relevance, perception as a demand, and perception as a resource.
-Job characteristics were not commonly categorized as solely resource or demand - rather, job resources were also frequently viewed as challenging demands.
-**sentence about lit-implied demands/resources**.
-**sentence about implications for job design**.
+O*NET work characteristics were rated by 568 employed respondents.
+Job characteristics were not commonly categorized as solely resource or demand.
+Rather, job resources were also frequently viewed as challenging demands.
+These findings have implications for job design.
 
@@
 
+```{r reproduced, echo=FALSE, fig.cap="LePine's (2022) revised challenge-hindrance stressor framework."}
+library(magick)
+library(grid)
+
+figure <- image_read("Reproduced_LepineFigure.png")
+
+grid.raster(figure) # works well with margins/etc
+
+```
+
 Prior to considering the subsequent empirical work on this topic, it is of value to explore *why* different outcomes are expected with these forms of demands.

### 2023-12-26 Submission.tex
new abstract

@@
 Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands.
-We build on an oppositional literature positing that \emph{individual differences} matter in our perceptions of characteristics as demands and resources.
 Our primary aim was to document the degree of variability in subjective ratings of job characteristics with respect to interpretation as resource and demand.
 Secondarily, we quantify the degree to which perceptions match the literature-implicated resources/demands of job characteristics.
-Procedurally, an exhaustive list of O*NET work characteristics were rated by 568 employed respondents in terms of relevance, perception as a demand, and perception as a resource.
-Job characteristics were not commonly categorized as solely resource or demand - rather, job resources were also frequently viewed as challenging demands.
-\textbf{sentence about lit-implied demands/resources}.
-\textbf{sentence about implications for job design}.
+O*NET work characteristics were rated by 568 employed respondents.
+Job characteristics were not commonly categorized as solely resource or demand.
+Rather, job resources were also frequently viewed as challenging demands.
+These findings have implications for job design.
 }
@@
 \includegraphics{Submission_files/figure-latex/reproduced-1.pdf}
-\caption{\label{fig:reproduced}LePine (2022) revised challenge-stress-appraisal framework.}
+\caption{\label{fig:reproduced}LePine's (2022) revised challenge-hindrance stressor framework.}
 \end{figure}

### 2023-12-30 Submission.Rmd
abstract stuff

@@
 ---
-title             : "Subjectivity of Job Demands and Resources through the comprehensive framework of O*NET"
+title             : "Subjective Experience of Demands and Resources across O*NET Job Elements"
 shorttitle        : "O*NET JD-R"
@@
 Rather, job resources were also frequently viewed as challenging demands.
-These findings have implications for job design.
+These findings have implications for job design and administration - resource-laden elements may also be interpreted by workers as demands.
 

### 2023-12-30 Submission.tex
abstract stuff

@@
 
-% \usepackage{etoolbox}
 \makeatletter
-\patchcmd{\HyOrg@maketitle}
+\usepackage{etoolbox}
+\patchcmd{\maketitle}
   {\section{\normalfont\normalsize\abstractname}}
@@
   {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
+\patchcmd{\maketitle}
   {\section{\protect\normalfont{\@title}}}
@@
 \hypersetup{
-  pdftitle={Subjectivity of Job Demands and Resources through the comprehensive framework of O*NET},
+  pdftitle={Subjective Experience of Demands and Resources across O*NET Job Elements},
   pdflang={en-EN},
@@
 
-\title{Subjectivity of Job Demands and Resources through the comprehensive framework of O*NET}
+\title{Subjective Experience of Demands and Resources across O*NET Job Elements}
 \author{Alicia Stachowski\textsuperscript{2}, John Kulas\textsuperscript{1}, \& Renata García Prieto Palacios Roji\textsuperscript{3}}
@@
 Rather, job resources were also frequently viewed as challenging demands.
-These findings have implications for job design.
+These findings have implications for job design and administration - resource-laden elements may also be interpreted by workers as demands.
 }

### 2023-12-30 Submission.Rmd
reworked intro to intro but nothing else

@@
 Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlights the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance, among other outcomes.
-However, much of our existing knowledge regarding the way this model functions is grounded in the assumption that job characteristics are generally considered resources or generally considered demands.
+However, much of our existing knowledge regarding the way this model functions is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands.
 We build on the work of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges].
@@
 *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [e.g., high work pressure is frequently cited as a common demand; @demerouti2001job].
-Cognitively, the perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation [resulting from resources; @bakker2014job].
-Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience despite the typical *a priori* assignment of a characteristic as objectively a "demand" or "resource".
+In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; @demerouti2001job).
+The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job).
+Of particular importance here is that it is *the perception* of a characteristic or situation that determines which process an employee will experience despite the *a priori* objective assumption of a characteristic as objectively a "demand" or "resource".
 We explore this further below.
@@
 
-As described above, job context and characteristics are assigned or appraised as demands or resources.
-Although much of our research on job demands in particular is based on *a priori* classifications [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand).
+Although much of our research on job demands in particular is based on *a priori* classifications [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
 The stress process speaks to how such individual difference in appraisal is possible.

### 2023-12-30 Submission.tex
reworked intro to intro but nothing else

@@
 Research on the job demands-resources model (Demerouti et al., 2001) and later job demands-resources theory (Bakker \& Demerouti, 2017) highlights the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance, among other outcomes.
-However, much of our existing knowledge regarding the way this model functions is grounded in the assumption that job characteristics are generally considered resources or generally considered demands.
+However, much of our existing knowledge regarding the way this model functions is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands.
 We build on the work of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020).
@@
 \emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain {[}e.g., high work pressure is frequently cited as a common demand; Demerouti et al.
-(2001){]}.
-Cognitively, the perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation {[}resulting from resources; Bakker and Demerouti (2014){]}.
-Of particular importance here is that it is the perception of a characteristic or situation determines which process an employee will experience despite the typical \emph{a priori} assignment of a characteristic as objectively a ``demand'' or ``resource''.
+In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; Demerouti et al.
+(2001)).
+The perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; Bakker and Demerouti (2014)).
+Of particular importance here is that it is \emph{the perception} of a characteristic or situation that determines which process an employee will experience despite the \emph{a priori} objective assumption of a characteristic as objectively a ``demand'' or ``resource''.
 We explore this further below.
@@
 
-As described above, job context and characteristics are assigned or appraised as demands or resources.
-Although much of our research on job demands in particular is based on \emph{a priori} classifications (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand).
+Although much of our research on job demands in particular is based on \emph{a priori} classifications (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
 The stress process speaks to how such individual difference in appraisal is possible.

### 2024-01-02 Submission.Rmd
updating documents for submission to work and occupations
linked figures

@@
 classoption       : "man"
+#output            : "word_document"
 output            : papaja::apa6_pdf
@@
 We explore this hypothesis first at the job characteristic level before presenting a broader perspective.
-Figures 1 and 2 present only extreme snapshots of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency.
-Figure 1 presents the resources, challenges, and hindrances that are *most consistently agreed on* as indexed by (relatively) low standard deviations, while Figure 2 presents the characteristics with the greatest amount of *disagreement* across workers.
+Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present only extreme snapshots of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency.
+Figure \@ref(fig:combinegraphs) presents the resources, challenges, and hindrances that are *most consistently agreed on* as indexed by (relatively) low standard deviations, while Figure \@ref(fig:combinegraphs2) presents the characteristics with the greatest amount of *disagreement* across workers.
 The figures demonstrate that what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
@@
  [^onlinelist]: A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
-The Figures 1 and 2  presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).
+The Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).
 
-In addition to highlighting extremely agreed- or disagreed-upon items, Figure 3 presents our standard deviation indices across all rated items.
-Here, the Figure 1 discrepancies receive greater context, with the *spread* of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively *bunched* levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
+In addition to highlighting extremely agreed- or disagreed-upon items, Figure \@ref(fig:overallhist) presents our standard deviation indices across all rated items.
+Here, the Figure \@ref(fig:combinegraphs) discrepancies receive greater context, with the *spread* of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively *bunched* levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
 Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
@@
 
-Figure 4 presents these comparisons visually, where the bar lengths represent mean ratings within element category (e.g., the white bar represents mean O\*Net resource ratings for a given JD-R element).
-First exploring the right side of Figure 4, there is a pattern of the highest level ratings being those of literature-derived resources (e.g., job control).
-As described above, the left side of Figure 4 shows literature-derived demand categories (e.g., work pressure).
+Figure \@ref(fig:scalelevelgraphs) presents these comparisons visually, where the bar lengths represent mean ratings within element category (e.g., the white bar represents mean O\*Net resource ratings for a given JD-R element).
+First exploring the right side of Figure \@ref(fig:scalelevelgraphs), there is a pattern of the highest level ratings being those of literature-derived resources (e.g., job control).
+As described above, the left side of Figure \@ref(fig:scalelevelgraphs) shows literature-derived demand categories (e.g., work pressure).
 However, in contrast, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as "high" gray and black bars and "low" white bars).
@@
 
-Repeated-measures ANOVAs were computed to further explain each of the patterns observed descriptively in Figure 4.
+Repeated-measures ANOVAs were computed to further explain each of the patterns observed descriptively in Figure \@ref(fig:scalelevelgraphs).
 The effect for Job Control was $F_{(`r report7$ANOVA$DFn`, `r report7$ANOVA$DFd`)}$ = `r report7$ANOVA$F` ($\eta^2$ = `r report7$ANOVA$pes`).
@@
 Here, the pattern was as expected.
-Across categories, resources were rated the highest (see white bars representing resources in Figure 4).
+Across categories, resources were rated the highest (see white bars representing resources in Figure \@ref(fig:scalelevelgraphs)).
 However, as can be seen, mean challenge (which is a demand) was rated quite similarly and above the midpoint of 3 across JD-R categories.
@@
 
-Next, repeated-measures ANOVAs were also run for the group of literature-implicated *demands* (see the left hand side of Figure 4).
+Next, repeated-measures ANOVAs were also run for the group of literature-implicated *demands* (see the left hand side of Figure \@ref(fig:scalelevelgraphs)).
 The effect for Overwork was $F_{(`r report1$ANOVA$DFn`, `r report1$ANOVA$DFd`)}$ = `r report1$ANOVA$F` ($\eta^2$ was `r report1$ANOVA$pes`).
@@
 Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance.
-See the pattern of white resource bars on the left hand side of Figure 4.
+See the pattern of white resource bars on the left hand side of Figure \@ref(fig:scalelevelgraphs).
 In other words, demands are viewed as resources.

### 2024-01-02 Submission.tex
linked figures

@@
 
+% \usepackage{etoolbox}
 \makeatletter
-\usepackage{etoolbox}
-\patchcmd{\maketitle}
+\patchcmd{\HyOrg@maketitle}
   {\section{\normalfont\normalsize\abstractname}}
@@
   {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\maketitle}
+\patchcmd{\HyOrg@maketitle}
   {\section{\protect\normalfont{\@title}}}
@@
 We explore this hypothesis first at the job characteristic level before presenting a broader perspective.
-Figures 1 and 2 present only extreme snapshots of characteristic variability in the form of the 8-most \emph{consistently rated} and \emph{inconsistently rated} resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
-The Figures 1 and 2 presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency.
-Figure 1 presents the resources, challenges, and hindrances that are \emph{most consistently agreed on} as indexed by (relatively) low standard deviations, while Figure 2 presents the characteristics with the greatest amount of \emph{disagreement} across workers.
+Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present only extreme snapshots of characteristic variability in the form of the 8-most \emph{consistently rated} and \emph{inconsistently rated} resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
+The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency.
+Figure \ref{fig:combinegraphs} presents the resources, challenges, and hindrances that are \emph{most consistently agreed on} as indexed by (relatively) low standard deviations, while Figure \ref{fig:combinegraphs2} presents the characteristics with the greatest amount of \emph{disagreement} across workers.
 The figures demonstrate that what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
@@
 
-In addition to highlighting extremely agreed- or disagreed-upon items, Figure 3 presents our standard deviation indices across all rated items.
-Here, the Figure 1 discrepancies receive greater context, with the \emph{spread} of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively \emph{bunched} levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
+In addition to highlighting extremely agreed- or disagreed-upon items, Figure \ref{fig:overallhist} presents our standard deviation indices across all rated items.
+Here, the Figure \ref{fig:combinegraphs} discrepancies receive greater context, with the \emph{spread} of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively \emph{bunched} levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
 Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
@@
 
-Figure 4 presents these comparisons visually, where the bar lengths represent mean ratings within element category (e.g., the white bar represents mean O*Net resource ratings for a given JD-R element).
-First exploring the right side of Figure 4, there is a pattern of the highest level ratings being those of literature-derived resources (e.g., job control).
-As described above, the left side of Figure 4 shows literature-derived demand categories (e.g., work pressure).
+Figure \ref{fig:scalelevelgraphs} presents these comparisons visually, where the bar lengths represent mean ratings within element category (e.g., the white bar represents mean O*Net resource ratings for a given JD-R element).
+First exploring the right side of Figure \ref{fig:scalelevelgraphs}, there is a pattern of the highest level ratings being those of literature-derived resources (e.g., job control).
+As described above, the left side of Figure \ref{fig:scalelevelgraphs} shows literature-derived demand categories (e.g., work pressure).
 However, in contrast, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as ``high'' gray and black bars and ``low'' white bars).
@@
 
-Repeated-measures ANOVAs were computed to further explain each of the patterns observed descriptively in Figure 4. The effect for Job Control was \(F_{(2, 1134)}\) = 52.78 (\(\eta^2\) = 0.08).
+Repeated-measures ANOVAs were computed to further explain each of the patterns observed descriptively in Figure \ref{fig:scalelevelgraphs}.
+The effect for Job Control was \(F_{(2, 1134)}\) = 52.78 (\(\eta^2\) = 0.08).
 The effect for Participation was \(F_{(2, 1124)}\) = 991.16 (\(\eta^2\) = 0.64).
@@
 Here, the pattern was as expected.
-Across categories, resources were rated the highest (see white bars representing resources in Figure 4).
+Across categories, resources were rated the highest (see white bars representing resources in Figure \ref{fig:scalelevelgraphs}).
 However, as can be seen, mean challenge (which is a demand) was rated quite similarly and above the midpoint of 3 across JD-R categories.
@@
 
-Next, repeated-measures ANOVAs were also run for the group of literature-implicated \emph{demands} (see the left hand side of Figure 4).
+Next, repeated-measures ANOVAs were also run for the group of literature-implicated \emph{demands} (see the left hand side of Figure \ref{fig:scalelevelgraphs}).
 The effect for Overwork was \(F_{(2, 1134)}\) = 17.71 (\(\eta^2\) was 0.03).
@@
 Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance.
-See the pattern of white resource bars on the left hand side of Figure 4.
+See the pattern of white resource bars on the left hand side of Figure \ref{fig:scalelevelgraphs}.
 In other words, demands are viewed as resources.

### 2024-01-04 Submission.Rmd
updating figure references
reworking intro

@@
   Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands.
-Our primary aim was to document the degree of variability in subjective ratings of job characteristics with respect to interpretation as resource and demand.
-Secondarily, we quantify the degree to which perceptions match the literature-implicated resources/demands of job characteristics.
-O*NET work characteristics were rated by 568 employed respondents.
+This study documents the degree of variability in subjective ratings of job characteristics with respect to interpretation as resource and demand.
+Next, we quantify the degree to which perceptions match the literature-implicated resources/demands of job characteristics and also document associations with stress, burnout, and engagement.
 Job characteristics were not commonly categorized as solely resource or demand.
 Rather, job resources were also frequently viewed as challenging demands.
+OUTCOME VARIABLE INFORMATION HERE.
 These findings have implications for job design and administration - resource-laden elements may also be interpreted by workers as demands.
@@
 #documentclass     : "apa7" #interact
-classoption       : "man"
+classoption       : "jou"
 #output            : "word_document"
@@
 
-Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlights the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance, among other outcomes.
-However, much of our existing knowledge regarding the way this model functions is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands.
-We build on the work of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges].
-We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resources) in the workplace, with a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
+Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes.
+However, much of our existing knowledge regarding the way these relationships function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands.
+We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges], with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
 Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.
@@
 
-The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model [@demerouti2001job].
-One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands.
 *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; @demerouti2001job).
+In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is commonly cited as a demand; @demerouti2001job).
 The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job).
@@
 
-Although much of our research on job demands in particular is based on *a priori* classifications [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
-The stress process speaks to how such individual difference in appraisal is possible.
-@lazarus1984stress presented the transactional theory of stress and coping, which states that people cognitively appraise stimuli in their environments on a continuous basis.
-Via this process, meaning is assigned to stimuli based on potential for gain or loss.
-If appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping.
-The cycle of appraisal then continues based on the action to cope with the stressor [@lazarus1984stress].
-Coping is considered a secondary appraisal and is the way that someone chooses to manage a stressor.
-Although not suggested by the names, primary and secondary appraisals can happen simultaneously.
-For instance, available resources to cope with a stressor may influence an employee’s initial appraisal of a stressor (e.g., amount of time [resource] available to prepare for the speech may influence one’s primary appraisal of this task).
+Although much of our research on job demands based on a priori classifications [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
+@lazarus1984stress's transactional theory of stress and coping suggests that people cognitively appraise stimuli in their environments on a continual basis.
+If a task or situation is appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates a coping response.
+These primary and secondary appraisals can happen simultaneously.
+For example, perceiving ample resources to cope with a stressor may influence an employee’s initial appraisal of a stressor (e.g., amount of time [resource] available to prepare for the speech may influence one’s primary appraisal of this task).
 
@@
 
-Although there is a tendency to attach a negative connotation to the word “stress”, @selye1936syndrome defined stress as simple a response to change.
-We return to the public figure for this next section.
-Consider two employees be called upon to serve as spokespeople for their organization.
-One may appraise the circumstance as an opportunity to positively influence others, while the other may feel daunted by the task.
+Demand --> appraisal (as challenge or hindrance)
 
-The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor [@cavanaugh2000empirical], in line with @lazarus1984stress.
-@cavanaugh2000empirical delineated between two forms of demands – that of *challenge* and *hindrance* demands.
+Demand=Stressor
+
+Decision (can overcome or not )
+
+@cavanaugh2000empirical delineated between two forms of demands -- *challenges* and *hindrances*.
+Both are considered stressors [e.g., @cavanaugh2000empirical].
 Challenge demands promote mastery, personal growth, and future gains – these stressors should lead to coping strategies that facilitate achievement.
-Stressors like time pressure and responsibility are considered challenge stressors/demands.
+Work characteristics consistent with this definition include time pressure and responsibility.
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Hindrance stressors (e.g., role conflict, role ambiguity, politics) are associated with negative job behaviors and attitudes.
-This distinction between challenges and hindrances has been of value in determining which demands are related to various outcomes.
+Hindrance stressors in a work context include role conflict, role ambiguity, and organizational politics.
 The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes [e.g., @cavanaugh2000empirical].
 
-```{r reproduced, echo=FALSE, fig.cap="LePine's (2022) revised challenge-hindrance stressor framework."}
+```{r reproduced, eval=FALSE, echo=FALSE, fig.cap="Going to put in new comprehensive picture."}
 library(magick)
@@
 
-Prior to considering the subsequent empirical work on this topic, it is of value to explore *why* different outcomes are expected with these forms of demands.
 @lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes.
-Similar to the job-demands resources theory [@bakker2017job], challenge and hindrance demands elicit two different paths or processes.
-First, challenge stressors typically result in a challenge appraisal, and engagement is likely to happen as a result.
+First, stressors appraised as challenges typically result in a challenge appraisal, and engagement is likely to happen as a result.
 Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing.
 Of note is that this energy may be depleted eventually, leading to strain.
-Hindrance stressors elicit a different process.
+Stressors appraised as hindrances elicit a different process.
 Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing.
@@
 Thus, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.
+COMBINE 1 and 2:
 
@@
 
-Two exploratory questions further address whether our *literature-implicated* resources (e.g., autonomy) and demands are consistently rated as our research models suggest across the job-demands resources theory [@bakker2017job] and challenge-hindrance stressor framework [@cavanaugh2000empirical].
+>Hyp 3: Are these perceptions aligned with the literature's presentation of job characteristics?
 
->*Research Question 1*: Do literature-implicated resources materialize as perceived resources?
+The second set of analyses focuses on associations. Do demands and resources have implications for work outcomes?
 
->*Research Question 2*: Do literature-implicated demands materialize as job demands?
+>Hyp 4.a: Job resources are associated with greater engagement, less stress, and less burnout. 
+>Hyp 4.b: More hindrances leads to less engagement, more stress, and greater burnout.
+
+>Hyp 4.exploratory: More challenges leads to greater satisfaction, engagement, and burnout.
 
@@
 a <- ggplot(topresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
-  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Agreed Upon as a Resource") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))
+  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Consensus as a Resource") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))
 
@@
 b <- ggplot(topchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
-  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Agreed Upon as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))
+  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Consensus as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))
 
@@
 c <- ggplot(tophindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
-  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Agreed upon as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))
+  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Most Consensus as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))
 
@@
 d <- ggplot(bottomresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
-  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed Upon as a Resource") + 
+  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Lack of Consensus as a Resource") + 
   geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
@@
 e <- ggplot(bottomchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
-  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed Upon as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
+  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Lack of Consensus as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
 
@@
 f <- ggplot(bottomhindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
-  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Least Agreed upon as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
+  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Lack of Consensus as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
 
@@
 When people perceived hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.
-Taken with the Figure 3 takeaway, this hints that workers are likely either generally experiencing hindrances at work or they are not.
+Taken with the Figure \@ref(fig:scalelevelgraphs) takeaway, this hints that workers are likely either generally experiencing hindrances at work or they are not.
 
@@
 While resources and challenges idiosyncratic more similarly experienced, what is experienced as a hindrance tends to be idiosyncratic.
+
 ```{r}
@@
 ```
-
-\newpage
 

### 2024-01-04 Submission.tex
updating figure references
reworking intro

@@
 \documentclass[
-  man,mask]{apa6}
+  jou,mask]{apa6}
 \usepackage{amsmath,amssymb}
@@
 Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands.
-Our primary aim was to document the degree of variability in subjective ratings of job characteristics with respect to interpretation as resource and demand.
-Secondarily, we quantify the degree to which perceptions match the literature-implicated resources/demands of job characteristics.
-O*NET work characteristics were rated by 568 employed respondents.
+This study documents the degree of variability in subjective ratings of job characteristics with respect to interpretation as resource and demand.
+Next, we quantify the degree to which perceptions match the literature-implicated resources/demands of job characteristics and also document associations with stress, burnout, and engagement.
 Job characteristics were not commonly categorized as solely resource or demand.
 Rather, job resources were also frequently viewed as challenging demands.
+OUTCOME VARIABLE INFORMATION HERE.
 These findings have implications for job design and administration - resource-laden elements may also be interpreted by workers as demands.
@@
 
-Research on the job demands-resources model (Demerouti et al., 2001) and later job demands-resources theory (Bakker \& Demerouti, 2017) highlights the importance of work characteristics on the experience of motivation and strain, which subsequently have an impact on job performance, among other outcomes.
-However, much of our existing knowledge regarding the way this model functions is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands.
-We build on the work of a small, but growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020).
-We extend this critical research to that of the subjective distinction between challenge and hindrance demands (and resources) in the workplace, with a primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
+Research on the job demands-resources model (Demerouti et al., 2001) and later job demands-resources theory (Bakker \& Demerouti, 2017) highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes.
+However, much of our existing knowledge regarding the way these relationships function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands.
+We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020), with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
 Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.
@@
 
-The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model (Demerouti et al., 2001).
-One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands.
 \emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; Demerouti et al.
+In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is commonly cited as a demand; Demerouti et al.
 (2001)).
@@
 
-Although much of our research on job demands in particular is based on \emph{a priori} classifications (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
-The stress process speaks to how such individual difference in appraisal is possible.
-Lazarus and Folkman (1984) presented the transactional theory of stress and coping, which states that people cognitively appraise stimuli in their environments on a continuous basis.
-Via this process, meaning is assigned to stimuli based on potential for gain or loss.
-If appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping.
-The cycle of appraisal then continues based on the action to cope with the stressor (Lazarus \& Folkman, 1984).
-Coping is considered a secondary appraisal and is the way that someone chooses to manage a stressor.
-Although not suggested by the names, primary and secondary appraisals can happen simultaneously.
-For instance, available resources to cope with a stressor may influence an employee's initial appraisal of a stressor (e.g., amount of time {[}resource{]} available to prepare for the speech may influence one's primary appraisal of this task).
+Although much of our research on job demands based on a priori classifications (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
+Lazarus and Folkman (1984)'s transactional theory of stress and coping suggests that people cognitively appraise stimuli in their environments on a continual basis.
+If a task or situation is appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates a coping response.
+These primary and secondary appraisals can happen simultaneously.
+For example, perceiving ample resources to cope with a stressor may influence an employee's initial appraisal of a stressor (e.g., amount of time {[}resource{]} available to prepare for the speech may influence one's primary appraisal of this task).
 
@@
 
-Although there is a tendency to attach a negative connotation to the word ``stress'', Selye (1936) defined stress as simple a response to change.
-We return to the public figure for this next section.
-Consider two employees be called upon to serve as spokespeople for their organization.
-One may appraise the circumstance as an opportunity to positively influence others, while the other may feel daunted by the task.
+Demand --\textgreater{} appraisal (as challenge or hindrance)
 
-The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor (Cavanaugh et al., 2000), in line with Lazarus and Folkman (1984).
+Demand=Stressor
+
+Decision (can overcome or not )
+
 Cavanaugh et al.
-(2000) delineated between two forms of demands -- that of \emph{challenge} and \emph{hindrance} demands.
+(2000) delineated between two forms of demands -- \emph{challenges} and \emph{hindrances}.
+Both are considered stressors (e.g., Cavanaugh et al., 2000).
 Challenge demands promote mastery, personal growth, and future gains -- these stressors should lead to coping strategies that facilitate achievement.
-Stressors like time pressure and responsibility are considered challenge stressors/demands.
+Work characteristics consistent with this definition include time pressure and responsibility.
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Hindrance stressors (e.g., role conflict, role ambiguity, politics) are associated with negative job behaviors and attitudes.
-This distinction between challenges and hindrances has been of value in determining which demands are related to various outcomes.
+Hindrance stressors in a work context include role conflict, role ambiguity, and organizational politics.
 The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes (e.g., Cavanaugh et al., 2000).
 
-\begin{figure}
-\centering
-\includegraphics{Submission_files/figure-latex/reproduced-1.pdf}
-\caption{\label{fig:reproduced}LePine's (2022) revised challenge-hindrance stressor framework.}
-\end{figure}
-
-Prior to considering the subsequent empirical work on this topic, it is of value to explore \emph{why} different outcomes are expected with these forms of demands.
 M.
@@
 LePine (2022) explain the mechanisms by which demands are related to performance and wellbeing outcomes.
-Similar to the job-demands resources theory (Bakker \& Demerouti, 2017), challenge and hindrance demands elicit two different paths or processes.
-First, challenge stressors typically result in a challenge appraisal, and engagement is likely to happen as a result.
+First, stressors appraised as challenges typically result in a challenge appraisal, and engagement is likely to happen as a result.
 Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing.
 Of note is that this energy may be depleted eventually, leading to strain.
-Hindrance stressors elicit a different process.
+Stressors appraised as hindrances elicit a different process.
 Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing.
@@
 
-Two exploratory questions further address whether our \emph{literature-implicated} resources (e.g., autonomy) and demands are consistently rated as our research models suggest across the job-demands resources theory (Bakker \& Demerouti, 2017) and challenge-hindrance stressor framework (Cavanaugh et al., 2000).
+\begin{quote}
+Hyp 3: Are these perceptions aligned with the literature's presentation of job characteristics?
+\end{quote}
+
+The second set of analyses focuses on associations. Do demands and resources have implications for work outcomes?
 
 \begin{quote}
-\emph{Research Question 1}: Do literature-implicated resources materialize as perceived resources?
+Hyp 4.a: Job resources are associated with greater engagement, less stress, and less burnout.
+Hyp 4.b: More hindrances leads to less engagement, more stress, and greater burnout.
 \end{quote}
@@
 \begin{quote}
-\emph{Research Question 2}: Do literature-implicated demands materialize as job demands?
+Hyp 4.exploratory: More challenges leads to greater satisfaction, engagement, and burnout.
 \end{quote}
@@
 When people perceived hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.
-Taken with the Figure 3 takeaway, this hints that workers are likely either generally experiencing hindrances at work or they are not.
+Taken with the Figure \ref{fig:scalelevelgraphs} takeaway, this hints that workers are likely either generally experiencing hindrances at work or they are not.
 
@@
 While resources and challenges idiosyncratic more similarly experienced, what is experienced as a hindrance tends to be idiosyncratic.
-
-\newpage
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-selye1936syndrome}{}}%
-Selye, H. (1936). A syndrome produced by diverse nocuous agents. \emph{Nature}, \emph{138}(3479), 32--32.
-
 \leavevmode\vadjust pre{\hypertarget{ref-webster2010toward}{}}%

### 2024-02-09 Submission.tex
desktop edits

@@
 \maketitle
+
+Outline:
+Work toward model (picture)
+
+I. Appraisals
+a. JD-R
+b. Challenge-hindrance framework
+1. combine the two (maybe Crawford, LePine \& Rich, 2010)
+II. Antecedents (job elements)
+a. O*Net - comprehensive
+III. Consequences (outcomes)
+a. Moderation
 
@@
 Thus, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.
+
+\begin{figure}
+\centering
+\includegraphics{Submission_files/figure-latex/ourmodel-1.pdf}
+\caption{\label{fig:ourmodel}This is our working model}
+\end{figure}
+
+Our model is represented in Figure \ref{fig:ourmodel}
+
 COMBINE 1 and 2:

### 2024-02-24 Submission.Rmd
desktop edits
small edits
coffee shop edits - shift focus to CH (from JDR)

@@
 
+Outline:
+Work toward model (picture)
+
++ Challenge-hindrance framework
+  + Cavanaugh (~2000)
+  + Last 20 years' research (variance - look at Pindek et al, 2024)
+  + Appraisals
+
++ Antecedents (job elements)
+  a. O\*Net - comprehensive
+III. Consequences (outcomes)
+  a. Moderation
+IV. Contribution
+  a. include resources
+
 Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes.
@@
 
+## ARGUE FOR H1 and H2 (Are perceptions universal?)
+
+Add resources here
+
 We next consider the empirical evidence on this topic.
@@
 
+>Hypothesis 1: Job characteristics differ in consistancy regarding subjective worker perception as a demand or resource.
+
+>Hypothesis 2: Job characteristics are not exclusively categorized as a resource or demand, but rather, some job characteristics are viewed as both a resource and a demand.
+
+## Connecting appraisals to workplace outcomes[^thought]
+
+[^thought]: add a sentence that adds a brief description of working conditions to first paragraph. Whole section needs expansion.
+
+The second set of analyses focuses on associations.
+Do demands and resources have implications for work outcomes?
 Appraisals are associated with different forms of coping, and subsequently, outcomes.
+See Figure 1 for proposed associations.
 The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing.
@@
 Thus, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.
-COMBINE 1 and 2:
 
->Hypothesis 1: Job characteristics differ in consistancy regarding subjective worker perception as a demand or resource.
+```{r ourmodel, eval=TRUE, echo=FALSE, fig.cap="This is our working model"}
+library(magick)
+library(grid)
 
->Hypothesis 2: Job characteristics are not exclusively categorized as a resource or demand, but rather, some job characteristics are viewed as both a resource and a demand.
+figure2 <- image_read("ourmodel.png")
 
->Hyp 3: Are these perceptions aligned with the literature's presentation of job characteristics?
+grid.raster(figure2) # works well with margins/etc
 
-The second set of analyses focuses on associations. Do demands and resources have implications for work outcomes?
+```
 
->Hyp 4.a: Job resources are associated with greater engagement, less stress, and less burnout. 
->Hyp 4.b: More hindrances leads to less engagement, more stress, and greater burnout.
+Our model is represented in Figure \@ref(fig:ourmodel)
 
->Hyp 4.exploratory: More challenges leads to greater satisfaction, engagement, and burnout.
+>Hyp 3.a: Job resources are associated with greater engagement, less stress, and less burnout.
+
+>Hyp 3.b: More hindrances leads to less engagement, more stress, and greater burnout.
+
+>Hyp 3.exploratory: More challenges leads to greater satisfaction, engagement, and burnout.[^figure]
+
+[^figure]: These need to be reframed to match Figure 1.
 
@@
 
+Cross-sectional
+
 As with all individual studies, this project was limited in scope, and as such, there are a number of avenues for future study worth exploring.

### 2024-02-24 Submission.tex
small edits
coffee shop edits - shift focus to CH (from JDR)

--- 2024-01-04 Submission.tex
@@
 
+Outline:
+Work toward model (picture)
+
+\begin{itemize}
+\tightlist
+\item
+  Challenge-hindrance framework
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Cavanaugh (\textasciitilde2000)
+  \item
+    Last 20 years' research (variance - look at Pindek et al, 2024)
+  \item
+    Appraisals
+  \end{itemize}
+\item
+  Antecedents (job elements)
+
+  \begin{enumerate}
+  \def\labelenumi{\alph{enumi}.}
+  \tightlist
+  \item
+    O*Net - comprehensive
+  \end{enumerate}
+\end{itemize}
+
+\begin{enumerate}
+\def\labelenumi{\Roman{enumi}.}
+\setcounter{enumi}{2}
+\tightlist
+\item
+  Consequences (outcomes)
+\end{enumerate}
+
+\begin{enumerate}
+\def\labelenumi{\alph{enumi}.}
+\tightlist
+\item
+  Moderation
+\end{enumerate}
+
+\begin{enumerate}
+\def\labelenumi{\Roman{enumi}.}
+\setcounter{enumi}{3}
+\tightlist
+\item
+  Contribution
+\end{enumerate}
+
+\begin{enumerate}
+\def\labelenumi{\alph{enumi}.}
+\tightlist
+\item
+  include resources
+\end{enumerate}
+
 Research on the job demands-resources model (Demerouti et al., 2001) and later job demands-resources theory (Bakker \& Demerouti, 2017) highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes.
@@
 
+\hypertarget{argue-for-h1-and-h2-are-perceptions-universal}{%
+\subsection{ARGUE FOR H1 and H2 (Are perceptions universal?)}\label{argue-for-h1-and-h2-are-perceptions-universal}}
+
+Add resources here
+
 We next consider the empirical evidence on this topic.
@@
 
+\begin{quote}
+Hypothesis 1: Job characteristics differ in consistancy regarding subjective worker perception as a demand or resource.
+\end{quote}
+
+\begin{quote}
+Hypothesis 2: Job characteristics are not exclusively categorized as a resource or demand, but rather, some job characteristics are viewed as both a resource and a demand.
+\end{quote}
+
+\hypertarget{connecting-appraisals-to-workplace-outcomesthought}{%
+\subsection[Connecting appraisals to workplace outcomes]{\texorpdfstring{Connecting appraisals to workplace outcomes\footnote{add a sentence that adds a brief description of working conditions to first paragraph.
+Whole section needs expansion.}}{Connecting appraisals to workplace outcomes}}\label{connecting-appraisals-to-workplace-outcomesthought}}
+
+The second set of analyses focuses on associations.
+Do demands and resources have implications for work outcomes?
 Appraisals are associated with different forms of coping, and subsequently, outcomes.
+See Figure 1 for proposed associations.
 The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing.
@@
 Thus, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.
-COMBINE 1 and 2:
+
+\begin{figure}
+\centering
+\includegraphics{Submission_files/figure-latex/ourmodel-1.pdf}
+\caption{\label{fig:ourmodel}This is our working model}
+\end{figure}
+
+Our model is represented in Figure \ref{fig:ourmodel}
 
 \begin{quote}
-Hypothesis 1: Job characteristics differ in consistancy regarding subjective worker perception as a demand or resource.
+Hyp 3.a: Job resources are associated with greater engagement, less stress, and less burnout.
 \end{quote}
@@
 \begin{quote}
-Hypothesis 2: Job characteristics are not exclusively categorized as a resource or demand, but rather, some job characteristics are viewed as both a resource and a demand.
+Hyp 3.b: More hindrances leads to less engagement, more stress, and greater burnout.
 \end{quote}
@@
 \begin{quote}
-Hyp 3: Are these perceptions aligned with the literature's presentation of job characteristics?
-\end{quote}
-
-The second set of analyses focuses on associations. Do demands and resources have implications for work outcomes?
-
-\begin{quote}
-Hyp 4.a: Job resources are associated with greater engagement, less stress, and less burnout.
-Hyp 4.b: More hindrances leads to less engagement, more stress, and greater burnout.
-\end{quote}
-
-\begin{quote}
-Hyp 4.exploratory: More challenges leads to greater satisfaction, engagement, and burnout.
+Hyp 3.exploratory: More challenges leads to greater satisfaction, engagement, and burnout.\footnote{These need to be reframed to match Figure 1.}
 \end{quote}

### 2024-02-24 Submission.Rmd
edits

@@
 This happens because resources are depleted via frustrations and other affectively negative reactions [@lepine2022challenge].
-The theoretical associations that drive the current study's purpose are presented in Figure \@ref(fig:reproduced), which has been reproduced from @lepine2022challenge.
 
@@
 
+```{r ourmodel, eval=TRUE, echo=FALSE, fig.cap="This is our working model"}
+library(magick)
+library(grid)
+
+figure2 <- image_read("ourmodel.png")
+
+grid.raster(figure2) # works well with margins/etc
+
+```
+
 ## Connecting appraisals to workplace outcomes[^thought]
@@
 Appraisals are associated with different forms of coping, and subsequently, outcomes.
-See Figure 1 for proposed associations.
+See Figure \@ref(fig:ourmodel) for proposed associations.
 The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing.
@@
 ## Current Study and Hypotheses
-
-The integration of the literature above culminates with two primary hypotheses.
-The first addresses whether employees generally agree on their appraisals of job characteristics as resources or challenge or hindrance demands.
-For instance, although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, others have reported variability in these appraisals [e.g., @lepine2022challenge].
-@lepine2022challenge, in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal.
-Thus, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.
-
-```{r ourmodel, eval=TRUE, echo=FALSE, fig.cap="This is our working model"}
-library(magick)
-library(grid)
-
-figure2 <- image_read("ourmodel.png")
-
-grid.raster(figure2) # works well with margins/etc
-
-```
-
-Our model is represented in Figure \@ref(fig:ourmodel)
 

### 2024-02-24 Submission.tex
edits

@@
 LePine, 2022).
-The theoretical associations that drive the current study's purpose are presented in Figure \ref{fig:reproduced}, which has been reproduced from M.
-A.
-LePine (2022).
 
@@
 
+\begin{figure}
+\centering
+\includegraphics{Submission_files/figure-latex/ourmodel-1.pdf}
+\caption{\label{fig:ourmodel}This is our working model}
+\end{figure}
+
 \hypertarget{connecting-appraisals-to-workplace-outcomesthought}{%
@@
 Appraisals are associated with different forms of coping, and subsequently, outcomes.
-See Figure 1 for proposed associations.
+See Figure \ref{fig:ourmodel} for proposed associations.
 The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing.
@@
 \subsection{Current Study and Hypotheses}\label{current-study-and-hypotheses}}
-
-The integration of the literature above culminates with two primary hypotheses.
-The first addresses whether employees generally agree on their appraisals of job characteristics as resources or challenge or hindrance demands.
-For instance, although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, others have reported variability in these appraisals (e.g., M.
-A.
-LePine, 2022).
-M.
-A.
-LePine (2022), in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal.
-Thus, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.
-
-\begin{figure}
-\centering
-\includegraphics{Submission_files/figure-latex/ourmodel-1.pdf}
-\caption{\label{fig:ourmodel}This is our working model}
-\end{figure}
-
-Our model is represented in Figure \ref{fig:ourmodel}
 

### 2024-02-27 Submission.Rmd
tinkering
Revising introduction to challenge-hindrance framework - beginning

@@
 
-Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes.
-However, much of our existing knowledge regarding the way these relationships function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands.
 We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges], with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
 Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.
-
-## The Job demands-Resources Theory
 
@@
 
-## The Essential Role of Appraisal
+## The Challenge-hindrance Stressor Framework
 
@@
 For example, perceiving ample resources to cope with a stressor may influence an employee’s initial appraisal of a stressor (e.g., amount of time [resource] available to prepare for the speech may influence one’s primary appraisal of this task).
-
-## The Challenge-hindrance Stressor Framework
-
-Demand --> appraisal (as challenge or hindrance)
-
-Demand=Stressor
-
-Decision (can overcome or not )
 
@@
 
-## ARGUE FOR H1 and H2 (Are perceptions universal?)
+## Are Perceptions of Job Resources, Challenge Demands, and Hindrance Demands Universal?
 
@@
 Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time [e.g., @searle2015merits].
-
-## Current Study and Hypotheses
 

### 2024-03-12 Submission.Rmd
updating introduction

@@
 
-We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges], with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
-Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.
+While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular.
+We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges], with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) explore whether these subjective appraisals are differentially related to positive and negative outcomes.
+We utilize the O\*Net database (https://www.onetcenter.org/content.html), which is the primary source of occupational information in the US, and as such, provides a rich source of information about occupational requirements (i.e., work activities and context) that may be rated in terms of level of demand or resource.
+We will refer to these as elements of working conditions throughout this paper (e.g., personal, contextual, or task-related conditions or elements of one's work).
 
+## The Job Demands-Resources Theory and Challenge-hindrance Stressor Framework
+
+Two related theories serve as the foundation for the current study: @demerouti2001job's job demands-resources theory and @cavanaugh2000empirical's later challenge-hindrance stressor framework.
+First, research on the job demands-resources model @demerouti2001job and later job demands-resources theory @bakker2017job highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes.
+The job demands-resources theory distinguishes between resources and demands.
 *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
@@
 The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job).
-Of particular importance here is that it is *the perception* of a characteristic or situation that determines which process an employee will experience despite the *a priori* objective assumption of a characteristic as objectively a "demand" or "resource".
-We explore this further below.
 
-## The Challenge-hindrance Stressor Framework
-
-Although much of our research on job demands based on a priori classifications [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
-@lazarus1984stress's transactional theory of stress and coping suggests that people cognitively appraise stimuli in their environments on a continual basis.
-If a task or situation is appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates a coping response.
-These primary and secondary appraisals can happen simultaneously.
-For example, perceiving ample resources to cope with a stressor may influence an employee’s initial appraisal of a stressor (e.g., amount of time [resource] available to prepare for the speech may influence one’s primary appraisal of this task).
-
-@cavanaugh2000empirical delineated between two forms of demands -- *challenges* and *hindrances*.
+In response to inconsistent findings regarding demands and outcomes, @cavanaugh2000empirical expanded the job demands-resources theory in proposing the challenge-hindrance stressor framework, which draws from @lazarus1984stress's work on stress and coping.
+The challenge-hindrance stressor framework distinguishes between *two forms of demands* -- *challenges* and *hindrances*.
 Both are considered stressors [e.g., @cavanaugh2000empirical].
@@
 Hindrance stressors in a work context include role conflict, role ambiguity, and organizational politics.
-The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes [e.g., @cavanaugh2000empirical].
 
@@
 
+The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes [e.g., @cavanaugh2000empirical].
+Meta-analytic explorations of this the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (e.g., performance; [@lepine2005meta] and engagement, [@crawford2010linking]).
 @lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes.
@@
 This happens because resources are depleted via frustrations and other affectively negative reactions [@lepine2022challenge].
+Recent work affirms this appraisal process.
+@pindek2024dynamic meta-analyzed diary studies of dynamic stressors (i.e., short-term daily experiences of stressors) and concluded that daily challenge stressors had a postive direct association with performance, but a negative indirect association with performance through strain (as described by @lepine2022challenge above).
+As expected, hindrance stressors had both a direct and indirect (through strain) association with performance [@pindek2024dynamic].
 
@@
 
-Add resources here
+Interestingly, much of our existing knowledge regarding the way these relationships between resources/demands and outcomes (e.g., stress, engagement) function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands.
+Even @pindek2024dynamic notes this limitation of a priori classification of characteristics as demands, challenges, or hindrances, as do @horan2020review.
+In fact, although much of our research on job demands based on a priori classifications [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
 
-We next consider the empirical evidence on this topic.
-The first question we should ask is whether people distinguish between challenge vs.
-hindrance demands, or whether all demands are under a larger “demands” category.
-Evidence suggests the employees do, in fact, differentiate between challenge and hindrance stressors [e.g., @bakker2013weekly; @gerich2017relevance; @webster2011extending].
+@horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process described by @lazarus1984stress into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources into our study of the overarching JD-R model.
+In fact, @horan2020review state that “…stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p.
+3).
+They go on to suggest future research continue to move away from *a priori* classifications of stressors, as doing so can be problematic for theoretical and empirical reasons.
+Theoretically, *a priori* classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
+Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time [e.g., @searle2015merits].
+
+As such, the first question we ask is whether people distinguish between resources, challenges, and  hindrances, and whether a job characteristics might even be considered simultaneously as more than one of these (e.g., both a challenge and a resource).
+Evidence suggests the employees do, in fact, differentiate between challenge and hindrance stressors [e.g., @bakker2013weekly; @gerich2017relevance; @webster2011extending], at least.
 For example, @bakker2013weekly found that work pressure was perceived as a hindrance demand, and emotional demands as more of a challenge demand.
@@
 They found while that each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance demand to different degrees.
+We aim to both replicate the above findings and extend them to include resources.
 
->Hypothesis 1: Job characteristics differ in consistancy regarding subjective worker perception as a demand or resource.
+>Hypothesis 1: Job characteristics differ in consistancy regarding subjective worker perception as a challenge or hindrance demand, or resource.
 
 >Hypothesis 2: Job characteristics are not exclusively categorized as a resource or demand, but rather, some job characteristics are viewed as both a resource and a demand.
+
+## Connecting Appraisals to Workplace Outcomes
+
+The second set of analyses focuses on predicted associations without outcomes frequently studied across via job demands-resources @bakker2017job and challenge-hindrance stressor framework @cavanaugh2000empirical.
+Here, we specifically explore O\*Net specified working condition apprasials as resources, challenges, and/or hindrances in association with engagement, strain and burnout.
+As argued above, appraisals are predicted to be associated with different forms of coping, and subsequently, outcomes.
+See Figure \@ref(fig:ourmodel) for proposed associations.
 
@@
 
-## Connecting appraisals to workplace outcomes[^thought]
-
-[^thought]: add a sentence that adds a brief description of working conditions to first paragraph. Whole section needs expansion.
-
-The second set of analyses focuses on associations.
-Do demands and resources have implications for work outcomes?
-Appraisals are associated with different forms of coping, and subsequently, outcomes.
-See Figure \@ref(fig:ourmodel) for proposed associations.
-The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing.
+Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing.
+Beginning with resources ADD JDR STUFF ON RESOURCES AND MOTIVATION HERE.
 A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic.
@@
 Lastly, @gerich2017relevance concluded that employee wellbeing was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
-
-We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point, and a rich collection of them support differential associations across a variety of organizational outcomes as well.
+In addition to the studies above, several meta-analyses also support differential associations across a variety of organizational outcomes as well.
 For example, both challenges and hindrances have been shown to positively predict strain [@lepine2005meta; @podsakoff2007differential; @webster2010toward].
@@
 
-@horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process described by @lazarus1984stress into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources into our study of the overarching JD-R model.
-In fact, @horan2020review state that “…stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p.
-3).
-They go on to suggest future research continue to move away from *a priori* classifications of stressors, as doing so can be problematic for theoretical and empirical reasons.
-Theoretically, *a priori* classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
-Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time [e.g., @searle2015merits].
+>Hyp 3.a: Job resources are positively associated with engagement.
 
->Hyp 3.a: Job resources are associated with greater engagement, less stress, and less burnout.
+>Hyp 3.b: Challenge stressors are positively associated with engagement, strain, and burnout.
 
->Hyp 3.b: More hindrances leads to less engagement, more stress, and greater burnout.
+>Hyp 3.c: Hindrance stressors are negatively associated with strain, and burnout.
 
->Hyp 3.exploratory: More challenges leads to greater satisfaction, engagement, and burnout.[^figure]
+ADD JDR RESOURCES ACT AS A BUFFER INFO HERE ALONG WITH THESE NEW PREDICTIONS
 
-[^figure]: These need to be reframed to match Figure 1.
+>Hyp 4.a:Resources moderate the relationship between challenge stressors and the outcomes of strain and burnout such that these relationship become weaker as workers perceive more resources.
+
+>Hyp 4.b:Resources moderate the relationship between hindrance stressors and the outcomes of strain and burnout such that these relationship become weaker as workers perceive more resources.
 

### 2024-03-12 Submission.tex
tinkering
updating introduction

@@
 
-Research on the job demands-resources model (Demerouti et al., 2001) and later job demands-resources theory (Bakker \& Demerouti, 2017) highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes.
-However, much of our existing knowledge regarding the way these relationships function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands.
-We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020), with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics.
-Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.
+While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular.
+We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020), with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) explore whether these subjective appraisals are differentially related to positive and negative outcomes.
+We utilize the O*Net database (\url{https://www.onetcenter.org/content.html}), which is the primary source of occupational information in the US, and as such, provides a rich source of information about occupational requirements (i.e., work activities and context) that may be rated in terms of level of demand or resource.
+We will refer to these as elements of working conditions throughout this paper (e.g., personal, contextual, or task-related conditions or elements of one's work).
 
-\hypertarget{the-job-demands-resources-theory}{%
-\subsection{The Job demands-Resources Theory}\label{the-job-demands-resources-theory}}
+\hypertarget{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}{%
+\subsection{The Job Demands-Resources Theory and Challenge-hindrance Stressor Framework}\label{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}}
 
+Two related theories serve as the foundation for the current study: Demerouti et al.
+(2001)'s job demands-resources theory and Cavanaugh et al.
+(2000)'s later challenge-hindrance stressor framework.
+First, research on the job demands-resources model Demerouti et al.
+(2001) and later job demands-resources theory Bakker and Demerouti (2017) highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes.
+The job demands-resources theory distinguishes between resources and demands.
 \emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
@@
 The perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; Bakker and Demerouti (2014)).
-Of particular importance here is that it is \emph{the perception} of a characteristic or situation that determines which process an employee will experience despite the \emph{a priori} objective assumption of a characteristic as objectively a ``demand'' or ``resource''.
-We explore this further below.
 
-\hypertarget{the-essential-role-of-appraisal}{%
-\subsection{The Essential Role of Appraisal}\label{the-essential-role-of-appraisal}}
-
-Although much of our research on job demands based on a priori classifications (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
-Lazarus and Folkman (1984)'s transactional theory of stress and coping suggests that people cognitively appraise stimuli in their environments on a continual basis.
-If a task or situation is appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates a coping response.
-These primary and secondary appraisals can happen simultaneously.
-For example, perceiving ample resources to cope with a stressor may influence an employee's initial appraisal of a stressor (e.g., amount of time {[}resource{]} available to prepare for the speech may influence one's primary appraisal of this task).
-
-\hypertarget{the-challenge-hindrance-stressor-framework}{%
-\subsection{The Challenge-hindrance Stressor Framework}\label{the-challenge-hindrance-stressor-framework}}
-
-Demand --\textgreater{} appraisal (as challenge or hindrance)
-
-Demand=Stressor
-
-Decision (can overcome or not )
-
-Cavanaugh et al.
-(2000) delineated between two forms of demands -- \emph{challenges} and \emph{hindrances}.
+In response to inconsistent findings regarding demands and outcomes, Cavanaugh et al.
+(2000) expanded the job demands-resources theory in proposing the challenge-hindrance stressor framework, which draws from Lazarus and Folkman (1984)'s work on stress and coping.
+The challenge-hindrance stressor framework distinguishes between \emph{two forms of demands} -- \emph{challenges} and \emph{hindrances}.
 Both are considered stressors (e.g., Cavanaugh et al., 2000).
@@
 Hindrance stressors in a work context include role conflict, role ambiguity, and organizational politics.
+
 The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes (e.g., Cavanaugh et al., 2000).
-
+Meta-analytic explorations of this the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (e.g., performance; (J.
+A.
+LePine et al., 2005) and engagement, (Crawford et al., 2010)).
 M.
@@
 LePine, 2022).
+Recent work affirms this appraisal process.
+Pindek et al.
+(2024) meta-analyzed diary studies of dynamic stressors (i.e., short-term daily experiences of stressors) and concluded that daily challenge stressors had a postive direct association with performance, but a negative indirect association with performance through strain (as described by M.
+A.
+LePine (2022) above).
+As expected, hindrance stressors had both a direct and indirect (through strain) association with performance (Pindek et al., 2024).
 
-\hypertarget{argue-for-h1-and-h2-are-perceptions-universal}{%
-\subsection{ARGUE FOR H1 and H2 (Are perceptions universal?)}\label{argue-for-h1-and-h2-are-perceptions-universal}}
+\hypertarget{are-perceptions-of-job-resources-challenge-demands-and-hindrance-demands-universal}{%
+\subsection{Are Perceptions of Job Resources, Challenge Demands, and Hindrance Demands Universal?}\label{are-perceptions-of-job-resources-challenge-demands-and-hindrance-demands-universal}}
 
-Add resources here
+Interestingly, much of our existing knowledge regarding the way these relationships between resources/demands and outcomes (e.g., stress, engagement) function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands.
+Even Pindek et al.
+(2024) notes this limitation of a priori classification of characteristics as demands, challenges, or hindrances, as do Horan et al.
+(2020).
+In fact, although much of our research on job demands based on a priori classifications (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
 
-We next consider the empirical evidence on this topic.
-The first question we should ask is whether people distinguish between challenge vs.~hindrance demands, or whether all demands are under a larger ``demands'' category.
-Evidence suggests the employees do, in fact, differentiate between challenge and hindrance stressors (e.g., Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011).
+Horan et al.
+(2020) and M.
+A.
+LePine (2022) specifically call out the need for additional research to incorporate the appraisal process described by Lazarus and Folkman (1984) into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources into our study of the overarching JD-R model.
+In fact, Horan et al.
+(2020) state that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3).
+They go on to suggest future research continue to move away from \emph{a priori} classifications of stressors, as doing so can be problematic for theoretical and empirical reasons.
+Theoretically, \emph{a priori} classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
+Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time (e.g., Searle \& Auton, 2015).
+
+As such, the first question we ask is whether people distinguish between resources, challenges, and hindrances, and whether a job characteristics might even be considered simultaneously as more than one of these (e.g., both a challenge and a resource).
+Evidence suggests the employees do, in fact, differentiate between challenge and hindrance stressors (e.g., Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011), at least.
 For example, Bakker and Sanz-Vergel (2013) found that work pressure was perceived as a hindrance demand, and emotional demands as more of a challenge demand.
@@
 They found while that each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance demand to different degrees.
+We aim to both replicate the above findings and extend them to include resources.
 
 \begin{quote}
-Hypothesis 1: Job characteristics differ in consistancy regarding subjective worker perception as a demand or resource.
+Hypothesis 1: Job characteristics differ in consistancy regarding subjective worker perception as a challenge or hindrance demand, or resource.
 \end{quote}
@@
 \end{quote}
+
+\hypertarget{connecting-appraisals-to-workplace-outcomes}{%
+\subsection{Connecting Appraisals to Workplace Outcomes}\label{connecting-appraisals-to-workplace-outcomes}}
+
+The second set of analyses focuses on predicted associations without outcomes frequently studied across via job demands-resources Bakker and Demerouti (2017) and challenge-hindrance stressor framework Cavanaugh et al.
+(2000).
+Here, we specifically explore O*Net specified working condition apprasials as resources, challenges, and/or hindrances in association with engagement, strain and burnout.
+As argued above, appraisals are predicted to be associated with different forms of coping, and subsequently, outcomes.
+See Figure \ref{fig:ourmodel} for proposed associations.
 
@@
 
-\hypertarget{connecting-appraisals-to-workplace-outcomesthought}{%
-\subsection[Connecting appraisals to workplace outcomes]{\texorpdfstring{Connecting appraisals to workplace outcomes\footnote{add a sentence that adds a brief description of working conditions to first paragraph.
-Whole section needs expansion.}}{Connecting appraisals to workplace outcomes}}\label{connecting-appraisals-to-workplace-outcomesthought}}
-
-The second set of analyses focuses on associations.
-Do demands and resources have implications for work outcomes?
-Appraisals are associated with different forms of coping, and subsequently, outcomes.
-See Figure \ref{fig:ourmodel} for proposed associations.
-The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing.
+Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing.
+Beginning with resources ADD JDR STUFF ON RESOURCES AND MOTIVATION HERE.
 A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic.
@@
 Lastly, Gerich (2017) concluded that employee wellbeing was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
-
-We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point, and a rich collection of them support differential associations across a variety of organizational outcomes as well.
+In addition to the studies above, several meta-analyses also support differential associations across a variety of organizational outcomes as well.
 For example, both challenges and hindrances have been shown to positively predict strain (J.
@@
 
-Horan et al.
-(2020) and M.
-A.
-LePine (2022) specifically call out the need for additional research to incorporate the appraisal process described by Lazarus and Folkman (1984) into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources into our study of the overarching JD-R model.
-In fact, Horan et al.
-(2020) state that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3).
-They go on to suggest future research continue to move away from \emph{a priori} classifications of stressors, as doing so can be problematic for theoretical and empirical reasons.
-Theoretically, \emph{a priori} classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
-Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time (e.g., Searle \& Auton, 2015).
-
-\hypertarget{current-study-and-hypotheses}{%
-\subsection{Current Study and Hypotheses}\label{current-study-and-hypotheses}}
-
 \begin{quote}
-Hyp 3.a: Job resources are associated with greater engagement, less stress, and less burnout.
+Hyp 3.a: Job resources are positively associated with engagement.
 \end{quote}
@@
 \begin{quote}
-Hyp 3.b: More hindrances leads to less engagement, more stress, and greater burnout.
+Hyp 3.b: Challenge stressors are positively associated with engagement, strain, and burnout.
 \end{quote}
@@
 \begin{quote}
-Hyp 3.exploratory: More challenges leads to greater satisfaction, engagement, and burnout.\footnote{These need to be reframed to match Figure 1.}
+Hyp 3.c: Hindrance stressors are negatively associated with strain, and burnout.
+\end{quote}
+
+ADD JDR RESOURCES ACT AS A BUFFER INFO HERE ALONG WITH THESE NEW PREDICTIONS
+
+\begin{quote}
+Hyp 4.a:Resources moderate the relationship between challenge stressors and the outcomes of strain and burnout such that these relationship become weaker as workers perceive more resources.
+\end{quote}
+
+\begin{quote}
+Hyp 4.b:Resources moderate the relationship between hindrance stressors and the outcomes of strain and burnout such that these relationship become weaker as workers perceive more resources.
 \end{quote}
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-pindek2024dynamic}{}}%
+Pindek, S., Meyer, K., Valvo, A., \& Arvan, M.
+(2024).
+A dynamic view of the challenge-hindrance stressor framework: A meta-analysis of daily diary studies.
+\emph{Journal of Business and Psychology}, 1--19.
+
 \leavevmode\vadjust pre{\hypertarget{ref-podsakoff2007differential}{}}%

### 2024-03-16 Submission.Rmd
revised intro

@@
 While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular.
-We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges], with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) explore whether these subjective appraisals are differentially related to positive and negative outcomes.
+We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges], with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) *are there characteristics that are more likely to vary across demand and resource*, and 3) explore whether these subjective appraisals are differentially related to positive and negative outcomes.
 We utilize the O\*Net database (https://www.onetcenter.org/content.html), which is the primary source of occupational information in the US, and as such, provides a rich source of information about occupational requirements (i.e., work activities and context) that may be rated in terms of level of demand or resource.
@@
 Two related theories serve as the foundation for the current study: @demerouti2001job's job demands-resources theory and @cavanaugh2000empirical's later challenge-hindrance stressor framework.
-First, research on the job demands-resources model @demerouti2001job and later job demands-resources theory @bakker2017job highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes.
+The job demands-resources model @demerouti2001job,  @bakker2017job highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes.
 The job demands-resources theory distinguishes between resources and demands.
@@
 
->Hyp 3.a: Job resources are positively associated with engagement.
+>Hyp 3.a: Engagement is predicted by resources and challenges.
 
->Hyp 3.b: Challenge stressors are positively associated with engagement, strain, and burnout.
+>Hyp 3.b: Strain and burnout are differentially predicted by challenges and hindrances.
 
->Hyp 3.c: Hindrance stressors are negatively associated with strain, and burnout.
-
-ADD JDR RESOURCES ACT AS A BUFFER INFO HERE ALONG WITH THESE NEW PREDICTIONS
+ADD JDR RESOURCES ACT AS A BUFFER INFO HERE ALONG WITH THESE NEW PREDICTIONS 2017 JOHP moving forward
 

### 2024-03-16 Submission.tex
knit with updates

@@
 While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular.
-We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020), with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) explore whether these subjective appraisals are differentially related to positive and negative outcomes.
+We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020), with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) \emph{are there characteristics that are more likely to vary across demand and resource}, and 3) explore whether these subjective appraisals are differentially related to positive and negative outcomes.
 We utilize the O*Net database (\url{https://www.onetcenter.org/content.html}), which is the primary source of occupational information in the US, and as such, provides a rich source of information about occupational requirements (i.e., work activities and context) that may be rated in terms of level of demand or resource.
@@
 (2000)'s later challenge-hindrance stressor framework.
-First, research on the job demands-resources model Demerouti et al.
-(2001) and later job demands-resources theory Bakker and Demerouti (2017) highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes.
+The job demands-resources model Demerouti et al.
+(2001), Bakker and Demerouti (2017) highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes.
 The job demands-resources theory distinguishes between resources and demands.
@@
 \begin{quote}
-Hyp 3.a: Job resources are positively associated with engagement.
+Hyp 3.a: Engagement is predicted by resources and challenges.
 \end{quote}
@@
 \begin{quote}
-Hyp 3.b: Challenge stressors are positively associated with engagement, strain, and burnout.
+Hyp 3.b: Strain and burnout are differentially predicted by challenges and hindrances.
 \end{quote}
 
-\begin{quote}
-Hyp 3.c: Hindrance stressors are negatively associated with strain, and burnout.
-\end{quote}
-
-ADD JDR RESOURCES ACT AS A BUFFER INFO HERE ALONG WITH THESE NEW PREDICTIONS
+ADD JDR RESOURCES ACT AS A BUFFER INFO HERE ALONG WITH THESE NEW PREDICTIONS 2017 JOHP moving forward
 

### 2024-04-09 Submission.Rmd
desktop push so Alicia has most recent

@@
 OUTCOME VARIABLE INFORMATION HERE.
-These findings have implications for job design and administration - resource-laden elements may also be interpreted by workers as demands.
+These findings have implications for job design and administration particularly with regard to resource-laden elements that may also be experienced as demanding.
 
@@
 csl               : "apa7.csl"
-#documentclass     : "apa7" #interact
+documentclass     : "apa7" #interact
 classoption       : "jou"
@@
 
-+ Challenge-hindrance framework
+I. Challenge-hindrance framework
   + Cavanaugh (~2000)
   + Last 20 years' research (variance - look at Pindek et al, 2024)
-  + Appraisals
+  + Appraisals [^JDR]
 
-+ Antecedents (job elements)
+[^JDR]: Ignore JD theory terminology - only talk about JDR *model*, otherwise the verbage becomes confused (4/6/24)
+
+II. Antecedents (job elements)
   a. O\*Net - comprehensive
@@
 While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular.
-We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges], with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) *are there characteristics that are more likely to vary across demand and resource*, and 3) explore whether these subjective appraisals are differentially related to positive and negative outcomes.
-We utilize the O\*Net database (https://www.onetcenter.org/content.html), which is the primary source of occupational information in the US, and as such, provides a rich source of information about occupational requirements (i.e., work activities and context) that may be rated in terms of level of demand or resource.
-We will refer to these as elements of working conditions throughout this paper (e.g., personal, contextual, or task-related conditions or elements of one's work).
+We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges].
+Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, and 3) subjective appraisals are differentially related to positive and negative outcomes.
+To illuminate these questions, we consult the [O\*Net database](https://www.onetcenter.org/content.html), which provides a rich source of information about occupational requirements (i.e., work activities and context).
+We retain O\*Net terminology of working condition elements throughout this paper (e.g., personal, contextual, or task-related conditions or elements of one's work).
 
-## The Job Demands-Resources Theory and Challenge-hindrance Stressor Framework
+## The Job Demands-Resources Theory and Challenge-Hindrance Stressor Framework
 
-Two related theories serve as the foundation for the current study: @demerouti2001job's job demands-resources theory and @cavanaugh2000empirical's later challenge-hindrance stressor framework.
-The job demands-resources model @demerouti2001job,  @bakker2017job highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes.
-The job demands-resources theory distinguishes between resources and demands.
+Two related theories serve as the foundation for the current study: @demerouti2001job's job demands-resources theory and @cavanaugh2000empirical's challenge-hindrance stressor framework.
+The job demands-resources model [@demerouti2001job] highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes.
 *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
@@
 
-In response to inconsistent findings regarding demands and outcomes, @cavanaugh2000empirical expanded the job demands-resources theory in proposing the challenge-hindrance stressor framework, which draws from @lazarus1984stress's work on stress and coping.
-The challenge-hindrance stressor framework distinguishes between *two forms of demands* -- *challenges* and *hindrances*.
+In response to inconsistent findings regarding demanding work characteristics and outcomes, @cavanaugh2000empirical proposed a challenge-hindrance stressor framework, which draws from @lazarus1984stress's perspective on stress and coping.
+The challenge-hindrance stressor framework distinguishes between *two forms* of demands -- *challenges* and *hindrances*.
 Both are considered stressors [e.g., @cavanaugh2000empirical].
@@
 @lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes.
+
 First, stressors appraised as challenges typically result in a challenge appraisal, and engagement is likely to happen as a result.

### 2024-04-09 Submission.tex
desktop push so Alicia has most recent

@@
 \documentclass[
-  jou,mask]{apa6}
+  jou,mask]{apa7}
 \usepackage{amsmath,amssymb}
@@
 OUTCOME VARIABLE INFORMATION HERE.
-These findings have implications for job design and administration - resource-laden elements may also be interpreted by workers as demands.
+These findings have implications for job design and administration particularly with regard to resource-laden elements that may also be experienced as demanding.
 }
@@
 
-\begin{itemize}
+I. Challenge-hindrance framework
++ Cavanaugh (\textasciitilde2000)
++ Last 20 years' research (variance - look at Pindek et al, 2024)
++ Appraisals \footnote{Ignore JD theory terminology - only talk about JDR \emph{model}, otherwise the verbage becomes confused (4/6/24)}
+
+\begin{enumerate}
+\def\labelenumi{\Roman{enumi}.}
+\setcounter{enumi}{1}
 \tightlist
 \item
-  Challenge-hindrance framework
-
-  \begin{itemize}
-  \tightlist
-  \item
-    Cavanaugh (\textasciitilde2000)
-  \item
-    Last 20 years' research (variance - look at Pindek et al, 2024)
-  \item
-    Appraisals
-  \end{itemize}
-\item
   Antecedents (job elements)
+\end{enumerate}
 
@@
 \end{enumerate}
-\end{itemize}
 
@@
 While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular.
-We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020), with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) \emph{are there characteristics that are more likely to vary across demand and resource}, and 3) explore whether these subjective appraisals are differentially related to positive and negative outcomes.
-We utilize the O*Net database (\url{https://www.onetcenter.org/content.html}), which is the primary source of occupational information in the US, and as such, provides a rich source of information about occupational requirements (i.e., work activities and context) that may be rated in terms of level of demand or resource.
-We will refer to these as elements of working conditions throughout this paper (e.g., personal, contextual, or task-related conditions or elements of one's work).
+We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020).
+Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, and 3) subjective appraisals are differentially related to positive and negative outcomes.
+To illuminate these questions, we consult the \href{https://www.onetcenter.org/content.html}{O*Net database}, which provides a rich source of information about occupational requirements (i.e., work activities and context).
+We retain O*Net terminology of working condition elements throughout this paper (e.g., personal, contextual, or task-related conditions or elements of one's work).
 
 \hypertarget{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}{%
-\subsection{The Job Demands-Resources Theory and Challenge-hindrance Stressor Framework}\label{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}}
+\subsection{The Job Demands-Resources Theory and Challenge-Hindrance Stressor Framework}\label{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}}
 
@@
 (2001)'s job demands-resources theory and Cavanaugh et al.
-(2000)'s later challenge-hindrance stressor framework.
-The job demands-resources model Demerouti et al.
-(2001), Bakker and Demerouti (2017) highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes.
-The job demands-resources theory distinguishes between resources and demands.
+(2000)'s challenge-hindrance stressor framework.
+The job demands-resources model (Demerouti et al., 2001) highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes.
 \emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
@@
 
-In response to inconsistent findings regarding demands and outcomes, Cavanaugh et al.
-(2000) expanded the job demands-resources theory in proposing the challenge-hindrance stressor framework, which draws from Lazarus and Folkman (1984)'s work on stress and coping.
-The challenge-hindrance stressor framework distinguishes between \emph{two forms of demands} -- \emph{challenges} and \emph{hindrances}.
+In response to inconsistent findings regarding demanding work characteristics and outcomes, Cavanaugh et al.
+(2000) proposed a challenge-hindrance stressor framework, which draws from Lazarus and Folkman (1984)'s perspective on stress and coping.
+The challenge-hindrance stressor framework distinguishes between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}.
 Both are considered stressors (e.g., Cavanaugh et al., 2000).
@@
 LePine (2022) explain the mechanisms by which demands are related to performance and wellbeing outcomes.
+
 First, stressors appraised as challenges typically result in a challenge appraisal, and engagement is likely to happen as a result.

### 2024-04-13 Submission.Rmd
updating JDR discussion

@@
 
-Two related theories serve as the foundation for the current study: @demerouti2001job's job demands-resources theory and @cavanaugh2000empirical's challenge-hindrance stressor framework.
-The job demands-resources model [@demerouti2001job] highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes.
-*Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
+Two related theories serve as the foundation for the current study: the job demands-resources theory [e.g., @bakker2014job; @bakker2017job] and @cavanaugh2000empirical's challenge-hindrance stressor framework.
+The job demands-resources theory [e.g., @bakker2014job; @bakker2017job] highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes.
+*Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job].
 In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is commonly cited as a demand; @demerouti2001job).
@@
 
-In response to inconsistent findings regarding demanding work characteristics and outcomes, @cavanaugh2000empirical proposed a challenge-hindrance stressor framework, which draws from @lazarus1984stress's perspective on stress and coping.
+@cavanaugh2000empirical proposed the idea that not all demands are equal with her challenge-hindrance stressor framework, which draws from @lazarus1984stress's perspective on stress and coping.
 The challenge-hindrance stressor framework distinguishes between *two forms* of demands -- *challenges* and *hindrances*.
@@
 
-ADD JDR RESOURCES ACT AS A BUFFER INFO HERE ALONG WITH THESE NEW PREDICTIONS 2017 JOHP moving forward
+In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain [e.g., @bakker2005job] and burnout [e.g., @xanthopoulou2007job].
+BUILD ON THIS - DETAILS OF THESE TWO STUDIES AND MORE - BAKKER 2010
 

### 2024-04-13 Submission.Rmd
dunn bros edits (intro)

@@
   Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands.
-This study documents the degree of variability in subjective ratings of job characteristics with respect to interpretation as resource and demand.
+This study documents variability in subjective ratings of job characteristics with respect to interpretation as resource and demand.
 Next, we quantify the degree to which perceptions match the literature-implicated resources/demands of job characteristics and also document associations with stress, burnout, and engagement.
@@
 OUTCOME VARIABLE INFORMATION HERE.
-These findings have implications for job design and administration particularly with regard to resource-laden elements that may also be experienced as demanding.
+These findings have implications for job design and management particularly with regard to resource-laden elements that may also be experienced as demanding.
 
@@
 *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job].
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is commonly cited as a demand; @demerouti2001job).
+In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [high work pressure, for example, is commonly cited as a demand, e.g., @demerouti2001job].
 The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job).
 
-@cavanaugh2000empirical proposed the idea that not all demands are equal with her challenge-hindrance stressor framework, which draws from @lazarus1984stress's perspective on stress and coping.
+@cavanaugh2000empirical proposed the idea that not all demands are equal with her challenge-hindrance stressor framework, which draws from @lazarus1984stress's perspectives on stress and coping.
 The challenge-hindrance stressor framework distinguishes between *two forms* of demands -- *challenges* and *hindrances*.
@@
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Hindrance stressors in a work context include role conflict, role ambiguity, and organizational politics.
+Hindrance stressors in a work context include role conflict, role ambiguity, and organizational politics.[^challhind]
+
+[^challhind]: Need citations here for hindrance and challenge examples (because subjectivity vs. "typically a demand" is a central issue within the paper)
 
@@
 The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes [e.g., @cavanaugh2000empirical].
-Meta-analytic explorations of this the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (e.g., performance; [@lepine2005meta] and engagement, [@crawford2010linking]).
+Meta-analytic explorations of this the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, @lepine2005meta regarding performance and @crawford2010linking regarding engagement).
+
 @lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes.
-
-First, stressors appraised as challenges typically result in a challenge appraisal, and engagement is likely to happen as a result.
+First, stressors appraised as challenges typically result in a more positive appraisal, and engagement is likely to happen as a result.
 Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing.
@@
 This happens because resources are depleted via frustrations and other affectively negative reactions [@lepine2022challenge].
-Recent work affirms this appraisal process.
-@pindek2024dynamic meta-analyzed diary studies of dynamic stressors (i.e., short-term daily experiences of stressors) and concluded that daily challenge stressors had a postive direct association with performance, but a negative indirect association with performance through strain (as described by @lepine2022challenge above).
-As expected, hindrance stressors had both a direct and indirect (through strain) association with performance [@pindek2024dynamic].
+
+Recent work affirms these appraisal processes.
+@pindek2024dynamic meta-analyzed diary studies of dynamic stressors (i.e., short-term daily experiences of stressors) and concluded that daily challenge stressors had a positive *direct* association with performance, but a negative *indirect* association with performance through strain (as described by @lepine2022challenge above).
+As expected, hindrance stressors had both direct and indirect (through strain) associations with performance [@pindek2024dynamic].
 
@@
 Even @pindek2024dynamic notes this limitation of a priori classification of characteristics as demands, challenges, or hindrances, as do @horan2020review.
-In fact, although much of our research on job demands based on a priori classifications [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
+In fact, although much of our research on job demands based on a priori classifications [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).[^gimmecite]
 
-@horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process described by @lazarus1984stress into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources into our study of the overarching JD-R model.
+[^gimmecite]: Citations needed here or alternatively frame the sentence as, "we contend that..."
+
+@horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process described by @lazarus1984stress into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources.
 In fact, @horan2020review state that “…stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p.
@@
 Theoretically, *a priori* classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
-Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time [e.g., @searle2015merits].
+Empirically, as shown above, we have some evidence suggesting people can appraise a stressor[^checkit] as both a hindrance and challenge at the same time [e.g., @searle2015merits].
+
+[^checkit]: Do you mean "stressor" or "work characteristic"?
 
@@
 
-The second set of analyses focuses on predicted associations without outcomes frequently studied across via job demands-resources @bakker2017job and challenge-hindrance stressor framework @cavanaugh2000empirical.
-Here, we specifically explore O\*Net specified working condition apprasials as resources, challenges, and/or hindrances in association with engagement, strain and burnout.
+The second set of analyses focuses on predicted associations without relevant work-relevant outcomes frequently studied across via job demands-resources- [@bakker2017job] and challenge-hindrance stressor-frameworks [@cavanaugh2000empirical].
+Here, we specifically explore appraisals of O\*Net-derived work characteristics as resources, challenges, and/or hindrances in association with engagement, strain and burnout.
 As argued above, appraisals are predicted to be associated with different forms of coping, and subsequently, outcomes.
@@
 Beginning with resources ADD JDR STUFF ON RESOURCES AND MOTIVATION HERE.
-A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic.
-@kim2020thriving found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing.
+@kim2020thriving found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources[^dontsaythat] (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing.
 The opposite occurred when a demand was appraised as a hindrance – in those instances, the appraisal had a negative association with motivational resources.
@@
 BUILD ON THIS - DETAILS OF THESE TWO STUDIES AND MORE - BAKKER 2010
+
+[^dontsaythat]: Is there a different term that can be used here? This is confusing given the more straightforward Resource/Demand terminology from above
 

### 2024-04-13 Submission.tex
dunn bros edits (intro)

@@
 Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands.
-This study documents the degree of variability in subjective ratings of job characteristics with respect to interpretation as resource and demand.
+This study documents variability in subjective ratings of job characteristics with respect to interpretation as resource and demand.
 Next, we quantify the degree to which perceptions match the literature-implicated resources/demands of job characteristics and also document associations with stress, burnout, and engagement.
@@
 OUTCOME VARIABLE INFORMATION HERE.
-These findings have implications for job design and administration particularly with regard to resource-laden elements that may also be experienced as demanding.
+These findings have implications for job design and management particularly with regard to resource-laden elements that may also be experienced as demanding.
 }
@@
 
-Two related theories serve as the foundation for the current study: Demerouti et al.
-(2001)'s job demands-resources theory and Cavanaugh et al.
+Two related theories serve as the foundation for the current study: the job demands-resources theory (e.g., Bakker \& Demerouti, 2014, 2017) and Cavanaugh et al.
 (2000)'s challenge-hindrance stressor framework.
-The job demands-resources model (Demerouti et al., 2001) highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes.
-\emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001).
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is commonly cited as a demand; Demerouti et al.
-(2001)).
+The job demands-resources theory (e.g., Bakker \& Demerouti, 2014, 2017) highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes.
+\emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017).
+In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001).
 The perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; Bakker and Demerouti (2014)).
 
-In response to inconsistent findings regarding demanding work characteristics and outcomes, Cavanaugh et al.
-(2000) proposed a challenge-hindrance stressor framework, which draws from Lazarus and Folkman (1984)'s perspective on stress and coping.
+Cavanaugh et al.
+(2000) proposed the idea that not all demands are equal with her challenge-hindrance stressor framework, which draws from Lazarus and Folkman (1984)'s perspectives on stress and coping.
 The challenge-hindrance stressor framework distinguishes between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}.
@@
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Hindrance stressors in a work context include role conflict, role ambiguity, and organizational politics.
+Hindrance stressors in a work context include role conflict, role ambiguity, and organizational politics.\footnote{Need citations here for hindrance and challenge examples (because subjectivity vs.~``typically a demand'' is a central issue within the paper)}
 
 The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes (e.g., Cavanaugh et al., 2000).
-Meta-analytic explorations of this the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (e.g., performance; (J.
+Meta-analytic explorations of this the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, J.
 A.
-LePine et al., 2005) and engagement, (Crawford et al., 2010)).
+LePine et al.
+(2005) regarding performance and Crawford et al.
+(2010) regarding engagement).
+
 M.
@@
 LePine (2022) explain the mechanisms by which demands are related to performance and wellbeing outcomes.
-
-First, stressors appraised as challenges typically result in a challenge appraisal, and engagement is likely to happen as a result.
+First, stressors appraised as challenges typically result in a more positive appraisal, and engagement is likely to happen as a result.
 Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing.
@@
 LePine, 2022).
-Recent work affirms this appraisal process.
+
+Recent work affirms these appraisal processes.
 Pindek et al.
-(2024) meta-analyzed diary studies of dynamic stressors (i.e., short-term daily experiences of stressors) and concluded that daily challenge stressors had a postive direct association with performance, but a negative indirect association with performance through strain (as described by M.
+(2024) meta-analyzed diary studies of dynamic stressors (i.e., short-term daily experiences of stressors) and concluded that daily challenge stressors had a positive \emph{direct} association with performance, but a negative \emph{indirect} association with performance through strain (as described by M.
 A.
 LePine (2022) above).
-As expected, hindrance stressors had both a direct and indirect (through strain) association with performance (Pindek et al., 2024).
+As expected, hindrance stressors had both direct and indirect (through strain) associations with performance (Pindek et al., 2024).
 
@@
 (2020).
-In fact, although much of our research on job demands based on a priori classifications (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
+In fact, although much of our research on job demands based on a priori classifications (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).\footnote{Citations needed here or alternatively frame the sentence as, ``we contend that\ldots{}''}
 
@@
 A.
-LePine (2022) specifically call out the need for additional research to incorporate the appraisal process described by Lazarus and Folkman (1984) into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources into our study of the overarching JD-R model.
+LePine (2022) specifically call out the need for additional research to incorporate the appraisal process described by Lazarus and Folkman (1984) into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources.
 In fact, Horan et al.
@@
 Theoretically, \emph{a priori} classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
-Empirically, as shown above, we have some evidence suggesting people can appraise a stressor as both a hindrance and challenge at the same time (e.g., Searle \& Auton, 2015).
+Empirically, as shown above, we have some evidence suggesting people can appraise a stressor\footnote{Do you mean ``stressor'' or ``work characteristic''?} as both a hindrance and challenge at the same time (e.g., Searle \& Auton, 2015).
 
@@
 
-The second set of analyses focuses on predicted associations without outcomes frequently studied across via job demands-resources Bakker and Demerouti (2017) and challenge-hindrance stressor framework Cavanaugh et al.
-(2000).
-Here, we specifically explore O*Net specified working condition apprasials as resources, challenges, and/or hindrances in association with engagement, strain and burnout.
+The second set of analyses focuses on predicted associations without relevant work-relevant outcomes frequently studied across via job demands-resources- (Bakker \& Demerouti, 2017) and challenge-hindrance stressor-frameworks (Cavanaugh et al., 2000).
+Here, we specifically explore appraisals of O*Net-derived work characteristics as resources, challenges, and/or hindrances in association with engagement, strain and burnout.
 As argued above, appraisals are predicted to be associated with different forms of coping, and subsequently, outcomes.
@@
 Beginning with resources ADD JDR STUFF ON RESOURCES AND MOTIVATION HERE.
-A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic.
-Kim and Beehr (2020) found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing.
+Kim and Beehr (2020) found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources\footnote{Is there a different term that can be used here?
+This is confusing given the more straightforward Resource/Demand terminology from above} (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing.
 The opposite occurred when a demand was appraised as a hindrance -- in those instances, the appraisal had a negative association with motivational resources.
@@
 
-ADD JDR RESOURCES ACT AS A BUFFER INFO HERE ALONG WITH THESE NEW PREDICTIONS 2017 JOHP moving forward
+In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain (e.g., Bakker et al., 2005) and burnout (e.g., Xanthopoulou et al., 2007).
+BUILD ON THIS - DETAILS OF THESE TWO STUDIES AND MORE - BAKKER 2010
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2005job}{}}%
+Bakker, A. B., Demerouti, E., \& Euwema, M. C. (2005). Job resources buffer the impact of job demands on burnout. \emph{Journal of Occupational Health Psychology}, \emph{10}(2), 170.
+
 \leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-xanthopoulou2007job}{}}%
+Xanthopoulou, D., Bakker, A.
+B., Dollard, M.
+F., Demerouti, E., Schaufeli, W.
+B., Taris, T.
+W., \& Schreurs, P.
+J.
+(2007).
+When do job demands particularly predict burnout?
+The moderating role of job resources.
+\emph{Journal of Managerial Psychology}, \emph{22}(8), 766--786.
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-careless}{}}%

### 2024-04-25 moderated_regressions.Rmd
creating tables

---
title: "moderated_regressions"
output: html_document
date: "2024-04-13"
---

```{r data, include = FALSE}
data <- read.csv("SIOPcleaned.csv")      ## from "datacleaning.R" script

## Study 2 DVs

data$item387      <- 7- data$item387           ## only reflected engagement item

data$absorption   <- rowMeans(data[c(380:386)], na.rm=TRUE)
data$vigor        <- rowMeans(data[c(387:392)], na.rm=TRUE) 
data$dedication   <- rowMeans(data[c(393:399)], na.rm=TRUE)

data$cognitive    <- rowMeans(data[c(380:382, 387:388, 393:395)], na.rm=TRUE)
data$affective    <- rowMeans(data[c(383:384, 389:390, 396:397)], na.rm=TRUE) 
data$behavioral   <- rowMeans(data[c(385:386, 391:392, 398:399)], na.rm=TRUE)

######################################################

data$burnout      <- rowMeans(data[c(373:376)], na.rm=TRUE)
data$stress       <- rowMeans(data[c(377:379)], na.rm=TRUE)
data$engagement   <- rowMeans(data[c(380:399)], na.rm=TRUE)        ## added 10/12 because analyses too wonky with 3 subscales

alpha.abs <- psych::alpha(data[c(380:386)])
alpha.vig <- psych::alpha(data[c(387:392)])
alpha.ded <- psych::alpha(data[c(393:399)])
alpha.eng <- psych::alpha(data[c(380:399)])

alpha.bur <- psych::alpha(data[c(373:376)])
alpha.str <- psych::alpha(data[c(377:379)])

## O*NET categories

data$onet.resource.ii <- rowMeans(data[c(162:166)], na.rm=TRUE)
data$onet.resource.mp <- rowMeans(data[c(167:176)], na.rm=TRUE)
data$onet.resource.wo <- rowMeans(data[c(177:185)], na.rm=TRUE)
data$onet.resource.io <- rowMeans(data[c(186:202)], na.rm=TRUE)
data$onet.resource.ir <- rowMeans(data[c(149:161)], na.rm=TRUE)
data$onet.resource.pc <- rowMeans(data[c(128:144,146:148)], na.rm=TRUE)
data$onet.resource.sc <- rowMeans(data[c(118:127)], na.rm=TRUE)

overall.resource <- rowMeans(data[c(118:144,147:202)], na.rm=TRUE)

data$onet.hindrance.ii <- rowMeans(data[c(246:247,249:252)], na.rm=TRUE)
data$onet.hindrance.mp <- rowMeans(data[c(252:261)], na.rm=TRUE)
data$onet.hindrance.wo <- rowMeans(data[c(262:270)], na.rm=TRUE)
data$onet.hindrance.io <- rowMeans(data[c(271:287)], na.rm=TRUE)
data$onet.hindrance.ir <- rowMeans(data[c(233:245)], na.rm=TRUE)
data$onet.hindrance.pc <- rowMeans(data[c(213:232)], na.rm=TRUE)
data$onet.hindrance.sc <- rowMeans(data[c(203:212)], na.rm=TRUE)

overall.hindrance <- rowMeans(data[c(203:247,249:287)], na.rm=TRUE)

data$onet.challenge.ii <- rowMeans(data[c(332:336)], na.rm=TRUE)
data$onet.challenge.mp <- rowMeans(data[c(337:346)], na.rm=TRUE)
data$onet.challenge.wo <- rowMeans(data[c(347:355)], na.rm=TRUE)
data$onet.challenge.io <- rowMeans(data[c(356:372)], na.rm=TRUE)
data$onet.challenge.ir <- rowMeans(data[c(319:331)], na.rm=TRUE)
data$onet.challenge.pc <- rowMeans(data[c(298:307,309:318)], na.rm=TRUE)
data$onet.challenge.sc <- rowMeans(data[c(288:297)], na.rm=TRUE)

overall.challenge <- rowMeans(data[c(288:307,309:372)], na.rm=TRUE)

```

```{r Analyses with Row Sums}
overall.resource <- rowSums(data[c(118:144,147:202)], na.rm=TRUE)
summary(overall.resource) #202.3
overall.hindrance <- rowSums(data[c(203:247,249:287)], na.rm=TRUE)
summary(overall.hindrance) #159.2
overall.challenge <- rowSums(data[c(288:307,309:372)], na.rm=TRUE)
summary(overall.challenge) #204.2

#centered predictors
overall.resource_center <- overall.resource - 202.3
overall.hindrance_center <- overall.hindrance - 159.2
overall.challenge_center <- overall.challenge - 204.2
```

```{r Moderated Regression Challenge-Resource Burnout}

challenge_resource_burnout_model1 <- lm(burnout ~ overall.challenge_center, data = data)
summary(challenge_resource_burnout_model1)

challenge_resource_burnout_model2 <- lm(burnout ~ overall.challenge_center + overall.resource, data = data)
summary(challenge_resource_burnout_model2)

challenge_resource_burnout_model3 <- lm(burnout ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
summary(challenge_resource_burnout_model3)

aov_test <- anova(challenge_resource_burnout_model2, challenge_resource_burnout_model3)
```

```{r Moderated Regression Challenge-Resource Stress}

challenge_resource_stress_model1 <- lm(stress ~ overall.challenge_center, data = data)
summary(challenge_resource_stress_model1)

challenge_resource_stress_model2 <- lm(stress ~ overall.challenge_center + overall.resource_center, data = data)
summary(challenge_resource_stress_model2)

challenge_resource_stress_model3 <- lm(stress ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
summary(challenge_resource_stress_model3)

anova(challenge_resource_stress_model2, challenge_resource_stress_model3)
```

```{r Moderated Regression Challenge-Resource Engagement}

challenge_resource_engagement_model1 <- lm(engagement ~ overall.challenge_center, data = data)
summary(challenge_resource_engagement_model1)

challenge_resource_engagement_model2 <- lm(engagement ~ overall.challenge_center + overall.resource_center, data = data)
summary(challenge_resource_engagement_model2)

challenge_resource_engagement_model3 <- lm(engagement ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
summary(challenge_resource_engagement_model3)

anova(challenge_resource_engagement_model2, challenge_resource_engagement_model3)
```

```{r Moderated Regression Hindrance-Resource Burnout}

hindrance_resource_model1 <- lm(burnout ~ overall.hindrance_center, data = data)
summary(hindrance_resource_model1)

hindrance_resource_burnout_model2 <- lm(burnout ~ overall.hindrance_center + overall.resource_center, data = data)
summary(hindrance_resource_burnout_model2)

hindrance_resource_burnout_model3 <- lm(burnout ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
summary(hindrance_resource_burnout_model3)

anova(hindrance_resource_burnout_model2, hindrance_resource_burnout_model3)
```

```{r Moderated Regression Hindrance-Resource Stress}

hindrance_resource_stress_model1 <- lm(stress ~ overall.hindrance_center, data = data)
summary(hindrance_resource_stress_model1)

hindrance_resource_stress_model2 <- lm(stress ~ overall.hindrance_center + overall.resource_center, data = data)
summary(hindrance_resource_stress_model2)

hindrance_resource_stress_model3 <- lm(stress ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
summary(hindrance_resource_stress_model3)

anova(hindrance_resource_stress_model2, hindrance_resource_stress_model3)
```

```{r Moderated Regression Hindrance-Resource Engagement}

hindrance_resource_engagement_model1 <- lm(engagement ~ overall.hindrance_center, data = data)
summary(hindrance_resource_engagement_model1)

hindrance_resource_engagement_model2 <- lm(engagement ~ overall.hindrance_center + overall.resource_center, data = data)
summary(hindrance_resource_engagement_model2)

hindrance_resource_engagement_model3 <- lm(engagement ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
summary(hindrance_resource_engagement_model3)

anova(hindrance_resource_engagement_model2, hindrance_resource_engagement_model3)
```

```{r Numbers for Tables}
summary(challenge_resource_burnout_model3)$coefficients

#estimates - b weights
summary(challenge_resource_burnout_model3)$coefficients[1, 1]
summary(challenge_resource_burnout_model3)$coefficients[1, 2]
summary(challenge_resource_burnout_model3)$coefficients[1, 3]
summary(challenge_resource_burnout_model3)$coefficients[1, 4]

# p values
summary(challenge_resource_burnout_model3)$coefficients[4, 1]
summary(challenge_resource_burnout_model3)$coefficients[4, 2]
summary(challenge_resource_burnout_model3)$coefficients[4, 3]
summary(challenge_resource_burnout_model3)$coefficients[4, 4]

#F values (these are just the change from model 2 with main effects to model 3 that adds the interaction)
challenge_resource_burnout_anova <- anova(challenge_resource_burnout_model2, challenge_resource_burnout_model3)
challenge_resource_burnout_anova$F
challenge_resource_burnout_anova$`Pr(>F)`

#r squared
summary(challenge_resource_burnout_model2)
summary(challenge_resource_burnout_model2)$coefficients[3, 1]

summary(challenge_resource_burnout_model3)
```

### 2024-04-25 moderated_regressions.Rmd
adding info for tables
finalizing numbers for tables

@@
 summary(challenge_resource_burnout_model2)
-summary(challenge_resource_burnout_model2)$coefficients[3, 1]
+challenge_resource_burnout_model2_r <- summary(challenge_resource_burnout_model2)$r.squared
+summary(challenge_resource_burnout_model3)
+challenge_resource_burnout_model3_r <- summary(challenge_resource_burnout_model3)$r.squared
 
-summary(challenge_resource_burnout_model3)
+challenge_resource_burnout_r_square_change <- challenge_resource_burnout_model3_r - challenge_resource_burnout_model2_r
+challenge_resource_burnout_r_square_change
+
 ```

### 2024-04-28 moderated_regressions.Rmd
example table

--- 2024-04-25 moderated_regressions.Rmd
@@
 title: "moderated_regressions"
-output: html_document
+output: pdf_document
 date: "2024-04-13"
@@
 ```{r Numbers for Tables}
-summary(challenge_resource_burnout_model3)$coefficients
 
-#estimates - b weights
-summary(challenge_resource_burnout_model3)$coefficients[1, 1]
-summary(challenge_resource_burnout_model3)$coefficients[1, 2]
-summary(challenge_resource_burnout_model3)$coefficients[1, 3]
-summary(challenge_resource_burnout_model3)$coefficients[1, 4]
+options(scipen=999)  ## Suppresses scientific notation
 
-# p values
-summary(challenge_resource_burnout_model3)$coefficients[4, 1]
-summary(challenge_resource_burnout_model3)$coefficients[4, 2]
-summary(challenge_resource_burnout_model3)$coefficients[4, 3]
-summary(challenge_resource_burnout_model3)$coefficients[4, 4]
+# b weights
+chal.2.burn <- round(summary(challenge_resource_burnout_model2)$coefficients[2, 1],6)
+res.2.burn <- round(summary(challenge_resource_burnout_model2)$coefficients[3, 1],6)
 
-#F values (these are just the change from model 2 with main effects to model 3 that adds the interaction)
-challenge_resource_burnout_anova <- anova(challenge_resource_burnout_model2, challenge_resource_burnout_model3)
-challenge_resource_burnout_anova$F
-challenge_resource_burnout_anova$`Pr(>F)`
+int.3.burn <- round(summary(challenge_resource_burnout_model3)$coefficients[4, 1],6)
 
 #r squared
-summary(challenge_resource_burnout_model2)
-summary(challenge_resource_burnout_model2)$coefficients[3, 1]
+challenge_resource_burnout_model2_r <- round(summary(challenge_resource_burnout_model2)$r.squared,4)
+challenge_resource_burnout_model3_r <- round(summary(challenge_resource_burnout_model3)$r.squared,4)
 
-summary(challenge_resource_burnout_model3)
+## R square change
+challenge_resource_burnout_anova <- anova(challenge_resource_burnout_model2, challenge_resource_burnout_model3)
+challenge_resource_burnout_r_square_change <- round(challenge_resource_burnout_model3_r - challenge_resource_burnout_model2_r,4)
+
 ```
+
+```{r, results='asis'}
+
+library(kableExtra)
+
+DV <- c("Burnout","","")
+Step <- c("1", "","2")
+Model <- c("Challenge", "Resource", "Challenge X Resource")
+b <- c(chal.2.burn,res.2.burn,int.3.burn)
+DeltaR <- c("",paste(challenge_resource_burnout_model2_r,"**"),challenge_resource_burnout_r_square_change)
+
+regtable <- cbind(DV, Step, Model, b, DeltaR)
+
+papaja::apa_table(regtable)
+
+```

### 2024-04-30 moderated_regressions.Rmd
updating tables

@@
 
-challenge_resource_burnout_model1 <- lm(burnout ~ overall.challenge_center, data = data)
-summary(challenge_resource_burnout_model1)
+cr_burn_m1 <- lm(burnout ~ overall.challenge_center, data = data)
+summary(cr_burn_m1)
 
-challenge_resource_burnout_model2 <- lm(burnout ~ overall.challenge_center + overall.resource, data = data)
-summary(challenge_resource_burnout_model2)
+cr_burn_m2 <- lm(burnout ~ overall.challenge_center + overall.resource, data = data)
+summary(cr_burn_m2)
 
-challenge_resource_burnout_model3 <- lm(burnout ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
-summary(challenge_resource_burnout_model3)
+cr_burn_m3 <- lm(burnout ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
+summary(cr_burn_m3)
 
-aov_test <- anova(challenge_resource_burnout_model2, challenge_resource_burnout_model3)
+aov_test <- anova(cr_burn_m2, cr_burn_m3)
 ```
@@
 
-challenge_resource_stress_model1 <- lm(stress ~ overall.challenge_center, data = data)
-summary(challenge_resource_stress_model1)
+cr_stress_m1 <- lm(stress ~ overall.challenge_center, data = data)
+summary(cr_stress_m1)
 
-challenge_resource_stress_model2 <- lm(stress ~ overall.challenge_center + overall.resource_center, data = data)
-summary(challenge_resource_stress_model2)
+cr_stress_m2 <- lm(stress ~ overall.challenge_center + overall.resource_center, data = data)
+summary(cr_stress_m2)
 
-challenge_resource_stress_model3 <- lm(stress ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
-summary(challenge_resource_stress_model3)
+cr_stress_m3 <- lm(stress ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
+summary(cr_stress_m3)
 
-anova(challenge_resource_stress_model2, challenge_resource_stress_model3)
+anova(cr_stress_m2, cr_stress_m3)
 ```
@@
 
-challenge_resource_engagement_model1 <- lm(engagement ~ overall.challenge_center, data = data)
-summary(challenge_resource_engagement_model1)
+cr_eng_m1 <- lm(engagement ~ overall.challenge_center, data = data)
+summary(cr_eng_m1)
 
-challenge_resource_engagement_model2 <- lm(engagement ~ overall.challenge_center + overall.resource_center, data = data)
-summary(challenge_resource_engagement_model2)
+cr_eng_m2 <- lm(engagement ~ overall.challenge_center + overall.resource_center, data = data)
+summary(cr_eng_m2)
 
-challenge_resource_engagement_model3 <- lm(engagement ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
-summary(challenge_resource_engagement_model3)
+cr_eng_m3 <- lm(engagement ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
+summary(cr_eng_m3)
 
-anova(challenge_resource_engagement_model2, challenge_resource_engagement_model3)
+anova(cr_eng_m2, cr_eng_m3)
 ```
@@
 
-hindrance_resource_model1 <- lm(burnout ~ overall.hindrance_center, data = data)
-summary(hindrance_resource_model1)
+hr_burn_m1 <- lm(burnout ~ overall.hindrance_center, data = data)
+summary(hr_burn_m1)
 
-hindrance_resource_burnout_model2 <- lm(burnout ~ overall.hindrance_center + overall.resource_center, data = data)
-summary(hindrance_resource_burnout_model2)
+hr_burn_m2 <- lm(burnout ~ overall.hindrance_center + overall.resource_center, data = data)
+summary(hr_burn_m2)
 
-hindrance_resource_burnout_model3 <- lm(burnout ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
-summary(hindrance_resource_burnout_model3)
+hr_burn_m3 <- lm(burnout ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
+summary(hr_burn_m3)
 
-anova(hindrance_resource_burnout_model2, hindrance_resource_burnout_model3)
+anova(hr_burn_m2, hr_burn_m3)
 ```
@@
 
-hindrance_resource_stress_model1 <- lm(stress ~ overall.hindrance_center, data = data)
-summary(hindrance_resource_stress_model1)
+hr_stress_m1 <- lm(stress ~ overall.hindrance_center, data = data)
+summary(hr_stress_m1)
 
-hindrance_resource_stress_model2 <- lm(stress ~ overall.hindrance_center + overall.resource_center, data = data)
-summary(hindrance_resource_stress_model2)
+hr_stress_m2 <- lm(stress ~ overall.hindrance_center + overall.resource_center, data = data)
+summary(hr_stress_m2)
 
-hindrance_resource_stress_model3 <- lm(stress ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
-summary(hindrance_resource_stress_model3)
+hr_stress_m3 <- lm(stress ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
+summary(hr_stress_m3)
 
-anova(hindrance_resource_stress_model2, hindrance_resource_stress_model3)
+anova(hr_stress_m2, hr_stress_m3)
 ```
@@
 
-hindrance_resource_engagement_model1 <- lm(engagement ~ overall.hindrance_center, data = data)
-summary(hindrance_resource_engagement_model1)
+hr_eng_m1 <- lm(engagement ~ overall.hindrance_center, data = data)
+summary(hr_eng_m1)
 
-hindrance_resource_engagement_model2 <- lm(engagement ~ overall.hindrance_center + overall.resource_center, data = data)
-summary(hindrance_resource_engagement_model2)
+hr_eng_m2 <- lm(engagement ~ overall.hindrance_center + overall.resource_center, data = data)
+summary(hr_eng_m2)
 
-hindrance_resource_engagement_model3 <- lm(engagement ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
-summary(hindrance_resource_engagement_model3)
+hr_eng_m3 <- lm(engagement ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
+summary(hr_eng_m3)
 
-anova(hindrance_resource_engagement_model2, hindrance_resource_engagement_model3)
+anova(hr_eng_m2, hr_eng_m3)
 ```
 
-```{r Numbers for Tables}
+```{r Numbers for Table1}
 
@@
 
+#Challenge-Resource-Burnout
+
 # b weights
-chal.2.burn <- round(summary(challenge_resource_burnout_model2)$coefficients[2, 1],6)
-res.2.burn <- round(summary(challenge_resource_burnout_model2)$coefficients[3, 1],6)
+chal.2.burn <- round(summary(cr_burn_m2)$coefficients[2, 1],2)
+res.2.burn <- round(summary(cr_burn_m2)$coefficients[3, 1],2)
 
-int.3.burn <- round(summary(challenge_resource_burnout_model3)$coefficients[4, 1],6)
+int.cr.3.burn <- round(summary(cr_burn_m3)$coefficients[4, 1],2)
 
 #r squared
-challenge_resource_burnout_model2_r <- round(summary(challenge_resource_burnout_model2)$r.squared,4)
-challenge_resource_burnout_model3_r <- round(summary(challenge_resource_burnout_model3)$r.squared,4)
+cr_burn_m2_r <- round(summary(cr_burn_m2)$r.squared,2)
+cr_burn_m3_r <- round(summary(cr_burn_m3)$r.squared,2)
 
 ## R square change
-challenge_resource_burnout_anova <- anova(challenge_resource_burnout_model2, challenge_resource_burnout_model3)
-challenge_resource_burnout_r_square_change <- round(challenge_resource_burnout_model3_r - challenge_resource_burnout_model2_r,4)
+cr_burn_anova <- anova(cr_burn_m2, cr_burn_m3)
+cr_burn_r_square_change <- round(cr_burn_m3_r - cr_burn_m2_r,2)
+
+#Challenge-Resource-Stress
+
+# b weights
+chal.2.stress <- round(summary(cr_stress_m2)$coefficients[2, 1],2)
+res.2.stress <- round(summary(cr_stress_m2)$coefficients[3, 1],2)
+
+int.cr.3.stress <- round(summary(cr_stress_m3)$coefficients[4, 1],2)
+
+#r squared
+cr_stress_m2_r <- round(summary(cr_stress_m2)$r.squared,2)
+cr_stress_m3_r <- round(summary(cr_stress_m3)$r.squared,2)
+
+## R square change
+cr_stress_anova <- anova(cr_stress_m2, cr_stress_m3)
+cr_stress_r_square_change <- round(cr_stress_m3_r - cr_stress_m2_r,2)
+
+#Challenge-Resource-Engagement
+
+# b weights
+chal.2.eng <- round(summary(cr_eng_m2)$coefficients[2, 1],2)
+res.2.eng <- round(summary(cr_eng_m2)$coefficients[3, 1],2)
+
+int.cr.3.eng <- round(summary(cr_eng_m3)$coefficients[4, 1],2)
+
+#r squared
+cr_eng_m2_r <- round(summary(cr_eng_m2)$r.squared,2)
+cr_eng_m3_r <- round(summary(cr_eng_m3)$r.squared,2)
+
+## R square change
+cr_eng_anova <- anova(cr_eng_m2, cr_eng_m3)
+cr_eng_r_square_change <- round(cr_eng_m3_r - cr_eng_m2_r,2)
+```
+
+```{r Numbers for Table2}
+
+options(scipen=999)  ## Suppresses scientific notation
+
+#Hindrance-Resource-Burnout
+
+# b weights
+hind.2.burn <- round(summary(hr_burn_m2)$coefficients[2, 1],2)
+res.2hr.burn <- round(summary(hr_burn_m2)$coefficients[3, 1],2)
+
+int.hr.3.burn <- round(summary(hr_burn_m3)$coefficients[4, 1],2)
+
+#r squared
+hr_burn_m2_r <- round(summary(hr_burn_m2)$r.squared,2)
+hr_burn_m3_r <- round(summary(hr_burn_m3)$r.squared,2)
+
+## R square change
+hr_burn_anova <- anova(hr_burn_m2, hr_burn_m3)
+hr_burn_r_square_change <- round(hr_burn_m3_r - hr_burn_m2_r,2)
+
+#Hindrance-Resource-Stress
+
+# b weights
+hind.2.stress <- round(summary(hr_stress_m2)$coefficients[2, 1],2)
+res.2hr.stress <- round(summary(hr_stress_m2)$coefficients[3, 1],2)
+
+int.hr.3.stress <- round(summary(hr_stress_m3)$coefficients[4, 1],2)
+
+#r squared
+hr_stress_m2_r <- round(summary(hr_stress_m2)$r.squared,2)
+hr_stress_m3_r <- round(summary(hr_stress_m3)$r.squared,2)
+
+## R square change
+hr_stress_anova <- anova(hr_stress_m2, hr_stress_m3)
+hr_stress_r_square_change <- round(hr_stress_m3_r - hr_stress_m2_r,2)
+
+#Hindrance-Resource-Engagement
+
+# b weights
+hind.2.eng <- round(summary(hr_eng_m2)$coefficients[2, 1],2)
+res.2hr.eng <- round(summary(hr_eng_m2)$coefficients[3, 1],2)
+
+int.hr.3.eng <- round(summary(hr_eng_m3)$coefficients[4, 1],2)
+
+#r squared
+hr_eng_m2_r <- round(summary(hr_eng_m2)$r.squared,2)
+hr_eng_m3_r <- round(summary(hr_eng_m3)$r.squared,2)
+
+## R square change
+hr_eng_anova <- anova(hr_eng_m2, hr_eng_m3)
+hr_eng_r_square_change <- round(hr_eng_m3_r - hr_eng_m2_r,2)
+```
+
+```{r, results='asis'}
+#I'm not touching this script - using it as a model and making two new chunks
+library(kableExtra)
+
+DV <- c("Burnout","","")
+Step <- c("1", "","2")
+Model <- c("Challenge", "Resource", "Challenge X Resource")
+b <- c(chal.2.burn,res.2.burn,int.cr.3.burn)
+DeltaR <- c("",paste(cr_burn_m2_r,"**"),cr_burn_r_square_change)
+
+regtable <- cbind(DV, Step, Model, b, DeltaR)
+
+papaja::apa_table(regtable)
 
@@
 
-DV <- c("Burnout","","")
-Step <- c("1", "","2")
-Model <- c("Challenge", "Resource", "Challenge X Resource")
-b <- c(chal.2.burn,res.2.burn,int.3.burn)
-DeltaR <- c("",paste(challenge_resource_burnout_model2_r,"**"),challenge_resource_burnout_r_square_change)
+DV <- c("Engagement","","", "Stress","","", "Burnout","","")
+Step <- c("1", "","2", "1", "","2", "1", "","2")
+Model <- c("Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource")
+b <- c(chal.2.eng, res.2.eng, int.cr.3.eng, chal.2.stress, res.2.stress, int.cr.3.stress, chal.2.burn, res.2.burn, int.cr.3.burn)
+R2 <- c("", cr_eng_m2_r, cr_eng_m3_r, "", cr_stress_m2_r, cr_stress_m3_r, "", cr_burn_m2_r, cr_burn_m3_r)
+DeltaR <- c("",paste(cr_eng_m2_r),cr_eng_r_square_change, "",paste(cr_stress_m2_r),cr_stress_r_square_change, "",paste(cr_burn_m2_r),cr_burn_r_square_change)
 
-regtable <- cbind(DV, Step, Model, b, DeltaR)
+regtable <- cbind(DV, Step, Model, b, R2, DeltaR)
 
@@
 ```
+
+```{r, results='asis'}
+
+library(kableExtra)
+
+DV <- c("Engagement","","", "Stress","","", "Burnout","","")
+Step <- c("1", "","2", "1", "","2", "1", "","2")
+Model <- c("Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource")
+b <- c(hind.2.eng, res.2hr.eng, int.hr.3.eng, hind.2.stress, res.2hr.stress, int.hr.3.stress, hind.2.burn, res.2hr.burn, int.hr.3.burn)
+R2 <- c("", hr_eng_m2_r, hr_eng_m3_r, "", hr_stress_m2_r, hr_stress_m3_r, "", hr_burn_m2_r, hr_burn_m3_r)
+DeltaR <- c("",paste(hr_eng_m2_r,"**"),hr_eng_r_square_change, "",paste(hr_stress_m2_r,"**"),hr_stress_r_square_change, "",paste(hr_burn_m2_r,"**"),hr_burn_r_square_change)
+
+regtable <- cbind(DV, Step, Model, b, R2, DeltaR)
+
+papaja::apa_table(regtable)
+# How to get delta symbol and superscript
+#https://cran.r-project.org/web/packages/reporter/vignettes/reporter-super.html#:~:text=To%20get%20superscripts%20or%20subscripts,to%20the%20desired%20cell%20value.
+
+```

### 2024-05-01 moderated_regressions.Rmd
updating tables

@@
 
-cr_burn_m1 <- lm(burnout ~ overall.challenge_center, data = data)
+cr_burn_m1 <- lm(scale(burnout) ~ scale(overall.challenge_center), data = data)
 summary(cr_burn_m1)
 
-cr_burn_m2 <- lm(burnout ~ overall.challenge_center + overall.resource, data = data)
+cr_burn_m2 <- lm(scale(burnout) ~ scale(overall.challenge_center) + scale(overall.resource), data = data)
 summary(cr_burn_m2)
 
-cr_burn_m3 <- lm(burnout ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
+cr_burn_m3 <- lm(scale(burnout) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), data = data)
 summary(cr_burn_m3)
@@
 aov_test <- anova(cr_burn_m2, cr_burn_m3)
+aov_test
 ```
@@
 
-cr_stress_m1 <- lm(stress ~ overall.challenge_center, data = data)
+cr_stress_m1 <- lm(scale(stress) ~ scale(overall.challenge_center), data = data)
 summary(cr_stress_m1)
 
-cr_stress_m2 <- lm(stress ~ overall.challenge_center + overall.resource_center, data = data)
+cr_stress_m2 <- lm(scale(stress) ~ scale(overall.challenge_center) + scale(overall.resource_center), data = data)
 summary(cr_stress_m2)
 
-cr_stress_m3 <- lm(stress ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
+cr_stress_m3 <- lm(scale(stress) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), data = data)
 summary(cr_stress_m3)
 
-anova(cr_stress_m2, cr_stress_m3)
+cr_stress_anova <- anova(cr_stress_m2, cr_stress_m3)
+cr_stress_anova
 ```
@@
 
-cr_eng_m1 <- lm(engagement ~ overall.challenge_center, data = data)
+cr_eng_m1 <- lm(scale(engagement) ~ scale(overall.challenge_center), data = data)
 summary(cr_eng_m1)
 
-cr_eng_m2 <- lm(engagement ~ overall.challenge_center + overall.resource_center, data = data)
+cr_eng_m2 <- lm(scale(engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center), data = data)
 summary(cr_eng_m2)
 
-cr_eng_m3 <- lm(engagement ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
+cr_eng_m3 <- lm(scale(engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), data = data)
 summary(cr_eng_m3)
 
-anova(cr_eng_m2, cr_eng_m3)
+cr_eng_anova <- anova(cr_eng_m2, cr_eng_m3)
+cr_eng_anova
 ```
@@
 
-hr_burn_m1 <- lm(burnout ~ overall.hindrance_center, data = data)
+hr_burn_m1 <- lm(scale(burnout) ~ scale(overall.hindrance_center), data = data)
 summary(hr_burn_m1)
 
-hr_burn_m2 <- lm(burnout ~ overall.hindrance_center + overall.resource_center, data = data)
+hr_burn_m2 <- lm(scale(burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center), data = data)
 summary(hr_burn_m2)
 
-hr_burn_m3 <- lm(burnout ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
+hr_burn_m3 <- lm(scale(burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), data = data)
 summary(hr_burn_m3)
 
-anova(hr_burn_m2, hr_burn_m3)
+hr_burn_anova <- anova(hr_burn_m2, hr_burn_m3)
+hr_burn_anova
 ```
@@
 
-hr_stress_m1 <- lm(stress ~ overall.hindrance_center, data = data)
+hr_stress_m1 <- lm(scale(stress) ~ scale(overall.hindrance_center), data = data)
 summary(hr_stress_m1)
 
-hr_stress_m2 <- lm(stress ~ overall.hindrance_center + overall.resource_center, data = data)
+hr_stress_m2 <- lm(scale(stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center), data = data)
 summary(hr_stress_m2)
 
-hr_stress_m3 <- lm(stress ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
+hr_stress_m3 <- lm(scale(stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), data = data)
 summary(hr_stress_m3)
 
-anova(hr_stress_m2, hr_stress_m3)
+hr_stress_anova <- anova(hr_stress_m2, hr_stress_m3)
+hr_stress_anova
 ```
@@
 
-hr_eng_m1 <- lm(engagement ~ overall.hindrance_center, data = data)
+hr_eng_m1 <- lm(scale(engagement) ~ scale(overall.hindrance_center), data = data)
 summary(hr_eng_m1)
 
-hr_eng_m2 <- lm(engagement ~ overall.hindrance_center + overall.resource_center, data = data)
+hr_eng_m2 <- lm(scale(engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center), data = data)
 summary(hr_eng_m2)
 
-hr_eng_m3 <- lm(engagement ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
+hr_eng_m3 <- lm(scale(engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), data = data)
 summary(hr_eng_m3)
 
-anova(hr_eng_m2, hr_eng_m3)
+hr_eng_anova <- anova(hr_eng_m2, hr_eng_m3)
+hr_eng_anova
 ```
@@
 Model <- c("Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource")
-b <- c(chal.2.eng, res.2.eng, int.cr.3.eng, chal.2.stress, res.2.stress, int.cr.3.stress, chal.2.burn, res.2.burn, int.cr.3.burn)
-R2 <- c("", cr_eng_m2_r, cr_eng_m3_r, "", cr_stress_m2_r, cr_stress_m3_r, "", cr_burn_m2_r, cr_burn_m3_r)
-DeltaR <- c("",paste(cr_eng_m2_r),cr_eng_r_square_change, "",paste(cr_stress_m2_r),cr_stress_r_square_change, "",paste(cr_burn_m2_r),cr_burn_r_square_change)
+Beta <- c(chal.2.eng, res.2.eng, int.cr.3.eng, chal.2.stress, res.2.stress, int.cr.3.stress, chal.2.burn, res.2.burn, int.cr.3.burn)
+R <- c("", cr_eng_m2_r, cr_eng_m3_r, "", cr_stress_m2_r, cr_stress_m3_r, "", cr_burn_m2_r, cr_burn_m3_r)
+DeltaR <- c("","",cr_eng_r_square_change, "","",cr_stress_r_square_change, "","",cr_burn_r_square_change)
 
-regtable <- cbind(DV, Step, Model, b, R2, DeltaR)
-
+regtable <- cbind(DV, Step, Model, Beta, R, DeltaR)
 papaja::apa_table(regtable)
-
 ```
@@
 Model <- c("Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource")
-b <- c(hind.2.eng, res.2hr.eng, int.hr.3.eng, hind.2.stress, res.2hr.stress, int.hr.3.stress, hind.2.burn, res.2hr.burn, int.hr.3.burn)
+Beta <- c(hind.2.eng, res.2hr.eng, int.hr.3.eng, hind.2.stress, res.2hr.stress, int.hr.3.stress, hind.2.burn, res.2hr.burn, int.hr.3.burn)
 R2 <- c("", hr_eng_m2_r, hr_eng_m3_r, "", hr_stress_m2_r, hr_stress_m3_r, "", hr_burn_m2_r, hr_burn_m3_r)
-DeltaR <- c("",paste(hr_eng_m2_r,"**"),hr_eng_r_square_change, "",paste(hr_stress_m2_r,"**"),hr_stress_r_square_change, "",paste(hr_burn_m2_r,"**"),hr_burn_r_square_change)
-
-regtable <- cbind(DV, Step, Model, b, R2, DeltaR)
+#DeltaR <- c("",paste(hr_eng_m2_r,"**"),hr_eng_r_square_change, "",paste(hr_stress_m2_r,"**"),hr_stress_r_square_change, "",paste(hr_burn_m2_r,"**"),hr_burn_r_square_change)
+DeltaR <- c("","",hr_eng_r_square_change, "","",hr_stress_r_square_change, "","",hr_burn_r_square_change)
+regtable <- cbind(DV, Step, Model, Beta, R2, DeltaR)
 

### 2024-05-07 moderated_regressions.Rmd
table prettied

@@
 title: "moderated_regressions"
-output: pdf_document
+output: 
+  pdf_document:
+    latex_engine: xelatex
 date: "2024-04-13"
@@
 ```{r data, include = FALSE}
+
+sigfill <- function(x, sigfigs = 3){
+  out <- gsub("\\.$", "",
+              formatC(signif(x, digits = sigfigs),
+                      digits = sigfigs, format = "fg", flag = "#"))
+  out[grepl(".", out, fixed = TRUE)] <- strtrim(out[grepl(".", out, fixed = TRUE)],
+                                                sigfigs + c(1, 2)[grepl("-", out, fixed = TRUE) + 1])
+  return(out)
+}
+
 data <- read.csv("SIOPcleaned.csv")      ## from "datacleaning.R" script
@@
 #r squared
-hr_eng_m2_r <- round(summary(hr_eng_m2)$r.squared,2)
-hr_eng_m3_r <- round(summary(hr_eng_m3)$r.squared,2)
+hr_eng_m2_r <- summary(hr_eng_m2)$r.squared
+hr_eng_m3_r <- summary(hr_eng_m3)$r.squared
 
@@
 hr_eng_anova <- anova(hr_eng_m2, hr_eng_m3)
-hr_eng_r_square_change <- round(hr_eng_m3_r - hr_eng_m2_r,2)
+hr_eng_r_square_change <- sigfill(hr_eng_m3_r - hr_eng_m2_r)
 ```
@@
 Model <- c("Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource")
-Beta <- c(hind.2.eng, res.2hr.eng, int.hr.3.eng, hind.2.stress, res.2hr.stress, int.hr.3.stress, hind.2.burn, res.2hr.burn, int.hr.3.burn)
-R2 <- c("", hr_eng_m2_r, hr_eng_m3_r, "", hr_stress_m2_r, hr_stress_m3_r, "", hr_burn_m2_r, hr_burn_m3_r)
+Beta <- c(paste(hind.2.eng,"**"), paste(res.2hr.eng,"**"), int.hr.3.eng, paste(sigfill(hind.2.stress),"*"), paste(res.2hr.stress,"**"), paste(int.hr.3.stress,"**"), paste(sigfill(hind.2.burn),"*"), paste(res.2hr.burn,"*"), paste(int.hr.3.burn,"**"))
+R2 <- c("", paste(round(hr_eng_m2_r,2),"**"), paste(round(hr_eng_m3_r,2),"**"), "", paste(hr_stress_m2_r,"*"), paste(hr_stress_m3_r, "**"), "", paste(hr_burn_m2_r,"**"), paste(hr_burn_m3_r,"**"))
 #DeltaR <- c("",paste(hr_eng_m2_r,"**"),hr_eng_r_square_change, "",paste(hr_stress_m2_r,"**"),hr_stress_r_square_change, "",paste(hr_burn_m2_r,"**"),hr_burn_r_square_change)
-DeltaR <- c("","",hr_eng_r_square_change, "","",hr_stress_r_square_change, "","",hr_burn_r_square_change)
-regtable <- cbind(DV, Step, Model, Beta, R2, DeltaR)
+DeltaR <- c("","",hr_eng_r_square_change, "","",paste(hr_stress_r_square_change,"**"), "","",paste(hr_burn_r_square_change, "**"))
+regtable <- as.data.frame(cbind(DV, Step, Model, Beta, R2, DeltaR))
 
-papaja::apa_table(regtable)
+colnames(regtable)[4] <- "$\\beta$"
+colnames(regtable)[5] <- "$R^2$"
+colnames(regtable)[6] <- "$\\Delta R^2$"
+
+#kableExtra::kable(regtable,
+#                  format="latex",
+#                  escape=FALSE)
+
+papaja::apa_table(regtable,
+                 escape=FALSE,
+                 note="* = p < .05; ** = p < .01")
 # How to get delta symbol and superscript

### 2024-05-10 moderated_regressions.Rmd
updating regression tables. yet need to align numbers and add plot of the interaction

@@
 #r squared
-cr_burn_m2_r <- round(summary(cr_burn_m2)$r.squared,2)
-cr_burn_m3_r <- round(summary(cr_burn_m3)$r.squared,2)
+cr_burn_m2_r <- summary(cr_burn_m2)$r.squared
+cr_burn_m3_r <- summary(cr_burn_m3)$r.squared
 
@@
 cr_burn_anova <- anova(cr_burn_m2, cr_burn_m3)
-cr_burn_r_square_change <- round(cr_burn_m3_r - cr_burn_m2_r,2)
+cr_burn_r_square_change <- sigfill(cr_burn_m3_r - cr_burn_m2_r)
 
@@
 #r squared
-cr_stress_m2_r <- round(summary(cr_stress_m2)$r.squared,2)
-cr_stress_m3_r <- round(summary(cr_stress_m3)$r.squared,2)
+cr_stress_m2_r <- summary(cr_stress_m2)$r.squared
+cr_stress_m3_r <- summary(cr_stress_m3)$r.squared
 
@@
 cr_stress_anova <- anova(cr_stress_m2, cr_stress_m3)
-cr_stress_r_square_change <- round(cr_stress_m3_r - cr_stress_m2_r,2)
+cr_stress_r_square_change <- sigfill(cr_stress_m3_r - cr_stress_m2_r)
 
@@
 Model <- c("Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource")
-Beta <- c(chal.2.eng, res.2.eng, int.cr.3.eng, chal.2.stress, res.2.stress, int.cr.3.stress, chal.2.burn, res.2.burn, int.cr.3.burn)
-R <- c("", cr_eng_m2_r, cr_eng_m3_r, "", cr_stress_m2_r, cr_stress_m3_r, "", cr_burn_m2_r, cr_burn_m3_r)
-DeltaR <- c("","",cr_eng_r_square_change, "","",cr_stress_r_square_change, "","",cr_burn_r_square_change)
+Beta <- c(chal.2.eng, paste(res.2.eng,"**"), paste(int.cr.3.eng,"*"), chal.2.stress, res.2.stress, int.cr.3.stress, paste(chal.2.burn,"**"), res.2.burn, int.cr.3.burn)
+R2 <- c("", paste(cr_eng_m2_r,"**"), paste(cr_eng_m3_r,"**"), "", round(cr_stress_m2_r,2), round(cr_stress_m3_r,2), "", paste(round(cr_burn_m2_r,2),"**"), paste(round(cr_burn_m3_r,2),"**"))
+DeltaR <- c("","", paste(cr_eng_r_square_change,"*"), "","",cr_stress_r_square_change, "","",cr_burn_r_square_change)
 
-regtable <- cbind(DV, Step, Model, Beta, R, DeltaR)
-papaja::apa_table(regtable)
+#paste(round(hr_eng_m3_r,2),"**")
+
+regtable <- as.data.frame(cbind(DV, Step, Model, Beta, R2, DeltaR))
+
+colnames(regtable)[4] <- "$\\beta$"
+colnames(regtable)[5] <- "$R^2$"
+colnames(regtable)[6] <- "$\\Delta R^2$"
+
+#kableExtra::kable(regtable,
+#                  format="latex",
+#                  escape=FALSE)
+
+papaja::apa_table(regtable,
+                 escape=FALSE,
+                 note="* = p < .05; ** = p < .01")
+
+#https://stackoverflow.com/questions/67088456/r-aligning-table-content-to-decimal-points-in-kable
+
+#tribble(
+#  ~Variable_1,~Variable_2,
+#  "13.5","4.4**",
+#  "12.7***","1.2*",
+#  "0.4","0.3***",
+#  "2.3**","11.5**"
+#)%>%
+#  rename_all( ~ str_c("{ ",.," }"))%>%
+#  kable(format = "latex", booktabs=T, escape = T)%>%
+#  kable_styling(position = "center", latex_options = "hold_position")
 ```
@@
                  note="* = p < .05; ** = p < .01")
-# How to get delta symbol and superscript
-#https://cran.r-project.org/web/packages/reporter/vignettes/reporter-super.html#:~:text=To%20get%20superscripts%20or%20subscripts,to%20the%20desired%20cell%20value.
-
 ```

### 2024-05-14 moderated_regressions.Rmd
Adding interaction graphs

@@
 Model <- c("Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource")
-Beta <- c(chal.2.eng, paste(res.2.eng,"**"), paste(int.cr.3.eng,"*"), chal.2.stress, res.2.stress, int.cr.3.stress, paste(chal.2.burn,"**"), res.2.burn, int.cr.3.burn)
+Beta <- c(sigfill(chal.2.eng), paste(res.2.eng,"**"), paste(int.cr.3.eng,"*"), chal.2.stress, res.2.stress, int.cr.3.stress, paste(chal.2.burn,"**"), res.2.burn, int.cr.3.burn)
 R2 <- c("", paste(cr_eng_m2_r,"**"), paste(cr_eng_m3_r,"**"), "", round(cr_stress_m2_r,2), round(cr_stress_m3_r,2), "", paste(round(cr_burn_m2_r,2),"**"), paste(round(cr_burn_m3_r,2),"**"))
 DeltaR <- c("","", paste(cr_eng_r_square_change,"*"), "","",cr_stress_r_square_change, "","",cr_burn_r_square_change)
-
-#paste(round(hr_eng_m3_r,2),"**")
 
@@
 
-#kableExtra::kable(regtable,
-#                  format="latex",
-#                  escape=FALSE)
-
 papaja::apa_table(regtable, 
@@
                 note="* = p < .05; ** = p < .01")
-
-#https://stackoverflow.com/questions/67088456/r-aligning-table-content-to-decimal-points-in-kable
-
-#tribble(
-#  ~Variable_1,~Variable_2,
-#  "13.5","4.4**",
-#  "12.7***","1.2*",
-#  "0.4","0.3***",
-#  "2.3**","11.5**"
-#)%>%
-#  rename_all( ~ str_c("{ ",.," }"))%>%
-#  kable(format = "latex", booktabs=T, escape = T)%>%
-#  kable_styling(position = "center", latex_options = "hold_position")
 ```
@@
 ```
+
+```{r fig.cap="Interaction between Challenge and Resources on Engagement"}
+#install.packages("interactions")
+library(interactions)
+
+#running it with unstandardized bs here. 
+cr_eng_m3u <- lm(engagement ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
+summary(cr_eng_m3u)
+
+cr_eng_plot <- interact_plot(cr_eng_m3u, pred = overall.challenge_center, modx = overall.resource_center, interval = TRUE,
+              int.width = 0.8)
+cr_eng_plot
+```
+
+```{r fig.cap="Interaction between Hindrances and Resources on Stress"}
+#install.packages("interactions")
+library(interactions)
+
+hr_stress_m3u <- lm(stress ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
+summary(hr_stress_m3u)
+
+hr_stress_plot <- interact_plot(hr_stress_m3u, pred = overall.hindrance_center, modx = overall.resource_center, interval = TRUE,
+              int.width = 0.8)
+hr_stress_plot
+```
+
+```{r fig.cap="Interaction between Hindrances and Resources on Burnout"}
+#install.packages("interactions")
+library(interactions)
+
+hr_burn_m3u <- lm(burnout ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
+summary(hr_burn_m3u)
+
+hr_burn_plot <- interact_plot(hr_burn_m3u, pred = overall.hindrance_center, modx = overall.resource_center, interval = TRUE,
+              int.width = 0.8)
+hr_burn_plot
+```

### 2024-05-14 moderated_regressions.Rmd
changing plots

@@
 
-cr_eng_plot <- interact_plot(cr_eng_m3u, pred = overall.challenge_center, modx = overall.resource_center, interval = TRUE,
+cr_eng_plot <- interact_plot(cr_eng_m3u, pred = overall.challenge_center, modx = overall.resource_center, interval = FALSE,
               int.width = 0.8)
@@
 
-hr_stress_plot <- interact_plot(hr_stress_m3u, pred = overall.hindrance_center, modx = overall.resource_center, interval = TRUE,
+hr_stress_plot <- interact_plot(hr_stress_m3u, pred = overall.hindrance_center, modx = overall.resource_center, interval = FALSE, 
               int.width = 0.8)
@@
 
-hr_burn_plot <- interact_plot(hr_burn_m3u, pred = overall.hindrance_center, modx = overall.resource_center, interval = TRUE,
+hr_burn_plot <- interact_plot(hr_burn_m3u, pred = overall.hindrance_center, modx = overall.resource_center, interval = FALSE, 
               int.width = 0.8)

### 2024-05-21 Submission.Rmd
creating tables
updating results section

@@
 
->Hyp 4.a:Resources moderate the relationship between challenge stressors and the outcomes of strain and burnout such that these relationship become weaker as workers perceive more resources.
-
->Hyp 4.b:Resources moderate the relationship between hindrance stressors and the outcomes of strain and burnout such that these relationship become weaker as workers perceive more resources.
+>Hyp 4.a:Resources moderate the relationship between challenge stressors and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
+
+>Hyp 4.b:Resources moderate the relationship between hindrance stressors and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
 
@@
 
+```{r modreg, include = FALSE}
+# This is pasted from this point below (data object = modreg) from the 
+# moderated regression rmd file on 5/21/2024
+
+sigfill <- function(x, sigfigs = 3){
+  out <- gsub("\\.$", "",
+              formatC(signif(x, digits = sigfigs),
+                      digits = sigfigs, format = "fg", flag = "#"))
+  out[grepl(".", out, fixed = TRUE)] <- strtrim(out[grepl(".", out, fixed = TRUE)],
+                                                sigfigs + c(1, 2)[grepl("-", out, fixed = TRUE) + 1])
+  return(out)
+}
+
+modreg <- read.csv("SIOPcleaned.csv")      ## from "datacleaning.R" script
+
+## Study 2 DVs
+
+modreg$item387      <- 7- modreg$item387           ## only reflected engagement item
+
+modreg$absorption   <- rowMeans(modreg[c(380:386)], na.rm=TRUE)
+modreg$vigor        <- rowMeans(modreg[c(387:392)], na.rm=TRUE) 
+modreg$dedication   <- rowMeans(modreg[c(393:399)], na.rm=TRUE)
+
+modreg$cognitive    <- rowMeans(modreg[c(380:382, 387:388, 393:395)], na.rm=TRUE)
+modreg$affective    <- rowMeans(modreg[c(383:384, 389:390, 396:397)], na.rm=TRUE) 
+modreg$behavioral   <- rowMeans(modreg[c(385:386, 391:392, 398:399)], na.rm=TRUE)
+
+######################################################
+
+modreg$burnout      <- rowMeans(modreg[c(373:376)], na.rm=TRUE)
+modreg$stress       <- rowMeans(modreg[c(377:379)], na.rm=TRUE)
+modreg$engagement   <- rowMeans(modreg[c(380:399)], na.rm=TRUE)        ## added 10/12 because analyses too wonky with 3 subscales
+
+alpha.abs <- psych::alpha(modreg[c(380:386)])
+alpha.vig <- psych::alpha(modreg[c(387:392)])
+alpha.ded <- psych::alpha(modreg[c(393:399)])
+alpha.eng <- psych::alpha(modreg[c(380:399)])
+
+alpha.bur <- psych::alpha(modreg[c(373:376)])
+alpha.str <- psych::alpha(modreg[c(377:379)])
+
+## O*NET categories
+
+modreg$onet.resource.ii <- rowMeans(modreg[c(162:166)], na.rm=TRUE)
+modreg$onet.resource.mp <- rowMeans(modreg[c(167:176)], na.rm=TRUE)
+modreg$onet.resource.wo <- rowMeans(modreg[c(177:185)], na.rm=TRUE)
+modreg$onet.resource.io <- rowMeans(modreg[c(186:202)], na.rm=TRUE)
+modreg$onet.resource.ir <- rowMeans(modreg[c(149:161)], na.rm=TRUE)
+modreg$onet.resource.pc <- rowMeans(modreg[c(128:144,146:148)], na.rm=TRUE)
+modreg$onet.resource.sc <- rowMeans(modreg[c(118:127)], na.rm=TRUE)
+
+overall.resource <- rowMeans(modreg[c(118:144,147:202)], na.rm=TRUE)
+
+modreg$onet.hindrance.ii <- rowMeans(modreg[c(246:247,249:252)], na.rm=TRUE)
+modreg$onet.hindrance.mp <- rowMeans(modreg[c(252:261)], na.rm=TRUE)
+modreg$onet.hindrance.wo <- rowMeans(modreg[c(262:270)], na.rm=TRUE)
+modreg$onet.hindrance.io <- rowMeans(modreg[c(271:287)], na.rm=TRUE)
+modreg$onet.hindrance.ir <- rowMeans(modreg[c(233:245)], na.rm=TRUE)
+modreg$onet.hindrance.pc <- rowMeans(modreg[c(213:232)], na.rm=TRUE)
+modreg$onet.hindrance.sc <- rowMeans(modreg[c(203:212)], na.rm=TRUE)
+
+overall.hindrance <- rowMeans(modreg[c(203:247,249:287)], na.rm=TRUE)
+
+modreg$onet.challenge.ii <- rowMeans(modreg[c(332:336)], na.rm=TRUE)
+modreg$onet.challenge.mp <- rowMeans(modreg[c(337:346)], na.rm=TRUE)
+modreg$onet.challenge.wo <- rowMeans(modreg[c(347:355)], na.rm=TRUE)
+modreg$onet.challenge.io <- rowMeans(modreg[c(356:372)], na.rm=TRUE)
+modreg$onet.challenge.ir <- rowMeans(modreg[c(319:331)], na.rm=TRUE)
+modreg$onet.challenge.pc <- rowMeans(modreg[c(298:307,309:318)], na.rm=TRUE)
+modreg$onet.challenge.sc <- rowMeans(modreg[c(288:297)], na.rm=TRUE)
+
+overall.challenge <- rowMeans(modreg[c(288:307,309:372)], na.rm=TRUE)
+
+```
+We next explored whether there was statistical support for the hypothesis that the relationship between the challenge stressors and outcomes (i.e., engagement, stress, and burnout) were moderated by resources.
+In order to test for the presence of an interactive effect, a series of hierarchical regressions were conducted with challenge stressors and resources added in step one of the model and an interaction term, challenge stressors*resources, added in step two of the model.
+
+```{r AnalyseswithRowSums}
+overall.resource <- rowSums(modreg[c(118:144,147:202)], na.rm=TRUE)
+#summary(overall.resource) #202.3
+overall.hindrance <- rowSums(modreg[c(203:247,249:287)], na.rm=TRUE)
+#summary(overall.hindrance) #159.2
+overall.challenge <- rowSums(modreg[c(288:307,309:372)], na.rm=TRUE)
+#summary(overall.challenge) #204.2
+
+#centered predictors
+overall.resource_center <- overall.resource - 202.3
+overall.hindrance_center <- overall.hindrance - 159.2
+overall.challenge_center <- overall.challenge - 204.2
+```
+
+```{r ModeratedRegressionChallenge-ResourceBurnout}
+
+cr_burn_m1 <- lm(scale(burnout) ~ scale(overall.challenge_center), modreg)
+#summary(cr_burn_m1)
+
+cr_burn_m2 <- lm(scale(burnout) ~ scale(overall.challenge_center) + scale(overall.resource), modreg)
+#summary(cr_burn_m2)
+
+cr_burn_m3 <- lm(scale(burnout) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
+#summary(cr_burn_m3)
+
+aov_test <- anova(cr_burn_m2, cr_burn_m3)
+#aov_test
+```
+
+```{r ModeratedRegressionChallenge-ResourceStress}
+
+cr_stress_m1 <- lm(scale(stress) ~ scale(overall.challenge_center), modreg)
+#summary(cr_stress_m1)
+
+cr_stress_m2 <- lm(scale(stress) ~ scale(overall.challenge_center) + scale(overall.resource_center), modreg)
+#summary(cr_stress_m2)
+
+cr_stress_m3 <- lm(scale(stress) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
+#summary(cr_stress_m3)
+
+cr_stress_anova <- anova(cr_stress_m2, cr_stress_m3)
+#cr_stress_anova
+```
+
+```{r Moderated Regression Challenge-ResourceEngagement}
+
+cr_eng_m1 <- lm(scale(engagement) ~ scale(overall.challenge_center), modreg)
+#summary(cr_eng_m1)
+
+cr_eng_m2 <- lm(scale(engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center), modreg)
+#summary(cr_eng_m2)
+
+cr_eng_m3 <- lm(scale(engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
+#summary(cr_eng_m3)
+
+cr_eng_anova <- anova(cr_eng_m2, cr_eng_m3)
+#cr_eng_anova
+```
+
+```{r Moderated Regression Hindrance-Resource Burnout}
+
+hr_burn_m1 <- lm(scale(burnout) ~ scale(overall.hindrance_center), modreg)
+#summary(hr_burn_m1)
+
+hr_burn_m2 <- lm(scale(burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
+#summary(hr_burn_m2)
+
+hr_burn_m3 <- lm(scale(burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
+#summary(hr_burn_m3)
+
+hr_burn_anova <- anova(hr_burn_m2, hr_burn_m3)
+#hr_burn_anova
+```
+
+```{r ModeratedRegressionHindrance-ResourceStress}
+
+hr_stress_m1 <- lm(scale(stress) ~ scale(overall.hindrance_center), modreg)
+#summary(hr_stress_m1)
+
+hr_stress_m2 <- lm(scale(stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
+#summary(hr_stress_m2)
+
+hr_stress_m3 <- lm(scale(stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
+#summary(hr_stress_m3)
+
+hr_stress_anova <- anova(hr_stress_m2, hr_stress_m3)
+#hr_stress_anova
+```
+
+```{r Moderated Regression Hindrance-Resource Engagement}
+
+hr_eng_m1 <- lm(scale(engagement) ~ scale(overall.hindrance_center), modreg)
+#summary(hr_eng_m1)
+
+hr_eng_m2 <- lm(scale(engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
+#summary(hr_eng_m2)
+
+hr_eng_m3 <- lm(scale(engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
+#summary(hr_eng_m3)
+
+hr_eng_anova <- anova(hr_eng_m2, hr_eng_m3)
+#hr_eng_anova
+```
+
+```{r NumbersforTable1}
+
+options(scipen=999)  ## Suppresses scientific notation
+
+#Challenge-Resource-Burnout
+
+# b weights
+chal.2.burn <- round(summary(cr_burn_m2)$coefficients[2, 1],2)
+res.2.burn <- round(summary(cr_burn_m2)$coefficients[3, 1],2)
+
+int.cr.3.burn <- round(summary(cr_burn_m3)$coefficients[4, 1],2)
+
+#r squared
+cr_burn_m2_r <- summary(cr_burn_m2)$r.squared
+cr_burn_m3_r <- summary(cr_burn_m3)$r.squared
+
+## R square change
+cr_burn_anova <- anova(cr_burn_m2, cr_burn_m3)
+cr_burn_r_square_change <- sigfill(cr_burn_m3_r - cr_burn_m2_r)
+
+#Challenge-Resource-Stress
+
+# b weights
+chal.2.stress <- round(summary(cr_stress_m2)$coefficients[2, 1],2)
+res.2.stress <- round(summary(cr_stress_m2)$coefficients[3, 1],2)
+
+int.cr.3.stress <- round(summary(cr_stress_m3)$coefficients[4, 1],2)
+
+#r squared
+cr_stress_m2_r <- summary(cr_stress_m2)$r.squared
+cr_stress_m3_r <- summary(cr_stress_m3)$r.squared
+
+## R square change
+cr_stress_anova <- anova(cr_stress_m2, cr_stress_m3)
+cr_stress_r_square_change <- sigfill(cr_stress_m3_r - cr_stress_m2_r)
+
+#Challenge-Resource-Engagement
+
+# b weights
+chal.2.eng <- round(summary(cr_eng_m2)$coefficients[2, 1],2)
+res.2.eng <- round(summary(cr_eng_m2)$coefficients[3, 1],2)
+
+int.cr.3.eng <- round(summary(cr_eng_m3)$coefficients[4, 1],2)
+
+#r squared
+cr_eng_m2_r <- round(summary(cr_eng_m2)$r.squared,2)
+cr_eng_m3_r <- round(summary(cr_eng_m3)$r.squared,2)
+
+## R square change
+cr_eng_anova <- anova(cr_eng_m2, cr_eng_m3)
+cr_eng_r_square_change <- round(cr_eng_m3_r - cr_eng_m2_r,2)
+```
+
+```{r NumbersforTable2}
+
+options(scipen=999)  ## Suppresses scientific notation
+
+#Hindrance-Resource-Burnout
+
+# b weights
+hind.2.burn <- round(summary(hr_burn_m2)$coefficients[2, 1],2)
+res.2hr.burn <- round(summary(hr_burn_m2)$coefficients[3, 1],2)
+
+int.hr.3.burn <- round(summary(hr_burn_m3)$coefficients[4, 1],2)
+
+#r squared
+hr_burn_m2_r <- round(summary(hr_burn_m2)$r.squared,2)
+hr_burn_m3_r <- round(summary(hr_burn_m3)$r.squared,2)
+
+## R square change
+hr_burn_anova <- anova(hr_burn_m2, hr_burn_m3)
+hr_burn_r_square_change <- round(hr_burn_m3_r - hr_burn_m2_r,2)
+
+#Hindrance-Resource-Stress
+
+# b weights
+hind.2.stress <- round(summary(hr_stress_m2)$coefficients[2, 1],2)
+res.2hr.stress <- round(summary(hr_stress_m2)$coefficients[3, 1],2)
+
+int.hr.3.stress <- round(summary(hr_stress_m3)$coefficients[4, 1],2)
+
+#r squared
+hr_stress_m2_r <- round(summary(hr_stress_m2)$r.squared,2)
+hr_stress_m3_r <- round(summary(hr_stress_m3)$r.squared,2)
+
+## R square change
+hr_stress_anova <- anova(hr_stress_m2, hr_stress_m3)
+hr_stress_r_square_change <- round(hr_stress_m3_r - hr_stress_m2_r,2)
+
+#Hindrance-Resource-Engagement
+
+# b weights
+hind.2.eng <- round(summary(hr_eng_m2)$coefficients[2, 1],2)
+res.2hr.eng <- round(summary(hr_eng_m2)$coefficients[3, 1],2)
+
+int.hr.3.eng <- round(summary(hr_eng_m3)$coefficients[4, 1],2)
+
+#r squared
+hr_eng_m2_r <- summary(hr_eng_m2)$r.squared
+hr_eng_m3_r <- summary(hr_eng_m3)$r.squared
+
+## R square change
+hr_eng_anova <- anova(hr_eng_m2, hr_eng_m3)
+hr_eng_r_square_change <- sigfill(hr_eng_m3_r - hr_eng_m2_r)
+```
+
+```{r, results='asis', include=FALSE}
+#I'm not touching this script - using it as a model and making two new chunks
+library(kableExtra)
+
+DV <- c("Burnout","","")
+Step <- c("1", "","2")
+Model <- c("Challenge", "Resource", "Challenge X Resource")
+b <- c(chal.2.burn,res.2.burn,int.cr.3.burn)
+DeltaR <- c("",paste(cr_burn_m2_r,"**"),cr_burn_r_square_change)
+
+regtable <- cbind(DV, Step, Model, b, DeltaR)
+
+papaja::apa_table(regtable)
+
+```
+
+```{r chal-resource-table, results='asis'}
+
+library(kableExtra)
+
+DV <- c("Engagement","","", "Stress","","", "Burnout","","")
+Step <- c("1", "","2", "1", "","2", "1", "","2")
+Model <- c("Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource")
+Beta <- c(sigfill(chal.2.eng), paste(res.2.eng,"**"), paste(int.cr.3.eng,"*"), chal.2.stress, res.2.stress, int.cr.3.stress, paste(chal.2.burn,"**"), res.2.burn, int.cr.3.burn)
+R2 <- c("", paste(cr_eng_m2_r,"**"), paste(cr_eng_m3_r,"**"), "", round(cr_stress_m2_r,2), round(cr_stress_m3_r,2), "", paste(round(cr_burn_m2_r,2),"**"), paste(round(cr_burn_m3_r,2),"**"))
+DeltaR <- c("","", paste(cr_eng_r_square_change,"*"), "","",cr_stress_r_square_change, "","",cr_burn_r_square_change)
+
+regtable <- as.data.frame(cbind(DV, Step, Model, Beta, R2, DeltaR))
+
+colnames(regtable)[4] <- "$\\beta$"
+colnames(regtable)[5] <- "$R^2$"
+colnames(regtable)[6] <- "$\\Delta R^2$"
+
+papaja::apa_table(regtable, 
+                 escape=FALSE,
+                note="* = p < .05; ** = p < .01")
+```
+
+Table \@ref(tab:chal-resource-table) summarizes the results.
+Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions.
+First exploring engagement, challenge stressors and resources explained XX% of the variance in engagement, $R^2$ = .xx.
+Adj.
+$R^2$ = .xx, which represents a statistically significant effect, *F*(x, xx) = xx.xx, *p* < xxx.
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, $Delta R^2$ = .xx, $Delta F$(xx, xx) = .xx, *p* = xx, and thus provides statistical support for the presence of moderation.
+The total model explained xx% of the variance in engagement, $R^2$ = .xx.
+Adj.
+$R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx.
+Figure \@ref(fig:chal-resource-int) illustrates the interaction.
+With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low.
+With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.
+
+Next, challenge stressors and resources explained XX% of the variance in stress, $R^2$ = .xx.
+Adj.
+$R^2$ = .xx, which represents a non-significant effect, *F*(x, xx) = xx.xx, *p* xxx.
+The inclusion of the interaction term in step two of the model did not add significantly to the model, $Delta R^2$ = .xx, $Delta F$(xx, xx) = .xx, *p* = xxx.
+The total model explained xx% of the variance in stress, $R^2$ = .xx.
+Adj.
+$R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx.
+
+Finally, challenge stressors and resources explained XX% of the variance in burnout, $R^2$ = .xx.
+Adj.
+$R^2$ = .xx, which represents a statistically significant effect, *F*(x, xx) = xx.xx, *p* xxx.
+The inclusion of the interaction term in step two of the model did not add significantly to the model, $Delta R^2$ = .xx, $Delta F$(xx, xx) = .xx, *p* = xxx.
+The total model explained xx% of the variance in stress, $R^2$ = .xx.
+Adj.
+$R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx.
+In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge stressors and the outcomes of strain  and burnout.
+
+```{r hind-resource-table, results='asis'}
+
+library(kableExtra)
+
+DV <- c("Engagement","","", "Stress","","", "Burnout","","")
+Step <- c("1", "","2", "1", "","2", "1", "","2")
+Model <- c("Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource")
+Beta <- c(paste(hind.2.eng,"**"), paste(res.2hr.eng,"**"), int.hr.3.eng, paste(sigfill(hind.2.stress),"*"), paste(res.2hr.stress,"**"), paste(int.hr.3.stress,"**"), paste(sigfill(hind.2.burn),"*"), paste(res.2hr.burn,"*"), paste(int.hr.3.burn,"**"))
+R2 <- c("", paste(round(hr_eng_m2_r,2),"**"), paste(round(hr_eng_m3_r,2),"**"), "", paste(hr_stress_m2_r,"*"), paste(hr_stress_m3_r, "**"), "", paste(hr_burn_m2_r,"**"), paste(hr_burn_m3_r,"**"))
+#DeltaR <- c("",paste(hr_eng_m2_r,"**"),hr_eng_r_square_change, "",paste(hr_stress_m2_r,"**"),hr_stress_r_square_change, "",paste(hr_burn_m2_r,"**"),hr_burn_r_square_change)
+DeltaR <- c("","",hr_eng_r_square_change, "","",paste(hr_stress_r_square_change,"**"), "","",paste(hr_burn_r_square_change, "**"))
+regtable <- as.data.frame(cbind(DV, Step, Model, Beta, R2, DeltaR))
+
+colnames(regtable)[4] <- "$\\beta$"
+colnames(regtable)[5] <- "$R^2$"
+colnames(regtable)[6] <- "$\\Delta R^2$"
+
+#kableExtra::kable(regtable,
+#                  format="latex",
+#                  escape=FALSE)
+
+papaja::apa_table(regtable,
+                 escape=FALSE,
+                 note="* = p < .05; ** = p < .01")
+```
+We also explored whether there was an interaction between hindrance stressors and resources on the outcomes (i.e., engagement, stress, and burnout).
+A second group of hierarchical regressions were conducted with hindrance stressors and resources added in step one of the model and an interaction term, hindrance stressors*resources, added in step two of the model.
+See Table \@ref(tab:ind-resource-table).
+
+Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions.
+First, hindrance stressors and resources explained XX% of the variance in engagement, $R^2$ = .xx.
+Adj.
+$R^2$ = .xx, which represents a statistically significant effect, *F*(x, xx) = xx.xx, *p* xxx.
+The inclusion of the interaction term in step two of the model did not add significantly to the model, $Delta R^2$ = .xx, $Delta F$(xx, xx) = .xx, *p* = xxx.
+The total model explained xx% of the variance in engagement, $R^2$ = .xx.
+Adj.
+$R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx.
+
+Next exploring stress, hindrance stressors and resources explained XX% of the variance in stress, $R^2$ = .xx.
+Adj.
+$R^2$ = .xx, which represents a statistically significant effect, *F*(x, xx) = xx.xx, *p* xxx.
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, $Delta R^2$ = .xx, $Delta F$(xx, xx) = .xx, *p* = xx, and thus provides statistical support for the presence of moderation.
+The total model explained xx% of the variance in stress, $R^2$ = .xx.
+Adj.
+$R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx.
+See Figure \@ref(fig:hind-resource-stress-int).
+As expected, the relationship between hindrance stressors and strain becomes weaker as workers perceive more resources.
+
+Similarly, hindrance stressors and resources explained XX% of the variance in burnout, $R^2$ = .xx.
+Adj.
+$R^2$ = .xx, *F*(x, xx) = xx.xx, *p* xxx.
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, $Delta R^2$ = .xx, $Delta F$(xx, xx) = .xx, *p* = xx.
+The total model explained xx% of the variance in burnout,$R^2$ = .xx.
+Adj.
+$R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx.
+Again, see Figure \@ref(fig:hind-resource-burn-int).
+As expected, the relationship between hindrance stressors and burnout becomes weaker as workers perceive more resources.
+
+Summatively these findings provide support for the assertion that resources would moderate the relationships between hindrance stressors and the outcomes of strain and burnout.
+
+```{r chal-resource-int, fig.cap="Interaction between Challenge and Resources on Engagement"}
+#install.packages("interactions")
+library(interactions)
+
+#running it with unstandardized bs here. 
+cr_eng_m3u <- lm(engagement ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, modreg)
+#summary(cr_eng_m3u)
+
+cr_eng_plot <- interact_plot(cr_eng_m3u, pred = overall.challenge_center, modx = overall.resource_center, interval = FALSE,
+              int.width = 0.8)
+cr_eng_plot
+```
+
+```{r hind-resource-stress-int, fig.cap="Interaction between Hindrances and Resources on Stress"}
+#install.packages("interactions")
+library(interactions)
+
+hr_stress_m3u <- lm(stress ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, modreg)
+#summary(hr_stress_m3u)
+
+hr_stress_plot <- interact_plot(hr_stress_m3u, pred = overall.hindrance_center, modx = overall.resource_center, interval = FALSE, 
+              int.width = 0.8)
+hr_stress_plot
+```
+
+```{r hind-resource-burn-int, fig.cap="Interaction between Hindrances and Resources on Burnout"}
+#install.packages("interactions")
+library(interactions)
+
+hr_burn_m3u <- lm(burnout ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, modreg)
+#summary(hr_burn_m3u)
+
+hr_burn_plot <- interact_plot(hr_burn_m3u, pred = overall.hindrance_center, modx = overall.resource_center, interval = FALSE, 
+              int.width = 0.8)
+hr_burn_plot
+```
+
 In addition to the two hypotheses, two related research questions were proposed: 1) do literature-implicated resources materialize as perceived resources and 2) do literature-implicated demands materialize as perceived demands?

### 2024-05-21 Submission.tex
updating results section

@@
 \begin{quote}
-Hyp 4.a:Resources moderate the relationship between challenge stressors and the outcomes of strain and burnout such that these relationship become weaker as workers perceive more resources.
+Hyp 4.a:Resources moderate the relationship between challenge stressors and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
 \end{quote}
@@
 \begin{quote}
-Hyp 4.b:Resources moderate the relationship between hindrance stressors and the outcomes of strain and burnout such that these relationship become weaker as workers perceive more resources.
+Hyp 4.b:Resources moderate the relationship between hindrance stressors and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
 \end{quote}
@@
 \caption{\label{fig:scalelevelgraphs}Average characteristic rating grouped by literature-implicated categorizations.}
+\end{figure}
+
+We next explored whether there was statistical support for the hypothesis that the relationship between the challenge stressors and outcomes (i.e., engagement, stress, and burnout) were moderated by resources.
+In order to test for the presence of an interactive effect, a series of hierarchical regressions were conducted with challenge stressors and resources added in step one of the model and an interaction term, challenge stressors*resources, added in step two of the model.
+
+\begin{table*}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:chal-resource-table}}
+
+\begin{tabular}{llllll}
+\toprule
+DV & \multicolumn{1}{c}{Step} & \multicolumn{1}{c}{Model} & \multicolumn{1}{c}{$\beta$} & \multicolumn{1}{c}{$R^2$} & \multicolumn{1}{c}{$\Delta R^2$}\\
+\midrule
+Engagement & 1 & Challenge & -0.10 &  & \\
+ &  & Resource & 0.48 ** & 0.15 ** & \\
+ & 2 & Challenge X Resource & -0.09 * & 0.16 ** & 0.01 *\\
+Stress & 1 & Challenge & 0.14 &  & \\
+ &  & Resource & -0.07 & 0.01 & \\
+ & 2 & Challenge X Resource & 0.02 & 0.01 & 0.00\\
+Burnout & 1 & Challenge & 0.33 ** &  & \\
+ &  & Resource & -0.14 & 0.04 ** & \\
+ & 2 & Challenge X Resource & 0.06 & 0.04 ** & 0.00\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} * = p < .05; ** = p < .01}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table*}
+
+Table \ref{tab:chal-resource-table} summarizes the results.
+Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions.
+First exploring engagement, challenge stressors and resources explained XX\% of the variance in engagement, \(R^2\) = .xx.
+Adj.
+\(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} \textless{} xxx.
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(Delta R^2\) = .xx, \(Delta F\)(xx, xx) = .xx, \emph{p} = xx, and thus provides statistical support for the presence of moderation.
+The total model explained xx\% of the variance in engagement, \(R^2\) = .xx.
+Adj.
+\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
+Figure \ref{fig:chal-resource-int} illustrates the interaction.
+With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low.
+With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.
+
+Next, challenge stressors and resources explained XX\% of the variance in stress, \(R^2\) = .xx.
+Adj.
+\(R^2\) = .xx, which represents a non-significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
+The inclusion of the interaction term in step two of the model did not add significantly to the model, \(Delta R^2\) = .xx, \(Delta F\)(xx, xx) = .xx, \emph{p} = xxx.
+The total model explained xx\% of the variance in stress, \(R^2\) = .xx.
+Adj.
+\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
+
+Finally, challenge stressors and resources explained XX\% of the variance in burnout, \(R^2\) = .xx.
+Adj.
+\(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
+The inclusion of the interaction term in step two of the model did not add significantly to the model, \(Delta R^2\) = .xx, \(Delta F\)(xx, xx) = .xx, \emph{p} = xxx.
+The total model explained xx\% of the variance in stress, \(R^2\) = .xx.
+Adj.
+\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
+In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge stressors and the outcomes of strain and burnout.
+
+\begin{table*}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:hind-resource-table}}
+
+\begin{tabular}{llllll}
+\toprule
+DV & \multicolumn{1}{c}{Step} & \multicolumn{1}{c}{Model} & \multicolumn{1}{c}{$\beta$} & \multicolumn{1}{c}{$R^2$} & \multicolumn{1}{c}{$\Delta R^2$}\\
+\midrule
+Engagement & 1 & Hindrance & -0.14 ** &  & \\
+ &  & Resource & 0.46 ** & 0.17 ** & \\
+ & 2 & Hindrance X Resource & -0.02 & 0.17 ** & 0.00\\
+Stress & 1 & Hindrance & 0.10 * &  & \\
+ &  & Resource & 0.02 ** & 0.01 * & \\
+ & 2 & Hindrance X Resource & -0.19 ** & 0.04 ** & 0.03 **\\
+Burnout & 1 & Hindrance & 0.10 * &  & \\
+ &  & Resource & 0.12 * & 0.04 ** & \\
+ & 2 & Hindrance X Resource & -0.13 ** & 0.05 ** & 0.01 **\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} * = p < .05; ** = p < .01}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table*}
+
+We also explored whether there was an interaction between hindrance stressors and resources on the outcomes (i.e., engagement, stress, and burnout).
+A second group of hierarchical regressions were conducted with hindrance stressors and resources added in step one of the model and an interaction term, hindrance stressors*resources, added in step two of the model.
+See Table \ref{tab:ind-resource-table}.
+
+Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions.
+First, hindrance stressors and resources explained XX\% of the variance in engagement, \(R^2\) = .xx.
+Adj.
+\(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
+The inclusion of the interaction term in step two of the model did not add significantly to the model, \(Delta R^2\) = .xx, \(Delta F\)(xx, xx) = .xx, \emph{p} = xxx.
+The total model explained xx\% of the variance in engagement, \(R^2\) = .xx.
+Adj.
+\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
+
+Next exploring stress, hindrance stressors and resources explained XX\% of the variance in stress, \(R^2\) = .xx.
+Adj.
+\(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(Delta R^2\) = .xx, \(Delta F\)(xx, xx) = .xx, \emph{p} = xx, and thus provides statistical support for the presence of moderation.
+The total model explained xx\% of the variance in stress, \(R^2\) = .xx.
+Adj.
+\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
+See Figure \ref{fig:hind-resource-stress-int}.
+As expected, the relationship between hindrance stressors and strain becomes weaker as workers perceive more resources.
+
+Similarly, hindrance stressors and resources explained XX\% of the variance in burnout, \(R^2\) = .xx.
+Adj.
+\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(Delta R^2\) = .xx, \(Delta F\)(xx, xx) = .xx, \emph{p} = xx.
+The total model explained xx\% of the variance in burnout,\(R^2\) = .xx.
+Adj.
+\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
+Again, see Figure \ref{fig:hind-resource-burn-int}.
+As expected, the relationship between hindrance stressors and burnout becomes weaker as workers perceive more resources.
+
+Summatively these findings provide support for the assertion that resources would moderate the relationships between hindrance stressors and the outcomes of strain and burnout.
+
+\begin{figure}
+\centering
+\includegraphics{Submission_files/figure-latex/chal-resource-int-1.pdf}
+\caption{\label{fig:chal-resource-int}Interaction between Challenge and Resources on Engagement}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Submission_files/figure-latex/hind-resource-stress-int-1.pdf}
+\caption{\label{fig:hind-resource-stress-int}Interaction between Hindrances and Resources on Stress}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Submission_files/figure-latex/hind-resource-burn-int-1.pdf}
+\caption{\label{fig:hind-resource-burn-int}Interaction between Hindrances and Resources on Burnout}
 \end{figure}

### 2024-05-21 moderated_regressions.Rmd
updating results section

@@
 
-```{r data, include = FALSE}
+```{r modreg, include = FALSE}
 
@@
 
-data <- read.csv("SIOPcleaned.csv")      ## from "datacleaning.R" script
+modreg <- read.csv("SIOPcleaned.csv")      ## from "datacleaning.R" script
 
@@
 
-data$item387      <- 7- data$item387           ## only reflected engagement item
+modreg$item387      <- 7- modreg$item387           ## only reflected engagement item
 
-data$absorption   <- rowMeans(data[c(380:386)], na.rm=TRUE)
-data$vigor        <- rowMeans(data[c(387:392)], na.rm=TRUE) 
-data$dedication   <- rowMeans(data[c(393:399)], na.rm=TRUE)
+modreg$absorption   <- rowMeans(modreg[c(380:386)], na.rm=TRUE)
+modreg$vigor        <- rowMeans(modreg[c(387:392)], na.rm=TRUE) 
+modreg$dedication   <- rowMeans(modreg[c(393:399)], na.rm=TRUE)
 
-data$cognitive    <- rowMeans(data[c(380:382, 387:388, 393:395)], na.rm=TRUE)
-data$affective    <- rowMeans(data[c(383:384, 389:390, 396:397)], na.rm=TRUE) 
-data$behavioral   <- rowMeans(data[c(385:386, 391:392, 398:399)], na.rm=TRUE)
+modreg$cognitive    <- rowMeans(modreg[c(380:382, 387:388, 393:395)], na.rm=TRUE)
+modreg$affective    <- rowMeans(modreg[c(383:384, 389:390, 396:397)], na.rm=TRUE) 
+modreg$behavioral   <- rowMeans(modreg[c(385:386, 391:392, 398:399)], na.rm=TRUE)
 
@@
 
-data$burnout      <- rowMeans(data[c(373:376)], na.rm=TRUE)
-data$stress       <- rowMeans(data[c(377:379)], na.rm=TRUE)
-data$engagement   <- rowMeans(data[c(380:399)], na.rm=TRUE)        ## added 10/12 because analyses too wonky with 3 subscales
+modreg$burnout      <- rowMeans(modreg[c(373:376)], na.rm=TRUE)
+modreg$stress       <- rowMeans(modreg[c(377:379)], na.rm=TRUE)
+modreg$engagement   <- rowMeans(modreg[c(380:399)], na.rm=TRUE)        ## added 10/12 because analyses too wonky with 3 subscales
 
-alpha.abs <- psych::alpha(data[c(380:386)])
-alpha.vig <- psych::alpha(data[c(387:392)])
-alpha.ded <- psych::alpha(data[c(393:399)])
-alpha.eng <- psych::alpha(data[c(380:399)])
+alpha.abs <- psych::alpha(modreg[c(380:386)])
+alpha.vig <- psych::alpha(modreg[c(387:392)])
+alpha.ded <- psych::alpha(modreg[c(393:399)])
+alpha.eng <- psych::alpha(modreg[c(380:399)])
 
-alpha.bur <- psych::alpha(data[c(373:376)])
-alpha.str <- psych::alpha(data[c(377:379)])
+alpha.bur <- psych::alpha(modreg[c(373:376)])
+alpha.str <- psych::alpha(modreg[c(377:379)])
 
@@
 
-data$onet.resource.ii <- rowMeans(data[c(162:166)], na.rm=TRUE)
-data$onet.resource.mp <- rowMeans(data[c(167:176)], na.rm=TRUE)
-data$onet.resource.wo <- rowMeans(data[c(177:185)], na.rm=TRUE)
-data$onet.resource.io <- rowMeans(data[c(186:202)], na.rm=TRUE)
-data$onet.resource.ir <- rowMeans(data[c(149:161)], na.rm=TRUE)
-data$onet.resource.pc <- rowMeans(data[c(128:144,146:148)], na.rm=TRUE)
-data$onet.resource.sc <- rowMeans(data[c(118:127)], na.rm=TRUE)
+modreg$onet.resource.ii <- rowMeans(modreg[c(162:166)], na.rm=TRUE)
+modreg$onet.resource.mp <- rowMeans(modreg[c(167:176)], na.rm=TRUE)
+modreg$onet.resource.wo <- rowMeans(modreg[c(177:185)], na.rm=TRUE)
+modreg$onet.resource.io <- rowMeans(modreg[c(186:202)], na.rm=TRUE)
+modreg$onet.resource.ir <- rowMeans(modreg[c(149:161)], na.rm=TRUE)
+modreg$onet.resource.pc <- rowMeans(modreg[c(128:144,146:148)], na.rm=TRUE)
+modreg$onet.resource.sc <- rowMeans(modreg[c(118:127)], na.rm=TRUE)
 
-overall.resource <- rowMeans(data[c(118:144,147:202)], na.rm=TRUE)
+overall.resource <- rowMeans(modreg[c(118:144,147:202)], na.rm=TRUE)
 
-data$onet.hindrance.ii <- rowMeans(data[c(246:247,249:252)], na.rm=TRUE)
-data$onet.hindrance.mp <- rowMeans(data[c(252:261)], na.rm=TRUE)
-data$onet.hindrance.wo <- rowMeans(data[c(262:270)], na.rm=TRUE)
-data$onet.hindrance.io <- rowMeans(data[c(271:287)], na.rm=TRUE)
-data$onet.hindrance.ir <- rowMeans(data[c(233:245)], na.rm=TRUE)
-data$onet.hindrance.pc <- rowMeans(data[c(213:232)], na.rm=TRUE)
-data$onet.hindrance.sc <- rowMeans(data[c(203:212)], na.rm=TRUE)
+modreg$onet.hindrance.ii <- rowMeans(modreg[c(246:247,249:252)], na.rm=TRUE)
+modreg$onet.hindrance.mp <- rowMeans(modreg[c(252:261)], na.rm=TRUE)
+modreg$onet.hindrance.wo <- rowMeans(modreg[c(262:270)], na.rm=TRUE)
+modreg$onet.hindrance.io <- rowMeans(modreg[c(271:287)], na.rm=TRUE)
+modreg$onet.hindrance.ir <- rowMeans(modreg[c(233:245)], na.rm=TRUE)
+modreg$onet.hindrance.pc <- rowMeans(modreg[c(213:232)], na.rm=TRUE)
+modreg$onet.hindrance.sc <- rowMeans(modreg[c(203:212)], na.rm=TRUE)
 
-overall.hindrance <- rowMeans(data[c(203:247,249:287)], na.rm=TRUE)
+overall.hindrance <- rowMeans(modreg[c(203:247,249:287)], na.rm=TRUE)
 
-data$onet.challenge.ii <- rowMeans(data[c(332:336)], na.rm=TRUE)
-data$onet.challenge.mp <- rowMeans(data[c(337:346)], na.rm=TRUE)
-data$onet.challenge.wo <- rowMeans(data[c(347:355)], na.rm=TRUE)
-data$onet.challenge.io <- rowMeans(data[c(356:372)], na.rm=TRUE)
-data$onet.challenge.ir <- rowMeans(data[c(319:331)], na.rm=TRUE)
-data$onet.challenge.pc <- rowMeans(data[c(298:307,309:318)], na.rm=TRUE)
-data$onet.challenge.sc <- rowMeans(data[c(288:297)], na.rm=TRUE)
+modreg$onet.challenge.ii <- rowMeans(modreg[c(332:336)], na.rm=TRUE)
+modreg$onet.challenge.mp <- rowMeans(modreg[c(337:346)], na.rm=TRUE)
+modreg$onet.challenge.wo <- rowMeans(modreg[c(347:355)], na.rm=TRUE)
+modreg$onet.challenge.io <- rowMeans(modreg[c(356:372)], na.rm=TRUE)
+modreg$onet.challenge.ir <- rowMeans(modreg[c(319:331)], na.rm=TRUE)
+modreg$onet.challenge.pc <- rowMeans(modreg[c(298:307,309:318)], na.rm=TRUE)
+modreg$onet.challenge.sc <- rowMeans(modreg[c(288:297)], na.rm=TRUE)
 
-overall.challenge <- rowMeans(data[c(288:307,309:372)], na.rm=TRUE)
+overall.challenge <- rowMeans(modreg[c(288:307,309:372)], na.rm=TRUE)
 
@@
 ```{r Analyses with Row Sums}
-overall.resource <- rowSums(data[c(118:144,147:202)], na.rm=TRUE)
+overall.resource <- rowSums(modreg[c(118:144,147:202)], na.rm=TRUE)
 summary(overall.resource) #202.3
-overall.hindrance <- rowSums(data[c(203:247,249:287)], na.rm=TRUE)
+overall.hindrance <- rowSums(modreg[c(203:247,249:287)], na.rm=TRUE)
 summary(overall.hindrance) #159.2
-overall.challenge <- rowSums(data[c(288:307,309:372)], na.rm=TRUE)
+overall.challenge <- rowSums(modreg[c(288:307,309:372)], na.rm=TRUE)
 summary(overall.challenge) #204.2
@@
 
-cr_burn_m1 <- lm(scale(burnout) ~ scale(overall.challenge_center), data = data)
+cr_burn_m1 <- lm(scale(burnout) ~ scale(overall.challenge_center), modreg)
 summary(cr_burn_m1)
 
-cr_burn_m2 <- lm(scale(burnout) ~ scale(overall.challenge_center) + scale(overall.resource), data = data)
+cr_burn_m2 <- lm(scale(burnout) ~ scale(overall.challenge_center) + scale(overall.resource), modreg)
 summary(cr_burn_m2)
 
-cr_burn_m3 <- lm(scale(burnout) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), data = data)
+cr_burn_m3 <- lm(scale(burnout) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
 summary(cr_burn_m3)
@@
 
-cr_stress_m1 <- lm(scale(stress) ~ scale(overall.challenge_center), data = data)
+cr_stress_m1 <- lm(scale(stress) ~ scale(overall.challenge_center), modreg)
 summary(cr_stress_m1)
 
-cr_stress_m2 <- lm(scale(stress) ~ scale(overall.challenge_center) + scale(overall.resource_center), data = data)
+cr_stress_m2 <- lm(scale(stress) ~ scale(overall.challenge_center) + scale(overall.resource_center), modreg)
 summary(cr_stress_m2)
 
-cr_stress_m3 <- lm(scale(stress) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), data = data)
+cr_stress_m3 <- lm(scale(stress) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
 summary(cr_stress_m3)
@@
 
-cr_eng_m1 <- lm(scale(engagement) ~ scale(overall.challenge_center), data = data)
+cr_eng_m1 <- lm(scale(engagement) ~ scale(overall.challenge_center), modreg)
 summary(cr_eng_m1)
 
-cr_eng_m2 <- lm(scale(engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center), data = data)
+cr_eng_m2 <- lm(scale(engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center), modreg)
 summary(cr_eng_m2)
 
-cr_eng_m3 <- lm(scale(engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), data = data)
+cr_eng_m3 <- lm(scale(engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
 summary(cr_eng_m3)
@@
 
-hr_burn_m1 <- lm(scale(burnout) ~ scale(overall.hindrance_center), data = data)
+hr_burn_m1 <- lm(scale(burnout) ~ scale(overall.hindrance_center), modreg)
 summary(hr_burn_m1)
 
-hr_burn_m2 <- lm(scale(burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center), data = data)
+hr_burn_m2 <- lm(scale(burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
 summary(hr_burn_m2)
 
-hr_burn_m3 <- lm(scale(burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), data = data)
+hr_burn_m3 <- lm(scale(burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
 summary(hr_burn_m3)
@@
 
-hr_stress_m1 <- lm(scale(stress) ~ scale(overall.hindrance_center), data = data)
+hr_stress_m1 <- lm(scale(stress) ~ scale(overall.hindrance_center), modreg)
 summary(hr_stress_m1)
 
-hr_stress_m2 <- lm(scale(stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center), data = data)
+hr_stress_m2 <- lm(scale(stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
 summary(hr_stress_m2)
 
-hr_stress_m3 <- lm(scale(stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), data = data)
+hr_stress_m3 <- lm(scale(stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
 summary(hr_stress_m3)
@@
 
-hr_eng_m1 <- lm(scale(engagement) ~ scale(overall.hindrance_center), data = data)
+hr_eng_m1 <- lm(scale(engagement) ~ scale(overall.hindrance_center), modreg)
 summary(hr_eng_m1)
 
-hr_eng_m2 <- lm(scale(engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center), data = data)
+hr_eng_m2 <- lm(scale(engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
 summary(hr_eng_m2)
 
-hr_eng_m3 <- lm(scale(engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), data = data)
+hr_eng_m3 <- lm(scale(engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
 summary(hr_eng_m3)
@@
 #running it with unstandardized bs here. 
-cr_eng_m3u <- lm(engagement ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
+cr_eng_m3u <- lm(engagement ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, modreg)
 summary(cr_eng_m3u)
@@
 
-hr_stress_m3u <- lm(stress ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
+hr_stress_m3u <- lm(stress ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, modreg)
 summary(hr_stress_m3u)
@@
 
-hr_burn_m3u <- lm(burnout ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
+hr_burn_m3u <- lm(burnout ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, modreg)
 summary(hr_burn_m3u)

### 2024-05-28 Submission.Rmd
updating results and intro

@@
 
-Outline:
-Work toward model (picture)
-
-I. Challenge-hindrance framework
-  + Cavanaugh (~2000)
-  + Last 20 years' research (variance - look at Pindek et al, 2024)
-  + Appraisals [^JDR]
-
-[^JDR]: Ignore JD theory terminology - only talk about JDR *model*, otherwise the verbage becomes confused (4/6/24)
-
-II. Antecedents (job elements)
-  a. O\*Net - comprehensive
-III. Consequences (outcomes)
-  a. Moderation
-IV. Contribution
-  a. include resources
-
 While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular.
 We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges].
-Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, and 3) subjective appraisals are differentially related to positive and negative outcomes.
+Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) whether subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between stressors (challenge and hindrance) and outcomes.
 To illuminate these questions, we consult the [O\*Net database](https://www.onetcenter.org/content.html), which provides a rich source of information about occupational requirements (i.e., work activities and context).
@@
 Challenge demands promote mastery, personal growth, and future gains – these stressors should lead to coping strategies that facilitate achievement.
-Work characteristics consistent with this definition include time pressure and responsibility.
+Work characteristics consistent with this definition include time pressure and responsibility [@lepine2022challenge].
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Hindrance stressors in a work context include role conflict, role ambiguity, and organizational politics.[^challhind]
-
-[^challhind]: Need citations here for hindrance and challenge examples (because subjectivity vs. "typically a demand" is a central issue within the paper)
+Hindrance stressors in a work context include role conflict and role ambiguity [@lepine2022challenge].
 
@@
 Even @pindek2024dynamic notes this limitation of a priori classification of characteristics as demands, challenges, or hindrances, as do @horan2020review.
-In fact, although much of our research on job demands based on a priori classifications [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).[^gimmecite]
-
-[^gimmecite]: Citations needed here or alternatively frame the sentence as, "we contend that..."
+In fact, although much of our research on job demands based on a priori classifications [@searle2015merits], we contend that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
 
@@
 Theoretically, *a priori* classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
-Empirically, as shown above, we have some evidence suggesting people can appraise a stressor[^checkit] as both a hindrance and challenge at the same time [e.g., @searle2015merits].
-
-[^checkit]: Do you mean "stressor" or "work characteristic"?
+Empirically, as shown above, we have some evidence suggesting people can appraise a work characteristic as both a hindrance and challenge at the same time [e.g., @searle2015merits].
 

### 2024-06-04 Submission.Rmd
working on results

@@
 
+```{r}
+hr_burn_info2 <- apa_print(hr_burn_m2)
+hr_burn_info3 <- apa_print(hr_burn_m3)
+```
+
 Table \@ref(tab:chal-resource-table) summarizes the results.
 Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions.
-First exploring engagement, challenge stressors and resources explained XX% of the variance in engagement, $R^2$ = .xx.
-Adj.
-$R^2$ = .xx, which represents a statistically significant effect, *F*(x, xx) = xx.xx, *p* < xxx.
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, $Delta R^2$ = .xx, $Delta F$(xx, xx) = .xx, *p* = xx, and thus provides statistical support for the presence of moderation.
-The total model explained xx% of the variance in engagement, $R^2$ = .xx.
-Adj.
-$R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx.
-Figure \@ref(fig:chal-resource-int) illustrates the interaction.
+First exploring engagement, $R^2$ = `r round(summary(cr_eng_m2)$r.squared, 2)`, Adj.
+$R^2$ =  `r round(summary(cr_eng_m2)$adj.r.squared, 2)` which represents a statistically significant effect, `r hr_burn_info2$statistic$modelfit$r2`.
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, $\Delta R^2$ = `r cr_stress_r_square_change`, $\Delta F$ (`r cr_eng_anova$Df[2]`, `r cr_eng_anova$Res.Df[2]`) = `r cr_eng_anova$F[2]`,  and thus provides statistical support for the presence of moderation.
+The total model explained xx% of the variance in engagement, `r hr_burn_info3$statistic$modelfit$r2` Figure \@ref(fig:chal-resource-int) illustrates the interaction.
 With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low.
@@
 $R^2$ = .xx, which represents a non-significant effect, *F*(x, xx) = xx.xx, *p* xxx.
-The inclusion of the interaction term in step two of the model did not add significantly to the model, $Delta R^2$ = .xx, $Delta F$(xx, xx) = .xx, *p* = xxx.
+The inclusion of the interaction term in step two of the model did not add significantly to the model, $\Delta R^2$ = .xx, $\Delta F$(xx, xx) = .xx, *p* = xxx.
 The total model explained xx% of the variance in stress, $R^2$ = .xx.
@@
 $R^2$ = .xx, which represents a statistically significant effect, *F*(x, xx) = xx.xx, *p* xxx.
-The inclusion of the interaction term in step two of the model did not add significantly to the model, $Delta R^2$ = .xx, $Delta F$(xx, xx) = .xx, *p* = xxx.
+The inclusion of the interaction term in step two of the model did not add significantly to the model, $\Delta R^2$ = .xx, $\Delta F$(xx, xx) = .xx, *p* = xxx.
 The total model explained xx% of the variance in stress, $R^2$ = .xx.
@@
 
-```{r hind-resource-table, results='asis'}
+```{r hind-resource-table, results='asis', eval = FALSE}
 
@@
 ```
+
 We also explored whether there was an interaction between hindrance stressors and resources on the outcomes (i.e., engagement, stress, and burnout).
@@
 $R^2$ = .xx, which represents a statistically significant effect, *F*(x, xx) = xx.xx, *p* xxx.
-The inclusion of the interaction term in step two of the model did not add significantly to the model, $Delta R^2$ = .xx, $Delta F$(xx, xx) = .xx, *p* = xxx.
+The inclusion of the interaction term in step two of the model did not add significantly to the model, $\Delta R^2$ = .xx, $\Delta F$(xx, xx) = .xx, *p* = xxx.
 The total model explained xx% of the variance in engagement, $R^2$ = .xx.
@@
 $R^2$ = .xx, which represents a statistically significant effect, *F*(x, xx) = xx.xx, *p* xxx.
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, $Delta R^2$ = .xx, $Delta F$(xx, xx) = .xx, *p* = xx, and thus provides statistical support for the presence of moderation.
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, $\Delta R^2$ = .xx, $\Delta F$(xx, xx) = .xx, *p* = xx, and thus provides statistical support for the presence of moderation.
 The total model explained xx% of the variance in stress, $R^2$ = .xx.
@@
 $R^2$ = .xx, *F*(x, xx) = xx.xx, *p* xxx.
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, $Delta R^2$ = .xx, $Delta F$(xx, xx) = .xx, *p* = xx.
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, $\Delta R^2$ = .xx, $\Delta F$(xx, xx) = .xx, *p* = xx.
 The total model explained xx% of the variance in burnout,$R^2$ = .xx.
@@
 As expected, the relationship between hindrance stressors and burnout becomes weaker as workers perceive more resources.
+Papaja gives us `r test$full_result`
 

### 2024-06-04 Submission.tex
working on results

@@
 
-Outline:
-Work toward model (picture)
-
-I. Challenge-hindrance framework
-+ Cavanaugh (\textasciitilde2000)
-+ Last 20 years' research (variance - look at Pindek et al, 2024)
-+ Appraisals \footnote{Ignore JD theory terminology - only talk about JDR \emph{model}, otherwise the verbage becomes confused (4/6/24)}
-
-\begin{enumerate}
-\def\labelenumi{\Roman{enumi}.}
-\setcounter{enumi}{1}
-\tightlist
-\item
-  Antecedents (job elements)
-\end{enumerate}
-
-\begin{enumerate}
-\def\labelenumi{\alph{enumi}.}
-\tightlist
-\item
-  O*Net - comprehensive
-\end{enumerate}
-
-\begin{enumerate}
-\def\labelenumi{\Roman{enumi}.}
-\setcounter{enumi}{2}
-\tightlist
-\item
-  Consequences (outcomes)
-\end{enumerate}
-
-\begin{enumerate}
-\def\labelenumi{\alph{enumi}.}
-\tightlist
-\item
-  Moderation
-\end{enumerate}
-
-\begin{enumerate}
-\def\labelenumi{\Roman{enumi}.}
-\setcounter{enumi}{3}
-\tightlist
-\item
-  Contribution
-\end{enumerate}
-
-\begin{enumerate}
-\def\labelenumi{\alph{enumi}.}
-\tightlist
-\item
-  include resources
-\end{enumerate}
-
 While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular.
 We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020).
-Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, and 3) subjective appraisals are differentially related to positive and negative outcomes.
+Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) whether subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between stressors (challenge and hindrance) and outcomes.
 To illuminate these questions, we consult the \href{https://www.onetcenter.org/content.html}{O*Net database}, which provides a rich source of information about occupational requirements (i.e., work activities and context).
@@
 Challenge demands promote mastery, personal growth, and future gains -- these stressors should lead to coping strategies that facilitate achievement.
-Work characteristics consistent with this definition include time pressure and responsibility.
+Work characteristics consistent with this definition include time pressure and responsibility (M.
+A.
+LePine, 2022).
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Hindrance stressors in a work context include role conflict, role ambiguity, and organizational politics.\footnote{Need citations here for hindrance and challenge examples (because subjectivity vs.~``typically a demand'' is a central issue within the paper)}
+Hindrance stressors in a work context include role conflict and role ambiguity (M.
+A.
+LePine, 2022).
 
@@
 (2020).
-In fact, although much of our research on job demands based on a priori classifications (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).\footnote{Citations needed here or alternatively frame the sentence as, ``we contend that\ldots{}''}
+In fact, although much of our research on job demands based on a priori classifications (Searle \& Auton, 2015), we contend that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
 
@@
 Theoretically, \emph{a priori} classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
-Empirically, as shown above, we have some evidence suggesting people can appraise a stressor\footnote{Do you mean ``stressor'' or ``work characteristic''?} as both a hindrance and challenge at the same time (e.g., Searle \& Auton, 2015).
+Empirically, as shown above, we have some evidence suggesting people can appraise a work characteristic as both a hindrance and challenge at the same time (e.g., Searle \& Auton, 2015).
 
@@
 Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions.
-First exploring engagement, challenge stressors and resources explained XX\% of the variance in engagement, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} \textless{} xxx.
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(Delta R^2\) = .xx, \(Delta F\)(xx, xx) = .xx, \emph{p} = xx, and thus provides statistical support for the presence of moderation.
+First exploring engagement, challenge stressors and resources explained XX\% of the variance in engagement, \(R^2\) = 0.15, Adj.
+\(R^2\) = 0.15 which represents a statistically significant effect, \(F(3, 564) = 9.49\), \(p < .001\).
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(\Delta R^2\) = 0.00, 2), \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation.
 The total model explained xx\% of the variance in engagement, \(R^2\) = .xx.
@@
 \(R^2\) = .xx, which represents a non-significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
-The inclusion of the interaction term in step two of the model did not add significantly to the model, \(Delta R^2\) = .xx, \(Delta F\)(xx, xx) = .xx, \emph{p} = xxx.
+The inclusion of the interaction term in step two of the model did not add significantly to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xxx.
 The total model explained xx\% of the variance in stress, \(R^2\) = .xx.
@@
 \(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
-The inclusion of the interaction term in step two of the model did not add significantly to the model, \(Delta R^2\) = .xx, \(Delta F\)(xx, xx) = .xx, \emph{p} = xxx.
+The inclusion of the interaction term in step two of the model did not add significantly to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xxx.
 The total model explained xx\% of the variance in stress, \(R^2\) = .xx.
@@
 \(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
-The inclusion of the interaction term in step two of the model did not add significantly to the model, \(Delta R^2\) = .xx, \(Delta F\)(xx, xx) = .xx, \emph{p} = xxx.
+The inclusion of the interaction term in step two of the model did not add significantly to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xxx.
 The total model explained xx\% of the variance in engagement, \(R^2\) = .xx.
@@
 \(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(Delta R^2\) = .xx, \(Delta F\)(xx, xx) = .xx, \emph{p} = xx, and thus provides statistical support for the presence of moderation.
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xx, and thus provides statistical support for the presence of moderation.
 The total model explained xx\% of the variance in stress, \(R^2\) = .xx.
@@
 \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(Delta R^2\) = .xx, \(Delta F\)(xx, xx) = .xx, \emph{p} = xx.
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xx.
 The total model explained xx\% of the variance in burnout,\(R^2\) = .xx.
@@
 As expected, the relationship between hindrance stressors and burnout becomes weaker as workers perceive more resources.
+Papaja gives us \(b = 0.00\), 95\% CI \([-0.08, 0.08]\), \(t(564) = 0.00\), \(p > .999\), \(b = 0.16\), 95\% CI \([0.06, 0.26]\), \(t(564) = 3.10\), \(p = .002\), \(b = 0.03\), 95\% CI \([-0.08, 0.15]\), \(t(564) = 0.56\), \(p = .576\), \(b = -0.13\), 95\% CI \([-0.23, -0.03]\), \(t(564) = -2.63\), \(p = .009\), list(r2 = ``\(R^2 = .05\), 90\textbackslash\% CI \([0.02, 0.08]\), \(F(3, 564) = 9.49\), \(p < .001\)'')
 

### 2024-06-06 Submission.Rmd
error message was due to `test` object (line 1111) that was renamed - we had referenced the old object within the document text

@@
 hr_burn_info3 <- apa_print(hr_burn_m3)
+
 ```
@@
 
+```{r hind-resource-table, results='asis', eval = TRUE}
+
+library(kableExtra)
+
+DV <- c("Engagement","","", "Stress","","", "Burnout","","")
+Step <- c("1", "","2", "1", "","2", "1", "","2")
+Model <- c("Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource")
+Beta <- c(paste(hind.2.eng,"**"), paste(res.2hr.eng,"**"), int.hr.3.eng, paste(sigfill(hind.2.stress),"*"), paste(res.2hr.stress,"**"), paste(int.hr.3.stress,"**"), paste(sigfill(hind.2.burn),"*"), paste(res.2hr.burn,"*"), paste(int.hr.3.burn,"**"))
+R2 <- c("", paste(round(hr_eng_m2_r,2),"**"), paste(round(hr_eng_m3_r,2),"**"), "", paste(hr_stress_m2_r,"*"), paste(hr_stress_m3_r, "**"), "", paste(hr_burn_m2_r,"**"), paste(hr_burn_m3_r,"**"))
+#DeltaR <- c("",paste(hr_eng_m2_r,"**"),hr_eng_r_square_change, "",paste(hr_stress_m2_r,"**"),hr_stress_r_square_change, "",paste(hr_burn_m2_r,"**"),hr_burn_r_square_change)
+DeltaR <- c("","",hr_eng_r_square_change, "","",paste(hr_stress_r_square_change,"**"), "","",paste(hr_burn_r_square_change, "**"))
+regtable <- as.data.frame(cbind(DV, Step, Model, Beta, R2, DeltaR))
+
+colnames(regtable)[4] <- "$\\beta$"
+colnames(regtable)[5] <- "$R^2$"
+colnames(regtable)[6] <- "$\\Delta R^2$"
+
+#kableExtra::kable(regtable,
+#                  format="latex",
+#                  escape=FALSE)
+
+papaja::apa_table(regtable,
+                 escape=FALSE,
+                 note="* = p < .05; ** = p < .01")
+```
+
+We also explored whether there was an interaction between hindrance stressors and resources on the outcomes (i.e., engagement, stress, and burnout).
+A second group of hierarchical regressions were conducted with hindrance stressors and resources added in step one of the model and an interaction term, hindrance stressors x resources, added in step two of the model.
+See Table \@ref(tab:hind-resource-table).
+
 Next, challenge stressors and resources explained XX% of the variance in stress, $R^2$ = .xx.
@@
 In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge stressors and the outcomes of strain  and burnout.
-
-```{r hind-resource-table, results='asis', eval = FALSE}
-
-library(kableExtra)
-
-DV <- c("Engagement","","", "Stress","","", "Burnout","","")
-Step <- c("1", "","2", "1", "","2", "1", "","2")
-Model <- c("Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource")
-Beta <- c(paste(hind.2.eng,"**"), paste(res.2hr.eng,"**"), int.hr.3.eng, paste(sigfill(hind.2.stress),"*"), paste(res.2hr.stress,"**"), paste(int.hr.3.stress,"**"), paste(sigfill(hind.2.burn),"*"), paste(res.2hr.burn,"*"), paste(int.hr.3.burn,"**"))
-R2 <- c("", paste(round(hr_eng_m2_r,2),"**"), paste(round(hr_eng_m3_r,2),"**"), "", paste(hr_stress_m2_r,"*"), paste(hr_stress_m3_r, "**"), "", paste(hr_burn_m2_r,"**"), paste(hr_burn_m3_r,"**"))
-#DeltaR <- c("",paste(hr_eng_m2_r,"**"),hr_eng_r_square_change, "",paste(hr_stress_m2_r,"**"),hr_stress_r_square_change, "",paste(hr_burn_m2_r,"**"),hr_burn_r_square_change)
-DeltaR <- c("","",hr_eng_r_square_change, "","",paste(hr_stress_r_square_change,"**"), "","",paste(hr_burn_r_square_change, "**"))
-regtable <- as.data.frame(cbind(DV, Step, Model, Beta, R2, DeltaR))
-
-colnames(regtable)[4] <- "$\\beta$"
-colnames(regtable)[5] <- "$R^2$"
-colnames(regtable)[6] <- "$\\Delta R^2$"
-
-#kableExtra::kable(regtable,
-#                  format="latex",
-#                  escape=FALSE)
-
-papaja::apa_table(regtable,
-                 escape=FALSE,
-                 note="* = p < .05; ** = p < .01")
-```
-
-We also explored whether there was an interaction between hindrance stressors and resources on the outcomes (i.e., engagement, stress, and burnout).
-A second group of hierarchical regressions were conducted with hindrance stressors and resources added in step one of the model and an interaction term, hindrance stressors*resources, added in step two of the model.
-See Table \@ref(tab:ind-resource-table).
 
@@
 As expected, the relationship between hindrance stressors and burnout becomes weaker as workers perceive more resources.
-Papaja gives us `r test$full_result`
 

### 2024-06-06 Submission.tex
error message was due to `test` object (line 1111) that was renamed - we had referenced the old object within the document text

@@
 \fi
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
   \fi
   % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{bookmark}
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
@@
 
-\hypertarget{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}{%
-\subsection{The Job Demands-Resources Theory and Challenge-Hindrance Stressor Framework}\label{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}}
+\subsection{The Job Demands-Resources Theory and Challenge-Hindrance Stressor Framework}\label{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}
 
@@
 
-\hypertarget{are-perceptions-of-job-resources-challenge-demands-and-hindrance-demands-universal}{%
-\subsection{Are Perceptions of Job Resources, Challenge Demands, and Hindrance Demands Universal?}\label{are-perceptions-of-job-resources-challenge-demands-and-hindrance-demands-universal}}
+\subsection{Are Perceptions of Job Resources, Challenge Demands, and Hindrance Demands Universal?}\label{are-perceptions-of-job-resources-challenge-demands-and-hindrance-demands-universal}
 
@@
 
-\hypertarget{connecting-appraisals-to-workplace-outcomes}{%
-\subsection{Connecting Appraisals to Workplace Outcomes}\label{connecting-appraisals-to-workplace-outcomes}}
+\subsection{Connecting Appraisals to Workplace Outcomes}\label{connecting-appraisals-to-workplace-outcomes}
 
@@
 
-\hypertarget{method}{%
-\section{Method}\label{method}}
+\section{Method}\label{method}
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+\subsection{Participants}\label{participants}
 
@@
 
-\hypertarget{materials}{%
-\subsection{Materials}\label{materials}}
+\subsection{Materials}\label{materials}
 
@@
 
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
+\subsection{Procedure}\label{procedure}
 
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\section{Results}\label{results}
 
@@
 Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions.
-First exploring engagement, challenge stressors and resources explained XX\% of the variance in engagement, \(R^2\) = 0.15, Adj.
-\(R^2\) = 0.15 which represents a statistically significant effect, \(F(3, 564) = 9.49\), \(p < .001\).
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(\Delta R^2\) = 0.00, 2), \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation.
-The total model explained xx\% of the variance in engagement, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
-Figure \ref{fig:chal-resource-int} illustrates the interaction.
+First exploring engagement, \(R^2\) = 0.15, Adj.
+\(R^2\) = 0.15 which represents a statistically significant effect, \(F(2, 565) = 10.68\), \(p < .001\).
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation.
+The total model explained xx\% of the variance in engagement, \(F(3, 564) = 9.49\), \(p < .001\) Figure \ref{fig:chal-resource-int} illustrates the interaction.
 With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low.
 With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.
-
-Next, challenge stressors and resources explained XX\% of the variance in stress, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, which represents a non-significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
-The inclusion of the interaction term in step two of the model did not add significantly to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xxx.
-The total model explained xx\% of the variance in stress, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
-
-Finally, challenge stressors and resources explained XX\% of the variance in burnout, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
-The inclusion of the interaction term in step two of the model did not add significantly to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xxx.
-The total model explained xx\% of the variance in stress, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
-In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge stressors and the outcomes of strain and burnout.
 
@@
 We also explored whether there was an interaction between hindrance stressors and resources on the outcomes (i.e., engagement, stress, and burnout).
-A second group of hierarchical regressions were conducted with hindrance stressors and resources added in step one of the model and an interaction term, hindrance stressors*resources, added in step two of the model.
-See Table \ref{tab:ind-resource-table}.
+A second group of hierarchical regressions were conducted with hindrance stressors and resources added in step one of the model and an interaction term, hindrance stressors x resources, added in step two of the model.
+See Table \ref{tab:hind-resource-table}.
+
+Next, challenge stressors and resources explained XX\% of the variance in stress, \(R^2\) = .xx.
+Adj.
+\(R^2\) = .xx, which represents a non-significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
+The inclusion of the interaction term in step two of the model did not add significantly to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xxx.
+The total model explained xx\% of the variance in stress, \(R^2\) = .xx.
+Adj.
+\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
+
+Finally, challenge stressors and resources explained XX\% of the variance in burnout, \(R^2\) = .xx.
+Adj.
+\(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
+The inclusion of the interaction term in step two of the model did not add significantly to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xxx.
+The total model explained xx\% of the variance in stress, \(R^2\) = .xx.
+Adj.
+\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
+In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge stressors and the outcomes of strain and burnout.
 
@@
 As expected, the relationship between hindrance stressors and burnout becomes weaker as workers perceive more resources.
-Papaja gives us \(b = 0.00\), 95\% CI \([-0.08, 0.08]\), \(t(564) = 0.00\), \(p > .999\), \(b = 0.16\), 95\% CI \([0.06, 0.26]\), \(t(564) = 3.10\), \(p = .002\), \(b = 0.03\), 95\% CI \([-0.08, 0.15]\), \(t(564) = 0.56\), \(p = .576\), \(b = -0.13\), 95\% CI \([-0.23, -0.03]\), \(t(564) = -2.63\), \(p = .009\), list(r2 = ``\(R^2 = .05\), 90\textbackslash\% CI \([0.02, 0.08]\), \(F(3, 564) = 9.49\), \(p < .001\)'')
 
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\section{Discussion}\label{discussion}
 
@@
 
-\hypertarget{implications}{%
-\subsection{Implications}\label{implications}}
+\subsection{Implications}\label{implications}
 
@@
 
-\hypertarget{limitations-and-future-directions}{%
-\subsection{Limitations and Future Directions}\label{limitations-and-future-directions}}
+\subsection{Limitations and Future Directions}\label{limitations-and-future-directions}
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\section{References}\label{references}
 
@@
 
-\hypertarget{refs}{}
+\phantomsection\label{refs}
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-abbas2019challenge}{}}%
+\bibitem[\citeproctext]{ref-abbas2019challenge}
 Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
+\bibitem[\citeproctext]{ref-bakker2014job}
 Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
+\bibitem[\citeproctext]{ref-bakker2017job}
 Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2005job}{}}%
+\bibitem[\citeproctext]{ref-bakker2005job}
 Bakker, A. B., Demerouti, E., \& Euwema, M. C. (2005). Job resources buffer the impact of job demands on burnout. \emph{Journal of Occupational Health Psychology}, \emph{10}(2), 170.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
+\bibitem[\citeproctext]{ref-bakker2013weekly}
 Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
 
-\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
+\bibitem[\citeproctext]{ref-cavanaugh2000empirical}
 Cavanaugh, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-chen2021daily}{}}%
+\bibitem[\citeproctext]{ref-chen2021daily}
 Chen, H., Wang, H., Yuan, M., \& Xu, S. (2021). Daily challenge/hindrance demands and cognitive wellbeing: A multilevel moderated mediation model. \emph{Frontiers in Psychology}, \emph{12}, 616002.
 
-\leavevmode\vadjust pre{\hypertarget{ref-crawford2010linking}{}}%
+\bibitem[\citeproctext]{ref-crawford2010linking}
 Crawford, E.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
+\bibitem[\citeproctext]{ref-demerouti2001job}
 Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
 
-\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
+\bibitem[\citeproctext]{ref-gerich2017relevance}
 Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
 
-\leavevmode\vadjust pre{\hypertarget{ref-horan2020review}{}}%
+\bibitem[\citeproctext]{ref-horan2020review}
 Horan, K.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-kim2020thriving}{}}%
+\bibitem[\citeproctext]{ref-kim2020thriving}
 Kim, M., \& Beehr, T.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
+\bibitem[\citeproctext]{ref-lazarus1984stress}
 Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
 
-\leavevmode\vadjust pre{\hypertarget{ref-lepine2005meta}{}}%
+\bibitem[\citeproctext]{ref-lepine2005meta}
 LePine, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lepine2022challenge}{}}%
+\bibitem[\citeproctext]{ref-lepine2022challenge}
 LePine, M. A. (2022). The challenge-hindrance stressor framework: An integrative conceptual review and path forward. \emph{Group \& Organization Management}, \emph{47}(2), 223--254.
 
-\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
+\bibitem[\citeproctext]{ref-peterson2001understanding}
 Peterson, N.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-pindek2024dynamic}{}}%
+\bibitem[\citeproctext]{ref-pindek2024dynamic}
 Pindek, S., Meyer, K., Valvo, A., \& Arvan, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-podsakoff2007differential}{}}%
+\bibitem[\citeproctext]{ref-podsakoff2007differential}
 Podsakoff, N.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-rodell2009can}{}}%
+\bibitem[\citeproctext]{ref-rodell2009can}
 Rodell, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-rosen2020challenges}{}}%
+\bibitem[\citeproctext]{ref-rosen2020challenges}
 Rosen, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-searle2015merits}{}}%
+\bibitem[\citeproctext]{ref-searle2015merits}
 Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.
 
-\leavevmode\vadjust pre{\hypertarget{ref-webster2010toward}{}}%
+\bibitem[\citeproctext]{ref-webster2010toward}
 Webster, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
+\bibitem[\citeproctext]{ref-webster2011extending}
 Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.
 
-\leavevmode\vadjust pre{\hypertarget{ref-xanthopoulou2007job}{}}%
+\bibitem[\citeproctext]{ref-xanthopoulou2007job}
 Xanthopoulou, D., Bakker, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-careless}{}}%
+\bibitem[\citeproctext]{ref-R-careless}
 Yentes, R. D., \& Wilhelm, F. (2021). \emph{Careless: Procedures for computing indices of careless responding}.

### 2024-06-06 Submission.Rmd
updated moderated regressions. Results section ready to read through.

@@
 ```{r}
+cr_eng_info2 <- apa_print(cr_eng_m2)
+cr_eng_info3 <- apa_print(cr_eng_m3)
+
+cr_stress_info2 <- apa_print(cr_stress_m2)
+cr_stress_info3 <- apa_print(cr_stress_m3)
+
+cr_burn_info2 <- apa_print(cr_stress_m2)
+cr_burn_info3 <- apa_print(cr_stress_m3)
+
+hr_eng_info2 <- apa_print(hr_eng_m2)
+hr_eng_info3 <- apa_print(hr_eng_m3)
+
+hr_stress_info2 <- apa_print(hr_stress_m2)
+hr_stress_info3 <- apa_print(hr_stress_m3)
+
 hr_burn_info2 <- apa_print(hr_burn_m2)
@@
 Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions.
-First exploring engagement, $R^2$ = `r round(summary(cr_eng_m2)$r.squared, 2)`, Adj.
-$R^2$ =  `r round(summary(cr_eng_m2)$adj.r.squared, 2)` which represents a statistically significant effect, `r hr_burn_info2$statistic$modelfit$r2`.
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, $\Delta R^2$ = `r cr_stress_r_square_change`, $\Delta F$ (`r cr_eng_anova$Df[2]`, `r cr_eng_anova$Res.Df[2]`) = `r cr_eng_anova$F[2]`,  and thus provides statistical support for the presence of moderation.
-The total model explained xx% of the variance in engagement, `r hr_burn_info3$statistic$modelfit$r2` Figure \@ref(fig:chal-resource-int) illustrates the interaction.
+First, challenges and resources explained a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(cr_eng_m2)$r.squared, 2)`, Adj.
+$R^2$ =  `r round(summary(cr_eng_m2)$adj.r.squared, 2)`, `r cr_eng_info2$statistic$modelfit$r2`.
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r cr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_eng_r_square_change`, $\Delta F$ (`r cr_eng_anova$Df[2]`, `r cr_eng_anova$Res.Df[2]`) = `r cr_eng_anova$F[2]`,  and thus provides statistical support for the presence of moderation.
+Figure \@ref(fig:chal-resource-int) illustrates the interaction.
 With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low.
 With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.
+
+Next, challenge stressors and resources did not explain a significant amount of the variance in stress,  $R^2$ = `r round(summary(cr_stress_m2)$r.squared, 2)`, Adj.
+$R^2$ =  `r round(summary(cr_stress_m2)$adj.r.squared, 2)`, `r cr_stress_info2$statistic$modelfit$r2`.
+The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, `r cr_stress_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_stress_r_square_change`, $\Delta F$ (`r cr_stress_anova$Df[2]`, `r cr_stress_anova$Res.Df[2]`) = `r cr_stress_anova$F[2]`, and thus does not support the presence of moderation.
+
+Finally, challenge stressors and resources explained a statsically significant amount of the variability in burnout, $R^2$ = `r round(summary(cr_burn_m2)$r.squared, 2)`, Adj.
+$R^2$ =  `r round(summary(cr_burn_m2)$adj.r.squared, 2)`, `r cr_burn_info2$statistic$modelfit$r2`.
+The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, `r cr_burn_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_burn_r_square_change`, $\Delta F$ (`r cr_burn_anova$Df[2]`, `r cr_burn_anova$Res.Df[2]`) = `r cr_burn_anova$F[2]`,  and thus failing to provide statistical support for the presence of moderation.
+In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge stressors and the outcomes of strain and burnout.
 
@@
 
-Next, challenge stressors and resources explained XX% of the variance in stress, $R^2$ = .xx.
-Adj.
-$R^2$ = .xx, which represents a non-significant effect, *F*(x, xx) = xx.xx, *p* xxx.
-The inclusion of the interaction term in step two of the model did not add significantly to the model, $\Delta R^2$ = .xx, $\Delta F$(xx, xx) = .xx, *p* = xxx.
-The total model explained xx% of the variance in stress, $R^2$ = .xx.
-Adj.
-$R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx.
-
-Finally, challenge stressors and resources explained XX% of the variance in burnout, $R^2$ = .xx.
-Adj.
-$R^2$ = .xx, which represents a statistically significant effect, *F*(x, xx) = xx.xx, *p* xxx.
-The inclusion of the interaction term in step two of the model did not add significantly to the model, $\Delta R^2$ = .xx, $\Delta F$(xx, xx) = .xx, *p* = xxx.
-The total model explained xx% of the variance in stress, $R^2$ = .xx.
-Adj.
-$R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx.
-In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge stressors and the outcomes of strain  and burnout.
-
 Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions.
-First, hindrance stressors and resources explained XX% of the variance in engagement, $R^2$ = .xx.
-Adj.
-$R^2$ = .xx, which represents a statistically significant effect, *F*(x, xx) = xx.xx, *p* xxx.
-The inclusion of the interaction term in step two of the model did not add significantly to the model, $\Delta R^2$ = .xx, $\Delta F$(xx, xx) = .xx, *p* = xxx.
-The total model explained xx% of the variance in engagement, $R^2$ = .xx.
-Adj.
-$R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx.
-
-Next exploring stress, hindrance stressors and resources explained XX% of the variance in stress, $R^2$ = .xx.
-Adj.
-$R^2$ = .xx, which represents a statistically significant effect, *F*(x, xx) = xx.xx, *p* xxx.
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, $\Delta R^2$ = .xx, $\Delta F$(xx, xx) = .xx, *p* = xx, and thus provides statistical support for the presence of moderation.
-The total model explained xx% of the variance in stress, $R^2$ = .xx.
-Adj.
-$R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx.
+First, hindrance stressors and resources explained a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(hr_eng_m2)$r.squared, 2)`, Adj.
+$R^2$ =  `r round(summary(hr_eng_m2)$adj.r.squared, 2)`, `r hr_eng_info2$statistic$modelfit$r2`.
+The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, `r hr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_eng_r_square_change`, $\Delta F$ (`r hr_eng_anova$Df[2]`, `r hr_eng_anova$Res.Df[2]`) = `r hr_eng_anova$F[2]`.
+An interaction between hindrances and resources was not found.
+
+Next exploring stress, hindrance stressors and resources explained a statistically significant amount of the variability in stress, $R^2$ = `r round(summary(hr_stress_m2)$r.squared, 2)`, Adj.
+$R^2$ =  `r round(summary(hr_stress_m2)$adj.r.squared, 2)`, `r hr_stress_info2$statistic$modelfit$r2`.
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r hr_stress_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_stress_r_square_change`, $\Delta F$ (`r hr_stress_anova$Df[2]`, `r hr_stress_anova$Res.Df[2]`) = `r hr_stress_anova$F[2]`, supporting the presence of a moderated effect.
 See Figure \@ref(fig:hind-resource-stress-int).
@@
 
-Similarly, hindrance stressors and resources explained XX% of the variance in burnout, $R^2$ = .xx.
-Adj.
-$R^2$ = .xx, *F*(x, xx) = xx.xx, *p* xxx.
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, $\Delta R^2$ = .xx, $\Delta F$(xx, xx) = .xx, *p* = xx.
+Similarly, hindrance stressors and resources explained a statistically significant amount of the variability in burnout, $R^2$ = `r round(summary(hr_burn_m2)$r.squared, 2)`, Adj.
+$R^2$ =  `r round(summary(hr_burn_m2)$adj.r.squared, 2)`, `r hr_burn_info2$statistic$modelfit$r2`.
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r hr_burn_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_burn_r_square_change`, $\Delta F$ (`r hr_burn_anova$Df[2]`, `r hr_burn_anova$Res.Df[2]`) = `r hr_burn_anova$F[2]`, supporting the presence of a moderated effect.
 The total model explained xx% of the variance in burnout,$R^2$ = .xx.

### 2024-06-06 Submission.tex
updated moderated regressions. Results section ready to read through.

--- 2024-06-04 Submission.tex
@@
 Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions.
-First exploring engagement, challenge stressors and resources explained XX\% of the variance in engagement, \(R^2\) = 0.15, Adj.
-\(R^2\) = 0.15 which represents a statistically significant effect, \(F(3, 564) = 9.49\), \(p < .001\).
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(\Delta R^2\) = 0.00, 2), \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation.
-The total model explained xx\% of the variance in engagement, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
+First, challenges and resources explained a statistically significant amount of the variability in engagement, \(R^2\) = 0.15, Adj.
+\(R^2\) = 0.15, \(F(2, 565) = 50.09\), \(p < .001\).
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 35.62\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation.
 Figure \ref{fig:chal-resource-int} illustrates the interaction.
@@
 
-Next, challenge stressors and resources explained XX\% of the variance in stress, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, which represents a non-significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
-The inclusion of the interaction term in step two of the model did not add significantly to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xxx.
-The total model explained xx\% of the variance in stress, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
+Next, challenge stressors and resources did not explain a significant amount of the variance in stress, \(R^2\) = 0.01, Adj.
+\(R^2\) = 0, \(F(2, 565) = 1.67\), \(p = .189\).
+The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model,\(F(3, 564) = 1.17\), \(p = .320\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 0.17, and thus does not support the presence of moderation.
 
-Finally, challenge stressors and resources explained XX\% of the variance in burnout, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
-The inclusion of the interaction term in step two of the model did not add significantly to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xxx.
-The total model explained xx\% of the variance in stress, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
+Finally, challenge stressors and resources explained a statsically significant amount of the variability in burnout, \(R^2\) = 0.04, Adj.
+\(R^2\) = 0.04, \(F(2, 565) = 1.67\), \(p = .189\).
+The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 1.17\), \(p = .320\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 2.25, and thus failing to provide statistical support for the presence of moderation.
 In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge stressors and the outcomes of strain and burnout.
@@
 We also explored whether there was an interaction between hindrance stressors and resources on the outcomes (i.e., engagement, stress, and burnout).
-A second group of hierarchical regressions were conducted with hindrance stressors and resources added in step one of the model and an interaction term, hindrance stressors*resources, added in step two of the model.
-See Table \ref{tab:ind-resource-table}.
+A second group of hierarchical regressions were conducted with hindrance stressors and resources added in step one of the model and an interaction term, hindrance stressors x resources, added in step two of the model.
+See Table \ref{tab:hind-resource-table}.
 
 Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions.
-First, hindrance stressors and resources explained XX\% of the variance in engagement, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
-The inclusion of the interaction term in step two of the model did not add significantly to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xxx.
-The total model explained xx\% of the variance in engagement, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
+First, hindrance stressors and resources explained a statistically significant amount of the variability in engagement, \(R^2\) = 0.17, Adj.
+\(R^2\) = 0.16, \(F(2, 565) = 55.90\), \(p < .001\).
+The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 37.25\), \(p < .001\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 0.13.
+An interaction between hindrances and resources was not found.
 
-Next exploring stress, hindrance stressors and resources explained XX\% of the variance in stress, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xx, and thus provides statistical support for the presence of moderation.
-The total model explained xx\% of the variance in stress, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
+Next exploring stress, hindrance stressors and resources explained a statistically significant amount of the variability in stress, \(R^2\) = 0.01, Adj.
+\(R^2\) = 0.01, \(F(2, 565) = 3.13\), \(p = .045\).
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 6.89\), \(p < .001\), \(\Delta R^2\) = 0.03, \(\Delta F\) (1, 564) = 14.28, supporting the presence of a moderated effect.
 See Figure \ref{fig:hind-resource-stress-int}.
@@
 
-Similarly, hindrance stressors and resources explained XX\% of the variance in burnout, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xx.
+Similarly, hindrance stressors and resources explained a statistically significant amount of the variability in burnout, \(R^2\) = 0.04, Adj.
+\(R^2\) = 0.03, \(F(2, 565) = 10.68\), \(p < .001\).
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 9.49\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 6.89, supporting the presence of a moderated effect.
 The total model explained xx\% of the variance in burnout,\(R^2\) = .xx.

### 2024-06-11 Submission.Rmd
small tweaks

@@
 >Hyp 3.b: Strain and burnout are differentially predicted by challenges and hindrances.
+**Take a look at significant difference between slope coefficients (b's) of, for example, challenge-->strain & hindrance-->strain**
 
@@
   scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Lack of Consensus as a Resource") + 
-  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
+  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))
 
@@
 e <- ggplot(bottomchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
-  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Lack of Consensus as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
+  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Lack of Consensus as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))
 
@@
 f <- ggplot(bottomhindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
-  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Lack of Consensus as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))
-
-```
-
-```{r combinegraphs2, fig.cap="Characteristics percieved most *DIS*similarly (largest standard deviations).", fig.height=10}
+  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Lack of Consensus as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))
+
+```
+
+```{r combinegraphs2, fig.cap="Characteristics percieved most **dissimilarly** (largest standard deviations).", fig.height=10}
 

### 2024-06-11 Submission.tex
small tweaks

--- 2024-06-06 Submission.tex
@@
 Hyp 3.b: Strain and burnout are differentially predicted by challenges and hindrances.
+\textbf{Take a look at significant difference between slope coefficients (b's) of, for example, challenge--\textgreater strain \& hindrance--\textgreater strain}
 \end{quote}
@@
 \includegraphics{Submission_files/figure-latex/combinegraphs2-1.pdf}
-\caption{\label{fig:combinegraphs2}Characteristics percieved most \emph{DIS}similarly (largest standard deviations).}
+\caption{\label{fig:combinegraphs2}Characteristics percieved most \textbf{dissimilarly} (largest standard deviations).}
 \end{figure}
@@
 Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions.
-First exploring engagement, \(R^2\) = 0.15, Adj.
-\(R^2\) = 0.15 which represents a statistically significant effect, \(F(2, 565) = 10.68\), \(p < .001\).
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation.
-The total model explained xx\% of the variance in engagement, \(F(3, 564) = 9.49\), \(p < .001\) Figure \ref{fig:chal-resource-int} illustrates the interaction.
+First, challenges and resources explained a statistically significant amount of the variability in engagement, \(R^2\) = 0.15, Adj.
+\(R^2\) = 0.15, \(F(2, 565) = 50.09\), \(p < .001\).
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 35.62\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation.
+Figure \ref{fig:chal-resource-int} illustrates the interaction.
 With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low.
 With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.
+
+Next, challenge stressors and resources did not explain a significant amount of the variance in stress, \(R^2\) = 0.01, Adj.
+\(R^2\) = 0, \(F(2, 565) = 1.67\), \(p = .189\).
+The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 1.17\), \(p = .320\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 0.17, and thus does not support the presence of moderation.
+
+Finally, challenge stressors and resources explained a statsically significant amount of the variability in burnout, \(R^2\) = 0.04, Adj.
+\(R^2\) = 0.04, \(F(2, 565) = 1.67\), \(p = .189\).
+The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 1.17\), \(p = .320\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 2.25, and thus failing to provide statistical support for the presence of moderation.
+In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge stressors and the outcomes of strain and burnout.
 
@@
 
-Next, challenge stressors and resources explained XX\% of the variance in stress, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, which represents a non-significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
-The inclusion of the interaction term in step two of the model did not add significantly to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xxx.
-The total model explained xx\% of the variance in stress, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
+Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions.
+First, hindrance stressors and resources explained a statistically significant amount of the variability in engagement, \(R^2\) = 0.17, Adj.
+\(R^2\) = 0.16, \(F(2, 565) = 55.90\), \(p < .001\).
+The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 37.25\), \(p < .001\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 0.13.
+An interaction between hindrances and resources was not found.
 
-Finally, challenge stressors and resources explained XX\% of the variance in burnout, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
-The inclusion of the interaction term in step two of the model did not add significantly to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xxx.
-The total model explained xx\% of the variance in stress, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
-In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge stressors and the outcomes of strain and burnout.
-
-Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions.
-First, hindrance stressors and resources explained XX\% of the variance in engagement, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
-The inclusion of the interaction term in step two of the model did not add significantly to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xxx.
-The total model explained xx\% of the variance in engagement, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
-
-Next exploring stress, hindrance stressors and resources explained XX\% of the variance in stress, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx.
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xx, and thus provides statistical support for the presence of moderation.
-The total model explained xx\% of the variance in stress, \(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
+Next exploring stress, hindrance stressors and resources explained a statistically significant amount of the variability in stress, \(R^2\) = 0.01, Adj.
+\(R^2\) = 0.01, \(F(2, 565) = 3.13\), \(p = .045\).
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 6.89\), \(p < .001\), \(\Delta R^2\) = 0.03, \(\Delta F\) (1, 564) = 14.28, supporting the presence of a moderated effect.
 See Figure \ref{fig:hind-resource-stress-int}.

### 2024-06-21 Submission.Rmd
Updating intro
finalizing paper

@@
 Challenge demands promote mastery, personal growth, and future gains – these stressors should lead to coping strategies that facilitate achievement.
-Work characteristics consistent with this definition include time pressure and responsibility [@lepine2022challenge].
+Work characteristics consistent with this definition, for example, include time pressure and responsibility [@lepine2022challenge].
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Hindrance stressors in a work context include role conflict and role ambiguity [@lepine2022challenge].
+Example hindrance stressors in a work context include role conflict and role ambiguity [@lepine2022challenge].
 
@@
 Beginning with resources ADD JDR STUFF ON RESOURCES AND MOTIVATION HERE.
-@kim2020thriving found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources[^dontsaythat] (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing.
-The opposite occurred when a demand was appraised as a hindrance – in those instances, the appraisal had a negative association with motivational resources.
+@kim2020thriving found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a *challenge* was associated with motivational resources[^dontsaythat] (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing.
+The opposite occurred when a demand was appraised as a *hindrance* – in those instances, the appraisal had a negative association with motivational resources.
 @cavanaugh2000empirical, in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern.
@@
 
->Hyp 3.a: Engagement is predicted by resources and challenges.
-
->Hyp 3.b: Strain and burnout are differentially predicted by challenges and hindrances.
+>Hypothesis 3a: Engagement is predicted by resources and challenges.
+
+>Hypothesis 3b: Strain and burnout are differentially predicted by challenges and hindrances.
 **Take a look at significant difference between slope coefficients (b's) of, for example, challenge-->strain & hindrance-->strain**
@@
 
->Hyp 4.a:Resources moderate the relationship between challenge stressors and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
-
->Hyp 4.b:Resources moderate the relationship between hindrance stressors and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
+>Hypothesis 4a:Resources moderate the relationship between challenge stressors and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
+
+>Hypothesis 4b:Resources moderate the relationship between hindrance stressors and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
 
@@
 The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r hr_burn_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_burn_r_square_change`, $\Delta F$ (`r hr_burn_anova$Df[2]`, `r hr_burn_anova$Res.Df[2]`) = `r hr_burn_anova$F[2]`, supporting the presence of a moderated effect.
-The total model explained xx% of the variance in burnout,$R^2$ = .xx.
-Adj.
-$R^2$ = .xx, *F*(x, xx) = xx.xx, *p* <.xxx.
 Again, see Figure \@ref(fig:hind-resource-burn-int).

### 2024-06-21 Submission.tex
finalizing paper

--- 2024-06-06 Submission.tex
@@
 Challenge demands promote mastery, personal growth, and future gains -- these stressors should lead to coping strategies that facilitate achievement.
-Work characteristics consistent with this definition include time pressure and responsibility (M.
+Work characteristics consistent with this definition, for example, include time pressure and responsibility (M.
 A.
@@
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Hindrance stressors in a work context include role conflict and role ambiguity (M.
+Example hindrance stressors in a work context include role conflict and role ambiguity (M.
 A.
@@
 \(R^2\) = 0, \(F(2, 565) = 1.67\), \(p = .189\).
-The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model,\(F(3, 564) = 1.17\), \(p = .320\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 0.17, and thus does not support the presence of moderation.
+The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 1.17\), \(p = .320\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 0.17, and thus does not support the presence of moderation.
 
@@
 The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 9.49\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 6.89, supporting the presence of a moderated effect.
-The total model explained xx\% of the variance in burnout,\(R^2\) = .xx.
-Adj.
-\(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.
 Again, see Figure \ref{fig:hind-resource-burn-int}.

### 2024-06-23 Submission.Rmd
forgot to push coffee shop edits from yesterday (Rogers Caribou)

@@
 documentclass     : "apa7" #interact
-classoption       : "jou"
+classoption       : "man"
 #output            : "word_document"
@@
 
-```{r ourmodel, eval=TRUE, echo=FALSE, fig.cap="This is our working model"}
+```{r ourmodel, eval=TRUE, echo=FALSE, fig.cap="Focal constructs and associations of interest"}
 library(magick)
@@
 Beginning with resources ADD JDR STUFF ON RESOURCES AND MOTIVATION HERE.
-@kim2020thriving found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a *challenge* was associated with motivational resources[^dontsaythat] (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing.
+@kim2020thriving found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a *challenge* was associated with sources of motivation (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing.
 The opposite occurred when a demand was appraised as a *hindrance* – in those instances, the appraisal had a negative association with motivational resources.
@@
 
-[^dontsaythat]: Is there a different term that can be used here? This is confusing given the more straightforward Resource/Demand terminology from above
-
 >Hypothesis 4a:Resources moderate the relationship between challenge stressors and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
@@
 
-```{r cortab, results="asis", eval=FALSE}
+```{r cortab, results="asis", eval=TRUE}
 
@@
 papaja::apa_table(regtable, 
+              caption = "Moderated regression summary of outcomes regressed on challenges and resources",
               escape=FALSE,
@@
 $R^2$ =  `r round(summary(cr_eng_m2)$adj.r.squared, 2)`, `r cr_eng_info2$statistic$modelfit$r2`.
+H3A DESCRIPTION HERE: resource slope is significant, challenge is not significant.
 The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r cr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_eng_r_square_change`, $\Delta F$ (`r cr_eng_anova$Df[2]`, `r cr_eng_anova$Res.Df[2]`) = `r cr_eng_anova$F[2]`,  and thus provides statistical support for the presence of moderation.
@@
 papaja::apa_table(regtable,
+                 caption = "Moderated regression summary of outcomes regressed on hindrances and resources",
                  escape=FALSE,
@@
 
-In addition to the two hypotheses, two related research questions were proposed: 1) do literature-implicated resources materialize as perceived resources and 2) do literature-implicated demands materialize as perceived demands?
+In addition to the two hypotheses, two sets of exploratory analyses were also pursued: 1) do literature-implicated resources materialize as perceived resources and 2) do literature-implicated demands materialize as perceived demands?
 To answer these questions, authors first categorized O\*Net items into the elements listed in the JD-R literature.

### 2024-06-23 Submission.tex
forgot to push coffee shop edits from yesterday (Rogers Caribou)

@@
 \documentclass[
-  jou,mask]{apa7}
+  man,mask]{apa7}
 \usepackage{amsmath,amssymb}
@@
 \includegraphics{Submission_files/figure-latex/ourmodel-1.pdf}
-\caption{\label{fig:ourmodel}This is our working model}
+\caption{\label{fig:ourmodel}Focal constructs and associations of interest}
 \end{figure}
@@
 Beginning with resources ADD JDR STUFF ON RESOURCES AND MOTIVATION HERE.
-Kim and Beehr (2020) found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources\footnote{Is there a different term that can be used here?
-This is confusing given the more straightforward Resource/Demand terminology from above} (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing.
-The opposite occurred when a demand was appraised as a hindrance -- in those instances, the appraisal had a negative association with motivational resources.
+Kim and Beehr (2020) found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a \emph{challenge} was associated with sources of motivation (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing.
+The opposite occurred when a demand was appraised as a \emph{hindrance} -- in those instances, the appraisal had a negative association with motivational resources.
 Cavanaugh et al.
@@
 \begin{quote}
-Hyp 3.a: Engagement is predicted by resources and challenges.
+Hypothesis 3a: Engagement is predicted by resources and challenges.
 \end{quote}
@@
 \begin{quote}
-Hyp 3.b: Strain and burnout are differentially predicted by challenges and hindrances.
+Hypothesis 3b: Strain and burnout are differentially predicted by challenges and hindrances.
 \textbf{Take a look at significant difference between slope coefficients (b's) of, for example, challenge--\textgreater strain \& hindrance--\textgreater strain}
@@
 \begin{quote}
-Hyp 4.a:Resources moderate the relationship between challenge stressors and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
+Hypothesis 4a:Resources moderate the relationship between challenge stressors and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
 \end{quote}
@@
 \begin{quote}
-Hyp 4.b:Resources moderate the relationship between hindrance stressors and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
+Hypothesis 4b:Resources moderate the relationship between hindrance stressors and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
 \end{quote}
@@
 
+\begin{lltable}
+
+\begin{TableNotes}[para]
+\normalsize{\textit{Note.} The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)}
+\end{TableNotes}
+
+\tiny{
+
+\begin{longtable}{lllllllllllllllllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:cortab}Challenge, hindrance, and resource bivariate correlations.}\\
+\toprule
+ & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{6} & \multicolumn{1}{c}{7} & \multicolumn{1}{c}{8} & \multicolumn{1}{c}{9} & \multicolumn{1}{c}{10} & \multicolumn{1}{c}{11} & \multicolumn{1}{c}{12} & \multicolumn{1}{c}{13} & \multicolumn{1}{c}{14} & \multicolumn{1}{c}{15} & \multicolumn{1}{c}{16} & \multicolumn{1}{c}{17} & \multicolumn{1}{c}{18} & \multicolumn{1}{c}{19} & \multicolumn{1}{c}{20} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
+\midrule
+\endfirsthead
+\caption*{\normalfont{Table \ref{tab:cortab} continued}}\\
+\toprule
+ & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{6} & \multicolumn{1}{c}{7} & \multicolumn{1}{c}{8} & \multicolumn{1}{c}{9} & \multicolumn{1}{c}{10} & \multicolumn{1}{c}{11} & \multicolumn{1}{c}{12} & \multicolumn{1}{c}{13} & \multicolumn{1}{c}{14} & \multicolumn{1}{c}{15} & \multicolumn{1}{c}{16} & \multicolumn{1}{c}{17} & \multicolumn{1}{c}{18} & \multicolumn{1}{c}{19} & \multicolumn{1}{c}{20} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
+\midrule
+\endhead
+1. onet.resource.ii & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
+2. onet.resource.mp & .61*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.19 & 0.60\\
+3. onet.resource.wo & .46*** & .50*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.79 & 0.84\\
+4. onet.resource.io & .49*** & .64*** & .45*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.10 & 0.60\\
+5. onet.resource.ir & .46*** & .55*** & .37*** & .60*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.80 & 0.61\\
+6. onet.resource.pc & .19*** & .15*** & .32*** & .18*** & .37*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 2.99 & 0.77\\
+7. onet.resource.sc & .43*** & .46*** & .41*** & .45*** & .48*** & .37*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.61\\
+8. onet.challenge.ii & .62*** & .49*** & .37*** & .41*** & .33*** & .08 & .33*** & - &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
+9. onet.challenge.mp & .47*** & .63*** & .42*** & .50*** & .41*** & .09* & .38*** & .65*** & - &  &  &  &  &  &  &  &  &  &  &  & 4.20 & 0.64\\
+10. onet.challenge.wo & .34*** & .39*** & .64*** & .34*** & .30*** & .29*** & .38*** & .45*** & .49*** & - &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.88\\
+11. onet.challenge.io & .34*** & .48*** & .33*** & .65*** & .48*** & .13** & .40*** & .50*** & .68*** & .43*** & - &  &  &  &  &  &  &  &  &  & 4.07 & 0.64\\
+12. onet.challenge.ir & .32*** & .40*** & .26*** & .48*** & .63*** & .23*** & .39*** & .46*** & .60*** & .39*** & .70*** & - &  &  &  &  &  &  &  &  & 3.85 & 0.63\\
+13. onet.challenge.pc & .12** & .08 & .21*** & .13** & .26*** & .66*** & .29*** & .14** & .12** & .33*** & .20*** & .31*** & - &  &  &  &  &  &  &  & 2.85 & 0.79\\
+14. onet.challenge.sc & .27*** & .31*** & .28*** & .38*** & .40*** & .27*** & .62*** & .36*** & .41*** & .38*** & .51*** & .45*** & .40*** & - &  &  &  &  &  &  & 3.66 & 0.59\\
+15. onet.hindrance.ii & -.26*** & -.26*** & -.17*** & -.24*** & -.18*** & -.02 & -.08 & -.27*** & -.26*** & -.10* & -.19*** & -.16*** & .06 & -.10* & - &  &  &  &  &  & 2.15 & 1.01\\
+16. onet.hindrance.mp & -.23*** & -.30*** & -.17*** & -.22*** & -.15*** & .05 & -.07 & -.22*** & -.27*** & -.10* & -.18*** & -.15*** & .12** & -.06 & .86*** & - &  &  &  &  & 2.10 & 1.05\\
+17. onet.hindrance.wo & -.21*** & -.25*** & -.22*** & -.22*** & -.06 & -.02 & -.12** & -.14** & -.21*** & -.23*** & -.15*** & -.09* & .05 & -.10* & .66*** & .69*** & - &  &  &  & 2.31 & 1.02\\
+18.
+onet.hindrance.io & -.22*** & -.27*** & -.14*** & -.29*** & -.18*** & -.01 & -.10* & -.21*** & -.25*** & -.10* & -.27*** & -.19*** & .07 & -.10* & .79*** & .86*** & .69*** & - &  &  & 2.23 & 1.03\\
+19.
+onet.hindrance.ir & -.22*** & -.24*** & -.15*** & -.24*** & -.25*** & -.06 & -.11** & -.19*** & -.21*** & -.08* & -.20*** & -.23*** & .04 & -.12** & .79*** & .80*** & .61*** & .82*** & - &  & 2.35 & 0.89\\
+20. onet.hindrance.pc & -.04 & -.08* & -.09* & -.11** & -.10* & -.16*** & -.13** & -.03 & -.04 & -.06 & -.08* & -.10* & -.04 & -.13** & .38*** & .33*** & .47*** & .35*** & .47*** & - & 2.66 & 0.83\\
+21.
+onet.hindrance.sc & -.13** & -.15*** & -.13** & -.19*** & -.13** & -.09* & -.23*** & -.12** & -.10* & -.05 & -.16*** & -.12** & -.01 & -.17*** & .62*** & .62*** & .56*** & .64*** & .66*** & .45*** & 2.64 & 0.80\\
+\bottomrule
+\addlinespace
+\insertTableNotes
+\end{longtable}
+
+}
+
+\end{lltable}
+
 \begin{figure}
@@
 
-\caption{\label{tab:chal-resource-table}}
+\caption{\label{tab:chal-resource-table}Moderated regression summary of outcomes regressed on challenges and resources}
 
@@
 \(R^2\) = 0.15, \(F(2, 565) = 50.09\), \(p < .001\).
+H3A DESCRIPTION HERE: resource slope is significant, challenge is not significant.
 The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 35.62\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation.
@@
 
-\caption{\label{tab:hind-resource-table}}
+\caption{\label{tab:hind-resource-table}Moderated regression summary of outcomes regressed on hindrances and resources}
 
@@
 
-In addition to the two hypotheses, two related research questions were proposed: 1) do literature-implicated resources materialize as perceived resources and 2) do literature-implicated demands materialize as perceived demands?
+In addition to the two hypotheses, two sets of exploratory analyses were also pursued: 1) do literature-implicated resources materialize as perceived resources and 2) do literature-implicated demands materialize as perceived demands?
 To answer these questions, authors first categorized O*Net items into the elements listed in the JD-R literature.

### 2024-06-24 Submission.Rmd
not perfect but all correlations shown (deleted p<.001 with ***)

@@
                 triangle = "lower",
- #               stars = c(0.05, 0.01, 0.001),
-                describe = c(`$M$` = mean, `$SD$` = sd))
-
-papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table,
+                stars = c(0.05, 0.01)) #, 0.001),
+ #               describe = c(`$M$` = mean, `$SD$` = sd))
+
+#rapa <- as.data.frame(r$apa)
+
+papaja::apa_table(r$apa, # changed from r$apa list 6/23/24
                   caption = "Challenge, hindrance, and resource bivariate correlations.",
@@
 #                  stub_indents = list(a=1:10, b = 11:21),
-                  note = "The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)")
+                  align = c("m{2.6cm}", rep("m{.7cm}",21)),
+                  note = "$*$ p < .05, $**$ p < .01; The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)")
 trial <- data_new[c(405:411, 413:419, 421:427)]

### 2024-06-24 Submission.tex
not perfect but all correlations shown (deleted p<.001 with ***)

@@
 \begin{TableNotes}[para]
-\normalsize{\textit{Note.} The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)}
+\normalsize{\textit{Note.} $*$ p < .05, $**$ p < .01; The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)}
 \end{TableNotes}
@@
 
-\begin{longtable}{lllllllllllllllllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\begin{longtable}{m{2.6cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}m{.7cm}}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
 \caption{\label{tab:cortab}Challenge, hindrance, and resource bivariate correlations.}\\
 \toprule
- & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{6} & \multicolumn{1}{c}{7} & \multicolumn{1}{c}{8} & \multicolumn{1}{c}{9} & \multicolumn{1}{c}{10} & \multicolumn{1}{c}{11} & \multicolumn{1}{c}{12} & \multicolumn{1}{c}{13} & \multicolumn{1}{c}{14} & \multicolumn{1}{c}{15} & \multicolumn{1}{c}{16} & \multicolumn{1}{c}{17} & \multicolumn{1}{c}{18} & \multicolumn{1}{c}{19} & \multicolumn{1}{c}{20} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
+ & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{6} & \multicolumn{1}{c}{7} & \multicolumn{1}{c}{8} & \multicolumn{1}{c}{9} & \multicolumn{1}{c}{10} & \multicolumn{1}{c}{11} & \multicolumn{1}{c}{12} & \multicolumn{1}{c}{13} & \multicolumn{1}{c}{14} & \multicolumn{1}{c}{15} & \multicolumn{1}{c}{16} & \multicolumn{1}{c}{17} & \multicolumn{1}{c}{18} & \multicolumn{1}{c}{19} & \multicolumn{1}{c}{20}\\
 \midrule
@@
 \toprule
- & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{6} & \multicolumn{1}{c}{7} & \multicolumn{1}{c}{8} & \multicolumn{1}{c}{9} & \multicolumn{1}{c}{10} & \multicolumn{1}{c}{11} & \multicolumn{1}{c}{12} & \multicolumn{1}{c}{13} & \multicolumn{1}{c}{14} & \multicolumn{1}{c}{15} & \multicolumn{1}{c}{16} & \multicolumn{1}{c}{17} & \multicolumn{1}{c}{18} & \multicolumn{1}{c}{19} & \multicolumn{1}{c}{20} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
+ & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{6} & \multicolumn{1}{c}{7} & \multicolumn{1}{c}{8} & \multicolumn{1}{c}{9} & \multicolumn{1}{c}{10} & \multicolumn{1}{c}{11} & \multicolumn{1}{c}{12} & \multicolumn{1}{c}{13} & \multicolumn{1}{c}{14} & \multicolumn{1}{c}{15} & \multicolumn{1}{c}{16} & \multicolumn{1}{c}{17} & \multicolumn{1}{c}{18} & \multicolumn{1}{c}{19} & \multicolumn{1}{c}{20}\\
 \midrule
 \endhead
-1. onet.resource.ii & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
-2. onet.resource.mp & .61*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.19 & 0.60\\
-3. onet.resource.wo & .46*** & .50*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.79 & 0.84\\
-4. onet.resource.io & .49*** & .64*** & .45*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 4.10 & 0.60\\
-5. onet.resource.ir & .46*** & .55*** & .37*** & .60*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.80 & 0.61\\
-6. onet.resource.pc & .19*** & .15*** & .32*** & .18*** & .37*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 2.99 & 0.77\\
-7. onet.resource.sc & .43*** & .46*** & .41*** & .45*** & .48*** & .37*** & - &  &  &  &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.61\\
-8. onet.challenge.ii & .62*** & .49*** & .37*** & .41*** & .33*** & .08 & .33*** & - &  &  &  &  &  &  &  &  &  &  &  &  & 3.98 & 0.80\\
-9. onet.challenge.mp & .47*** & .63*** & .42*** & .50*** & .41*** & .09* & .38*** & .65*** & - &  &  &  &  &  &  &  &  &  &  &  & 4.20 & 0.64\\
-10. onet.challenge.wo & .34*** & .39*** & .64*** & .34*** & .30*** & .29*** & .38*** & .45*** & .49*** & - &  &  &  &  &  &  &  &  &  &  & 3.65 & 0.88\\
-11. onet.challenge.io & .34*** & .48*** & .33*** & .65*** & .48*** & .13** & .40*** & .50*** & .68*** & .43*** & - &  &  &  &  &  &  &  &  &  & 4.07 & 0.64\\
-12. onet.challenge.ir & .32*** & .40*** & .26*** & .48*** & .63*** & .23*** & .39*** & .46*** & .60*** & .39*** & .70*** & - &  &  &  &  &  &  &  &  & 3.85 & 0.63\\
-13. onet.challenge.pc & .12** & .08 & .21*** & .13** & .26*** & .66*** & .29*** & .14** & .12** & .33*** & .20*** & .31*** & - &  &  &  &  &  &  &  & 2.85 & 0.79\\
-14. onet.challenge.sc & .27*** & .31*** & .28*** & .38*** & .40*** & .27*** & .62*** & .36*** & .41*** & .38*** & .51*** & .45*** & .40*** & - &  &  &  &  &  &  & 3.66 & 0.59\\
-15. onet.hindrance.ii & -.26*** & -.26*** & -.17*** & -.24*** & -.18*** & -.02 & -.08 & -.27*** & -.26*** & -.10* & -.19*** & -.16*** & .06 & -.10* & - &  &  &  &  &  & 2.15 & 1.01\\
-16. onet.hindrance.mp & -.23*** & -.30*** & -.17*** & -.22*** & -.15*** & .05 & -.07 & -.22*** & -.27*** & -.10* & -.18*** & -.15*** & .12** & -.06 & .86*** & - &  &  &  &  & 2.10 & 1.05\\
-17. onet.hindrance.wo & -.21*** & -.25*** & -.22*** & -.22*** & -.06 & -.02 & -.12** & -.14** & -.21*** & -.23*** & -.15*** & -.09* & .05 & -.10* & .66*** & .69*** & - &  &  &  & 2.31 & 1.02\\
-18.
-onet.hindrance.io & -.22*** & -.27*** & -.14*** & -.29*** & -.18*** & -.01 & -.10* & -.21*** & -.25*** & -.10* & -.27*** & -.19*** & .07 & -.10* & .79*** & .86*** & .69*** & - &  &  & 2.23 & 1.03\\
-19.
-onet.hindrance.ir & -.22*** & -.24*** & -.15*** & -.24*** & -.25*** & -.06 & -.11** & -.19*** & -.21*** & -.08* & -.20*** & -.23*** & .04 & -.12** & .79*** & .80*** & .61*** & .82*** & - &  & 2.35 & 0.89\\
-20. onet.hindrance.pc & -.04 & -.08* & -.09* & -.11** & -.10* & -.16*** & -.13** & -.03 & -.04 & -.06 & -.08* & -.10* & -.04 & -.13** & .38*** & .33*** & .47*** & .35*** & .47*** & - & 2.66 & 0.83\\
-21.
-onet.hindrance.sc & -.13** & -.15*** & -.13** & -.19*** & -.13** & -.09* & -.23*** & -.12** & -.10* & -.05 & -.16*** & -.12** & -.01 & -.17*** & .62*** & .62*** & .56*** & .64*** & .66*** & .45*** & 2.64 & 0.80\\
+1. onet.resource.ii & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
+2. onet.resource.mp & .61** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
+3. onet.resource.wo & .46** & .50** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
+4. onet.resource.io & .49** & .64** & .45** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
+5. onet.resource.ir & .46** & .55** & .37** & .60** & - &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
+6. onet.resource.pc & .19** & .15** & .32** & .18** & .37** & - &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
+7. onet.resource.sc & .43** & .46** & .41** & .45** & .48** & .37** & - &  &  &  &  &  &  &  &  &  &  &  &  & \\
+8. onet.challenge.ii & .62** & .49** & .37** & .41** & .33** & .08 & .33** & - &  &  &  &  &  &  &  &  &  &  &  & \\
+9. onet.challenge.mp & .47** & .63** & .42** & .50** & .41** & .09* & .38** & .65** & - &  &  &  &  &  &  &  &  &  &  & \\
+10. onet.challenge.wo & .34** & .39** & .64** & .34** & .30** & .29** & .38** & .45** & .49** & - &  &  &  &  &  &  &  &  &  & \\
+11. onet.challenge.io & .34** & .48** & .33** & .65** & .48** & .13** & .40** & .50** & .68** & .43** & - &  &  &  &  &  &  &  &  & \\
+12. onet.challenge.ir & .32** & .40** & .26** & .48** & .63** & .23** & .39** & .46** & .60** & .39** & .70** & - &  &  &  &  &  &  &  & \\
+13. onet.challenge.pc & .12** & .08 & .21** & .13** & .26** & .66** & .29** & .14** & .12** & .33** & .20** & .31** & - &  &  &  &  &  &  & \\
+14. onet.challenge.sc & .27** & .31** & .28** & .38** & .40** & .27** & .62** & .36** & .41** & .38** & .51** & .45** & .40** & - &  &  &  &  &  & \\
+15. onet.hindrance.ii & -.26** & -.26** & -.17** & -.24** & -.18** & -.02 & -.08 & -.27** & -.26** & -.10* & -.19** & -.16** & .06 & -.10* & - &  &  &  &  & \\
+16. onet.hindrance.mp & -.23** & -.30** & -.17** & -.22** & -.15** & .05 & -.07 & -.22** & -.27** & -.10* & -.18** & -.15** & .12** & -.06 & .86** & - &  &  &  & \\
+17. onet.hindrance.wo & -.21** & -.25** & -.22** & -.22** & -.06 & -.02 & -.12** & -.14** & -.21** & -.23** & -.15** & -.09* & .05 & -.10* & .66** & .69** & - &  &  & \\
+18. onet.hindrance.io & -.22** & -.27** & -.14** & -.29** & -.18** & -.01 & -.10* & -.21** & -.25** & -.10* & -.27** & -.19** & .07 & -.10* & .79** & .86** & .69** & - &  & \\
+19. onet.hindrance.ir & -.22** & -.24** & -.15** & -.24** & -.25** & -.06 & -.11** & -.19** & -.21** & -.08* & -.20** & -.23** & .04 & -.12** & .79** & .80** & .61** & .82** & - & \\
+20. onet.hindrance.pc & -.04 & -.08* & -.09* & -.11** & -.10* & -.16** & -.13** & -.03 & -.04 & -.06 & -.08* & -.10* & -.04 & -.13** & .38** & .33** & .47** & .35** & .47** & -\\
+21. onet.hindrance.sc & -.13** & -.15** & -.13** & -.19** & -.13** & -.09* & -.23** & -.12** & -.10* & -.05 & -.16** & -.12** & -.01 & -.17** & .62** & .62** & .56** & .64** & .66** & .45**\\
 \bottomrule

### 2024-07-10 Submission.Rmd
Updating the Introduction Section

@@
 
-Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing.
-Beginning with resources ADD JDR STUFF ON RESOURCES AND MOTIVATION HERE.
-@kim2020thriving found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a *challenge* was associated with sources of motivation (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing.
-The opposite occurred when a demand was appraised as a *hindrance* – in those instances, the appraisal had a negative association with motivational resources.
-@cavanaugh2000empirical, in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern.
-@chen2021daily found that daily challenge demands were positively related to cognitive wellbeing and work-family enrichment.
-Daily hindrance demands were negatively related to these outcomes.
-In contrast, @abbas2019challenge found that challenge and hindrance stressors were *both* positively related to strain and turnover intentions.
-We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with it [@crawford2010linking].
-Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety [@rodell2009can].
-Lastly, @gerich2017relevance concluded that employee wellbeing was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
-In addition to the studies above, several meta-analyses also support differential associations across a variety of organizational outcomes as well.
-For example, both challenges and hindrances have been shown to positively predict strain [@lepine2005meta; @podsakoff2007differential; @webster2010toward].
-Many other outcomes are differentially related to challenges and hindrances, largely in the expected direction.
-For example, motivation, job satisfaction, commitment, and performance have been shown to positively relate to challenge stressors and negatively relate to hindrance stressors [@lepine2005meta].
-Turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance stressors [@podsakoff2007differential].
-@kim2020thriving, similarly, found evidence for the differential results via challenge and hindrance appraisals.
+Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance [e.g., @lepine2005meta].
+We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout.
+Beginning with resources, @hakanen2008job found job resources influenced future work engagement.
+Moreover, in a sample of teachers and dentists, @bakker2007job found that resources were most predictive of engagement when job demands were especially high.
+
+The findings regarding demands are more complex, presumably because the way challenge vs.
+hindrance appraisal influence coping strategies.
+Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and work meaningful [@chen2021daily], engagement [@crawford2010linking], and strain and turnover intentions [e.g., @abbas2019challenge], for example.
+Challenge appraisals have been negatively associated with job search behaviors [e.g., @cavanaugh2000empirical].
+
+Hindrance demands (appraisals) are largely related to outcomes as the job demands-resources model predicts.
+When a demand was appraised as a hindrance – it was negatively associated with motivational resources [@kim2020thriving], engagement [@crawford2010linking], job search behaviors and job satisfaction, [@cavanaugh2000empirical].
+@chen2021daily found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment.
+Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance stressors [@podsakoff2007differential]].
+Interestingly, both challenges and hindrances have been shown to positively predict strain [(Abbas & Raja, 2019]@abbas2019challenge; @lepine2005meta; @podsakoff2007differential; @webster2010toward], which further highlights the complex association between appraisals and subsequent outcomes.
+Given the differential relationships described above, we make the following predictions:
 
@@
 In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain [e.g., @bakker2005job] and burnout [e.g., @xanthopoulou2007job].
-BUILD ON THIS - DETAILS OF THESE TWO STUDIES AND MORE - BAKKER 2010
+Bakker and colleagues (2005) were the first to report empirical evidence to support the idea job resources could potentially buffer the negative impact of job demands on stress reactions like burnout.
+@bakker2005job explored the interaction between 4 demands (e.g., work overload, physical demands) and 4 resources (e.g., social support, feedback) and three dimensions of burnout (exhaustion, cynicism, and professional efficacy), and found some support for the prediction that high demands with low resources predicted greater levels of cynicism and exhaustion among employees in higher education.
+Similarly, @xanthopoulou2007job also found some support for this interaction (high demands + low resources leads to greater burnout) among home healthcare employees.
+They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout.
+We extend the established job demands-resources model buffer proposition to both challenge and hindrance stressors (demands) as follows:
 

### 2024-07-10 Submission.tex
Updating the Introduction Section

@@
 
-Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing.
-Beginning with resources ADD JDR STUFF ON RESOURCES AND MOTIVATION HERE.
-Kim and Beehr (2020) found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a \emph{challenge} was associated with sources of motivation (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing.
-The opposite occurred when a demand was appraised as a \emph{hindrance} -- in those instances, the appraisal had a negative association with motivational resources.
-Cavanaugh et al.
-(2000), in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern.
-Chen et al.
-(2021) found that daily challenge demands were positively related to cognitive wellbeing and work-family enrichment.
-Daily hindrance demands were negatively related to these outcomes.
-In contrast, Abbas and Raja (2019) found that challenge and hindrance stressors were \emph{both} positively related to strain and turnover intentions.
-We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with it (Crawford et al., 2010).
-Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety (Rodell \& Judge, 2009).
-Lastly, Gerich (2017) concluded that employee wellbeing was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.
-In addition to the studies above, several meta-analyses also support differential associations across a variety of organizational outcomes as well.
-For example, both challenges and hindrances have been shown to positively predict strain (J.
-A.
-LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010).
-Many other outcomes are differentially related to challenges and hindrances, largely in the expected direction.
-For example, motivation, job satisfaction, commitment, and performance have been shown to positively relate to challenge stressors and negatively relate to hindrance stressors (J.
+Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance (e.g., J.
 A.
 LePine et al., 2005).
-Turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance stressors (Podsakoff et al., 2007).
-Kim and Beehr (2020), similarly, found evidence for the differential results via challenge and hindrance appraisals.
+We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout.
+Beginning with resources, Hakanen et al.
+(2008) found job resources influenced future work engagement.
+Moreover, in a sample of teachers and dentists, Bakker et al.
+(2007) found that resources were most predictive of engagement when job demands were especially high.
+
+The findings regarding demands are more complex, presumably because the way challenge vs.~hindrance appraisal influence coping strategies.
+Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and work meaningful (Chen et al., 2021), engagement (Crawford et al., 2010), and strain and turnover intentions (e.g., Abbas \& Raja, 2019), for example.
+Challenge appraisals have been negatively associated with job search behaviors (e.g., Cavanaugh et al., 2000).
+
+Hindrance demands (appraisals) are largely related to outcomes as the job demands-resources model predicts.
+When a demand was appraised as a hindrance -- it was negatively associated with motivational resources (Kim \& Beehr, 2020), engagement (Crawford et al., 2010), job search behaviors and job satisfaction, (Cavanaugh et al., 2000).
+Chen et al.
+(2021) found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment.
+Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance stressors (Podsakoff et al., 2007){]}.
+Interestingly, both challenges and hindrances have been shown to positively predict strain ((Abbas \& Raja, 2019 Abbas \& Raja, 2019; J.
+A.
+LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010), which further highlights the complex association between appraisals and subsequent outcomes.
+Given the differential relationships described above, we make the following predictions:
 
@@
 In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain (e.g., Bakker et al., 2005) and burnout (e.g., Xanthopoulou et al., 2007).
-BUILD ON THIS - DETAILS OF THESE TWO STUDIES AND MORE - BAKKER 2010
+Bakker and colleagues (2005) were the first to report empirical evidence to support the idea job resources could potentially buffer the negative impact of job demands on stress reactions like burnout.
+Bakker et al.
+(2005) explored the interaction between 4 demands (e.g., work overload, physical demands) and 4 resources (e.g., social support, feedback) and three dimensions of burnout (exhaustion, cynicism, and professional efficacy), and found some support for the prediction that high demands with low resources predicted greater levels of cynicism and exhaustion among employees in higher education.
+Similarly, Xanthopoulou et al.
+(2007) also found some support for this interaction (high demands + low resources leads to greater burnout) among home healthcare employees.
+They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout.
+We extend the established job demands-resources model buffer proposition to both challenge and hindrance stressors (demands) as follows:
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2007job}{}}%
+Bakker, A.
+B., Hakanen, J.
+J., Demerouti, E., \& Xanthopoulou, D.
+(2007).
+Job resources boost work engagement, particularly when job demands are high.
+\emph{Journal of Educational Psychology}, \emph{99}(2), 274.
+
 \leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
@@
 Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hakanen2008job}{}}%
+Hakanen, J.
+J., Schaufeli, W.
+B., \& Ahola, K.
+(2008).
+The job demands-resources model: A three-year cross-lagged study of burnout, depression, commitment, and work engagement.
+\emph{Work \& Stress}, \emph{22}(3), 224--241.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-rodell2009can}{}}%
-Rodell, J.
-B., \& Judge, T.
-A.
-(2009).
-Can {``good''} stressors spark {``bad''} behaviors?
-The mediating role of emotions in links of challenge and hindrance stressors with citizenship and counterproductive behaviors.
-\emph{Journal of Applied Psychology}, \emph{94}(6), 1438.
-
 \leavevmode\vadjust pre{\hypertarget{ref-rosen2020challenges}{}}%

### 2024-07-11 Submission.Rmd
enable line numbers
added second correlation table

@@
 footnotelist      : no
-linenumbers       : no
+linenumbers       : yes
 mask              : yes
@@
 
+```
+
+```{r}
+
+names(data_new)[names(data_new) == "engagement"] <- "Engagement"
+names(data_new)[names(data_new) == "burnout"] <- "Burnout"
+
+r_second <- corx::corx(data_new, x =c("Challenge", "Hindrance", "Resource", "Stress", "Burnout", "Engagement"),                          triangle = "lower",
+                stars = c(0.05, 0.01, 0.001),
+                describe = c(`$M$` = mean, `$SD$` = sd))
+
+papaja::apa_table(r_second$apa, 
+                  caption = "Overall variable bivariate correlations.",
+                  escape = FALSE, 
+                  note = "$*$ p < .05, $**$ p < .01, $***$ p < .001")
 ```
@@
 
-cr_eng_m1 <- lm(scale(engagement) ~ scale(overall.challenge_center), modreg)
+cr_eng_m1 <- lm((engagement) ~ scale(overall.challenge_center), modreg)
 #summary(cr_eng_m1)
 
-cr_eng_m2 <- lm(scale(engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center), modreg)
+cr_eng_m2 <- lm((engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center), modreg)
 #summary(cr_eng_m2)
 
-cr_eng_m3 <- lm(scale(engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
+cr_eng_m3 <- lm((engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
 #summary(cr_eng_m3)
@@
 
-hr_burn_m1 <- lm(scale(burnout) ~ scale(overall.hindrance_center), modreg)
+hr_burn_m1 <- lm((burnout) ~ scale(overall.hindrance_center), modreg)
 #summary(hr_burn_m1)
 
-hr_burn_m2 <- lm(scale(burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
+hr_burn_m2 <- lm((burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
 #summary(hr_burn_m2)
 
-hr_burn_m3 <- lm(scale(burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
+hr_burn_m3 <- lm((burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
 #summary(hr_burn_m3)
@@
 
-hr_stress_m1 <- lm(scale(stress) ~ scale(overall.hindrance_center), modreg)
+hr_stress_m1 <- lm((stress) ~ scale(overall.hindrance_center), modreg)
 #summary(hr_stress_m1)
 
-hr_stress_m2 <- lm(scale(stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
+hr_stress_m2 <- lm((stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
 #summary(hr_stress_m2)
 
-hr_stress_m3 <- lm(scale(stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
+hr_stress_m3 <- lm((stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
 #summary(hr_stress_m3)
@@
 
-hr_eng_m1 <- lm(scale(engagement) ~ scale(overall.hindrance_center), modreg)
+hr_eng_m1 <- lm((engagement) ~ scale(overall.hindrance_center), modreg)
 #summary(hr_eng_m1)
 
-hr_eng_m2 <- lm(scale(engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
+hr_eng_m2 <- lm((engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
 #summary(hr_eng_m2)
 
-hr_eng_m3 <- lm(scale(engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
+hr_eng_m3 <- lm((engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
 #summary(hr_eng_m3)
@@
 Step <- c("1", "","2", "1", "","2", "1", "","2")
-Model <- c("Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource")
+Model <- c("Challenge", "Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge", "Resource", "Challenge X Resource")
 Beta <- c(sigfill(chal.2.eng), paste(res.2.eng,"**"), paste(int.cr.3.eng,"*"), chal.2.stress, res.2.stress, int.cr.3.stress, paste(chal.2.burn,"**"), res.2.burn, int.cr.3.burn)

### 2024-07-11 Submission.tex
enable line numbers
added second correlation table

@@
 
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:unnamed-chunk-1}Overall variable bivariate correlations.}
+
+\begin{tabular}{llllllll}
+\toprule
+ & \multicolumn{1}{c}{1} & \multicolumn{1}{c}{2} & \multicolumn{1}{c}{3} & \multicolumn{1}{c}{4} & \multicolumn{1}{c}{5} & \multicolumn{1}{c}{$M$} & \multicolumn{1}{c}{$SD$}\\
+\midrule
+1. Challenge & - &  &  &  &  & 3.75 & 0.50\\
+2. Hindrance & -.21*** & - &  &  &  & 2.39 & 0.78\\
+3. Resource & .74*** & -.25*** & - &  &  & 3.77 & 0.48\\
+4. Stress & -.03 & .11** & -.08 & - &  & 2.59 & 0.97\\
+5. Burnout & -.05 & .08 & -.08 & .70*** & - & 3.04 & 0.87\\
+6. Engagement & .28*** & -.11** & .33*** & -.24*** & -.30*** & 4.03 & 0.79\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} $*$ p < .05, $**$ p < .01, $***$ p < .001}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
 \begin{figure}
@@
 \midrule
-Engagement & 1 & Challenge & -0.10 &  & \\
- &  & Resource & 0.48 ** & 0.15 ** & \\
- & 2 & Challenge X Resource & -0.09 * & 0.16 ** & 0.01 *\\
+Engagement & 1 & Challenge & -0.08 &  & \\
+ &  & Resource & 0.37 ** & 0.15 ** & \\
+ & 2 & Challenge & -0.07 * & 0.16 ** & 0.01 *\\
+Stress & 1 & Resource & 0.14 &  & \\
+ &  & Challenge X Resource & -0.07 & 0.01 & \\
+ & 2 & Challenge & 0.02 & 0.01 & 0.00\\
+Burnout & 1 & Resource & 0.33 ** &  & \\
+ &  & Challenge & -0.14 & 0.04 ** & \\
+ & 2 & Resource & 0.06 & 0.04 ** & 0.00\\
+Engagement & 1 & Challenge X Resource & -0.08 &  & \\
+ &  & Challenge & 0.37 ** & 0.15 ** & \\
+ & 2 & Resource & -0.07 * & 0.16 ** & 0.01 *\\
 Stress & 1 & Challenge & 0.14 &  & \\
@@
  & 2 & Challenge X Resource & 0.02 & 0.01 & 0.00\\
-Burnout & 1 & Challenge & 0.33 ** &  & \\
- &  & Resource & -0.14 & 0.04 ** & \\
- & 2 & Challenge X Resource & 0.06 & 0.04 ** & 0.00\\
 \bottomrule
@@
 \midrule
-Engagement & 1 & Hindrance & -0.14 ** &  & \\
- &  & Resource & 0.46 ** & 0.17 ** & \\
- & 2 & Hindrance X Resource & -0.02 & 0.17 ** & 0.00\\
-Stress & 1 & Hindrance & 0.10 * &  & \\
- &  & Resource & 0.02 ** & 0.01 * & \\
- & 2 & Hindrance X Resource & -0.19 ** & 0.04 ** & 0.03 **\\
-Burnout & 1 & Hindrance & 0.10 * &  & \\
- &  & Resource & 0.12 * & 0.04 ** & \\
- & 2 & Hindrance X Resource & -0.13 ** & 0.05 ** & 0.01 **\\
+Engagement & 1 & Hindrance & -0.11 ** &  & \\
+ &  & Resource & 0.35 ** & 0.17 ** & \\
+ & 2 & Hindrance X Resource & -0.01 & 0.17 ** & 0.00\\
+Stress & 1 & Hindrance & 0.08 * &  & \\
+ &  & Resource & 0.01 ** & 0.01 * & \\
+ & 2 & Hindrance X Resource & -0.17 ** & 0.04 ** & 0.03 **\\
+Burnout & 1 & Hindrance & 0.09 * &  & \\
+ &  & Resource & 0.1 * & 0.04 ** & \\
+ & 2 & Hindrance X Resource & -0.11 ** & 0.05 ** & 0.01 **\\
 \bottomrule

### 2024-07-11 Submission.Rmd
updating regression tables

@@
 
-cr_burn_m1 <- lm(scale(burnout) ~ scale(overall.challenge_center), modreg)
+cr_burn_m1 <- lm(burnout ~ scale(overall.challenge_center), modreg)
 #summary(cr_burn_m1)
 
-cr_burn_m2 <- lm(scale(burnout) ~ scale(overall.challenge_center) + scale(overall.resource), modreg)
+cr_burn_m2 <- lm(burnout ~ scale(overall.challenge_center) + scale(overall.resource), modreg)
 #summary(cr_burn_m2)
 
-cr_burn_m3 <- lm(scale(burnout) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
+cr_burn_m3 <- lm(burnout ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
 #summary(cr_burn_m3)
@@
 
-cr_stress_m1 <- lm(scale(stress) ~ scale(overall.challenge_center), modreg)
+cr_stress_m1 <- lm(stress ~ scale(overall.challenge_center), modreg)
 #summary(cr_stress_m1)
 
-cr_stress_m2 <- lm(scale(stress) ~ scale(overall.challenge_center) + scale(overall.resource_center), modreg)
+cr_stress_m2 <- lm(stress ~ scale(overall.challenge_center) + scale(overall.resource_center), modreg)
 #summary(cr_stress_m2)
 
-cr_stress_m3 <- lm(scale(stress) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
+cr_stress_m3 <- lm(stress ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
 #summary(cr_stress_m3)
@@
 
-cr_eng_m1 <- lm((engagement) ~ scale(overall.challenge_center), modreg)
+cr_eng_m1 <- lm(engagement ~ scale(overall.challenge_center), modreg)
 #summary(cr_eng_m1)
 
-cr_eng_m2 <- lm((engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center), modreg)
+cr_eng_m2 <- lm(engagement ~ scale(overall.challenge_center) + scale(overall.resource_center), modreg)
 #summary(cr_eng_m2)
 
-cr_eng_m3 <- lm((engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
+cr_eng_m3 <- lm(engagement ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
 #summary(cr_eng_m3)
@@
 
-hr_burn_m1 <- lm((burnout) ~ scale(overall.hindrance_center), modreg)
+hr_burn_m1 <- lm(burnout ~ scale(overall.hindrance_center), modreg)
 #summary(hr_burn_m1)
 
-hr_burn_m2 <- lm((burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
+hr_burn_m2 <- lm(burnout ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
 #summary(hr_burn_m2)
 
-hr_burn_m3 <- lm((burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
+hr_burn_m3 <- lm(burnout ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
 #summary(hr_burn_m3)
@@
 
-hr_stress_m1 <- lm((stress) ~ scale(overall.hindrance_center), modreg)
+hr_stress_m1 <- lm(stress ~ scale(overall.hindrance_center), modreg)
 #summary(hr_stress_m1)
 
-hr_stress_m2 <- lm((stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
+hr_stress_m2 <- lm(stress ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
 #summary(hr_stress_m2)
 
-hr_stress_m3 <- lm((stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
+hr_stress_m3 <- lm(stress ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
 #summary(hr_stress_m3)
@@
 
-hr_eng_m1 <- lm((engagement) ~ scale(overall.hindrance_center), modreg)
+hr_eng_m1 <- lm(engagement ~ scale(overall.hindrance_center), modreg)
 #summary(hr_eng_m1)
 
-hr_eng_m2 <- lm((engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
+hr_eng_m2 <- lm(engagement ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
 #summary(hr_eng_m2)
 
-hr_eng_m3 <- lm((engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
+hr_eng_m3 <- lm(engagement ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
 #summary(hr_eng_m3)
@@
 res.2.burn <- round(summary(cr_burn_m2)$coefficients[3, 1],2)
-
+chal.3.burn <- round(summary(cr_burn_m3)$coefficients[2, 1],2)
+res.3.burn <- round(summary(cr_burn_m3)$coefficients[3, 1],2)
 int.cr.3.burn <- round(summary(cr_burn_m3)$coefficients[4, 1],2)
@@
 
+chal.3.stress <- round(summary(cr_stress_m3)$coefficients[2, 1],2)
+res.3.stress <- round(summary(cr_stress_m3)$coefficients[3, 1],2)
 int.cr.3.stress <- round(summary(cr_stress_m3)$coefficients[4, 1],2)
@@
 
+chal.3.eng <- round(summary(cr_eng_m3)$coefficients[2, 1],2)
+res.3.eng <- round(summary(cr_eng_m3)$coefficients[3, 1],2)
 int.cr.3.eng <- round(summary(cr_eng_m3)$coefficients[4, 1],2)
@@
 res.2hr.burn <- round(summary(hr_burn_m2)$coefficients[3, 1],2)
-
+hind.3.burn <- round(summary(hr_burn_m3)$coefficients[2, 1],2)
+res.3hr.burn <- round(summary(hr_burn_m3)$coefficients[3, 1],2)
 int.hr.3.burn <- round(summary(hr_burn_m3)$coefficients[4, 1],2)
@@
 
+hind.3.stress <- round(summary(hr_stress_m3)$coefficients[2, 1],2)
+res.3hr.stress <- round(summary(hr_stress_m3)$coefficients[3, 1],2)
 int.hr.3.stress <- round(summary(hr_stress_m3)$coefficients[4, 1],2)
@@
 
+hind.3.eng <- round(summary(hr_eng_m3)$coefficients[2, 1],2)
+res.3hr.eng <- round(summary(hr_eng_m3)$coefficients[3, 1],2)
 int.hr.3.eng <- round(summary(hr_eng_m3)$coefficients[4, 1],2)
@@
 
-DV <- c("Engagement","","", "Stress","","", "Burnout","","")
-Step <- c("1", "","2", "1", "","2", "1", "","2")
+DV <- c("Engagement","","","","","Stress","","","","", "Burnout","","","","")
+Step <- c("1", "","2", "", "", "1", "","2", "","", "1", "","2", "","")
 Model <- c("Challenge", "Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge", "Resource", "Challenge X Resource")
-Beta <- c(sigfill(chal.2.eng), paste(res.2.eng,"**"), paste(int.cr.3.eng,"*"), chal.2.stress, res.2.stress, int.cr.3.stress, paste(chal.2.burn,"**"), res.2.burn, int.cr.3.burn)
-R2 <- c("", paste(cr_eng_m2_r,"**"), paste(cr_eng_m3_r,"**"), "", round(cr_stress_m2_r,2), round(cr_stress_m3_r,2), "", paste(round(cr_burn_m2_r,2),"**"), paste(round(cr_burn_m3_r,2),"**"))
-DeltaR <- c("","", paste(cr_eng_r_square_change,"*"), "","",cr_stress_r_square_change, "","",cr_burn_r_square_change)
-
+Beta <- c(sigfill(chal.2.eng), paste(res.2.eng,"**"), chal.3.eng, paste(res.3.eng,"**"), paste(int.cr.3.eng,"*"), chal.2.stress, res.2.stress, chal.3.stress, res.3.stress, int.cr.3.stress, paste(chal.2.burn,"**"), res.2.burn, paste(chal.3.burn,"**"), res.3.burn, int.cr.3.burn)
+R2 <- c("", paste(cr_eng_m2_r,"**"), "", "", paste(cr_eng_m3_r,"**"), "", round(cr_stress_m2_r,2), "", "", round(cr_stress_m3_r,2), "", paste(round(cr_burn_m2_r,2),"**"), "", "",paste(round(cr_burn_m3_r,2),"**"))
+DeltaR <- c("","","","", paste(cr_eng_r_square_change,"*"), "","","","",cr_stress_r_square_change, "","","","",cr_burn_r_square_change)
 regtable <- as.data.frame(cbind(DV, Step, Model, Beta, R2, DeltaR))
@@
 
-DV <- c("Engagement","","", "Stress","","", "Burnout","","")
-Step <- c("1", "","2", "1", "","2", "1", "","2")
-Model <- c("Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource")
-Beta <- c(paste(hind.2.eng,"**"), paste(res.2hr.eng,"**"), int.hr.3.eng, paste(sigfill(hind.2.stress),"*"), paste(res.2hr.stress,"**"), paste(int.hr.3.stress,"**"), paste(sigfill(hind.2.burn),"*"), paste(res.2hr.burn,"*"), paste(int.hr.3.burn,"**"))
-R2 <- c("", paste(round(hr_eng_m2_r,2),"**"), paste(round(hr_eng_m3_r,2),"**"), "", paste(hr_stress_m2_r,"*"), paste(hr_stress_m3_r, "**"), "", paste(hr_burn_m2_r,"**"), paste(hr_burn_m3_r,"**"))
+DV <- c("Engagement","","","","","Stress","","","","", "Burnout","","","","")
+Step <- c("1", "","2", "", "", "1", "","2", "","", "1", "","2", "","")
+Model <- c("Hindrance", "Resource", "Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance", "Resource", "Hindrance X Resource")
+Beta <- c(paste(hind.2.eng,"**"), paste(res.2hr.eng,"**"), paste(sigfill(hind.3.eng),"**"), paste(res.3hr.eng,"**"), int.hr.3.eng, paste(sigfill(hind.2.stress),"*"), paste(res.2hr.stress), paste(hind.3.stress, "**"), paste(sigfill(res.3hr.stress)), paste(int.hr.3.stress,"**"), paste(sigfill(hind.2.burn),"*"), paste(sigfill(res.2hr.burn),"*"), paste(sigfill(hind.3.burn),"*"), paste(res.3hr.burn), paste(int.hr.3.burn,"**"))
+R2 <- c("", paste(round(hr_eng_m2_r,2),"**"), "", "", paste(round(hr_eng_m3_r,2),"**"), "", paste(hr_stress_m2_r,"*"), "", "", paste(hr_stress_m3_r, "**"), "", paste(hr_burn_m2_r,"**"), "", "", paste(hr_burn_m3_r,"**"))
 #DeltaR <- c("",paste(hr_eng_m2_r,"**"),hr_eng_r_square_change, "",paste(hr_stress_m2_r,"**"),hr_stress_r_square_change, "",paste(hr_burn_m2_r,"**"),hr_burn_r_square_change)
-DeltaR <- c("","",hr_eng_r_square_change, "","",paste(hr_stress_r_square_change,"**"), "","",paste(hr_burn_r_square_change, "**"))
+DeltaR <- c("","","","",hr_eng_r_square_change, "","","","",paste(hr_stress_r_square_change,"**"), "","","","",paste(hr_burn_r_square_change, "**"))
 regtable <- as.data.frame(cbind(DV, Step, Model, Beta, R2, DeltaR))

### 2024-07-11 Submission.tex
updating regression tables

@@
  &  & Resource & 0.37 ** & 0.15 ** & \\
- & 2 & Challenge & -0.07 * & 0.16 ** & 0.01 *\\
-Stress & 1 & Resource & 0.14 &  & \\
- &  & Challenge X Resource & -0.07 & 0.01 & \\
- & 2 & Challenge & 0.02 & 0.01 & 0.00\\
-Burnout & 1 & Resource & 0.33 ** &  & \\
- &  & Challenge & -0.14 & 0.04 ** & \\
- & 2 & Resource & 0.06 & 0.04 ** & 0.00\\
-Engagement & 1 & Challenge X Resource & -0.08 &  & \\
- &  & Challenge & 0.37 ** & 0.15 ** & \\
- & 2 & Resource & -0.07 * & 0.16 ** & 0.01 *\\
-Stress & 1 & Challenge & 0.14 &  & \\
- &  & Resource & -0.07 & 0.01 & \\
- & 2 & Challenge X Resource & 0.02 & 0.01 & 0.00\\
+ & 2 & Challenge & -0.08 &  & \\
+ &  & Resource & 0.37 ** &  & \\
+ &  & Challenge X Resource & -0.07 * & 0.16 ** & 0.01 *\\
+Stress & 1 & Challenge & 0.12 &  & \\
+ &  & Resource & -0.06 & 0.01 & \\
+ & 2 & Challenge & 0.12 &  & \\
+ &  & Resource & -0.06 &  & \\
+ &  & Challenge X Resource & 0.02 & 0.01 & 0.00\\
+Burnout & 1 & Challenge & 0.28 ** &  & \\
+ &  & Resource & -0.12 & 0.04 ** & \\
+ & 2 & Challenge & 0.28 ** &  & \\
+ &  & Resource & -0.12 &  & \\
+ &  & Challenge X Resource & 0.05 & 0.04 ** & 0.00\\
 \bottomrule
@@
  &  & Resource & 0.35 ** & 0.17 ** & \\
- & 2 & Hindrance X Resource & -0.01 & 0.17 ** & 0.00\\
+ & 2 & Hindrance & -0.10 ** &  & \\
+ &  & Resource & 0.34 ** &  & \\
+ &  & Hindrance X Resource & -0.01 & 0.17 ** & 0.00\\
 Stress & 1 & Hindrance & 0.08 * &  & \\
- &  & Resource & 0.01 ** & 0.01 * & \\
- & 2 & Hindrance X Resource & -0.17 ** & 0.04 ** & 0.03 **\\
+ &  & Resource & 0.01 & 0.01 * & \\
+ & 2 & Hindrance & 0.16 ** &  & \\
+ &  & Resource & -0.10 &  & \\
+ &  & Hindrance X Resource & -0.17 ** & 0.04 ** & 0.03 **\\
 Burnout & 1 & Hindrance & 0.09 * &  & \\
- &  & Resource & 0.1 * & 0.04 ** & \\
- & 2 & Hindrance X Resource & -0.11 ** & 0.05 ** & 0.01 **\\
+ &  & Resource & 0.10 * & 0.04 ** & \\
+ & 2 & Hindrance & 0.13 * &  & \\
+ &  & Resource & 0.03 &  & \\
+ &  & Hindrance X Resource & -0.11 ** & 0.05 ** & 0.01 **\\
 \bottomrule

### 2024-07-16 Submission.Rmd
relabeling figures (interactions)

@@
 cr_eng_plot <- interact_plot(cr_eng_m3u, pred = overall.challenge_center, modx = overall.resource_center, interval = FALSE,
-              int.width = 0.8)
+              int.width = 0.8, x.label = "Challenge", legend.main = "Resource", y.label = "Engagement")
 cr_eng_plot
@@
 hr_stress_plot <- interact_plot(hr_stress_m3u, pred = overall.hindrance_center, modx = overall.resource_center, interval = FALSE, 
-              int.width = 0.8)
+              int.width = 0.8, x.label = "Hindrance", legend.main = "Resource", y.label = "Stress")
 hr_stress_plot
@@
 hr_burn_plot <- interact_plot(hr_burn_m3u, pred = overall.hindrance_center, modx = overall.resource_center, interval = FALSE, 
-              int.width = 0.8)
+              int.width = 0.8, x.label = "Hindrance", legend.main = "Resource", y.label = "Burnout")
 hr_burn_plot

### 2024-07-16 Submission.tex
relabeling figures (interactions)

@@
 
-\hypertarget{refs}{}
+\phantomsection\label{refs}
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-abbas2019challenge}{}}%
+\bibitem[\citeproctext]{ref-abbas2019challenge}
 Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
+\bibitem[\citeproctext]{ref-bakker2014job}
 Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
+\bibitem[\citeproctext]{ref-bakker2017job}
 Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2005job}{}}%
+\bibitem[\citeproctext]{ref-bakker2005job}
 Bakker, A. B., Demerouti, E., \& Euwema, M. C. (2005). Job resources buffer the impact of job demands on burnout. \emph{Journal of Occupational Health Psychology}, \emph{10}(2), 170.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2007job}{}}%
+\bibitem[\citeproctext]{ref-bakker2007job}
 Bakker, A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
+\bibitem[\citeproctext]{ref-bakker2013weekly}
 Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
 
-\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
+\bibitem[\citeproctext]{ref-cavanaugh2000empirical}
 Cavanaugh, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
+\bibitem[\citeproctext]{ref-demerouti2001job}
 Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
 
-\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
+\bibitem[\citeproctext]{ref-gerich2017relevance}
 Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
 
-\leavevmode\vadjust pre{\hypertarget{ref-hakanen2008job}{}}%
+\bibitem[\citeproctext]{ref-hakanen2008job}
 Hakanen, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-horan2020review}{}}%
+\bibitem[\citeproctext]{ref-horan2020review}
 Horan, K.

### 2024-07-18 Submission.Rmd
updating intro

@@
 
-The second set of analyses focuses on predicted associations without relevant work-relevant outcomes frequently studied across via job demands-resources- [@bakker2017job] and challenge-hindrance stressor-frameworks [@cavanaugh2000empirical].
+The second set of predictions focuses on associations with work-relevant outcomes frequently studied across via job demands-resources- [@bakker2017job] and challenge-hindrance stressor-frameworks [@cavanaugh2000empirical].
 Here, we specifically explore appraisals of O\*Net-derived work characteristics as resources, challenges, and/or hindrances in association with engagement, strain and burnout.
@@
 We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout.
-Beginning with resources, @hakanen2008job found job resources influenced future work engagement.
+Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job], and empirical work suggests that they are associated with positive outcomes.
+Relevant to the current study, for example, @hakanen2008job found job resources influenced future work engagement.
 Moreover, in a sample of teachers and dentists, @bakker2007job found that resources were most predictive of engagement when job demands were especially high.
+Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement [e.g., @schaufeli2017applying].
 
@@
 
->Hypothesis 3a: Engagement is predicted by resources and challenges.
-
->Hypothesis 3b: Strain and burnout are differentially predicted by challenges and hindrances.
-**Take a look at significant difference between slope coefficients (b's) of, for example, challenge-->strain & hindrance-->strain**
+>Hypothesis 3a: Resources and challenges positively predict engagement.
+
+>Hypothesis 3b: Although both challenge and hindrance demands positively predict stress and burnout, hindrance demands are a stronger predictor of both stress and burnout.
 
@@
 $R^2$ =  `r round(summary(cr_eng_m2)$adj.r.squared, 2)`, `r cr_eng_info2$statistic$modelfit$r2`.
-H3A DESCRIPTION HERE: resource slope is significant, challenge is not significant.
+H3A predicted that both resources and challenges would predict engagement.
+Here, the resource slope is significant, wheras the challenge slope is not significant (providing partial support for H3a).
 The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r cr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_eng_r_square_change`, $\Delta F$ (`r cr_eng_anova$Df[2]`, `r cr_eng_anova$Res.Df[2]`) = `r cr_eng_anova$F[2]`,  and thus provides statistical support for the presence of moderation.

### 2024-07-18 Submission.tex
updating intro

@@
 
-The second set of analyses focuses on predicted associations without relevant work-relevant outcomes frequently studied across via job demands-resources- (Bakker \& Demerouti, 2017) and challenge-hindrance stressor-frameworks (Cavanaugh et al., 2000).
+The second set of predictions focuses on associations with work-relevant outcomes frequently studied across via job demands-resources- (Bakker \& Demerouti, 2017) and challenge-hindrance stressor-frameworks (Cavanaugh et al., 2000).
 Here, we specifically explore appraisals of O*Net-derived work characteristics as resources, challenges, and/or hindrances in association with engagement, strain and burnout.
@@
 We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout.
-Beginning with resources, Hakanen et al.
+Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017), and empirical work suggests that they are associated with positive outcomes.
+Relevant to the current study, for example, Hakanen et al.
 (2008) found job resources influenced future work engagement.
@@
 (2007) found that resources were most predictive of engagement when job demands were especially high.
+Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement (e.g., Schaufeli, 2017).
 
@@
 \begin{quote}
-Hypothesis 3a: Engagement is predicted by resources and challenges.
+Hypothesis 3a: Resources and challenges positively predict engagement.
 \end{quote}
@@
 \begin{quote}
-Hypothesis 3b: Strain and burnout are differentially predicted by challenges and hindrances.
-\textbf{Take a look at significant difference between slope coefficients (b's) of, for example, challenge--\textgreater strain \& hindrance--\textgreater strain}
+Hypothesis 3b: Although both challenge and hindrance demands positively predict stress and burnout, hindrance demands are a stronger predictor of both stress and burnout.
 \end{quote}
@@
 \(R^2\) = 0.15, \(F(2, 565) = 50.09\), \(p < .001\).
-H3A DESCRIPTION HERE: resource slope is significant, challenge is not significant.
+H3A predicted that both resources and challenges would predict engagement.
+Here, the resource slope is significant, wheras the challenge slope is not significant (providing partial support for H3a).
 The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 35.62\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation.
@@
 
+\bibitem[\citeproctext]{ref-schaufeli2017applying}
+Schaufeli, W. B. (2017). Applying the job demands-resources model: A `how to'guide to measuring and tackling work engagement and burnout. \emph{Organizational Dynamics}, \emph{46}(2), 120--132.
+
 \bibitem[\citeproctext]{ref-searle2015merits}

### 2024-07-19 Submission.Rmd
gutting results

@@
 
->Hypothesis 3b: Although both challenge and hindrance demands positively predict stress and burnout, hindrance demands are a stronger predictor of both stress and burnout.
+>Hypothesis 3b: Both challenge and hindrance demands positively predict stress and burnout.
 
@@
 #ggplot(resource, aes(x=sd)) + geom_histogram()
-ggplot(toplottogether, aes(x=sd)) + geom_histogram() + facet_grid(RD ~ .)
+ggplot(toplottogether, aes(x=sd)) + geom_histogram() + facet_grid(RD ~ .) + labs(x = "Standard Deviation")
 
@@
 We explore this hypothesis first at the job characteristic level before presenting a broader perspective.
-Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present only extreme snapshots of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency.
+Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present only extreme snapshots of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative most and least consistency.
 Figure \@ref(fig:combinegraphs) presents the resources, challenges, and hindrances that are *most consistently agreed on* as indexed by (relatively) low standard deviations, while Figure \@ref(fig:combinegraphs2) presents the characteristics with the greatest amount of *disagreement* across workers.
-The figures demonstrate that what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
+The figures demonstrate that what is perceived as resource and challenge tends to be somewhat agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
 However, there is considerably less relative agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`).
@@
 
-In addition to highlighting extremely agreed- or disagreed-upon items, Figure \@ref(fig:overallhist) presents our standard deviation indices across all rated items.
-Here, the Figure \@ref(fig:combinegraphs) discrepancies receive greater context, with the *spread* of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively *bunched* levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
+In addition to highlighting extremely agreed- or disagreed-upon characteristics, Figure \@ref(fig:overallhist) presents our standard deviation indices across all rated items.
+Here, discrepancies receive greater context, with the *spread* of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively *bunched* levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
 Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
@@
 When people perceived hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.
-Taken with the Figure \@ref(fig:scalelevelgraphs) takeaway, this hints that workers are likely either generally experiencing hindrances at work or they are not.
 
@@
 library("gridExtra")
-grid.arrange(a, b, ncol = 2, nrow = 1)
+#grid.arrange(a, b, ncol = 2, nrow = 1)
 
@@
 ```
-We next explored whether there was statistical support for the hypothesis that the relationship between the challenge stressors and outcomes (i.e., engagement, stress, and burnout) were moderated by resources.
-In order to test for the presence of an interactive effect, a series of hierarchical regressions were conducted with challenge stressors and resources added in step one of the model and an interaction term, challenge stressors*resources, added in step two of the model.
+### Challenges, Resources, and Outcomes
 
@@
 
-Table \@ref(tab:chal-resource-table) summarizes the results.
-Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions.
+H3A predicted that both resources and challenges would predict engagement.
+Table \@ref(tab:chal-resource-table) summarizes the results for engagement (as well as stress and burnout).
+Sum scores for the predictors were used here such that the overall amount of resource or demand is recognized, and these predictor variables were mean centered prior to running the regressions.
 First, challenges and resources explained a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(cr_eng_m2)$r.squared, 2)`, Adj.
 $R^2$ =  `r round(summary(cr_eng_m2)$adj.r.squared, 2)`, `r cr_eng_info2$statistic$modelfit$r2`.
-H3A predicted that both resources and challenges would predict engagement.
 Here, the resource slope is significant, wheras the challenge slope is not significant (providing partial support for H3a).
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r cr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_eng_r_square_change`, $\Delta F$ (`r cr_eng_anova$Df[2]`, `r cr_eng_anova$Res.Df[2]`) = `r cr_eng_anova$F[2]`,  and thus provides statistical support for the presence of moderation.
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r cr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_eng_r_square_change`, $\Delta F$ (`r cr_eng_anova$Df[2]`, `r cr_eng_anova$Res.Df[2]`) = `r cr_eng_anova$F[2]`,  and thus provides statistical support for the presence of moderation (Hypothesis 4a).
 Figure \@ref(fig:chal-resource-int) illustrates the interaction.
@@
 
-Next, challenge stressors and resources did not explain a significant amount of the variance in stress,  $R^2$ = `r round(summary(cr_stress_m2)$r.squared, 2)`, Adj.
-$R^2$ =  `r round(summary(cr_stress_m2)$adj.r.squared, 2)`, `r cr_stress_info2$statistic$modelfit$r2`.
+Next, challenge demands and resources did not explain a significant amount of the variance in stress,  $R^2$ = `r round(summary(cr_stress_m2)$r.squared, 2)`, Adj.
+$R^2$ =  `r round(summary(cr_stress_m2)$adj.r.squared, 2)`, `r cr_stress_info2$statistic$modelfit$r2`, failing to provide support for Hypothesis 3b.
 The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, `r cr_stress_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_stress_r_square_change`, $\Delta F$ (`r cr_stress_anova$Df[2]`, `r cr_stress_anova$Res.Df[2]`) = `r cr_stress_anova$F[2]`, and thus does not support the presence of moderation.
 
-Finally, challenge stressors and resources explained a statsically significant amount of the variability in burnout, $R^2$ = `r round(summary(cr_burn_m2)$r.squared, 2)`, Adj.
+Finally, challenge demands and resources explained a statistically significant amount of the variability in burnout, $R^2$ = `r round(summary(cr_burn_m2)$r.squared, 2)`, Adj.
 $R^2$ =  `r round(summary(cr_burn_m2)$adj.r.squared, 2)`, `r cr_burn_info2$statistic$modelfit$r2`.
-The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, `r cr_burn_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_burn_r_square_change`, $\Delta F$ (`r cr_burn_anova$Df[2]`, `r cr_burn_anova$Res.Df[2]`) = `r cr_burn_anova$F[2]`,  and thus failing to provide statistical support for the presence of moderation.
-In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge stressors and the outcomes of strain and burnout.
+The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, `r cr_burn_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_burn_r_square_change`, $\Delta F$ (`r cr_burn_anova$Df[2]`, `r cr_burn_anova$Res.Df[2]`) = `r cr_burn_anova$F[2]`,  and thus failing to provide statistical support for the presence of moderation (Hypothesis 4a).
+In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge demands and the outcomes of strain and burnout.
 
@@
 ```
-
-We also explored whether there was an interaction between hindrance stressors and resources on the outcomes (i.e., engagement, stress, and burnout).
-A second group of hierarchical regressions were conducted with hindrance stressors and resources added in step one of the model and an interaction term, hindrance stressors x resources, added in step two of the model.
-See Table \@ref(tab:hind-resource-table).
-
-Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions.
-First, hindrance stressors and resources explained a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(hr_eng_m2)$r.squared, 2)`, Adj.
-$R^2$ =  `r round(summary(hr_eng_m2)$adj.r.squared, 2)`, `r hr_eng_info2$statistic$modelfit$r2`.
+### Hindrances, Resources, and Outcomes
+
+We also explored whether there was an interaction between hindrance demands and resources on the outcome variables.
+Sum scores for the predictors were used here again, and predictor variables were mean centered prior to running the regressions.
+First, hindrance demands and resources explained a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(hr_eng_m2)$r.squared, 2)`, Adj.
+$R^2$ =  `r round(summary(hr_eng_m2)$adj.r.squared, 2)`, `r hr_eng_info2$statistic$modelfit$r2` [see Table \@ref(tab:hind-resource-table)].
 The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, `r hr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_eng_r_square_change`, $\Delta F$ (`r hr_eng_anova$Df[2]`, `r hr_eng_anova$Res.Df[2]`) = `r hr_eng_anova$F[2]`.
@@
 
-Next exploring stress, hindrance stressors and resources explained a statistically significant amount of the variability in stress, $R^2$ = `r round(summary(hr_stress_m2)$r.squared, 2)`, Adj.
+Next exploring stress, hindrance demands and resources explained a statistically significant amount of the variability in stress, $R^2$ = `r round(summary(hr_stress_m2)$r.squared, 2)`, Adj.
 $R^2$ =  `r round(summary(hr_stress_m2)$adj.r.squared, 2)`, `r hr_stress_info2$statistic$modelfit$r2`.
@@
 See Figure \@ref(fig:hind-resource-stress-int).
-As expected, the relationship between hindrance stressors and strain becomes weaker as workers perceive more resources.
-
-Similarly, hindrance stressors and resources explained a statistically significant amount of the variability in burnout, $R^2$ = `r round(summary(hr_burn_m2)$r.squared, 2)`, Adj.
+As expected, the relationship between hindrance demands and strain becomes weaker as workers perceive more resources.
+
+Similarly, hindrance demands and resources explained a statistically significant amount of the variability in burnout, $R^2$ = `r round(summary(hr_burn_m2)$r.squared, 2)`, Adj.
 $R^2$ =  `r round(summary(hr_burn_m2)$adj.r.squared, 2)`, `r hr_burn_info2$statistic$modelfit$r2`.
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r hr_burn_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_burn_r_square_change`, $\Delta F$ (`r hr_burn_anova$Df[2]`, `r hr_burn_anova$Res.Df[2]`) = `r hr_burn_anova$F[2]`, supporting the presence of a moderated effect.
-Again, see Figure \@ref(fig:hind-resource-burn-int).
-As expected, the relationship between hindrance stressors and burnout becomes weaker as workers perceive more resources.
-
-Summatively these findings provide support for the assertion that resources would moderate the relationships between hindrance stressors and the outcomes of strain and burnout.
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r hr_burn_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_burn_r_square_change`, $\Delta F$ (`r hr_burn_anova$Df[2]`, `r hr_burn_anova$Res.Df[2]`) = `r hr_burn_anova$F[2]`, supporting the presence of a moderated effect [see Figure \@ref(fig:hind-resource-burn-int)].
+As expected, the relationship between hindrance demands and burnout becomes weaker as workers perceive more resources.
+Summatively these findings provide support for the assertion that resources would moderate the relationships between hindrance demands and the outcomes of strain and burnout.
 
@@
 ```
-
-In addition to the two hypotheses, two sets of exploratory analyses were also pursued: 1) do literature-implicated resources materialize as perceived resources and 2) do literature-implicated demands materialize as perceived demands?
-To answer these questions, authors first categorized O\*Net items into the elements listed in the JD-R literature.
-For example, autonomy is frequently described as a resource.
-An O\*Net item is, “How much decision making freedom, without supervision, does your job offer?”.
-This O\*Net item was retained within the "autonomy" category.
-Mean ratings of the O\*Net items were then computed by element (e.g., all of the items representing autonomy) to explore whether literature-implicated resources and demands were evaluated as such.
-
-Figure \@ref(fig:scalelevelgraphs) presents these comparisons visually, where the bar lengths represent mean ratings within element category (e.g., the white bar represents mean O\*Net resource ratings for a given JD-R element).
-First exploring the right side of Figure \@ref(fig:scalelevelgraphs), there is a pattern of the highest level ratings being those of literature-derived resources (e.g., job control).
-As described above, the left side of Figure \@ref(fig:scalelevelgraphs) shows literature-derived demand categories (e.g., work pressure).
-However, in contrast, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as "high" gray and black bars and "low" white bars).
-In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be "hindrances" at work.
-
-Repeated-measures ANOVAs were computed to further explain each of the patterns observed descriptively in Figure \@ref(fig:scalelevelgraphs).
-The effect for Job Control was $F_{(`r report7$ANOVA$DFn`, `r report7$ANOVA$DFd`)}$ = `r report7$ANOVA$F` ($\eta^2$ = `r report7$ANOVA$pes`).
-The effect for Participation was $F_{(`r report8$ANOVA$DFn`, `r report8$ANOVA$DFd`)}$ = `r report8$ANOVA$F` ($\eta^2$ = `r report8$ANOVA$pes`).
-The effect for Autonomy was $F_{(`r report9$ANOVA$DFn`, `r report9$ANOVA$DFd`)}$ = `r report9$ANOVA$F` ($\eta^2$ = `r report9$ANOVA$pes`).
-The effect for Team Cohesion was $F_{(`r report10$ANOVA$DFn`, `r report10$ANOVA$DFd`)}$ = `r report10$ANOVA$F` ($\eta^2$ = `r report10$ANOVA$pes`).
-Statistical significance was less than .001 for all four category comparisons.
-Here, the pattern was as expected.
-Across categories, resources were rated the highest (see white bars representing resources in Figure \@ref(fig:scalelevelgraphs)).
-However, as can be seen, mean challenge (which is a demand) was rated quite similarly and above the midpoint of 3 across JD-R categories.
-In fact, the means were nearly identical for resource and challenge ratings for all for categories.
-The literature-implied category with the lowest resource rating also has the highest hindrance rating, so job control is positive and negative.
-
-Next, repeated-measures ANOVAs were also run for the group of literature-implicated *demands* (see the left hand side of Figure \@ref(fig:scalelevelgraphs)).
-The effect for Overwork was $F_{(`r report1$ANOVA$DFn`, `r report1$ANOVA$DFd`)}$ = `r report1$ANOVA$F` ($\eta^2$ was `r report1$ANOVA$pes`).
-The effect for Physical Environment was $F_{(`r report2$ANOVA$DFn`, `r report2$ANOVA$DFd`)}$ = `r report2$ANOVA$F` ($\eta^2$ = `r report2$ANOVA$pes`).
-The effect for `Time Pressure` was $F_{(`r report3$ANOVA$DFn`, `r report3$ANOVA$DFd`)}$ = `r report3$ANOVA$F` ($\eta^2$ = `r report3$ANOVA$pes`).
-The effect for Emotional Demands was $F_{(`r report4$ANOVA$DFn`, `r report4$ANOVA$DFd`)}$ = `r report4$ANOVA$F` ($\eta^2$ = `r report4$ANOVA$pes`).
-The effect for Recipient Contact was $F_{(`r report5$ANOVA$DFn`, `r report5$ANOVA$DFd`)}$ = `r report5$ANOVA$F` ($\eta^2$ = `r report5$ANOVA$pes`).
-The effect for Work Pressure was $F_{(`r report6$ANOVA$DFn`, `r report6$ANOVA$DFd`)}$ = `r report6$ANOVA$F` ($\eta^2$ = `r report6$ANOVA$pes`).
-In all cases, statistical significance was less then .001.
-However, the findings revealed that what the literature implicates as a demand was actually evaluated as a *resource* (all resource means are above the midpoint).
-This is contrary to the expectation that ratings would match our assumption of what a demand constitutes.
-Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance.
-See the pattern of white resource bars on the left hand side of Figure \@ref(fig:scalelevelgraphs).
-In other words, demands are viewed as resources.
-In sum, these results provide some support for RQ 1 and 2.
 

### 2024-07-19 Submission.tex
gutting results

@@
 \begin{quote}
-Hypothesis 3b: Although both challenge and hindrance demands positively predict stress and burnout, hindrance demands are a stronger predictor of both stress and burnout.
+Hypothesis 3b: Both challenge and hindrance demands positively predict stress and burnout.
 \end{quote}
@@
 Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present only extreme snapshots of characteristic variability in the form of the 8-most \emph{consistently rated} and \emph{inconsistently rated} resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
-The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative greatest and least consistency.
+The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative most and least consistency.
 Figure \ref{fig:combinegraphs} presents the resources, challenges, and hindrances that are \emph{most consistently agreed on} as indexed by (relatively) low standard deviations, while Figure \ref{fig:combinegraphs2} presents the characteristics with the greatest amount of \emph{disagreement} across workers.
-The figures demonstrate that what is widely seen as a resource and challenge tends to be somewhat agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
+The figures demonstrate that what is perceived as resource and challenge tends to be somewhat agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
 However, there is considerably less relative agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16).
 
-In addition to highlighting extremely agreed- or disagreed-upon items, Figure \ref{fig:overallhist} presents our standard deviation indices across all rated items.
-Here, the Figure \ref{fig:combinegraphs} discrepancies receive greater context, with the \emph{spread} of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively \emph{bunched} levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
+In addition to highlighting extremely agreed- or disagreed-upon characteristics, Figure \ref{fig:overallhist} presents our standard deviation indices across all rated items.
+Here, discrepancies receive greater context, with the \emph{spread} of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively \emph{bunched} levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
 Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
@@
 When people perceived hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.
-Taken with the Figure \ref{fig:scalelevelgraphs} takeaway, this hints that workers are likely either generally experiencing hindrances at work or they are not.
 
@@
 
-\begin{figure}
-\centering
-\includegraphics{Submission_files/figure-latex/scalelevelgraphs-1.pdf}
-\caption{\label{fig:scalelevelgraphs}Average characteristic rating grouped by literature-implicated categorizations.}
-\end{figure}
-
-We next explored whether there was statistical support for the hypothesis that the relationship between the challenge stressors and outcomes (i.e., engagement, stress, and burnout) were moderated by resources.
-In order to test for the presence of an interactive effect, a series of hierarchical regressions were conducted with challenge stressors and resources added in step one of the model and an interaction term, challenge stressors*resources, added in step two of the model.
+\subsubsection{Challenges, Resources, and Outcomes}\label{challenges-resources-and-outcomes}
 
@@
 
-Table \ref{tab:chal-resource-table} summarizes the results.
-Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions.
+H3A predicted that both resources and challenges would predict engagement.
+Table \ref{tab:chal-resource-table} summarizes the results for engagement (as well as stress and burnout).
+Sum scores for the predictors were used here such that the overall amount of resource or demand is recognized, and these predictor variables were mean centered prior to running the regressions.
 First, challenges and resources explained a statistically significant amount of the variability in engagement, \(R^2\) = 0.15, Adj.
 \(R^2\) = 0.15, \(F(2, 565) = 50.09\), \(p < .001\).
-H3A predicted that both resources and challenges would predict engagement.
 Here, the resource slope is significant, wheras the challenge slope is not significant (providing partial support for H3a).
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 35.62\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation.
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 35.62\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation (Hypothesis 4a).
 Figure \ref{fig:chal-resource-int} illustrates the interaction.
@@
 
-Next, challenge stressors and resources did not explain a significant amount of the variance in stress, \(R^2\) = 0.01, Adj.
-\(R^2\) = 0, \(F(2, 565) = 1.67\), \(p = .189\).
+Next, challenge demands and resources did not explain a significant amount of the variance in stress, \(R^2\) = 0.01, Adj.
+\(R^2\) = 0, \(F(2, 565) = 1.67\), \(p = .189\), failing to provide support for Hypothesis 3b.
 The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 1.17\), \(p = .320\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 0.17, and thus does not support the presence of moderation.
 
-Finally, challenge stressors and resources explained a statsically significant amount of the variability in burnout, \(R^2\) = 0.04, Adj.
+Finally, challenge demands and resources explained a statistically significant amount of the variability in burnout, \(R^2\) = 0.04, Adj.
 \(R^2\) = 0.04, \(F(2, 565) = 1.67\), \(p = .189\).
-The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 1.17\), \(p = .320\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 2.25, and thus failing to provide statistical support for the presence of moderation.
-In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge stressors and the outcomes of strain and burnout.
+The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 1.17\), \(p = .320\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 2.25, and thus failing to provide statistical support for the presence of moderation (Hypothesis 4a).
+In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge demands and the outcomes of strain and burnout.
 
@@
 
-We also explored whether there was an interaction between hindrance stressors and resources on the outcomes (i.e., engagement, stress, and burnout).
-A second group of hierarchical regressions were conducted with hindrance stressors and resources added in step one of the model and an interaction term, hindrance stressors x resources, added in step two of the model.
-See Table \ref{tab:hind-resource-table}.
+\subsubsection{Hindrances, Resources, and Outcomes}\label{hindrances-resources-and-outcomes}
 
-Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions.
-First, hindrance stressors and resources explained a statistically significant amount of the variability in engagement, \(R^2\) = 0.17, Adj.
-\(R^2\) = 0.16, \(F(2, 565) = 55.90\), \(p < .001\).
+We also explored whether there was an interaction between hindrance demands and resources on the outcome variables.
+Sum scores for the predictors were used here again, and predictor variables were mean centered prior to running the regressions.
+First, hindrance demands and resources explained a statistically significant amount of the variability in engagement, \(R^2\) = 0.17, Adj.
+\(R^2\) = 0.16, \(F(2, 565) = 55.90\), \(p < .001\) {[}see Table \ref{tab:hind-resource-table}{]}.
 The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 37.25\), \(p < .001\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 0.13.
@@
 
-Next exploring stress, hindrance stressors and resources explained a statistically significant amount of the variability in stress, \(R^2\) = 0.01, Adj.
+Next exploring stress, hindrance demands and resources explained a statistically significant amount of the variability in stress, \(R^2\) = 0.01, Adj.
 \(R^2\) = 0.01, \(F(2, 565) = 3.13\), \(p = .045\).
@@
 See Figure \ref{fig:hind-resource-stress-int}.
-As expected, the relationship between hindrance stressors and strain becomes weaker as workers perceive more resources.
+As expected, the relationship between hindrance demands and strain becomes weaker as workers perceive more resources.
 
-Similarly, hindrance stressors and resources explained a statistically significant amount of the variability in burnout, \(R^2\) = 0.04, Adj.
+Similarly, hindrance demands and resources explained a statistically significant amount of the variability in burnout, \(R^2\) = 0.04, Adj.
 \(R^2\) = 0.03, \(F(2, 565) = 10.68\), \(p < .001\).
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 9.49\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 6.89, supporting the presence of a moderated effect.
-Again, see Figure \ref{fig:hind-resource-burn-int}.
-As expected, the relationship between hindrance stressors and burnout becomes weaker as workers perceive more resources.
-
-Summatively these findings provide support for the assertion that resources would moderate the relationships between hindrance stressors and the outcomes of strain and burnout.
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 9.49\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 6.89, supporting the presence of a moderated effect {[}see Figure \ref{fig:hind-resource-burn-int}{]}.
+As expected, the relationship between hindrance demands and burnout becomes weaker as workers perceive more resources.
+Summatively these findings provide support for the assertion that resources would moderate the relationships between hindrance demands and the outcomes of strain and burnout.
 
@@
 \end{figure}
-
-In addition to the two hypotheses, two sets of exploratory analyses were also pursued: 1) do literature-implicated resources materialize as perceived resources and 2) do literature-implicated demands materialize as perceived demands?
-To answer these questions, authors first categorized O*Net items into the elements listed in the JD-R literature.
-For example, autonomy is frequently described as a resource.
-An O*Net item is, ``How much decision making freedom, without supervision, does your job offer?''.
-This O*Net item was retained within the ``autonomy'' category.
-Mean ratings of the O*Net items were then computed by element (e.g., all of the items representing autonomy) to explore whether literature-implicated resources and demands were evaluated as such.
-
-Figure \ref{fig:scalelevelgraphs} presents these comparisons visually, where the bar lengths represent mean ratings within element category (e.g., the white bar represents mean O*Net resource ratings for a given JD-R element).
-First exploring the right side of Figure \ref{fig:scalelevelgraphs}, there is a pattern of the highest level ratings being those of literature-derived resources (e.g., job control).
-As described above, the left side of Figure \ref{fig:scalelevelgraphs} shows literature-derived demand categories (e.g., work pressure).
-However, in contrast, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as ``high'' gray and black bars and ``low'' white bars).
-In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be ``hindrances'' at work.
-
-Repeated-measures ANOVAs were computed to further explain each of the patterns observed descriptively in Figure \ref{fig:scalelevelgraphs}.
-The effect for Job Control was \(F_{(2, 1134)}\) = 52.78 (\(\eta^2\) = 0.08).
-The effect for Participation was \(F_{(2, 1124)}\) = 991.16 (\(\eta^2\) = 0.64).
-The effect for Autonomy was \(F_{(2, 1074)}\) = 951.90 (\(\eta^2\) = 0.64).
-The effect for Team Cohesion was \(F_{(2, 1120)}\) = 853.39 (\(\eta^2\) = 0.60).
-Statistical significance was less than .001 for all four category comparisons.
-Here, the pattern was as expected.
-Across categories, resources were rated the highest (see white bars representing resources in Figure \ref{fig:scalelevelgraphs}).
-However, as can be seen, mean challenge (which is a demand) was rated quite similarly and above the midpoint of 3 across JD-R categories.
-In fact, the means were nearly identical for resource and challenge ratings for all for categories.
-The literature-implied category with the lowest resource rating also has the highest hindrance rating, so job control is positive and negative.
-
-Next, repeated-measures ANOVAs were also run for the group of literature-implicated \emph{demands} (see the left hand side of Figure \ref{fig:scalelevelgraphs}).
-The effect for Overwork was \(F_{(2, 1134)}\) = 17.71 (\(\eta^2\) was 0.03).
-The effect for Physical Environment was \(F_{(2, 1108)}\) = 112.97 (\(\eta^2\) = 0.17).
-The effect for \texttt{Time\ Pressure} was \(F_{(2, 1090)}\) = 82.22 (\(\eta^2\) = 0.13).
-The effect for Emotional Demands was \(F_{(2, 1098)}\) = 393.43 (\(\eta^2\) = 0.42).
-The effect for Recipient Contact was \(F_{(2, 1126)}\) = 1,031.73 (\(\eta^2\) = 0.65).
-The effect for Work Pressure was \(F_{(2, 1132)}\) = 718.12 (\(\eta^2\) = 0.56).
-In all cases, statistical significance was less then .001.
-However, the findings revealed that what the literature implicates as a demand was actually evaluated as a \emph{resource} (all resource means are above the midpoint).
-This is contrary to the expectation that ratings would match our assumption of what a demand constitutes.
-Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance.
-See the pattern of white resource bars on the left hand side of Figure \ref{fig:scalelevelgraphs}.
-In other words, demands are viewed as resources.
-In sum, these results provide some support for RQ 1 and 2.
 

### 2024-07-24 Submission.Rmd
one edit to intro made
Finished Discussion Updates and Abstract

@@
   Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands.
-This study documents variability in subjective ratings of job characteristics with respect to interpretation as resource and demand.
-Next, we quantify the degree to which perceptions match the literature-implicated resources/demands of job characteristics and also document associations with stress, burnout, and engagement.
-Job characteristics were not commonly categorized as solely resource or demand.
-Rather, job resources were also frequently viewed as challenging demands.
-OUTCOME VARIABLE INFORMATION HERE.
+This study documents variability in subjective ratings of O\*Net job characteristics with respect to interpretation as resource and demand (defined as challenge/hindrance), and further predicts demands and resources will be differentially related to outcomes of engagement, stress, and burnout.
+We lastly explore the moderating role of resources.
+We found that job characteristics were not uniquely categorized as a resource or demand, but rather, some job characteristics were rated highly as both a resource and a demand.
+We consistently observed a pattern of job characteristics seen as challenging also being cited as a resource.
+While we did not find support for the prediction, that demands were differentially related to stress and burnout, we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships as predicted.
+The findings broadly revealed that there was relatively more consistency in ratings of resource and challenge characteristics, and far more variability in job characteristics rated as hindrance demands.
 These findings have implications for job design and management particularly with regard to resource-laden elements that may also be experienced as demanding.
@@
 We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges].
-Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) whether subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between stressors (challenge and hindrance) and outcomes.
+Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) whether subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and outcomes.
 To illuminate these questions, we consult the [O\*Net database](https://www.onetcenter.org/content.html), which provides a rich source of information about occupational requirements (i.e., work activities and context).
@@
 Both are considered stressors [e.g., @cavanaugh2000empirical].
-Challenge demands promote mastery, personal growth, and future gains – these stressors should lead to coping strategies that facilitate achievement.
+Challenge demands promote mastery, personal growth, and future gains – these demands should lead to coping strategies that facilitate achievement.
 Work characteristics consistent with this definition, for example, include time pressure and responsibility [@lepine2022challenge].
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Example hindrance stressors in a work context include role conflict and role ambiguity [@lepine2022challenge].
+Example hindrance demands in a work context include role conflict and role ambiguity [@lepine2022challenge].
 
@@
 
-The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes [e.g., @cavanaugh2000empirical].
+The original work on this topic suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes [e.g., @cavanaugh2000empirical].
 Meta-analytic explorations of this the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, @lepine2005meta regarding performance and @crawford2010linking regarding engagement).
@@
 @lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes.
-First, stressors appraised as challenges typically result in a more positive appraisal, and engagement is likely to happen as a result.
+First, demands appraised as challenges typically result in a more positive appraisal, and engagement is likely to happen as a result.
 Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing.
 Of note is that this energy may be depleted eventually, leading to strain.
-Stressors appraised as hindrances elicit a different process.
+demands appraised as hindrances elicit a different process.
 Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing.
@@
 Recent work affirms these appraisal processes.
-@pindek2024dynamic meta-analyzed diary studies of dynamic stressors (i.e., short-term daily experiences of stressors) and concluded that daily challenge stressors had a positive *direct* association with performance, but a negative *indirect* association with performance through strain (as described by @lepine2022challenge above).
-As expected, hindrance stressors had both direct and indirect (through strain) associations with performance [@pindek2024dynamic].
+@pindek2024dynamic meta-analyzed diary studies of dynamic demands (i.e., short-term daily experiences of demands) and concluded that daily challenge demands had a positive *direct* association with performance, but a negative *indirect* association with performance through strain (as described by @lepine2022challenge above).
+As expected, hindrance demands had both direct and indirect (through strain) associations with performance [@pindek2024dynamic].
 
@@
 @horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process described by @lazarus1984stress into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources.
-In fact, @horan2020review state that “…stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p.
+In fact, @horan2020review state that “…stressors are only challenge or hindrance demands to the extent that they are perceived as such by employees” (p.
 3).
-They go on to suggest future research continue to move away from *a priori* classifications of stressors, as doing so can be problematic for theoretical and empirical reasons.
+They go on to suggest future research continue to move away from *a priori* classifications of demands, as doing so can be problematic for theoretical and empirical reasons.
 Theoretically, *a priori* classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
@@
 As such, the first question we ask is whether people distinguish between resources, challenges, and  hindrances, and whether a job characteristics might even be considered simultaneously as more than one of these (e.g., both a challenge and a resource).
-Evidence suggests the employees do, in fact, differentiate between challenge and hindrance stressors [e.g., @bakker2013weekly; @gerich2017relevance; @webster2011extending], at least.
+Evidence suggests the employees do, in fact, differentiate between challenge and hindrance demands [e.g., @bakker2013weekly; @gerich2017relevance; @webster2011extending], at least.
 For example, @bakker2013weekly found that work pressure was perceived as a hindrance demand, and emotional demands as more of a challenge demand.
@@
 @chen2021daily found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment.
-Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance stressors [@podsakoff2007differential]].
+Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands [@podsakoff2007differential]].
 Interestingly, both challenges and hindrances have been shown to positively predict strain [(Abbas & Raja, 2019]@abbas2019challenge; @lepine2005meta; @podsakoff2007differential; @webster2010toward], which further highlights the complex association between appraisals and subsequent outcomes.
@@
 They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout.
-We extend the established job demands-resources model buffer proposition to both challenge and hindrance stressors (demands) as follows:
-
->Hypothesis 4a:Resources moderate the relationship between challenge stressors and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
-
->Hypothesis 4b:Resources moderate the relationship between hindrance stressors and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
+We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows:
+
+>Hypothesis 4a:Resources moderate the relationship between challenge demands and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
+
+>Hypothesis 4b:Resources moderate the relationship between hindrance demands and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
 
@@
 
-H3A predicted that both resources and challenges would predict engagement.
+H3a predicted that both resources and challenges would predict engagement.
 Table \@ref(tab:chal-resource-table) summarizes the results for engagement (as well as stress and burnout).
@@
 
-The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands (both challenge and hindrance), and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using the comprehensive taxonomy provided by O\*Net.
-The findings broadly revealed that there was relatively more consistency in ratings of resource and challenge characteristics, and far more variability in job characteristics rated as hindrance stressors.
+The major aims of this paper were to explore whether: 1) there was variability in subjective ratings of job characteristics as resources and demands, 2) some characteristics were more likely to vary across demand and resource, 3) subjective appraisals were differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and outcomes.
+We found that job characteristics were not uniquely categorized as a resource or demand, but rather, some job characteristics were rated highly as both a resource and a demand.
+We consistently observed a pattern of job characteristics seen as challenging also being cited as a resource.
+While we did not find support for the prediction, that demands were differentially related to stress and burnout, we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships as predicted.
+The findings broadly revealed that there was relatively more consistency in ratings of resource and challenge characteristics, and far more variability in job characteristics rated as hindrance demands.
 This finding lends additional evidence to @horan2020review’s conclusion that “...stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p.
 3).
-Lastly, we also found support for the hypothesis that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand (H2).
-Specifically, we consistently observed a pattern of job characteristics seen as challenging also being cited as a resource.
+
+In addition to the above findings, this paper made several additional important contributions.
+We utilized a diverse sample of employees across industries, who responded to common O\*Net items.
+While O\*Net provides detailed information about frequency and importance ratings among employees, we begin the process of expanding what we know of job characteristics to ratings of demands and resources.
+Further, we provide a repository for other researchers with listing of item level *perceived* demands and resources across activity and context items for the benefit of all future researchers.
+We also explored not only context and activity holistically, but at the dimension level, which enhances our knowledge of how employees perceive different categories of resources, challenges, and hindrances at work, as well as the relationships among them.
 
@@
 First, this research is couched within the well-studied job demands-resources theory [@demerouti2001job].
-We argue that while useful, additional emphasis should be placed on individual differences in perceptions of job characteristics.
+We argue that static assignment of characteristics as a demand or resource may be useful, additional emphasis should be placed on individual differences in perceptions of job characteristics.
 In fact, our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs [@webster2011extending].
 This finding aligns quite well with both the transactional theory of stress and coping, and the challenge-hindrance stressor framework, which collectively argue that employees perceive stimuli (i.e., job characteristics) uniquely [@lazarus1984stress], and thus, could appraise them as either a challenge or hindrance to their job performance [@cavanaugh2000empirical].
-Further, @cavanaugh2000empirical suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes [e.g., @cavanaugh2000empirical].
-
-Differences in outcomes depending on whether or not an employee perceives a job characteristic to be a challenge or hindrance has practical implications.
-Our results suggest that what is generally seen as a resource and challenge tends to be agreed upon moreso that what is seen a hindrance.
+Further, @cavanaugh2000empirical suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes [e.g., @cavanaugh2000empirical].
+
+Our results suggest that what is generally seen as a resource and challenge tends to be agreed upon more so that what is seen a hindrance.
 In fact, hindrance demands are rated more variably and thus, it may be important to have conversations about job characteristics and expectations at multiple time points after hire.
@@
 
+Resources did predict engagement, and did moderate several of the challenge-outcome, and hindrance-outcome relationships.
+As such, we provide further evidence of the importance of perceived resources, particularly when a job is high in hindrance demands, as resources acted as a buffer in both instances.
+It is worth noting that this paper focused on *perceived* resources, challenges, and hindrances.
+Differences in outcomes depending on whether or not an employee perceives a job characteristic to be a challenge or hindrance have practical implications especially for managers.
+Helping employees to manage expectations and frame the work is quite likely to shape how activities are appraised (e.g., as a challenge, or as a resource).
+Of course, in some instances, framing an activity or job context variable as an opportunity or positive aspect of work is unrealistic, and so interventions aimed at supporting employees (e.g., stress interventions) may be necessary.
+
 ## Limitations and Future Directions
-
-Cross-sectional
 
@@
 For example, O\*Net also includes styles and values, which we did not sample.
-Future studies may want to expand to explore these additional aspects of work.
+Future studies may want to expand to explore these additional aspects of work, and perhaps longitudinally.
 
@@
 It would also be prudent to consider work-relevant outcomes associated with similar job characteristic ratings.
+We also note that effect sizes were small and thus it is important to consider the practical significance when thinking about potential interventions.
+We encourage future thought on how consideration of resource and demand perceptions might be combined with additional levers to reduce employee stress and burnout, as well as enhance engagement.
 
@@
 
-In sum, this endeavor explored the job-demands-resources literature from a unique lens from within a universally accessible framework.
+## Conclusion
+
+In sum, this endeavor builds on the job-demands-resources, and challenge-hindrance stressor literature from a unique lens from within a universally accessible framework.
 We showed that there are far more individual differences in how employees perceive demands and resources than much of our current research suggests.
 While resources and challenges idiosyncratic more similarly experienced, what is experienced as a hindrance tends to be idiosyncratic.
+We further provide additional evidence highlighting the value of perceived resources in the workplace, as they were demonstrated to moderate both challenge-engagement, and hindrance-stress/hindrance burnout relationships as we would expect.
 

### 2024-07-24 Submission.tex
Finished Discussion Updates and Abstract

@@
 Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands.
-This study documents variability in subjective ratings of job characteristics with respect to interpretation as resource and demand.
-Next, we quantify the degree to which perceptions match the literature-implicated resources/demands of job characteristics and also document associations with stress, burnout, and engagement.
-Job characteristics were not commonly categorized as solely resource or demand.
-Rather, job resources were also frequently viewed as challenging demands.
-OUTCOME VARIABLE INFORMATION HERE.
+This study documents variability in subjective ratings of O*Net job characteristics with respect to interpretation as resource and demand (defined as challenge/hindrance), and further predicts demands and resources will be differentially related to outcomes of engagement, stress, and burnout.
+We lastly explore the moderating role of resources.
+We found that job characteristics were not uniquely categorized as a resource or demand, but rather, some job characteristics were rated highly as both a resource and a demand.
+We consistently observed a pattern of job characteristics seen as challenging also being cited as a resource.
+While we did not find support for the prediction, that demands were differentially related to stress and burnout, we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships as predicted.
+The findings broadly revealed that there was relatively more consistency in ratings of resource and challenge characteristics, and far more variability in job characteristics rated as hindrance demands.
 These findings have implications for job design and management particularly with regard to resource-laden elements that may also be experienced as demanding.
@@
 We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020).
-Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) whether subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between stressors (challenge and hindrance) and outcomes.
+Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) whether subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and outcomes.
 To illuminate these questions, we consult the \href{https://www.onetcenter.org/content.html}{O*Net database}, which provides a rich source of information about occupational requirements (i.e., work activities and context).
@@
 Both are considered stressors (e.g., Cavanaugh et al., 2000).
-Challenge demands promote mastery, personal growth, and future gains -- these stressors should lead to coping strategies that facilitate achievement.
+Challenge demands promote mastery, personal growth, and future gains -- these demands should lead to coping strategies that facilitate achievement.
 Work characteristics consistent with this definition, for example, include time pressure and responsibility (M.
@@
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Example hindrance stressors in a work context include role conflict and role ambiguity (M.
+Example hindrance demands in a work context include role conflict and role ambiguity (M.
 A.
@@
 
-The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes (e.g., Cavanaugh et al., 2000).
+The original work on this topic suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes (e.g., Cavanaugh et al., 2000).
 Meta-analytic explorations of this the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, J.
@@
 LePine (2022) explain the mechanisms by which demands are related to performance and wellbeing outcomes.
-First, stressors appraised as challenges typically result in a more positive appraisal, and engagement is likely to happen as a result.
+First, demands appraised as challenges typically result in a more positive appraisal, and engagement is likely to happen as a result.
 Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing.
 Of note is that this energy may be depleted eventually, leading to strain.
-Stressors appraised as hindrances elicit a different process.
+demands appraised as hindrances elicit a different process.
 Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing.
@@
 Pindek et al.
-(2024) meta-analyzed diary studies of dynamic stressors (i.e., short-term daily experiences of stressors) and concluded that daily challenge stressors had a positive \emph{direct} association with performance, but a negative \emph{indirect} association with performance through strain (as described by M.
+(2024) meta-analyzed diary studies of dynamic demands (i.e., short-term daily experiences of demands) and concluded that daily challenge demands had a positive \emph{direct} association with performance, but a negative \emph{indirect} association with performance through strain (as described by M.
 A.
 LePine (2022) above).
-As expected, hindrance stressors had both direct and indirect (through strain) associations with performance (Pindek et al., 2024).
+As expected, hindrance demands had both direct and indirect (through strain) associations with performance (Pindek et al., 2024).
 
@@
 In fact, Horan et al.
-(2020) state that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3).
-They go on to suggest future research continue to move away from \emph{a priori} classifications of stressors, as doing so can be problematic for theoretical and empirical reasons.
+(2020) state that ``\ldots stressors are only challenge or hindrance demands to the extent that they are perceived as such by employees'' (p.~3).
+They go on to suggest future research continue to move away from \emph{a priori} classifications of demands, as doing so can be problematic for theoretical and empirical reasons.
 Theoretically, \emph{a priori} classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
@@
 As such, the first question we ask is whether people distinguish between resources, challenges, and hindrances, and whether a job characteristics might even be considered simultaneously as more than one of these (e.g., both a challenge and a resource).
-Evidence suggests the employees do, in fact, differentiate between challenge and hindrance stressors (e.g., Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011), at least.
+Evidence suggests the employees do, in fact, differentiate between challenge and hindrance demands (e.g., Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011), at least.
 For example, Bakker and Sanz-Vergel (2013) found that work pressure was perceived as a hindrance demand, and emotional demands as more of a challenge demand.
@@
 (2021) found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment.
-Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance stressors (Podsakoff et al., 2007){]}.
+Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands (Podsakoff et al., 2007){]}.
 Interestingly, both challenges and hindrances have been shown to positively predict strain ((Abbas \& Raja, 2019 Abbas \& Raja, 2019; J.
@@
 They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout.
-We extend the established job demands-resources model buffer proposition to both challenge and hindrance stressors (demands) as follows:
+We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows:
 
 \begin{quote}
-Hypothesis 4a:Resources moderate the relationship between challenge stressors and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
+Hypothesis 4a:Resources moderate the relationship between challenge demands and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
 \end{quote}
@@
 \begin{quote}
-Hypothesis 4b:Resources moderate the relationship between hindrance stressors and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
+Hypothesis 4b:Resources moderate the relationship between hindrance demands and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
 \end{quote}
@@
 
-H3A predicted that both resources and challenges would predict engagement.
+H3a predicted that both resources and challenges would predict engagement.
 Table \ref{tab:chal-resource-table} summarizes the results for engagement (as well as stress and burnout).
@@
 
-The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands (both challenge and hindrance), and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using the comprehensive taxonomy provided by O*Net.
-The findings broadly revealed that there was relatively more consistency in ratings of resource and challenge characteristics, and far more variability in job characteristics rated as hindrance stressors.
+The major aims of this paper were to explore whether: 1) there was variability in subjective ratings of job characteristics as resources and demands, 2) some characteristics were more likely to vary across demand and resource, 3) subjective appraisals were differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and outcomes.
+We found that job characteristics were not uniquely categorized as a resource or demand, but rather, some job characteristics were rated highly as both a resource and a demand.
+We consistently observed a pattern of job characteristics seen as challenging also being cited as a resource.
+While we did not find support for the prediction, that demands were differentially related to stress and burnout, we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships as predicted.
+The findings broadly revealed that there was relatively more consistency in ratings of resource and challenge characteristics, and far more variability in job characteristics rated as hindrance demands.
 This finding lends additional evidence to Horan et al.
 (2020)'s conclusion that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3).
-Lastly, we also found support for the hypothesis that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand (H2).
-Specifically, we consistently observed a pattern of job characteristics seen as challenging also being cited as a resource.
+
+In addition to the above findings, this paper made several additional important contributions.
+We utilized a diverse sample of employees across industries, who responded to common O*Net items.
+While O*Net provides detailed information about frequency and importance ratings among employees, we begin the process of expanding what we know of job characteristics to ratings of demands and resources.
+Further, we provide a repository for other researchers with listing of item level \emph{perceived} demands and resources across activity and context items for the benefit of all future researchers.
+We also explored not only context and activity holistically, but at the dimension level, which enhances our knowledge of how employees perceive different categories of resources, challenges, and hindrances at work, as well as the relationships among them.
 
@@
 First, this research is couched within the well-studied job demands-resources theory (Demerouti et al., 2001).
-We argue that while useful, additional emphasis should be placed on individual differences in perceptions of job characteristics.
+We argue that static assignment of characteristics as a demand or resource may be useful, additional emphasis should be placed on individual differences in perceptions of job characteristics.
 In fact, our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs (Webster et al., 2011).
@@
 Further, Cavanaugh et al.
-(2000) suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes (e.g., Cavanaugh et al., 2000).
+(2000) suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes (e.g., Cavanaugh et al., 2000).
 
-Differences in outcomes depending on whether or not an employee perceives a job characteristic to be a challenge or hindrance has practical implications.
-Our results suggest that what is generally seen as a resource and challenge tends to be agreed upon moreso that what is seen a hindrance.
+Our results suggest that what is generally seen as a resource and challenge tends to be agreed upon more so that what is seen a hindrance.
 In fact, hindrance demands are rated more variably and thus, it may be important to have conversations about job characteristics and expectations at multiple time points after hire.
@@
 
+Resources did predict engagement, and did moderate several of the challenge-outcome, and hindrance-outcome relationships.
+As such, we provide further evidence of the importance of perceived resources, particularly when a job is high in hindrance demands, as resources acted as a buffer in both instances.
+It is worth noting that this paper focused on \emph{perceived} resources, challenges, and hindrances.
+Differences in outcomes depending on whether or not an employee perceives a job characteristic to be a challenge or hindrance have practical implications especially for managers.
+Helping employees to manage expectations and frame the work is quite likely to shape how activities are appraised (e.g., as a challenge, or as a resource).
+Of course, in some instances, framing an activity or job context variable as an opportunity or positive aspect of work is unrealistic, and so interventions aimed at supporting employees (e.g., stress interventions) may be necessary.
+
 \subsection{Limitations and Future Directions}\label{limitations-and-future-directions}
-
-Cross-sectional
 
@@
 For example, O*Net also includes styles and values, which we did not sample.
-Future studies may want to expand to explore these additional aspects of work.
+Future studies may want to expand to explore these additional aspects of work, and perhaps longitudinally.
 
@@
 
-In sum, this endeavor explored the job-demands-resources literature from a unique lens from within a universally accessible framework.
+\subsection{Conclusion}\label{conclusion}
+
+In sum, this endeavor builds on the job-demands-resources, and challenge-hindrance stressor literature from a unique lens from within a universally accessible framework.
 We showed that there are far more individual differences in how employees perceive demands and resources than much of our current research suggests.
 While resources and challenges idiosyncratic more similarly experienced, what is experienced as a hindrance tends to be idiosyncratic.
+We further provide additional evidence highlighting the value of perceived resources in the workplace, as they were demonstrated to moderate both challenge-engagement, and hindrance-stress/hindrance burnout relationships as we would expect.
 

### 2024-07-26 Submission.Rmd
Final Paper Read-through

@@
 We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges].
-Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) whether subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and outcomes.
-To illuminate these questions, we consult the [O\*Net database](https://www.onetcenter.org/content.html), which provides a rich source of information about occupational requirements (i.e., work activities and context).
-We retain O\*Net terminology of working condition elements throughout this paper (e.g., personal, contextual, or task-related conditions or elements of one's work).
+Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes.
+As an additional contribution, we utilize the [O\*Net database](https://www.onetcenter.org/content.html), which provides a rich and generalizable source of information about occupational requirements (i.e., work activities and context).
 
@@
 The challenge-hindrance stressor framework distinguishes between *two forms* of demands -- *challenges* and *hindrances*.
-Both are considered stressors [e.g., @cavanaugh2000empirical].
+Both are considered stressors/demands [e.g., @cavanaugh2000empirical].
 Challenge demands promote mastery, personal growth, and future gains – these demands should lead to coping strategies that facilitate achievement.
@@
 The original work on this topic suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes [e.g., @cavanaugh2000empirical].
-Meta-analytic explorations of this the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, @lepine2005meta regarding performance and @crawford2010linking regarding engagement).
+Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, @lepine2005meta regarding performance and @crawford2010linking regarding engagement).
 
@@
 Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing.
-Of note is that this energy may be depleted eventually, leading to strain.
-demands appraised as hindrances elicit a different process.
-Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing.
+Demands appraised as hindrances elicit a different process.
+Disengagement is likely to result from a hindrance appraisal, which then negatively impacts motivation, performance, growth and wellbeing.
 This happens because resources are depleted via frustrations and other affectively negative reactions [@lepine2022challenge].
@@
 Interestingly, much of our existing knowledge regarding the way these relationships between resources/demands and outcomes (e.g., stress, engagement) function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands.
-Even @pindek2024dynamic notes this limitation of a priori classification of characteristics as demands, challenges, or hindrances, as do @horan2020review.
-In fact, although much of our research on job demands based on a priori classifications [@searle2015merits], we contend that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
-
-@horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process described by @lazarus1984stress into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources.
+@pindek2024dynamic notes this limitation of *a priori* classification of characteristics as demands, challenges, or hindrances, as do @horan2020review.
+In fact, although much of our research on job demands based on *a priori* classifications [@searle2015merits], the recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
+
+Aligned with this dynamic perspective on the experience of work, @horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process described by @lazarus1984stress into the challenge-hindrance stressor framework.
 In fact, @horan2020review state that “…stressors are only challenge or hindrance demands to the extent that they are perceived as such by employees” (p.
@@
 
-As such, the first question we ask is whether people distinguish between resources, challenges, and  hindrances, and whether a job characteristics might even be considered simultaneously as more than one of these (e.g., both a challenge and a resource).
-Evidence suggests the employees do, in fact, differentiate between challenge and hindrance demands [e.g., @bakker2013weekly; @gerich2017relevance; @webster2011extending], at least.
-For example, @bakker2013weekly found that work pressure was perceived as a hindrance demand, and emotional demands as more of a challenge demand.
-@webster2011extending approached this question with three common workplace demands: workload, role ambiguity, and role conflict.
-They found while that each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance demand to different degrees.
+Given the above, the first question we ask is whether people exclusively categorize resources, challenges, and  hindrances, and whether a job characteristics might even be considered simultaneously as more than one of these (e.g., both a challenge and a resource).
+Evidence suggests that employees do, at least, differentiate between challenge and hindrance demands [e.g., @bakker2013weekly; @gerich2017relevance; @webster2011extending].
+For example, @bakker2013weekly found that work pressure was perceived as a hindrance, and emotional demands as more of a challenge.
+@webster2011extending approached this question with three commonly implicated workplace demands: workload, role ambiguity, and role conflict.
+They found while that each could be appraised primarily as a challenge or hindrance, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees.
 We aim to both replicate the above findings and extend them to include resources.
@@
 
-The second set of predictions focuses on associations with work-relevant outcomes frequently studied across via job demands-resources- [@bakker2017job] and challenge-hindrance stressor-frameworks [@cavanaugh2000empirical].
-Here, we specifically explore appraisals of O\*Net-derived work characteristics as resources, challenges, and/or hindrances in association with engagement, strain and burnout.
-As argued above, appraisals are predicted to be associated with different forms of coping, and subsequently, outcomes.
-See Figure \@ref(fig:ourmodel) for proposed associations.
-
-```{r ourmodel, eval=TRUE, echo=FALSE, fig.cap="Focal constructs and associations of interest"}
-library(magick)
-library(grid)
-
-figure2 <- image_read("ourmodel.png")
-
-grid.raster(figure2) # works well with margins/etc
-
-```
-
+The second set of predictions focus on associations with theory-relevant outcomes across via job demands-resources- [@bakker2017job] and challenge-hindrance stressor-frameworks [@cavanaugh2000empirical].
 Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance [e.g., @lepine2005meta].
 We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout.
+See Figure \@ref(fig:ourmodel) for proposed associations.
 Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job], and empirical work suggests that they are associated with positive outcomes.
@@
 
+```{r ourmodel, eval=TRUE, echo=FALSE, fig.cap="Focal constructs and associations of interest"}
+library(magick)
+library(grid)
+
+figure2 <- image_read("ourmodel.png")
+
+grid.raster(figure2) # works well with margins/etc
+
+```
+
 The findings regarding demands are more complex, presumably because the way challenge vs.
-hindrance appraisal influence coping strategies.
-Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and work meaningful [@chen2021daily], engagement [@crawford2010linking], and strain and turnover intentions [e.g., @abbas2019challenge], for example.
+hindrance appraisals influence coping strategies.
+Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work [@chen2021daily], engagement [@crawford2010linking], and strain and turnover intentions [e.g., @abbas2019challenge], for example.
 Challenge appraisals have been negatively associated with job search behaviors [e.g., @cavanaugh2000empirical].
 
-Hindrance demands (appraisals) are largely related to outcomes as the job demands-resources model predicts.
-When a demand was appraised as a hindrance – it was negatively associated with motivational resources [@kim2020thriving], engagement [@crawford2010linking], job search behaviors and job satisfaction, [@cavanaugh2000empirical].
+Hindrance demands (appraisals) have been found to be related to job demands-resources model outcomes such as decreased motivation and increased stress.
+When a demand is appraised as a hindrance – it is negatively associated with motivational resources [@kim2020thriving], engagement [@crawford2010linking], job search behaviors and job satisfaction [@cavanaugh2000empirical].
 @chen2021daily found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment.
@@
 Interestingly, both challenges and hindrances have been shown to positively predict strain [(Abbas & Raja, 2019]@abbas2019challenge; @lepine2005meta; @podsakoff2007differential; @webster2010toward], which further highlights the complex association between appraisals and subsequent outcomes.
-Given the differential relationships described above, we make the following predictions:
+Given the differential relationships described above, we make the following predictions [see Figure \@ref(fig:ourmodel)]:
 
@@
 In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain [e.g., @bakker2005job] and burnout [e.g., @xanthopoulou2007job].
-Bakker and colleagues (2005) were the first to report empirical evidence to support the idea job resources could potentially buffer the negative impact of job demands on stress reactions like burnout.
+Bakker and colleagues (2005) were the first to report empirical evidence to support the idea that job resources could potentially buffer the negative impact of job demands on distal outcomes like burnout.
 @bakker2005job explored the interaction between 4 demands (e.g., work overload, physical demands) and 4 resources (e.g., social support, feedback) and three dimensions of burnout (exhaustion, cynicism, and professional efficacy), and found some support for the prediction that high demands with low resources predicted greater levels of cynicism and exhaustion among employees in higher education.
@@
 They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout.
-We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows:
+We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows [see Figure \@ref(fig:ourmodel)]:
 

### 2024-07-26 Submission.tex
Final Paper Read-through

@@
 We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020).
-Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) whether subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and outcomes.
-To illuminate these questions, we consult the \href{https://www.onetcenter.org/content.html}{O*Net database}, which provides a rich source of information about occupational requirements (i.e., work activities and context).
-We retain O*Net terminology of working condition elements throughout this paper (e.g., personal, contextual, or task-related conditions or elements of one's work).
+Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes.
+As an additional contribution, we utilize the \href{https://www.onetcenter.org/content.html}{O*Net database}, which provides a rich and generalizable source of information about occupational requirements (i.e., work activities and context).
 
@@
 The challenge-hindrance stressor framework distinguishes between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}.
-Both are considered stressors (e.g., Cavanaugh et al., 2000).
+Both are considered stressors/demands (e.g., Cavanaugh et al., 2000).
 Challenge demands promote mastery, personal growth, and future gains -- these demands should lead to coping strategies that facilitate achievement.
@@
 The original work on this topic suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes (e.g., Cavanaugh et al., 2000).
-Meta-analytic explorations of this the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, J.
+Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, J.
 A.
@@
 Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing.
-Of note is that this energy may be depleted eventually, leading to strain.
-demands appraised as hindrances elicit a different process.
-Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing.
+Demands appraised as hindrances elicit a different process.
+Disengagement is likely to result from a hindrance appraisal, which then negatively impacts motivation, performance, growth and wellbeing.
 This happens because resources are depleted via frustrations and other affectively negative reactions (M.
@@
 Interestingly, much of our existing knowledge regarding the way these relationships between resources/demands and outcomes (e.g., stress, engagement) function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands.
-Even Pindek et al.
-(2024) notes this limitation of a priori classification of characteristics as demands, challenges, or hindrances, as do Horan et al.
+Pindek et al.
+(2024) notes this limitation of \emph{a priori} classification of characteristics as demands, challenges, or hindrances, as do Horan et al.
 (2020).
-In fact, although much of our research on job demands based on a priori classifications (Searle \& Auton, 2015), we contend that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
+In fact, although much of our research on job demands based on \emph{a priori} classifications (Searle \& Auton, 2015), the recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
 
-Horan et al.
+Aligned with this dynamic perspective on the experience of work, Horan et al.
 (2020) and M.
 A.
-LePine (2022) specifically call out the need for additional research to incorporate the appraisal process described by Lazarus and Folkman (1984) into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources.
+LePine (2022) specifically call out the need for additional research to incorporate the appraisal process described by Lazarus and Folkman (1984) into the challenge-hindrance stressor framework.
 In fact, Horan et al.
@@
 
-As such, the first question we ask is whether people distinguish between resources, challenges, and hindrances, and whether a job characteristics might even be considered simultaneously as more than one of these (e.g., both a challenge and a resource).
-Evidence suggests the employees do, in fact, differentiate between challenge and hindrance demands (e.g., Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011), at least.
-For example, Bakker and Sanz-Vergel (2013) found that work pressure was perceived as a hindrance demand, and emotional demands as more of a challenge demand.
+Given the above, the first question we ask is whether people exclusively categorize resources, challenges, and hindrances, and whether a job characteristics might even be considered simultaneously as more than one of these (e.g., both a challenge and a resource).
+Evidence suggests that employees do, at least, differentiate between challenge and hindrance demands (e.g., Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011).
+For example, Bakker and Sanz-Vergel (2013) found that work pressure was perceived as a hindrance, and emotional demands as more of a challenge.
 Webster et al.
-(2011) approached this question with three common workplace demands: workload, role ambiguity, and role conflict.
-They found while that each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance demand to different degrees.
+(2011) approached this question with three commonly implicated workplace demands: workload, role ambiguity, and role conflict.
+They found while that each could be appraised primarily as a challenge or hindrance, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees.
 We aim to both replicate the above findings and extend them to include resources.
@@
 
-The second set of predictions focuses on associations with work-relevant outcomes frequently studied across via job demands-resources- (Bakker \& Demerouti, 2017) and challenge-hindrance stressor-frameworks (Cavanaugh et al., 2000).
-Here, we specifically explore appraisals of O*Net-derived work characteristics as resources, challenges, and/or hindrances in association with engagement, strain and burnout.
-As argued above, appraisals are predicted to be associated with different forms of coping, and subsequently, outcomes.
+The second set of predictions focus on associations with theory-relevant outcomes across via job demands-resources- (Bakker \& Demerouti, 2017) and challenge-hindrance stressor-frameworks (Cavanaugh et al., 2000).
+Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance (e.g., J.
+A.
+LePine et al., 2005).
+We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout.
 See Figure \ref{fig:ourmodel} for proposed associations.
+Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017), and empirical work suggests that they are associated with positive outcomes.
+Relevant to the current study, for example, Hakanen et al.
+(2008) found job resources influenced future work engagement.
+Moreover, in a sample of teachers and dentists, Bakker et al.
+(2007) found that resources were most predictive of engagement when job demands were especially high.
+Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement (e.g., Schaufeli, 2017).
 
@@
 
-Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance (e.g., J.
-A.
-LePine et al., 2005).
-We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout.
-Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017), and empirical work suggests that they are associated with positive outcomes.
-Relevant to the current study, for example, Hakanen et al.
-(2008) found job resources influenced future work engagement.
-Moreover, in a sample of teachers and dentists, Bakker et al.
-(2007) found that resources were most predictive of engagement when job demands were especially high.
-Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement (e.g., Schaufeli, 2017).
-
-The findings regarding demands are more complex, presumably because the way challenge vs.~hindrance appraisal influence coping strategies.
-Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and work meaningful (Chen et al., 2021), engagement (Crawford et al., 2010), and strain and turnover intentions (e.g., Abbas \& Raja, 2019), for example.
+The findings regarding demands are more complex, presumably because the way challenge vs.~hindrance appraisals influence coping strategies.
+Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work (Chen et al., 2021), engagement (Crawford et al., 2010), and strain and turnover intentions (e.g., Abbas \& Raja, 2019), for example.
 Challenge appraisals have been negatively associated with job search behaviors (e.g., Cavanaugh et al., 2000).
 
-Hindrance demands (appraisals) are largely related to outcomes as the job demands-resources model predicts.
-When a demand was appraised as a hindrance -- it was negatively associated with motivational resources (Kim \& Beehr, 2020), engagement (Crawford et al., 2010), job search behaviors and job satisfaction, (Cavanaugh et al., 2000).
+Hindrance demands (appraisals) have been found to be related to job demands-resources model outcomes such as decreased motivation and increased stress.
+When a demand is appraised as a hindrance -- it is negatively associated with motivational resources (Kim \& Beehr, 2020), engagement (Crawford et al., 2010), job search behaviors and job satisfaction (Cavanaugh et al., 2000).
 Chen et al.
@@
 LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010), which further highlights the complex association between appraisals and subsequent outcomes.
-Given the differential relationships described above, we make the following predictions:
+Given the differential relationships described above, we make the following predictions {[}see Figure \ref{fig:ourmodel}{]}:
 
@@
 In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain (e.g., Bakker et al., 2005) and burnout (e.g., Xanthopoulou et al., 2007).
-Bakker and colleagues (2005) were the first to report empirical evidence to support the idea job resources could potentially buffer the negative impact of job demands on stress reactions like burnout.
+Bakker and colleagues (2005) were the first to report empirical evidence to support the idea that job resources could potentially buffer the negative impact of job demands on distal outcomes like burnout.
 Bakker et al.
@@
 They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout.
-We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows:
+We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows {[}see Figure \ref{fig:ourmodel}{]}:
 

### 2024-07-28 Submission.Rmd
coffee shop edits (Methods)

@@
 ---
-title             : "Subjective Experience of Demands and Resources across O*NET Job Elements"
+title             : "Non-exclusive Characteriazations of Demands and Resources across O*NET Job Elements"
 shorttitle        : "O*NET JD-R"
@@
 @chen2021daily found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment.
-Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands [@podsakoff2007differential]].
-Interestingly, both challenges and hindrances have been shown to positively predict strain [(Abbas & Raja, 2019]@abbas2019challenge; @lepine2005meta; @podsakoff2007differential; @webster2010toward], which further highlights the complex association between appraisals and subsequent outcomes.
-Given the differential relationships described above, we make the following predictions [see Figure \@ref(fig:ourmodel)]:
+Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands [@podsakoff2007differential].
+Interestingly, both challenges and hindrances have been shown to positively predict strain [@abbas2019challenge; @lepine2005meta; @podsakoff2007differential; @webster2010toward], which further highlights the complex association between appraisals and subsequent outcomes.
+Given the differential relationships described above, we make the following predictions (see Figure \@ref(fig:ourmodel)):
 
@@
 They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout.
-We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows [see Figure \@ref(fig:ourmodel)]:
+We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows (see Figure \@ref(fig:ourmodel)):
 
@@
 
+```{r litresources}
+
+###############################################
+############################################### include & eval=FALSE on 1/16/23 because of new figure which replaced this older attempt
+
+### ACTUALLY, just commented out the graph because other code chunks needed for subsequent commands - 1/17/23 , fig.cap="Average and standard deviation of O*Net characteristics retained as indicators of Autonomy, Cohesion, Control, Participation, and Supervisor Support."
+
+labels <- read.csv("truncatedlabels.csv", header=FALSE)  ## Changed on 12/19 to fix zero sd issues
+
+resource <- as.data.frame(t(data[118:202]))
+
+resource$description <- labels[c(118:202),1]
+resource$mean <- round(rowMeans(resource[1:nrow(data)], na.rm=TRUE),2)
+resource$sd   <- round(apply(resource[1:nrow(data)], 1, sd, na.rm=TRUE),2)
+
+resource <- resource[-28,]   ## attention check
+
+resource.control <- resource[ which(resource$description=='job structured for you, rather than allowing you to determine tasks, priorities, and goals' | resource$description=='regular work schedules'), ]
+resource.control$category <- "Control"
+
+resource.participation <- resource[ which(resource$description=='responsible for work outcomes and results of other workers' | resource$description=='responsibility for the health and safety of others' | resource$description=='developing specific goals and plans to prioritize, organize, and accomplish your work' | resource$description=='scheduling events, programs, and activities, as well as the work of others' | resource$description=='developing, designing, or creating new applications, ideas, relationships, systems, or products' | resource$description=='providing information to supervisors, co-workers, and subordinates by telephone, in written form, e-mail, or in person'), ]
+resource.participation$category <- "Participation"
+
+resource.sup.support <- resource[ which(resource$description=='providing guidance and expert advice to management or other groups on technical, systems-, or process-related topics' | resource$description=='identifying the educational needs of others, developing formal educational or training programs or classes, and teaching or instructing others'), ]
+resource.sup.support$category <- "Support"
+
+resource.autonomy <- resource[ which(resource$description=='decision making freedom, without supervision'), ]
+resource.autonomy$category <- "Autonomy"
+
+resource.cohesion <- resource[ which(resource$description=='work with others in a group or team' | resource$description=='getting members of a group to work together to accomplish tasks' | resource$description=='' | resource$description=='' | resource$description=='' | resource$description=='encouraging and building mutual trust, respect, and cooperation among team members'), ]
+resource.cohesion$category <- "Cohesion"
+
+notedresource <- rbind(resource.control, resource.participation, resource.sup.support, resource.autonomy, resource.cohesion)
+notedresource$RD <- "Resource"
+
+#########################################################
+#########################################################
+
+challenge <- as.data.frame(t(data[288:372]))
+
+challenge$description <- labels[c(288:372),1]
+challenge$mean <- round(rowMeans(challenge[1:nrow(data)], na.rm=TRUE),2)
+challenge$sd   <- round(apply(challenge[1:nrow(data)], 1, sd, na.rm=TRUE),2)
+
+challenge <- challenge[-21,]
+
+challenge.control <- challenge[ which(challenge$description=='job structured for you, rather than allowing you to determine tasks, priorities, and goals' | challenge$description=='regular work schedules'), ]
+challenge.control$category <- "Control"
+
+challenge.participation <- challenge[ which(challenge$description=='responsible for work outcomes and results of other workers' | challenge$description=='responsibility for the health and safety of others' | challenge$description=='developing specific goals and plans to prioritize, organize, and accomplish your work' | challenge$description=='scheduling events, programs, and activities, as well as the work of others' | challenge$description=='developing, designing, or creating new applications, ideas, relationships, systems, or products' | challenge$description=='providing information to supervisors, co-workers, and subordinates by telephone, in written form, e-mail, or in person'), ]
+challenge.participation$category <- "Participation"
+
+challenge.sup.support <- challenge[ which(challenge$description=='providing guidance and expert advice to management or other groups on technical, systems-, or process-related topics' | challenge$description=='identifying the educational needs of others, developing formal educational or training programs or classes, and teaching or instructing others'), ]
+challenge.sup.support$category <- "Support"
+
+#challenge.autonomy <- challenge[ which(challenge$description=='decision making freedom, without supervision'), ]
+#challenge.autonomy$category <- "Autonomy"
+
+challenge.cohesion <- challenge[ which(challenge$description=='work with others in a group or team' | challenge$description=='getting members of a group to work together to accomplish tasks' | challenge$description=='' | challenge$description=='' | challenge$description=='' | challenge$description=='encouraging and building mutual trust, respect, and cooperation among team members'), ]
+challenge.cohesion$category <- "Cohesion"
+
+notedchallenge <- rbind(challenge.control, challenge.participation, challenge.sup.support,  challenge.cohesion)     ## removed challenge.autonomy 8/24/22
+notedchallenge$RD <- "Challenge"
+
+############################################################
+############################################################
+
+hindrance <- as.data.frame(t(data[203:287]))
+
+hindrance$description <- labels[c(203:287),1]
+hindrance$mean <- round(rowMeans(hindrance[1:nrow(data)], na.rm=TRUE),2)
+hindrance$sd   <- round(apply(hindrance[1:nrow(data)], 1, sd, na.rm=TRUE),2)
+
+hindrance <- hindrance[-46,]   ## attention check = 248
+
+hindrance.control <- hindrance[ which(hindrance$description=='job structured for you, rather than allowing you to determine tasks, priorities, and goals' | hindrance$description=='regular work schedules'), ]
+hindrance.control$category <- "Control"
+
+hindrance.participation <- hindrance[ which(hindrance$description=='responsible for work outcomes and results of other workers' | hindrance$description=='responsibility for the health and safety of others' | hindrance$description=='developing specific goals and plans to prioritize, organize, and accomplish your work' | hindrance$description=='scheduling events, programs, and activities, as well as the work of others' | hindrance$description=='developing, designing, or creating new applications, ideas, relationships, systems, or products' | hindrance$description=='providing information to supervisors, co-workers, and subordinates by telephone, in written form, e-mail, or in person'), ]
+hindrance.participation$category <- "Participation"
+
+hindrance.sup.support <- hindrance[ which(hindrance$description=='providing guidance and expert advice to management or other groups on technical, systems-, or process-related topics' | hindrance$description=='identifying the educational needs of others, developing formal educational or training programs or classes, and teaching or instructing others'), ]
+hindrance.sup.support$category <- "Support"
+
+hindrance.autonomy <- hindrance[ which(hindrance$description=='decision making freedom, without supervision'), ]
+hindrance.autonomy$category <- "Autonomy"
+
+hindrance.cohesion <- hindrance[ which(hindrance$description=='work with others in a group or team' | hindrance$description=='getting members of a group to work together to accomplish tasks' | hindrance$description=='' | hindrance$description=='' | hindrance$description=='' | hindrance$description=='encouraging and building mutual trust, respect, and cooperation among team members'), ]
+hindrance.cohesion$category <- "Cohesion"
+
+notedhindrance <- rbind(hindrance.control, hindrance.participation, hindrance.sup.support, hindrance.autonomy, hindrance.cohesion)
+notedhindrance$RD <- "Hindrance"
+
+###########################################################
+###########################################################  Name issue somehow above
+
+labels <- names(notedresource)
+colnames(notedchallenge) <- labels
+colnames(notedhindrance) <- labels
+
+together <- rbind(notedchallenge,notedhindrance,notedresource)
+
+############################################################
+############################################################
+
+library(ggplot2)
+library(dplyr)
+
+summarized <- together %>%                               # Summary by group using dplyr
+  group_by(category, RD) %>% 
+  summarize(mean = mean(mean),
+            sd = mean(sd))
+
+summarized$RD <- factor(summarized$RD, levels = c("Resource", "Challenge", "Hindrance"))
+
+#ggplot(summarized, aes(x=category, y=mean, fill=RD)) + geom_bar(stat="identity", position=position_dodge()) + theme_bw() + xlab("") + ylab("Average Job Characteristic Rating") + coord_cartesian(ylim=c(1,5)) + scale_fill_brewer(palette="Blues") +
+#  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.5, size=0.8, position=position_dodge(.9))
+
+```
+
+## Procedure
+
+Data were collected through Prolific, an online data collection platform.
+An email was sent to **a random subset???** of all "eligible" members of the Prolific respondent pool, notifying them of their opportunity to participate.
+Eligibility requirements **included??** being 18 or older and holding either a full-time or part-time job.
+Eligible individuals then voluntarily chose whether or not to respond to the invitation after reading an informed consent.
+
+Participants were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of **98???** different O\*Net job characteristics.
+For example, if a respondent indicated that any one characteristic **was not** applicable for their job, they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
+Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).
+
 ## Participants
@@
 
-```{r litresources}
-
-###############################################
-############################################### include & eval=FALSE on 1/16/23 because of new figure which replaced this older attempt
-
-### ACTUALLY, just commented out the graph because other code chunks needed for subsequent commands - 1/17/23 , fig.cap="Average and standard deviation of O*Net characteristics retained as indicators of Autonomy, Cohesion, Control, Participation, and Supervisor Support."
-
-labels <- read.csv("truncatedlabels.csv", header=FALSE)  ## Changed on 12/19 to fix zero sd issues
-
-resource <- as.data.frame(t(data[118:202]))
-
-resource$description <- labels[c(118:202),1]
-resource$mean <- round(rowMeans(resource[1:nrow(data)], na.rm=TRUE),2)
-resource$sd   <- round(apply(resource[1:nrow(data)], 1, sd, na.rm=TRUE),2)
-
-resource <- resource[-28,]   ## attention check
-
-resource.control <- resource[ which(resource$description=='job structured for you, rather than allowing you to determine tasks, priorities, and goals' | resource$description=='regular work schedules'), ]
-resource.control$category <- "Control"
-
-resource.participation <- resource[ which(resource$description=='responsible for work outcomes and results of other workers' | resource$description=='responsibility for the health and safety of others' | resource$description=='developing specific goals and plans to prioritize, organize, and accomplish your work' | resource$description=='scheduling events, programs, and activities, as well as the work of others' | resource$description=='developing, designing, or creating new applications, ideas, relationships, systems, or products' | resource$description=='providing information to supervisors, co-workers, and subordinates by telephone, in written form, e-mail, or in person'), ]
-resource.participation$category <- "Participation"
-
-resource.sup.support <- resource[ which(resource$description=='providing guidance and expert advice to management or other groups on technical, systems-, or process-related topics' | resource$description=='identifying the educational needs of others, developing formal educational or training programs or classes, and teaching or instructing others'), ]
-resource.sup.support$category <- "Support"
-
-resource.autonomy <- resource[ which(resource$description=='decision making freedom, without supervision'), ]
-resource.autonomy$category <- "Autonomy"
-
-resource.cohesion <- resource[ which(resource$description=='work with others in a group or team' | resource$description=='getting members of a group to work together to accomplish tasks' | resource$description=='' | resource$description=='' | resource$description=='' | resource$description=='encouraging and building mutual trust, respect, and cooperation among team members'), ]
-resource.cohesion$category <- "Cohesion"
-
-notedresource <- rbind(resource.control, resource.participation, resource.sup.support, resource.autonomy, resource.cohesion)
-notedresource$RD <- "Resource"
-
-#########################################################
-#########################################################
-
-challenge <- as.data.frame(t(data[288:372]))
-
-challenge$description <- labels[c(288:372),1]
-challenge$mean <- round(rowMeans(challenge[1:nrow(data)], na.rm=TRUE),2)
-challenge$sd   <- round(apply(challenge[1:nrow(data)], 1, sd, na.rm=TRUE),2)
-
-challenge <- challenge[-21,]
-
-challenge.control <- challenge[ which(challenge$description=='job structured for you, rather than allowing you to determine tasks, priorities, and goals' | challenge$description=='regular work schedules'), ]
-challenge.control$category <- "Control"
-
-challenge.participation <- challenge[ which(challenge$description=='responsible for work outcomes and results of other workers' | challenge$description=='responsibility for the health and safety of others' | challenge$description=='developing specific goals and plans to prioritize, organize, and accomplish your work' | challenge$description=='scheduling events, programs, and activities, as well as the work of others' | challenge$description=='developing, designing, or creating new applications, ideas, relationships, systems, or products' | challenge$description=='providing information to supervisors, co-workers, and subordinates by telephone, in written form, e-mail, or in person'), ]
-challenge.participation$category <- "Participation"
-
-challenge.sup.support <- challenge[ which(challenge$description=='providing guidance and expert advice to management or other groups on technical, systems-, or process-related topics' | challenge$description=='identifying the educational needs of others, developing formal educational or training programs or classes, and teaching or instructing others'), ]
-challenge.sup.support$category <- "Support"
-
-#challenge.autonomy <- challenge[ which(challenge$description=='decision making freedom, without supervision'), ]
-#challenge.autonomy$category <- "Autonomy"
-
-challenge.cohesion <- challenge[ which(challenge$description=='work with others in a group or team' | challenge$description=='getting members of a group to work together to accomplish tasks' | challenge$description=='' | challenge$description=='' | challenge$description=='' | challenge$description=='encouraging and building mutual trust, respect, and cooperation among team members'), ]
-challenge.cohesion$category <- "Cohesion"
-
-notedchallenge <- rbind(challenge.control, challenge.participation, challenge.sup.support,  challenge.cohesion)     ## removed challenge.autonomy 8/24/22
-notedchallenge$RD <- "Challenge"
-
-############################################################
-############################################################
-
-hindrance <- as.data.frame(t(data[203:287]))
-
-hindrance$description <- labels[c(203:287),1]
-hindrance$mean <- round(rowMeans(hindrance[1:nrow(data)], na.rm=TRUE),2)
-hindrance$sd   <- round(apply(hindrance[1:nrow(data)], 1, sd, na.rm=TRUE),2)
-
-hindrance <- hindrance[-46,]   ## attention check = 248
-
-hindrance.control <- hindrance[ which(hindrance$description=='job structured for you, rather than allowing you to determine tasks, priorities, and goals' | hindrance$description=='regular work schedules'), ]
-hindrance.control$category <- "Control"
-
-hindrance.participation <- hindrance[ which(hindrance$description=='responsible for work outcomes and results of other workers' | hindrance$description=='responsibility for the health and safety of others' | hindrance$description=='developing specific goals and plans to prioritize, organize, and accomplish your work' | hindrance$description=='scheduling events, programs, and activities, as well as the work of others' | hindrance$description=='developing, designing, or creating new applications, ideas, relationships, systems, or products' | hindrance$description=='providing information to supervisors, co-workers, and subordinates by telephone, in written form, e-mail, or in person'), ]
-hindrance.participation$category <- "Participation"
-
-hindrance.sup.support <- hindrance[ which(hindrance$description=='providing guidance and expert advice to management or other groups on technical, systems-, or process-related topics' | hindrance$description=='identifying the educational needs of others, developing formal educational or training programs or classes, and teaching or instructing others'), ]
-hindrance.sup.support$category <- "Support"
-
-hindrance.autonomy <- hindrance[ which(hindrance$description=='decision making freedom, without supervision'), ]
-hindrance.autonomy$category <- "Autonomy"
-
-hindrance.cohesion <- hindrance[ which(hindrance$description=='work with others in a group or team' | hindrance$description=='getting members of a group to work together to accomplish tasks' | hindrance$description=='' | hindrance$description=='' | hindrance$description=='' | hindrance$description=='encouraging and building mutual trust, respect, and cooperation among team members'), ]
-hindrance.cohesion$category <- "Cohesion"
-
-notedhindrance <- rbind(hindrance.control, hindrance.participation, hindrance.sup.support, hindrance.autonomy, hindrance.cohesion)
-notedhindrance$RD <- "Hindrance"
-
-###########################################################
-###########################################################  Name issue somehow above
-
-labels <- names(notedresource)
-colnames(notedchallenge) <- labels
-colnames(notedhindrance) <- labels
-
-together <- rbind(notedchallenge,notedhindrance,notedresource)
-
-############################################################
-############################################################
-
-library(ggplot2)
-library(dplyr)
-
-summarized <- together %>%                               # Summary by group using dplyr
-  group_by(category, RD) %>% 
-  summarize(mean = mean(mean),
-            sd = mean(sd))
-
-summarized$RD <- factor(summarized$RD, levels = c("Resource", "Challenge", "Hindrance"))
-
-#ggplot(summarized, aes(x=category, y=mean, fill=RD)) + geom_bar(stat="identity", position=position_dodge()) + theme_bw() + xlab("") + ylab("Average Job Characteristic Rating") + coord_cartesian(ylim=c(1,5)) + scale_fill_brewer(palette="Blues") +
-#  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.5, size=0.8, position=position_dodge(.9))
-
-```
-
 ## Materials
 
-The Occupational Information Network (O\*Net) contains a comprehensive description of occupations [@peterson2001understanding].
-This widely accessed database houses hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are continually updated.
+The Occupational Information Network (O\*Net) serves as a repository of information broadly descriptive of occupations [@peterson2001understanding].
+The O\*Net database consists of hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are frequently updated.
 We focused on 98 work [activity and context statements](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*Net groups into *activity* categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
@@
 Other than minor grammatical editing (for example, changing “the worker” to “you”), we also retained the O\*Net wording for our item stems.
-
-## Procedure
-
-Data were collected through Prolific, an online data collection platform.
-An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
-Eligibility requirements included being 18 or older and holding either a full-time or part-time job.
-Participants then voluntarily chose to respond to the online survey after reading an informed consent.
-Participants were asked to think about their primary job, and the items they were presented with depended on the specific job characteristics they initially specified.
-Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
-The total number of items on the survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
-Participants were compensated for their participation in this study estimated to require 45 minutes' time in the amount of six dollars through Prolific.
+The total number of items on each administered survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
 

### 2024-07-28 Submission.tex
coffee shop edits (Methods)

@@
 \fi
-% definitions for citeproc citations
-\NewDocumentCommand\citeproctext{}{}
-\NewDocumentCommand\citeproc{mm}{%
-  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
-\makeatletter
- % allow citations to break across lines
- \let\@cite@ofmt\@firstofone
- % avoid brackets around text for \cite:
- \def\@biblabel#1{}
- \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
-\makeatother
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
- {\begin{list}{}{%
-  \setlength{\itemindent}{0pt}
-  \setlength{\leftmargin}{0pt}
-  \setlength{\parsep}{0pt}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-   \setlength{\leftmargin}{\cslhangindent}
-   \setlength{\itemindent}{-1\cslhangindent}
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
   \fi
   % set entry spacing
-  \setlength{\itemsep}{#2\baselineskip}}}
- {\end{list}}
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
@@
 \fi
-\usepackage{bookmark}
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
@@
 \hypersetup{
-  pdftitle={Subjective Experience of Demands and Resources across O*NET Job Elements},
+  pdftitle={Non-exclusive Characteriazations of Demands and Resources across O*NET Job Elements},
   pdflang={en-EN},
@@
 
-\title{Subjective Experience of Demands and Resources across O*NET Job Elements}
+\title{Non-exclusive Characteriazations of Demands and Resources across O*NET Job Elements}
 \author{Alicia Stachowski\textsuperscript{2}, John Kulas\textsuperscript{1}, \& Renata García Prieto Palacios Roji\textsuperscript{3}}
@@
 
-\subsection{The Job Demands-Resources Theory and Challenge-Hindrance Stressor Framework}\label{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}
+\hypertarget{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}{%
+\subsection{The Job Demands-Resources Theory and Challenge-Hindrance Stressor Framework}\label{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}}
 
@@
 
-\subsection{Are Perceptions of Job Resources, Challenge Demands, and Hindrance Demands Universal?}\label{are-perceptions-of-job-resources-challenge-demands-and-hindrance-demands-universal}
+\hypertarget{are-perceptions-of-job-resources-challenge-demands-and-hindrance-demands-universal}{%
+\subsection{Are Perceptions of Job Resources, Challenge Demands, and Hindrance Demands Universal?}\label{are-perceptions-of-job-resources-challenge-demands-and-hindrance-demands-universal}}
 
@@
 
-\subsection{Connecting Appraisals to Workplace Outcomes}\label{connecting-appraisals-to-workplace-outcomes}
+\hypertarget{connecting-appraisals-to-workplace-outcomes}{%
+\subsection{Connecting Appraisals to Workplace Outcomes}\label{connecting-appraisals-to-workplace-outcomes}}
 
@@
 (2021) found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment.
-Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands (Podsakoff et al., 2007){]}.
-Interestingly, both challenges and hindrances have been shown to positively predict strain ((Abbas \& Raja, 2019 Abbas \& Raja, 2019; J.
+Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands (Podsakoff et al., 2007).
+Interestingly, both challenges and hindrances have been shown to positively predict strain (Abbas \& Raja, 2019; J.
 A.
 LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010), which further highlights the complex association between appraisals and subsequent outcomes.
-Given the differential relationships described above, we make the following predictions {[}see Figure \ref{fig:ourmodel}{]}:
+Given the differential relationships described above, we make the following predictions (see Figure \ref{fig:ourmodel}):
 
@@
 They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout.
-We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows {[}see Figure \ref{fig:ourmodel}{]}:
+We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows (see Figure \ref{fig:ourmodel}):
 
@@
 
-\section{Method}\label{method}
+\hypertarget{method}{%
+\section{Method}\label{method}}
 
-\subsection{Participants}\label{participants}
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
+
+Data were collected through Prolific, an online data collection platform.
+An email was sent to \textbf{a random subset???} of all ``eligible'' members of the Prolific respondent pool, notifying them of their opportunity to participate.
+Eligibility requirements \textbf{included??} being 18 or older and holding either a full-time or part-time job.
+Eligible individuals then voluntarily chose whether or not to respond to the invitation after reading an informed consent.
+
+Participants were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of \textbf{98???} different O*Net job characteristics.
+For example, if a respondent indicated that any one characteristic \textbf{was not} applicable for their job, they were not subsequently asked to rate the level of resource (\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
+Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).
+
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
 
@@
 
-\subsection{Materials}\label{materials}
+\hypertarget{materials}{%
+\subsection{Materials}\label{materials}}
 
-The Occupational Information Network (O*Net) contains a comprehensive description of occupations (Peterson et al., 2001).
-This widely accessed database houses hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are continually updated.
+The Occupational Information Network (O*Net) serves as a repository of information broadly descriptive of occupations (Peterson et al., 2001).
+The O*Net database consists of hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are frequently updated.
 We focused on 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context statements} which O*Net groups into \emph{activity} categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
@@
 Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we also retained the O*Net wording for our item stems.
+The total number of items on each administered survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
 
-\subsection{Procedure}\label{procedure}
-
-Data were collected through Prolific, an online data collection platform.
-An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
-Eligibility requirements included being 18 or older and holding either a full-time or part-time job.
-Participants then voluntarily chose to respond to the online survey after reading an informed consent.
-Participants were asked to think about their primary job, and the items they were presented with depended on the specific job characteristics they initially specified.
-Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
-The total number of items on the survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
-Participants were compensated for their participation in this study estimated to require 45 minutes' time in the amount of six dollars through Prolific.
-
-\section{Results}\label{results}
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
@@
 
-\subsubsection{Challenges, Resources, and Outcomes}\label{challenges-resources-and-outcomes}
+\hypertarget{challenges-resources-and-outcomes}{%
+\subsubsection{Challenges, Resources, and Outcomes}\label{challenges-resources-and-outcomes}}
 
@@
 
-\subsubsection{Hindrances, Resources, and Outcomes}\label{hindrances-resources-and-outcomes}
+\hypertarget{hindrances-resources-and-outcomes}{%
+\subsubsection{Hindrances, Resources, and Outcomes}\label{hindrances-resources-and-outcomes}}
 
@@
 
-\section{Discussion}\label{discussion}
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
 
@@
 
-\subsection{Implications}\label{implications}
+\hypertarget{implications}{%
+\subsection{Implications}\label{implications}}
 
@@
 
-\subsection{Limitations and Future Directions}\label{limitations-and-future-directions}
+\hypertarget{limitations-and-future-directions}{%
+\subsection{Limitations and Future Directions}\label{limitations-and-future-directions}}
 
@@
 
-\subsection{Conclusion}\label{conclusion}
+\hypertarget{conclusion}{%
+\subsection{Conclusion}\label{conclusion}}
 
@@
 
-\section{References}\label{references}
+\hypertarget{references}{%
+\section{References}\label{references}}
 
@@
 
-\phantomsection\label{refs}
+\hypertarget{refs}{}
 \begin{CSLReferences}{1}{0}
-\bibitem[\citeproctext]{ref-abbas2019challenge}
+\leavevmode\vadjust pre{\hypertarget{ref-abbas2019challenge}{}}%
 Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.
 
-\bibitem[\citeproctext]{ref-bakker2014job}
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
 Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
 
-\bibitem[\citeproctext]{ref-bakker2017job}
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
 Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
 
-\bibitem[\citeproctext]{ref-bakker2005job}
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2005job}{}}%
 Bakker, A. B., Demerouti, E., \& Euwema, M. C. (2005). Job resources buffer the impact of job demands on burnout. \emph{Journal of Occupational Health Psychology}, \emph{10}(2), 170.
 
-\bibitem[\citeproctext]{ref-bakker2007job}
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2007job}{}}%
 Bakker, A.
@@
 
-\bibitem[\citeproctext]{ref-bakker2013weekly}
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
 Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
 
-\bibitem[\citeproctext]{ref-cavanaugh2000empirical}
+\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
 Cavanaugh, M.
@@
 
-\bibitem[\citeproctext]{ref-chen2021daily}
+\leavevmode\vadjust pre{\hypertarget{ref-chen2021daily}{}}%
 Chen, H., Wang, H., Yuan, M., \& Xu, S. (2021). Daily challenge/hindrance demands and cognitive wellbeing: A multilevel moderated mediation model. \emph{Frontiers in Psychology}, \emph{12}, 616002.
 
-\bibitem[\citeproctext]{ref-crawford2010linking}
+\leavevmode\vadjust pre{\hypertarget{ref-crawford2010linking}{}}%
 Crawford, E.
@@
 
-\bibitem[\citeproctext]{ref-demerouti2001job}
+\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
 Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
 
-\bibitem[\citeproctext]{ref-gerich2017relevance}
+\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
 Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
 
-\bibitem[\citeproctext]{ref-hakanen2008job}
+\leavevmode\vadjust pre{\hypertarget{ref-hakanen2008job}{}}%
 Hakanen, J.
@@
 
-\bibitem[\citeproctext]{ref-horan2020review}
+\leavevmode\vadjust pre{\hypertarget{ref-horan2020review}{}}%
 Horan, K.
@@
 
-\bibitem[\citeproctext]{ref-kim2020thriving}
+\leavevmode\vadjust pre{\hypertarget{ref-kim2020thriving}{}}%
 Kim, M., \& Beehr, T.
@@
 
-\bibitem[\citeproctext]{ref-lazarus1984stress}
+\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
 Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
 
-\bibitem[\citeproctext]{ref-lepine2005meta}
+\leavevmode\vadjust pre{\hypertarget{ref-lepine2005meta}{}}%
 LePine, J.
@@
 
-\bibitem[\citeproctext]{ref-lepine2022challenge}
+\leavevmode\vadjust pre{\hypertarget{ref-lepine2022challenge}{}}%
 LePine, M. A. (2022). The challenge-hindrance stressor framework: An integrative conceptual review and path forward. \emph{Group \& Organization Management}, \emph{47}(2), 223--254.
 
-\bibitem[\citeproctext]{ref-peterson2001understanding}
+\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
 Peterson, N.
@@
 
-\bibitem[\citeproctext]{ref-pindek2024dynamic}
+\leavevmode\vadjust pre{\hypertarget{ref-pindek2024dynamic}{}}%
 Pindek, S., Meyer, K., Valvo, A., \& Arvan, M.
@@
 
-\bibitem[\citeproctext]{ref-podsakoff2007differential}
+\leavevmode\vadjust pre{\hypertarget{ref-podsakoff2007differential}{}}%
 Podsakoff, N.
@@
 
-\bibitem[\citeproctext]{ref-rosen2020challenges}
+\leavevmode\vadjust pre{\hypertarget{ref-rosen2020challenges}{}}%
 Rosen, C.
@@
 
-\bibitem[\citeproctext]{ref-schaufeli2017applying}
+\leavevmode\vadjust pre{\hypertarget{ref-schaufeli2017applying}{}}%
 Schaufeli, W. B. (2017). Applying the job demands-resources model: A `how to'guide to measuring and tackling work engagement and burnout. \emph{Organizational Dynamics}, \emph{46}(2), 120--132.
 
-\bibitem[\citeproctext]{ref-searle2015merits}
+\leavevmode\vadjust pre{\hypertarget{ref-searle2015merits}{}}%
 Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.
 
-\bibitem[\citeproctext]{ref-webster2010toward}
+\leavevmode\vadjust pre{\hypertarget{ref-webster2010toward}{}}%
 Webster, J.
@@
 
-\bibitem[\citeproctext]{ref-webster2011extending}
+\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
 Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.
 
-\bibitem[\citeproctext]{ref-xanthopoulou2007job}
+\leavevmode\vadjust pre{\hypertarget{ref-xanthopoulou2007job}{}}%
 Xanthopoulou, D., Bakker, A.
@@
 
-\bibitem[\citeproctext]{ref-R-careless}
+\leavevmode\vadjust pre{\hypertarget{ref-R-careless}{}}%
 Yentes, R. D., \& Wilhelm, F. (2021). \emph{Careless: Procedures for computing indices of careless responding}.

### 2024-07-31 Submission.Rmd
Preparing Manuscript for journal submission

@@
 abstract: |
-  Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands.
-This study documents variability in subjective ratings of O\*Net job characteristics with respect to interpretation as resource and demand (defined as challenge/hindrance), and further predicts demands and resources will be differentially related to outcomes of engagement, stress, and burnout.
-We lastly explore the moderating role of resources.
-We found that job characteristics were not uniquely categorized as a resource or demand, but rather, some job characteristics were rated highly as both a resource and a demand.
-We consistently observed a pattern of job characteristics seen as challenging also being cited as a resource.
-While we did not find support for the prediction, that demands were differentially related to stress and burnout, we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships as predicted.
-The findings broadly revealed that there was relatively more consistency in ratings of resource and challenge characteristics, and far more variability in job characteristics rated as hindrance demands.
+  Much of our understanding of job demands and resources rests on an assumption that some job characteristics are resources and some are demands.
+This study documents variability in subjective ratings of O\*Net job characteristics with respect to interpretation as resource and demand (defined as challenge/hindrance), and further predicts the form of demand will be differentially related to work-relevant outcomes.
+We lastly explore the moderating role of resources on these relationships.
+We found that job characteristics were not uniquely categorized as a resource or demand, but rather, some job characteristics were rated highly as both a resource and a challenge.
+While we did not find support for the prediction that demands were related to stress and burnout, we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships.
+These findings broadly reveal that there is relatively more consistency in ratings of resource and challenge characteristics, and far more variability in job characteristics rated as hindrance demands.
 These findings have implications for job design and management particularly with regard to resource-laden elements that may also be experienced as demanding.
@@
 footnotelist      : no
-linenumbers       : yes
-mask              : yes
+linenumbers       : no
+mask              : no
 draft             : no
@@
 The major aims of this paper were to explore whether: 1) there was variability in subjective ratings of job characteristics as resources and demands, 2) some characteristics were more likely to vary across demand and resource, 3) subjective appraisals were differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and outcomes.
-We found that job characteristics were not uniquely categorized as a resource or demand, but rather, some job characteristics were rated highly as both a resource and a demand.
-We consistently observed a pattern of job characteristics seen as challenging also being cited as a resource.
-While we did not find support for the prediction, that demands were differentially related to stress and burnout, we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships as predicted.
+We found that job characteristics were not uniquely categorized as a resource or demand, but rather, some job characteristics were rated highly as both a resource and a demand (particularly challenge demands).
 The findings broadly revealed that there was relatively more consistency in ratings of resource and challenge characteristics, and far more variability in job characteristics rated as hindrance demands.
@@
 3).
+While we did not find support for the prediction that different types of demands would be related to stress and burnout, we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships (as predicted).
 
 In addition to the above findings, this paper made several additional important contributions.
-We utilized a diverse sample of employees across industries, who responded to common O\*Net items.
+We utilized a diverse sample of employees across industries who responded to common O\*Net items.
 While O\*Net provides detailed information about frequency and importance ratings among employees, we begin the process of expanding what we know of job characteristics to ratings of demands and resources.
-Further, we provide a repository for other researchers with listing of item level *perceived* demands and resources across activity and context items for the benefit of all future researchers.
-We also explored not only context and activity holistically, but at the dimension level, which enhances our knowledge of how employees perceive different categories of resources, challenges, and hindrances at work, as well as the relationships among them.
+Further, we provide a repository for other researchers with listing of O\*Net demands and resources across activity and context items for the benefit of all future researchers.
+We also explored not only context and activity holistically, but at a higher level aggregation, which enhances our knowledge of how employees perceive different categories of resources, challenges, and hindrances within different work dimensions, as well as the relationships among them.
 
@@
 The findings presented above have implications for both theory and practice.
-First, this research is couched within the well-studied job demands-resources theory [@demerouti2001job].
-We argue that static assignment of characteristics as a demand or resource may be useful, additional emphasis should be placed on individual differences in perceptions of job characteristics.
+First, this research is situated within the familiar job demands-resources theory [@demerouti2001job].
+Although the static assignment of characteristics as a demand or resource may be useful, additional emphasis should be placed on differences in perceptions of job characteristics.
 In fact, our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs [@webster2011extending].
 This finding aligns quite well with both the transactional theory of stress and coping, and the challenge-hindrance stressor framework, which collectively argue that employees perceive stimuli (i.e., job characteristics) uniquely [@lazarus1984stress], and thus, could appraise them as either a challenge or hindrance to their job performance [@cavanaugh2000empirical].
-Further, @cavanaugh2000empirical suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes [e.g., @cavanaugh2000empirical].
+Further, @cavanaugh2000empirical suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes [e.g., @cavanaugh2000empirical], which we partially supported here.
 
@@
 For example, having open conversations with employees regarding their subjective perceptions of characteristics that may be unique in limiting their performance or comfort.
-Such conversations could happen during an annual performance review or more informally.
+Such conversations could happen during an annual performance review.
 In addition, @lepine2005meta and @podsakoff2007differential encourage organizations to incorporate strain-reducing activities like training and support to offset the negative effects of challenging job demands, which may be associated with increased performance in the short term, but strain when prolonged.
@@
 As with all individual studies, this project was limited in scope, and as such, there are a number of avenues for future study worth exploring.
-First, although we aggregated to both literature-derived as well as O\*Net groupings, essentially we were dealing with single-item scales.
+First, although we aggregated to O\*Net groupings, we were also dealing with single-item measures for much our operationalization.
 Although not ideal psychometrically, this provided a strong linkage to the established O\*Net framework.
-Related to that, we intentionally worked within the O\*Net database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources/demands.
+Related to that, we intentionally worked within the O\*Net database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources and demands.
 Therefore, to the extent that O\*Net is not an exhaustive repository, there are existing characteristics that we did not capture.
 For example, O\*Net also includes styles and values, which we did not sample.
-Future studies may want to expand to explore these additional aspects of work, and perhaps longitudinally.
+Future studies may want to expand to explore these additional aspects of work.
 
@@
 Future investigations may wish to explore the colloquial versus academic phrasing of these questions and how that may impact observed associations between resources and challenges.
-It would also be prudent to consider work-relevant outcomes associated with similar job characteristic ratings.
 We also note that effect sizes were small and thus it is important to consider the practical significance when thinking about potential interventions.
-We encourage future thought on how consideration of resource and demand perceptions might be combined with additional levers to reduce employee stress and burnout, as well as enhance engagement.
+We encourage future thought on how consideration of resource and demand perceptions might be combined with moderators to reduce employee stress and burnout, as well as enhance engagement.
 
@@
 We showed that there are far more individual differences in how employees perceive demands and resources than much of our current research suggests.
-While resources and challenges idiosyncratic more similarly experienced, what is experienced as a hindrance tends to be idiosyncratic.
-We further provide additional evidence highlighting the value of perceived resources in the workplace, as they were demonstrated to moderate both challenge-engagement, and hindrance-stress/hindrance burnout relationships as we would expect.
+While resources and challenges were more similarly experienced, what is experienced as a hindrance tends to be more variable.
+We further provide additional evidence highlighting the value of perceived resources in the workplace, as they were demonstrated to moderate both challenge-engagement, and hindrance-stress/hindrance burnout relationships.
 

### 2024-07-31 Submission.tex
Preparing Manuscript for journal submission

--- 2024-07-26 Submission.tex
@@
 \documentclass[
-  man,mask]{apa7}
+  man]{apa7}
 \usepackage{amsmath,amssymb}
@@
 \hypersetup{
-  pdftitle={Subjective Experience of Demands and Resources across O*NET Job Elements},
+  pdftitle={Non-exclusive Characteriazations of Demands and Resources across O*NET Job Elements},
+  pdfauthor={Alicia Stachowski2, John Kulas1, \& Renata García Prieto Palacios Roji3},
   pdflang={en-EN},
@@
 \abstract{%
-Much of our understanding of job demands and resources rests on an assumption that some aspects of jobs are resources and some are demands.
-This study documents variability in subjective ratings of O*Net job characteristics with respect to interpretation as resource and demand (defined as challenge/hindrance), and further predicts demands and resources will be differentially related to outcomes of engagement, stress, and burnout.
-We lastly explore the moderating role of resources.
-We found that job characteristics were not uniquely categorized as a resource or demand, but rather, some job characteristics were rated highly as both a resource and a demand.
-We consistently observed a pattern of job characteristics seen as challenging also being cited as a resource.
-While we did not find support for the prediction, that demands were differentially related to stress and burnout, we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships as predicted.
-The findings broadly revealed that there was relatively more consistency in ratings of resource and challenge characteristics, and far more variability in job characteristics rated as hindrance demands.
+Much of our understanding of job demands and resources rests on an assumption that some job characteristics are resources and some are demands.
+This study documents variability in subjective ratings of O*Net job characteristics with respect to interpretation as resource and demand (defined as challenge/hindrance), and further predicts the form of demand will be differentially related to work-relevant outcomes.
+We lastly explore the moderating role of resources on these relationships.
+We found that job characteristics were not uniquely categorized as a resource or demand, but rather, some job characteristics were rated highly as both a resource and a challenge.
+While we did not find support for the prediction that demands were related to stress and burnout, we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships.
+These findings broadly reveal that there is relatively more consistency in ratings of resource and challenge characteristics, and far more variability in job characteristics rated as hindrance demands.
 These findings have implications for job design and management particularly with regard to resource-laden elements that may also be experienced as demanding.
@@
 
+\subsection{Procedure}\label{procedure}
+
+Data were collected through Prolific, an online data collection platform.
+An email was sent to \textbf{a random subset???} of all ``eligible'' members of the Prolific respondent pool, notifying them of their opportunity to participate.
+Eligibility requirements \textbf{included??} being 18 or older and holding either a full-time or part-time job.
+Eligible individuals then voluntarily chose whether or not to respond to the invitation after reading an informed consent.
+
+Participants were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of \textbf{98???} different O*Net job characteristics.
+For example, if a respondent indicated that any one characteristic \textbf{was not} applicable for their job, they were not subsequently asked to rate the level of resource (\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
+Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).
+
 \subsection{Participants}\label{participants}
@@
 
-The Occupational Information Network (O*Net) contains a comprehensive description of occupations (Peterson et al., 2001).
-This widely accessed database houses hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are continually updated.
+The Occupational Information Network (O*Net) serves as a repository of information broadly descriptive of occupations (Peterson et al., 2001).
+The O*Net database consists of hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are frequently updated.
 We focused on 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context statements} which O*Net groups into \emph{activity} categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
@@
 Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we also retained the O*Net wording for our item stems.
-
-\subsection{Procedure}\label{procedure}
-
-Data were collected through Prolific, an online data collection platform.
-An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information.
-Eligibility requirements included being 18 or older and holding either a full-time or part-time job.
-Participants then voluntarily chose to respond to the online survey after reading an informed consent.
-Participants were asked to think about their primary job, and the items they were presented with depended on the specific job characteristics they initially specified.
-Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
-The total number of items on the survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
-Participants were compensated for their participation in this study estimated to require 45 minutes' time in the amount of six dollars through Prolific.
+The total number of items on each administered survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
 
@@
 (2020)'s conclusion that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3).
+While we did not find support for the prediction that different types of demands would be related to stress and burnout, we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships (as predicted).
 
 In addition to the above findings, this paper made several additional important contributions.
-We utilized a diverse sample of employees across industries, who responded to common O*Net items.
+We utilized a diverse sample of employees across industries who responded to common O*Net items.
 While O*Net provides detailed information about frequency and importance ratings among employees, we begin the process of expanding what we know of job characteristics to ratings of demands and resources.
-Further, we provide a repository for other researchers with listing of item level \emph{perceived} demands and resources across activity and context items for the benefit of all future researchers.
-We also explored not only context and activity holistically, but at the dimension level, which enhances our knowledge of how employees perceive different categories of resources, challenges, and hindrances at work, as well as the relationships among them.
+Further, we provide a repository for other researchers with listing of O*Net demands and resources across activity and context items for the benefit of all future researchers.
+We also explored not only context and activity holistically, but at a higher level aggregation, which enhances our knowledge of how employees perceive different categories of resources, challenges, and hindrances within different work dimensions, as well as the relationships among them.
 
@@
 The findings presented above have implications for both theory and practice.
-First, this research is couched within the well-studied job demands-resources theory (Demerouti et al., 2001).
-We argue that static assignment of characteristics as a demand or resource may be useful, additional emphasis should be placed on individual differences in perceptions of job characteristics.
+First, this research is situated within the familiar job demands-resources theory (Demerouti et al., 2001).
+Although the static assignment of characteristics as a demand or resource may be useful, additional emphasis should be placed on differences in perceptions of job characteristics.
 In fact, our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs (Webster et al., 2011).
@@
 Further, Cavanaugh et al.
-(2000) suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes (e.g., Cavanaugh et al., 2000).
+(2000) suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes (e.g., Cavanaugh et al., 2000), which we partially supported here.
 
@@
 For example, having open conversations with employees regarding their subjective perceptions of characteristics that may be unique in limiting their performance or comfort.
-Such conversations could happen during an annual performance review or more informally.
+Such conversations could happen during an annual performance review.
 In addition, J.
@@
 As with all individual studies, this project was limited in scope, and as such, there are a number of avenues for future study worth exploring.
-First, although we aggregated to both literature-derived as well as O*Net groupings, essentially we were dealing with single-item scales.
+First, although we aggregated to O*Net groupings, we were also dealing with single-item measures for much our operationalization.
 Although not ideal psychometrically, this provided a strong linkage to the established O*Net framework.
-Related to that, we intentionally worked within the O*Net database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources/demands.
+Related to that, we intentionally worked within the O*Net database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources and demands.
 Therefore, to the extent that O*Net is not an exhaustive repository, there are existing characteristics that we did not capture.
 For example, O*Net also includes styles and values, which we did not sample.
-Future studies may want to expand to explore these additional aspects of work, and perhaps longitudinally.
+Future studies may want to expand to explore these additional aspects of work.
 

### 2024-08-02 Submission.Rmd
Updating the paper per journal editor request in preparation for review.

@@
 Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.
+
+The next group of hypotheses focuses on the relationship among resources and demands (challenge and hindrance) and outcomes.
+Table 2 shows the overall associations between resource/challenge/hindrances and outcomes of engagement, stress, and burnout.
+Here, we observe positive associations between resources, and challenges with engagement, and a negative association between hindrances and engagement.
+A positive association is observed between hindrances and stress.
 

### 2024-12-30 Submission.Rmd
Updated manuscript per reviewer feedback

@@
 Data were collected through Prolific, an online data collection platform.
-An email was sent to **a random subset???** of all "eligible" members of the Prolific respondent pool, notifying them of their opportunity to participate.
-Eligibility requirements **included??** being 18 or older and holding either a full-time or part-time job.
+An email was sent to eligible members of the Prolific respondent pool, notifying them of their opportunity to participate.
+Eligibility requirements included being 18 or older and holding either a full-time or part-time job.
 Eligible individuals then voluntarily chose whether or not to respond to the invitation after reading an informed consent.
 
-Participants were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of **98???** different O\*Net job characteristics.
-For example, if a respondent indicated that any one characteristic **was not** applicable for their job, they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
+Participants were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of 98 different O\*Net job characteristics.
+For example, if a respondent indicated that any one characteristic was not applicable for their job (e.g., answered *never* or *not at all*), they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
 Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).
@@
 $R^2$ =  `r round(summary(hr_burn_m2)$adj.r.squared, 2)`, `r hr_burn_info2$statistic$modelfit$r2`.
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r hr_burn_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_burn_r_square_change`, $\Delta F$ (`r hr_burn_anova$Df[2]`, `r hr_burn_anova$Res.Df[2]`) = `r hr_burn_anova$F[2]`, supporting the presence of a moderated effect [see Figure \@ref(fig:hind-resource-burn-int)].
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r hr_burn_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_burn_r_square_change`, $\Delta F$ (`r hr_burn_anova$Df[2]`, `r hr_burn_anova$Res.Df[2]`) = `r hr_burn_anova$F[2]`, supporting the presence of a moderated effect (see Figure \@ref(fig:hind-resource-burn-int)).
 As expected, the relationship between hindrance demands and burnout becomes weaker as workers perceive more resources.

### 2024-12-30 Submission.tex
Updated manuscript per reviewer feedback

@@
 Data were collected through Prolific, an online data collection platform.
-An email was sent to \textbf{a random subset???} of all ``eligible'' members of the Prolific respondent pool, notifying them of their opportunity to participate.
-Eligibility requirements \textbf{included??} being 18 or older and holding either a full-time or part-time job.
+An email was sent to eligible members of the Prolific respondent pool, notifying them of their opportunity to participate.
+Eligibility requirements included being 18 or older and holding either a full-time or part-time job.
 Eligible individuals then voluntarily chose whether or not to respond to the invitation after reading an informed consent.
 
-Participants were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of \textbf{98???} different O*Net job characteristics.
-For example, if a respondent indicated that any one characteristic \textbf{was not} applicable for their job, they were not subsequently asked to rate the level of resource (\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
+Participants were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of 98 different O*Net job characteristics.
+For example, if a respondent indicated that any one characteristic was not applicable for their job (e.g., answered \emph{never} or \emph{not at all}), they were not subsequently asked to rate the level of resource (\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
 Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).

### 2025-01-04 Submission.tex
tried applying vancouver style

@@
 While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular.
-We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020).
+We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands {[}1{]} or that appraisals may change over time {[}2{]}.
 Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes.
@@
 
-Two related theories serve as the foundation for the current study: the job demands-resources theory (e.g., Bakker \& Demerouti, 2014, 2017) and Cavanaugh et al.
-(2000)'s challenge-hindrance stressor framework.
-The job demands-resources theory (e.g., Bakker \& Demerouti, 2014, 2017) highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes.
-\emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017).
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001).
-The perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; Bakker and Demerouti (2014)).
+Two related theories serve as the foundation for the current study: the job demands-resources theory {[}e.g., 3,4{]} and {[}5{]}'s challenge-hindrance stressor framework.
+The job demands-resources theory {[}e.g., 3,4{]} highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes.
+\emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development {[}e.g., 3,4{]}.
+In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain {[}high work pressure, for example, is commonly cited as a demand, e.g., 6{]}.
+The perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; {[}3{]}).
 
-Cavanaugh et al.
-(2000) proposed the idea that not all demands are equal with her challenge-hindrance stressor framework, which draws from Lazarus and Folkman (1984)'s perspectives on stress and coping.
+{[}5{]} proposed the idea that not all demands are equal with her challenge-hindrance stressor framework, which draws from {[}7{]}'s perspectives on stress and coping.
 The challenge-hindrance stressor framework distinguishes between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}.
-Both are considered stressors/demands (e.g., Cavanaugh et al., 2000).
+Both are considered stressors/demands {[}e.g., 5{]}.
 Challenge demands promote mastery, personal growth, and future gains -- these demands should lead to coping strategies that facilitate achievement.
-Work characteristics consistent with this definition, for example, include time pressure and responsibility (M.
-A.
-LePine, 2022).
+Work characteristics consistent with this definition, for example, include time pressure and responsibility {[}8{]}.
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Example hindrance demands in a work context include role conflict and role ambiguity (M.
-A.
-LePine, 2022).
+Example hindrance demands in a work context include role conflict and role ambiguity {[}8{]}.
 
-The original work on this topic suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes (e.g., Cavanaugh et al., 2000).
-Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, J.
-A.
-LePine et al.
-(2005) regarding performance and Crawford et al.
-(2010) regarding engagement).
+The original work on this topic suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes {[}e.g., 5{]}.
+Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, {[}9{]} regarding performance and {[}10{]} regarding engagement).
 
-M.
-A.
-LePine (2022) explain the mechanisms by which demands are related to performance and wellbeing outcomes.
+{[}8{]} explain the mechanisms by which demands are related to performance and wellbeing outcomes.
 First, demands appraised as challenges typically result in a more positive appraisal, and engagement is likely to happen as a result.
@@
 Disengagement is likely to result from a hindrance appraisal, which then negatively impacts motivation, performance, growth and wellbeing.
-This happens because resources are depleted via frustrations and other affectively negative reactions (M.
-A.
-LePine, 2022).
+This happens because resources are depleted via frustrations and other affectively negative reactions {[}8{]}.
 
 Recent work affirms these appraisal processes.
-Pindek et al.
-(2024) meta-analyzed diary studies of dynamic demands (i.e., short-term daily experiences of demands) and concluded that daily challenge demands had a positive \emph{direct} association with performance, but a negative \emph{indirect} association with performance through strain (as described by M.
-A.
-LePine (2022) above).
-As expected, hindrance demands had both direct and indirect (through strain) associations with performance (Pindek et al., 2024).
+{[}11{]} meta-analyzed diary studies of dynamic demands (i.e., short-term daily experiences of demands) and concluded that daily challenge demands had a positive \emph{direct} association with performance, but a negative \emph{indirect} association with performance through strain (as described by {[}8{]} above).
+As expected, hindrance demands had both direct and indirect (through strain) associations with performance {[}11{]}.
 
@@
 Interestingly, much of our existing knowledge regarding the way these relationships between resources/demands and outcomes (e.g., stress, engagement) function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands.
-Pindek et al.
-(2024) notes this limitation of \emph{a priori} classification of characteristics as demands, challenges, or hindrances, as do Horan et al.
-(2020).
-In fact, although much of our research on job demands based on \emph{a priori} classifications (Searle \& Auton, 2015), the recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
+{[}11{]} notes this limitation of \emph{a priori} classification of characteristics as demands, challenges, or hindrances, as do {[}12{]}.
+In fact, although much of our research on job demands based on \emph{a priori} classifications {[}13{]}, the recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
 
-Aligned with this dynamic perspective on the experience of work, Horan et al.
-(2020) and M.
-A.
-LePine (2022) specifically call out the need for additional research to incorporate the appraisal process described by Lazarus and Folkman (1984) into the challenge-hindrance stressor framework.
-In fact, Horan et al.
-(2020) state that ``\ldots stressors are only challenge or hindrance demands to the extent that they are perceived as such by employees'' (p.~3).
+Aligned with this dynamic perspective on the experience of work, {[}12{]} and {[}8{]} specifically call out the need for additional research to incorporate the appraisal process described by {[}7{]} into the challenge-hindrance stressor framework.
+In fact, {[}12{]} state that ``\ldots stressors are only challenge or hindrance demands to the extent that they are perceived as such by employees'' (p.~3).
 They go on to suggest future research continue to move away from \emph{a priori} classifications of demands, as doing so can be problematic for theoretical and empirical reasons.
 Theoretically, \emph{a priori} classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
-Empirically, as shown above, we have some evidence suggesting people can appraise a work characteristic as both a hindrance and challenge at the same time (e.g., Searle \& Auton, 2015).
+Empirically, as shown above, we have some evidence suggesting people can appraise a work characteristic as both a hindrance and challenge at the same time {[}e.g., 13{]}.
 
 Given the above, the first question we ask is whether people exclusively categorize resources, challenges, and hindrances, and whether a job characteristics might even be considered simultaneously as more than one of these (e.g., both a challenge and a resource).
-Evidence suggests that employees do, at least, differentiate between challenge and hindrance demands (e.g., Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011).
-For example, Bakker and Sanz-Vergel (2013) found that work pressure was perceived as a hindrance, and emotional demands as more of a challenge.
-Webster et al.
-(2011) approached this question with three commonly implicated workplace demands: workload, role ambiguity, and role conflict.
+Evidence suggests that employees do, at least, differentiate between challenge and hindrance demands {[}1,e.g., 14,15{]}.
+For example, {[}14{]} found that work pressure was perceived as a hindrance, and emotional demands as more of a challenge.
+{[}1{]} approached this question with three commonly implicated workplace demands: workload, role ambiguity, and role conflict.
 They found while that each could be appraised primarily as a challenge or hindrance, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees.
@@
 
-The second set of predictions focus on associations with theory-relevant outcomes across via job demands-resources- (Bakker \& Demerouti, 2017) and challenge-hindrance stressor-frameworks (Cavanaugh et al., 2000).
-Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance (e.g., J.
-A.
-LePine et al., 2005).
+The second set of predictions focus on associations with theory-relevant outcomes across via job demands-resources- {[}4{]} and challenge-hindrance stressor-frameworks {[}5{]}.
+Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance {[}e.g., 9{]}.
 We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout.
 See Figure \ref{fig:ourmodel} for proposed associations.
-Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017), and empirical work suggests that they are associated with positive outcomes.
-Relevant to the current study, for example, Hakanen et al.
-(2008) found job resources influenced future work engagement.
-Moreover, in a sample of teachers and dentists, Bakker et al.
-(2007) found that resources were most predictive of engagement when job demands were especially high.
-Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement (e.g., Schaufeli, 2017).
+Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development {[}e.g., 3,4{]}, and empirical work suggests that they are associated with positive outcomes.
+Relevant to the current study, for example, {[}16{]} found job resources influenced future work engagement.
+Moreover, in a sample of teachers and dentists, {[}17{]} found that resources were most predictive of engagement when job demands were especially high.
+Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement {[}e.g., 18{]}.
 
@@
 The findings regarding demands are more complex, presumably because the way challenge vs.~hindrance appraisals influence coping strategies.
-Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work (Chen et al., 2021), engagement (Crawford et al., 2010), and strain and turnover intentions (e.g., Abbas \& Raja, 2019), for example.
-Challenge appraisals have been negatively associated with job search behaviors (e.g., Cavanaugh et al., 2000).
+Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work {[}19{]}, engagement {[}10{]}, and strain and turnover intentions {[}e.g., 20{]}, for example.
+Challenge appraisals have been negatively associated with job search behaviors {[}e.g., 5{]}.
 
 Hindrance demands (appraisals) have been found to be related to job demands-resources model outcomes such as decreased motivation and increased stress.
-When a demand is appraised as a hindrance -- it is negatively associated with motivational resources (Kim \& Beehr, 2020), engagement (Crawford et al., 2010), job search behaviors and job satisfaction (Cavanaugh et al., 2000).
-Chen et al.
-(2021) found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment.
-Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands (Podsakoff et al., 2007).
-Interestingly, both challenges and hindrances have been shown to positively predict strain (Abbas \& Raja, 2019; J.
-A.
-LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010), which further highlights the complex association between appraisals and subsequent outcomes.
+When a demand is appraised as a hindrance -- it is negatively associated with motivational resources {[}21{]}, engagement {[}10{]}, job search behaviors and job satisfaction {[}5{]}.
+{[}19{]} found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment.
+Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands {[}22{]}.
+Interestingly, both challenges and hindrances have been shown to positively predict strain {[}9,20,22,23{]}, which further highlights the complex association between appraisals and subsequent outcomes.
 Given the differential relationships described above, we make the following predictions (see Figure \ref{fig:ourmodel}):
@@
 
-In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain (e.g., Bakker et al., 2005) and burnout (e.g., Xanthopoulou et al., 2007).
+In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain {[}e.g., 24{]} and burnout {[}e.g., 25{]}.
 Bakker and colleagues (2005) were the first to report empirical evidence to support the idea that job resources could potentially buffer the negative impact of job demands on distal outcomes like burnout.
-Bakker et al.
-(2005) explored the interaction between 4 demands (e.g., work overload, physical demands) and 4 resources (e.g., social support, feedback) and three dimensions of burnout (exhaustion, cynicism, and professional efficacy), and found some support for the prediction that high demands with low resources predicted greater levels of cynicism and exhaustion among employees in higher education.
-Similarly, Xanthopoulou et al.
-(2007) also found some support for this interaction (high demands + low resources leads to greater burnout) among home healthcare employees.
+{[}24{]} explored the interaction between 4 demands (e.g., work overload, physical demands) and 4 resources (e.g., social support, feedback) and three dimensions of burnout (exhaustion, cynicism, and professional efficacy), and found some support for the prediction that high demands with low resources predicted greater levels of cynicism and exhaustion among employees in higher education.
+Similarly, {[}25{]} also found some support for this interaction (high demands + low resources leads to greater burnout) among home healthcare employees.
 They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout.
@@
 
-Of the 785 individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021).
+Of the 785 individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses {[}26{]}.
 Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current sample.
@@
 
-The Occupational Information Network (O*Net) serves as a repository of information broadly descriptive of occupations (Peterson et al., 2001).
+The Occupational Information Network (O*Net) serves as a repository of information broadly descriptive of occupations {[}27{]}.
 The O*Net database consists of hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are frequently updated.
@@
 \(R^2\) = 0.03, \(F(2, 565) = 10.68\), \(p < .001\).
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 9.49\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 6.89, supporting the presence of a moderated effect {[}see Figure \ref{fig:hind-resource-burn-int}{]}.
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 9.49\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 6.89, supporting the presence of a moderated effect (see Figure \ref{fig:hind-resource-burn-int}).
 As expected, the relationship between hindrance demands and burnout becomes weaker as workers perceive more resources.
@@
 The findings broadly revealed that there was relatively more consistency in ratings of resource and challenge characteristics, and far more variability in job characteristics rated as hindrance demands.
-This finding lends additional evidence to Horan et al.
-(2020)'s conclusion that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3).
+This finding lends additional evidence to {[}12{]}'s conclusion that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3).
 While we did not find support for the prediction that different types of demands would be related to stress and burnout, we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships (as predicted).
@@
 The findings presented above have implications for both theory and practice.
-First, this research is situated within the familiar job demands-resources theory (Demerouti et al., 2001).
+First, this research is situated within the familiar job demands-resources theory {[}6{]}.
 Although the static assignment of characteristics as a demand or resource may be useful, additional emphasis should be placed on differences in perceptions of job characteristics.
-In fact, our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs (Webster et al., 2011).
-This finding aligns quite well with both the transactional theory of stress and coping, and the challenge-hindrance stressor framework, which collectively argue that employees perceive stimuli (i.e., job characteristics) uniquely (Lazarus \& Folkman, 1984), and thus, could appraise them as either a challenge or hindrance to their job performance (Cavanaugh et al., 2000).
-Further, Cavanaugh et al.
-(2000) suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes (e.g., Cavanaugh et al., 2000), which we partially supported here.
+In fact, our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs {[}1{]}.
+This finding aligns quite well with both the transactional theory of stress and coping, and the challenge-hindrance stressor framework, which collectively argue that employees perceive stimuli (i.e., job characteristics) uniquely {[}7{]}, and thus, could appraise them as either a challenge or hindrance to their job performance {[}5{]}.
+Further, {[}5{]} suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes {[}e.g., 5{]}, which we partially supported here.
 
@@
 Such conversations could happen during an annual performance review.
-In addition, J.
-A.
-LePine et al.
-(2005) and Podsakoff et al.
-(2007) encourage organizations to incorporate strain-reducing activities like training and support to offset the negative effects of challenging job demands, which may be associated with increased performance in the short term, but strain when prolonged.
+In addition, {[}9{]} and {[}22{]} encourage organizations to incorporate strain-reducing activities like training and support to offset the negative effects of challenging job demands, which may be associated with increased performance in the short term, but strain when prolonged.
 The current results suggest that these activities and training sessions would ideally be personalized.
@@
 
-We also retained the literature-derived definitions of resources, challenges, and hindrances (Demerouti et al., 2001).
+We also retained the literature-derived definitions of resources, challenges, and hindrances {[}6{]}.
 Given the high associations observed between ratings of resource and challenge, it is possible that respondents did not distinguish between these definitions as cleanly as we intended.
@@
 \phantomsection\label{refs}
-\begin{CSLReferences}{1}{0}
-\bibitem[\citeproctext]{ref-abbas2019challenge}
-Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.
+\begin{CSLReferences}{0}{0}
+\bibitem[\citeproctext]{ref-webster2011extending}
+\CSLLeftMargin{{[}1{]} }%
+\CSLRightInline{Webster JR, Beehr TA, Love K. Extending the challenge-hindrance model of occupational stress: The role of appraisal. Journal of Vocational Behavior 2011;79:505--16.}
+
+\bibitem[\citeproctext]{ref-rosen2020challenges}
+\CSLLeftMargin{{[}2{]} }%
+\CSLRightInline{Rosen CC, Dimotakis N, Cole MS, Taylor SG, Simon LS, Smith TA, et al.
+When challenges hinder: An investigation of when and how challenge stressors impact employee outcomes.
+Journal of Applied Psychology 2020;105:1181.}
 
 \bibitem[\citeproctext]{ref-bakker2014job}
-Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
+\CSLLeftMargin{{[}3{]} }%
+\CSLRightInline{Bakker AB, Demerouti E. Job demands--resources theory. Wellbeing: A Complete Reference Guide 2014:1--28.}
 
 \bibitem[\citeproctext]{ref-bakker2017job}
-Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
+\CSLLeftMargin{{[}4{]} }%
+\CSLRightInline{Bakker AB, Demerouti E. Job demands--resources theory: Taking stock and looking forward. Journal of Occupational Health Psychology 2017;22:273.}
+
+\bibitem[\citeproctext]{ref-cavanaugh2000empirical}
+\CSLLeftMargin{{[}5{]} }%
+\CSLRightInline{Cavanaugh MA, Boswell WR, Roehling MV, Boudreau JW. An empirical examination of self-reported work stress among US managers. Journal of Applied Psychology 2000;85:65.}
+
+\bibitem[\citeproctext]{ref-demerouti2001job}
+\CSLLeftMargin{{[}6{]} }%
+\CSLRightInline{Demerouti E, Bakker AB, Nachreiner F, Schaufeli WB. The job demands-resources model of burnout. Journal of Applied Psychology 2001;86:499.}
+
+\bibitem[\citeproctext]{ref-lazarus1984stress}
+\CSLLeftMargin{{[}7{]} }%
+\CSLRightInline{Lazarus RS, Folkman S. Stress, appraisal, and coping. Springer publishing company; 1984.}
+
+\bibitem[\citeproctext]{ref-lepine2022challenge}
+\CSLLeftMargin{{[}8{]} }%
+\CSLRightInline{LePine MA. The challenge-hindrance stressor framework: An integrative conceptual review and path forward. Group \& Organization Management 2022;47:223--54.}
+
+\bibitem[\citeproctext]{ref-lepine2005meta}
+\CSLLeftMargin{{[}9{]} }%
+\CSLRightInline{LePine JA, Podsakoff NP, LePine MA.
+A meta-analytic test of the challenge stressor--hindrance stressor framework: An explanation for inconsistent relationships among stressors and performance.
+Academy of Management Journal 2005;48:764--75.}
+
+\bibitem[\citeproctext]{ref-crawford2010linking}
+\CSLLeftMargin{{[}10{]} }%
+\CSLRightInline{Crawford ER, LePine JA, Rich BL.
+Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test.
+Journal of Applied Psychology 2010;95:834.}
+
+\bibitem[\citeproctext]{ref-pindek2024dynamic}
+\CSLLeftMargin{{[}11{]} }%
+\CSLRightInline{Pindek S, Meyer K, Valvo A, Arvan M.
+A dynamic view of the challenge-hindrance stressor framework: A meta-analysis of daily diary studies.
+Journal of Business and Psychology 2024:1--19.}
+
+\bibitem[\citeproctext]{ref-horan2020review}
+\CSLLeftMargin{{[}12{]} }%
+\CSLRightInline{Horan KA, Nakahara WH, DiStaso MJ, Jex SM.
+A review of the challenge-hindrance stress model: Recent advances, expanded paradigms, and recommendations for future research.
+Frontiers in Psychology 2020;11:560346.}
+
+\bibitem[\citeproctext]{ref-searle2015merits}
+\CSLLeftMargin{{[}13{]} }%
+\CSLRightInline{Searle BJ, Auton JC. The merits of measuring challenge and hindrance appraisals. Anxiety, Stress, \& Coping 2015;28:121--43.}
+
+\bibitem[\citeproctext]{ref-bakker2013weekly}
+\CSLLeftMargin{{[}14{]} }%
+\CSLRightInline{Bakker AB, Sanz-Vergel AI. Weekly work engagement and flourishing: The role of hindrance and challenge job demands. Journal of Vocational Behavior 2013;83:397--409.}
+
+\bibitem[\citeproctext]{ref-gerich2017relevance}
+\CSLLeftMargin{{[}15{]} }%
+\CSLRightInline{Gerich J. The relevance of challenge and hindrance appraisals of working conditions for employees' health. International Journal of Stress Management 2017;24:270.}
+
+\bibitem[\citeproctext]{ref-hakanen2008job}
+\CSLLeftMargin{{[}16{]} }%
+\CSLRightInline{Hakanen JJ, Schaufeli WB, Ahola K.
+The job demands-resources model: A three-year cross-lagged study of burnout, depression, commitment, and work engagement.
+Work \& Stress 2008;22:224--41.}
+
+\bibitem[\citeproctext]{ref-bakker2007job}
+\CSLLeftMargin{{[}17{]} }%
+\CSLRightInline{Bakker AB, Hakanen JJ, Demerouti E, Xanthopoulou D. Job resources boost work engagement, particularly when job demands are high. Journal of Educational Psychology 2007;99:274.}
+
+\bibitem[\citeproctext]{ref-schaufeli2017applying}
+\CSLLeftMargin{{[}18{]} }%
+\CSLRightInline{Schaufeli WB. Applying the job demands-resources model: A `how to'guide to measuring and tackling work engagement and burnout. Organizational Dynamics 2017;46:120--32.}
+
+\bibitem[\citeproctext]{ref-chen2021daily}
+\CSLLeftMargin{{[}19{]} }%
+\CSLRightInline{Chen H, Wang H, Yuan M, Xu S. Daily challenge/hindrance demands and cognitive wellbeing: A multilevel moderated mediation model. Frontiers in Psychology 2021;12:616002.}
+
+\bibitem[\citeproctext]{ref-abbas2019challenge}
+\CSLLeftMargin{{[}20{]} }%
+\CSLRightInline{Abbas M, Raja U. Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. Journal of Business and Psychology 2019;34:189--201.}
+
+\bibitem[\citeproctext]{ref-kim2020thriving}
+\CSLLeftMargin{{[}21{]} }%
+\CSLRightInline{Kim M, Beehr TA. Thriving on demand: Challenging work results in employee flourishing through appraisals and resources. International Journal of Stress Management 2020;27:111.}
+
+\bibitem[\citeproctext]{ref-podsakoff2007differential}
+\CSLLeftMargin{{[}22{]} }%
+\CSLRightInline{Podsakoff NP, LePine JA, LePine MA.
+Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis.
+Journal of Applied Psychology 2007;92:438.}
+
+\bibitem[\citeproctext]{ref-webster2010toward}
+\CSLLeftMargin{{[}23{]} }%
+\CSLRightInline{Webster JR, Beehr TA, Christiansen ND.
+Toward a better understanding of the effects of hindrance and challenge stressors on work behavior.
+Journal of Vocational Behavior 2010;76:68--77.}
 
 \bibitem[\citeproctext]{ref-bakker2005job}
-Bakker, A. B., Demerouti, E., \& Euwema, M. C. (2005). Job resources buffer the impact of job demands on burnout. \emph{Journal of Occupational Health Psychology}, \emph{10}(2), 170.
+\CSLLeftMargin{{[}24{]} }%
+\CSLRightInline{Bakker AB, Demerouti E, Euwema MC. Job resources buffer the impact of job demands on burnout. Journal of Occupational Health Psychology 2005;10:170.}
 
-\bibitem[\citeproctext]{ref-bakker2007job}
-Bakker, A.
-B., Hakanen, J.
-J., Demerouti, E., \& Xanthopoulou, D.
-(2007).
-Job resources boost work engagement, particularly when job demands are high.
-\emph{Journal of Educational Psychology}, \emph{99}(2), 274.
+\bibitem[\citeproctext]{ref-xanthopoulou2007job}
+\CSLLeftMargin{{[}25{]} }%
+\CSLRightInline{Xanthopoulou D, Bakker AB, Dollard MF, Demerouti E, Schaufeli WB, Taris TW, et al.
+When do job demands particularly predict burnout?
+The moderating role of job resources.
+Journal of Managerial Psychology 2007;22:766--86.}
 
-\bibitem[\citeproctext]{ref-bakker2013weekly}
-Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
-
-\bibitem[\citeproctext]{ref-cavanaugh2000empirical}
-Cavanaugh, M.
-A., Boswell, W.
-R., Roehling, M.
-V., \& Boudreau, J.
-W.
-(2000).
-An empirical examination of self-reported work stress among US managers.
-\emph{Journal of Applied Psychology}, \emph{85}(1), 65.
-
-\bibitem[\citeproctext]{ref-chen2021daily}
-Chen, H., Wang, H., Yuan, M., \& Xu, S. (2021). Daily challenge/hindrance demands and cognitive wellbeing: A multilevel moderated mediation model. \emph{Frontiers in Psychology}, \emph{12}, 616002.
-
-\bibitem[\citeproctext]{ref-crawford2010linking}
-Crawford, E.
-R., LePine, J.
-A., \& Rich, B.
-L.
-(2010).
-Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test.
-\emph{Journal of Applied Psychology}, \emph{95}(5), 834.
-
-\bibitem[\citeproctext]{ref-demerouti2001job}
-Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
-
-\bibitem[\citeproctext]{ref-gerich2017relevance}
-Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
-
-\bibitem[\citeproctext]{ref-hakanen2008job}
-Hakanen, J.
-J., Schaufeli, W.
-B., \& Ahola, K.
-(2008).
-The job demands-resources model: A three-year cross-lagged study of burnout, depression, commitment, and work engagement.
-\emph{Work \& Stress}, \emph{22}(3), 224--241.
-
-\bibitem[\citeproctext]{ref-horan2020review}
-Horan, K.
-A., Nakahara, W.
-H., DiStaso, M.
-J., \& Jex, S.
-M.
-(2020).
-A review of the challenge-hindrance stress model: Recent advances, expanded paradigms, and recommendations for future research.
-\emph{Frontiers in Psychology}, \emph{11}, 560346.
-
-\bibitem[\citeproctext]{ref-kim2020thriving}
-Kim, M., \& Beehr, T.
-A.
-(2020).
-Thriving on demand: Challenging work results in employee flourishing through appraisals and resources.
-\emph{International Journal of Stress Management}, \emph{27}(2), 111.
-
-\bibitem[\citeproctext]{ref-lazarus1984stress}
-Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
-
-\bibitem[\citeproctext]{ref-lepine2005meta}
-LePine, J.
-A., Podsakoff, N.
-P., \& LePine, M.
-A.
-(2005).
-A meta-analytic test of the challenge stressor--hindrance stressor framework: An explanation for inconsistent relationships among stressors and performance.
-\emph{Academy of Management Journal}, \emph{48}(5), 764--775.
-
-\bibitem[\citeproctext]{ref-lepine2022challenge}
-LePine, M. A. (2022). The challenge-hindrance stressor framework: An integrative conceptual review and path forward. \emph{Group \& Organization Management}, \emph{47}(2), 223--254.
+\bibitem[\citeproctext]{ref-R-careless}
+\CSLLeftMargin{{[}26{]} }%
+\CSLRightInline{Yentes RD, Wilhelm F. Careless: Procedures for computing indices of careless responding. 2021.}
 
 \bibitem[\citeproctext]{ref-peterson2001understanding}
-Peterson, N.
-G., Mumford, M.
-D., Borman, W.
-C., Jeanneret, P.
-R., Fleishman, E.
-A., Levin, K.
-Y., Campion, M.
-A., Mayfield, M.
-S., Morgeson, F.
-P., Pearlman, K., et al.
-(2001).
+\CSLLeftMargin{{[}27{]} }%
+\CSLRightInline{Peterson NG, Mumford MD, Borman WC, Jeanneret PR, Fleishman EA, Levin KY, et al.
 Understanding work using the occupational information network (o* NET): Implications for practice and research.
-\emph{Personnel Psychology}, \emph{54}(2), 451--492.
-
-\bibitem[\citeproctext]{ref-pindek2024dynamic}
-Pindek, S., Meyer, K., Valvo, A., \& Arvan, M.
-(2024).
-A dynamic view of the challenge-hindrance stressor framework: A meta-analysis of daily diary studies.
-\emph{Journal of Business and Psychology}, 1--19.
-
-\bibitem[\citeproctext]{ref-podsakoff2007differential}
-Podsakoff, N.
-P., LePine, J.
-A., \& LePine, M.
-A.
-(2007).
-Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis.
-\emph{Journal of Applied Psychology}, \emph{92}(2), 438.
-
-\bibitem[\citeproctext]{ref-rosen2020challenges}
-Rosen, C.
-C., Dimotakis, N., Cole, M.
-S., Taylor, S.
-G., Simon, L.
-S., Smith, T.
-A., \& Reina, C.
-S.
-(2020).
-When challenges hinder: An investigation of when and how challenge stressors impact employee outcomes.
-\emph{Journal of Applied Psychology}, \emph{105}(10), 1181.
-
-\bibitem[\citeproctext]{ref-schaufeli2017applying}
-Schaufeli, W. B. (2017). Applying the job demands-resources model: A `how to'guide to measuring and tackling work engagement and burnout. \emph{Organizational Dynamics}, \emph{46}(2), 120--132.
-
-\bibitem[\citeproctext]{ref-searle2015merits}
-Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.
-
-\bibitem[\citeproctext]{ref-webster2010toward}
-Webster, J.
-R., Beehr, T.
-A., \& Christiansen, N.
-D.
-(2010).
-Toward a better understanding of the effects of hindrance and challenge stressors on work behavior.
-\emph{Journal of Vocational Behavior}, \emph{76}(1), 68--77.
-
-\bibitem[\citeproctext]{ref-webster2011extending}
-Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.
-
-\bibitem[\citeproctext]{ref-xanthopoulou2007job}
-Xanthopoulou, D., Bakker, A.
-B., Dollard, M.
-F., Demerouti, E., Schaufeli, W.
-B., Taris, T.
-W., \& Schreurs, P.
-J.
-(2007).
-When do job demands particularly predict burnout?
-The moderating role of job resources.
-\emph{Journal of Managerial Psychology}, \emph{22}(8), 766--786.
-
-\bibitem[\citeproctext]{ref-R-careless}
-Yentes, R. D., \& Wilhelm, F. (2021). \emph{Careless: Procedures for computing indices of careless responding}.
+Personnel Psychology 2001;54:451--92.}
 

### 2025-03-29 Submission.Rmd
tried applying vancouver style
updating paper

@@
 ---
-title             : "Non-exclusive Characteriazations of Demands and Resources across O*NET Job Elements"
+title             : "Non-exclusive Characterizations of Demands and Resources across O*NET Job Elements"
 shorttitle        : "O*NET JD-R"
@@
 
-## The Job Demands-Resources Theory and Challenge-Hindrance Stressor Framework
-
-Two related theories serve as the foundation for the current study: the job demands-resources theory [e.g., @bakker2014job; @bakker2017job] and @cavanaugh2000empirical's challenge-hindrance stressor framework.
-The job demands-resources theory [e.g., @bakker2014job; @bakker2017job] highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes.
-*Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job].
+## The Challenge-Hindrance Stressor Framework
+
+@cavanaugh2000empirical's challenge-hindrance stressor framework serves as the theoretical foundation for this work.
+First, *resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job].
 In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [high work pressure, for example, is commonly cited as a demand, e.g., @demerouti2001job].
 The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job).
-
-@cavanaugh2000empirical proposed the idea that not all demands are equal with her challenge-hindrance stressor framework, which draws from @lazarus1984stress's perspectives on stress and coping.
-The challenge-hindrance stressor framework distinguishes between *two forms* of demands -- *challenges* and *hindrances*.
-Both are considered stressors/demands [e.g., @cavanaugh2000empirical].
+@cavanaugh2000empirical proposed the challenge-hindrance stressor framework distinguishes between *two forms* of demands -- *challenges* and *hindrances*.
 Challenge demands promote mastery, personal growth, and future gains – these demands should lead to coping strategies that facilitate achievement.
@@
 The original work on this topic suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes [e.g., @cavanaugh2000empirical].
-Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, @lepine2005meta regarding performance and @crawford2010linking regarding engagement).
+Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, @lepine2005meta regarding performance and @crawford2010linking regarding engagement), although there have been criticisms of this framework [e.g., @mazzola2019should; @kubicek2023all].
 
@@
 
-## Are Perceptions of Job Resources, Challenge Demands, and Hindrance Demands Universal?
-
 Interestingly, much of our existing knowledge regarding the way these relationships between resources/demands and outcomes (e.g., stress, engagement) function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands.
@@
 
-Aligned with this dynamic perspective on the experience of work, @horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process described by @lazarus1984stress into the challenge-hindrance stressor framework.
+Aligned with this dynamic perspective on the experience of work, @horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process into the challenge-hindrance stressor framework.
 In fact, @horan2020review state that “…stressors are only challenge or hindrance demands to the extent that they are perceived as such by employees” (p.
@@
 They go on to suggest future research continue to move away from *a priori* classifications of demands, as doing so can be problematic for theoretical and empirical reasons.
-Theoretically, *a priori* classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
 Empirically, as shown above, we have some evidence suggesting people can appraise a work characteristic as both a hindrance and challenge at the same time [e.g., @searle2015merits].
@@
 
-The second set of predictions focus on associations with theory-relevant outcomes across via job demands-resources- [@bakker2017job] and challenge-hindrance stressor-frameworks [@cavanaugh2000empirical].
-Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance [e.g., @lepine2005meta].
+IS THIS TOO CLOSELY TIED TO THE JOB DEMANDS RESOURCES THEORY? CHECK
+
+The second set of predictions focus on associations with theory-relevant outcomes of the challenge-hindrance stressor-frameworks [@cavanaugh2000empirical].
+The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance [e.g., @lepine2005meta].
 We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout.
@@
 
+AGAIN, CHECK TO SEE IF THIS IS TOO CLOSELY ALIGNED WITH JDR RATHER THAN CHALLENGE-HINDRANCE
+
 In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain [e.g., @bakker2005job] and burnout [e.g., @xanthopoulou2007job].
@@
 
-## Procedure
-
-Data were collected through Prolific, an online data collection platform.
-An email was sent to eligible members of the Prolific respondent pool, notifying them of their opportunity to participate.
-Eligibility requirements included being 18 or older and holding either a full-time or part-time job.
-Eligible individuals then voluntarily chose whether or not to respond to the invitation after reading an informed consent.
-
-Participants were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of 98 different O\*Net job characteristics.
-For example, if a respondent indicated that any one characteristic was not applicable for their job (e.g., answered *never* or *not at all*), they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
-Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).
-
 ## Participants
 
-Of the `r nrow(use)` individuals who initially accessed the survey link, `r nrow(different)` indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses [@R-careless].
-Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of `r nrow(data)` respondents who constitute the current sample.
+The final usable sample consisted of `r nrow(data)`.
 Regarding tenure, `r round(a[1,3],2)`% had been in their referent job less than 6 months, `r round(a[2,3],1)`% between 6 months and a year, `r round(a[3,3],2)`% between one and five years, `r round(a[4,3],2)`% between 5 and 10 years, and `r round(a[5,3],2)`% more than 10 years.
@@
 
+Characteristics, Challenge Demands, Hindrance Demands, and Resources.
 The Occupational Information Network (O\*Net) serves as a repository of information broadly descriptive of occupations [@peterson2001understanding].
@@
 
+Participants were asked to think about whether or not their job could be described as consisting of 98 different O\*Net job characteristics.
+For example, if a respondent indicated that any one characteristic was not applicable for their job (e.g., answered *never* or *not at all*), they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
+Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).
+
+Stress.
+Stress was captured via three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019).
+Responses were provided using a Likert-type scale ranging from (1) Not at All to (5) All the Time.
+A sample item is, “How often have you had problems relaxing because of your job?”.
+Obtained alpha was .85 in this sample.
+
+Burnout.
+Four items from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019) were used to assess burnout.
+Again, responses were provided using a Likert-type scale ranging from (1) Not at All to (5) All the Time.
+A sample item is, “How often have you felt worn out?”.
+Alpha was 0.85 in this sample.
+
+Engagement. The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample 𝛼’s of
+0.68 (absorption) and 0.80 (vigor), and 0.90 (dedication).
+Responses were provided using a Likert-type scale ranging from (1) Strongly Disagree to (6) Strongly Agree.
+A sample item is, “I enjoy thinking about work even when I'm not at work”.
+For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).
+
+## Procedure
+
+Data were collected through Prolific, an online data collection platform.
+An email was sent to eligible members of the Prolific respondent pool, notifying them of their opportunity to participate.
+Eligibility requirements included being 18 or older and holding either a full-time or part-time job.
+Eligible individuals then voluntarily chose whether or not to respond to the invitation after reading an informed consent.
+
+Participants were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of 98 different O\*Net job characteristics in randomized order.
+Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).
+
 # Results
+
+Of the `r nrow(use)` individuals who initially accessed the survey link, `r nrow(different)` indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses [@R-careless].
+Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of `r nrow(data)` respondents who constitute the current sample.
 
@@
 The findings presented above have implications for both theory and practice.
-First, this research is situated within the familiar job demands-resources theory [@demerouti2001job].
-Although the static assignment of characteristics as a demand or resource may be useful, additional emphasis should be placed on differences in perceptions of job characteristics.
-In fact, our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs [@webster2011extending].
-This finding aligns quite well with both the transactional theory of stress and coping, and the challenge-hindrance stressor framework, which collectively argue that employees perceive stimuli (i.e., job characteristics) uniquely [@lazarus1984stress], and thus, could appraise them as either a challenge or hindrance to their job performance [@cavanaugh2000empirical].
+our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs [@webster2011extending].
+This finding aligns quite well with the challenge-hindrance stressor framework, which collectively argue that employees perceive stimuli (i.e., job characteristics) uniquely [@lazarus1984stress], and thus, could appraise them as either a challenge or hindrance to their job performance [@cavanaugh2000empirical].
 Further, @cavanaugh2000empirical suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes [e.g., @cavanaugh2000empirical], which we partially supported here.
@@
 
-In sum, this endeavor builds on the job-demands-resources, and challenge-hindrance stressor literature from a unique lens from within a universally accessible framework.
+In sum, this endeavor builds on the challenge-hindrance stressor literature from a unique lens from within a universally accessible framework.
 We showed that there are far more individual differences in how employees perceive demands and resources than much of our current research suggests.

### 2025-03-29 Submission.tex
updating paper

@@
 \hypersetup{
-  pdftitle={Non-exclusive Characteriazations of Demands and Resources across O*NET Job Elements},
+  pdftitle={Non-exclusive Characterizations of Demands and Resources across O*NET Job Elements},
   pdfauthor={Alicia Stachowski2, John Kulas1, \& Renata García Prieto Palacios Roji3},
@@
 
-\title{Non-exclusive Characteriazations of Demands and Resources across O*NET Job Elements}
+\title{Non-exclusive Characterizations of Demands and Resources across O*NET Job Elements}
 \author{Alicia Stachowski\textsuperscript{2}, John Kulas\textsuperscript{1}, \& Renata García Prieto Palacios Roji\textsuperscript{3}}
@@
 
-\subsection{The Job Demands-Resources Theory and Challenge-Hindrance Stressor Framework}\label{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}
+\subsection{The Challenge-Hindrance Stressor Framework}\label{the-challenge-hindrance-stressor-framework}
 
-Two related theories serve as the foundation for the current study: the job demands-resources theory (e.g., Bakker \& Demerouti, 2014, 2017) and Cavanaugh et al.
-(2000)'s challenge-hindrance stressor framework.
-The job demands-resources theory (e.g., Bakker \& Demerouti, 2014, 2017) highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes.
-\emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017).
+Cavanaugh et al.
+(2000)'s challenge-hindrance stressor framework serves as the theoretical foundation for this work.
+First, \emph{resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017).
 In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001).
 The perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; Bakker and Demerouti (2014)).
-
 Cavanaugh et al.
-(2000) proposed the idea that not all demands are equal with her challenge-hindrance stressor framework, which draws from Lazarus and Folkman (1984)'s perspectives on stress and coping.
-The challenge-hindrance stressor framework distinguishes between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}.
-Both are considered stressors/demands (e.g., Cavanaugh et al., 2000).
+(2000) proposed the challenge-hindrance stressor framework distinguishes between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}.
 Challenge demands promote mastery, personal growth, and future gains -- these demands should lead to coping strategies that facilitate achievement.
@@
 (2005) regarding performance and Crawford et al.
-(2010) regarding engagement).
+(2010) regarding engagement), although there have been criticisms of this framework (Kubicek et al., 2023; e.g., Mazzola \& Disselhorst, 2019).
 
@@
 
-\subsection{Are Perceptions of Job Resources, Challenge Demands, and Hindrance Demands Universal?}\label{are-perceptions-of-job-resources-challenge-demands-and-hindrance-demands-universal}
-
 Interestingly, much of our existing knowledge regarding the way these relationships between resources/demands and outcomes (e.g., stress, engagement) function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands.
@@
 A.
-LePine (2022) specifically call out the need for additional research to incorporate the appraisal process described by Lazarus and Folkman (1984) into the challenge-hindrance stressor framework.
+LePine (2022) specifically call out the need for additional research to incorporate the appraisal process into the challenge-hindrance stressor framework.
 In fact, Horan et al.
@@
 They go on to suggest future research continue to move away from \emph{a priori} classifications of demands, as doing so can be problematic for theoretical and empirical reasons.
-Theoretically, \emph{a priori} classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component.
 Empirically, as shown above, we have some evidence suggesting people can appraise a work characteristic as both a hindrance and challenge at the same time (e.g., Searle \& Auton, 2015).
@@
 
-The second set of predictions focus on associations with theory-relevant outcomes across via job demands-resources- (Bakker \& Demerouti, 2017) and challenge-hindrance stressor-frameworks (Cavanaugh et al., 2000).
-Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance (e.g., J.
+IS THIS TOO CLOSELY TIED TO THE JOB DEMANDS RESOURCES THEORY? CHECK
+
+The second set of predictions focus on associations with theory-relevant outcomes of the challenge-hindrance stressor-frameworks (Cavanaugh et al., 2000).
+The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance (e.g., J.
 A.
@@
 
+AGAIN, CHECK TO SEE IF THIS IS TOO CLOSELY ALIGNED WITH JDR RATHER THAN CHALLENGE-HINDRANCE
+
 In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain (e.g., Bakker et al., 2005) and burnout (e.g., Xanthopoulou et al., 2007).
@@
 
-\subsection{Procedure}\label{procedure}
-
-Data were collected through Prolific, an online data collection platform.
-An email was sent to eligible members of the Prolific respondent pool, notifying them of their opportunity to participate.
-Eligibility requirements included being 18 or older and holding either a full-time or part-time job.
-Eligible individuals then voluntarily chose whether or not to respond to the invitation after reading an informed consent.
-
-Participants were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of 98 different O*Net job characteristics.
-For example, if a respondent indicated that any one characteristic was not applicable for their job (e.g., answered \emph{never} or \emph{not at all}), they were not subsequently asked to rate the level of resource (\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
-Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).
-
 \subsection{Participants}\label{participants}
 
-Of the 785 individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021).
-Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current sample.
+The final usable sample consisted of 568.
 Regarding tenure, 13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.
@@
 
+Characteristics, Challenge Demands, Hindrance Demands, and Resources.
 The Occupational Information Network (O*Net) serves as a repository of information broadly descriptive of occupations (Peterson et al., 2001).
@@
 
+Participants were asked to think about whether or not their job could be described as consisting of 98 different O*Net job characteristics.
+For example, if a respondent indicated that any one characteristic was not applicable for their job (e.g., answered \emph{never} or \emph{not at all}), they were not subsequently asked to rate the level of resource (\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
+Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).
+
+Stress.
+Stress was captured via three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019).
+Responses were provided using a Likert-type scale ranging from (1) Not at All to (5) All the Time.
+A sample item is, ``How often have you had problems relaxing because of your job?''.
+Obtained alpha was .85 in this sample.
+
+Burnout.
+Four items from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019) were used to assess burnout.
+Again, responses were provided using a Likert-type scale ranging from (1) Not at All to (5) All the Time.
+A sample item is, ``How often have you felt worn out?''.
+Alpha was 0.85 in this sample.
+
+Engagement. The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample 𝛼's of
+0.68 (absorption) and 0.80 (vigor), and 0.90 (dedication).
+Responses were provided using a Likert-type scale ranging from (1) Strongly Disagree to (6) Strongly Agree.
+A sample item is, ``I enjoy thinking about work even when I'm not at work''.
+For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).
+
+\subsection{Procedure}\label{procedure}
+
+Data were collected through Prolific, an online data collection platform.
+An email was sent to eligible members of the Prolific respondent pool, notifying them of their opportunity to participate.
+Eligibility requirements included being 18 or older and holding either a full-time or part-time job.
+Eligible individuals then voluntarily chose whether or not to respond to the invitation after reading an informed consent.
+
+Participants were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of 98 different O*Net job characteristics in randomized order.
+Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).
+
 \section{Results}\label{results}
+
+Of the 785 individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021).
+Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current sample.
 
@@
 The findings presented above have implications for both theory and practice.
-First, this research is situated within the familiar job demands-resources theory (Demerouti et al., 2001).
-Although the static assignment of characteristics as a demand or resource may be useful, additional emphasis should be placed on differences in perceptions of job characteristics.
-In fact, our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs (Webster et al., 2011).
-This finding aligns quite well with both the transactional theory of stress and coping, and the challenge-hindrance stressor framework, which collectively argue that employees perceive stimuli (i.e., job characteristics) uniquely (Lazarus \& Folkman, 1984), and thus, could appraise them as either a challenge or hindrance to their job performance (Cavanaugh et al., 2000).
+our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs (Webster et al., 2011).
+This finding aligns quite well with the challenge-hindrance stressor framework, which collectively argue that employees perceive stimuli (i.e., job characteristics) uniquely (Lazarus \& Folkman, 1984), and thus, could appraise them as either a challenge or hindrance to their job performance (Cavanaugh et al., 2000).
 Further, Cavanaugh et al.
@@
 
+\bibitem[\citeproctext]{ref-kubicek2023all}
+Kubicek, B., Uhlig, L., Hülsheger, U.
+R., Korunka, C., \& Prem, R.
+(2023).
+Are all challenge stressors beneficial for learning?
+A meta-analytical assessment of differential effects of workload and cognitive demands.
+\emph{Work \& Stress}, \emph{37}(3), 269--298.
+
 \bibitem[\citeproctext]{ref-lazarus1984stress}
@@
 LePine, M. A. (2022). The challenge-hindrance stressor framework: An integrative conceptual review and path forward. \emph{Group \& Organization Management}, \emph{47}(2), 223--254.
+
+\bibitem[\citeproctext]{ref-mazzola2019should}
+Mazzola, J.
+J., \& Disselhorst, R.
+(2019).
+Should we be {``challenging''} employees?: A critical review and meta-analysis of the challenge-hindrance model of stress.
+\emph{Journal of Organizational Behavior}, \emph{40}(8), 949--961.
 

### 2025-04-14 SIOP2023/Counts/convergence.tex
Editing the full paper again.

@@
 % Make \paragraph and \subparagraph free-standing
+\makeatletter
 \ifx\paragraph\undefined\else
   \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+  \renewcommand{\paragraph}{
+    \@ifstar
+      \xxxParagraphStar
+      \xxxParagraphNoStar
+  }
+  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
+  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
 \fi
@@
   \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+  \renewcommand{\subparagraph}{
+    \@ifstar
+      \xxxSubParagraphStar
+      \xxxSubParagraphNoStar
+  }
+  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
+  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
 \fi
+\makeatother
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
 \newlength{\cslhangindent}
@@
   {\xapptocmd\section
-    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi: #1}}
     {}{\InnerPatchFailed}%
@@
 {}{\PatchFailed}
+\makeatother
 \keywords{keywords\newline\indent Word count: X}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{bookmark}
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 
-\hypertarget{could-a-work-demand-be-appraised-positively-the-challenge-hindrance-framework}{%
-\subsection{Could a Work Demand be Appraised ``Positively''?: The Challenge-Hindrance Framework}\label{could-a-work-demand-be-appraised-positively-the-challenge-hindrance-framework}}
+\subsection{Could a Work Demand be Appraised ``Positively''?: The Challenge-Hindrance Framework}\label{could-a-work-demand-be-appraised-positively-the-challenge-hindrance-framework}
 
@@
 
-\hypertarget{current-study-and-hypotheses}{%
-\subsection{Current Study and Hypotheses}\label{current-study-and-hypotheses}}
+\subsection{Current Study and Hypotheses}\label{current-study-and-hypotheses}
 
@@
 
-\hypertarget{value-of-consulting-onet.}{%
-\subsubsection{Value of consulting O*Net.}\label{value-of-consulting-onet.}}
+\subsubsection{Value of consulting O*Net.}\label{value-of-consulting-onet.}
 
@@
 
-\hypertarget{method}{%
-\section{Method}\label{method}}
+\section{Method}\label{method}
 
@@
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+\subsection{Participants}\label{participants}
 
@@
 
-\hypertarget{resource-challenge-and-hindrance-associations}{%
-\subsection{Resource, Challenge, and Hindrance Associations}\label{resource-challenge-and-hindrance-associations}}
+\subsection{Resource, Challenge, and Hindrance Associations}\label{resource-challenge-and-hindrance-associations}
 
@@
 
-\hypertarget{convergence-same-characteristic.}{%
-\subsubsection{Convergence (same characteristic).}\label{convergence-same-characteristic.}}
+\subsubsection{Convergence (same characteristic).}\label{convergence-same-characteristic.}
 
@@
 
-\hypertarget{references}{%
-\section*{References}\label{references}}
+\section*{References}\label{references}
 \addcontentsline{toc}{section}{References}
 
-\hypertarget{refs}{}
+\phantomsection\label{refs}
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
+\bibitem[\citeproctext]{ref-bakker2014job}
 Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
+\bibitem[\citeproctext]{ref-bakker2017job}
 Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
+\bibitem[\citeproctext]{ref-bakker2013weekly}
 Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
 
-\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
+\bibitem[\citeproctext]{ref-cavanaugh2000empirical}
 Cavanaugh, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-crawford2010linking}{}}%
+\bibitem[\citeproctext]{ref-crawford2010linking}
 Crawford, E.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
+\bibitem[\citeproctext]{ref-demerouti2001job}
 Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
 
-\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
+\bibitem[\citeproctext]{ref-peterson2001understanding}
 Peterson, N.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-selye1936syndrome}{}}%
+\bibitem[\citeproctext]{ref-selye1936syndrome}
 Selye, H. (1936). A syndrome produced by diverse nocuous agents. \emph{Nature}, \emph{138}(3479), 32--32.
 
-\leavevmode\vadjust pre{\hypertarget{ref-selye1974stress}{}}%
+\bibitem[\citeproctext]{ref-selye1974stress}
 Selye, H. (1974). \emph{Stress without distress}. Lippincott Williams \& Wilkins.
 
-\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
+\bibitem[\citeproctext]{ref-webster2011extending}
 Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.

### 2025-04-14 Submission.Rmd
updating paper
Editing the full paper again.

@@
 classoption       : "man"
-#output            : "word_document"
-output            : papaja::apa6_pdf
-
+output:
+  papaja::apa6_pdf:
+    latex_engine: xelatex 
 ---
@@
 While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular.
-We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges].
+We build on a growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges].
 Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes.
@@
 
-## The Challenge-Hindrance Stressor Framework
-
-@cavanaugh2000empirical's challenge-hindrance stressor framework serves as the theoretical foundation for this work.
-First, *resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job].
-In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [high work pressure, for example, is commonly cited as a demand, e.g., @demerouti2001job].
+## Theoretical Foundations
+
+The job demands-resources theory (e.g., Bakker & Demerouti, 2014; 2017) highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes.
+Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job].
+In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001).
+Demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [high work pressure, for example, is commonly cited as a demand, e.g., @demerouti2001job].
 The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job).
+
 @cavanaugh2000empirical proposed the challenge-hindrance stressor framework distinguishes between *two forms* of demands -- *challenges* and *hindrances*.
@@
 
-IS THIS TOO CLOSELY TIED TO THE JOB DEMANDS RESOURCES THEORY? CHECK
-
-The second set of predictions focus on associations with theory-relevant outcomes of the challenge-hindrance stressor-frameworks [@cavanaugh2000empirical].
-The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance [e.g., @lepine2005meta].
+he second set of predictions focus on associations with theory-relevant outcomes across via job demands-resources- @bakker2017job and challenge-hindrance stressor-frameworks @cavanaugh2000empirical.
+Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance [e.g., @lepine2005meta].
 We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout.
@@
 
-AGAIN, CHECK TO SEE IF THIS IS TOO CLOSELY ALIGNED WITH JDR RATHER THAN CHALLENGE-HINDRANCE
-
 In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain [e.g., @bakker2005job] and burnout [e.g., @xanthopoulou2007job].
@@
 
+```{r workcat, fig.cap="Percent agreement (resource and challenge) across O*Net occupational categories (previous was across 84 O/*Net items - this is across 568 individual workers).", fig.height=10}
+
+## Job classifications
+
+workers <- read.csv("workers.csv")             ## Probably need to revisit our coding - 10/14/22
+
+# ggplot(workers, aes(O.Net.Job.Family.Categories))+
+#   geom_histogram(stat="count") + coord_flip()
+
+## Combining categories
+
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Transportation and Material Moving"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Protective Service"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Production"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Personal Care and Service"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Installation Maintenance and Repair"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Food Preparation and Serving Related"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Farming Fishing and Forestry"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Construction and Extraction"] <- "Physical Labor"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Building and Grounds Cleaning and Maintenance"] <- "Physical Labor"
+
+## with Alicia 12/1
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Architecture and Engineering"] <- "Computer & Engineering"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Computer and Mathematical"] <- "Computer & Engineering"
+
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Life Physical and Social Science"] <- "Education, Science & Health"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Educational Instruction and Library"] <- "Education, Science & Health"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Healthcare Practitioner and Technical"] <- "Education, Science & Health"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Community and Social Service"] <- "Education, Science & Health"
+
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Office and Administrative Support"] <- "Admin, Healthcare & Legal"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Legal"] <- "Admin, Healthcare & Legal"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Healthcare Support"] <- "Admin, Healthcare & Legal"
+
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Arts Design Entertainment Sports Media"] <- "Other"
+workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Military Specific"] <- "Other"
+
+#3 in plot all categories, combined and standalone
+
+#ggplot(workers, aes(O.Net.Job.Family.Categories)) +
+#  geom_histogram(stat="count") + coord_flip()
+
+forworkers2 <- anova[,c(2:85)]
+dataworker <- cbind(forworkers2,workers$O.Net.Job.Family.Categories)    ## to repeat O*Net analyses
+                                     ## This gets worker info into convergence file
+
+dataworker$overall <- rowMeans(dataworker[1:84], na.rm=TRUE)
+
+names(dataworker)[names(dataworker) == 'workers$O.Net.Job.Family.Categories'] <- 'JobFamily'
+
+ggplot(dataworker, aes(x=overall)) + geom_histogram() + facet_wrap(~JobFamily, nrow=8)
+
+workeraov <- aov(overall ~ JobFamily, data=dataworker)
+
+library(lsr)  ## for eta squared
+effect.size <- etaSquared(workeraov)
+
 ```{r resourcesagree, fig.cap="Characteristics most similarly viewed as resources (lowest standard deviations)."}
@@
 The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand.
-Table 1 provides the correlations among the O\*Net "scale"-level groupings across ratings of resource, challenge, and hindrance.
+Table 1 provides the correlations among the O\*Net "scale"-level groupings across ratings of resource, challenge, and hindrance (i.e., Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)).
 We would expect to see minimal correlations if job characteristics *were* uniquely categorized.
@@
               escape=FALSE,
-              note="* = p < .05; ** = p < .01")
+              note="* = p < .05; ** = p < .01, coefficients are unstandardized and mean-centered")
 ```
@@
                  escape=FALSE,
-                 note="* = p < .05; ** = p < .01")
+                 note="* = p < .05; ** = p < .01, coefficients are unstandardized and mean-centered")
 ```
@@
 #running it with unstandardized bs here. 
-cr_eng_m3u <- lm(engagement ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, modreg)
+cr_eng_m3u <- lm(engagement ~ overall.challenge + overall.resource + overall.challenge*overall.resource, modreg)
 #summary(cr_eng_m3u)
 
-cr_eng_plot <- interact_plot(cr_eng_m3u, pred = overall.challenge_center, modx = overall.resource_center, interval = FALSE,
+cr_eng_plot <- interact_plot(cr_eng_m3u, pred = overall.challenge, modx = overall.resource, interval = FALSE,
               int.width = 0.8, x.label = "Challenge", legend.main = "Resource", y.label = "Engagement")
@@
 
-hr_stress_m3u <- lm(stress ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, modreg)
+hr_stress_m3u <- lm(stress ~ overall.hindrance + overall.resource + overall.hindrance*overall.resource, modreg)
 #summary(hr_stress_m3u)
 
-hr_stress_plot <- interact_plot(hr_stress_m3u, pred = overall.hindrance_center, modx = overall.resource_center, interval = FALSE, 
+hr_stress_plot <- interact_plot(hr_stress_m3u, pred = overall.hindrance, modx = overall.resource, interval = FALSE, 
               int.width = 0.8, x.label = "Hindrance", legend.main = "Resource", y.label = "Stress")
@@
 
-hr_burn_m3u <- lm(burnout ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, modreg)
+hr_burn_m3u <- lm(burnout ~ overall.hindrance + overall.resource + overall.hindrance*overall.resource, modreg)
 #summary(hr_burn_m3u)
 
-hr_burn_plot <- interact_plot(hr_burn_m3u, pred = overall.hindrance_center, modx = overall.resource_center, interval = FALSE, 
+hr_burn_plot <- interact_plot(hr_burn_m3u, pred = overall.hindrance, modx = overall.resource, interval = FALSE, 
               int.width = 0.8, x.label = "Hindrance", legend.main = "Resource", y.label = "Burnout")
@@
 We utilized a diverse sample of employees across industries who responded to common O\*Net items.
-While O\*Net provides detailed information about frequency and importance ratings among employees, we begin the process of expanding what we know of job characteristics to ratings of demands and resources.
+While O\*Net provides detailed information about frequency and importance ratings among employees, we begin the process of expanding what we know of job characteristics to ratings of an extensive range of demands and resources.
 Further, we provide a repository for other researchers with listing of O\*Net demands and resources across activity and context items for the benefit of all future researchers.
@@
 
+Another interesting avenue for future research is to explore these patterns by job type.
+@kubicek2023all, for instance, found that employee workload was positively related to strain, and that this relationship was stronger for care and social workers compared to other types of employees.
+This finding suggests that job type may be an important moderator, and worthy of exploration moving forward.
+
 Lastly, there may be some practical utility to pursue training interventions aimed at *how* characteristics are appraised.

### 2025-04-14 Submission.tex
updating paper
Editing the full paper again.

@@
   \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+  \renewcommand{\subparagraph}{
+    \@ifstar
+      \xxxSubParagraphStar
+      \xxxSubParagraphNoStar
+  }
+  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
+  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
 \fi
+\makeatother
 % definitions for citeproc citations
@@
 {}{\PatchFailed}
+\makeatother
 \keywords{O*Net, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: 4,942}
@@
 While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular.
-We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020).
+We build on a growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020).
 Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes.
@@
 
-\subsection{The Challenge-Hindrance Stressor Framework}\label{the-challenge-hindrance-stressor-framework}
+\subsection{Theoretical Foundations}\label{theoretical-foundations}
 
-Cavanaugh et al.
-(2000)'s challenge-hindrance stressor framework serves as the theoretical foundation for this work.
-First, \emph{resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017).
+The job demands-resources theory (e.g., Bakker \& Demerouti, 2014; 2017) highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes.
+Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017).
 In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001).
+Demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001).
 The perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; Bakker and Demerouti (2014)).
+
 Cavanaugh et al.
@@
 
-IS THIS TOO CLOSELY TIED TO THE JOB DEMANDS RESOURCES THEORY? CHECK
-
-The second set of predictions focus on associations with theory-relevant outcomes of the challenge-hindrance stressor-frameworks (Cavanaugh et al., 2000).
-The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance (e.g., J.
+he second set of predictions focus on associations with theory-relevant outcomes across via job demands-resources- Bakker and Demerouti (2017) and challenge-hindrance stressor-frameworks Cavanaugh et al.
+(2000).
+Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance (e.g., J.
 A.
@@
 \end{quote}
-
-AGAIN, CHECK TO SEE IF THIS IS TOO CLOSELY ALIGNED WITH JDR RATHER THAN CHALLENGE-HINDRANCE
 
@@
 The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand.
-Table 1 provides the correlations among the O*Net ``scale''-level groupings across ratings of resource, challenge, and hindrance.
+Table 1 provides the correlations among the O*Net ``scale''-level groupings across ratings of resource, challenge, and hindrance (i.e., Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)).
 We would expect to see minimal correlations if job characteristics \emph{were} uniquely categorized.
@@
 \begin{tablenotes}[para]
-\normalsize{\textit{Note.} * = p < .05; ** = p < .01}
+\normalsize{\textit{Note.} * = p < .05; ** = p < .01, coefficients are unstandardized and mean-centered}
 \end{tablenotes}
@@
 We utilized a diverse sample of employees across industries who responded to common O*Net items.
-While O*Net provides detailed information about frequency and importance ratings among employees, we begin the process of expanding what we know of job characteristics to ratings of demands and resources.
+While O*Net provides detailed information about frequency and importance ratings among employees, we begin the process of expanding what we know of job characteristics to ratings of an extensive range of demands and resources.
 Further, we provide a repository for other researchers with listing of O*Net demands and resources across activity and context items for the benefit of all future researchers.

### 2025-04-14 Submission.Rmd
omitting one extra analysis

@@
 Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of `r nrow(data)` respondents who constitute the current sample.
-
-```{r workcat, fig.cap="Percent agreement (resource and challenge) across O*Net occupational categories (previous was across 84 O/*Net items - this is across 568 individual workers).", fig.height=10}
-
-## Job classifications
-
-workers <- read.csv("workers.csv")             ## Probably need to revisit our coding - 10/14/22
-
-# ggplot(workers, aes(O.Net.Job.Family.Categories))+
-#   geom_histogram(stat="count") + coord_flip()
-
-## Combining categories
-
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Transportation and Material Moving"] <- "Physical Labor"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Protective Service"] <- "Physical Labor"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Production"] <- "Physical Labor"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Personal Care and Service"] <- "Physical Labor"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Installation Maintenance and Repair"] <- "Physical Labor"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Food Preparation and Serving Related"] <- "Physical Labor"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Farming Fishing and Forestry"] <- "Physical Labor"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Construction and Extraction"] <- "Physical Labor"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Building and Grounds Cleaning and Maintenance"] <- "Physical Labor"
-
-## with Alicia 12/1
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Architecture and Engineering"] <- "Computer & Engineering"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Computer and Mathematical"] <- "Computer & Engineering"
-
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Life Physical and Social Science"] <- "Education, Science & Health"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Educational Instruction and Library"] <- "Education, Science & Health"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Healthcare Practitioner and Technical"] <- "Education, Science & Health"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Community and Social Service"] <- "Education, Science & Health"
-
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Office and Administrative Support"] <- "Admin, Healthcare & Legal"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Legal"] <- "Admin, Healthcare & Legal"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Healthcare Support"] <- "Admin, Healthcare & Legal"
-
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Arts Design Entertainment Sports Media"] <- "Other"
-workers$O.Net.Job.Family.Categories[workers$O.Net.Job.Family.Categories == "Military Specific"] <- "Other"
-
-#3 in plot all categories, combined and standalone
-
-#ggplot(workers, aes(O.Net.Job.Family.Categories)) +
-#  geom_histogram(stat="count") + coord_flip()
-
-forworkers2 <- anova[,c(2:85)]
-dataworker <- cbind(forworkers2,workers$O.Net.Job.Family.Categories)    ## to repeat O*Net analyses
-                                     ## This gets worker info into convergence file
-
-dataworker$overall <- rowMeans(dataworker[1:84], na.rm=TRUE)
-
-names(dataworker)[names(dataworker) == 'workers$O.Net.Job.Family.Categories'] <- 'JobFamily'
-
-ggplot(dataworker, aes(x=overall)) + geom_histogram() + facet_wrap(~JobFamily, nrow=8)
-
-workeraov <- aov(overall ~ JobFamily, data=dataworker)
-
-library(lsr)  ## for eta squared
-effect.size <- etaSquared(workeraov)
 

### 2025-04-14 Submission.tex
omitting one extra analysis

@@
 
+Another interesting avenue for future research is to explore these patterns by job type.
+Kubicek et al.
+(2023), for instance, found that employee workload was positively related to strain, and that this relationship was stronger for care and social workers compared to other types of employees.
+This finding suggests that job type may be an important moderator, and worthy of exploration moving forward.
+
 Lastly, there may be some practical utility to pursue training interventions aimed at \emph{how} characteristics are appraised.

### 2025-04-14 Submission.Rmd
Adding a figure

@@
 
-Participants were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of 98 different O\*Net job characteristics in randomized order.
+Respondents were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of 98 different O\*Net job characteristics in randomized order.
 Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).
+See Figure \@ref(fig:onetviz) for a visual representation of the process experienced by respondents.
+
+```{r onetviz, fig.cap="Visual representation of how respondents experienced the survey."}
+library(magick)
+library(grid)
+
+onetviz <- image_read("current_submission/Methods_visual.png")
+grid.raster(onetviz)
+```
 

### 2025-04-14 Submission.tex
Adding a figure

@@
 
-Participants were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of 98 different O*Net job characteristics in randomized order.
+Respondents were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of 98 different O*Net job characteristics in randomized order.
 Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).
+See Figure \ref{fig:onetviz} for a visual representation of the process experienced by respondents.
+
+\begin{figure}
+\centering
+\includegraphics{Submission_files/figure-latex/onetviz-1.pdf}
+\caption{\label{fig:onetviz}Visual representation of how respondents experienced the survey.}
+\end{figure}
 

### 2025-04-15 Submission.Rmd
Updating results

@@
 
-cr_burn_m1 <- lm(burnout ~ scale(overall.challenge_center), modreg)
+cr_burn_m1 <- lm(burnout ~ scale(overall.challenge), modreg)
 #summary(cr_burn_m1)
 
-cr_burn_m2 <- lm(burnout ~ scale(overall.challenge_center) + scale(overall.resource), modreg)
+cr_burn_m2 <- lm(burnout ~ scale(overall.challenge) + scale(overall.resource), modreg)
 #summary(cr_burn_m2)
 
-cr_burn_m3 <- lm(burnout ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
+cr_burn_m3 <- lm(burnout ~ scale(overall.challenge) + scale(overall.resource) + scale(overall.challenge*overall.resource), modreg)
 #summary(cr_burn_m3)
@@
 
-cr_stress_m1 <- lm(stress ~ scale(overall.challenge_center), modreg)
+cr_stress_m1 <- lm(stress ~ scale(overall.challenge), modreg)
 #summary(cr_stress_m1)
 
-cr_stress_m2 <- lm(stress ~ scale(overall.challenge_center) + scale(overall.resource_center), modreg)
+cr_stress_m2 <- lm(stress ~ scale(overall.challenge) + scale(overall.resource), modreg)
 #summary(cr_stress_m2)
 
-cr_stress_m3 <- lm(stress ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
+cr_stress_m3 <- lm(stress ~ scale(overall.challenge) + scale(overall.resource) + scale(overall.challenge*overall.resource), modreg)
 #summary(cr_stress_m3)
@@
 
-cr_eng_m1 <- lm(engagement ~ scale(overall.challenge_center), modreg)
+cr_eng_m1 <- lm(engagement ~ scale(overall.challenge), modreg)
 #summary(cr_eng_m1)
 
-cr_eng_m2 <- lm(engagement ~ scale(overall.challenge_center) + scale(overall.resource_center), modreg)
+cr_eng_m2 <- lm(engagement ~ scale(overall.challenge) + scale(overall.resource), modreg)
 #summary(cr_eng_m2)
 
-cr_eng_m3 <- lm(engagement ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
+cr_eng_m3 <- lm(engagement ~ scale(overall.challenge) + scale(overall.resource) + scale(overall.challenge*overall.resource), modreg)
 #summary(cr_eng_m3)
@@
 
-hr_burn_m1 <- lm(burnout ~ scale(overall.hindrance_center), modreg)
+hr_burn_m1 <- lm(burnout ~ scale(overall.hindrance), modreg)
 #summary(hr_burn_m1)
 
-hr_burn_m2 <- lm(burnout ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
+hr_burn_m2 <- lm(burnout ~ scale(overall.hindrance) + scale(overall.resource), modreg)
 #summary(hr_burn_m2)
 
-hr_burn_m3 <- lm(burnout ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
+hr_burn_m3 <- lm(burnout ~ scale(overall.hindrance) + scale(overall.resource) + scale(overall.hindrance*overall.resource), modreg)
 #summary(hr_burn_m3)
@@
 
-hr_stress_m1 <- lm(stress ~ scale(overall.hindrance_center), modreg)
+hr_stress_m1 <- lm(stress ~ scale(overall.hindrance), modreg)
 #summary(hr_stress_m1)
 
-hr_stress_m2 <- lm(stress ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
+hr_stress_m2 <- lm(stress ~ scale(overall.hindrance) + scale(overall.resource), modreg)
 #summary(hr_stress_m2)
 
-hr_stress_m3 <- lm(stress ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
+hr_stress_m3 <- lm(stress ~ scale(overall.hindrance) + scale(overall.resource) + scale(overall.hindrance*overall.resource), modreg)
 #summary(hr_stress_m3)
@@
 
-hr_eng_m1 <- lm(engagement ~ scale(overall.hindrance_center), modreg)
+hr_eng_m1 <- lm(engagement ~ scale(overall.hindrance), modreg)
 #summary(hr_eng_m1)
 
-hr_eng_m2 <- lm(engagement ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
+hr_eng_m2 <- lm(engagement ~ scale(overall.hindrance) + scale(overall.resource), modreg)
 #summary(hr_eng_m2)
 
-hr_eng_m3 <- lm(engagement ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
+hr_eng_m3 <- lm(engagement ~ scale(overall.hindrance) + scale(overall.resource) + scale(overall.hindrance*overall.resource), modreg)
 #summary(hr_eng_m3)
@@
               escape=FALSE,
-              note="* = p < .05; ** = p < .01, coefficients are unstandardized and mean-centered")
+              note="* = p < .05; ** = p < .01, coefficients are unstandardized")
 ```
@@
 Table \@ref(tab:chal-resource-table) summarizes the results for engagement (as well as stress and burnout).
-Sum scores for the predictors were used here such that the overall amount of resource or demand is recognized, and these predictor variables were mean centered prior to running the regressions.
+Sum scores for the predictors were used here such that the overall amount of resource or demand is recognized.
 First, challenges and resources explained a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(cr_eng_m2)$r.squared, 2)`, Adj.
@@
                  escape=FALSE,
-                 note="* = p < .05; ** = p < .01, coefficients are unstandardized and mean-centered")
+                 note="* = p < .05; ** = p < .01, coefficients are unstandardized")
 ```
@@
 We also explored whether there was an interaction between hindrance demands and resources on the outcome variables.
-Sum scores for the predictors were used here again, and predictor variables were mean centered prior to running the regressions.
+Sum scores for the predictors were used here again.
 First, hindrance demands and resources explained a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(hr_eng_m2)$r.squared, 2)`, Adj.

### 2025-04-15 Submission.tex
Updating results

@@
  &  & Resource & 0.37 ** & 0.15 ** & \\
- & 2 & Challenge & -0.08 &  & \\
- &  & Resource & 0.37 ** &  & \\
- &  & Challenge X Resource & -0.07 * & 0.16 ** & 0.01 *\\
+ & 2 & Challenge & 0.12 &  & \\
+ &  & Resource & 0.57 ** &  & \\
+ &  & Challenge X Resource & -0.4 * & 0.16 ** & 0.01 *\\
 Stress & 1 & Challenge & 0.12 &  & \\
  &  & Resource & -0.06 & 0.01 & \\
- & 2 & Challenge & 0.12 &  & \\
- &  & Resource & -0.06 &  & \\
- &  & Challenge X Resource & 0.02 & 0.01 & 0.00\\
+ & 2 & Challenge & 0.08 &  & \\
+ &  & Resource & -0.1 &  & \\
+ &  & Challenge X Resource & 0.09 & 0.01 & 0.00\\
 Burnout & 1 & Challenge & 0.28 ** &  & \\
  &  & Resource & -0.12 & 0.04 ** & \\
- & 2 & Challenge & 0.28 ** &  & \\
- &  & Resource & -0.12 &  & \\
- &  & Challenge X Resource & 0.05 & 0.04 ** & 0.00\\
+ & 2 & Challenge & 0.13 ** &  & \\
+ &  & Resource & -0.26 &  & \\
+ &  & Challenge X Resource & 0.29 & 0.04 ** & 0.00\\
 \bottomrule
@@
 \begin{tablenotes}[para]
-\normalsize{\textit{Note.} * = p < .05; ** = p < .01, coefficients are unstandardized and mean-centered}
+\normalsize{\textit{Note.} * = p < .05; ** = p < .01, coefficients are unstandardized}
 \end{tablenotes}
@@
 Table \ref{tab:chal-resource-table} summarizes the results for engagement (as well as stress and burnout).
-Sum scores for the predictors were used here such that the overall amount of resource or demand is recognized, and these predictor variables were mean centered prior to running the regressions.
+Sum scores for the predictors were used here such that the overall amount of resource or demand is recognized.
 First, challenges and resources explained a statistically significant amount of the variability in engagement, \(R^2\) = 0.15, Adj.
@@
  &  & Resource & 0.35 ** & 0.17 ** & \\
- & 2 & Hindrance & -0.10 ** &  & \\
- &  & Resource & 0.34 ** &  & \\
- &  & Hindrance X Resource & -0.01 & 0.17 ** & 0.00\\
+ & 2 & Hindrance & -0.07 ** &  & \\
+ &  & Resource & 0.37 ** &  & \\
+ &  & Hindrance X Resource & -0.06 & 0.17 ** & 0.00\\
 Stress & 1 & Hindrance & 0.08 * &  & \\
  &  & Resource & 0.01 & 0.01 * & \\
- & 2 & Hindrance & 0.16 ** &  & \\
- &  & Resource & -0.10 &  & \\
- &  & Hindrance X Resource & -0.17 ** & 0.04 ** & 0.03 **\\
+ & 2 & Hindrance & 0.66 ** &  & \\
+ &  & Resource & 0.30 &  & \\
+ &  & Hindrance X Resource & -0.77 ** & 0.04 ** & 0.03 **\\
 Burnout & 1 & Hindrance & 0.09 * &  & \\
  &  & Resource & 0.10 * & 0.04 ** & \\
- & 2 & Hindrance & 0.13 * &  & \\
- &  & Resource & 0.03 &  & \\
- &  & Hindrance X Resource & -0.11 ** & 0.05 ** & 0.01 **\\
+ & 2 & Hindrance & 0.46 * &  & \\
+ &  & Resource & 0.29 &  & \\
+ &  & Hindrance X Resource & -0.5 ** & 0.05 ** & 0.01 **\\
 \bottomrule
@@
 We also explored whether there was an interaction between hindrance demands and resources on the outcome variables.
-Sum scores for the predictors were used here again, and predictor variables were mean centered prior to running the regressions.
+Sum scores for the predictors were used here again.
 First, hindrance demands and resources explained a statistically significant amount of the variability in engagement, \(R^2\) = 0.17, Adj.

### 2025-04-15 Submission.Rmd
classroom edits

@@
 ---
-title             : "Non-exclusive Characterizations of Demands and Resources across O*NET Job Elements"
+title             : "Shared Characterizations of Demands and Resources across O*NET Job Elements"
 shorttitle        : "O*NET JD-R"
@@
   Much of our understanding of job demands and resources rests on an assumption that some job characteristics are resources and some are demands.
-This study documents variability in subjective ratings of O\*Net job characteristics with respect to interpretation as resource and demand (defined as challenge/hindrance), and further predicts the form of demand will be differentially related to work-relevant outcomes.
+This study documents variability in subjective ratings of O\*Net job characteristics with respect to interpretation as resource and demand (defined as challenge/hindrance), and further predicts the form of demand will be differentially related to work--related outcomes.
 We lastly explore the moderating role of resources on these relationships.
 We found that job characteristics were not uniquely categorized as a resource or demand, but rather, some job characteristics were rated highly as both a resource and a challenge.
-While we did not find support for the prediction that demands were related to stress and burnout, we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships.
-These findings broadly reveal that there is relatively more consistency in ratings of resource and challenge characteristics, and far more variability in job characteristics rated as hindrance demands.
-These findings have implications for job design and management particularly with regard to resource-laden elements that may also be experienced as demanding.
+Resources moderated the challenge-engagement relationship, and further, also moderated the hindrance-stress, and hindrance-burnout relationships.
+These findings broadly suggest that challenging demands may also be interpreted as job resources, and hindrance demands exhibit considerable variability.
+These findings have implications for job design and management particularly with regard to demanding elements that may also be experienced as resources.
 

### 2025-04-15 Submission.tex
classroom edits

@@
 % Make \paragraph and \subparagraph free-standing
-\makeatletter
 \ifx\paragraph\undefined\else
   \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}{
-    \@ifstar
-      \xxxParagraphStar
-      \xxxParagraphNoStar
-  }
-  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
-  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
+  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
 \fi
@@
   \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}{
-    \@ifstar
-      \xxxSubParagraphStar
-      \xxxSubParagraphNoStar
-  }
-  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
-  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
+  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
 \fi
-\makeatother
-% definitions for citeproc citations
-\NewDocumentCommand\citeproctext{}{}
-\NewDocumentCommand\citeproc{mm}{%
-  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
-\makeatletter
- % allow citations to break across lines
- \let\@cite@ofmt\@firstofone
- % avoid brackets around text for \cite:
- \def\@biblabel#1{}
- \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
-\makeatother
 \newlength{\cslhangindent}
@@
   {\xapptocmd\section
-    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi: #1}}
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
     {}{\InnerPatchFailed}%
@@
 {}{\PatchFailed}
-\makeatother
 \keywords{O*Net, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: 4,942}
@@
 \hypersetup{
-  pdftitle={Non-exclusive Characterizations of Demands and Resources across O*NET Job Elements},
+  pdftitle={Shared Characterizations of Demands and Resources across O*NET Job Elements},
   pdfauthor={Alicia Stachowski2, John Kulas1, \& Renata García Prieto Palacios Roji3},
@@
 
-\title{Non-exclusive Characterizations of Demands and Resources across O*NET Job Elements}
+\title{Shared Characterizations of Demands and Resources across O*NET Job Elements}
 \author{Alicia Stachowski\textsuperscript{2}, John Kulas\textsuperscript{1}, \& Renata García Prieto Palacios Roji\textsuperscript{3}}
@@
 Much of our understanding of job demands and resources rests on an assumption that some job characteristics are resources and some are demands.
-This study documents variability in subjective ratings of O*Net job characteristics with respect to interpretation as resource and demand (defined as challenge/hindrance), and further predicts the form of demand will be differentially related to work-relevant outcomes.
+This study documents variability in subjective ratings of O*Net job characteristics with respect to interpretation as resource and demand (defined as challenge/hindrance), and further predicts the form of demand will be differentially related to work--related outcomes.
 We lastly explore the moderating role of resources on these relationships.
 We found that job characteristics were not uniquely categorized as a resource or demand, but rather, some job characteristics were rated highly as both a resource and a challenge.
-While we did not find support for the prediction that demands were related to stress and burnout, we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships.
-These findings broadly reveal that there is relatively more consistency in ratings of resource and challenge characteristics, and far more variability in job characteristics rated as hindrance demands.
-These findings have implications for job design and management particularly with regard to resource-laden elements that may also be experienced as demanding.
+Resources moderated the challenge-engagement relationship, and further, also moderated the hindrance-stress, and hindrance-burnout relationships.
+These findings broadly suggest that challenging demands may also be interpreted as job resources, and hindrance demands exhibit considerable variability.
+These findings have implications for job design and management particularly with regard to demanding elements that may also be experienced as resources.
 }
@@
 
-\subsection{Theoretical Foundations}\label{theoretical-foundations}
+\hypertarget{theoretical-foundations}{%
+\subsection{Theoretical Foundations}\label{theoretical-foundations}}
 
@@
 
-\section{Method}\label{method}
+\hypertarget{method}{%
+\section{Method}\label{method}}
 
-\subsection{Participants}\label{participants}
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
 
@@
 
-\subsection{Materials}\label{materials}
+\hypertarget{materials}{%
+\subsection{Materials}\label{materials}}
 
@@
 
-\subsection{Procedure}\label{procedure}
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
 
@@
 
-\section{Results}\label{results}
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
@@
 
-\bibitem[\citeproctext]{ref-kubicek2023all}
+\leavevmode\vadjust pre{\hypertarget{ref-kubicek2023all}{}}%
 Kubicek, B., Uhlig, L., Hülsheger, U.
@@
 
-\bibitem[\citeproctext]{ref-lepine2022challenge}
+\leavevmode\vadjust pre{\hypertarget{ref-lepine2022challenge}{}}%
 LePine, M. A. (2022). The challenge-hindrance stressor framework: An integrative conceptual review and path forward. \emph{Group \& Organization Management}, \emph{47}(2), 223--254.
 
-\bibitem[\citeproctext]{ref-mazzola2019should}
+\leavevmode\vadjust pre{\hypertarget{ref-mazzola2019should}{}}%
 Mazzola, J.
@@
 
-\bibitem[\citeproctext]{ref-peterson2001understanding}
+\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
 Peterson, N.

### 2025-04-26 Submission.Rmd
pushing apaquarto to Alicia

@@
 abstract: |
-  Much of our understanding of job demands and resources rests on an assumption that some job characteristics are resources and some are demands.
-This study documents variability in subjective ratings of O\*Net job characteristics with respect to interpretation as resource and demand (defined as challenge/hindrance), and further predicts the form of demand will be differentially related to work--related outcomes.
-We lastly explore the moderating role of resources on these relationships.
-We found that job characteristics were not uniquely categorized as a resource or demand, but rather, some job characteristics were rated highly as both a resource and a challenge.
+  Many discussions of job demands and resources include a tacit characterization that some job elements are resources and others are demands.
+This study documents variability in ratings of O\*Net job characteristics with respect to subjective interpretation of job characteristics, and further predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes.
+We additionally explore the potential moderating role of resources on these relationships.
+The results indicate that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are experienced both as resource and challenge.
 Resources moderated the challenge-engagement relationship, and further, also moderated the hindrance-stress, and hindrance-burnout relationships.
-These findings broadly suggest that challenging demands may also be interpreted as job resources, and hindrance demands exhibit considerable variability.
-These findings have implications for job design and management particularly with regard to demanding elements that may also be experienced as resources.
+These findings broadly suggest that challenging demands may also serve as job resources, and what is viewed as a hindrance exhibits considerable variability.
+These findings have implications for job design and management particularly with regard to the opportunity with demanding elements: these may be amenable to reframing as resources.
 
@@
 We build on a growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges].
-Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes.
-As an additional contribution, we utilize the [O\*Net database](https://www.onetcenter.org/content.html), which provides a rich and generalizable source of information about occupational requirements (i.e., work activities and context).
+Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes.
+As an additional contribution, we investigate these associations retaining [O\*Net specifications](https://www.onetcenter.org/content.html), which provides a rich and generalizable source of information about occupational requirements (i.e., work activities and context).
 
@@
 
-The job demands-resources theory (e.g., Bakker & Demerouti, 2014; 2017) highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes.
+The job demands-resources theory (e.g., Bakker & Demerouti, 2014; 2017) highlights the importance of demands and resources on the experience of motivation and strain as well as other, less proximal outcomes.
 Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job].
 In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001).
-Demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain [high work pressure, for example, is commonly cited as a demand, e.g., @demerouti2001job].
 The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job).
 
-@cavanaugh2000empirical proposed the challenge-hindrance stressor framework distinguishes between *two forms* of demands -- *challenges* and *hindrances*.
+@cavanaugh2000empirical proposed the challenge-hindrance stressor framework that distinguishes between *two forms* of demands -- *challenges* and *hindrances*.
 Challenge demands promote mastery, personal growth, and future gains – these demands should lead to coping strategies that facilitate achievement.

### 2025-04-26 Submission.tex
pushing apaquarto to Alicia

@@
 \abstract{%
-Much of our understanding of job demands and resources rests on an assumption that some job characteristics are resources and some are demands.
-This study documents variability in subjective ratings of O*Net job characteristics with respect to interpretation as resource and demand (defined as challenge/hindrance), and further predicts the form of demand will be differentially related to work--related outcomes.
-We lastly explore the moderating role of resources on these relationships.
-We found that job characteristics were not uniquely categorized as a resource or demand, but rather, some job characteristics were rated highly as both a resource and a challenge.
+Many discussions of job demands and resources include a tacit characterization that some job elements are resources and others are demands.
+This study documents variability in ratings of O*Net job characteristics with respect to subjective interpretation of job characteristics, and further predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes.
+We additionally explore the potential moderating role of resources on these relationships.
+The results indicate that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are experienced both as resource and challenge.
 Resources moderated the challenge-engagement relationship, and further, also moderated the hindrance-stress, and hindrance-burnout relationships.
-These findings broadly suggest that challenging demands may also be interpreted as job resources, and hindrance demands exhibit considerable variability.
-These findings have implications for job design and management particularly with regard to demanding elements that may also be experienced as resources.
+These findings broadly suggest that challenging demands may also serve as job resources, and what is viewed as a hindrance exhibits considerable variability.
+These findings have implications for job design and management particularly with regard to the opportunity with demanding elements: these may be amenable to reframing as resources.
 }
@@
 We build on a growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020).
-Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes.
-As an additional contribution, we utilize the \href{https://www.onetcenter.org/content.html}{O*Net database}, which provides a rich and generalizable source of information about occupational requirements (i.e., work activities and context).
+Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes.
+As an additional contribution, we investigate these associations retaining \href{https://www.onetcenter.org/content.html}{O*Net specifications}, which provides a rich and generalizable source of information about occupational requirements (i.e., work activities and context).
 
@@
 
-The job demands-resources theory (e.g., Bakker \& Demerouti, 2014; 2017) highlights the importance of demands and resources on the experience of motivation and strain as well as other, more distal outcomes.
+The job demands-resources theory (e.g., Bakker \& Demerouti, 2014; 2017) highlights the importance of demands and resources on the experience of motivation and strain as well as other, less proximal outcomes.
 Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017).
 In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001).
-Demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001).
 The perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; Bakker and Demerouti (2014)).
@@
 Cavanaugh et al.
-(2000) proposed the challenge-hindrance stressor framework distinguishes between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}.
+(2000) proposed the challenge-hindrance stressor framework that distinguishes between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}.
 Challenge demands promote mastery, personal growth, and future gains -- these demands should lead to coping strategies that facilitate achievement.

### 2025-06-05 Submission.Rmd
Panera pushes - need to expand Cavanaugh associations with "job search" (more job searching if jobs are challenging?)

@@
 abstract: |
-  Many discussions of job demands and resources include a tacit characterization that some job elements are resources and others are demands.
-This study documents variability in ratings of O\*Net job characteristics with respect to subjective interpretation of job characteristics, and further predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes.
+  Many discussions of job demands and resources include a tacit characterization that job elements are either resources or demands.
+This study documents variability in ratings of O\*Net job characteristics with respect to subjective interpretation of job characteristics and predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes.
 We additionally explore the potential moderating role of resources on these relationships.
-The results indicate that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are experienced both as resource and challenge.
-Resources moderated the challenge-engagement relationship, and further, also moderated the hindrance-stress, and hindrance-burnout relationships.
-These findings broadly suggest that challenging demands may also serve as job resources, and what is viewed as a hindrance exhibits considerable variability.
-These findings have implications for job design and management particularly with regard to the opportunity with demanding elements: these may be amenable to reframing as resources.
+The results support the perspective that job characteristics are not uniquely categorized as a resource or demand, but rather, challenging elements tend to also be experienced as job resources.
+Furthermore, greater experienced resources moderated the challenge-engagement relationship as well as the hindrance-stress and hindrance-burnout relationships.
+These findings broadly suggest that challenging demands may also provide opportunity in the form of job resources, and what is viewed as a *hindrance* exhibits considerable variability.
+These findings have implications for job design and management particularly with regard to opportunity with *some* demanding elements: these may be candidates for growth opportunity.
 
@@
 We build on a growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges].
-Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes.
-As an additional contribution, we investigate these associations retaining [O\*Net specifications](https://www.onetcenter.org/content.html), which provides a rich and generalizable source of information about occupational requirements (i.e., work activities and context).
+Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to perception as resource and/or demand, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) resources buffer the relationships between demands and negative work outcomes.
+We investigate these associations via the lens of [O\*Net job specifications](https://www.onetcenter.org/content.html), which provides a broad framework of specification regarding generalizable job characteristics.
 
@@
 
-@cavanaugh2000empirical proposed the challenge-hindrance stressor framework that distinguishes between *two forms* of demands -- *challenges* and *hindrances*.
+@cavanaugh2000empirical extended this orientation by proposing a framework that distinguishes between *two forms* of demands -- *challenges* and *hindrances*.
 Challenge demands promote mastery, personal growth, and future gains – these demands should lead to coping strategies that facilitate achievement.
@@
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Example hindrance demands in a work context include role conflict and role ambiguity [@lepine2022challenge].
+Example hindrance demands that have been previously noted include role conflict and role ambiguity [@lepine2022challenge].
 
@@
 
-The original work on this topic suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes [e.g., @cavanaugh2000empirical].
-Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, @lepine2005meta regarding performance and @crawford2010linking regarding engagement), although there have been criticisms of this framework [e.g., @mazzola2019should; @kubicek2023all].
-
 @lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes.
-First, demands appraised as challenges typically result in a more positive appraisal, and engagement is likely to happen as a result.
+First, demands appraised as *challenges* typically result in a more positive appraisal, and engagement is likely to happen as a result.
 Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing.
-Demands appraised as hindrances elicit a different process.
+Demands appraised as *hindrances* elicit a different process.
 Disengagement is likely to result from a hindrance appraisal, which then negatively impacts motivation, performance, growth and wellbeing.
-This happens because resources are depleted via frustrations and other affectively negative reactions [@lepine2022challenge].
-
-Recent work affirms these appraisal processes.
+This happens because resources are depleted via frustrations and other negative affect reactions [@lepine2022challenge].
+
+Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, @lepine2005meta regarding performance and @crawford2010linking regarding engagement).
 @pindek2024dynamic meta-analyzed diary studies of dynamic demands (i.e., short-term daily experiences of demands) and concluded that daily challenge demands had a positive *direct* association with performance, but a negative *indirect* association with performance through strain (as described by @lepine2022challenge above).
@@
 @pindek2024dynamic notes this limitation of *a priori* classification of characteristics as demands, challenges, or hindrances, as do @horan2020review.
-In fact, although much of our research on job demands based on *a priori* classifications [@searle2015merits], the recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
-
-Aligned with this dynamic perspective on the experience of work, @horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process into the challenge-hindrance stressor framework.
+In fact, although much of our research on job demands is based on *a priori* classifications [@searle2015merits], the most recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., two different employees could most certainly perceive "delivering face--to--face presentations" as a resource or as a demand).
+
+Aligned with this relativistic perspective on the experience of work, @horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process into the challenge-hindrance stressor framework.
 In fact, @horan2020review state that “…stressors are only challenge or hindrance demands to the extent that they are perceived as such by employees” (p.
@@
 They go on to suggest future research continue to move away from *a priori* classifications of demands, as doing so can be problematic for theoretical and empirical reasons.
-Empirically, as shown above, we have some evidence suggesting people can appraise a work characteristic as both a hindrance and challenge at the same time [e.g., @searle2015merits].
-
-Given the above, the first question we ask is whether people exclusively categorize resources, challenges, and  hindrances, and whether a job characteristics might even be considered simultaneously as more than one of these (e.g., both a challenge and a resource).
+
+Given the above, the first question we pose is whether people exclusively experience job elements as resources, challenges, or hindrances, or whether a given job characteristic might be mutually considered as more than one of these (e.g., both a challenge and a resource).
 Evidence suggests that employees do, at least, differentiate between challenge and hindrance demands [e.g., @bakker2013weekly; @gerich2017relevance; @webster2011extending].
@@
 
->Hypothesis 1: Job characteristics differ in consistancy regarding subjective worker perception as a challenge or hindrance demand, or resource.
+>Hypothesis 1: Job characteristics vary regarding subjective worker perception as a challenge or hindrance demand, or resource.
 
@@
 
-he second set of predictions focus on associations with theory-relevant outcomes across via job demands-resources- @bakker2017job and challenge-hindrance stressor-frameworks @cavanaugh2000empirical.
-Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance [e.g., @lepine2005meta].
+The second set of predictions focus on associations with theory--derived outcomes across two theoretical frameworks.
+Both the job demands--resources model [@bakker2017job] and the challenge-hindrance stressor framework [@cavanaugh2000empirical] have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, commitment, and performance [e.g., @lepine2005meta].
 We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout.
-See Figure \@ref(fig:ourmodel) for proposed associations.
+See Figure \@ref(fig:ourmodel) for proposed associations, **with dotted and solid lines indicating...** .
 Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job], and empirical work suggests that they are associated with positive outcomes.
@@
 Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work [@chen2021daily], engagement [@crawford2010linking], and strain and turnover intentions [e.g., @abbas2019challenge], for example.
-Challenge appraisals have been negatively associated with job search behaviors [e.g., @cavanaugh2000empirical].
-
-Hindrance demands (appraisals) have been found to be related to job demands-resources model outcomes such as decreased motivation and increased stress.
-When a demand is appraised as a hindrance – it is negatively associated with motivational resources [@kim2020thriving], engagement [@crawford2010linking], job search behaviors and job satisfaction [@cavanaugh2000empirical].
+Challenge appraisals have also been negatively associated with job search behaviors [e.g., @cavanaugh2000empirical].
+**CLARIFY**
+
+When a demand is appraised as a hindrance, it is negatively associated with motivational resources [@kim2020thriving], engagement [@crawford2010linking], job search behaviors and job satisfaction [@cavanaugh2000empirical].
 @chen2021daily found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment.

### 2025-06-05 Submission.tex
Panera pushes - need to expand Cavanaugh associations with "job search" (more job searching if jobs are challenging?)

@@
 \abstract{%
-Many discussions of job demands and resources include a tacit characterization that some job elements are resources and others are demands.
-This study documents variability in ratings of O*Net job characteristics with respect to subjective interpretation of job characteristics, and further predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes.
+Many discussions of job demands and resources include a tacit characterization that job elements are either resources or demands.
+This study documents variability in ratings of O*Net job characteristics with respect to subjective interpretation of job characteristics and predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes.
 We additionally explore the potential moderating role of resources on these relationships.
-The results indicate that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are experienced both as resource and challenge.
-Resources moderated the challenge-engagement relationship, and further, also moderated the hindrance-stress, and hindrance-burnout relationships.
-These findings broadly suggest that challenging demands may also serve as job resources, and what is viewed as a hindrance exhibits considerable variability.
-These findings have implications for job design and management particularly with regard to the opportunity with demanding elements: these may be amenable to reframing as resources.
+The results support the perspective that job characteristics are not uniquely categorized as a resource or demand, but rather, challenging elements tend to also be experienced as job resources.
+Furthermore, greater experienced resources moderated the challenge-engagement relationship as well as the hindrance-stress and hindrance-burnout relationships.
+These findings broadly suggest that challenging demands may also provide opportunity in the form of job resources, and what is viewed as a \emph{hindrance} exhibits considerable variability.
+These findings have implications for job design and management particularly with regard to opportunity with \emph{some} demanding elements: these may be candidates for growth opportunity.
 }
@@
 We build on a growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020).
-Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes.
-As an additional contribution, we investigate these associations retaining \href{https://www.onetcenter.org/content.html}{O*Net specifications}, which provides a rich and generalizable source of information about occupational requirements (i.e., work activities and context).
+Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to perception as resource and/or demand, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) resources buffer the relationships between demands and negative work outcomes.
+We investigate these associations via the lens of \href{https://www.onetcenter.org/content.html}{O*Net job specifications}, which provides a broad framework of specification regarding generalizable job characteristics.
 
@@
 Cavanaugh et al.
-(2000) proposed the challenge-hindrance stressor framework that distinguishes between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}.
+(2000) extended this orientation by proposing a framework that distinguishes between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}.
 Challenge demands promote mastery, personal growth, and future gains -- these demands should lead to coping strategies that facilitate achievement.
@@
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Example hindrance demands in a work context include role conflict and role ambiguity (M.
+Example hindrance demands that have been previously noted include role conflict and role ambiguity (M.
 A.
@@
 
-The original work on this topic suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes (e.g., Cavanaugh et al., 2000).
+M.
+A.
+LePine (2022) explain the mechanisms by which demands are related to performance and wellbeing outcomes.
+First, demands appraised as \emph{challenges} typically result in a more positive appraisal, and engagement is likely to happen as a result.
+Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing.
+Demands appraised as \emph{hindrances} elicit a different process.
+Disengagement is likely to result from a hindrance appraisal, which then negatively impacts motivation, performance, growth and wellbeing.
+This happens because resources are depleted via frustrations and other negative affect reactions (M.
+A.
+LePine, 2022).
+
 Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, J.
@@
 (2005) regarding performance and Crawford et al.
-(2010) regarding engagement), although there have been criticisms of this framework (Kubicek et al., 2023; e.g., Mazzola \& Disselhorst, 2019).
-
-M.
-A.
-LePine (2022) explain the mechanisms by which demands are related to performance and wellbeing outcomes.
-First, demands appraised as challenges typically result in a more positive appraisal, and engagement is likely to happen as a result.
-Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing.
-Demands appraised as hindrances elicit a different process.
-Disengagement is likely to result from a hindrance appraisal, which then negatively impacts motivation, performance, growth and wellbeing.
-This happens because resources are depleted via frustrations and other affectively negative reactions (M.
-A.
-LePine, 2022).
-
-Recent work affirms these appraisal processes.
+(2010) regarding engagement).
 Pindek et al.
@@
 (2020).
-In fact, although much of our research on job demands based on \emph{a priori} classifications (Searle \& Auton, 2015), the recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).
+In fact, although much of our research on job demands is based on \emph{a priori} classifications (Searle \& Auton, 2015), the most recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., two different employees could most certainly perceive ``delivering face--to--face presentations'' as a resource or as a demand).
 
-Aligned with this dynamic perspective on the experience of work, Horan et al.
+Aligned with this relativistic perspective on the experience of work, Horan et al.
 (2020) and M.
@@
 They go on to suggest future research continue to move away from \emph{a priori} classifications of demands, as doing so can be problematic for theoretical and empirical reasons.
-Empirically, as shown above, we have some evidence suggesting people can appraise a work characteristic as both a hindrance and challenge at the same time (e.g., Searle \& Auton, 2015).
 
-Given the above, the first question we ask is whether people exclusively categorize resources, challenges, and hindrances, and whether a job characteristics might even be considered simultaneously as more than one of these (e.g., both a challenge and a resource).
+Given the above, the first question we pose is whether people exclusively experience job elements as resources, challenges, or hindrances, or whether a given job characteristic might be mutually considered as more than one of these (e.g., both a challenge and a resource).
 Evidence suggests that employees do, at least, differentiate between challenge and hindrance demands (e.g., Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011).
@@
 \begin{quote}
-Hypothesis 1: Job characteristics differ in consistancy regarding subjective worker perception as a challenge or hindrance demand, or resource.
+Hypothesis 1: Job characteristics vary regarding subjective worker perception as a challenge or hindrance demand, or resource.
 \end{quote}
@@
 
-he second set of predictions focus on associations with theory-relevant outcomes across via job demands-resources- Bakker and Demerouti (2017) and challenge-hindrance stressor-frameworks Cavanaugh et al.
-(2000).
-Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance (e.g., J.
+The second set of predictions focus on associations with theory--derived outcomes across two theoretical frameworks.
+Both the job demands--resources model (Bakker \& Demerouti, 2017) and the challenge-hindrance stressor framework (Cavanaugh et al., 2000) have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, commitment, and performance (e.g., J.
 A.
@@
 We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout.
-See Figure \ref{fig:ourmodel} for proposed associations.
+See Figure \ref{fig:ourmodel} for proposed associations, \textbf{with dotted and solid lines indicating\ldots{}} .
 Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017), and empirical work suggests that they are associated with positive outcomes.
@@
 Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work (Chen et al., 2021), engagement (Crawford et al., 2010), and strain and turnover intentions (e.g., Abbas \& Raja, 2019), for example.
-Challenge appraisals have been negatively associated with job search behaviors (e.g., Cavanaugh et al., 2000).
+Challenge appraisals have also been negatively associated with job search behaviors (e.g., Cavanaugh et al., 2000).
+\textbf{CLARIFY}
 
-Hindrance demands (appraisals) have been found to be related to job demands-resources model outcomes such as decreased motivation and increased stress.
-When a demand is appraised as a hindrance -- it is negatively associated with motivational resources (Kim \& Beehr, 2020), engagement (Crawford et al., 2010), job search behaviors and job satisfaction (Cavanaugh et al., 2000).
+When a demand is appraised as a hindrance, it is negatively associated with motivational resources (Kim \& Beehr, 2020), engagement (Crawford et al., 2010), job search behaviors and job satisfaction (Cavanaugh et al., 2000).
 Chen et al.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-mazzola2019should}{}}%
-Mazzola, J.
-J., \& Disselhorst, R.
-(2019).
-Should we be {``challenging''} employees?: A critical review and meta-analysis of the challenge-hindrance model of stress.
-\emph{Journal of Organizational Behavior}, \emph{40}(8), 949--961.
-
 \leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%

### 2025-06-12 Submission.Rmd
pushing to laptop for Dunn brothers

@@
 abstract: |
-  Many discussions of job demands and resources include a tacit characterization that job elements are either resources or demands.
-This study documents variability in ratings of O\*Net job characteristics with respect to subjective interpretation of job characteristics and predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes.
+  Discussions of job characteristics often include a (tacit) characterization that these job elements are either resources or demands.
+The current study documents variability in ratings of O\*Net specifications with respect to subjective interpretation of job characteristics and predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes.
 We additionally explore the potential moderating role of resources on these relationships.
-The results support the perspective that job characteristics are not uniquely categorized as a resource or demand, but rather, challenging elements tend to also be experienced as job resources.
-Furthermore, greater experienced resources moderated the challenge-engagement relationship as well as the hindrance-stress and hindrance-burnout relationships.
+Results support the perspective that job characteristics are not uniquely categorized as a resource or demand, but rather, challenging elements tend to *also* be interpreted as job resources.
+Furthermore, greater experienced resources moderate the challenge--engagement relationship as well as the hindrance-stress and hindrance--burnout relationships.
 These findings broadly suggest that challenging demands may also provide opportunity in the form of job resources, and what is viewed as a *hindrance* exhibits considerable variability.
-These findings have implications for job design and management particularly with regard to opportunity with *some* demanding elements: these may be candidates for growth opportunity.
 
@@
 
-csl               : "apa7.csl"
+csl               : "sage-harvard.csl"
 documentclass     : "apa7" #interact
@@
 ```
+
+8,000 words inclusive of everything, references, etc
+
+Abstract = 150 words
+
+preference for Word document
 
@@
 
-The final usable sample consisted of `r nrow(data)`.
+The Montclair State University Institutional Review Board approved the project and respondents provided consent after reviewing a project description but before starting the survey.
+Written consent was obtained via The final screened sample consisted of `r nrow(data)`.
 Regarding tenure, `r round(a[1,3],2)`% had been in their referent job less than 6 months, `r round(a[2,3],1)`% between 6 months and a year, `r round(a[3,3],2)`% between one and five years, `r round(a[4,3],2)`% between 5 and 10 years, and `r round(a[5,3],2)`% more than 10 years.

### 2025-06-12 Submission.tex
pushing to laptop for Dunn brothers

@@
 \abstract{%
-Many discussions of job demands and resources include a tacit characterization that job elements are either resources or demands.
-This study documents variability in ratings of O*Net job characteristics with respect to subjective interpretation of job characteristics and predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes.
+Discussions of job characteristics often include a (tacit) characterization that these job elements are either resources or demands.
+The current study documents variability in ratings of O*Net specifications with respect to subjective interpretation of job characteristics and predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes.
 We additionally explore the potential moderating role of resources on these relationships.
-The results support the perspective that job characteristics are not uniquely categorized as a resource or demand, but rather, challenging elements tend to also be experienced as job resources.
-Furthermore, greater experienced resources moderated the challenge-engagement relationship as well as the hindrance-stress and hindrance-burnout relationships.
+Results support the perspective that job characteristics are not uniquely categorized as a resource or demand, but rather, challenging elements tend to \emph{also} be interpreted as job resources.
+Furthermore, greater experienced resources moderate the challenge--engagement relationship as well as the hindrance-stress and hindrance--burnout relationships.
 These findings broadly suggest that challenging demands may also provide opportunity in the form of job resources, and what is viewed as a \emph{hindrance} exhibits considerable variability.
-These findings have implications for job design and management particularly with regard to opportunity with \emph{some} demanding elements: these may be candidates for growth opportunity.
 }
@@
 \maketitle
+
+8,000 words inclusive of everything, references, etc
+
+Abstract = 150 words
+
+preference for Word document
 
@@
 
-\hypertarget{theoretical-foundations}{%
-\subsection{Theoretical Foundations}\label{theoretical-foundations}}
+\subsection{Theoretical Foundations}\label{theoretical-foundations}
 
 The job demands-resources theory (e.g., Bakker \& Demerouti, 2014; 2017) highlights the importance of demands and resources on the experience of motivation and strain as well as other, less proximal outcomes.
-Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017).
+Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker and Demerouti, 2014, 2017).
 In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001).
@@
 Challenge demands promote mastery, personal growth, and future gains -- these demands should lead to coping strategies that facilitate achievement.
-Work characteristics consistent with this definition, for example, include time pressure and responsibility (M.
-A.
-LePine, 2022).
+Work characteristics consistent with this definition, for example, include time pressure and responsibility (LePine, 2022).
 Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
-Example hindrance demands that have been previously noted include role conflict and role ambiguity (M.
-A.
-LePine, 2022).
+Example hindrance demands that have been previously noted include role conflict and role ambiguity (LePine, 2022).
 
-M.
-A.
 LePine (2022) explain the mechanisms by which demands are related to performance and wellbeing outcomes.
@@
 Disengagement is likely to result from a hindrance appraisal, which then negatively impacts motivation, performance, growth and wellbeing.
-This happens because resources are depleted via frustrations and other negative affect reactions (M.
-A.
-LePine, 2022).
+This happens because resources are depleted via frustrations and other negative affect reactions (LePine, 2022).
 
-Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, J.
-A.
-LePine et al.
+Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, LePine et al.
 (2005) regarding performance and Crawford et al.
@@
 Pindek et al.
-(2024) meta-analyzed diary studies of dynamic demands (i.e., short-term daily experiences of demands) and concluded that daily challenge demands had a positive \emph{direct} association with performance, but a negative \emph{indirect} association with performance through strain (as described by M.
-A.
-LePine (2022) above).
+(2024) meta-analyzed diary studies of dynamic demands (i.e., short-term daily experiences of demands) and concluded that daily challenge demands had a positive \emph{direct} association with performance, but a negative \emph{indirect} association with performance through strain (as described by LePine (2022) above).
 As expected, hindrance demands had both direct and indirect (through strain) associations with performance (Pindek et al., 2024).
@@
 (2020).
-In fact, although much of our research on job demands is based on \emph{a priori} classifications (Searle \& Auton, 2015), the most recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., two different employees could most certainly perceive ``delivering face--to--face presentations'' as a resource or as a demand).
+In fact, although much of our research on job demands is based on \emph{a priori} classifications (Searle and Auton, 2015), the most recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., two different employees could most certainly perceive ``delivering face--to--face presentations'' as a resource or as a demand).
 
 Aligned with this relativistic perspective on the experience of work, Horan et al.
-(2020) and M.
-A.
-LePine (2022) specifically call out the need for additional research to incorporate the appraisal process into the challenge-hindrance stressor framework.
+(2020) and LePine (2022) specifically call out the need for additional research to incorporate the appraisal process into the challenge-hindrance stressor framework.
 In fact, Horan et al.
@@
 Given the above, the first question we pose is whether people exclusively experience job elements as resources, challenges, or hindrances, or whether a given job characteristic might be mutually considered as more than one of these (e.g., both a challenge and a resource).
-Evidence suggests that employees do, at least, differentiate between challenge and hindrance demands (e.g., Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011).
+Evidence suggests that employees do, at least, differentiate between challenge and hindrance demands (e.g., Bakker and Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011).
 For example, Bakker and Sanz-Vergel (2013) found that work pressure was perceived as a hindrance, and emotional demands as more of a challenge.
@@
 
-\hypertarget{connecting-appraisals-to-workplace-outcomes}{%
-\subsection{Connecting Appraisals to Workplace Outcomes}\label{connecting-appraisals-to-workplace-outcomes}}
+\subsection{Connecting Appraisals to Workplace Outcomes}\label{connecting-appraisals-to-workplace-outcomes}
 
 The second set of predictions focus on associations with theory--derived outcomes across two theoretical frameworks.
-Both the job demands--resources model (Bakker \& Demerouti, 2017) and the challenge-hindrance stressor framework (Cavanaugh et al., 2000) have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, commitment, and performance (e.g., J.
-A.
-LePine et al., 2005).
+Both the job demands--resources model (Bakker and Demerouti, 2017) and the challenge-hindrance stressor framework (Cavanaugh et al., 2000) have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, commitment, and performance (e.g., LePine et al., 2005).
 We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout.
 See Figure \ref{fig:ourmodel} for proposed associations, \textbf{with dotted and solid lines indicating\ldots{}} .
-Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017), and empirical work suggests that they are associated with positive outcomes.
+Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker and Demerouti, 2014, 2017), and empirical work suggests that they are associated with positive outcomes.
 Relevant to the current study, for example, Hakanen et al.
@@
 The findings regarding demands are more complex, presumably because the way challenge vs.~hindrance appraisals influence coping strategies.
-Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work (Chen et al., 2021), engagement (Crawford et al., 2010), and strain and turnover intentions (e.g., Abbas \& Raja, 2019), for example.
+Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work (Chen et al., 2021), engagement (Crawford et al., 2010), and strain and turnover intentions (e.g., Abbas and Raja, 2019), for example.
 Challenge appraisals have also been negatively associated with job search behaviors (e.g., Cavanaugh et al., 2000).
@@
 
-When a demand is appraised as a hindrance, it is negatively associated with motivational resources (Kim \& Beehr, 2020), engagement (Crawford et al., 2010), job search behaviors and job satisfaction (Cavanaugh et al., 2000).
+When a demand is appraised as a hindrance, it is negatively associated with motivational resources (Kim and Beehr, 2020), engagement (Crawford et al., 2010), job search behaviors and job satisfaction (Cavanaugh et al., 2000).
 Chen et al.
@@
 Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands (Podsakoff et al., 2007).
-Interestingly, both challenges and hindrances have been shown to positively predict strain (Abbas \& Raja, 2019; J.
-A.
-LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010), which further highlights the complex association between appraisals and subsequent outcomes.
+Interestingly, both challenges and hindrances have been shown to positively predict strain (Abbas and Raja, 2019; LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010), which further highlights the complex association between appraisals and subsequent outcomes.
 Given the differential relationships described above, we make the following predictions (see Figure \ref{fig:ourmodel}):
@@
 
-\hypertarget{method}{%
-\section{Method}\label{method}}
+\section{Method}\label{method}
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+\subsection{Participants}\label{participants}
 
-The final usable sample consisted of 568.
+The Montclair State University Institutional Review Board approved the project and respondents provided consent after reviewing a project description but before starting the survey.
+Written consent was obtained via The final screened sample consisted of 568.
 Regarding tenure, 13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\section{Results}\label{results}
 
-Of the 785 individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021).
+Of the 785 individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes and Wilhelm, 2021).
 Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current sample.
@@
 
-\hypertarget{challenges-resources-and-outcomes}{%
-\subsubsection{Challenges, Resources, and Outcomes}\label{challenges-resources-and-outcomes}}
+\subsubsection{Challenges, Resources, and Outcomes}\label{challenges-resources-and-outcomes}
 
@@
 
-\hypertarget{hindrances-resources-and-outcomes}{%
-\subsubsection{Hindrances, Resources, and Outcomes}\label{hindrances-resources-and-outcomes}}
+\subsubsection{Hindrances, Resources, and Outcomes}\label{hindrances-resources-and-outcomes}
 
@@
 our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs (Webster et al., 2011).
-This finding aligns quite well with the challenge-hindrance stressor framework, which collectively argue that employees perceive stimuli (i.e., job characteristics) uniquely (Lazarus \& Folkman, 1984), and thus, could appraise them as either a challenge or hindrance to their job performance (Cavanaugh et al., 2000).
+This finding aligns quite well with the challenge-hindrance stressor framework, which collectively argue that employees perceive stimuli (i.e., job characteristics) uniquely (Lazarus and Folkman, 1984), and thus, could appraise them as either a challenge or hindrance to their job performance (Cavanaugh et al., 2000).
 Further, Cavanaugh et al.
@@
 Such conversations could happen during an annual performance review.
-In addition, J.
-A.
-LePine et al.
+In addition, LePine et al.
 (2005) and Podsakoff et al.
@@
 
-\hypertarget{conclusion}{%
-\subsection{Conclusion}\label{conclusion}}
+\subsection{Conclusion}\label{conclusion}
 
@@
 
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-abbas2019challenge}{}}%
-Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.
+\phantomsection\label{refs}
+\begin{CSLReferences}{1}{1}
+\bibitem[\citeproctext]{ref-abbas2019challenge}
+Abbas M and Raja U (2019) Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology} 34(2). Springer: 189--201.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
-Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
+\bibitem[\citeproctext]{ref-bakker2014job}
+Bakker AB and Demerouti E (2014) Job demands--resources theory. \emph{Wellbeing: A complete reference guide}. John Wiley \& Sons, Ltd Chichester, UK: 1--28.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
-Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
+\bibitem[\citeproctext]{ref-bakker2017job}
+Bakker AB and Demerouti E (2017) Job demands--resources theory: Taking stock and looking forward. \emph{Journal of occupational health psychology} 22(3). Educational Publishing Foundation: 273.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2005job}{}}%
-Bakker, A. B., Demerouti, E., \& Euwema, M. C. (2005). Job resources buffer the impact of job demands on burnout. \emph{Journal of Occupational Health Psychology}, \emph{10}(2), 170.
+\bibitem[\citeproctext]{ref-bakker2013weekly}
+Bakker AB and Sanz-Vergel AI (2013) Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior} 83(3). Elsevier: 397--409.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2007job}{}}%
-Bakker, A.
-B., Hakanen, J.
-J., Demerouti, E., \& Xanthopoulou, D.
-(2007).
-Job resources boost work engagement, particularly when job demands are high.
-\emph{Journal of Educational Psychology}, \emph{99}(2), 274.
+\bibitem[\citeproctext]{ref-bakker2005job}
+Bakker AB, Demerouti E and Euwema MC (2005) Job resources buffer the impact of job demands on burnout. \emph{Journal of occupational health psychology} 10(2). Educational Publishing Foundation: 170.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
-Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
+\bibitem[\citeproctext]{ref-bakker2007job}
+Bakker AB, Hakanen JJ, Demerouti E, et al.
+(2007) Job resources boost work engagement, particularly when job demands are high.
+\emph{Journal of educational psychology} 99(2).
+American Psychological Association: 274.
 
-\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
-Cavanaugh, M.
-A., Boswell, W.
-R., Roehling, M.
-V., \& Boudreau, J.
-W.
-(2000).
-An empirical examination of self-reported work stress among US managers.
-\emph{Journal of Applied Psychology}, \emph{85}(1), 65.
+\bibitem[\citeproctext]{ref-cavanaugh2000empirical}
+Cavanaugh MA, Boswell WR, Roehling MV, et al.
+(2000) An empirical examination of self-reported work stress among US managers.
+\emph{Journal of applied psychology} 85(1).
+American Psychological Association: 65.
 
-\leavevmode\vadjust pre{\hypertarget{ref-chen2021daily}{}}%
-Chen, H., Wang, H., Yuan, M., \& Xu, S. (2021). Daily challenge/hindrance demands and cognitive wellbeing: A multilevel moderated mediation model. \emph{Frontiers in Psychology}, \emph{12}, 616002.
+\bibitem[\citeproctext]{ref-chen2021daily}
+Chen H, Wang H, Yuan M, et al. (2021) Daily challenge/hindrance demands and cognitive wellbeing: A multilevel moderated mediation model. \emph{Frontiers in Psychology} 12. Frontiers Media SA: 616002.
 
-\leavevmode\vadjust pre{\hypertarget{ref-crawford2010linking}{}}%
-Crawford, E.
-R., LePine, J.
-A., \& Rich, B.
-L.
-(2010).
-Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test.
-\emph{Journal of Applied Psychology}, \emph{95}(5), 834.
+\bibitem[\citeproctext]{ref-crawford2010linking}
+Crawford ER, LePine JA and Rich BL (2010) Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test.
+\emph{Journal of applied psychology} 95(5).
+American Psychological Association: 834.
 
-\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
-Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
+\bibitem[\citeproctext]{ref-demerouti2001job}
+Demerouti E, Bakker AB, Nachreiner F, et al. (2001) The job demands-resources model of burnout. \emph{Journal of Applied psychology} 86(3). American Psychological Association: 499.
 
-\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
-Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
+\bibitem[\citeproctext]{ref-gerich2017relevance}
+Gerich J (2017) The relevance of challenge and hindrance appraisals of working conditions for employees' health.
+\emph{International Journal of Stress Management} 24(3).
+Educational Publishing Foundation: 270.
 
-\leavevmode\vadjust pre{\hypertarget{ref-hakanen2008job}{}}%
-Hakanen, J.
-J., Schaufeli, W.
-B., \& Ahola, K.
-(2008).
-The job demands-resources model: A three-year cross-lagged study of burnout, depression, commitment, and work engagement.
-\emph{Work \& Stress}, \emph{22}(3), 224--241.
+\bibitem[\citeproctext]{ref-hakanen2008job}
+Hakanen JJ, Schaufeli WB and Ahola K (2008) The job demands-resources model: A three-year cross-lagged study of burnout, depression, commitment, and work engagement.
+\emph{Work \& stress} 22(3).
+Taylor \& Francis: 224--241.
 
-\leavevmode\vadjust pre{\hypertarget{ref-horan2020review}{}}%
-Horan, K.
-A., Nakahara, W.
-H., DiStaso, M.
-J., \& Jex, S.
-M.
-(2020).
-A review of the challenge-hindrance stress model: Recent advances, expanded paradigms, and recommendations for future research.
-\emph{Frontiers in Psychology}, \emph{11}, 560346.
+\bibitem[\citeproctext]{ref-horan2020review}
+Horan KA, Nakahara WH, DiStaso MJ, et al.
+(2020) A review of the challenge-hindrance stress model: Recent advances, expanded paradigms, and recommendations for future research.
+\emph{Frontiers in Psychology} 11.
+Frontiers Media SA: 560346.
 
-\leavevmode\vadjust pre{\hypertarget{ref-kim2020thriving}{}}%
-Kim, M., \& Beehr, T.
-A.
-(2020).
-Thriving on demand: Challenging work results in employee flourishing through appraisals and resources.
-\emph{International Journal of Stress Management}, \emph{27}(2), 111.
+\bibitem[\citeproctext]{ref-kim2020thriving}
+Kim M and Beehr TA (2020) Thriving on demand: Challenging work results in employee flourishing through appraisals and resources.
+\emph{International Journal of Stress Management} 27(2).
+Educational Publishing Foundation: 111.
 
-\leavevmode\vadjust pre{\hypertarget{ref-kubicek2023all}{}}%
-Kubicek, B., Uhlig, L., Hülsheger, U.
-R., Korunka, C., \& Prem, R.
-(2023).
-Are all challenge stressors beneficial for learning?
+\bibitem[\citeproctext]{ref-kubicek2023all}
+Kubicek B, Uhlig L, Hülsheger UR, et al.
+(2023) Are all challenge stressors beneficial for learning?
 A meta-analytical assessment of differential effects of workload and cognitive demands.
-\emph{Work \& Stress}, \emph{37}(3), 269--298.
+\emph{Work \& Stress} 37(3).
+Taylor \& Francis: 269--298.
 
-\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
-Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
+\bibitem[\citeproctext]{ref-lazarus1984stress}
+Lazarus RS and Folkman S (1984) \emph{Stress, Appraisal, and Coping}. Springer publishing company.
 
-\leavevmode\vadjust pre{\hypertarget{ref-lepine2005meta}{}}%
-LePine, J.
-A., Podsakoff, N.
-P., \& LePine, M.
-A.
-(2005).
-A meta-analytic test of the challenge stressor--hindrance stressor framework: An explanation for inconsistent relationships among stressors and performance.
-\emph{Academy of Management Journal}, \emph{48}(5), 764--775.
+\bibitem[\citeproctext]{ref-lepine2005meta}
+LePine JA, Podsakoff NP and LePine MA (2005) A meta-analytic test of the challenge stressor--hindrance stressor framework: An explanation for inconsistent relationships among stressors and performance.
+\emph{Academy of management journal} 48(5).
+Academy of Management Briarcliff Manor, NY 10510: 764--775.
 
-\leavevmode\vadjust pre{\hypertarget{ref-lepine2022challenge}{}}%
-LePine, M. A. (2022). The challenge-hindrance stressor framework: An integrative conceptual review and path forward. \emph{Group \& Organization Management}, \emph{47}(2), 223--254.
+\bibitem[\citeproctext]{ref-lepine2022challenge}
+LePine MA (2022) The challenge-hindrance stressor framework: An integrative conceptual review and path forward.
+\emph{Group \& Organization Management} 47(2).
+SAGE Publications Sage CA: Los Angeles, CA: 223--254.
 
-\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
-Peterson, N.
-G., Mumford, M.
-D., Borman, W.
-C., Jeanneret, P.
-R., Fleishman, E.
-A., Levin, K.
-Y., Campion, M.
-A., Mayfield, M.
-S., Morgeson, F.
-P., Pearlman, K., et al.
-(2001).
-Understanding work using the occupational information network (o* NET): Implications for practice and research.
-\emph{Personnel Psychology}, \emph{54}(2), 451--492.
+\bibitem[\citeproctext]{ref-peterson2001understanding}
+Peterson NG, Mumford MD, Borman WC, et al.
+(2001) Understanding work using the occupational information network (o* NET): Implications for practice and research.
+\emph{Personnel psychology} 54(2).
+Wiley Online Library: 451--492.
 
-\leavevmode\vadjust pre{\hypertarget{ref-pindek2024dynamic}{}}%
-Pindek, S., Meyer, K., Valvo, A., \& Arvan, M.
-(2024).
-A dynamic view of the challenge-hindrance stressor framework: A meta-analysis of daily diary studies.
-\emph{Journal of Business and Psychology}, 1--19.
+\bibitem[\citeproctext]{ref-pindek2024dynamic}
+Pindek S, Meyer K, Valvo A, et al.
+(2024) A dynamic view of the challenge-hindrance stressor framework: A meta-analysis of daily diary studies.
+\emph{Journal of Business and Psychology}.
+Springer: 1--19.
 
-\leavevmode\vadjust pre{\hypertarget{ref-podsakoff2007differential}{}}%
-Podsakoff, N.
-P., LePine, J.
-A., \& LePine, M.
-A.
-(2007).
-Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis.
-\emph{Journal of Applied Psychology}, \emph{92}(2), 438.
+\bibitem[\citeproctext]{ref-podsakoff2007differential}
+Podsakoff NP, LePine JA and LePine MA (2007) Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis.
+\emph{Journal of applied psychology} 92(2).
+American Psychological Association: 438.
 
-\leavevmode\vadjust pre{\hypertarget{ref-rosen2020challenges}{}}%
-Rosen, C.
-C., Dimotakis, N., Cole, M.
-S., Taylor, S.
-G., Simon, L.
-S., Smith, T.
-A., \& Reina, C.
-S.
-(2020).
-When challenges hinder: An investigation of when and how challenge stressors impact employee outcomes.
-\emph{Journal of Applied Psychology}, \emph{105}(10), 1181.
+\bibitem[\citeproctext]{ref-rosen2020challenges}
+Rosen CC, Dimotakis N, Cole MS, et al.
+(2020) When challenges hinder: An investigation of when and how challenge stressors impact employee outcomes.
+\emph{Journal of Applied Psychology} 105(10).
+American Psychological Association: 1181.
 
-\leavevmode\vadjust pre{\hypertarget{ref-schaufeli2017applying}{}}%
-Schaufeli, W. B. (2017). Applying the job demands-resources model: A `how to'guide to measuring and tackling work engagement and burnout. \emph{Organizational Dynamics}, \emph{46}(2), 120--132.
+\bibitem[\citeproctext]{ref-schaufeli2017applying}
+Schaufeli WB (2017) Applying the job demands-resources model: A `how to'guide to measuring and tackling work engagement and burnout. \emph{Organizational dynamics} 46(2). Elsevier: 120--132.
 
-\leavevmode\vadjust pre{\hypertarget{ref-searle2015merits}{}}%
-Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.
+\bibitem[\citeproctext]{ref-searle2015merits}
+Searle BJ and Auton JC (2015) The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping} 28(2). Taylor \& Francis: 121--143.
 
-\leavevmode\vadjust pre{\hypertarget{ref-webster2010toward}{}}%
-Webster, J.
-R., Beehr, T.
-A., \& Christiansen, N.
-D.
-(2010).
-Toward a better understanding of the effects of hindrance and challenge stressors on work behavior.
-\emph{Journal of Vocational Behavior}, \emph{76}(1), 68--77.
+\bibitem[\citeproctext]{ref-webster2010toward}
+Webster JR, Beehr TA and Christiansen ND (2010) Toward a better understanding of the effects of hindrance and challenge stressors on work behavior.
+\emph{Journal of Vocational Behavior} 76(1).
+Elsevier: 68--77.
 
-\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
-Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.
+\bibitem[\citeproctext]{ref-webster2011extending}
+Webster JR, Beehr TA and Love K (2011) Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior} 79(2). Elsevier: 505--516.
 
-\leavevmode\vadjust pre{\hypertarget{ref-xanthopoulou2007job}{}}%
-Xanthopoulou, D., Bakker, A.
-B., Dollard, M.
-F., Demerouti, E., Schaufeli, W.
-B., Taris, T.
-W., \& Schreurs, P.
-J.
-(2007).
-When do job demands particularly predict burnout?
+\bibitem[\citeproctext]{ref-xanthopoulou2007job}
+Xanthopoulou D, Bakker AB, Dollard MF, et al.
+(2007) When do job demands particularly predict burnout?
 The moderating role of job resources.
-\emph{Journal of Managerial Psychology}, \emph{22}(8), 766--786.
+\emph{Journal of managerial psychology} 22(8).
+Emerald Group Publishing Limited: 766--786.
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-careless}{}}%
-Yentes, R. D., \& Wilhelm, F. (2021). \emph{Careless: Procedures for computing indices of careless responding}.
+\bibitem[\citeproctext]{ref-R-careless}
+Yentes RD and Wilhelm F (2021) \emph{Careless: Procedures for Computing Indices of Careless Responding}.
 

### 2025-06-12 Submission.Rmd
coffee shop edits

@@
 abstract: |
-  Discussions of job characteristics often include a (tacit) characterization that these job elements are either resources or demands.
+  Discussions of job characteristics often include a tacit characterization that these job elements are either resources or demands.
 The current study documents variability in ratings of O\*Net specifications with respect to subjective interpretation of job characteristics and predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes.
 We additionally explore the potential moderating role of resources on these relationships.
-Results support the perspective that job characteristics are not uniquely categorized as a resource or demand, but rather, challenging elements tend to *also* be interpreted as job resources.
+Results support the perspective that job characteristics are not uniquely categorized as a resource or demand, but rather, what is viewed as challenging is also commonly be interpreted as resourceful.
 Furthermore, greater experienced resources moderate the challenge--engagement relationship as well as the hindrance-stress and hindrance--burnout relationships.
-These findings broadly suggest that challenging demands may also provide opportunity in the form of job resources, and what is viewed as a *hindrance* exhibits considerable variability.
+These findings broadly suggest that challenging demands may also provide job redesign opportunity via reframing as resource.
 
@@
 
-The job demands-resources theory (e.g., Bakker & Demerouti, 2014; 2017) highlights the importance of demands and resources on the experience of motivation and strain as well as other, less proximal outcomes.
-Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job].
+Job demands-resources theory (e.g., Bakker & Demerouti, 2014; 2017) highlights the importance of demands and resources on the employee experience of motivation and strain as well as other, less proximal outcomes.
+Resources include physical, psychological, social, or organizational aspects of jobs that help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job].
 In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001).
@@
 
-@cavanaugh2000empirical extended this orientation by proposing a framework that distinguishes between *two forms* of demands -- *challenges* and *hindrances*.
-Challenge demands promote mastery, personal growth, and future gains – these demands should lead to coping strategies that facilitate achievement.
+@cavanaugh2000empirical extended this framework by proposing a distinction between *two forms* of demands -- *challenges* and *hindrances*.
+Challenge demands promote mastery, personal growth, and future gains –- these demands should lead to coping strategies that facilitate achievement.
 Work characteristics consistent with this definition, for example, include time pressure and responsibility [@lepine2022challenge].
-Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
+Hindrance demands, in contrast, inhibit growth, learning, and the general achievement of goals.
 Example hindrance demands that have been previously noted include role conflict and role ambiguity [@lepine2022challenge].
@@
 
-@lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes.
+@lepine2022challenge deconstruct the mechanisms by which demands are related to performance and wellbeing outcomes.
 First, demands appraised as *challenges* typically result in a more positive appraisal, and engagement is likely to happen as a result.
@@
 Disengagement is likely to result from a hindrance appraisal, which then negatively impacts motivation, performance, growth and wellbeing.
-This happens because resources are depleted via frustrations and other negative affect reactions [@lepine2022challenge].
+This happens because resources are depleted via frustrations and other negative affect--laden reactions [@lepine2022challenge].
 

### 2025-06-12 Submission.tex
coffee shop edits

@@
 \abstract{%
-Discussions of job characteristics often include a (tacit) characterization that these job elements are either resources or demands.
+Discussions of job characteristics often include a tacit characterization that these job elements are either resources or demands.
 The current study documents variability in ratings of O*Net specifications with respect to subjective interpretation of job characteristics and predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes.
 We additionally explore the potential moderating role of resources on these relationships.
-Results support the perspective that job characteristics are not uniquely categorized as a resource or demand, but rather, challenging elements tend to \emph{also} be interpreted as job resources.
+Results support the perspective that job characteristics are not uniquely categorized as a resource or demand, but rather, what is viewed as challenging is also commonly be interpreted as resourceful.
 Furthermore, greater experienced resources moderate the challenge--engagement relationship as well as the hindrance-stress and hindrance--burnout relationships.
-These findings broadly suggest that challenging demands may also provide opportunity in the form of job resources, and what is viewed as a \emph{hindrance} exhibits considerable variability.
+These findings broadly suggest that challenging demands may also provide job redesign opportunity via reframing as resource.
 }
@@
 
-\subsection{Theoretical Foundations}\label{theoretical-foundations}
+\hypertarget{theoretical-foundations}{%
+\subsection{Theoretical Foundations}\label{theoretical-foundations}}
 
-The job demands-resources theory (e.g., Bakker \& Demerouti, 2014; 2017) highlights the importance of demands and resources on the experience of motivation and strain as well as other, less proximal outcomes.
-Resources include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker and Demerouti, 2014, 2017).
+Job demands-resources theory (e.g., Bakker \& Demerouti, 2014; 2017) highlights the importance of demands and resources on the employee experience of motivation and strain as well as other, less proximal outcomes.
+Resources include physical, psychological, social, or organizational aspects of jobs that help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker and Demerouti, 2014, 2017).
 In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001).
@@
 Cavanaugh et al.
-(2000) extended this orientation by proposing a framework that distinguishes between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}.
-Challenge demands promote mastery, personal growth, and future gains -- these demands should lead to coping strategies that facilitate achievement.
+(2000) extended this framework by proposing a distinction between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}.
+Challenge demands promote mastery, personal growth, and future gains --- these demands should lead to coping strategies that facilitate achievement.
 Work characteristics consistent with this definition, for example, include time pressure and responsibility (LePine, 2022).
-Hindrance demands, in contrast, inhibit growth, learning and goal achievement.
+Hindrance demands, in contrast, inhibit growth, learning, and the general achievement of goals.
 Example hindrance demands that have been previously noted include role conflict and role ambiguity (LePine, 2022).
 
-LePine (2022) explain the mechanisms by which demands are related to performance and wellbeing outcomes.
+LePine (2022) deconstruct the mechanisms by which demands are related to performance and wellbeing outcomes.
 First, demands appraised as \emph{challenges} typically result in a more positive appraisal, and engagement is likely to happen as a result.
@@
 Disengagement is likely to result from a hindrance appraisal, which then negatively impacts motivation, performance, growth and wellbeing.
-This happens because resources are depleted via frustrations and other negative affect reactions (LePine, 2022).
+This happens because resources are depleted via frustrations and other negative affect--laden reactions (LePine, 2022).
 
@@
 
-\phantomsection\label{refs}
-\begin{CSLReferences}{1}{1}
-\bibitem[\citeproctext]{ref-abbas2019challenge}
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-abbas2019challenge}{}}%
 Abbas M and Raja U (2019) Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology} 34(2). Springer: 189--201.
 
-\bibitem[\citeproctext]{ref-bakker2014job}
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
 Bakker AB and Demerouti E (2014) Job demands--resources theory. \emph{Wellbeing: A complete reference guide}. John Wiley \& Sons, Ltd Chichester, UK: 1--28.
 
-\bibitem[\citeproctext]{ref-bakker2017job}
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
 Bakker AB and Demerouti E (2017) Job demands--resources theory: Taking stock and looking forward. \emph{Journal of occupational health psychology} 22(3). Educational Publishing Foundation: 273.
 
-\bibitem[\citeproctext]{ref-bakker2013weekly}
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
 Bakker AB and Sanz-Vergel AI (2013) Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior} 83(3). Elsevier: 397--409.
 
-\bibitem[\citeproctext]{ref-bakker2005job}
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2005job}{}}%
 Bakker AB, Demerouti E and Euwema MC (2005) Job resources buffer the impact of job demands on burnout. \emph{Journal of occupational health psychology} 10(2). Educational Publishing Foundation: 170.
 
-\bibitem[\citeproctext]{ref-bakker2007job}
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2007job}{}}%
 Bakker AB, Hakanen JJ, Demerouti E, et al.
@@
 
-\bibitem[\citeproctext]{ref-cavanaugh2000empirical}
+\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
 Cavanaugh MA, Boswell WR, Roehling MV, et al.
@@
 
-\bibitem[\citeproctext]{ref-chen2021daily}
+\leavevmode\vadjust pre{\hypertarget{ref-chen2021daily}{}}%
 Chen H, Wang H, Yuan M, et al. (2021) Daily challenge/hindrance demands and cognitive wellbeing: A multilevel moderated mediation model. \emph{Frontiers in Psychology} 12. Frontiers Media SA: 616002.
 
-\bibitem[\citeproctext]{ref-crawford2010linking}
+\leavevmode\vadjust pre{\hypertarget{ref-crawford2010linking}{}}%
 Crawford ER, LePine JA and Rich BL (2010) Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test.
@@
 
-\bibitem[\citeproctext]{ref-demerouti2001job}
+\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
 Demerouti E, Bakker AB, Nachreiner F, et al. (2001) The job demands-resources model of burnout. \emph{Journal of Applied psychology} 86(3). American Psychological Association: 499.
 
-\bibitem[\citeproctext]{ref-gerich2017relevance}
+\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
 Gerich J (2017) The relevance of challenge and hindrance appraisals of working conditions for employees' health.
@@
 
-\bibitem[\citeproctext]{ref-hakanen2008job}
+\leavevmode\vadjust pre{\hypertarget{ref-hakanen2008job}{}}%
 Hakanen JJ, Schaufeli WB and Ahola K (2008) The job demands-resources model: A three-year cross-lagged study of burnout, depression, commitment, and work engagement.
@@
 
-\bibitem[\citeproctext]{ref-horan2020review}
+\leavevmode\vadjust pre{\hypertarget{ref-horan2020review}{}}%
 Horan KA, Nakahara WH, DiStaso MJ, et al.
@@
 
-\bibitem[\citeproctext]{ref-kim2020thriving}
+\leavevmode\vadjust pre{\hypertarget{ref-kim2020thriving}{}}%
 Kim M and Beehr TA (2020) Thriving on demand: Challenging work results in employee flourishing through appraisals and resources.
@@
 
-\bibitem[\citeproctext]{ref-kubicek2023all}
+\leavevmode\vadjust pre{\hypertarget{ref-kubicek2023all}{}}%
 Kubicek B, Uhlig L, Hülsheger UR, et al.
@@
 
-\bibitem[\citeproctext]{ref-lazarus1984stress}
+\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
 Lazarus RS and Folkman S (1984) \emph{Stress, Appraisal, and Coping}. Springer publishing company.
 
-\bibitem[\citeproctext]{ref-lepine2005meta}
+\leavevmode\vadjust pre{\hypertarget{ref-lepine2005meta}{}}%
 LePine JA, Podsakoff NP and LePine MA (2005) A meta-analytic test of the challenge stressor--hindrance stressor framework: An explanation for inconsistent relationships among stressors and performance.
@@
 
-\bibitem[\citeproctext]{ref-lepine2022challenge}
+\leavevmode\vadjust pre{\hypertarget{ref-lepine2022challenge}{}}%
 LePine MA (2022) The challenge-hindrance stressor framework: An integrative conceptual review and path forward.
@@
 
-\bibitem[\citeproctext]{ref-peterson2001understanding}
+\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
 Peterson NG, Mumford MD, Borman WC, et al.
@@
 
-\bibitem[\citeproctext]{ref-pindek2024dynamic}
+\leavevmode\vadjust pre{\hypertarget{ref-pindek2024dynamic}{}}%
 Pindek S, Meyer K, Valvo A, et al.
@@
 
-\bibitem[\citeproctext]{ref-podsakoff2007differential}
+\leavevmode\vadjust pre{\hypertarget{ref-podsakoff2007differential}{}}%
 Podsakoff NP, LePine JA and LePine MA (2007) Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis.
@@
 
-\bibitem[\citeproctext]{ref-rosen2020challenges}
+\leavevmode\vadjust pre{\hypertarget{ref-rosen2020challenges}{}}%
 Rosen CC, Dimotakis N, Cole MS, et al.
@@
 
-\bibitem[\citeproctext]{ref-schaufeli2017applying}
+\leavevmode\vadjust pre{\hypertarget{ref-schaufeli2017applying}{}}%
 Schaufeli WB (2017) Applying the job demands-resources model: A `how to'guide to measuring and tackling work engagement and burnout. \emph{Organizational dynamics} 46(2). Elsevier: 120--132.
 
-\bibitem[\citeproctext]{ref-searle2015merits}
+\leavevmode\vadjust pre{\hypertarget{ref-searle2015merits}{}}%
 Searle BJ and Auton JC (2015) The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping} 28(2). Taylor \& Francis: 121--143.
 
-\bibitem[\citeproctext]{ref-webster2010toward}
+\leavevmode\vadjust pre{\hypertarget{ref-webster2010toward}{}}%
 Webster JR, Beehr TA and Christiansen ND (2010) Toward a better understanding of the effects of hindrance and challenge stressors on work behavior.
@@
 
-\bibitem[\citeproctext]{ref-webster2011extending}
+\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
 Webster JR, Beehr TA and Love K (2011) Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior} 79(2). Elsevier: 505--516.
 
-\bibitem[\citeproctext]{ref-xanthopoulou2007job}
+\leavevmode\vadjust pre{\hypertarget{ref-xanthopoulou2007job}{}}%
 Xanthopoulou D, Bakker AB, Dollard MF, et al.
@@
 
-\bibitem[\citeproctext]{ref-R-careless}
+\leavevmode\vadjust pre{\hypertarget{ref-R-careless}{}}%
 Yentes RD and Wilhelm F (2021) \emph{Careless: Procedures for Computing Indices of Careless Responding}.

### 2025-06-19 Submission.Rmd
Caribou edits

@@
 ---
-title             : "Shared Characterizations of Demands and Resources across O*NET Job Elements"
+title             : "Shared Characterizations of Challenging Demands and Job Resources across O*NET Element Classifications"
 shorttitle        : "O*NET JD-R"
@@
 Furthermore, greater experienced resources moderate the challenge--engagement relationship as well as the hindrance-stress and hindrance--burnout relationships.
-These findings broadly suggest that challenging demands may also provide job redesign opportunity via reframing as resource.
+These findings broadly support the non--mutually exclusive perspective on job characteristic appraisal as well as multiple theoretically--specified outcome associations.
 
@@
 We build on a growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges].
-Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to perception as resource and/or demand, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) resources buffer the relationships between demands and negative work outcomes.
-We investigate these associations via the lens of [O\*Net job specifications](https://www.onetcenter.org/content.html), which provides a broad framework of specification regarding generalizable job characteristics.
+Our primary aims explore: 1) variability in subjective ratings of job characteristics with respect to perception as resource and/or demand, 2) differential association (of subjective appraisals) with positive and negative outcomes, and 3) the buffering effect of resources on the relationships between demands and negative work outcomes^[Took out previous #2 -- make sure this isn't revisited in Results or Discussion].
+We investigate these associations via the lens of [O\*Net job specifications](https://www.onetcenter.org/content.html), which provide a near--exhaustive listing of generalizable characteristic specifications.
 
@@
 @cavanaugh2000empirical extended this framework by proposing a distinction between *two forms* of demands -- *challenges* and *hindrances*.
-Challenge demands promote mastery, personal growth, and future gains –- these demands should lead to coping strategies that facilitate achievement.
+Challenge demands promote mastery, personal growth, and future gains.
+These demands should lead to coping strategies that facilitate achievement.
 Work characteristics consistent with this definition, for example, include time pressure and responsibility [@lepine2022challenge].
@@
 
-@lepine2022challenge deconstruct the mechanisms by which demands are related to performance and wellbeing outcomes.
+@lepine2022challenge deconstructs the mechanisms by which demands are related to performance and wellbeing outcomes.
 First, demands appraised as *challenges* typically result in a more positive appraisal, and engagement is likely to happen as a result.
@@
 Interestingly, much of our existing knowledge regarding the way these relationships between resources/demands and outcomes (e.g., stress, engagement) function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands.
-@pindek2024dynamic notes this limitation of *a priori* classification of characteristics as demands, challenges, or hindrances, as do @horan2020review.
-In fact, although much of our research on job demands is based on *a priori* classifications [@searle2015merits], the most recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., two different employees could most certainly perceive "delivering face--to--face presentations" as a resource or as a demand).
-
-Aligned with this relativistic perspective on the experience of work, @horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process into the challenge-hindrance stressor framework.
+@pindek2024dynamic notes these *a priori* classification of characteristics as demands, challenges, or hindrances as a methdological limitation, as do @horan2020review.
+In fact, although much of our research on job demands is based on such exclusive classifications [@searle2015merits], the most recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., two different employees could most certainly perceive "daily interaction with co-workers" as a resource or as a demand).
+
+Aligned with this relativistic perspective on the experience of work, @horan2020review and @lepine2022challenge explicitly articulate the need for future research to incorporate the *appraisal process* into the challenge-hindrance stressor framework.
 In fact, @horan2020review state that “…stressors are only challenge or hindrance demands to the extent that they are perceived as such by employees” (p.
@@
 
-Given the above, the first question we pose is whether people exclusively experience job elements as resources, challenges, or hindrances, or whether a given job characteristic might be mutually considered as more than one of these (e.g., both a challenge and a resource).
+Given the above, the first question we pose is whether workers exclusively experience job elements as resources, challenges, or hindrances, or whether a given job characteristic might be mutually considered as more than one of these (e.g., both a challenge and a resource).
 Evidence suggests that employees do, at least, differentiate between challenge and hindrance demands [e.g., @bakker2013weekly; @gerich2017relevance; @webster2011extending].
@@
 
->Hypothesis 1: Job characteristics vary regarding subjective worker perception as a challenge or hindrance demand, or resource.
-
->Hypothesis 2: Job characteristics are not exclusively categorized as a resource or demand, but rather, some job characteristics are viewed as both a resource and a demand.
-
-## Connecting Appraisals to Workplace Outcomes
-
-The second set of predictions focus on associations with theory--derived outcomes across two theoretical frameworks.
-Both the job demands--resources model [@bakker2017job] and the challenge-hindrance stressor framework [@cavanaugh2000empirical] have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, commitment, and performance [e.g., @lepine2005meta].
-We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout.
-See Figure \@ref(fig:ourmodel) for proposed associations, **with dotted and solid lines indicating...** .
+>Hypothesis 1: Job characteristics vary regarding subjective worker perception as challenge, hindrance, or resource
+
+>Hypothesis 2: Job characteristics are not exclusively categorized as a resource or demand, but rather, some job characteristics are viewed as both resourceful and demanding
+
+## Connecting Appraisals to Workplace Outcomes^[whole section needs reworking/reframing -- above ok 6/19/25]
+
+The second set of predictions is focused on associations between appraisals and work outcomes.
+Both the job demands--resources model [@bakker2017job] as well as the challenge-hindrance stressor framework [@cavanaugh2000empirical] have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, commitment, and performance [e.g., @lepine2005meta].
+The current project will focus on three outcomes: engagement, strain, and burnout.
+See Figure \@ref(fig:ourmodel) for proposed associations.
 Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job], and empirical work suggests that they are associated with positive outcomes.

### 2025-06-19 Submission.tex
Caribou edits

@@
 \hypersetup{
-  pdftitle={Shared Characterizations of Demands and Resources across O*NET Job Elements},
+  pdftitle={Shared Characterizations of Challenging Demands and Job Resources across O*NET Element Classifications},
   pdfauthor={Alicia Stachowski2, John Kulas1, \& Renata García Prieto Palacios Roji3},
@@
 
-\title{Shared Characterizations of Demands and Resources across O*NET Job Elements}
+\title{Shared Characterizations of Challenging Demands and Job Resources across O*NET Element Classifications}
 \author{Alicia Stachowski\textsuperscript{2}, John Kulas\textsuperscript{1}, \& Renata García Prieto Palacios Roji\textsuperscript{3}}
@@
 Furthermore, greater experienced resources moderate the challenge--engagement relationship as well as the hindrance-stress and hindrance--burnout relationships.
-These findings broadly suggest that challenging demands may also provide job redesign opportunity via reframing as resource.
+These findings broadly support the non--mutually exclusive perspective on job characteristic appraisal as well as multiple theoretically--specified outcome associations.
 }
@@
 We build on a growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020).
-Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to perception as resource and/or demand, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) resources buffer the relationships between demands and negative work outcomes.
-We investigate these associations via the lens of \href{https://www.onetcenter.org/content.html}{O*Net job specifications}, which provides a broad framework of specification regarding generalizable job characteristics.
+Our primary aims explore: 1) variability in subjective ratings of job characteristics with respect to perception as resource and/or demand, 2) differential association (of subjective appraisals) with positive and negative outcomes, and 3) the buffering effect of resources on the relationships between demands and negative work outcomes\footnote{Took out previous \#2 -- make sure this isn't revisited in Results or Discussion}.
+We investigate these associations via the lens of \href{https://www.onetcenter.org/content.html}{O*Net job specifications}, which provide a near--exhaustive listing of generalizable characteristic specifications.
 
@@
 (2000) extended this framework by proposing a distinction between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}.
-Challenge demands promote mastery, personal growth, and future gains --- these demands should lead to coping strategies that facilitate achievement.
+Challenge demands promote mastery, personal growth, and future gains.
+These demands should lead to coping strategies that facilitate achievement.
 Work characteristics consistent with this definition, for example, include time pressure and responsibility (LePine, 2022).
@@
 
-LePine (2022) deconstruct the mechanisms by which demands are related to performance and wellbeing outcomes.
+LePine (2022) deconstructs the mechanisms by which demands are related to performance and wellbeing outcomes.
 First, demands appraised as \emph{challenges} typically result in a more positive appraisal, and engagement is likely to happen as a result.
@@
 Pindek et al.
-(2024) notes this limitation of \emph{a priori} classification of characteristics as demands, challenges, or hindrances, as do Horan et al.
+(2024) notes these \emph{a priori} classification of characteristics as demands, challenges, or hindrances as a methdological limitation, as do Horan et al.
 (2020).
-In fact, although much of our research on job demands is based on \emph{a priori} classifications (Searle and Auton, 2015), the most recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., two different employees could most certainly perceive ``delivering face--to--face presentations'' as a resource or as a demand).
+In fact, although much of our research on job demands is based on such exclusive classifications (Searle and Auton, 2015), the most recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., two different employees could most certainly perceive ``daily interaction with co-workers'' as a resource or as a demand).
 
 Aligned with this relativistic perspective on the experience of work, Horan et al.
-(2020) and LePine (2022) specifically call out the need for additional research to incorporate the appraisal process into the challenge-hindrance stressor framework.
+(2020) and LePine (2022) explicitly articulate the need for future research to incorporate the \emph{appraisal process} into the challenge-hindrance stressor framework.
 In fact, Horan et al.
@@
 
-Given the above, the first question we pose is whether people exclusively experience job elements as resources, challenges, or hindrances, or whether a given job characteristic might be mutually considered as more than one of these (e.g., both a challenge and a resource).
+Given the above, the first question we pose is whether workers exclusively experience job elements as resources, challenges, or hindrances, or whether a given job characteristic might be mutually considered as more than one of these (e.g., both a challenge and a resource).
 Evidence suggests that employees do, at least, differentiate between challenge and hindrance demands (e.g., Bakker and Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011).
@@
 \begin{quote}
-Hypothesis 1: Job characteristics vary regarding subjective worker perception as a challenge or hindrance demand, or resource.
+Hypothesis 1: Job characteristics vary regarding subjective worker perception as challenge, hindrance, or resource
 \end{quote}
@@
 \begin{quote}
-Hypothesis 2: Job characteristics are not exclusively categorized as a resource or demand, but rather, some job characteristics are viewed as both a resource and a demand.
+Hypothesis 2: Job characteristics are not exclusively categorized as a resource or demand, but rather, some job characteristics are viewed as both resourceful and demanding
 \end{quote}
@@
 \hypertarget{connecting-appraisals-to-workplace-outcomes}{%
-\subsection{Connecting Appraisals to Workplace Outcomes}\label{connecting-appraisals-to-workplace-outcomes}}
+\subsection[Connecting Appraisals to Workplace Outcomes]{\texorpdfstring{Connecting Appraisals to Workplace Outcomes\footnote{whole section needs reworking/reframing -- above ok 6/19/25}}{Connecting Appraisals to Workplace Outcomes}}\label{connecting-appraisals-to-workplace-outcomes}}
 
-The second set of predictions focus on associations with theory--derived outcomes across two theoretical frameworks.
-Both the job demands--resources model (Bakker and Demerouti, 2017) and the challenge-hindrance stressor framework (Cavanaugh et al., 2000) have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, commitment, and performance (e.g., LePine et al., 2005).
-We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout.
-See Figure \ref{fig:ourmodel} for proposed associations, \textbf{with dotted and solid lines indicating\ldots{}} .
+The second set of predictions is focused on associations between appraisals and work outcomes.
+Both the job demands--resources model (Bakker and Demerouti, 2017) as well as the challenge-hindrance stressor framework (Cavanaugh et al., 2000) have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, commitment, and performance (e.g., LePine et al., 2005).
+The current project will focus on three outcomes: engagement, strain, and burnout.
+See Figure \ref{fig:ourmodel} for proposed associations.
 Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker and Demerouti, 2014, 2017), and empirical work suggests that they are associated with positive outcomes.

### 2025-07-03 Submission.Rmd
pushing to desktop

@@
 
-## Connecting Appraisals to Workplace Outcomes^[whole section needs reworking/reframing -- above ok 6/19/25]
-
-The second set of predictions is focused on associations between appraisals and work outcomes.
-Both the job demands--resources model [@bakker2017job] as well as the challenge-hindrance stressor framework [@cavanaugh2000empirical] have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, commitment, and performance [e.g., @lepine2005meta].
-The current project will focus on three outcomes: engagement, strain, and burnout.
-See Figure \@ref(fig:ourmodel) for proposed associations.
-Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job], and empirical work suggests that they are associated with positive outcomes.
-Relevant to the current study, for example, @hakanen2008job found job resources influenced future work engagement.
+## Connecting Appraisals to Workplace Outcomes
+
+Both the job demands--resources model [@bakker2017job] as well as the challenge--hindrance stressor framework [@cavanaugh2000empirical] have been useful in the prediction of a wide variety of organizational outcomes including job satisfaction, motivation, commitment, and performance [e.g., @lepine2005meta].
+Empirical work generally suggests that *resources* are commonly associated with positive outcomes, including, most relevant for the current investigation, employee engagement.
+For example, @hakanen2008job found that job resources influenced future work engagement.
 Moreover, in a sample of teachers and dentists, @bakker2007job found that resources were most predictive of engagement when job demands were especially high.
-Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement [e.g., @schaufeli2017applying].
-
-```{r ourmodel, eval=TRUE, echo=FALSE, fig.cap="Focal constructs and associations of interest"}
+Meta analyses have also concluded that there is a positive association with a variety of resource elements and engagement [e.g., @schaufeli2017applying].
+
+```{r ourmodel, eval=TRUE, echo=FALSE, fig.cap="Focal constructs and predicted associations"}
 library(magick)
@@
 
-The findings regarding demands are more complex, presumably because the way challenge vs.
-hindrance appraisals influence coping strategies.
-Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work [@chen2021daily], engagement [@crawford2010linking], and strain and turnover intentions [e.g., @abbas2019challenge], for example.
-Challenge appraisals have also been negatively associated with job search behaviors [e.g., @cavanaugh2000empirical].
-**CLARIFY**
-
-When a demand is appraised as a hindrance, it is negatively associated with motivational resources [@kim2020thriving], engagement [@crawford2010linking], job search behaviors and job satisfaction [@cavanaugh2000empirical].
-@chen2021daily found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment.
-Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands [@podsakoff2007differential].
-Interestingly, both challenges and hindrances have been shown to positively predict strain [@abbas2019challenge; @lepine2005meta; @podsakoff2007differential; @webster2010toward], which further highlights the complex association between appraisals and subsequent outcomes.
-Given the differential relationships described above, we make the following predictions (see Figure \@ref(fig:ourmodel)):
+The findings regarding demands are more complex.
+When a demand is appraised as a hindrance, it is negatively associated with motivational resources [@kim2020thriving], engagement [@crawford2010linking], job search behaviors, and job satisfaction [@cavanaugh2000empirical].
+@chen2021daily further found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment.
+Turnover intentions, actual turnover and withdrawal behaviors have also been associated with hindrance demands [@podsakoff2007differential].
+Appraising a demand as a *challenge*, however, has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work, @chen2021daily, engagement, @crawford2010linking, and strain and turnover intentions, e.g., @abbas2019challenge).
+Challenge appraisals have also been found to ehave negative associations with job search behaviors [e.g., @cavanaugh2000empirical].
+Interestingly, both challenges and hindrances have been shown to positively predict strain [@abbas2019challenge; @lepine2005meta; @podsakoff2007differential; @webster2010toward], which further highlights the complex association between characteristic appraisals and important work outcomes.
+Given the differential relationships described above, and a focus on three outcomes (engagement, strain, and burnout) we make the following predictions (see Figure \@ref(fig:ourmodel)):
 

### 2025-07-03 Submission.tex
pushing to desktop

@@
 \hypertarget{connecting-appraisals-to-workplace-outcomes}{%
-\subsection[Connecting Appraisals to Workplace Outcomes]{\texorpdfstring{Connecting Appraisals to Workplace Outcomes\footnote{whole section needs reworking/reframing -- above ok 6/19/25}}{Connecting Appraisals to Workplace Outcomes}}\label{connecting-appraisals-to-workplace-outcomes}}
+\subsection{Connecting Appraisals to Workplace Outcomes}\label{connecting-appraisals-to-workplace-outcomes}}
 
-The second set of predictions is focused on associations between appraisals and work outcomes.
-Both the job demands--resources model (Bakker and Demerouti, 2017) as well as the challenge-hindrance stressor framework (Cavanaugh et al., 2000) have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, commitment, and performance (e.g., LePine et al., 2005).
-The current project will focus on three outcomes: engagement, strain, and burnout.
-See Figure \ref{fig:ourmodel} for proposed associations.
-Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker and Demerouti, 2014, 2017), and empirical work suggests that they are associated with positive outcomes.
-Relevant to the current study, for example, Hakanen et al.
-(2008) found job resources influenced future work engagement.
+Both the job demands--resources model (Bakker and Demerouti, 2017) as well as the challenge--hindrance stressor framework (Cavanaugh et al., 2000) have been useful in the prediction of a wide variety of organizational outcomes including job satisfaction, motivation, commitment, and performance (e.g., LePine et al., 2005).
+Empirical work generally suggests that \emph{resources} are commonly associated with positive outcomes, including, most relevant for the current investigation, employee engagement.
+For example, Hakanen et al.
+(2008) found that job resources influenced future work engagement.
 Moreover, in a sample of teachers and dentists, Bakker et al.
 (2007) found that resources were most predictive of engagement when job demands were especially high.
-Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement (e.g., Schaufeli, 2017).
+Meta analyses have also concluded that there is a positive association with a variety of resource elements and engagement (e.g., Schaufeli, 2017).
 
@@
 \includegraphics{Submission_files/figure-latex/ourmodel-1.pdf}
-\caption{\label{fig:ourmodel}Focal constructs and associations of interest}
+\caption{\label{fig:ourmodel}Focal constructs and predicted associations}
 \end{figure}
 
-The findings regarding demands are more complex, presumably because the way challenge vs.~hindrance appraisals influence coping strategies.
-Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work (Chen et al., 2021), engagement (Crawford et al., 2010), and strain and turnover intentions (e.g., Abbas and Raja, 2019), for example.
-Challenge appraisals have also been negatively associated with job search behaviors (e.g., Cavanaugh et al., 2000).
-\textbf{CLARIFY}
-
-When a demand is appraised as a hindrance, it is negatively associated with motivational resources (Kim and Beehr, 2020), engagement (Crawford et al., 2010), job search behaviors and job satisfaction (Cavanaugh et al., 2000).
+The findings regarding demands are more complex.
+When a demand is appraised as a hindrance, it is negatively associated with motivational resources (Kim and Beehr, 2020), engagement (Crawford et al., 2010), job search behaviors, and job satisfaction (Cavanaugh et al., 2000).
 Chen et al.
-(2021) found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment.
-Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands (Podsakoff et al., 2007).
-Interestingly, both challenges and hindrances have been shown to positively predict strain (Abbas and Raja, 2019; LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010), which further highlights the complex association between appraisals and subsequent outcomes.
-Given the differential relationships described above, we make the following predictions (see Figure \ref{fig:ourmodel}):
+(2021) further found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment.
+Turnover intentions, actual turnover and withdrawal behaviors have also been associated with hindrance demands (Podsakoff et al., 2007).
+Appraising a demand as a \emph{challenge}, however, has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work, Chen et al.
+(2021), engagement, Crawford et al.
+(2010), and strain and turnover intentions, e.g., Abbas and Raja (2019)).
+Challenge appraisals have also been found to ehave negative associations with job search behaviors (e.g., Cavanaugh et al., 2000).
+Interestingly, both challenges and hindrances have been shown to positively predict strain (Abbas and Raja, 2019; LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010), which further highlights the complex association between characteristic appraisals and important work outcomes.
+Given the differential relationships described above, and a focus on three outcomes (engagement, strain, and burnout) we make the following predictions (see Figure \ref{fig:ourmodel}):
 

### 2025-07-22 Submission.Rmd
coffee shop edits

@@
   Discussions of job characteristics often include a tacit characterization that these job elements are either resources or demands.
-The current study documents variability in ratings of O\*Net specifications with respect to subjective interpretation of job characteristics and predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes.
+The current study documents variability in ratings of O\*NET specifications with respect to subjective interpretation of job characteristics and predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes.
 We additionally explore the potential moderating role of resources on these relationships.
@@
 
-keywords         : "O*Net, challenge-hindrance framework, job demands-resources, job characteristics"
+keywords         : "O*NET, challenge-hindrance framework, job demands-resources, job characteristics"
 wordcount        : "4,942"
@@
 Our primary aims explore: 1) variability in subjective ratings of job characteristics with respect to perception as resource and/or demand, 2) differential association (of subjective appraisals) with positive and negative outcomes, and 3) the buffering effect of resources on the relationships between demands and negative work outcomes^[Took out previous #2 -- make sure this isn't revisited in Results or Discussion].
-We investigate these associations via the lens of [O\*Net job specifications](https://www.onetcenter.org/content.html), which provide a near--exhaustive listing of generalizable characteristic specifications.
+We investigate these associations via the lens of [O\*NET job specifications](https://www.onetcenter.org/content.html), which provide a near--exhaustive listing of generalizable characteristic specifications.
 
@@
 
-### ACTUALLY, just commented out the graph because other code chunks needed for subsequent commands - 1/17/23 , fig.cap="Average and standard deviation of O*Net characteristics retained as indicators of Autonomy, Cohesion, Control, Participation, and Supervisor Support."
+### ACTUALLY, just commented out the graph because other code chunks needed for subsequent commands - 1/17/23 , fig.cap="Average and standard deviation of O*NET characteristics retained as indicators of Autonomy, Cohesion, Control, Participation, and Supervisor Support."
 
@@
 
+We sampled from a Prolific panel with eligibility requirements being 18 years of age (or older) and holding either a full-- or part--time job.
 The Montclair State University Institutional Review Board approved the project and respondents provided consent after reviewing a project description but before starting the survey.
-Written consent was obtained via The final screened sample consisted of `r nrow(data)`.
+To account for multiple--job holders, participants were asked to think about their primary job while responding.
 Regarding tenure, `r round(a[1,3],2)`% had been in their referent job less than 6 months, `r round(a[2,3],1)`% between 6 months and a year, `r round(a[3,3],2)`% between one and five years, `r round(a[4,3],2)`% between 5 and 10 years, and `r round(a[5,3],2)`% more than 10 years.
@@
 
-Characteristics, Challenge Demands, Hindrance Demands, and Resources.
-The Occupational Information Network (O\*Net) serves as a repository of information broadly descriptive of occupations [@peterson2001understanding].
-The O\*Net database consists of hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are frequently updated.
-We focused on 98 work [activity and context statements](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*Net groups into *activity* categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
+>NOTE. grab O\*NET description from desktop (this paragraph only)
+
+### Characteristics, Challenge Demands, Hindrance Demands, and Resources
+
+The Occupational Information Network (O\*NET) serves as a repository of information broadly descriptive of occupations [@peterson2001understanding].
+The O\*NET database consists of hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are frequently updated.
+We focused on 98 work [activity and context statements](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*NET groups into *activity* categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
 Work *context* statements are grouped into interpersonal relationships (e.g., the context of the job in terms of human interaction processes), physical work conditions (e.g., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (e.g., the relationships or interactions between the worker and the structural characteristics of the job).
 
-O\*Net collects information about these categories by periodically asking workers job characteristic questions, which often have [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).
+O\*NET collects information about these elements by periodically surveying workers with job characteristic questions, which often have [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).
 For example, "How responsible is the worker for work outcomes and results of other workers?" has response options ranging from *no responsibility* to *very high responsibility*, while the question, "How often do you use electronic mail in this job?" has options ranging from *never* to *every day*.
-We retained O\*Net’s response scales while asking for statement relevance, all of which shared the same 5-point scale regardless of semantic label difference.
-Other than minor grammatical editing (for example, changing “the worker” to “you”), we also retained the O\*Net wording for our item stems.
-The total number of items on each administered survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).
-
-Participants were asked to think about whether or not their job could be described as consisting of 98 different O\*Net job characteristics.
-For example, if a respondent indicated that any one characteristic was not applicable for their job (e.g., answered *never* or *not at all*), they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
-Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).
-
-Stress.
+We retained O\*NET’s response scales while asking for statement relevance, all of which shared the same number of response option categories (5) regardless of semantic label difference.
+We also retained original O\*NET wording for our item stems, with minor grammatical exceptions^[For example, the worker responsibility question was changed from "How responsible is the worker..." to "How responsible are you..."].
+The total number of items on each administered survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for evaluations for 14 O\*NET characteristics that we surmised to have extremely low frequency of affirmative endorsement across respondents (one such excluded characteristic, for example, was "...the extent to which the worker is exposed to radiation on the job").
+
+Participants were first asked to think about whether or not their job could be described as consisting of these job characteristics.
+If a respondent indicated that any one characteristic was not applicable for their job (e.g., answered *never* or *not at all*), they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment).
+All questions were administered in randomized order within blocks of characteristic, resource, challenge, and hindrance.
+
+### Stress
+
 Stress was captured via three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019).
@@
 A sample item is, “How often have you had problems relaxing because of your job?”.
-Obtained alpha was .85 in this sample.
-
-Burnout.
+Coefficient alpha [@cronbach1951coefficient] was 0.85 in this sample.
+
+### Burnout
+
 Four items from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019) were used to assess burnout.
@@
 A sample item is, “How often have you felt worn out?”.
-Alpha was 0.85 in this sample.
-
-Engagement. The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample 𝛼’s of
-0.68 (absorption) and 0.80 (vigor), and 0.90 (dedication).
+Within our sample, coefficient alpha was 0.85.
+
+### Engagement
+
+The 18-item engagement measure was recently developed by Russell et al.
+(2022).
 Responses were provided using a Likert-type scale ranging from (1) Strongly Disagree to (6) Strongly Agree.
 A sample item is, “I enjoy thinking about work even when I'm not at work”.
-For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).
+For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, $\alpha$ = 0.91).
 
@@
 
-Data were collected through Prolific, an online data collection platform.
-An email was sent to eligible members of the Prolific respondent pool, notifying them of their opportunity to participate.
-Eligibility requirements included being 18 or older and holding either a full-time or part-time job.
-Eligible individuals then voluntarily chose whether or not to respond to the invitation after reading an informed consent.
-
-Respondents were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of 98 different O\*Net job characteristics in randomized order.
+Respondents were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of the different O\*NET job characteristics.
 Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).
-See Figure \@ref(fig:onetviz) for a visual representation of the process experienced by respondents.
+See Figure \@ref(fig:onetviz) for a visual representation of the survey experience.
 
@@
 
-H1 posits that static job characteristics are not necessarily always experienced similarly across workers - as hindrances, challenges, or resources.
+>NOTE.
+Get rid of Fig 3 - present the histograms as indicating that "not everyone agrees that a characterisitic is a...
+(challenge, hindrance, resource)", then highlight items with greatest discrepancy to provide flavor to the histograms (flip the current $\P$ ordering)
+
+H1 posits that the same job characteristic is not necessarily experienced similarly across workers - as hindrance, challenge, or resource.
 We explore this hypothesis first at the job characteristic level before presenting a broader perspective.
-Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present only extreme snapshots of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative most and least consistency.
-Figure \@ref(fig:combinegraphs) presents the resources, challenges, and hindrances that are *most consistently agreed on* as indexed by (relatively) low standard deviations, while Figure \@ref(fig:combinegraphs2) presents the characteristics with the greatest amount of *disagreement* across workers.
+Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present only extreme snapshots of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] Figure \@ref(fig:combinegraphs) presents the resources, challenges, and hindrances that are *most consistently agreed on* as indexed by lowest empirical standard deviations, while Figure \@ref(fig:combinegraphs2) presents the characteristics with the greatest amount of *disagreement* across workers.
 The figures demonstrate that what is perceived as resource and challenge tends to be somewhat agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
-However, there is considerably less relative agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`).
+However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`).
 
@@
 
-In addition to highlighting extremely agreed- or disagreed-upon characteristics, Figure \@ref(fig:overallhist) presents our standard deviation indices across all rated items.
+In addition to highlighting extremely agreed-- or disagreed--upon characteristics, Figure \@ref(fig:overallhist) presents our standard deviation indices across all rated items.
 Here, discrepancies receive greater context, with the *spread* of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively *bunched* levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
@@
 
-The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand.
-Table 1 provides the correlations among the O\*Net "scale"-level groupings across ratings of resource, challenge, and hindrance (i.e., Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)).
-We would expect to see minimal correlations if job characteristics *were* uniquely categorized.
-First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16).
+The second hypothesis, similarly oriented to H1, stated that job characteristics would not be *uniquely* categorized as a resource or demand.
+Table 1 provides the correlations among the O\*NET "scale"--level groupings^[Survey items are grouped by O\*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc).
+These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.] across evaluations as resource, challenge, and hindrance.
+Here would expect trivial correlations if job characteristics *were* uniquely categorized.
+First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, coefficient magnitude ranges from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16).
 Hindrance categories, however, had less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, *M* = .62, *SD* = .17.
-When people perceived hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.
+When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.
 
@@
 Challenge and hindrance demands demonstrated smaller relationships, but mostly negative.
-Challenges and resources within the same O\*Net dimensions are strongly and positively related.
+Challenges and resources within the same O\*NET dimensions are strongly and positively related.
 These results provide support for H2, suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is perceived as a *resource* being also perceived as a *challenge*.
-Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.
+Stated differently, job characteristics should not be uniquely categorized as resource or demand.
 
@@
                   align = c("m{2.6cm}", rep("m{.7cm}",21)),
-                  note = "$*$ p < .05, $**$ p < .01; The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)")
+                  note = "$*$ p < .05, $**$ p < .01; The seven O*NET grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)")
 trial <- data_new[c(405:411, 413:419, 421:427)]
@@
 In addition to the above findings, this paper made several additional important contributions.
-We utilized a diverse sample of employees across industries who responded to common O\*Net items.
-While O\*Net provides detailed information about frequency and importance ratings among employees, we begin the process of expanding what we know of job characteristics to ratings of an extensive range of demands and resources.
-Further, we provide a repository for other researchers with listing of O\*Net demands and resources across activity and context items for the benefit of all future researchers.
+We utilized a diverse sample of employees across industries who responded to common O\*NET items.
+While O\*NET provides detailed information about frequency and importance ratings among employees, we begin the process of expanding what we know of job characteristics to ratings of an extensive range of demands and resources.
+Further, we provide a repository for other researchers with listing of O\*NET demands and resources across activity and context items for the benefit of all future researchers.
 We also explored not only context and activity holistically, but at a higher level aggregation, which enhances our knowledge of how employees perceive different categories of resources, challenges, and hindrances within different work dimensions, as well as the relationships among them.
@@
 As with all individual studies, this project was limited in scope, and as such, there are a number of avenues for future study worth exploring.
-First, although we aggregated to O\*Net groupings, we were also dealing with single-item measures for much our operationalization.
-Although not ideal psychometrically, this provided a strong linkage to the established O\*Net framework.
-Related to that, we intentionally worked within the O\*Net database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources and demands.
-Therefore, to the extent that O\*Net is not an exhaustive repository, there are existing characteristics that we did not capture.
-For example, O\*Net also includes styles and values, which we did not sample.
+First, although we aggregated to O\*NET groupings, we were also dealing with single-item measures for much our operationalization.
+Although not ideal psychometrically, this provided a strong linkage to the established O\*NET framework.
+Related to that, we intentionally worked within the O\*NET database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources and demands.
+Therefore, to the extent that O\*NET is not an exhaustive repository, there are existing characteristics that we did not capture.
+For example, O\*NET also includes styles and values, which we did not sample.
 Future studies may want to expand to explore these additional aspects of work.

### 2025-07-22 Submission.tex
coffee shop edits

@@
 {}{\PatchFailed}
-\keywords{O*Net, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: 4,942}
+\keywords{O*NET, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: 4,942}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
   pdflang={en-EN},
-  pdfkeywords={O*Net, challenge-hindrance framework, job demands-resources, job characteristics},
+  pdfkeywords={O*NET, challenge-hindrance framework, job demands-resources, job characteristics},
   hidelinks,
@@
 Discussions of job characteristics often include a tacit characterization that these job elements are either resources or demands.
-The current study documents variability in ratings of O*Net specifications with respect to subjective interpretation of job characteristics and predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes.
+The current study documents variability in ratings of O*NET specifications with respect to subjective interpretation of job characteristics and predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes.
 We additionally explore the potential moderating role of resources on these relationships.
@@
 Our primary aims explore: 1) variability in subjective ratings of job characteristics with respect to perception as resource and/or demand, 2) differential association (of subjective appraisals) with positive and negative outcomes, and 3) the buffering effect of resources on the relationships between demands and negative work outcomes\footnote{Took out previous \#2 -- make sure this isn't revisited in Results or Discussion}.
-We investigate these associations via the lens of \href{https://www.onetcenter.org/content.html}{O*Net job specifications}, which provide a near--exhaustive listing of generalizable characteristic specifications.
+We investigate these associations via the lens of \href{https://www.onetcenter.org/content.html}{O*NET job specifications}, which provide a near--exhaustive listing of generalizable characteristic specifications.
 
@@
 
+We sampled from a Prolific panel with eligibility requirements being 18 years of age (or older) and holding either a full-- or part--time job.
 The Montclair State University Institutional Review Board approved the project and respondents provided consent after reviewing a project description but before starting the survey.
-Written consent was obtained via The final screened sample consisted of 568.
+To account for multiple--job holders, participants were asked to think about their primary job while responding.
 Regarding tenure, 13.57\% had been in their referent job less than 6 months, 19.20\% between 6 months and a year, 49.12\% between one and five years, 13.27\% between 5 and 10 years, and 4.87\% more than 10 years.
@@
 
-Characteristics, Challenge Demands, Hindrance Demands, and Resources.
-The Occupational Information Network (O*Net) serves as a repository of information broadly descriptive of occupations (Peterson et al., 2001).
-The O*Net database consists of hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are frequently updated.
-We focused on 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context statements} which O*Net groups into \emph{activity} categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
+\begin{quote}
+NOTE. grab O*NET description from desktop (this paragraph only)
+\end{quote}
+
+\hypertarget{characteristics-challenge-demands-hindrance-demands-and-resources}{%
+\subsubsection{Characteristics, Challenge Demands, Hindrance Demands, and Resources}\label{characteristics-challenge-demands-hindrance-demands-and-resources}}
+
+The Occupational Information Network (O*NET) serves as a repository of information broadly descriptive of occupations (Peterson et al., 2001).
+The O*NET database consists of hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are frequently updated.
+We focused on 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context statements} which O*NET groups into \emph{activity} categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
 Work \emph{context} statements are grouped into interpersonal relationships (e.g., the context of the job in terms of human interaction processes), physical work conditions (e.g., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (e.g., the relationships or interactions between the worker and the structural characteristics of the job).
 
-O*Net collects information about these categories by periodically asking workers job characteristic questions, which often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}.
+O*NET collects information about these elements by periodically surveying workers with job characteristic questions, which often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}.
 For example, ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{no responsibility} to \emph{very high responsibility}, while the question, ``How often do you use electronic mail in this job?'' has options ranging from \emph{never} to \emph{every day}.
-We retained O*Net's response scales while asking for statement relevance, all of which shared the same 5-point scale regardless of semantic label difference.
-Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we also retained the O*Net wording for our item stems.
-The total number of items on each administered survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).
+We retained O*NET's response scales while asking for statement relevance, all of which shared the same number of response option categories (5) regardless of semantic label difference.
+We also retained original O*NET wording for our item stems, with minor grammatical exceptions\footnote{For example, the worker responsibility question was changed from ``How responsible is the worker\ldots{}'' to ``How responsible are you\ldots{}''}.
+The total number of items on each administered survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for evaluations for 14 O*NET characteristics that we surmised to have extremely low frequency of affirmative endorsement across respondents (one such excluded characteristic, for example, was ``\ldots the extent to which the worker is exposed to radiation on the job'').
 
-Participants were asked to think about whether or not their job could be described as consisting of 98 different O*Net job characteristics.
-For example, if a respondent indicated that any one characteristic was not applicable for their job (e.g., answered \emph{never} or \emph{not at all}), they were not subsequently asked to rate the level of resource (\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order.
-Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).
+Participants were first asked to think about whether or not their job could be described as consisting of these job characteristics.
+If a respondent indicated that any one characteristic was not applicable for their job (e.g., answered \emph{never} or \emph{not at all}), they were not subsequently asked to rate the level of resource (\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment).
+All questions were administered in randomized order within blocks of characteristic, resource, challenge, and hindrance.
 
-Stress.
+\hypertarget{stress}{%
+\subsubsection{Stress}\label{stress}}
+
 Stress was captured via three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019).
@@
 A sample item is, ``How often have you had problems relaxing because of your job?''.
-Obtained alpha was .85 in this sample.
+Coefficient alpha (Cronbach, 1951) was 0.85 in this sample.
 
-Burnout.
+\hypertarget{burnout}{%
+\subsubsection{Burnout}\label{burnout}}
+
 Four items from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019) were used to assess burnout.
@@
 A sample item is, ``How often have you felt worn out?''.
-Alpha was 0.85 in this sample.
+Within our sample, coefficient alpha was 0.85.
 
-Engagement. The 18-item engagement measure was recently developed (Russell et al., 2022), with the authors specifying three subscales which yielded current sample 𝛼's of
-0.68 (absorption) and 0.80 (vigor), and 0.90 (dedication).
+\hypertarget{engagement}{%
+\subsubsection{Engagement}\label{engagement}}
+
+The 18-item engagement measure was recently developed by Russell et al.~(2022).
 Responses were provided using a Likert-type scale ranging from (1) Strongly Disagree to (6) Strongly Agree.
 A sample item is, ``I enjoy thinking about work even when I'm not at work''.
-For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, α = 0.91).
+For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, \(\alpha\) = 0.91).
 
@@
 
-Data were collected through Prolific, an online data collection platform.
-An email was sent to eligible members of the Prolific respondent pool, notifying them of their opportunity to participate.
-Eligibility requirements included being 18 or older and holding either a full-time or part-time job.
-Eligible individuals then voluntarily chose whether or not to respond to the invitation after reading an informed consent.
-
-Respondents were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of 98 different O*Net job characteristics in randomized order.
+Respondents were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of the different O*NET job characteristics.
 Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).
-See Figure \ref{fig:onetviz} for a visual representation of the process experienced by respondents.
+See Figure \ref{fig:onetviz} for a visual representation of the survey experience.
 
@@
 
-H1 posits that static job characteristics are not necessarily always experienced similarly across workers - as hindrances, challenges, or resources.
+\begin{quote}
+NOTE.
+Get rid of Fig 3 - present the histograms as indicating that ``not everyone agrees that a characterisitic is a\ldots{} (challenge, hindrance, resource)'', then highlight items with greatest discrepancy to provide flavor to the histograms (flip the current \(\P\) ordering)
+\end{quote}
+
+H1 posits that the same job characteristic is not necessarily experienced similarly across workers - as hindrance, challenge, or resource.
 We explore this hypothesis first at the job characteristic level before presenting a broader perspective.
 Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present only extreme snapshots of characteristic variability in the form of the 8-most \emph{consistently rated} and \emph{inconsistently rated} resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
-The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} These figures present average item ratings, but the central elements of interest are the standard deviations, which reflect the characteristics with the relative most and least consistency.
-Figure \ref{fig:combinegraphs} presents the resources, challenges, and hindrances that are \emph{most consistently agreed on} as indexed by (relatively) low standard deviations, while Figure \ref{fig:combinegraphs2} presents the characteristics with the greatest amount of \emph{disagreement} across workers.
+The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} Figure \ref{fig:combinegraphs} presents the resources, challenges, and hindrances that are \emph{most consistently agreed on} as indexed by lowest empirical standard deviations, while Figure \ref{fig:combinegraphs2} presents the characteristics with the greatest amount of \emph{disagreement} across workers.
 The figures demonstrate that what is perceived as resource and challenge tends to be somewhat agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
-However, there is considerably less relative agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16).
+However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16).
 
-In addition to highlighting extremely agreed- or disagreed-upon characteristics, Figure \ref{fig:overallhist} presents our standard deviation indices across all rated items.
+In addition to highlighting extremely agreed-- or disagreed--upon characteristics, Figure \ref{fig:overallhist} presents our standard deviation indices across all rated items.
 Here, discrepancies receive greater context, with the \emph{spread} of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively \emph{bunched} levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
@@
 
-The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand.
-Table 1 provides the correlations among the O*Net ``scale''-level groupings across ratings of resource, challenge, and hindrance (i.e., Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)).
-We would expect to see minimal correlations if job characteristics \emph{were} uniquely categorized.
-First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (\emph{SD} = .13, range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, \emph{M} = .43, \emph{SD} =.16).
+The second hypothesis, similarly oriented to H1, stated that job characteristics would not be \emph{uniquely} categorized as a resource or demand.
+Table 1 provides the correlations among the O*NET ``scale''--level groupings\footnote{Survey items are grouped by O*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc).
+These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.} across evaluations as resource, challenge, and hindrance.
+Here would expect trivial correlations if job characteristics \emph{were} uniquely categorized.
+First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (\emph{SD} = .13, coefficient magnitude ranges from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, \emph{M} = .43, \emph{SD} =.16).
 Hindrance categories, however, had less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, \emph{M} = .62, \emph{SD} = .17.
-When people perceived hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.
+When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.
 
@@
 Challenge and hindrance demands demonstrated smaller relationships, but mostly negative.
-Challenges and resources within the same O*Net dimensions are strongly and positively related.
+Challenges and resources within the same O*NET dimensions are strongly and positively related.
 These results provide support for H2, suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is perceived as a \emph{resource} being also perceived as a \emph{challenge}.
-Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.
+Stated differently, job characteristics should not be uniquely categorized as resource or demand.
 
@@
 \begin{TableNotes}[para]
-\normalsize{\textit{Note.} $*$ p < .05, $**$ p < .01; The seven O*Net grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)}
+\normalsize{\textit{Note.} $*$ p < .05, $**$ p < .01; The seven O*NET grouping categories represented here are: Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc)}
 \end{TableNotes}
@@
 In addition to the above findings, this paper made several additional important contributions.
-We utilized a diverse sample of employees across industries who responded to common O*Net items.
-While O*Net provides detailed information about frequency and importance ratings among employees, we begin the process of expanding what we know of job characteristics to ratings of an extensive range of demands and resources.
-Further, we provide a repository for other researchers with listing of O*Net demands and resources across activity and context items for the benefit of all future researchers.
+We utilized a diverse sample of employees across industries who responded to common O*NET items.
+While O*NET provides detailed information about frequency and importance ratings among employees, we begin the process of expanding what we know of job characteristics to ratings of an extensive range of demands and resources.
+Further, we provide a repository for other researchers with listing of O*NET demands and resources across activity and context items for the benefit of all future researchers.
 We also explored not only context and activity holistically, but at a higher level aggregation, which enhances our knowledge of how employees perceive different categories of resources, challenges, and hindrances within different work dimensions, as well as the relationships among them.
@@
 As with all individual studies, this project was limited in scope, and as such, there are a number of avenues for future study worth exploring.
-First, although we aggregated to O*Net groupings, we were also dealing with single-item measures for much our operationalization.
-Although not ideal psychometrically, this provided a strong linkage to the established O*Net framework.
-Related to that, we intentionally worked within the O*Net database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources and demands.
-Therefore, to the extent that O*Net is not an exhaustive repository, there are existing characteristics that we did not capture.
-For example, O*Net also includes styles and values, which we did not sample.
+First, although we aggregated to O*NET groupings, we were also dealing with single-item measures for much our operationalization.
+Although not ideal psychometrically, this provided a strong linkage to the established O*NET framework.
+Related to that, we intentionally worked within the O*NET database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources and demands.
+Therefore, to the extent that O*NET is not an exhaustive repository, there are existing characteristics that we did not capture.
+For example, O*NET also includes styles and values, which we did not sample.
 Future studies may want to expand to explore these additional aspects of work.
@@
 American Psychological Association: 834.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cronbach1951coefficient}{}}%
+Cronbach LJ (1951) Coefficient alpha and the internal structure of tests. \emph{psychometrika} 16(3). Springer-Verlag: 297--334.
 

### 2025-08-21 Submission.Rmd
avoiding conflict - stashing desktop and accepting these laptop revisions

@@
 If a respondent indicated that any one characteristic was not applicable for their job (e.g., answered *never* or *not at all*), they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment).
+These ratings were made along a 5--point Likert--type agreement scale with values of (1) Strongly Disagree, (2) Disagree, (3) Neither Agree nor Disagree, (4) Agree, and (5) Strongly Agree.
 All questions were administered in randomized order within blocks of characteristic, resource, challenge, and hindrance.
@@
 
-```{r overallhist, fig.cap="Frequency distribution of standard deviations across characteristics deemed resources, challenges, and demands."}
+```{r overallhist, fig.cap="Frequency distributions of standard deviations across characteristics rated as resources, challenges, and demands."}
 
@@
 
-H1 posits that the same job characteristic is not necessarily experienced similarly across workers - as hindrance, challenge, or resource.
-We explore this hypothesis first at the job characteristic level before presenting a broader perspective.
-Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present only extreme snapshots of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] Figure \@ref(fig:combinegraphs) presents the resources, challenges, and hindrances that are *most consistently agreed on* as indexed by lowest empirical standard deviations, while Figure \@ref(fig:combinegraphs2) presents the characteristics with the greatest amount of *disagreement* across workers.
-The figures demonstrate that what is perceived as resource and challenge tends to be somewhat agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
+H1 posits that *not everyone agrees* that a characterisitic is a hindrance, challenge, or resource.
+Figure \@ref(fig:overallhist) presents standard deviations of characteristic rating across all rated items.
+Here,the *spread* of difference exhibits wider distributions of (dis)agreement for challenge and resource ratings (and a relatively more leptokurtic distribution of (dis)agreement for hindrances).
+The distributions demonstrate that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
+This points to *hindrances*, in particular, as being likely amenable to future probing regarding moderating conditions.
+A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* < .01).
+
+Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present the most extreme examples of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] Figure \@ref(fig:combinegraphs) presents the *most consistently agreed on* resources, hindrances, and challenges as indexed by lowest empirical standard deviations, while Figure \@ref(fig:combinegraphs2) presents the characteristics with the greatest amount of *disagreement* across workers.
+The figures again highlight that what is perceived as resource and challenge tends to be relatively agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
 However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`).
+In sum, these results provide some collective support for H1, and  particularly so for hindrances, which are differently experienced across our raters.
 
@@
 
-In addition to highlighting extremely agreed-- or disagreed--upon characteristics, Figure \@ref(fig:overallhist) presents our standard deviation indices across all rated items.
-Here, discrepancies receive greater context, with the *spread* of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively *bunched* levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
-Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
-This points to *hindrances*, in particular, as being likely amenable to future probing regarding moderating conditions.
-A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* < .01).
-In sum, these results provide some collective support for H1, and  particularly so for hindrances, which are differently experienced across our raters.
-
 The second hypothesis, similarly oriented to H1, stated that job characteristics would not be *uniquely* categorized as a resource or demand.
+We explore this via pattern of correlation similar in intent to @campbell1959convergent's multi--trait multi--method matrix.
 Table 1 provides the correlations among the O\*NET "scale"--level groupings^[Survey items are grouped by O\*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc).
@@
 The mean resource to challenge correlations within the same dimension ranged from .62 to .66 (*M* = .64, *SD* = .02; for example, the association between information input ratings as a resource and as a challenge was .62).
-The correlations between resources and challenges *across* dimensions (for example, the correlation between mental processes and work output was .42 and .39) ranged from .08 to .50, *M* = .32, *SD* = .12.
+The correlations between resources and challenges *across* dimensions (for example, the correlation between mental processes [resource] and work output [challenge] was .39) ranged from .08 to .50, *M* = .32, *SD* = .12.
 The resource-hindrance correlations within the same dimension ranged from -.16 to -.30 (*M* = -.24, *SD* = .05), while the correlations between resources and hindrances *across* dimensions ranged from .05 to -.27, *M* = -.14, *SD* = .08.

### 2025-08-21 Submission.tex
avoiding conflict - stashing desktop and accepting these laptop revisions

@@
 If a respondent indicated that any one characteristic was not applicable for their job (e.g., answered \emph{never} or \emph{not at all}), they were not subsequently asked to rate the level of resource (\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment).
+These ratings were made along a 5--point Likert--type agreement scale with values of (1) Strongly Disagree, (2) Disagree, (3) Neither Agree nor Disagree, (4) Agree, and (5) Strongly Agree.
 All questions were administered in randomized order within blocks of characteristic, resource, challenge, and hindrance.
@@
 \includegraphics{Submission_files/figure-latex/overallhist-1.pdf}
-\caption{\label{fig:overallhist}Frequency distribution of standard deviations across characteristics deemed resources, challenges, and demands.}
+\caption{\label{fig:overallhist}Frequency distributions of standard deviations across characteristics rated as resources, challenges, and demands.}
 \end{figure}
@@
 
-H1 posits that the same job characteristic is not necessarily experienced similarly across workers - as hindrance, challenge, or resource.
-We explore this hypothesis first at the job characteristic level before presenting a broader perspective.
-Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present only extreme snapshots of characteristic variability in the form of the 8-most \emph{consistently rated} and \emph{inconsistently rated} resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
-The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} Figure \ref{fig:combinegraphs} presents the resources, challenges, and hindrances that are \emph{most consistently agreed on} as indexed by lowest empirical standard deviations, while Figure \ref{fig:combinegraphs2} presents the characteristics with the greatest amount of \emph{disagreement} across workers.
-The figures demonstrate that what is perceived as resource and challenge tends to be somewhat agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
-However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16).
-
-In addition to highlighting extremely agreed-- or disagreed--upon characteristics, Figure \ref{fig:overallhist} presents our standard deviation indices across all rated items.
-Here, discrepancies receive greater context, with the \emph{spread} of difference exhibiting wider distributions of agreement for challenge and resource ratings (and relatively \emph{bunched} levels of disagreement for hindrances; note the spread of the challenge and resource histograms relative to the hindrance histogram).
-Some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
+H1 posits that \emph{not everyone agrees} that a characterisitic is a hindrance, challenge, or resource.
+Figure \ref{fig:overallhist} presents standard deviations of characteristic rating across all rated items.
+Here,the \emph{spread} of difference exhibits wider distributions of (dis)agreement for challenge and resource ratings (and a relatively more leptokurtic distribution of (dis)agreement for hindrances).
+The distributions demonstrate that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
 This points to \emph{hindrances}, in particular, as being likely amenable to future probing regarding moderating conditions.
 A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} \textless{} .01).
+
+Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the 8-most \emph{consistently rated} and \emph{inconsistently rated} resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
+The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} Figure \ref{fig:combinegraphs} presents the \emph{most consistently agreed on} resources, hindrances, and challenges as indexed by lowest empirical standard deviations, while Figure \ref{fig:combinegraphs2} presents the characteristics with the greatest amount of \emph{disagreement} across workers.
+The figures again highlight that what is perceived as resource and challenge tends to be relatively agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
+However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16).
 In sum, these results provide some collective support for H1, and particularly so for hindrances, which are differently experienced across our raters.
@@
 The second hypothesis, similarly oriented to H1, stated that job characteristics would not be \emph{uniquely} categorized as a resource or demand.
+We explore this via pattern of correlation similar to Campbell and Fiske (1959)'s multi--trait multi--method matrix.
 Table 1 provides the correlations among the O*NET ``scale''--level groupings\footnote{Survey items are grouped by O*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc).
@@
 The mean resource to challenge correlations within the same dimension ranged from .62 to .66 (\emph{M} = .64, \emph{SD} = .02; for example, the association between information input ratings as a resource and as a challenge was .62).
-The correlations between resources and challenges \emph{across} dimensions (for example, the correlation between mental processes and work output was .42 and .39) ranged from .08 to .50, \emph{M} = .32, \emph{SD} = .12.
+The correlations between resources and challenges \emph{across} dimensions (for example, the correlation between mental processes {[}resource{]} and work output {[}challenge{]} was .39) ranged from .08 to .50, \emph{M} = .32, \emph{SD} = .12.
 The resource-hindrance correlations within the same dimension ranged from -.16 to -.30 (\emph{M} = -.24, \emph{SD} = .05), while the correlations between resources and hindrances \emph{across} dimensions ranged from .05 to -.27, \emph{M} = -.14, \emph{SD} = .08.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-campbell1959convergent}{}}%
+Campbell DT and Fiske DW (1959) Convergent and discriminant validation by the multitrait-multimethod matrix. \emph{Psychological bulletin} 56(2). American Psychological Association: 81--105.
+
 \leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%

### 2025-09-06 Submission.Rmd
testing Alicia's computer

@@
 
->Hypothesis 1: Job characteristics vary regarding subjective worker perception as challenge, hindrance, or resource
-
->Hypothesis 2: Job characteristics are not exclusively categorized as a resource or demand, but rather, some job characteristics are viewed as both resourceful and demanding
+>**Hypothesis 1**: Job characteristics vary regarding subjective worker perception as challenge, hindrance, or resource
+
+>**Hypothesis 2**: Job characteristics are not exclusively categorized as a resource or demand, but rather, some job characteristics are viewed as both resourceful and demanding
 
@@
 
->Hypothesis 3a: Resources and challenges positively predict engagement.
-
->Hypothesis 3b: Both challenge and hindrance demands positively predict stress and burnout.
+>**Hypothesis 3a**: Resources and challenges positively predict engagement.
+
+>**Hypothesis 3b**: Both challenge and hindrance demands positively predict stress and burnout.
 
@@
 
->Hypothesis 4a:Resources moderate the relationship between challenge demands and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
-
->Hypothesis 4b:Resources moderate the relationship between hindrance demands and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
+>**Hypothesis 4a**: Resources moderate the relationship between challenge demands and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
+
+>**Hypothesis 4b**: Resources moderate the relationship between hindrance demands and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
 

### 2025-09-06 Submission.tex
testing Alicia's computer

@@
 \begin{quote}
-Hypothesis 1: Job characteristics vary regarding subjective worker perception as challenge, hindrance, or resource
+\textbf{Hypothesis 1}: Job characteristics vary regarding subjective worker perception as challenge, hindrance, or resource
 \end{quote}
@@
 \begin{quote}
-Hypothesis 2: Job characteristics are not exclusively categorized as a resource or demand, but rather, some job characteristics are viewed as both resourceful and demanding
+\textbf{Hypothesis 2}: Job characteristics are not exclusively categorized as a resource or demand, but rather, some job characteristics are viewed as both resourceful and demanding
 \end{quote}
@@
 \begin{quote}
-Hypothesis 3a: Resources and challenges positively predict engagement.
+\textbf{Hypothesis 3a}: Resources and challenges positively predict engagement.
 \end{quote}
@@
 \begin{quote}
-Hypothesis 3b: Both challenge and hindrance demands positively predict stress and burnout.
+\textbf{Hypothesis 3b}: Both challenge and hindrance demands positively predict stress and burnout.
 \end{quote}
@@
 \begin{quote}
-Hypothesis 4a:Resources moderate the relationship between challenge demands and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
+\textbf{Hypothesis 4a}: Resources moderate the relationship between challenge demands and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
 \end{quote}
@@
 \begin{quote}
-Hypothesis 4b:Resources moderate the relationship between hindrance demands and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
+\textbf{Hypothesis 4b}: Resources moderate the relationship between hindrance demands and the outcomes of strain and burnout such that these relationships become weaker as workers perceive more resources.
 \end{quote}
@@
 The second hypothesis, similarly oriented to H1, stated that job characteristics would not be \emph{uniquely} categorized as a resource or demand.
-We explore this via pattern of correlation similar to Campbell and Fiske (1959)'s multi--trait multi--method matrix.
+We explore this via pattern of correlation similar in intent to Campbell and Fiske (1959)'s multi--trait multi--method matrix.
 Table 1 provides the correlations among the O*NET ``scale''--level groupings\footnote{Survey items are grouped by O*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc).

### 2025-09-09 Submission.Rmd
checking for conflicts

--- 2025-08-21 Submission.Rmd
@@
 
->NOTE. grab O\*NET description from desktop (this paragraph only)
-
 ### Characteristics, Challenge Demands, Hindrance Demands, and Resources
 
-The Occupational Information Network (O\*NET) serves as a repository of information broadly descriptive of occupations [@peterson2001understanding].
-The O\*NET database consists of hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are frequently updated.
+The Occupational Information Network (O\*NET) serves as a repository of information broadly descriptive of occupations [@peterson2001understanding] and these descriptions are frequently updated.
 We focused on 98 work [activity and context statements](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*NET groups into *activity* categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
@@
 
-O\*NET collects information about these elements by periodically surveying workers with job characteristic questions, which often have [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).
+O\*NET collects information about these elements by periodically surveying workers with job characteristic questions, each of which often has [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).
 For example, "How responsible is the worker for work outcomes and results of other workers?" has response options ranging from *no responsibility* to *very high responsibility*, while the question, "How often do you use electronic mail in this job?" has options ranging from *never* to *every day*.
-We retained O\*NET’s response scales while asking for statement relevance, all of which shared the same number of response option categories (5) regardless of semantic label difference.
-We also retained original O\*NET wording for our item stems, with minor grammatical exceptions^[For example, the worker responsibility question was changed from "How responsible is the worker..." to "How responsible are you..."].
+For the current investigation, O\*NET’s response scales were retained when asking for *statement relevance* (all response scales shared the same *number* of response option categories [5] regardless of semantic labeling).
+We also retained the original O\*NET wording for our item stems, with minor grammatical referent exceptions^[For example, the worker responsibility question was changed from "How responsible is the worker..." to "How responsible are you..."].
 The total number of items on each administered survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for evaluations for 14 O\*NET characteristics that we surmised to have extremely low frequency of affirmative endorsement across respondents (one such excluded characteristic, for example, was "...the extent to which the worker is exposed to radiation on the job").
 
-Participants were first asked to think about whether or not their job could be described as consisting of these job characteristics.
+Participants were first asked to consider whether or not their job could reasonably be described as consisting of each job characteristic.
 If a respondent indicated that any one characteristic was not applicable for their job (e.g., answered *never* or *not at all*), they were not subsequently asked to rate the level of resource (...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment).
-These ratings were made along a 5--point Likert--type agreement scale with values of (1) Strongly Disagree, (2) Disagree, (3) Neither Agree nor Disagree, (4) Agree, and (5) Strongly Agree.
+The challenge, hindrance, and resource ratings were made along a 5--point Likert--type agreement scale with values of (1) Strongly Disagree, (2) Disagree, (3) Neither Agree nor Disagree, (4) Agree, and (5) Strongly Agree.
 All questions were administered in randomized order within blocks of characteristic, resource, challenge, and hindrance.
@@
 
-Stress was captured via three items taken from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019).
+Stress was captured via three items taken from the Copenhagen Psychosocial Questionnaire [@burr2019third].
 Responses were provided using a Likert-type scale ranging from (1) Not at All to (5) All the Time.
@@
 
-Four items from the Copenhagen Psychosocial Questionnaire (Burr et al., 2019) were used to assess burnout.
+Four items from the Copenhagen Psychosocial Questionnaire [@burr2019third] were used to assess burnout.
 Again, responses were provided using a Likert-type scale ranging from (1) Not at All to (5) All the Time.
@@
 
-Respondents were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of the different O\*NET job characteristics.
+Respondents were asked to think only about their *primary* job, and each administered survey branched content dependent on whether or not this job could be described as consisting of the different O\*NET job characteristics.
 Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).
@@
 
->NOTE.
-Get rid of Fig 3 - present the histograms as indicating that "not everyone agrees that a characterisitic is a...
-(challenge, hindrance, resource)", then highlight items with greatest discrepancy to provide flavor to the histograms (flip the current $\P$ ordering)
-
 H1 posits that *not everyone agrees* that a characterisitic is a hindrance, challenge, or resource.
 Figure \@ref(fig:overallhist) presents standard deviations of characteristic rating across all rated items.
-Here,the *spread* of difference exhibits wider distributions of (dis)agreement for challenge and resource ratings (and a relatively more leptokurtic distribution of (dis)agreement for hindrances).
+Here,the *spread* of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic distribution of disagreement for hindrances).
 The distributions demonstrate that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
-This points to *hindrances*, in particular, as being likely amenable to future probing regarding moderating conditions.
 A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* < .01).
-
-Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present the most extreme examples of characteristic variability in the form of the 8-most *consistently rated* and *inconsistently rated* resources, challenges, and demands.[^onlinelist] Figure \@ref(fig:combinegraphs) presents the *most consistently agreed on* resources, hindrances, and challenges as indexed by lowest empirical standard deviations, while Figure \@ref(fig:combinegraphs2) presents the characteristics with the greatest amount of *disagreement* across workers.
-The figures again highlight that what is perceived as resource and challenge tends to be relatively agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
+This points to *hindrances*, in particular, as being most generally amenable to future probing regarding moderating conditions.
+
+To provide context to the Figure \@ref(fig:overallhist) distributions, we present the Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present the most extreme examples of characteristic variability in the form of the 8-most *similarly rated* (Figure \@ref(fig:combinegraphs)) and *dissimilarly rated* resources, challenges, and demands (Figure \@ref(fig:combinegraphs2)).[^onlinelist] These figures again highlight that what is perceived as resource and challenge tends to be relatively agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
 However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`).
-In sum, these results provide some collective support for H1, and  particularly so for hindrances, which are differently experienced across our raters.
+In sum, these results provide support for H1, and  particularly so for hindrances, which are differently experienced across our raters.
 
@@
 These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.] across evaluations as resource, challenge, and hindrance.
-Here would expect trivial correlations if job characteristics *were* uniquely categorized.
+Here one would expect only trivial associations if job characteristics *were* uniquely categorized.
 First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, coefficient magnitude ranges from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16).
-Hindrance categories, however, had less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, *M* = .62, *SD* = .17.
-When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.
+Job hindrances, however, exhibited less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, *M* = .62, *SD* = .17.
+When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater selectivity.
+
+>STOPPED HERE: Too much description
 

### 2025-09-09 Submission.tex
checking for conflicts

--- 2025-08-21 Submission.tex
@@
 {}{\PatchFailed}
+\makeatother
 \keywords{O*NET, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: 4,942}
@@
 
-\hypertarget{theoretical-foundations}{%
-\subsection{Theoretical Foundations}\label{theoretical-foundations}}
+\subsection{Theoretical Foundations}\label{theoretical-foundations}
 
@@
 
-\hypertarget{materials}{%
-\subsection{Materials}\label{materials}}
+\subsection{Materials}\label{materials}
 
-\begin{quote}
-NOTE. grab O*NET description from desktop (this paragraph only)
-\end{quote}
+\subsubsection{Characteristics, Challenge Demands, Hindrance Demands, and Resources}\label{characteristics-challenge-demands-hindrance-demands-and-resources}
 
-\hypertarget{characteristics-challenge-demands-hindrance-demands-and-resources}{%
-\subsubsection{Characteristics, Challenge Demands, Hindrance Demands, and Resources}\label{characteristics-challenge-demands-hindrance-demands-and-resources}}
-
-The Occupational Information Network (O*NET) serves as a repository of information broadly descriptive of occupations (Peterson et al., 2001).
-The O*NET database consists of hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are frequently updated.
+The Occupational Information Network (O*NET) serves as a repository of information broadly descriptive of occupations (Peterson et al., 2001) and these descriptions are frequently updated.
 We focused on 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context statements} which O*NET groups into \emph{activity} categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
@@
 
-O*NET collects information about these elements by periodically surveying workers with job characteristic questions, which often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}.
+O*NET collects information about these elements by periodically surveying workers with job characteristic questions, each of which often has \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}.
 For example, ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{no responsibility} to \emph{very high responsibility}, while the question, ``How often do you use electronic mail in this job?'' has options ranging from \emph{never} to \emph{every day}.
-We retained O*NET's response scales while asking for statement relevance, all of which shared the same number of response option categories (5) regardless of semantic label difference.
-We also retained original O*NET wording for our item stems, with minor grammatical exceptions\footnote{For example, the worker responsibility question was changed from ``How responsible is the worker\ldots{}'' to ``How responsible are you\ldots{}''}.
+For the current investigation, O*NET's response scales were retained when asking for \emph{statement relevance} (all response scales shared the same \emph{number} of response option categories {[}5{]} regardless of semantic labeling).
+We also retained the original O*NET wording for our item stems, with minor grammatical referent exceptions\footnote{For example, the worker responsibility question was changed from ``How responsible is the worker\ldots{}'' to ``How responsible are you\ldots{}''}.
 The total number of items on each administered survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for evaluations for 14 O*NET characteristics that we surmised to have extremely low frequency of affirmative endorsement across respondents (one such excluded characteristic, for example, was ``\ldots the extent to which the worker is exposed to radiation on the job'').
 
-Participants were first asked to think about whether or not their job could be described as consisting of these job characteristics.
+Participants were first asked to consider whether or not their job could reasonably be described as consisting of each job characteristic.
 If a respondent indicated that any one characteristic was not applicable for their job (e.g., answered \emph{never} or \emph{not at all}), they were not subsequently asked to rate the level of resource (\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment).
-These ratings were made along a 5--point Likert--type agreement scale with values of (1) Strongly Disagree, (2) Disagree, (3) Neither Agree nor Disagree, (4) Agree, and (5) Strongly Agree.
+The challenge, hindrance, and resource ratings were made along a 5--point Likert--type agreement scale with values of (1) Strongly Disagree, (2) Disagree, (3) Neither Agree nor Disagree, (4) Agree, and (5) Strongly Agree.
 All questions were administered in randomized order within blocks of characteristic, resource, challenge, and hindrance.
 
-\hypertarget{stress}{%
-\subsubsection{Stress}\label{stress}}
+\subsubsection{Stress}\label{stress}
 
@@
 
-\hypertarget{burnout}{%
-\subsubsection{Burnout}\label{burnout}}
+\subsubsection{Burnout}\label{burnout}
 
@@
 
-\hypertarget{engagement}{%
-\subsubsection{Engagement}\label{engagement}}
+\subsubsection{Engagement}\label{engagement}
 
@@
 
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
+\subsection{Procedure}\label{procedure}
 
-Respondents were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of the different O*NET job characteristics.
+Respondents were asked to think only about their \emph{primary} job, and each administered survey branched content dependent on whether or not this job could be described as consisting of the different O*NET job characteristics.
 Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).
@@
 
-\begin{quote}
-NOTE.
-Get rid of Fig 3 - present the histograms as indicating that ``not everyone agrees that a characterisitic is a\ldots{} (challenge, hindrance, resource)'', then highlight items with greatest discrepancy to provide flavor to the histograms (flip the current \(\P\) ordering)
-\end{quote}
-
 H1 posits that \emph{not everyone agrees} that a characterisitic is a hindrance, challenge, or resource.
 Figure \ref{fig:overallhist} presents standard deviations of characteristic rating across all rated items.
-Here,the \emph{spread} of difference exhibits wider distributions of (dis)agreement for challenge and resource ratings (and a relatively more leptokurtic distribution of (dis)agreement for hindrances).
+Here,the \emph{spread} of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic distribution of disagreement for hindrances).
 The distributions demonstrate that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
-This points to \emph{hindrances}, in particular, as being likely amenable to future probing regarding moderating conditions.
 A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} \textless{} .01).
+This points to \emph{hindrances}, in particular, as being most generally amenable to future probing regarding moderating conditions.
 
-Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the 8-most \emph{consistently rated} and \emph{inconsistently rated} resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
-The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} Figure \ref{fig:combinegraphs} presents the \emph{most consistently agreed on} resources, hindrances, and challenges as indexed by lowest empirical standard deviations, while Figure \ref{fig:combinegraphs2} presents the characteristics with the greatest amount of \emph{disagreement} across workers.
-The figures again highlight that what is perceived as resource and challenge tends to be relatively agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
+To provide context to the Figure \ref{fig:overallhist} distributions, we present the Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the 8-most \emph{similarly rated} (Figure \ref{fig:combinegraphs}) and \emph{dissimilarly rated} resources, challenges, and demands (Figure \ref{fig:combinegraphs2}).\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
+The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} These figures again highlight that what is perceived as resource and challenge tends to be relatively agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
 However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16).
-In sum, these results provide some collective support for H1, and particularly so for hindrances, which are differently experienced across our raters.
+In sum, these results provide support for H1, and particularly so for hindrances, which are differently experienced across our raters.
 
 The second hypothesis, similarly oriented to H1, stated that job characteristics would not be \emph{uniquely} categorized as a resource or demand.
-We explore this via pattern of correlation similar to Campbell and Fiske (1959)'s multi--trait multi--method matrix.
+We explore this via pattern of correlation similar in intent to Campbell and Fiske (1959)'s multi--trait multi--method matrix.
 Table 1 provides the correlations among the O*NET ``scale''--level groupings\footnote{Survey items are grouped by O*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc).
 These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.} across evaluations as resource, challenge, and hindrance.
-Here would expect trivial correlations if job characteristics \emph{were} uniquely categorized.
+Here one would expect only trivial associations if job characteristics \emph{were} uniquely categorized.
 First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (\emph{SD} = .13, coefficient magnitude ranges from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, \emph{M} = .43, \emph{SD} =.16).
-Hindrance categories, however, had less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, \emph{M} = .62, \emph{SD} = .17.
-When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.
+Job hindrances, however, exhibited less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, \emph{M} = .62, \emph{SD} = .17.
+When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater selectivity.
+
+\begin{quote}
+STOPPED HERE: Too much description
+\end{quote}
 
@@
 
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-abbas2019challenge}{}}%
+\phantomsection\label{refs}
+\begin{CSLReferences}{1}{1}
+\bibitem[\citeproctext]{ref-abbas2019challenge}
 Abbas M and Raja U (2019) Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology} 34(2). Springer: 189--201.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
+\bibitem[\citeproctext]{ref-bakker2014job}
 Bakker AB and Demerouti E (2014) Job demands--resources theory. \emph{Wellbeing: A complete reference guide}. John Wiley \& Sons, Ltd Chichester, UK: 1--28.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
+\bibitem[\citeproctext]{ref-bakker2017job}
 Bakker AB and Demerouti E (2017) Job demands--resources theory: Taking stock and looking forward. \emph{Journal of occupational health psychology} 22(3). Educational Publishing Foundation: 273.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
+\bibitem[\citeproctext]{ref-bakker2013weekly}
 Bakker AB and Sanz-Vergel AI (2013) Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior} 83(3). Elsevier: 397--409.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2005job}{}}%
+\bibitem[\citeproctext]{ref-bakker2005job}
 Bakker AB, Demerouti E and Euwema MC (2005) Job resources buffer the impact of job demands on burnout. \emph{Journal of occupational health psychology} 10(2). Educational Publishing Foundation: 170.
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2007job}{}}%
+\bibitem[\citeproctext]{ref-bakker2007job}
 Bakker AB, Hakanen JJ, Demerouti E, et al.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-campbell1959convergent}{}}%
+\bibitem[\citeproctext]{ref-burr2019third}
+Burr H, Berthelsen H, Moncada S, et al. (2019) The third version of the copenhagen psychosocial questionnaire. \emph{Safety and health at work} 10(4). Elsevier: 482--503.
+
+\bibitem[\citeproctext]{ref-campbell1959convergent}
 Campbell DT and Fiske DW (1959) Convergent and discriminant validation by the multitrait-multimethod matrix. \emph{Psychological bulletin} 56(2). American Psychological Association: 81--105.
 
-\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
+\bibitem[\citeproctext]{ref-cavanaugh2000empirical}
 Cavanaugh MA, Boswell WR, Roehling MV, et al.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-chen2021daily}{}}%
+\bibitem[\citeproctext]{ref-chen2021daily}
 Chen H, Wang H, Yuan M, et al. (2021) Daily challenge/hindrance demands and cognitive wellbeing: A multilevel moderated mediation model. \emph{Frontiers in Psychology} 12. Frontiers Media SA: 616002.
 
-\leavevmode\vadjust pre{\hypertarget{ref-crawford2010linking}{}}%
+\bibitem[\citeproctext]{ref-crawford2010linking}
 Crawford ER, LePine JA and Rich BL (2010) Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-cronbach1951coefficient}{}}%
+\bibitem[\citeproctext]{ref-cronbach1951coefficient}
 Cronbach LJ (1951) Coefficient alpha and the internal structure of tests. \emph{psychometrika} 16(3). Springer-Verlag: 297--334.
 
-\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
+\bibitem[\citeproctext]{ref-demerouti2001job}
 Demerouti E, Bakker AB, Nachreiner F, et al. (2001) The job demands-resources model of burnout. \emph{Journal of Applied psychology} 86(3). American Psychological Association: 499.
 
-\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
+\bibitem[\citeproctext]{ref-gerich2017relevance}
 Gerich J (2017) The relevance of challenge and hindrance appraisals of working conditions for employees' health.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-hakanen2008job}{}}%
+\bibitem[\citeproctext]{ref-hakanen2008job}
 Hakanen JJ, Schaufeli WB and Ahola K (2008) The job demands-resources model: A three-year cross-lagged study of burnout, depression, commitment, and work engagement.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-horan2020review}{}}%
+\bibitem[\citeproctext]{ref-horan2020review}
 Horan KA, Nakahara WH, DiStaso MJ, et al.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-kim2020thriving}{}}%
+\bibitem[\citeproctext]{ref-kim2020thriving}
 Kim M and Beehr TA (2020) Thriving on demand: Challenging work results in employee flourishing through appraisals and resources.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-kubicek2023all}{}}%
+\bibitem[\citeproctext]{ref-kubicek2023all}
 Kubicek B, Uhlig L, Hülsheger UR, et al.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
+\bibitem[\citeproctext]{ref-lazarus1984stress}
 Lazarus RS and Folkman S (1984) \emph{Stress, Appraisal, and Coping}. Springer publishing company.
 
-\leavevmode\vadjust pre{\hypertarget{ref-lepine2005meta}{}}%
+\bibitem[\citeproctext]{ref-lepine2005meta}
 LePine JA, Podsakoff NP and LePine MA (2005) A meta-analytic test of the challenge stressor--hindrance stressor framework: An explanation for inconsistent relationships among stressors and performance.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lepine2022challenge}{}}%
+\bibitem[\citeproctext]{ref-lepine2022challenge}
 LePine MA (2022) The challenge-hindrance stressor framework: An integrative conceptual review and path forward.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
+\bibitem[\citeproctext]{ref-peterson2001understanding}
 Peterson NG, Mumford MD, Borman WC, et al.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-pindek2024dynamic}{}}%
+\bibitem[\citeproctext]{ref-pindek2024dynamic}
 Pindek S, Meyer K, Valvo A, et al.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-podsakoff2007differential}{}}%
+\bibitem[\citeproctext]{ref-podsakoff2007differential}
 Podsakoff NP, LePine JA and LePine MA (2007) Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-rosen2020challenges}{}}%
+\bibitem[\citeproctext]{ref-rosen2020challenges}
 Rosen CC, Dimotakis N, Cole MS, et al.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-schaufeli2017applying}{}}%
+\bibitem[\citeproctext]{ref-schaufeli2017applying}
 Schaufeli WB (2017) Applying the job demands-resources model: A `how to'guide to measuring and tackling work engagement and burnout. \emph{Organizational dynamics} 46(2). Elsevier: 120--132.
 
-\leavevmode\vadjust pre{\hypertarget{ref-searle2015merits}{}}%
+\bibitem[\citeproctext]{ref-searle2015merits}
 Searle BJ and Auton JC (2015) The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping} 28(2). Taylor \& Francis: 121--143.
 
-\leavevmode\vadjust pre{\hypertarget{ref-webster2010toward}{}}%
+\bibitem[\citeproctext]{ref-webster2010toward}
 Webster JR, Beehr TA and Christiansen ND (2010) Toward a better understanding of the effects of hindrance and challenge stressors on work behavior.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
+\bibitem[\citeproctext]{ref-webster2011extending}
 Webster JR, Beehr TA and Love K (2011) Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior} 79(2). Elsevier: 505--516.
 
-\leavevmode\vadjust pre{\hypertarget{ref-xanthopoulou2007job}{}}%
+\bibitem[\citeproctext]{ref-xanthopoulou2007job}
 Xanthopoulou D, Bakker AB, Dollard MF, et al.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-careless}{}}%
+\bibitem[\citeproctext]{ref-R-careless}
 Yentes RD and Wilhelm F (2021) \emph{Careless: Procedures for Computing Indices of Careless Responding}.

### 2025-09-27 Submission.Rmd
Dunn bros - stuck in the middle of Table 1 (big cor matrix)

@@
 
-We sampled from a Prolific panel with eligibility requirements being 18 years of age (or older) and holding either a full-- or part--time job.
+We sampled from a Prolific panel with eligibility requirements being at least 18 years of age and holding either a full-- or part--time job.
 The Montclair State University Institutional Review Board approved the project and respondents provided consent after reviewing a project description but before starting the survey.
@@
 
-The Occupational Information Network (O\*NET) serves as a repository of information broadly descriptive of occupations [@peterson2001understanding] and these descriptions are frequently updated.
-We focused on 98 work [activity and context statements](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*NET groups into *activity* categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
-Work *context* statements are grouped into interpersonal relationships (e.g., the context of the job in terms of human interaction processes), physical work conditions (e.g., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (e.g., the relationships or interactions between the worker and the structural characteristics of the job).
+The Occupational Information Network (O\*NET) serves as a repository of information broadly descriptive of American occupations [@peterson2001understanding] and these descriptions are frequently updated.
+We focused on 98 work [activity and context statements](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*NET groups into *activity* categories of information input (e.g., where and how is the information and data gained that is needed to perform the job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing the job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
+Work *context* statements are grouped into interpersonal relationships (e.g., the context of the job in terms of human interaction processes), physical work conditions (e.g., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (e.g., the interactions between the worker and the structural characteristics of the job).
 
@@
 For example, "How responsible is the worker for work outcomes and results of other workers?" has response options ranging from *no responsibility* to *very high responsibility*, while the question, "How often do you use electronic mail in this job?" has options ranging from *never* to *every day*.
-For the current investigation, O\*NET’s response scales were retained when asking for *statement relevance* (all response scales shared the same *number* of response option categories [5] regardless of semantic labeling).
+All response scales, regardless of semantic labeling, have the same *number* of response option categories (five).
+For the current investigation, O\*NET’s uniquely--labeled response scales were retained when asking for *statement relevance*.
 We also retained the original O\*NET wording for our item stems, with minor grammatical referent exceptions^[For example, the worker responsibility question was changed from "How responsible is the worker..." to "How responsible are you..."].
@@
 
-The 18-item engagement measure was recently developed by Russell et al.
+The 18-item engagement measure was developed by Russell et al.
 (2022).
@@
 
-H1 posits that *not everyone agrees* that a characterisitic is a hindrance, challenge, or resource.
+H1 states that *not everyone agrees* that a given characterisitic is a work hindrance, challenge, or resource.
 Figure \@ref(fig:overallhist) presents standard deviations of characteristic rating across all rated items.
@@
 A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* < .01).
-This points to *hindrances*, in particular, as being most generally amenable to future probing regarding moderating conditions.
-
-To provide context to the Figure \@ref(fig:overallhist) distributions, we present the Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present the most extreme examples of characteristic variability in the form of the 8-most *similarly rated* (Figure \@ref(fig:combinegraphs)) and *dissimilarly rated* resources, challenges, and demands (Figure \@ref(fig:combinegraphs2)).[^onlinelist] These figures again highlight that what is perceived as resource and challenge tends to be relatively agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
+This points to *hindrances*, in particular, as being differentially experienced across workers (whereas some characteristics exist that are agreed--upon as being (un)resourceful or (non)challenging).
+
+To provide more tangible flavor to the Figure \@ref(fig:overallhist) distributions, Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present the most extreme examples of characteristic variability in the form of the 8-most *similarly rated* (Figure \@ref(fig:combinegraphs)) and *dissimilarly rated* resources, challenges, and demands (Figure \@ref(fig:combinegraphs2)).[^onlinelist] These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
 However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`).
-In sum, these results provide support for H1, and  particularly so for hindrances, which are differently experienced across our raters.
+In sum, these results provide support for H1, and particularly so for hindrances.
 
  [^onlinelist]: A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
-The Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).
-
-The second hypothesis, similarly oriented to H1, stated that job characteristics would not be *uniquely* categorized as a resource or demand.
-We explore this via pattern of correlation similar in intent to @campbell1959convergent's multi--trait multi--method matrix.
-Table 1 provides the correlations among the O\*NET "scale"--level groupings^[Survey items are grouped by O\*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc).
+The Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) presentations are only limited to 8 characteristics per perceived category in consideration of page--space (there are 252 individual characteristic ratings in the online resources).
+
+The second hypothesis, similarly oriented to H1, stated that job characteristics would not be *exclusively* categorized as a resource or demand.
+We explore this via pattern of correlation, procedurally derivative of @campbell1959convergent's multi--trait multi--method matrix.
+Table 1 provides correlations among the O\*NET "scale"--level groupings^[Survey items are grouped by O\*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc).
 These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.] across evaluations as resource, challenge, and hindrance.
-Here one would expect only trivial associations if job characteristics *were* uniquely categorized.
+Here one would expect only trivial associations across resource, challenge, and hindrance ratings if job characteristics *were* uniquely categorized as such.
 First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, coefficient magnitude ranges from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16).

### 2025-09-27 Submission.tex
Dunn bros - stuck in the middle of Table 1 (big cor matrix)

--- 2025-09-06 Submission.tex
@@
 
-\begin{quote}
-NOTE. grab O*NET description from desktop (this paragraph only)
-\end{quote}
-
 \hypertarget{characteristics-challenge-demands-hindrance-demands-and-resources}{%
@@
 
-The Occupational Information Network (O*NET) serves as a repository of information broadly descriptive of occupations (Peterson et al., 2001).
-The O*NET database consists of hundreds of standardized and occupation-specific descriptors of occupations in the US and these descriptions are frequently updated.
-We focused on 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context statements} which O*NET groups into \emph{activity} categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
-Work \emph{context} statements are grouped into interpersonal relationships (e.g., the context of the job in terms of human interaction processes), physical work conditions (e.g., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (e.g., the relationships or interactions between the worker and the structural characteristics of the job).
+The Occupational Information Network (O*NET) serves as a repository of information broadly descriptive of American occupations (Peterson et al., 2001) and these descriptions are frequently updated.
+We focused on 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context statements} which O*NET groups into \emph{activity} categories of information input (e.g., where and how is the information and data gained that is needed to perform the job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing the job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
+Work \emph{context} statements are grouped into interpersonal relationships (e.g., the context of the job in terms of human interaction processes), physical work conditions (e.g., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (e.g., the interactions between the worker and the structural characteristics of the job).
 
-O*NET collects information about these elements by periodically surveying workers with job characteristic questions, which often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}.
+O*NET collects information about these elements by periodically surveying workers with job characteristic questions, each of which often has \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}.
 For example, ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{no responsibility} to \emph{very high responsibility}, while the question, ``How often do you use electronic mail in this job?'' has options ranging from \emph{never} to \emph{every day}.
-We retained O*NET's response scales while asking for statement relevance, all of which shared the same number of response option categories (5) regardless of semantic label difference.
-We also retained original O*NET wording for our item stems, with minor grammatical exceptions\footnote{For example, the worker responsibility question was changed from ``How responsible is the worker\ldots{}'' to ``How responsible are you\ldots{}''}.
+All response scales, regardless of semantic labeling, have the same \emph{number} of response option categories (five).
+For the current investigation, O*NET's uniquely--labeled response scales were retained when asking for \emph{statement relevance}.
+We also retained the original O*NET wording for our item stems, with minor grammatical referent exceptions\footnote{For example, the worker responsibility question was changed from ``How responsible is the worker\ldots{}'' to ``How responsible are you\ldots{}''}.
 The total number of items on each administered survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for evaluations for 14 O*NET characteristics that we surmised to have extremely low frequency of affirmative endorsement across respondents (one such excluded characteristic, for example, was ``\ldots the extent to which the worker is exposed to radiation on the job'').
 
-Participants were first asked to think about whether or not their job could be described as consisting of these job characteristics.
+Participants were first asked to consider whether or not their job could reasonably be described as consisting of each job characteristic.
 If a respondent indicated that any one characteristic was not applicable for their job (e.g., answered \emph{never} or \emph{not at all}), they were not subsequently asked to rate the level of resource (\ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (\ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (\ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment).
-These ratings were made along a 5--point Likert--type agreement scale with values of (1) Strongly Disagree, (2) Disagree, (3) Neither Agree nor Disagree, (4) Agree, and (5) Strongly Agree.
+The challenge, hindrance, and resource ratings were made along a 5--point Likert--type agreement scale with values of (1) Strongly Disagree, (2) Disagree, (3) Neither Agree nor Disagree, (4) Agree, and (5) Strongly Agree.
 All questions were administered in randomized order within blocks of characteristic, resource, challenge, and hindrance.
@@
 
-The 18-item engagement measure was recently developed by Russell et al.~(2022).
+The 18-item engagement measure was developed by Russell et al.~(2022).
 Responses were provided using a Likert-type scale ranging from (1) Strongly Disagree to (6) Strongly Agree.
@@
 
-Respondents were asked to think about their primary job, and each administered survey branched content dependent on whether or not the respondent's job could be described as consisting of the different O*NET job characteristics.
+Respondents were asked to think only about their \emph{primary} job, and each administered survey branched content dependent on whether or not this job could be described as consisting of the different O*NET job characteristics.
 Participants were compensated six USD for their participation (the estimated time commitment pre-administration was 45 minutes).
@@
 
+H1 states that \emph{not everyone agrees} that a given characterisitic is a work hindrance, challenge, or resource.
+Figure \ref{fig:overallhist} presents standard deviations of characteristic rating across all rated items.
+Here,the \emph{spread} of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic distribution of disagreement for hindrances).
+The distributions demonstrate that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
+A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} \textless{} .01).
+This points to \emph{hindrances}, in particular, as being differentially experienced across workers (whereas some characteristics exist that are agreed--upon as being (un)resourceful or (non)challenging).
+
+To provide more tangible flavor to the Figure \ref{fig:overallhist} distributions, Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the 8-most \emph{similarly rated} (Figure \ref{fig:combinegraphs}) and \emph{dissimilarly rated} resources, challenges, and demands (Figure \ref{fig:combinegraphs2}).\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
+The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category in consideration of page--space (there are 252 individual characteristic ratings in the online resources).} These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
+However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16).
+In sum, these results provide support for H1, and particularly so for hindrances.
+
+The second hypothesis, similarly oriented to H1, stated that job characteristics would not be \emph{exclusively} categorized as a resource or demand.
+We explore this via pattern of correlation, procedurally derivative of Campbell and Fiske (1959)'s multi--trait multi--method matrix.
+Table 1 provides correlations among the O*NET ``scale''--level groupings\footnote{Survey items are grouped by O*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc).
+These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.} across evaluations as resource, challenge, and hindrance.
+Here one would expect only trivial associations across resource, challenge, and hindrance ratings if job characteristics \emph{were} uniquely categorized as such.
+First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (\emph{SD} = .13, coefficient magnitude ranges from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, \emph{M} = .43, \emph{SD} =.16).
+Job hindrances, however, exhibited less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, \emph{M} = .62, \emph{SD} = .17.
+When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater selectivity.
+
 \begin{quote}
-NOTE.
-Get rid of Fig 3 - present the histograms as indicating that ``not everyone agrees that a characterisitic is a\ldots{} (challenge, hindrance, resource)'', then highlight items with greatest discrepancy to provide flavor to the histograms (flip the current \(\P\) ordering)
+STOPPED HERE: Too much description
 \end{quote}
-
-H1 posits that \emph{not everyone agrees} that a characterisitic is a hindrance, challenge, or resource.
-Figure \ref{fig:overallhist} presents standard deviations of characteristic rating across all rated items.
-Here,the \emph{spread} of difference exhibits wider distributions of (dis)agreement for challenge and resource ratings (and a relatively more leptokurtic distribution of (dis)agreement for hindrances).
-The distributions demonstrate that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
-This points to \emph{hindrances}, in particular, as being likely amenable to future probing regarding moderating conditions.
-A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} \textless{} .01).
-
-Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the 8-most \emph{consistently rated} and \emph{inconsistently rated} resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
-The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} Figure \ref{fig:combinegraphs} presents the \emph{most consistently agreed on} resources, hindrances, and challenges as indexed by lowest empirical standard deviations, while Figure \ref{fig:combinegraphs2} presents the characteristics with the greatest amount of \emph{disagreement} across workers.
-The figures again highlight that what is perceived as resource and challenge tends to be relatively agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
-However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16).
-In sum, these results provide some collective support for H1, and particularly so for hindrances, which are differently experienced across our raters.
-
-The second hypothesis, similarly oriented to H1, stated that job characteristics would not be \emph{uniquely} categorized as a resource or demand.
-We explore this via pattern of correlation similar in intent to Campbell and Fiske (1959)'s multi--trait multi--method matrix.
-Table 1 provides the correlations among the O*NET ``scale''--level groupings\footnote{Survey items are grouped by O*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc).
-These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.} across evaluations as resource, challenge, and hindrance.
-Here would expect trivial correlations if job characteristics \emph{were} uniquely categorized.
-First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (\emph{SD} = .13, coefficient magnitude ranges from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, \emph{M} = .43, \emph{SD} =.16).
-Hindrance categories, however, had less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, \emph{M} = .62, \emph{SD} = .17.
-When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater differentiation.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-burr2019third}{}}%
+Burr H, Berthelsen H, Moncada S, et al. (2019) The third version of the copenhagen psychosocial questionnaire. \emph{Safety and health at work} 10(4). Elsevier: 482--503.
+
 \leavevmode\vadjust pre{\hypertarget{ref-campbell1959convergent}{}}%

### 2025-09-30 Submission.tex
moved "Figure 5" chunk above "Figure 3 & 4" so proper numbering sequence would render

--- 2025-09-09 Submission.tex
@@
 
-The Occupational Information Network (O*NET) serves as a repository of information broadly descriptive of occupations (Peterson et al., 2001) and these descriptions are frequently updated.
-We focused on 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context statements} which O*NET groups into \emph{activity} categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
-Work \emph{context} statements are grouped into interpersonal relationships (e.g., the context of the job in terms of human interaction processes), physical work conditions (e.g., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (e.g., the relationships or interactions between the worker and the structural characteristics of the job).
+The Occupational Information Network (O*NET) serves as a repository of information broadly descriptive of American occupations (Peterson et al., 2001) and these descriptions are frequently updated.
+We focused on 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context statements} which O*NET groups into \emph{activity} categories of information input (e.g., where and how is the information and data gained that is needed to perform the job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing the job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?).
+Work \emph{context} statements are grouped into interpersonal relationships (e.g., the context of the job in terms of human interaction processes), physical work conditions (e.g., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (e.g., the interactions between the worker and the structural characteristics of the job).
 
@@
 For example, ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{no responsibility} to \emph{very high responsibility}, while the question, ``How often do you use electronic mail in this job?'' has options ranging from \emph{never} to \emph{every day}.
-For the current investigation, O*NET's response scales were retained when asking for \emph{statement relevance} (all response scales shared the same \emph{number} of response option categories {[}5{]} regardless of semantic labeling).
+All response scales, regardless of semantic labeling, have the same \emph{number} of response option categories (five).
+For the current investigation, O*NET's uniquely--labeled response scales were retained when asking for \emph{statement relevance}.
 We also retained the original O*NET wording for our item stems, with minor grammatical referent exceptions\footnote{For example, the worker responsibility question was changed from ``How responsible is the worker\ldots{}'' to ``How responsible are you\ldots{}''}.
@@
 \centering
+\includegraphics{Submission_files/figure-latex/overallhist-1.pdf}
+\caption{\label{fig:overallhist}Frequency distributions of standard deviations across characteristics rated as resources, challenges, and demands.}
+\end{figure}
+
+\begin{figure}
+\centering
 \includegraphics{Submission_files/figure-latex/combinegraphs-1.pdf}
@@
 
-\begin{figure}
-\centering
-\includegraphics{Submission_files/figure-latex/overallhist-1.pdf}
-\caption{\label{fig:overallhist}Frequency distributions of standard deviations across characteristics rated as resources, challenges, and demands.}
-\end{figure}
-
-H1 posits that \emph{not everyone agrees} that a characterisitic is a hindrance, challenge, or resource.
+H1 states that \emph{not everyone agrees} that a given characterisitic is a work hindrance, challenge, or resource.
 Figure \ref{fig:overallhist} presents standard deviations of characteristic rating across all rated items.
@@
 A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} \textless{} .01).
-This points to \emph{hindrances}, in particular, as being most generally amenable to future probing regarding moderating conditions.
+This points to \emph{hindrances}, in particular, as being differentially experienced across workers (whereas some characteristics exist that are agreed--upon as being (un)resourceful or (non)challenging).
 
-To provide context to the Figure \ref{fig:overallhist} distributions, we present the Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the 8-most \emph{similarly rated} (Figure \ref{fig:combinegraphs}) and \emph{dissimilarly rated} resources, challenges, and demands (Figure \ref{fig:combinegraphs2}).\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
-The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category because of space restrictions (there are 252 individual characteristic ratings in the online resources).} These figures again highlight that what is perceived as resource and challenge tends to be relatively agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
+To provide more tangible flavor to the Figure \ref{fig:overallhist} distributions, Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the 8-most \emph{similarly rated} (Figure \ref{fig:combinegraphs}) and \emph{dissimilarly rated} resources, challenges, and demands (Figure \ref{fig:combinegraphs2}).\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
+The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category in consideration of page--space (there are 252 individual characteristic ratings in the online resources).} These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
 However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16).
-In sum, these results provide support for H1, and particularly so for hindrances, which are differently experienced across our raters.
+In sum, these results provide support for H1, and particularly so for hindrances.
 
-The second hypothesis, similarly oriented to H1, stated that job characteristics would not be \emph{uniquely} categorized as a resource or demand.
-We explore this via pattern of correlation similar in intent to Campbell and Fiske (1959)'s multi--trait multi--method matrix.
-Table 1 provides the correlations among the O*NET ``scale''--level groupings\footnote{Survey items are grouped by O*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc).
+The second hypothesis, similarly oriented to H1, stated that job characteristics would not be \emph{exclusively} categorized as a resource or demand.
+We explore this via pattern of correlation, procedurally derivative of Campbell and Fiske (1959)'s multi--trait multi--method matrix.
+Table 1 provides correlations among the O*NET ``scale''--level groupings\footnote{Survey items are grouped by O*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc).
 These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.} across evaluations as resource, challenge, and hindrance.
-Here one would expect only trivial associations if job characteristics \emph{were} uniquely categorized.
+Here one would expect only trivial associations across resource, challenge, and hindrance ratings if job characteristics \emph{were} uniquely categorized as such.
 First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (\emph{SD} = .13, coefficient magnitude ranges from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, \emph{M} = .43, \emph{SD} =.16).

### 2025-10-04 Submission.Rmd
moved "Figure 5" chunk above "Figure 3 & 4" so proper numbering sequence would render
first 2 paragraphs correlation section ok

@@
 
+```{r overallhist, fig.cap="Frequency distributions of standard deviations across characteristics rated as resources, challenges, and demands."}
+
+## Moved up from lower location 9/30 because of Figure numbering within paper
+## resource$sd
+
+toplotresource <- resource
+toplotchallenge <- challenge
+toplothindrance <- hindrance
+
+toplotresource$RD <- "Resource"
+toplotchallenge$RD <- "Challenge"
+toplothindrance$RD <- "Hindrance"
+
+toplottogether <- rbind(toplotresource,toplotchallenge,toplothindrance)
+
+library(ggplot2)
+#ggplot(resource, aes(x=sd)) + geom_histogram()
+ggplot(toplottogether, aes(x=sd)) + geom_histogram() + facet_grid(RD ~ .) + labs(x = "Standard Deviation")
+
+lookie <- stats::bartlett.test(sd ~ RD, toplottogether)
+
+```
+
 ```{r resourcesagree, fig.cap="Characteristics most similarly viewed as resources (lowest standard deviations)."}
@@
 library(gridExtra)
-grid.arrange(b, c, a, nrow = 3)
+grid.arrange(b, a, c, nrow = 3)
 
@@
 library(gridExtra)
-grid.arrange(e, f, d, nrow = 3)
-
-```
-
-```{r overallhist, fig.cap="Frequency distributions of standard deviations across characteristics rated as resources, challenges, and demands."}
-
-## resource$sd
-
-toplotresource <- resource
-toplotchallenge <- challenge
-toplothindrance <- hindrance
-
-toplotresource$RD <- "Resource"
-toplotchallenge$RD <- "Challenge"
-toplothindrance$RD <- "Hindrance"
-
-toplottogether <- rbind(toplotresource,toplotchallenge,toplothindrance)
-
-library(ggplot2)
-#ggplot(resource, aes(x=sd)) + geom_histogram()
-ggplot(toplottogether, aes(x=sd)) + geom_histogram() + facet_grid(RD ~ .) + labs(x = "Standard Deviation")
-
-lookie <- stats::bartlett.test(sd ~ RD, toplottogether)
+grid.arrange(e, d, f, nrow = 3)
 
@@
 Figure \@ref(fig:overallhist) presents standard deviations of characteristic rating across all rated items.
-Here,the *spread* of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic distribution of disagreement for hindrances).
-The distributions demonstrate that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
+Here,the *spread* of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic and elevated distribution of disagreement for hindrances).
+These distributions reflect that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
 A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* < .01).
-This points to *hindrances*, in particular, as being differentially experienced across workers (whereas some characteristics exist that are agreed--upon as being (un)resourceful or (non)challenging).
-
-To provide more tangible flavor to the Figure \@ref(fig:overallhist) distributions, Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present the most extreme examples of characteristic variability in the form of the 8-most *similarly rated* (Figure \@ref(fig:combinegraphs)) and *dissimilarly rated* resources, challenges, and demands (Figure \@ref(fig:combinegraphs2)).[^onlinelist] These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
+This points to *hindrances*, in particular, as being differentially experienced across workers (whereas some characteristics are agreed--upon as being universally (un)resourceful or (non)challenging).
+
+To provide more context to the Figure \@ref(fig:overallhist) distributions, Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present the most extreme examples of characteristic variability in the form of the 8-most *similarly rated* (Figure \@ref(fig:combinegraphs)) and *dissimilarly rated* resources, challenges, and demands (Figure \@ref(fig:combinegraphs2)).[^onlinelist] These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
 However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`).
@@
 The second hypothesis, similarly oriented to H1, stated that job characteristics would not be *exclusively* categorized as a resource or demand.
-We explore this via pattern of correlation, procedurally derivative of @campbell1959convergent's multi--trait multi--method matrix.
-Table 1 provides correlations among the O\*NET "scale"--level groupings^[Survey items are grouped by O\*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc).
-These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.] across evaluations as resource, challenge, and hindrance.
-Here one would expect only trivial associations across resource, challenge, and hindrance ratings if job characteristics *were* uniquely categorized as such.
-First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, coefficient magnitude ranges from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16).
+We explore this via pattern of correlation, procedurally derivative of @campbell1959convergent's multi--trait multi--method matrix exploration.
+Table \@ref(tab:cortab) provides correlations among O\*NET item "scale"--level groupings^[Survey items are grouped by O\*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc).
+These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.] across resource, challenge, and hindrance evaluations.
+Here one would expect only trivial associations *across* resource, challenge, and hindrance ratings if job characteristics were uniquely categorized as such.
+
+First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, coefficient magnitudes range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16).
 Job hindrances, however, exhibited less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, *M* = .62, *SD* = .17.
-When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater selectivity.
+When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater selectivity across different categories of job activities.
 
@@
 
+Hindrances exhibit greater variability, but a visual scan of the items reveals some with heavy physicality content (see, for example \@ref(fig:combinegraphs2)), perhaps reflecting some artificiality (for example, indicating "not terribly hindering" if the physical demand was not commonplace).
+
 ## Implications

### 2025-10-04 Submission.tex
first 2 paragraphs correlation section ok

--- 2025-09-27 Submission.tex
@@
 
-\begin{figure}
-\centering
-\includegraphics{Submission_files/figure-latex/overallhist-1.pdf}
-\caption{\label{fig:overallhist}Frequency distributions of standard deviations across characteristics rated as resources, challenges, and demands.}
-\end{figure}
-
 H1 states that \emph{not everyone agrees} that a given characterisitic is a work hindrance, challenge, or resource.
 Figure \ref{fig:overallhist} presents standard deviations of characteristic rating across all rated items.
-Here,the \emph{spread} of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic distribution of disagreement for hindrances).
-The distributions demonstrate that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
+Here,the \emph{spread} of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic and elevated distribution of disagreement for hindrances).
+These distributions reflect that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
 A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} \textless{} .01).
-This points to \emph{hindrances}, in particular, as being differentially experienced across workers (whereas some characteristics exist that are agreed--upon as being (un)resourceful or (non)challenging).
+This points to \emph{hindrances}, in particular, as being differentially experienced across workers (whereas some characteristics are agreed--upon as being universally (un)resourceful or (non)challenging).
 
-To provide more tangible flavor to the Figure \ref{fig:overallhist} distributions, Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the 8-most \emph{similarly rated} (Figure \ref{fig:combinegraphs}) and \emph{dissimilarly rated} resources, challenges, and demands (Figure \ref{fig:combinegraphs2}).\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
+To provide more context to the Figure \ref{fig:overallhist} distributions, Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the 8-most \emph{similarly rated} (Figure \ref{fig:combinegraphs}) and \emph{dissimilarly rated} resources, challenges, and demands (Figure \ref{fig:combinegraphs2}).\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
 The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category in consideration of page--space (there are 252 individual characteristic ratings in the online resources).} These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
@@
 The second hypothesis, similarly oriented to H1, stated that job characteristics would not be \emph{exclusively} categorized as a resource or demand.
-We explore this via pattern of correlation, procedurally derivative of Campbell and Fiske (1959)'s multi--trait multi--method matrix.
-Table 1 provides correlations among the O*NET ``scale''--level groupings\footnote{Survey items are grouped by O*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc).
-These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.} across evaluations as resource, challenge, and hindrance.
-Here one would expect only trivial associations across resource, challenge, and hindrance ratings if job characteristics \emph{were} uniquely categorized as such.
-First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (\emph{SD} = .13, coefficient magnitude ranges from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, \emph{M} = .43, \emph{SD} =.16).
+We explore this via pattern of correlation, procedurally derivative of Campbell and Fiske (1959)'s multi--trait multi--method matrix exploration.
+Table \ref{tab:cortab} provides correlations among O*NET item ``scale''--level groupings\footnote{Survey items are grouped by O*NET into categories of Information Input (ii), Mental Processes (mp), Work Output (wo), Interacting with Others (io), Interpersonal Relationships (ir), Physical Work Conditions (pc), and Structural Job Characteristics (sc).
+These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.} across resource, challenge, and hindrance evaluations.
+Here one would expect only trivial associations \emph{across} resource, challenge, and hindrance ratings if job characteristics were uniquely categorized as such.
+
+First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (\emph{SD} = .13, coefficient magnitudes range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, \emph{M} = .43, \emph{SD} =.16).
 Job hindrances, however, exhibited less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, \emph{M} = .62, \emph{SD} = .17.
-When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater selectivity.
+When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater selectivity across different categories of job activities.
 
@@
 
+Hindrances exhibit greater variability, but a visual scan of the items reveals some with heavy physicality content (see, for example \ref{fig:combinegraphs2}), perhaps reflecting some artificiality (for example, indicating ``not terribly hindering'' if the physical demand was not commonplace).
+
 \hypertarget{implications}{%

### 2025-10-24 Submission.tex
pushing for laptop

--- 2025-09-30 Submission.tex
@@
 Figure \ref{fig:overallhist} presents standard deviations of characteristic rating across all rated items.
-Here,the \emph{spread} of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic distribution of disagreement for hindrances).
-The distributions demonstrate that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
+Here,the \emph{spread} of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic and elevated distribution of disagreement for hindrances).
+These distributions reflect that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
 A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} \textless{} .01).
-This points to \emph{hindrances}, in particular, as being differentially experienced across workers (whereas some characteristics exist that are agreed--upon as being (un)resourceful or (non)challenging).
+This points to \emph{hindrances}, in particular, as being differentially experienced across workers (whereas some characteristics are agreed--upon as being universally (un)resourceful or (non)challenging).
 
-To provide more tangible flavor to the Figure \ref{fig:overallhist} distributions, Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the 8-most \emph{similarly rated} (Figure \ref{fig:combinegraphs}) and \emph{dissimilarly rated} resources, challenges, and demands (Figure \ref{fig:combinegraphs2}).\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
+To provide more context to the Figure \ref{fig:overallhist} distributions, Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the 8-most \emph{similarly rated} (Figure \ref{fig:combinegraphs}) and \emph{dissimilarly rated} resources, challenges, and demands (Figure \ref{fig:combinegraphs2}).\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
 The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category in consideration of page--space (there are 252 individual characteristic ratings in the online resources).} These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
@@
 
+Hindrances exhibit greater variability, but a visual scan of the items reveals some with heavy physicality content (see, for example \ref{fig:combinegraphs2}), perhaps reflecting some artificiality (for example, indicating ``not terribly hindering'' if the physical demand was not commonplace).
+
 \subsection{Implications}\label{implications}

### 2025-10-31 Submission.Rmd
dunn bros adds - moving to desktop

@@
 Figure \@ref(fig:overallhist) presents standard deviations of characteristic rating across all rated items.
-Here,the *spread* of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic and elevated distribution of disagreement for hindrances).
+Here, the *spread* of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic and elevated distribution of disagreement for hindrances).
 These distributions reflect that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
 A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* < .01).
-This points to *hindrances*, in particular, as being differentially experienced across workers (whereas some characteristics are agreed--upon as being universally (un)resourceful or (non)challenging).
-
-To provide more context to the Figure \@ref(fig:overallhist) distributions, Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present the most extreme examples of characteristic variability in the form of the 8-most *similarly rated* (Figure \@ref(fig:combinegraphs)) and *dissimilarly rated* resources, challenges, and demands (Figure \@ref(fig:combinegraphs2)).[^onlinelist] These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
+This points to *hindrances*, in particular, as being differentially experienced across workers (whereas characteristics exist that are agreed--upon as being (un)resourceful or (non)challenging).
+
+To provide descriptive context, Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present the most extreme examples of characteristic variability in the form of the top eight *similarly rated* (Figure \@ref(fig:combinegraphs)) and *dissimilarly rated* (Figure \@ref(fig:combinegraphs2)) resources, challenges, and demands.[^onlinelist] These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
 However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`).
@@
 [^onlinelist]: A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
-The Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) presentations are only limited to 8 characteristics per perceived category in consideration of page--space (there are 252 individual characteristic ratings in the online resources).
-
-The second hypothesis, similarly oriented to H1, stated that job characteristics would not be *exclusively* categorized as a resource or demand.
+The Figure \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) presentations are limited to "top eight" characteristics per category in consideration of page--space (there are 252 individual characteristic ratings in the online resources).
+
+The second hypothesis stated that job characteristics would not be *exclusively* categorized as a resource or demand.
 We explore this via pattern of correlation, procedurally derivative of @campbell1959convergent's multi--trait multi--method matrix exploration.
@@
 These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.] across resource, challenge, and hindrance evaluations.
-Here one would expect only trivial associations *across* resource, challenge, and hindrance ratings if job characteristics were uniquely categorized as such.
+Here one would expect only trivial associations *across* resource, challenge, and hindrance perceptions if job characteristics were uniquely categorized as such.
 
 First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (*SD* = .13, coefficient magnitudes range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, *M* = .43, *SD* =.16).
-Job hindrances, however, exhibited less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, *M* = .62, *SD* = .17.
+Job hindrances, however, exhibited relatively elevated associations across categories, with correlations ranging from .33 to .86, *M* = .62, *SD* = .17.
 When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater selectivity across different categories of job activities.
 
->STOPPED HERE: Too much description
-
-The mean resource to challenge correlations within the same dimension ranged from .62 to .66 (*M* = .64, *SD* = .02; for example, the association between information input ratings as a resource and as a challenge was .62).
-The correlations between resources and challenges *across* dimensions (for example, the correlation between mental processes [resource] and work output [challenge] was .39) ranged from .08 to .50, *M* = .32, *SD* = .12.
-The resource-hindrance correlations within the same dimension ranged from -.16 to -.30 (*M* = -.24, *SD* = .05), while the correlations between resources and hindrances *across* dimensions ranged from .05 to -.27, *M* = -.14, *SD* = .08.
-The mean challenge to hindrance correlations within the same dimension ranged from -.04 to -.27 (*M* = -.21, *SD* = .08).
-The correlations between challenges to hindrances across dimensions ranged from .12 to -.26, *M* = -.11, *SD* = .09.
-In summary, correlations were larger when what was being rated was the same type of characteristic.
-Challenge and hindrance demands demonstrated smaller relationships, but mostly negative.
-Challenges and resources within the same O\*NET dimensions are strongly and positively related.
-These results provide support for H2, suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is perceived as a *resource* being also perceived as a *challenge*.
+Regarding comparisons *across perception type*, the mean resource to challenge correlations within the same O\*Net grouping ranged from .62 to .66 (*M* = .64, *SD* = .02; for example, the association between information input ratings as a resource and as a challenge was .62).
+The correlations between resources and challenges *across* O\*Net grouping ranged from .08 to .50, *M* = .32, *SD* = .12 (for example, the correlation between mental processes [resource] and work output [challenge] was .39).
+The resource-hindrance correlations within the same O\*Net grouping ranged from -.16 to -.30 (*M* = -.24, *SD* = .05), while the correlations between resources and hindrances *across* O\*Net grouping ranged from .05 to -.27 (*M* = -.14, *SD* = .08).
+The mean challenge to hindrance correlations within the same O\*Net grouping ranged from -.04 to -.27 (*M* = -.21, *SD* = .08).
+The correlations between challenges to hindrances across O\*Net grouping ranged from .12 to -.26, *M* = -.11, *SD* = .09.
+In summary, observed correlations were larger  *within* O\*Net grouping than *across* (for all comparisons).
+Challenge and resource demands demonstrated the largest associations, with even the magnitude of across--category associations (.32) exceeding all hindrance perception associations -.11 to -.24).
+These results provide support for H2, -- particularly regarding what is perceived as a *resource* being also perceived as a *challenge*.
 Stated differently, job characteristics should not be uniquely categorized as resource or demand.
 
-The next group of hypotheses focuses on the relationship among resources and demands (challenge and hindrance) and outcomes.
-Table 2 shows the overall associations between resource/challenge/hindrances and outcomes of engagement, stress, and burnout.
-Here, we observe positive associations between resources, and challenges with engagement, and a negative association between hindrances and engagement.
-A positive association is observed between hindrances and stress.
+### Outcome Associations
 
 ```{r cortab, results="asis", eval=TRUE}
+
+library(dplyr)
 
@@
 library(plyr)
-library(dplyr)
 
@@
 ```
-### Challenges, Resources, and Outcomes
 
@@
 
+Table 2 presents associations between total estimates of resource/ challenge/ hindrance within one's job and outcomes of engagement, stress, and burnout.
+Here, workers' perceptions were aggregated across all characteristics to provide "overall" resource and demand indices.
+Engagement exhibited non-trivial associations with all three types of perception whereas stress was only associated with the hindrance aggregate.
+The more percieved hindrances, the higher the rating of stress.
+
+Regarding the specific hypotheses we applied a series of hierarchical regressions.
 H3a predicted that both resources and challenges would predict engagement.

### 2025-10-31 Submission.tex
dunn bros adds - moving to desktop

--- 2025-10-04 Submission.tex
@@
 A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} \textless{} .01).
-This points to \emph{hindrances}, in particular, as being differentially experienced across workers (whereas some characteristics are agreed--upon as being universally (un)resourceful or (non)challenging).
+This points to \emph{hindrances}, in particular, as being differentially experienced across workers (whereas characteristics exist that are agreed--upon as being (un)resourceful or (non)challenging).
 
-To provide more context to the Figure \ref{fig:overallhist} distributions, Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the 8-most \emph{similarly rated} (Figure \ref{fig:combinegraphs}) and \emph{dissimilarly rated} resources, challenges, and demands (Figure \ref{fig:combinegraphs2}).\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
-The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category in consideration of page--space (there are 252 individual characteristic ratings in the online resources).} These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
+To provide descriptive context, Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the top eight \emph{similarly rated} (Figure \ref{fig:combinegraphs}) and \emph{dissimilarly rated} (Figure \ref{fig:combinegraphs2}) resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
+The Figure \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are limited to ``top eight'' characteristics per category in consideration of page--space (there are 252 individual characteristic ratings in the online resources).} These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
 However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16).
@@
 
-The second hypothesis, similarly oriented to H1, stated that job characteristics would not be \emph{exclusively} categorized as a resource or demand.
+The second hypothesis stated that job characteristics would not be \emph{exclusively} categorized as a resource or demand.
 We explore this via pattern of correlation, procedurally derivative of Campbell and Fiske (1959)'s multi--trait multi--method matrix exploration.
@@
 These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.} across resource, challenge, and hindrance evaluations.
-Here one would expect only trivial associations \emph{across} resource, challenge, and hindrance ratings if job characteristics were uniquely categorized as such.
+Here one would expect only trivial associations \emph{across} resource, challenge, and hindrance perceptions if job characteristics were uniquely categorized as such.
 
 First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (\emph{SD} = .13, coefficient magnitudes range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, \emph{M} = .43, \emph{SD} =.16).
-Job hindrances, however, exhibited less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, \emph{M} = .62, \emph{SD} = .17.
+Job hindrances, however, exhibited relatively elevated associations across categories, with correlations ranging from .33 to .86, \emph{M} = .62, \emph{SD} = .17.
 When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater selectivity across different categories of job activities.
 
-\begin{quote}
-STOPPED HERE: Too much description
-\end{quote}
-
-The mean resource to challenge correlations within the same dimension ranged from .62 to .66 (\emph{M} = .64, \emph{SD} = .02; for example, the association between information input ratings as a resource and as a challenge was .62).
-The correlations between resources and challenges \emph{across} dimensions (for example, the correlation between mental processes {[}resource{]} and work output {[}challenge{]} was .39) ranged from .08 to .50, \emph{M} = .32, \emph{SD} = .12.
-The resource-hindrance correlations within the same dimension ranged from -.16 to -.30 (\emph{M} = -.24, \emph{SD} = .05), while the correlations between resources and hindrances \emph{across} dimensions ranged from .05 to -.27, \emph{M} = -.14, \emph{SD} = .08.
-The mean challenge to hindrance correlations within the same dimension ranged from -.04 to -.27 (\emph{M} = -.21, \emph{SD} = .08).
-The correlations between challenges to hindrances across dimensions ranged from .12 to -.26, \emph{M} = -.11, \emph{SD} = .09.
-In summary, correlations were larger when what was being rated was the same type of characteristic.
-Challenge and hindrance demands demonstrated smaller relationships, but mostly negative.
-Challenges and resources within the same O*NET dimensions are strongly and positively related.
-These results provide support for H2, suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is perceived as a \emph{resource} being also perceived as a \emph{challenge}.
+Regarding comparisons \emph{across perception type}, the mean resource to challenge correlations within the same O*Net grouping ranged from .62 to .66 (\emph{M} = .64, \emph{SD} = .02; for example, the association between information input ratings as a resource and as a challenge was .62).
+The correlations between resources and challenges \emph{across} O*Net grouping ranged from .08 to .50, \emph{M} = .32, \emph{SD} = .12 (for example, the correlation between mental processes {[}resource{]} and work output {[}challenge{]} was .39).
+The resource-hindrance correlations within the same O*Net grouping ranged from -.16 to -.30 (\emph{M} = -.24, \emph{SD} = .05), while the correlations between resources and hindrances \emph{across} O*Net grouping ranged from .05 to -.27 (\emph{M} = -.14, \emph{SD} = .08).
+The mean challenge to hindrance correlations within the same O*Net grouping ranged from -.04 to -.27 (\emph{M} = -.21, \emph{SD} = .08).
+The correlations between challenges to hindrances across O*Net grouping ranged from .12 to -.26, \emph{M} = -.11, \emph{SD} = .09.
+In summary, observed correlations were larger \emph{within} O*Net grouping than \emph{across} (for all comparisons).
+Challenge and resource demands demonstrated the largest associations, with even the magnitude of across--category associations (.32) exceeding all hindrance perception associations -.11 to -.24).
+These results provide support for H2, -- particularly regarding what is perceived as a \emph{resource} being also perceived as a \emph{challenge}.
 Stated differently, job characteristics should not be uniquely categorized as resource or demand.
 
-The next group of hypotheses focuses on the relationship among resources and demands (challenge and hindrance) and outcomes.
-Table 2 shows the overall associations between resource/challenge/hindrances and outcomes of engagement, stress, and burnout.
-Here, we observe positive associations between resources, and challenges with engagement, and a negative association between hindrances and engagement.
-A positive association is observed between hindrances and stress.
+\hypertarget{outcome-associations}{%
+\subsubsection{Outcome Associations}\label{outcome-associations}}
 
@@
 
-\hypertarget{challenges-resources-and-outcomes}{%
-\subsubsection{Challenges, Resources, and Outcomes}\label{challenges-resources-and-outcomes}}
-
 \begin{table}[tbp]
@@
 
+Table 2 presents associations between total estimates of resource/ challenge/ hindrance within one's job and outcomes of engagement, stress, and burnout.
+Here, workers' perceptions were aggregated across all characteristics to provide ``overall'' resource and demand indices.
+Engagement exhibited non-trivial associations with all three types of perception whereas stress was only associated with the hindrance aggregate.
+The more percieved hindrances, the higher the rating of stress.
+
+Regarding the specific hypotheses we applied a series of hierarchical regressions.
 H3a predicted that both resources and challenges would predict engagement.

### 2025-11-18 Submission.Rmd
pushing to desktop - overwriting desktop (mostly attempts to format large cor table)

@@
 
-To provide descriptive context, Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present the most extreme examples of characteristic variability in the form of the top eight *similarly rated* (Figure \@ref(fig:combinegraphs)) and *dissimilarly rated* (Figure \@ref(fig:combinegraphs2)) resources, challenges, and demands.[^onlinelist] These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
+For some descriptive context, Figures \@ref(fig:combinegraphs) and \@ref(fig:combinegraphs2) present the most extreme examples of characteristic variability in the form of the top eight *similarly rated* (Figure \@ref(fig:combinegraphs)) and *dissimilarly rated* (Figure \@ref(fig:combinegraphs2)) resources, challenges, and demands.[^onlinelist] These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the "lowest 8" resource standard deviations is `r min(topresource$sd)` to `r max(topresource$sd)` and the range of lowest 8 challenge standard deviations is `r min(topchallenge$sd)` to `r max(topchallenge$sd)`).
 However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the *greatest agreement* still ranging in fairly large standard deviations (ranging from `r min(tophindrance$sd)` to `r max(tophindrance$sd)`).
@@
 Job hindrances, however, exhibited relatively elevated associations across categories, with correlations ranging from .33 to .86, *M* = .62, *SD* = .17.
-When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater selectivity across different categories of job activities.
-
-Regarding comparisons *across perception type*, the mean resource to challenge correlations within the same O\*Net grouping ranged from .62 to .66 (*M* = .64, *SD* = .02; for example, the association between information input ratings as a resource and as a challenge was .62).
+When people perceive hindrances, these seem to be more likely to be shared across different types of job activities, whereas challenges and resources can be relatively isolated within different job activities.
+
+Regarding comparisons *across perception type*, the mean resource to challenge correlations within the same O\*Net grouping ranged from .62 to .66 (*M* = .64, *SD* = .02; for example, the association between information input ratings as a resource and information input challenges was .62).
 The correlations between resources and challenges *across* O\*Net grouping ranged from .08 to .50, *M* = .32, *SD* = .12 (for example, the correlation between mental processes [resource] and work output [challenge] was .39).
@@
 Challenge and resource demands demonstrated the largest associations, with even the magnitude of across--category associations (.32) exceeding all hindrance perception associations -.11 to -.24).
-These results provide support for H2, -- particularly regarding what is perceived as a *resource* being also perceived as a *challenge*.
-Stated differently, job characteristics should not be uniquely categorized as resource or demand.
+These results provide support for H2 -- particularly regarding *resource* and *challenge* perceptions.
+Stated differently, job characteristics should not be expected to be uniquely categorized as resource or demand.
 
@@
 
-Table 2 presents associations between total estimates of resource/ challenge/ hindrance within one's job and outcomes of engagement, stress, and burnout.
-Here, workers' perceptions were aggregated across all characteristics to provide "overall" resource and demand indices.
+The consequences of demands and resources are theoretically varied.
+Table 2 presents empirical  associations between estimates of resource, challenge, and hindrance and worker *engagement*, *stress*, and *burnout*.
+Here, workers' perceptions were aggregated across all characteristics to provide indications of "overall" resource and demand experience.
 Engagement exhibited non-trivial associations with all three types of perception whereas stress was only associated with the hindrance aggregate.

### 2025-11-18 Submission.tex
pushing to desktop - overwriting desktop (mostly attempts to format large cor table)

@@
 Figure \ref{fig:overallhist} presents standard deviations of characteristic rating across all rated items.
-Here,the \emph{spread} of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic and elevated distribution of disagreement for hindrances).
+Here, the \emph{spread} of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic and elevated distribution of disagreement for hindrances).
 These distributions reflect that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
@@
 
-To provide descriptive context, Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the top eight \emph{similarly rated} (Figure \ref{fig:combinegraphs}) and \emph{dissimilarly rated} (Figure \ref{fig:combinegraphs2}) resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
+For some descriptive context, Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the top eight \emph{similarly rated} (Figure \ref{fig:combinegraphs}) and \emph{dissimilarly rated} (Figure \ref{fig:combinegraphs2}) resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
 The Figure \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are limited to ``top eight'' characteristics per category in consideration of page--space (there are 252 individual characteristic ratings in the online resources).} These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).

### 2025-12-01 Submission.Rmd
discussion needs review for redundancy/clarity, etc

@@
 ```
-
-8,000 words inclusive of everything, references, etc
-
-Abstract = 150 words
-
-preference for Word document
 
@@
 papaja::apa_table(r_second$apa, 
-                  caption = "Overall variable bivariate correlations.",
+                  caption = "Outcome variable bivariate correlations.",
                   escape = FALSE, 
@@
 
-The consequences of demands and resources are theoretically varied.
 Table 2 presents empirical  associations between estimates of resource, challenge, and hindrance and worker *engagement*, *stress*, and *burnout*.
@@
 Engagement exhibited non-trivial associations with all three types of perception whereas stress was only associated with the hindrance aggregate.
-The more percieved hindrances, the higher the rating of stress.
-
-Regarding the specific hypotheses we applied a series of hierarchical regressions.
+The more percieved hindrances, the higher the rating of stress, indicating only weak partial support for Hypothesis 3b.
+All subsequent analyses retain this "overall" operationalization of workers' experience of resources, challenges, and hindrances.
+
+### Challenges, Resources, and Job Outcomes
+
+Hypotheses 3a, 4a, and 4b were formally tested via targeted hierarchical regressions.
 H3a predicted that both resources and challenges would predict engagement.
-Table \@ref(tab:chal-resource-table) summarizes the results for engagement (as well as stress and burnout).
-Sum scores for the predictors were used here such that the overall amount of resource or demand is recognized.
-First, challenges and resources explained a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(cr_eng_m2)$r.squared, 2)`, Adj.
+Table \@ref(tab:chal-resource-table) summarizes the results for the hypothesized engagement effect as well as the H4a investigations of both stress and burnout.
+As expected given the Table 2 bivariate associations, the combined effect of challenges and resources did explain a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(cr_eng_m2)$r.squared, 2)`, Adj.
 $R^2$ =  `r round(summary(cr_eng_m2)$adj.r.squared, 2)`, `r cr_eng_info2$statistic$modelfit$r2`.
-Here, the resource slope is significant, wheras the challenge slope is not significant (providing partial support for H3a).
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r cr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_eng_r_square_change`, $\Delta F$ (`r cr_eng_anova$Df[2]`, `r cr_eng_anova$Res.Df[2]`) = `r cr_eng_anova$F[2]`,  and thus provides statistical support for the presence of moderation (Hypothesis 4a).
-Figure \@ref(fig:chal-resource-int) illustrates the interaction.
+However, the resource slope is significant, wheras the challenge slope is not significant.
+This results in only partial support for H3a.
+The inclusion of the interaction term in step two of the model was not hypothesized but is included for completeness.
+The interaction effect did contribute a significant addition to the model, `r cr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_eng_r_square_change`, $\Delta F$ (`r cr_eng_anova$Df[2]`, `r cr_eng_anova$Res.Df[2]`) = `r cr_eng_anova$F[2]`, and thus provides some statistical support for the possibility of moderation.
+Figure \@ref(fig:chal-resource-int) illustrates the nature of the interaction.
 With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low.
@@
 
-Next, challenge demands and resources did not explain a significant amount of the variance in stress,  $R^2$ = `r round(summary(cr_stress_m2)$r.squared, 2)`, Adj.
-$R^2$ =  `r round(summary(cr_stress_m2)$adj.r.squared, 2)`, `r cr_stress_info2$statistic$modelfit$r2`, failing to provide support for Hypothesis 3b.
+Regarding Hypothesis 4a, challenge demands and resources did not explain a significant amount of the variance in stress,  $R^2$ = `r round(summary(cr_stress_m2)$r.squared, 2)`, Adj.
+$R^2$ =  `r round(summary(cr_stress_m2)$adj.r.squared, 2)`, `r cr_stress_info2$statistic$modelfit$r2`.
 The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, `r cr_stress_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_stress_r_square_change`, $\Delta F$ (`r cr_stress_anova$Df[2]`, `r cr_stress_anova$Res.Df[2]`) = `r cr_stress_anova$F[2]`, and thus does not support the presence of moderation.
-
-Finally, challenge demands and resources explained a statistically significant amount of the variability in burnout, $R^2$ = `r round(summary(cr_burn_m2)$r.squared, 2)`, Adj.
+These challenge demands and resources did, however, explain a statistically significant amount of the variability in burnout, $R^2$ = `r round(summary(cr_burn_m2)$r.squared, 2)`, Adj.
 $R^2$ =  `r round(summary(cr_burn_m2)$adj.r.squared, 2)`, `r cr_burn_info2$statistic$modelfit$r2`.
-The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, `r cr_burn_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_burn_r_square_change`, $\Delta F$ (`r cr_burn_anova$Df[2]`, `r cr_burn_anova$Res.Df[2]`) = `r cr_burn_anova$F[2]`,  and thus failing to provide statistical support for the presence of moderation (Hypothesis 4a).
+The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, `r cr_burn_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_burn_r_square_change`, $\Delta F$ (`r cr_burn_anova$Df[2]`, `r cr_burn_anova$Res.Df[2]`) = `r cr_burn_anova$F[2]`, and thus collectively these analyses fail to provide statistical support for the presence of moderation (Hypothesis 4a).
 In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge demands and the outcomes of strain and burnout.
@@
 ```
-### Hindrances, Resources, and Outcomes
+### Hindrances, Resources, and Job Outcomes
 
 We also explored whether there was an interaction between hindrance demands and resources on the outcome variables.
-Sum scores for the predictors were used here again.
-First, hindrance demands and resources explained a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(hr_eng_m2)$r.squared, 2)`, Adj.
-$R^2$ =  `r round(summary(hr_eng_m2)$adj.r.squared, 2)`, `r hr_eng_info2$statistic$modelfit$r2` [see Table \@ref(tab:hind-resource-table)].
-The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, `r hr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_eng_r_square_change`, $\Delta F$ (`r hr_eng_anova$Df[2]`, `r hr_eng_anova$Res.Df[2]`) = `r hr_eng_anova$F[2]`.
+First, hindrance demands and resources did explain a statistically significant amount of the variability in engagement, $R^2$ = `r round(summary(hr_eng_m2)$r.squared, 2)`, Adj.
+$R^2$ =  `r round(summary(hr_eng_m2)$adj.r.squared, 2)`, `r hr_eng_info2$statistic$modelfit$r2` (see Table \@ref(tab:hind-resource-table)).
+The inclusion of the interaction term in step two of the model (again not hypothesized but included for completeness) did not contribute a significant addition to the model, `r hr_eng_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_eng_r_square_change`, $\Delta F$ (`r hr_eng_anova$Df[2]`, `r hr_eng_anova$Res.Df[2]`) = `r hr_eng_anova$F[2]`.
 An interaction between hindrances and resources was not found.
-
 Next exploring stress, hindrance demands and resources explained a statistically significant amount of the variability in stress, $R^2$ = `r round(summary(hr_stress_m2)$r.squared, 2)`, Adj.
 $R^2$ =  `r round(summary(hr_stress_m2)$adj.r.squared, 2)`, `r hr_stress_info2$statistic$modelfit$r2`.
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r hr_stress_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_stress_r_square_change`, $\Delta F$ (`r hr_stress_anova$Df[2]`, `r hr_stress_anova$Res.Df[2]`) = `r hr_stress_anova$F[2]`, supporting the presence of a moderated effect.
-See Figure \@ref(fig:hind-resource-stress-int).
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r hr_stress_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_stress_r_square_change`, $\Delta F$ (`r hr_stress_anova$Df[2]`, `r hr_stress_anova$Res.Df[2]`) = `r hr_stress_anova$F[2]`, supporting the presence of a moderated effect -- see Figure \@ref(fig:hind-resource-stress-int).
 As expected, the relationship between hindrance demands and strain becomes weaker as workers perceive more resources.
@@
 $R^2$ =  `r round(summary(hr_burn_m2)$adj.r.squared, 2)`, `r hr_burn_info2$statistic$modelfit$r2`.
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r hr_burn_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_burn_r_square_change`, $\Delta F$ (`r hr_burn_anova$Df[2]`, `r hr_burn_anova$Res.Df[2]`) = `r hr_burn_anova$F[2]`, supporting the presence of a moderated effect (see Figure \@ref(fig:hind-resource-burn-int)).
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, `r hr_burn_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r hr_burn_r_square_change`, $\Delta F$ (`r hr_burn_anova$Df[2]`, `r hr_burn_anova$Res.Df[2]`) = `r hr_burn_anova$F[2]`, supporting the presence of a moderated effect (Figure \@ref(fig:hind-resource-burn-int)).
 As expected, the relationship between hindrance demands and burnout becomes weaker as workers perceive more resources.
-Summatively these findings provide support for the assertion that resources would moderate the relationships between hindrance demands and the outcomes of strain and burnout.
+Summatively these findings provide support for the assertion that resources would moderate the relationships between hindrance demands and the unwanted outcomes of strain and burnout.
 
@@
 The major aims of this paper were to explore whether: 1) there was variability in subjective ratings of job characteristics as resources and demands, 2) some characteristics were more likely to vary across demand and resource, 3) subjective appraisals were differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and outcomes.
-We found that job characteristics were not uniquely categorized as a resource or demand, but rather, some job characteristics were rated highly as both a resource and a demand (particularly challenge demands).
-The findings broadly revealed that there was relatively more consistency in ratings of resource and challenge characteristics, and far more variability in job characteristics rated as hindrance demands.
-This finding lends additional evidence to @horan2020review’s conclusion that “...stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p.
-3).
-While we did not find support for the prediction that different types of demands would be related to stress and burnout, we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships (as predicted).
-
-In addition to the above findings, this paper made several additional important contributions.
-We utilized a diverse sample of employees across industries who responded to common O\*NET items.
-While O\*NET provides detailed information about frequency and importance ratings among employees, we begin the process of expanding what we know of job characteristics to ratings of an extensive range of demands and resources.
-Further, we provide a repository for other researchers with listing of O\*NET demands and resources across activity and context items for the benefit of all future researchers.
-We also explored not only context and activity holistically, but at a higher level aggregation, which enhances our knowledge of how employees perceive different categories of resources, challenges, and hindrances within different work dimensions, as well as the relationships among them.
-
-Hindrances exhibit greater variability, but a visual scan of the items reveals some with heavy physicality content (see, for example \@ref(fig:combinegraphs2)), perhaps reflecting some artificiality (for example, indicating "not terribly hindering" if the physical demand was not commonplace).
-
-## Implications
-
-The findings presented above have implications for both theory and practice.
-our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs [@webster2011extending].
-This finding aligns quite well with the challenge-hindrance stressor framework, which collectively argue that employees perceive stimuli (i.e., job characteristics) uniquely [@lazarus1984stress], and thus, could appraise them as either a challenge or hindrance to their job performance [@cavanaugh2000empirical].
+We found that job characteristics were not uniquely categorized as a resource or demand, but rather, job characteristics were often viewed similarly as both a resource and a challenging demand.
+The findings broadly revealed further that there was relatively more consistency in ratings of resource and challenge characteristics, and far more variability in hindering elements across workers and jobs.
+While engagement exhibits moderate associations with all investigated perceptions, we did not find support for the prediction that different types of demands would be related to stress and burnout, but we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships (as predicted).
+
+In addition to the above findings, this paper makes several additional important contributions.
+We utilized a diverse sample of employees across industries who responded to items derived from O\*NET specifications.
+O\*NET provides a rich and fairly exhaustive repository of job characteristics that also provides some consistency across investigations -- a somewhat "standardized" lens through which jobs can be deconstructed and investigations compared.
+We also explored characteristics at a higher level of aggregation (retaining O\*NET category groupings), which again expands our collective knowledge of how employees perceive different categories of resources, challenges, and hindrances within different work domains, as well as the relationships among them.
+
+Perceptions of resources and demands, broadly, are not universal -- there are individual differences in how employees experience job characteristics.
+This finding aligns quite well with the challenge-hindrance stressor framework, which posits that employees perceive stimuli (i.e., job characteristics) uniquely [@lazarus1984stress], and thus, could appraise them as either a challenge or hindrance to their job performance [@cavanaugh2000empirical].
 Further, @cavanaugh2000empirical suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes [e.g., @cavanaugh2000empirical], which we partially supported here.
@@
 
+Hindrances exhibit greater variability, but a visual scan of the items reveals some with heavy physicality content (see, for example \@ref(fig:combinegraphs2)), perhaps reflecting some artificiality (for example, indicating "not terribly hindering" if the physical demand was not commonplace).
+
 We also retained the literature-derived definitions of resources, challenges, and hindrances [@demerouti2001job].

### 2025-12-01 Submission.tex
discussion needs review for redundancy/clarity, etc

--- 2025-10-24 Submission.tex
@@
 
-8,000 words inclusive of everything, references, etc
-
-Abstract = 150 words
-
-preference for Word document
-
 While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular.
@@
 Figure \ref{fig:overallhist} presents standard deviations of characteristic rating across all rated items.
-Here,the \emph{spread} of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic and elevated distribution of disagreement for hindrances).
+Here, the \emph{spread} of difference exhibits wider distributions of disagreement for challenge and resource ratings (and a relatively more leptokurtic and elevated distribution of disagreement for hindrances).
 These distributions reflect that some characteristics are largely agreed upon as being challenges and resources, while all hindrance perceptions exhibit a relatively higher level of disagreement.
 A Bartlett's test for homogeneity of variance across the challenge, hindrance, and resource ratings confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} \textless{} .01).
-This points to \emph{hindrances}, in particular, as being differentially experienced across workers (whereas some characteristics are agreed--upon as being universally (un)resourceful or (non)challenging).
+This points to \emph{hindrances}, in particular, as being differentially experienced across workers (whereas characteristics exist that are agreed--upon as being (un)resourceful or (non)challenging).
 
-To provide more context to the Figure \ref{fig:overallhist} distributions, Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the 8-most \emph{similarly rated} (Figure \ref{fig:combinegraphs}) and \emph{dissimilarly rated} resources, challenges, and demands (Figure \ref{fig:combinegraphs2}).\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
-The Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are only limited to 8 characteristics per perceived category in consideration of page--space (there are 252 individual characteristic ratings in the online resources).} These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
+For some descriptive context, Figures \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} present the most extreme examples of characteristic variability in the form of the top eight \emph{similarly rated} (Figure \ref{fig:combinegraphs}) and \emph{dissimilarly rated} (Figure \ref{fig:combinegraphs2}) resources, challenges, and demands.\footnote{A full list of item characteristic ratings, along with summary averages and standard deviations is available in supplementary online resources.
+The Figure \ref{fig:combinegraphs} and \ref{fig:combinegraphs2} presentations are limited to ``top eight'' characteristics per category in consideration of page--space (there are 252 individual characteristic ratings in the online resources).} These figures again highlight that what is perceived as resource and challenge can, with some characteristics, be agreed upon (the range of the ``lowest 8'' resource standard deviations is 0.70 to 0.88 and the range of lowest 8 challenge standard deviations is 0.79 to 0.86).
 However, there is considerably less agreement regarding the degree to which job elements should be considered to be hindrances, with the 8 elements showing the \emph{greatest agreement} still ranging in fairly large standard deviations (ranging from 1.12 to 1.16).
@@
 These groupings were not presented to respondents but are leveraged here to facilitate interpretation of characteristic association.} across resource, challenge, and hindrance evaluations.
-Here one would expect only trivial associations \emph{across} resource, challenge, and hindrance ratings if job characteristics were uniquely categorized as such.
+Here one would expect only trivial associations \emph{across} resource, challenge, and hindrance perceptions if job characteristics were uniquely categorized as such.
 
 First, the average correlation within all resource categories (variables 1 through 7 in Table 1) was .43 (\emph{SD} = .13, coefficient magnitudes range from .15 to .64), and challenge categories exhibited similar associations (ranging from .12 to .70, \emph{M} = .43, \emph{SD} =.16).
-Job hindrances, however, exhibited less differentiation across categories, with relatively elevated correlations ranging from .33 to .86, \emph{M} = .62, \emph{SD} = .17.
-When people perceive hindrances, these seem to be shared across different types of job activities, whereas challenges and resources exhibit greater selectivity across different categories of job activities.
+Job hindrances, however, exhibited relatively elevated associations across categories, with correlations ranging from .33 to .86, \emph{M} = .62, \emph{SD} = .17.
+When people perceive hindrances, these seem to be more likely to be shared across different types of job activities, whereas challenges and resources can be relatively isolated within different job activities.
 
-\begin{quote}
-STOPPED HERE: Too much description
-\end{quote}
+Regarding comparisons \emph{across perception type}, the mean resource to challenge correlations within the same O*Net grouping ranged from .62 to .66 (\emph{M} = .64, \emph{SD} = .02; for example, the association between information input ratings as a resource and information input challenges was .62).
+The correlations between resources and challenges \emph{across} O*Net grouping ranged from .08 to .50, \emph{M} = .32, \emph{SD} = .12 (for example, the correlation between mental processes {[}resource{]} and work output {[}challenge{]} was .39).
+The resource-hindrance correlations within the same O*Net grouping ranged from -.16 to -.30 (\emph{M} = -.24, \emph{SD} = .05), while the correlations between resources and hindrances \emph{across} O*Net grouping ranged from .05 to -.27 (\emph{M} = -.14, \emph{SD} = .08).
+The mean challenge to hindrance correlations within the same O*Net grouping ranged from -.04 to -.27 (\emph{M} = -.21, \emph{SD} = .08).
+The correlations between challenges to hindrances across O*Net grouping ranged from .12 to -.26, \emph{M} = -.11, \emph{SD} = .09.
+In summary, observed correlations were larger \emph{within} O*Net grouping than \emph{across} (for all comparisons).
+Challenge and resource demands demonstrated the largest associations, with even the magnitude of across--category associations (.32) exceeding all hindrance perception associations -.11 to -.24).
+These results provide support for H2 -- particularly regarding \emph{resource} and \emph{challenge} perceptions.
+Stated differently, job characteristics should not be expected to be uniquely categorized as resource or demand.
 
-The mean resource to challenge correlations within the same dimension ranged from .62 to .66 (\emph{M} = .64, \emph{SD} = .02; for example, the association between information input ratings as a resource and as a challenge was .62).
-The correlations between resources and challenges \emph{across} dimensions (for example, the correlation between mental processes {[}resource{]} and work output {[}challenge{]} was .39) ranged from .08 to .50, \emph{M} = .32, \emph{SD} = .12.
-The resource-hindrance correlations within the same dimension ranged from -.16 to -.30 (\emph{M} = -.24, \emph{SD} = .05), while the correlations between resources and hindrances \emph{across} dimensions ranged from .05 to -.27, \emph{M} = -.14, \emph{SD} = .08.
-The mean challenge to hindrance correlations within the same dimension ranged from -.04 to -.27 (\emph{M} = -.21, \emph{SD} = .08).
-The correlations between challenges to hindrances across dimensions ranged from .12 to -.26, \emph{M} = -.11, \emph{SD} = .09.
-In summary, correlations were larger when what was being rated was the same type of characteristic.
-Challenge and hindrance demands demonstrated smaller relationships, but mostly negative.
-Challenges and resources within the same O*NET dimensions are strongly and positively related.
-These results provide support for H2, suggesting that there is overlap in how employees perceive job characteristics - particularly regarding what is perceived as a \emph{resource} being also perceived as a \emph{challenge}.
-Stated differently, job characteristics should not be uniquely categorized as resource or demand.
-
-The next group of hypotheses focuses on the relationship among resources and demands (challenge and hindrance) and outcomes.
-Table 2 shows the overall associations between resource/challenge/hindrances and outcomes of engagement, stress, and burnout.
-Here, we observe positive associations between resources, and challenges with engagement, and a negative association between hindrances and engagement.
-A positive association is observed between hindrances and stress.
+\subsubsection{Outcome Associations}\label{outcome-associations}
 
@@
 
-\caption{\label{tab:unnamed-chunk-1}Overall variable bivariate correlations.}
+\caption{\label{tab:unnamed-chunk-1}Outcome variable bivariate correlations.}
 
@@
 \end{table}
-
-\subsubsection{Challenges, Resources, and Outcomes}\label{challenges-resources-and-outcomes}
 
@@
 
+Table 2 presents empirical associations between estimates of resource, challenge, and hindrance and worker \emph{engagement}, \emph{stress}, and \emph{burnout}.
+Here, workers' perceptions were aggregated across all characteristics to provide indications of ``overall'' resource and demand experience.
+Engagement exhibited non-trivial associations with all three types of perception whereas stress was only associated with the hindrance aggregate.
+The more percieved hindrances, the higher the rating of stress, indicating only weak partial support for Hypothesis 3b.
+All subsequent analyses retain this ``overall'' operationalization of workers' experience of resources, challenges, and hindrances.
+
+\subsubsection{Challenges, Resources, and Job Outcomes}\label{challenges-resources-and-job-outcomes}
+
+Hypotheses 3a, 4a, and 4b were formally tested via targeted hierarchical regressions.
 H3a predicted that both resources and challenges would predict engagement.
-Table \ref{tab:chal-resource-table} summarizes the results for engagement (as well as stress and burnout).
-Sum scores for the predictors were used here such that the overall amount of resource or demand is recognized.
-First, challenges and resources explained a statistically significant amount of the variability in engagement, \(R^2\) = 0.15, Adj.
+Table \ref{tab:chal-resource-table} summarizes the results for the hypothesized engagement effect as well as the H4a investigations of both stress and burnout.
+As expected given the Table 2 bivariate associations, the combined effect of challenges and resources did explain a statistically significant amount of the variability in engagement, \(R^2\) = 0.15, Adj.
 \(R^2\) = 0.15, \(F(2, 565) = 50.09\), \(p < .001\).
-Here, the resource slope is significant, wheras the challenge slope is not significant (providing partial support for H3a).
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 35.62\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation (Hypothesis 4a).
-Figure \ref{fig:chal-resource-int} illustrates the interaction.
+However, the resource slope is significant, wheras the challenge slope is not significant.
+This results in only partial support for H3a.
+The inclusion of the interaction term in step two of the model was not hypothesized but is included for completeness.
+The interaction effect did contribute a significant addition to the model, \(F(3, 564) = 35.62\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 5.82, and thus provides some statistical support for the possibility of moderation.
+Figure \ref{fig:chal-resource-int} illustrates the nature of the interaction.
 With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low.
@@
 
-Next, challenge demands and resources did not explain a significant amount of the variance in stress, \(R^2\) = 0.01, Adj.
-\(R^2\) = 0, \(F(2, 565) = 1.67\), \(p = .189\), failing to provide support for Hypothesis 3b.
+Regarding Hypothesis 4a, challenge demands and resources did not explain a significant amount of the variance in stress, \(R^2\) = 0.01, Adj.
+\(R^2\) = 0, \(F(2, 565) = 1.67\), \(p = .189\).
 The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 1.17\), \(p = .320\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 0.17, and thus does not support the presence of moderation.
-
-Finally, challenge demands and resources explained a statistically significant amount of the variability in burnout, \(R^2\) = 0.04, Adj.
+These challenge demands and resources did, however, explain a statistically significant amount of the variability in burnout, \(R^2\) = 0.04, Adj.
 \(R^2\) = 0.04, \(F(2, 565) = 1.67\), \(p = .189\).
-The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 1.17\), \(p = .320\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 2.25, and thus failing to provide statistical support for the presence of moderation (Hypothesis 4a).
+The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 1.17\), \(p = .320\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 2.25, and thus collectively these analyses fail to provide statistical support for the presence of moderation (Hypothesis 4a).
 In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge demands and the outcomes of strain and burnout.
@@
 
-\subsubsection{Hindrances, Resources, and Outcomes}\label{hindrances-resources-and-outcomes}
+\subsubsection{Hindrances, Resources, and Job Outcomes}\label{hindrances-resources-and-job-outcomes}
 
 We also explored whether there was an interaction between hindrance demands and resources on the outcome variables.
-Sum scores for the predictors were used here again.
-First, hindrance demands and resources explained a statistically significant amount of the variability in engagement, \(R^2\) = 0.17, Adj.
-\(R^2\) = 0.16, \(F(2, 565) = 55.90\), \(p < .001\) {[}see Table \ref{tab:hind-resource-table}{]}.
-The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 37.25\), \(p < .001\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 0.13.
+First, hindrance demands and resources did explain a statistically significant amount of the variability in engagement, \(R^2\) = 0.17, Adj.
+\(R^2\) = 0.16, \(F(2, 565) = 55.90\), \(p < .001\) (see Table \ref{tab:hind-resource-table}).
+The inclusion of the interaction term in step two of the model (again not hypothesized but included for completeness) did not contribute a significant addition to the model, \(F(3, 564) = 37.25\), \(p < .001\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 0.13.
 An interaction between hindrances and resources was not found.
-
 Next exploring stress, hindrance demands and resources explained a statistically significant amount of the variability in stress, \(R^2\) = 0.01, Adj.
 \(R^2\) = 0.01, \(F(2, 565) = 3.13\), \(p = .045\).
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 6.89\), \(p < .001\), \(\Delta R^2\) = 0.03, \(\Delta F\) (1, 564) = 14.28, supporting the presence of a moderated effect.
-See Figure \ref{fig:hind-resource-stress-int}.
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 6.89\), \(p < .001\), \(\Delta R^2\) = 0.03, \(\Delta F\) (1, 564) = 14.28, supporting the presence of a moderated effect -- see Figure \ref{fig:hind-resource-stress-int}.
 As expected, the relationship between hindrance demands and strain becomes weaker as workers perceive more resources.
@@
 \(R^2\) = 0.03, \(F(2, 565) = 10.68\), \(p < .001\).
-The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 9.49\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 6.89, supporting the presence of a moderated effect (see Figure \ref{fig:hind-resource-burn-int}).
+The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 9.49\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 6.89, supporting the presence of a moderated effect (Figure \ref{fig:hind-resource-burn-int}).
 As expected, the relationship between hindrance demands and burnout becomes weaker as workers perceive more resources.
-Summatively these findings provide support for the assertion that resources would moderate the relationships between hindrance demands and the outcomes of strain and burnout.
+Summatively these findings provide support for the assertion that resources would moderate the relationships between hindrance demands and the unwanted outcomes of strain and burnout.
 
@@
 The major aims of this paper were to explore whether: 1) there was variability in subjective ratings of job characteristics as resources and demands, 2) some characteristics were more likely to vary across demand and resource, 3) subjective appraisals were differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and outcomes.
-We found that job characteristics were not uniquely categorized as a resource or demand, but rather, some job characteristics were rated highly as both a resource and a demand (particularly challenge demands).
-The findings broadly revealed that there was relatively more consistency in ratings of resource and challenge characteristics, and far more variability in job characteristics rated as hindrance demands.
-This finding lends additional evidence to Horan et al.
-(2020)'s conclusion that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3).
-While we did not find support for the prediction that different types of demands would be related to stress and burnout, we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships (as predicted).
+We found that job characteristics were not uniquely categorized as a resource or demand, but rather, job characteristics were often viewed similarly as both a resource and a challenging demand.
+The findings broadly revealed further that there was relatively more consistency in ratings of resource and challenge characteristics, and far more variability in hindering elements across workers and jobs.
+While engagement exhibits moderate associations with all investigated perceptions, we did not find support for the prediction that different types of demands would be related to stress and burnout, but we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships (as predicted).
 
-In addition to the above findings, this paper made several additional important contributions.
-We utilized a diverse sample of employees across industries who responded to common O*NET items.
-While O*NET provides detailed information about frequency and importance ratings among employees, we begin the process of expanding what we know of job characteristics to ratings of an extensive range of demands and resources.
-Further, we provide a repository for other researchers with listing of O*NET demands and resources across activity and context items for the benefit of all future researchers.
-We also explored not only context and activity holistically, but at a higher level aggregation, which enhances our knowledge of how employees perceive different categories of resources, challenges, and hindrances within different work dimensions, as well as the relationships among them.
+In addition to the above findings, this paper makes several additional important contributions.
+We utilized a diverse sample of employees across industries who responded to items derived from O*NET specifications.
+O*NET provides a rich and fairly exhaustive repository of job characteristics that also provides some consistency across investigations -- a somewhat ``standardized'' lens through which jobs can be deconstructed and investigations compared.
+We also explored characteristics at a higher level of aggregation (retaining O*NET category groupings), which again expands our collective knowledge of how employees perceive different categories of resources, challenges, and hindrances within different work domains, as well as the relationships among them.
 
-Hindrances exhibit greater variability, but a visual scan of the items reveals some with heavy physicality content (see, for example \ref{fig:combinegraphs2}), perhaps reflecting some artificiality (for example, indicating ``not terribly hindering'' if the physical demand was not commonplace).
-
-\subsection{Implications}\label{implications}
-
-The findings presented above have implications for both theory and practice.
-our findings support the related literature suggesting that perceptions of resources and demands, broadly, are not universal - there are individual differences in how employees experience the characteristics of their jobs (Webster et al., 2011).
-This finding aligns quite well with the challenge-hindrance stressor framework, which collectively argue that employees perceive stimuli (i.e., job characteristics) uniquely (Lazarus and Folkman, 1984), and thus, could appraise them as either a challenge or hindrance to their job performance (Cavanaugh et al., 2000).
+Perceptions of resources and demands, broadly, are not universal -- there are individual differences in how employees experience job characteristics.
+This finding aligns quite well with the challenge-hindrance stressor framework, which posits that employees perceive stimuli (i.e., job characteristics) uniquely (Lazarus and Folkman, 1984), and thus, could appraise them as either a challenge or hindrance to their job performance (Cavanaugh et al., 2000).
 Further, Cavanaugh et al.
@@
 Future studies may want to expand to explore these additional aspects of work.
+
+Hindrances exhibit greater variability, but a visual scan of the items reveals some with heavy physicality content (see, for example \ref{fig:combinegraphs2}), perhaps reflecting some artificiality (for example, indicating ``not terribly hindering'' if the physical demand was not commonplace).
 

### 2025-12-02 Submission.Rmd
Making minor edits

@@
 
-csl               : "sage-harvard.csl"
+csl               : "apa7.csl"
 documentclass     : "apa7" #interact
@@
 
-```{r demos}
+```{r demos, eval=FALSE}
 
@@
 attention$id <- 1:nrow(attention) #adds unique identifier to satisfy inane requirement of classify_occupation()
-
+R.version
 ISCO <- classify_occupation(attention, text_col = 'item400', isco_level = 1)

### 2025-12-06 Submission.Rmd
hudson dunn bros

@@
 abstract: |
-  Discussions of job characteristics often include a tacit characterization that these job elements are either resources or demands.
-The current study documents variability in ratings of O\*NET specifications with respect to subjective interpretation of job characteristics and predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes.
-We additionally explore the potential moderating role of resources on these relationships.
-Results support the perspective that job characteristics are not uniquely categorized as a resource or demand, but rather, what is viewed as challenging is also commonly be interpreted as resourceful.
-Furthermore, greater experienced resources moderate the challenge--engagement relationship as well as the hindrance-stress and hindrance--burnout relationships.
-These findings broadly support the non--mutually exclusive perspective on job characteristic appraisal as well as multiple theoretically--specified outcome associations.
-
+ **Purpose**: Discussions of job characteristics often include a tacit characterization that these job elements are either resources or demands.
+The purpose of this paper was to examine 1) variability in subjective ratings of job characteristics with respect to perception as resource and/or demand, 2) differential association with positive and negative outcomes, and 3) the potential buffering effect of resources on the relationships between demands and negative work outcomes.
+**Design/methodology/approach**: A sample of 568 respondents recruited from Prolific completed an online survey.
+They were asked to think only about their primary job, and each administered survey branched content dependent on whether this job could be described as consisting of the different O\*NET job characteristics.
+They subsequently rated level of resource, challenge, or hindrance.
+**Findings**: Results support the perspective that job characteristics are not uniquely categorized as a resource or demand, but rather, what is viewed as challenging is also commonly interpreted as resourceful.
+Furthermore, greater experienced resources moderate the challenge–engagement relationship as well as the hindrance-stress and hindrance–burnout relationships.
+**Originality/value**: We utilized a diverse sample of employees across industries who responded to items derived from O*NET specifications.
+O*NET provides a rich and fairly exhaustive repository of job characteristics that also provides some consistency across investigations.
+We also explored characteristics at a higher level of aggregation (retaining O*NET category groupings), which again expands our collective knowledge of how employees perceive different categories of resources, challenges, and hindrances within different work domains, as well as the relationships among them.
 keywords         : "O*NET, challenge-hindrance framework, job demands-resources, job characteristics"
@@
 
-```{r demos, eval=FALSE}
+```{r demos}
 

### 2025-12-06 Submission.tex
hudson dunn bros

@@
 {}{\PatchFailed}
-\makeatother
 \keywords{O*NET, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: 4,942}
@@
 \abstract{%
-Discussions of job characteristics often include a tacit characterization that these job elements are either resources or demands.
-The current study documents variability in ratings of O*NET specifications with respect to subjective interpretation of job characteristics and predicts the form of demand (challenge or hindrance) will exhibit differential association with work--related outcomes.
-We additionally explore the potential moderating role of resources on these relationships.
-Results support the perspective that job characteristics are not uniquely categorized as a resource or demand, but rather, what is viewed as challenging is also commonly be interpreted as resourceful.
+\textbf{Purpose}: Discussions of job characteristics often include a tacit characterization that these job elements are either resources or demands.
+The purpose of this paper was to examine 1) variability in subjective ratings of job characteristics with respect to perception as resource and/or demand, 2) differential association with positive and negative outcomes, and 3) the potential buffering effect of resources on the relationships between demands and negative work outcomes.
+\textbf{Design/methodology/approach}: A sample of 568 respondents recruited from Prolific completed an online survey.
+They were asked to think only about their primary job, and each administered survey branched content dependent on whether this job could be described as consisting of the different O*NET job characteristics.
+They subsequently rated level of resource, challenge, or hindrance.
+\textbf{Findings}: Results support the perspective that job characteristics are not uniquely categorized as a resource or demand, but rather, what is viewed as challenging is also commonly interpreted as resourceful.
 Furthermore, greater experienced resources moderate the challenge--engagement relationship as well as the hindrance-stress and hindrance--burnout relationships.
-These findings broadly support the non--mutually exclusive perspective on job characteristic appraisal as well as multiple theoretically--specified outcome associations.
+\textbf{Originality/value}: We utilized a diverse sample of employees across industries who responded to items derived from O\emph{NET specifications.
+O}NET provides a rich and fairly exhaustive repository of job characteristics that also provides some consistency across investigations.
+We also explored characteristics at a higher level of aggregation (retaining O*NET category groupings), which again expands our collective knowledge of how employees perceive different categories of resources, challenges, and hindrances within different work domains, as well as the relationships among them.
 }
@@
 
-\subsection{Theoretical Foundations}\label{theoretical-foundations}
+\hypertarget{theoretical-foundations}{%
+\subsection{Theoretical Foundations}\label{theoretical-foundations}}
 
 Job demands-resources theory (e.g., Bakker \& Demerouti, 2014; 2017) highlights the importance of demands and resources on the employee experience of motivation and strain as well as other, less proximal outcomes.
-Resources include physical, psychological, social, or organizational aspects of jobs that help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker and Demerouti, 2014, 2017).
+Resources include physical, psychological, social, or organizational aspects of jobs that help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017).
 In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (high work pressure, for example, is commonly cited as a demand, e.g., Demerouti et al., 2001).
@@
 These demands should lead to coping strategies that facilitate achievement.
-Work characteristics consistent with this definition, for example, include time pressure and responsibility (LePine, 2022).
+Work characteristics consistent with this definition, for example, include time pressure and responsibility (M.
+A.
+LePine, 2022).
 Hindrance demands, in contrast, inhibit growth, learning, and the general achievement of goals.
-Example hindrance demands that have been previously noted include role conflict and role ambiguity (LePine, 2022).
+Example hindrance demands that have been previously noted include role conflict and role ambiguity (M.
+A.
+LePine, 2022).
 
+M.
+A.
 LePine (2022) deconstructs the mechanisms by which demands are related to performance and wellbeing outcomes.
@@
 Disengagement is likely to result from a hindrance appraisal, which then negatively impacts motivation, performance, growth and wellbeing.
-This happens because resources are depleted via frustrations and other negative affect--laden reactions (LePine, 2022).
+This happens because resources are depleted via frustrations and other negative affect--laden reactions (M.
+A.
+LePine, 2022).
 
-Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, LePine et al.
+Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, J.
+A.
+LePine et al.
 (2005) regarding performance and Crawford et al.
@@
 Pindek et al.
-(2024) meta-analyzed diary studies of dynamic demands (i.e., short-term daily experiences of demands) and concluded that daily challenge demands had a positive \emph{direct} association with performance, but a negative \emph{indirect} association with performance through strain (as described by LePine (2022) above).
+(2024) meta-analyzed diary studies of dynamic demands (i.e., short-term daily experiences of demands) and concluded that daily challenge demands had a positive \emph{direct} association with performance, but a negative \emph{indirect} association with performance through strain (as described by M.
+A.
+LePine (2022) above).
 As expected, hindrance demands had both direct and indirect (through strain) associations with performance (Pindek et al., 2024).
@@
 (2020).
-In fact, although much of our research on job demands is based on such exclusive classifications (Searle and Auton, 2015), the most recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., two different employees could most certainly perceive ``daily interaction with co-workers'' as a resource or as a demand).
+In fact, although much of our research on job demands is based on such exclusive classifications (Searle \& Auton, 2015), the most recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., two different employees could most certainly perceive ``daily interaction with co-workers'' as a resource or as a demand).
 
 Aligned with this relativistic perspective on the experience of work, Horan et al.
-(2020) and LePine (2022) explicitly articulate the need for future research to incorporate the \emph{appraisal process} into the challenge-hindrance stressor framework.
+(2020) and M.
+A.
+LePine (2022) explicitly articulate the need for future research to incorporate the \emph{appraisal process} into the challenge-hindrance stressor framework.
 In fact, Horan et al.
@@
 Given the above, the first question we pose is whether workers exclusively experience job elements as resources, challenges, or hindrances, or whether a given job characteristic might be mutually considered as more than one of these (e.g., both a challenge and a resource).
-Evidence suggests that employees do, at least, differentiate between challenge and hindrance demands (e.g., Bakker and Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011).
+Evidence suggests that employees do, at least, differentiate between challenge and hindrance demands (e.g., Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011).
 For example, Bakker and Sanz-Vergel (2013) found that work pressure was perceived as a hindrance, and emotional demands as more of a challenge.
@@
 
-\subsection{Connecting Appraisals to Workplace Outcomes}\label{connecting-appraisals-to-workplace-outcomes}
+\hypertarget{connecting-appraisals-to-workplace-outcomes}{%
+\subsection{Connecting Appraisals to Workplace Outcomes}\label{connecting-appraisals-to-workplace-outcomes}}
 
-Both the job demands--resources model (Bakker and Demerouti, 2017) as well as the challenge--hindrance stressor framework (Cavanaugh et al., 2000) have been useful in the prediction of a wide variety of organizational outcomes including job satisfaction, motivation, commitment, and performance (e.g., LePine et al., 2005).
+Both the job demands--resources model (Bakker \& Demerouti, 2017) as well as the challenge--hindrance stressor framework (Cavanaugh et al., 2000) have been useful in the prediction of a wide variety of organizational outcomes including job satisfaction, motivation, commitment, and performance (e.g., J.
+A.
+LePine et al., 2005).
 Empirical work generally suggests that \emph{resources} are commonly associated with positive outcomes, including, most relevant for the current investigation, employee engagement.
@@
 The findings regarding demands are more complex.
-When a demand is appraised as a hindrance, it is negatively associated with motivational resources (Kim and Beehr, 2020), engagement (Crawford et al., 2010), job search behaviors, and job satisfaction (Cavanaugh et al., 2000).
+When a demand is appraised as a hindrance, it is negatively associated with motivational resources (Kim \& Beehr, 2020), engagement (Crawford et al., 2010), job search behaviors, and job satisfaction (Cavanaugh et al., 2000).
 Chen et al.
@@
 Challenge appraisals have also been found to ehave negative associations with job search behaviors (e.g., Cavanaugh et al., 2000).
-Interestingly, both challenges and hindrances have been shown to positively predict strain (Abbas and Raja, 2019; LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010), which further highlights the complex association between characteristic appraisals and important work outcomes.
+Interestingly, both challenges and hindrances have been shown to positively predict strain (Abbas \& Raja, 2019; J.
+A.
+LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010), which further highlights the complex association between characteristic appraisals and important work outcomes.
 Given the differential relationships described above, and a focus on three outcomes (engagement, strain, and burnout) we make the following predictions (see Figure \ref{fig:ourmodel}):
@@
 
-\section{Method}\label{method}
+\begin{verbatim}
+##                _                                
+## platform       x86_64-w64-mingw32               
+## arch           x86_64                           
+## os             mingw32                          
+## crt            ucrt                             
+## system         x86_64, mingw32                  
+## status                                          
+## major          4                                
+## minor          3.1                              
+## year           2023                             
+## month          06                               
+## day            16                               
+## svn rev        84548                            
+## language       R                                
+## version.string R version 4.3.1 (2023-06-16 ucrt)
+## nickname       Beagle Scouts
+\end{verbatim}
 
-\subsection{Participants}\label{participants}
+\hypertarget{method}{%
+\section{Method}\label{method}}
+
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
 
@@
 
-\subsection{Materials}\label{materials}
+\hypertarget{materials}{%
+\subsection{Materials}\label{materials}}
 
-\subsubsection{Characteristics, Challenge Demands, Hindrance Demands, and Resources}\label{characteristics-challenge-demands-hindrance-demands-and-resources}
+\hypertarget{characteristics-challenge-demands-hindrance-demands-and-resources}{%
+\subsubsection{Characteristics, Challenge Demands, Hindrance Demands, and Resources}\label{characteristics-challenge-demands-hindrance-demands-and-resources}}
 
@@
 
-\subsubsection{Stress}\label{stress}
+\hypertarget{stress}{%
+\subsubsection{Stress}\label{stress}}
 
@@
 
-\subsubsection{Burnout}\label{burnout}
+\hypertarget{burnout}{%
+\subsubsection{Burnout}\label{burnout}}
 
@@
 
-\subsubsection{Engagement}\label{engagement}
+\hypertarget{engagement}{%
+\subsubsection{Engagement}\label{engagement}}
 
@@
 
-\section{Results}\label{results}
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
-Of the 785 individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes and Wilhelm, 2021).
+Of the 785 individuals who initially accessed the survey link, 112 indicated that they were not interested, had more than 200 missing responses, or had 20 or more identical consecutive sequential responses (Yentes \& Wilhelm, 2021).
 Applying a further screen regarding attention checks (there were four attention checks embedded throughout, asking respondents to indicate a specific answer) resulted in the retention of 568 respondents who constitute the current sample.
@@
 
-\subsubsection{Outcome Associations}\label{outcome-associations}
+\hypertarget{outcome-associations}{%
+\subsubsection{Outcome Associations}\label{outcome-associations}}
 
@@
 
-\subsubsection{Challenges, Resources, and Job Outcomes}\label{challenges-resources-and-job-outcomes}
+\hypertarget{challenges-resources-and-job-outcomes}{%
+\subsubsection{Challenges, Resources, and Job Outcomes}\label{challenges-resources-and-job-outcomes}}
 
@@
 
-\subsubsection{Hindrances, Resources, and Job Outcomes}\label{hindrances-resources-and-job-outcomes}
+\hypertarget{hindrances-resources-and-job-outcomes}{%
+\subsubsection{Hindrances, Resources, and Job Outcomes}\label{hindrances-resources-and-job-outcomes}}
 
@@
 Perceptions of resources and demands, broadly, are not universal -- there are individual differences in how employees experience job characteristics.
-This finding aligns quite well with the challenge-hindrance stressor framework, which posits that employees perceive stimuli (i.e., job characteristics) uniquely (Lazarus and Folkman, 1984), and thus, could appraise them as either a challenge or hindrance to their job performance (Cavanaugh et al., 2000).
+This finding aligns quite well with the challenge-hindrance stressor framework, which posits that employees perceive stimuli (i.e., job characteristics) uniquely (Lazarus \& Folkman, 1984), and thus, could appraise them as either a challenge or hindrance to their job performance (Cavanaugh et al., 2000).
 Further, Cavanaugh et al.
@@
 Such conversations could happen during an annual performance review.
-In addition, LePine et al.
+In addition, J.
+A.
+LePine et al.
 (2005) and Podsakoff et al.
@@
 
-\phantomsection\label{refs}
-\begin{CSLReferences}{1}{1}
-\bibitem[\citeproctext]{ref-abbas2019challenge}
-Abbas M and Raja U (2019) Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology} 34(2). Springer: 189--201.
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-abbas2019challenge}{}}%
+Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.
 
-\bibitem[\citeproctext]{ref-bakker2014job}
-Bakker AB and Demerouti E (2014) Job demands--resources theory. \emph{Wellbeing: A complete reference guide}. John Wiley \& Sons, Ltd Chichester, UK: 1--28.
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
+Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.
 
-\bibitem[\citeproctext]{ref-bakker2017job}
-Bakker AB and Demerouti E (2017) Job demands--resources theory: Taking stock and looking forward. \emph{Journal of occupational health psychology} 22(3). Educational Publishing Foundation: 273.
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
+Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.
 
-\bibitem[\citeproctext]{ref-bakker2013weekly}
-Bakker AB and Sanz-Vergel AI (2013) Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior} 83(3). Elsevier: 397--409.
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2005job}{}}%
+Bakker, A. B., Demerouti, E., \& Euwema, M. C. (2005). Job resources buffer the impact of job demands on burnout. \emph{Journal of Occupational Health Psychology}, \emph{10}(2), 170.
 
-\bibitem[\citeproctext]{ref-bakker2005job}
-Bakker AB, Demerouti E and Euwema MC (2005) Job resources buffer the impact of job demands on burnout. \emph{Journal of occupational health psychology} 10(2). Educational Publishing Foundation: 170.
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2007job}{}}%
+Bakker, A.
+B., Hakanen, J.
+J., Demerouti, E., \& Xanthopoulou, D.
+(2007).
+Job resources boost work engagement, particularly when job demands are high.
+\emph{Journal of Educational Psychology}, \emph{99}(2), 274.
 
-\bibitem[\citeproctext]{ref-bakker2007job}
-Bakker AB, Hakanen JJ, Demerouti E, et al.
-(2007) Job resources boost work engagement, particularly when job demands are high.
-\emph{Journal of educational psychology} 99(2).
-American Psychological Association: 274.
+\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
+Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
 
-\bibitem[\citeproctext]{ref-burr2019third}
-Burr H, Berthelsen H, Moncada S, et al. (2019) The third version of the copenhagen psychosocial questionnaire. \emph{Safety and health at work} 10(4). Elsevier: 482--503.
+\leavevmode\vadjust pre{\hypertarget{ref-burr2019third}{}}%
+Burr, H., Berthelsen, H., Moncada, S., Nübling, M., Dupret, E., Demiral, Y., Oudyk, J., Kristensen, T.
+S., Llorens, C., Navarro, A., et al.
+(2019).
+The third version of the copenhagen psychosocial questionnaire.
+\emph{Safety and Health at Work}, \emph{10}(4), 482--503.
 
-\bibitem[\citeproctext]{ref-campbell1959convergent}
-Campbell DT and Fiske DW (1959) Convergent and discriminant validation by the multitrait-multimethod matrix. \emph{Psychological bulletin} 56(2). American Psychological Association: 81--105.
+\leavevmode\vadjust pre{\hypertarget{ref-campbell1959convergent}{}}%
+Campbell, D. T., \& Fiske, D. W. (1959). Convergent and discriminant validation by the multitrait-multimethod matrix. \emph{Psychological Bulletin}, \emph{56}(2), 81--105.
 
-\bibitem[\citeproctext]{ref-cavanaugh2000empirical}
-Cavanaugh MA, Boswell WR, Roehling MV, et al.
-(2000) An empirical examination of self-reported work stress among US managers.
-\emph{Journal of applied psychology} 85(1).
-American Psychological Association: 65.
+\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
+Cavanaugh, M.
+A., Boswell, W.
+R., Roehling, M.
+V., \& Boudreau, J.
+W.
+(2000).
+An empirical examination of self-reported work stress among US managers.
+\emph{Journal of Applied Psychology}, \emph{85}(1), 65.
 
-\bibitem[\citeproctext]{ref-chen2021daily}
-Chen H, Wang H, Yuan M, et al. (2021) Daily challenge/hindrance demands and cognitive wellbeing: A multilevel moderated mediation model. \emph{Frontiers in Psychology} 12. Frontiers Media SA: 616002.
+\leavevmode\vadjust pre{\hypertarget{ref-chen2021daily}{}}%
+Chen, H., Wang, H., Yuan, M., \& Xu, S. (2021). Daily challenge/hindrance demands and cognitive wellbeing: A multilevel moderated mediation model. \emph{Frontiers in Psychology}, \emph{12}, 616002.
 
-\bibitem[\citeproctext]{ref-crawford2010linking}
-Crawford ER, LePine JA and Rich BL (2010) Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test.
-\emph{Journal of applied psychology} 95(5).
-American Psychological Association: 834.
+\leavevmode\vadjust pre{\hypertarget{ref-crawford2010linking}{}}%
+Crawford, E.
+R., LePine, J.
+A., \& Rich, B.
+L.
+(2010).
+Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test.
+\emph{Journal of Applied Psychology}, \emph{95}(5), 834.
 
-\bibitem[\citeproctext]{ref-cronbach1951coefficient}
-Cronbach LJ (1951) Coefficient alpha and the internal structure of tests. \emph{psychometrika} 16(3). Springer-Verlag: 297--334.
+\leavevmode\vadjust pre{\hypertarget{ref-cronbach1951coefficient}{}}%
+Cronbach, L. J. (1951). Coefficient alpha and the internal structure of tests. \emph{Psychometrika}, \emph{16}(3), 297--334.
 
-\bibitem[\citeproctext]{ref-demerouti2001job}
-Demerouti E, Bakker AB, Nachreiner F, et al. (2001) The job demands-resources model of burnout. \emph{Journal of Applied psychology} 86(3). American Psychological Association: 499.
+\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
+Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
 
-\bibitem[\citeproctext]{ref-gerich2017relevance}
-Gerich J (2017) The relevance of challenge and hindrance appraisals of working conditions for employees' health.
-\emph{International Journal of Stress Management} 24(3).
-Educational Publishing Foundation: 270.
+\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
+Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
 
-\bibitem[\citeproctext]{ref-hakanen2008job}
-Hakanen JJ, Schaufeli WB and Ahola K (2008) The job demands-resources model: A three-year cross-lagged study of burnout, depression, commitment, and work engagement.
-\emph{Work \& stress} 22(3).
-Taylor \& Francis: 224--241.
+\leavevmode\vadjust pre{\hypertarget{ref-hakanen2008job}{}}%
+Hakanen, J.
+J., Schaufeli, W.
+B., \& Ahola, K.
+(2008).
+The job demands-resources model: A three-year cross-lagged study of burnout, depression, commitment, and work engagement.
+\emph{Work \& Stress}, \emph{22}(3), 224--241.
 
-\bibitem[\citeproctext]{ref-horan2020review}
-Horan KA, Nakahara WH, DiStaso MJ, et al.
-(2020) A review of the challenge-hindrance stress model: Recent advances, expanded paradigms, and recommendations for future research.
-\emph{Frontiers in Psychology} 11.
-Frontiers Media SA: 560346.
+\leavevmode\vadjust pre{\hypertarget{ref-horan2020review}{}}%
+Horan, K.
+A., Nakahara, W.
+H., DiStaso, M.
+J., \& Jex, S.
+M.
+(2020).
+A review of the challenge-hindrance stress model: Recent advances, expanded paradigms, and recommendations for future research.
+\emph{Frontiers in Psychology}, \emph{11}, 560346.
 
-\bibitem[\citeproctext]{ref-kim2020thriving}
-Kim M and Beehr TA (2020) Thriving on demand: Challenging work results in employee flourishing through appraisals and resources.
-\emph{International Journal of Stress Management} 27(2).
-Educational Publishing Foundation: 111.
+\leavevmode\vadjust pre{\hypertarget{ref-kim2020thriving}{}}%
+Kim, M., \& Beehr, T.
+A.
+(2020).
+Thriving on demand: Challenging work results in employee flourishing through appraisals and resources.
+\emph{International Journal of Stress Management}, \emph{27}(2), 111.
 
-\bibitem[\citeproctext]{ref-kubicek2023all}
-Kubicek B, Uhlig L, Hülsheger UR, et al.
-(2023) Are all challenge stressors beneficial for learning?
+\leavevmode\vadjust pre{\hypertarget{ref-kubicek2023all}{}}%
+Kubicek, B., Uhlig, L., Hülsheger, U.
+R., Korunka, C., \& Prem, R.
+(2023).
+Are all challenge stressors beneficial for learning?
 A meta-analytical assessment of differential effects of workload and cognitive demands.
-\emph{Work \& Stress} 37(3).
-Taylor \& Francis: 269--298.
+\emph{Work \& Stress}, \emph{37}(3), 269--298.
 
-\bibitem[\citeproctext]{ref-lazarus1984stress}
-Lazarus RS and Folkman S (1984) \emph{Stress, Appraisal, and Coping}. Springer publishing company.
+\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
+Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.
 
-\bibitem[\citeproctext]{ref-lepine2005meta}
-LePine JA, Podsakoff NP and LePine MA (2005) A meta-analytic test of the challenge stressor--hindrance stressor framework: An explanation for inconsistent relationships among stressors and performance.
-\emph{Academy of management journal} 48(5).
-Academy of Management Briarcliff Manor, NY 10510: 764--775.
+\leavevmode\vadjust pre{\hypertarget{ref-lepine2005meta}{}}%
+LePine, J.
+A., Podsakoff, N.
+P., \& LePine, M.
+A.
+(2005).
+A meta-analytic test of the challenge stressor--hindrance stressor framework: An explanation for inconsistent relationships among stressors and performance.
+\emph{Academy of Management Journal}, \emph{48}(5), 764--775.
 
-\bibitem[\citeproctext]{ref-lepine2022challenge}
-LePine MA (2022) The challenge-hindrance stressor framework: An integrative conceptual review and path forward.
-\emph{Group \& Organization Management} 47(2).
-SAGE Publications Sage CA: Los Angeles, CA: 223--254.
+\leavevmode\vadjust pre{\hypertarget{ref-lepine2022challenge}{}}%
+LePine, M. A. (2022). The challenge-hindrance stressor framework: An integrative conceptual review and path forward. \emph{Group \& Organization Management}, \emph{47}(2), 223--254.
 
-\bibitem[\citeproctext]{ref-peterson2001understanding}
-Peterson NG, Mumford MD, Borman WC, et al.
-(2001) Understanding work using the occupational information network (o* NET): Implications for practice and research.
-\emph{Personnel psychology} 54(2).
-Wiley Online Library: 451--492.
+\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
+Peterson, N.
+G., Mumford, M.
+D., Borman, W.
+C., Jeanneret, P.
+R., Fleishman, E.
+A., Levin, K.
+Y., Campion, M.
+A., Mayfield, M.
+S., Morgeson, F.
+P., Pearlman, K., et al.
+(2001).
+Understanding work using the occupational information network (o* NET): Implications for practice and research.
+\emph{Personnel Psychology}, \emph{54}(2), 451--492.
 
-\bibitem[\citeproctext]{ref-pindek2024dynamic}
-Pindek S, Meyer K, Valvo A, et al.
-(2024) A dynamic view of the challenge-hindrance stressor framework: A meta-analysis of daily diary studies.
-\emph{Journal of Business and Psychology}.
-Springer: 1--19.
+\leavevmode\vadjust pre{\hypertarget{ref-pindek2024dynamic}{}}%
+Pindek, S., Meyer, K., Valvo, A., \& Arvan, M.
+(2024).
+A dynamic view of the challenge-hindrance stressor framework: A meta-analysis of daily diary studies.
+\emph{Journal of Business and Psychology}, 1--19.
 
-\bibitem[\citeproctext]{ref-podsakoff2007differential}
-Podsakoff NP, LePine JA and LePine MA (2007) Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis.
-\emph{Journal of applied psychology} 92(2).
-American Psychological Association: 438.
+\leavevmode\vadjust pre{\hypertarget{ref-podsakoff2007differential}{}}%
+Podsakoff, N.
+P., LePine, J.
+A., \& LePine, M.
+A.
+(2007).
+Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis.
+\emph{Journal of Applied Psychology}, \emph{92}(2), 438.
 
-\bibitem[\citeproctext]{ref-rosen2020challenges}
-Rosen CC, Dimotakis N, Cole MS, et al.
-(2020) When challenges hinder: An investigation of when and how challenge stressors impact employee outcomes.
-\emph{Journal of Applied Psychology} 105(10).
-American Psychological Association: 1181.
+\leavevmode\vadjust pre{\hypertarget{ref-rosen2020challenges}{}}%
+Rosen, C.
+C., Dimotakis, N., Cole, M.
+S., Taylor, S.
+G., Simon, L.
+S., Smith, T.
+A., \& Reina, C.
+S.
+(2020).
+When challenges hinder: An investigation of when and how challenge stressors impact employee outcomes.
+\emph{Journal of Applied Psychology}, \emph{105}(10), 1181.
 
-\bibitem[\citeproctext]{ref-schaufeli2017applying}
-Schaufeli WB (2017) Applying the job demands-resources model: A `how to'guide to measuring and tackling work engagement and burnout. \emph{Organizational dynamics} 46(2). Elsevier: 120--132.
+\leavevmode\vadjust pre{\hypertarget{ref-schaufeli2017applying}{}}%
+Schaufeli, W. B. (2017). Applying the job demands-resources model: A `how to'guide to measuring and tackling work engagement and burnout. \emph{Organizational Dynamics}, \emph{46}(2), 120--132.
 
-\bibitem[\citeproctext]{ref-searle2015merits}
-Searle BJ and Auton JC (2015) The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping} 28(2). Taylor \& Francis: 121--143.
+\leavevmode\vadjust pre{\hypertarget{ref-searle2015merits}{}}%
+Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.
 
-\bibitem[\citeproctext]{ref-webster2010toward}
-Webster JR, Beehr TA and Christiansen ND (2010) Toward a better understanding of the effects of hindrance and challenge stressors on work behavior.
-\emph{Journal of Vocational Behavior} 76(1).
-Elsevier: 68--77.
+\leavevmode\vadjust pre{\hypertarget{ref-webster2010toward}{}}%
+Webster, J.
+R., Beehr, T.
+A., \& Christiansen, N.
+D.
+(2010).
+Toward a better understanding of the effects of hindrance and challenge stressors on work behavior.
+\emph{Journal of Vocational Behavior}, \emph{76}(1), 68--77.
 
-\bibitem[\citeproctext]{ref-webster2011extending}
-Webster JR, Beehr TA and Love K (2011) Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior} 79(2). Elsevier: 505--516.
+\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
+Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.
 
-\bibitem[\citeproctext]{ref-xanthopoulou2007job}
-Xanthopoulou D, Bakker AB, Dollard MF, et al.
-(2007) When do job demands particularly predict burnout?
+\leavevmode\vadjust pre{\hypertarget{ref-xanthopoulou2007job}{}}%
+Xanthopoulou, D., Bakker, A.
+B., Dollard, M.
+F., Demerouti, E., Schaufeli, W.
+B., Taris, T.
+W., \& Schreurs, P.
+J.
+(2007).
+When do job demands particularly predict burnout?
 The moderating role of job resources.
-\emph{Journal of managerial psychology} 22(8).
-Emerald Group Publishing Limited: 766--786.
+\emph{Journal of Managerial Psychology}, \emph{22}(8), 766--786.
 
-\bibitem[\citeproctext]{ref-R-careless}
-Yentes RD and Wilhelm F (2021) \emph{Careless: Procedures for Computing Indices of Careless Responding}.
+\leavevmode\vadjust pre{\hypertarget{ref-R-careless}{}}%
+Yentes, R. D., \& Wilhelm, F. (2021). \emph{Careless: Procedures for computing indices of careless responding}.
 

### 2025-12-06 Submission.Rmd
word count and masked

@@
 keywords         : "O*NET, challenge-hindrance framework, job demands-resources, job characteristics"
-wordcount        : "4,942"
+#wordcount        : "4,942"
 

### 2025-12-06 Submission.tex
word count and masked

@@
 \documentclass[
-  man]{apa7}
+  man,mask]{apa7}
 \usepackage{amsmath,amssymb}
@@
 {}{\PatchFailed}
-\keywords{O*NET, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: 4,942}
+\keywords{O*NET, challenge-hindrance framework, job demands-resources, job characteristics}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
   pdftitle={Shared Characterizations of Challenging Demands and Job Resources across O*NET Element Classifications},
-  pdfauthor={Alicia Stachowski2, John Kulas1, \& Renata García Prieto Palacios Roji3},
   pdflang={en-EN},

### 2025-12-06 Submission.Rmd
r.version output removed

@@
 attention$id <- 1:nrow(attention) #adds unique identifier to satisfy inane requirement of classify_occupation()
-R.version
+
 ISCO <- classify_occupation(attention, text_col = 'item400', isco_level = 1)

### 2025-12-09 Submission.Rmd
final edits

--- 2025-12-06 Submission.Rmd
@@
 linenumbers       : no
-mask              : yes
+mask              : no
 draft             : no
@@
 We build on a growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges].
-Our primary aims explore: 1) variability in subjective ratings of job characteristics with respect to perception as resource and/or demand, 2) differential association (of subjective appraisals) with positive and negative outcomes, and 3) the buffering effect of resources on the relationships between demands and negative work outcomes^[Took out previous #2 -- make sure this isn't revisited in Results or Discussion].
+Our primary aims explore: 1) variability in subjective ratings of job characteristics with respect to perception as resource and/or demand, 2) differential association (of subjective appraisals) with positive and negative outcomes, and 3) the buffering effect of resources on the relationships between demands and negative work outcomes.
 We investigate these associations via the lens of [O\*NET job specifications](https://www.onetcenter.org/content.html), which provide a near--exhaustive listing of generalizable characteristic specifications.
@@
 Similarly, @xanthopoulou2007job also found some support for this interaction (high demands + low resources leads to greater burnout) among home healthcare employees.
-They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout.
+They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttressed the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout.
 We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows (see Figure \@ref(fig:ourmodel)):
@@
 Engagement exhibited non-trivial associations with all three types of perception whereas stress was only associated with the hindrance aggregate.
-The more percieved hindrances, the higher the rating of stress, indicating only weak partial support for Hypothesis 3b.
+The more percieved hindrances, the higher the rating of stress ($r$=.11, $p$<.01), indicating only weak partial support for Hypothesis 3b.
 All subsequent analyses retain this "overall" operationalization of workers' experience of resources, challenges, and hindrances.
@@
 Regarding Hypothesis 4a, challenge demands and resources did not explain a significant amount of the variance in stress,  $R^2$ = `r round(summary(cr_stress_m2)$r.squared, 2)`, Adj.
-$R^2$ =  `r round(summary(cr_stress_m2)$adj.r.squared, 2)`, `r cr_stress_info2$statistic$modelfit$r2`.
+$R^2$ =  0.00, `r cr_stress_info2$statistic$modelfit$r2`.
 The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, `r cr_stress_info3$statistic$modelfit$r2`, $\Delta R^2$ = `r cr_stress_r_square_change`, $\Delta F$ (`r cr_stress_anova$Df[2]`, `r cr_stress_anova$Res.Df[2]`) = `r cr_stress_anova$F[2]`, and thus does not support the presence of moderation.
@@
 
-The major aims of this paper were to explore whether: 1) there was variability in subjective ratings of job characteristics as resources and demands, 2) some characteristics were more likely to vary across demand and resource, 3) subjective appraisals were differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and outcomes.
+The major aims of this paper were to explore whether: 1) there was variability in subjective ratings of job characteristics as resources and demands, 2) subjective appraisals were differentially related to positive and negative outcomes, and lastly, 3) if resources buffer the relationships between demands (challenge and hindrance) and outcomes.
 We found that job characteristics were not uniquely categorized as a resource or demand, but rather, job characteristics were often viewed similarly as both a resource and a challenging demand.
@@
 Related to that, we intentionally worked within the O\*NET database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources and demands.
-Therefore, to the extent that O\*NET is not an exhaustive repository, there are existing characteristics that we did not capture.
-For example, O\*NET also includes styles and values, which we did not sample.
-Future studies may want to expand to explore these additional aspects of work.
-
-Hindrances exhibit greater variability, but a visual scan of the items reveals some with heavy physicality content (see, for example \@ref(fig:combinegraphs2)), perhaps reflecting some artificiality (for example, indicating "not terribly hindering" if the physical demand was not commonplace).
+Therefore, to the extent that O\*NET is not an exhaustive repository, there are existing characteristics that were not captured.
+Future studies may want to expand to explore additional aspects of work.
+
+Hindrances exhibit greater variability, but a visual scan of the items reveals some with heavy physicality content (see, for example Figure \@ref(fig:combinegraphs2)), perhaps reflecting some artificiality (for example, indicating "not terribly hindering" if the physical demand was not commonplace).
 
@@
 Given the high associations observed between ratings of resource and challenge, it is possible that respondents did not distinguish between these definitions as cleanly as we intended.
-Future investigations may wish to explore the colloquial versus academic phrasing of these questions and how that may impact observed associations between resources and challenges.
+Future investigations may wish to explore the colloquial versus academic phrasing of characteristics and how that may impact observed associations between resources and challenges.
 We also note that effect sizes were small and thus it is important to consider the practical significance when thinking about potential interventions.
@@
 ```
-
+\newpage
 # References

### 2025-12-09 Submission.tex
r.version output removed
final edits

--- 2025-12-06 Submission.tex
@@
 {}{\PatchFailed}
-\keywords{O*NET, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: 4,942}
+\makeatother
+\keywords{O*NET, challenge-hindrance framework, job demands-resources, job characteristics}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 We build on a growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020).
-Our primary aims explore: 1) variability in subjective ratings of job characteristics with respect to perception as resource and/or demand, 2) differential association (of subjective appraisals) with positive and negative outcomes, and 3) the buffering effect of resources on the relationships between demands and negative work outcomes\footnote{Took out previous \#2 -- make sure this isn't revisited in Results or Discussion}.
+Our primary aims explore: 1) variability in subjective ratings of job characteristics with respect to perception as resource and/or demand, 2) differential association (of subjective appraisals) with positive and negative outcomes, and 3) the buffering effect of resources on the relationships between demands and negative work outcomes.
 We investigate these associations via the lens of \href{https://www.onetcenter.org/content.html}{O*NET job specifications}, which provide a near--exhaustive listing of generalizable characteristic specifications.
 
-\hypertarget{theoretical-foundations}{%
-\subsection{Theoretical Foundations}\label{theoretical-foundations}}
+\subsection{Theoretical Foundations}\label{theoretical-foundations}
 
@@
 (2007) also found some support for this interaction (high demands + low resources leads to greater burnout) among home healthcare employees.
-They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout.
+They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttressed the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout.
 We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows (see Figure \ref{fig:ourmodel}):
@@
 ## major          4                                
-## minor          3.1                              
-## year           2023                             
-## month          06                               
-## day            16                               
-## svn rev        84548                            
+## minor          5.0                              
+## year           2025                             
+## month          04                               
+## day            11                               
+## svn rev        88135                            
 ## language       R                                
-## version.string R version 4.3.1 (2023-06-16 ucrt)
-## nickname       Beagle Scouts
+## version.string R version 4.5.0 (2025-04-11 ucrt)
+## nickname       How About a Twenty-Six
 \end{verbatim}
 
-\hypertarget{method}{%
-\section{Method}\label{method}}
+\section{Method}\label{method}
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+\subsection{Participants}\label{participants}
 
@@
 
-\hypertarget{materials}{%
-\subsection{Materials}\label{materials}}
+\subsection{Materials}\label{materials}
 
-\hypertarget{characteristics-challenge-demands-hindrance-demands-and-resources}{%
-\subsubsection{Characteristics, Challenge Demands, Hindrance Demands, and Resources}\label{characteristics-challenge-demands-hindrance-demands-and-resources}}
+\subsubsection{Characteristics, Challenge Demands, Hindrance Demands, and Resources}\label{characteristics-challenge-demands-hindrance-demands-and-resources}
 
@@
 
-\hypertarget{stress}{%
-\subsubsection{Stress}\label{stress}}
+\subsubsection{Stress}\label{stress}
 
@@
 
-\hypertarget{outcome-associations}{%
-\subsubsection{Outcome Associations}\label{outcome-associations}}
+\subsubsection{Outcome Associations}\label{outcome-associations}
 
@@
 Engagement exhibited non-trivial associations with all three types of perception whereas stress was only associated with the hindrance aggregate.
-The more percieved hindrances, the higher the rating of stress, indicating only weak partial support for Hypothesis 3b.
+The more percieved hindrances, the higher the rating of stress (\(r\)=.11, \(p\)\textless.01), indicating only weak partial support for Hypothesis 3b.
 All subsequent analyses retain this ``overall'' operationalization of workers' experience of resources, challenges, and hindrances.
 
-\hypertarget{challenges-resources-and-job-outcomes}{%
-\subsubsection{Challenges, Resources, and Job Outcomes}\label{challenges-resources-and-job-outcomes}}
+\subsubsection{Challenges, Resources, and Job Outcomes}\label{challenges-resources-and-job-outcomes}
 
@@
 Regarding Hypothesis 4a, challenge demands and resources did not explain a significant amount of the variance in stress, \(R^2\) = 0.01, Adj.
-\(R^2\) = 0, \(F(2, 565) = 1.67\), \(p = .189\).
+\(R^2\) = 0.00, \(F(2, 565) = 1.67\), \(p = .189\).
 The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 1.17\), \(p = .320\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 0.17, and thus does not support the presence of moderation.
@@
 
-\hypertarget{hindrances-resources-and-job-outcomes}{%
-\subsubsection{Hindrances, Resources, and Job Outcomes}\label{hindrances-resources-and-job-outcomes}}
+\subsubsection{Hindrances, Resources, and Job Outcomes}\label{hindrances-resources-and-job-outcomes}
 
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\section{Discussion}\label{discussion}
 
-The major aims of this paper were to explore whether: 1) there was variability in subjective ratings of job characteristics as resources and demands, 2) some characteristics were more likely to vary across demand and resource, 3) subjective appraisals were differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and outcomes.
+The major aims of this paper were to explore whether: 1) there was variability in subjective ratings of job characteristics as resources and demands, 2) subjective appraisals were differentially related to positive and negative outcomes, and lastly, 3) if resources buffer the relationships between demands (challenge and hindrance) and outcomes.
 We found that job characteristics were not uniquely categorized as a resource or demand, but rather, job characteristics were often viewed similarly as both a resource and a challenging demand.
@@
 Related to that, we intentionally worked within the O*NET database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources and demands.
-Therefore, to the extent that O*NET is not an exhaustive repository, there are existing characteristics that we did not capture.
-For example, O*NET also includes styles and values, which we did not sample.
-Future studies may want to expand to explore these additional aspects of work.
+Therefore, to the extent that O*NET is not an exhaustive repository, there are existing characteristics that were not captured.
+Future studies may want to expand to explore additional aspects of work.
 
-Hindrances exhibit greater variability, but a visual scan of the items reveals some with heavy physicality content (see, for example \ref{fig:combinegraphs2}), perhaps reflecting some artificiality (for example, indicating ``not terribly hindering'' if the physical demand was not commonplace).
+Hindrances exhibit greater variability, but a visual scan of the items reveals some with heavy physicality content (see, for example Figure \ref{fig:combinegraphs2}), perhaps reflecting some artificiality (for example, indicating ``not terribly hindering'' if the physical demand was not commonplace).
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\newpage
+
+\section{References}\label{references}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
+\bibitem[\citeproctext]{ref-bakker2013weekly}
 Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.
 
-\leavevmode\vadjust pre{\hypertarget{ref-burr2019third}{}}%
+\bibitem[\citeproctext]{ref-burr2019third}
 Burr, H., Berthelsen, H., Moncada, S., Nübling, M., Dupret, E., Demiral, Y., Oudyk, J., Kristensen, T.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-campbell1959convergent}{}}%
+\bibitem[\citeproctext]{ref-campbell1959convergent}
 Campbell, D. T., \& Fiske, D. W. (1959). Convergent and discriminant validation by the multitrait-multimethod matrix. \emph{Psychological Bulletin}, \emph{56}(2), 81--105.
 
-\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
+\bibitem[\citeproctext]{ref-cavanaugh2000empirical}
 Cavanaugh, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-cronbach1951coefficient}{}}%
+\bibitem[\citeproctext]{ref-cronbach1951coefficient}
 Cronbach, L. J. (1951). Coefficient alpha and the internal structure of tests. \emph{Psychometrika}, \emph{16}(3), 297--334.
 
-\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
+\bibitem[\citeproctext]{ref-demerouti2001job}
 Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.
 
-\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
+\bibitem[\citeproctext]{ref-gerich2017relevance}
 Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.
 
-\leavevmode\vadjust pre{\hypertarget{ref-hakanen2008job}{}}%
+\bibitem[\citeproctext]{ref-hakanen2008job}
 Hakanen, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-kubicek2023all}{}}%
+\bibitem[\citeproctext]{ref-kubicek2023all}
 Kubicek, B., Uhlig, L., Hülsheger, U.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-schaufeli2017applying}{}}%
+\bibitem[\citeproctext]{ref-schaufeli2017applying}
 Schaufeli, W. B. (2017). Applying the job demands-resources model: A `how to'guide to measuring and tackling work engagement and burnout. \emph{Organizational Dynamics}, \emph{46}(2), 120--132.
 
-\leavevmode\vadjust pre{\hypertarget{ref-searle2015merits}{}}%
+\bibitem[\citeproctext]{ref-searle2015merits}
 Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.
 
-\leavevmode\vadjust pre{\hypertarget{ref-webster2010toward}{}}%
+\bibitem[\citeproctext]{ref-webster2010toward}
 Webster, J.
